### 2022-05-25 SFE-report/Forward_sensitivity_analysis_of_SFE_Sliczniuk.tex
25.02

% ---------------------------------------------------------------
% Preamble
% ---------------------------------------------------------------
%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}
\documentclass[a4paper,fleqn]{cas-dc}
%\documentclass[a4paper]{cas-dc}
%\documentclass[a4paper]{cas-sc}
% ---------------------------------------------------------------

% -------------------------------------------------------------------- 
% Packages
% --------------------------------------------------------------------
% Figure packages
\usepackage{float}
\usepackage{adjustbox}
% Text, input, formatting, and language-related packages
\usepackage[T1]{fontenc}
\usepackage{subcaption}
% \usepackage[utf8]{inputenc}
% \usepackage[nomath]{lmodern}

% Margin and formatting specifications
%\usepackage[authoryear]{natbib}
\usepackage[sort]{natbib}
\setcitestyle{square,numbers}

 %\bibliographystyle{cas-model2-names}

\usepackage{setspace}

% \usepackage[authoryear,longnamesfirst]{natbib}

% Math packages
\usepackage{amsmath, amsthm, amssymb, amsfonts, bm, nccmath, mathdots, mathtools, bigints, ulem}

% --------------------------------------------------------------------
% Packages Configurations
% --------------------------------------------------------------------
% (General) General configurations and fixes
\AtBeginDocument{\setlength{\FullWidth}{\textwidth}}	% Solves els-cas caption positioning issue
\setlength{\parindent}{20pt}
%\doublespacing
% --------------------------------------------------------------------
% Other Definitions
% --------------------------------------------------------------------

% --------------------------------------------------------------------
% Environments
% --------------------------------------------------------------------
% ...

% --------------------------------------------------------------------
% Commands
% --------------------------------------------------------------------

% ==============================================================
% ========================== DOCUMENT ==========================
% ==============================================================
\begin{document} 
%  --------------------------------------------------------------------

% ===================================================
% METADATA
% ===================================================
\title[mode=title]{Parameter estimation}                      
\shorttitle{Forward sensitivity analysis of the supercritical extraction process}

\shortauthors{A, B, C}

\author[1]{Oliwer Sliczniuk*}[orcid=0000-0003-2593-5956]
\ead{oliwer.sliczniuk@aalto.fi}
\cormark[1]
%\credit{a}

\author[1]{Pekka Oinas}[orcid=0000-0002-0183-5558]
%\credit{b}

\author[1]{Francesco Corona}[orcid=0000-0002-3615-1359]
%\credit{c}

\address[1]{Aalto University, School of Chemical Engineering, Espoo, 02150, Finland}
%\address[2]{2}

\cortext[cor1]{Corresponding author}

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output. As an example, the supercritical extraction process is presented. The impact of mass flow rate, pressure, and inlet temperature on the model's output is discussed. The sensitivity analysis results prove that the considered variables can affect the extraction's yield and be used as control variables in optimization problems. Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.

\end{abstract}

\begin{keywords}
Supercritical extraction \sep Parameter estimation \sep Mathematical modelling
\end{keywords}

% ===================================================
% TITLE
% ===================================================
\maketitle

% ===================================================
% Section: Introduction
% ===================================================\section{Introduction}

\section{Introduction}
%{\color{brown}Intro about extraction}\\
The extraction of natural substances from solid materials and liquids with solvents have been a popular subject of research and development in the last years. Supercritical fluids have multiple applications in an extraction process due to the pressure-dependent dissolving power and {\color{blue} both gas-and liquid-like properties (for example fluid-like density and gas-like diffusivity). Among different supercritical fluids, the supercritical $CO_2$ is one of the most popular due to it is nontoxic, non-flammable and non-corrosive properties. The critical point of $CO_2$ is relatively low ($73.8$ bar and $31 ^\circ C$), compare to other fluids. The supercritical extraction with $CO_2$ become attractive alternative, to replace traditional extraction techniques.}

%{\color{brown} Literature review of the models}\\
\sout{The supercritical extraction process is considered unconventional due to the lack of formulation of one general model, properties that strongly depend on working conditions and its unsteady nature. Understanding the physics behind the phenomena and the proper mathematical description is necessary to predict the process outcome. Several extraction models have been developed to characterize different mass transfer mechanisms and equilibrium relationships.}
{\color{blue}The extraction of valuable compounds from fixed bed of biomass can be described by one of many mathematical models as presented by \citet{Huang2012}. The selection the extraction model is not arbitrary and should be based on the knowledge of phenomenons occurring in the operational unit. Each model has its own assumptions and describe different mass transfer mechanisms and equilibrium relationships}.

\citet{Reverchon1996} developed a model, which considers an oil as a single component and assumes that the extraction process is controlled by internal-mass transfer resistance. As a result of these assumptions, the external mass transfer was neglected. The original model of Reverchon does not consider the influence of axial dispersion and does not take into account the change of density and flow rate along the bed.

Based on analogy to heat transfer, \citet{Reverchon1993} suggested a hot ball model, where the extraction process is treated analogously to {\color{blue} a process in which a hot ball is cooled in a uniform medium} \sout{the process of cooling down a hot ball in a uniform medium}. {\color{blue}The hot ball model is used to describe an extraction process from solid particles which contains small quantities of solute so that the solubility is not a limiting factor. }

\citet{Sovova1994} \sout{presented the Broken-and-Intact Cell model, which assumes the presence of two solid phases, the broken and intact cells. The results of applying Sovova's model allow distinguishing three phases of the extraction process (constant extraction rate, falling extraction rate, and diffusion-controlled periods) directly at the modelling stage.}
{\color{blue} presented the Broken-and-Intact Cell model. The BIC model describes a system where the outer surfaces of particles have been mechanically interrupted. The solute from the broken cells is easily accessible for the solvent. The extraction of easily accessible solute is fast and directly controlled by its diffusion and convection in the solvent.
However, the rest of the solute is less accessible because it is closed in the particle's core or intact cells. This solute slowly diffuses through the walls of a cell due to high mass transfer resistance.
In this model, the extraction process is divided into three periods controlled by different mass transfer mechanisms: Constant extraction rate (CER) period, Falling extraction rate (FER) period and Diffusion-controlled (DC) period.}

%{\color{brown}Methodology: sensitivity analysis }\\
As in many engineering problems, mathematical modelling is crucial to mimic real-life objects, but it requires knowing multiple parameter values. One way to better understand the phenomena occurring in the process is to investigate the influences of various parameters on the model's output. One of the methods that can be applied is sensitivity analysis. Among different types of sensitivity analyses, there are two main groups: a local and global sensitivity analysis.
The local method involves taking the total derivative of the output with respect to an input parameter at a single point. The derivative can be estimated directly by the automatic differentiation. {\color{blue}The total derivatives form an additional set of equations that is solved simultaneously with the original system. An alternative approach to the direct method is the Adjoint Sensitivity Analysis method. In this method, the original model is integrated to obtain the full trajectory of the state. Then the adjoint equation is solved backwards in time. The adjoint operates backwards in the sense that it determines a gradient with respect to input from a gradient with respect to output as discussed by \citet{Errico1997}.}
The adjoint method is faster and requires the least memory than the local method. However, not all ODEs are stable under backwards integration. Moreover, both methods belong to one-at-a-time (OAT) methods, as they allow an investigation of the influence of only one parameter at a time. One way to determine the model response to "interactions" between parameters and to observe the non-linear behaviour of the system is to use higher-order derivatives.
An alternative method is to apply a global sensitivity analysis, which utilises information about parameter uncertainty. A sensitivity analysis is considered global when all the parameters vary simultaneously. According to \citet{Razavi2015}, the main problem of generalising local sensitivity measures to represent "global" properties is the lack of a unique definition of global sensitivity. 
\sout{These methods allow selecting the most influential parameters, which can be used for optimisation (the finding is a set of control variables, which requires the least effort to affect a model's output), model reduction (removing the least influential parameters), or parameter fitting. In this work, the example of supercritical extraction is used to show the practical application of sensitivity analysis. Some researchers working with the supercritical fluids extraction process examined the influence of the parameters on the model's output. Most of them perform a parametrisation of the process model and solve it multiple times for different combinations of parameters. The literature review is presented below.}
{\color{blue}A sensitivity analysis is helpful to identify parameters that have the greatest effect on the model's output. The sensitivity analysis results can be used to find regions in the space of input factors for which the model output is maximum. Another application is model reduction - for example, by identifying and removing redundant parts of the model structure. In the case of parameter fitting with a large number of parameters, non-sensitive parameters can be excluded from the fitting procedure, reducing the computational cost. A sensitivity analysis is used to increase understanding of the relationships between input and output variables in a model.

%{\color{brown} Literature review of the sensitivity analysis}\\
\citet{Fiori_2007} presented how a model uncertainty affects a supercritical extraction process. Authors performed a local sensitivity analysis taken at the mean values of the parameters, determined during the parameter estimation. Their analysis shows the importance of two parameters: the particle diameter and the internal mass transfer coefficient. The authors found that the supercritical extraction process is almost completely insensitive during the first phase of the process (controlled by the solute's solubility in the supercritical solvent) for a change of these parameters. However, the authors claim that the model's sensitivity to parameters becomes high during the second phase of the process (controlled by internal diffusion).

\citet{Rabi_2019} analysed how the different parameters affect the model's output. The parameters are dimensionless numbers (e.g., mass transfer Biot, Péclet and Damköhler numbers), which are assumed to take one of few discrete values. The simulations are performed for each value of parameters and compared with each other. The authors found that the Péclet number can strongly affect the extraction efficiency, so the diffusive transport should not be neglected. The authors investigated effect of the Damköhler number on the process. The authors observed that higher intra-particle diffusion accelerated solid particles depletion so that an optimal extraction time can then be looked for. Furthermore, the authors proved that others investigated parameters like partition coefficient and bed porosity influence the extraction yield.

\citet{Glover2008} presented a local sensitivity analysis for an adsorption process. Considering the similarities between extraction and adsorption processes, it is interesting to see how the same technique can be applied to different cases. The authors examine the sensitivity of the breakthrough of adsorption beds to system parameters. The impact of mass and energy transfer effects and adsorbent layer thicknesses are determined by calculating the derivatives of the outlet concentration and outlet temperature. The authors applied a Newton-based method along with the sensitivities to determine the optimal layering of an adsorption bed.}

%{\color{brown} Summary of the manuscript}\\
\sout{In this work, the process model represents supercritical extraction and consists of a set partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables. The process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.The impact of mass flow rate, pressure, and inlet temperature on the model's output is analyzed. In this work, the sensitivity analysis results are used to prove if the considered variables affect the extraction process and can be used as decision variables in optimization problems. The novelty is the application of the local sensitivity analysis in the case of supercritical extraction.}
{\color{blue}In this work, a distributed-parameter model, based on \citet{Reverchon1996} and \citet{Vargas2006}, is used to describe a fluid-solid extraction process of 'carqueja' oil from 'Baccharis Trimera' leaves with $CO_2$ as a solvent. The process model consists of three partial differential equations: two mass balance equations and one heat balance equation. To enhance understanding of the process model, the local sensitivity analysis is used to investigate the effect of parameters on the model's output. The presented sensitivity analysis results are restricted to parameters related to operating conditions only. Furthermore, the sensitivity analysis is used to prove which of the analysed variables can be used as decision variables in optimisation problems.}

\section{Materials and methods} \label{CH: Materials and methods}
\sout{The extraction process is assumed to operate in a semi-continuous mode in a cylindrical vessel. The solvent is firstly brought to super-critical condition, pumped through a fixed-bed, of finely chopped biomass, where the solute is extracted from the biomass. Then, the solvent and solute from the extractor are separated in a flush drum, and the extract is collected. The flow rate ($F_{in}$) and inlet temperature ($T_{in}$) of the extractor’s feed can be measured and manipulated. The pressure ($P$) in the vessel can be measured and manipulated, while the outlet temperature ($T_{out}$) can only be measured. A simplified flow diagram is depicted in Figure \ref{fig: SFE_drawing} }.

{\color{blue}The solid-fluid extraction process is assumed to operate in a semi-continuous mode in a cylindrical vessel. In the extractor, essential oils are removed from biomass (for example, carqueja seeds) by supercritical carbon dioxide. As the solvent flows continuously through the bed of porous particles, the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles. Then the solute dissolves and diffuses into the solvent in the pores and eventually into the bulk. The solvent-solute mixture leaves the extractor and undergoes depressurization. The $CO_2$ is released to a gaseous state, and the solute precipitates. In the vapour-liquid separator, the gaseous solvent is vent off while the precipitated product is collected.

In Figure \ref{fig: SFE_drawing}, an instrumental set-up is presented. The flow rate ($F_{in}$) and the temperature ($T_{in}$) of the solvent entering the extractor are measured and can be adjusted using a pump and a heat exchanger, respectively. Moreover, the extractor's pressure ($P$) is assumed to be measurable and adjustable using a back-pressure regulator valve. In addition, the temperature of the outlet stream $T_{out}$ and the temperature profile of the fixed-bed can be measured. }

\begin{figure}[h]
	\centering
	\includegraphics[trim = 6cm 7.5cm 8cm 6cm, clip, width=\linewidth]{Figures/SFE_PFD.pdf}
	\caption{Process flow diagram for solid-fluid extraction process}
	\label{fig: SFE_drawing}
\end{figure}

\subsection{Extraction model} \label{CH: Extraction_model}

\sout{The main components of the model are three one-dimensional differential equations related to mass balances (solid and fluid phase) and heat balance. As in all batch processes, our system has only one steady state. The steady-state occurs only if the solute is entirely taken out of the biomass.

The extraction from a fixed bed is an unsteady process, implying that the solute concentrations in the solid and solvent phases vary over time and space. The convection and the diffusion of the mass and the heat are considered only in the axial direction. The radial distribution of such properties like a velocity is assumed to be flat in that direction. The assumption of the flat velocity profile allows considering a lack of back mixing. The pressure drop in the bed is assumed to be assumed to negligible. Under such conditions, the fluid flow can be considered a plug flow.

Since the solute is assumed to be a single pseudo-component, there is only one mass balance equation for each phase (Eq. s \ref{Model_fluid} and \ref{Model_solid}). On the other hand, there is only one heat balance (Eq.  \ref{Model_heat}) because the presence of a single pseudo-phase is assumed.

Moreover, the process model does not consider the change of particle size or the void fraction during the process. The particles are assumed to be uniformly distributed along the bed and to have the same size.}

{\color{blue}A distributed-parameter model, based on \citet{Reverchon1996}, is used to describe the solid-fluid extraction process. The process model consists of three partial differential equations: two mass balance equations relative to the concentration of solute in the fixed solid phase and the mobile fluid phase, and the heat balance equation relative to the temperature of the fluid phase. The amount of solute in the solvent is considered negligible. Therefore, the fluid phase can be described as pseudo-homogenous, and its properties are assumed to be the same as the solvent.

The movement of the mobile pseudo-homogeneous phase (Eq. \ref{Model_fluid}) is considered only in the axial direction. The properties of the system in the radial direction is assumed to be uniform. In addition, it is considered that the boundary layer adjacent to the inner wall of the extractor does not exist. Therefore, the velocity profile is constant across any cross-section of the extractor perpendicular to the axial direction. As a result, the plug flow model can be introduced. The particle size distribution and the void fraction of the solid phase are assumed to be uniform in space and remain constant in time. Moreover, the pressure is considered to be constant along the fixed bed. The mass balance for the fluid phase consists of convection, diffusion, and kinetic terms.

Considering the solid phase to be fixed, the convection and diffusion terms in the corresponding mass balance are both assumed to be negligible or absent. Therefore, the mass balance for the solid phase (Eq. \ref{Model_solid}) consists of the kinetic term only.

As for the mass transfer from the solid to the fluid phase, a kinetic term based on two-film theory for the solute is considered. The mass transfer kinetic (Eq. \ref{Model_kinetic_basic}) consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process. A single pseudo-component is used to represent the extract collectively.

The heat balance (Eq. \ref{Model_heat}) consists of the convective and diffusive terms. It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases. We consider no heat loss through the wall, and there is no heat generation in the system. Therefore, the temperature of the extractor can be changed only by manipulating the temperature of the inlet stream $T_{In}(t)$.
}

For the sake of clarity of the process model, different colors have been used in the equations to indicate: 
{\color{red}control variables},
{\color{blue}state variables},
{\color{orange}variables} and
{\color{magenta}parameters}.

\subsubsection{Mass balance for the fluid phase} \label{CH: Mass_balance_fluid}
The fluid phase is a mobile phase, which means that the fluids mass balance (Eq. \ref{Model_fluid}) is made of convection, diffusion, and mass transfer kinetic terms.

{\footnotesize
		\begin{align} 
			\label{Model_fluid}
			\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t} &	=  \underbrace{-\cfrac{1}{ {\color{magenta}\varepsilon A}}\cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]} \cfrac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} \\
			&+ \underbrace{ {\color{orange}D^M_e}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] \cfrac{\partial^2 {\color{blue}c_f}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusive term}} 
			+ \underbrace{ \cfrac{1-{\color{magenta}\varepsilon}}{{\color{magenta}\varepsilon}} {\color{blue}r_e}(t,z) }_{\text{Kinetic term}} 
		\end{align} }

where ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z), {\color{blue}T}(t,z)$ correspond to concentration of solute in the fluid phase, concentration of solute in the solid phase and the temperature, respectively. ${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term. ${\color{red}F}(t)$ is the mass flow rate, ${\color{red}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{magenta}A}$ is the extractor’s cross section, ${\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient.

\subsubsection{Mass balance for the solid phase} \label{Mass_balance_solid}
The solid phase is a stationary phase, which indicates a lack of convection and diffusion terms in the mass balance (Eq.  \ref{Model_solid}). Therefore, the only term present in this equation is the kinetic term (defined as presented in equation \ref{Model_kinetic_basic}), which links solid and fluid phases.

{\footnotesize
		\begin{equation} 
			\label{Model_solid}
			%		{\scriptsize\begin{align*}
			\cfrac{\partial {\color{blue}c_s}(t,z)}{\partial t} = \underbrace{ {\color{blue}r_e}(t,z) }_{\text{Kinetics}}
		\end{equation} }

\subsubsection{Kinetic term} \label{CH: Kinetic}
As the solvent flows through the bed, \sout{it forms a film around the porous solid particle and occupies its pores.} {\color{blue}the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to for an external fluid film around the solid particles through the solvent–solid matrix interactions. Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected. In this work, the molecular diffusion is assumed.}. The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk. The graphical representation of the mass transfer mechanism is shown in Figure \ref{fig: SFE_Mechanism}. The mean solute concentration in the solid phase is denoted as ${\color{blue}c_s}$. At the solid-fluid interface, the equilibrium concentrations are given as ${\color{blue}c_s^*}$ and ${\color{blue}c_P^*}$, respectively for solid and fluid phases. The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{blue}c_{P}}$. As the solute diffuses through the pore, its concentration changes and reaches ${\color{blue}c_{Pf}}$ at \sout{the end} {\color{blue}the opening} of the pore. The solute diffuses through the film around the particle and reaches a concentration in the bulk ${\color{blue}c_f}$. It can be assumed that the two-film theory describes the solid-fluid interface inside the pore. The overall mass transfer coefficient can be introduced if the relation between the solute concentration in one phase and its equilibrium concentration is known.

\begin{figure}[h!]
	\centering
%	\includegraphics[trim  = 6cm 0cm 3cm 0cm,clip,width=\linewidth]{Figures/SFE_draft.png}
	\includegraphics[trim = 5.8cm 1.1cm 6cm 0.8cm,clip,width=1.0\linewidth]{Figures/SFE_draft.pdf}	
	\caption{The extraction mechanism}
	\label{fig: SFE_Mechanism}
\end{figure}

\citet{Bulley1984} suggest a process where the driving force for extraction is given by the difference between concentration of the solute in the bulk, ${\color{blue}c_f}$, and in the centre of the pore, ${\color{blue}c_P^*}$. The concentration ${\color{blue}c_P^*}$ is in equilibrium with ${\color{blue}c_s}$ according to an equilibrium relationship. The rate of extraction is thus ${\color{blue}r_\text{e}}\left({\color{blue}c_f} - {\color{blue}c^*_P}({\color{blue}c_s})\right)$.

On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between ${\color{blue}c_s}$ and ${\color{blue}c_P^*}$. ${\color{blue}c_P^*}$ is determined by an equilibrium relationship with ${\color{blue}c_f}$ and the extraction rate is ${\color{blue}r_\text{e}}\left({\color{blue}c_s} - {\color{blue}c^*_P}({\color{blue}c_f})\right)$.

\sout{The kinetic term, denoted as equation \ref{Model_kinetic_basic}, corresponds to a solute transfer rate between both phases. This term is made of the overall diffusion coefficient and the concentration gradient (between one phase and its equilibrium concentration), which acts as a driving force for the process.} {\color{blue}The mass transfer kinetic (Eq. \ref{Model_kinetic_basic}) describes a diffusion rate of the solute from solid particles to the solvent. The kinetic term consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.} Based on the work of \citet{Bulley1984}, \citet{Reverchon1996} proposed to define the kinetic terms as

{\footnotesize
\begin{equation} \label{Model_kinetic_basic}
	{\color{blue}r_e}(t,z) = \cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}q}(t,z) - {\color{blue}q^*}(t,z) \right)
\end{equation} }

where ${\color{orange}D_i}({\color{blue}T}(t,z))$ corresponds to the overall diffusion coefficient and ${\color{blue}q^*}(t,z)$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase). ${\color{blue}q^*}(t,z)$ can be calculated based on the equilibrium relationship (Eq.  \ref{Linear_equilibirum}).

\sout{The kinetic term of the model takes into account the properties of the biomass like a sphericity (through the shape coefficient ${\color{magenta}\mu}$ equal to $1/3$ for slabs and $3/5$ for spheres), a characteristic dimension of particles (through the parameter ${\color{magenta}l} = {\color{magenta}r}/3$ where ${\color{magenta}r}$ is the mean particle radius), and the solid density ${\color{magenta}\rho_s}$. The fixed bed is characterized by a void fraction ${\color{magenta}\epsilon}$. }

{\color{blue} The kinetic term of the model takes into account properties of the solid particles like a sphericity (through the shape coefficient ${\color{magenta}\mu}$), a characteristic dimension of particles (through the parameter ${\color{magenta}l} = {\color{magenta}r}/3$ where ${\color{magenta}r}$ is the mean particle radius), and the bulk density ${\color{magenta}\rho_s}$. The fixed bed is characterized by a void fraction ${\color{magenta}\epsilon}$. }

According to \citet{Bulley1984}, a linear equilibrium relationship (Eq.  \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{blue}c_f^*}(t,z)$ is based on concentration of the solute in the solid phase ${\color{blue}c_s}(t,z)$

{\footnotesize
\begin{align} \label{Linear_equilibirum}
	{\color{blue}c}(t,z) &= {\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t)) \allowbreak {\color{blue}q^*}(t,z)
\end{align} }

The volumetric partition coefficient ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase. \sout{ The ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$ according to $\citet{Spiro2007}$ .}
{\color{blue} According to \citet{Spiro2007}, the term ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as the function of mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$ }

{\footnotesize
\begin{align}
	{\color{orange}k_m}({\color{blue}T}(t,z)) = \cfrac{{\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{magenta}\rho_s}}{{\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}
\end{align} }

Equation \ref{Model_kinetic} is the full representation of the kinetic term.

{\footnotesize
	\begin{align}
		\label{Model_kinetic}
		{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}q}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c}(t,z) \right)
\end{align} }

\subsubsection{Heat balance} \label{CH: heat_balance}
\sout{The heat balance equation (Eq.  \ref{Model_heat}) was developed, assuming the existence of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases (the amount of solute is considered small enough not to affect the overall heat balance). Equation \ref{Model_heat} contains the convection and the diffusion terms. It is considered that there is no heat loss through the wall, and there is no heat generation in the system. The temperature of the extractor can be changed only by increasing the temperature of the inlet stream. The pseudo-homogenous phase is assumed to flow only in the axial direction. 
The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ because the solid phase is stationary. Therefore, this factor can be understood as the fraction of the fluid's total heat through convection. On the other hand, the axial heat diffusion is calculated based on the definition of thermal diffusivity for the fluid, as explained in the appendix. }

{\color{blue} The heat balance (Eq. \ref{Model_heat}), is based on \citet{Srinivasan2012}, and consists of convective and diffusive terms. It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases. It is considered that there is no heat loss through the walls, and there is no heat generation in the system. The temperature of the extractor can be changed only by manipulating the temperature of the inlet stream ${\color{red}T_{Inlet}}(t)$.
	}

{\footnotesize
	\begin{equation} \label{Model_heat}
		\begin{split}
			\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} &= 
			\underbrace{ -\cfrac{{\color{red}F}(t) {\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))}{{\color{magenta}A} 	[(1-{\color{magenta}\epsilon}){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{orange}C_p} ({\color{blue}T}(t,z),{\color{red}P}(t)) + {\color{magenta} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}}  }_{\text{Convection}} + \\
			& + \underbrace{ {\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{red}P}(t)) \cfrac{\partial^2 {\color{blue}T}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusion}}
		\end{split}
	\end{equation} }

where $ {\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient, ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's specific heat, ${\color{magenta}C_{ps}}$ is the specific heat of the solid phase, ${\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial heat diffusion coefficient.

\subsubsection{Extraction yield} \label{CH: Yield}
\sout{The efficiency of the process (the yield) is calculated according to equation \ref{Model_measurment}. The yield is defined as the ratio between a difference of initial solute's mass in the solid phase ${\color{magenta}m_0}$, and an actual amount of solute in the same phase ${\color{blue}m}$, compared to the initial amount of the solute in the fixed bed ${\color{magenta}m_0}$. The yield can also be calculated based on the change of solutes concentration in the solid phase if the volume of the extractor ${\color{magenta}V}$ is constant.
An output function ${\color{blue}y}(t)$ returns a yield curve that represents the fraction of the solute's mass over time. The yield is obtained by function ${\color{blue}g}({\color{blue}q}(t,z))$. Function ${\color{blue}g}({\color{blue}q}(t,z))$ corresponds to a 'measurement device' that allows to calculate the yield based on the state variable ${\color{blue}q}(t,z)$. }
{\color{blue}The efficiency of the process (the yield) is calculated according to Eq. \ref{Model_measurment}, and is based on the change of solute's mass in the solid phase. It is defined as ratio the ratio between the difference of its initial value ${\color{magenta}m_0}$ and the actual value ${\color{blue}m}(t,z)$, compared to the initial one. The yield can also be calculated based on the change of solutes concentration in the solid phase if the volume of the extractor ${\color{magenta}V}$ is constant.}

{\footnotesize
	\begin{align} 
		\label{Model_measurment}
		{\color{blue}y}(t) ={\color{blue}g}({\color{blue}q}(t,z)) &= \cfrac{ \left({\color{magenta}m_0} - {\color{blue}m}({\color{blue}q}(t,z)) \right) }{{\color{magenta}m_0}} = \cfrac{ {\color{magenta}V} \left({\color{magenta}q_0} - {\color{blue}q}(t,z) \right) }{{\color{magenta}V q_0}} 
	\end{align}	}

\sout{where ${\color{blue}q}(t,z)$ is concentration of solute in a solid phase and a temperature, respectively. ${\color{magenta}m_0}$ is a initial mass of the solute in the solid phase, ${\color{magenta}q_0}$ is a  initial concentration of the solute in the solid phase, ${\color{magenta}V}$ is an extractor volume.}

\subsubsection{Dependencies} \label{CH: Dependencies}
{\color{blue}The Peng-Robinson equation of state is used to describe the thermodynamics of the fluid phase. The thermal properties of the pseudo-homogeneous phase are assumed to vary along the extractor, though always remaining equal to the corresponding mean values between the fluid and solid phase. }

In the process model, properties of the supercritical fluid such as the density ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$, the specific heat ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$, the thermal conductivity ${\color{orange}k^T}({\color{blue}T}(t,z),{\color{red}P}(t))$, or the viscosity ${\color{orange}\eta}({\color{blue}T}(t,z),{\color{red}P}(t))$ are calculated based on the local temperatures along the fixed bed and the pressure. The Peng-Robinson equation of state is used to find values of a ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$ and ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$.

The inter-particle diffusion coefficient ${\color{orange}D^M_e}(\allowbreak{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is calculated from the empirical correlation, as the function of the Reynolds number ${\color{orange}R_e}({\color{blue}T}(t,z),{\color{red}P}(t),\allowbreak{\color{red}F}(t))$ and the Peclet's number ${\color{orange}P_e}({\color{blue}T}(t,z),\allowbreak{\color{red}P}(t),{\color{red}F}(t))$.
The values of the internal diffusion ${\color{orange}D_i} ({\color{blue}T}(t,z))$ and the partition coefficient ${\color{orange}k_m} ({\color{blue}T}(t,z))$ come from the laboratory experiments. The expressions and the detailed information of the parameter fitting can be found in the appendix.

\subsubsection{State-space representation} \label{CH: State_space}
It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}q_0}$. Moreover, it is considered that the initial temperature of the extractor in every place is equal to ${\color{magenta}T_0}$. Therefore, the initial conditions employed in the simulation are:

{\footnotesize
\begin{subequations}
	\begin{align*}
		{\color{blue}c}(t = 0, z) &= 0   \\
		{\color{blue}q}(t = 0, z) &= {\color{magenta}q_0} \\
		{\color{blue}T}(t = 0, z) &= {\color{magenta}T_0}
	\end{align*}
\end{subequations} }

The process model can be written in a general form:

{\footnotesize
\begin{align}
	\begin{bmatrix}
		\cfrac{\partial {\color{blue}c}(t,z)}{\partial t}\\
		\cfrac{\partial {\color{blue}q}(t,z)}{\partial t}\\
		\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} 
	\end{bmatrix}
	& =
	\begin{bmatrix}
		{\color{blue}\phi_1} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)\\
		{\color{blue}\phi_2} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)\\
		{\color{blue}\phi_3} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)
	\end{bmatrix} = {\color{blue}\phi} \left( t,z; {\color{magenta}\theta} \right) = \cfrac{\partial {\color{blue}\chi}(t,z)}{\partial t}
\end{align} }

where ${\color{magenta}\theta}$ is a set of parameters present in the model, ${\color{blue}\phi}$ is a set of functions that correspond to state equations of the model, and ${\color{blue}\chi}$ is the state-space model.

The method of lines is used to transform the process model equations into a set of ODEs denoted as ${\color{blue}G}({\color{blue}x}(t);{\color{magenta}p})$. The partial derivatives in $z$-direction are computed using a first-order and second-order finite difference approximation. The backward finite difference is used to approximate first-order derivative, while the central difference scheme is used to approximate second-order derivative. The length of the fixed bed is divided into $N_z$ equally distributed points in $z$-direction. Each function ${\color{blue}\phi_i}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{blue}G}_{i\times N_z+1}$ to ${\color{blue}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation. The state-space model ${\color{blue}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{blue}x}}(t)$ (Eq.  \ref{discretization}).

{\footnotesize
\begin{align*} \label{discretization}
	\dot{{\color{blue}x}}(t) &= \cfrac{d {\color{blue}x}(t)}{d t} = 
	\begin{bmatrix}
		\cfrac{d {\color{blue}c_{f,1}}(t)}{d t} 	  \\
		\vdots					  \\
		\cfrac{d {\color{blue}c_{f,N_z}}(t)}{d t} \\
		\\ \hline \\
		\cfrac{d {\color{blue}c_{s,1}}(t)}{d t} 	  \\
		\vdots					  \\
		\cfrac{d {\color{blue}c_{s,N_z}}(t)}{d t} \\
		\\ \hline \\
		\cfrac{d {\color{blue}T_1}(t)}{d t} 	  \\
		\vdots 					  \\
		\cfrac{d {\color{blue}T_{N_z}}(t)}{d t}
	\end{bmatrix}
	=
	\underbrace{\begin{bmatrix}
			{\color{blue}G_1} \left( {\color{blue}x}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
			\vdots\\ 
			{\color{blue}G_{N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
			\\ \hline \\ \\
			{\color{blue}G_{N_z+1}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
			\vdots\\
			{\color{blue}G_{2N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
			\\ \\ \hline \\ 
			{\color{blue}G_{2N_z+1}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right) \\
			\vdots\\
			{\color{blue}G_{3N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)
	\end{bmatrix}}_{{\color{blue}G} \left( {\color{blue}x}(t); {\color{magenta}p} \right)} 
\end{align*} }

where ${\color{blue}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{magenta}p} \in \mathbb{R}^{N_p =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of model parameters, $N_{u}$ is the number of control variables.

{\color{blue} In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases ($c(t,z)$ and $q(t,z)$, respectively), and the local temperature of the pseudo-homogeneous phase ($T(t,z)$). The controllable input variables are the mass flow-rate and temperature of the solvent in the feed ($F_\text{in}(t) = F(t)$ and $T_\text{in}(t) = T(t,z=0)$, respectively) and the pressure in the extractor ($P(t,z) = P(t)$). {\color{red}We also assume that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator ($Y(t)$).} The system is controllable by manipulating the flow-rate and temperature of CO2 in the feed, and the pressure in the extractor. }

\newpage
\section{Parameter estimation} \label{CH: Parameter_estimation}
Estimation theory is a branch of statistics that deals with estimating the values of parameters based on measured empirical data that has a random component. The parameters describe an underlying physical setting in such a way that their value affects the distribution of the measured data. An estimator attempts to approximate the unknown parameters using the measurements.

For a given model, several statistical "ingredients" are needed so the estimator can be implemented. The first is a statistical sample – a set of data points taken from a random vector (RV) of size $N$. Let denote a statistical sample as $x$ and parameters whose vales are to be estimated as $\theta$. Both can be written into a vector form:
\begin{align}
	x &= [x[0], x[1], \dots, x[N-1] ]^T, &&x \in \mathbb{R}^N \\
	\theta &= [\theta_0, \theta_1, \dots, \theta_M ]^T,  &&\theta \in \mathbb{R}^M
\end{align}

where $N$ is the number of samples and $M$ is the number of parameter to estimation.

The continuous probability density function (pdf) or its discrete counterpart, the probability mass function (pmf), of the underlying distribution that generated the data must be stated conditional on the values of the parameters: $p(x|\theta)$. It is also possible for the parameters themselves to have a probability distribution (e.g., Bayesian statistics). It is then necessary to define the Bayesian probability $\pi(\theta)$. After the model is formed, the goal is to estimate the parameters, with the estimates commonly denoted $\hat{\theta}$.

One common estimator is the minimum mean squared error (MMSE) estimator, which utilizes the error between the estimated parameters and the actual value of the parameters as the basis for optimality. This error term is then squared and the expected value of this squared value is minimized for the MMSE estimator.

\subsection{Bayes theorem} \label{CH: Bayes_theorem}
In probability theory and statistics, Bayes' theorem (alternatively Bayes' law or Bayes' rule; recently Bayes–Price theorem[1]: 44, 45, 46 and 67 ), named after Thomas Bayes, describes the probability of an event, based on prior knowledge of conditions that might be related to the event.[2] For example, if the risk of developing health problems is known to increase with age, Bayes' theorem allows the risk to an individual of a known age to be assessed more accurately (by conditioning it on their age) than simply assuming that the individual is typical of the population as a whole.

One of the many applications of Bayes' theorem is Bayesian inference, a particular approach to statistical inference. When applied, the probabilities involved in the theorem may have different probability interpretations. With Bayesian probability interpretation, the theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence. Bayesian inference is fundamental to Bayesian statistics.

\subsection{Maximum likelihood estimation} \label{CH: MLE}
\subsection{Maximum a posteriori} \label{CH: MAP}
\subsection{Bayesian inference} \label{CH: Bayesian_inference}

\section{Results} \label{CH: Results}

\section{Conclusions}

% ===================================================
% Bibliography
% ===================================================
%% Loading bibliography style file
\clearpage
%\bibliographystyle{model1-num-names}
\bibliographystyle{unsrtnat}
\bibliography{mybibfile}

\clearpage \appendix \label{appendix}
\section{Appendix}

\newpage
\begin{table*}[p]
		\caption{Notation}
		\label{tab::symbols}
		\begin{tabular}{ |c|l|c| } 
			\hline
			Symbol 		& 	Description 							& Unit 						\\ \hline
			$A$			&	cross-section							& $m^2$ 					\\ \hline
			$c$			&	concentration in fluid phase			& $kg ~ m^{-3}$				\\ \hline
			$Cp$		&	specific heat of the fluid				& $J ~ mol^{-1} ~ K^{-1}$ 	\\ \hline
			$Cp_s$		&	specific heat of the solid				& $J ~ mol^{-1} ~ K^{-1}$ 	\\ \hline
			$D_e^M$		&	axial mass diffusion coefficient		& $m^2 ~ s^{-1}$			\\ \hline
			$D_e^T$		&	axial heat diffusion coefficient		& $m^2 ~ s^{-1}$			\\ \hline
			$Di$		&	internal diffusion coefficient			& $m^2 ~ s^{-1}$			\\ \hline
			$dp$		&	particle diameter						& $m$						\\ \hline
			$F(t)$		&	mass flow-rate							& $kg ~ s^{-1}$				\\ \hline
			$km$		&	partition coefficient					& $[-]$						\\ \hline
			$k^T$		&	thermal conductivity					& $W ~ m^{-1} ~ K^{-1}$		\\ \hline
			$l$			&	characteristic dimension				& $m$						\\ \hline
			$L$			&	total length of the bed					& $m$						\\ \hline
			$m$			&	mass of the oil in solid phase			& $kg$						\\ \hline
			$m_0$		&	initial mass of the oil in solid phase	& $kg$						\\ \hline
			$M_{CO_2}$	&	molecular mass of CO2					& $mol ~ kg^{-1}$			\\ \hline
			$Np$		&	number of model parameters and control variables & $[-]$			\\ \hline
			$N_{\theta}$&	number of model parameters				& $[-]$						\\ \hline
			$Nu$		&	number of control variables				& $[-]$						\\ \hline
			$Nz$		&	number of grid points in z-direction	& $[-]$						\\ \hline
			$p$			&	vector of model parameters and control variables	& $[-]$			\\ \hline
			$P(t)$		&	pressure								& $bar$						\\ \hline
			$Pe$		&	Peclet's number							& $[-]$						\\ \hline
			$q$			&	concentration in solid phase			& $kg ~ m^{-3}$				\\ \hline
			$R$			&	gas constant							& $J ~ K^{-1} ~ mol^{-1}$	\\ \hline
			$Re$		&	Reynolds number							& $[-]$						\\ \hline
			$t$			&	time									& $s$						\\ \hline
			$T$			&	temperature								& $K$						\\ \hline
			$T_0$		&	initial temperature						& $K$						\\ \hline
			$V$			&	volume of the extractor					& $m^3$						\\ \hline
			$y$			&	yield	 								& $[-]$						\\ \hline
			$z$			&	length									& $m$						\\ \hline
			$Z$			&	compressibility	factor					& $[-]$						\\ \hline
			$\epsilon$	&	void fraction							& $[-]$						\\ \hline
			$\rho$		&	density of the fluid					& $kg ~ m^{-3}$				\\ \hline
			$\rho_s$	&	solid density							& $kg ~ m^{-3}$				\\ \hline
			$\mu$		&	shape coefficient						& $[-]$						\\ \hline
			$\theta$	&	vector of model parameters				& $[-]$						\\ \hline
			$\eta$		&	viscosity								& $cP$						\\ \hline				
						& 											&							\\ \hline			
		 	Subscript	& 											&							\\ \hline
			$0$			&	initial conditions						& $[-]$						\\ \hline
			$^*$		&	equilibrium conditions					& $[-]$						\\ \hline							
		\end{tabular}
\end{table*}
\end{document}

### 2022-05-25 SFE-report/Poster/main_2.tex
25.02

\documentclass[17pt, a0paper, portrait, margin=10mm, innermargin=15mm, blockverticalspace=15mm, colspace=15mm, subcolspace=8mm]{tikzposter}
%\documentclass[a0paper,17pt]{tikzposter}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{adjustbox}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{SUtheme}
\usepackage[sort]{natbib}
\usepackage{wrapfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{etoolbox}
\usepackage{ragged2e}

\captionsetup{font=normalsize}

\makeatletter
\newcounter{tablecounter}
\newenvironment{tikztable}[1][]{
	\def \rememberparameter{#1}
	\vspace{10pt}
	\refstepcounter{tablecounter}
	\begin{center}
	}{
		\ifx\rememberparameter\@empty
		\else
		\\[10pt]
		{\small Tab.~\thetablecounter: \rememberparameter}
		\fi
	\end{center}
}
\makeatother

\AtBeginEnvironment{tikzfigure}{\captionsetup{type=figure}}

\setcitestyle{square,numbers}

\usepackage{mwe} % for placeholder images

% set theme parameters
\tikzposterlatexaffectionproofoff
%\usetheme{SUTheme}
\usecolorstyle{SUStyle}
\usetheme{Autumn}
%\usecolorstyle[colorPalette=BrownBlueOrange]{Germany}
\usetitlestyle{Filled}

\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

\title{Forward sensitivity analysis of a supercritical extraction process}
\author{Oliwer Sliczniuk, Pekka Oinas, Francesco Corona}
\institute{Aalto University, School of Chemical Engineering}
\titlegraphic{\includegraphics[width=0.06\textwidth]{aalto_logo.png}}

% begin document
\begin{document}
	\maketitle
	\centering
	\begin{columns}
		\column{0.5}

		\block{Introduction}{
				In the supercritical extraction process, a solvent in supercritical conditions is used to separate a solute from solid particles. A distributed-parameter model with three partial differential equations can be used to describe the fluid-solid extraction process. We study the effect of the parameters on the model solution using a forward sensitivity analysis method.
				% The set of additional equations, so called sensitivity equations, is obtained by taking the total derivative of the process model with respect to each parameter. The sensitivity equations are solved simultaneously with the process model. As the results the sensitivity profiles are obtained.
		}

%		\block{Supercritical extraction}{

%			\begin{minipage}[c]{0.35\linewidth}		
%			The representation of an extractor bed and mass transfer mechanism are shown in figure \ref{SFE_Mechanism}.	\\
%			
%			\begin{itemize} 
%				\item A pre-heated and pressurized solvent (for example $\text{CO}_2$) is pumped through an extractor. 
%				\item The solvent extracts soluble compounds from solid particles as it flows along the fixed bed. 
%				\begin{itemize} 
%					\item The solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
%				\end{itemize}
%				\item The solvent-solute mixture leaves the operational unit and its pumped to the phase separator.
%			\end{itemize}
%			\end{minipage}
%			\hspace{0.5cm}
%			\vrule
%			\hspace{0.5cm}
%			\begin{minipage}[c]{0.60\linewidth}
%			\begin{tikzfigure}
%				\includegraphics[width=0.75\textwidth]{Figures/SFE_draft_cropped.png}
%				\label{SFE_Mechanism}
%			\end{tikzfigure}
%			\captionof{figure}{Schematic representation of the extracting bed} 
%			\vspace{0.5cm}
%			%The solutes' concentration in the solid phase is denoted as ${\color{blue}c_s}$. The equilibrium concentrations of solid and fluid phases are denoted as ${\color{blue}c_s^*}$ and ${\color{blue}c_f^*}$, respectively. The solute concentration in the fluid in the center of the pore is denoted as ${\color{blue}c_{fB}}$, at the end of the pore as ${\color{blue}c_{Bf}}$ and in the bulk as ${\color{blue}c_B}$.
%			\begin{multicols}{3}
%				\begin{itemize}
%					\item[] ${\color{blue}c_s}$ - solutes' concentration in the core of the particle
%					\item[] ${\color{blue}c_s^*}$ - equilibrium concentrations of solid
%					\item[] ${\color{blue}c_f^*}$ - equilibrium concentrations of fluid
%					\item[] ${\color{blue}c_{fB}}$ - solute concentration in the fluid in the center of the pore
%					\item[] ${\color{blue}c_{Bf}}$ - solute concentration in the fluid at the end of the pore
%					\item[] ${\color{blue}c_B}$ - solute concentration in the bulk 
%				\end{itemize}
%			\end{multicols}
%		\end{minipage}

%		}
		\block{Process model}{

			We consider a fluid-solid extraction process model which extends a reference model commonly used in the literature \citep{Reverchon1996}. %The model consists of two mass balance equations related to the concentration of the solute in the fluid and the solid phases, and one heat balance equation related to the pseudo-homogenous phase. 
			\begin{subequations}\begin{align}
					\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t} &	=  \underbrace{-\cfrac{1}{ {\color{magenta}\varepsilon A}}\cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]} \cfrac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} 
					+ \underbrace{ {\color{orange}D^M_e}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] \cfrac{\partial^2 {\color{blue}c_f}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusive term}} 
					+ \underbrace{ \cfrac{1-{\color{magenta}\varepsilon}}{{\color{magenta}\varepsilon}} {\color{blue}r_e}(t,z) }_{\text{Kinetic term}} \label{eq: Model_fluid} \\
					\cfrac{\partial {\color{blue}c_s}(t,z)}{\partial t} &	= \underbrace{ {\color{blue}r_e}(t,z) }_{\text{Kinetic term}} \label{eq: Model_solid} \\
					\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} &	= \underbrace{ -\cfrac{{\color{red}F}(t) {\color{orange}C_p^f}({\color{blue}T}(t,z),{\color{red}P}(t))}{{\color{magenta}A} [(1-{\color{magenta}\varepsilon}){\color{orange}\rho_f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] {\color{orange}C_p^f} \left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] + {\color{magenta}\varepsilon}{\color{magenta}\rho_s}{\color{magenta}C_p^s } ]} \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}}  }_{\text{Convective term}} 
					+ \underbrace{ {\color{orange}D^T_e}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] \cfrac{\partial^2 {\color{blue}T}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusive term}} \label{eq: Heat_balance}
			\end{align}\end{subequations}

	\vspace{1.4cm}

%			where ${\color{blue}c}(t,z)$, ${\color{blue}q}(t,z)$, and ${\color{blue}T}(t,z)$ denote the concentration of solute in the fluid, concentration of solute in the solid, and temperature of the pseudo-homogenous phase at time $t$ and axial position $z$ along the bed, respectively. ${\color{red}F}(t)$ denotes the mass flow-rate along the extractor and ${\color{red}P}(t)$ is the pressure. ${\color{magenta}\epsilon}$ denotes the void fraction of the bed, ${\color{magenta}\rho_s}$ is the density of the solid phase, and ${\color{magenta}A}$ is the extractor’s cross section. ${\color{orange}\rho_f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]$ denotes the density of the fluid phase, ${\color{orange}D^M_e}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right]$ is the axial mass diffusion coefficient, ${\color{orange}C_p^f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]$ is the specific heat of the fluid phase, and ${\color{orange}D_e^T}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]$ is the axial heat diffusion coefficient. ${\color{magenta}C_p^s}$ denotes the specific heat of the solid particles.

%			\begin{tikztable}
%				\centering
%				\begin{tabular}{p{0.325\linewidth}|p{0.325\linewidth}|p{0.325\linewidth}}
%					\hline
%					${\color{blue}c}(t,z)$	&  ${\color{blue}q}(t,z)$ & ${\color{blue}T}(t,z)$  \\
%					 Solute's concentration in the fluid phase & Solute's concentration in the solid phase & Temperature of the pseudo-homogeneous phase \\
%					 \hline
%				\end{tabular}
%				\begin{tabular}{p{0.19\linewidth}|p{0.19\linewidth}|p{0.19\linewidth}|p{0.19\linewidth}|p{0.19\linewidth}}
%					${\color{red}F}(t)$ & ${\color{red}P}(t)$	& ${\color{magenta}\epsilon}$ & ${\color{magenta}\rho_s}$ & ${\color{magenta}A}$ \\
%					Solvent flow rate & Pressure & Void fraction & Density of the solid particles & Extractor's cross-section \\ 
%					\hline
%				\end{tabular}	
%				\begin{tabular}{p{0.19\linewidth}|p{0.19\linewidth}|p{0.19\linewidth}|p{0.19\linewidth}|p{0.19\linewidth}}
%					 ${\color{orange}\rho_f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]$& 					${\color{orange}D^M_e}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right]$ & ${\color{orange}C_p^f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]$ & ${\color{orange}D_e^T}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]$ & ${\color{magenta}C_p^s}$ \\
%					Density of the solvent & Axial mass diffusion factor & Specific heat of the fluid phase & Axial heat diffusion factor & Specific heat of the solid particles \\
%					\hline
%				\end{tabular}
%			\end{tikztable}
%			\captionof{table}{Symbols used in the process model}

			\begin{multicols}{2}
				\begin{itemize}
					\item[] ${\color{blue}c_f}(t,z)$ - Concentration of the solute in the solvent [$kg~m^{-3}$]
					\item[] ${\color{blue}c_s}(t,z)$ - Concentration of the solute in the solid phase [$kg~m^{-3}$]
					\item[] ${\color{blue}T}(t,z)$ - Temperature of the pseudo-homogeneous phase [$^\circ C$]
					\item[] ${\color{red}F}(t)$ - Flow rate of the solvent [$kg~s^{-1}$]
					\item[] ${\color{red}P}(t)$ - Pressure [$bar$]
					\item[] ${\color{magenta}A}$ - Cross-section of the extractor [$m^2$]
					\item[] ${\color{magenta}\epsilon}$ - Void fraction [$-$]
					\item[] ${\color{magenta}\rho_s}$ - Density of the solid particles [$kg~m^{-3}$]
					\item[] ${\color{orange}\rho_f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]$ - Density of the solvent [$kg~m^{-3}$]
					\item[] ${\color{orange}D^M_e}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right]$ - Axial mass diffusion coefficient of the solute in the solvent [$m^2 ~ s^{-1}$]
					\item[] ${\color{orange}C_p^f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]$ - Specific heat of the solvent [$J~mol^{-1}~K^{-1}$]
					\item[] ${\color{orange}D_e^T}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]$ - Axial heat diffusion coefficient of the pseudo-homogenous phase [$m^2 ~ s^{-1}$]
					\item[] ${\color{magenta}C_p^s}$ - Specific heat of the solid phase [$J ~ mol^{-1} ~ K^{-1}$]
				\end{itemize}
			\end{multicols}

		\vspace{1.0cm}
		\hrule
		\vspace{1.5cm}

		%		The movement of the solvent and the pseudo-homogeneous phase is considered only in the axial direction. The perfect mixing in the radial direction is assumed. In addition, if the boundary layer adjacent to the inner wall of the extractor does not exist, then the velocity profile is constant across any cross-section of the extractor perpendicular to the axial direction. As a result, the plug flow model can be introduced. The particle size distribution and the void fraction of the solid phase are assumed to be uniform in space and remain constant in time. Moreover, the pressure is assumed to be constant along the extractor.

			\textit{Model assumptions and description}

			\begin{multicols}{2}
				\begin{itemize}
					\item One-dimensional model
					%					\item Movement in the axial direction
					\item No radial profiles
					\item Plug flow 
					\item No pressure drop
					%					\item Negligible external diffusion 
					\item Uniform particle size distribution
					\item Constant particle-size and void fraction
					\item Single component solute
					\item The amount of solute in the solvent is considered negligible
					\item Two-film theory
					\item Pseudo-homogeneous thermal properties
				\end{itemize}
			\end{multicols}

%		 The mass balance equation of the fluid phase (Eq. \ref{eq: Model_fluid}) consists of convective, diffusive and kinetic terms. The mass balance equation of the solid (Eq. \ref{eq: Model solid}) phase has only the kinetic term because the solid particles are fixed.

				\vspace{1.5cm}

				The solvent flows through a fixed bed of solid particles and dissolves the soluble substances. We consider the axial dispersion of the solute in the solvent and assume that radial dispersion is negligible. The mass balance for the fluid phase (Eq. \ref{eq: Model_fluid}) consist of convection, diffusion, and kinetic terms.\\

				The solid phase is fixed, which indicates lack of a convective movement of the solid particles. We assume that the diffusion of the solute between solid particles is negligible. The mass balance for the solid phase (Eq. \ref{eq: Model_solid}) consist of the kinetic term only.% Therefore, the only term present in this equation is the kinetic term (defined as presented in Eq. \ref{Model_kinetic_basic}), which links solid and fluid phases.

				\begin{itemize}
					\item The mass transfer kinetic (Eq. \ref{Model_kinetic_basic}) describe a diffusion rate of the solute from solid particles to the solvent. The kinetic term consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.

%					\begin{minipage}[c]{0.5\linewidth}
%					
%					\end{minipage}
%%
%				\begin{multicols}{2}
%					\begin{itemize}
%						\item[] ${\color{orange}D_i}({\color{blue}T}(t,z))$ - overall diffusion coefficient [$m^2 ~ s^{-1}$]
%						\item[] ${\color{magenta}\mu}$ - shape coefficient [$-$]
%						\item[] ${\color{magenta}l}$ - characteristic dimension of particles [$m$]
%						\item[] ${\color{orange}k_m}({\color{blue}T}(t,z))$ - mass partition factor [$-$]
%					\end{itemize}
%				\end{multicols}

			\end{itemize}		
				\begin{minipage}[c]{0.5\linewidth}
					\begin{equation}
						{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}c_s}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}\left[{\color{blue}T}(t,z)\right]{\color{orange}\rho_f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}  {\color{blue}c_f}(t,z) \right) \label{Model_kinetic_basic}
					\end{equation}
				\end{minipage}
				\hspace{2.0cm}
				\begin{minipage}[c]{0.44\linewidth}	
					\vspace{0.2cm}
					\begin{itemize}
						\item[] ${\color{orange}D_i}({\color{blue}T}(t,z))$ - Overall diffusion coefficient [$m^2 ~ s^{-1}$]
						\item[] ${\color{magenta}\mu}$ - Shape coefficient [$-$]
						\item[] ${\color{magenta}l}$ - Characteristic dimension of particles [$m$]
						\item[] ${\color{orange}k_m}({\color{blue}T}(t,z))$ - Mass partition factor [$-$]
					\end{itemize}
				\end{minipage}
			\vspace{1.0cm}
			\hrule
			\vspace{1.0cm}
				\begin{minipage}[c]{0.5\linewidth}
					\begin{tikzfigure} \label{SFE_MassTransfer}
						\centering
						\includegraphics[trim = 5.8cm 1.1cm 6cm 0.8cm,clip,width=1.0\linewidth]{Figures/SFE_draft.pdf}
						\label{SFE_Mechanism}
					\end{tikzfigure}
					\captionof{figure}{Schematic representation of the extracting bed} 
				\end{minipage}
				\hspace{2.0cm}
				\begin{minipage}[c]{0.44\linewidth}
					\vspace{0.2cm}
						\begin{itemize}
							\item[] $L$ - Length of the fixed bed
							\item[] $z$ - Axial coordinate of the fixed bed
							\item[] $\Delta z$ - Length interval
						\end{itemize}
%					\vspace{-0.25cm}
					\hrule
					\begin{itemize}
						\item[] ${\color{blue}c_s}$ - Concentration of the solute in the core of the particle
						\item[] ${\color{blue}c_s^*}$ - Equilibrium concentrations of the solute in the solid phase at the solid-fluid interface
						\item[] ${\color{blue}c_P^*}$ - Equilibrium concentrations of the solute in the fluid phase at the solid-fluid interface
						\item[] ${\color{blue}c_{P}}$ - Concentration of the solute in the fluid phase in the centre of the pore
						\item[] ${\color{blue}c_{Pf}}$ - Concentration of the solute in the fluid phase at the end of the pore
						\item[] ${\color{blue}c_f}$ - Concentration of the solute in the solvent 
						\vspace{0.2cm}
						\hrule
					\end{itemize}
				\end{minipage}

%					${\color{orange}D_i}({\color{blue}T}(t,z))$ corresponds to the overall diffusion coefficient. ${\color{magenta}\mu}$ denotes the shape coefficient, ${\color{magenta}l}$ is the characteristic dimension of particles and ${\color{orange}k_m}({\color{blue}T}(t,z))$ is the mass partition factor.

			\vspace{1.5cm}

			The heat balance (Eq. \ref{eq: Heat_balance}) consists of the convective and diffusive terms. It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases. We consider that there is no heat loss through the wall, and there is no heat generation in the system. The temperature of the extractor can be changed only by manipulating the temperature of the inlet stream ${\color{red}T_{Inlet}}(t)$.

			\vspace{1.0cm}
			\hrule
			\vspace{1.5cm}

			\textit{Observations}:

%			The process performance is indicated by the measurement equation (Eq. \ref{eq: Yield}). The yield is based on the solute concentration in the solid phase. It is calculated as the ratio between the difference of its initial value ${\color{magenta}c_s^0}$ and the actual value, compared to the initial one.

			The efficiency of the process (the yield) is calculated according to Eq. \ref{eq: Yield}, and is based on the change of solutes concentration in the solid phase. It is defined as ratio the ratio between the difference of its initial value ${\color{magenta}c_s^0}$ and the actual value ${\color{blue}c_s}(t,z)$, compared to the initial one.

			\begin{equation}
				{\color{blue}y}(t) = \cfrac{\left({\color{magenta}c_s^0} - {\color{blue}c_s}(t,z) \right) }{{\color{magenta}c_s^0}} 100\% \label{eq: Yield}
			\end{equation}

%			The volume of the extractor is ${\color{magenta}V}$. The ${\color{magenta}q_0}$ is the initial concentration of the solute in the solid phase. \\

%			\begin{center} ${\color{magenta}V}$ - volume of the extractor [$m^3$] ~ ${\color{magenta}q_0}$ - initial concentration of the solute in the solid phase [$kg m^{-3}$] \end{center}

			%        \textcolor{blue}{State variables}, \textcolor{red}{control variables}, \textcolor{magenta}{parameters}, \textcolor{orange}{other variables}

			\vspace{1.0cm}
			\hrule
			\vspace{1.5cm}

			\textit{Numerics}:

			The method of lines is used to transform the process model equations into a set of ODEs denoted as ${\color{blue}G}({\color{blue}x}(t);{\color{magenta}\theta})$, where ${\color{blue}x}(t)$ is the discretized state and the ${\color{magenta}\theta}$ represents the collection of model parameters and the control variables (assuming they are constant).

			The partial derivatives in $z$-direction are computed using a first-order and second-order finite difference approximation. The backward finite difference is used to approximate first-order derivatives, while the central difference scheme is used to approximate second-order derivatives.

			The length of the fixed bed is divided into $N_z$ equally distributed points in the $z$-direction.

		}

		\column{0.5}

		\block{Sensitivity analysis}{

			The sensitivity analysis aims to measure the effect of the parameters on process model solution. The sensitivity analysis equations (${\color{blue}\dot{Z}}$) are obtained by taking the total derivative of the discretized system ${\color{blue}G}({\color{blue}x}(t);{\color{magenta}\theta})$ with respect to ${\color{magenta}\theta}$, as presented in \citep{Maly1996}. In this work, the direct method is considered and restricted to the analysis of linear sensitivity coefficients.

			\begin{align} \label{SA_def}
				{\color{orange}Z}({\color{blue}x}(t);{\color{magenta}\theta}) &= \cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}\theta}}
			\end{align}

			As the process model depends on parameters ${\color{magenta}\theta}$ and initial conditions, each parameter's sensitivity depends on time $t$. Therefore, the new system of equations can be obtained by taking derivatives with respect to time $t$ and applying the chain rule.

			\begin{equation} \label{SA_dt} 
				{\color{blue}\dot{Z}}({\color{blue}x}(t);{\color{magenta}\theta})  = \cfrac{d {\color{orange}Z}(x(t);{\color{magenta}\theta})}{d t} = \cfrac{\partial }{\partial t} \left( \cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}\theta}} \right) = \cfrac{\partial }{\partial {\color{magenta}\theta}} \left( \cfrac{\partial {\color{blue}x}(t)}{\partial t} \right) = \cfrac{d {\color{blue}G}({\color{blue}x}(t);{\color{magenta}\theta})}{d {\color{magenta}\theta}} 
			\end{equation}

			By applying the definition of the total derivative to the Eq. \ref{SA_dt}, the sensitivity equation can be obtained.

			\begin{align}		
				\label{SA_eq_full}\cfrac{d {\color{blue}G}({\color{blue}x}(t);{\color{magenta}\theta})}{d {\color{magenta}\theta}} &=  \underbrace{ \cfrac{\partial {\color{blue}G}({\color{blue}x}(t);{\color{magenta}\theta})}{\partial {\color{blue}x}(t)} }_{{\color{blue}J_x}({\color{blue}x}(t);{\color{magenta}\theta})} \underbrace{\cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}\theta}} }_{{\color{blue}S}({\color{blue}x}(t);{\color{magenta}\theta})} + \underbrace{ \cfrac{\partial {\color{blue}G}({\color{blue}x}(t);{\color{magenta}\theta})}{\partial {\color{magenta}\theta}} }_{{\color{blue}J_p}({\color{blue}x}(t);{\color{magenta}\theta})}
			\end{align}

			This equation consists of three terms: Jacobian ${\color{blue}J_x}({\color{blue}x}(t);{\color{magenta}\theta})$, sensitivity matrix ${\color{blue}S}({\color{blue}x}(t);{\color{magenta}\theta})$ and Jacobian ${\color{blue}J_p}({\color{blue}x}(t);{\color{magenta}\theta})$. The Jacobians are obtained by automatic differentiation. The sensitivity equations are coupled with the process model and solved simultaneously. As the result,  the gradients of the solution with respect to each parameter along the time series are obtained.

%			Given the system of $N_x$ ordinary differential equations $\dot{x}(t) = f\left(x(t)|u_\text{const},\theta\right)$ resulting from the space discretisation of the process model, Eq. {\color{red}REF}, where $f : \mathbb{R}^{N_x} \to \mathbb{R}^{N_x}$ is the vector field, $u_\text{const} \in \mathbb{R}^{N_u}$ and $\theta \in \mathbb{R}^{N_\theta}$ are constant controls and model parameters collectively denoted as $p \in \mathbb{R}^{N_p = N_u + N_\theta}$, we simultaneously solve for both $\{x_{n_x}(t)\}_{n_x=1}^{N_x}$ and a set of sensitivity functions $\left\{ \partial{x_{n_x}(t)} / \partial{p_{n_p}}\right\}_{n_p=1}^{N_p}$ for $t \ge 0$. The partial derivatives measure the sensitivity of the solution with respect to individual changes in the parameters $\{p_{n_p}\}_{n_p=1}^{N_p}$, over time. These functions are obtained by solving an additional set of ordinary differential equations called sensitivity equations. To determine the effect of the parameters, we consider the direct method ({\color{red}{REFS}}) and restrict our analysis to a first-order sensitivity analysis. Though, directed method can be used to execute higher-order analysis, their usefulness is seldom emphasised {\color{red}{REF}}; Therefore, we only compute linear sensitivity coefficients.
%			
%			The original system of $N_x$ ODEs has solutions $\{x_{n_x}(t \ge 0)\}$  that are dependent on the parameters $p$ as well as on the initial conditions $\{x_{n_x}(t=0)\}$. As such solutions are understood as functions of both time $t$ and the parameters $p$ (that is, $x_{n_x}\left(t \ge 0|p\right)$), to determine their sensitivity to each parameter $p_{n_p}$, we introduce $N_x$ new variables $\{z_{n_x}(t| p_{n_p})\}_{n_x=1}^{N_x}$ with $z_{n_x}(t|p_{n_p}) \in \mathbb{R}^{N_p}$ and such that $z_{n_x}(t|p_{n_p}) = \partial{x_{n_x}(t)} / \partial{p_{n_p}}$, for $n_p=1,\dots,N_p$. The functions $z_{n_x}(t \ge 0|n_p)$ are obtained as solutions to $N_x$ sensitivity differential models $\{\dot{z}_{n_p}(t | p_{n_p}) = h_{n_p}\left(z_{n_p}(t|p_{n_p}),x(t)|p\right)\}$ to be solved simultaneously with $\dot{x}(t) = f\left(x(t)|p\right)$, from an appropriate set of conditions $\{z_{n_x}(t=0 | p_{n_p})\}$. Each sensitivity model $\dot{z}_{n_x}(t|p_{n_p}) = h_{n_p}\left(z_{n_x}(t|p_{n_p}),x(t)|p\right)$ is given by
%			\begin{align}\begin{split}
%					\dot{z}_{n_x}(t|p_{n_p}) & = \cfrac{\partial{z_{n_x}(t | p_{n_p})}}{\partial{t}} \\
%					& = \cfrac{\partial}{\partial{t}}\left(\cfrac{\partial{x_{n_x}(t)}}{\partial{p_{n_p}}}\right) \\
%					& = \cfrac{\partial}{\partial{p_{n_p}}}\left(\cfrac{\partial{x_{n_x}(t)}}{\partial{t}}\right) \\
%					& = \cfrac{\partial}{\partial{p_{n_p}}}\left(f_{n_x}\left(x(t)|p\right)\right) \\
%					& = \cfrac{\partial{f_{n_x}\left(x(t)|p\right)}}{\partial{p_{n_p}}} + \sum_{\overline{n_x} = 1}^{N_x}{\cfrac{\partial{f_{n_x}\left(x(t)|p\right)}}{\partial{x_{\overline{n_x}}(t)}}\cfrac{\partial{x_{\overline{n_x}}(t)}}{\partial{p_{n_p}}}} \\
%					& = \cfrac{\partial{f_{n_x}\left(x(t)|p\right)}}{\partial{p_{n_p}}} + \sum_{\overline{n_x} = 1}^{N_x}{\cfrac{\partial{f_{n_x}(x(t)|p)}}{\partial{x_{\overline{n_x}}}}z_{n_x}(t|p_{n_p})}, \quad (n_x = 1, \dots, N_x).
%			\end{split}\end{align}
%			The term $\partial{f_{n_x}(x(t)|p)}/\partial{x_{\overline{n_x}}} = \left(J\right)_{n_x,\overline{n_x}}$ is the $(n_x,\overline{n_x})$-th entry in the $N_x \times N_x$ Jacobian $J_x$ of the original differential model with respect to $x$. We can write the $N_x$ sensitivity models with respect to $p_{n_p}$ in vector form,
%			\begin{equation}
%				\dot{z}(t|p_{n_p}) = \begin{bmatrix} \cfrac{\partial{f_{1}\left(x(t)|p\right)}}{\partial{p_{n_p}}} & \cdots & \cfrac{\partial{f_{N_x}\left(x(t)|p\right)}}{\partial{p_{n_p}}}\end{bmatrix}^T + J_xz(t|p_{n_p}) \quad (n_p = 1, \dots, N_p),
%			\end{equation}
%			$z(t|p_{n_p}) \in \mathbb{R}^{N_x}$ is $z(t|p_{n_p}) = \begin{bmatrix}z_1(t|p_{n_p}) \cdots z_{N_x}(t|p_{n_p})\end{bmatrix}^T$ and the term $\begin{bmatrix} {\partial{f_{1}\left(x(t)|p\right)}}/{\partial{p_{n_p}}} \cdots {\partial{f_{N_x}\left(x(t)|p\right)}}/{\partial{p_{n_p}}}\end{bmatrix}^T$ is the $n_p$-th column in the $N_x \times N_p$ Jacobian $J_p$ of the original differential model with respect to $p_{n_p}$. We let $z(t) \in \mathbb{R}^{N_x \cdot N_p}$ be $z(t) = \begin{bmatrix} z(t|p_{1})^T \cdots z(t|p_{N_p})^T \end{bmatrix}^T$ and obtain the complete differential model by combining the $N_x \times N_p$ sensitivity models with respect to all parameters. The model $\dot{z}(t) = h\left(z(t),x(t)|p\right)$ in matrix form is
%			\begin{equation}
%				\dot{z}(t) = J_p(x(t)|p)+ J_x(x(t)|p)z(t), \quad  (z(t=0) = 0).
%			\end{equation}

		}

		\block{Results}{

			The model parameters and the operating conditions come from \citet{Vargas2006}, who conducted the supercritical extraction to obtain essential oil, known as 'carqueja', from 'Baccharis Trimera' leaves. The experiments were performed in a temperature range from 313.15 [K] to 343.15 [K] at 90 [bar]. The inital conditions and the operating conditions are presented in the table \ref{Inital}.

			\begin{tikztable}
				\begin{tabular}{c | c | c | c | c | c}
						${\color{blue}c_f^0}(t,z)~[kg~ m^{-3}] $ & ${\color{blue}c_s^0}(t,z)~[kg~ m^{-3}] $ & ${\color{blue}T^0}(t,z)~[^{\circ}C] $ 	& ${\color{red}T_{Inlet}}(t)~[^{\circ}C] $ & ${\color{red}F}(t)~[kg~ hr^{-1}] $ &  ${\color{red}P}(t)~[bar] $  \\ \hline % &  &  &  &  &  \\
						$0$ &  $27$ & $50$ & $50$ & $0.035$ & $90$
					\end{tabular}
			\end{tikztable}
			\captionof{table}{Initial conditions and operating conditions}  \label{Inital}

			\vspace{0.5cm}

			The solution of the process model is presented in figure \ref{Model_Solution}

%			\vspace{0.5cm}
%			\hrule
			\begin{tikzpicture} 
				\node[inner sep=2pt] (Liq) at (0,0)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/ConcentrationLiquid.pdf} };
%				\node[yshift=3.3cm] at (Liq) {$c_f$};
				\node[xshift=-6.7cm,rotate=90] at (Liq) {${\color{white}F(t)}$};
				\node[inner sep=2pt] (Solid) at (12,0)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/ConcentrationSolid.pdf} };
%				\node[yshift=3.3cm] at (Solid) {$c_s$};
				\node[inner sep=2pt] (Yield) at (24,0)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Yield.pdf} };
%				\node[yshift=3.3cm] at (Yield) {$y(t)$};
%				\draw (-6.1,4.5) -- (-6.1,-2);
			\end{tikzpicture}

			\captionof{figure}{Solution of the process model}\label{Model_Solution}

			\vspace{0.5cm}
%			
			\hrule

			\vspace{1.0cm}

			We examine the effect of the operating conditions: ${\color{red}F}(t)$, ${\color{red}P}(t)$, ${\color{red}T_{Inlet}}(t)$ on the state variables: ${\color{blue}c_f}(t,z)$, ${\color{blue}c_s}(t,z)$ and on the observation function ${\color{blue}y}(t)$. The obtained results of the sensitivity analysis are presented in figure \ref{Sensitivty_Oper_Cond}

			\begin{tikzpicture} 
				\node[inner sep=2pt] (Liq1) at (0,0)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/2SS_RF.pdf} };
				\node[xshift=-6.7cm,rotate=90] at (Liq1) {${\color{red}F}(t)$};
				\node[inner sep=2pt] (Solid) at (12,0)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/3SS_RF.pdf} };
				\node[inner sep=2pt] (Yield) at (24,0)
				{\includegraphics[trim = 3cm 3.5cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/1SS_RF.pdf} };
				\draw (-6.1,2.3) -- (-6.1,-16);

				\node[inner sep=2pt] (Liq2) at (0,-7)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/2SS_RP.pdf} };
				\node[xshift=-6.7cm,rotate=90] at (Liq2) {${\color{red}P}(t)$};
				\node[inner sep=2pt] (Solid) at (12,-7)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/3SS_RP.pdf} };
				\node[inner sep=2pt] (Yield) at (24,-7)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/1SS_RP.pdf} };

				\node[inner sep=2pt] (Liq3) at (0,-14)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/2SS_RT.pdf} };
				\node[xshift=-6.7cm,rotate=90] at (Liq3) {${\color{red}T_{Inlet}}(t)$};
				\node[inner sep=2pt] (Solid) at (12,-14)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/3SS_RT.pdf} };
				\node[inner sep=2pt] (Yield) at (24,-14)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/1SS_RT.pdf} };
			\end{tikzpicture}
			\captionof{figure}{Results of the sensitivity analysis with respect to operating conditions} \label{Sensitivty_Oper_Cond}

			\vspace{0.5cm}

			\hrule

			\vspace{1.0cm}

			Similarly, we examine the effect of selected parameters: ${\color{magenta}\epsilon}$ and ${\color{magenta}l}$ on state variables: ${\color{blue}c_f}(t,z)$, ${\color{blue}c_s}(t,z)$ and on the observation function ${\color{blue}y}(t)$. The obtained results of the sensitivity analysis are presented in figure \ref{Sensitivty_Parameters}

			\begin{tikzpicture}
				\node[inner sep=2pt] (Liq1) at (0,0)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/2SS_Repsi.pdf} };
				\node[xshift=-6.7cm,rotate=90] at (Liq1) {${\color{magenta}\epsilon}{\color{white}(t)}$};
				\node[inner sep=2pt] (Solid) at (12,0)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/3SS_Repsi.pdf} };
				\node[inner sep=2pt] (Yield) at (24,0)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/1SS_Repsi.pdf} };
				\draw (-6.1,2.3) -- (-6.1,-9);

				\node[inner sep=2pt] (Liq2) at (0,-7)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/2SS_Rdp.pdf} };
				\node[xshift=-6.7cm,rotate=90] at (Liq2) {${\color{magenta}l}{\color{white}(t)}$};
				\node[inner sep=2pt] (Solid) at (12,-7)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/3SS_Rdp.pdf} };
				\node[inner sep=2pt] (Yield) at (24,-7)
				{\includegraphics[trim = 3cm 4cm 2.5cm 4.3cm,clip,width=0.32\linewidth]{Figures/Sensitivity/Imagesc/1SS_Rdp.pdf} };
			\end{tikzpicture}
			\captionof{figure}{Results of the sensitivity analysis with respect to selected model parameters}  \label{Sensitivty_Parameters}

%			\begin{tikzfigure}
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/ConcentrationLiquid.png}         	
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/ConcentrationSolid.png}
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/Yield.png}
%			\end{tikzfigure}
%			\captionof{figure}{Solution of the process model}
%			\hrule
%			\begin{tikzfigure}
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/Imagesc/2_SS_R_F.png}
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/Imagesc/3_SS_R_F.png}
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/Plots/1_SS_R_F.png}
%			\end{tikzfigure}     
%			\captionof{figure}{Sensitivity with respect to the flowrate}
%			\begin{tikzfigure}
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/Imagesc/2_SS_R_P.png}
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/Imagesc/3_SS_R_P.png}
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/Plots/1_SS_R_P.png}
%			\end{tikzfigure}  
%			\captionof{figure}{Sensitivity with respect of the pressure}          
%			\begin{tikzfigure}
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/Imagesc/2_SS_R_T.png}
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/Imagesc/3_SS_R_T.png}
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/Plots/1_SS_R_T.png}
%			\end{tikzfigure}        	
%			\captionof{figure}{Sensitivity with respect to the inlet temperature}
%			\hrule
%			\begin{tikzfigure}
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/Imagesc/2_SS_R_epsi.png}
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/Imagesc/3_SS_R_epsi.png}
%				\includegraphics[width=0.32\linewidth]{Figures/Sensitivity/Plots/1_SS_R_epsi.png}
%				\caption{Yield sensitivity}
%			\end{tikzfigure}     
%			\captionof{figure}{Sensitivity with respect to the void fraction} 
		}

		\block{References}{
			\renewcommand{\bibsection}{}
			\bibliographystyle{unsrtnat}
			\bibliography{mybibfile}

		}
	\end{columns}
\end{document}

### 2022-05-25 SFE - Copy/CostFunction.m

@@ -1,0 +1,43 @@
+function J = CostFunction(OCP, x0, u, k0,  parameters)
+
+%addpath('C:\Users\slicz\Desktop\Aalto\Matlab\SFE\casadi-windows-matlabR2016a-v3.5.1');
+%addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
+import casadi.*
+
+nstages = parameters{1};
+
+OCP_solver = casadi.Opti();
+
+% http://www.diva-portal.se/smash/get/diva2:956377/FULLTEXT01.pdf
+nlp_opts = struct;
+%nlp_opts.ipopt.max_iter = 100;
+%nlp_opts.ipopt.acceptable_iter = 50;
+%nlp_opts.ipopt.acceptable_tol = 1e-6;
+%nlp_opts.ipopt.tol = 1e-7;
+
+ocp_opts = {'nlp_opts', nlp_opts};
+OCP_solver.solver('ipopt',nlp_opts)
+
+K = OCP_solver.variable(OCP.Nk);
+X = [MX(x0) zeros(OCP.Nx,OCP.N)];
+J = 0;
+
+yout = MX(zeros(OCP.Ny,OCP.N+1));   
+
+%g = @(x, u, y_old) modelSFE_out2(x, u, y_old, parameters, timeStep_in_sec);
+
+for j=1:OCP.N
+    %J=J+OCP.L(U(:,j));
+    X(:,j+1)=OCP.F(X(:,j),u(:,j),K);
+    %yout(:,j+1) = g(X(:,j+1), u(:,j), yout(:,j));
+end
+
+%data = yy(1:N_Sample:end);
+data = X(3*nstages+1,:);
+data = [zeros(1,OCP.N_Delay) data(1:end-OCP.N_Delay)];
+data = diff(data(1:OCP.N_Sample:end));
+
+%J = J + OCP.LS(data);
+%J = J + OCP.MSE(data,K(end));
+J = J + OCP.MAP(data,K(1),K(end));
+

### 2022-05-25 SFE - Copy/cpRHOcp_Comp.m

@@ -1,0 +1,13 @@
+function cprhocp = cpRHOcp_Comp(T,P,Z,RHO,CP,theta)
+
+    epsi     = theta{4};     % Void bed fraction    
+    rhoSolid = theta{7};     % Density of solid
+    cpSolid = theta{24};
+    
+    cpFluid = CP;
+    
+    %cpSolid = 1.5E3; %theta(); % J / K / Kg 
+
+   cprhocp = cpFluid ./ (cpFluid.*(1-epsi).*RHO + cpSolid.*epsi*rhoSolid);
+
+end

### 2022-05-25 SFE - Copy/main_fitting_SFE.m

@@ -1,0 +1,256 @@
+clc, close all
+%clear all
+%addpath('C:\dev\casadi-windows-matlabR2016a-v3.5.2');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
+import casadi.*
+
+DATA = {'Data_40_200.mat', 'Data_50_200.mat', 'Data_40_300.mat', 'Data_50_300.mat'};
+
+%% Parameters
+nstages = 5;                                                   %
+
+C0fluid = 0;                                            % Extractor initial concentration of extract
+% Fluid phase kg / m^3
+C0solid = 32;                                           % Solid phase kg / m^3
+V       = 0.01/4;                                       % Volume of the extractor  [m3] - Vargas
+epsi    = 0.70;                                         % Porosity [-] - Vargas
+dp      = 0.001;                                        % Diameter of the particle [m] - Vargas
+L       = 0.70;                                         % Length of the extractor [m] - Vargas
+rho_s   = 1087.2;                                       % Densisty of the solid phase [kg / m^3] - Vargas
+km      = 0.29;                                         % Partition coefficient (?)
+mi      = 1/5;                                          % Geometric shape coefficient (?) - Vargas
+Ti      = [313.15, 323.15, 333.15, 343.15];
+Di      = [ 3.03E-11, 3.66E-11, 1.97E-10, 2.73E-10];
+T_kp    = [313.15, 323.15, 333.15, 343.15];
+dkp     = [8.13E-01 6.94E-01 1.04E-01 6.67E-02];
+
+
+Tc      = 304.1;                                        % Critical temperature [K]
+Pc      = 73.8;                                         % Critical pressure [bar]
+omega   = 0.228;                                        % Acentric factor [-]
+R       = 8.314e-5;                                     % Universal gas constant, [m3-bar/K-mol]
+
[…]

### 2022-05-25 SFE - Copy/modelSFE_SS.m

@@ -1,0 +1,113 @@
+function xdot = modelSFE_SS(x, u, k, parameters,which_parameter)
+    % (t, x, u, parameters)
+    % Model with (F)luid, (S)olid, (T)emperature
+    % Di is a function of temperature (T), the function works with numbers,
+    % vectors of numbers and vectors of symbolic variables
+    % Rho (Peng-Robinson) are constant numbers
+
+    %% parameters is the vector of model parameters
+    % parameters = [nstages, C0solid, V, epsi, dp, L, rho_s, km, mi, Tc, Pc, R, kappa];
+    %          1        2        3  4     5   6  7      8   9   10  11  12 13
+
+    %% Substitute parameters to estimate with symbolic variables k
+    if ~isempty(which_parameter)
+        fprintf(['The following parameters will be estimated:'])
+        for i=1:length(which_parameter)
+            parameters{which_parameter{i}} = k(i);
+            formatSpec = ' %d,';
+            fprintf(formatSpec, which_parameter{i})
+        end
+    else
+        fprintf(['None of the parameters has been selected\n' ...
+            '-------------------------------------------------\n'])
+    end
+    
+    %% TODO: T_bottom (N+1) - boundary conditions
+
+    nstages_index = parameters{1};     % Number of stages
+    nstages       = parameters{1};
+    C0solid       = parameters{2};                                            % Extractor initial concentration of extract
+    V             = parameters{3};     % Extractor volume (m3)
+    epsi          = parameters{4};     % Void bed fraction
+    dp            = parameters{5};     % Diameter of the particle (m)
+    L             = parameters{6};     % Length of the extractor (m)
+    rho_s         = parameters{7};     %
+    km            = parameters{8};
+    mi            = parameters{9};
+
+    Di            = parameters{44};
+    Dx            = parameters{45};
+    
+    T_u           = u(1);
+    P_u           = u(2);
[…]

### 2022-05-25 SFE/Arrhenius_Di.m

@@ -1,0 +1,33 @@
+function [EA, D0] = Arrhenius_Di(T,D, R)
+
+    [P,S] = polyfit(1./T,log(D),1);
+
+    EA = -P(1)*R;
+    D0 = exp(P(2));
+    
+    %{
+    dT  = [ ones(numel(T),1) 1./T' ];        % Data temperatures of some biomass
+    EA1 = -R * log10(D(1) / D(end)) / (dT(1,2) - dT(numel(T),2)); % Activation energies
+                                                        % We assume that dDi = beta * dT and estimate beta using least-squares
+    betah1 = inv(dT'*dT)*dT'*D';                            % Estimated coefficients
+    betah = betah1(1);                                       %
+
+    
+    %EA1 = -R * log(D(1) / D(end)) / (dT(1,2) - dT(4,2)); % Activation energies
+                                                        % We assume that dDi = beta * dT and estimate beta using least-squares
+    %betah = inv(dT'*dT)*dT'*D';                            % Estimated coefficients
+    %betah = betah(1); 
+    %}
+%     TT = linspace(T(1),T(end));
+%     hold on
+%     plot(1./T,log(D),'o')
+%     plot(1./TT, P(1).*(1./TT) + P(2),'-')
+%     xlabel('1/T [1/K]','interpreter','latex')
+%     ylabel('$ln(Di) [m^2/s]$','interpreter','latex')
+%     R2 = 1 - (S.normr/norm(log(D) - mean(log(D))))^2;
+%     str = sprintf('$R^2 =$%.3f',R2);
+%     annotation('textbox',[.8 .6 .3 .3],'string',str,'FitBoxToText','on','EdgeColor','black','FontSize',15,'interpreter','latex')   
+%     hold off
+%     title(['Line Equation is y = F(x) = ',num2str(P(1)),'*x + ','(',num2str(P(2)),')'],'interpreter','latex');
+%     
+end

### 2022-05-25 SFE/Compressibility.m

@@ -1,0 +1,69 @@
+function Z = Compressibility(t,p,theta)
+    
+    import casadi.*
+    T = MX.sym('T',length(t));
+    P = MX.sym('P',length(p));
+
+    %% Unpacking parameters
+    % theta = [nstages, C0solid, V, epsi, dp, L, rho_s, km, mi, Tc, Pc, R, kappa];
+    %          1        2        3  4     5   6  7      8   9   10  11  12 13
+
+    Tc      = theta{10};   % Critical temperature [K]
+    Pc      = theta{11};   % Critical pressure [bar]
+    R       = theta{12};   % Universal gas constant, [m3-bar/K-mol]
+    kappa   = theta{13};
+    MW      = theta{14};   % Molar mass [g/mol]
+    Tr      = T ./ Tc;
+    a       = 0.4572350 .* R.^2 .* Tc.^2 ./ Pc;
+    b       = 0.0777961 .* R    .* Tc    ./ Pc;
+
+    alpha = (1 + kappa .* (1 - sqrt(Tr))).^2;
+
+    A = a .* alpha .* P ./ R.^2 ./ T.^2;
+    B = b .* P ./ R ./ T;
+
+    %% Creating symbolic variables for CasADi rootfinder
+    z = MX.sym('z',length(T));      % Compressibility factor
+
+    %%
+    % Cubic polynomial in z from Equation of State
+    % Find z such that the polynomial is zero
+    pol =                         z.^3 ...
+        - (1 - B)              .* z.^2 ...
+        + (A - 2.*B - 3.*B.^2) .* z ...
+        - ( A .* B - B.^2 - B.^3);
+
+    %disp("Case 1, T and P are symbolic")
+    g = Function('g',{z,T,P},{pol});
+    
+%{
+
+     * If it failed due to an unrecoverable failure in rhs, then we return
+     * the value CV_RHSFUNC_FAIL.
+     *
+     * Otherwise, a recoverable failure occurred when solving the 
+     * nonlinear system (cvNls returned nflag == CONV_FAIL or RHSFUNC_RECVR). 
+     * In this case, if ncf is now equal to maxncf or |h| = hmin, 
+     * we return the value CV_CONV_FAILURE (if nflag=CONV_FAIL) or
+     * CV_REPTD_RHSFUNC_ERR (if nflag=RHSFUNC_RECVR).
[…]

### 2022-05-25 SFE/km_of_T.m

@@ -1,0 +1,16 @@
+function km = km_of_T(T, theta, k)
+
+% I will get back to you, promised!
+% Dataset comes in as theta
+
+    R   = theta{12};     % R = 8.31446;
+    EA = theta{22};
+    betah = theta{23};
+
+    % k0 = [EA_Di, betah_Di, EA_km, betah_km];
+    %EA = k(3);
+    %betah = k(4);
+
+    km = betah .* exp( -EA ./ R ./ T);                   % Estimated Di for some T
+  
+end

### 2022-05-25 SFE/main_fitting_SFE.m

@@ -1,0 +1,163 @@
+clc, clear all, close all, clearvars -global
+%addpath('C:\dev\casadi-windows-matlabR2016a-v3.5.2');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
+import casadi.*
+
+%% Parameters
+nstages = 3;                                                   %
+
+dataset = 'Vargas';
+
+switch dataset
+    case 'Reverchon'
+        C0solid = 9;                                            % Extractor initial concentration of extract - Reverchon
+        V       = 4e-4;                                         % Volume of the extractor (400 ml)
+        epsi    = 0.8;                                          % Porosity [-]
+        dp      = 0.75e-3;                                      % Diameter of the particle [m]
+        L       = 0.165;                                        % Length of the extractor [m]
+        rho_s   = 413.25;                                       % Densisty of the solid phase [kg / m^3]
+        km      = 0.29;                                         % Partition coefficient (?)
+        mi      = 3/5;                                          % Geometric shape coefficient (?)
+        Ti      = (273.15 + [25, 40, 70]);                      % Data temperatures of some biomass
+        Di      = [ 3.04, 2.88, 4.64] * 10^-12;                 % Data diffusivities of some biomass - King
+        %Di      = [ 6, 6, 6] * 10^-13;                         % Data diffusivities of some biomass - Reverchon
+        T_kp    = [313.15, 323.15, 333.15, 343.15];
+        dkp     = (rho_s .*km ./[485.15 285 235.4 212.4]);
+        feedFlow  = 0.53/3600;                                  % Kg / sec
+        disp('Reverchon dataset')
+    case 'Vargas'
+        C0solid = 27;                                           % Vargas
+        V       = 4.173e-6;                                     % Volume of the extractor  [m3] - Vargas
+        epsi    = 0.669;                                        % Porosity [-] - Vargas
[…]

### 2022-05-25 SFE/modelSFE_out.m

@@ -1,0 +1,20 @@
+function y = modelSFE_out(x, theta)
+
+% theta = [nstages, C0solid, V, epsi, dp, L, rho_s, km, mi];
+%          1        2        3  4     5   6  7      8   9
+    nstages = theta{1};
+    C0solid = theta{2};
+    V       = theta{3};
+    
+    Csolid = x(1 + nstages : 2 * nstages,:);    % Extract concentration is solid
+                                              % Each stage
+    
+    stageV = V / nstages;                     % Volume of one stage
+    
+    Mextracted = stageV * (C0solid - Csolid); % Mass of extract extracted
+                                              % Each stage
+   
+    y = sum(Mextracted) / C0solid / V * 100;  % Percentage of extract extracted
+                                              % Total, from all stages
+    
+end    

### 2022-05-25 Test/model_out.m

@@ -1,0 +1,3 @@
+function y = model_out(x)
+    y = x(3,:);
+end

### 2022-05-25 Test/simulateSystem_ParameterEstimation.m

@@ -1,0 +1,39 @@
+function [yout,tout,xout] = simulateSystem_ParameterEstimation(varargin)
+
+    % [y, t, x] = Simulate(F, g, x0, u); 
+    
+    import casadi.*
+    
+    F = varargin{1}; 
+    g = varargin{2}; 
+    x0 = varargin{3};
+    
+    u = varargin{4};
+    N = size(u,1);
+        
+    k = varargin{5};
+
+    f = @(x,u,k) full(F(x,u,k));
+    
+    % aux
+    Nx = size(x0,1); 
+    Ny = size(g(x0),1);
+    
+    tout = 1:N;
+    
+    xout = zeros(Nx,N+1);  
+    xout(:,1) = x0;
+    
+    yout = zeros(Ny,N+1);   
+    yout(:,1) = g(xout(:,1));
+    
+    % sim
+    for i = 1:N
+        xout(:,i+1) = f(xout(:,i), u(i,:),k);
+        yout(:,i+1) = g(xout(:,i+1));
+        
+    end
+    
+    % extract the initial state from the vector that is returned
+    %xout = xout(:,2:end); yout = yout(:,2:end);
+end

### 2022-05-25 Test/singleShooting_ParameterEstimation.m

@@ -1,0 +1,48 @@
+function [xout, kout] = singleShooting_ParameterEstimation(OCP, x0, u, yd, k0)
+
+%addpath('C:\Users\slicz\Desktop\Aalto\Matlab\SFE\casadi-windows-matlabR2016a-v3.5.1');
+%addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
+import casadi.*
+
+OCP_solver = casadi.Opti();
+%OCP_solver.solver('ipopt')
+
+% http://www.diva-portal.se/smash/get/diva2:956377/FULLTEXT01.pdf
+nlp_opts = struct;
+nlp_opts.ipopt.max_iter = 100;
+%nlp_opts.ipopt.acceptable_iter = 50;
+%nlp_opts.ipopt.acceptable_tol = 1e-6;
+%nlp_opts.ipopt.tol = 1e-7;
+ocp_opts = {'nlp_opts', nlp_opts};
+
+OCP_solver.solver('ipopt',nlp_opts)
+
+K = OCP_solver.variable(OCP.Nk);
+X = [MX(x0) zeros(OCP.Nx,OCP.N)];
+J = 0;
+for j=1:OCP.N
+    %J=J+OCP.L(U(:,j));
+    X(:,j+1)=OCP.F(X(:,j),u(:,j),K);
+end
+J = J + OCP.Lf(X,yd);
+
+% for nx=1:OCP.Nx
+%     OCP_solver.subject_to(OCP.x_lu(nx,1)<=X(nx,:)<= OCP.x_lu(nx,2));
+% end
+% 
+% for nk=1:OCP.Nk
+%     OCP_solver.subject_to(OCP.k_lu(nk,1)<=K(nk,:)<= OCP.k_lu(nk,2));
+% end
+
+OCP_solver.minimize(J);
+OCP_solver.set_initial(K, k0);
+
+try
+    sol = OCP_solver.solve();
+    kout = sol.value(K);
+catch
+    kout = OCP_solver.debug.value(K);
+end
+
+xout = 1;
+end

### 2022-05-25 Test/test.m

@@ -1,0 +1,74 @@
+clc, clear all, close all
+%addpath('C:\dev\casadi-windows-matlabR2016a-v3.5.2');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
+import casadi.*
+
+%% States
+
+% Create symbolic variables
+x     = MX.sym('x', 3);                                   % states
+u     = MX.sym('u', 1);                                   % controls
+k     = MX.sym('k', 2);                                   % parameters to estimate
+
+% Number of Variables
+Nx = 3;
+Nu = 1;
+Nk = 2;
+Ny = 1;
+
+%% Time
+simulationTime       = 20/60;                                     % Minutes 
+timeStep             = 0.01 ;                                     % Minutes  
+timeStep_in_sec      = timeStep*60;                               % Seconds
+Time_in_sec          = (0:timeStep:simulationTime)*60;            % Seconds
+Time                 = Time_in_sec/60;                            % Minutes
+
+%% Parameters
+k0 = [0.1, 0.5];
+theta = 1;
+
+%% Controls
+uu = zeros(length(Time_in_sec),1);
+
+%% Model
+% Model Equations
+f = @(x, u, k) test_model(x, u, k, theta);
+g = @(x) model_out(x);
+
+% Integrator
+F = buildIntegrator_ParameterEstimation(f, [Nx,Nu,Nk] , timeStep_in_sec);       
+
+% Initial conditions
+x0 = [1; 0; 0.1];
+k_initial = [0.08 0.55];
+
+% Simulate system with initial parameter
+[yy, tt, xx] = simulateSystem_ParameterEstimation(F, g, x0, uu, k0);
+data = yy;
+
+ %% Optimization
+
+OCP = struct('Nx', Nx, 'Nu', Nu, 'Nk', Nk, 'Ny', Ny, 'N', length(uu), ...
+    'x_lu', [0*ones(Nx,1) inf*ones(Nx,1)],  ...
+    'k_lu', [ ],  ...
+    'x_eq', [], ...
+    'k_eq', [], ...
+    'F'   , F, ...
+    'L'   , [  ], ...       % 
+    'Lf'  , @(x,yd) 0.5*( sum(g(x)-yd) )'*( sum(g(x)-yd) )    );
+
+%% Solve LSE
[…]

### 2022-05-27 SFE-report/Paramter_fitting.tex
27.05

--- 2022-05-25 SFE-report/Forward_sensitivity_analysis_of_SFE_Sliczniuk.tex
@@
 \title[mode=title]{Parameter estimation}                      
-\shorttitle{Forward sensitivity analysis of the supercritical extraction process}
+\shorttitle{Parameter estimation}
 
@@
 \newpage
+\section{Bayes theorem} \label{CH: Bayes}
+
+As discussed by \citet{Himmelblau1970}, The Bayesian approach to estimation make use of prior information.
+Such prior knowledge can come from theoretical considerations, from the results of previous experiments, or from assumptions by the experimenter.
+Typically, a Bayesian approach assumes a prior probability distribution of an unknown parameter $\theta$ in some parameter space $\boldsymbol{\theta}$.
+The distribution is updated by using Bayes' rule to obtain the posterior probability distribution.
+
+Consider a set of events or outcomes, $A_1,A_2,...,A_n$, and some other event $B$.
+Bayes' theorem states that the probability that event $A_i$ will occur, given that event $B$ has already occured, which will denoted by $P\{A_i|B\}$, is equal to the product of the probability that $A_i$ will occur regardless of whether $B$ will take place and the probability that $B$ will occur, given that $A_i$  has already taken place, divided by the probability of the occurrence of $B$:
+
+\begin{equation}
+	P\{A_i|B\} = \cfrac{P\{B|A_i\}P\{A_i\}}{P\{B\}}
+\end{equation}
+
+Further, if al events comprising the set $\{A_i\}$ are included in $A_1,A_2,...,A_n$, then
+
+\begin{equation} \label{EQ: Bayes_discrit}
+	P\{A_i|B\} = \cfrac{P\{B|A_i\}P\{A_i\}}{ \sum_{i=1}^{n} P\{B|A_i\} P\{A_i\} }
+\end{equation}
+
+We can interpret these symbols as follows:
+
+\begin{enumerate}
+	\item $P\{A_i\}$ is a measure of our degree of belief that event $A_i$ will occur or that hypothesis $A_i$ is true prior to the acquisition of additional evidence that may alter the measure.
+$P\{A_i\}$ is denoted the \textit{prior probability}.
+	\item $P\{A_i|B\}$ is a measure of our degree of belief that event $A_i$ will occur or that hypothesis $A_i$ is true, given additional evidence $B$ pertinent ot the hypothesis.
+$P\{A_i|B\}$ is termed the \textit{posterior probability}.
+	\item $P\{B|A_i\}$ denotes the likelihood that event $B$ will occur, given that event $A_i$ is true.
+$P\{B|A_i\}$ is a conditional probability, interpreted in the Bayesian framework as a likelihood, $L(A_i|B)$.
+\end{enumerate}
+
+For continuous variable, Bayes' theorem can be more conveniently expressed in terms of the probability density function rather than the probabilities themselves.
+Equation \ref{EQ: Bayes_discrit} can be expressed in terms of a set of observed values of the random variable $X$, \textbf{x} and unknown parameter $(s)\theta$ as
+
+\begin{equation} \label{EQ: Bayes_continous}
+	p\left( \theta|X=\textbf{x} \right) = p\left( \theta|\textbf{x} \right) = \cfrac{L\left( \theta|\textbf{x} \right) p(\theta)}{\int_{-\infty}^{+\infty} L\left( \theta|\textbf{x} \right) p(\theta) d\theta}
+\end{equation}
+
+where
+
+$p(\theta|\textbf{x}) = ~$the posterior probability density function for $\theta$; it includes knowledge of the possible values of $\theta$ gained from the experimental data \textbf{x}
+
+$p(\theta) = ~$ the prior probability density function for $\theta$ (before the experiment in which \textbf{x} was observed)
+
+$L\left( \theta|\textbf{x} \right) = p\left( \textbf{x}|\theta \right) = ~$ the probability density function termed the likelihood function of $\theta$ given \textbf{x}
+
+The denominator in Equation \ref{EQ: Bayes_continous} is a normalizing factor chosen so that the integration of the posterior distribution is unit, i.e., $\int_{-\infty}^{+\infty} p\left( \theta|\textbf{x} \right) = 1$.
+By taking into account the law of total probability, the denominator can be written as
+
+\begin{equation}
+	\int_{-\infty}^{+\infty} p\left( \textbf{x}|\theta \right) p(\theta) d\theta = p(\textbf{x})
+\end{equation}
+
+If the prior distribution is a uniform distribution, that is the prior distribution is a constant, the \ref{EQ: Bayes_continous} reduces to
+
+\begin{equation}
+	p\left( \theta|\textbf{x} \right) = \cfrac{L\left( \theta|\textbf{x} \right)}{\int_{-\infty}^{+\infty} L\left( \theta|\textbf{x}\right) d\theta}
+\end{equation}
+
+If the prior knowledge concerning a postulated event or hypothesis is poor, the posterior probability is largely or entirely determined by the likelihood function, that is, by the additional accumulated evidence for which the likelihood function acts as a mathematical expression.
+If prior knowledge outweighs recent evidence, however, then the posterior probability is determined almost solely by the prior probability.
+
+In the application of tests and the design of experiments, certain definitions and rules concerning probability are needed and are listed below.
+
+\begin{enumerate}
+	\item It follows from the frequency theory of probability that: $0 \leq P \leq 1$
+	\item If the probability of occurrence of one event $A$ depends on whether or not event $B$ has occurred, the two events are termed \textit{dependent}; if the probability of occurrence of event $A$ does not depend on the occurrence of $B$, or the reverse, the two events are \textit{independent}.
+	\item \textbf{Addition Rule}
+	If $A_1,A_2,...,A_n$ are mutually exclusive events, i.e., cannot occur at the same time, the probability of occurrence of just one of the events is equal to the sum of the probabilities of each $A_i$:
+
+	\begin{equation}
+		P\left( A_1, \text{or~} A_2,..., \text{or~} A_n \right) = \sum_{i=1}^{n} P\left( A_i \right)
+	\end{equation}
+
+	Very often we let
+	\begin{equation}
+		\sum_{i=1}^{n} P\left( A_i \right) = 1
+	\end{equation}
+
+	Also, if each event is equi-probable so that $P(A_i) = q$,
+
+	\begin{equation}
+		\sum_{i=1}^{n} q = nq = 1 \qquad \text{or} \qquad  q=\cfrac{1}{n} = P\left( A_i \right)
+	\end{equation}
+
+	In set theory, mutually exclusive event have no points in common. The union of the sets which represents the set of all elements that belong to
+
+	\begin{equation}
+		P\left( A_1 \cup A_2 \cup ... \cup A_n \right) = P(A_1) + P(A_2) + ... + P(A_n)
+	\end{equation}
+
+	\item \textbf{Multiplication Rule}
+	If $A$ and $B$ are \textit{independent} event
+
+	\begin{equation}
+		P\left( A \text{~and~} B\right) = P(A)P(B)
+	\end{equation}
+
+	In set theory the intersection of $A$ and $B$ is the set of all elements that belong to $A$ and $B$:
+
+	\begin{equation} \label{EQ: Probabiltiy_independet_a}
+		P\left( A \cap B  \right) = P(A)P(B)
+	\end{equation}
+
+	If the $A$ and $B$ are \textit{dependet} events,
+
+	\begin{equation} \label{EQ: Probabiltiy_independet_b}
+		P\left(A|B\right) = \cfrac{P\left( A \cap B \right)}{P(B)}
+	\end{equation}
+
+	where the symbol $P(A|B)$ means "probability of $A$ given $B$". As a corollary,
+
+	 \begin{subequations}
+		\begin{alignat}{2}
+			P\left( A \cap B \right) &= P(B) P(A|B) \label{EQ: Probabiltiy_dependet_a} \\
+			&= P(A)P(B|A) \label{EQ: Probabiltiy_dependet_b}
+		\end{alignat}
+	\end{subequations}
+
+	Two kind of probabilities enter Equation \ref{EQ: Probabiltiy_dependet_a} (or Equation \ref{EQ: Probabiltiy_dependet_b}): the absolute probability of event $B$ (or $A$) irrespective of whether or not $A$ (or $B$) has occurred, and that the conditional probability of event $A$ (or $B$) computed on the assumption that $B$ (or $B$) has occurred.
+Equation \ref{EQ: Probabiltiy_independet_a} or \ref{EQ: Probabiltiy_independet_b} is special case of Equation \ref{EQ: Probabiltiy_dependet_a} or \ref{EQ: Probabiltiy_dependet_b}, because if the event are independent $P(A|B)=P(A)$.
+	For the case of many event, Equation \ref{EQ: Probabiltiy_independet_a} can be expanded to
+
+	\begin{equation}
+		\begin{split}
+			P(A_1 \text{~and~} A_2 \text{~and~} ... \text{~and~} A_n) &= P(A_1)\cdot P(A_2) \cdot  ...\cdot P(A_n) \\ &= \prod_{i=1}^{n} P(A_i)
+		\end{split}
+	\end{equation}
+
+	\item Another useful relationship for event which are not mutually exclusive is
+
+	\begin{equation}
+		P(A) + P(B) - P(A \cap B) = P(A \cup B)
+	\end{equation}
+
+\end{enumerate}
+
+\newpage
 \section{Parameter estimation} \label{CH: Parameter_estimation}
-Estimation theory is a branch of statistics that deals with estimating the values of parameters based on measured empirical data that has a random component.
-The parameters describe an underlying physical setting in such a way that their value affects the distribution of the measured data.
-An estimator attempts to approximate the unknown parameters using the measurements.
 
-For a given model, several statistical "ingredients" are needed so the estimator can be implemented.
-The first is a statistical sample – a set of data points taken from a random vector (RV) of size $N$.
-Let denote a statistical sample as $x$ and parameters whose vales are to be estimated as $\theta$.
-Both can be written into a vector form:
+Conceptually, in the measurement equation the unobservable $\epsilon(t)$ is added to $y(t)$ to give the observable dependent variable $Y(t)$ defined as:
+
+\begin{equation}
+	Y(t) = y(t) + \epsilon(t)
+\end{equation}
+
+If the estimated parameter $\hat{\alpha}$ replaces the model parameter $\alpha$, the residue error is $\textbf{E} = Y(t) - \hat{Y}(t)$.
+The objective in parameter estimation is to obtain the "best" estimate of $\alpha$ based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$.
+
+We assume that $x(t)$ is given \textit{a priori} but the $\textbf{y}_0$ and $\alpha$ are to be estimated over the time interval $0 \leq t \leq t_n$ from discrete observation described by the following relation:
+
+\begin{equation}
+	\textbf{Y}(t_i) = h(t_i)y(t_i) + \epsilon(t_i) \qquad 1 \leq i \leq n
+\end{equation}
+
+where $\textbf{Y}(t_i)$ is an $n \times 1$ column vector, $h(t_i)$ is an $n \times v$ matrix given \textit{a priori}, and $\epsilon (t_i)$ is an $x \times 1$ column vector ("noise" vector) whose elements are the unobservable errors.
+The above equation can be written in general form as:
+
+\begin{equation} \label{EQ: Measurment_noise}
+	\textbf{Y}(t_i) = \Psi(\alpha, y_0, t_i) + \epsilon(t_i)
+\end{equation}
+where $\Psi$ is the matrix of functions.
+
+Because of the difficulty of obtaining analytical solutions to the deterministic process model, experiments have been arranged wherby the vector of derivatives $d\textbf{Y}/dy$ is measured rather than \textbf{Y} itself.
+In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy/dt$ as follows:
+
+\begin{equation}
+	\cfrac{d\textbf{Y}}{dt} = \cfrac{dy}{dt} + \epsilon
+\end{equation}
+
+\subsection{Least squares estimation}
+A least squares parameter estimation does not require prior knowledge of the distribution of unobservable errors, yield  unbiased estimates, that is, $ \mathbb{E}\{\hat{Y}(t) = y(t) \} $, and results in the minimum variance among all linear unbiased estimators.
+If the observations $\textbf{Y}$ for the model responses are continuous functions of time from $t = 0$ to $t = t_f$, the Markov (or "rigorous least squares") criterion is to minimize:
+
+\begin{equation}
+	\phi =  \cfrac{1}{2} \int_{0}^{t_f}  \left[ \textbf{Y} - \Psi \right]^T \Gamma^{-1} \left[ \textbf{Y} - \Psi \right] dt
+\end{equation}
+
+where $\Gamma$ is the covariance matrix (or perhaps a matrix of appropriate weights), and $\phi$ is the time integrated value of the error squared ("integral squared error").
+If the observations are made at discrete instants of time, $t_i$, $i = 1,2,...,n$, the Markov criterion is to minimize:
+
+\begin{equation}
+	\phi = \cfrac{1}{2} \sum_{i=1}^{n} \left[ \textbf{Y}(t_i) - \Psi(t_i) \right]^T \Gamma^{-1} \left[ \textbf{Y}(t_i) - \Psi(t_i) \right] 
+\end{equation}
+
+If $\Gamma$ is a diagonal matrix, $\phi$  becomes a "weighted least squares" criterion; if $\Gamma = \sigma^2 \textbf{I}$ where $\sigma$ is a standard deviation, $\phi$ is the "ordinary least squares" criterion.
+
+\subsection{Maximum likelihood estimation}
+
+Maximum likelihood estimation (MLE) is a method of estimating the parameters of an assumed probability distribution, given some observed data.
+This is achieved by maximizing a likelihood function so that, under the assumed statistical model, the observed data is most probable.
+The MLE has the desirable characteristics of asymptotic efficiency and normality.
+Each time it has been associated with the (joint) normal distribution because of mathematical convenience.
+Consider the joint probability density function (the likelihood function) $p(\alpha, y_0|y(t_1),y(t_2),...,y(t_n))$ for $\alpha$ and $y_0$ if a maximum of this function over all choices of $y_0$ and $\alpha$ can be found, the estimates so obtained are maximum likelihood estimates.
+The conditions at the maximum can be evolved incorporating prior information as follows.
+
+The posterior probability density $p(\alpha,y_0|y(1),y(2),...,y(t_n))$ can be expressed as the ratio of two probability densities if we make use of the analog for continuous variables of Equation \ref{EQ: Probabiltiy_independet_b}:
+
+\begin{equation} \label{EQ: Posterior_distribution}
+	p\left( \alpha,y_0|y(t_n,...,y(1)) \right) = \cfrac{p\left( \alpha, y_0, y(t_n),...,y(t_1) \right)}{p\left( y(t_n),...,y(t_1) \right)}
+\end{equation}
+
+The numerator of the right-hand side od Equation \ref{EQ: Posterior_distribution} using Equation \ref{EQ: Probabiltiy_dependet_a} becomes
+
+\begin{equation}
+	\begin{split}
+		p\left( \alpha,y_0,y(t_n),...,y(t_1) \right) &= p\left( y(t_n)|\alpha,y0,y(t_{i-1},...,y(t_1)) \right) \\ &\cdot p\left( \alpha,y_0,y(t_{n-1}),...,y(t_1) \right)
+	\end{split}
+\end{equation}
+
+These operations can be continued repetitively until we get
+
+\begin{equation}
+	p\left( \alpha,y_0,y(t_n),...,y(t_1) \right) = p\left( \alpha,y_0 \right) \prod_{i=1}^{n} p\left( \alpha,y_0,y(t_{n-1}),...,y(t_1) \right)
+\end{equation}
+
+Examination of Equation \ref{EQ: Measurment_noise} shows that $\textbf{Y}(t_i)$ depends only on $t_i$, $y_0$, $\alpha$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement.
+Consequently, we can write
+
+\begin{equation}
+	p\left( y(t_i)|\alpha,y_0, y(t_{i-1}),...,y(t_1) \right) = p\left( y(t_i)|\alpha,y_0 \right)
+\end{equation}
+
+provided Equation \ref{EQ: Measurment_noise} is observed as a constraint. The desired joint conditional probability function is thus
+
+\begin{equation}
+	p\left( \alpha,y_0|y(t_n),...,y(t_1) \right) = \cfrac{p\left( \alpha,y_0 \right) \prod_{i=1}^{n} p\left( y(t_i)|\alpha,y_0 \right) }{p\left( y(t_n),...,y(t_1) \right)}
+\end{equation}
+
+The function to be maximized will be the logarithm of the likelihood function $L = p\left( \alpha,y_0, y(t_n),...,y(t_1) \right)$ constrained by equation \ref{EQ: Measurment_noise}, which can be written as $\ln(L)$ plus the Lagrangian multipliers $\lambda(t_k)$ times the constraint function, or
+
+\begin{equation} \label{EQ: MLE_Lagrangian}
+	\begin{split}
+		L^* \equiv \ln p\left( \alpha,y_0 \right) + \sum_{i=1}^{n} \left\{ \ln p(y(t_i)|\alpha,y_0) \right. \\
+		\left. + \lambda^T \cdot \left[ y(t_i) - \Psi\left( \alpha,y_0,t_i \right) - \epsilon(t_i) \right] \right\} \\ - \ln \left[ p\left( y(t_n),...,y(t_1) \right) \right]
+	\end{split}
+\end{equation}
+
+By assumption of the relation of Equation \ref{EQ: Measurment_noise}
+
+\begin{equation} \label{EQ: Noise_prob}
+	p\left( y(t_i) | \alpha,y_0 \right) = p\left( \epsilon(t_i) \right)
+\end{equation}
+
+and specially
+
+\begin{equation} \label{EQ: Noise_prob_norm}
+	p\left( \epsilon(t_i) \right) = \cfrac{1}{ (2\pi)^{v/2} |\Gamma(t_i)|^{1/2} } \exp \left[ -\cfrac{1}{2}\epsilon(t_i) \left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \right]
+\end{equation}
+where $|\Gamma|$ is the det$~\Gamma$, and $\Gamma$ is the covariance matrix of $\epsilon$, i.e., of the response.
+
+After Equation \ref{EQ: Noise_prob} is substituted into Equation \ref{EQ: MLE_Lagrangian}, and $L^*$ is differentiated with respect to each of the estimated and $\epsilon(t_i)$, and the resulting expression is equated to zero, we get
+
+ \begin{subequations} \label{EQ: MLE_Lag_diff}
+	\begin{alignat}{2}
+		\cfrac{\partial L^*}{\partial y_0} &= \cfrac{\partial}{\partial y_0} \ln p(\alpha,y_0) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial y_0} \Psi(\alpha, y_0,t_i) = 0^T \\
+		\cfrac{\partial L^*}{\partial \alpha} &= \cfrac{\partial}{\partial \alpha} \ln p(\alpha,y_0) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial \alpha} \Psi(\alpha, y_0,t_i) =0 \\
+		\cfrac{\partial L^*}{\partial \epsilon(t_i)} &= \cfrac{\partial}{\partial \epsilon(t_i)} \ln p(\epsilon(t_i)) - \lambda^T(t_i) = 0^T
+	\end{alignat}
+ \end{subequations}
+
+Substitution of Equation \ref{EQ: Noise_prob_norm} into the last Equation of \ref{EQ: MLE_Lag_diff} makes it possible to solve for $\lambda(t_i)$:
+
 \begin{align}
-	x &= [x[0], x[1], \dots, x[N-1] ]^T, &&x \in \mathbb{R}^N \\
-	\theta &= [\theta_0, \theta_1, \dots, \theta_M ]^T,  &&\theta \in \mathbb{R}^M
+	\lambda(t_i) &= -\left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \nonumber \\
+	&= -\left( \Gamma(t_i) \right)^{-1} \left[ \textbf{Y}(t_i) - \Psi(\alpha,y_0,t_i) \right]
 \end{align}
 
-where $N$ is the number of samples and $M$ is the number of parameter to estimation.
+and to eliminate $\lambda(t_i)$ from the first two equations of \ref{EQ: MLE_Lag_diff}.
 
-The continuous probability density function (pdf) or its discrete counterpart, the probability mass function (pmf), of the underlying distribution that generated the data must be stated conditional on the values of the parameters: $p(x|\theta)$.
-It is also possible for the parameters themselves to have a probability distribution (e.g., Bayesian statistics).
-It is then necessary to define the Bayesian probability $\pi(\theta)$.
-After the model is formed, the goal is to estimate the parameters, with the estimates commonly denoted $\hat{\theta}$.
+For convenience we shall define a new column vector $\alpha^*$ in which all the elements of $\alpha$ are arranged as follows:
 
-One common estimator is the minimum mean squared error (MMSE) estimator, which utilizes the error between the estimated parameters and the actual value of the parameters as the basis for optimality.
-This error term is then squared and the expected value of this squared value is minimized for the MMSE estimator.
+\begin{equation}
+	\alpha^* = \begin{bmatrix}
+		\alpha_{1,1} & \alpha_{1,2} & \cdots & \alpha_{1,v} & \alpha_{2,1} & \cdots & \alpha_{2,v} & \cdots & \alpha_{v,v}
+	\end{bmatrix}^T	
+\end{equation}
 
-\subsection{Bayes theorem} \label{CH: Bayes_theorem}
-In probability theory and statistics, Bayes' theorem (alternatively Bayes' law or Bayes' rule; recently Bayes–Price theorem[1]: 44, 45, 46 and 67 ), named after Thomas Bayes, describes the probability of an event, based on prior knowledge of conditions that might be related to the event.[2] For example, if the risk of developing health problems is known to increase with age, Bayes' theorem allows the risk to an individual of a known age to be assessed more accurately (by conditioning it on their age) than simply assuming that the individual is typical of the population as a whole.
+Finally, we assume that $y_0$ and $\alpha^*$ are distributed by a joint normal distribution and that the prior  distribution are, respectively
 
-One of the many applications of Bayes' theorem is Bayesian inference, a particular approach to statistical inference.
-When applied, the probabilities involved in the theorem may have different probability interpretations.
-With Bayesian probability interpretation, the theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
-Bayesian inference is fundamental to Bayesian statistics.
+\begin{subequations} \label{EQ: MLE_Priors}
+	\begin{align}
+		&p\left( \alpha^* \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{\alpha^*}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( \alpha^* - \alpha^{*(0)} \right)^T \Omega_{\alpha^*}^{-1} \left( \alpha^* - \alpha^{*(0)} \right) \right] \\
+		&p\left( y_0 \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{y_0}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( y_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} \left( y_0 - y_0^{(0)} \right) \right] 
+	\end{align}
+\end{subequations}
+where $\Omega$'s are the respective covariance matrices for $\alpha^*$ and $y_0$, and the subscript $(0)$ designates the prior estimated of $\alpha^*$ and $y_0$.
+If we assume that $\alpha^*$ and $y_0$ are independent
 
-\subsection{Maximum likelihood estimation} \label{CH: MLE}
-\subsection{Maximum a posteriori} \label{CH: MAP}
-\subsection{Bayesian inference} \label{CH: Bayesian_inference}
+\begin{equation}
+	\ln p(\alpha^*,y_0) = \ln p(\alpha^*) + \ln p(y_0)
+\end{equation}
+
+Introduction of the prior distributions, Equations \ref{EQ: MLE_Priors}, plus the expression for $\lambda(t_i)$ into the first two equations of \ref{EQ: MLE_Lag_diff} gives the final equations from which the estimators of $\alpha^*$ and $y_0$ can be obtained:
+
+\begin{subequations} 
+	\begin{align}
+	-\left( \hat{y}_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} &+ \sum_{i=1}^{n}\left[ \textbf{Y}(t_i) - \Psi\left( \hat{\alpha}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \nonumber \\ 
+	&\cdot \cfrac{\partial}{\partial y_0} \Psi\left( \hat{\alpha}, \hat{y}, t_i \right) = 0^T \\
+	-\left( \hat{\alpha}^* - \alpha^{*(0)} \right)^T \Omega_{\alpha^*}^{-1} &+ \sum_{i=1}^{n}\left[ \textbf{Y}(t_i) - \Psi\left( \hat{\alpha}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \nonumber \\
+	&\cdot \cfrac{\partial}{\partial \alpha^*} \Psi\left( \hat{\alpha}, \hat{y}, t_i \right) = 0^T \nonumber \\
+	\end{align}
+\end{subequations}
+where the overlay caret denotes estimated parameters.
+
+Note that under the assumption that the elements of $\Omega$ are essentially infinite (prior knowledge is diffuse), the elements of $\Omega^-1$ are zero, the equations for the maximum likelihood estimates coincide with those for the least squares estimates, and the same calculations for precision in the estimates apply.
+
+\hrule
+
+For some models, these equations can be explicitly solved for $\hat{\alpha}^*$ and $\hat{y}$ but in general no closed-form solution to the maximization problem is known or available, and an MLE can only be found via numerical optimization.
+Under the assumption of normality, the lack of prior knowledge about the parameters and known initial conditions, the optimization problem is defined as follow:
+
+\begin{equation}
+	\hat{\alpha} = \arg \max_{\alpha \in \Theta} L = \arg \max_{\alpha \in \Theta} p(\alpha|y(t_1),y(t_2),...,y(t_n))
+\end{equation}
+
+Intuitively, this selects the parameter values that make the observed data most probable.
+The specific value $\hat{\alpha}$ that maximizes the likelihood function $L$ is called the maximum likelihood estimate.
+Further, if the function $\hat{\alpha}:\mathbb{R}\rightarrow\Theta$ so defined is measurable, then it is called the maximum likelihood estimator.
+
+If the random samples $y(t_1)$, $y(t_2)$,...,$y(t_n)$ come from a normal distribution with unknown mean $\hat{\alpha}$ and variance $\sigma^2$, then the joint probability function can be written as
+
+\begin{equation}
+	p(\alpha|y(t_i)) = \cfrac{1}{\sqrt{2\pi\sigma}}\exp\left[-\cfrac{ \left( \textbf{Y}(t_i) - \Psi\left( \hat{\alpha}, \hat{y}, t_i \right) \right)^2}{2\sigma}\right]
+\end{equation}
+
+Then the likelihood function is defined as follow:
+
+\begin{multline} 
+	L =\prod\limits_{i=1}^n p(\alpha|y(t_i))= \\ \sigma^{-n/2}(2\pi)^{-n/2}\exp\left[-\cfrac{1}{2\sigma}\sum\limits_{i=1}^n \left( \textbf{Y}(t_i) - \Psi\left( \hat{\alpha}, \hat{y}, t_i \right) \right)^2\right]
+\end{multline}
+
+By taking the ln of the likelihood function, the final form of a cost function is obtained:
+
+\begin{equation} 
+	\ln L=-\cfrac{n}{2}\ln\sigma-\cfrac{n}{2}\ln(2\pi)-\cfrac{\sum\limits_{i=1}^n \left( \textbf{Y}(t_i) - \Psi\left( \hat{\alpha}, \hat{y}, t_i \right) \right)^2}{2\sigma}
+\end{equation}
 

### 2022-05-31 SFE-report/Paramter_fitting.tex
31.05

@@
 
-If the estimated parameter $\hat{\alpha}$ replaces the model parameter $\alpha$, the residue error is $\textbf{E} = Y(t) - \hat{Y}(t)$.
-The objective in parameter estimation is to obtain the "best" estimate of $\alpha$ based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$.
+If the estimated parameter $\hat{\theta}$ replaces the model parameter $\theta$, the residue error is $\textbf{E} = Y(t) - \hat{Y}(t)$.
+The objective in parameter estimation is to obtain the "best" estimate of $\theta$ based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$.
 
-We assume that $x(t)$ is given \textit{a priori} but the $\textbf{y}_0$ and $\alpha$ are to be estimated over the time interval $0 \leq t \leq t_n$ from discrete observation described by the following relation:
+We assume that $x(t)$ is given \textit{a priori} but the $\textbf{y}_0$ and $\theta$ are to be estimated over the time interval $0 \leq t \leq t_n$ from discrete observation described by the following relation:
 
@@
 \begin{equation} \label{EQ: Measurment_noise}
-	\textbf{Y}(t_i) = \Psi(\alpha, y_0, t_i) + \epsilon(t_i)
+	\textbf{Y}(t_i) = \Psi(\theta, y_0, t_i) + \epsilon(t_i)
 \end{equation}
@@
 Each time it has been associated with the (joint) normal distribution because of mathematical convenience.
-Consider the joint probability density function (the likelihood function) $p(\alpha, y_0|y(t_1),y(t_2),...,y(t_n))$ for $\alpha$ and $y_0$ if a maximum of this function over all choices of $y_0$ and $\alpha$ can be found, the estimates so obtained are maximum likelihood estimates.
+Consider the joint probability density function (the likelihood function) $p(\theta, y_0|y)$ for random sample $y = y(t_1),y(t_2),...,y(t_n)$, parameter $\theta$ and initial condition $y_0$ if a maximum of this function over all choices of $y_0$ and $\theta$ can be found, the estimates so obtained are maximum likelihood estimates.
 The conditions at the maximum can be evolved incorporating prior information as follows.
 
-The posterior probability density $p(\alpha,y_0|y(1),y(2),...,y(t_n))$ can be expressed as the ratio of two probability densities if we make use of the analog for continuous variables of Equation \ref{EQ: Probabiltiy_independet_b}:
+The posterior probability density $p(\theta,y_0|y)$ can be expressed as the ratio of two probability densities if we make use of the analog for continuous variables of Equation \ref{EQ: Probabiltiy_independet_b}:
 
 \begin{equation} \label{EQ: Posterior_distribution}
-	p\left( \alpha,y_0|y(t_n,...,y(1)) \right) = \cfrac{p\left( \alpha, y_0, y(t_n),...,y(t_1) \right)}{p\left( y(t_n),...,y(t_1) \right)}
+	p\left( \theta,y_0|y \right) = \cfrac{p\left( \theta, y_0, y \right)}{p\left( y \right)}
 \end{equation}
@@
 	\begin{split}
-		p\left( \alpha,y_0,y(t_n),...,y(t_1) \right) &= p\left( y(t_n)|\alpha,y0,y(t_{i-1},...,y(t_1)) \right) \\ &\cdot p\left( \alpha,y_0,y(t_{n-1}),...,y(t_1) \right)
+		p\left( \theta,y_0,y \right) &= p\left( y(t_n)|\theta,y_0,y(t_{n-1}),...,y(t_1) \right) \\ &\cdot p\left( \theta,y_0,y(t_{n-1}),...,y(t_1) \right)
 	\end{split}
@@
 \begin{equation}
-	p\left( \alpha,y_0,y(t_n),...,y(t_1) \right) = p\left( \alpha,y_0 \right) \prod_{i=1}^{n} p\left( \alpha,y_0,y(t_{n-1}),...,y(t_1) \right)
+	p\left( \theta,y_0,y \right) = p\left( \theta,y_0 \right) \prod_{i=1}^{n} p\left( \theta,y_0|y \right)
 \end{equation}
 
-Examination of Equation \ref{EQ: Measurment_noise} shows that $\textbf{Y}(t_i)$ depends only on $t_i$, $y_0$, $\alpha$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement.
+Examination of Equation \ref{EQ: Measurment_noise} shows that $\textbf{Y}(t_i)$ depends only on $t_i$, $y_0$, $\theta$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement.
 Consequently, we can write
@@
 \begin{equation}
-	p\left( y(t_i)|\alpha,y_0, y(t_{i-1}),...,y(t_1) \right) = p\left( y(t_i)|\alpha,y_0 \right)
+	p\left( y(t_i)|\theta,y_0, y(t_{i-1}),...,y(t_1) \right) = p\left( y(t_i)|\theta,y_0 \right)
 \end{equation}
@@
 \begin{equation}
-	p\left( \alpha,y_0|y(t_n),...,y(t_1) \right) = \cfrac{p\left( \alpha,y_0 \right) \prod_{i=1}^{n} p\left( y(t_i)|\alpha,y_0 \right) }{p\left( y(t_n),...,y(t_1) \right)}
+	p\left( \theta,y_0|y \right) = \cfrac{p\left( \theta,y_0 \right) \prod_{i=1}^{n} p\left( y(t_i)|\theta,y_0 \right) }{p\left( y \right)}
 \end{equation}
 
-The function to be maximized will be the logarithm of the likelihood function $L = p\left( \alpha,y_0, y(t_n),...,y(t_1) \right)$ constrained by equation \ref{EQ: Measurment_noise}, which can be written as $\ln(L)$ plus the Lagrangian multipliers $\lambda(t_k)$ times the constraint function, or
+The function to be maximized will be the logarithm of the likelihood function $L = p\left( \theta,y_0| y(t_n),...,y(t_1) \right)$ constrained by equation \ref{EQ: Measurment_noise}, which can be written as $\ln(L)$ plus the Lagrangian multipliers $\lambda(t_k)$ times the constraint function, or
 
@@
 	\begin{split}
-		L^* \equiv \ln p\left( \alpha,y_0 \right) + \sum_{i=1}^{n} \left\{ \ln p(y(t_i)|\alpha,y_0) \right. \\
-		\left. + \lambda^T \cdot \left[ y(t_i) - \Psi\left( \alpha,y_0,t_i \right) - \epsilon(t_i) \right] \right\} \\ - \ln \left[ p\left( y(t_n),...,y(t_1) \right) \right]
+		L^* \equiv \ln p\left( \theta,y_0 \right) + \sum_{i=1}^{n} \left\{ \ln p(y(t_i)|\theta,y_0) \right. \\
+		\left. + \lambda^T \cdot \left[ y(t_i) - \Psi\left( \theta,y_0,t_i \right) - \epsilon(t_i) \right] \right\} \\ - \ln \left[ p\left( y \right) \right]
 	\end{split}
@@
 \begin{equation} \label{EQ: Noise_prob}
-	p\left( y(t_i) | \alpha,y_0 \right) = p\left( \epsilon(t_i) \right)
+	p\left( y(t_i) | \theta,y_0 \right) = p\left( \epsilon(t_i) \right)
 \end{equation}
@@
 \begin{equation} \label{EQ: Noise_prob_norm}
-	p\left( \epsilon(t_i) \right) = \cfrac{1}{ (2\pi)^{v/2} |\Gamma(t_i)|^{1/2} } \exp \left[ -\cfrac{1}{2}\epsilon(t_i) \left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \right]
+	p\left( \epsilon(t_i) \right) = \cfrac{1}{ (2\pi)^{v/2} |\Gamma(t_i)|^{1/2} } \exp \left[ -\cfrac{1}{2}\epsilon^T(t_i) \left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \right]
 \end{equation}
@@
 	\begin{alignat}{2}
-		\cfrac{\partial L^*}{\partial y_0} &= \cfrac{\partial}{\partial y_0} \ln p(\alpha,y_0) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial y_0} \Psi(\alpha, y_0,t_i) = 0^T \\
-		\cfrac{\partial L^*}{\partial \alpha} &= \cfrac{\partial}{\partial \alpha} \ln p(\alpha,y_0) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial \alpha} \Psi(\alpha, y_0,t_i) =0 \\
-		\cfrac{\partial L^*}{\partial \epsilon(t_i)} &= \cfrac{\partial}{\partial \epsilon(t_i)} \ln p(\epsilon(t_i)) - \lambda^T(t_i) = 0^T
+		\cfrac{\partial L^*}{\partial y_0} &= \cfrac{\partial}{\partial y_0} \ln p(\theta,y_0) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial y_0} \Psi(\theta, y_0,t_i) = 0^T \\
+		\cfrac{\partial L^*}{\partial \theta} &= \cfrac{\partial}{\partial \theta} \ln p(\theta,y_0) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial \theta} \Psi(\theta, y_0,t_i) =0 \\
+		\cfrac{\partial L^*}{\partial \epsilon(t_i)} &= \cfrac{\partial}{\partial \epsilon^T(t_i)} \ln p(\epsilon(t_i)) - \lambda^T(t_i) = 0^T
 	\end{alignat}
@@
 	\lambda(t_i) &= -\left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \nonumber \\
-	&= -\left( \Gamma(t_i) \right)^{-1} \left[ \textbf{Y}(t_i) - \Psi(\alpha,y_0,t_i) \right]
+	&= -\left( \Gamma(t_i) \right)^{-1} \left[ \textbf{Y}(t_i) - \Psi(\theta,y_0,t_i) \right]
 \end{align}
@@
 
-For convenience we shall define a new column vector $\alpha^*$ in which all the elements of $\alpha$ are arranged as follows:
+For convenience we shall define a new column vector $\theta^*$ in which all the elements of $\theta$ are arranged as follows:
 
 \begin{equation}
-	\alpha^* = \begin{bmatrix}
-		\alpha_{1,1} & \alpha_{1,2} & \cdots & \alpha_{1,v} & \alpha_{2,1} & \cdots & \alpha_{2,v} & \cdots & \alpha_{v,v}
+	\theta^* = \begin{bmatrix}
+		\theta_{1,1} & \theta_{1,2} & \cdots & \theta_{1,v} & \theta_{2,1} & \cdots & \theta_{2,v} & \cdots & \theta_{v,v}
 	\end{bmatrix}^T	
@@
 
-Finally, we assume that $y_0$ and $\alpha^*$ are distributed by a joint normal distribution and that the prior  distribution are, respectively
+Finally, we assume that $y_0$ and $\theta^*$ are distributed by a joint normal distribution and that the prior distribution are, respectively
 
@@
 	\begin{align}
-		&p\left( \alpha^* \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{\alpha^*}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( \alpha^* - \alpha^{*(0)} \right)^T \Omega_{\alpha^*}^{-1} \left( \alpha^* - \alpha^{*(0)} \right) \right] \\
+		&p\left( \theta^* \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{\theta^*}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( \theta^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} \left( \theta^* - \theta^{*(0)} \right) \right] \\
 		&p\left( y_0 \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{y_0}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( y_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} \left( y_0 - y_0^{(0)} \right) \right] 
@@
 \end{subequations}
-where $\Omega$'s are the respective covariance matrices for $\alpha^*$ and $y_0$, and the subscript $(0)$ designates the prior estimated of $\alpha^*$ and $y_0$.
-If we assume that $\alpha^*$ and $y_0$ are independent
+where $\Omega$'s are the respective covariance matrices for $\theta^*$ and $y_0$, and the subscript $(0)$ designates the prior estimated of $\theta^*$ and $y_0$.
+If we assume that $\theta^*$ and $y_0$ are independent
 
 \begin{equation}
-	\ln p(\alpha^*,y_0) = \ln p(\alpha^*) + \ln p(y_0)
+	\ln p(\theta^*,y_0) = \ln p(\theta^*) + \ln p(y_0)
 \end{equation}
 
-Introduction of the prior distributions, Equations \ref{EQ: MLE_Priors}, plus the expression for $\lambda(t_i)$ into the first two equations of \ref{EQ: MLE_Lag_diff} gives the final equations from which the estimators of $\alpha^*$ and $y_0$ can be obtained:
+Introduction of the prior distributions, Equations \ref{EQ: MLE_Priors}, plus the expression for $\lambda(t_i)$ into the first two equations of \ref{EQ: MLE_Lag_diff} gives the final equations from which the estimators of $\theta^*$ and $y_0$ can be obtained:
 
@@
 	\begin{align}
-	-\left( \hat{y}_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} &+ \sum_{i=1}^{n}\left[ \textbf{Y}(t_i) - \Psi\left( \hat{\alpha}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \nonumber \\ 
-	&\cdot \cfrac{\partial}{\partial y_0} \Psi\left( \hat{\alpha}, \hat{y}, t_i \right) = 0^T \\
-	-\left( \hat{\alpha}^* - \alpha^{*(0)} \right)^T \Omega_{\alpha^*}^{-1} &+ \sum_{i=1}^{n}\left[ \textbf{Y}(t_i) - \Psi\left( \hat{\alpha}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \nonumber \\
-	&\cdot \cfrac{\partial}{\partial \alpha^*} \Psi\left( \hat{\alpha}, \hat{y}, t_i \right) = 0^T \nonumber \\
+	-\left( \hat{y}_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} &+ \sum_{i=1}^{n}\left[ \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \nonumber \\ 
+	&\cdot \cfrac{\partial}{\partial y_0} \Psi\left( \hat{\theta}, \hat{y}, t_i \right) = 0^T \\
+	-\left( \hat{\theta}^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} &+ \sum_{i=1}^{n}\left[ \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \nonumber \\
+	&\cdot \cfrac{\partial}{\partial \theta^*} \Psi\left( \hat{\theta}, \hat{y}, t_i \right) = 0^T \nonumber \\
 	\end{align}
@@
 
-For some models, these equations can be explicitly solved for $\hat{\alpha}^*$ and $\hat{y}$ but in general no closed-form solution to the maximization problem is known or available, and an MLE can only be found via numerical optimization.
-Under the assumption of normality, the lack of prior knowledge about the parameters and known initial conditions, the optimization problem is defined as follow:
+For some models, these equations can be explicitly solved for $\hat{\theta}^*$ and $\hat{y}$ but in general no closed-form solution to the maximization problem is known or available, and an MLE can only be found via numerical optimization.
+Under the assumption of normality, the lack of prior knowledge about the parameters $\theta^{(0)}$ and known initial conditions $y_0$, the optimization problem is defined as follow:
 
 \begin{equation}
-	\hat{\alpha} = \arg \max_{\alpha \in \Theta} L = \arg \max_{\alpha \in \Theta} p(\alpha|y(t_1),y(t_2),...,y(t_n))
+	\hat{\theta}_{MLE} = \arg \max_{\theta \in \Theta} L = \arg \max_{\theta \in \Theta} p(\theta|y)
 \end{equation}
@@
 Intuitively, this selects the parameter values that make the observed data most probable.
-The specific value $\hat{\alpha}$ that maximizes the likelihood function $L$ is called the maximum likelihood estimate.
-Further, if the function $\hat{\alpha}:\mathbb{R}\rightarrow\Theta$ so defined is measurable, then it is called the maximum likelihood estimator.
+The specific value $\hat{\theta}$ that maximizes the likelihood function $L$ is called the maximum likelihood estimate.
+Further, if the function $\hat{\theta}:\mathbb{R}\rightarrow\Theta$ so defined is measurable, then it is called the maximum likelihood estimator.
 
-If the random samples $y(t_1)$, $y(t_2)$,...,$y(t_n)$ come from a normal distribution with unknown mean $\hat{\alpha}$ and variance $\sigma^2$, then the joint probability function can be written as
+If the random samples $y(t_1)$, $y(t_2)$,...,$y(t_n)$ come from a normal distribution with unknown mean $\hat{\theta}$ and variance $\sigma^2$, then the joint probability function can be written as
 
 \begin{equation}
-	p(\alpha|y(t_i)) = \cfrac{1}{\sqrt{2\pi\sigma}}\exp\left[-\cfrac{ \left( \textbf{Y}(t_i) - \Psi\left( \hat{\alpha}, \hat{y}, t_i \right) \right)^2}{2\sigma}\right]
+	p(\theta|y(t_i)) = \cfrac{1}{\sqrt{2\pi\sigma}}\exp\left[-\cfrac{ \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}\right]
 \end{equation}
@@
 \begin{multline} 
-	L =\prod\limits_{i=1}^n p(\alpha|y(t_i))= \\ \sigma^{-n/2}(2\pi)^{-n/2}\exp\left[-\cfrac{1}{2\sigma}\sum\limits_{i=1}^n \left( \textbf{Y}(t_i) - \Psi\left( \hat{\alpha}, \hat{y}, t_i \right) \right)^2\right]
+	L =\prod\limits_{i=1}^n p(\theta|y(t_i)) = \\ (2\pi\sigma)^{-n/2}\exp\left[-\cfrac{1}{2\sigma}\sum\limits_{i=1}^n \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2\right]
 \end{multline}
 
-By taking the ln of the likelihood function, the final form of a cost function is obtained:
+By taking the ln of the likelihood function, the final form of the cost function is obtained:
 
 \begin{equation} 
-	\ln L=-\cfrac{n}{2}\ln\sigma-\cfrac{n}{2}\ln(2\pi)-\cfrac{\sum\limits_{i=1}^n \left( \textbf{Y}(t_i) - \Psi\left( \hat{\alpha}, \hat{y}, t_i \right) \right)^2}{2\sigma}
+	\ln L=-\cfrac{n}{2}\ln\sigma-\cfrac{n}{2}\ln(2\pi)-\cfrac{\sum\limits_{i=1}^n \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}
 \end{equation}
+
+\subsection{Maximum a posteriori estimation}
+
+As already discussed, the prior information about the estimated parameters can be incorporated in to the maximum likelihood estimator to form a maximum a posteriori probability (MAP) estimate.
+MAP can be used to obtain a point estimate of an unobserved quantity on the basis of empirical data.
+MAP estimation can therefore be seen as a regularization of maximum likelihood estimation.
+MLE and MAP can be connected by Bayes' rule:
+
+\begin{equation} 
+	\begin{split}
+		{\bf \hat{\theta}_{\text{MAP}}} &= \arg\max_{\bf \theta} p(\theta | y) \\
+		&= \arg\max_{\bf \theta} \frac{p(y | \theta) p(\theta)}{p(y)} \\
+		&= \arg\max_{\bf \theta} p(y | \theta) p(\theta) \\
+		&= \arg\max_{\bf \theta} \ln(p(y | \theta) p(\theta)) \\
+		&= \arg\max_{\bf \theta} \ln p(y | \theta) + \ln p(\theta)
+	\end{split}
+\end{equation}
+
+Notice that we can get rid of the evidence term $P(y)$ because it's constant with respect to the maximization and also take the ln of the inner function because it's monotonically increasing.
+
+We assume the normal distribution of random samples, with identical variance and the prior distribution of $\theta$ given by $\mathcal{N}(\theta^{(0)},\,\sigma_\theta^{2})$.
+The likelihood function to be maximized can be written as
+
+\begin{equation} \label{EQ: MAP_L2}
+	\begin{split}
+	&\arg\max_{\bf \theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2 }{2\sigma^2}}
+	+ \ln \prod_{j=0}^{p} \frac{1}{\sigma_\theta\sqrt{2\pi}}e^{-\frac{ \left( \hat{\theta} - \theta^{(0)} \right)^2}{2\sigma_\theta^2}} \right]  \\
+	&= \arg\max_{\bf \theta} \left[- \sum_{i=1}^{n} {\frac{\left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma^2}}
+	- \sum_{j=0}^{p} {\frac{\left( \hat{\theta} - \theta^{(0)} \right)^2}{2\sigma_\theta^2}} \right]\\
+	&= \arg\min_{\bf \theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2
+	+ \frac{\sigma^2}{\sigma_\theta^2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^{(0)} \right)^2 \right] \\
+	&= \arg\min_{\bf \theta} \left[ \sum_{i=1}^{n} \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2 + \lambda_{L2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^{(0)} \right)^2 \right]
+	\end{split}
+\end{equation}
+
+Notice that we dropped some of the constants (with respect to $\theta$) and factored to simplify the expression.
+You can see this is the same expression as Equation \ref{EQ: MAP_L2} (L2 Regularization) with $\lambda_{L2}$.
+We can adjust the amount of regularization we want by changing $\lambda_{L2}$.
+Equivalently, we can adjust how much we want to weight the priors carry on the coefficients ($\theta$).
+If we have a very small variance (large $\lambda_{L2}$) then the coefficients will be very close to 0; if we have a large variance (small $\lambda_{L2}$) then the coefficients will not be affected much (similar to as if we didn't have any regularization).
 

### 2022-05-31 SFE-report/Paramter_fitting.tex
31.05

@@
 
+{\footnotesize
 \begin{equation}
 	P\{A_i|B\} = \cfrac{P\{B|A_i\}P\{A_i\}}{P\{B\}}
-\end{equation}
+\end{equation} }
 
@@
 
+{\footnotesize
 \begin{equation} \label{EQ: Bayes_discrit}
 	P\{A_i|B\} = \cfrac{P\{B|A_i\}P\{A_i\}}{ \sum_{i=1}^{n} P\{B|A_i\} P\{A_i\} }
-\end{equation}
+\end{equation} }
 
@@
 
+{\footnotesize
 \begin{equation} \label{EQ: Bayes_continous}
 	p\left( \theta|X=\textbf{x} \right) = p\left( \theta|\textbf{x} \right) = \cfrac{L\left( \theta|\textbf{x} \right) p(\theta)}{\int_{-\infty}^{+\infty} L\left( \theta|\textbf{x} \right) p(\theta) d\theta}
-\end{equation}
+\end{equation} }
 
@@
 
+{\footnotesize
 \begin{equation}
 	\int_{-\infty}^{+\infty} p\left( \textbf{x}|\theta \right) p(\theta) d\theta = p(\textbf{x})
-\end{equation}
+\end{equation} }
 
@@
 
+{\footnotesize
 \begin{equation}
 	p\left( \theta|\textbf{x} \right) = \cfrac{L\left( \theta|\textbf{x} \right)}{\int_{-\infty}^{+\infty} L\left( \theta|\textbf{x}\right) d\theta}
-\end{equation}
+\end{equation} }
 
@@
 
+	{\footnotesize
 	\begin{equation}
 		P\left( A_1, \text{or~} A_2,..., \text{or~} A_n \right) = \sum_{i=1}^{n} P\left( A_i \right)
-	\end{equation}
+	\end{equation} }
 
 	Very often we let
+
+	{\footnotesize
 	\begin{equation}
 		\sum_{i=1}^{n} P\left( A_i \right) = 1
-	\end{equation}
+	\end{equation} }
 
@@
 
+	{\footnotesize
 	\begin{equation}
 		\sum_{i=1}^{n} q = nq = 1 \qquad \text{or} \qquad  q=\cfrac{1}{n} = P\left( A_i \right)
-	\end{equation}
+	\end{equation} }
 
@@
 
+	{\footnotesize
 	\begin{equation}
 		P\left( A_1 \cup A_2 \cup ... \cup A_n \right) = P(A_1) + P(A_2) + ... + P(A_n)
-	\end{equation}
+	\end{equation} }
 
@@
 
+	{\footnotesize
 	\begin{equation}
 		P\left( A \text{~and~} B\right) = P(A)P(B)
-	\end{equation}
+	\end{equation} }
 
@@
 
+	{\footnotesize
 	\begin{equation} \label{EQ: Probabiltiy_independet_a}
 		P\left( A \cap B  \right) = P(A)P(B)
-	\end{equation}
+	\end{equation} }
 
@@
 
+	{\footnotesize
 	\begin{equation} \label{EQ: Probabiltiy_independet_b}
 		P\left(A|B\right) = \cfrac{P\left( A \cap B \right)}{P(B)}
-	\end{equation}
+	\end{equation} }
 
@@
 
+	{\footnotesize
 	 \begin{subequations}
@@
 		\end{alignat}
-	\end{subequations}
+	\end{subequations} }
 
@@
 
+	{\footnotesize
 	\begin{equation}
@@
 		\end{split}
-	\end{equation}
+	\end{equation} }
 
@@
 
+	{\footnotesize
 	\begin{equation}
 		P(A) + P(B) - P(A \cap B) = P(A \cup B)
-	\end{equation}
+	\end{equation} }
 
@@
 
+{\footnotesize
 \begin{equation}
 	Y(t) = y(t) + \epsilon(t)
-\end{equation}
+\end{equation} }
 
@@
 
+{\footnotesize
 \begin{equation}
 	\textbf{Y}(t_i) = h(t_i)y(t_i) + \epsilon(t_i) \qquad 1 \leq i \leq n
-\end{equation}
-
+\end{equation} }
 where $\textbf{Y}(t_i)$ is an $n \times 1$ column vector, $h(t_i)$ is an $n \times v$ matrix given \textit{a priori}, and $\epsilon (t_i)$ is an $x \times 1$ column vector ("noise" vector) whose elements are the unobservable errors.
@@
 
+{\footnotesize
 \begin{equation} \label{EQ: Measurment_noise}
 	\textbf{Y}(t_i) = \Psi(\theta, y_0, t_i) + \epsilon(t_i)
-\end{equation}
+\end{equation}}
 where $\Psi$ is the matrix of functions.
@@
 
+{\footnotesize
 \begin{equation}
 	\cfrac{d\textbf{Y}}{dt} = \cfrac{dy}{dt} + \epsilon
-\end{equation}
+\end{equation} }
 
@@
 
+{\footnotesize
 \begin{equation}
 	\phi =  \cfrac{1}{2} \int_{0}^{t_f}  \left[ \textbf{Y} - \Psi \right]^T \Gamma^{-1} \left[ \textbf{Y} - \Psi \right] dt
-\end{equation}
-
+\end{equation} }
 where $\Gamma$ is the covariance matrix (or perhaps a matrix of appropriate weights), and $\phi$ is the time integrated value of the error squared ("integral squared error").
@@
 
+{\footnotesize
 \begin{equation}
 	\phi = \cfrac{1}{2} \sum_{i=1}^{n} \left[ \textbf{Y}(t_i) - \Psi(t_i) \right]^T \Gamma^{-1} \left[ \textbf{Y}(t_i) - \Psi(t_i) \right] 
-\end{equation}
+\end{equation} }
 
 If $\Gamma$ is a diagonal matrix, $\phi$  becomes a "weighted least squares" criterion; if $\Gamma = \sigma^2 \textbf{I}$ where $\sigma$ is a standard deviation, $\phi$ is the "ordinary least squares" criterion.
+
+\subsection{Cumulative data}
+
+One characteristic feature of certain special experiments is the use of the same batch of materials for the entire series of measurements.
+If unobservable error in the first observation is designated as $\epsilon_1$, the second error observation $\epsilon_2'$ includes $\epsilon_1$ plus a random component introduced side from $\epsilon_1$, or $\epsilon_2' = \epsilon_1 + \epsilon_2$.
+The error in the third observation is $\epsilon_3' = \epsilon_1 + \epsilon_2 + \epsilon_3$, and so forth.
+\citet{Mandel1957} distinguished between the usually assumed type of independent measuring error in the dependent variable and a 'cumulative' or interval error in which each new observation includes the error of the previous observations.
+Cumulative errors, arising because of the fluctuations as a function of time in the process itself due to small changes in operating, are not independent - only the differences in measurment from one period to the next are independent.
+Thus, if we consider two model:
+
+{\footnotesize
+\begin{flalign*}
+	&\text{Model A - independent error:} &&\nonumber \\
+	Y_i &= \Psi(\theta, y_0, t_i) + \epsilon_i \qquad i = 1,2,...,n&& \\
+	&\text{Model B - cumulative data:}&& \nonumber \\
+	Y_j - Y_{j-1} &= \Psi(\theta, y_0, t_j) - \Psi(\theta, y_0, t_{j-1}) + \epsilon_j, \quad j = 1,2,...,n&& \\
+	&\text{or}&& \nonumber \\
+	Y_i = \sum_{j=1}^{i} &\left( Y_j - Y_{j-1} \right) = \sum_{j=1}^{i} \left( \Psi(\theta, y_0, t_j) - \Psi(\theta, y_0, t_{j-1}) \right) + \sum_{j=1}^{i} \epsilon_j &&
+\end{flalign*} }
 
@@
 
+{\footnotesize
 \begin{equation} \label{EQ: Posterior_distribution}
 	p\left( \theta,y_0|y \right) = \cfrac{p\left( \theta, y_0, y \right)}{p\left( y \right)}
-\end{equation}
+\end{equation} }
 
@@
 
+{\footnotesize
 \begin{equation}
@@
 	\end{split}
-\end{equation}
+\end{equation} }
 
@@
 
+{\footnotesize
 \begin{equation}
 	p\left( \theta,y_0,y \right) = p\left( \theta,y_0 \right) \prod_{i=1}^{n} p\left( \theta,y_0|y \right)
-\end{equation}
+\end{equation} }
 
@@
 
+{\footnotesize
 \begin{equation}
 	p\left( y(t_i)|\theta,y_0, y(t_{i-1}),...,y(t_1) \right) = p\left( y(t_i)|\theta,y_0 \right)
-\end{equation}
+\end{equation} }
 
@@
 
+{\footnotesize
 \begin{equation}
 	p\left( \theta,y_0|y \right) = \cfrac{p\left( \theta,y_0 \right) \prod_{i=1}^{n} p\left( y(t_i)|\theta,y_0 \right) }{p\left( y \right)}
-\end{equation}
+\end{equation} }
 
@@
 
+{\footnotesize
 \begin{equation} \label{EQ: MLE_Lagrangian}
@@
 	\end{split}
-\end{equation}
+\end{equation}}
 

### 2022-05-31 SFE - Copy/Arrhenius_Di.m

@@ -18,16 +18,16 @@ function [EA, D0] = Arrhenius_Di(T,D, R)
     %betah = inv(dT'*dT)*dT'*D';                            % Estimated coefficients
     %betah = betah(1); 
     %}
-%     TT = linspace(T(1),T(end));
-%     hold on
-%     plot(1./T,log(D),'o')
-%     plot(1./TT, P(1).*(1./TT) + P(2),'-')
-%     xlabel('1/T [1/K]','interpreter','latex')
-%     ylabel('$ln(Di) [m^2/s]$','interpreter','latex')
-%     R2 = 1 - (S.normr/norm(log(D) - mean(log(D))))^2;
-%     str = sprintf('$R^2 =$%.3f',R2);
-%     annotation('textbox',[.8 .6 .3 .3],'string',str,'FitBoxToText','on','EdgeColor','black','FontSize',15,'interpreter','latex')   
-%     hold off
-%     title(['Line Equation is y = F(x) = ',num2str(P(1)),'*x + ','(',num2str(P(2)),')'],'interpreter','latex');
-%     
+    TT = linspace(min(T),max(T));
+    hold on
+    plot(1./T,log(D),'o')
+    plot(1./TT, P(1).*(1./TT) + P(2),'-')
+    xlabel('1/T [1/K]','interpreter','latex')
+    ylabel('$ln(Di) [m^2/s]$','interpreter','latex')
+    R2 = 1 - (S.normr/norm(log(D) - mean(log(D))))^2;
+    str = sprintf('$R^2 =$%.3f',R2);
+    annotation('textbox',[.8 .6 .3 .3],'string',str,'FitBoxToText','on','EdgeColor','black','FontSize',15,'interpreter','latex')   
+    hold off
+    title(['Line Equation is y = F(x) = ',num2str(P(1)),'*x + ','(',num2str(P(2)),')'],'interpreter','latex');
+    
 end

### 2022-05-31 SFE - Copy/singleShooting_ParameterEstimation.m

@@ -10,7 +10,7 @@ OCP_solver = casadi.Opti();
 
 % http://www.diva-portal.se/smash/get/diva2:956377/FULLTEXT01.pdf
 nlp_opts = struct;
-%nlp_opts.ipopt.max_iter = 100;
+nlp_opts.ipopt.max_iter = 100;
 %nlp_opts.ipopt.acceptable_iter = 50;
 %nlp_opts.ipopt.acceptable_tol = 1e-6;
 %nlp_opts.ipopt.tol = 1e-7;
@@ -38,8 +38,8 @@ data = [zeros(1,OCP.N_Delay) data(1:end-OCP.N_Delay)];
 data = diff(data(1:OCP.N_Sample:end));
 
 %J = J + OCP.LS(data);
-%J = J + OCP.MSE(data,K(end));
-J = J + OCP.MAP(data,K(1),K(end));
+J = J + OCP.MSE(data,K(end));
+%J = J + OCP.MAP(data,K(1),K(end));
 
 % state constraints
 if ~isempty(OCP.x_lu)

### 2022-05-31 SFE - MegaFitting/CostFunction.m

@@ -1,8 +1,10 @@
-function [xout, kout] = singleShooting_ParameterEstimation(OCP, x0, u, yd, k0)
+function J = CostFunction(OCP, x0, u, k0,  parameters)
 
 %addpath('C:\Users\slicz\Desktop\Aalto\Matlab\SFE\casadi-windows-matlabR2016a-v3.5.1');
 %addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
 import casadi.*
+
+nstages = parameters{1};
 
 OCP_solver = casadi.Opti();
 
@@ -19,29 +21,23 @@ OCP_solver.solver('ipopt',nlp_opts)
 K = OCP_solver.variable(OCP.Nk);
 X = [MX(x0) zeros(OCP.Nx,OCP.N)];
 J = 0;
+
+yout = MX(zeros(OCP.Ny,OCP.N+1));   
+
+%g = @(x, u, y_old) modelSFE_out2(x, u, y_old, parameters, timeStep_in_sec);
+
 for j=1:OCP.N
     %J=J+OCP.L(U(:,j));
     X(:,j+1)=OCP.F(X(:,j),u(:,j),K);
-end
-J = J + OCP.Lf(X,yd);
-
-% for nx=1:OCP.Nx
-%     OCP_solver.subject_to(OCP.x_lu(nx,1)<=X(nx,:)<= OCP.x_lu(nx,2));
-% end
-% 
-% for nk=1:OCP.Nk
-%     OCP_solver.subject_to(OCP.k_lu(nk,1)<=K(nk,:)<= OCP.k_lu(nk,2));
-% end
-
-OCP_solver.minimize(J);
-OCP_solver.set_initial(K, k0);
-
-try
-    sol = OCP_solver.solve();
-    kout = sol.value(K);
-catch
-    kout = OCP_solver.debug.value(K);
+    %yout(:,j+1) = g(X(:,j+1), u(:,j), yout(:,j));
 end
 
-xout = 1;
-end
+%data = yy(1:N_Sample:end);
+data = X(3*nstages+1,:);
+data = [zeros(1,OCP.N_Delay) data(1:end-OCP.N_Delay)];
+data = diff(data(1:OCP.N_Sample:end));
+
+%J = J + OCP.LS(data);
+%J = J + OCP.MSE(data,K(end));
+J = J + OCP.MAP(data,K(1),K(end));
+

### 2022-05-31 SFE - MegaFitting/main_MegaFitting_SFE.m

@@ -4,7 +4,7 @@ clear all
 addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
 import casadi.*
 
-DATA = {'Data_40_200.mat', 'Data_50_200.mat', 'Data_40_300.mat', 'Data_50_300.mat'};
+DATA = {'Data_40_200.mat', 'Data_50_200.mat', 'Data_50_300.mat', 'Data_40_300.mat'};
 
 %% Parameters
 nstages = 5;                                                   %
@@ -71,16 +71,15 @@ A8_visc = -3.567559E-1;
 A9_visc =  3.180473E-2;
 
 sigma   = 1;
-sigma_km = 5;
+sigma_km = 2;
 mu_km    = 1;
-Di_slack = 7e-12;
+Di = 7e-12;
 Dx = 0.0001;
 
 %                 1        2    3    4    5  6     7   8   9   10  11  12   13   14   15      16       17    18    19    20    21    22      23        24      25        26       27      28       29        30        31       32       33       34      35       36        37      38       39       40      41        42       43      44   45   46
-parameters = {nstages, C0solid, V, epsi, dp, L, rho_s, km, mi, Tc, Pc, R, kappa, MW, EA_Di, betah_Di, CP_0, CP_A, CP_B, CP_C, CP_D, EA_km, betah_km, cpSolid, a_axial, b_axial, c_axial, A1_cond, A2_cond, A3_cond, A4_cond, A5_cond, A6_cond, A7_cond, A1_visc, A2_visc, A3_visc, A4_visc, A5_visc, A6_visc, A7_visc, A8_visc, A9_visc, Di_slack, Dx ,sigma };
+parameters = {nstages, C0solid, V, epsi, dp, L, rho_s, km, mi, Tc, Pc, R, kappa, MW, EA_Di, betah_Di, CP_0, CP_A, CP_B, CP_C, CP_D, EA_km, betah_km, cpSolid, a_axial, b_axial, c_axial, A1_cond, A2_cond, A3_cond, A4_cond, A5_cond, A6_cond, A7_cond, A1_visc, A2_visc, A3_visc, A4_visc, A5_visc, A6_visc, A7_visc, A8_visc, A9_visc, Di, Dx ,sigma };
 which_parameter= {15, 16, 22, 23, 25, 26, 27, 46};
[…]

### 2022-06-13 SFE-report/Paramter_fitting.tex
13.06

@@
 % Packages Configurations
+\usepackage{enumitem}
 % --------------------------------------------------------------------
@@
 $P\{A_i\}$ is denoted the \textit{prior probability}.
-	\item $P\{A_i|B\}$ is a measure of our degree of belief that event $A_i$ will occur or that hypothesis $A_i$ is true, given additional evidence $B$ pertinent ot the hypothesis.
+	\item $P\{A_i|B\}$ is a measure of our degree of belief that event $A_i$ will occur or that hypothesis $A_i$ is true, given additional evidence $B$ pertinent to the hypothesis.
 $P\{A_i|B\}$ is termed the \textit{posterior probability}.
@@
 For continuous variable, Bayes' theorem can be more conveniently expressed in terms of the probability density function rather than the probabilities themselves.
-Equation \ref{EQ: Bayes_discrit} can be expressed in terms of a set of observed values of the random variable $X$, \textbf{x} and unknown parameter $(s)\theta$ as
+Equation \ref{EQ: Bayes_discrit} can be expressed in terms of a set of observed values of the random variable $X$, the experimental data \textbf{x} and unknown parameter $\theta$ as
 
@@
 
-If the prior distribution is a uniform distribution, that is the prior distribution is a constant, the \ref{EQ: Bayes_continous} reduces to
+If the prior distribution is a uniform distribution, that is the prior distribution is a constant, the Equation \ref{EQ: Bayes_continous} reduces to
 
@@
 
-Conceptually, in the measurement equation the unobservable $\epsilon(t)$ is added to $y(t)$ to give the observable dependent variable $Y(t)$ defined as:
+Conceptually, the unobservable $\epsilon(t)$ is added to $y(t)$ to give the observable dependent variable $Y(t)$. For discrete observations:
+
+{\footnotesize
+	\begin{equation}
+		Y(t_i) = y(t_i) + \epsilon(t_i)
+\end{equation} }
+and for continuos variables:
 
@@
 
-If the estimated parameter $\hat{\theta}$ replaces the model parameter $\theta$, the residue error is $\textbf{E} = Y(t) - \hat{Y}(t)$.
+If the estimated parameter $\hat{\theta}$ replaces the model parameter $\theta$, the residue error is $\textbf{E} = Y(t) - \hat{Y}(t)$, where $\hat{Y}(t)$ is the predicted value of $Y_i$ at $x_i$.
 The objective in parameter estimation is to obtain the "best" estimate of $\theta$ based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$.
@@
 \begin{equation}
-	\textbf{Y}(t_i) = h(t_i)y(t_i) + \epsilon(t_i) \qquad 1 \leq i \leq n
-\end{equation} }
-where $\textbf{Y}(t_i)$ is an $n \times 1$ column vector, $h(t_i)$ is an $n \times v$ matrix given \textit{a priori}, and $\epsilon (t_i)$ is an $x \times 1$ column vector ("noise" vector) whose elements are the unobservable errors.
+	\textbf{Y}(t_i) = \textbf{h}(t_i)y(t_i) + \boldsymbol{\epsilon}(t_i) \qquad 1 \leq i \leq n
+\end{equation} }
+where $\textbf{Y}(t_i)$ is an $n \times 1$ column vector, $\textbf{h}(t_i)$ is an $n \times v$ matrix given \textit{a priori}, and $ \boldsymbol{\epsilon} (t_i)$ is an $n \times 1$ column vector ("noise" vector) whose elements are the unobservable errors.
 The above equation can be written in general form as:
@@
 
-\subsection{Cumulative data}
+\subsection{Weighted sum of squares - Cumulative data}
 
@@
 \citet{Mandel1957} distinguished between the usually assumed type of independent measuring error in the dependent variable and a 'cumulative' or interval error in which each new observation includes the error of the previous observations.
-Cumulative errors, arising because of the fluctuations as a function of time in the process itself due to small changes in operating, are not independent - only the differences in measurment from one period to the next are independent.
+Cumulative errors, arising because of the fluctuations as a function of time in the process itself due to small changes in operating, are not independent - only the differences in measurement from one period to the next are independent.
 Thus, if we consider two model:
@@
 \begin{flalign*}
-	&\text{Model A - independent error:} &&\nonumber \\
+	&{\normalsize \text{Model A - independent error:} } &&\nonumber \\
 	Y_i &= \Psi(\theta, y_0, t_i) + \epsilon_i \qquad i = 1,2,...,n&& \\
-	&\text{Model B - cumulative data:}&& \nonumber \\
+	&{\normalsize \text{Model B - cumulative data:}} && \nonumber \\
 	Y_j - Y_{j-1} &= \Psi(\theta, y_0, t_j) - \Psi(\theta, y_0, t_{j-1}) + \epsilon_j, \quad j = 1,2,...,n&& \\
-	&\text{or}&& \nonumber \\
+	&{\normalsize \text{or}} && \nonumber \\
 	Y_i = \sum_{j=1}^{i} &\left( Y_j - Y_{j-1} \right) = \sum_{j=1}^{i} \left( \Psi(\theta, y_0, t_j) - \Psi(\theta, y_0, t_{j-1}) \right) + \sum_{j=1}^{i} \epsilon_j &&
@@
 
+in which $\epsilon_i$ are independent random variables with $\mathbb{E}\{\epsilon_i\}$ and Var$\{\epsilon_i\} = \sigma_1^2$, a constant.
+The $\epsilon_j$ are also random independent variables because they represent differences such as $\epsilon_3' - \epsilon_2' = \left( \epsilon_1 + \epsilon_2 + \epsilon_3 \right) - \left( \epsilon_1 + \epsilon_2 \right) = \epsilon_3$.
+We assume that $\mathbb{E}\{\epsilon_j\}$ and Var$\{\epsilon_i\} = \sigma_1^2\left(x_j - x_{j-1}\right)$; i.e., the variance of $\epsilon_j$ can be a function of the test interval.
+The experimental point tend to stay on one side of the regression line of the best fit for Model B.
+
+The best unbiased estimate of the Model B is obtained by minimizing the weighted sum of squares:
+
+{\footnotesize
+\begin{equation*}
+	\sum_{j=1}^{n} \left( \cfrac{1}{x_j - x_{j-1}} \right) \left[ \left( Y_j - Y_{j-1} \right) - \left( \Psi(\theta, y_0, t_j) - \Psi(\theta, y_0, t_{j-1}) \right) \right]^2 
+\end{equation*} }
+
 \subsection{Maximum likelihood estimation}
+A well-know and desirable procedure (when it can be carried out) is that of maximum likelihood which leads asymptotically to estimates with the greatest efficiency but not necessarily unbiased.
+A desirable feature of the maximum likelihood methods is that, under certain conditions (which are not ntoo rigorous), the estimated parameters are normally distributed for large samples.
+
+Suppose that $p(x; \theta_1, \theta_2,...,)$ is a probability density function of \textit{known} form for the random variable $X$, a function which contains one or more parameters $\theta_1, \theta_2,...$.
+Also, suppose that we do not know what the values of $\theta_1, \theta_2, ...$ are.How can the most suitable values of $\theta_1, \theta_2, ...$ be estimated?
+One way is to collect a random sample of values of the random variable $X$, $\{x_1,x_2,...x_n\}$ and select the values of $\theta_1, \theta_2, ...$ now regarded random variables, that maximize the likelihood function $L\left( \theta_1, \theta_2, ...
+| x_1,x_2,...,x_n \right)$, a function described in chapter \ref{CH: Bayes} in connection with Bayes' theorem.
+Such estimators, $\hat{\theta}_1,\hat{\theta}_2, ...$ are known as maximum likelihood estimators.
+In effect, the methods selects those values of $\theta_1, \theta_2, ...$ that are at least as likely to generate the observed sample as any other set of values of the parameters if the probability density of values of the parameters if the probability density of the random variable $X$ were to be extensively simulated through use if the probability density $p\left( x|\theta_1, \theta_2, ...
+\right)$.
+In making a maximum likelihood estimate, we assume that the form of the probability density is connect (only the $\theta$'s need be determined) and that all possible values of $\theta_i$ are equally likely before experimentation.
+
+The likelihood function for the parameters given one observation is just the probability density in which the observation is regarded as a fixed number and the parameters as the variables:
+
+{\footnotesize
+\begin{equation}
+	L\left( \theta_1, \theta_2,...|x_1 \right) = p\left( x_1; \theta_1, \theta_2, ... \right)
+\end{equation} }
+where the lower case $x$'s and the number subscripts designate the value of the respective observation that is inserted into the probability density function.
+The likelihood function for the parameters based on several observations is the product of the individual functions if the observations are independent:
+
+{\footnotesize 
+\begin{multline}
+	L\left( \theta_1, \theta_2,...|x_1, x_2, ..., x_n \right) = \prod_{i=1}^{n} L\left( \theta_1, \theta_2,...|x_1 \right) \\
+	= p\left( x_1; \theta_1, \theta_2, ... \right)p\left( x_2; \theta_1, \theta_2, ... \right)\cdots p\left( x_n; \theta_1, \theta_2, ... \right)
+\end{multline} }
+
+In choosing as estimates of $\theta_i$ the values that maximize $L$ for the given values $\left( x_1, x_2, ..., x_n \right)$, it turns out that it is more convenient to work with the $\ln L$ than with $L$ itself:
+
+{\footnotesize 
+\begin{align}
+	\ln L &= \ln p \left( x_1; \theta_1, \theta_2, ... \right) + \ln p\left( x_3; \theta_1, \theta_2, ... \right) + ... \nonumber \\
+	&= \sum_{i=1}^{n} \ln p\left( x_i; \theta_1, \theta_2, ... \right)
+\end{align} }
+
+The $\ln L$ can be maximized with respect to the vector $\theta$ by equating to zero the partial derivatives of $\ln L$ with respect to each of the parameters:
+
+{\footnotesize
+\begin{align}\label{EQ: MLE_Basic_Solution}
+	\cfrac{\partial \ln L}{\partial \theta_1} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( x_1; \theta_1, \theta_2, ... \right) }{\partial \theta_1} = 0 \nonumber \\
+	\cfrac{\partial \ln L}{\partial \theta_2} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( x_1; \theta_1, \theta_2, ... \right) }{\partial \theta_2} = 0
+\end{align} }
+
+Solution of Equations \ref{EQ: MLE_Basic_Solution} yield the desired estimates $\hat{\theta}_1, \hat{\theta}_2, ...$.
+(Often iterative rather than analytical methods must be employed to obtain vector \boldsymbol{$\hat{\theta}$}).
+By carrying out this operation, under fairly unrestrictive conditions, it can be shown that as $n$ approaches infinity the maximum likelihood estimates have the desirable asymptotic properties:
+
+\begin{enumerate}[label=(\arabic*)]
+	\item {\footnotesize $\lim\limits_{n \rightarrow \infty} \mathbb{E}\{\hat{\theta_i}\} = \theta_i$ }
+	\item {\footnotesize $\left[ \sqrt{n}\left( \hat{\theta_i} - \theta_i \right) \right]$ } is normally distributed
+\end{enumerate}
+and for the case of two parameters:
+
+\begin{enumerate}[resume,label=(\arabic*)]
+	\item {\footnotesize $\lim\limits_{n \rightarrow \infty} \text{Var}\{\hat{\theta_i}\} = \cfrac{1}{n} \left[ \mathbb{E} \left\{ \left( \cfrac{\partial \ln p}{\partial \theta_i} \right)^2 \right\} \right]^{-1} \cfrac{1}{1-\rho^2_{\hat{\theta_1}, \hat{\theta_2}}} $ } \label{Assumption_MLE}
+\end{enumerate}
+
+where $\rho^2_{\hat{\theta_1}, \hat{\theta_2}}$ is the coefficient of correlation of the two $\hat{\theta}$'s.
+Extension of \ref{Assumption_MLE} to more than two parameters requires the use od matrix notation and will not be shown here.
+
+Maximum likelihood estimates are not necessarily unbiased.
+Maximum likelihood estimates, however are efficient and, hence, consistent estimates.
+Furthermore, where a sufficient estimate can be obtained, the maximum likelihood method will obtain it.
+Finally, if $\hat{\theta}$ is a maximum likelihood estimator of $\theta$, the $f\left( \theta \right)$ is a maximum likelihood estimator of $f\left( \theta \right)$, a function of $\theta$.
+
+\hrule
+
+By assuming that the conditional distribution of $\bar{Y}_i$, given $x_i$, is normal about $\eta_i = \mathbb{E}\left\{ \bar{Y}_i | x_i \right\}$, then we form the likelihood function based on the probability density:
+
+{\footnotesize
+\begin{align} \label{EQ: MLE_Norm}
+	p\left( y | x; \theta, \sigma^2_{\bar{Y}_i} \right) &= \cfrac{1}{\sqrt{2 \pi} \sigma^2_{\bar{Y}_i} } \exp \left[ \cfrac{1}{2  \sigma_{\bar{Y}_i} } \left( Y - \Psi(\theta_i) \right)^2 p_i \right] \nonumber \\
+	L\left( \theta, \sigma_{\bar{Y}_i} | y,x \right) &\equiv L = \prod_{i=1}^{n} \cfrac{1}{\sqrt{2 \pi} \sigma^2_{\bar{Y}_i} } \exp \left[ \cfrac{1}{2  \sigma_{\bar{Y}_i} } \left( Y - \Psi(\theta_i) \right)^2 p_i \right]
+\end{align}}
+
+In Equation \ref{EQ: MLE_Norm} the parameters are the variables, and the values of $Y$ and $x$ are given. Then
+
+{\footnotesize
+	\begin{equation}
+		\ln L = -n \ln \sqrt{2 \pi} - \cfrac{n}{2} \ln \sigma_{\bar{Y}_i}
+		- \cfrac{ \sum_{i=1}^{n} p \left\{ \left[  \bar{Y}_i - \Psi(\theta_i) \right]^2 \right\} }{2 \sigma^2_{\bar{Y}_i}}
+	\end{equation}
+	}
+
+To obtain the maximum likelihood estimates, we place
+
+{\footnotesize
+	\begin{equation}
+		\cfrac{\partial \ln L}{\partial \theta} = \cfrac{\partial \ln L}{\partial \left( \sigma_{\bar{Y}^2_i} \right)} = 0
+	\end{equation}
+}
+
+or iteratively solve
+
+{\footnotesize
+	\begin{equation}
+		\hat{\theta}_{MLE} = \arg \max_{\theta \in \Theta} L = \arg \max_{\theta \in \Theta} p(\theta|y)
+	\end{equation}
+}
+
+\hrule
 
@@
 
-The posterior probability density $p(\theta,y_0|y)$ can be expressed as the ratio of two probability densities if we make use of the analog for continuous variables of Equation \ref{EQ: Probabiltiy_independet_b}:
-
-{\footnotesize
-\begin{equation} \label{EQ: Posterior_distribution}
+The posterior probability density $p(\theta,y_0|y)$ can be expressed as the ratio of two probability densities if we make use of the analogue for continuous variables of Equation \ref{EQ: Probabiltiy_independet_b}:
+
+{\footnotesize
+\begin{align} \label{EQ: Posterior_distribution}
 	p\left( \theta,y_0|y \right) = \cfrac{p\left( \theta, y_0, y \right)}{p\left( y \right)}
-\end{equation} }
+\end{align} }
 
@@
 
+{\footnotesize
 \begin{equation} \label{EQ: Noise_prob}
 	p\left( y(t_i) | \theta,y_0 \right) = p\left( \epsilon(t_i) \right)
-\end{equation}
+\end{equation} }
 
@@
 
+{\footnotesize
 \begin{equation} \label{EQ: Noise_prob_norm}
 	p\left( \epsilon(t_i) \right) = \cfrac{1}{ (2\pi)^{v/2} |\Gamma(t_i)|^{1/2} } \exp \left[ -\cfrac{1}{2}\epsilon^T(t_i) \left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \right]
-\end{equation}
+\end{equation} }
 where $|\Gamma|$ is the det$~\Gamma$, and $\Gamma$ is the covariance matrix of $\epsilon$, i.e., of the response.
@@
 
+{\footnotesize
  \begin{subequations} \label{EQ: MLE_Lag_diff}
@@
 	\end{alignat}
- \end{subequations}
+ \end{subequations} }
 
@@
 
+{\footnotesize
 \begin{align}
@@
 	&= -\left( \Gamma(t_i) \right)^{-1} \left[ \textbf{Y}(t_i) - \Psi(\theta,y_0,t_i) \right]
-\end{align}
+\end{align} }
 
@@
 	\end{bmatrix}^T	
-\end{equation}
+\end{equation} }
 
@@
 
+{\footnotesize
 \begin{subequations} \label{EQ: MLE_Priors}
@@
 	\end{align}
-\end{subequations}
+\end{subequations} }
 where $\Omega$'s are the respective covariance matrices for $\theta^*$ and $y_0$, and the subscript $(0)$ designates the prior estimated of $\theta^*$ and $y_0$.
@@
 
+{\footnotesize
 \begin{equation}
 	\ln p(\theta^*,y_0) = \ln p(\theta^*) + \ln p(y_0)
-\end{equation}
+\end{equation} }
 
@@
 
+{\footnotesize
 \begin{subequations} 
-	\begin{align}
-	-\left( \hat{y}_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} &+ \sum_{i=1}^{n}\left[ \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \nonumber \\ 
-	&\cdot \cfrac{\partial}{\partial y_0} \Psi\left( \hat{\theta}, \hat{y}, t_i \right) = 0^T \\
-	-\left( \hat{\theta}^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} &+ \sum_{i=1}^{n}\left[ \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \nonumber \\
-	&\cdot \cfrac{\partial}{\partial \theta^*} \Psi\left( \hat{\theta}, \hat{y}, t_i \right) = 0^T \nonumber \\
-	\end{align}
-\end{subequations}
+	\begin{flalign}
+	&-\left( \hat{y}_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} + \sum_{i=1}^{n}\left[ \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \cdot \cfrac{\partial}{\partial y_0} \Psi\left( \hat{\theta}, \hat{y}, t_i \right) = 0^T  &&\\
+	&-\left( \hat{\theta}^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} + \sum_{i=1}^{n}\left[ \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \cdot \cfrac{\partial}{\partial \theta^*} \Psi\left( \hat{\theta}, \hat{y}, t_i \right) = 0^T &&
+	\end{flalign}
+\end{subequations} }
 where the overlay caret denotes estimated parameters.
 
-Note that under the assumption that the elements of $\Omega$ are essentially infinite (prior knowledge is diffuse), the elements of $\Omega^-1$ are zero, the equations for the maximum likelihood estimates coincide with those for the least squares estimates, and the same calculations for precision in the estimates apply.
-
-\hrule
-
-For some models, these equations can be explicitly solved for $\hat{\theta}^*$ and $\hat{y}$ but in general no closed-form solution to the maximization problem is known or available, and an MLE can only be found via numerical optimization.
+Note that under the assumption that the elements of $\Omega$ are essentially infinite (prior knowledge is diffuse), the elements of $\Omega^{-1}$ are zero, the equations for the maximum likelihood estimates coincide with those for the least squares estimates, and the same calculations for precision in the estimates apply.
+
+%For some models, these equations can be explicitly solved for $\hat{\theta}^*$ and $\hat{y}$ but in general no closed-form solution to the maximization problem is known or available, and an MLE can only be found via numerical optimization.
 Under the assumption of normality, the lack of prior knowledge about the parameters $\theta^{(0)}$ and known initial conditions $y_0$, the optimization problem is defined as follow:
-
-\begin{equation}
-	\hat{\theta}_{MLE} = \arg \max_{\theta \in \Theta} L = \arg \max_{\theta \in \Theta} p(\theta|y)
-\end{equation}
-
-Intuitively, this selects the parameter values that make the observed data most probable.
+%
+%{\footnotesize
+%\begin{equation}
+%	\hat{\theta}_{MLE} = \arg \max_{\theta \in \Theta} L = \arg \max_{\theta \in \Theta} p(\theta|y)
+%\end{equation} }
+%
+%Intuitively, this selects the parameter values that make the observed data most probable.
 The specific value $\hat{\theta}$ that maximizes the likelihood function $L$ is called the maximum likelihood estimate.
 Further, if the function $\hat{\theta}:\mathbb{R}\rightarrow\Theta$ so defined is measurable, then it is called the maximum likelihood estimator.
-
-If the random samples $y(t_1)$, $y(t_2)$,...,$y(t_n)$ come from a normal distribution with unknown mean $\hat{\theta}$ and variance $\sigma^2$, then the joint probability function can be written as
-
-\begin{equation}
-	p(\theta|y(t_i)) = \cfrac{1}{\sqrt{2\pi\sigma}}\exp\left[-\cfrac{ \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}\right]
-\end{equation}
-
-Then the likelihood function is defined as follow:
-
-\begin{multline} 
-	L =\prod\limits_{i=1}^n p(\theta|y(t_i)) = \\ (2\pi\sigma)^{-n/2}\exp\left[-\cfrac{1}{2\sigma}\sum\limits_{i=1}^n \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2\right]
-\end{multline}
-
-By taking the ln of the likelihood function, the final form of the cost function is obtained:
-
-\begin{equation} 
-	\ln L=-\cfrac{n}{2}\ln\sigma-\cfrac{n}{2}\ln(2\pi)-\cfrac{\sum\limits_{i=1}^n \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}
-\end{equation}
-
-\subsection{Maximum a posteriori estimation}
-
-As already discussed, the prior information about the estimated parameters can be incorporated in to the maximum likelihood estimator to form a maximum a posteriori probability (MAP) estimate.
+%
+%If the random samples $y(t_1)$, $y(t_2)$,...,$y(t_n)$ come from a normal distribution with unknown mean $\hat{\theta}$ and variance $\sigma^2$, then the joint probability function can be written as 
+%
+%{\footnotesize
+%\begin{equation}
+%	p(\theta|y(t_i)) = \cfrac{1}{\sqrt{2\pi\sigma}}\exp\left[-\cfrac{ \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}\right]
+%\end{equation} }
+%
+%Then the likelihood function is defined as follow:
+%
+%{\footnotesize
+%\begin{equation} 
+%	L =\prod\limits_{i=1}^n p(\theta|y(t_i)) = (2\pi\sigma)^{-n/2}\exp\left[-\cfrac{1}{2\sigma}\sum\limits_{i=1}^n \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2\right]
+%\end{equation} }
+%
+%By taking the ln of the likelihood function, the final form of the cost function is obtained:
+%
+%{\footnotesize
+%\begin{equation} 
+%	\ln L=-\cfrac{n}{2}\ln\sigma-\cfrac{n}{2}\ln(2\pi)-\cfrac{\sum\limits_{i=1}^n \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}
+%\end{equation} }
+%
+%\subsection{Maximum a posteriori estimation}
+%
+%As already discussed, the prior information about the estimated parameters can be incorporated in to the maximum likelihood estimator to form a maximum a posteriori probability (MAP) estimate.
 MAP can be used to obtain a point estimate of an unobserved quantity on the basis of empirical data.
@@
 MLE and MAP can be connected by Bayes' rule:
-
-\begin{equation} 
-	\begin{split}
-		{\bf \hat{\theta}_{\text{MAP}}} &= \arg\max_{\bf \theta} p(\theta | y) \\
-		&= \arg\max_{\bf \theta} \frac{p(y | \theta) p(\theta)}{p(y)} \\
-		&= \arg\max_{\bf \theta} p(y | \theta) p(\theta) \\
-		&= \arg\max_{\bf \theta} \ln(p(y | \theta) p(\theta)) \\
-		&= \arg\max_{\bf \theta} \ln p(y | \theta) + \ln p(\theta)
-	\end{split}
-\end{equation}
-
-Notice that we can get rid of the evidence term $P(y)$ because it's constant with respect to the maximization and also take the ln of the inner function because it's monotonically increasing.
-
-We assume the normal distribution of random samples, with identical variance and the prior distribution of $\theta$ given by $\mathcal{N}(\theta^{(0)},\,\sigma_\theta^{2})$.
+%
+%{\footnotesize
+%\begin{equation} 
+%	\begin{split}
+%		{\bf \hat{\theta}_{\text{MAP}}} &= \arg\max_{\bf \theta} p(\theta | y) \\
+%		&= \arg\max_{\bf \theta} \frac{p(y | \theta) p(\theta)}{p(y)} \\
+%		&= \arg\max_{\bf \theta} p(y | \theta) p(\theta) \\
+%		&= \arg\max_{\bf \theta} \ln(p(y | \theta) p(\theta)) \\
+%		&= \arg\max_{\bf \theta} \ln p(y | \theta) + \ln p(\theta)
+%	\end{split}
+%\end{equation} }
+%
+%Notice that we can get rid of the evidence term $P(y)$ because it's constant with respect to the maximization and also take the ln of the inner function because it's monotonically increasing.
+%
+%We assume the normal distribution of random samples, with identical variance and the prior distribution of $\theta$ given by $\mathcal{N}(\theta^{(0)},\,\sigma_\theta^{2})$.
 The likelihood function to be maximized can be written as
-
-\begin{equation} \label{EQ: MAP_L2}
-	\begin{split}
-	&\arg\max_{\bf \theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2 }{2\sigma^2}}
-	+ \ln \prod_{j=0}^{p} \frac{1}{\sigma_\theta\sqrt{2\pi}}e^{-\frac{ \left( \hat{\theta} - \theta^{(0)} \right)^2}{2\sigma_\theta^2}} \right]  \\
-	&= \arg\max_{\bf \theta} \left[- \sum_{i=1}^{n} {\frac{\left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma^2}}
-	- \sum_{j=0}^{p} {\frac{\left( \hat{\theta} - \theta^{(0)} \right)^2}{2\sigma_\theta^2}} \right]\\
-	&= \arg\min_{\bf \theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2
-	+ \frac{\sigma^2}{\sigma_\theta^2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^{(0)} \right)^2 \right] \\
-	&= \arg\min_{\bf \theta} \left[ \sum_{i=1}^{n} \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2 + \lambda_{L2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^{(0)} \right)^2 \right]
-	\end{split}
-\end{equation}
-
-Notice that we dropped some of the constants (with respect to $\theta$) and factored to simplify the expression.
+%
+%{\footnotesize
+%\begin{equation} \label{EQ: MAP_L2}
+%	\begin{split}
+%	&\arg\max_{\bf \theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2 }{2\sigma^2}}
+%	+ \ln \prod_{j=0}^{p} \frac{1}{\sigma_\theta\sqrt{2\pi}}e^{-\frac{ \left( \hat{\theta} - \theta^{(0)} \right)^2}{2\sigma_\theta^2}} \right]  \\
+%	&= \arg\max_{\bf \theta} \left[- \sum_{i=1}^{n} {\frac{\left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma^2}}
+%	- \sum_{j=0}^{p} {\frac{\left( \hat{\theta} - \theta^{(0)} \right)^2}{2\sigma_\theta^2}} \right]\\
+%	&= \arg\min_{\bf \theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2
+%	+ \frac{\sigma^2}{\sigma_\theta^2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^{(0)} \right)^2 \right] \\
+%	&= \arg\min_{\bf \theta} \left[ \sum_{i=1}^{n} \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2 + \lambda_{L2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^{(0)} \right)^2 \right]
+%	\end{split}
+%\end{equation} }
+%
+%Notice that we dropped some of the constants (with respect to $\theta$) and factored to simplify the expression.
 You can see this is the same expression as Equation \ref{EQ: MAP_L2} (L2 Regularization) with $\lambda_{L2}$.

### 2022-08-14 SFE-report/Paramter_fitting.tex
14.08

@@
 
-As discussed by \citet{Himmelblau1970}, The Bayesian approach to estimation make use of prior information.
+As discussed by \citet{Himmelblau1970}, the Bayesian approach to estimation make use of prior information.
 Such prior knowledge can come from theoretical considerations, from the results of previous experiments, or from assumptions by the experimenter.
@@
 
-Further, if al events comprising the set $\{A_i\}$ are included in $A_1,A_2,...,A_n$, then
+Further, if all events comprising the set $\{A_i\}$ are included in $A_1,A_2,...,A_n$, then
 
@@
 	\begin{equation}
-		P\left( A_1, \text{or~} A_2,..., \text{or~} A_n \right) = \sum_{i=1}^{n} P\left( A_i \right)
+		P\left( A_1 \text{or~} A_2... \text{or~} A_n \right) = \sum_{i=1}^{n} P\left( A_i \right)
 	\end{equation} }
@@
 
-\newpage
+\clearpage
+
 \section{Parameter estimation} \label{CH: Parameter_estimation}
 
-Conceptually, the unobservable $\epsilon(t)$ is added to $y(t)$ to give the observable dependent variable $Y(t)$. For discrete observations:
+Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, $y(t)$, to give the observable dependent variable $Y(t)$, for example the experimental process output.
+For discrete observations:
 
@@
 
-If the estimated parameter $\hat{\theta}$ replaces the model parameter $\theta$, the residue error is $\textbf{E} = Y(t) - \hat{Y}(t)$, where $\hat{Y}(t)$ is the predicted value of $Y_i$ at $x_i$.
+%If the estimated parameter $\hat{\theta}$ replaces the model parameter $\theta$, the residue error is $\textbf{E} = Y(t) - \hat{Y}(t)$, where $\hat{Y}(t)$ is the predicted value of $Y_i$ at $y_i$. 
 The objective in parameter estimation is to obtain the "best" estimate of $\theta$ based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$. 
-
-We assume that $x(t)$ is given \textit{a priori} but the $\textbf{y}_0$ and $\theta$ are to be estimated over the time interval $0 \leq t \leq t_n$ from discrete observation described by the following relation:
-
-{\footnotesize
-\begin{equation}
-	\textbf{Y}(t_i) = \textbf{h}(t_i)y(t_i) + \boldsymbol{\epsilon}(t_i) \qquad 1 \leq i \leq n
-\end{equation} }
-where $\textbf{Y}(t_i)$ is an $n \times 1$ column vector, $\textbf{h}(t_i)$ is an $n \times v$ matrix given \textit{a priori}, and $ \boldsymbol{\epsilon} (t_i)$ is an $n \times 1$ column vector ("noise" vector) whose elements are the unobservable errors.
-The above equation can be written in general form as:
+\sout{
+We assume that $x(t)$ is given \textit{a priori} (for example as a solution of process model) but $\theta$ is to be estimated over the time interval $0 \leq t \leq t_n$ from discrete observation described by the following relation:}
+
+{\footnotesize
+\begin{equation}
+	 Y(t_i) = \textbf{h}(t_i)y(t_i) + \boldsymbol{\epsilon}(t_i) \qquad 1 \leq i \leq n
+\end{equation} }
+\sout{where $ Y(t_i)$ is an $n \times 1$ column vector, $\textbf{h}(t_i)$ is an $n \times v$ matrix given \textit{a priori}, and $ \boldsymbol{\epsilon} (t_i)$ is an $n \times 1$ column vector ("noise" vector) whose elements are the unobservable errors.
+The above equation can be written in general form as:}
 
@@
 \begin{equation} \label{EQ: Measurment_noise}
-	\textbf{Y}(t_i) = \Psi(\theta, y_0, t_i) + \epsilon(t_i)
+	 Y(t_i) = y(\theta, t_i) + \epsilon(t_i)
 \end{equation}}
-where $\Psi$ is the matrix of functions.
-
-Because of the difficulty of obtaining analytical solutions to the deterministic process model, experiments have been arranged wherby the vector of derivatives $d\textbf{Y}/dy$ is measured rather than \textbf{Y} itself.
-In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy/dt$ as follows:
-
-{\footnotesize
-\begin{equation}
-	\cfrac{d\textbf{Y}}{dt} = \cfrac{dy}{dt} + \epsilon
+where $y$ is the output model, which is a function of $\theta$ and time $t_i$.
+
+Because of the difficulty of obtaining analytical solutions to the deterministic process model, experiments have been arranged whereby the vector of derivatives $d Y(t_i)/dt$ is measured rather than $Y(t_i)$ itself.
+In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ as follows:
+
+{\footnotesize
+\begin{equation}
+	\cfrac{d Y(t_i)}{dt} = \cfrac{dy(\theta, t_i)}{dt} + \epsilon(t_i)
 \end{equation} }
@@
 \subsection{Least squares estimation}
-A least squares parameter estimation does not require prior knowledge of the distribution of unobservable errors, yield  unbiased estimates, that is, $ \mathbb{E}\{\hat{Y}(t) = y(t) \} $, and results in the minimum variance among all linear unbiased estimators.
-If the observations $\textbf{Y}$ for the model responses are continuous functions of time from $t = 0$ to $t = t_f$, the Markov (or "rigorous least squares") criterion is to minimize:
-
-{\footnotesize
-\begin{equation}
-	\phi =  \cfrac{1}{2} \int_{0}^{t_f}  \left[ \textbf{Y} - \Psi \right]^T \Gamma^{-1} \left[ \textbf{Y} - \Psi \right] dt
-\end{equation} }
-where $\Gamma$ is the covariance matrix (or perhaps a matrix of appropriate weights), and $\phi$ is the time integrated value of the error squared ("integral squared error").
+A least squares parameter estimation does not require prior knowledge of the distribution of unobservable errors, yield  unbiased estimates, \sout{that is, $ \mathbb{E}\{\hat{Y}(t) = y(t) \} $,} and results in the minimum variance among all linear unbiased estimators.
+If the observations $ Y$ for the model responses are continuous functions of time from $t = 0$ to $t = t_f$, the Markov (or "rigorous least squares") criterion is to minimize:
+
+{\footnotesize
+\begin{align}
+	\phi &= \cfrac{1}{2} \int_{0}^{t_f}  \left[ Y(t) - y(\theta,t) \right]^T \Gamma^{-1} \left[ Y(t) - y(\theta,t) \right] dt \\
+	\hat{\theta} &= \arg \min_{\theta \in \Theta} \phi
+\end{align} }
+where $\Gamma$ is the covariance matrix (or perhaps a matrix of appropriate weights), $\hat{\theta}$ is the parameter estimate, $\Theta$ is the parameter space, and $\phi$ is the time integrated value of the error squared ("integral squared error").
 If the observations are made at discrete instants of time, $t_i$, $i = 1,2,...,n$, the Markov criterion is to minimize:
@@
 {\footnotesize
-\begin{equation}
-	\phi = \cfrac{1}{2} \sum_{i=1}^{n} \left[ \textbf{Y}(t_i) - \Psi(t_i) \right]^T \Gamma^{-1} \left[ \textbf{Y}(t_i) - \Psi(t_i) \right] 
-\end{equation} }
-
-If $\Gamma$ is a diagonal matrix, $\phi$  becomes a "weighted least squares" criterion; if $\Gamma = \sigma^2 \textbf{I}$ where $\sigma$ is a standard deviation, $\phi$ is the "ordinary least squares" criterion.
+\begin{align}
+	\phi &= \cfrac{1}{2} \sum_{i=1}^{n} \left[ Y(t_i) - y(\theta,t_i) \right]^T \Gamma^{-1} \left[ Y(t_i) - y(\theta,t_i) \right] \\
+	\hat{\theta} &= \arg \min_{\theta \in \Theta} \phi
+\end{align} }
+
+If $\Gamma$ is a diagonal matrix, $\phi$  becomes a "weighted least squares" criterion; if $\Gamma = \sigma^2 \textbf{I}$ where $\sigma$ is a standard deviation., $\phi$ is the "ordinary least squares" criterion.
 
@@
 	&{\normalsize \text{Model A - independent error:} } &&\nonumber \\
-	Y_i &= \Psi(\theta, y_0, t_i) + \epsilon_i \qquad i = 1,2,...,n&& \\
+	Y(t_i) &= y(\theta, t_i) + \epsilon_i  \qquad i = 1,2,...,n&& \\
 	&{\normalsize \text{Model B - cumulative data:}} && \nonumber \\
-	Y_j - Y_{j-1} &= \Psi(\theta, y_0, t_j) - \Psi(\theta, y_0, t_{j-1}) + \epsilon_j, \quad j = 1,2,...,n&& \\
+	Y(t_j) - Y(t_{j-1}) &= y(\theta, t_j) - y(\theta, t_{j-1}) + \epsilon_j, \quad j = 1,2,...,n&& \\
 	&{\normalsize \text{or}} && \nonumber \\
-	Y_i = \sum_{j=1}^{i} &\left( Y_j - Y_{j-1} \right) = \sum_{j=1}^{i} \left( \Psi(\theta, y_0, t_j) - \Psi(\theta, y_0, t_{j-1}) \right) + \sum_{j=1}^{i} \epsilon_j &&
+	Y(t_i) = \sum_{j=1}^{i} &\left( Y(t_j) - Y(t_{j-1}) \right) = \sum_{j=1}^{i} \left( y(\theta, t_j) - y(\theta, t_{j-1}) \right) + \sum_{j=1}^{i} \epsilon_j &&
 \end{flalign*} }
@@
 The $\epsilon_j$ are also random independent variables because they represent differences such as $\epsilon_3' - \epsilon_2' = \left( \epsilon_1 + \epsilon_2 + \epsilon_3 \right) - \left( \epsilon_1 + \epsilon_2 \right) = \epsilon_3$.
-We assume that $\mathbb{E}\{\epsilon_j\}$ and Var$\{\epsilon_i\} = \sigma_1^2\left(x_j - x_{j-1}\right)$; i.e., the variance of $\epsilon_j$ can be a function of the test interval.
+We assume that $\mathbb{E}\{\epsilon_j\}$ and Var$\{\epsilon_i\} = \sigma_1^2\left(y_j - y_{j-1}\right)$; i.e., the variance of $\epsilon_j$ can be a function of the test interval.
 The experimental point tend to stay on one side of the regression line of the best fit for Model B.
 
-The best unbiased estimate of the Model B is obtained by minimizing the weighted sum of squares:
+The \sout{best} unbiased estimate of the Model B is obtained by minimizing the weighted sum of squares:
 
@@
 \begin{equation*}
-	\sum_{j=1}^{n} \left( \cfrac{1}{x_j - x_{j-1}} \right) \left[ \left( Y_j - Y_{j-1} \right) - \left( \Psi(\theta, y_0, t_j) - \Psi(\theta, y_0, t_{j-1}) \right) \right]^2 
+	\hat{\theta} = \arg \min_{\theta \in \Theta} \sum_{j=1}^{n} \cfrac{ \left[ \left( Y(t_j) - Y(t_{j-1}) \right) - \left( y(\theta, t_j) - y(\theta, t_{j-1}) \right) \right]^2  }{y(\theta, t_j) - y(\theta, t_{j-1})}
 \end{equation*} }
@@
 \subsection{Maximum likelihood estimation}
-A well-know and desirable procedure (when it can be carried out) is that of maximum likelihood which leads asymptotically to estimates with the greatest efficiency but not necessarily unbiased.
-A desirable feature of the maximum likelihood methods is that, under certain conditions (which are not ntoo rigorous), the estimated parameters are normally distributed for large samples.
-
-Suppose that $p(x; \theta_1, \theta_2,...,)$ is a probability density function of \textit{known} form for the random variable $X$, a function which contains one or more parameters $\theta_1, \theta_2,...$.
-Also, suppose that we do not know what the values of $\theta_1, \theta_2, ...$ are.How can the most suitable values of $\theta_1, \theta_2, ...$ be estimated?
-One way is to collect a random sample of values of the random variable $X$, $\{x_1,x_2,...x_n\}$ and select the values of $\theta_1, \theta_2, ...$ now regarded random variables, that maximize the likelihood function $L\left( \theta_1, \theta_2, ...
-| x_1,x_2,...,x_n \right)$, a function described in chapter \ref{CH: Bayes} in connection with Bayes' theorem.
-Such estimators, $\hat{\theta}_1,\hat{\theta}_2, ...$ are known as maximum likelihood estimators.
-In effect, the methods selects those values of $\theta_1, \theta_2, ...$ that are at least as likely to generate the observed sample as any other set of values of the parameters if the probability density of values of the parameters if the probability density of the random variable $X$ were to be extensively simulated through use if the probability density $p\left( x|\theta_1, \theta_2, ...
-\right)$.
-In making a maximum likelihood estimate, we assume that the form of the probability density is connect (only the $\theta$'s need be determined) and that all possible values of $\theta_i$ are equally likely before experimentation.
-
-The likelihood function for the parameters given one observation is just the probability density in which the observation is regarded as a fixed number and the parameters as the variables:
-
-{\footnotesize
-\begin{equation}
-	L\left( \theta_1, \theta_2,...|x_1 \right) = p\left( x_1; \theta_1, \theta_2, ... \right)
-\end{equation} }
-where the lower case $x$'s and the number subscripts designate the value of the respective observation that is inserted into the probability density function.
-The likelihood function for the parameters based on several observations is the product of the individual functions if the observations are independent:
-
-{\footnotesize 
-\begin{multline}
-	L\left( \theta_1, \theta_2,...|x_1, x_2, ..., x_n \right) = \prod_{i=1}^{n} L\left( \theta_1, \theta_2,...|x_1 \right) \\
-	= p\left( x_1; \theta_1, \theta_2, ... \right)p\left( x_2; \theta_1, \theta_2, ... \right)\cdots p\left( x_n; \theta_1, \theta_2, ... \right)
-\end{multline} }
-
-In choosing as estimates of $\theta_i$ the values that maximize $L$ for the given values $\left( x_1, x_2, ..., x_n \right)$, it turns out that it is more convenient to work with the $\ln L$ than with $L$ itself:
-
-{\footnotesize 
-\begin{align}
-	\ln L &= \ln p \left( x_1; \theta_1, \theta_2, ... \right) + \ln p\left( x_3; \theta_1, \theta_2, ... \right) + ... \nonumber \\
-	&= \sum_{i=1}^{n} \ln p\left( x_i; \theta_1, \theta_2, ... \right)
-\end{align} }
-
-The $\ln L$ can be maximized with respect to the vector $\theta$ by equating to zero the partial derivatives of $\ln L$ with respect to each of the parameters:
-
-{\footnotesize
-\begin{align}\label{EQ: MLE_Basic_Solution}
-	\cfrac{\partial \ln L}{\partial \theta_1} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( x_1; \theta_1, \theta_2, ... \right) }{\partial \theta_1} = 0 \nonumber \\
-	\cfrac{\partial \ln L}{\partial \theta_2} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( x_1; \theta_1, \theta_2, ... \right) }{\partial \theta_2} = 0
-\end{align} }
-
-Solution of Equations \ref{EQ: MLE_Basic_Solution} yield the desired estimates $\hat{\theta}_1, \hat{\theta}_2, ...$.
-(Often iterative rather than analytical methods must be employed to obtain vector \boldsymbol{$\hat{\theta}$}).
-By carrying out this operation, under fairly unrestrictive conditions, it can be shown that as $n$ approaches infinity the maximum likelihood estimates have the desirable asymptotic properties:
-
-\begin{enumerate}[label=(\arabic*)]
-	\item {\footnotesize $\lim\limits_{n \rightarrow \infty} \mathbb{E}\{\hat{\theta_i}\} = \theta_i$ }
-	\item {\footnotesize $\left[ \sqrt{n}\left( \hat{\theta_i} - \theta_i \right) \right]$ } is normally distributed
-\end{enumerate}
-and for the case of two parameters:
-
-\begin{enumerate}[resume,label=(\arabic*)]
-	\item {\footnotesize $\lim\limits_{n \rightarrow \infty} \text{Var}\{\hat{\theta_i}\} = \cfrac{1}{n} \left[ \mathbb{E} \left\{ \left( \cfrac{\partial \ln p}{\partial \theta_i} \right)^2 \right\} \right]^{-1} \cfrac{1}{1-\rho^2_{\hat{\theta_1}, \hat{\theta_2}}} $ } \label{Assumption_MLE}
-\end{enumerate}
-
-where $\rho^2_{\hat{\theta_1}, \hat{\theta_2}}$ is the coefficient of correlation of the two $\hat{\theta}$'s.
-Extension of \ref{Assumption_MLE} to more than two parameters requires the use od matrix notation and will not be shown here.
-
-Maximum likelihood estimates are not necessarily unbiased.
-Maximum likelihood estimates, however are efficient and, hence, consistent estimates.
-Furthermore, where a sufficient estimate can be obtained, the maximum likelihood method will obtain it.
-Finally, if $\hat{\theta}$ is a maximum likelihood estimator of $\theta$, the $f\left( \theta \right)$ is a maximum likelihood estimator of $f\left( \theta \right)$, a function of $\theta$.
-
-\hrule
-
-By assuming that the conditional distribution of $\bar{Y}_i$, given $x_i$, is normal about $\eta_i = \mathbb{E}\left\{ \bar{Y}_i | x_i \right\}$, then we form the likelihood function based on the probability density:
-
-{\footnotesize
-\begin{align} \label{EQ: MLE_Norm}
-	p\left( y | x; \theta, \sigma^2_{\bar{Y}_i} \right) &= \cfrac{1}{\sqrt{2 \pi} \sigma^2_{\bar{Y}_i} } \exp \left[ \cfrac{1}{2  \sigma_{\bar{Y}_i} } \left( Y - \Psi(\theta_i) \right)^2 p_i \right] \nonumber \\
-	L\left( \theta, \sigma_{\bar{Y}_i} | y,x \right) &\equiv L = \prod_{i=1}^{n} \cfrac{1}{\sqrt{2 \pi} \sigma^2_{\bar{Y}_i} } \exp \left[ \cfrac{1}{2  \sigma_{\bar{Y}_i} } \left( Y - \Psi(\theta_i) \right)^2 p_i \right]
-\end{align}}
-
-In Equation \ref{EQ: MLE_Norm} the parameters are the variables, and the values of $Y$ and $x$ are given. Then
-
-{\footnotesize
-	\begin{equation}
-		\ln L = -n \ln \sqrt{2 \pi} - \cfrac{n}{2} \ln \sigma_{\bar{Y}_i}
-		- \cfrac{ \sum_{i=1}^{n} p \left\{ \left[  \bar{Y}_i - \Psi(\theta_i) \right]^2 \right\} }{2 \sigma^2_{\bar{Y}_i}}
-	\end{equation}
-	}
-
-To obtain the maximum likelihood estimates, we place
-
-{\footnotesize
-	\begin{equation}
-		\cfrac{\partial \ln L}{\partial \theta} = \cfrac{\partial \ln L}{\partial \left( \sigma_{\bar{Y}^2_i} \right)} = 0
-	\end{equation}
-}
-
-or iteratively solve
-
-{\footnotesize
-	\begin{equation}
-		\hat{\theta}_{MLE} = \arg \max_{\theta \in \Theta} L = \arg \max_{\theta \in \Theta} p(\theta|y)
-	\end{equation}
-}
-
-\hrule
 
@@
 Each time it has been associated with the (joint) normal distribution because of mathematical convenience.
-Consider the joint probability density function (the likelihood function) $p(\theta, y_0|y)$ for random sample $y = y(t_1),y(t_2),...,y(t_n)$, parameter $\theta$ and initial condition $y_0$ if a maximum of this function over all choices of $y_0$ and $\theta$ can be found, the estimates so obtained are maximum likelihood estimates.
+Consider the joint probability density function (the likelihood function) $p(\theta |y)$ for random sample $y = y(t_1),y(t_2),...,y(t_n)$, parameter $\theta$.
+If a maximum of this function over all choices of $\theta$ can be found, the estimates so obtained are maximum likelihood estimates.
 The conditions at the maximum can be evolved incorporating prior information as follows.
 
-The posterior probability density $p(\theta,y_0|y)$ can be expressed as the ratio of two probability densities if we make use of the analogue for continuous variables of Equation \ref{EQ: Probabiltiy_independet_b}:
+The posterior probability density $p(\theta|y)$ can be expressed as the ratio of two probability densities if we make use of the analogue for continuous variables of Equation \ref{EQ: Probabiltiy_independet_b}:
 
@@
 	\begin{align} \label{EQ: Posterior_distribution}
-	p\left( \theta,y_0|y \right) = \cfrac{p\left( \theta, y_0, y \right)}{p\left( y \right)}
+		p\left( \theta| y(t_n),...,y(t_1) \right) = \cfrac{p\left( \theta, y(t_n),...,y(t_1) \right)}{p\left( y(t_n),...,y(t_1) \right)}
 \end{align} }
@@
 		\begin{split}
-		p\left( \theta,y_0,y \right) &= p\left( y(t_n)|\theta,y_0,y(t_{n-1}),...,y(t_1) \right) \\ &\cdot p\left( \theta,y_0,y(t_{n-1}),...,y(t_1) \right)
+			p\left( \theta,y(t_n),...,y(t_1) \right) &= p\left( y(t_n)|\theta,y(t_{n-1}),...,y(t_1) \right) \\ &\cdot p\left( \theta,y(t_{n-1}),...,y(t_1) \right)
 		\end{split}
@@
 	\begin{equation}
-	p\left( \theta,y_0,y \right) = p\left( \theta,y_0 \right) \prod_{i=1}^{n} p\left( \theta,y_0|y \right)
-\end{equation} }
-
-Examination of Equation \ref{EQ: Measurment_noise} shows that $\textbf{Y}(t_i)$ depends only on $t_i$, $y_0$, $\theta$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement.
+		p\left( \theta, y(t_n),...,y(t_1) \right) = p\left( \theta \right) \prod_{i=1}^{n} p\left( y(t_i)|\theta, y(t_{i-1}),...,y(t_1) \right)
+\end{equation} }
+
+Examination of Equation \ref{EQ: Measurment_noise} shows that $ Y(t_i)$ depends only on $t_i$, $\theta$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement.
 Consequently, we can write
@@
 	\begin{equation}
-	p\left( y(t_i)|\theta,y_0, y(t_{i-1}),...,y(t_1) \right) = p\left( y(t_i)|\theta,y_0 \right)
+		p\left( y(t_i)|\theta, y(t_{i-1}),...,y(t_1) \right) = p\left( y(t_i)|\theta \right)
 \end{equation} }
@@
 	\begin{equation}
-	p\left( \theta,y_0|y \right) = \cfrac{p\left( \theta,y_0 \right) \prod_{i=1}^{n} p\left( y(t_i)|\theta,y_0 \right) }{p\left( y \right)}
-\end{equation} }
-
-The function to be maximized will be the logarithm of the likelihood function $L = p\left( \theta,y_0| y(t_n),...,y(t_1) \right)$ constrained by equation \ref{EQ: Measurment_noise}, which can be written as $\ln(L)$ plus the Lagrangian multipliers $\lambda(t_k)$ times the constraint function, or
+		p\left( \theta| y(t_n),...,y(t_1) \right) = \cfrac{p\left( \theta \right) \prod_{i=1}^{n} p\left( y(t_i)|\theta \right) }{p\left( y(t_n),...,y(t_1) \right)}
+\end{equation} }
+
+We can get rid of the evidence term $p\left( y(t_n),...,y(t_1) \right)$ because it's constant with respect to the maximization.
+Moreover, if we are lacking a prior distribution over the quantity we want to estimate, then $p(\theta)$ can be omitted.
+In such a case:
+
+{\footnotesize
+	\begin{equation}
+		p\left( \theta| y(t_n),...,y(t_1) \right) = \prod_{i=1}^{n} p\left( y(t_i)|\theta \right) = \prod_{i=1}^{n} L\left( \theta|y(t_i) \right) 
+\end{equation} }
+
+By collecting a random sample of values of the random variable $y$ and selecting the values of $\theta$ that maximize the likelihood function $L\left( \theta | y \right)$, a function described in chapter \ref{CH: Bayes} in connection with Bayes' theorem.
+Such estimators, $\hat{\theta}$, are known as maximum likelihood estimators.
+In effect, the methods selects those values of $\theta$ that are at least as likely to generate the observed sample as any other set of values of the parameters if the probability density of the random variable $y$ were to be extensively simulated through use of the probability density $p\left( y|\theta \right)$.
+In making a maximum likelihood estimate, we assume that the form of the probability density (\sout{only the $\theta$ need be determined}) and that all possible values of $\theta$ are equally likely before experimentation.
+
+%The likelihood function for the parameters given one observation is just the probability density in which the observation is regarded as a fixed number and the parameters as the variables:
+%
+%{\footnotesize
+%	\begin{equation}
+%		p\left( \theta| y(t_i) \right) = L\left( \theta|y_{t_i} \right) = p\left( y(t_i)| \theta \right)
+%\end{equation} }
+%where the lower case $y$'s and the number subscripts designate the value of the respective observation that is inserted into the probability density function. 
+The likelihood function for the parameters based on several observations is the product of the individual functions if the observations are independent.
+
+{\footnotesize 
+	\begin{multline}
+		L\left( \theta|y(t_n),...,y(t_1) \right) = \prod_{i=1}^{n} L\left( \theta|y(t_i) \right) \\
+		= p\left( y(t_1)| \theta \right)p\left( y(t_2)| \theta \right) ... p\left( y(t_n)| \theta \right)
+\end{multline} }
+
+In choosing as estimates of $\theta$ the values that maximize $L$ for the given values $\left( y(t_i) \right)$, it turns out that it is more convenient to work with the $\ln L$ than with $L$ itself:
+
+{\footnotesize 
+	\begin{equation}
+		\ln L = \ln p \left( y(t_1)| \theta \right) + \ln p\left( y(t_2)| \theta \right) + ... + \ln p \left( y(t_n)| \theta \right) = \sum_{i=1}^{n} \ln p\left( y(t_i); \theta \right)
+	\end{equation} }
+
+By assuming that the conditional distribution of $\bar{Y}_i$, given $y_i$, is normal, then we form the likelihood function based on the probability density:
+
+{\footnotesize
+	\begin{align} \label{EQ: MLE_Norm}
+		p\left(  \theta, \sigma | y(t_n),...,y(t_1) \right) &= \prod_{i=1}^{n} \cfrac{1}{\sqrt{2 \pi} \sigma } \exp \left[ \cfrac{1}{2  \sigma } \left( Y(t_i) - y(\theta , t_i) \right)^2 \right] \nonumber \\
+		L\left( \theta, \sigma | y(t_n),...,y(t_1) \right) &= \prod_{i=1}^{n} \cfrac{1}{\sqrt{2 \pi} \sigma } \exp \left[ \cfrac{1}{2  \sigma } \left( Y(t_i) - y(\theta , t_i) \right)^2 \right]
+\end{align}}
+where $\sigma$ is the variance
+
+%In Equation \ref{EQ: MLE_Norm} the parameters are the variables, and the values of $Y$ and $x$ are given. Then
+By taking the natural logarithm of the Equation \ref{EQ: MLE_Norm}, the final form of the objective function can be obtained:
+
+{\footnotesize
+	\begin{equation}
+		\ln L = -n \ln \sqrt{2 \pi} - \cfrac{n}{2} \ln \sigma
+		- \cfrac{ \sum_{i=1}^{n} \left[  Y(t_i) - y(\theta , t_i) \right]^2 }{2 \sigma^2}
+	\end{equation}
+}
+
+The parameter estimation problem can be formulated as follow:
+
+{\footnotesize
+	\begin{equation}
+		\begin{aligned}
+			&\hat{\theta}_{MLE} &= \arg \max_{\sigma, \theta \in \Theta} \ln L = \arg \max_{\sigma,\theta \in \Theta} p(\theta|y) \\
+			&\text{subject to}
+			& \dot{x} = f(t,x,\theta) \\
+			&& \dot{\theta} = 0 \\
+			&& y = g(x)
+		\end{aligned}
+\end{equation} }
+
+{\color{red}Based on the first order optimality condition,} the $\ln L$ can be maximized with respect to the vector $\theta$ by equating to zero the partial derivatives of $\ln L$ with respect to each of the parameters:
+
+{\footnotesize
+	\begin{align}\label{EQ: MLE_Basic_Solution}
+		\cfrac{\partial \ln L}{\partial \theta} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( y(t_i) | \theta \right) }{\partial \theta} = 0 
+\end{align} }
+
+Solution of Equations \ref{EQ: MLE_Basic_Solution} yield the desired estimates $\hat{\theta}$.
+For some models, these equations can be explicitly solved for $\hat{\theta}$ but in general no closed-form solution to the maximization problem is known or available, and an MLE can only be found via numerical optimization.
+
+\sout{By carrying out this operation, under fairly unrestrictive conditions,} 
+It can be shown that as $n$ approaches infinity the maximum likelihood estimates have the desirable asymptotic properties:
+
+\begin{enumerate}[label=(\arabic*)]
+	\item {\footnotesize $\lim\limits_{n \rightarrow \infty} \mathbb{E}\{\hat{\theta}\} = \theta$ }
+	\item {\footnotesize $\left[ \sqrt{n}\left( \hat{\theta} - \theta \right) \right]$ } is normally distributed
+\end{enumerate}
+and for the case of two parameters:
+
+\begin{enumerate}[resume,label=(\arabic*)]
+	\item {\footnotesize $\lim\limits_{n \rightarrow \infty} \text{Var}\{\hat{\theta}\} = \cfrac{1}{n} \left[ \mathbb{E} \left\{ \left( \cfrac{\partial \ln p}{\partial \theta} \right)^2 \right\} \right]^{-1} \cfrac{1}{1-\rho^2_{\hat{\theta}}} $ } \label{Assumption_MLE}
+\end{enumerate}
+
+where $\rho^2_{\hat{\theta}}$ is the matrix of correlation coefficients.
+
+Maximum likelihood estimates are not necessarily unbiased.
+Maximum likelihood estimates, however are efficient and, hence, consistent estimates.
+Furthermore, where a sufficient estimate can be obtained, the maximum likelihood method will obtain it.
+Finally, if $\hat{\theta}$ is a maximum likelihood estimator of $\theta$, the $f\left( \hat{\theta} \right)$ is a maximum likelihood estimator of $f\left( \theta \right)$, a function of $\theta$.
+
+\hrule
+
+%Under the assumption of normality, the lack of prior knowledge about the parameters $\theta^0$ and known initial conditions $y_0$.
+Intuitively, this selects the parameter values that make the observed data most probable.
+The specific value $\hat{\theta}$ that maximizes the likelihood function $L$ is called the maximum likelihood estimate.
+
+As already discussed, the prior information about the estimated parameters can be incorporated in to the maximum likelihood estimator to form a maximum a posteriori probability (MAP) estimate.
+MAP can be used to obtain a point estimate of an unobserved quantity on the basis of empirical data.
+MAP estimation can therefore be seen as a regularization of maximum likelihood estimation.
+The relationship between MAP and MLE can be obtained from the Bayes' rule:
+
+{\footnotesize
+\begin{equation} 
+	\begin{split} \label{EQ: MAP_probability}
+		{\bf \hat{\theta}_{\text{MAP}}} &= \arg\max_{\sigma, \theta \in \Theta} p(\theta | y) \\
+		&= \arg\max_{\sigma, \theta \in \Theta} \frac{p(y | \theta) p(\theta)}{p(y)} \\
+		&= \arg\max_{\sigma, \theta \in \Theta} p(y | \theta) p(\theta) \\
+		&= \arg\max_{\sigma, \theta \in \Theta} \ln(p(y | \theta) p(\theta)) \\
+		&= \arg\max_{\sigma, \theta \in \Theta} \ln p(y | \theta) + \ln p(\theta)
+	\end{split}
+\end{equation} }
+
+We assume the normal distribution of random samples, with identical variance and the prior distribution of $\theta$ given by $\mathcal{N}(\theta^0,\,\sigma_\theta^{2})$.
+The function to be maximized can be written as
+
+{\footnotesize
+\begin{equation} \label{EQ: MAP_L2}
+	\begin{aligned}
+	&\arg\max_{\sigma, \theta \in \Theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 }{2\sigma^2}}
+	+ \ln \prod_{j=0}^{p} \frac{1}{\sigma_\theta\sqrt{2\pi}}e^{-\frac{ \left( \theta - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]  \\
+	= &\arg\max_{\sigma, \theta \in \Theta} \left[- \sum_{i=1}^{n} {\frac{\left( Y(t_i) - y\left( \theta, t_i \right) \right)^2}{2\sigma^2}}
+	- \sum_{j=0}^{p} {\frac{\left( \theta - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]\\
+	= &\arg\min_{\sigma, \theta \in \Theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2
+	+ \frac{\sigma^2}{\sigma_\theta^2} \sum_{j=0}^{p} \left( \theta - \theta^0 \right)^2 \right] \\
+	= &\arg\min_{\sigma, \theta \in \Theta} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 + \lambda_{L2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^0 \right)^2 \right]
+	\end{aligned}
+\end{equation} }
+
+In Equation \ref{EQ: MAP_L2} some of the constants (with respect to $\theta$) were dropped and factored to simplify the expression.
+We can adjust the amount of regularization we want by changing $\lambda_{L2}$.
+Equivalently, we can adjust how much we want to weight the priors carry on the coefficients ($\theta$).
+If we have a very small variance (large $\lambda_{L2}$) then the coefficients will be very close to 0; if we have a large variance (small $\lambda_{L2}$) then the coefficients will not be affected much (similar to as if we didn't have any regularization).
+
+Let's assume that the prior distribution of parameter $\theta$ is given by the Laplace distribution. The likelihood function can defined as follow:
+
+{\footnotesize
+\begin{equation} \label{EQ: MAP_L1}
+	\begin{aligned}
+	&\arg\max_{\sigma, \theta \in \Theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 }{2\sigma^2}}
+	+ \ln \prod_{j=0}^{p} \frac{1}{2b}e^{-\frac{ | \theta - \theta^0 | }{\sigma_\theta}} \right]  \\
+	= &\arg\max_{\sigma, \theta \in \Theta} \left[- \sum_{i=1}^{n} {\frac{\left( Y(t_i) - y\left( \theta, t_i \right) \right)^2}{2\sigma^2}}
+	- \sum_{j=0}^{p} {\frac{ | \theta - \theta^0 | }{\sigma_\theta}} \right]\\
+	= &\arg\min_{\sigma, \theta \in \Theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2
+	+ \frac{\sigma^2}{\sigma_\theta} \sum_{j=0}^{p} | \theta - \theta^0 | \right] \\
+	= &\arg\min_{\sigma, \theta \in \Theta} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 + \lambda_{L1} \sum_{j=0}^{p} | \theta - \theta^0 | \right]
+	\end{aligned}
+\end{equation} }
+
+The Laplacean prior act as $L1$-type of regularization on the optimization problem.
+Instead of preventing any of the coefficients from being too large (due to the squaring), $L1$ promotes sparsity.
+Due to the sparsity some of the parameters can be zero out, and eventually removed from the model.
+$L1$ is more robust to outliers than $L2$.
+
+If the cost function is given by Equations \ref{EQ: MAP_L2} or \ref{EQ: MAP_L1}, then the optimization problem can be formulated as follow:
+
+{\footnotesize
+	\begin{equation}
+		\begin{aligned}
+			&\hat{\theta}_{MAP} &= \arg\max_{\sigma, \theta \in \Theta} \ln p(y | \theta) + \ln p(\theta) \\
+			&\text{subject to}
+			& \dot{x} = f(t,x,\theta) \\
+			&& \dot{\theta} = 0 \\
+			&& y = g(x)
+		\end{aligned}
+\end{equation} }
+
+\hrule
+If the cost function to be maximized is given be Equation \ref{EQ: MAP_probability} and constrained by Equation \ref{EQ: Measurment_noise}, then the method of Lagrange multipliers can be used to convert a constrained problem into a form such that the derivative test of an unconstrained problem can be applied.
+The Lagrange function ($L^*$) can be defined as $\ln(L)$ plus the Lagrangian multipliers $\lambda(t_i)$ times the constraint function
 
@@
 		\begin{split}
-		L^* \equiv \ln p\left( \theta,y_0 \right) + \sum_{i=1}^{n} \left\{ \ln p(y(t_i)|\theta,y_0) \right. \\
-		\left. + \lambda^T \cdot \left[ y(t_i) - \Psi\left( \theta,y_0,t_i \right) - \epsilon(t_i) \right] \right\} \\ - \ln \left[ p\left( y \right) \right]
+			L^* \equiv \ln p\left( \theta \right) + \sum_{i=1}^{n} \left\{ \ln p(y(t_i)|\theta) \right. \\
+			\left. + \lambda^T \cdot {\color{red} \left[ Y(t_i) - y\left( \theta,t_i \right) - \epsilon(t_i) \right] } \right\} \\ - \ln \left[ p\left( y \right) \right]
 		\end{split}
@@
 
-After Equation \ref{EQ: Noise_prob} is substituted into Equation \ref{EQ: MLE_Lagrangian}, and $L^*$ is differentiated with respect to each of the estimated and $\epsilon(t_i)$, and the resulting expression is equated to zero, we get
+After Equation \ref{EQ: Noise_prob} is substituted into Equation \ref{EQ: MLE_Lagrangian}, and $L^*$ can be differentiated with respect to each of the estimates and $\epsilon(t_i)$.
+{\color{red}Based on the first order optimality conditions}, the resulting expression is equated to zero:
 
@@
 		\begin{alignat}{2}
-		\cfrac{\partial L^*}{\partial y_0} &= \cfrac{\partial}{\partial y_0} \ln p(\theta,y_0) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial y_0} \Psi(\theta, y_0,t_i) = 0^T \\
-		\cfrac{\partial L^*}{\partial \theta} &= \cfrac{\partial}{\partial \theta} \ln p(\theta,y_0) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial \theta} \Psi(\theta, y_0,t_i) =0 \\
-		\cfrac{\partial L^*}{\partial \epsilon(t_i)} &= \cfrac{\partial}{\partial \epsilon^T(t_i)} \ln p(\epsilon(t_i)) - \lambda^T(t_i) = 0^T
+			%\cfrac{\partial L^*}{\partial y_0} &= \cfrac{\partial}{\partial y_0} \ln p(\theta,y_0) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial y_0} y(\theta ,t_i) = 0^T \\
+			\cfrac{\partial L^*}{\partial \theta} &= \cfrac{\partial}{\partial \theta} \ln p(\theta) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial \theta} y(\theta,t_i) =0 \\
+			\cfrac{\partial L^*}{\partial \epsilon(t_i)} &= \cfrac{\partial}{\partial \epsilon(t_i)} \ln p(\epsilon(t_i)) - \lambda^T(t_i) = 0^T
 		\end{alignat}
@@
 		\lambda(t_i) &= -\left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \nonumber \\
-	&= -\left( \Gamma(t_i) \right)^{-1} \left[ \textbf{Y}(t_i) - \Psi(\theta,y_0,t_i) \right]
+		&= -\left( \Gamma(t_i) \right)^{-1} \left[ Y(t_i) - y(\theta,t_i) \right]
 \end{align} }
 
-and to eliminate $\lambda(t_i)$ from the first two equations of \ref{EQ: MLE_Lag_diff}.
+and to eliminate $\lambda(t_i)$ from the first equation of \ref{EQ: MLE_Lag_diff}.
 
@@
 
-Finally, we assume that $y_0$ and $\theta^*$ are distributed by a joint normal distribution and that the prior distribution are, respectively
+Finally, we assume that and $\theta^*$ are distributed by a joint normal distribution and that the prior distribution are, respectively
 
@@
 		\begin{align}
-		&p\left( \theta^* \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{\theta^*}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( \theta^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} \left( \theta^* - \theta^{*(0)} \right) \right] \\
-		&p\left( y_0 \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{y_0}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( y_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} \left( y_0 - y_0^{(0)} \right) \right] 
+			&p\left( \theta^* \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{\theta^*}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( \theta^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} \left( \theta^* - \theta^{*(0)} \right) \right]
+			%&p\left( y_0 \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{y_0}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( y_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} \left( y_0 - y_0^{(0)} \right) \right] 
 		\end{align}
@@
 
-{\footnotesize
-\begin{equation}
-	\ln p(\theta^*,y_0) = \ln p(\theta^*) + \ln p(y_0)
-\end{equation} }
+%{\footnotesize
+%	\begin{equation}
+%		\ln p(\theta^*,y_0) = \ln p(\theta^*) + \ln p(y_0)
+%\end{equation} }
 
@@
 		\begin{flalign}
-	&-\left( \hat{y}_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} + \sum_{i=1}^{n}\left[ \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \cdot \cfrac{\partial}{\partial y_0} \Psi\left( \hat{\theta}, \hat{y}, t_i \right) = 0^T  &&\\
-	&-\left( \hat{\theta}^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} + \sum_{i=1}^{n}\left[ \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \cdot \cfrac{\partial}{\partial \theta^*} \Psi\left( \hat{\theta}, \hat{y}, t_i \right) = 0^T &&
+%			&-\left( \hat{y}_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} + \sum_{i=1}^{n}\left[ Y(t_i) - y\left( \hat{\theta}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \cdot \cfrac{\partial}{\partial y_0} y\left( \hat{\theta}, \hat{y}, t_i \right) = 0^T  &&\\
+			&-\left( \hat{\theta}^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} + \sum_{i=1}^{n}\left[ Y(t_i) - y\left( \hat{\theta}, t_i \right) \right]^T \Gamma^{-1}(t_i) \cdot \cfrac{\partial}{\partial \theta^*} y\left( \hat{\theta}, t_i \right) = 0^T &&
 		\end{flalign}
@@
 %For some models, these equations can be explicitly solved for $\hat{\theta}^*$ and $\hat{y}$ but in general no closed-form solution to the maximization problem is known or available, and an MLE can only be found via numerical optimization.
-Under the assumption of normality, the lack of prior knowledge about the parameters $\theta^{(0)}$ and known initial conditions $y_0$, the optimization problem is defined as follow:
+Under the assumption of normality, the lack of prior knowledge about the parameters $\theta^0$ and known initial conditions $y_0$, the optimization problem is defined as follow:
 %
@@
 %\begin{equation}
-%	p(\theta|y(t_i)) = \cfrac{1}{\sqrt{2\pi\sigma}}\exp\left[-\cfrac{ \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}\right]
+%	p(\theta|y(t_i)) = \cfrac{1}{\sqrt{2\pi\sigma}}\exp\left[-\cfrac{ \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}\right]
 %\end{equation} }
@@
 %\begin{equation} 
-%	L =\prod\limits_{i=1}^n p(\theta|y(t_i)) = (2\pi\sigma)^{-n/2}\exp\left[-\cfrac{1}{2\sigma}\sum\limits_{i=1}^n \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2\right]
+%	L =\prod\limits_{i=1}^n p(\theta|y(t_i)) = (2\pi\sigma)^{-n/2}\exp\left[-\cfrac{1}{2\sigma}\sum\limits_{i=1}^n \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2\right]
 %\end{equation} }
@@
 %\begin{equation} 
-%	\ln L=-\cfrac{n}{2}\ln\sigma-\cfrac{n}{2}\ln(2\pi)-\cfrac{\sum\limits_{i=1}^n \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}
+%	\ln L=-\cfrac{n}{2}\ln\sigma-\cfrac{n}{2}\ln(2\pi)-\cfrac{\sum\limits_{i=1}^n \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}
 %\end{equation} }
@@
 %	\begin{split}
-%		{\bf \hat{\theta}_{\text{MAP}}} &= \arg\max_{\bf \theta} p(\theta | y) \\
-%		&= \arg\max_{\bf \theta} \frac{p(y | \theta) p(\theta)}{p(y)} \\
-%		&= \arg\max_{\bf \theta} p(y | \theta) p(\theta) \\
-%		&= \arg\max_{\bf \theta} \ln(p(y | \theta) p(\theta)) \\
-%		&= \arg\max_{\bf \theta} \ln p(y | \theta) + \ln p(\theta)
+%		{\bf \hat{\theta}_{\text{MAP}}} &= \arg\max_{\sigma, \theta \in \Theta} p(\theta | y) \\
+%		&= \arg\max_{\sigma, \theta \in \Theta} \frac{p(y | \theta) p(\theta)}{p(y)} \\
+%		&= \arg\max_{\sigma, \theta \in \Theta} p(y | \theta) p(\theta) \\
+%		&= \arg\max_{\sigma, \theta \in \Theta} \ln(p(y | \theta) p(\theta)) \\
+%		&= \arg\max_{\sigma, \theta \in \Theta} \ln p(y | \theta) + \ln p(\theta)
 %	\end{split}
@@
 %
-%We assume the normal distribution of random samples, with identical variance and the prior distribution of $\theta$ given by $\mathcal{N}(\theta^{(0)},\,\sigma_\theta^{2})$.
+%We assume the normal distribution of random samples, with identical variance and the prior distribution of $\theta$ given by $\mathcal{N}(\theta^0,\,\sigma_\theta^{2})$.
 The likelihood function to be maximized can be written as
@@
 %	\begin{split}
-%	&\arg\max_{\bf \theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2 }{2\sigma^2}}
-%	+ \ln \prod_{j=0}^{p} \frac{1}{\sigma_\theta\sqrt{2\pi}}e^{-\frac{ \left( \hat{\theta} - \theta^{(0)} \right)^2}{2\sigma_\theta^2}} \right]  \\
-%	&= \arg\max_{\bf \theta} \left[- \sum_{i=1}^{n} {\frac{\left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma^2}}
-%	- \sum_{j=0}^{p} {\frac{\left( \hat{\theta} - \theta^{(0)} \right)^2}{2\sigma_\theta^2}} \right]\\
-%	&= \arg\min_{\bf \theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2
-%	+ \frac{\sigma^2}{\sigma_\theta^2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^{(0)} \right)^2 \right] \\
-%	&= \arg\min_{\bf \theta} \left[ \sum_{i=1}^{n} \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2 + \lambda_{L2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^{(0)} \right)^2 \right]
+%	&\arg\max_{\sigma, \theta \in \Theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2 }{2\sigma^2}}
+%	+ \ln \prod_{j=0}^{p} \frac{1}{\sigma_\theta\sqrt{2\pi}}e^{-\frac{ \left( \hat{\theta} - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]  \\
+%	&= \arg\max_{\sigma, \theta \in \Theta} \left[- \sum_{i=1}^{n} {\frac{\left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma^2}}
+%	- \sum_{j=0}^{p} {\frac{\left( \hat{\theta} - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]\\
+%	&= \arg\min_{\bf \theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2
+%	+ \frac{\sigma^2}{\sigma_\theta^2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^0 \right)^2 \right] \\
+%	&= \arg\min_{\bf \theta} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2 + \lambda_{L2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^0 \right)^2 \right]
 %	\end{split}

### 2022-08-14 SFE - Code/RBF.m

@@ -1,0 +1,39 @@
+function [] = RBF()
+    %% import libraries
+    %addpath('C:\dev\casadi-windows-matlabR2016a-v3.5.2');
+    addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
+    import casadi.*
+
+    %% define data - toy example
+    x = linspace(0,1,14);
+    func = @(x) exp(x .* cos(3*pi*x) );
+    y = func(x);
+
+    %% choose a kernel
+    phi = @(r) exp(-(3*r).^2);
+    
+    %% define phi matrix and fill it with data
+    phi_matrix = nan(numel(x));
+
+    for i=1:numel(x)
+        for j=1:numel(x)
+            % find the distance between each point
+            r = pdist([x(i); x(j)],'euclidean');
+            % fill the matrix with phi
+            phi_matrix(i,j) = phi(r);
+        end
+    end
+    phi_matrix
+    %% solve the matrix equation Ax=b to find weights
+    w = phi_matrix / y
+
+    %% evaluate the function
+    s = phi_matrix * w;
+    
+    %%
+    hold on
+    plot(x,y)
+    plot(x,s,'o')
+    hold off
+
+end

### 2022-08-14 SFE - Code/main_fitting_SFE.m

@@ -1,0 +1,179 @@
+clc, close all
+clear all
+%addpath('C:\dev\casadi-windows-matlabR2016a-v3.5.2');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
+import casadi.*
+
+DATA = {'Data_40_200.mat', 'Data_50_200.mat', 'Data_40_300.mat', 'Data_50_300.mat'};
+
+%% Parameters
+nstages = 5;                                                   %
+
+C0fluid = 0;                                            % Extractor initial concentration of extract
+% Fluid phase kg / m^3
+C0solid = 32;                                           % Solid phase kg / m^3
+V       = 0.01/4;                                       % Volume of the extractor  [m3] - Vargas
+epsi    = 0.70;                                         % Porosity [-] - Vargas
+dp      = 0.001;                                        % Diameter of the particle [m] - Vargas
+L       = 0.70;                                         % Length of the extractor [m] - Vargas
+rho_s   = 1087.2;                                       % Densisty of the solid phase [kg / m^3] - Vargas
+km      = 0.29;                                         % Partition coefficient (?)
+mi      = 1/5;                                          % Geometric shape coefficient (?) - Vargas
+Ti      = [313.15, 323.15, 333.15, 343.15];
+Di      = [ 3.03E-11, 3.66E-11, 1.97E-10, 2.73E-10];
+T_kp    = [313.15, 323.15, 333.15, 343.15];
+dkp     = [8.13E-01 6.94E-01 1.04E-01 6.67E-02];
+
+
+Tc      = 304.1;                                        % Critical temperature [K]
+Pc      = 73.8;                                         % Critical pressure [bar]
+omega   = 0.228;                                        % Acentric factor [-]
+R       = 8.314e-5;                                     % Universal gas constant, [m3-bar/K-mol]
+
+kappa   = 0.37464 + 1.54226 * omega - 0.26992 * omega^2;
+
[…]

### 2022-08-14 SFE - Code/plot_fitting.m

@@ -1,0 +1,64 @@
+function [] = plot_fitting(DATA, Time_in_sec, RHO, F, g, x0, KOUT, which_parameter, N_Delay, N_Sample, theta, print_mode)
+
+    Time = 0:numel(Time_in_sec);
+
+    for i = 1:numel(DATA)
+        load(DATA{i});
+    
+        %T0homog   = 50 + 273.15;                             % Extractor initial temperature (pseudo-homogeneous)
+        feedTemp  = T0homog      * ones(1,length(Time_in_sec));  % Kelvin
+        feedPress = feedPress(1) * ones(1,length(Time_in_sec));  % Bars
+    
+        feedFlow  = 0.4 * RHO(i) * 1e-3 / 60 * ones(1,length(Time_in_sec));  % l/min -> kg/min -> Kg / sec
+    
+        %% Inital values
+  
+        uu = [feedTemp', feedPress', feedFlow'];
+    
+        %% Substitute the initial parameters with their estimates
+        if ~isempty(which_parameter)
+            for j=1:length(which_parameter)
+                theta{which_parameter{j}} = KOUT(:,j);
+            end
+        end
+    
+        %% Simulate system with estiamted parameter
+        [yy_out, tt_out, xx_out] = simulateSystem_ParameterEstimation(F, g, x0, uu, KOUT(:,i));
+    
+        %% Confidence interval
+        % Confidence 80   | 85    | 90    | 95    | 99    | 99.5  | 99.9
+        % Interval  1,282 | 1,440 | 1,645 | 1,960 | 2,576 | 2,807 | 3,291
+    
+        %CI = [1.282, 1.440, 1.645, 1.960, 2.576, 2.807, 3.291];
+        subplot(2,2,i)
+    
+        set(gcf,'Units','inches');
+        screenposition = get(gcf,'Position');
+        set(gcf,...
+            'PaperPosition',[0 0 screenposition(3:4)],...
+            'PaperSize',[screenposition(3:4)], ...
+            'renderer','OpenGL');
+        set(gca,'TickLabelInterpreter','latex')
+
+        yy_out_D = [ zeros(1,N_Delay) yy_out(1:end-N_Delay)];
+    
+        hold on
+        plot(Time, yy_out_D, 'LineWidth',1);
+        plot(Time(1:N_Sample:end), data, 'o','MarkerSize',2)
+        hold off
+        xlim([0,Time(end)])
+        ylim([-10,110])
+        
[…]

### 2022-08-14 SFE - Copy/singleShooting_ParameterEstimation.m

@@ -1,69 +1,0 @@
-function [xout, kout] = singleShooting_ParameterEstimation(OCP, x0, u, k0,  parameters)
-
-%addpath('C:\Users\slicz\Desktop\Aalto\Matlab\SFE\casadi-windows-matlabR2016a-v3.5.1');
-%addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
-import casadi.*
-
-nstages = parameters{1};
-
-OCP_solver = casadi.Opti();
-
-% http://www.diva-portal.se/smash/get/diva2:956377/FULLTEXT01.pdf
-nlp_opts = struct;
-nlp_opts.ipopt.max_iter = 100;
-%nlp_opts.ipopt.acceptable_iter = 50;
-%nlp_opts.ipopt.acceptable_tol = 1e-6;
-%nlp_opts.ipopt.tol = 1e-7;
-
-ocp_opts = {'nlp_opts', nlp_opts};
-OCP_solver.solver('ipopt',nlp_opts)
-
-K = OCP_solver.variable(OCP.Nk);
-X = [MX(x0) zeros(OCP.Nx,OCP.N)];
-J = 0;
-
-yout = MX(zeros(OCP.Ny,OCP.N+1));   
-
-%g = @(x, u, y_old) modelSFE_out2(x, u, y_old, parameters, timeStep_in_sec);
-
-for j=1:OCP.N
-    %J=J+OCP.L(U(:,j));
-    X(:,j+1)=OCP.F(X(:,j),u(:,j),K);
-    %yout(:,j+1) = g(X(:,j+1), u(:,j), yout(:,j));
-end
-
-%data = yy(1:N_Sample:end);
-data = X(3*nstages+1,:);
-data = [zeros(1,OCP.N_Delay) data(1:end-OCP.N_Delay)];
-data = diff(data(1:OCP.N_Sample:end));
-
-%J = J + OCP.LS(data);
-J = J + OCP.MSE(data,K(end));
-%J = J + OCP.MAP(data,K(1),K(end));
-
-% state constraints
-if ~isempty(OCP.x_lu)
-    for nx=1:OCP.Nx
-        OCP_solver.subject_to(OCP.x_lu(nx,1)<=X(nx,:)<= OCP.x_lu(nx,2));
-    end
-end
-
-% parameter constraints
-if ~isempty(OCP.k_lu)
-    for nk=1:OCP.Nk
[…]

### 2022-08-14 SFE - MegaFitting/Arrhenius_Di.m

@@ -1,33 +1,0 @@
-function [EA, D0] = Arrhenius_Di(T,D, R)
-
-    [P,S] = polyfit(1./T,log(D),1);
-
-    EA = -P(1)*R;
-    D0 = exp(P(2));
-    
-    %{
-    dT  = [ ones(numel(T),1) 1./T' ];        % Data temperatures of some biomass
-    EA1 = -R * log10(D(1) / D(end)) / (dT(1,2) - dT(numel(T),2)); % Activation energies
-                                                        % We assume that dDi = beta * dT and estimate beta using least-squares
-    betah1 = inv(dT'*dT)*dT'*D';                            % Estimated coefficients
-    betah = betah1(1);                                       %
-
-    
-    %EA1 = -R * log(D(1) / D(end)) / (dT(1,2) - dT(4,2)); % Activation energies
-                                                        % We assume that dDi = beta * dT and estimate beta using least-squares
-    %betah = inv(dT'*dT)*dT'*D';                            % Estimated coefficients
-    %betah = betah(1); 
-    %}
-%     TT = linspace(T(1),T(end));
-%     hold on
-%     plot(1./T,log(D),'o')
-%     plot(1./TT, P(1).*(1./TT) + P(2),'-')
-%     xlabel('1/T [1/K]','interpreter','latex')
-%     ylabel('$ln(Di) [m^2/s]$','interpreter','latex')
-%     R2 = 1 - (S.normr/norm(log(D) - mean(log(D))))^2;
-%     str = sprintf('$R^2 =$%.3f',R2);
-%     annotation('textbox',[.8 .6 .3 .3],'string',str,'FitBoxToText','on','EdgeColor','black','FontSize',15,'interpreter','latex')   
-%     hold off
-%     title(['Line Equation is y = F(x) = ',num2str(P(1)),'*x + ','(',num2str(P(2)),')'],'interpreter','latex');
-%     
-end

### 2022-08-14 SFE - MegaFitting/buildIntegrator_ParameterEstimation.m

@@ -1,41 +1,0 @@
-function F = buildIntegrator_ParameterEstimation(varargin)
-    
-    import casadi.*
-
-    f = varargin{1};
-    d = varargin{2};
-    
-    % Verify if additional arguments were provided
-    
-    options = struct;
-    
-    if(numel(varargin) > 2)
-        options.tf = varargin{3};
-    else
-        options.tf = 1;     
-    end
-    
-    if(numel(varargin) > 3)
-        method = varargin{4};     
-    else                    
-        method = 'cvodes';     
-    end
-    
-    x = MX.sym('x',d(1));
-    u = MX.sym('u',d(2));
-    k = MX.sym('k',d(3));
-    p = [u];
-    
-    DAE      = struct('x', x, 'p', [u; k], 'ode', f(x,u, k));
-    args     = { x , u , k };
-    args_str = {'x','u','k'};
-    
-    %options.nonlinear_solver_iteration = 'functional';
-    %options.newton_scheme = 'tfqmr';
-    
-    F     = integrator('F', method, DAE, options);
-    F_res = F('x0', x, 'p', [u; k]);
-    
-    F     = Function('F', args, {F_res.xf}, args_str, {'x_next'});
-    
-end

### 2022-08-14 SFE - MegaFitting/km_of_T.m

@@ -1,14 +1,0 @@
-function km = km_of_T(T, theta)
-
-% I will get back to you, promised!
-% Dataset comes in as theta
-
-    R  = theta{12};     % R = 8.31446;
-    EA = theta{22};
-    betah = theta{23};
-
-    km = betah .* exp( -EA ./ R ./ T);                   % Estimated Di for some T
-
-    %km = EA.*T + betah;
-  
-end

### 2022-08-14 SFE - MegaFitting/modelSFE_SS.m

@@ -1,113 +1,0 @@
-function xdot = modelSFE_SS(x, u, k, parameters,which_parameter)
-    % (t, x, u, parameters)
-    % Model with (F)luid, (S)olid, (T)emperature
-    % Di is a function of temperature (T), the function works with numbers,
-    % vectors of numbers and vectors of symbolic variables
-    % Rho (Peng-Robinson) are constant numbers
-
-    %% parameters is the vector of model parameters
-    % parameters = [nstages, C0solid, V, epsi, dp, L, rho_s, km, mi, Tc, Pc, R, kappa];
-    %          1        2        3  4     5   6  7      8   9   10  11  12 13
-
-    %% Substitute parameters to estimate with symbolic variables k
-    if ~isempty(which_parameter)
-        fprintf(['The following parameters will be estimated:'])
-        for i=1:length(which_parameter)
-            parameters{which_parameter{i}} = k(i);
-            formatSpec = ' %d,';
-            fprintf(formatSpec, which_parameter{i})
-        end
-    else
-        fprintf(['None of the parameters has been selected\n' ...
-            '-------------------------------------------------\n'])
-    end
-    
-    %% TODO: T_bottom (N+1) - boundary conditions
-
-    nstages_index = parameters{1};     % Number of stages
-    nstages       = parameters{1};
-    C0solid       = parameters{2};                                            % Extractor initial concentration of extract
-    V             = parameters{3};     % Extractor volume (m3)
-    epsi          = parameters{4};     % Void bed fraction
-    dp            = parameters{5};     % Diameter of the particle (m)
-    L             = parameters{6};     % Length of the extractor (m)
-    rho_s         = parameters{7};     %
-    km            = parameters{8};
-    mi            = parameters{9};
-
-    Di            = parameters{44};
-    Dx            = parameters{45};
-    
-    T_u           = u(1);
-    P_u           = u(2);
[…]

### 2022-08-14 SFE - MegaFitting/singleShooting_ParameterEstimation.m

@@ -1,31 +1,0 @@
-function [J] = singleShooting_ParameterEstimation(OCP, x0, u, K,  parameters)
-
-%addpath('C:\Users\slicz\Desktop\Aalto\Matlab\SFE\casadi-windows-matlabR2016a-v3.5.1');
-%addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
-import casadi.*
-
-nstages = parameters{1};
-
-X = [MX(x0) zeros(OCP.Nx,OCP.N)];
-J = 0;
-
-yout = MX(zeros(OCP.Ny,OCP.N+1));   
-
-%g = @(x, u, y_old) modelSFE_out2(x, u, y_old, parameters, timeStep_in_sec);
-
-for j=1:OCP.N
-    %J=J+OCP.L(U(:,j));
-    X(:,j+1)=OCP.F(X(:,j),u(:,j),K);
-    %yout(:,j+1) = g(X(:,j+1), u(:,j), yout(:,j));
-end
-
-%data = yy(1:N_Sample:end);
-data = X(3*nstages+1,:);
-data = [zeros(1,OCP.N_Delay) data(1:end-OCP.N_Delay)];
-data = diff(data(1:OCP.N_Sample:end));
-
-%J = J + OCP.LS(data);
-J = J + OCP.MSE(data,K(end));
-%J = J + OCP.MAP(data,K(1),K(end));
-
-end

### 2022-08-14 SFE - Properties/modelSFE_SS.m

@@ -1,0 +1,113 @@
+function xdot = modelSFE_SS(x, u, k, parameters,which_parameter)
+    % (t, x, u, parameters)
+    % Model with (F)luid, (S)olid, (T)emperature
+    % Di is a function of temperature (T), the function works with numbers,
+    % vectors of numbers and vectors of symbolic variables
+    % Rho (Peng-Robinson) are constant numbers
+
+    %% parameters is the vector of model parameters
+    % parameters = [nstages, C0solid, V, epsi, dp, L, rho_s, km, mi, Tc, Pc, R, kappa];
+    %          1        2        3  4     5   6  7      8   9   10  11  12 13
+
+    %% Substitute parameters to estimate with symbolic variables k
+    if ~isempty(which_parameter)
+        fprintf(['The following parameters will be estimated:'])
+        for i=1:length(which_parameter)
+            parameters{which_parameter{i}} = k(i);
+            formatSpec = ' %d,';
+            fprintf(formatSpec, which_parameter{i})
+        end
+    else
+        fprintf(['None of the parameters has been selected\n' ...
+            '-------------------------------------------------\n'])
+    end
+    
+    %% TODO: T_bottom (N+1) - boundary conditions
+
+    nstages_index = parameters{1};     % Number of stages
+    nstages       = parameters{1};
+    C0solid       = parameters{2};                                            % Extractor initial concentration of extract
+    V             = parameters{3};     % Extractor volume (m3)
+    epsi          = parameters{4};     % Void bed fraction
+    dp            = parameters{5};     % Diameter of the particle (m)
+    L             = parameters{6};     % Length of the extractor (m)
+    rho_s         = parameters{7};     %
+    km            = parameters{8};
+    mi            = parameters{9};
+
+    Di            = parameters{44};
+    Dx            = parameters{45};
+    
+    T_u           = u(1);
+    P_u           = u(2);
[…]

### 2022-08-14 SFE - Properties/singleShooting_ParameterEstimation.m

@@ -1,0 +1,69 @@
+function [xout, kout] = singleShooting_ParameterEstimation(OCP, x0, u, k0,  parameters)
+
+%addpath('C:\Users\slicz\Desktop\Aalto\Matlab\SFE\casadi-windows-matlabR2016a-v3.5.1');
+%addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
+import casadi.*
+
+nstages = parameters{1};
+
+OCP_solver = casadi.Opti();
+
+% http://www.diva-portal.se/smash/get/diva2:956377/FULLTEXT01.pdf
+nlp_opts = struct;
+nlp_opts.ipopt.max_iter = 100;
+%nlp_opts.ipopt.acceptable_iter = 50;
+%nlp_opts.ipopt.acceptable_tol = 1e-6;
+%nlp_opts.ipopt.tol = 1e-7;
+
+ocp_opts = {'nlp_opts', nlp_opts};
+OCP_solver.solver('ipopt',nlp_opts)
+
+K = OCP_solver.variable(OCP.Nk);
+X = [MX(x0) zeros(OCP.Nx,OCP.N)];
+J = 0;
+
+yout = MX(zeros(OCP.Ny,OCP.N+1));   
+
+%g = @(x, u, y_old) modelSFE_out2(x, u, y_old, parameters, timeStep_in_sec);
+
+for j=1:OCP.N
+    %J=J+OCP.L(U(:,j));
+    X(:,j+1)=OCP.F(X(:,j),u(:,j),K);
+    %yout(:,j+1) = g(X(:,j+1), u(:,j), yout(:,j));
+end
+
+%data = yy(1:N_Sample:end);
+data = X(3*nstages+1,:);
+data = [zeros(1,OCP.N_Delay) data(1:end-OCP.N_Delay)];
+data = data(1:OCP.N_Sample:end);
+
+%J = J + OCP.LS(data);
+J = J + OCP.MSE(data,K(end));
+%J = J + OCP.MAP(data,K(1),K(end));
+
+% state constraints
+if ~isempty(OCP.x_lu)
+    for nx=1:OCP.Nx
+        OCP_solver.subject_to(OCP.x_lu(nx,1)<=X(nx,:)<= OCP.x_lu(nx,2));
+    end
+end
+
+% parameter constraints
+if ~isempty(OCP.k_lu)
+    for nk=1:OCP.Nk
[…]

### 2023-01-24 SFE-report/Paramter_fitting.tex
24.01

--- 2022-05-31 SFE-report/Paramter_fitting.tex
@@
 \usepackage{setspace}
+\usepackage{subfiles} % Best loaded last in the preamble
 
@@
 
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric,angles,quotes,calc}
+
 % --------------------------------------------------------------------
 % Packages Configurations
+\usepackage{enumitem}
 % --------------------------------------------------------------------
@@
 % --------------------------------------------------------------------
-
+\graphicspath{{Figures/}}
 % --------------------------------------------------------------------
@@
 \section{Introduction}
-%{\color{brown}Intro about extraction}\\
-The extraction of natural substances from solid materials and liquids with solvents have been a popular subject of research and development in the last years.
-Supercritical fluids have multiple applications in an extraction process due to the pressure-dependent dissolving power and {\color{blue} both gas-and liquid-like properties (for example fluid-like density and gas-like diffusivity).
-Among different supercritical fluids, the supercritical $CO_2$ is one of the most popular due to it is nontoxic, non-flammable and non-corrosive properties.
-The critical point of $CO_2$ is relatively low ($73.8$ bar and $31 ^\circ C$), compare to other fluids.
-The supercritical extraction with $CO_2$ become attractive alternative, to replace traditional extraction techniques.}
-
-%{\color{brown} Literature review of the models}\\
-\sout{The supercritical extraction process is considered unconventional due to the lack of formulation of one general model, properties that strongly depend on working conditions and its unsteady nature.
-Understanding the physics behind the phenomena and the proper mathematical description is necessary to predict the process outcome.
-Several extraction models have been developed to characterize different mass transfer mechanisms and equilibrium relationships.}
-{\color{blue}The extraction of valuable compounds from fixed bed of biomass can be described by one of many mathematical models as presented by \citet{Huang2012}.
-The selection the extraction model is not arbitrary and should be based on the knowledge of phenomenons occurring in the operational unit.
-Each model has its own assumptions and describe different mass transfer mechanisms and equilibrium relationships}.
-
-\citet{Reverchon1996} developed a model, which considers an oil as a single component and assumes that the extraction process is controlled by internal-mass transfer resistance.
-As a result of these assumptions, the external mass transfer was neglected.
-The original model of Reverchon does not consider the influence of axial dispersion and does not take into account the change of density and flow rate along the bed.
-
-Based on analogy to heat transfer, \citet{Reverchon1993} suggested a hot ball model, where the extraction process is treated analogously to {\color{blue} a process in which a hot ball is cooled in a uniform medium} \sout{the process of cooling down a hot ball in a uniform medium}.
-{\color{blue}The hot ball model is used to describe an extraction process from solid particles which contains small quantities of solute so that the solubility is not a limiting factor.
-}
-
-\citet{Sovova1994} \sout{presented the Broken-and-Intact Cell model, which assumes the presence of two solid phases, the broken and intact cells.
-The results of applying Sovova's model allow distinguishing three phases of the extraction process (constant extraction rate, falling extraction rate, and diffusion-controlled periods) directly at the modelling stage.}
-{\color{blue} presented the Broken-and-Intact Cell model.
-The BIC model describes a system where the outer surfaces of particles have been mechanically interrupted.
-The solute from the broken cells is easily accessible for the solvent.
-The extraction of easily accessible solute is fast and directly controlled by its diffusion and convection in the solvent.
-However, the rest of the solute is less accessible because it is closed in the particle's core or intact cells.
-This solute slowly diffuses through the walls of a cell due to high mass transfer resistance.
-In this model, the extraction process is divided into three periods controlled by different mass transfer mechanisms: Constant extraction rate (CER) period, Falling extraction rate (FER) period and Diffusion-controlled (DC) period.}
-
-%{\color{brown}Methodology: sensitivity analysis }\\
-As in many engineering problems, mathematical modelling is crucial to mimic real-life objects, but it requires knowing multiple parameter values.
-One way to better understand the phenomena occurring in the process is to investigate the influences of various parameters on the model's output.
-One of the methods that can be applied is sensitivity analysis.
-Among different types of sensitivity analyses, there are two main groups: a local and global sensitivity analysis.
-The local method involves taking the total derivative of the output with respect to an input parameter at a single point.
-The derivative can be estimated directly by the automatic differentiation.
-{\color{blue}The total derivatives form an additional set of equations that is solved simultaneously with the original system.
-An alternative approach to the direct method is the Adjoint Sensitivity Analysis method.
-In this method, the original model is integrated to obtain the full trajectory of the state.
-Then the adjoint equation is solved backwards in time.
-The adjoint operates backwards in the sense that it determines a gradient with respect to input from a gradient with respect to output as discussed by \citet{Errico1997}.}
-The adjoint method is faster and requires the least memory than the local method.
-However, not all ODEs are stable under backwards integration.
-Moreover, both methods belong to one-at-a-time (OAT) methods, as they allow an investigation of the influence of only one parameter at a time.
-One way to determine the model response to "interactions" between parameters and to observe the non-linear behaviour of the system is to use higher-order derivatives.
-An alternative method is to apply a global sensitivity analysis, which utilises information about parameter uncertainty.
-A sensitivity analysis is considered global when all the parameters vary simultaneously.
-According to \citet{Razavi2015}, the main problem of generalising local sensitivity measures to represent "global" properties is the lack of a unique definition of global sensitivity.
-\sout{These methods allow selecting the most influential parameters, which can be used for optimisation (the finding is a set of control variables, which requires the least effort to affect a model's output), model reduction (removing the least influential parameters), or parameter fitting.
-In this work, the example of supercritical extraction is used to show the practical application of sensitivity analysis.
-Some researchers working with the supercritical fluids extraction process examined the influence of the parameters on the model's output.
-Most of them perform a parametrisation of the process model and solve it multiple times for different combinations of parameters.
-The literature review is presented below.}
-{\color{blue}A sensitivity analysis is helpful to identify parameters that have the greatest effect on the model's output.
-The sensitivity analysis results can be used to find regions in the space of input factors for which the model output is maximum.
-Another application is model reduction - for example, by identifying and removing redundant parts of the model structure.
-In the case of parameter fitting with a large number of parameters, non-sensitive parameters can be excluded from the fitting procedure, reducing the computational cost.
-A sensitivity analysis is used to increase understanding of the relationships between input and output variables in a model.
-
-%{\color{brown} Literature review of the sensitivity analysis}\\
-\citet{Fiori_2007} presented how a model uncertainty affects a supercritical extraction process.
-Authors performed a local sensitivity analysis taken at the mean values of the parameters, determined during the parameter estimation.
-Their analysis shows the importance of two parameters: the particle diameter and the internal mass transfer coefficient.
-The authors found that the supercritical extraction process is almost completely insensitive during the first phase of the process (controlled by the solute's solubility in the supercritical solvent) for a change of these parameters.
-However, the authors claim that the model's sensitivity to parameters becomes high during the second phase of the process (controlled by internal diffusion).
-
-\citet{Rabi_2019} analysed how the different parameters affect the model's output.
-The parameters are dimensionless numbers (e.g., mass transfer Biot, Péclet and Damköhler numbers), which are assumed to take one of few discrete values.
-The simulations are performed for each value of parameters and compared with each other.
-The authors found that the Péclet number can strongly affect the extraction efficiency, so the diffusive transport should not be neglected.
-The authors investigated effect of the Damköhler number on the process.
-The authors observed that higher intra-particle diffusion accelerated solid particles depletion so that an optimal extraction time can then be looked for.
-Furthermore, the authors proved that others investigated parameters like partition coefficient and bed porosity influence the extraction yield.
-
-\citet{Glover2008} presented a local sensitivity analysis for an adsorption process.
-Considering the similarities between extraction and adsorption processes, it is interesting to see how the same technique can be applied to different cases.
-The authors examine the sensitivity of the breakthrough of adsorption beds to system parameters.
-The impact of mass and energy transfer effects and adsorbent layer thicknesses are determined by calculating the derivatives of the outlet concentration and outlet temperature.
-The authors applied a Newton-based method along with the sensitivities to determine the optimal layering of an adsorption bed.}
-
-%{\color{brown} Summary of the manuscript}\\
-\sout{In this work, the process model represents supercritical extraction and consists of a set partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables.
-The process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.The impact of mass flow rate, pressure, and inlet temperature on the model's output is analyzed.
-In this work, the sensitivity analysis results are used to prove if the considered variables affect the extraction process and can be used as decision variables in optimization problems.
-The novelty is the application of the local sensitivity analysis in the case of supercritical extraction.}
-{\color{blue}In this work, a distributed-parameter model, based on \citet{Reverchon1996} and \citet{Vargas2006}, is used to describe a fluid-solid extraction process of 'carqueja' oil from 'Baccharis Trimera' leaves with $CO_2$ as a solvent.
-The process model consists of three partial differential equations: two mass balance equations and one heat balance equation.
-To enhance understanding of the process model, the local sensitivity analysis is used to investigate the effect of parameters on the model's output.
-The presented sensitivity analysis results are restricted to parameters related to operating conditions only.
-Furthermore, the sensitivity analysis is used to prove which of the analysed variables can be used as decision variables in optimisation problems.}
+%\subfile{Sections/introduction}
 
 \section{Materials and methods} \label{CH: Materials and methods}
-\sout{The extraction process is assumed to operate in a semi-continuous mode in a cylindrical vessel.
-The solvent is firstly brought to super-critical condition, pumped through a fixed-bed, of finely chopped biomass, where the solute is extracted from the biomass.
-Then, the solvent and solute from the extractor are separated in a flush drum, and the extract is collected.
-The flow rate ($F_{in}$) and inlet temperature ($T_{in}$) of the extractor’s feed can be measured and manipulated.
-The pressure ($P$) in the vessel can be measured and manipulated, while the outlet temperature ($T_{out}$) can only be measured.
-A simplified flow diagram is depicted in Figure \ref{fig: SFE_drawing} }.
-
-{\color{blue}The solid-fluid extraction process is assumed to operate in a semi-continuous mode in a cylindrical vessel.
-In the extractor, essential oils are removed from biomass (for example, carqueja seeds) by supercritical carbon dioxide.
-As the solvent flows continuously through the bed of porous particles, the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles.
-Then the solute dissolves and diffuses into the solvent in the pores and eventually into the bulk.
-The solvent-solute mixture leaves the extractor and undergoes depressurization.
-The $CO_2$ is released to a gaseous state, and the solute precipitates.
-In the vapour-liquid separator, the gaseous solvent is vent off while the precipitated product is collected.
-
-In Figure \ref{fig: SFE_drawing}, an instrumental set-up is presented.
-The flow rate ($F_{in}$) and the temperature ($T_{in}$) of the solvent entering the extractor are measured and can be adjusted using a pump and a heat exchanger, respectively.
-Moreover, the extractor's pressure ($P$) is assumed to be measurable and adjustable using a back-pressure regulator valve.
-In addition, the temperature of the outlet stream $T_{out}$ and the temperature profile of the fixed-bed can be measured.
-}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[trim = 6cm 7.5cm 8cm 6cm, clip, width=\linewidth]{Figures/SFE_PFD.pdf}
-	\caption{Process flow diagram for solid-fluid extraction process}
-	\label{fig: SFE_drawing}
-\end{figure}
+%\subfile{Sections/Materials_and_methods}
 
 \subsection{Extraction model} \label{CH: Extraction_model}
+\subfile{Sections/Model}
 
-\sout{The main components of the model are three one-dimensional differential equations related to mass balances (solid and fluid phase) and heat balance.
-As in all batch processes, our system has only one steady state.
-The steady-state occurs only if the solute is entirely taken out of the biomass.
+%\newpage
+%\section{Bayes theorem} \label{CH: Bayes}
+%\subfile{Sections/Bayes_Theorem}
+%\clearpage
 
-The extraction from a fixed bed is an unsteady process, implying that the solute concentrations in the solid and solvent phases vary over time and space.
-The convection and the diffusion of the mass and the heat are considered only in the axial direction.
-The radial distribution of such properties like a velocity is assumed to be flat in that direction.
-The assumption of the flat velocity profile allows considering a lack of back mixing.
-The pressure drop in the bed is assumed to be assumed to negligible.
-Under such conditions, the fluid flow can be considered a plug flow.
-
-Since the solute is assumed to be a single pseudo-component, there is only one mass balance equation for each phase (Eq.
-s \ref{Model_fluid} and \ref{Model_solid}).
-On the other hand, there is only one heat balance (Eq.
-\ref{Model_heat}) because the presence of a single pseudo-phase is assumed.
-
-Moreover, the process model does not consider the change of particle size or the void fraction during the process.
-The particles are assumed to be uniformly distributed along the bed and to have the same size.}
-
-{\color{blue}A distributed-parameter model, based on \citet{Reverchon1996}, is used to describe the solid-fluid extraction process.
-The process model consists of three partial differential equations: two mass balance equations relative to the concentration of solute in the fixed solid phase and the mobile fluid phase, and the heat balance equation relative to the temperature of the fluid phase.
-The amount of solute in the solvent is considered negligible.
-Therefore, the fluid phase can be described as pseudo-homogenous, and its properties are assumed to be the same as the solvent.
-
-The movement of the mobile pseudo-homogeneous phase (Eq.
-\ref{Model_fluid}) is considered only in the axial direction.
-The properties of the system in the radial direction is assumed to be uniform.
-In addition, it is considered that the boundary layer adjacent to the inner wall of the extractor does not exist.
-Therefore, the velocity profile is constant across any cross-section of the extractor perpendicular to the axial direction.
-As a result, the plug flow model can be introduced.
-The particle size distribution and the void fraction of the solid phase are assumed to be uniform in space and remain constant in time.
-Moreover, the pressure is considered to be constant along the fixed bed.
-The mass balance for the fluid phase consists of convection, diffusion, and kinetic terms.
-
-Considering the solid phase to be fixed, the convection and diffusion terms in the corresponding mass balance are both assumed to be negligible or absent.
-Therefore, the mass balance for the solid phase (Eq.
-\ref{Model_solid}) consists of the kinetic term only.
-
-As for the mass transfer from the solid to the fluid phase, a kinetic term based on two-film theory for the solute is considered.
-The mass transfer kinetic (Eq.
-\ref{Model_kinetic_basic}) consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.
-A single pseudo-component is used to represent the extract collectively.
-
-The heat balance (Eq.
-\ref{Model_heat}) consists of the convective and diffusive terms.
-It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases.
-We consider no heat loss through the wall, and there is no heat generation in the system.
-Therefore, the temperature of the extractor can be changed only by manipulating the temperature of the inlet stream $T_{In}(t)$.
-}
-
-For the sake of clarity of the process model, different colors have been used in the equations to indicate: 
-{\color{red}control variables},
-{\color{blue}state variables},
-{\color{orange}variables} and
-{\color{magenta}parameters}.
-
-\subsubsection{Mass balance for the fluid phase} \label{CH: Mass_balance_fluid}
-The fluid phase is a mobile phase, which means that the fluids mass balance (Eq. \ref{Model_fluid}) is made of convection, diffusion, and mass transfer kinetic terms.
-
-{\footnotesize
-		\begin{align} 
-			\label{Model_fluid}
-			\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t} &	=  \underbrace{-\cfrac{1}{ {\color{magenta}\varepsilon A}}\cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]} \cfrac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} \\
-			&+ \underbrace{ {\color{orange}D^M_e}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] \cfrac{\partial^2 {\color{blue}c_f}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusive term}}
-			+ \underbrace{ \cfrac{1-{\color{magenta}\varepsilon}}{{\color{magenta}\varepsilon}} {\color{blue}r_e}(t,z) }_{\text{Kinetic term}} 
-		\end{align} }
-
-where ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z), {\color{blue}T}(t,z)$ correspond to concentration of solute in the fluid phase, concentration of solute in the solid phase and the temperature, respectively.
-${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term.
-${\color{red}F}(t)$ is the mass flow rate, ${\color{red}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{magenta}A}$ is the extractor’s cross section, ${\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient.
-
-\subsubsection{Mass balance for the solid phase} \label{Mass_balance_solid}
-The solid phase is a stationary phase, which indicates a lack of convection and diffusion terms in the mass balance (Eq.
-\ref{Model_solid}).
-Therefore, the only term present in this equation is the kinetic term (defined as presented in equation \ref{Model_kinetic_basic}), which links solid and fluid phases.
-
-{\footnotesize
-		\begin{equation} 
-			\label{Model_solid}
-			%		{\scriptsize\begin{align*}
-			\cfrac{\partial {\color{blue}c_s}(t,z)}{\partial t} = \underbrace{ {\color{blue}r_e}(t,z) }_{\text{Kinetics}}
-		\end{equation} }
-
-\subsubsection{Kinetic term} \label{CH: Kinetic}
-As the solvent flows through the bed, \sout{it forms a film around the porous solid particle and occupies its pores.} {\color{blue}the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to for an external fluid film around the solid particles through the solvent–solid matrix interactions.
-Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected.
-In this work, the molecular diffusion is assumed.}.
-The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
-The graphical representation of the mass transfer mechanism is shown in Figure \ref{fig: SFE_Mechanism}.
-The mean solute concentration in the solid phase is denoted as ${\color{blue}c_s}$.
-At the solid-fluid interface, the equilibrium concentrations are given as ${\color{blue}c_s^*}$ and ${\color{blue}c_P^*}$, respectively for solid and fluid phases.
-The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{blue}c_{P}}$.
-As the solute diffuses through the pore, its concentration changes and reaches ${\color{blue}c_{Pf}}$ at \sout{the end} {\color{blue}the opening} of the pore.
-The solute diffuses through the film around the particle and reaches a concentration in the bulk ${\color{blue}c_f}$.
-It can be assumed that the two-film theory describes the solid-fluid interface inside the pore.
-The overall mass transfer coefficient can be introduced if the relation between the solute concentration in one phase and its equilibrium concentration is known.
-
-\begin{figure}[h!]
-	\centering
-%	\includegraphics[trim  = 6cm 0cm 3cm 0cm,clip,width=\linewidth]{Figures/SFE_draft.png}
-	\includegraphics[trim = 5.8cm 1.1cm 6cm 0.8cm,clip,width=1.0\linewidth]{Figures/SFE_draft.pdf}	
-	\caption{The extraction mechanism}
-	\label{fig: SFE_Mechanism}
-\end{figure}
-
-\citet{Bulley1984} suggest a process where the driving force for extraction is given by the difference between concentration of the solute in the bulk, ${\color{blue}c_f}$, and in the centre of the pore, ${\color{blue}c_P^*}$.
-The concentration ${\color{blue}c_P^*}$ is in equilibrium with ${\color{blue}c_s}$ according to an equilibrium relationship.
-The rate of extraction is thus ${\color{blue}r_\text{e}}\left({\color{blue}c_f} - {\color{blue}c^*_P}({\color{blue}c_s})\right)$.
-
-On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between ${\color{blue}c_s}$ and ${\color{blue}c_P^*}$.
-${\color{blue}c_P^*}$ is determined by an equilibrium relationship with ${\color{blue}c_f}$ and the extraction rate is ${\color{blue}r_\text{e}}\left({\color{blue}c_s} - {\color{blue}c^*_P}({\color{blue}c_f})\right)$.
-
-\sout{The kinetic term, denoted as equation \ref{Model_kinetic_basic}, corresponds to a solute transfer rate between both phases.
-This term is made of the overall diffusion coefficient and the concentration gradient (between one phase and its equilibrium concentration), which acts as a driving force for the process.} {\color{blue}The mass transfer kinetic (Eq.
-\ref{Model_kinetic_basic}) describes a diffusion rate of the solute from solid particles to the solvent.
-The kinetic term consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.} Based on the work of \citet{Bulley1984}, \citet{Reverchon1996} proposed to define the kinetic terms as
-
-{\footnotesize
-\begin{equation} \label{Model_kinetic_basic}
-	{\color{blue}r_e}(t,z) = \cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}q}(t,z) - {\color{blue}q^*}(t,z) \right)
-\end{equation} }
-
-where ${\color{orange}D_i}({\color{blue}T}(t,z))$ corresponds to the overall diffusion coefficient and ${\color{blue}q^*}(t,z)$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).
-${\color{blue}q^*}(t,z)$ can be calculated based on the equilibrium relationship (Eq.
-\ref{Linear_equilibirum}).
-
-\sout{The kinetic term of the model takes into account the properties of the biomass like a sphericity (through the shape coefficient ${\color{magenta}\mu}$ equal to $1/3$ for slabs and $3/5$ for spheres), a characteristic dimension of particles (through the parameter ${\color{magenta}l} = {\color{magenta}r}/3$ where ${\color{magenta}r}$ is the mean particle radius), and the solid density ${\color{magenta}\rho_s}$.
-The fixed bed is characterized by a void fraction ${\color{magenta}\epsilon}$.
-}
-
-{\color{blue} The kinetic term of the model takes into account properties of the solid particles like a sphericity (through the shape coefficient ${\color{magenta}\mu}$), a characteristic dimension of particles (through the parameter ${\color{magenta}l} = {\color{magenta}r}/3$ where ${\color{magenta}r}$ is the mean particle radius), and the bulk density ${\color{magenta}\rho_s}$.
-The fixed bed is characterized by a void fraction ${\color{magenta}\epsilon}$.
-}
-
-According to \citet{Bulley1984}, a linear equilibrium relationship (Eq.
-\ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{blue}c_f^*}(t,z)$ is based on concentration of the solute in the solid phase ${\color{blue}c_s}(t,z)$
-
-{\footnotesize
-\begin{align} \label{Linear_equilibirum}
-	{\color{blue}c}(t,z) &= {\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t)) \allowbreak {\color{blue}q^*}(t,z)
-\end{align} }
-
-The volumetric partition coefficient ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
-\sout{ The ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$ according to $\citet{Spiro2007}$ .}
-{\color{blue} According to \citet{Spiro2007}, the term ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as the function of mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$ }
-
-{\footnotesize
-\begin{align}
-	{\color{orange}k_m}({\color{blue}T}(t,z)) = \cfrac{{\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{magenta}\rho_s}}{{\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}
-\end{align} }
-
-Equation \ref{Model_kinetic} is the full representation of the kinetic term.
-
-{\footnotesize
-	\begin{align}
-		\label{Model_kinetic}
-		{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}q}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c}(t,z) \right)
-\end{align} }
-
-\subsubsection{Heat balance} \label{CH: heat_balance}
-\sout{The heat balance equation (Eq.
-\ref{Model_heat}) was developed, assuming the existence of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases (the amount of solute is considered small enough not to affect the overall heat balance).
-Equation \ref{Model_heat} contains the convection and the diffusion terms.
-It is considered that there is no heat loss through the wall, and there is no heat generation in the system.
-The temperature of the extractor can be changed only by increasing the temperature of the inlet stream.
-The pseudo-homogenous phase is assumed to flow only in the axial direction.
-The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ because the solid phase is stationary.
-Therefore, this factor can be understood as the fraction of the fluid's total heat through convection.
-On the other hand, the axial heat diffusion is calculated based on the definition of thermal diffusivity for the fluid, as explained in the appendix.
-}
-
-{\color{blue} The heat balance (Eq.
-\ref{Model_heat}), is based on \citet{Srinivasan2012}, and consists of convective and diffusive terms.
-It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases.
-It is considered that there is no heat loss through the walls, and there is no heat generation in the system.
-The temperature of the extractor can be changed only by manipulating the temperature of the inlet stream ${\color{red}T_{Inlet}}(t)$.
-	}
-
-{\footnotesize
-	\begin{equation} \label{Model_heat}
-		\begin{split}
-			\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} &= 
-			\underbrace{ -\cfrac{{\color{red}F}(t) {\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))}{{\color{magenta}A} 	[(1-{\color{magenta}\epsilon}){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{orange}C_p} ({\color{blue}T}(t,z),{\color{red}P}(t)) + {\color{magenta} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}}  }_{\text{Convection}} + \\
-			& + \underbrace{ {\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{red}P}(t)) \cfrac{\partial^2 {\color{blue}T}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusion}}
-		\end{split}
-	\end{equation} }
-
-where $ {\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient, ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's specific heat, ${\color{magenta}C_{ps}}$ is the specific heat of the solid phase, ${\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial heat diffusion coefficient.
-
-\subsubsection{Extraction yield} \label{CH: Yield}
-\sout{The efficiency of the process (the yield) is calculated according to equation \ref{Model_measurment}.
-The yield is defined as the ratio between a difference of initial solute's mass in the solid phase ${\color{magenta}m_0}$, and an actual amount of solute in the same phase ${\color{blue}m}$, compared to the initial amount of the solute in the fixed bed ${\color{magenta}m_0}$.
-The yield can also be calculated based on the change of solutes concentration in the solid phase if the volume of the extractor ${\color{magenta}V}$ is constant.
-An output function ${\color{blue}y}(t)$ returns a yield curve that represents the fraction of the solute's mass over time.
-The yield is obtained by function ${\color{blue}g}({\color{blue}q}(t,z))$.
-Function ${\color{blue}g}({\color{blue}q}(t,z))$ corresponds to a 'measurement device' that allows to calculate the yield based on the state variable ${\color{blue}q}(t,z)$.
-}
-{\color{blue}The efficiency of the process (the yield) is calculated according to Eq.
-\ref{Model_measurment}, and is based on the change of solute's mass in the solid phase.
-It is defined as ratio the ratio between the difference of its initial value ${\color{magenta}m_0}$ and the actual value ${\color{blue}m}(t,z)$, compared to the initial one.
-The yield can also be calculated based on the change of solutes concentration in the solid phase if the volume of the extractor ${\color{magenta}V}$ is constant.}
-
-{\footnotesize
-	\begin{align} 
-		\label{Model_measurment}
-		{\color{blue}y}(t) ={\color{blue}g}({\color{blue}q}(t,z)) &= \cfrac{ \left({\color{magenta}m_0} - {\color{blue}m}({\color{blue}q}(t,z)) \right) }{{\color{magenta}m_0}} = \cfrac{ {\color{magenta}V} \left({\color{magenta}q_0} - {\color{blue}q}(t,z) \right) }{{\color{magenta}V q_0}}
-	\end{align}	}
-
-\sout{where ${\color{blue}q}(t,z)$ is concentration of solute in a solid phase and a temperature, respectively.
-${\color{magenta}m_0}$ is a initial mass of the solute in the solid phase, ${\color{magenta}q_0}$ is a  initial concentration of the solute in the solid phase, ${\color{magenta}V}$ is an extractor volume.}
-
-\subsubsection{Dependencies} \label{CH: Dependencies}
-{\color{blue}The Peng-Robinson equation of state is used to describe the thermodynamics of the fluid phase.
-The thermal properties of the pseudo-homogeneous phase are assumed to vary along the extractor, though always remaining equal to the corresponding mean values between the fluid and solid phase.
-}
-
-In the process model, properties of the supercritical fluid such as the density ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$, the specific heat ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$, the thermal conductivity ${\color{orange}k^T}({\color{blue}T}(t,z),{\color{red}P}(t))$, or the viscosity ${\color{orange}\eta}({\color{blue}T}(t,z),{\color{red}P}(t))$ are calculated based on the local temperatures along the fixed bed and the pressure.
-The Peng-Robinson equation of state is used to find values of a ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$ and ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$.
-
-The inter-particle diffusion coefficient ${\color{orange}D^M_e}(\allowbreak{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is calculated from the empirical correlation, as the function of the Reynolds number ${\color{orange}R_e}({\color{blue}T}(t,z),{\color{red}P}(t),\allowbreak{\color{red}F}(t))$ and the Peclet's number ${\color{orange}P_e}({\color{blue}T}(t,z),\allowbreak{\color{red}P}(t),{\color{red}F}(t))$.
-The values of the internal diffusion ${\color{orange}D_i} ({\color{blue}T}(t,z))$ and the partition coefficient ${\color{orange}k_m} ({\color{blue}T}(t,z))$ come from the laboratory experiments.
-The expressions and the detailed information of the parameter fitting can be found in the appendix.
-
-\subsubsection{State-space representation} \label{CH: State_space}
-It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}q_0}$.
-Moreover, it is considered that the initial temperature of the extractor in every place is equal to ${\color{magenta}T_0}$.
-Therefore, the initial conditions employed in the simulation are:
-
-{\footnotesize
-\begin{subequations}
-	\begin{align*}
-		{\color{blue}c}(t = 0, z) &= 0   \\
-		{\color{blue}q}(t = 0, z) &= {\color{magenta}q_0} \\
-		{\color{blue}T}(t = 0, z) &= {\color{magenta}T_0}
-	\end{align*}
-\end{subequations} }
-
-The process model can be written in a general form:
-
-{\footnotesize
-\begin{align}
-	\begin{bmatrix}
-		\cfrac{\partial {\color{blue}c}(t,z)}{\partial t}\\
-		\cfrac{\partial {\color{blue}q}(t,z)}{\partial t}\\
-		\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} 
-	\end{bmatrix}
-	& =
-	\begin{bmatrix}
-		{\color{blue}\phi_1} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)\\
-		{\color{blue}\phi_2} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)\\
-		{\color{blue}\phi_3} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)
-	\end{bmatrix} = {\color{blue}\phi} \left( t,z; {\color{magenta}\theta} \right) = \cfrac{\partial {\color{blue}\chi}(t,z)}{\partial t}
-\end{align} }
-
-where ${\color{magenta}\theta}$ is a set of parameters present in the model, ${\color{blue}\phi}$ is a set of functions that correspond to state equations of the model, and ${\color{blue}\chi}$ is the state-space model.
-
-The method of lines is used to transform the process model equations into a set of ODEs denoted as ${\color{blue}G}({\color{blue}x}(t);{\color{magenta}p})$.
-The partial derivatives in $z$-direction are computed using a first-order and second-order finite difference approximation.
-The backward finite difference is used to approximate first-order derivative, while the central difference scheme is used to approximate second-order derivative.
-The length of the fixed bed is divided into $N_z$ equally distributed points in $z$-direction.
-Each function ${\color{blue}\phi_i}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{blue}G}_{i\times N_z+1}$ to ${\color{blue}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation.
-The state-space model ${\color{blue}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{blue}x}}(t)$ (Eq.
-\ref{discretization}).
-
-{\footnotesize
-\begin{align*} \label{discretization}
-	\dot{{\color{blue}x}}(t) &= \cfrac{d {\color{blue}x}(t)}{d t} = 
-	\begin{bmatrix}
-		\cfrac{d {\color{blue}c_{f,1}}(t)}{d t} 	  \\
-		\vdots					  \\
-		\cfrac{d {\color{blue}c_{f,N_z}}(t)}{d t} \\
-		\\ \hline \\
-		\cfrac{d {\color{blue}c_{s,1}}(t)}{d t} 	  \\
-		\vdots					  \\
-		\cfrac{d {\color{blue}c_{s,N_z}}(t)}{d t} \\
-		\\ \hline \\
-		\cfrac{d {\color{blue}T_1}(t)}{d t} 	  \\
-		\vdots 					  \\
-		\cfrac{d {\color{blue}T_{N_z}}(t)}{d t}
-	\end{bmatrix}
-	=
-	\underbrace{\begin{bmatrix}
-			{\color{blue}G_1} \left( {\color{blue}x}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
-			\vdots\\ 
-			{\color{blue}G_{N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
-			\\ \hline \\ \\
-			{\color{blue}G_{N_z+1}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
-			\vdots\\
-			{\color{blue}G_{2N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
-			\\ \\ \hline \\ 
-			{\color{blue}G_{2N_z+1}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right) \\
-			\vdots\\
-			{\color{blue}G_{3N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)
-	\end{bmatrix}}_{{\color{blue}G} \left( {\color{blue}x}(t); {\color{magenta}p} \right)} 
-\end{align*} }
-
-where ${\color{blue}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{magenta}p} \in \mathbb{R}^{N_p =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of model parameters, $N_{u}$ is the number of control variables.
-
-{\color{blue} In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases ($c(t,z)$ and $q(t,z)$, respectively), and the local temperature of the pseudo-homogeneous phase ($T(t,z)$).
-The controllable input variables are the mass flow-rate and temperature of the solvent in the feed ($F_\text{in}(t) = F(t)$ and $T_\text{in}(t) = T(t,z=0)$, respectively) and the pressure in the extractor ($P(t,z) = P(t)$).
-{\color{red}We also assume that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator ($Y(t)$).} The system is controllable by manipulating the flow-rate and temperature of CO2 in the feed, and the pressure in the extractor.
-}
-
-\newpage
-\section{Bayes theorem} \label{CH: Bayes}
-
-As discussed by \citet{Himmelblau1970}, The Bayesian approach to estimation make use of prior information.
-Such prior knowledge can come from theoretical considerations, from the results of previous experiments, or from assumptions by the experimenter.
-Typically, a Bayesian approach assumes a prior probability distribution of an unknown parameter $\theta$ in some parameter space $\boldsymbol{\theta}$.
-The distribution is updated by using Bayes' rule to obtain the posterior probability distribution.
-
-Consider a set of events or outcomes, $A_1,A_2,...,A_n$, and some other event $B$.
-Bayes' theorem states that the probability that event $A_i$ will occur, given that event $B$ has already occured, which will denoted by $P\{A_i|B\}$, is equal to the product of the probability that $A_i$ will occur regardless of whether $B$ will take place and the probability that $B$ will occur, given that $A_i$  has already taken place, divided by the probability of the occurrence of $B$:
-
-{\footnotesize
-\begin{equation}
-	P\{A_i|B\} = \cfrac{P\{B|A_i\}P\{A_i\}}{P\{B\}}
-\end{equation} }
-
-Further, if al events comprising the set $\{A_i\}$ are included in $A_1,A_2,...,A_n$, then
-
-{\footnotesize
-\begin{equation} \label{EQ: Bayes_discrit}
-	P\{A_i|B\} = \cfrac{P\{B|A_i\}P\{A_i\}}{ \sum_{i=1}^{n} P\{B|A_i\} P\{A_i\} }
-\end{equation} }
-
-We can interpret these symbols as follows:
-
-\begin{enumerate}
-	\item $P\{A_i\}$ is a measure of our degree of belief that event $A_i$ will occur or that hypothesis $A_i$ is true prior to the acquisition of additional evidence that may alter the measure.
-$P\{A_i\}$ is denoted the \textit{prior probability}.
-	\item $P\{A_i|B\}$ is a measure of our degree of belief that event $A_i$ will occur or that hypothesis $A_i$ is true, given additional evidence $B$ pertinent ot the hypothesis.
-$P\{A_i|B\}$ is termed the \textit{posterior probability}.
-	\item $P\{B|A_i\}$ denotes the likelihood that event $B$ will occur, given that event $A_i$ is true.
-$P\{B|A_i\}$ is a conditional probability, interpreted in the Bayesian framework as a likelihood, $L(A_i|B)$.
-\end{enumerate}
-
-For continuous variable, Bayes' theorem can be more conveniently expressed in terms of the probability density function rather than the probabilities themselves.
-Equation \ref{EQ: Bayes_discrit} can be expressed in terms of a set of observed values of the random variable $X$, \textbf{x} and unknown parameter $(s)\theta$ as
-
-{\footnotesize
-\begin{equation} \label{EQ: Bayes_continous}
-	p\left( \theta|X=\textbf{x} \right) = p\left( \theta|\textbf{x} \right) = \cfrac{L\left( \theta|\textbf{x} \right) p(\theta)}{\int_{-\infty}^{+\infty} L\left( \theta|\textbf{x} \right) p(\theta) d\theta}
-\end{equation} }
-
-where
-
-$p(\theta|\textbf{x}) = ~$the posterior probability density function for $\theta$; it includes knowledge of the possible values of $\theta$ gained from the experimental data \textbf{x}
-
-$p(\theta) = ~$ the prior probability density function for $\theta$ (before the experiment in which \textbf{x} was observed)
-
-$L\left( \theta|\textbf{x} \right) = p\left( \textbf{x}|\theta \right) = ~$ the probability density function termed the likelihood function of $\theta$ given \textbf{x}
-
-The denominator in Equation \ref{EQ: Bayes_continous} is a normalizing factor chosen so that the integration of the posterior distribution is unit, i.e., $\int_{-\infty}^{+\infty} p\left( \theta|\textbf{x} \right) = 1$.
-By taking into account the law of total probability, the denominator can be written as
-
-{\footnotesize
-\begin{equation}
-	\int_{-\infty}^{+\infty} p\left( \textbf{x}|\theta \right) p(\theta) d\theta = p(\textbf{x})
-\end{equation} }
-
-If the prior distribution is a uniform distribution, that is the prior distribution is a constant, the \ref{EQ: Bayes_continous} reduces to
-
-{\footnotesize
-\begin{equation}
-	p\left( \theta|\textbf{x} \right) = \cfrac{L\left( \theta|\textbf{x} \right)}{\int_{-\infty}^{+\infty} L\left( \theta|\textbf{x}\right) d\theta}
-\end{equation} }
-
-If the prior knowledge concerning a postulated event or hypothesis is poor, the posterior probability is largely or entirely determined by the likelihood function, that is, by the additional accumulated evidence for which the likelihood function acts as a mathematical expression.
-If prior knowledge outweighs recent evidence, however, then the posterior probability is determined almost solely by the prior probability.
-
-In the application of tests and the design of experiments, certain definitions and rules concerning probability are needed and are listed below.
-
-\begin{enumerate}
-	\item It follows from the frequency theory of probability that: $0 \leq P \leq 1$
-	\item If the probability of occurrence of one event $A$ depends on whether or not event $B$ has occurred, the two events are termed \textit{dependent}; if the probability of occurrence of event $A$ does not depend on the occurrence of $B$, or the reverse, the two events are \textit{independent}.
-	\item \textbf{Addition Rule}
-	If $A_1,A_2,...,A_n$ are mutually exclusive events, i.e., cannot occur at the same time, the probability of occurrence of just one of the events is equal to the sum of the probabilities of each $A_i$:
-
-	{\footnotesize
-	\begin{equation}
-		P\left( A_1, \text{or~} A_2,..., \text{or~} A_n \right) = \sum_{i=1}^{n} P\left( A_i \right)
-	\end{equation} }
-
-	Very often we let
-
-	{\footnotesize
-	\begin{equation}
-		\sum_{i=1}^{n} P\left( A_i \right) = 1
-	\end{equation} }
-
-	Also, if each event is equi-probable so that $P(A_i) = q$,
-
-	{\footnotesize
-	\begin{equation}
-		\sum_{i=1}^{n} q = nq = 1 \qquad \text{or} \qquad  q=\cfrac{1}{n} = P\left( A_i \right)
-	\end{equation} }
-
-	In set theory, mutually exclusive event have no points in common. The union of the sets which represents the set of all elements that belong to
-
-	{\footnotesize
-	\begin{equation}
-		P\left( A_1 \cup A_2 \cup ... \cup A_n \right) = P(A_1) + P(A_2) + ... + P(A_n)
-	\end{equation} }
-
-	\item \textbf{Multiplication Rule}
-	If $A$ and $B$ are \textit{independent} event
-
-	{\footnotesize
-	\begin{equation}
-		P\left( A \text{~and~} B\right) = P(A)P(B)
-	\end{equation} }
-
-	In set theory the intersection of $A$ and $B$ is the set of all elements that belong to $A$ and $B$:
-
-	{\footnotesize
-	\begin{equation} \label{EQ: Probabiltiy_independet_a}
-		P\left( A \cap B  \right) = P(A)P(B)
-	\end{equation} }
-
-	If the $A$ and $B$ are \textit{dependet} events,
-
-	{\footnotesize
-	\begin{equation} \label{EQ: Probabiltiy_independet_b}
-		P\left(A|B\right) = \cfrac{P\left( A \cap B \right)}{P(B)}
-	\end{equation} }
-
-	where the symbol $P(A|B)$ means "probability of $A$ given $B$". As a corollary,
-
-	{\footnotesize
-	 \begin{subequations}
-		\begin{alignat}{2}
-			P\left( A \cap B \right) &= P(B) P(A|B) \label{EQ: Probabiltiy_dependet_a} \\
-			&= P(A)P(B|A) \label{EQ: Probabiltiy_dependet_b}
-		\end{alignat}
-	\end{subequations} }
-
-	Two kind of probabilities enter Equation \ref{EQ: Probabiltiy_dependet_a} (or Equation \ref{EQ: Probabiltiy_dependet_b}): the absolute probability of event $B$ (or $A$) irrespective of whether or not $A$ (or $B$) has occurred, and that the conditional probability of event $A$ (or $B$) computed on the assumption that $B$ (or $B$) has occurred.
-Equation \ref{EQ: Probabiltiy_independet_a} or \ref{EQ: Probabiltiy_independet_b} is special case of Equation \ref{EQ: Probabiltiy_dependet_a} or \ref{EQ: Probabiltiy_dependet_b}, because if the event are independent $P(A|B)=P(A)$.
-	For the case of many event, Equation \ref{EQ: Probabiltiy_independet_a} can be expanded to
-
-	{\footnotesize
-	\begin{equation}
-		\begin{split}
-			P(A_1 \text{~and~} A_2 \text{~and~} ... \text{~and~} A_n) &= P(A_1)\cdot P(A_2) \cdot  ...\cdot P(A_n) \\ &= \prod_{i=1}^{n} P(A_i)
-		\end{split}
-	\end{equation} }
-
-	\item Another useful relationship for event which are not mutually exclusive is
-
-	{\footnotesize
-	\begin{equation}
-		P(A) + P(B) - P(A \cap B) = P(A \cup B)
-	\end{equation} }
-
-\end{enumerate}
-
-\newpage
-\section{Parameter estimation} \label{CH: Parameter_estimation}
-
-Conceptually, in the measurement equation the unobservable $\epsilon(t)$ is added to $y(t)$ to give the observable dependent variable $Y(t)$ defined as:
-
-{\footnotesize
-\begin{equation}
-	Y(t) = y(t) + \epsilon(t)
-\end{equation} }
-
-If the estimated parameter $\hat{\theta}$ replaces the model parameter $\theta$, the residue error is $\textbf{E} = Y(t) - \hat{Y}(t)$.
-The objective in parameter estimation is to obtain the "best" estimate of $\theta$ based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$.
-
-We assume that $x(t)$ is given \textit{a priori} but the $\textbf{y}_0$ and $\theta$ are to be estimated over the time interval $0 \leq t \leq t_n$ from discrete observation described by the following relation:
-
-{\footnotesize
-\begin{equation}
-	\textbf{Y}(t_i) = h(t_i)y(t_i) + \epsilon(t_i) \qquad 1 \leq i \leq n
-\end{equation} }
-where $\textbf{Y}(t_i)$ is an $n \times 1$ column vector, $h(t_i)$ is an $n \times v$ matrix given \textit{a priori}, and $\epsilon (t_i)$ is an $x \times 1$ column vector ("noise" vector) whose elements are the unobservable errors.
-The above equation can be written in general form as:
-
-{\footnotesize
-\begin{equation} \label{EQ: Measurment_noise}
-	\textbf{Y}(t_i) = \Psi(\theta, y_0, t_i) + \epsilon(t_i)
-\end{equation}}
-where $\Psi$ is the matrix of functions.
-
-Because of the difficulty of obtaining analytical solutions to the deterministic process model, experiments have been arranged wherby the vector of derivatives $d\textbf{Y}/dy$ is measured rather than \textbf{Y} itself.
-In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy/dt$ as follows:
-
-{\footnotesize
-\begin{equation}
-	\cfrac{d\textbf{Y}}{dt} = \cfrac{dy}{dt} + \epsilon
-\end{equation} }
-
-\subsection{Least squares estimation}
-A least squares parameter estimation does not require prior knowledge of the distribution of unobservable errors, yield  unbiased estimates, that is, $ \mathbb{E}\{\hat{Y}(t) = y(t) \} $, and results in the minimum variance among all linear unbiased estimators.
-If the observations $\textbf{Y}$ for the model responses are continuous functions of time from $t = 0$ to $t = t_f$, the Markov (or "rigorous least squares") criterion is to minimize:
-
-{\footnotesize
-\begin{equation}
-	\phi =  \cfrac{1}{2} \int_{0}^{t_f}  \left[ \textbf{Y} - \Psi \right]^T \Gamma^{-1} \left[ \textbf{Y} - \Psi \right] dt
-\end{equation} }
-where $\Gamma$ is the covariance matrix (or perhaps a matrix of appropriate weights), and $\phi$ is the time integrated value of the error squared ("integral squared error").
-If the observations are made at discrete instants of time, $t_i$, $i = 1,2,...,n$, the Markov criterion is to minimize:
-
-{\footnotesize
-\begin{equation}
-	\phi = \cfrac{1}{2} \sum_{i=1}^{n} \left[ \textbf{Y}(t_i) - \Psi(t_i) \right]^T \Gamma^{-1} \left[ \textbf{Y}(t_i) - \Psi(t_i) \right] 
-\end{equation} }
-
-If $\Gamma$ is a diagonal matrix, $\phi$  becomes a "weighted least squares" criterion; if $\Gamma = \sigma^2 \textbf{I}$ where $\sigma$ is a standard deviation, $\phi$ is the "ordinary least squares" criterion.
-
-\subsection{Cumulative data}
-
-One characteristic feature of certain special experiments is the use of the same batch of materials for the entire series of measurements.
-If unobservable error in the first observation is designated as $\epsilon_1$, the second error observation $\epsilon_2'$ includes $\epsilon_1$ plus a random component introduced side from $\epsilon_1$, or $\epsilon_2' = \epsilon_1 + \epsilon_2$.
-The error in the third observation is $\epsilon_3' = \epsilon_1 + \epsilon_2 + \epsilon_3$, and so forth.
-\citet{Mandel1957} distinguished between the usually assumed type of independent measuring error in the dependent variable and a 'cumulative' or interval error in which each new observation includes the error of the previous observations.
-Cumulative errors, arising because of the fluctuations as a function of time in the process itself due to small changes in operating, are not independent - only the differences in measurment from one period to the next are independent.
-Thus, if we consider two model:
-
-{\footnotesize
-\begin{flalign*}
-	&\text{Model A - independent error:} &&\nonumber \\
-	Y_i &= \Psi(\theta, y_0, t_i) + \epsilon_i \qquad i = 1,2,...,n&& \\
-	&\text{Model B - cumulative data:}&& \nonumber \\
-	Y_j - Y_{j-1} &= \Psi(\theta, y_0, t_j) - \Psi(\theta, y_0, t_{j-1}) + \epsilon_j, \quad j = 1,2,...,n&& \\
-	&\text{or}&& \nonumber \\
-	Y_i = \sum_{j=1}^{i} &\left( Y_j - Y_{j-1} \right) = \sum_{j=1}^{i} \left( \Psi(\theta, y_0, t_j) - \Psi(\theta, y_0, t_{j-1}) \right) + \sum_{j=1}^{i} \epsilon_j &&
-\end{flalign*} }
-
-\subsection{Maximum likelihood estimation}
-
-Maximum likelihood estimation (MLE) is a method of estimating the parameters of an assumed probability distribution, given some observed data.
-This is achieved by maximizing a likelihood function so that, under the assumed statistical model, the observed data is most probable.
-The MLE has the desirable characteristics of asymptotic efficiency and normality.
-Each time it has been associated with the (joint) normal distribution because of mathematical convenience.
-Consider the joint probability density function (the likelihood function) $p(\theta, y_0|y)$ for random sample $y = y(t_1),y(t_2),...,y(t_n)$, parameter $\theta$ and initial condition $y_0$ if a maximum of this function over all choices of $y_0$ and $\theta$ can be found, the estimates so obtained are maximum likelihood estimates.
-The conditions at the maximum can be evolved incorporating prior information as follows.
-
-The posterior probability density $p(\theta,y_0|y)$ can be expressed as the ratio of two probability densities if we make use of the analog for continuous variables of Equation \ref{EQ: Probabiltiy_independet_b}:
-
-{\footnotesize
-\begin{equation} \label{EQ: Posterior_distribution}
-	p\left( \theta,y_0|y \right) = \cfrac{p\left( \theta, y_0, y \right)}{p\left( y \right)}
-\end{equation} }
-
-The numerator of the right-hand side od Equation \ref{EQ: Posterior_distribution} using Equation \ref{EQ: Probabiltiy_dependet_a} becomes
-
-{\footnotesize
-\begin{equation}
-	\begin{split}
-		p\left( \theta,y_0,y \right) &= p\left( y(t_n)|\theta,y_0,y(t_{n-1}),...,y(t_1) \right) \\ &\cdot p\left( \theta,y_0,y(t_{n-1}),...,y(t_1) \right)
-	\end{split}
-\end{equation} }
-
-These operations can be continued repetitively until we get
-
-{\footnotesize
-\begin{equation}
-	p\left( \theta,y_0,y \right) = p\left( \theta,y_0 \right) \prod_{i=1}^{n} p\left( \theta,y_0|y \right)
-\end{equation} }
-
-Examination of Equation \ref{EQ: Measurment_noise} shows that $\textbf{Y}(t_i)$ depends only on $t_i$, $y_0$, $\theta$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement.
-Consequently, we can write
-
-{\footnotesize
-\begin{equation}
-	p\left( y(t_i)|\theta,y_0, y(t_{i-1}),...,y(t_1) \right) = p\left( y(t_i)|\theta,y_0 \right)
-\end{equation} }
-
-provided Equation \ref{EQ: Measurment_noise} is observed as a constraint. The desired joint conditional probability function is thus
-
-{\footnotesize
-\begin{equation}
-	p\left( \theta,y_0|y \right) = \cfrac{p\left( \theta,y_0 \right) \prod_{i=1}^{n} p\left( y(t_i)|\theta,y_0 \right) }{p\left( y \right)}
-\end{equation} }
-
-The function to be maximized will be the logarithm of the likelihood function $L = p\left( \theta,y_0| y(t_n),...,y(t_1) \right)$ constrained by equation \ref{EQ: Measurment_noise}, which can be written as $\ln(L)$ plus the Lagrangian multipliers $\lambda(t_k)$ times the constraint function, or
-
-{\footnotesize
-\begin{equation} \label{EQ: MLE_Lagrangian}
-	\begin{split}
-		L^* \equiv \ln p\left( \theta,y_0 \right) + \sum_{i=1}^{n} \left\{ \ln p(y(t_i)|\theta,y_0) \right. \\
-		\left. + \lambda^T \cdot \left[ y(t_i) - \Psi\left( \theta,y_0,t_i \right) - \epsilon(t_i) \right] \right\} \\ - \ln \left[ p\left( y \right) \right]
-	\end{split}
-\end{equation}}
-
-By assumption of the relation of Equation \ref{EQ: Measurment_noise}
-
-\begin{equation} \label{EQ: Noise_prob}
-	p\left( y(t_i) | \theta,y_0 \right) = p\left( \epsilon(t_i) \right)
-\end{equation}
-
-and specially
-
-\begin{equation} \label{EQ: Noise_prob_norm}
-	p\left( \epsilon(t_i) \right) = \cfrac{1}{ (2\pi)^{v/2} |\Gamma(t_i)|^{1/2} } \exp \left[ -\cfrac{1}{2}\epsilon^T(t_i) \left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \right]
-\end{equation}
-where $|\Gamma|$ is the det$~\Gamma$, and $\Gamma$ is the covariance matrix of $\epsilon$, i.e., of the response.
-
-After Equation \ref{EQ: Noise_prob} is substituted into Equation \ref{EQ: MLE_Lagrangian}, and $L^*$ is differentiated with respect to each of the estimated and $\epsilon(t_i)$, and the resulting expression is equated to zero, we get
-
- \begin{subequations} \label{EQ: MLE_Lag_diff}
-	\begin{alignat}{2}
-		\cfrac{\partial L^*}{\partial y_0} &= \cfrac{\partial}{\partial y_0} \ln p(\theta,y_0) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial y_0} \Psi(\theta, y_0,t_i) = 0^T \\
-		\cfrac{\partial L^*}{\partial \theta} &= \cfrac{\partial}{\partial \theta} \ln p(\theta,y_0) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial \theta} \Psi(\theta, y_0,t_i) =0 \\
-		\cfrac{\partial L^*}{\partial \epsilon(t_i)} &= \cfrac{\partial}{\partial \epsilon^T(t_i)} \ln p(\epsilon(t_i)) - \lambda^T(t_i) = 0^T
-	\end{alignat}
- \end{subequations}
-
-Substitution of Equation \ref{EQ: Noise_prob_norm} into the last Equation of \ref{EQ: MLE_Lag_diff} makes it possible to solve for $\lambda(t_i)$:
-
-\begin{align}
-	\lambda(t_i) &= -\left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \nonumber \\
-	&= -\left( \Gamma(t_i) \right)^{-1} \left[ \textbf{Y}(t_i) - \Psi(\theta,y_0,t_i) \right]
-\end{align}
-
-and to eliminate $\lambda(t_i)$ from the first two equations of \ref{EQ: MLE_Lag_diff}.
-
-For convenience we shall define a new column vector $\theta^*$ in which all the elements of $\theta$ are arranged as follows:
-
-\begin{equation}
-	\theta^* = \begin{bmatrix}
-		\theta_{1,1} & \theta_{1,2} & \cdots & \theta_{1,v} & \theta_{2,1} & \cdots & \theta_{2,v} & \cdots & \theta_{v,v}
-	\end{bmatrix}^T	
-\end{equation}
-
-Finally, we assume that $y_0$ and $\theta^*$ are distributed by a joint normal distribution and that the prior distribution are, respectively
-
-\begin{subequations} \label{EQ: MLE_Priors}
-	\begin{align}
-		&p\left( \theta^* \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{\theta^*}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( \theta^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} \left( \theta^* - \theta^{*(0)} \right) \right] \\
-		&p\left( y_0 \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{y_0}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( y_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} \left( y_0 - y_0^{(0)} \right) \right] 
-	\end{align}
-\end{subequations}
-where $\Omega$'s are the respective covariance matrices for $\theta^*$ and $y_0$, and the subscript $(0)$ designates the prior estimated of $\theta^*$ and $y_0$.
-If we assume that $\theta^*$ and $y_0$ are independent
-
-\begin{equation}
-	\ln p(\theta^*,y_0) = \ln p(\theta^*) + \ln p(y_0)
-\end{equation}
-
-Introduction of the prior distributions, Equations \ref{EQ: MLE_Priors}, plus the expression for $\lambda(t_i)$ into the first two equations of \ref{EQ: MLE_Lag_diff} gives the final equations from which the estimators of $\theta^*$ and $y_0$ can be obtained:
-
-\begin{subequations} 
-	\begin{align}
-	-\left( \hat{y}_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} &+ \sum_{i=1}^{n}\left[ \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \nonumber \\ 
-	&\cdot \cfrac{\partial}{\partial y_0} \Psi\left( \hat{\theta}, \hat{y}, t_i \right) = 0^T \\
-	-\left( \hat{\theta}^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} &+ \sum_{i=1}^{n}\left[ \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \nonumber \\
-	&\cdot \cfrac{\partial}{\partial \theta^*} \Psi\left( \hat{\theta}, \hat{y}, t_i \right) = 0^T \nonumber \\
-	\end{align}
-\end{subequations}
-where the overlay caret denotes estimated parameters.
-
-Note that under the assumption that the elements of $\Omega$ are essentially infinite (prior knowledge is diffuse), the elements of $\Omega^-1$ are zero, the equations for the maximum likelihood estimates coincide with those for the least squares estimates, and the same calculations for precision in the estimates apply.
-
-\hrule
-
-For some models, these equations can be explicitly solved for $\hat{\theta}^*$ and $\hat{y}$ but in general no closed-form solution to the maximization problem is known or available, and an MLE can only be found via numerical optimization.
-Under the assumption of normality, the lack of prior knowledge about the parameters $\theta^{(0)}$ and known initial conditions $y_0$, the optimization problem is defined as follow:
-
-\begin{equation}
-	\hat{\theta}_{MLE} = \arg \max_{\theta \in \Theta} L = \arg \max_{\theta \in \Theta} p(\theta|y)
-\end{equation}
-
-Intuitively, this selects the parameter values that make the observed data most probable.
-The specific value $\hat{\theta}$ that maximizes the likelihood function $L$ is called the maximum likelihood estimate.
-Further, if the function $\hat{\theta}:\mathbb{R}\rightarrow\Theta$ so defined is measurable, then it is called the maximum likelihood estimator.
-
-If the random samples $y(t_1)$, $y(t_2)$,...,$y(t_n)$ come from a normal distribution with unknown mean $\hat{\theta}$ and variance $\sigma^2$, then the joint probability function can be written as
-
-\begin{equation}
-	p(\theta|y(t_i)) = \cfrac{1}{\sqrt{2\pi\sigma}}\exp\left[-\cfrac{ \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}\right]
-\end{equation}
-
-Then the likelihood function is defined as follow:
-
-\begin{multline} 
-	L =\prod\limits_{i=1}^n p(\theta|y(t_i)) = \\ (2\pi\sigma)^{-n/2}\exp\left[-\cfrac{1}{2\sigma}\sum\limits_{i=1}^n \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2\right]
-\end{multline}
-
-By taking the ln of the likelihood function, the final form of the cost function is obtained:
-
-\begin{equation} 
-	\ln L=-\cfrac{n}{2}\ln\sigma-\cfrac{n}{2}\ln(2\pi)-\cfrac{\sum\limits_{i=1}^n \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}
-\end{equation}
-
-\subsection{Maximum a posteriori estimation}
-
-As already discussed, the prior information about the estimated parameters can be incorporated in to the maximum likelihood estimator to form a maximum a posteriori probability (MAP) estimate.
-MAP can be used to obtain a point estimate of an unobserved quantity on the basis of empirical data.
-MAP estimation can therefore be seen as a regularization of maximum likelihood estimation.
-MLE and MAP can be connected by Bayes' rule:
-
-\begin{equation} 
-	\begin{split}
-		{\bf \hat{\theta}_{\text{MAP}}} &= \arg\max_{\bf \theta} p(\theta | y) \\
-		&= \arg\max_{\bf \theta} \frac{p(y | \theta) p(\theta)}{p(y)} \\
-		&= \arg\max_{\bf \theta} p(y | \theta) p(\theta) \\
-		&= \arg\max_{\bf \theta} \ln(p(y | \theta) p(\theta)) \\
-		&= \arg\max_{\bf \theta} \ln p(y | \theta) + \ln p(\theta)
-	\end{split}
-\end{equation}
-
-Notice that we can get rid of the evidence term $P(y)$ because it's constant with respect to the maximization and also take the ln of the inner function because it's monotonically increasing.
-
-We assume the normal distribution of random samples, with identical variance and the prior distribution of $\theta$ given by $\mathcal{N}(\theta^{(0)},\,\sigma_\theta^{2})$.
-The likelihood function to be maximized can be written as
-
-\begin{equation} \label{EQ: MAP_L2}
-	\begin{split}
-	&\arg\max_{\bf \theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2 }{2\sigma^2}}
-	+ \ln \prod_{j=0}^{p} \frac{1}{\sigma_\theta\sqrt{2\pi}}e^{-\frac{ \left( \hat{\theta} - \theta^{(0)} \right)^2}{2\sigma_\theta^2}} \right]  \\
-	&= \arg\max_{\bf \theta} \left[- \sum_{i=1}^{n} {\frac{\left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma^2}}
-	- \sum_{j=0}^{p} {\frac{\left( \hat{\theta} - \theta^{(0)} \right)^2}{2\sigma_\theta^2}} \right]\\
-	&= \arg\min_{\bf \theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2
-	+ \frac{\sigma^2}{\sigma_\theta^2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^{(0)} \right)^2 \right] \\
-	&= \arg\min_{\bf \theta} \left[ \sum_{i=1}^{n} \left( \textbf{Y}(t_i) - \Psi\left( \hat{\theta}, t_i \right) \right)^2 + \lambda_{L2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^{(0)} \right)^2 \right]
-	\end{split}
-\end{equation}
-
-Notice that we dropped some of the constants (with respect to $\theta$) and factored to simplify the expression.
-You can see this is the same expression as Equation \ref{EQ: MAP_L2} (L2 Regularization) with $\lambda_{L2}$.
-We can adjust the amount of regularization we want by changing $\lambda_{L2}$.
-Equivalently, we can adjust how much we want to weight the priors carry on the coefficients ($\theta$).
-If we have a very small variance (large $\lambda_{L2}$) then the coefficients will be very close to 0; if we have a large variance (small $\lambda_{L2}$) then the coefficients will not be affected much (similar to as if we didn't have any regularization).
+\subsection{Parameter estimation} \label{CH: Parameter_estimation}
+%\subfile{Sections/Parameter_estimation}
 
@@
 \section{Appendix} 
+\subsection{Governing equations}
+\subsubsection{Mass continuity}
+\subfile{Sections/Gouverning_equation_derivation}
 

### 2023-01-24 SFE-report/Sections/Bayes_Theorem.tex
24.01

\documentclass[../Parameter_fitting.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

As discussed by \citet{Himmelblau1970}, the Bayesian approach to estimation make use of prior information. Such prior knowledge can come from theoretical considerations, from the results of previous experiments, or from assumptions by the experimenter. Typically, a Bayesian approach assumes a prior probability distribution of an unknown parameter $\theta$ in some parameter space $\boldsymbol{\theta}$. The distribution is updated by using Bayes' rule to obtain the posterior probability distribution.

Consider a set of events or outcomes, $A_1,A_2,...,A_n$, and some other event $B$. Bayes' theorem states that the probability that event $A_i$ will occur, given that event $B$ has already occured, which will denoted by $P\{A_i|B\}$, is equal to the product of the probability that $A_i$ will occur regardless of whether $B$ will take place and the probability that $B$ will occur, given that $A_i$  has already taken place, divided by the probability of the occurrence of $B$:

{\footnotesize
	\begin{equation}
		P\{A_i|B\} = \cfrac{P\{B|A_i\}P\{A_i\}}{P\{B\}}
\end{equation} }

Further, if all events comprising the set $\{A_i\}$ are included in $A_1,A_2,...,A_n$, then

{\footnotesize
	\begin{equation} \label{EQ: Bayes_discrit}
		P\{A_i|B\} = \cfrac{P\{B|A_i\}P\{A_i\}}{ \sum_{i=1}^{n} P\{B|A_i\} P\{A_i\} }
\end{equation} }

We can interpret these symbols as follows:

\begin{enumerate}
	\item $P\{A_i\}$ is a measure of our degree of belief that event $A_i$ will occur or that hypothesis $A_i$ is true prior to the acquisition of additional evidence that may alter the measure. $P\{A_i\}$ is denoted the \textit{prior probability}.
	\item $P\{A_i|B\}$ is a measure of our degree of belief that event $A_i$ will occur or that hypothesis $A_i$ is true, given additional evidence $B$ pertinent to the hypothesis. $P\{A_i|B\}$ is termed the \textit{posterior probability}.
	\item $P\{B|A_i\}$ denotes the likelihood that event $B$ will occur, given that event $A_i$ is true. $P\{B|A_i\}$ is a conditional probability, interpreted in the Bayesian framework as a likelihood, $L(A_i|B)$.
\end{enumerate}

For continuous variable, Bayes' theorem can be more conveniently expressed in terms of the probability density function rather than the probabilities themselves. Equation \ref{EQ: Bayes_discrit} can be expressed in terms of a set of observed values of the random variable $X$, the experimental data \textbf{x} and unknown parameter $\theta$ as

{\footnotesize
	\begin{equation} \label{EQ: Bayes_continous}
		p\left( \theta|X=\textbf{x} \right) = p\left( \theta|\textbf{x} \right) = \cfrac{L\left( \theta|\textbf{x} \right) p(\theta)}{\int_{-\infty}^{+\infty} L\left( \theta|\textbf{x} \right) p(\theta) d\theta}
\end{equation} }

where

$p(\theta|\textbf{x}) = ~$the posterior probability density function for $\theta$; it includes knowledge of the possible values of $\theta$ gained from the experimental data \textbf{x}

$p(\theta) = ~$ the prior probability density function for $\theta$ (before the experiment in which \textbf{x} was observed)

$L\left( \theta|\textbf{x} \right) = p\left( \textbf{x}|\theta \right) = ~$ the probability density function termed the likelihood function of $\theta$ given \textbf{x}

The denominator in Equation \ref{EQ: Bayes_continous} is a normalizing factor chosen so that the integration of the posterior distribution is unit, i.e., $\int_{-\infty}^{+\infty} p\left( \theta|\textbf{x} \right) = 1$. By taking into account the law of total probability, the denominator can be written as

{\footnotesize
	\begin{equation}
		\int_{-\infty}^{+\infty} p\left( \textbf{x}|\theta \right) p(\theta) d\theta = p(\textbf{x})
\end{equation} }

If the prior distribution is a uniform distribution, that is the prior distribution is a constant, the Equation \ref{EQ: Bayes_continous} reduces to

{\footnotesize
	\begin{equation}
		p\left( \theta|\textbf{x} \right) = \cfrac{L\left( \theta|\textbf{x} \right)}{\int_{-\infty}^{+\infty} L\left( \theta|\textbf{x}\right) d\theta}
\end{equation} }

If the prior knowledge concerning a postulated event or hypothesis is poor, the posterior probability is largely or entirely determined by the likelihood function, that is, by the additional accumulated evidence for which the likelihood function acts as a mathematical expression. If prior knowledge outweighs recent evidence, however, then the posterior probability is determined almost solely by the prior probability.

In the application of tests and the design of experiments, certain definitions and rules concerning probability are needed and are listed below.

\begin{enumerate}
	\item It follows from the frequency theory of probability that: $0 \leq P \leq 1$
	\item If the probability of occurrence of one event $A$ depends on whether or not event $B$ has occurred, the two events are termed \textit{dependent}; if the probability of occurrence of event $A$ does not depend on the occurrence of $B$, or the reverse, the two events are \textit{independent}.
	\item \textbf{Addition Rule}
	If $A_1,A_2,...,A_n$ are mutually exclusive events, i.e., cannot occur at the same time, the probability of occurrence of just one of the events is equal to the sum of the probabilities of each $A_i$:

	{\footnotesize
		\begin{equation}
			P\left( A_1 \text{or~} A_2... \text{or~} A_n \right) = \sum_{i=1}^{n} P\left( A_i \right)
	\end{equation} }

	Very often we let

	{\footnotesize
		\begin{equation}
			\sum_{i=1}^{n} P\left( A_i \right) = 1
	\end{equation} }

	Also, if each event is equi-probable so that $P(A_i) = q$,

	{\footnotesize
		\begin{equation}
			\sum_{i=1}^{n} q = nq = 1 \qquad \text{or} \qquad  q=\cfrac{1}{n} = P\left( A_i \right)
	\end{equation} }

	In set theory, mutually exclusive event have no points in common. The union of the sets which represents the set of all elements that belong to

	{\footnotesize
		\begin{equation}
			P\left( A_1 \cup A_2 \cup ... \cup A_n \right) = P(A_1) + P(A_2) + ... + P(A_n)
	\end{equation} }

	\item \textbf{Multiplication Rule}
	If $A$ and $B$ are \textit{independent} event

	{\footnotesize
		\begin{equation}
			P\left( A \text{~and~} B\right) = P(A)P(B)
	\end{equation} }

	In set theory the intersection of $A$ and $B$ is the set of all elements that belong to $A$ and $B$:

	{\footnotesize
		\begin{equation} \label{EQ: Probabiltiy_independet_a}
			P\left( A \cap B  \right) = P(A)P(B)
	\end{equation} }

	If the $A$ and $B$ are \textit{dependet} events,

	{\footnotesize
		\begin{equation} \label{EQ: Probabiltiy_independet_b}
			P\left(A|B\right) = \cfrac{P\left( A \cap B \right)}{P(B)}
	\end{equation} }

	where the symbol $P(A|B)$ means "probability of $A$ given $B$". As a corollary,

	{\footnotesize
		\begin{subequations}
			\begin{alignat}{2}
				P\left( A \cap B \right) &= P(B) P(A|B) \label{EQ: Probabiltiy_dependet_a} \\
				&= P(A)P(B|A) \label{EQ: Probabiltiy_dependet_b}
			\end{alignat}
	\end{subequations} }

	Two kind of probabilities enter Equation \ref{EQ: Probabiltiy_dependet_a} (or Equation \ref{EQ: Probabiltiy_dependet_b}): the absolute probability of event $B$ (or $A$) irrespective of whether or not $A$ (or $B$) has occurred, and that the conditional probability of event $A$ (or $B$) computed on the assumption that $B$ (or $B$) has occurred. Equation \ref{EQ: Probabiltiy_independet_a} or \ref{EQ: Probabiltiy_independet_b} is special case of Equation \ref{EQ: Probabiltiy_dependet_a} or \ref{EQ: Probabiltiy_dependet_b}, because if the event are independent $P(A|B)=P(A)$.
	For the case of many event, Equation \ref{EQ: Probabiltiy_independet_a} can be expanded to

	{\footnotesize
		\begin{equation}
			\begin{split}
				P(A_1 \text{~and~} A_2 \text{~and~} ... \text{~and~} A_n) &= P(A_1)\cdot P(A_2) \cdot  ...\cdot P(A_n) \\ &= \prod_{i=1}^{n} P(A_i)
			\end{split}
	\end{equation} }

	\item Another useful relationship for event which are not mutually exclusive is

	{\footnotesize
		\begin{equation}
			P(A) + P(B) - P(A \cap B) = P(A \cup B)
	\end{equation} }

\end{enumerate}

\end{document}

### 2023-01-24 SFE-report/Sections/Gouverning_equation_derivation.tex
24.01

\documentclass[../Parameter_fitting.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Gouverning equations}

	Let's assume that any properties of the flow are uniform across any given cross-section of an extractor. The variation of the cross-section might be an result of partial filling of an extractor or its irregular shape. In reality, such a flow is two-dimensional, because with the area changing as a function of $z$, in actuality there will be flow-field variations in both directions. The assumption of quasi-one-dimensional flow dictates that the flow properties are function of $z$ only. The equations described by quasi-one-dimensional assumption hold: (1) mass conservation, (2) Newton's second law, and (3) energy conservation. To ensure that these physical principles are satisfied the modified governing equation can be derived.	Let's start with the integral form of the continuity equation:

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} \rho_f d\mathcal{V}_f + \iint_S \rho_f \textbf{V} \cdot \textbf{dS} = 0
			\label{EQ: Continuity_integral_general}
		\end{equation}
	}

	We apply this equation to the shaded control volume shown in Fig. \ref{fig: control_volume}.

	\begin{figure}[h]
		\centering
		\begin{tikzpicture}
			\draw [fill=blue!20!white,opacity=0.5] (2.25,2.44) -- (2.25,0.57) -- (1.25,0.31) -- (1.25,2.69) -- cycle;%smmall triangle
			\draw[dashed,color=gray] (0,0) arc (-90:90:0.5 and 1.5);% right half of the left ellipse
			\draw[semithick] (0,0) -- (4,1);% bottom line
			\draw[semithick] (0,3) -- (4,2);% top line
			\draw[semithick] (0,0) arc (270:90:0.5 and 1.5);% left half of the left ellipse
			\draw[semithick] (4,1.5) ellipse (0.166 and 0.5);% right ellipse
			\draw (-1,1.5) node {$A_1$};
			\draw (3.3,1.5) node {$A_2$};
			\draw[|-,semithick] (0,-1.5) -- (4,-1.5);
			\draw[|->,semithick] (4,-1.5) -- (4.5,-1.5);
			\draw (0,-1) node {$z=0$};
			\draw (4,-1) node {$z=L$};
			\draw (1.75,-0.25) node{\scriptsize $ dz $}; %a number
			\draw[|<->|] (1.25,-0.5) -- (2.25,-0.5); %lenght indicator
			\draw[dashed] (1.25,-0.5) -- (1.25,0.3); %dashed line
			\draw[dashed] (2.25,-0.5) -- (2.25,0.58); %dashed line
		\end{tikzpicture}
		\caption{Control volume for deriving partial differential equation for unsteady, quasi-one-dimensional flow}
		\label{fig: control_volume}
	\end{figure}

	This control volume is a slice of an extractor, where the infinitesimal thickens of the slice is $dz$. On the left side of the control volume, consistent with the quasi-one-dimensional assumptions, the density, velocity, pressure and internal energy denoted by $\rho_f$, $V$, $P$, and $e$, respectively, are uniform over the are $A$. Similarly, on the right side of the control volume, the density, velocity, pressure, and internal energy $\rho_f+d\rho_f$, $V+dV$, $P+dP$, and $e+de$, respectively, are uniform over the area available for fluid phase $A_f+dA_f$. Applied to the control volume in Fig. \ref{fig: control_volume}, the volume integral in Eq. \ref{EQ: Continuity_integral_general} becomes, in the limit as $dz$ becomes very small,

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} \rho_f d\mathcal{V}_f = \cfrac{\partial}{\partial t}\left( \rho_f A_f dz \right)
			\label{EQ: Cont_Simpl_Vol}
		\end{equation}
	}

	where $A~dz$ is the volume of the control volume in the limit of $dz$ becoming vanishingly small. The surface integral in Eq. \ref{EQ: Continuity_integral_general} becomes

	{\footnotesize
		\begin{equation}
			\iint_S \rho_f \textbf{V} \cdot \textbf{dS} = -\rho_f V A_f + (\rho_f+d\rho_f)(V+dV)(A_f+dA_f)
		\end{equation}
	}

	where the minus sign on the leading term on the right-hand side is due to the vectors $\textbf{V}$ and $\textbf{dS}$ pointing in opposite directions over the left of the control volume, and hence the dot product is negative. Expending the triple product term

	{\footnotesize
		\begin{align}
			\iint_S \rho_f \textbf{V} \cdot \textbf{dS} &= -\rho_f V A_f + \rho_f V A_f + \rho_f V dA_f + \rho_f A_f dV + \rho_f dV dA_f \nonumber \\ 
			&+ V A_f d\rho_f + V d\rho_f dA + A_f d\rho_f dV + d\rho_f dV dA_f
			\label{EQ: Triple_Prod_Cont_Surf}
		\end{align}
	}

	In the limit as $dz$ becomes very small, the terms involving products of the differential in Eq. \ref{EQ: Triple_Prod_Cont_Surf}, sych as $\rho_f dV dA_f,~d\rho_f dV dA_f$, go to zero much faster than those terms involving only one differential. Hence, all terms involving products of differentials can be dropped, yielding in the limit as $dz$ becomes very small

	{\footnotesize
		\begin{equation}
			\iint_S \rho_f \textbf{V} \cdot \textbf{dS} = \rho_f V dA_f + \rho_f A_f dV + V A_f d\rho_f 
			\label{EQ: Cont_Simpl_Surf}
		\end{equation}
	}

	Substituting Eqs. \ref{EQ: Cont_Simpl_Vol} and \ref{EQ: Cont_Simpl_Surf} into \ref{EQ: Continuity_integral_general}, we have

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_f A_f V \right)}{\partial z} = 0
		\end{equation}
	}

	Above partial differential equation form of the continuity equation suitable for unsteady, quasi-one-dimensional flow. It ensures that mass is conserved for this mode of the flow. The $A_f(z)$ is an arbitrary function, which describe change of the cross-section of an extractor. The function $A_f(z)$ can be defined as $A_f(z) = \textbf{A} \varepsilon(z)$, where $\varepsilon$ is the bed porosity and $\textbf{A}$ is the cross-section of an empty extractor.

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f \textbf{A} \varepsilon (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f \textbf{A} \varepsilon (z) V \right)}{\partial z} = 0
		\end{equation}
	}
	The equation can be simplified by cancel out a constant $\textbf{A}$

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f \varepsilon (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f \varepsilon (z) V \right)}{\partial z} = 0
		\end{equation}
	}

	If so called superficial velocity is defined $u=\varepsilon V$, the mass continuity becomes

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f \varepsilon (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f u \right)}{\partial z} = 0
			\label{EQ: Mass_Continuity}
		\end{equation}
	}

	\hrule

	\subsubsection{Transport of a species}

	The transport of a chemical species, in this case a solute, can be described by analogous equation to the Eq. \ref{EQ: Continuity_integral_general} with additional terms on the right-hand side. The first term on the right-hand side describes that a substance goes from high density regions to low density regions and is based on the Fick's law ${\footnotesize\left( J_{diff}=-D\cfrac{\partial C_f}{\partial z} \right)}$. The other term correspond for the mass transfer between solid and fluid phases, which is treated as a source term.

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} C_f d\mathcal{V}_f + \iint_S C_f \textbf{V} \cdot \textbf{dS} = \iint_S J_{diff} \cdot \textbf{n}~\textbf{dS} + \cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_s} C_s d\mathcal{V}_s
			\label{EQ: Integral_Mass_Species_general}
		\end{equation}
	}

	Similarly to the continuity equation, in the limit as $dz$ becomes very small

	{\footnotesize
		\begin{align}
			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} C_f d\mathcal{V}_f &= \cfrac{\partial}{\partial t}\left( C_f A_f dz \right) \\
			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_s} C_s d\mathcal{V}_s &= \cfrac{\partial}{\partial t}\left( C_s A_s dz \right)
		\end{align}
	}

	The surface integrals in the limit of $dz$ becomes

	{\footnotesize
		\begin{equation}
			\iint_S C_f \textbf{V} \cdot \textbf{dS} = C_f V dA_f + C_f A_f dV + V A_f dC_f 
		\end{equation}
	}

	From the Divergence theorem in multi-variable calculus, we have

	{\footnotesize
		\begin{equation}
			\iint_S J_{diff} \cdot \textbf{n}~\textbf{dS} = \iiint_{\mathcal{V}_f} \nabla J_{diff} dV_f = \nabla \iiint_{\mathcal{V}_f} J_{diff} dV_f = \nabla \left( J_{diff} A_f dz \right)
		\end{equation}
	}

	By substituting the equations derived above into Eq. \ref{EQ: Integral_Mass_Species_general} we obtain

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( C_f A_f \right)}{\partial t} + \cfrac{\partial \left( C_f A_f V \right)}{\partial x} = \cfrac{\partial \left( C_s A_s \right) }{\partial t} + \cfrac{\partial \left( J_{diff} A_f \right) }{\partial z}
		\end{equation}
	}

	By defining $A_f = A \cdot \varepsilon$, $A_s = A \cdot \left( 1-\varepsilon \right)$ and $u=V \cdot \varepsilon$, and assuming that $A$ is constant, the above equation becomes

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( C_f \varepsilon \right)}{\partial t} + \cfrac{\partial \left( C_f u\right)}{\partial x} = \cfrac{\partial \left( C_s (1-\varepsilon) \right) }{\partial t} + \cfrac{\partial \left( J_{diff} \varepsilon \right) }{\partial z}
		\end{equation}
	}

	By expanding above equation, splitting variable and assuming that ${\footnotesize \cfrac{\partial \varepsilon}{\partial t}=0}$ we get

	{\footnotesize
		\begin{equation}
			\cfrac{\partial C_f}{\partial t} + \cfrac{u}{\varepsilon} \cfrac{\partial C_f}{\partial z} + \cfrac{C_f}{\varepsilon} \cfrac{\partial u}{\partial z} = \cfrac{1-\varepsilon}{\varepsilon} \cfrac{\partial C_s}{\partial t} - \cfrac{D}{\varepsilon} \cfrac{\partial C_f}{\partial z} \cfrac{\partial \varepsilon}{\partial z} - \cfrac{\partial}{\partial z} \left( D \cfrac{\partial C_f}{\partial z} \right)
		\end{equation}
	}

	The equation can be further simplified if $\cfrac{\partial u}{\partial z} = \cfrac{\partial \varepsilon}{\partial z} = D = 0$, which corresponds to the assumptions of constant velocity along the bed( which might be a case of isothermal and low-mach number flow), constant porosity( which comes from the assumption of constant area for both solid and fluid phase) and no radial diffusion.

	{\footnotesize
		\begin{equation}
			\cfrac{\partial C_f}{\partial t} + \cfrac{u}{\varepsilon} \cfrac{\partial C_f}{\partial z}  = \cfrac{1-\varepsilon}{\varepsilon} \cfrac{\partial C_s}{\partial t} 
			\label{EQ: Simplified_Species_Conservation}
		\end{equation}
	}

	The Eq. \ref{EQ: Simplified_Species_Conservation} is equivalent to the equation presented by \citet{Reverchon1996}.

	\hrule

	\subsubsection{Momentum conservation}

	Similarly to the mass conservation, the momentum conservation is derived for inviscid fluid with no body forces

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} \left( \rho_f V_z \right) d\mathcal{V}_f + \iint_S \left( \rho_f V_z \textbf{V} \right) \textbf{dS} = \iint_S \left( P dS \right)_z
			\label{EQ: Momentum_Integral_Form}
		\end{equation}
	}
	where $V_z$ is the $z$ component of the velocity.

	We the momentum conservation to the shaded control volume in Fig. \ref{fig: control_volume}, the integrals on the left side are evaluated in the same manner as discussed above in the regard to the continuity equation. That is,

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} \left( \rho_f V_z \right) d \mathcal{V}_f = \cfrac{\partial}{\partial t} \left( \rho_f V A_f dz \right)
			\label{EQ: Force_Continuity_Monenmtum}
		\end{equation}equation
	}

	and

	{\footnotesize
		\begin{equation}
			\iint_S \left( \rho_f V_z \textbf{V} \right) dS = -\rho_f V^2 + \left( \rho_f + d \rho_f \right) \left( V+dV \right)^2 \left( A+dA \right)
		\end{equation}
	}

	\begin{figure}[h]
		\centering
		\includegraphics[width=\columnwidth]{Forces.pdf}
		\caption{The forces in the $z$ direction acting on the control volume}
		\label{fig: Forces_Momentum_Control_Volume}
	\end{figure}

	The evaluation of the pressure force term on the right side of Eq. \ref{EQ: Momentum_Integral_Form} can be understood based on the Fig. \ref{fig: Forces_Momentum_Control_Volume}. Here, the $z$ components of the vector $PdS$ are shown on all four side of the control volume. Remember that $\textbf{dS}$ is assumed to points away from the control volume; hence  any $z$ component $\left( PdS \right)_z$ that acts toward the left (in the negative $z$ direction) is a negative quantity, and any $z$ component that acts toward the right (in the positive $z$ direction) is a positive quantity. Also note that the $z$ component of $P\textbf{dS}$ acting on the top and the bottom inclined faces of the control volume in Fig. \ref{fig: Forces_Momentum_Control_Volume} can be expressed as the pressure $P$ acting on the component of the inclined are projected perpendicular to the $z$ direction, $dA_f/2$; hence, the contribution of each inclined face (top or bottom) to the pressure integral in Eq. \ref{EQ: Momentum_Integral_Form} is $-P(dA_f/2)$. All together, the right-hand side of Eq. \ref{EQ: Momentum_Integral_Form} is expressed as follows:

	{\footnotesize
		\begin{equation}
			\iint \left( PdS \right)_z = -PA_f + (P+dP)(A+dA_f)-2P\cfrac{dA_f}{2}
			\label{EQ: Force_Integral_Varying_Cross_Section}
		\end{equation}
	}

	Substituting Eqs. \ref{EQ: Force_Continuity_Monenmtum} to \ref{EQ: Force_Integral_Varying_Cross_Section} into Eq. \ref{EQ: Momentum_Integral_Form}, we have

	{\footnotesize
		\begin{align}
			& \cfrac{\partial}{\partial t} \left( \rho_f V A_f dz \right) - \rho_f V^2 A_f + (\rho_f + d\rho_f)(V+dV)^2(A_f+dA_f)  \nonumber \\
			&= PA_f - (P+dP)(A+dA_f)+PdA_f
		\end{align}
	}

	Cancelling like terms and ignoring products of differentials, equation above becomes in the limit $dz$ becoming  very small

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial t} \left( \rho_f V A_f dz \right) + d\left( \rho_f V^2 A_f \right) = -A dP
		\end{equation}
	}

	Dividing above equation by $dz$ and taking the limit as $dz$ goes to zero, we obtain

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f V A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_f V^2 A_f \right)}{\partial z} = -A_f \cfrac{\partial P}{\partial z}
			\label{EQ: Conservative_Momentum}
		\end{equation}
	}

	The Eq. \ref{EQ: Conservative_Momentum} can be expanded further by assuming that $A_f = \textbf{A}\varepsilon$

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f V \textbf{A} \varepsilon \right) }{\partial t} + \cfrac{\partial \left( \rho_f V^2 \textbf{A} \varepsilon \right) }{\partial z} = - 	\textbf{A} \varepsilon \cfrac{\partial P}{\partial t}
		\end{equation}
	}

	The equation can be further simplified by assuming that the cross-section of an extractor $\textbf{A}$ is constant and cancel out

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f V \varepsilon \right) }{\partial t} + \cfrac{\partial \left( \rho_f V^2 \varepsilon \right) }{\partial z} = - \varepsilon 	\cfrac{\partial P}{\partial t}
		\end{equation}
	}

	If the superficial velocity $u=\varepsilon V$ is introduced, then the momentum conservation becomes

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f u \right)}{\partial z} + \cfrac{\partial \left( \rho_f u^2/\varepsilon \right) }{\partial z} = -\varepsilon \cfrac{\partial 	P}{\partial z}
		\end{equation}
	}

	Eq. \ref{EQ: Conservative_Momentum} represents the conservative form of the momentum equation for the quasi-one-dimensional flow. The equivalent non-conservative form can be obtained by multiplying the continuity equation by $V$ and subtracting it from Eq. \ref{EQ: Conservative_Momentum}

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f V A_f \right)}{\partial t} - V\cfrac{ \partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\left( \rho_f V^2 A_f 	\right)}{\partial z} - V \cfrac{\left( \rho_f V A_f \right)}{\partial z} = -A_f \cfrac{\partial P}{\partial z}
		\end{equation}
	}

	Expanding the derivatives on the left-hand size of above equation and cancelling like terms, gives

	{\footnotesize
		\begin{equation}
			\rho_f A_f \cfrac{\partial V}{\partial t} + \rho_f A_f V \cfrac{\partial V}{\partial z} = -A_f \cfrac{\partial P}{\partial z}
		\end{equation}
	}

	Dividing above equation by $A_f$ the non-conservative form of the momentum can be obtained

	{\footnotesize
		\begin{equation}
			\rho_f \cfrac{\partial V}{\partial t} + \rho_f V \cfrac{\partial V}{\partial z} = -\cfrac{\partial P}{\partial z}
			\label{EQ: Non-conservative_Momentum}
		\end{equation}
	}

	The Eq. \ref{EQ: Non-conservative_Momentum} is stylistically the same as the general momentum conservation for one-dimensional flow with no-body forces. The momentum equation can be expressed in terms of superficial velocity $u=V\varepsilon$. If $\cfrac{\partial \varepsilon}{\partial t}=0$

	{\footnotesize
		\begin{equation}
			\cfrac{\rho_f}{\varepsilon} \left( \cfrac{\partial u}{\partial t} + \cfrac{u}{\varepsilon} \cfrac{\partial u}{\partial z} + u^2 \cfrac{\partial \varepsilon^{-1}}{\partial z} \right) = -\cfrac{\partial P}{\partial z}
		\end{equation}
	}

	If the porosity is constant along an extractor, then the momentum conservation equation becomes

	{\footnotesize
		\begin{equation}
			\cfrac{\rho_f}{\varepsilon} \left( \cfrac{\partial u}{\partial t} + \cfrac{u}{\varepsilon} \cfrac{\partial u}{\partial z} \right) = -\cfrac{\partial P}{\partial z}
		\end{equation}
	}

\end{document}

### 2023-01-24 SFE-report/Sections/Model.tex
24.01

--- 2022-05-25 SFE-report/Forward_sensitivity_analysis_of_SFE_Sliczniuk.tex
@@
-% ---------------------------------------------------------------
-% Preamble
-% ---------------------------------------------------------------
-%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}
-\documentclass[a4paper,fleqn]{cas-dc}
-%\documentclass[a4paper]{cas-dc}
-%\documentclass[a4paper]{cas-sc}
-% ---------------------------------------------------------------
-
-% -------------------------------------------------------------------- 
-% Packages
-% --------------------------------------------------------------------
-% Figure packages
-\usepackage{float}
-\usepackage{adjustbox}
-% Text, input, formatting, and language-related packages
-\usepackage[T1]{fontenc}
-\usepackage{subcaption}
-% \usepackage[utf8]{inputenc}
-% \usepackage[nomath]{lmodern}
-
-% Margin and formatting specifications
-%\usepackage[authoryear]{natbib}
-\usepackage[sort]{natbib}
-\setcitestyle{square,numbers}
-
- %\bibliographystyle{cas-model2-names}
-
-\usepackage{setspace}
-
-% \usepackage[authoryear,longnamesfirst]{natbib}
-
-% Math packages
-\usepackage{amsmath, amsthm, amssymb, amsfonts, bm, nccmath, mathdots, mathtools, bigints, ulem}
-
-% --------------------------------------------------------------------
-% Packages Configurations
-% --------------------------------------------------------------------
-% (General) General configurations and fixes
-\AtBeginDocument{\setlength{\FullWidth}{\textwidth}}	% Solves els-cas caption positioning issue
-\setlength{\parindent}{20pt}
-%\doublespacing
-% --------------------------------------------------------------------
-% Other Definitions
-% --------------------------------------------------------------------
-
-% --------------------------------------------------------------------
-% Environments
-% --------------------------------------------------------------------
-% ...
-
-% --------------------------------------------------------------------
-% Commands
-% --------------------------------------------------------------------
-
-% ==============================================================
-% ========================== DOCUMENT ==========================
-% ==============================================================
+\documentclass[../Parameter_fitting.tex]{subfiles}
+\graphicspath{{\subfix{../Figures/}}}
 \begin{document}
-%  --------------------------------------------------------------------
-
-% ===================================================
-% METADATA
-% ===================================================
-\title[mode=title]{Parameter estimation}                      
-\shorttitle{Forward sensitivity analysis of the supercritical extraction process}
-
-\shortauthors{A, B, C}
-
-\author[1]{Oliwer Sliczniuk*}[orcid=0000-0003-2593-5956]
-\ead{oliwer.sliczniuk@aalto.fi}
-\cormark[1]
-%\credit{a}
-
-\author[1]{Pekka Oinas}[orcid=0000-0002-0183-5558]
-%\credit{b}
-
-\author[1]{Francesco Corona}[orcid=0000-0002-3615-1359]
-%\credit{c}
-
-\address[1]{Aalto University, School of Chemical Engineering, Espoo, 02150, Finland}
-%\address[2]{2}
-
-\cortext[cor1]{Corresponding author}
-
-% ===================================================
-% ABSTRACT
-% ===================================================
-\begin{abstract}
-Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output.
-As an example, the supercritical extraction process is presented.
-The impact of mass flow rate, pressure, and inlet temperature on the model's output is discussed.
-The sensitivity analysis results prove that the considered variables can affect the extraction's yield and be used as control variables in optimization problems.
-Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
-
-\end{abstract}
-
-\begin{keywords}
-Supercritical extraction \sep Parameter estimation \sep Mathematical modelling
-\end{keywords}
-
-% ===================================================
-% TITLE
-% ===================================================
-\maketitle
-
-% ===================================================
-% Section: Introduction
-% ===================================================\section{Introduction}
-
-\section{Introduction}
-%{\color{brown}Intro about extraction}\\
-The extraction of natural substances from solid materials and liquids with solvents have been a popular subject of research and development in the last years.
-Supercritical fluids have multiple applications in an extraction process due to the pressure-dependent dissolving power and {\color{blue} both gas-and liquid-like properties (for example fluid-like density and gas-like diffusivity).
-Among different supercritical fluids, the supercritical $CO_2$ is one of the most popular due to it is nontoxic, non-flammable and non-corrosive properties.
-The critical point of $CO_2$ is relatively low ($73.8$ bar and $31 ^\circ C$), compare to other fluids.
-The supercritical extraction with $CO_2$ become attractive alternative, to replace traditional extraction techniques.}
-
-%{\color{brown} Literature review of the models}\\
-\sout{The supercritical extraction process is considered unconventional due to the lack of formulation of one general model, properties that strongly depend on working conditions and its unsteady nature.
-Understanding the physics behind the phenomena and the proper mathematical description is necessary to predict the process outcome.
-Several extraction models have been developed to characterize different mass transfer mechanisms and equilibrium relationships.}
-{\color{blue}The extraction of valuable compounds from fixed bed of biomass can be described by one of many mathematical models as presented by \citet{Huang2012}.
-The selection the extraction model is not arbitrary and should be based on the knowledge of phenomenons occurring in the operational unit.
-Each model has its own assumptions and describe different mass transfer mechanisms and equilibrium relationships}.
-
-\citet{Reverchon1996} developed a model, which considers an oil as a single component and assumes that the extraction process is controlled by internal-mass transfer resistance.
-As a result of these assumptions, the external mass transfer was neglected.
-The original model of Reverchon does not consider the influence of axial dispersion and does not take into account the change of density and flow rate along the bed.
-
-Based on analogy to heat transfer, \citet{Reverchon1993} suggested a hot ball model, where the extraction process is treated analogously to {\color{blue} a process in which a hot ball is cooled in a uniform medium} \sout{the process of cooling down a hot ball in a uniform medium}.
-{\color{blue}The hot ball model is used to describe an extraction process from solid particles which contains small quantities of solute so that the solubility is not a limiting factor.
-}
-
-\citet{Sovova1994} \sout{presented the Broken-and-Intact Cell model, which assumes the presence of two solid phases, the broken and intact cells.
-The results of applying Sovova's model allow distinguishing three phases of the extraction process (constant extraction rate, falling extraction rate, and diffusion-controlled periods) directly at the modelling stage.}
-{\color{blue} presented the Broken-and-Intact Cell model.
-The BIC model describes a system where the outer surfaces of particles have been mechanically interrupted.
-The solute from the broken cells is easily accessible for the solvent.
-The extraction of easily accessible solute is fast and directly controlled by its diffusion and convection in the solvent.
-However, the rest of the solute is less accessible because it is closed in the particle's core or intact cells.
-This solute slowly diffuses through the walls of a cell due to high mass transfer resistance.
-In this model, the extraction process is divided into three periods controlled by different mass transfer mechanisms: Constant extraction rate (CER) period, Falling extraction rate (FER) period and Diffusion-controlled (DC) period.}
-
-%{\color{brown}Methodology: sensitivity analysis }\\
-As in many engineering problems, mathematical modelling is crucial to mimic real-life objects, but it requires knowing multiple parameter values.
-One way to better understand the phenomena occurring in the process is to investigate the influences of various parameters on the model's output.
-One of the methods that can be applied is sensitivity analysis.
-Among different types of sensitivity analyses, there are two main groups: a local and global sensitivity analysis.
-The local method involves taking the total derivative of the output with respect to an input parameter at a single point.
-The derivative can be estimated directly by the automatic differentiation.
-{\color{blue}The total derivatives form an additional set of equations that is solved simultaneously with the original system.
-An alternative approach to the direct method is the Adjoint Sensitivity Analysis method.
-In this method, the original model is integrated to obtain the full trajectory of the state.
-Then the adjoint equation is solved backwards in time.
-The adjoint operates backwards in the sense that it determines a gradient with respect to input from a gradient with respect to output as discussed by \citet{Errico1997}.}
-The adjoint method is faster and requires the least memory than the local method.
-However, not all ODEs are stable under backwards integration.
-Moreover, both methods belong to one-at-a-time (OAT) methods, as they allow an investigation of the influence of only one parameter at a time.
-One way to determine the model response to "interactions" between parameters and to observe the non-linear behaviour of the system is to use higher-order derivatives.
-An alternative method is to apply a global sensitivity analysis, which utilises information about parameter uncertainty.
-A sensitivity analysis is considered global when all the parameters vary simultaneously.
-According to \citet{Razavi2015}, the main problem of generalising local sensitivity measures to represent "global" properties is the lack of a unique definition of global sensitivity.
-\sout{These methods allow selecting the most influential parameters, which can be used for optimisation (the finding is a set of control variables, which requires the least effort to affect a model's output), model reduction (removing the least influential parameters), or parameter fitting.
-In this work, the example of supercritical extraction is used to show the practical application of sensitivity analysis.
-Some researchers working with the supercritical fluids extraction process examined the influence of the parameters on the model's output.
-Most of them perform a parametrisation of the process model and solve it multiple times for different combinations of parameters.
-The literature review is presented below.}
-{\color{blue}A sensitivity analysis is helpful to identify parameters that have the greatest effect on the model's output.
-The sensitivity analysis results can be used to find regions in the space of input factors for which the model output is maximum.
-Another application is model reduction - for example, by identifying and removing redundant parts of the model structure.
-In the case of parameter fitting with a large number of parameters, non-sensitive parameters can be excluded from the fitting procedure, reducing the computational cost.
-A sensitivity analysis is used to increase understanding of the relationships between input and output variables in a model.
-
-%{\color{brown} Literature review of the sensitivity analysis}\\
-\citet{Fiori_2007} presented how a model uncertainty affects a supercritical extraction process.
-Authors performed a local sensitivity analysis taken at the mean values of the parameters, determined during the parameter estimation.
-Their analysis shows the importance of two parameters: the particle diameter and the internal mass transfer coefficient.
-The authors found that the supercritical extraction process is almost completely insensitive during the first phase of the process (controlled by the solute's solubility in the supercritical solvent) for a change of these parameters.
-However, the authors claim that the model's sensitivity to parameters becomes high during the second phase of the process (controlled by internal diffusion).
-
-\citet{Rabi_2019} analysed how the different parameters affect the model's output.
-The parameters are dimensionless numbers (e.g., mass transfer Biot, Péclet and Damköhler numbers), which are assumed to take one of few discrete values.
-The simulations are performed for each value of parameters and compared with each other.
-The authors found that the Péclet number can strongly affect the extraction efficiency, so the diffusive transport should not be neglected.
-The authors investigated effect of the Damköhler number on the process.
-The authors observed that higher intra-particle diffusion accelerated solid particles depletion so that an optimal extraction time can then be looked for.
-Furthermore, the authors proved that others investigated parameters like partition coefficient and bed porosity influence the extraction yield.
-
-\citet{Glover2008} presented a local sensitivity analysis for an adsorption process.
-Considering the similarities between extraction and adsorption processes, it is interesting to see how the same technique can be applied to different cases.
-The authors examine the sensitivity of the breakthrough of adsorption beds to system parameters.
-The impact of mass and energy transfer effects and adsorbent layer thicknesses are determined by calculating the derivatives of the outlet concentration and outlet temperature.
-The authors applied a Newton-based method along with the sensitivities to determine the optimal layering of an adsorption bed.}
-
-%{\color{brown} Summary of the manuscript}\\
-\sout{In this work, the process model represents supercritical extraction and consists of a set partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables.
-The process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.The impact of mass flow rate, pressure, and inlet temperature on the model's output is analyzed.
-In this work, the sensitivity analysis results are used to prove if the considered variables affect the extraction process and can be used as decision variables in optimization problems.
-The novelty is the application of the local sensitivity analysis in the case of supercritical extraction.}
-{\color{blue}In this work, a distributed-parameter model, based on \citet{Reverchon1996} and \citet{Vargas2006}, is used to describe a fluid-solid extraction process of 'carqueja' oil from 'Baccharis Trimera' leaves with $CO_2$ as a solvent.
-The process model consists of three partial differential equations: two mass balance equations and one heat balance equation.
-To enhance understanding of the process model, the local sensitivity analysis is used to investigate the effect of parameters on the model's output.
-The presented sensitivity analysis results are restricted to parameters related to operating conditions only.
-Furthermore, the sensitivity analysis is used to prove which of the analysed variables can be used as decision variables in optimisation problems.}
-
-\section{Materials and methods} \label{CH: Materials and methods}
-\sout{The extraction process is assumed to operate in a semi-continuous mode in a cylindrical vessel.
-The solvent is firstly brought to super-critical condition, pumped through a fixed-bed, of finely chopped biomass, where the solute is extracted from the biomass.
-Then, the solvent and solute from the extractor are separated in a flush drum, and the extract is collected.
-The flow rate ($F_{in}$) and inlet temperature ($T_{in}$) of the extractor’s feed can be measured and manipulated.
-The pressure ($P$) in the vessel can be measured and manipulated, while the outlet temperature ($T_{out}$) can only be measured.
-A simplified flow diagram is depicted in Figure \ref{fig: SFE_drawing} }.
-
-{\color{blue}The solid-fluid extraction process is assumed to operate in a semi-continuous mode in a cylindrical vessel.
-In the extractor, essential oils are removed from biomass (for example, carqueja seeds) by supercritical carbon dioxide.
-As the solvent flows continuously through the bed of porous particles, the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles.
-Then the solute dissolves and diffuses into the solvent in the pores and eventually into the bulk.
-The solvent-solute mixture leaves the extractor and undergoes depressurization.
-The $CO_2$ is released to a gaseous state, and the solute precipitates.
-In the vapour-liquid separator, the gaseous solvent is vent off while the precipitated product is collected.
-
-In Figure \ref{fig: SFE_drawing}, an instrumental set-up is presented.
-The flow rate ($F_{in}$) and the temperature ($T_{in}$) of the solvent entering the extractor are measured and can be adjusted using a pump and a heat exchanger, respectively.
-Moreover, the extractor's pressure ($P$) is assumed to be measurable and adjustable using a back-pressure regulator valve.
-In addition, the temperature of the outlet stream $T_{out}$ and the temperature profile of the fixed-bed can be measured.
-}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[trim = 6cm 7.5cm 8cm 6cm, clip, width=\linewidth]{Figures/SFE_PFD.pdf}
-	\caption{Process flow diagram for solid-fluid extraction process}
-	\label{fig: SFE_drawing}
-\end{figure}
-
-\subsection{Extraction model} \label{CH: Extraction_model}
 
@@
 Therefore, the temperature of the extractor can be changed only by manipulating the temperature of the inlet stream $T_{In}(t)$.
+
+		We assume that at a given section, where the cross-sectional area is $A$, the flow properties are uniform across that section.
+Hence, although the are of an extractor changes  as a function of a distance along an extractor (e.g.
+if a fixed fill an extractor partially), $z$, and therefore in reality the flow field is two-dimensional (the flow varies in the two-dimensional space), we make the assumption that the flow properties vary only with $z$; this is tantamount to assuming uniform properties across any given cross section.
+Such flow is defined as quasi-one-dimensional flow.
+
 	}
@@
 
+	\subsubsection{Continuity equation} \label{CH: Continuity}
+	The continuity equation for the fluid phase is given by Eq. \ref{EQ: Continuity}. The details of derivation can be found in the appendix \ref{CH: Gouverning equations}
+
+	{\footnotesize
+		\begin{equation}
+			\cfrac{\partial \left( \rho_f \varepsilon (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f u \right)}{\partial z} = 0
+			\label{EQ: Continuity}
+		\end{equation}
+	}
+
+	where $u$ is the superficial velocity, $\varepsilon$ is the bed porosity and $\rho_f$ is the fluid density.
+
 	\subsubsection{Mass balance for the fluid phase} \label{CH: Mass_balance_fluid}
@@
 			\label{Model_fluid}
-			\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t} &	=  \underbrace{-\cfrac{1}{ {\color{magenta}\varepsilon A}}\cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]} \cfrac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} \\
+			\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t} &	=  \underbrace{-\cfrac{1}{ {\color{magenta}\varepsilon A}}\cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]} \cfrac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} \nonumber \\
 			&+ \underbrace{ {\color{orange}D^M_e}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] \cfrac{\partial^2 {\color{blue}c_f}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusive term}}
@@
 			The volumetric partition coefficient ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
-\sout{ The ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$ according to $\citet{Spiro2007}$ .}
+\sout{ The ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$ according to} \citet{Spiro2007} .
 			{\color{blue} According to \citet{Spiro2007}, the term ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as the function of mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$ }
@@
 
-\newpage
-\section{Parameter estimation} \label{CH: Parameter_estimation}
-Estimation theory is a branch of statistics that deals with estimating the values of parameters based on measured empirical data that has a random component.
-The parameters describe an underlying physical setting in such a way that their value affects the distribution of the measured data.
-An estimator attempts to approximate the unknown parameters using the measurements.
-
-For a given model, several statistical "ingredients" are needed so the estimator can be implemented.
-The first is a statistical sample – a set of data points taken from a random vector (RV) of size $N$.
-Let denote a statistical sample as $x$ and parameters whose vales are to be estimated as $\theta$.
-Both can be written into a vector form:
-\begin{align}
-	x &= [x[0], x[1], \dots, x[N-1] ]^T, &&x \in \mathbb{R}^N \\
-	\theta &= [\theta_0, \theta_1, \dots, \theta_M ]^T,  &&\theta \in \mathbb{R}^M
-\end{align}
-
-where $N$ is the number of samples and $M$ is the number of parameter to estimation.
-
-The continuous probability density function (pdf) or its discrete counterpart, the probability mass function (pmf), of the underlying distribution that generated the data must be stated conditional on the values of the parameters: $p(x|\theta)$.
-It is also possible for the parameters themselves to have a probability distribution (e.g., Bayesian statistics).
-It is then necessary to define the Bayesian probability $\pi(\theta)$.
-After the model is formed, the goal is to estimate the parameters, with the estimates commonly denoted $\hat{\theta}$.
-
-One common estimator is the minimum mean squared error (MMSE) estimator, which utilizes the error between the estimated parameters and the actual value of the parameters as the basis for optimality.
-This error term is then squared and the expected value of this squared value is minimized for the MMSE estimator.
-
-\subsection{Bayes theorem} \label{CH: Bayes_theorem}
-In probability theory and statistics, Bayes' theorem (alternatively Bayes' law or Bayes' rule; recently Bayes–Price theorem[1]: 44, 45, 46 and 67 ), named after Thomas Bayes, describes the probability of an event, based on prior knowledge of conditions that might be related to the event.[2] For example, if the risk of developing health problems is known to increase with age, Bayes' theorem allows the risk to an individual of a known age to be assessed more accurately (by conditioning it on their age) than simply assuming that the individual is typical of the population as a whole.
-
-One of the many applications of Bayes' theorem is Bayesian inference, a particular approach to statistical inference.
-When applied, the probabilities involved in the theorem may have different probability interpretations.
-With Bayesian probability interpretation, the theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
-Bayesian inference is fundamental to Bayesian statistics.
-
-\subsection{Maximum likelihood estimation} \label{CH: MLE}
-\subsection{Maximum a posteriori} \label{CH: MAP}
-\subsection{Bayesian inference} \label{CH: Bayesian_inference}
-
-\section{Results} \label{CH: Results}
-
-\section{Conclusions}
-
-% ===================================================
-% Bibliography
-% ===================================================
-%% Loading bibliography style file
-\clearpage
-%\bibliographystyle{model1-num-names}
-\bibliographystyle{unsrtnat}
-\bibliography{mybibfile}
-
-\clearpage \appendix \label{appendix}
-\section{Appendix}
-
-\newpage
-\begin{table*}[p]
-		\caption{Notation}
-		\label{tab::symbols}
-		\begin{tabular}{ |c|l|c| } 
-			\hline
-			Symbol 		& 	Description 							& Unit 						\\ \hline
-			$A$			&	cross-section							& $m^2$ 					\\ \hline
-			$c$			&	concentration in fluid phase			& $kg ~ m^{-3}$				\\ \hline
-			$Cp$		&	specific heat of the fluid				& $J ~ mol^{-1} ~ K^{-1}$ 	\\ \hline
-			$Cp_s$		&	specific heat of the solid				& $J ~ mol^{-1} ~ K^{-1}$ 	\\ \hline
-			$D_e^M$		&	axial mass diffusion coefficient		& $m^2 ~ s^{-1}$			\\ \hline
-			$D_e^T$		&	axial heat diffusion coefficient		& $m^2 ~ s^{-1}$			\\ \hline
-			$Di$		&	internal diffusion coefficient			& $m^2 ~ s^{-1}$			\\ \hline
-			$dp$		&	particle diameter						& $m$						\\ \hline
-			$F(t)$		&	mass flow-rate							& $kg ~ s^{-1}$				\\ \hline
-			$km$		&	partition coefficient					& $[-]$						\\ \hline
-			$k^T$		&	thermal conductivity					& $W ~ m^{-1} ~ K^{-1}$		\\ \hline
-			$l$			&	characteristic dimension				& $m$						\\ \hline
-			$L$			&	total length of the bed					& $m$						\\ \hline
-			$m$			&	mass of the oil in solid phase			& $kg$						\\ \hline
-			$m_0$		&	initial mass of the oil in solid phase	& $kg$						\\ \hline
-			$M_{CO_2}$	&	molecular mass of CO2					& $mol ~ kg^{-1}$			\\ \hline
-			$Np$		&	number of model parameters and control variables & $[-]$			\\ \hline
-			$N_{\theta}$&	number of model parameters				& $[-]$						\\ \hline
-			$Nu$		&	number of control variables				& $[-]$						\\ \hline
-			$Nz$		&	number of grid points in z-direction	& $[-]$						\\ \hline
-			$p$			&	vector of model parameters and control variables	& $[-]$			\\ \hline
-			$P(t)$		&	pressure								& $bar$						\\ \hline
-			$Pe$		&	Peclet's number							& $[-]$						\\ \hline
-			$q$			&	concentration in solid phase			& $kg ~ m^{-3}$				\\ \hline
-			$R$			&	gas constant							& $J ~ K^{-1} ~ mol^{-1}$	\\ \hline
-			$Re$		&	Reynolds number							& $[-]$						\\ \hline
-			$t$			&	time									& $s$						\\ \hline
-			$T$			&	temperature								& $K$						\\ \hline
-			$T_0$		&	initial temperature						& $K$						\\ \hline
-			$V$			&	volume of the extractor					& $m^3$						\\ \hline
-			$y$			&	yield	 								& $[-]$						\\ \hline
-			$z$			&	length									& $m$						\\ \hline
-			$Z$			&	compressibility	factor					& $[-]$						\\ \hline
-			$\epsilon$	&	void fraction							& $[-]$						\\ \hline
-			$\rho$		&	density of the fluid					& $kg ~ m^{-3}$				\\ \hline
-			$\rho_s$	&	solid density							& $kg ~ m^{-3}$				\\ \hline
-			$\mu$		&	shape coefficient						& $[-]$						\\ \hline
-			$\theta$	&	vector of model parameters				& $[-]$						\\ \hline
-			$\eta$		&	viscosity								& $cP$						\\ \hline				
-						& 											&							\\ \hline			
-		 	Subscript	& 											&							\\ \hline
-			$0$			&	initial conditions						& $[-]$						\\ \hline
-			$^*$		&	equilibrium conditions					& $[-]$						\\ \hline							
-		\end{tabular}
-\end{table*}
 \end{document}

### 2023-01-24 SFE-report/Sections/Parameter_estimation.tex
24.01

\documentclass[../Parameter_fitting.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, $y(t)$, to give the observable dependent variable $Y(t)$, for example the experimental process output. For discrete observations:

{\footnotesize
	\begin{equation}
		Y(t_i) = y(t_i) + \epsilon(t_i)
\end{equation} }
and for continuos variables:

{\footnotesize
	\begin{equation}
		Y(t) = y(t) + \epsilon(t)
\end{equation} }

%If the estimated parameter $\hat{\theta}$ replaces the model parameter $\theta$, the residue error is $\textbf{E} = Y(t) - \hat{Y}(t)$, where $\hat{Y}(t)$ is the predicted value of $Y_i$ at $y_i$. 
The objective in parameter estimation is to obtain the "best" estimate of $\theta$ based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$. 
\sout{
	We assume that $x(t)$ is given \textit{a priori} (for example as a solution of process model) but $\theta$ is to be estimated over the time interval $0 \leq t \leq t_n$ from discrete observation described by the following relation:}

{\footnotesize
	\begin{equation}
		Y(t_i) = \textbf{h}(t_i)y(t_i) + \boldsymbol{\epsilon}(t_i) \qquad 1 \leq i \leq n
\end{equation} }
\sout{where $ Y(t_i)$ is an $n \times 1$ column vector, $\textbf{h}(t_i)$ is an $n \times v$ matrix given \textit{a priori}, and $ \boldsymbol{\epsilon} (t_i)$ is an $n \times 1$ column vector ("noise" vector) whose elements are the unobservable errors. The above equation can be written in general form as:}

{\footnotesize
	\begin{equation} \label{EQ: Measurment_noise}
		Y(t_i) = y(\theta, t_i) + \epsilon(t_i)
\end{equation}}
where $y$ is the output model, which is a function of $\theta$ and time $t_i$.

Because of the difficulty of obtaining analytical solutions to the deterministic process model, experiments have been arranged whereby the vector of derivatives $d Y(t_i)/dt$ is measured rather than $Y(t_i)$ itself. In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ as follows:

{\footnotesize
	\begin{equation}
		\cfrac{d Y(t_i)}{dt} = \cfrac{dy(\theta, t_i)}{dt} + \epsilon(t_i)
\end{equation} }

\subsection{Least squares estimation}
A least squares parameter estimation does not require prior knowledge of the distribution of unobservable errors, yield  unbiased estimates, \sout{that is, $ \mathbb{E}\{\hat{Y}(t) = y(t) \} $,} and results in the minimum variance among all linear unbiased estimators. If the observations $ Y$ for the model responses are continuous functions of time from $t = 0$ to $t = t_f$, the Markov (or "rigorous least squares") criterion is to minimize:

{\footnotesize
	\begin{align}
		\phi &= \cfrac{1}{2} \int_{0}^{t_f}  \left[ Y(t) - y(\theta,t) \right]^T \Gamma^{-1} \left[ Y(t) - y(\theta,t) \right] dt \\
		\hat{\theta} &= \arg \min_{\theta \in \Theta} \phi
\end{align} }
where $\Gamma$ is the covariance matrix (or perhaps a matrix of appropriate weights), $\hat{\theta}$ is the parameter estimate, $\Theta$ is the parameter space, and $\phi$ is the time integrated value of the error squared ("integral squared error"). 
If the observations are made at discrete instants of time, $t_i$, $i = 1,2,...,n$, the Markov criterion is to minimize:

{\footnotesize
	\begin{align}
		\phi &= \cfrac{1}{2} \sum_{i=1}^{n} \left[ Y(t_i) - y(\theta,t_i) \right]^T \Gamma^{-1} \left[ Y(t_i) - y(\theta,t_i) \right] \\
		\hat{\theta} &= \arg \min_{\theta \in \Theta} \phi
\end{align} }

If $\Gamma$ is a diagonal matrix, $\phi$  becomes a "weighted least squares" criterion; if $\Gamma = \sigma^2 \textbf{I}$ where $\sigma$ is a standard deviation., $\phi$ is the "ordinary least squares" criterion.

\subsection{Weighted sum of squares - Cumulative data}

One characteristic feature of certain special experiments is the use of the same batch of materials for the entire series of measurements. If unobservable error in the first observation is designated as $\epsilon_1$, the second error observation $\epsilon_2'$ includes $\epsilon_1$ plus a random component introduced side from $\epsilon_1$, or $\epsilon_2' = \epsilon_1 + \epsilon_2$. The error in the third observation is $\epsilon_3' = \epsilon_1 + \epsilon_2 + \epsilon_3$, and so forth. \citet{Mandel1957} distinguished between the usually assumed type of independent measuring error in the dependent variable and a 'cumulative' or interval error in which each new observation includes the error of the previous observations. Cumulative errors, arising because of the fluctuations as a function of time in the process itself due to small changes in operating, are not independent - only the differences in measurement from one period to the next are independent. Thus, if we consider two model:

{\footnotesize
	\begin{flalign*}
		&{\normalsize \text{Model A - independent error:} } &&\nonumber \\
		Y(t_i) &= y(\theta, t_i) + \epsilon_i  \qquad i = 1,2,...,n&& \\
		&{\normalsize \text{Model B - cumulative data:}} && \nonumber \\
		Y(t_j) - Y(t_{j-1}) &= y(\theta, t_j) - y(\theta, t_{j-1}) + \epsilon_j, \quad j = 1,2,...,n&& \\
		&{\normalsize \text{or}} && \nonumber \\
		Y(t_i) = \sum_{j=1}^{i} &\left( Y(t_j) - Y(t_{j-1}) \right) = \sum_{j=1}^{i} \left( y(\theta, t_j) - y(\theta, t_{j-1}) \right) + \sum_{j=1}^{i} \epsilon_j &&
\end{flalign*} }

in which $\epsilon_i$ are independent random variables with $\mathbb{E}\{\epsilon_i\}$ and Var$\{\epsilon_i\} = \sigma_1^2$, a constant. The $\epsilon_j$ are also random independent variables because they represent differences such as $\epsilon_3' - \epsilon_2' = \left( \epsilon_1 + \epsilon_2 + \epsilon_3 \right) - \left( \epsilon_1 + \epsilon_2 \right) = \epsilon_3$. We assume that $\mathbb{E}\{\epsilon_j\}$ and Var$\{\epsilon_i\} = \sigma_1^2\left(y_j - y_{j-1}\right)$; i.e., the variance of $\epsilon_j$ can be a function of the test interval. The experimental point tend to stay on one side of the regression line of the best fit for Model B.

The \sout{best} unbiased estimate of the Model B is obtained by minimizing the weighted sum of squares:

{\footnotesize
	\begin{equation*}
		\hat{\theta} = \arg \min_{\theta \in \Theta} \sum_{j=1}^{n} \cfrac{ \left[ \left( Y(t_j) - Y(t_{j-1}) \right) - \left( y(\theta, t_j) - y(\theta, t_{j-1}) \right) \right]^2  }{y(\theta, t_j) - y(\theta, t_{j-1})}
\end{equation*} }

\subsection{Maximum likelihood estimation}

Maximum likelihood estimation (MLE) is a method of estimating the parameters of an assumed probability distribution, given some observed data. This is achieved by maximizing a likelihood function so that, under the assumed statistical model, the observed data is most probable. The MLE has the desirable characteristics of asymptotic efficiency and normality. Each time it has been associated with the (joint) normal distribution because of mathematical convenience. Consider the joint probability density function (the likelihood function) $p(\theta |y)$ for random sample $y = y(t_1),y(t_2),...,y(t_n)$, parameter $\theta$. If a maximum of this function over all choices of $\theta$ can be found, the estimates so obtained are maximum likelihood estimates. The conditions at the maximum can be evolved incorporating prior information as follows.

The posterior probability density $p(\theta|y)$ can be expressed as the ratio of two probability densities if we make use of the analogue for continuous variables of Equation \ref{EQ: Probabiltiy_independet_b}:

{\footnotesize
	\begin{align} \label{EQ: Posterior_distribution}
		p\left( \theta| y(t_n),...,y(t_1) \right) = \cfrac{p\left( \theta, y(t_n),...,y(t_1) \right)}{p\left( y(t_n),...,y(t_1) \right)}
\end{align} }

The numerator of the right-hand side od Equation \ref{EQ: Posterior_distribution} using Equation \ref{EQ: Probabiltiy_dependet_a} becomes

{\footnotesize
	\begin{equation}
		\begin{split}
			p\left( \theta,y(t_n),...,y(t_1) \right) &= p\left( y(t_n)|\theta,y(t_{n-1}),...,y(t_1) \right) \\ &\cdot p\left( \theta,y(t_{n-1}),...,y(t_1) \right)
		\end{split}
\end{equation} }

These operations can be continued repetitively until we get

{\footnotesize
	\begin{equation}
		p\left( \theta, y(t_n),...,y(t_1) \right) = p\left( \theta \right) \prod_{i=1}^{n} p\left( y(t_i)|\theta, y(t_{i-1}),...,y(t_1) \right)
\end{equation} }

Examination of Equation \ref{EQ: Measurment_noise} shows that $ Y(t_i)$ depends only on $t_i$, $\theta$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement. Consequently, we can write

{\footnotesize
	\begin{equation}
		p\left( y(t_i)|\theta, y(t_{i-1}),...,y(t_1) \right) = p\left( y(t_i)|\theta \right)
\end{equation} }

provided Equation \ref{EQ: Measurment_noise} is observed as a constraint. The desired joint conditional probability function is thus

{\footnotesize
	\begin{equation}
		p\left( \theta| y(t_n),...,y(t_1) \right) = \cfrac{p\left( \theta \right) \prod_{i=1}^{n} p\left( y(t_i)|\theta \right) }{p\left( y(t_n),...,y(t_1) \right)}
\end{equation} }

We can get rid of the evidence term $p\left( y(t_n),...,y(t_1) \right)$ because it's constant with respect to the maximization. Moreover, if we are lacking a prior distribution over the quantity we want to estimate, then $p(\theta)$ can be omitted. In such a case:

{\footnotesize
	\begin{equation}
		p\left( \theta| y(t_n),...,y(t_1) \right) = \prod_{i=1}^{n} p\left( y(t_i)|\theta \right) = \prod_{i=1}^{n} L\left( \theta|y(t_i) \right) 
\end{equation} }

By collecting a random sample of values of the random variable $y$ and selecting the values of $\theta$ that maximize the likelihood function $L\left( \theta | y \right)$, a function described in chapter \ref{CH: Bayes} in connection with Bayes' theorem. Such estimators, $\hat{\theta}$, are known as maximum likelihood estimators. In effect, the methods selects those values of $\theta$ that are at least as likely to generate the observed sample as any other set of values of the parameters if the probability density of the random variable $y$ were to be extensively simulated through use of the probability density $p\left( y|\theta \right)$. In making a maximum likelihood estimate, we assume that the form of the probability density (\sout{only the $\theta$ need be determined}) and that all possible values of $\theta$ are equally likely before experimentation.

%The likelihood function for the parameters given one observation is just the probability density in which the observation is regarded as a fixed number and the parameters as the variables:
%
%{\footnotesize
	%	\begin{equation}
		%		p\left( \theta| y(t_i) \right) = L\left( \theta|y_{t_i} \right) = p\left( y(t_i)| \theta \right)
		%\end{equation} }
		%where the lower case $y$'s and the number subscripts designate the value of the respective observation that is inserted into the probability density function. 
		The likelihood function for the parameters based on several observations is the product of the individual functions if the observations are independent.

		{\footnotesize 
			\begin{multline}
				L\left( \theta|y(t_n),...,y(t_1) \right) = \prod_{i=1}^{n} L\left( \theta|y(t_i) \right) \\
				= p\left( y(t_1)| \theta \right)p\left( y(t_2)| \theta \right) ... p\left( y(t_n)| \theta \right)
		\end{multline} }

		In choosing as estimates of $\theta$ the values that maximize $L$ for the given values $\left( y(t_i) \right)$, it turns out that it is more convenient to work with the $\ln L$ than with $L$ itself:

		{\footnotesize 
			\begin{equation}
				\ln L = \ln p \left( y(t_1)| \theta \right) + \ln p\left( y(t_2)| \theta \right) + ... + \ln p \left( y(t_n)| \theta \right) = \sum_{i=1}^{n} \ln p\left( y(t_i); \theta \right)
		\end{equation} }

		By assuming that the conditional distribution of $\bar{Y}_i$, given $y_i$, is normal, then we form the likelihood function based on the probability density:

		{\footnotesize
			\begin{align} \label{EQ: MLE_Norm}
				p\left(  \theta, \sigma | y(t_n),...,y(t_1) \right) &= \prod_{i=1}^{n} \cfrac{1}{\sqrt{2 \pi} \sigma } \exp \left[ \cfrac{1}{2  \sigma } \left( Y(t_i) - y(\theta , t_i) \right)^2 \right] \nonumber \\
				L\left( \theta, \sigma | y(t_n),...,y(t_1) \right) &= \prod_{i=1}^{n} \cfrac{1}{\sqrt{2 \pi} \sigma } \exp \left[ \cfrac{1}{2  \sigma } \left( Y(t_i) - y(\theta , t_i) \right)^2 \right]
		\end{align}}
		where $\sigma$ is the variance

		%In Equation \ref{EQ: MLE_Norm} the parameters are the variables, and the values of $Y$ and $x$ are given. Then
		By taking the natural logarithm of the Equation \ref{EQ: MLE_Norm}, the final form of the objective function can be obtained:

		{\footnotesize
			\begin{equation}
				\ln L = -n \ln \sqrt{2 \pi} - \cfrac{n}{2} \ln \sigma
				- \cfrac{ \sum_{i=1}^{n} \left[  Y(t_i) - y(\theta , t_i) \right]^2 }{2 \sigma^2}
			\end{equation}
		}

		The parameter estimation problem can be formulated as follow:

		{\footnotesize
			\begin{equation}
				\begin{aligned}
					&\hat{\theta}_{MLE} &= \arg \max_{\sigma, \theta \in \Theta} \ln L = \arg \max_{\sigma,\theta \in \Theta} p(\theta|y) \\
					&\text{subject to}
					& \dot{x} = f(t,x,\theta) \\
					&& \dot{\theta} = 0 \\
					&& y = g(x)
				\end{aligned}
		\end{equation} }

		{\color{red}Based on the first order optimality condition,} the $\ln L$ can be maximized with respect to the vector $\theta$ by equating to zero the partial derivatives of $\ln L$ with respect to each of the parameters:

		{\footnotesize
			\begin{align}\label{EQ: MLE_Basic_Solution}
				\cfrac{\partial \ln L}{\partial \theta} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( y(t_i) | \theta \right) }{\partial \theta} = 0 
		\end{align} }

		Solution of Equations \ref{EQ: MLE_Basic_Solution} yield the desired estimates $\hat{\theta}$. For some models, these equations can be explicitly solved for $\hat{\theta}$ but in general no closed-form solution to the maximization problem is known or available, and an MLE can only be found via numerical optimization.

		\sout{By carrying out this operation, under fairly unrestrictive conditions,} 
		It can be shown that as $n$ approaches infinity the maximum likelihood estimates have the desirable asymptotic properties:

		\begin{enumerate}[label=(\arabic*)]
			\item {\footnotesize $\lim\limits_{n \rightarrow \infty} \mathbb{E}\{\hat{\theta}\} = \theta$ }
			\item {\footnotesize $\left[ \sqrt{n}\left( \hat{\theta} - \theta \right) \right]$ } is normally distributed
		\end{enumerate}
		and for the case of two parameters:

		\begin{enumerate}[resume,label=(\arabic*)]
			\item {\footnotesize $\lim\limits_{n \rightarrow \infty} \text{Var}\{\hat{\theta}\} = \cfrac{1}{n} \left[ \mathbb{E} \left\{ \left( \cfrac{\partial \ln p}{\partial \theta} \right)^2 \right\} \right]^{-1} \cfrac{1}{1-\rho^2_{\hat{\theta}}} $ } \label{Assumption_MLE}
		\end{enumerate}

		where $\rho^2_{\hat{\theta}}$ is the matrix of correlation coefficients.

		Maximum likelihood estimates are not necessarily unbiased. Maximum likelihood estimates, however are efficient and, hence, consistent estimates. Furthermore, where a sufficient estimate can be obtained, the maximum likelihood method will obtain it. Finally, if $\hat{\theta}$ is a maximum likelihood estimator of $\theta$, the $f\left( \hat{\theta} \right)$ is a maximum likelihood estimator of $f\left( \theta \right)$, a function of $\theta$.

		\hrule

		%Under the assumption of normality, the lack of prior knowledge about the parameters $\theta^0$ and known initial conditions $y_0$. Intuitively, this selects the parameter values that make the observed data most probable. The specific value $\hat{\theta}$ that maximizes the likelihood function $L$ is called the maximum likelihood estimate.

		As already discussed, the prior information about the estimated parameters can be incorporated in to the maximum likelihood estimator to form a maximum a posteriori probability (MAP) estimate. MAP can be used to obtain a point estimate of an unobserved quantity on the basis of empirical data. MAP estimation can therefore be seen as a regularization of maximum likelihood estimation. The relationship between MAP and MLE can be obtained from the Bayes' rule:

		{\footnotesize
			\begin{equation} 
				\begin{split} \label{EQ: MAP_probability}
					{\bf \hat{\theta}_{\text{MAP}}} &= \arg\max_{\sigma, \theta \in \Theta} p(\theta | y) \\
					&= \arg\max_{\sigma, \theta \in \Theta} \frac{p(y | \theta) p(\theta)}{p(y)} \\
					&= \arg\max_{\sigma, \theta \in \Theta} p(y | \theta) p(\theta) \\
					&= \arg\max_{\sigma, \theta \in \Theta} \ln(p(y | \theta) p(\theta)) \\
					&= \arg\max_{\sigma, \theta \in \Theta} \ln p(y | \theta) + \ln p(\theta)
				\end{split}
		\end{equation} }

		We assume the normal distribution of random samples, with identical variance and the prior distribution of $\theta$ given by $\mathcal{N}(\theta^0,\,\sigma_\theta^{2})$. The function to be maximized can be written as

		{\footnotesize
			\begin{equation} \label{EQ: MAP_L2}
				\begin{aligned}
					&\arg\max_{\sigma, \theta \in \Theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 }{2\sigma^2}}
					+ \ln \prod_{j=0}^{p} \frac{1}{\sigma_\theta\sqrt{2\pi}}e^{-\frac{ \left( \theta - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]  \\
					= &\arg\max_{\sigma, \theta \in \Theta} \left[- \sum_{i=1}^{n} {\frac{\left( Y(t_i) - y\left( \theta, t_i \right) \right)^2}{2\sigma^2}}
					- \sum_{j=0}^{p} {\frac{\left( \theta - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]\\
					= &\arg\min_{\sigma, \theta \in \Theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2
					+ \frac{\sigma^2}{\sigma_\theta^2} \sum_{j=0}^{p} \left( \theta - \theta^0 \right)^2 \right] \\
					= &\arg\min_{\sigma, \theta \in \Theta} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 + \lambda_{L2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^0 \right)^2 \right]
				\end{aligned}
		\end{equation} }

		In Equation \ref{EQ: MAP_L2} some of the constants (with respect to $\theta$) were dropped and factored to simplify the expression. We can adjust the amount of regularization we want by changing $\lambda_{L2}$. Equivalently, we can adjust how much we want to weight the priors carry on the coefficients ($\theta$). If we have a very small variance (large $\lambda_{L2}$) then the coefficients will be very close to 0; if we have a large variance (small $\lambda_{L2}$) then the coefficients will not be affected much (similar to as if we didn't have any regularization).

		Let's assume that the prior distribution of parameter $\theta$ is given by the Laplace distribution. The likelihood function can defined as follow:

		{\footnotesize
			\begin{equation} \label{EQ: MAP_L1}
				\begin{aligned}
					&\arg\max_{\sigma, \theta \in \Theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 }{2\sigma^2}}
					+ \ln \prod_{j=0}^{p} \frac{1}{2b}e^{-\frac{ | \theta - \theta^0 | }{\sigma_\theta}} \right]  \\
					= &\arg\max_{\sigma, \theta \in \Theta} \left[- \sum_{i=1}^{n} {\frac{\left( Y(t_i) - y\left( \theta, t_i \right) \right)^2}{2\sigma^2}}
					- \sum_{j=0}^{p} {\frac{ | \theta - \theta^0 | }{\sigma_\theta}} \right]\\
					= &\arg\min_{\sigma, \theta \in \Theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2
					+ \frac{\sigma^2}{\sigma_\theta} \sum_{j=0}^{p} | \theta - \theta^0 | \right] \\
					= &\arg\min_{\sigma, \theta \in \Theta} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 + \lambda_{L1} \sum_{j=0}^{p} | \theta - \theta^0 | \right]
				\end{aligned}
		\end{equation} }

		The Laplacean prior act as $L1$-type of regularization on the optimization problem. Instead of preventing any of the coefficients from being too large (due to the squaring), $L1$ promotes sparsity. Due to the sparsity some of the parameters can be zero out, and eventually removed from the model. $L1$ is more robust to outliers than $L2$.

		If the cost function is given by Equations \ref{EQ: MAP_L2} or \ref{EQ: MAP_L1}, then the optimization problem can be formulated as follow:

		{\footnotesize
			\begin{equation}
				\begin{aligned}
					&\hat{\theta}_{MAP} &= \arg\max_{\sigma, \theta \in \Theta} \ln p(y | \theta) + \ln p(\theta) \\
					&\text{subject to}
					& \dot{x} = f(t,x,\theta) \\
					&& \dot{\theta} = 0 \\
					&& y = g(x)
				\end{aligned}
		\end{equation} }

		\hrule
		If the cost function to be maximized is given be Equation \ref{EQ: MAP_probability} and constrained by Equation \ref{EQ: Measurment_noise}, then the method of Lagrange multipliers can be used to convert a constrained problem into a form such that the derivative test of an unconstrained problem can be applied. The Lagrange function ($L^*$) can be defined as $\ln(L)$ plus the Lagrangian multipliers $\lambda(t_i)$ times the constraint function

		{\footnotesize
			\begin{equation} \label{EQ: MLE_Lagrangian}
				\begin{split}
					L^* \equiv \ln p\left( \theta \right) + \sum_{i=1}^{n} \left\{ \ln p(y(t_i)|\theta) \right. \\
					\left. + \lambda^T \cdot {\color{red} \left[ Y(t_i) - y\left( \theta,t_i \right) - \epsilon(t_i) \right] } \right\} \\ - \ln \left[ p\left( y \right) \right]
				\end{split}
		\end{equation}}

		By assumption of the relation of Equation \ref{EQ: Measurment_noise}

		{\footnotesize
			\begin{equation} \label{EQ: Noise_prob}
				p\left( y(t_i) | \theta,y_0 \right) = p\left( \epsilon(t_i) \right)
		\end{equation} }

		and specially

		{\footnotesize
			\begin{equation} \label{EQ: Noise_prob_norm}
				p\left( \epsilon(t_i) \right) = \cfrac{1}{ (2\pi)^{v/2} |\Gamma(t_i)|^{1/2} } \exp \left[ -\cfrac{1}{2}\epsilon^T(t_i) \left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \right]
		\end{equation} }
		where $|\Gamma|$ is the det$~\Gamma$, and $\Gamma$ is the covariance matrix of $\epsilon$, i.e., of the response.

		After Equation \ref{EQ: Noise_prob} is substituted into Equation \ref{EQ: MLE_Lagrangian}, and $L^*$ can be differentiated with respect to each of the estimates and $\epsilon(t_i)$. {\color{red}Based on the first order optimality conditions}, the resulting expression is equated to zero:

		{\footnotesize
			\begin{subequations} \label{EQ: MLE_Lag_diff}
				\begin{alignat}{2}
					%\cfrac{\partial L^*}{\partial y_0} &= \cfrac{\partial}{\partial y_0} \ln p(\theta,y_0) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial y_0} y(\theta ,t_i) = 0^T \\
					\cfrac{\partial L^*}{\partial \theta} &= \cfrac{\partial}{\partial \theta} \ln p(\theta) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial \theta} y(\theta,t_i) =0 \\
					\cfrac{\partial L^*}{\partial \epsilon(t_i)} &= \cfrac{\partial}{\partial \epsilon(t_i)} \ln p(\epsilon(t_i)) - \lambda^T(t_i) = 0^T
				\end{alignat}
		\end{subequations} }

		Substitution of Equation \ref{EQ: Noise_prob_norm} into the last Equation of \ref{EQ: MLE_Lag_diff} makes it possible to solve for $\lambda(t_i)$:

		{\footnotesize
			\begin{align}
				\lambda(t_i) &= -\left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \nonumber \\
				&= -\left( \Gamma(t_i) \right)^{-1} \left[ Y(t_i) - y(\theta,t_i) \right]
		\end{align} }

		and to eliminate $\lambda(t_i)$ from the first equation of \ref{EQ: MLE_Lag_diff}.

		For convenience we shall define a new column vector $\theta^*$ in which all the elements of $\theta$ are arranged as follows:

		{\footnotesize
			\begin{equation}
				\theta^* = \begin{bmatrix}
					\theta_{1,1} & \theta_{1,2} & \cdots & \theta_{1,v} & \theta_{2,1} & \cdots & \theta_{2,v} & \cdots & \theta_{v,v}
				\end{bmatrix}^T	
		\end{equation} }

		Finally, we assume that and $\theta^*$ are distributed by a joint normal distribution and that the prior distribution are, respectively

		{\footnotesize
			\begin{subequations} \label{EQ: MLE_Priors}
				\begin{align}
					&p\left( \theta^* \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{\theta^*}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( \theta^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} \left( \theta^* - \theta^{*(0)} \right) \right] 
					%&p\left( y_0 \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{y_0}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( y_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} \left( y_0 - y_0^{(0)} \right) \right] 
				\end{align}
		\end{subequations} }
		where $\Omega$'s are the respective covariance matrices for $\theta^*$ and $y_0$, and the subscript $(0)$ designates the prior estimated of $\theta^*$ and $y_0$. If we assume that $\theta^*$ and $y_0$ are independent

		%{\footnotesize
			%	\begin{equation}
				%		\ln p(\theta^*,y_0) = \ln p(\theta^*) + \ln p(y_0)
				%\end{equation} }

				Introduction of the prior distributions, Equations \ref{EQ: MLE_Priors}, plus the expression for $\lambda(t_i)$ into the first two equations of \ref{EQ: MLE_Lag_diff} gives the final equations from which the estimators of $\theta^*$ and $y_0$ can be obtained:

				{\footnotesize
					\begin{subequations} 
						\begin{flalign}
							%			&-\left( \hat{y}_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} + \sum_{i=1}^{n}\left[ Y(t_i) - y\left( \hat{\theta}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \cdot \cfrac{\partial}{\partial y_0} y\left( \hat{\theta}, \hat{y}, t_i \right) = 0^T  &&\\
							&-\left( \hat{\theta}^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} + \sum_{i=1}^{n}\left[ Y(t_i) - y\left( \hat{\theta}, t_i \right) \right]^T \Gamma^{-1}(t_i) \cdot \cfrac{\partial}{\partial \theta^*} y\left( \hat{\theta}, t_i \right) = 0^T &&
						\end{flalign}
				\end{subequations} }
				where the overlay caret denotes estimated parameters.

				Note that under the assumption that the elements of $\Omega$ are essentially infinite (prior knowledge is diffuse), the elements of $\Omega^{-1}$ are zero, the equations for the maximum likelihood estimates coincide with those for the least squares estimates, and the same calculations for precision in the estimates apply.

				%For some models, these equations can be explicitly solved for $\hat{\theta}^*$ and $\hat{y}$ but in general no closed-form solution to the maximization problem is known or available, and an MLE can only be found via numerical optimization. Under the assumption of normality, the lack of prior knowledge about the parameters $\theta^0$ and known initial conditions $y_0$, the optimization problem is defined as follow:
				%
				%{\footnotesize
					%\begin{equation}
					%	\hat{\theta}_{MLE} = \arg \max_{\theta \in \Theta} L = \arg \max_{\theta \in \Theta} p(\theta|y)
					%\end{equation} }
					%
					%Intuitively, this selects the parameter values that make the observed data most probable. The specific value $\hat{\theta}$ that maximizes the likelihood function $L$ is called the maximum likelihood estimate. Further, if the function $\hat{\theta}:\mathbb{R}\rightarrow\Theta$ so defined is measurable, then it is called the maximum likelihood estimator.
					%
					%If the random samples $y(t_1)$, $y(t_2)$,...,$y(t_n)$ come from a normal distribution with unknown mean $\hat{\theta}$ and variance $\sigma^2$, then the joint probability function can be written as 
					%
					%{\footnotesize
						%\begin{equation}
						%	p(\theta|y(t_i)) = \cfrac{1}{\sqrt{2\pi\sigma}}\exp\left[-\cfrac{ \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}\right]
						%\end{equation} }
						%
						%Then the likelihood function is defined as follow:
						%
						%{\footnotesize
							%\begin{equation} 
							%	L =\prod\limits_{i=1}^n p(\theta|y(t_i)) = (2\pi\sigma)^{-n/2}\exp\left[-\cfrac{1}{2\sigma}\sum\limits_{i=1}^n \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2\right]
							%\end{equation} }
							%
							%By taking the ln of the likelihood function, the final form of the cost function is obtained:
							%
							%{\footnotesize
								%\begin{equation} 
								%	\ln L=-\cfrac{n}{2}\ln\sigma-\cfrac{n}{2}\ln(2\pi)-\cfrac{\sum\limits_{i=1}^n \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}
								%\end{equation} }
								%
								%\subsection{Maximum a posteriori estimation}
								%
								%As already discussed, the prior information about the estimated parameters can be incorporated in to the maximum likelihood estimator to form a maximum a posteriori probability (MAP) estimate. MAP can be used to obtain a point estimate of an unobserved quantity on the basis of empirical data. MAP estimation can therefore be seen as a regularization of maximum likelihood estimation. MLE and MAP can be connected by Bayes' rule:
								%
								%{\footnotesize
									%\begin{equation} 
									%	\begin{split}
										%		{\bf \hat{\theta}_{\text{MAP}}} &= \arg\max_{\sigma, \theta \in \Theta} p(\theta | y) \\
										%		&= \arg\max_{\sigma, \theta \in \Theta} \frac{p(y | \theta) p(\theta)}{p(y)} \\
										%		&= \arg\max_{\sigma, \theta \in \Theta} p(y | \theta) p(\theta) \\
										%		&= \arg\max_{\sigma, \theta \in \Theta} \ln(p(y | \theta) p(\theta)) \\
										%		&= \arg\max_{\sigma, \theta \in \Theta} \ln p(y | \theta) + \ln p(\theta)
										%	\end{split}
									%\end{equation} }
									%
									%Notice that we can get rid of the evidence term $P(y)$ because it's constant with respect to the maximization and also take the ln of the inner function because it's monotonically increasing.
									%
									%We assume the normal distribution of random samples, with identical variance and the prior distribution of $\theta$ given by $\mathcal{N}(\theta^0,\,\sigma_\theta^{2})$. The likelihood function to be maximized can be written as
									%
									%{\footnotesize
										%\begin{equation} \label{EQ: MAP_L2}
										%	\begin{split}
											%	&\arg\max_{\sigma, \theta \in \Theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2 }{2\sigma^2}}
											%	+ \ln \prod_{j=0}^{p} \frac{1}{\sigma_\theta\sqrt{2\pi}}e^{-\frac{ \left( \hat{\theta} - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]  \\
											%	&= \arg\max_{\sigma, \theta \in \Theta} \left[- \sum_{i=1}^{n} {\frac{\left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma^2}}
											%	- \sum_{j=0}^{p} {\frac{\left( \hat{\theta} - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]\\
											%	&= \arg\min_{\bf \theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2
											%	+ \frac{\sigma^2}{\sigma_\theta^2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^0 \right)^2 \right] \\
											%	&= \arg\min_{\bf \theta} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2 + \lambda_{L2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^0 \right)^2 \right]
											%	\end{split}
										%\end{equation} }
										%
										%Notice that we dropped some of the constants (with respect to $\theta$) and factored to simplify the expression. You can see this is the same expression as Equation \ref{EQ: MAP_L2} (L2 Regularization) with $\lambda_{L2}$. We can adjust the amount of regularization we want by changing $\lambda_{L2}$. Equivalently, we can adjust how much we want to weight the priors carry on the coefficients ($\theta$). If we have a very small variance (large $\lambda_{L2}$) then the coefficients will be very close to 0; if we have a large variance (small $\lambda_{L2}$) then the coefficients will not be affected much (similar to as if we didn't have any regularization).

\end{document}

### 2023-02-16 SFE-report/Paramter_fitting.tex
16.02

@@
 
-\author[1]{Pekka Oinas}[orcid=0000-0002-0183-5558]
+%\author[1]{Pekka Oinas}[orcid=0000-0002-0183-5558]
 %\credit{b}
 
-\author[1]{Francesco Corona}[orcid=0000-0002-3615-1359]
+%\author[1]{Francesco Corona}[orcid=0000-0002-3615-1359]
 %\credit{c}
@@
 \begin{abstract}
-Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output.
+%Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output.
 As an example, the supercritical extraction process is presented.
@@
 Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
+Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process.
+The process model describes a partially filled extractor with a fixed bed, which work under constant operating conditions.
+We assume that the flow is uniform across any cross-section, although the area available for the fluid phase is a function of distance.
+We apply the concept of quasi-one-dimensional flow to mimic the modelling of a two-dimensional case.
+The collected dataset, obtained from the extraction of caraway seeds at different operating conditions, is used to estimate unknown parameters.
+The model-based parameter estimation applies the maximum likelihood method to estimate values of the extraction kinetic parameters such as mass partition factor, internal diffusion coefficient and radial diffusion.
 
@@
 
+\subsection{Low Mach number expansion}
+\subfile{Sections/Low_mach_number_expansion}
+
 %\newpage
@@
 
+\clearpage
+
 \subsection{Parameter estimation} \label{CH: Parameter_estimation}
-%\subfile{Sections/Parameter_estimation}
+\subfile{Sections/Parameter_estimation}
 
 \section{Results} \label{CH: Results}
+
+\begin{figure*}[h!]
+		\centering
+		\includegraphics[trim = 0cm 0cm 0cm 0cm,clip,width=\textwidth]{Figures/Results_estimation/Yield.pdf}	
+		\caption{The yield curve vs dataset}
+\end{figure*}
+
+\begin{figure*}[h!]
+	\centering
+	\includegraphics[trim = 0cm 0cm 0cm 0cm,clip,width=\textwidth]{Figures/Results_estimation/Profiles.pdf}	
+	\caption{The fluid density based on the Peng-Robinson equation of state}
+\end{figure*}
 
@@
 \subsection{Governing equations}
-\subsubsection{Mass continuity}
 \subfile{Sections/Gouverning_equation_derivation}
+
+\subsection{Bayes theorem} \label{CH: Bayes}
+\subfile{Sections/Bayes_Theorem}
 

### 2023-02-16 SFE-report/Sections/Gouverning_equation_derivation.tex
16.02

@@
 \begin{document}
+
+	\subsubsection{Mass continuity}
 
@@
 		\begin{align}
-			\iint_S \rho_f \textbf{V} \cdot \textbf{dS} &= -\rho_f V A_f + \rho_f V A_f + \rho_f V dA_f + \rho_f A_f dV + \rho_f dV dA_f \nonumber \\ 
-			&+ V A_f d\rho_f + V d\rho_f dA + A_f d\rho_f dV + d\rho_f dV dA_f
+			&\iint_S \rho_f \textbf{V} \cdot \textbf{dS} = -\rho_f V A_f + \rho_f V A_f + \rho_f V dA_f + \rho_f A_f dV \nonumber \\ 
+			&+ \rho_f dV dA_f + V A_f d\rho_f + V d\rho_f dA + A_f d\rho_f dV + d\rho_f dV dA_f
 			\label{EQ: Triple_Prod_Cont_Surf}
@@
 			\cfrac{\partial \left( \rho_f A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_f A_f V \right)}{\partial z} = 0
+			\label{EQ: Conservative_continuity}
 		\end{equation}
@@
 \ref{EQ: Continuity_integral_general} with additional terms on the right-hand side.
-The first term on the right-hand side describes that a substance goes from high density regions to low density regions and is based on the Fick's law ${\footnotesize\left( J_{diff}=-D\cfrac{\partial C_f}{\partial z} \right)}$.
+The first term on the right-hand side describes that a substance goes from high density regions to low density regions and is based on the Fick's law ${\footnotesize\left( J_{diff} = D\cfrac{\partial C_f}{\partial z} \right)}$.
 The other term correspond for the mass transfer between solid and fluid phases, which is treated as a source term.
@@
 		\begin{equation}
-			\cfrac{\partial C_f}{\partial t} + \cfrac{u}{\varepsilon} \cfrac{\partial C_f}{\partial z} + \cfrac{C_f}{\varepsilon} \cfrac{\partial u}{\partial z} = \cfrac{1-\varepsilon}{\varepsilon} \cfrac{\partial C_s}{\partial t} - \cfrac{D}{\varepsilon} \cfrac{\partial C_f}{\partial z} \cfrac{\partial \varepsilon}{\partial z} - \cfrac{\partial}{\partial z} \left( D \cfrac{\partial C_f}{\partial z} \right)
+			\cfrac{\partial C_f}{\partial t} + \cfrac{u}{\varepsilon} \cfrac{\partial C_f}{\partial z} + \cfrac{C_f}{\varepsilon} \cfrac{\partial u}{\partial z} = \cfrac{1-\varepsilon}{\varepsilon} \cfrac{\partial C_s}{\partial t} + \cfrac{D}{\varepsilon} \cfrac{\partial C_f}{\partial z} \cfrac{\partial \varepsilon}{\partial z} + \cfrac{\partial}{\partial z} \left( D \cfrac{\partial C_f}{\partial z} \right)
 		\end{equation}
@@
 The momentum equation can be expressed in terms of superficial velocity $u=V\varepsilon$.
-If $\cfrac{\partial \varepsilon}{\partial t}=0$
+
+	{\footnotesize
+		\begin{equation}
+			\rho_f \cfrac{\partial \left(u / \varepsilon \right)}{\partial t} + \rho_f \cfrac{u}{\varepsilon} \cfrac{\partial \left( u / \varepsilon \right)}{\partial z} = - \cfrac{\partial P}{\partial z}
+		\end{equation}
+	}
+
+	By expanding all the terms of equation above, we get
+
+	{\footnotesize
+		\begin{equation}
+			\cfrac{\rho_f}{\varepsilon} \cfrac{\partial u}{\partial t} + \rho_f u \cfrac{\partial \varepsilon^{-1}}{\partial t} + \rho_f \cfrac{u}{\varepsilon} \cfrac{1}{\varepsilon} \cfrac{\partial u}{\partial z} + \rho_f \cfrac{u}{\varepsilon} u \cfrac{\partial \varepsilon^{-1} }{\partial z} = - \cfrac{\partial P}{\partial z}
+		\end{equation}
+	}
+
+	If the bed is not compressible and doesn't change its properties during the batch, then ${\footnotesize\cfrac{\partial \varepsilon}{\partial t}=0}$
 
@@
 			\cfrac{\rho_f}{\varepsilon} \left( \cfrac{\partial u}{\partial t} + \cfrac{u}{\varepsilon} \cfrac{\partial u}{\partial z} \right) = -\cfrac{\partial P}{\partial z}
+			\label{EQ: Non-conservative_Momentum_Const_Porosity}
 		\end{equation}
@@
 
+	The Eq. \ref{EQ: Non-conservative_Momentum_Const_Porosity} represents non-conservative form of the momentum equation for quasi-one-dimensional flow with no body forces and constant porosity.
+
+	\hrule
+
+	\subsubsection{Energy conservation}
+
+	Let's consider the integral form of the energy equation for adiabatic flow with no body forces and no viscous effects
+
+	{\footnotesize
+		\begin{equation}
+			\cfrac{\partial}{\partial} \iiint_{\mathcal{V}_f} \rho_f \left( e_f + \cfrac{V^2}{2} \right) d\mathcal{V}_f + \iint_S \rho_f \left( e_f + \cfrac{V^2}{2} \right) \textbf{V} \cdot \textbf{dS} = - \iint_S \left( P\textbf{V} \right) \cdot \textbf{dS}
+			\label{EQ: Energy_equation_integral}
+		\end{equation}
+	}
+
+	Applied to the shaded control volume in Fig.
+\ref{fig: control_volume}, and keeping in mind the pressure forces shown in Fig.
+\ref{fig: Forces_Momentum_Control_Volume}, Eq.
+\ref{EQ: Energy_equation_integral} becomes
+
+	{\footnotesize
+		\begin{align}
+			&\cfrac{\partial}{\partial t} \left[ \rho_f \left( e_f + \cfrac{V^2}{2} \right) A_f dz \right] - \rho_f \left( e_f + \cfrac{V^2}{2} \right) V A_f \nonumber \\
+			&+ \left( \rho_f + d\rho_f \right) \left[ e_f + de_f + \cfrac{\left( V + dV \right)^2}{2} \right] \left( V+fV \right) \left( A_f+dA_f \right) \nonumber \\
+			&= - \left[ -PVA_f + \left(P+dP\right) \left(V+dV\right) \left(A_f+dA_f\right) - 2\left( PV\cfrac{dA_f}{2} \right) \right]
+		\end{align}
+	}
+
+	Neglecting products of differential and cancelling like terms, the above equation becomes
+
+	{\footnotesize
+		\begin{equation}
+			\cfrac{\partial}{\partial t} \left[ \rho_f \left( e_f + \cfrac{V^2}{2} \right) A_f dz \right] + d\left( \rho_f r_f A_f \right) + \cfrac{ \left( \rho_f V^3 A_f \right) }{2} = -d \left( P A_f V \right)
+		\end{equation}
+	}
+
+	or
+
+	{\footnotesize
+		\begin{equation}
+			\cfrac{\partial}{\partial t} \left[ \rho_f \left( e_f + \cfrac{V^2}{2} \right) A_f dz \right] + d \left[ \rho_f \left( e_f \cfrac{V^2}{2} \right) VA_f \right] = - d\left( P A_f V \right)
+		\end{equation}
+	}
+
+	Taking the limit as $dz$ approaches zero, the equation above becomes the following partial differential equation
+
+	{\footnotesize
+		\begin{equation}
+			\cfrac{\partial \left[ \rho_f \left( e_f + V^2 / 2 \right) A \right]}{\partial t} + \cfrac{\partial \rho_f \left( e_f + V^2 / 2 \right)VA_f}{\partial z} = -\cfrac{\partial \left( P A_f V \right)}{\partial z}
+			\label{EQ: Energy_equation_conservative_total}
+		\end{equation}
+	}
+
+	Equation \ref{EQ: Energy_equation_conservative_total} is the conservation form of the energy expressed in terms of the total energy $e~+~V^2/2$, appropriate for unsteady, quasi-one-dimensional flow.
+The energy equation can be expressed in terms of internal energy if Eq.
+\ref{EQ: Conservative_Momentum} is multiplicated by $V$ and then subtracted from Eq.
+\ref{EQ: Energy_equation_conservative_total}
+
+	{\footnotesize
+		\begin{equation}
+			\cfrac{\partial \left( \rho_f e_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f  e_f V A_f \right)}{\partial z} = -P \cfrac{\partial A_f V}{\partial z}
+			\label{EQ: Energy_conservative_internal}
+		\end{equation}
+	}
+
+	The equation above is the conservation form of the energy equation expressed in terms of internal energy $e_f$ suitable for quasi-one-dimensional flow.
+The non-conservative for is then obtained by multiplying the continuity equation \ref{EQ: Conservative_continuity}, by $e_f$ and substructing it from \ref{EQ: Energy_conservative_internal}, yielding
+
+	{\footnotesize
+		\begin{equation}
+			\rho_f A_f \cfrac{\partial e_f}{\partial t} + \rho_f A_f V \cfrac{\partial e_f}{\partial z} = - P \cfrac{\partial (A_f V) }{\partial z}
+		\end{equation}
+	}
+
+	Expanding right-hand side and dividing by $A_f$, the above equation becomes
+
+	{\footnotesize
+		\begin{equation}
+			\rho_f \cfrac{\partial e_f}{\partial t} + \rho_f V \cfrac{\partial e_f}{\partial z} = -P \cfrac{V}{A_f} \cfrac{\partial A_f}{\partial z}
+		\end{equation}
+	}
+
+	or
+
+	{\footnotesize
+		\begin{equation}
+			\rho_f \cfrac{\partial e_f}{\partial t} + \rho_f V \cfrac{\partial e_f}{\partial z} = -P \cfrac{\partial V}{\partial z} - P V \cfrac{\partial (ln~A_f)}{\partial z}
+			\label{EQ: Energy_equation_nonconservative}
+		\end{equation}
+	}
+
+	Equation \ref{EQ: Energy_equation_nonconservative} is the non-conservative for of the energy equation expressed in therms of internal energy, appropriate to unsteady quasi-one-dimensional flow.
+The reason for obtaining the energy equation in the form of Eq.
+\ref{EQ: Energy_equation_nonconservative} is that, for a calorically perfect gas, it leads directly to a form of the energy equation in therms of temperature $T$.
+For calorically perfect gas ${\footnotesize e_f=C_vT}$
+
+	\hrule
+
+	{\footnotesize
+		\begin{equation}
+			\cfrac{\partial \left( \rho_f e_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f  e_f V A_f \right)}{\partial z} = -P \cfrac{\partial A_f V}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
+		\end{equation}
+	}
+
+	{TODO: \color{red}finish derivation of energy equation for real gas and introduce homogenous version of the energy equation}
+
 \end{document}

### 2023-03-06 SFE-article/Sections/Low_mach_number_expansion.tex
06.03

\documentclass[../Parameter_fitting.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	As discussed by \citet{Lions2013}, the low Mach number equations are a subset of the fully compressible equations of motion (continuity, momentum and energy). Such a set of equations allow for large variations in gas density but it is consider to be acoustically incompressible. The low Mach number equations are preferred over the full compressible equations for low speed flow problems $\left( M_a = \cfrac{|V|}{\sqrt{ \partial P / \partial \rho }} \ll 1 \right)$ to avoids the need to resolve fast-moving acoustic signals. The equations are derived from the compressible equations based on the perturbation theory. The perturbation theory develops an expression for the desired solution in terms of a formal power series known as a perturbation series in some "small" parameter $\zeta$, that quantifies the deviation from the exactly solvable problem. The leading term in this power series is the solution of the exactly solvable problem, while further terms describe the deviation in the solution, due to the deviation from the initial problem.

	The equations {\color{red}RED} describe the fully compressible equations of motion (respectively the transport of mass, momentum and energy) for quasi-one-dimensional case. We rescale the time variable, considering finally

	{\footnotesize
		\begin{equation*}
			\rho_\zeta 	= \rho\left( z, t/M_a \right), \quad
			V_\zeta 	= \cfrac{1}{\zeta} V\left( z, t/M_a \right) \quad
			T_\zeta 	= T\left( z, t/M_a \right),  \quad 
			k_\zeta 	= \zeta k(\rho_f, T) 
		\end{equation*} 
	}

	The conservative non-dimensional equations of motion becomes

	{\footnotesize
		\begin{align*}
			\cfrac{\partial \left( \rho_\zeta A_f \right)}{\partial t} &+ \cfrac{\partial \left( \rho_\zeta A_f V_\zeta \right)}{\partial z} = 0 \\
			\cfrac{\partial \left( \rho_\zeta A_f V_\zeta \right) }{\partial t}	&+ \cfrac{\partial \left( \rho_\zeta V_\zeta A_f V_\zeta \right)}{\partial z} + \cfrac{A_f}{M_a^2} \cfrac{\partial P_\zeta}{\partial z} = 0\\
			\cfrac{\partial \left( \rho_\zeta e_\zeta A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_\zeta e_\zeta V_\zeta A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_\zeta}{\partial z} \right) + P_\zeta \cfrac{\partial A_f V_\zeta}{\partial z} = 0
		\end{align*}
	}

	Let's define $\zeta=M_a^2$ and assume small Mach numbers, $M_a \ll 1$, then the kinetic energy, viscous work, and gravity work terms can be neglected in the energy equation since those terms are scaled by the square of the Mach number. The inverse of Mach number squared remains in the momentum equations, suggesting singular behaviour. In order to explore the singularity, the pressure, velocity and temperature are expanded as asymptotic series in terms of the parameter $\zeta$

	{\footnotesize
		\begin{align*}
			P_\zeta 	& = P_0 	+ P_1 \zeta		+ P_2 \zeta^2 		+ \mathcal{O}(\zeta^3) \\
			\rho_\zeta 	& = \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \\
			V_\zeta 	& = V_0		+ V_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
			T_\zeta 	& = T_0 	+ T_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
			e_\zeta 	& = e_0 	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
		\end{align*}
	}

	 By expanding performing power expansion on the continuity equation and taking the limit of $\zeta$ from the positive side we get

	 {\footnotesize
	 	\begin{align*}
	 		& \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left( \left( \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \right)}{\partial t} + \\
	 		&+ \cfrac{\partial \left(  \left(  \rho_0 + \rho_1 \zeta + \mathcal{O}(\zeta^2) \right) A_f \left( V_0	+V_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial z} = 0
	 	\end{align*}
	 }

	The continuity equation become

		 {\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_0 A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_0 A_f V_0 \right)}{\partial z} = 0
		\end{equation}
	}

	The form of the continuity equation stays the same. Considering the momentum equation, it can be seen that the inverse of Mach number squared remains which suggests singular behavior.

	{\footnotesize
		\begin{align*}
		 & \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left(  \left(  \rho_0 + \rho_1 \zeta + \mathcal{O}(\zeta^2) \right) A_f \left( V_0	+V_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial t} + \\
		 &+ \cfrac{\partial \left(  \left(  \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( V_0	+ V_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \left( V_0	+ V_1 \zeta + \mathcal{O}(\zeta^2) \right) \right) }{\partial z} + \\
		 &+ A_f \cfrac{\partial }{\partial z} \left(  \cfrac{P_0}{M_a^2}	+ \cfrac{P_1 \zeta}{M_a^2}	+ \cfrac{P_2 \zeta^2}{M_a^2} + \mathcal{O}(\zeta^3) \right)
		\end{align*}
	}

	The first two terms stays the same, but the third one become different in structure. By further investigation of the pressure term in the momentum equation it can be observed

	{\footnotesize
		\begin{align*}
			& \lim_{\zeta \rightarrow 0_+} \cfrac{\partial }{\partial z} \left(  \cfrac{P_0}{M_a^2}	+ \cfrac{P_1 \zeta}{M_a^2}	+ \cfrac{P_2 \zeta^2}{M_a^2} + \mathcal{O}(\zeta^3) \right) = \\
			& = \lim_{\zeta \rightarrow 0_+} \cfrac{\partial }{\partial z} \left(  \cfrac{P_0}{M_a^2} \right) + \cfrac{\partial }{\partial z} \left(  \cfrac{P_1 \zeta^2}{M_a^2} \right) + \cfrac{\partial }{\partial z} \left(  \cfrac{P_2 \zeta^2}{M_a^2} \right) \\
			& = \lim_{\zeta=M_a^2 \rightarrow 0_+} \cfrac{\partial }{\partial z} \left(  \cfrac{P_0}{M_a^2} \right) + \cfrac{\partial }{\partial z} \left(  \cfrac{P_1 M_a^2}{M_a^2} \right) + \cfrac{\partial }{\partial z} \left(  \cfrac{P_2 M_a^4}{M_a^2} \right) \\
			& = \lim_{\zeta=M_a^2 \rightarrow 0_+} 0 + \cfrac{\partial P_1}{\partial z}  + 0 \\
		\end{align*}
	}

	The simplification of the $P_0$ in the momentum equation comes from the fact that $P_0$ is independent of $z$. The term related to $P_2$ and higher order terms become zero at the limit of $M_a \rightarrow 0$. The momentum equation become

	{\footnotesize
		\begin{equation*}
			\cfrac{\partial \left( \rho_0 A_f V_0 \right) }{\partial t}	+ \cfrac{\partial \left( \rho_0 V_0 A_f V_0 \right)}{\partial z} + A_f \cfrac{\partial P_1}{\partial z} = 0
		\end{equation*}
	}

	By expanding performing power expansion on the energy equation and taking the limit of $\zeta$ from the positive side we get

	{\footnotesize
		\begin{align*}
			& \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left( \left( \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( e_0	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right)}{\partial t} + \\
			&+ \cfrac{\partial \left(  \left(  \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( V_0	+ V_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \left( e_0	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial z} + \\
			&+ \cfrac{\partial}{\partial z} \left( k \cfrac{\partial }{\partial z} \left( T_0 	+ T_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) + \\
			&- \left(  P_0 	+ P_1 \zeta		+ P_2 \zeta^2 		+ \mathcal{O}(\zeta^3)  \right) \cfrac{\partial \left( A_f \left( V_0 + V_1 \zeta + \mathcal{O}(\zeta^2) \right) \right) }{\partial z} = 0
		\end{align*}
	}

	The form of the energy equation stays the same.

	{\footnotesize
		\begin{equation*}
			\cfrac{\partial \left( \rho_0 e_0 A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_0 e_0 V_0 A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_0}{\partial z} \right) + P_0 \cfrac{\partial A_f V_0}{\partial z} = 0
		\end{equation*}
	}

	where $e_0 = e(\rho_0, T_0)$ and $k=k(\rho_0, T_0)$.

	The expansion results in two different types of pressure and they are considered to be split into a thermodynamic component ($P_0$) and a dynamic component ($P_1$). The thermodynamic pressure is constant in space, but can change in time. The thermodynamic pressure is used in the equation of state. The dynamic pressure only arises as a gradient term in the momentum equation and acts to enforce continuity.

	The resulting unscaled low Mach number equations are:

	{\footnotesize
		\begin{align*}
			\cfrac{\partial \left( \rho_f A_f \right)}{\partial t} &+ \cfrac{\partial \left( \rho_f A_f V \right)}{\partial z} = 0 \\
			\cfrac{\partial \left( \rho_f A_f V \right) }{\partial t}	&+ \cfrac{\partial \left( \rho_f V A_f V \right)}{\partial z} + A_f \cfrac{\partial P_1}{\partial z} = 0\\
			\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_f e V A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
		\end{align*}
	}

	The energy equation can be expanded through the chain rule to obtain

	{\footnotesize
		\begin{equation*}
			 \rho A_f \left( \cfrac{\partial e }{\partial t} + V \cfrac{\partial e}{\partial z} \right) + e  \underbrace{ \left( \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f V A_f \right)}{\partial z} \right) }_{Continutiy}  - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
		\end{equation*}
	}

	The non-conservative form of the energy equation become

	{\footnotesize
		\begin{equation*}
		\rho A_f \left( \cfrac{\partial e }{\partial t} + V \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
		\end{equation*}
	}

	If the calorically perfect gas is assumed then $e=C_vT$, where $C_v$ is the constant specific heat. The energy equation can derived in terms of temperature $T$

	{\footnotesize
		\begin{equation*}
			\rho A_f C_v \left( \cfrac{\partial T }{\partial t} + V \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
		\end{equation*}
	}

	If isothermal case is assumed then, the energy equation becomes

	{\footnotesize
		\begin{equation*}
			\lim_{\Delta T \rightarrow 0_+} \rho A_f C_v \left( \cfrac{\partial T }{\partial t} + V \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
		\end{equation*}
	}

	which leads to

	{\footnotesize
		\begin{equation}
			\cfrac{\partial A_f V}{\partial z} = 0
			\label{EQ: Incompressibility_Condition_Ideal_IsoThermal}
		\end{equation}
	}

	In one-dimensional case, the equation \ref{EQ: Incompressibility_Condition_Ideal_IsoThermal} become equivalent of $\text{div} ( A_f V) = 0$, which known as the incompressibility condition (\citet{Lions2013}).

\end{document}

### 2023-03-06 SFE-article/Sections/Materials_and_methods.tex
06.03

--- 2022-05-25 SFE-report/Forward_sensitivity_analysis_of_SFE_Sliczniuk.tex
@@
-% ---------------------------------------------------------------
-% Preamble
-% ---------------------------------------------------------------
-%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}
-\documentclass[a4paper,fleqn]{cas-dc}
-%\documentclass[a4paper]{cas-dc}
-%\documentclass[a4paper]{cas-sc}
-% ---------------------------------------------------------------
-
-% -------------------------------------------------------------------- 
-% Packages
-% --------------------------------------------------------------------
-% Figure packages
-\usepackage{float}
-\usepackage{adjustbox}
-% Text, input, formatting, and language-related packages
-\usepackage[T1]{fontenc}
-\usepackage{subcaption}
-% \usepackage[utf8]{inputenc}
-% \usepackage[nomath]{lmodern}
-
-% Margin and formatting specifications
-%\usepackage[authoryear]{natbib}
-\usepackage[sort]{natbib}
-\setcitestyle{square,numbers}
-
- %\bibliographystyle{cas-model2-names}
-
-\usepackage{setspace}
-
-% \usepackage[authoryear,longnamesfirst]{natbib}
-
-% Math packages
-\usepackage{amsmath, amsthm, amssymb, amsfonts, bm, nccmath, mathdots, mathtools, bigints, ulem}
-
-% --------------------------------------------------------------------
-% Packages Configurations
-% --------------------------------------------------------------------
-% (General) General configurations and fixes
-\AtBeginDocument{\setlength{\FullWidth}{\textwidth}}	% Solves els-cas caption positioning issue
-\setlength{\parindent}{20pt}
-%\doublespacing
-% --------------------------------------------------------------------
-% Other Definitions
-% --------------------------------------------------------------------
-
-% --------------------------------------------------------------------
-% Environments
-% --------------------------------------------------------------------
-% ...
-
-% --------------------------------------------------------------------
-% Commands
-% --------------------------------------------------------------------
-
-% ==============================================================
-% ========================== DOCUMENT ==========================
-% ==============================================================
+\documentclass[../Parameter_fitting.tex]{subfiles}
+\graphicspath{{\subfix{../Figures/}}}
 \begin{document}
-%  --------------------------------------------------------------------
-
-% ===================================================
-% METADATA
-% ===================================================
-\title[mode=title]{Parameter estimation}                      
-\shorttitle{Forward sensitivity analysis of the supercritical extraction process}
-
-\shortauthors{A, B, C}
-
-\author[1]{Oliwer Sliczniuk*}[orcid=0000-0003-2593-5956]
-\ead{oliwer.sliczniuk@aalto.fi}
-\cormark[1]
-%\credit{a}
-
-\author[1]{Pekka Oinas}[orcid=0000-0002-0183-5558]
-%\credit{b}
-
-\author[1]{Francesco Corona}[orcid=0000-0002-3615-1359]
-%\credit{c}
-
-\address[1]{Aalto University, School of Chemical Engineering, Espoo, 02150, Finland}
-%\address[2]{2}
-
-\cortext[cor1]{Corresponding author}
-
-% ===================================================
-% ABSTRACT
-% ===================================================
-\begin{abstract}
-Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output.
-As an example, the supercritical extraction process is presented.
-The impact of mass flow rate, pressure, and inlet temperature on the model's output is discussed.
-The sensitivity analysis results prove that the considered variables can affect the extraction's yield and be used as control variables in optimization problems.
-Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
-
-\end{abstract}
-
-\begin{keywords}
-Supercritical extraction \sep Parameter estimation \sep Mathematical modelling
-\end{keywords}
-
-% ===================================================
-% TITLE
-% ===================================================
-\maketitle
-
-% ===================================================
-% Section: Introduction
-% ===================================================\section{Introduction}
-
-\section{Introduction}
-%{\color{brown}Intro about extraction}\\
-The extraction of natural substances from solid materials and liquids with solvents have been a popular subject of research and development in the last years.
-Supercritical fluids have multiple applications in an extraction process due to the pressure-dependent dissolving power and {\color{blue} both gas-and liquid-like properties (for example fluid-like density and gas-like diffusivity).
-Among different supercritical fluids, the supercritical $CO_2$ is one of the most popular due to it is nontoxic, non-flammable and non-corrosive properties.
-The critical point of $CO_2$ is relatively low ($73.8$ bar and $31 ^\circ C$), compare to other fluids.
-The supercritical extraction with $CO_2$ become attractive alternative, to replace traditional extraction techniques.}
-
-%{\color{brown} Literature review of the models}\\
-\sout{The supercritical extraction process is considered unconventional due to the lack of formulation of one general model, properties that strongly depend on working conditions and its unsteady nature.
-Understanding the physics behind the phenomena and the proper mathematical description is necessary to predict the process outcome.
-Several extraction models have been developed to characterize different mass transfer mechanisms and equilibrium relationships.}
-{\color{blue}The extraction of valuable compounds from fixed bed of biomass can be described by one of many mathematical models as presented by \citet{Huang2012}.
-The selection the extraction model is not arbitrary and should be based on the knowledge of phenomenons occurring in the operational unit.
-Each model has its own assumptions and describe different mass transfer mechanisms and equilibrium relationships}.
-
-\citet{Reverchon1996} developed a model, which considers an oil as a single component and assumes that the extraction process is controlled by internal-mass transfer resistance.
-As a result of these assumptions, the external mass transfer was neglected.
-The original model of Reverchon does not consider the influence of axial dispersion and does not take into account the change of density and flow rate along the bed.
-
-Based on analogy to heat transfer, \citet{Reverchon1993} suggested a hot ball model, where the extraction process is treated analogously to {\color{blue} a process in which a hot ball is cooled in a uniform medium} \sout{the process of cooling down a hot ball in a uniform medium}.
-{\color{blue}The hot ball model is used to describe an extraction process from solid particles which contains small quantities of solute so that the solubility is not a limiting factor.
-}
-
-\citet{Sovova1994} \sout{presented the Broken-and-Intact Cell model, which assumes the presence of two solid phases, the broken and intact cells.
-The results of applying Sovova's model allow distinguishing three phases of the extraction process (constant extraction rate, falling extraction rate, and diffusion-controlled periods) directly at the modelling stage.}
-{\color{blue} presented the Broken-and-Intact Cell model.
-The BIC model describes a system where the outer surfaces of particles have been mechanically interrupted.
-The solute from the broken cells is easily accessible for the solvent.
-The extraction of easily accessible solute is fast and directly controlled by its diffusion and convection in the solvent.
-However, the rest of the solute is less accessible because it is closed in the particle's core or intact cells.
-This solute slowly diffuses through the walls of a cell due to high mass transfer resistance.
-In this model, the extraction process is divided into three periods controlled by different mass transfer mechanisms: Constant extraction rate (CER) period, Falling extraction rate (FER) period and Diffusion-controlled (DC) period.}
-
-%{\color{brown}Methodology: sensitivity analysis }\\
-As in many engineering problems, mathematical modelling is crucial to mimic real-life objects, but it requires knowing multiple parameter values.
-One way to better understand the phenomena occurring in the process is to investigate the influences of various parameters on the model's output.
-One of the methods that can be applied is sensitivity analysis.
-Among different types of sensitivity analyses, there are two main groups: a local and global sensitivity analysis.
-The local method involves taking the total derivative of the output with respect to an input parameter at a single point.
-The derivative can be estimated directly by the automatic differentiation.
-{\color{blue}The total derivatives form an additional set of equations that is solved simultaneously with the original system.
-An alternative approach to the direct method is the Adjoint Sensitivity Analysis method.
-In this method, the original model is integrated to obtain the full trajectory of the state.
-Then the adjoint equation is solved backwards in time.
-The adjoint operates backwards in the sense that it determines a gradient with respect to input from a gradient with respect to output as discussed by \citet{Errico1997}.}
-The adjoint method is faster and requires the least memory than the local method.
-However, not all ODEs are stable under backwards integration.
-Moreover, both methods belong to one-at-a-time (OAT) methods, as they allow an investigation of the influence of only one parameter at a time.
-One way to determine the model response to "interactions" between parameters and to observe the non-linear behaviour of the system is to use higher-order derivatives.
-An alternative method is to apply a global sensitivity analysis, which utilises information about parameter uncertainty.
-A sensitivity analysis is considered global when all the parameters vary simultaneously.
-According to \citet{Razavi2015}, the main problem of generalising local sensitivity measures to represent "global" properties is the lack of a unique definition of global sensitivity.
-\sout{These methods allow selecting the most influential parameters, which can be used for optimisation (the finding is a set of control variables, which requires the least effort to affect a model's output), model reduction (removing the least influential parameters), or parameter fitting.
-In this work, the example of supercritical extraction is used to show the practical application of sensitivity analysis.
-Some researchers working with the supercritical fluids extraction process examined the influence of the parameters on the model's output.
-Most of them perform a parametrisation of the process model and solve it multiple times for different combinations of parameters.
-The literature review is presented below.}
-{\color{blue}A sensitivity analysis is helpful to identify parameters that have the greatest effect on the model's output.
-The sensitivity analysis results can be used to find regions in the space of input factors for which the model output is maximum.
-Another application is model reduction - for example, by identifying and removing redundant parts of the model structure.
-In the case of parameter fitting with a large number of parameters, non-sensitive parameters can be excluded from the fitting procedure, reducing the computational cost.
-A sensitivity analysis is used to increase understanding of the relationships between input and output variables in a model.
-
-%{\color{brown} Literature review of the sensitivity analysis}\\
-\citet{Fiori_2007} presented how a model uncertainty affects a supercritical extraction process.
-Authors performed a local sensitivity analysis taken at the mean values of the parameters, determined during the parameter estimation.
-Their analysis shows the importance of two parameters: the particle diameter and the internal mass transfer coefficient.
-The authors found that the supercritical extraction process is almost completely insensitive during the first phase of the process (controlled by the solute's solubility in the supercritical solvent) for a change of these parameters.
-However, the authors claim that the model's sensitivity to parameters becomes high during the second phase of the process (controlled by internal diffusion).
-
-\citet{Rabi_2019} analysed how the different parameters affect the model's output.
-The parameters are dimensionless numbers (e.g., mass transfer Biot, Péclet and Damköhler numbers), which are assumed to take one of few discrete values.
-The simulations are performed for each value of parameters and compared with each other.
-The authors found that the Péclet number can strongly affect the extraction efficiency, so the diffusive transport should not be neglected.
-The authors investigated effect of the Damköhler number on the process.
-The authors observed that higher intra-particle diffusion accelerated solid particles depletion so that an optimal extraction time can then be looked for.
-Furthermore, the authors proved that others investigated parameters like partition coefficient and bed porosity influence the extraction yield.
-
-\citet{Glover2008} presented a local sensitivity analysis for an adsorption process.
-Considering the similarities between extraction and adsorption processes, it is interesting to see how the same technique can be applied to different cases.
-The authors examine the sensitivity of the breakthrough of adsorption beds to system parameters.
-The impact of mass and energy transfer effects and adsorbent layer thicknesses are determined by calculating the derivatives of the outlet concentration and outlet temperature.
-The authors applied a Newton-based method along with the sensitivities to determine the optimal layering of an adsorption bed.}
-
-%{\color{brown} Summary of the manuscript}\\
-\sout{In this work, the process model represents supercritical extraction and consists of a set partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables.
-The process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.The impact of mass flow rate, pressure, and inlet temperature on the model's output is analyzed.
-In this work, the sensitivity analysis results are used to prove if the considered variables affect the extraction process and can be used as decision variables in optimization problems.
-The novelty is the application of the local sensitivity analysis in the case of supercritical extraction.}
-{\color{blue}In this work, a distributed-parameter model, based on \citet{Reverchon1996} and \citet{Vargas2006}, is used to describe a fluid-solid extraction process of 'carqueja' oil from 'Baccharis Trimera' leaves with $CO_2$ as a solvent.
-The process model consists of three partial differential equations: two mass balance equations and one heat balance equation.
-To enhance understanding of the process model, the local sensitivity analysis is used to investigate the effect of parameters on the model's output.
-The presented sensitivity analysis results are restricted to parameters related to operating conditions only.
-Furthermore, the sensitivity analysis is used to prove which of the analysed variables can be used as decision variables in optimisation problems.}
-
-\section{Materials and methods} \label{CH: Materials and methods}
 	\sout{The extraction process is assumed to operate in a semi-continuous mode in a cylindrical vessel.
@@
 		\centering
-	\includegraphics[trim = 6cm 7.5cm 8cm 6cm, clip, width=\linewidth]{Figures/SFE_PFD.pdf}
+		\includegraphics[trim = 6cm 7.5cm 8cm 6cm, clip, width=\linewidth]{SFE_PFD.pdf}
 		\caption{Process flow diagram for solid-fluid extraction process}
@@
 
-\subsection{Extraction model} \label{CH: Extraction_model}
-
-\sout{The main components of the model are three one-dimensional differential equations related to mass balances (solid and fluid phase) and heat balance.
-As in all batch processes, our system has only one steady state.
-The steady-state occurs only if the solute is entirely taken out of the biomass.
-
-The extraction from a fixed bed is an unsteady process, implying that the solute concentrations in the solid and solvent phases vary over time and space.
-The convection and the diffusion of the mass and the heat are considered only in the axial direction.
-The radial distribution of such properties like a velocity is assumed to be flat in that direction.
-The assumption of the flat velocity profile allows considering a lack of back mixing.
-The pressure drop in the bed is assumed to be assumed to negligible.
-Under such conditions, the fluid flow can be considered a plug flow.
-
-Since the solute is assumed to be a single pseudo-component, there is only one mass balance equation for each phase (Eq.
-s \ref{Model_fluid} and \ref{Model_solid}).
-On the other hand, there is only one heat balance (Eq.
-\ref{Model_heat}) because the presence of a single pseudo-phase is assumed.
-
-Moreover, the process model does not consider the change of particle size or the void fraction during the process.
-The particles are assumed to be uniformly distributed along the bed and to have the same size.}
-
-{\color{blue}A distributed-parameter model, based on \citet{Reverchon1996}, is used to describe the solid-fluid extraction process.
-The process model consists of three partial differential equations: two mass balance equations relative to the concentration of solute in the fixed solid phase and the mobile fluid phase, and the heat balance equation relative to the temperature of the fluid phase.
-The amount of solute in the solvent is considered negligible.
-Therefore, the fluid phase can be described as pseudo-homogenous, and its properties are assumed to be the same as the solvent.
-
-The movement of the mobile pseudo-homogeneous phase (Eq.
-\ref{Model_fluid}) is considered only in the axial direction.
-The properties of the system in the radial direction is assumed to be uniform.
-In addition, it is considered that the boundary layer adjacent to the inner wall of the extractor does not exist.
-Therefore, the velocity profile is constant across any cross-section of the extractor perpendicular to the axial direction.
-As a result, the plug flow model can be introduced.
-The particle size distribution and the void fraction of the solid phase are assumed to be uniform in space and remain constant in time.
-Moreover, the pressure is considered to be constant along the fixed bed.
-The mass balance for the fluid phase consists of convection, diffusion, and kinetic terms.
-
-Considering the solid phase to be fixed, the convection and diffusion terms in the corresponding mass balance are both assumed to be negligible or absent.
-Therefore, the mass balance for the solid phase (Eq.
-\ref{Model_solid}) consists of the kinetic term only.
-
-As for the mass transfer from the solid to the fluid phase, a kinetic term based on two-film theory for the solute is considered.
-The mass transfer kinetic (Eq.
-\ref{Model_kinetic_basic}) consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.
-A single pseudo-component is used to represent the extract collectively.
-
-The heat balance (Eq.
-\ref{Model_heat}) consists of the convective and diffusive terms.
-It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases.
-We consider no heat loss through the wall, and there is no heat generation in the system.
-Therefore, the temperature of the extractor can be changed only by manipulating the temperature of the inlet stream $T_{In}(t)$.
-}
-
-For the sake of clarity of the process model, different colors have been used in the equations to indicate: 
-{\color{red}control variables},
-{\color{blue}state variables},
-{\color{orange}variables} and
-{\color{magenta}parameters}.
-
-\subsubsection{Mass balance for the fluid phase} \label{CH: Mass_balance_fluid}
-The fluid phase is a mobile phase, which means that the fluids mass balance (Eq. \ref{Model_fluid}) is made of convection, diffusion, and mass transfer kinetic terms.
-
-{\footnotesize
-		\begin{align} 
-			\label{Model_fluid}
-			\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t} &	=  \underbrace{-\cfrac{1}{ {\color{magenta}\varepsilon A}}\cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]} \cfrac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} \\
-			&+ \underbrace{ {\color{orange}D^M_e}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] \cfrac{\partial^2 {\color{blue}c_f}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusive term}}
-			+ \underbrace{ \cfrac{1-{\color{magenta}\varepsilon}}{{\color{magenta}\varepsilon}} {\color{blue}r_e}(t,z) }_{\text{Kinetic term}} 
-		\end{align} }
-
-where ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z), {\color{blue}T}(t,z)$ correspond to concentration of solute in the fluid phase, concentration of solute in the solid phase and the temperature, respectively.
-${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term.
-${\color{red}F}(t)$ is the mass flow rate, ${\color{red}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{magenta}A}$ is the extractor’s cross section, ${\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient.
-
-\subsubsection{Mass balance for the solid phase} \label{Mass_balance_solid}
-The solid phase is a stationary phase, which indicates a lack of convection and diffusion terms in the mass balance (Eq.
-\ref{Model_solid}).
-Therefore, the only term present in this equation is the kinetic term (defined as presented in equation \ref{Model_kinetic_basic}), which links solid and fluid phases.
-
-{\footnotesize
-		\begin{equation} 
-			\label{Model_solid}
-			%		{\scriptsize\begin{align*}
-			\cfrac{\partial {\color{blue}c_s}(t,z)}{\partial t} = \underbrace{ {\color{blue}r_e}(t,z) }_{\text{Kinetics}}
-		\end{equation} }
-
-\subsubsection{Kinetic term} \label{CH: Kinetic}
-As the solvent flows through the bed, \sout{it forms a film around the porous solid particle and occupies its pores.} {\color{blue}the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to for an external fluid film around the solid particles through the solvent–solid matrix interactions.
-Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected.
-In this work, the molecular diffusion is assumed.}.
-The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
-The graphical representation of the mass transfer mechanism is shown in Figure \ref{fig: SFE_Mechanism}.
-The mean solute concentration in the solid phase is denoted as ${\color{blue}c_s}$.
-At the solid-fluid interface, the equilibrium concentrations are given as ${\color{blue}c_s^*}$ and ${\color{blue}c_P^*}$, respectively for solid and fluid phases.
-The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{blue}c_{P}}$.
-As the solute diffuses through the pore, its concentration changes and reaches ${\color{blue}c_{Pf}}$ at \sout{the end} {\color{blue}the opening} of the pore.
-The solute diffuses through the film around the particle and reaches a concentration in the bulk ${\color{blue}c_f}$.
-It can be assumed that the two-film theory describes the solid-fluid interface inside the pore.
-The overall mass transfer coefficient can be introduced if the relation between the solute concentration in one phase and its equilibrium concentration is known.
-
-\begin{figure}[h!]
-	\centering
-%	\includegraphics[trim  = 6cm 0cm 3cm 0cm,clip,width=\linewidth]{Figures/SFE_draft.png}
-	\includegraphics[trim = 5.8cm 1.1cm 6cm 0.8cm,clip,width=1.0\linewidth]{Figures/SFE_draft.pdf}	
-	\caption{The extraction mechanism}
-	\label{fig: SFE_Mechanism}
-\end{figure}
-
-\citet{Bulley1984} suggest a process where the driving force for extraction is given by the difference between concentration of the solute in the bulk, ${\color{blue}c_f}$, and in the centre of the pore, ${\color{blue}c_P^*}$.
-The concentration ${\color{blue}c_P^*}$ is in equilibrium with ${\color{blue}c_s}$ according to an equilibrium relationship.
-The rate of extraction is thus ${\color{blue}r_\text{e}}\left({\color{blue}c_f} - {\color{blue}c^*_P}({\color{blue}c_s})\right)$.
-
-On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between ${\color{blue}c_s}$ and ${\color{blue}c_P^*}$.
-${\color{blue}c_P^*}$ is determined by an equilibrium relationship with ${\color{blue}c_f}$ and the extraction rate is ${\color{blue}r_\text{e}}\left({\color{blue}c_s} - {\color{blue}c^*_P}({\color{blue}c_f})\right)$.
-
-\sout{The kinetic term, denoted as equation \ref{Model_kinetic_basic}, corresponds to a solute transfer rate between both phases.
-This term is made of the overall diffusion coefficient and the concentration gradient (between one phase and its equilibrium concentration), which acts as a driving force for the process.} {\color{blue}The mass transfer kinetic (Eq.
-\ref{Model_kinetic_basic}) describes a diffusion rate of the solute from solid particles to the solvent.
-The kinetic term consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.} Based on the work of \citet{Bulley1984}, \citet{Reverchon1996} proposed to define the kinetic terms as
-
-{\footnotesize
-\begin{equation} \label{Model_kinetic_basic}
-	{\color{blue}r_e}(t,z) = \cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}q}(t,z) - {\color{blue}q^*}(t,z) \right)
-\end{equation} }
-
-where ${\color{orange}D_i}({\color{blue}T}(t,z))$ corresponds to the overall diffusion coefficient and ${\color{blue}q^*}(t,z)$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).
-${\color{blue}q^*}(t,z)$ can be calculated based on the equilibrium relationship (Eq.
-\ref{Linear_equilibirum}).
-
-\sout{The kinetic term of the model takes into account the properties of the biomass like a sphericity (through the shape coefficient ${\color{magenta}\mu}$ equal to $1/3$ for slabs and $3/5$ for spheres), a characteristic dimension of particles (through the parameter ${\color{magenta}l} = {\color{magenta}r}/3$ where ${\color{magenta}r}$ is the mean particle radius), and the solid density ${\color{magenta}\rho_s}$.
-The fixed bed is characterized by a void fraction ${\color{magenta}\epsilon}$.
-}
-
-{\color{blue} The kinetic term of the model takes into account properties of the solid particles like a sphericity (through the shape coefficient ${\color{magenta}\mu}$), a characteristic dimension of particles (through the parameter ${\color{magenta}l} = {\color{magenta}r}/3$ where ${\color{magenta}r}$ is the mean particle radius), and the bulk density ${\color{magenta}\rho_s}$.
-The fixed bed is characterized by a void fraction ${\color{magenta}\epsilon}$.
-}
-
-According to \citet{Bulley1984}, a linear equilibrium relationship (Eq.
-\ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{blue}c_f^*}(t,z)$ is based on concentration of the solute in the solid phase ${\color{blue}c_s}(t,z)$
-
-{\footnotesize
-\begin{align} \label{Linear_equilibirum}
-	{\color{blue}c}(t,z) &= {\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t)) \allowbreak {\color{blue}q^*}(t,z)
-\end{align} }
-
-The volumetric partition coefficient ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
-\sout{ The ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$ according to $\citet{Spiro2007}$ .}
-{\color{blue} According to \citet{Spiro2007}, the term ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as the function of mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$ }
-
-{\footnotesize
-\begin{align}
-	{\color{orange}k_m}({\color{blue}T}(t,z)) = \cfrac{{\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{magenta}\rho_s}}{{\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}
-\end{align} }
-
-Equation \ref{Model_kinetic} is the full representation of the kinetic term.
-
-{\footnotesize
-	\begin{align}
-		\label{Model_kinetic}
-		{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}q}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c}(t,z) \right)
-\end{align} }
-
-\subsubsection{Heat balance} \label{CH: heat_balance}
-\sout{The heat balance equation (Eq.
-\ref{Model_heat}) was developed, assuming the existence of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases (the amount of solute is considered small enough not to affect the overall heat balance).
-Equation \ref{Model_heat} contains the convection and the diffusion terms.
-It is considered that there is no heat loss through the wall, and there is no heat generation in the system.
-The temperature of the extractor can be changed only by increasing the temperature of the inlet stream.
-The pseudo-homogenous phase is assumed to flow only in the axial direction.
-The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ because the solid phase is stationary.
-Therefore, this factor can be understood as the fraction of the fluid's total heat through convection.
-On the other hand, the axial heat diffusion is calculated based on the definition of thermal diffusivity for the fluid, as explained in the appendix.
-}
-
-{\color{blue} The heat balance (Eq.
-\ref{Model_heat}), is based on \citet{Srinivasan2012}, and consists of convective and diffusive terms.
-It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases.
-It is considered that there is no heat loss through the walls, and there is no heat generation in the system.
-The temperature of the extractor can be changed only by manipulating the temperature of the inlet stream ${\color{red}T_{Inlet}}(t)$.
-	}
-
-{\footnotesize
-	\begin{equation} \label{Model_heat}
-		\begin{split}
-			\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} &= 
-			\underbrace{ -\cfrac{{\color{red}F}(t) {\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))}{{\color{magenta}A} 	[(1-{\color{magenta}\epsilon}){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{orange}C_p} ({\color{blue}T}(t,z),{\color{red}P}(t)) + {\color{magenta} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}}  }_{\text{Convection}} + \\
-			& + \underbrace{ {\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{red}P}(t)) \cfrac{\partial^2 {\color{blue}T}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusion}}
-		\end{split}
-	\end{equation} }
-
-where $ {\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient, ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's specific heat, ${\color{magenta}C_{ps}}$ is the specific heat of the solid phase, ${\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial heat diffusion coefficient.
-
-\subsubsection{Extraction yield} \label{CH: Yield}
-\sout{The efficiency of the process (the yield) is calculated according to equation \ref{Model_measurment}.
-The yield is defined as the ratio between a difference of initial solute's mass in the solid phase ${\color{magenta}m_0}$, and an actual amount of solute in the same phase ${\color{blue}m}$, compared to the initial amount of the solute in the fixed bed ${\color{magenta}m_0}$.
-The yield can also be calculated based on the change of solutes concentration in the solid phase if the volume of the extractor ${\color{magenta}V}$ is constant.
-An output function ${\color{blue}y}(t)$ returns a yield curve that represents the fraction of the solute's mass over time.
-The yield is obtained by function ${\color{blue}g}({\color{blue}q}(t,z))$.
-Function ${\color{blue}g}({\color{blue}q}(t,z))$ corresponds to a 'measurement device' that allows to calculate the yield based on the state variable ${\color{blue}q}(t,z)$.
-}
-{\color{blue}The efficiency of the process (the yield) is calculated according to Eq.
-\ref{Model_measurment}, and is based on the change of solute's mass in the solid phase.
-It is defined as ratio the ratio between the difference of its initial value ${\color{magenta}m_0}$ and the actual value ${\color{blue}m}(t,z)$, compared to the initial one.
-The yield can also be calculated based on the change of solutes concentration in the solid phase if the volume of the extractor ${\color{magenta}V}$ is constant.}
-
-{\footnotesize
-	\begin{align} 
-		\label{Model_measurment}
-		{\color{blue}y}(t) ={\color{blue}g}({\color{blue}q}(t,z)) &= \cfrac{ \left({\color{magenta}m_0} - {\color{blue}m}({\color{blue}q}(t,z)) \right) }{{\color{magenta}m_0}} = \cfrac{ {\color{magenta}V} \left({\color{magenta}q_0} - {\color{blue}q}(t,z) \right) }{{\color{magenta}V q_0}}
-	\end{align}	}
-
-\sout{where ${\color{blue}q}(t,z)$ is concentration of solute in a solid phase and a temperature, respectively.
-${\color{magenta}m_0}$ is a initial mass of the solute in the solid phase, ${\color{magenta}q_0}$ is a  initial concentration of the solute in the solid phase, ${\color{magenta}V}$ is an extractor volume.}
-
-\subsubsection{Dependencies} \label{CH: Dependencies}
-{\color{blue}The Peng-Robinson equation of state is used to describe the thermodynamics of the fluid phase.
-The thermal properties of the pseudo-homogeneous phase are assumed to vary along the extractor, though always remaining equal to the corresponding mean values between the fluid and solid phase.
-}
-
-In the process model, properties of the supercritical fluid such as the density ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$, the specific heat ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$, the thermal conductivity ${\color{orange}k^T}({\color{blue}T}(t,z),{\color{red}P}(t))$, or the viscosity ${\color{orange}\eta}({\color{blue}T}(t,z),{\color{red}P}(t))$ are calculated based on the local temperatures along the fixed bed and the pressure.
-The Peng-Robinson equation of state is used to find values of a ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$ and ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$.
-
-The inter-particle diffusion coefficient ${\color{orange}D^M_e}(\allowbreak{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is calculated from the empirical correlation, as the function of the Reynolds number ${\color{orange}R_e}({\color{blue}T}(t,z),{\color{red}P}(t),\allowbreak{\color{red}F}(t))$ and the Peclet's number ${\color{orange}P_e}({\color{blue}T}(t,z),\allowbreak{\color{red}P}(t),{\color{red}F}(t))$.
-The values of the internal diffusion ${\color{orange}D_i} ({\color{blue}T}(t,z))$ and the partition coefficient ${\color{orange}k_m} ({\color{blue}T}(t,z))$ come from the laboratory experiments.
-The expressions and the detailed information of the parameter fitting can be found in the appendix.
-
-\subsubsection{State-space representation} \label{CH: State_space}
-It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}q_0}$.
-Moreover, it is considered that the initial temperature of the extractor in every place is equal to ${\color{magenta}T_0}$.
-Therefore, the initial conditions employed in the simulation are:
-
-{\footnotesize
-\begin{subequations}
-	\begin{align*}
-		{\color{blue}c}(t = 0, z) &= 0   \\
-		{\color{blue}q}(t = 0, z) &= {\color{magenta}q_0} \\
-		{\color{blue}T}(t = 0, z) &= {\color{magenta}T_0}
-	\end{align*}
-\end{subequations} }
-
-The process model can be written in a general form:
-
-{\footnotesize
-\begin{align}
-	\begin{bmatrix}
-		\cfrac{\partial {\color{blue}c}(t,z)}{\partial t}\\
-		\cfrac{\partial {\color{blue}q}(t,z)}{\partial t}\\
-		\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} 
-	\end{bmatrix}
-	& =
-	\begin{bmatrix}
-		{\color{blue}\phi_1} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)\\
-		{\color{blue}\phi_2} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)\\
-		{\color{blue}\phi_3} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)
-	\end{bmatrix} = {\color{blue}\phi} \left( t,z; {\color{magenta}\theta} \right) = \cfrac{\partial {\color{blue}\chi}(t,z)}{\partial t}
-\end{align} }
-
-where ${\color{magenta}\theta}$ is a set of parameters present in the model, ${\color{blue}\phi}$ is a set of functions that correspond to state equations of the model, and ${\color{blue}\chi}$ is the state-space model.
-
-The method of lines is used to transform the process model equations into a set of ODEs denoted as ${\color{blue}G}({\color{blue}x}(t);{\color{magenta}p})$.
-The partial derivatives in $z$-direction are computed using a first-order and second-order finite difference approximation.
-The backward finite difference is used to approximate first-order derivative, while the central difference scheme is used to approximate second-order derivative.
-The length of the fixed bed is divided into $N_z$ equally distributed points in $z$-direction.
-Each function ${\color{blue}\phi_i}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{blue}G}_{i\times N_z+1}$ to ${\color{blue}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation.
-The state-space model ${\color{blue}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{blue}x}}(t)$ (Eq.
-\ref{discretization}).
-
-{\footnotesize
-\begin{align*} \label{discretization}
-	\dot{{\color{blue}x}}(t) &= \cfrac{d {\color{blue}x}(t)}{d t} = 
-	\begin{bmatrix}
-		\cfrac{d {\color{blue}c_{f,1}}(t)}{d t} 	  \\
-		\vdots					  \\
-		\cfrac{d {\color{blue}c_{f,N_z}}(t)}{d t} \\
-		\\ \hline \\
-		\cfrac{d {\color{blue}c_{s,1}}(t)}{d t} 	  \\
-		\vdots					  \\
-		\cfrac{d {\color{blue}c_{s,N_z}}(t)}{d t} \\
-		\\ \hline \\
-		\cfrac{d {\color{blue}T_1}(t)}{d t} 	  \\
-		\vdots 					  \\
-		\cfrac{d {\color{blue}T_{N_z}}(t)}{d t}
-	\end{bmatrix}
-	=
-	\underbrace{\begin{bmatrix}
-			{\color{blue}G_1} \left( {\color{blue}x}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
-			\vdots\\ 
-			{\color{blue}G_{N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
-			\\ \hline \\ \\
-			{\color{blue}G_{N_z+1}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
-			\vdots\\
-			{\color{blue}G_{2N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
-			\\ \\ \hline \\ 
-			{\color{blue}G_{2N_z+1}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right) \\
-			\vdots\\
-			{\color{blue}G_{3N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)
-	\end{bmatrix}}_{{\color{blue}G} \left( {\color{blue}x}(t); {\color{magenta}p} \right)} 
-\end{align*} }
-
-where ${\color{blue}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{magenta}p} \in \mathbb{R}^{N_p =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of model parameters, $N_{u}$ is the number of control variables.
-
-{\color{blue} In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases ($c(t,z)$ and $q(t,z)$, respectively), and the local temperature of the pseudo-homogeneous phase ($T(t,z)$).
-The controllable input variables are the mass flow-rate and temperature of the solvent in the feed ($F_\text{in}(t) = F(t)$ and $T_\text{in}(t) = T(t,z=0)$, respectively) and the pressure in the extractor ($P(t,z) = P(t)$).
-{\color{red}We also assume that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator ($Y(t)$).} The system is controllable by manipulating the flow-rate and temperature of CO2 in the feed, and the pressure in the extractor.
-}
-
-\newpage
-\section{Parameter estimation} \label{CH: Parameter_estimation}
-Estimation theory is a branch of statistics that deals with estimating the values of parameters based on measured empirical data that has a random component.
-The parameters describe an underlying physical setting in such a way that their value affects the distribution of the measured data.
-An estimator attempts to approximate the unknown parameters using the measurements.
-
-For a given model, several statistical "ingredients" are needed so the estimator can be implemented.
-The first is a statistical sample – a set of data points taken from a random vector (RV) of size $N$.
-Let denote a statistical sample as $x$ and parameters whose vales are to be estimated as $\theta$.
-Both can be written into a vector form:
-\begin{align}
-	x &= [x[0], x[1], \dots, x[N-1] ]^T, &&x \in \mathbb{R}^N \\
-	\theta &= [\theta_0, \theta_1, \dots, \theta_M ]^T,  &&\theta \in \mathbb{R}^M
-\end{align}
-
-where $N$ is the number of samples and $M$ is the number of parameter to estimation.
-
-The continuous probability density function (pdf) or its discrete counterpart, the probability mass function (pmf), of the underlying distribution that generated the data must be stated conditional on the values of the parameters: $p(x|\theta)$.
-It is also possible for the parameters themselves to have a probability distribution (e.g., Bayesian statistics).
-It is then necessary to define the Bayesian probability $\pi(\theta)$.
-After the model is formed, the goal is to estimate the parameters, with the estimates commonly denoted $\hat{\theta}$.
-
-One common estimator is the minimum mean squared error (MMSE) estimator, which utilizes the error between the estimated parameters and the actual value of the parameters as the basis for optimality.
-This error term is then squared and the expected value of this squared value is minimized for the MMSE estimator.
-
-\subsection{Bayes theorem} \label{CH: Bayes_theorem}
-In probability theory and statistics, Bayes' theorem (alternatively Bayes' law or Bayes' rule; recently Bayes–Price theorem[1]: 44, 45, 46 and 67 ), named after Thomas Bayes, describes the probability of an event, based on prior knowledge of conditions that might be related to the event.[2] For example, if the risk of developing health problems is known to increase with age, Bayes' theorem allows the risk to an individual of a known age to be assessed more accurately (by conditioning it on their age) than simply assuming that the individual is typical of the population as a whole.
-
-One of the many applications of Bayes' theorem is Bayesian inference, a particular approach to statistical inference.
-When applied, the probabilities involved in the theorem may have different probability interpretations.
-With Bayesian probability interpretation, the theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
-Bayesian inference is fundamental to Bayesian statistics.
-
-\subsection{Maximum likelihood estimation} \label{CH: MLE}
-\subsection{Maximum a posteriori} \label{CH: MAP}
-\subsection{Bayesian inference} \label{CH: Bayesian_inference}
-
-\section{Results} \label{CH: Results}
-
-\section{Conclusions}
-
-% ===================================================
-% Bibliography
-% ===================================================
-%% Loading bibliography style file
-\clearpage
-%\bibliographystyle{model1-num-names}
-\bibliographystyle{unsrtnat}
-\bibliography{mybibfile}
-
-\clearpage \appendix \label{appendix}
-\section{Appendix}
-
-\newpage
-\begin{table*}[p]
-		\caption{Notation}
-		\label{tab::symbols}
-		\begin{tabular}{ |c|l|c| } 
-			\hline
-			Symbol 		& 	Description 							& Unit 						\\ \hline
-			$A$			&	cross-section							& $m^2$ 					\\ \hline
-			$c$			&	concentration in fluid phase			& $kg ~ m^{-3}$				\\ \hline
-			$Cp$		&	specific heat of the fluid				& $J ~ mol^{-1} ~ K^{-1}$ 	\\ \hline
-			$Cp_s$		&	specific heat of the solid				& $J ~ mol^{-1} ~ K^{-1}$ 	\\ \hline
-			$D_e^M$		&	axial mass diffusion coefficient		& $m^2 ~ s^{-1}$			\\ \hline
-			$D_e^T$		&	axial heat diffusion coefficient		& $m^2 ~ s^{-1}$			\\ \hline
-			$Di$		&	internal diffusion coefficient			& $m^2 ~ s^{-1}$			\\ \hline
-			$dp$		&	particle diameter						& $m$						\\ \hline
-			$F(t)$		&	mass flow-rate							& $kg ~ s^{-1}$				\\ \hline
-			$km$		&	partition coefficient					& $[-]$						\\ \hline
-			$k^T$		&	thermal conductivity					& $W ~ m^{-1} ~ K^{-1}$		\\ \hline
-			$l$			&	characteristic dimension				& $m$						\\ \hline
-			$L$			&	total length of the bed					& $m$						\\ \hline
-			$m$			&	mass of the oil in solid phase			& $kg$						\\ \hline
-			$m_0$		&	initial mass of the oil in solid phase	& $kg$						\\ \hline
-			$M_{CO_2}$	&	molecular mass of CO2					& $mol ~ kg^{-1}$			\\ \hline
-			$Np$		&	number of model parameters and control variables & $[-]$			\\ \hline
-			$N_{\theta}$&	number of model parameters				& $[-]$						\\ \hline
-			$Nu$		&	number of control variables				& $[-]$						\\ \hline
-			$Nz$		&	number of grid points in z-direction	& $[-]$						\\ \hline
-			$p$			&	vector of model parameters and control variables	& $[-]$			\\ \hline
-			$P(t)$		&	pressure								& $bar$						\\ \hline
-			$Pe$		&	Peclet's number							& $[-]$						\\ \hline
-			$q$			&	concentration in solid phase			& $kg ~ m^{-3}$				\\ \hline
-			$R$			&	gas constant							& $J ~ K^{-1} ~ mol^{-1}$	\\ \hline
-			$Re$		&	Reynolds number							& $[-]$						\\ \hline
-			$t$			&	time									& $s$						\\ \hline
-			$T$			&	temperature								& $K$						\\ \hline
-			$T_0$		&	initial temperature						& $K$						\\ \hline
-			$V$			&	volume of the extractor					& $m^3$						\\ \hline
-			$y$			&	yield	 								& $[-]$						\\ \hline
-			$z$			&	length									& $m$						\\ \hline
-			$Z$			&	compressibility	factor					& $[-]$						\\ \hline
-			$\epsilon$	&	void fraction							& $[-]$						\\ \hline
-			$\rho$		&	density of the fluid					& $kg ~ m^{-3}$				\\ \hline
-			$\rho_s$	&	solid density							& $kg ~ m^{-3}$				\\ \hline
-			$\mu$		&	shape coefficient						& $[-]$						\\ \hline
-			$\theta$	&	vector of model parameters				& $[-]$						\\ \hline
-			$\eta$		&	viscosity								& $cP$						\\ \hline				
-						& 											&							\\ \hline			
-		 	Subscript	& 											&							\\ \hline
-			$0$			&	initial conditions						& $[-]$						\\ \hline
-			$^*$		&	equilibrium conditions					& $[-]$						\\ \hline							
-		\end{tabular}
-\end{table*}
 \end{document}

### 2023-03-06 SFE-article/Sections/Model.tex
06.03

--- 2023-01-24 SFE-report/Sections/Model.tex
@@
 		We assume that at a given section, where the cross-sectional area is $A$, the flow properties are uniform across that section.
-Hence, although the are of an extractor changes  as a function of a distance along an extractor (e.g.
+Hence, although the area of an extractor changes  as a function of a distance along an extractor (e.g.
 if a fixed fill an extractor partially), $z$, and therefore in reality the flow field is two-dimensional (the flow varies in the two-dimensional space), we make the assumption that the flow properties vary only with $z$; this is tantamount to assuming uniform properties across any given cross section.
@@
 			\label{Model_fluid}
-			\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t} &	=  \underbrace{-\cfrac{1}{ {\color{magenta}\varepsilon A}}\cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]} \cfrac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} \nonumber \\
-			&+ \underbrace{ {\color{orange}D^M_e}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] \cfrac{\partial^2 {\color{blue}c_f}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusive term}}
+			\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t} &	=  \underbrace{- \cfrac{u}{\varepsilon} \cfrac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} - \underbrace{ \cfrac{ {\color{blue}c_f}(t,z) }{\varepsilon} \cfrac{\partial {\color{blue}u}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} \nonumber \\
+			&+ \underbrace{ \cfrac{ {\color{orange}D^M_e} }{\varepsilon} \left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] \cfrac{\partial^2 {\color{blue}c_f}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusive term}}
 			+ \underbrace{ \cfrac{1-{\color{magenta}\varepsilon}}{{\color{magenta}\varepsilon}} {\color{blue}r_e}(t,z) }_{\text{Kinetic term}} 
@@
 			\subsubsection{Extraction yield} \label{CH: Yield}
-			\sout{The efficiency of the process (the yield) is calculated according to equation \ref{Model_measurment}.
-The yield is defined as the ratio between a difference of initial solute's mass in the solid phase ${\color{magenta}m_0}$, and an actual amount of solute in the same phase ${\color{blue}m}$, compared to the initial amount of the solute in the fixed bed ${\color{magenta}m_0}$.
-The yield can also be calculated based on the change of solutes concentration in the solid phase if the volume of the extractor ${\color{magenta}V}$ is constant.
-				An output function ${\color{blue}y}(t)$ returns a yield curve that represents the fraction of the solute's mass over time.
-The yield is obtained by function ${\color{blue}g}({\color{blue}q}(t,z))$.
-Function ${\color{blue}g}({\color{blue}q}(t,z))$ corresponds to a 'measurement device' that allows to calculate the yield based on the state variable ${\color{blue}q}(t,z)$.
-}
-			{\color{blue}The efficiency of the process (the yield) is calculated according to Eq.
-\ref{Model_measurment}, and is based on the change of solute's mass in the solid phase.
-It is defined as ratio the ratio between the difference of its initial value ${\color{magenta}m_0}$ and the actual value ${\color{blue}m}(t,z)$, compared to the initial one.
-The yield can also be calculated based on the change of solutes concentration in the solid phase if the volume of the extractor ${\color{magenta}V}$ is constant.}
+
+			The efficiency of the process (the yield) is calculated according to one of Eq.
+\ref{Model_measurment}, which evaluates the mass of solute at the exit of the extraction unit and sums it.
+The integral form of the measurement equation can be transformed into the differential form, and augmented with model equations to be solved simultaneously.
 
@@
 					\label{Model_measurment}
-					{\color{blue}y}(t) ={\color{blue}g}({\color{blue}q}(t,z)) &= \cfrac{ \left({\color{magenta}m_0} - {\color{blue}m}({\color{blue}q}(t,z)) \right) }{{\color{magenta}m_0}} = \cfrac{ {\color{magenta}V} \left({\color{magenta}q_0} - {\color{blue}q}(t,z) \right) }{{\color{magenta}V q_0}}
+					y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
+					y(t) \left[ kg \right] &= \int_{t_0}^{t_f} \cfrac{F(t)}{\rho(t,z)} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] 	\\
+					\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
+					\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= \cfrac{F(t)}{\rho(t,z)} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]
 			\end{align}	}
 
-			\sout{where ${\color{blue}q}(t,z)$ is concentration of solute in a solid phase and a temperature, respectively.
-${\color{magenta}m_0}$ is a initial mass of the solute in the solid phase, ${\color{magenta}q_0}$ is a  initial concentration of the solute in the solid phase, ${\color{magenta}V}$ is an extractor volume.}
-
-			\subsubsection{Dependencies} \label{CH: Dependencies}
-			{\color{blue}The Peng-Robinson equation of state is used to describe the thermodynamics of the fluid phase.
+			\subsubsection{Thermodynamic} \label{CH: Thermodynamic}
+			%{\color{blue}The Peng-Robinson equation of state is used to describe the thermodynamics of the fluid phase.
 The thermal properties of the pseudo-homogeneous phase are assumed to vary along the extractor, though always remaining equal to the corresponding mean values between the fluid and solid phase.
@@
 
-			In the process model, properties of the supercritical fluid such as the density ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$, the specific heat ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$, the thermal conductivity ${\color{orange}k^T}({\color{blue}T}(t,z),{\color{red}P}(t))$, or the viscosity ${\color{orange}\eta}({\color{blue}T}(t,z),{\color{red}P}(t))$ are calculated based on the local temperatures along the fixed bed and the pressure.
+			%In the process model, properties of the supercritical fluid such as the density ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$, the specific heat ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$, the thermal conductivity ${\color{orange}k^T}({\color{blue}T}(t,z),{\color{red}P}(t))$, or the viscosity ${\color{orange}\eta}({\color{blue}T}(t,z),{\color{red}P}(t))$ are calculated based on the local temperatures along the fixed bed and the pressure.
 The Peng-Robinson equation of state is used to find values of a ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$ and ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$.
 
-			The inter-particle diffusion coefficient ${\color{orange}D^M_e}(\allowbreak{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is calculated from the empirical correlation, as the function of the Reynolds number ${\color{orange}R_e}({\color{blue}T}(t,z),{\color{red}P}(t),\allowbreak{\color{red}F}(t))$ and the Peclet's number ${\color{orange}P_e}({\color{blue}T}(t,z),\allowbreak{\color{red}P}(t),{\color{red}F}(t))$.
-			The values of the internal diffusion ${\color{orange}D_i} ({\color{blue}T}(t,z))$ and the partition coefficient ${\color{orange}k_m} ({\color{blue}T}(t,z))$ come from the laboratory experiments.
+			At standard atmospheric pressure and temperature, the $CO_2$ behaves as an ideal gas, and its compressibility factor equals to unity.
+However, at high temperature and pressure, the compressibility factor varies from unity, due to real gas effects.
+In order to predict this real gas effects, the Peng-Robinson equation of state (P-R EOS) is used to compute properties of $CO_2$.
+As the density is obtained from the continuity equation,store the P-R EOS can used to evaluate: compressibility, density and specific heat.
+The properties of the $CO_2$ computed as a function of operating conditions (temperature and pressure) are presented on fig.
+\ref{fig: SFE_Properties}
+
+			\begin{figure*}[h!]
+				\begin{subfigure}[b]{\textwidth}
+					\centering
+					\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
+					\caption{The compressibility factor based on the Peng-Robinson equation of state}
+				\end{subfigure}
+				\hfill
+				\begin{subfigure}[b]{\textwidth}
+					\centering
+					\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/RHO.pdf}	
+					\caption{The fluid density based on the Peng-Robinson equation of state}
+				\end{subfigure}
+				\hfill
+				\begin{subfigure}[b]{\textwidth}
+					\centering
+					\includegraphics[trim = 2.9cm 7cm 3.cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
+					\caption{The specific heat of the $CO_2$ based on the Peng-Robinson equation of state}
+				\end{subfigure}
+				\caption{Properties of $CO_2$ based on the equation of state}
+				\label{fig: SFE_Properties}
+			\end{figure*}
+
+			\subsubsection{Dependencies} \label{CH: Dependencies}
+			%The inter-particle diffusion coefficient ${\color{orange}D^M_e}(\allowbreak{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is calculated from the empirical correlation, as the function of the Reynolds number ${\color{orange}R_e}({\color{blue}T}(t,z),{\color{red}P}(t),\allowbreak{\color{red}F}(t))$ and the Peclet's number ${\color{orange}P_e}({\color{blue}T}(t,z),\allowbreak{\color{red}P}(t),{\color{red}F}(t))$.
+			%The values of the internal diffusion ${\color{orange}D_i} ({\color{blue}T}(t,z))$ and the partition coefficient ${\color{orange}k_m} ({\color{blue}T}(t,z))$ come from the laboratory experiments.
 The expressions and the detailed information of the parameter fitting can be found in the appendix.
+
+			TODO:
+
+			\begin{enumerate}
+				\item Viscosity
+				\item Thermal conductivity
+				\item Internal diffusion
+				\item Partition factor
+			\end{enumerate}
 

### 2023-03-06 SFE-article/Sections/Model_2.tex
06.03

\documentclass[../Parameter_fitting.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	We consider a conventional solid-fluid extraction process in which soluble essential oils are removed from a solid matrix of biomass in super-critical carbon dioxide. A conventional configuration in which the extraction process is operated in semi-continuous mode typically may consist of an extraction vessel followed by a separation unit, like a fluid-solid flash drum. In the illustrative diagram in Fig. \ref{fig: SFE_drawing}, the solvent ($\text{CO}_2$ in super-critical conditions) is circulated through the, extractor in which it gets in contact with finely chopped biomass arranged on a fixed-bed. In the extractor, the solute (the essential oils) is firstly transferred from the solid phase to the fluid phase, then separated downstream in the drum and collected for further processing. The solvent from the drum can be recovered and recycled into the process. In Fig. \ref{fig: SFE_drawing}, we also depict a typical instrumentation set-up used to configure the operating conditions of the process and to monitor and control it: The flow-rate ($F_\text{in}$) and the temperature ($T_\text{in}$) of the solvent entering the extractor are expected to be measured and adjustable, for example using a pump and a heat exchanger as actuators, respectively. Moreover, it is expected that the pressure ($P$) in the extractor is measured and adjustable, for example using a back-pressure regulator valve. Basic process regulation can be achieved with PID controllers whose set-points are manually provided, whereas a more advanced control strategy would include a supervisory controller to optimally determine the set-points.
	\begin{figure}[h]
		\begin{center}
			\includegraphics[width=0.66\linewidth]{Figures/SFE_PFD_cropped.pdf}
			\caption{Solid-fluid extraction process: Simplified process diagram and essential instrumentation.}
			\label{fig: SFE_drawing}
		\end{center}
	\end{figure}

	As solvent influent flow-rate and temperature, together with the pressure in the extractor, are understood as the main conditions that characterise the process from an operational point of view, we are interested in how these quantities affect the extraction process. More specifically, we are interested in understanding how they can be used in a supervisory control strategy based on a dynamic model of the extractor. The study is based on a forward sensitivity analysis (Section \ref{sec: State-space and sensitivity}) of a pragmatically designed model of the system. In Subsection \ref{subsec: Extraction model} and \ref{subsec: Measurement model}, the distributed-parameter model and the measurement model used for the task are presented.

	\subsection{Extraction model} \label{subsec: Extraction model}
	We consider an operational description of the fluid-solid extraction process in the extractor developed from a distributed-parameter model with three partial differential equations: Namely, two mass balance equations, relative to concentration of solute in the fixed solid phase and in the mobile fluid phase, and the heat balance equation, relative to the temperature of the fluid phase. We assume that the fluid, a mixture of solute and solvent, in the extractor can be treated as a pseudo-homogenous phase whose properties are those of the dominant component, the solvent. A single pseudo-component collectively representing the extract is also used. \\

	For the convection of the fluid phase, we consider a plug-flow model of the velocity profile. Furthermore, we assume that no pressure drops and no heat losses occur along the extractor. We also limit the model to represent only axial diffusion for both mass and heat. As for the mass transfer from the solid to the fluid phase, an extraction term based on the two-film theory is used.  Being the solid phase fixed, the convection and diffusion terms in the corresponding mass balance are both exlcuded. Similarly, we assume that the extraction is an isothermal process and exclude the generative term from the heat balance. The particle size distribution, and thus the void fraction of the solid phase, is assumed to be uniform in space and to remain constant in time. \\

	Under these fairly general and simplifying assumptions, a macroscopic model of the extractor's bed reads

	\begin{subequations}\begin{align}
			\cfrac{\partial {\color{blue}c_{\text{F}}}(t,z)}{\partial t} &	= -\cfrac{1}{{\color{magenta}\varepsilon A}}\cfrac{{\color{red}F}(t)}{{\color{orange}\rho_\text{F}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]} \cfrac{\partial {\color{blue}c_{\text{F}}}(t,z)}{\partial{\color{blue}z}}
			+ {\color{orange}D^M_{\text{eff}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] \cfrac{\partial^2 {\color{blue}c_{\text{F}}}(t,z)}{\partial {\color{blue}z^2}}
			+ \cfrac{1-{\color{magenta}\varepsilon}}{{\color{magenta}\varepsilon}}{\color{blue}r_e}(t,z)	\label{eq: Model fluid} \\
			\cfrac{\partial {\color{blue}c_{\text{S}}}(t,z)}{\partial t} &	= {\color{blue}r_e}(t,z)		\label{eq: Model solid} \\
			\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} &	= -\cfrac{{\color{red}F}(t) {\color{orange}C_p^\text{F}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}{{\color{magenta}A} [(1-{\color{magenta}\varepsilon}){\color{orange}\rho_\text{F}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] {\color{orange}C_p^\text{F}} \left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] + {\color{magenta}\varepsilon}{\color{magenta}\rho_\text{S}}{\color{magenta}C_p^\text{S} } ]} \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}} 
			+ {\color{orange}D^T_{\text{eff}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] \cfrac{\partial^2 {\color{blue}T}(t,z)}{\partial {\color{blue}z^2}}	\label{eq: Model heat}
		\end{align}\label{eq: SFE model}\end{subequations}

	where ${\color{blue}c_{\text{F}}}(t,z)$, ${\color{blue}c_{\text{S}}}(t,z)$, and ${\color{blue}T}(t,z)$ denote respectively the concentration of solute in the fluid, concentration of solute in the solid, and temperature of the pseudo-homogeneous phase, all at axial positions $z \in [0,L]$ along the bed and at times $t \in [t_{\text{ini}},t_{\text{end}}]$. We use ${\color{magenta}A}$ to denote the cross-section of the bed, $L$ will be used to denote its length. The void fraction of the bed is denoted by ${\color{magenta}\varepsilon}$, whereas ${\color{magenta}\rho_\text{S}}$  and ${\color{magenta}C_p^\text{S} }$ are used to denote the density and the specific heat of the solid phase: These quantities are assumed to be known and to remain constant in space and time. We collectively denote these quantities as $\varphi_{\text{exp}} = \left(A,L,\varepsilon,\rho_{\text{S}},C^{\text{S}}_p\right)$.  ${\color{red}F}(t) = F_\text{in}(t)$ denotes the mass flow-rate through the extractor and ${\color{red}P}(t)$ its pressure: Together with the feed temperature $T(t,z=0) = T_{\text{in}}(t)$, these three variables define the process operating conditions and can be varied over time to control the extraction. \\

	The density ${\color{orange}\rho_\text{F}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]$ of the fluid phase, the axial mass diffusion coefficient $ {\color{orange}D^M_{\text{eff}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t),\right]$, the specific heat ${\color{orange}C_p^\text{F}}\left[T(t,z),P(t)\right]$ of the fluid phase, and the axial heat diffusion coefficient ${\color{orange}D_{\text{eff}}^T}\left[T(t,z),P(t)\right]$ are assumed to change in space and over time, due to their dependence on the local temperature $T(t,z)$, and on pressure $P(t)$ and mass flow-rate $F(t)$. Similarly, the term ${\color{blue}r_e}(t,z)$ used to model the rate of extraction is assumed to vary in space and time, due to its dependence on the concentrations ${\color{blue}c_{\text{F}}}(t,z)$ and ${\color{blue}c_{\text{S}}}(t,z)$ of solute. \\

	The differential model in Eq. \eqref{eq: SFE model} augments what commonly found in the literature ({\color{red}ADD REFS}) in relation to mass balances (Eq. \eqref{eq: Model fluid} and \eqref{eq: Model solid}), by adding a heat balance (Eq. \eqref{eq: Model heat}) to describe changes in the concentrations of solute and temperature due to a potentially varying temperature of the influent solvent and pressure in the extractor. Because of the generality of the formulation, conventional relationships commonly found in the literature can used to describe the extraction rate, density and heat capacity in the fluid phase, and the diffusion coefficients: The specific choices used in this study are overviewed in the following subsections. To describe the properties of the fluid phase and to account for the aforementioned dependencies, an equation of state must be selected: In Subsection \ref{subsubsec: Equation of state}, we overview how we used the Peng-Robinson's equation for this task. As for the extraction rate, we overview in Subsection \ref{subsubsec: Extraction rate}

	\subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}
	We consider equations of state in the general form ${\color{red}P}(t) {\color{orange}V_{\text{CO}_2}}\left[T(t,z),P(t)\right] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, where ${\color{magenta}V_{\text{CO}_2}}$ denotes the molar volume of $\text{CO}_2$, ${\color{orange}Z}$ represents its compressibility factor, and $R$ is the universal gas constant. More specifically, we are interested in these equations because of the possibility to express the compressibility $Z$ as an explicit function of temperature and pressure. This is the case when $Z$ is obtained as one of the physically meaningful roots of a polynomial equation, like the Peng-Robinson's and {\color{red} stuff with REFS to equations of state}. \\

	In Peng-Robinson's equation, the compressibility ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ solves the third-order polynomial equation
	\vskip-0.500cm

	\begin{equation}\label{eq: Compressibility}
		{\color{orange}Z}^3 - \left[1 - {\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]\right] {\color{orange}Z}^2 + \left[{\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] - 2{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] - 3{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]^2\right] {\color{orange}Z} = 0, 
	\end{equation}

	where ${\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are functions of time and space defined on the attraction parameter, ${\color{orange}a}\left[{\color{blue}T}(t,z)\right] = {\color{magenta}a^c_{\text{CO}_2}}{\color{orange}\alpha}\left[{\color{blue}T}(t,z)\right]$ with ${\color{magenta}a^c_{\text{CO}_2}} \approx 0.45724 {{\color{magenta}R}^2{\color{magenta}T^c_{\text{CO}_2}}^2}/{{\color{magenta}P^c_{\text{CO}_2}}}$, and the repulsion parameter, ${\color{magenta}b_{\text{CO}_2}} \approx 0.07780 {{\color{magenta}R}{\color{magenta}T^c_{\text{CO}_2}}}/{{\color{magenta}P^c_{\text{CO}_2}}}$, both functions of the critical temperature ${\color{magenta}T^c_{\text{CO}_2}}$ and pressure ${\color{magenta}P^c_{\text{CO}_2}}$. Specifically, we have
	\vskip-0.250cm
	\begin{subequations} \label{eq: PR_AB}
		\begin{align} 
			{\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]	& = \dfrac{{\color{orange}\alpha}\left[T\left(t,z\right)\right]{\color{magenta}a^c_{\text{CO}_2}}{\color{red}P}(t)}{{\color{magenta}R}^2{\color{blue}T}^2(t,z)};													\label{eq: PR_A}\\
			{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]	& = \dfrac{{\color{magenta}b_{\text{CO}_2}}{\color{red}P}(t)}{{\color{magenta}R}{\color{blue}T}(t,z)}	\label{eq: PR_B}.
		\end{align}
	\end{subequations}
	The quantity ${\color{orange}\alpha}\left[{\color{blue}T}\left(t,z\right)\right]= \left[1 + {\color{magenta}\kappa_{\text{CO}_2}} \left[1 - \sqrt{{\color{blue}T}\left(t,z\right) / {\color{magenta}T^c_{\text{CO}_2}}} \right] \right]^2$, with constant ${\color{magenta}\kappa_{\text{CO}_2}} = 0.37464 + 1.54226 {\color{magenta}\omega_{\text{CO}_2}} - 0.26992 {\color{magenta}\omega_{\text{CO}_2}}^2$, is a dimensionless correction term defined on the acentric factor ${\color{magenta}\omega_{\text{CO}_2}} = 0.239$ of $\text{CO}_2$ molecules. \\

	By denoting the physical constants as $\varphi_{Z} = \left(R,T^c_{\text{CO}_2},P^c_{\text{CO}_2},\kappa_{\text{CO}_2}\right)$, we obtain a spatio-temporal representation of the compressibility ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi_{Z}\right]$ with its complete set of functional dependencies and parameters. \\

	%\subsubsection{Density of the fluid phase} \label{subsubsec: Fluid density}
	\noindent \textbf{Density of the fluid phase} \\

	The density $\rho_{\text{F}}$ of the fluid phase is assumed to be equal to the density of solvent, at given temperature and pressure. Because temperature $T(t,z)$ of the fluid phase is a modelled variable, we allow for the density to vary along the bed and in time. From an equation of state of the form ${\color{red}P}(t) {\color{orange}V_{\text{CO}_2}}\left[T(t,z),P(t)\right] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, we get

	\begin{equation} \label{eq: Density}
		{\color{orange}\rho_{\text{F}}} \left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid {\color{magenta}\varphi_{\rho_{\text{F}}}}\right] = \dfrac{{\color{red}P}(t) {\color{magenta}M_{\text{CO}_2}}}{{\color{magenta}R}{\color{blue}T}(t,z){\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid \varphi_{Z}\right]},
	\end{equation}

	where ${\color{magenta}M_{\text{CO}_2}}$ denotes the molar mass of $\text{CO}_2$ and ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ is the compressibility factor that solves Eq. \eqref{eq: Compressibility}. The density of the fluid is thus a function of space and time, due to its dependence on temperature and pressure, and it is expressed in terms of the set of physical constants $\varphi_{\rho_\text{F}} = \left({\color{magenta}R}, {\color{magenta}M_{\text{CO}_2}}, {\color{magenta}T^c_{\text{CO}_2}}, {\color{magenta}P^c_{\text{CO}_2}}, {\color{magenta}\omega_{\text{CO}_2}}\right)$. \\

	%\subsubsection{Heat capacity of the fluid phase} \label{subsubsec: Fluid heat capacity}
	\noindent\textbf{Heat capacity of the fluid phase} \\

	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term {\color{red}REF}. In the following, we report only the main steps in the derivation of ${\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$: Step-by-step derivations using the Peng-Robinson's equation are given in Appendix {\color{red}REF}. \\

	At given temperature and pressure, for $\text{CO}_2$ we have
	\begin{subequations}\begin{align}
			{\color{orange}C^{\text{CO}_2}_v}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] & = {\color{orange}C_v^{\text{I}}}\left[{\color{blue}T}(t,z),P(t)\right] + {\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] \label{eq: Cv_CO2}; \\ 
			{\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] & = \underbrace{{\color{orange}C_p^{\text{I}}}\left[{\color{blue}T}(t,z),P(t)\right]}_{\text{Eq. } \eqref{eq: Cp_I}} + \underbrace{{\color{orange}C_p^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}_{\text{Eq. } \eqref{eq: Cp_R}}  \label{eq: Cp_CO2}.
	\end{align}\end{subequations}
	${\color{orange}C^{\text{CO}_2}_v}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are the specific heat of $\text{CO}_2$ at constant volume and pressure, respectively. ${\color{orange}C_v^{\text{I}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}C_p^{\text{I}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$, with ${\color{orange}C_p^{\text{I}}}({\color{blue}T}(t,z)) - {\color{orange}C_v^{\text{I}}}({\color{blue}T}(t,z)) = {\color{magenta}R}$, are the specific heat of an ideal gas at constant volume and pressure. ${\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}C_p^{\text{R}}}({\color{blue}T}(t,z), {\color{red}P}(t))$ are the correction terms. \\

	For $CO_2$ {\color{red}REF}, we have the ideal gas contribution to the specific heat at constant $P(t)$, as function of $T(t,z)$,
	\begin{equation}
		{\color{orange}C_p^{\text{I}}}\left[{\color{blue}T}(t,z),P(t)\right] = {\color{magenta}C_{P0}} + {\color{magenta}C_{P1}}T(t,z) + {\color{magenta}C_{P2}}{\color{blue}T}^2(t,z) + {\color{magenta}C_{P3}}{\color{blue}T}^3(t,z) \label{eq: Cp_I}
	\end{equation}
	where the coefficients of the expansion are ${\color{magenta}C_{P0}} = 4.728$, ${\color{magenta}C_{P1}} = 1.75 \times 10^{-3}$, ${\color{magenta}C_{P2}} = -1.34 \times 10^{-5}$, and ${\color{magenta}C_{P3}} = 4.10 \times 10^{-9}$. For the correction term ${\color{orange}C_p^{\text{R}}}\left[{\color{blue}T}(t,z){\color{red}P}(t)\right]$ at constant pressure $P(t)$, we have
	\begin{equation}
		{\color{orange}C_p^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] = \underbrace{{\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}_{\text{Eq. }\eqref{eq: CvR}} + {\color{blue}T}(t,z) \underbrace{\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}V_{\text{CO}_2}}(t,z)}}_{\text{Eq. } \eqref{eq: dPdT}} \underbrace{\left(\cfrac{\partial {\color{orange}V_{\text{CO}_2}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)}}_{\text{Eq. } \eqref{eq: dVdT}} - {\color{magenta}R}. \label{eq: Cp_R}
	\end{equation}
	The braced terms are obtained from the chosen equation of state $P(t) V\left[T(t,z),P(t)\right] = Z\left[T(t,z),P(t)\right] R T(t,z)$. \\

	For the partial derivative of the volume with respect to temperature $T$ at constant pressure $P(t)$, we have
	\begin{equation}
		\left( \cfrac{\partial {\color{orange}V_{\text{CO}_2}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)} = \cfrac{{\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] {\color{magenta}R}}{{\color{red}P}(t)} + \cfrac{{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{red}P}(t)} \underbrace{\left( \cfrac{\partial {\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)}}_{\text{Eq. }\eqref{eq: dZdT}} \label{eq: dVdT}
	\end{equation} 
	with partial derivative of the compressibility factor with respect to temperature $T$ at constant pressure $P(t)$
	\begin{equation}
		\left(\cfrac{\partial{\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} = \left(\cfrac{\partial \dfrac{{\color{red}P}(t) {\color{orange}V_{\text{CO}_2}}\left[T(t,z),P(t)\right]}{{\color{magenta}R}{\color{blue}T}(t,z)}}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} \label{eq: dZdT}
	\end{equation}
	Similarly, for the partial derivative of the pressure with respect to temperature at constant volume, we have
	\begin{equation}
		\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}V_{\text{CO}_2}}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{magenta}V_{\text{CO}_2}}\left[T(t,z),P(t)\right]}}}{\partial{\color{blue}T}}\right)_{{\color{orange}V}(t,z)} \label{eq: dPdT}
	\end{equation}

	The residual specific heat at constant volume is obtained, by definition, by using the residual internal energy
	\begin{equation}
		{\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] = \left(\cfrac{\partial{\color{orange}U^{\text{R}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{orange}V}(t,z)}. \label{eq: CvR}
	\end{equation}

	By denoting the physical constants as $\varphi_{C_p^{\text{F}}} = \left({\color{magenta}R}, {\color{magenta}M_{\text{CO}_2}}, {\color{magenta}T^c_{\text{CO}_2}}, {\color{magenta}P^c_{\text{CO}_2}}, {\color{magenta}\omega_{\text{CO}_2}}\right)$, we get the spatio-temporal representation $C_p^{\text{F}}\left[T(t,z),P(t) \mid \varphi_{C_p^{\text{F}}}\right]$ of the specific heat of the fluid phase

	\subsubsection{The extraction rate} \label{subsubsec: Extraction rate}
	As the solvent flows through the extractor, the molecules of $\text{CO}_2$ occupy the pores of the particles of biomass and the molecules of solute diffuse from the particle through its pores and into the fluid bulk. We are interested in a macroscopic description of the extraction mechanism that allows to express the extraction term ${\color{blue}r_e}(t,z)$ in Eq. \eqref{eq: SFE model} in terms of the modelled concentrations, ${\color{blue}c_\text{S}}$ and ${\color{blue}c_\text{F}}$. The two-film theory ({\color{red}ADD REF}) of mass transfer between the solid and fluid phase is a conventional choice which is also commonly found in the literature. \\

	\citet{Bulley1984} suggest that the rate of extraction $r_e$ is driven by the difference in solute concentration between the bulk, ${\color{blue}c_\text{F}}$, and at the pore's end of the solid-fluid interface (this quantity is un-modelled, we use ${\color{blue}c_\text{PI}^*}$ to denote it). \citet{Reverchon1996} suggests that the driving force is the concentration difference between the solid particles, ${\color{blue}c_\text{S}}$, and at the particle's end on the interface (also this quantity is un-modelled, we denote it ${\color{blue}c_\text{SI}^*}$). Concentrations ${\color{blue}c_\text{PI}^*}$ and ${\color{blue}c_\text{SI}^*}$, although unknown, are related to each other by the assumed equilibrium condition existing at the interface. The two approaches are virtually equivalent and, depending on whether \citet{Bulley1984} or \citet{Reverchon1996} is preferred, ${\color{blue}c_\text{PI}^*}$ or ${\color{blue}c_\text{SI}^*}$ must be expressed in terms of either $c_\text{S}$ or $c_\text{F}$ before inclusion in Eq. \eqref{eq: SFE model}. \\

	For all positions along the bed and times, the extraction rate ${\color{blue}r_e}(t,z)$ gives to the rate at which the solute is transferred between phases. According to \citet{Reverchon1996}, ${\color{blue}r_e}(t,z)$ can be written in terms of an internal diffusion coefficient ${\color{orange}D_\text{int}}$: We follow this approach and extend it to allow for ${\color{orange}D_\text{int}}$ to depend on temperature $T(t,z)$ and possibly pressure $P(t)$. Multiple alternatives are available in the literature to represent dependence of ${\color{orange}D_\text{int}}$ on $T$ and $P$ (\ref{Asubsec: D_int} overviews some of them and presents the Arrhenius-type relation used in this study): It is important to note that, in general, a number of parameters collectively denoted by $\varphi_{D_\text{int}}$ is used to characterise the specific relation. More directly, the rate is also dependent on parameters $\varphi_{r_e}$ that account for properties of the particles like sphericity (the shape coefficient ${\color{magenta}\mu}$) and characteristic dimension ${\color{magenta}l}$. Specifically, we have 
	\begin{equation} \label{eq: Model_kinetic_basic}
		{\color{blue}r_e}(t,z) = \cfrac{{\color{orange}D_\text{int}}\left[{\color{blue}T}(t,z),P(t) \mid \varphi_{D_\text{int}}\right]}{{\color{magenta} \mu l^2} }\left[{\color{blue}C_\text{S}}(t,z) - {\color{blue}C_\text{SI}^*}(t,z) \right].
	\end{equation}
	According to the internal resistance model, ${\color{blue}C_\text{SI}^*}(t,z)$ can be expressed as a function of $C_\text{F}(t,z)$: That is, $C^*_\text{SI}(t,z)=C^*_\text{SI}\left(C_\text{F}(t,z)\right)$. Again, we follow \citet{Reverchon1996} who pragmatically suggests the linear relationship 
	\begin{equation} \label{eq: Linear equilibrium}
		{\color{blue}C_\text{F}}\left(t,z\right) = {\color{orange}k_p}\left[{\color{blue}T}\left(t,z\right),{\color{red}P}\left(t\right)\right] {\color{blue}C_\text{SI}^*}\left(t,z\right),
	\end{equation}
	where ${\color{orange}k_p}\left[{\color{blue}T}\left(t,z\right),{\color{red}P}(t)\right]$ is the volumetric partition coefficient, which we allow to depend on temperature and pressure. Also in this case, the literature offers multiple options to represent this dependence ({\color{red}ADD REFS}). To be consistent with \citet{Reverchon1996}, we consider the relation established by \citet{Spiro2007} in which $k_p$ is given in terms of the massic partition factor ${\color{orange}k_m}$, a quantity which we also allow to be dependent on temperature $T(t,z)$ and parameters $\varphi_{k_m}$ (see \ref{Asubsec: k_m} for a description of the relationship used in this study), as well as on the densities $\rho_{\text{F}}$ (defined earlier in Subsection \ref{subsubsec: Equation of state}) and $\rho_{\text{S}}$ of the fluid and solid phase, respectively: 
	\begin{equation} \label{eq: k_m}
		{{\color{orange}k_p}\left[{\color{blue}T}\left(t,z\right),{\color{red}P}(t) \mid \varphi_{k_m}, \varphi_{\rho_\text{F}}\right] {\color{magenta}\rho_\text{S}}} = {\color{orange}k_m}\left[{\color{blue}T}\left(t,z\right) \mid \varphi_{k_m}\right] {{\color{orange}\rho_\text{F}}\left[{\color{blue}T}\left(t,z\right),{\color{red}P}\left(t\right) \mid \varphi_{\rho_\text{F}}\right]}.
	\end{equation}

	Summarising, we get the formulation of the extraction rate with all its functional dependences and parameters 
	\begin{multline}\label{eq: Model_kinetic}
		{\color{blue}r_e}(t,z \mid \varphi_{r_e}, \varphi_{D_\text{int}}, \varphi_{k_m}, \varphi_{\rho_\text{F}}) = \\ 
		-\cfrac{{\color{orange}D_\text{int}}\left[{\color{blue}T}(t,z), P(t) \mid \varphi_{D_\text{int}}\right]}{{\color{magenta} \mu l^2} }\left[{\color{blue}C_\text{S}}(t,z) - \cfrac{{\color{magenta}\rho_\text{S}}}{{\color{orange}k_m}\left[{\color{blue}T}(t,z) \mid \varphi_{k_m}\right]{\color{orange}\rho_\text{F}}\left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid \varphi_{\rho_\text{F}}\right]} {\color{blue}C_\text{F}}(t,z) \right].
	\end{multline}
	%
	\subsubsection{Diffusion coefficients} \label{subsubsec: Diffusion coefficients}

	\noindent\textbf{Mass diffusion} 
	\begin{equation}
		{\color{orange}D_{\text{eff}}^M} \left[{\color{blue}T}(t,z), {\color{red}P}(t), {\color{red}F}(t)\right] = \cfrac{{\color{orange}u}\left[{\color{blue}T}(t,z), {\color{red}P}(t), {\color{red}F}(t)\right] {\color{magenta}d_p}}{{\color{magenta}\varepsilon} {\color{orange}\text{Pe}}\left[{\color{blue}T}(t,z), {\color{red}P}(t),{\color{red}F}(t)\right]}
	\end{equation}
	where ${\color{orange}u}\left[{\color{blue}T}(t,z), {\color{red}P}(t), {\color{red}F}(t)\right]$ is the superficial velocity in the axial direction, ${\color{magenta}\varepsilon}$ denotes the bed's porosity, and ${\color{magenta}d_p}$ denotes the particle diameter. ${\color{orange}\text{Pe}}\left[{\color{blue}T}(t,z), {\color{red}P}(t),{\color{red}F}(t)\right]$ is the Peclet's number and it is evaluated as the function of temperature, pressure and flow-rate as

	\begin{equation}
		{\color{orange}\text{Pe}}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] = \cfrac{{\color{magenta}\widehat{a}}}{{\color{magenta}\varepsilon}} + \cfrac{{\color{magenta}\widehat{b}}}{{\color{magenta}\varepsilon}}({\color{magenta}\varepsilon}{\color{orange} \text{Re}}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t) \right]^{\color{magenta}{\widehat{c}}}
	\end{equation}
	where ${\color{magenta}\hat{a}}$, ${\color{magenta}\hat{b}}$, and ${\color{magenta}\hat{c}}$ are the correlation's parameters. ${\color{orange}\text{Re}}$ is the Reynolds number, also determined as the function of temperature, pressure and feed flow-rate ${\color{orange}\text{Re}}\left[{\color{blue}T}(t,z), {\color{red}P}(t),{\color{red}F}(t)\right]$ 
	\begin{equation}
		{\color{orange}\text{Re}} \left[{\color{blue}T}(t,z), {\color{red}P}(t),{\color{red}F}(t)\right] = \cfrac{{\color{orange}\rho_\text{F}} \left[{\color{blue}T}(t,z), {\color{red}P}(t); {\color{magenta}\theta_\rho}\right] {\color{orange}u}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)) }{{\color{orange} \eta}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}
	\end{equation}

	where ${\color{orange}\eta} ({\color{blue}T}(t,z),{\color{red}P}(t))$ is the viscosity of the solvent, also dependent on temperature and pressure. \\

	%\begin{table}
	%	\begin{center}
		%		\caption{Axial mass diffusion: Parameters}
		%		\label{tab: Axial_Mass_Diffusion}
		%		\begin{tabular}{c c | c  c}
			%			\hline
			%			${\color{magenta}\hat{a}}$	& -105.161	& ${\color{magenta}\hat{b}}$	&  0.9007	\\
			%			${\color{magenta}\hat{c}}$ 	&  0.0007	&  								& 			\\
			%			\hline	
			%		\end{tabular}
		%	\end{center}
	%\end{table}

	\noindent \textbf{Thermal diffusion} 
	The thermal diffusion coefficient ${\color{orange}D_{\text{eff}}^T}$ of the pseudo-homogeneous fluid phase is assumed to be equal to that of pure carbon dioxide, at given temperature and pressure. By definition, we have%
	\begin{equation}
		{\color{orange}D_{\text{eff}}^T} \left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] = \cfrac{{\color{orange}k_t}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{{\color{orange}\rho_{\text{F}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi_{\rho_{\text{F}}}\right] {\color{orange}C_p^{\text{F}}} \left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid \varphi_{C_p^{\text{F}}}\right]}
	\end{equation}
	where ${\color{orange}C^{\text{F}}_p}[{\color{blue}T}(t,z),{\color{red}P}(t) \mid \varphi_{C_p^{\text{F}}}]$ and $\rho_{\text{F}}\left[{\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi_{\rho_{\text{F}}} \right]$ are the specific heat of $\text{CO}_2$ at constant pressure and its density discussed earlier, while ${\color{orange}k_t}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]$ is the thermal conductivity, again assumed to depend on temperature and pressure and parameters $\varphi_{k_t}$ specific of the chosen form of the dependence: We use the correlation suggested by \citet{Amooey2014} for supercritical $\text{CO}_2$ (in \ref{Asubsubsec: k_t}), though alternatives exist {\color{red}ADD REFS}. \\

	\noindent\textbf{Viscosity} 
	%
	%The viscosity of the solvent ($\text{CO}_2$) is expressed as a function of temperature and pressure using the expression proposed by \citet{Heidaryan2011}. The relationship is valid in the supercritical region for temperatures $T \in [313.15, 523.15]$ $[\text{K}]$ and pressures $P \in [7.7, 81.1]$ $[\text{MPa}]$
	%
	\begin{equation}
		{\color{orange}\eta} ({\color{blue}T}(t,z),{\color{red}P}(t) | {\color{magenta}\theta_\eta}) = \cfrac{\sum_{i=1}^{3}{{\color{magenta}\beta_i}{\color{red}P}^{i-1}(t)} + \sum_{i=4}^{6}{{\color{magenta}\beta_i}\ln({\color{blue}T}(t,z))^{i-3}}}{1 + {\color{magenta}\beta_7}{\color{red}P}(t) + {\color{magenta}\beta_8} \ln({\color{blue}T}(t,z)) + {\color{magenta}\beta_9}\ln({\color{blue}T}(t,z))^2}
	\end{equation}
	%
	%with parameters ${\color{magenta}\theta_\eta} = ({\color{magenta}\beta_1}, \dots, {\color{magenta}\beta_9})$ reported in Table \ref{tab: Viscosity_beta}
	%\begin{table}[pos=h!]
	%	\begin{center}
		%		\caption{Viscosity: Parameters ${\color{magenta}\theta_\eta}$.}
		%		\label{tab: Viscosity_beta}
		%		\begin{tabular}{c c | c  c}
			%			\hline
			%			${\color{magenta}\beta_1}$	& -1.1461E-01	& ${\color{magenta}\beta_2}$	&  6.9784E-07	\\
			%			${\color{magenta}\beta_3}$  &  3.9768E-10	& ${\color{magenta}\beta_4}$	&  6.3360E-02	\\
			%			${\color{magenta}\beta_5}$	& -1.1660E-02	& ${\color{magenta}\beta_6}$	&  7.1426E-04	\\
			%			${\color{magenta}\beta_7}$	&  6.5190E-06	& ${\color{magenta}\beta_8}$	& -3.5680E-01	\\
			%			${\color{magenta}\beta_9}$	&  3.1800E-02	&								&				\\
			%			\hline	
			%		\end{tabular}
		%	\end{center}
	%\end{table}
	%
	\newpage\subsection{Measurement model} \label{subsec: Measurement model}
	%The efficiency of the process (the yield) is calculated according to equation \ref{Model_measurment}. The yield is defined as the ratio between a difference of initial solute's mass in the solid phase ${\color{magenta}m_0}$, and an actual amount of solute in the same phase ${\color{blue}m}$, compared to the initial amount of the solute in the fixed bed ${\color{magenta}m_0}$. The yield can also be calculated based on the change of solutes concentration in the solid phase if the volume of the extractor ${\color{magenta}V}$ is constant.
	%An output function ${\color{blue}y}(t)$ returns a yield curve that represents the fraction of the solute's mass over time. The yield is obtained by function ${\color{blue}g}({\color{blue}q}(t,z))$. Function ${\color{blue}g}({\color{blue}q}(t,z))$ corresponds to a 'measurement device' that allows to calculate the yield based on the state variable ${\color{blue}q}(t,z)$. 
	%
	%\begin{align} 
	%		\label{Model_measurment}
	%		{\color{blue}y}(t) ={\color{blue}g}({\color{blue}q}(t,z)) &= \cfrac{ \left({\color{magenta}m_0} - {\color{blue}m}({\color{blue}q}(t,z)) \right) }{{\color{magenta}m_0}} = \cfrac{ {\color{magenta}V} \left({\color{magenta}q_0} - {\color{blue}q}(t,z) \right) }{{\color{magenta}V q_0}}
	%\end{align}
	%
	%where ${\color{blue}q}(t,z)$ is concentration of solute in a solid phase and a temperature, respectively. ${\color{magenta}m_0}$ is a initial mass of the solute in the solid phase, ${\color{magenta}q_0}$ is a  initial concentration of the solute in the solid phase, ${\color{magenta}V}$ is an extractor volume.
	%

\end{document}

### 2023-03-06 SFE-article/Sections/introduction.tex
06.03

--- 2022-05-25 SFE-report/Forward_sensitivity_analysis_of_SFE_Sliczniuk.tex
@@
-% ---------------------------------------------------------------
-% Preamble
-% ---------------------------------------------------------------
-%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}
-\documentclass[a4paper,fleqn]{cas-dc}
-%\documentclass[a4paper]{cas-dc}
-%\documentclass[a4paper]{cas-sc}
-% ---------------------------------------------------------------
+\documentclass[../Parameter_fitting.tex]{subfiles}
+\graphicspath{{\subfix{../Figures/}}}
+\begin{document}
 
-% -------------------------------------------------------------------- 
-% Packages
-% --------------------------------------------------------------------
-% Figure packages
-\usepackage{float}
-\usepackage{adjustbox}
-% Text, input, formatting, and language-related packages
-\usepackage[T1]{fontenc}
-\usepackage{subcaption}
-% \usepackage[utf8]{inputenc}
-% \usepackage[nomath]{lmodern}
-
-% Margin and formatting specifications
-%\usepackage[authoryear]{natbib}
-\usepackage[sort]{natbib}
-\setcitestyle{square,numbers}
-
- %\bibliographystyle{cas-model2-names}
-
-\usepackage{setspace}
-
-% \usepackage[authoryear,longnamesfirst]{natbib}
-
-% Math packages
-\usepackage{amsmath, amsthm, amssymb, amsfonts, bm, nccmath, mathdots, mathtools, bigints, ulem}
-
-% --------------------------------------------------------------------
-% Packages Configurations
-% --------------------------------------------------------------------
-% (General) General configurations and fixes
-\AtBeginDocument{\setlength{\FullWidth}{\textwidth}}	% Solves els-cas caption positioning issue
-\setlength{\parindent}{20pt}
-%\doublespacing
-% --------------------------------------------------------------------
-% Other Definitions
-% --------------------------------------------------------------------
-
-% --------------------------------------------------------------------
-% Environments
-% --------------------------------------------------------------------
-% ...
-
-% --------------------------------------------------------------------
-% Commands
-% --------------------------------------------------------------------
-
-% ==============================================================
-% ========================== DOCUMENT ==========================
-% ==============================================================
-\begin{document} 
-%  --------------------------------------------------------------------
-
-% ===================================================
-% METADATA
-% ===================================================
-\title[mode=title]{Parameter estimation}                      
-\shorttitle{Forward sensitivity analysis of the supercritical extraction process}
-
-\shortauthors{A, B, C}
-
-\author[1]{Oliwer Sliczniuk*}[orcid=0000-0003-2593-5956]
-\ead{oliwer.sliczniuk@aalto.fi}
-\cormark[1]
-%\credit{a}
-
-\author[1]{Pekka Oinas}[orcid=0000-0002-0183-5558]
-%\credit{b}
-
-\author[1]{Francesco Corona}[orcid=0000-0002-3615-1359]
-%\credit{c}
-
-\address[1]{Aalto University, School of Chemical Engineering, Espoo, 02150, Finland}
-%\address[2]{2}
-
-\cortext[cor1]{Corresponding author}
-
-% ===================================================
-% ABSTRACT
-% ===================================================
-\begin{abstract}
-Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output.
-As an example, the supercritical extraction process is presented.
-The impact of mass flow rate, pressure, and inlet temperature on the model's output is discussed.
-The sensitivity analysis results prove that the considered variables can affect the extraction's yield and be used as control variables in optimization problems.
-Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
-
-\end{abstract}
-
-\begin{keywords}
-Supercritical extraction \sep Parameter estimation \sep Mathematical modelling
-\end{keywords}
-
-% ===================================================
-% TITLE
-% ===================================================
-\maketitle
-
-% ===================================================
-% Section: Introduction
-% ===================================================\section{Introduction}
-
-\section{Introduction}
 	%{\color{brown}Intro about extraction}\\
@@
 
-\section{Materials and methods} \label{CH: Materials and methods}
-\sout{The extraction process is assumed to operate in a semi-continuous mode in a cylindrical vessel.
-The solvent is firstly brought to super-critical condition, pumped through a fixed-bed, of finely chopped biomass, where the solute is extracted from the biomass.
-Then, the solvent and solute from the extractor are separated in a flush drum, and the extract is collected.
-The flow rate ($F_{in}$) and inlet temperature ($T_{in}$) of the extractor’s feed can be measured and manipulated.
-The pressure ($P$) in the vessel can be measured and manipulated, while the outlet temperature ($T_{out}$) can only be measured.
-A simplified flow diagram is depicted in Figure \ref{fig: SFE_drawing} }.
-
-{\color{blue}The solid-fluid extraction process is assumed to operate in a semi-continuous mode in a cylindrical vessel.
-In the extractor, essential oils are removed from biomass (for example, carqueja seeds) by supercritical carbon dioxide.
-As the solvent flows continuously through the bed of porous particles, the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles.
-Then the solute dissolves and diffuses into the solvent in the pores and eventually into the bulk.
-The solvent-solute mixture leaves the extractor and undergoes depressurization.
-The $CO_2$ is released to a gaseous state, and the solute precipitates.
-In the vapour-liquid separator, the gaseous solvent is vent off while the precipitated product is collected.
-
-In Figure \ref{fig: SFE_drawing}, an instrumental set-up is presented.
-The flow rate ($F_{in}$) and the temperature ($T_{in}$) of the solvent entering the extractor are measured and can be adjusted using a pump and a heat exchanger, respectively.
-Moreover, the extractor's pressure ($P$) is assumed to be measurable and adjustable using a back-pressure regulator valve.
-In addition, the temperature of the outlet stream $T_{out}$ and the temperature profile of the fixed-bed can be measured.
-}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[trim = 6cm 7.5cm 8cm 6cm, clip, width=\linewidth]{Figures/SFE_PFD.pdf}
-	\caption{Process flow diagram for solid-fluid extraction process}
-	\label{fig: SFE_drawing}
-\end{figure}
-
-\subsection{Extraction model} \label{CH: Extraction_model}
-
-\sout{The main components of the model are three one-dimensional differential equations related to mass balances (solid and fluid phase) and heat balance.
-As in all batch processes, our system has only one steady state.
-The steady-state occurs only if the solute is entirely taken out of the biomass.
-
-The extraction from a fixed bed is an unsteady process, implying that the solute concentrations in the solid and solvent phases vary over time and space.
-The convection and the diffusion of the mass and the heat are considered only in the axial direction.
-The radial distribution of such properties like a velocity is assumed to be flat in that direction.
-The assumption of the flat velocity profile allows considering a lack of back mixing.
-The pressure drop in the bed is assumed to be assumed to negligible.
-Under such conditions, the fluid flow can be considered a plug flow.
-
-Since the solute is assumed to be a single pseudo-component, there is only one mass balance equation for each phase (Eq.
-s \ref{Model_fluid} and \ref{Model_solid}).
-On the other hand, there is only one heat balance (Eq.
-\ref{Model_heat}) because the presence of a single pseudo-phase is assumed.
-
-Moreover, the process model does not consider the change of particle size or the void fraction during the process.
-The particles are assumed to be uniformly distributed along the bed and to have the same size.}
-
-{\color{blue}A distributed-parameter model, based on \citet{Reverchon1996}, is used to describe the solid-fluid extraction process.
-The process model consists of three partial differential equations: two mass balance equations relative to the concentration of solute in the fixed solid phase and the mobile fluid phase, and the heat balance equation relative to the temperature of the fluid phase.
-The amount of solute in the solvent is considered negligible.
-Therefore, the fluid phase can be described as pseudo-homogenous, and its properties are assumed to be the same as the solvent.
-
-The movement of the mobile pseudo-homogeneous phase (Eq.
-\ref{Model_fluid}) is considered only in the axial direction.
-The properties of the system in the radial direction is assumed to be uniform.
-In addition, it is considered that the boundary layer adjacent to the inner wall of the extractor does not exist.
-Therefore, the velocity profile is constant across any cross-section of the extractor perpendicular to the axial direction.
-As a result, the plug flow model can be introduced.
-The particle size distribution and the void fraction of the solid phase are assumed to be uniform in space and remain constant in time.
-Moreover, the pressure is considered to be constant along the fixed bed.
-The mass balance for the fluid phase consists of convection, diffusion, and kinetic terms.
-
-Considering the solid phase to be fixed, the convection and diffusion terms in the corresponding mass balance are both assumed to be negligible or absent.
-Therefore, the mass balance for the solid phase (Eq.
-\ref{Model_solid}) consists of the kinetic term only.
-
-As for the mass transfer from the solid to the fluid phase, a kinetic term based on two-film theory for the solute is considered.
-The mass transfer kinetic (Eq.
-\ref{Model_kinetic_basic}) consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.
-A single pseudo-component is used to represent the extract collectively.
-
-The heat balance (Eq.
-\ref{Model_heat}) consists of the convective and diffusive terms.
-It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases.
-We consider no heat loss through the wall, and there is no heat generation in the system.
-Therefore, the temperature of the extractor can be changed only by manipulating the temperature of the inlet stream $T_{In}(t)$.
-}
-
-For the sake of clarity of the process model, different colors have been used in the equations to indicate: 
-{\color{red}control variables},
-{\color{blue}state variables},
-{\color{orange}variables} and
-{\color{magenta}parameters}.
-
-\subsubsection{Mass balance for the fluid phase} \label{CH: Mass_balance_fluid}
-The fluid phase is a mobile phase, which means that the fluids mass balance (Eq. \ref{Model_fluid}) is made of convection, diffusion, and mass transfer kinetic terms.
-
-{\footnotesize
-		\begin{align} 
-			\label{Model_fluid}
-			\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t} &	=  \underbrace{-\cfrac{1}{ {\color{magenta}\varepsilon A}}\cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]} \cfrac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} \\
-			&+ \underbrace{ {\color{orange}D^M_e}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] \cfrac{\partial^2 {\color{blue}c_f}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusive term}}
-			+ \underbrace{ \cfrac{1-{\color{magenta}\varepsilon}}{{\color{magenta}\varepsilon}} {\color{blue}r_e}(t,z) }_{\text{Kinetic term}} 
-		\end{align} }
-
-where ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z), {\color{blue}T}(t,z)$ correspond to concentration of solute in the fluid phase, concentration of solute in the solid phase and the temperature, respectively.
-${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term.
-${\color{red}F}(t)$ is the mass flow rate, ${\color{red}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{magenta}A}$ is the extractor’s cross section, ${\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient.
-
-\subsubsection{Mass balance for the solid phase} \label{Mass_balance_solid}
-The solid phase is a stationary phase, which indicates a lack of convection and diffusion terms in the mass balance (Eq.
-\ref{Model_solid}).
-Therefore, the only term present in this equation is the kinetic term (defined as presented in equation \ref{Model_kinetic_basic}), which links solid and fluid phases.
-
-{\footnotesize
-		\begin{equation} 
-			\label{Model_solid}
-			%		{\scriptsize\begin{align*}
-			\cfrac{\partial {\color{blue}c_s}(t,z)}{\partial t} = \underbrace{ {\color{blue}r_e}(t,z) }_{\text{Kinetics}}
-		\end{equation} }
-
-\subsubsection{Kinetic term} \label{CH: Kinetic}
-As the solvent flows through the bed, \sout{it forms a film around the porous solid particle and occupies its pores.} {\color{blue}the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to for an external fluid film around the solid particles through the solvent–solid matrix interactions.
-Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected.
-In this work, the molecular diffusion is assumed.}.
-The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
-The graphical representation of the mass transfer mechanism is shown in Figure \ref{fig: SFE_Mechanism}.
-The mean solute concentration in the solid phase is denoted as ${\color{blue}c_s}$.
-At the solid-fluid interface, the equilibrium concentrations are given as ${\color{blue}c_s^*}$ and ${\color{blue}c_P^*}$, respectively for solid and fluid phases.
-The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{blue}c_{P}}$.
-As the solute diffuses through the pore, its concentration changes and reaches ${\color{blue}c_{Pf}}$ at \sout{the end} {\color{blue}the opening} of the pore.
-The solute diffuses through the film around the particle and reaches a concentration in the bulk ${\color{blue}c_f}$.
-It can be assumed that the two-film theory describes the solid-fluid interface inside the pore.
-The overall mass transfer coefficient can be introduced if the relation between the solute concentration in one phase and its equilibrium concentration is known.
-
-\begin{figure}[h!]
-	\centering
-%	\includegraphics[trim  = 6cm 0cm 3cm 0cm,clip,width=\linewidth]{Figures/SFE_draft.png}
-	\includegraphics[trim = 5.8cm 1.1cm 6cm 0.8cm,clip,width=1.0\linewidth]{Figures/SFE_draft.pdf}	
-	\caption{The extraction mechanism}
-	\label{fig: SFE_Mechanism}
-\end{figure}
-
-\citet{Bulley1984} suggest a process where the driving force for extraction is given by the difference between concentration of the solute in the bulk, ${\color{blue}c_f}$, and in the centre of the pore, ${\color{blue}c_P^*}$.
-The concentration ${\color{blue}c_P^*}$ is in equilibrium with ${\color{blue}c_s}$ according to an equilibrium relationship.
-The rate of extraction is thus ${\color{blue}r_\text{e}}\left({\color{blue}c_f} - {\color{blue}c^*_P}({\color{blue}c_s})\right)$.
-
-On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between ${\color{blue}c_s}$ and ${\color{blue}c_P^*}$.
-${\color{blue}c_P^*}$ is determined by an equilibrium relationship with ${\color{blue}c_f}$ and the extraction rate is ${\color{blue}r_\text{e}}\left({\color{blue}c_s} - {\color{blue}c^*_P}({\color{blue}c_f})\right)$.
-
-\sout{The kinetic term, denoted as equation \ref{Model_kinetic_basic}, corresponds to a solute transfer rate between both phases.
-This term is made of the overall diffusion coefficient and the concentration gradient (between one phase and its equilibrium concentration), which acts as a driving force for the process.} {\color{blue}The mass transfer kinetic (Eq.
-\ref{Model_kinetic_basic}) describes a diffusion rate of the solute from solid particles to the solvent.
-The kinetic term consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.} Based on the work of \citet{Bulley1984}, \citet{Reverchon1996} proposed to define the kinetic terms as
-
-{\footnotesize
-\begin{equation} \label{Model_kinetic_basic}
-	{\color{blue}r_e}(t,z) = \cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}q}(t,z) - {\color{blue}q^*}(t,z) \right)
-\end{equation} }
-
-where ${\color{orange}D_i}({\color{blue}T}(t,z))$ corresponds to the overall diffusion coefficient and ${\color{blue}q^*}(t,z)$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).
-${\color{blue}q^*}(t,z)$ can be calculated based on the equilibrium relationship (Eq.
-\ref{Linear_equilibirum}).
-
-\sout{The kinetic term of the model takes into account the properties of the biomass like a sphericity (through the shape coefficient ${\color{magenta}\mu}$ equal to $1/3$ for slabs and $3/5$ for spheres), a characteristic dimension of particles (through the parameter ${\color{magenta}l} = {\color{magenta}r}/3$ where ${\color{magenta}r}$ is the mean particle radius), and the solid density ${\color{magenta}\rho_s}$.
-The fixed bed is characterized by a void fraction ${\color{magenta}\epsilon}$.
-}
-
-{\color{blue} The kinetic term of the model takes into account properties of the solid particles like a sphericity (through the shape coefficient ${\color{magenta}\mu}$), a characteristic dimension of particles (through the parameter ${\color{magenta}l} = {\color{magenta}r}/3$ where ${\color{magenta}r}$ is the mean particle radius), and the bulk density ${\color{magenta}\rho_s}$.
-The fixed bed is characterized by a void fraction ${\color{magenta}\epsilon}$.
-}
-
-According to \citet{Bulley1984}, a linear equilibrium relationship (Eq.
-\ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{blue}c_f^*}(t,z)$ is based on concentration of the solute in the solid phase ${\color{blue}c_s}(t,z)$
-
-{\footnotesize
-\begin{align} \label{Linear_equilibirum}
-	{\color{blue}c}(t,z) &= {\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t)) \allowbreak {\color{blue}q^*}(t,z)
-\end{align} }
-
-The volumetric partition coefficient ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
-\sout{ The ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$ according to $\citet{Spiro2007}$ .}
-{\color{blue} According to \citet{Spiro2007}, the term ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as the function of mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$ }
-
-{\footnotesize
-\begin{align}
-	{\color{orange}k_m}({\color{blue}T}(t,z)) = \cfrac{{\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{magenta}\rho_s}}{{\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}
-\end{align} }
-
-Equation \ref{Model_kinetic} is the full representation of the kinetic term.
-
-{\footnotesize
-	\begin{align}
-		\label{Model_kinetic}
-		{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}q}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c}(t,z) \right)
-\end{align} }
-
-\subsubsection{Heat balance} \label{CH: heat_balance}
-\sout{The heat balance equation (Eq.
-\ref{Model_heat}) was developed, assuming the existence of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases (the amount of solute is considered small enough not to affect the overall heat balance).
-Equation \ref{Model_heat} contains the convection and the diffusion terms.
-It is considered that there is no heat loss through the wall, and there is no heat generation in the system.
-The temperature of the extractor can be changed only by increasing the temperature of the inlet stream.
-The pseudo-homogenous phase is assumed to flow only in the axial direction.
-The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ because the solid phase is stationary.
-Therefore, this factor can be understood as the fraction of the fluid's total heat through convection.
-On the other hand, the axial heat diffusion is calculated based on the definition of thermal diffusivity for the fluid, as explained in the appendix.
-}
-
-{\color{blue} The heat balance (Eq.
-\ref{Model_heat}), is based on \citet{Srinivasan2012}, and consists of convective and diffusive terms.
-It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases.
-It is considered that there is no heat loss through the walls, and there is no heat generation in the system.
-The temperature of the extractor can be changed only by manipulating the temperature of the inlet stream ${\color{red}T_{Inlet}}(t)$.
-	}
-
-{\footnotesize
-	\begin{equation} \label{Model_heat}
-		\begin{split}
-			\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} &= 
-			\underbrace{ -\cfrac{{\color{red}F}(t) {\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))}{{\color{magenta}A} 	[(1-{\color{magenta}\epsilon}){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{orange}C_p} ({\color{blue}T}(t,z),{\color{red}P}(t)) + {\color{magenta} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}}  }_{\text{Convection}} + \\
-			& + \underbrace{ {\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{red}P}(t)) \cfrac{\partial^2 {\color{blue}T}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusion}}
-		\end{split}
-	\end{equation} }
-
-where $ {\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient, ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's specific heat, ${\color{magenta}C_{ps}}$ is the specific heat of the solid phase, ${\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial heat diffusion coefficient.
-
-\subsubsection{Extraction yield} \label{CH: Yield}
-\sout{The efficiency of the process (the yield) is calculated according to equation \ref{Model_measurment}.
-The yield is defined as the ratio between a difference of initial solute's mass in the solid phase ${\color{magenta}m_0}$, and an actual amount of solute in the same phase ${\color{blue}m}$, compared to the initial amount of the solute in the fixed bed ${\color{magenta}m_0}$.
-The yield can also be calculated based on the change of solutes concentration in the solid phase if the volume of the extractor ${\color{magenta}V}$ is constant.
-An output function ${\color{blue}y}(t)$ returns a yield curve that represents the fraction of the solute's mass over time.
-The yield is obtained by function ${\color{blue}g}({\color{blue}q}(t,z))$.
-Function ${\color{blue}g}({\color{blue}q}(t,z))$ corresponds to a 'measurement device' that allows to calculate the yield based on the state variable ${\color{blue}q}(t,z)$.
-}
-{\color{blue}The efficiency of the process (the yield) is calculated according to Eq.
-\ref{Model_measurment}, and is based on the change of solute's mass in the solid phase.
-It is defined as ratio the ratio between the difference of its initial value ${\color{magenta}m_0}$ and the actual value ${\color{blue}m}(t,z)$, compared to the initial one.
-The yield can also be calculated based on the change of solutes concentration in the solid phase if the volume of the extractor ${\color{magenta}V}$ is constant.}
-
-{\footnotesize
-	\begin{align} 
-		\label{Model_measurment}
-		{\color{blue}y}(t) ={\color{blue}g}({\color{blue}q}(t,z)) &= \cfrac{ \left({\color{magenta}m_0} - {\color{blue}m}({\color{blue}q}(t,z)) \right) }{{\color{magenta}m_0}} = \cfrac{ {\color{magenta}V} \left({\color{magenta}q_0} - {\color{blue}q}(t,z) \right) }{{\color{magenta}V q_0}}
-	\end{align}	}
-
-\sout{where ${\color{blue}q}(t,z)$ is concentration of solute in a solid phase and a temperature, respectively.
-${\color{magenta}m_0}$ is a initial mass of the solute in the solid phase, ${\color{magenta}q_0}$ is a  initial concentration of the solute in the solid phase, ${\color{magenta}V}$ is an extractor volume.}
-
-\subsubsection{Dependencies} \label{CH: Dependencies}
-{\color{blue}The Peng-Robinson equation of state is used to describe the thermodynamics of the fluid phase.
-The thermal properties of the pseudo-homogeneous phase are assumed to vary along the extractor, though always remaining equal to the corresponding mean values between the fluid and solid phase.
-}
-
-In the process model, properties of the supercritical fluid such as the density ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$, the specific heat ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$, the thermal conductivity ${\color{orange}k^T}({\color{blue}T}(t,z),{\color{red}P}(t))$, or the viscosity ${\color{orange}\eta}({\color{blue}T}(t,z),{\color{red}P}(t))$ are calculated based on the local temperatures along the fixed bed and the pressure.
-The Peng-Robinson equation of state is used to find values of a ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$ and ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$.
-
-The inter-particle diffusion coefficient ${\color{orange}D^M_e}(\allowbreak{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is calculated from the empirical correlation, as the function of the Reynolds number ${\color{orange}R_e}({\color{blue}T}(t,z),{\color{red}P}(t),\allowbreak{\color{red}F}(t))$ and the Peclet's number ${\color{orange}P_e}({\color{blue}T}(t,z),\allowbreak{\color{red}P}(t),{\color{red}F}(t))$.
-The values of the internal diffusion ${\color{orange}D_i} ({\color{blue}T}(t,z))$ and the partition coefficient ${\color{orange}k_m} ({\color{blue}T}(t,z))$ come from the laboratory experiments.
-The expressions and the detailed information of the parameter fitting can be found in the appendix.
-
-\subsubsection{State-space representation} \label{CH: State_space}
-It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}q_0}$.
-Moreover, it is considered that the initial temperature of the extractor in every place is equal to ${\color{magenta}T_0}$.
-Therefore, the initial conditions employed in the simulation are:
-
-{\footnotesize
-\begin{subequations}
-	\begin{align*}
-		{\color{blue}c}(t = 0, z) &= 0   \\
-		{\color{blue}q}(t = 0, z) &= {\color{magenta}q_0} \\
-		{\color{blue}T}(t = 0, z) &= {\color{magenta}T_0}
-	\end{align*}
-\end{subequations} }
-
-The process model can be written in a general form:
-
-{\footnotesize
-\begin{align}
-	\begin{bmatrix}
-		\cfrac{\partial {\color{blue}c}(t,z)}{\partial t}\\
-		\cfrac{\partial {\color{blue}q}(t,z)}{\partial t}\\
-		\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} 
-	\end{bmatrix}
-	& =
-	\begin{bmatrix}
-		{\color{blue}\phi_1} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)\\
-		{\color{blue}\phi_2} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)\\
-		{\color{blue}\phi_3} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)
-	\end{bmatrix} = {\color{blue}\phi} \left( t,z; {\color{magenta}\theta} \right) = \cfrac{\partial {\color{blue}\chi}(t,z)}{\partial t}
-\end{align} }
-
-where ${\color{magenta}\theta}$ is a set of parameters present in the model, ${\color{blue}\phi}$ is a set of functions that correspond to state equations of the model, and ${\color{blue}\chi}$ is the state-space model.
-
-The method of lines is used to transform the process model equations into a set of ODEs denoted as ${\color{blue}G}({\color{blue}x}(t);{\color{magenta}p})$.
-The partial derivatives in $z$-direction are computed using a first-order and second-order finite difference approximation.
-The backward finite difference is used to approximate first-order derivative, while the central difference scheme is used to approximate second-order derivative.
-The length of the fixed bed is divided into $N_z$ equally distributed points in $z$-direction.
-Each function ${\color{blue}\phi_i}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{blue}G}_{i\times N_z+1}$ to ${\color{blue}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation.
-The state-space model ${\color{blue}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{blue}x}}(t)$ (Eq.
-\ref{discretization}).
-
-{\footnotesize
-\begin{align*} \label{discretization}
-	\dot{{\color{blue}x}}(t) &= \cfrac{d {\color{blue}x}(t)}{d t} = 
-	\begin{bmatrix}
-		\cfrac{d {\color{blue}c_{f,1}}(t)}{d t} 	  \\
-		\vdots					  \\
-		\cfrac{d {\color{blue}c_{f,N_z}}(t)}{d t} \\
-		\\ \hline \\
-		\cfrac{d {\color{blue}c_{s,1}}(t)}{d t} 	  \\
-		\vdots					  \\
-		\cfrac{d {\color{blue}c_{s,N_z}}(t)}{d t} \\
-		\\ \hline \\
-		\cfrac{d {\color{blue}T_1}(t)}{d t} 	  \\
-		\vdots 					  \\
-		\cfrac{d {\color{blue}T_{N_z}}(t)}{d t}
-	\end{bmatrix}
-	=
-	\underbrace{\begin{bmatrix}
-			{\color{blue}G_1} \left( {\color{blue}x}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
-			\vdots\\ 
-			{\color{blue}G_{N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
-			\\ \hline \\ \\
-			{\color{blue}G_{N_z+1}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
-			\vdots\\
-			{\color{blue}G_{2N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
-			\\ \\ \hline \\ 
-			{\color{blue}G_{2N_z+1}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right) \\
-			\vdots\\
-			{\color{blue}G_{3N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)
-	\end{bmatrix}}_{{\color{blue}G} \left( {\color{blue}x}(t); {\color{magenta}p} \right)} 
-\end{align*} }
-
-where ${\color{blue}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{magenta}p} \in \mathbb{R}^{N_p =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of model parameters, $N_{u}$ is the number of control variables.
-
-{\color{blue} In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases ($c(t,z)$ and $q(t,z)$, respectively), and the local temperature of the pseudo-homogeneous phase ($T(t,z)$).
-The controllable input variables are the mass flow-rate and temperature of the solvent in the feed ($F_\text{in}(t) = F(t)$ and $T_\text{in}(t) = T(t,z=0)$, respectively) and the pressure in the extractor ($P(t,z) = P(t)$).
-{\color{red}We also assume that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator ($Y(t)$).} The system is controllable by manipulating the flow-rate and temperature of CO2 in the feed, and the pressure in the extractor.
-}
-
-\newpage
-\section{Parameter estimation} \label{CH: Parameter_estimation}
-Estimation theory is a branch of statistics that deals with estimating the values of parameters based on measured empirical data that has a random component.
-The parameters describe an underlying physical setting in such a way that their value affects the distribution of the measured data.
-An estimator attempts to approximate the unknown parameters using the measurements.
-
-For a given model, several statistical "ingredients" are needed so the estimator can be implemented.
-The first is a statistical sample – a set of data points taken from a random vector (RV) of size $N$.
-Let denote a statistical sample as $x$ and parameters whose vales are to be estimated as $\theta$.
-Both can be written into a vector form:
-\begin{align}
-	x &= [x[0], x[1], \dots, x[N-1] ]^T, &&x \in \mathbb{R}^N \\
-	\theta &= [\theta_0, \theta_1, \dots, \theta_M ]^T,  &&\theta \in \mathbb{R}^M
-\end{align}
-
-where $N$ is the number of samples and $M$ is the number of parameter to estimation.
-
-The continuous probability density function (pdf) or its discrete counterpart, the probability mass function (pmf), of the underlying distribution that generated the data must be stated conditional on the values of the parameters: $p(x|\theta)$.
-It is also possible for the parameters themselves to have a probability distribution (e.g., Bayesian statistics).
-It is then necessary to define the Bayesian probability $\pi(\theta)$.
-After the model is formed, the goal is to estimate the parameters, with the estimates commonly denoted $\hat{\theta}$.
-
-One common estimator is the minimum mean squared error (MMSE) estimator, which utilizes the error between the estimated parameters and the actual value of the parameters as the basis for optimality.
-This error term is then squared and the expected value of this squared value is minimized for the MMSE estimator.
-
-\subsection{Bayes theorem} \label{CH: Bayes_theorem}
-In probability theory and statistics, Bayes' theorem (alternatively Bayes' law or Bayes' rule; recently Bayes–Price theorem[1]: 44, 45, 46 and 67 ), named after Thomas Bayes, describes the probability of an event, based on prior knowledge of conditions that might be related to the event.[2] For example, if the risk of developing health problems is known to increase with age, Bayes' theorem allows the risk to an individual of a known age to be assessed more accurately (by conditioning it on their age) than simply assuming that the individual is typical of the population as a whole.
-
-One of the many applications of Bayes' theorem is Bayesian inference, a particular approach to statistical inference.
-When applied, the probabilities involved in the theorem may have different probability interpretations.
-With Bayesian probability interpretation, the theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.
-Bayesian inference is fundamental to Bayesian statistics.
-
-\subsection{Maximum likelihood estimation} \label{CH: MLE}
-\subsection{Maximum a posteriori} \label{CH: MAP}
-\subsection{Bayesian inference} \label{CH: Bayesian_inference}
-
-\section{Results} \label{CH: Results}
-
-\section{Conclusions}
-
-% ===================================================
-% Bibliography
-% ===================================================
-%% Loading bibliography style file
-\clearpage
-%\bibliographystyle{model1-num-names}
-\bibliographystyle{unsrtnat}
-\bibliography{mybibfile}
-
-\clearpage \appendix \label{appendix}
-\section{Appendix}
-
-\newpage
-\begin{table*}[p]
-		\caption{Notation}
-		\label{tab::symbols}
-		\begin{tabular}{ |c|l|c| } 
-			\hline
-			Symbol 		& 	Description 							& Unit 						\\ \hline
-			$A$			&	cross-section							& $m^2$ 					\\ \hline
-			$c$			&	concentration in fluid phase			& $kg ~ m^{-3}$				\\ \hline
-			$Cp$		&	specific heat of the fluid				& $J ~ mol^{-1} ~ K^{-1}$ 	\\ \hline
-			$Cp_s$		&	specific heat of the solid				& $J ~ mol^{-1} ~ K^{-1}$ 	\\ \hline
-			$D_e^M$		&	axial mass diffusion coefficient		& $m^2 ~ s^{-1}$			\\ \hline
-			$D_e^T$		&	axial heat diffusion coefficient		& $m^2 ~ s^{-1}$			\\ \hline
-			$Di$		&	internal diffusion coefficient			& $m^2 ~ s^{-1}$			\\ \hline
-			$dp$		&	particle diameter						& $m$						\\ \hline
-			$F(t)$		&	mass flow-rate							& $kg ~ s^{-1}$				\\ \hline
-			$km$		&	partition coefficient					& $[-]$						\\ \hline
-			$k^T$		&	thermal conductivity					& $W ~ m^{-1} ~ K^{-1}$		\\ \hline
-			$l$			&	characteristic dimension				& $m$						\\ \hline
-			$L$			&	total length of the bed					& $m$						\\ \hline
-			$m$			&	mass of the oil in solid phase			& $kg$						\\ \hline
-			$m_0$		&	initial mass of the oil in solid phase	& $kg$						\\ \hline
-			$M_{CO_2}$	&	molecular mass of CO2					& $mol ~ kg^{-1}$			\\ \hline
-			$Np$		&	number of model parameters and control variables & $[-]$			\\ \hline
-			$N_{\theta}$&	number of model parameters				& $[-]$						\\ \hline
-			$Nu$		&	number of control variables				& $[-]$						\\ \hline
-			$Nz$		&	number of grid points in z-direction	& $[-]$						\\ \hline
-			$p$			&	vector of model parameters and control variables	& $[-]$			\\ \hline
-			$P(t)$		&	pressure								& $bar$						\\ \hline
-			$Pe$		&	Peclet's number							& $[-]$						\\ \hline
-			$q$			&	concentration in solid phase			& $kg ~ m^{-3}$				\\ \hline
-			$R$			&	gas constant							& $J ~ K^{-1} ~ mol^{-1}$	\\ \hline
-			$Re$		&	Reynolds number							& $[-]$						\\ \hline
-			$t$			&	time									& $s$						\\ \hline
-			$T$			&	temperature								& $K$						\\ \hline
-			$T_0$		&	initial temperature						& $K$						\\ \hline
-			$V$			&	volume of the extractor					& $m^3$						\\ \hline
-			$y$			&	yield	 								& $[-]$						\\ \hline
-			$z$			&	length									& $m$						\\ \hline
-			$Z$			&	compressibility	factor					& $[-]$						\\ \hline
-			$\epsilon$	&	void fraction							& $[-]$						\\ \hline
-			$\rho$		&	density of the fluid					& $kg ~ m^{-3}$				\\ \hline
-			$\rho_s$	&	solid density							& $kg ~ m^{-3}$				\\ \hline
-			$\mu$		&	shape coefficient						& $[-]$						\\ \hline
-			$\theta$	&	vector of model parameters				& $[-]$						\\ \hline
-			$\eta$		&	viscosity								& $cP$						\\ \hline				
-						& 											&							\\ \hline			
-		 	Subscript	& 											&							\\ \hline
-			$0$			&	initial conditions						& $[-]$						\\ \hline
-			$^*$		&	equilibrium conditions					& $[-]$						\\ \hline							
-		\end{tabular}
-\end{table*}
 \end{document}

### 2023-03-06 SFE-article/Article_Model_Parameters.tex
06.03

--- 2023-02-16 SFE-report/Paramter_fitting.tex
@@
 
-\section{Materials and methods} \label{CH: Materials and methods}
+%\section{Materials and methods} \label{CH: Materials and methods}
+
+\section{$CO_2$ properties} \label{CH: Thermodynamic}
+%\subfile{Sections/Thermo}
+
+\clearpage
 %\subfile{Sections/Materials_and_methods}
 
-\subsection{Extraction model} \label{CH: Extraction_model}
-\subfile{Sections/Model}
+\subsection{Governing equations}
+The detail derivation of the governing equation can be found in the appendix (\ref{CH: Gouverning equations}).
+Let's assume that any properties of the flow are unifrom across any given cross-section of an channel (or any device like an extractor).
+Such a floww is called quasi-one-dimensional.
+The variation of the cross-section might be an result of its irregular shape (or partial filling of an extractor).
+
+The quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates is given be equations \ref{EQ: CompressibleEuler}
+
+{\footnotesize
+\begin{equation}
+\begin{align}
+        \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
+        \cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \\
+        \cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T}{\partial z} \right)
+    \end{align}    
+\end{equation}
+\label{EQ: CompressibleEuler}
+}
+
+where $\rho_f$ is the density of the fluid, $A_f$ is the function which describe change of the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
 
@@
 \subfile{Sections/Low_mach_number_expansion}
+
+\subsection{Extraction model} \label{CH: Extraction_model}
+%\subfile{Sections/Model}
 
@@
 
-\clearpage
-
 \subsection{Parameter estimation} \label{CH: Parameter_estimation}
-\subfile{Sections/Parameter_estimation}
+%\subfile{Sections/Parameter_estimation}
 
 \section{Results} \label{CH: Results}
-
-\begin{figure*}[h!]
-		\centering
-		\includegraphics[trim = 0cm 0cm 0cm 0cm,clip,width=\textwidth]{Figures/Results_estimation/Yield.pdf}	
-		\caption{The yield curve vs dataset}
-\end{figure*}
-
-\begin{figure*}[h!]
-	\centering
-	\includegraphics[trim = 0cm 0cm 0cm 0cm,clip,width=\textwidth]{Figures/Results_estimation/Profiles.pdf}	
-	\caption{The fluid density based on the Peng-Robinson equation of state}
-\end{figure*}
 
@@
 \subsection{Governing equations}
-\subfile{Sections/Gouverning_equation_derivation}
+%\subfile{Sections/Gouverning_equation_derivation}
 
 \subsection{Bayes theorem} \label{CH: Bayes}
-\subfile{Sections/Bayes_Theorem}
+%\subfile{Sections/Bayes_Theorem}
 

### 2023-03-06 SFE-article/Sections/Low_mach_number_expansion.tex
06.03

@@
 Such a set of equations allow for large variations in gas density but it is consider to be acoustically incompressible.
-The low Mach number equations are preferred over the full compressible equations for low speed flow problems $\left( M_a = \cfrac{|V|}{\sqrt{ \partial P / \partial \rho }} \ll 1 \right)$ to avoids the need to resolve fast-moving acoustic signals.
+The low Mach number equations are preferred over the full compressible equations for low speed flow problems $\left( M_a = \frac{|V|}{\sqrt{ \partial P / \partial \rho }} \ll 1 \right)$ to avoids the need to resolve fast-moving acoustic signals.
 The equations are derived from the compressible equations based on the perturbation theory.
@@
 
-	The equations {\color{red}RED} describe the fully compressible equations of motion (respectively the transport of mass, momentum and energy) for quasi-one-dimensional case.
+	The equations \ref{EQ: CompressibleEuler} describe the fully compressible equations of motion (respectively the transport of mass, momentum and energy) for quasi-one-dimensional case.
 We rescale the time variable, considering finally

### 2023-03-06 SFE-article/Sections/Materials_and_methods.tex
06.03

@@
 
-	{\color{blue}The solid-fluid extraction process is assumed to operate in a semi-continuous mode in a cylindrical vessel.
-In the extractor, essential oils are removed from biomass (for example, carqueja seeds) by supercritical carbon dioxide.
-As the solvent flows continuously through the bed of porous particles, the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles.
-Then the solute dissolves and diffuses into the solvent in the pores and eventually into the bulk.
-The solvent-solute mixture leaves the extractor and undergoes depressurization.
-The $CO_2$ is released to a gaseous state, and the solute precipitates.
-In the vapour-liquid separator, the gaseous solvent is vent off while the precipitated product is collected.
-
-		In Figure \ref{fig: SFE_drawing}, an instrumental set-up is presented.
-The flow rate ($F_{in}$) and the temperature ($T_{in}$) of the solvent entering the extractor are measured and can be adjusted using a pump and a heat exchanger, respectively.
-Moreover, the extractor's pressure ($P$) is assumed to be measurable and adjustable using a back-pressure regulator valve.
-In addition, the temperature of the outlet stream $T_{out}$ and the temperature profile of the fixed-bed can be measured.
-}
-
-	\begin{figure}[h]
-		\centering
-		\includegraphics[trim = 6cm 7.5cm 8cm 6cm, clip, width=\linewidth]{SFE_PFD.pdf}
-		\caption{Process flow diagram for solid-fluid extraction process}
-		\label{fig: SFE_drawing}
-	\end{figure}
-
 \end{document}

### 2023-03-06 SFE-article/Sections/Model.tex
06.03

@@
 
-		Since the solute is assumed to be a single pseudo-component, there is only one mass balance equation for each phase (Eq.
-s \ref{Model_fluid} and \ref{Model_solid}).
+		Since the solute is assumed to be a single pseudo-component, there is only one mass balance equation for each phase (Eq.s \ref{Model_fluid} and \ref{Model_solid}).
 On the other hand, there is only one heat balance (Eq.
@@
 
-			\subsubsection{Thermodynamic} \label{CH: Thermodynamic}
-			%{\color{blue}The Peng-Robinson equation of state is used to describe the thermodynamics of the fluid phase.
-The thermal properties of the pseudo-homogeneous phase are assumed to vary along the extractor, though always remaining equal to the corresponding mean values between the fluid and solid phase.
-}
-
-			%In the process model, properties of the supercritical fluid such as the density ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$, the specific heat ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$, the thermal conductivity ${\color{orange}k^T}({\color{blue}T}(t,z),{\color{red}P}(t))$, or the viscosity ${\color{orange}\eta}({\color{blue}T}(t,z),{\color{red}P}(t))$ are calculated based on the local temperatures along the fixed bed and the pressure.
-The Peng-Robinson equation of state is used to find values of a ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$ and ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$.
-
-			At standard atmospheric pressure and temperature, the $CO_2$ behaves as an ideal gas, and its compressibility factor equals to unity.
-However, at high temperature and pressure, the compressibility factor varies from unity, due to real gas effects.
-In order to predict this real gas effects, the Peng-Robinson equation of state (P-R EOS) is used to compute properties of $CO_2$.
-As the density is obtained from the continuity equation,store the P-R EOS can used to evaluate: compressibility, density and specific heat.
-The properties of the $CO_2$ computed as a function of operating conditions (temperature and pressure) are presented on fig.
-\ref{fig: SFE_Properties}
-
-			\begin{figure*}[h!]
-				\begin{subfigure}[b]{\textwidth}
-					\centering
-					\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
-					\caption{The compressibility factor based on the Peng-Robinson equation of state}
-				\end{subfigure}
-				\hfill
-				\begin{subfigure}[b]{\textwidth}
-					\centering
-					\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/RHO.pdf}	
-					\caption{The fluid density based on the Peng-Robinson equation of state}
-				\end{subfigure}
-				\hfill
-				\begin{subfigure}[b]{\textwidth}
-					\centering
-					\includegraphics[trim = 2.9cm 7cm 3.cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
-					\caption{The specific heat of the $CO_2$ based on the Peng-Robinson equation of state}
-				\end{subfigure}
-				\caption{Properties of $CO_2$ based on the equation of state}
-				\label{fig: SFE_Properties}
-			\end{figure*}
-
-			\subsubsection{Dependencies} \label{CH: Dependencies}
-			%The inter-particle diffusion coefficient ${\color{orange}D^M_e}(\allowbreak{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is calculated from the empirical correlation, as the function of the Reynolds number ${\color{orange}R_e}({\color{blue}T}(t,z),{\color{red}P}(t),\allowbreak{\color{red}F}(t))$ and the Peclet's number ${\color{orange}P_e}({\color{blue}T}(t,z),\allowbreak{\color{red}P}(t),{\color{red}F}(t))$.
-			%The values of the internal diffusion ${\color{orange}D_i} ({\color{blue}T}(t,z))$ and the partition coefficient ${\color{orange}k_m} ({\color{blue}T}(t,z))$ come from the laboratory experiments.
-The expressions and the detailed information of the parameter fitting can be found in the appendix.
-
-			TODO:
-
-			\begin{enumerate}
-				\item Viscosity
-				\item Thermal conductivity
-				\item Internal diffusion
-				\item Partition factor
-			\end{enumerate}
-
 			\subsubsection{State-space representation} \label{CH: State_space}

### 2023-03-06 SFE-article/Sections/Model_2.tex
06.03

@@
 \begin{document}
+
+    {\color{blue}The solid-fluid extraction process is assumed to operate in a semi-continuous mode in a cylindrical vessel.
+In the extractor, essential oils are removed from biomass (for example, carqueja seeds) by supercritical carbon dioxide.
+As the solvent flows continuously through the bed of porous particles, the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles.
+Then the solute dissolves and diffuses into the solvent in the pores and eventually into the bulk.
+The solvent-solute mixture leaves the extractor and undergoes depressurization.
+The $CO_2$ is released to a gaseous state, and the solute precipitates.
+In the vapour-liquid separator, the gaseous solvent is vent off while the precipitated product is collected.
+
+		In Figure \ref{fig: SFE_drawing}, an instrumental set-up is presented.
+The flow rate ($F_{in}$) and the temperature ($T_{in}$) of the solvent entering the extractor are measured and can be adjusted using a pump and a heat exchanger, respectively.
+Moreover, the extractor's pressure ($P$) is assumed to be measurable and adjustable using a back-pressure regulator valve.
+In addition, the temperature of the outlet stream $T_{out}$ and the temperature profile of the fixed-bed can be measured.
+}
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[trim = 6cm 7.5cm 8cm 6cm, clip, width=\linewidth]{SFE_PFD.pdf}
+		\caption{Process flow diagram for solid-fluid extraction process}
+		\label{fig: SFE_drawing}
+	\end{figure}
 

### 2023-03-06 SFE-article/Sections/Thermo.tex
06.03

\documentclass[../Parameter_fitting.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

    The properties of a fluid can be divided into two kinds, equilibrium properties and transport properties. The equation of state can be used accurately to predict the equilibrium properties, such as density, enthalpy, vapor pressure, fugacity and fugacity coefficient, vapor liquid equilibrium, and all kinds of excess properties.

    Carbon dioxide above its critical point attains a supercritical state and exhibits certain peculiar properties such as higher density as a liquid but with a lower viscosity comparable to a gas. The supercritical carbon dioxide (S-CO2) has a range of engineering applications.

    The thermodynamic properties of S-CO2 such as density, local speed of sound and specific heat capacity vary significantly for slight change in temperature and pressure due to real gas effects. Equation of state (EOS) which account these real gas effects is used to calculate the thermodynamic properties. In order to predict this real gas effects, the Peng-Robinson equation of state (P-R EOS) is used to compute properties of $CO_2$. The P-R EOS belongs to the specific class of thermodynamic models for modelling the pressure of a gas as a function of temperature and density and can be written as a cubic function of the molar volume (of the density). The P-R EOS is presented by equation \ref{EQ: PR}

    {\footnotesize
        \begin{equation}
            P = \cfrac{RT}{V_m - b} - \cfrac{a\alpha}{V_m^2 + 2bV_m - b^2}
            \label{EQ: PR}
        \end{equation}
    }

    where $a, b, \alpha$ are parameters defined as presented in the appendix.

    The properties of the $CO_2$ presented as a function of operating conditions (temperature and pressure) are presented on fig. \ref{fig: SFE_Properties}

    At standard atmospheric pressure and temperature, the $CO_2$ behaves as an ideal gas, and its compressibility factor equals to unity.  However, at high temperature and pressure, the compressibility factor varies from unity, due to real gas effects. As it is presented on Figure \ref{fig: SFE_Properties_Compressibility}, the compressibility factor obtained from the Peng-Robinson equation of state varies strongly depending on the operating conditions. The compressibility factor can be obtained by given temperature and pressure by solving the polynomial form of the P-R EOS given by equation \ref{EQ: PR_polynomial}.

    {\footnotesize
    \begin{equation}
        Z^3 - (1-B)Z^2+(A-2B-3B^2)Z -(AB-B^2-B^3) = 0
        \label{EQ: PR_polynomial}
    \end{equation}
    }

    where $A$ and $B$ are parameters as defined in the appendix. The roots of the polynomial can be found iteratively or by Cardano formula. Depends on the operating conditions, one or two roots can be found. In one-phase region the fluid can be describe as gas, liquid or super-critical. In the two-phase region the gas-liquid mixture is present. The biggest root is assigned to the gas phase and smallest root corresponds to the liquid phase.

    The real gas effects are also visible on the density plot presented on the Figure \ref{fig: SFE_Properties_Density}. The density can change significantly depends on the operating conditions. 
    By analysing the compressibility and density plots more it can be noticed that very near to the critical point, the fluid can neither be called a liquid nor a gas and has a unique combination of gas-like and liquid-like properties.

    The Figure \ref{fig: SFE_Properties_CP} show behaviour of the heat capacity of a supercritical fluid at constant pressure ($C_p$). The details of the calculations can be found in the appendix. In contrary to the density which varies monotonically, the specific heat shows very high levels in a narrow region. In the subcritical region, the phase transition is associated with an effective spike in the heat capacity (i.e., the latent heat). Approaching the critical point, the latent heat falls to zero but this is accompanied by a gradual rise in heat capacity in the pure phases near phase transition. At the critical point, the latent heat is zero but the heat capacity shows a diverging singularity. Beyond the critical point, there is no divergence, but rather a smooth peak in the heat capacity; the highest point of this peak identifies the Widom line. (ref: 10.1038/nphys1683, 10.3311/PPch.12871)

    In order to calculate thermodynamic properties from a real gas, the departure function for that property with respect to the chosen equation of state has to be evaluated. The departure function for any thermodynamic property of a real gas is defined as the difference in the value of that property determined from the chosen real gas equation of state and the value of the same property for an ideal gas under the same conditions of temperature and pressure. (0.1007/s10494-017-9872-4)

	%{\color{blue}The Peng-Robinson equation of state is used to describe the thermodynamics of the fluid phase. The thermal properties of the pseudo-homogeneous phase are assumed to vary along the extractor, though always remaining equal to the corresponding mean values between the fluid and solid phase. }

	%In the process model, properties of the supercritical fluid such as the density ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$, the specific heat ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$, the thermal conductivity ${\color{orange}k^T}({\color{blue}T}(t,z),{\color{red}P}(t))$, or the viscosity ${\color{orange}\eta}({\color{blue}T}(t,z),{\color{red}P}(t))$ are calculated based on the local temperatures along the fixed bed and the pressure. The Peng-Robinson equation of state is used to find values of a ${\color{orange}\rho} ({\color{blue}T}(t,z),{\color{red}P}(t))$ and ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$.

		\begin{figure*}[h!]
			\begin{subfigure}[b]{\textwidth}
				\centering
				\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
				\caption{The compressibility factor based on the Peng-Robinson equation of state}
                \label{fig: SFE_Properties_Compressibility}
			\end{subfigure}
			\hfill
			\begin{subfigure}[b]{\textwidth}
				\centering
				\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/RHO.pdf}	
				\caption{The fluid density based on the Peng-Robinson equation of state}
                \label{fig: SFE_Properties_Density}
			\end{subfigure}
			\hfill
			\begin{subfigure}[b]{\textwidth}
				\centering
				\includegraphics[trim = 2.9cm 7cm 3.cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
				\caption{The specific heat of the $CO_2$ based on the Peng-Robinson equation of state}
                \label{fig: SFE_Properties_CP}
			\end{subfigure}
			\caption{Properties of $CO_2$ based on the equation of state}
			\label{fig: SFE_Properties}
		\end{figure*}

        On the other hand, transport properties (viscosity and conductivity) are also important quantities required in engineering design for production, fluid transportation, and processing. According to (10.1007/BF00500714), there is no satisfactory theory of transport properties of real dense gases and liquids. The main difficulties in the study of transport properties are twofold: one is the inherent difficulties involved in accurate measurements, and the other is the complexity involved in theoretical treatments. Therefore, the generally used correlations of transport coefficient are either empirical or based on some theoretical foundation. Enskog (REF) developed a popular theory for the transport properties of dense gas based on the distribution function. However, the Enskog theory was proposed for rigid spherical molecules. For real gases, some modification is needed. Following the Enskog theory, many correlations have been proposed in the form of the reduced density and reduced temperature. The correlations of (10.1063/1.556013) and (10.1063/1.4977429) implemented and compared as presented on Figure \ref{fig: SFE_Properties_mu}. Eventually the NIST correlation was selected to be used. The viscosity formulation proposed by NIST consists of four contributions: (i) for the limit of zero density, (ii) for the initial density dependence, (iii) for the residual viscosity, and (iv) for the singularity of the viscosity at the critical point. The NIST correlation covers temperatures from 100 to 2000 $K$ for gaseous $CO_2$ and from 220 to 700 $K$ with pressures along the melting line up to 8000 $MPa$ for compressed and supercritical liquid states.

		%The inter-particle diffusion coefficient ${\color{orange}D^M_e}(\allowbreak{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is calculated from the empirical correlation, as the function of the Reynolds number ${\color{orange}R_e}({\color{blue}T}(t,z),{\color{red}P}(t),\allowbreak{\color{red}F}(t))$ and the Peclet's number ${\color{orange}P_e}({\color{blue}T}(t,z),\allowbreak{\color{red}P}(t),{\color{red}F}(t))$.
		%The values of the internal diffusion ${\color{orange}D_i} ({\color{blue}T}(t,z))$ and the partition coefficient ${\color{orange}k_m} ({\color{blue}T}(t,z))$ come from the laboratory experiments. The expressions and the detailed information of the parameter fitting can be found in the appendix.

        \begin{figure*}[h!]
			\centering
			\includegraphics[trim = 1.5cm 4.0cm 1.5cm 10.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
			\caption{Viscosity obtained based on different correlations}
            \label{fig: SFE_Properties_mu}
		\end{figure*}

        Similarly, several correlations for thermal conductivity of $CO_2$ were compared on Figure
        \ref{fig: SFE_Properties_kt}. The presented figures are focused around critical point, where the singularity is present. Similarities between specific heat and the thermal conductivity can be observed. Eventually, the NIST correlation were selected. The correlations are applicable for the temperature range from the triple point to 1100 $K$ and pressures up to 200 $MPa$.

        \begin{figure*}[h!]
			\centering
			\includegraphics[trim = 1.5cm 2.5cm 1.5cm 2.0cm,clip,width=\textwidth]{Figures/KT.pdf}	
			\caption{Thermal conductivity obtained based on different correlations}
            \label{fig: SFE_Properties_kt}
		\end{figure*}

\end{document}

### 2023-03-08 SFE-article/Sections/Low_mach_number_expansion.tex
08.03

@@
-\documentclass[../Parameter_fitting.tex]{subfiles}
+\documentclass[../Article_Model_Parameters.tex]{subfiles}
 \graphicspath{{\subfix{../Figures/}}}
@@
 
+		A general formulation the internal energy for a real gas is:
+
+	{\footnotesize
+		\begin{equation*}
+			de=C_vdT-\left[P-T\left(\cfrac{\partial P}{\partial T}\right)_{v_m}\right]dv_m
+	\end{equation*} }
+
+	where $v_m$ is the molar volume.
+
+	The internal energy is a function of two intensive properties, in this case $T$ and $V$.
+But, in the case of an ideal gas, the equation of state is such that the second term in this equation is identically equal to zero.
+So the ideal gas is a special case in which the molar internal energy is a function only of temperature.
+For Peng-Robinson equation of state, the internal energy is defined as
+
+	{\footnotesize
+	\begin{equation*}
+		e = C_vT + \cfrac{a\left(\alpha -T\cfrac{d \alpha}{dT}\right)}{2\sqrt{2}b} \ln \left[ \cfrac{1+b\left(1-\sqrt{2}\rho\right) }{1+b\left(1+\sqrt{2}\rho\right)} \right]
+	\end{equation*} }
+
+	Assuming constant temperature and pressure along space and in time:
+
+	{\footnotesize
+		\begin{equation*}
+			\lim_{\Delta T, \Delta P \rightarrow 0_+ } \rho A_f \left( \cfrac{\partial e }{\partial t} + V \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0 \rightarrow \cfrac{\partial A_f V}{\partial z} = 0
+		\end{equation*}
+	}
+
+	It can be deduce that the continuity equation becomes $\frac{\partial \rho_f}{\partial t} = 0$ at constant temperature and pressure.
+Moreover, the incompressibility condition $div(A_fV)=0$ is obtained.
+
+	Assuming an arbitrary function $\hat{P}$, which describe the total pressure, the dimensional momentum equation can be written as
+
+	{\footnotesize
+		\begin{equation*}
+			V \underbrace{ \left( \cfrac{\partial \rho_f A_f}{\partial t} + \cfrac{\rho_f V A_f}{\partial z} \right) }_{Continuity~equation} + \rho_f A_f \cfrac{\partial V}{\partial t} + \rho_f V A_f \cfrac{\partial V}{\partial z} = - A_f \cfrac{\partial \hat{P}}{\partial z}
+		\end{equation*}
+	}
+
+	From the incompressibility conditions we can deduce that
+
+	{\footnotesize
+		\begin{equation*}
+			\cfrac{\partial A_f V}{\partial z} = 0 \rightarrow A_f \cfrac{\partial V}{\partial z} = - V \cfrac{\partial A_f}{\partial z}
+		\end{equation*}
+	}
+
+	By combining both above equations, assuming that $\partial V / \partial t = 0$:
+
+	{\footnotesize
+		\begin{equation*}
+			\cfrac{\rho_f V^2}{A_f} \cfrac{\partial A_f}{\partial z} = \cfrac{\partial \hat{P}}{\partial z} \rightarrow \int	\cfrac{\rho_f V^2}{A_f} \cfrac{\partial A_f}{\partial z} dz = \int \cfrac{\partial\hat{P}}{\partial z} dz
+		\end{equation*}
+	}
+
+	The l.h.s integral can be solved by assuming $\rho_f$ is constant and introducing $u=A_f V$
+
+	{\footnotesize
+		\begin{align*}
+			& \int	\cfrac{\rho_f V^2}{A_f} \cfrac{\partial A_f}{\partial z} dz = \int	\cfrac{\rho_f V^2}{A_f} \cfrac{A_f^2}{A_f^2} \cfrac{\partial A_f}{\partial z} dz \\
+			&= \rho_f u^2  \int \cfrac{1}{A_f^3} \cfrac{\partial A_f}{\partial z} dz = - \cfrac{\rho_f u^2}{2 \Delta A_f^2} = - \cfrac{\rho_f \Delta V^2}{2} \\
+			& \int \cfrac{\partial \hat{P}}{\partial z} dz = \Delta \hat{P}
+		\end{align*}
+	}
+
+	The final form of the momentum equation corresponds to the Bernoulli's principle
+
+	{\footnotesize
+		\begin{equation*}
+			\Delta \hat{P} = - \cfrac{\rho_f \Delta V^2}{2} \xrightarrow[]{P_0 = \text{const}} \Delta M_a^2 P_1 = - \cfrac{\rho_f \Delta V^2}{2}
+		\end{equation*}
+	}
+
+	The Bernoulli's principle can be used to find the hydrodynamic pressure caused by varying cross-section at steady-state.
+Moreover, if the flow velocity is relatively low and so all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic.
+The effect of this is that $\partial \rho / \partial p = 0$.
+In other words, the small changes in pressure due to flow velocity changes do not change the density.
+This has a secondary effect -- the speed of sound in the fluid is $\partial p/\partial \rho = \infty$	in this instance.
+So there is an infinite speed of sound, which makes the equations elliptic in nature.
+It can be deduced that at the isothermal conditions the density in the system propagates with the same speed as pressure due to the fact that they are both connected through the equation of state.
+
 \end{document}

### 2023-03-08 SFE-article/Sections/Model.tex
08.03

@@
-\documentclass[../Parameter_fitting.tex]{subfiles}
+\documentclass[../Article_Model_Parameters.tex]{subfiles}
 \graphicspath{{\subfix{../Figures/}}}
 \begin{document}
-
-	\sout{The main components of the model are three one-dimensional differential equations related to mass balances (solid and fluid phase) and heat balance.
-As in all batch processes, our system has only one steady state.
-The steady-state occurs only if the solute is entirely taken out of the biomass.
-
-		The extraction from a fixed bed is an unsteady process, implying that the solute concentrations in the solid and solvent phases vary over time and space.
-The convection and the diffusion of the mass and the heat are considered only in the axial direction.
-The radial distribution of such properties like a velocity is assumed to be flat in that direction.
-The assumption of the flat velocity profile allows considering a lack of back mixing.
-The pressure drop in the bed is assumed to be assumed to negligible.
-Under such conditions, the fluid flow can be considered a plug flow.
-
-		Since the solute is assumed to be a single pseudo-component, there is only one mass balance equation for each phase (Eq.s \ref{Model_fluid} and \ref{Model_solid}).
-On the other hand, there is only one heat balance (Eq.
-\ref{Model_heat}) because the presence of a single pseudo-phase is assumed.
-
-		Moreover, the process model does not consider the change of particle size or the void fraction during the process.
-The particles are assumed to be uniformly distributed along the bed and to have the same size.}
 
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f \varepsilon (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f u \right)}{\partial z} = 0
+			\cfrac{\partial \left( \rho_f A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_f v A_f \right)}{\partial z} = 0
 			\label{EQ: Continuity}
@@
 
-	where $u$ is the superficial velocity, $\varepsilon$ is the bed porosity and $\rho_f$ is the fluid density.
+	Considering the mass flow-rate which is constant in time, the temporal derivative become zero and the spacial derivative can be integrated along $z$.
+
+	{\footnotesize
+		\begin{equation*}
+			\int \cfrac{\partial \left( \rho_f v A_f \right)}{\partial z} dz = 0 \rightarrow F=\rho_f v A_f
+		\end{equation*}
+	}
+
+	where $F$ is a constant obtained from the integration.
+The constant $F$ can be understood as the mass flux per unit area which is assumed to be constant along $z$.
+$F$ can treated as a control variable, which can change in time but it is constant in space.
+Such a assumption allows to find the velocity profile which satisfy the mass continuity based on $F, A_f$ and $\rho_f$.
+The fluid density $\rho_f$ density is connected through equation of state with thermodynamical pressure, which is assumed to be constant along $z$ (due to the low-Mach number) and temperature.
+The variation in density might be caused by the accumulation of the fluid in the system (which happen instantaneously along $z$) or by temperature change.
+To simplify the dynamic of the system, it is assumed that $F=F(t)$ is a control variable and affects the whole system instantaneously.
 
@@
 				%	\includegraphics[trim  = 6cm 0cm 3cm 0cm,clip,width=\linewidth]{Figures/SFE_draft.png}
-				\includegraphics[trim = 5.8cm 1.1cm 6cm 0.8cm,clip,width=1.0\linewidth]{Figures/SFE_draft.pdf}	
+				\includegraphics[trim = 5.8cm 1.1cm 6cm 0.8cm,clip,width=\columnwidth]{Figures/SFE_draft.pdf}	
 				\caption{The extraction mechanism}

### 2023-03-08 SFE - EmptySpace/Plot_Fit.m

@@ -51,9 +51,9 @@
     ylabel('Superficial velocity [m/s]','Interpreter','latex')
     xlabel('Time [min]','Interpreter','latex')
 
-    subtitle([DATA,'_',mat2str(round([DATA_K_OUT(:,ii)],5))],'Interpreter','latex')
+    subtitle([DATA,'_',mat2str(round([DATA_K_OUT(:,ii)],3))],'Interpreter','latex')
 
-    set(gcf,'PaperOrientation','landscape'); print(figure(ii),['Yield_',DATA,'_F',mat2str(V_Flow),'.pdf'],'-dpdf','-bestfit'); close all
+    set(gcf,'PaperOrientation','landscape'); print(figure(ii),['Yield_',DATA,'_F',mat2str(V_Flow),'_No_Delay.pdf'],'-dpdf','-bestfit'); close all
 
     %%
 %{

### 2023-03-08 SFE - EmptySpace/main_Opt_EmptySpace.m

@@ -11,7 +11,7 @@ import casadi.*
 DATA_set                = {'LUKE_T40_P200','LUKE_T50_P200','LUKE_T40_P300','LUKE_T50_P300'};
 Parameters_table        = readtable('Parameters.csv') ;        % Table with prameters
 
-DATA_K_OUT=nan(4,4);                                           % Store Parameters obatined from all fits (par num x num exper)
+DATA_K_OUT=nan(5,4);                                           % Store Parameters obatined from all fits (par num x num exper)
 
 %% Set time of the simulation
 PreparationTime         = 0;
@@ -99,28 +99,29 @@ m0fluid(nstagesbefore) = C0fluid * V_before / numel(nstagesbefore);
 m0fluid(nstagesbed)    = C0fluid * (V_bed * (1 - epsi)) / numel(nstagesbed);
 m0fluid(nstagesafter)  = C0fluid * V_after / numel(nstagesafter);
 
+%%
+Nx                      = 4*nstages+1;
+Nu                      = 3 + numel( Parameters_table{:,3} );
+Nk                      = numel(which_k)+1;
+
+%% symbolic variables
+% Create symbolic variables
+x                       = MX.sym('x', Nx);
+u                       = MX.sym('u', Nu);
+
+%% Set Integrator
+f                       = @(x, u) modelSFE_uniform_U(x, u, bed_mask);
+
+% Integrator
+F                       = buildIntegrator(f, [Nx,Nu] , timeStep_in_sec);
+
+V_Flow     = 0.41;
+
 parfor ii=1:numel(DATA_set)
-    
-    %%
-    Nx                      = 4*nstages+1;
-    Nu                      = 3 + numel( Parameters_table{:,3} );
-    Nk                      = numel(which_k)+0;
-    
-    %% symbolic variables
-    % Create symbolic variables
-    x                       = MX.sym('x', Nx);
-    u                       = MX.sym('u', Nu);
-    
-    %% Set Integrator
-    f                       = @(x, u) modelSFE_uniform_U(x, u, bed_mask);
-    
-    % Integrator
[…]

### 2023-03-08 SFE-article/Article_Model_Parameters.tex
08.03

@@
 We apply the concept of quasi-one-dimensional flow to mimic the modelling of a two-dimensional case.
-The collected dataset, obtained from the extraction of caraway seeds at different operating conditions, is used to estimate unknown parameters.
-The model-based parameter estimation applies the maximum likelihood method to estimate values of the extraction kinetic parameters such as mass partition factor, internal diffusion coefficient and radial diffusion.
+In this work, a distributed-parameter model, based on \citet{Reverchon1996} is used to describe a fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent.
+The model parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient and saturation concentration are obtained from parameter estimation.
+The parameters are estimated based on four experiments performed at $40^\circ C$ and $50^\circ C$ at $200$ bar and $300$ bar.
+The model-based parameter estimation uses the maximum likelihood estimation under assumption of normal error given for yield data.
 
@@
 \section{Introduction}
-%\subfile{Sections/introduction}
+\subfile{Sections/introduction}
 
-%\section{Materials and methods} \label{CH: Materials and methods}
+\section{Materials and methods} \label{CH: Materials and methods}
 
-\section{$CO_2$ properties} \label{CH: Thermodynamic}
-%\subfile{Sections/Thermo}
+\subsection{Supercritical fluids} \label{CH: Thermodynamic}
+\subfile{Sections/Thermo}
 
-\clearpage
+%\clearpage
 %\subfile{Sections/Materials_and_methods}
@@
 {\footnotesize
-\begin{equation}
 \begin{align}
@@
     \end{align}  
-\end{equation}
 \label{EQ: CompressibleEuler}
@@
 \subsection{Extraction model} \label{CH: Extraction_model}
-%\subfile{Sections/Model}
+\subfile{Sections/Model}
 
@@
 \subsection{Parameter estimation} \label{CH: Parameter_estimation}
-%\subfile{Sections/Parameter_estimation}
+\subfile{Sections/Parameter_estimation}
 
@@
 \subsection{Governing equations}
-%\subfile{Sections/Gouverning_equation_derivation}
+\subfile{Sections/Gouverning_equation_derivation}
 
 \subsection{Bayes theorem} \label{CH: Bayes}
-%\subfile{Sections/Bayes_Theorem}
+\subfile{Sections/Bayes_Theorem}
 

### 2023-03-08 SFE-article/Sections/Model.tex
08.03

@@
 As a result, the plug flow model can be introduced.
-The particle size distribution and the void fraction of the solid phase are assumed to be uniform in space and remain constant in time.
-Moreover, the pressure is considered to be constant along the fixed bed.
+The particle size distribution and the void fraction of the solid phase cab change along an extractor but they remain constant in time.
+Moreover, the thermodynamic pressure is considered to be constant along the device, as discussed above.
 The mass balance for the fluid phase consists of convection, diffusion, and kinetic terms.
@@
 
+    }
+
+    {\color{red}
 	The heat balance (Eq.
@@
 We consider no heat loss through the wall, and there is no heat generation in the system.
-Therefore, the temperature of the extractor can be changed only by manipulating the temperature of the inlet stream $T_{In}(t)$.
+Therefore, the temperature of the extractor can be changed only by manipulating the temperature of the inlet stream %$T_{In}(t)$.
 
@@
 	\subsubsection{Mass balance for the fluid phase} \label{CH: Mass_balance_fluid}
-	The fluid phase is a mobile phase, which means that the fluids mass balance (Eq. \ref{Model_fluid}) is made of convection, diffusion, and mass transfer kinetic terms.
+	The detail derivation of the mass balance equation for the fluid phase can be found in the appendix ({\color{red}REF}).
+The fluid phase is a mobile phase, which means that the fluids mass balance (Eq.
+\ref{Model_fluid}) is made of convection, diffusion, and mass transfer kinetic terms.
 
@@
 ${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term.
-${\color{red}F}(t)$ is the mass flow rate, ${\color{red}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{magenta}A}$ is the extractor’s cross section, ${\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient.
+${\color{red}F}(t)$ is the mass flow rate, ${\color{red}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient and $u$ is the superficial velocity.
 
@@
 	\subsubsection{Kinetic term} \label{CH: Kinetic}
-			As the solvent flows through the bed, \sout{it forms a film around the porous solid particle and occupies its pores.} {\color{blue}the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to for an external fluid film around the solid particles through the solvent–solid matrix interactions.
-Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected.
-In this work, the molecular diffusion is assumed.}.
+	As the solvent flows through the bed, {\color{blue}the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to for an external fluid film around the solid particles through the solvent–solid matrix interactions.
+Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected}.
 The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
@@
 
-			\sout{The kinetic term, denoted as equation \ref{Model_kinetic_basic}, corresponds to a solute transfer rate between both phases.
-This term is made of the overall diffusion coefficient and the concentration gradient (between one phase and its equilibrium concentration), which acts as a driving force for the process.} {\color{blue}The mass transfer kinetic (Eq.
+		{\color{blue}The mass transfer kinetic (Eq.
 \ref{Model_kinetic_basic}) describes a diffusion rate of the solute from solid particles to the solvent.
@@
 
-			Equation \ref{Model_kinetic} is the full representation of the kinetic term.
+			Equation \ref{Model_kinetic_no_sat} is the full representation of the kinetic term.
+
+			{\footnotesize
+				\begin{align}
+					\label{Model_kinetic_no_sat}
+					{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}q}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c}(t,z) \right)
+			\end{align} }
+
+        The above model does not take into account the saturation of fluid, which can be introduced by multiplying the gradient by a function $\Gamma(c_f)$ (equation \ref{EQ: C_sat_function}).
+$\Gamma(c_f)$ describe the reverse logistic function, which is equal to unity below the $c_{sat}$, the saturation concentration, and equal to zero, above the $c_{sat}$.
+
+        {\footnotesize
+            \begin{equation}
+                \Gamma(c_f) = \cfrac{1}{1+\exp ( -k_{sat} \left( c_f - c_{sat} \right) ) }
+                \label{EQ: C_sat_function}
+            \end{equation}
+        }
+
+        where $k_{sat}$ is the growth rate, and it is defined as $k_{sat} = 2c_{sat}$.
+
+        The final form of the extraction kinetic equation is given by equation \ref{Model_kinetic}
 
@@
 				\label{Model_kinetic}
-					{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}q}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c}(t,z) \right)
+				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} } \Gamma(c_f) \left({\color{blue}q}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c}(t,z) \right)
 		\end{align} }
@@
 
+        {\color{blue} The heat equation was introduced in the previous chapter.
+The heat balance describe movement of the internal energy in the system.
+For real gases it is complicated to write the heat balance in terms of temperature.
+Alternatively, the temperature can be obtained based on the equation of state if the internal energy and pressure are know.
+A roootfinder can be used to find a value of temperature, which satisfy the equation of state given values of internal energy and pressure.
+The temperature needs to be reconstructed from the internal energy in every time-step.
+		}
+
 		\subsubsection{Extraction yield} \label{CH: Yield}
 
-			The efficiency of the process (the yield) is calculated according to one of Eq.
-\ref{Model_measurment}, which evaluates the mass of solute at the exit of the extraction unit and sums it.
+		The efficiency of the process (the yield) is calculated according to equations \ref{Model_measurment_1} to \ref{Model_measurment_2}, which evaluate the mass of solute at the exit of the extraction unit and sums it.
 The integral form of the measurement equation can be transformed into the differential form, and augmented with model equations to be solved simultaneously.
@@
 			\begin{align} 
-					\label{Model_measurment}
+				\label{Model_measurment_1}
 				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
@@
 				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= \cfrac{F(t)}{\rho(t,z)} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]
+                \label{Model_measurment_2}
 		\end{align}	}

### 2023-03-08 SFE-article/Sections/Thermo.tex
08.03

@@
-\documentclass[../Parameter_fitting.tex]{subfiles}
+\documentclass[../Article_Model_Parameters.tex]{subfiles}
 \graphicspath{{\subfix{../Figures/}}}
 \begin{document}
+
+    A supercritical fluid (SCF) is any substance at a temperature and pressure above its critical point, where distinct liquid and gas phases do not exist, but below the pressure required to compress it into a solid.
+It can effuse through porous solids like a gas, overcoming the mass transfer limitations that slow liquid transport through such materials.
+SCF are much superior to gases in their ability to dissolve materials like liquids or solids.
+Also, near the critical point, small changes in pressure or temperature result in large changes in density, allowing many properties of a supercritical fluid to be "fine-tuned".
+By changing the pressure and temperature of the fluid, the properties can be "tuned" to be more liquid-like or more gas-like.
 
@@
 
-		\begin{figure*}[h!]
-			\begin{subfigure}[b]{\textwidth}
+		\begin{figure*}[H]
+			\begin{subfigure}[b]{0.95\textwidth}
 				\centering
@@
 			\hfill
-			\begin{subfigure}[b]{\textwidth}
+			\begin{subfigure}[b]{0.95\textwidth}
 				\centering
@@
 
-        \begin{figure*}[h!]
+        \begin{figure*}[H]
 			\centering
-			\includegraphics[trim = 1.5cm 4.0cm 1.5cm 10.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
+			\includegraphics[trim = 1.5cm 4.0cm 2.5cm 10.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
 			\caption{Viscosity obtained based on different correlations}
@@
 
-        \begin{figure*}[h!]
+        \begin{figure*}[H]
 			\centering
-			\includegraphics[trim = 1.5cm 2.5cm 1.5cm 2.0cm,clip,width=\textwidth]{Figures/KT.pdf}	
+			\includegraphics[trim = 1.5cm 2.5cm 1.5cm 2.0cm,clip,width=0.95\textwidth]{Figures/KT.pdf}	
 			\caption{Thermal conductivity obtained based on different correlations}

### 2023-03-08 SFE-article/Sections/introduction.tex
08.03

@@
 	The extraction of natural substances from solid materials and liquids with solvents have been a popular subject of research and development in the last years.
-Supercritical fluids have multiple applications in an extraction process due to the pressure-dependent dissolving power and {\color{blue} both gas-and liquid-like properties (for example fluid-like density and gas-like diffusivity).
+Supercritical fluids have multiple applications in an extraction process due to the pressure-dependent dissolving power and both gas-and liquid-like properties (for example fluid-like density and gas-like diffusivity).
 Among different supercritical fluids, the supercritical $CO_2$ is one of the most popular due to it is nontoxic, non-flammable and non-corrosive properties.
 The critical point of $CO_2$ is relatively low ($73.8$ bar and $31 ^\circ C$), compare to other fluids.
-The supercritical extraction with $CO_2$ become attractive alternative, to replace traditional extraction techniques.}
+The supercritical extraction with $CO_2$ become attractive alternative, to replace traditional extraction techniques.
 
 	%{\color{brown} Literature review of the models}\\
-	\sout{The supercritical extraction process is considered unconventional due to the lack of formulation of one general model, properties that strongly depend on working conditions and its unsteady nature.
-Understanding the physics behind the phenomena and the proper mathematical description is necessary to predict the process outcome.
-Several extraction models have been developed to characterize different mass transfer mechanisms and equilibrium relationships.}
-	{\color{blue}The extraction of valuable compounds from fixed bed of biomass can be described by one of many mathematical models as presented by \citet{Huang2012}.
+	The extraction of valuable compounds from fixed bed of biomass can be described by one of many mathematical models as presented by \citet{Huang2012}.
 The selection the extraction model is not arbitrary and should be based on the knowledge of phenomenons occurring in the operational unit.
-Each model has its own assumptions and describe different mass transfer mechanisms and equilibrium relationships}.
+Each model has its own assumptions and describe different mass transfer mechanisms and equilibrium relationships.
+
+	Based on analogy to heat transfer, \citet{Reverchon1993} suggested a hot ball model, where the extraction process is treated analogously to a process in which a hot ball is cooled in a uniform medium.
+The hot ball model is used to describe an extraction process from solid particles which contains small quantities of solute so that the solubility is not a limiting factor.
+
+	\citet{Sovova1994} presented the Broken-and-Intact Cell model.
+The BIC model describes a system where the outer surfaces of particles have been mechanically interrupted.
+The solute from the broken cells is easily accessible for the solvent.
+The extraction of easily accessible solute is fast and directly controlled by its diffusion and convection in the solvent.
+However, the rest of the solute is less accessible because it is closed in the particle's core or intact cells.
+This solute slowly diffuses through the walls of a cell due to high mass transfer resistance.
 
@@
 
-	Based on analogy to heat transfer, \citet{Reverchon1993} suggested a hot ball model, where the extraction process is treated analogously to {\color{blue} a process in which a hot ball is cooled in a uniform medium} \sout{the process of cooling down a hot ball in a uniform medium}.
-{\color{blue}The hot ball model is used to describe an extraction process from solid particles which contains small quantities of solute so that the solubility is not a limiting factor.
-}
+    \iffalse
 
-	\citet{Sovova1994} \sout{presented the Broken-and-Intact Cell model, which assumes the presence of two solid phases, the broken and intact cells.
-The results of applying Sovova's model allow distinguishing three phases of the extraction process (constant extraction rate, falling extraction rate, and diffusion-controlled periods) directly at the modelling stage.}
-	{\color{blue} presented the Broken-and-Intact Cell model.
-The BIC model describes a system where the outer surfaces of particles have been mechanically interrupted.
-The solute from the broken cells is easily accessible for the solvent.
-The extraction of easily accessible solute is fast and directly controlled by its diffusion and convection in the solvent.
-		However, the rest of the solute is less accessible because it is closed in the particle's core or intact cells.
-This solute slowly diffuses through the walls of a cell due to high mass transfer resistance.
-		In this model, the extraction process is divided into three periods controlled by different mass transfer mechanisms: Constant extraction rate (CER) period, Falling extraction rate (FER) period and Diffusion-controlled (DC) period.}
+    In this model, the extraction process is divided into three periods controlled by different mass transfer mechanisms: Constant extraction rate (CER) period, Falling extraction rate (FER) period and Diffusion-controlled (DC) period.
 
@@
 
-	%{\color{brown} Summary of the manuscript}\\
-	\sout{In this work, the process model represents supercritical extraction and consists of a set partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables.
-The process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.The impact of mass flow rate, pressure, and inlet temperature on the model's output is analyzed.
-In this work, the sensitivity analysis results are used to prove if the considered variables affect the extraction process and can be used as decision variables in optimization problems.
-The novelty is the application of the local sensitivity analysis in the case of supercritical extraction.}
-	{\color{blue}In this work, a distributed-parameter model, based on \citet{Reverchon1996} and \citet{Vargas2006}, is used to describe a fluid-solid extraction process of 'carqueja' oil from 'Baccharis Trimera' leaves with $CO_2$ as a solvent.
-The process model consists of three partial differential equations: two mass balance equations and one heat balance equation.
-To enhance understanding of the process model, the local sensitivity analysis is used to investigate the effect of parameters on the model's output.
-The presented sensitivity analysis results are restricted to parameters related to operating conditions only.
-Furthermore, the sensitivity analysis is used to prove which of the analysed variables can be used as decision variables in optimisation problems.}
+    \fi
+
+	In our model, the extraction process is assumed to operate in a semi-continuous mode in a cylindrical vessel.
+The solvent is firstly brought to super-critical condition, pumped through a fixed-bed, of finely chopped biomass, where the solute is extracted from the biomass.
+Then, the solvent and solute from the extractor are separated in a flush drum, and the extract is collected.
+The flow rate ($F_{in}$) and inlet temperature ($T_{in}$) of the extractor’s feed can be measured and manipulated.
+The pressure ($P$) in the vessel can be measured and manipulated, while the outlet temperature ($T_{out}$) can only be measured.
+A simplified flow diagram is depicted in Figure \ref{fig: SFE_drawing} .
+
+    \begin{figure}[h!]
+        \centering
+        \includegraphics[width=0.95\columnwidth]{SFE-article/Figures/SFE_PFD_cropped.pdf}
+        \caption{Process flow diagram}
+        \label{fig: SFE_drawing}
+    \end{figure}
 

### 2023-03-09 SFE-article/Article_Model_Parameters.tex
09.03

@@
 % ---------------------------------------------------------------
-
+% Make margins bigger to fit annotations. TO be removed later
+\paperwidth=\dimexpr \paperwidth + 6cm\relax
+\oddsidemargin=\dimexpr\oddsidemargin + 3cm\relax
+\evensidemargin=\dimexpr\evensidemargin + 3cm\relax
+%\marginparwidth=\dimexpr \marginparwidth + 3cm\relax
 % -------------------------------------------------------------------- 
@@
 \usepackage{subcaption}
+\usepackage[bordercolor=gray!20,backgroundcolor=blue!10,linecolor=black,textsize=footnotesize,textwidth=1in]{todonotes}
+\setlength{\marginparwidth}{1in}
 % \usepackage[utf8]{inputenc}
@@
 \usepackage{tikz}
+\usepackage{pgfplots}
 \usetikzlibrary{shapes.geometric,angles,quotes,calc}
@@
 Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
-Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process.
+Given a system of partial differential equations, $F(t,x,\dot{x},\Theta,u)=0$, where $x$ represents state variables, $\Theta$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process.
 The process model describes a partially filled extractor with a fixed bed, which work under constant operating conditions.
-We assume that the flow is uniform across any cross-section, although the area available for the fluid phase is a function of distance.
+We assume that the flow is uniform across any cross-section, although the area available for the fluid phase can change along the extractor.
 We apply the concept of quasi-one-dimensional flow to mimic the modelling of a two-dimensional case.
@@
 The parameters are estimated based on four experiments performed at $40^\circ C$ and $50^\circ C$ at $200$ bar and $300$ bar.
-The model-based parameter estimation uses the maximum likelihood estimation under assumption of normal error given for yield data.
+Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
 
@@
 \subsection{Governing equations}
-The detail derivation of the governing equation can be found in the appendix (\ref{CH: Gouverning equations}).
+The detail derivation of the governing equation can be found in the appendix (\ref{CH: Gouverning equations}) as well as in the work of \citet{Anderson1995}.
 Let's assume that any properties of the flow are unifrom across any given cross-section of an channel (or any device like an extractor).
-Such a floww is called quasi-one-dimensional.
+Such a flow is called quasi-one-dimensional.
 The variation of the cross-section might be an result of its irregular shape (or partial filling of an extractor).
 
-The quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates is given be equations \ref{EQ: CompressibleEuler}
+The quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates is given be equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_2}.
 
@@
 \begin{align}
+		\label{EQ: CompressibleEuler_1}
         \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
@@
         \cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T}{\partial z} \right)
+        \label{EQ: CompressibleEuler_2}
     \end{align}  
-\label{EQ: CompressibleEuler}
 }
@@
 where $\rho_f$ is the density of the fluid, $A_f$ is the function which describe change of the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
+
+Based on governing equations, the small discontinuity in flow properties, shown on figure \ref{fig: Discontinuity_slow_flow}, can be analysed. The analysis follow the work of \citet{Schreier1982}.
+
+\begin{figure}[h!]
+	\centering
+	\resizebox{0.95\columnwidth}{!}{%
+	\begin{tikzpicture}[]
+		\draw (0,2) -- (9,2);	% Top line
+		\draw (0,0) -- (9,0); 	% Bottom line
+		\draw (4.5,0) -- (4.5,2); 	% Bottom line
+		\node at (4,1.5) {$\rho$};
+		\node at (5.5,1.5) {$\rho+\delta\rho$};
+		\node at (4,1.0) {$P$};
+		\node at (5.5,1.0) {$P+\delta P$};
+		\node at (4,0.5) {$T$};
+		\node at (5.5,0.5) {$T+\delta T$};
+		\node at (1,1.0) {$v \rightarrow$};
+		\node at (8,1.0) {$v + \delta v \rightarrow$};
+	\end{tikzpicture} }
+	\caption{Small discontinuity in one-dimensional flow}
+	\label{fig: Discontinuity_slow_flow}
+\end{figure}
+
+The discontinuity is presumed to be at rest relative and \todo[]{Fix the notation of pressure perturbation section to be coherent with governing equations}  the balance equations become
+
+{\footnotesize
+	\begin{align*}
+		&\rho \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 \\
+		&\delta P = \delta v \delta \rho_f
+	\end{align*}
+}
+
+These relations are equally valid if the two regions are separated by a regions of finite width rather than a discontinuity.
+
+{\footnotesize
+	\begin{equation*}
+		\lim_{\rho_f v \rightarrow 0} \rho_f \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 / \delta \rho_f \rightarrow \cfrac{d v}{d \rho_f} = - \cfrac{v}{\rho_f}
+	\end{equation*}
+}
+
+By combining momentum equation with above equation we get
+
+{\footnotesize
+	\begin{equation*}
+		\cfrac{d v}{d \rho_f} = - \cfrac{d v}{dP} \cfrac{d P}{d \rho_f} = -\cfrac{1}{\rho v} \cfrac{dP}{d\rho_f} = -\cfrac{v}{\rho_f}
+	\end{equation*}
+}
+
+If the flow is presumed to be isentropic, $dP/d\rho = c^2$, so $V^2=c^2$, where $c$ is the speed of sound.
+This can be interpreted that a small pressure wave propagates with the speed of sound relative to the flow.
 
@@
 \section{Appendix} 
+\subsection{Thermodynamic}
+\subfile{Sections/Thermodynamic_details}
 \subsection{Governing equations}
@@
 
-\subsection{Bayes theorem} \label{CH: Bayes}
-\subfile{Sections/Bayes_Theorem}
+%\subsection{Bayes theorem} \label{CH: Bayes}
+%\subfile{Sections/Bayes_Theorem}
 
+\iffalse
 \newpage
@@
 \end{table*}
+\fi
 \end{document}

### 2023-03-09 SFE-article/Sections/Low_mach_number_expansion.tex
09.03

--- 2023-03-06 SFE-article/Sections/Low_mach_number_expansion.tex
@@
 
-	The equations \ref{EQ: CompressibleEuler} describe the fully compressible equations of motion (respectively the transport of mass, momentum and energy) for quasi-one-dimensional case.
+	The equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_2} describe the fully compressible equations of motion (respectively the transport of mass, momentum and energy) for quasi-one-dimensional case.
 We rescale the time variable, considering finally
@@
 	{\footnotesize
-		\begin{equation*}
-			\rho_\zeta 	= \rho\left( z, t/M_a \right), \quad
-			V_\zeta 	= \cfrac{1}{\zeta} V\left( z, t/M_a \right) \quad
-			T_\zeta 	= T\left( z, t/M_a \right),  \quad 
+		\begin{align*}
+			\rho_\zeta 	&= \rho\left( z, t/M_a \right), \quad
+			v_\zeta 	= \cfrac{1}{\zeta} v\left( z, t/M_a \right) \\ 
+			T_\zeta 	&= T\left( z, t/M_a \right),  \quad 
 			k_\zeta 	= \zeta k(\rho_f, T) 
-		\end{equation*} 
+		\end{align*} 
 	}
@@
 		\begin{align*}
-			\cfrac{\partial \left( \rho_\zeta A_f \right)}{\partial t} &+ \cfrac{\partial \left( \rho_\zeta A_f V_\zeta \right)}{\partial z} = 0 \\
-			\cfrac{\partial \left( \rho_\zeta A_f V_\zeta \right) }{\partial t}	&+ \cfrac{\partial \left( \rho_\zeta V_\zeta A_f V_\zeta \right)}{\partial z} + \cfrac{A_f}{M_a^2} \cfrac{\partial P_\zeta}{\partial z} = 0\\
-			\cfrac{\partial \left( \rho_\zeta e_\zeta A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_\zeta e_\zeta V_\zeta A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_\zeta}{\partial z} \right) + P_\zeta \cfrac{\partial A_f V_\zeta}{\partial z} = 0
+			\cfrac{\partial \left( \rho_\zeta A_f \right)}{\partial t} &+ \cfrac{\partial \left( \rho_\zeta A_f v_\zeta \right)}{\partial z} = 0 \\
+			\cfrac{\partial \left( \rho_\zeta A_f v_\zeta \right) }{\partial t}	&+ \cfrac{\partial \left( \rho_\zeta v_\zeta A_f v_\zeta \right)}{\partial z} + \cfrac{A_f}{M_a^2} \cfrac{\partial P_\zeta}{\partial z} = 0\\
+			\cfrac{\partial \left( \rho_\zeta e_\zeta A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_\zeta e_\zeta v_\zeta A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_\zeta}{\partial z} \right) + P_\zeta \cfrac{\partial A_f v_\zeta}{\partial z} = 0
 		\end{align*}
@@
 			\rho_\zeta 	& = \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \\
-			V_\zeta 	& = V_0		+ V_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
+			v_\zeta 	& = v_0		+ v_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
 			T_\zeta 	& = T_0 	+ T_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
@@
 	 		& \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left( \left( \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \right)}{\partial t} + \\
-	 		&+ \cfrac{\partial \left(  \left(  \rho_0 + \rho_1 \zeta + \mathcal{O}(\zeta^2) \right) A_f \left( V_0	+V_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial z} = 0
+	 		&+ \cfrac{\partial \left(  \left(  \rho_0 + \rho_1 \zeta + \mathcal{O}(\zeta^2) \right) A_f \left( v_0	+v_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial z} = 0
 	 	\end{align*}
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_0 A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_0 A_f V_0 \right)}{\partial z} = 0
+			\cfrac{\partial \left( \rho_0 A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_0 A_f v_0 \right)}{\partial z} = 0
 		\end{equation}
@@
 		\begin{align*}
-		 & \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left(  \left(  \rho_0 + \rho_1 \zeta + \mathcal{O}(\zeta^2) \right) A_f \left( V_0	+V_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial t} + \\
-		 &+ \cfrac{\partial \left(  \left(  \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( V_0	+ V_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \left( V_0	+ V_1 \zeta + \mathcal{O}(\zeta^2) \right) \right) }{\partial z} + \\
+		 & \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left(  \left(  \rho_0 + \rho_1 \zeta + \mathcal{O}(\zeta^2) \right) A_f \left( v_0	+v_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial t} + \\
+		 &+ \cfrac{\partial \left(  \left(  \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( v_0	+ v_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \left( v_0	+ v_1 \zeta + \mathcal{O}(\zeta^2) \right) \right) }{\partial z} + \\
 		 &+ A_f \cfrac{\partial }{\partial z} \left(  \cfrac{P_0}{M_a^2}	+ \cfrac{P_1 \zeta}{M_a^2}	+ \cfrac{P_2 \zeta^2}{M_a^2} + \mathcal{O}(\zeta^3) \right)
@@
 	The simplification of the $P_0$ in the momentum equation comes from the fact that $P_0$ is independent of $z$.
+As it was presented above, the thermodynamical pressure moves with speed of sound, and any perturbation propagates instantaneously.
 The term related to $P_2$ and higher order terms become zero at the limit of $M_a \rightarrow 0$.
@@
 		\begin{equation*}
-			\cfrac{\partial \left( \rho_0 A_f V_0 \right) }{\partial t}	+ \cfrac{\partial \left( \rho_0 V_0 A_f V_0 \right)}{\partial z} + A_f \cfrac{\partial P_1}{\partial z} = 0
+			\cfrac{\partial \left( \rho_0 A_f v_0 \right) }{\partial t}	+ \cfrac{\partial \left( \rho_0 v_0 A_f v_0 \right)}{\partial z} + A_f \cfrac{\partial P_1}{\partial z} = 0
 		\end{equation*}
@@
 			& \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left( \left( \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( e_0	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right)}{\partial t} + \\
-			&+ \cfrac{\partial \left(  \left(  \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( V_0	+ V_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \left( e_0	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial z} + \\
+			&+ \cfrac{\partial \left(  \left(  \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( v_0	+ v_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \left( e_0	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial z} + \\
 			&+ \cfrac{\partial}{\partial z} \left( k \cfrac{\partial }{\partial z} \left( T_0 	+ T_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) + \\
-			&- \left(  P_0 	+ P_1 \zeta		+ P_2 \zeta^2 		+ \mathcal{O}(\zeta^3)  \right) \cfrac{\partial \left( A_f \left( V_0 + V_1 \zeta + \mathcal{O}(\zeta^2) \right) \right) }{\partial z} = 0
+			&- \left(  P_0 	+ P_1 \zeta		+ P_2 \zeta^2 		+ \mathcal{O}(\zeta^3)  \right) \cfrac{\partial \left( A_f \left( v_0 + v_1 \zeta + \mathcal{O}(\zeta^2) \right) \right) }{\partial z} = 0
 		\end{align*}
@@
 		\begin{equation*}
-			\cfrac{\partial \left( \rho_0 e_0 A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_0 e_0 V_0 A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_0}{\partial z} \right) + P_0 \cfrac{\partial A_f V_0}{\partial z} = 0
+			\cfrac{\partial \left( \rho_0 e_0 A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_0 e_0 v_0 A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_0}{\partial z} \right) + P_0 \cfrac{\partial A_f v_0}{\partial z} = 0
 		\end{equation*}
@@
 		\begin{align*}
-			\cfrac{\partial \left( \rho_f A_f \right)}{\partial t} &+ \cfrac{\partial \left( \rho_f A_f V \right)}{\partial z} = 0 \\
-			\cfrac{\partial \left( \rho_f A_f V \right) }{\partial t}	&+ \cfrac{\partial \left( \rho_f V A_f V \right)}{\partial z} + A_f \cfrac{\partial P_1}{\partial z} = 0\\
-			\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_f e V A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
+			\cfrac{\partial \left( \rho_f A_f \right)}{\partial t} &+ \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} = 0 \\
+			\cfrac{\partial \left( \rho_f A_f v \right) }{\partial t}	&+ \cfrac{\partial \left( \rho_f v A_f v \right)}{\partial z} + A_f \cfrac{\partial P_1}{\partial z} = 0\\
+			\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_f e v A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
 		\end{align*}
@@
 		\begin{equation*}
-			 \rho A_f \left( \cfrac{\partial e }{\partial t} + V \cfrac{\partial e}{\partial z} \right) + e  \underbrace{ \left( \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f V A_f \right)}{\partial z} \right) }_{Continutiy}  - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
+			 \rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) + e  \underbrace{ \left( \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f v A_f \right)}{\partial z} \right) }_{Continutiy}  - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
 		\end{equation*}
@@
 		\begin{equation*}
-		\rho A_f \left( \cfrac{\partial e }{\partial t} + V \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
+		\rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
 		\end{equation*}
@@
 		\begin{equation*}
-			\rho A_f C_v \left( \cfrac{\partial T }{\partial t} + V \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
+			\rho A_f C_v \left( \cfrac{\partial T }{\partial t} + v \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
 		\end{equation*}
@@
 		\begin{equation*}
-			\lim_{\Delta T \rightarrow 0_+} \rho A_f C_v \left( \cfrac{\partial T }{\partial t} + V \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0
+			\lim_{\Delta T \rightarrow 0_+} \rho A_f C_v \left( \cfrac{\partial T }{\partial t} + v \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
 		\end{equation*}
@@
 		\begin{equation}
-			\cfrac{\partial A_f V}{\partial z} = 0
+			\cfrac{\partial A_f v}{\partial z} = 0
 			\label{EQ: Incompressibility_Condition_Ideal_IsoThermal}
@@
 
-	In one-dimensional case, the equation \ref{EQ: Incompressibility_Condition_Ideal_IsoThermal} become equivalent of $\text{div} ( A_f V) = 0$, which known as the incompressibility condition (\citet{Lions2013}).
+	In one-dimensional case, the equation \ref{EQ: Incompressibility_Condition_Ideal_IsoThermal} become equivalent of $\text{div} ( A_f v) = 0$, which known as the incompressibility condition (\citet{Lions2013}).
+
+		A general formulation the internal energy for a real gas is:
+
+	{\footnotesize
+		\begin{equation*}
+			de=C_vdT-\left[P-T\left(\cfrac{\partial P}{\partial T}\right)_{V_m}\right]dv_m
+	\end{equation*} }
+
+	where $v_m$ is the molar volume.
+
+	The internal energy is a function of two intensive properties, in this case $T$ and $v_m=1/\rho_f$.
+But, in the case of an ideal gas, the equation of state is such that the second term in this equation is identically equal to zero.
+So the ideal gas is a special case in which the molar internal energy is a function only of temperature.
+For Peng-Robinson equation of state, the internal energy is defined as
+
+	{\footnotesize
+	\begin{equation*}
+		e = C_vT + \cfrac{a\left(\alpha -T\cfrac{d \alpha}{dT}\right)}{2\sqrt{2}b} \ln \left[ \cfrac{1+b\left(1-\sqrt{2}\rho\right) }{1+b\left(1+\sqrt{2}\rho\right)} \right]
+	\end{equation*} }
+
+	Assuming constant temperature and pressure along space and in time:
+
+	{\footnotesize
+		\begin{equation*}
+			\lim_{\Delta T, \Delta P \rightarrow 0_+ } \rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0 \rightarrow \cfrac{\partial A_f v}{\partial z} = 0
+		\end{equation*}
+	}
+
+	It can be deduce that the continuity equation becomes $\frac{\partial \rho_f}{\partial t} = 0$ at constant temperature and pressure.
+Moreover, the incompressibility condition $div(A_fV)=0$ is obtained.
+
+	Assuming an arbitrary function $\hat{P}$, which describe the total pressure, the dimensional momentum equation can be written as
+
+	{\footnotesize
+		\begin{equation*}
+			V \underbrace{ \left( \cfrac{\partial \rho_f A_f}{\partial t} + \cfrac{\rho_f v A_f}{\partial z} \right) }_{Continuity~equation} + \rho_f A_f \cfrac{\partial v}{\partial t} + \rho_f v A_f \cfrac{\partial v}{\partial z} = - A_f \cfrac{\partial \hat{P}}{\partial z}
+		\end{equation*}
+	}
+
+	From the incompressibility conditions we can deduce that
+
+	{\footnotesize
+		\begin{equation*}
+			\cfrac{\partial A_f v}{\partial z} = 0 \rightarrow A_f \cfrac{\partial v}{\partial z} = - v \cfrac{\partial A_f}{\partial z}
+		\end{equation*}
+	}
+
+	By combining both above equations, assuming that $\partial v / \partial t = 0$:
+
+	{\footnotesize
+		\begin{equation*}
+			\cfrac{\rho_f v^2}{A_f} \cfrac{\partial A_f}{\partial z} = \cfrac{\partial \hat{P}}{\partial z} \rightarrow \int	\cfrac{\rho_f v^2}{A_f} \cfrac{\partial A_f}{\partial z} dz = \int \cfrac{\partial\hat{P}}{\partial z} dz
+		\end{equation*}
+	}
+
+	The l.h.s integral can be solved by assuming $\rho_f$ is constant and introducing superficial velocity $u_s=A_f v$
+
+	{\footnotesize
+		\begin{align*}
+			& \int	\cfrac{\rho_f v^2}{A_f} \cfrac{\partial A_f}{\partial z} dz = \int	\cfrac{\rho_f v^2}{A_f} \cfrac{A_f^2}{A_f^2} \cfrac{\partial A_f}{\partial z} dz \\
+			&= \rho_f u_s^2  \int \cfrac{1}{A_f^3} \cfrac{\partial A_f}{\partial z} dz = - \cfrac{\rho_f u_s^2}{2 \Delta A_f^2} = - \cfrac{\rho_f \Delta v^2}{2} \\
+			& \int \cfrac{\partial \hat{P}}{\partial z} dz = \Delta \hat{P}
+		\end{align*}
+	}
+
+	The final form of the momentum equation corresponds to the Bernoulli's principle
+
+	{\footnotesize
+		\begin{equation*}
+			\Delta \hat{P} = - \cfrac{\rho_f \Delta v^2}{2} \xrightarrow[]{P_0 = \text{const}} \Delta M_a^2 P_1 = - \cfrac{\rho_f \Delta v^2}{2}
+		\end{equation*}
+	}
+
+	The Bernoulli's principle can be used to find the hydrodynamic pressure caused by varying cross-section at steady-state.
+Moreover, if the flow velocity is relatively low and so all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic.
+The effect of this is that $\partial \rho / \partial P = 0$.
+In other words, the small changes in pressure due to flow velocity changes do not change the density.
+This has a secondary effect -- the speed of sound in the fluid is $\partial P/\partial \rho = \infty$	in this instance.
+So there is an infinite speed of sound, which makes the equations elliptic in nature.
+It can be deduced that at the isothermal conditions the density in the system propagates with the same speed as pressure due to the fact that they are both connected through the equation of state.
 

### 2023-03-09 SFE-article/Sections/Model.tex
09.03

@@
 
-	{\color{blue}A distributed-parameter model, based on \citet{Reverchon1996}, is used to describe the solid-fluid extraction process.
-The process model consists of three partial differential equations: two mass balance equations relative to the concentration of solute in the fixed solid phase and the mobile fluid phase, and the heat balance equation relative to the temperature of the fluid phase.
+	For the sake of clarity of the process model, different colors have been used in the equations to indicate: 
+	{\color{red}control variables},
+	{\color{blue}state variables},
+	{\color{orange}variables} and
+	{\color{magenta}parameters}.
+
+	\subsubsection{Continuity equation} \label{CH: Continuity}
+	The details of derivation can be found in the appendix \ref{CH: Gouverning equations}.
+The continuity equation for the fluid phase is given by equation \ref{EQ: CompressibleEuler_1}.
+If $A_f$ is specified to be a function of void fraction $A_f = A\varepsilon(z)$, where $\varepsilon$ is void fraction of the bed and $A$ is the cross-section of the empty extractor.
+The continuity equation become
+
+	{\footnotesize
+		\begin{equation*}
+			\cfrac{\partial \left( \rho_f \varepsilon \right)}{\partial t} + \cfrac{\partial \left( \rho_f v \varepsilon \right)}{\partial z} = 0
+		\end{equation*}
+	}
+
+	Assuming that the mass flow-rate is constant in time, the temporal derivative become zero and the spacial derivative can be integrated along $z$.
+
+	{\footnotesize
+		\begin{equation}
+			\int \cfrac{\partial \left( \rho_f v \varepsilon \right)}{\partial z} dz = 0 \rightarrow F=\rho_f v \varepsilon
+		\end{equation}
+	}
+
+	where $F$ is a constant obtained from the integration and it is understood as the mass flux per unit area which is assumed to be constant along $z$.
+$F$ can treated as a control variable, which can change in time but it is constant in space.
+Such a assumption allows to find the velocity profile which satisfy the mass continuity based on $F, \varepsilon$ and $\rho_f$.
+The fluid density $\rho_f$ density is connected through equation of state with thermodynamical pressure, which is assumed to be constant along $z$ (due to the low-Mach number) and temperature \todo{Elaborate, the pressure is know (a control variable) and temperature can be found from energy equation}.
+The variation in density might be caused by the accumulation of the fluid \todo{Introduce relation between accumulation, pressure and energy equation} in the system (which happen instantaneously along $z$) or by temperature change.
+To simplify the dynamic of the system, it is assumed that $F=F(t)$ is a control variable and affects the whole system instantaneously.
+
+	\subsubsection{Mass balance for the fluid phase} \label{CH: Mass_balance_fluid}
+
+	The detail derivation of the mass balance equation for the fluid phase can be found in the appendix (\ref{CH: Gouverning equations}).
+The movement of the mobile pseudo-homogeneous phase (equation \ref{Model_fluid}) is considered only in the axial direction.
+The properties of the system in the radial direction are assumed to be uniform.
+In addition, it is considered that the boundary layer adjacent to the inner wall of the extractor does not exist.
+Therefore, the velocity profile is constant across any cross-section of the extractor perpendicular to the axial direction.
+As a result, the plug flow model \todo{Double check if we can call it a plug flow} can be introduced.
+The particle size distribution and the void fraction of the solid phase cab change along an extractor but they remain constant in time.
+Moreover, the thermodynamic pressure is considered to be constant along the device, as discussed above.
 The amount of solute in the solvent is considered negligible.
 Therefore, the fluid phase can be described as pseudo-homogenous, and its properties are assumed to be the same as the solvent.
-
-	The movement of the mobile pseudo-homogeneous phase (Eq.
-\ref{Model_fluid}) is considered only in the axial direction.
-The properties of the system in the radial direction is assumed to be uniform.
-In addition, it is considered that the boundary layer adjacent to the inner wall of the extractor does not exist.
-Therefore, the velocity profile is constant across any cross-section of the extractor perpendicular to the axial direction.
-As a result, the plug flow model can be introduced.
-The particle size distribution and the void fraction of the solid phase cab change along an extractor but they remain constant in time.
-Moreover, the thermodynamic pressure is considered to be constant along the device, as discussed above.
 The mass balance for the fluid phase consists of convection, diffusion, and kinetic terms.
 
-	Considering the solid phase to be fixed, the convection and diffusion terms in the corresponding mass balance are both assumed to be negligible or absent.
-Therefore, the mass balance for the solid phase (Eq.
-\ref{Model_solid}) consists of the kinetic term only.
+	%The process model consists of three partial differential equations: two mass balance equations relative to the concentration of solute in the fixed solid phase and the mobile fluid phase, and the heat balance equation relative to the temperature of the fluid phase.
 
-	As for the mass transfer from the solid to the fluid phase, a kinetic term based on two-film theory for the solute is considered.
-The mass transfer kinetic (Eq.
-\ref{Model_kinetic_basic}) consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.
+	{\footnotesize
+		\begin{align} 
+			\label{Model_fluid}
+			\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t} &	=  \underbrace{- \cfrac{u_s}{\varepsilon} \cfrac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} - \underbrace{ \cfrac{ {\color{blue}c_f}(t,z) }{\varepsilon} \cfrac{\partial {\color{blue}u}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} \nonumber \\
+			&+ \underbrace{ \cfrac{ {\color{orange}D^M_e} }{\varepsilon} \left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] \cfrac{\partial^2 {\color{blue}c_f}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusive term}}
+			+ \underbrace{ \cfrac{1-{\color{magenta}\varepsilon}}{{\color{magenta}\varepsilon}} {\color{blue}r_e}(t,z) }_{\text{Kinetic term}}
+	\end{align} }
+
+	where ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z), {\color{blue}T}(t,z)$ correspond to concentration of solute in the fluid phase, concentration of solute in the solid phase and the temperature, respectively.
+${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term.
+${\color{red}F}(t)$ is the mass flow rate, ${\color{red}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient and $u$ is the superficial velocity.
+\todo{Remove symbols which have been introduced before}
+
+	\subsubsection{Mass balance for the solid phase} \label{Mass_balance_solid}
+
+	Considering the solid phase to be fixed, the convection and diffusion terms in the corresponding mass balance (equation \ref{Model_solid}) are both assumed to be negligible or absent.
+Therefore, the only term present in this equation is the kinetic term (defined as presented in equation \ref{Model_kinetic_basic}), which links solid and fluid phases.
 A single pseudo-component is used to represent the extract collectively.
 
+	{\footnotesize
+		\begin{equation} 
+			\label{Model_solid}
+			%		{\scriptsize\begin{align*}
+					\cfrac{\partial {\color{blue}c_s}(t,z)}{\partial t} = \underbrace{ {\color{blue}r_e}(t,z) }_{\text{Kinetics}}
+			\end{equation} }
+
+	\subsubsection{Kinetic term} \label{CH: Kinetic}
+
+	The kinetic term is based on two-film theory and follow work of \citet{Reverchon1996}.
+The mass transfer kinetic (equation \ref{Model_kinetic_basic}) consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.
+
+	As the solvent flows through the bed, the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to for an external fluid film around the solid particles through the solvent–solid matrix interactions.
+Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected.
+The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
+The graphical representation of the mass transfer mechanism is shown in Figure \ref{fig: SFE_Mechanism}.
+The mean solute concentration in the solid phase is denoted as ${\color{blue}c_s}$.
+At the solid-fluid interface, the equilibrium concentrations are given as ${\color{blue}c_s^*}$ and ${\color{blue}c_P^*}$, respectively for solid and fluid phases.
+The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{blue}c_{P}}$.
+As the solute diffuses through the pore, its concentration changes and reaches ${\color{blue}c_{Pf}}$ at the opening of the pore.
+The solute diffuses through the film around the particle and reaches a concentration in the bulk ${\color{blue}c_f}$.
+It can be assumed that the two-film theory describes the solid-fluid interface inside the pore.
+The overall mass transfer coefficient can be introduced if the relation between the solute concentration in one phase and its equilibrium concentration is known.
+
+		\begin{figure}[h!]
+			\centering
+			%	\includegraphics[trim  = 6cm 0cm 3cm 0cm,clip,width=\linewidth]{Figures/SFE_draft.png}
+			\includegraphics[trim = 5.8cm 1.1cm 6cm 3cm,clip,width=\columnwidth]{Figures/SFE_draft.pdf}	
+			\caption{The extraction mechanism}
+			\label{fig: SFE_Mechanism}
+		\end{figure}
+
+		\citet{Bulley1984} suggest a process where the driving force for extraction is given by the difference between concentration of the solute in the bulk, ${\color{blue}c_f}$, and in the centre of the pore, ${\color{blue}c_P^*}$.
+The concentration ${\color{blue}c_P^*}$ is in equilibrium with ${\color{blue}c_s}$ according to an equilibrium relationship.
+The rate of extraction is thus ${\color{blue}r_\text{e}}\left({\color{blue}c_f} - {\color{blue}c^*_P}({\color{blue}c_s})\right)$.
+
+		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between ${\color{blue}c_s}$ and ${\color{blue}c_P^*}$.
+${\color{blue}c_P^*}$ is determined by an equilibrium relationship with ${\color{blue}c_f}$ and the extraction rate is ${\color{blue}r_\text{e}}\left({\color{blue}c_s} - {\color{blue}c^*_P}({\color{blue}c_f})\right)$ or more precisely
+
+			{\footnotesize
+				\begin{equation} \label{Model_kinetic_basic}
+					{\color{blue}r_e}(t,z) = \cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} }\left({\color{blue}c_s}(t,z) - {\color{blue}c_P^*}(t,z) \right)
+			\end{equation} }
+
+		where ${\color{magenta}\mu}$ is sphericity, ${\color{magenta}l}$ a characteristic dimension of particles and can be defined as ${\color{magenta}l} = {\color{magenta}r}/3$, ${\color{magenta}r}$ is the mean particle radius, ${\color{magenta}\rho_s}$ is the solid density, ${\color{orange}D_i}({\color{blue}T}(t,z))$ corresponds to the overall diffusion coefficient and ${\color{blue}c_P^*}(t,z)$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).
+
+		According to \citet{Bulley1984}, a linear equilibrium relationship (equation  \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{blue}c_f^*}(t,z)$ is based on concentration of the solute in the solid phase ${\color{blue}c_s}(t,z)$
+
+			{\footnotesize
+				\begin{align} \label{Linear_equilibirum}
+					{\color{blue}c}(t,z) &= {\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t)) \allowbreak {\color{blue}q^*}(t,z)
+			\end{align} }
+
+			The volumetric partition coefficient ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
+According to \citet{Spiro2007}, the term ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as the function of mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$.
+
+			{\footnotesize
+				\begin{align}
+					{\color{orange}k_m}({\color{blue}T}(t,z)) = \cfrac{{\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{magenta}\rho_s}}{{\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}
+			\end{align} }
+
+			Equation \ref{Model_kinetic_no_sat} represents of the kinetic term according to \citet{Reverchon1996}
+
+			{\footnotesize
+				\begin{equation}
+					\label{Model_kinetic_no_sat}
+					{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} }\left({\color{blue}c_s}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
+			\end{equation} }
+
+        The above model does not take into account the saturation of fluid, which can be introduced by multiplying the gradient by a function $\gamma(c_f)$ (equation \ref{EQ: C_sat_function}).
+$\gamma(c_f)$ describe the reverse logistic function, which is equal to unity below the $c_{sat}$, the saturation concentration, and equal to zero, above the $c_{sat}$.
+The $\gamma(c_f)$ for $c_{sat}=5$ is shown on figure \ref{fig: Gamma_function}.
+
+        {\footnotesize
+            \begin{equation}
+                \gamma(c_f) = \cfrac{1}{1+\exp ( -k_{sat} \left( c_f - c_{sat} \right) ) }
+                \label{EQ: C_sat_function}
+            \end{equation}
         }
 
+        where $k_{sat}$ is the growth rate, and it is defined as $k_{sat} = 2c_{sat}$\todo{Explain why the growth rate is defined as it is}.
+
+        \begin{figure}[h!]
+        	\centering
+        	\begin{tikzpicture}
+
+        		\begin{axis}[
+        			legend style={draw=none},
+        			xmin = 0, xmax = 10,
+        			ymin = -0.5, ymax = 1.5,
+        			xlabel = {$c_f[kg/m^3]$},
+        			ylabel = {$\Gamma(c_f)[-]$}]
+        			\addplot[
+        			domain = 0:10,
+        			samples = 100,
+        			smooth,
+        			thick,
+        			blue,
+        			] { 1 / (1 + exp( 2*5 .* ( x - 5 ) ) ) };
+        			\addplot[thick, samples=50, dashed, domain=0:1.5, black] coordinates {(5,-0.5)(5,1.5)};
+
+        			\addlegendentry{$\gamma(c_f)$}
+        			\addlegendentry{$c_{sat}$}
+        		\end{axis}
+
+        	\end{tikzpicture}
+        \caption{$\gamma(c_f)$ function under assumption of $c_{sat}=5 [kg/m^3]$}
+        \label{fig: Gamma_function}
+        \end{figure}
+
+        The final form of the extraction kinetic equation is given by equation \ref{Model_kinetic}.
+
+        {\footnotesize
+			\begin{equation}
+				\label{Model_kinetic}
+				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} } \gamma(c_f) \left({\color{blue}c_s}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
+		\end{equation} }
+
+		\subsubsection{Heat balance} \label{CH: heat_balance} \todo{I will be back. The energy equation is not given as a in terms of temperature any more.}
+
 		 {\color{red}
-	The heat balance (Eq.
-\ref{Model_heat}) consists of the convective and diffusive terms.
+			The heat balance (equation \ref{Model_heat}) consists of the convective and diffusive terms.
 It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases.
@@
 
-	For the sake of clarity of the process model, different colors have been used in the equations to indicate: 
-	{\color{red}control variables},
-	{\color{blue}state variables},
-	{\color{orange}variables} and
-	{\color{magenta}parameters}.
-
-	\subsubsection{Continuity equation} \label{CH: Continuity}
-	The continuity equation for the fluid phase is given by Eq. \ref{EQ: Continuity}. The details of derivation can be found in the appendix \ref{CH: Gouverning equations}
-
-	{\footnotesize
-		\begin{equation}
-			\cfrac{\partial \left( \rho_f A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_f v A_f \right)}{\partial z} = 0
-			\label{EQ: Continuity}
-		\end{equation}
-	}
-
-	Considering the mass flow-rate which is constant in time, the temporal derivative become zero and the spacial derivative can be integrated along $z$.
-
-	{\footnotesize
-		\begin{equation*}
-			\int \cfrac{\partial \left( \rho_f v A_f \right)}{\partial z} dz = 0 \rightarrow F=\rho_f v A_f
-		\end{equation*}
-	}
-
-	where $F$ is a constant obtained from the integration.
-The constant $F$ can be understood as the mass flux per unit area which is assumed to be constant along $z$.
-$F$ can treated as a control variable, which can change in time but it is constant in space.
-Such a assumption allows to find the velocity profile which satisfy the mass continuity based on $F, A_f$ and $\rho_f$.
-The fluid density $\rho_f$ density is connected through equation of state with thermodynamical pressure, which is assumed to be constant along $z$ (due to the low-Mach number) and temperature.
-The variation in density might be caused by the accumulation of the fluid in the system (which happen instantaneously along $z$) or by temperature change.
-To simplify the dynamic of the system, it is assumed that $F=F(t)$ is a control variable and affects the whole system instantaneously.
-
-	\subsubsection{Mass balance for the fluid phase} \label{CH: Mass_balance_fluid}
-	The detail derivation of the mass balance equation for the fluid phase can be found in the appendix ({\color{red}REF}).
-The fluid phase is a mobile phase, which means that the fluids mass balance (Eq.
-\ref{Model_fluid}) is made of convection, diffusion, and mass transfer kinetic terms.
-
-	{\footnotesize
-		\begin{align} 
-			\label{Model_fluid}
-			\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t} &	=  \underbrace{- \cfrac{u}{\varepsilon} \cfrac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} - \underbrace{ \cfrac{ {\color{blue}c_f}(t,z) }{\varepsilon} \cfrac{\partial {\color{blue}u}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} \nonumber \\
-			&+ \underbrace{ \cfrac{ {\color{orange}D^M_e} }{\varepsilon} \left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] \cfrac{\partial^2 {\color{blue}c_f}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusive term}}
-			+ \underbrace{ \cfrac{1-{\color{magenta}\varepsilon}}{{\color{magenta}\varepsilon}} {\color{blue}r_e}(t,z) }_{\text{Kinetic term}}
-	\end{align} }
-
-	where ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z), {\color{blue}T}(t,z)$ correspond to concentration of solute in the fluid phase, concentration of solute in the solid phase and the temperature, respectively.
-${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term.
-${\color{red}F}(t)$ is the mass flow rate, ${\color{red}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient and $u$ is the superficial velocity.
-
-	\subsubsection{Mass balance for the solid phase} \label{Mass_balance_solid}
-	The solid phase is a stationary phase, which indicates a lack of convection and diffusion terms in the mass balance (Eq.
-\ref{Model_solid}).
-Therefore, the only term present in this equation is the kinetic term (defined as presented in equation \ref{Model_kinetic_basic}), which links solid and fluid phases.
-
-	{\footnotesize
-		\begin{equation} 
-			\label{Model_solid}
-			%		{\scriptsize\begin{align*}
-					\cfrac{\partial {\color{blue}c_s}(t,z)}{\partial t} = \underbrace{ {\color{blue}r_e}(t,z) }_{\text{Kinetics}}
-			\end{equation} }
-
-	\subsubsection{Kinetic term} \label{CH: Kinetic}
-	As the solvent flows through the bed, {\color{blue}the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to for an external fluid film around the solid particles through the solvent–solid matrix interactions.
-Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected}.
-The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
-The graphical representation of the mass transfer mechanism is shown in Figure \ref{fig: SFE_Mechanism}.
-The mean solute concentration in the solid phase is denoted as ${\color{blue}c_s}$.
-At the solid-fluid interface, the equilibrium concentrations are given as ${\color{blue}c_s^*}$ and ${\color{blue}c_P^*}$, respectively for solid and fluid phases.
-The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{blue}c_{P}}$.
-As the solute diffuses through the pore, its concentration changes and reaches ${\color{blue}c_{Pf}}$ at \sout{the end} {\color{blue}the opening} of the pore.
-The solute diffuses through the film around the particle and reaches a concentration in the bulk ${\color{blue}c_f}$.
-It can be assumed that the two-film theory describes the solid-fluid interface inside the pore.
-The overall mass transfer coefficient can be introduced if the relation between the solute concentration in one phase and its equilibrium concentration is known.
-
-		\begin{figure}[h!]
-			\centering
-			%	\includegraphics[trim  = 6cm 0cm 3cm 0cm,clip,width=\linewidth]{Figures/SFE_draft.png}
-			\includegraphics[trim = 5.8cm 1.1cm 6cm 0.8cm,clip,width=\columnwidth]{Figures/SFE_draft.pdf}	
-			\caption{The extraction mechanism}
-			\label{fig: SFE_Mechanism}
-		\end{figure}
-
-		\citet{Bulley1984} suggest a process where the driving force for extraction is given by the difference between concentration of the solute in the bulk, ${\color{blue}c_f}$, and in the centre of the pore, ${\color{blue}c_P^*}$.
-The concentration ${\color{blue}c_P^*}$ is in equilibrium with ${\color{blue}c_s}$ according to an equilibrium relationship.
-The rate of extraction is thus ${\color{blue}r_\text{e}}\left({\color{blue}c_f} - {\color{blue}c^*_P}({\color{blue}c_s})\right)$.
-
-		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between ${\color{blue}c_s}$ and ${\color{blue}c_P^*}$.
-${\color{blue}c_P^*}$ is determined by an equilibrium relationship with ${\color{blue}c_f}$ and the extraction rate is ${\color{blue}r_\text{e}}\left({\color{blue}c_s} - {\color{blue}c^*_P}({\color{blue}c_f})\right)$.
-
-		{\color{blue}The mass transfer kinetic (Eq.
-\ref{Model_kinetic_basic}) describes a diffusion rate of the solute from solid particles to the solvent.
-The kinetic term consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.} Based on the work of \citet{Bulley1984}, \citet{Reverchon1996} proposed to define the kinetic terms as
-
-			{\footnotesize
-				\begin{equation} \label{Model_kinetic_basic}
-					{\color{blue}r_e}(t,z) = \cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}q}(t,z) - {\color{blue}q^*}(t,z) \right)
-			\end{equation} }
-
-			where ${\color{orange}D_i}({\color{blue}T}(t,z))$ corresponds to the overall diffusion coefficient and ${\color{blue}q^*}(t,z)$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).
-${\color{blue}q^*}(t,z)$ can be calculated based on the equilibrium relationship (Eq.
-\ref{Linear_equilibirum}).
-
-			\sout{The kinetic term of the model takes into account the properties of the biomass like a sphericity (through the shape coefficient ${\color{magenta}\mu}$ equal to $1/3$ for slabs and $3/5$ for spheres), a characteristic dimension of particles (through the parameter ${\color{magenta}l} = {\color{magenta}r}/3$ where ${\color{magenta}r}$ is the mean particle radius), and the solid density ${\color{magenta}\rho_s}$.
-The fixed bed is characterized by a void fraction ${\color{magenta}\epsilon}$.
-}
-
-			{\color{blue} The kinetic term of the model takes into account properties of the solid particles like a sphericity (through the shape coefficient ${\color{magenta}\mu}$), a characteristic dimension of particles (through the parameter ${\color{magenta}l} = {\color{magenta}r}/3$ where ${\color{magenta}r}$ is the mean particle radius), and the bulk density ${\color{magenta}\rho_s}$.
-The fixed bed is characterized by a void fraction ${\color{magenta}\epsilon}$.
-}
-
-			According to \citet{Bulley1984}, a linear equilibrium relationship (Eq.
-\ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{blue}c_f^*}(t,z)$ is based on concentration of the solute in the solid phase ${\color{blue}c_s}(t,z)$
-
-			{\footnotesize
-				\begin{align} \label{Linear_equilibirum}
-					{\color{blue}c}(t,z) &= {\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t)) \allowbreak {\color{blue}q^*}(t,z)
-			\end{align} }
-
-			The volumetric partition coefficient ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
-\sout{ The ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$ according to} \citet{Spiro2007} .
-			{\color{blue} According to \citet{Spiro2007}, the term ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as the function of mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$ }
-
-			{\footnotesize
-				\begin{align}
-					{\color{orange}k_m}({\color{blue}T}(t,z)) = \cfrac{{\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{magenta}\rho_s}}{{\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}
-			\end{align} }
-
-			Equation \ref{Model_kinetic_no_sat} is the full representation of the kinetic term.
-
-			{\footnotesize
-				\begin{align}
-					\label{Model_kinetic_no_sat}
-					{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} }\left({\color{blue}q}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c}(t,z) \right)
-			\end{align} }
-
-        The above model does not take into account the saturation of fluid, which can be introduced by multiplying the gradient by a function $\Gamma(c_f)$ (equation \ref{EQ: C_sat_function}).
-$\Gamma(c_f)$ describe the reverse logistic function, which is equal to unity below the $c_{sat}$, the saturation concentration, and equal to zero, above the $c_{sat}$.
-
-        {\footnotesize
-            \begin{equation}
-                \Gamma(c_f) = \cfrac{1}{1+\exp ( -k_{sat} \left( c_f - c_{sat} \right) ) }
-                \label{EQ: C_sat_function}
-            \end{equation}
-        }
-
-        where $k_{sat}$ is the growth rate, and it is defined as $k_{sat} = 2c_{sat}$.
-
-        The final form of the extraction kinetic equation is given by equation \ref{Model_kinetic}
-
-        {\footnotesize
-			\begin{align}
-				\label{Model_kinetic}
-				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z))}{{\color{magenta} \mu l^2} } \Gamma(c_f) \left({\color{blue}q}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c}(t,z) \right)
-		\end{align} }
-
-		\subsubsection{Heat balance} \label{CH: heat_balance}
-		\sout{The heat balance equation (Eq.
-\ref{Model_heat}) was developed, assuming the existence of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases (the amount of solute is considered small enough not to affect the overall heat balance).
+		\sout{The heat balance equation (equation  \ref{Model_heat}) was developed, assuming the existence of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases (the amount of solute is considered small enough not to affect the overall heat balance).
 Equation \ref{Model_heat} contains the convection and the diffusion terms.
@@
 
-		{\color{blue} The heat balance (Eq.
-\ref{Model_heat}), is based on \citet{Srinivasan2012}, and consists of convective and diffusive terms.
+		{\color{blue} The heat balance (equation \ref{Model_heat}), is based on \citet{Srinivasan2012}, and consists of convective and diffusive terms.
 It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases.
@@
 
-		\subsubsection{Extraction yield} \label{CH: Yield}
+		\subsubsection{Extraction yield} \label{CH: Yield} \todo{Give reference for measurement function}
 
@@
 				\label{Model_measurment_1}
-				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
+%				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
 				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} \cfrac{F(t)}{\rho(t,z)} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] 	\\
-				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
+%				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
 				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= \cfrac{F(t)}{\rho(t,z)} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]
@@
 		\end{align}	}
+
+		\iffalse
 
@@
 Each function ${\color{blue}\phi_i}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{blue}G}_{i\times N_z+1}$ to ${\color{blue}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation.
-The state-space model ${\color{blue}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{blue}x}}(t)$ (Eq.
-\ref{discretization}).
+The state-space model ${\color{blue}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{blue}x}}(t)$ (equation  \ref{discretization}).
 
@@
 
+			\fi
+
 \end{document}

### 2023-03-09 SFE-article/Sections/Parameter_estimation.tex
08.03
09.03

--- 2023-01-24 SFE-report/Sections/Parameter_estimation.tex
@@
 
-Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, $y(t)$, to give the observable dependent variable $Y(t)$, for example the experimental process output.
+Conceptually, the unobservable error $\epsilon(t)$\todo[fancyline]{The same symbol as void fraction} is added to the deterministic model output, $y(t)$ (equation \ref{Model_measurment_1}), to give the observable dependent variable $Y(t)$ (for example results of an experiments).
 For discrete observations:
@@
 {\footnotesize
-	\begin{equation}
+	\begin{equation*}
 		Y(t_i) = y(t_i) + \epsilon(t_i)
-\end{equation} }
+\end{equation*} }
 and for continuos variables:
@@
 {\footnotesize
-	\begin{equation}
+	\begin{equation*}
 		Y(t) = y(t) + \epsilon(t)
-\end{equation} }
+\end{equation*} }
 
@@
 The objective in parameter estimation is to obtain the "best" estimate of $\theta$ based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$.
-\sout{
-	We assume that $x(t)$ is given \textit{a priori} (for example as a solution of process model) but $\theta$ is to be estimated over the time interval $0 \leq t \leq t_n$ from discrete observation described by the following relation:}
-
-{\footnotesize
-	\begin{equation}
-		Y(t_i) = \textbf{h}(t_i)y(t_i) + \boldsymbol{\epsilon}(t_i) \qquad 1 \leq i \leq n
-\end{equation} }
-\sout{where $ Y(t_i)$ is an $n \times 1$ column vector, $\textbf{h}(t_i)$ is an $n \times v$ matrix given \textit{a priori}, and $ \boldsymbol{\epsilon} (t_i)$ is an $n \times 1$ column vector ("noise" vector) whose elements are the unobservable errors.
-The above equation can be written in general form as:}
+The above equation can be written in general form as:
 
@@
 \end{equation}}
-where $y$ is the output model, which is a function of $\theta$ and time $t_i$.
+
+where $\theta$ is set of parameters to be estimated from the data. $\theta$ is a subset of parameter space $\Theta$, which contain all parameters of the model.
 
 Because of the difficulty of obtaining analytical solutions to the deterministic process model, experiments have been arranged whereby the vector of derivatives $d Y(t_i)/dt$ is measured rather than $Y(t_i)$ itself.
-In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ as follows:
+In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ (equation \ref{Model_measurment_2}) as follows:
 
 {\footnotesize
-	\begin{equation}
+	\begin{equation*}
 		\cfrac{d Y(t_i)}{dt} = \cfrac{dy(\theta, t_i)}{dt} + \epsilon(t_i)
-\end{equation} }
+\end{equation*} }
+
+If unobservable error in the first observation is designated as $\epsilon_1$, the second error observation $\epsilon_2'$ includes $\epsilon_1$ plus a random component introduced side from $\epsilon_1$, or $\epsilon_2' = \epsilon_1 + \epsilon_2$.
+The error in the third observation is $\epsilon_3' = \epsilon_1 + \epsilon_2 + \epsilon_3$, and so forth.
+\citet{Mandel1957} distinguished between the usually assumed type of independent measuring error in the dependent variable and a 'cumulative' or interval error in which each new observation includes the error of the previous observations.
+Cumulative errors, arising because of the fluctuations as a function of time in the process itself due to small changes in operating, are not independent - only the differences in measurement from one period to the next are independent.
 
 \subsection{Least squares estimation}
-A least squares parameter estimation does not require prior knowledge of the distribution of unobservable errors, yield  unbiased estimates, \sout{that is, $ \mathbb{E}\{\hat{Y}(t) = y(t) \} $,} and results in the minimum variance among all linear unbiased estimators.
+A least squares parameter estimation does not require prior knowledge of the distribution of unobservable errors, yield  unbiased estimates, and results in the minimum variance among all linear unbiased estimators.
 If the observations $ Y$ for the model responses are continuous functions of time from $t = 0$ to $t = t_f$, the Markov (or "rigorous least squares") criterion is to minimize:
@@
 
-If $\Gamma$ is a diagonal matrix, $\phi$  becomes a "weighted least squares" criterion; if $\Gamma = \sigma^2 \textbf{I}$ where $\sigma$ is a standard deviation., $\phi$ is the "ordinary least squares" criterion.
+If $\Gamma$ is a diagonal matrix, $\phi$  becomes a "weighted least squares" criterion; if $\Gamma = \sigma^2 \textbf{I}$ where $\sigma$ is a standard deviation, $\phi$ is the "ordinary least squares" criterion.
 
+\iffalse
 \subsection{Weighted sum of squares - Cumulative data}
@@
 
-The \sout{best} unbiased estimate of the Model B is obtained by minimizing the weighted sum of squares:
+The unbiased estimate of the Model B is obtained by minimizing the weighted sum of squares:
 
@@
 \end{equation*} }
+
+\fi
 
@@
 Each time it has been associated with the (joint) normal distribution because of mathematical convenience.
-Consider the joint probability density function (the likelihood function) $p(\theta |y)$ for random sample $y = y(t_1),y(t_2),...,y(t_n)$, parameter $\theta$.
+Consider the joint probability density function (the likelihood function) $p \left(\theta | y(t_1),y(t_2),...,y(t_n)\right)$ for parameter $\theta$.
 If a maximum of this function over all choices of $\theta$ can be found, the estimates so obtained are maximum likelihood estimates.
@@
 
-The numerator of the right-hand side od Equation \ref{EQ: Posterior_distribution} using Equation \ref{EQ: Probabiltiy_dependet_a} becomes
+\todo[]{Notation is a bit unclear}The numerator of the right-hand side od Equation \ref{EQ: Posterior_distribution} using Equation \ref{EQ: Probabiltiy_dependet_a} becomes
 
@@
 
-By collecting a random sample of values of the random variable $y$ and selecting the values of $\theta$ that maximize the likelihood function $L\left( \theta | y \right)$, a function described in chapter \ref{CH: Bayes} in connection with Bayes' theorem.
+By collecting a values of $y$ and selecting the values of $\theta$ that maximize the likelihood function $L\left( \theta | y \right)$, a function described in chapter \ref{CH: Bayes} in connection with Bayes' theorem\todo{Is the reference it previous chapter needed?}.
 Such estimators, $\hat{\theta}$, are known as maximum likelihood estimators.
-In effect, the methods selects those values of $\theta$ that are at least as likely to generate the observed sample as any other set of values of the parameters if the probability density of the random variable $y$ were to be extensively simulated through use of the probability density $p\left( y|\theta \right)$.
+In effect, the methods selects those values of $\theta$ that are at least as likely to generate the observed sample as any other set of values of the parameters if the probability density of $y$ were to be extensively simulated through use of the probability density $p\left( y|\theta \right)$.
 In making a maximum likelihood estimate, we assume that the form of the probability density (\sout{only the $\theta$ need be determined}) and that all possible values of $\theta$ are equally likely before experimentation.
+\todo{Needed?}
 
@@
 			\begin{equation}
-				\ln L = -n \ln \sqrt{2 \pi} - \cfrac{n}{2} \ln \sigma
+				\ln L = -\cfrac{n}{2} \left( \ln \sqrt{2 \pi} + \ln \sigma^2 \right)
 				- \cfrac{ \sum_{i=1}^{n} \left[  Y(t_i) - y(\theta , t_i) \right]^2 }{2 \sigma^2}
@@
 					&& \dot{\theta} = 0 \\
-					&& y = g(x)
+					&& y = y(x)
 				\end{aligned}
 		\end{equation} }
+
+		\todo{$x$ has not been defined}
 
@@
 
-		\sout{By carrying out this operation, under fairly unrestrictive conditions,} 
+		\iffalse
+
 		It can be shown that as $n$ approaches infinity the maximum likelihood estimates have the desirable asymptotic properties:
@@
 
+	\fi
+
 \end{document}

### 2023-03-09 SFE-article/Sections/Thermo.tex
09.03

@@
 
+    %Carbon dioxide above its critical point attains a supercritical state and exhibits certain peculiar properties such as higher density as a liquid but with a lower viscosity comparable to a gas.
+The supercritical carbon dioxide (S-CO2) has a range of engineering applications.
+
     The properties of a fluid can be divided into two kinds, equilibrium properties and transport properties.
@@
 
-    Carbon dioxide above its critical point attains a supercritical state and exhibits certain peculiar properties such as higher density as a liquid but with a lower viscosity comparable to a gas.
-The supercritical carbon dioxide (S-CO2) has a range of engineering applications.
-
-    The thermodynamic properties of S-CO2 such as density, local speed of sound and specific heat capacity vary significantly for slight change in temperature and pressure due to real gas effects.
+    The thermodynamic properties of supercritical $CO_2$ such as density, local speed of sound and specific heat capacity vary significantly for slight change in temperature and pressure due to real gas effects.
 Equation of state (EOS) which account these real gas effects is used to calculate the thermodynamic properties.
 In order to predict this real gas effects, the Peng-Robinson equation of state (P-R EOS) is used to compute properties of $CO_2$.
+Detail information about Peng-Robinson equation of state can be found in the work of \citet{Peng1976}, \citet{Elliott2011} or \citet{Pratt2001}.
 The P-R EOS belongs to the specific class of thermodynamic models for modelling the pressure of a gas as a function of temperature and density and can be written as a cubic function of the molar volume (of the density).
@@
 At the critical point, the latent heat is zero but the heat capacity shows a diverging singularity.
-Beyond the critical point, there is no divergence, but rather a smooth peak in the heat capacity; the highest point of this peak identifies the Widom line.
-(ref: 10.1038/nphys1683, 10.3311/PPch.12871)
+Beyond the critical point, there is no divergence, but rather a smooth peak in the heat capacity; the highest point of this peak identifies the Widom line (as discussed by \citet{Simeoni2010} and \citet{Banuti2019}).
 
     In order to calculate thermodynamic properties from a real gas, the departure function for that property with respect to the chosen equation of state has to be evaluated.
-The departure function for any thermodynamic property of a real gas is defined as the difference in the value of that property determined from the chosen real gas equation of state and the value of the same property for an ideal gas under the same conditions of temperature and pressure.
-(0.1007/s10494-017-9872-4)
+As presented by \citet{Elliott2011}, the departure function for any thermodynamic property of a real gas is defined as the difference in the value of that property determined from the chosen real gas equation of state and the value of the same property for an ideal gas under the same conditions of temperature and pressure.
+%(10.1007/s10494-017-9872-4)
 
@@
         On the other hand, transport properties (viscosity and conductivity) are also important quantities required in engineering design for production, fluid transportation, and processing.
-According to (10.1007/BF00500714), there is no satisfactory theory of transport properties of real dense gases and liquids.
+According to \citet{Sheng1989}, there is no satisfactory theory of transport properties of real dense gases and liquids.
 The main difficulties in the study of transport properties are twofold: one is the inherent difficulties involved in accurate measurements, and the other is the complexity involved in theoretical treatments.
 Therefore, the generally used correlations of transport coefficient are either empirical or based on some theoretical foundation.
-Enskog (REF) developed a popular theory for the transport properties of dense gas based on the distribution function.
+Enskog (\todo[fancyline]{Add ref}) developed a popular theory for the transport properties of dense gas based on the distribution function.
 However, the Enskog theory was proposed for rigid spherical molecules.
@@
 Following the Enskog theory, many correlations have been proposed in the form of the reduced density and reduced temperature.
-The correlations of (10.1063/1.556013) and (10.1063/1.4977429) implemented and compared as presented on Figure \ref{fig: SFE_Properties_mu}.
-Eventually the NIST correlation was selected to be used.
+The correlations of \citet{Fenghour1998} and \citet{Laesecke2017} implemented and compared as presented on Figure \ref{fig: SFE_Properties_mu}.
 The viscosity formulation proposed by NIST consists of four contributions: (i) for the limit of zero density, (ii) for the initial density dependence, (iii) for the residual viscosity, and (iv) for the singularity of the viscosity at the critical point.
@@
 			\includegraphics[trim = 1.5cm 4.0cm 2.5cm 10.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
-			\caption{Viscosity obtained based on different correlations}
+			\caption{Viscosity obtained based on different correlations ({\color{red}Decrease space between figures})} 
             \label{fig: SFE_Properties_mu}
@@
 
-        Similarly, several correlations for thermal conductivity of $CO_2$ were compared on Figure
-        \ref{fig: SFE_Properties_kt}.
+        Similarly, several correlations for thermal conductivity of $CO_2$ were compared on Figure \ref{fig: SFE_Properties_kt}.
 The presented figures are focused around critical point, where the singularity is present.
 Similarities between specific heat and the thermal conductivity can be observed.
-Eventually, the NIST correlation were selected.
+The NIST correlation (\citet{Huber2016}) captures the singular behaviour of thermal conductivity around the critical point.
 The correlations are applicable for the temperature range from the triple point to 1100 $K$ and pressures up to 200 $MPa$.
@@
 			\includegraphics[trim = 1.5cm 2.5cm 1.5cm 2.0cm,clip,width=0.95\textwidth]{Figures/KT.pdf}	
-			\caption{Thermal conductivity obtained based on different correlations}
+			\caption{Thermal conductivity obtained based on different correlations }
             \label{fig: SFE_Properties_kt}

### 2023-03-09 SFE-article/Sections/Thermodynamic_details.tex
09.03

--- 2023-03-06 SFE-article/Sections/Model_2.tex
@@
 
-	We consider a conventional solid-fluid extraction process in which soluble essential oils are removed from a solid matrix of biomass in super-critical carbon dioxide.
-A conventional configuration in which the extraction process is operated in semi-continuous mode typically may consist of an extraction vessel followed by a separation unit, like a fluid-solid flash drum.
-In the illustrative diagram in Fig.
-\ref{fig: SFE_drawing}, the solvent ($\text{CO}_2$ in super-critical conditions) is circulated through the, extractor in which it gets in contact with finely chopped biomass arranged on a fixed-bed.
-In the extractor, the solute (the essential oils) is firstly transferred from the solid phase to the fluid phase, then separated downstream in the drum and collected for further processing.
-The solvent from the drum can be recovered and recycled into the process.
-In Fig.
-\ref{fig: SFE_drawing}, we also depict a typical instrumentation set-up used to configure the operating conditions of the process and to monitor and control it: The flow-rate ($F_\text{in}$) and the temperature ($T_\text{in}$) of the solvent entering the extractor are expected to be measured and adjustable, for example using a pump and a heat exchanger as actuators, respectively.
-Moreover, it is expected that the pressure ($P$) in the extractor is measured and adjustable, for example using a back-pressure regulator valve.
-Basic process regulation can be achieved with PID controllers whose set-points are manually provided, whereas a more advanced control strategy would include a supervisory controller to optimally determine the set-points.
-	\begin{figure}[h]
-		\begin{center}
-			\includegraphics[width=0.66\linewidth]{Figures/SFE_PFD_cropped.pdf}
-			\caption{Solid-fluid extraction process: Simplified process diagram and essential instrumentation.}
-			\label{fig: SFE_drawing}
-		\end{center}
-	\end{figure}
-
-	As solvent influent flow-rate and temperature, together with the pressure in the extractor, are understood as the main conditions that characterise the process from an operational point of view, we are interested in how these quantities affect the extraction process.
-More specifically, we are interested in understanding how they can be used in a supervisory control strategy based on a dynamic model of the extractor.
-The study is based on a forward sensitivity analysis (Section \ref{sec: State-space and sensitivity}) of a pragmatically designed model of the system.
-In Subsection \ref{subsec: Extraction model} and \ref{subsec: Measurement model}, the distributed-parameter model and the measurement model used for the task are presented.
-
-	\subsection{Extraction model} \label{subsec: Extraction model}
-	We consider an operational description of the fluid-solid extraction process in the extractor developed from a distributed-parameter model with three partial differential equations: Namely, two mass balance equations, relative to concentration of solute in the fixed solid phase and in the mobile fluid phase, and the heat balance equation, relative to the temperature of the fluid phase.
-We assume that the fluid, a mixture of solute and solvent, in the extractor can be treated as a pseudo-homogenous phase whose properties are those of the dominant component, the solvent.
-A single pseudo-component collectively representing the extract is also used.
-\\
-
-	For the convection of the fluid phase, we consider a plug-flow model of the velocity profile.
-Furthermore, we assume that no pressure drops and no heat losses occur along the extractor.
-We also limit the model to represent only axial diffusion for both mass and heat.
-As for the mass transfer from the solid to the fluid phase, an extraction term based on the two-film theory is used.
-Being the solid phase fixed, the convection and diffusion terms in the corresponding mass balance are both exlcuded.
-Similarly, we assume that the extraction is an isothermal process and exclude the generative term from the heat balance.
-The particle size distribution, and thus the void fraction of the solid phase, is assumed to be uniform in space and to remain constant in time.
-\\
-
-	Under these fairly general and simplifying assumptions, a macroscopic model of the extractor's bed reads
-
-	\begin{subequations}\begin{align}
-			\cfrac{\partial {\color{blue}c_{\text{F}}}(t,z)}{\partial t} &	= -\cfrac{1}{{\color{magenta}\varepsilon A}}\cfrac{{\color{red}F}(t)}{{\color{orange}\rho_\text{F}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]} \cfrac{\partial {\color{blue}c_{\text{F}}}(t,z)}{\partial{\color{blue}z}}
-			+ {\color{orange}D^M_{\text{eff}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] \cfrac{\partial^2 {\color{blue}c_{\text{F}}}(t,z)}{\partial {\color{blue}z^2}}
-			+ \cfrac{1-{\color{magenta}\varepsilon}}{{\color{magenta}\varepsilon}}{\color{blue}r_e}(t,z)	\label{eq: Model fluid} \\
-			\cfrac{\partial {\color{blue}c_{\text{S}}}(t,z)}{\partial t} &	= {\color{blue}r_e}(t,z)		\label{eq: Model solid} \\
-			\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} &	= -\cfrac{{\color{red}F}(t) {\color{orange}C_p^\text{F}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}{{\color{magenta}A} [(1-{\color{magenta}\varepsilon}){\color{orange}\rho_\text{F}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] {\color{orange}C_p^\text{F}} \left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] + {\color{magenta}\varepsilon}{\color{magenta}\rho_\text{S}}{\color{magenta}C_p^\text{S} } ]} \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}}
-			+ {\color{orange}D^T_{\text{eff}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] \cfrac{\partial^2 {\color{blue}T}(t,z)}{\partial {\color{blue}z^2}}	\label{eq: Model heat}
-		\end{align}\label{eq: SFE model}\end{subequations}
-
-	where ${\color{blue}c_{\text{F}}}(t,z)$, ${\color{blue}c_{\text{S}}}(t,z)$, and ${\color{blue}T}(t,z)$ denote respectively the concentration of solute in the fluid, concentration of solute in the solid, and temperature of the pseudo-homogeneous phase, all at axial positions $z \in [0,L]$ along the bed and at times $t \in [t_{\text{ini}},t_{\text{end}}]$.
-We use ${\color{magenta}A}$ to denote the cross-section of the bed, $L$ will be used to denote its length.
-The void fraction of the bed is denoted by ${\color{magenta}\varepsilon}$, whereas ${\color{magenta}\rho_\text{S}}$  and ${\color{magenta}C_p^\text{S} }$ are used to denote the density and the specific heat of the solid phase: These quantities are assumed to be known and to remain constant in space and time.
-We collectively denote these quantities as $\varphi_{\text{exp}} = \left(A,L,\varepsilon,\rho_{\text{S}},C^{\text{S}}_p\right)$.
-${\color{red}F}(t) = F_\text{in}(t)$ denotes the mass flow-rate through the extractor and ${\color{red}P}(t)$ its pressure: Together with the feed temperature $T(t,z=0) = T_{\text{in}}(t)$, these three variables define the process operating conditions and can be varied over time to control the extraction.
-\\
-
-	The density ${\color{orange}\rho_\text{F}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]$ of the fluid phase, the axial mass diffusion coefficient $ {\color{orange}D^M_{\text{eff}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t),\right]$, the specific heat ${\color{orange}C_p^\text{F}}\left[T(t,z),P(t)\right]$ of the fluid phase, and the axial heat diffusion coefficient ${\color{orange}D_{\text{eff}}^T}\left[T(t,z),P(t)\right]$ are assumed to change in space and over time, due to their dependence on the local temperature $T(t,z)$, and on pressure $P(t)$ and mass flow-rate $F(t)$.
-Similarly, the term ${\color{blue}r_e}(t,z)$ used to model the rate of extraction is assumed to vary in space and time, due to its dependence on the concentrations ${\color{blue}c_{\text{F}}}(t,z)$ and ${\color{blue}c_{\text{S}}}(t,z)$ of solute.
-\\
-
-	The differential model in Eq.
-\eqref{eq: SFE model} augments what commonly found in the literature ({\color{red}ADD REFS}) in relation to mass balances (Eq.
-\eqref{eq: Model fluid} and \eqref{eq: Model solid}), by adding a heat balance (Eq.
-\eqref{eq: Model heat}) to describe changes in the concentrations of solute and temperature due to a potentially varying temperature of the influent solvent and pressure in the extractor.
-Because of the generality of the formulation, conventional relationships commonly found in the literature can used to describe the extraction rate, density and heat capacity in the fluid phase, and the diffusion coefficients: The specific choices used in this study are overviewed in the following subsections.
-To describe the properties of the fluid phase and to account for the aforementioned dependencies, an equation of state must be selected: In Subsection \ref{subsubsec: Equation of state}, we overview how we used the Peng-Robinson's equation for this task.
-As for the extraction rate, we overview in Subsection \ref{subsubsec: Extraction rate}
+	\label{CH: Thermodynamic_details}
 
@@
 
-	In Peng-Robinson's equation, the compressibility ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ solves the third-order polynomial equation
-	\vskip-0.500cm
+	In Peng-Robinson's equation, the compressibility ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ solves the third-order polynomial equation \todo{reference to Cardano formula}
 
+	{\footnotesize	
 	\begin{equation}\label{eq: Compressibility}
 		{\color{orange}Z}^3 - \left[1 - {\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]\right] {\color{orange}Z}^2 + \left[{\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] - 2{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] - 3{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]^2\right] {\color{orange}Z} = 0,
-	\end{equation}
+	\end{equation} }
 
@@
 From an equation of state of the form ${\color{red}P}(t) {\color{orange}V_{\text{CO}_2}}\left[T(t,z),P(t)\right] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, we get
-
 	\begin{equation} \label{eq: Density}
@@
 	\end{equation}
-
 	where ${\color{magenta}M_{\text{CO}_2}}$ denotes the molar mass of $\text{CO}_2$ and ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ is the compressibility factor that solves Eq.
@@
 
-	\subsubsection{The extraction rate} \label{subsubsec: Extraction rate}
-	As the solvent flows through the extractor, the molecules of $\text{CO}_2$ occupy the pores of the particles of biomass and the molecules of solute diffuse from the particle through its pores and into the fluid bulk.
-We are interested in a macroscopic description of the extraction mechanism that allows to express the extraction term ${\color{blue}r_e}(t,z)$ in Eq.
-\eqref{eq: SFE model} in terms of the modelled concentrations, ${\color{blue}c_\text{S}}$ and ${\color{blue}c_\text{F}}$.
-The two-film theory ({\color{red}ADD REF}) of mass transfer between the solid and fluid phase is a conventional choice which is also commonly found in the literature.
-\\
-
-	\citet{Bulley1984} suggest that the rate of extraction $r_e$ is driven by the difference in solute concentration between the bulk, ${\color{blue}c_\text{F}}$, and at the pore's end of the solid-fluid interface (this quantity is un-modelled, we use ${\color{blue}c_\text{PI}^*}$ to denote it).
-\citet{Reverchon1996} suggests that the driving force is the concentration difference between the solid particles, ${\color{blue}c_\text{S}}$, and at the particle's end on the interface (also this quantity is un-modelled, we denote it ${\color{blue}c_\text{SI}^*}$).
-Concentrations ${\color{blue}c_\text{PI}^*}$ and ${\color{blue}c_\text{SI}^*}$, although unknown, are related to each other by the assumed equilibrium condition existing at the interface.
-The two approaches are virtually equivalent and, depending on whether \citet{Bulley1984} or \citet{Reverchon1996} is preferred, ${\color{blue}c_\text{PI}^*}$ or ${\color{blue}c_\text{SI}^*}$ must be expressed in terms of either $c_\text{S}$ or $c_\text{F}$ before inclusion in Eq.
-\eqref{eq: SFE model}.
-\\
-
-	For all positions along the bed and times, the extraction rate ${\color{blue}r_e}(t,z)$ gives to the rate at which the solute is transferred between phases.
-According to \citet{Reverchon1996}, ${\color{blue}r_e}(t,z)$ can be written in terms of an internal diffusion coefficient ${\color{orange}D_\text{int}}$: We follow this approach and extend it to allow for ${\color{orange}D_\text{int}}$ to depend on temperature $T(t,z)$ and possibly pressure $P(t)$.
-Multiple alternatives are available in the literature to represent dependence of ${\color{orange}D_\text{int}}$ on $T$ and $P$ (\ref{Asubsec: D_int} overviews some of them and presents the Arrhenius-type relation used in this study): It is important to note that, in general, a number of parameters collectively denoted by $\varphi_{D_\text{int}}$ is used to characterise the specific relation.
-More directly, the rate is also dependent on parameters $\varphi_{r_e}$ that account for properties of the particles like sphericity (the shape coefficient ${\color{magenta}\mu}$) and characteristic dimension ${\color{magenta}l}$.
-Specifically, we have
-	\begin{equation} \label{eq: Model_kinetic_basic}
-		{\color{blue}r_e}(t,z) = \cfrac{{\color{orange}D_\text{int}}\left[{\color{blue}T}(t,z),P(t) \mid \varphi_{D_\text{int}}\right]}{{\color{magenta} \mu l^2} }\left[{\color{blue}C_\text{S}}(t,z) - {\color{blue}C_\text{SI}^*}(t,z) \right].
-	\end{equation}
-	According to the internal resistance model, ${\color{blue}C_\text{SI}^*}(t,z)$ can be expressed as a function of $C_\text{F}(t,z)$: That is, $C^*_\text{SI}(t,z)=C^*_\text{SI}\left(C_\text{F}(t,z)\right)$.
-Again, we follow \citet{Reverchon1996} who pragmatically suggests the linear relationship
-	\begin{equation} \label{eq: Linear equilibrium}
-		{\color{blue}C_\text{F}}\left(t,z\right) = {\color{orange}k_p}\left[{\color{blue}T}\left(t,z\right),{\color{red}P}\left(t\right)\right] {\color{blue}C_\text{SI}^*}\left(t,z\right),
-	\end{equation}
-	where ${\color{orange}k_p}\left[{\color{blue}T}\left(t,z\right),{\color{red}P}(t)\right]$ is the volumetric partition coefficient, which we allow to depend on temperature and pressure.
-Also in this case, the literature offers multiple options to represent this dependence ({\color{red}ADD REFS}).
-To be consistent with \citet{Reverchon1996}, we consider the relation established by \citet{Spiro2007} in which $k_p$ is given in terms of the massic partition factor ${\color{orange}k_m}$, a quantity which we also allow to be dependent on temperature $T(t,z)$ and parameters $\varphi_{k_m}$ (see \ref{Asubsec: k_m} for a description of the relationship used in this study), as well as on the densities $\rho_{\text{F}}$ (defined earlier in Subsection \ref{subsubsec: Equation of state}) and $\rho_{\text{S}}$ of the fluid and solid phase, respectively:
-	\begin{equation} \label{eq: k_m}
-		{{\color{orange}k_p}\left[{\color{blue}T}\left(t,z\right),{\color{red}P}(t) \mid \varphi_{k_m}, \varphi_{\rho_\text{F}}\right] {\color{magenta}\rho_\text{S}}} = {\color{orange}k_m}\left[{\color{blue}T}\left(t,z\right) \mid \varphi_{k_m}\right] {{\color{orange}\rho_\text{F}}\left[{\color{blue}T}\left(t,z\right),{\color{red}P}\left(t\right) \mid \varphi_{\rho_\text{F}}\right]}.
-	\end{equation}
-
-	Summarising, we get the formulation of the extraction rate with all its functional dependences and parameters 
-	\begin{multline}\label{eq: Model_kinetic}
-		{\color{blue}r_e}(t,z \mid \varphi_{r_e}, \varphi_{D_\text{int}}, \varphi_{k_m}, \varphi_{\rho_\text{F}}) = \\ 
-		-\cfrac{{\color{orange}D_\text{int}}\left[{\color{blue}T}(t,z), P(t) \mid \varphi_{D_\text{int}}\right]}{{\color{magenta} \mu l^2} }\left[{\color{blue}C_\text{S}}(t,z) - \cfrac{{\color{magenta}\rho_\text{S}}}{{\color{orange}k_m}\left[{\color{blue}T}(t,z) \mid \varphi_{k_m}\right]{\color{orange}\rho_\text{F}}\left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid \varphi_{\rho_\text{F}}\right]} {\color{blue}C_\text{F}}(t,z) \right].
-	\end{multline}
-	%
-	\subsubsection{Diffusion coefficients} \label{subsubsec: Diffusion coefficients}
-
-	\noindent\textbf{Mass diffusion} 
-	\begin{equation}
-		{\color{orange}D_{\text{eff}}^M} \left[{\color{blue}T}(t,z), {\color{red}P}(t), {\color{red}F}(t)\right] = \cfrac{{\color{orange}u}\left[{\color{blue}T}(t,z), {\color{red}P}(t), {\color{red}F}(t)\right] {\color{magenta}d_p}}{{\color{magenta}\varepsilon} {\color{orange}\text{Pe}}\left[{\color{blue}T}(t,z), {\color{red}P}(t),{\color{red}F}(t)\right]}
-	\end{equation}
-	where ${\color{orange}u}\left[{\color{blue}T}(t,z), {\color{red}P}(t), {\color{red}F}(t)\right]$ is the superficial velocity in the axial direction, ${\color{magenta}\varepsilon}$ denotes the bed's porosity, and ${\color{magenta}d_p}$ denotes the particle diameter.
-${\color{orange}\text{Pe}}\left[{\color{blue}T}(t,z), {\color{red}P}(t),{\color{red}F}(t)\right]$ is the Peclet's number and it is evaluated as the function of temperature, pressure and flow-rate as
-
-	\begin{equation}
-		{\color{orange}\text{Pe}}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] = \cfrac{{\color{magenta}\widehat{a}}}{{\color{magenta}\varepsilon}} + \cfrac{{\color{magenta}\widehat{b}}}{{\color{magenta}\varepsilon}}({\color{magenta}\varepsilon}{\color{orange} \text{Re}}\left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t) \right]^{\color{magenta}{\widehat{c}}}
-	\end{equation}
-	where ${\color{magenta}\hat{a}}$, ${\color{magenta}\hat{b}}$, and ${\color{magenta}\hat{c}}$ are the correlation's parameters.
-${\color{orange}\text{Re}}$ is the Reynolds number, also determined as the function of temperature, pressure and feed flow-rate ${\color{orange}\text{Re}}\left[{\color{blue}T}(t,z), {\color{red}P}(t),{\color{red}F}(t)\right]$
-	\begin{equation}
-		{\color{orange}\text{Re}} \left[{\color{blue}T}(t,z), {\color{red}P}(t),{\color{red}F}(t)\right] = \cfrac{{\color{orange}\rho_\text{F}} \left[{\color{blue}T}(t,z), {\color{red}P}(t); {\color{magenta}\theta_\rho}\right] {\color{orange}u}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)) }{{\color{orange} \eta}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}
-	\end{equation}
-
-	where ${\color{orange}\eta} ({\color{blue}T}(t,z),{\color{red}P}(t))$ is the viscosity of the solvent, also dependent on temperature and pressure. \\
-
-	%\begin{table}
-	%	\begin{center}
-		%		\caption{Axial mass diffusion: Parameters}
-		%		\label{tab: Axial_Mass_Diffusion}
-		%		\begin{tabular}{c c | c  c}
-			%			\hline
-			%			${\color{magenta}\hat{a}}$	& -105.161	& ${\color{magenta}\hat{b}}$	&  0.9007	\\
-			%			${\color{magenta}\hat{c}}$ 	&  0.0007	&  								& 			\\
-			%			\hline	
-			%		\end{tabular}
-		%	\end{center}
-	%\end{table}
-
-	\noindent \textbf{Thermal diffusion} 
-	The thermal diffusion coefficient ${\color{orange}D_{\text{eff}}^T}$ of the pseudo-homogeneous fluid phase is assumed to be equal to that of pure carbon dioxide, at given temperature and pressure.
-By definition, we have%
-	\begin{equation}
-		{\color{orange}D_{\text{eff}}^T} \left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] = \cfrac{{\color{orange}k_t}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{{\color{orange}\rho_{\text{F}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi_{\rho_{\text{F}}}\right] {\color{orange}C_p^{\text{F}}} \left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid \varphi_{C_p^{\text{F}}}\right]}
-	\end{equation}
-	where ${\color{orange}C^{\text{F}}_p}[{\color{blue}T}(t,z),{\color{red}P}(t) \mid \varphi_{C_p^{\text{F}}}]$ and $\rho_{\text{F}}\left[{\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi_{\rho_{\text{F}}} \right]$ are the specific heat of $\text{CO}_2$ at constant pressure and its density discussed earlier, while ${\color{orange}k_t}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]$ is the thermal conductivity, again assumed to depend on temperature and pressure and parameters $\varphi_{k_t}$ specific of the chosen form of the dependence: We use the correlation suggested by \citet{Amooey2014} for supercritical $\text{CO}_2$ (in \ref{Asubsubsec: k_t}), though alternatives exist {\color{red}ADD REFS}.
-\\
-
-	\noindent\textbf{Viscosity} 
-	%
-	%The viscosity of the solvent ($\text{CO}_2$) is expressed as a function of temperature and pressure using the expression proposed by \citet{Heidaryan2011}.
-The relationship is valid in the supercritical region for temperatures $T \in [313.15, 523.15]$ $[\text{K}]$ and pressures $P \in [7.7, 81.1]$ $[\text{MPa}]$
-	%
-	\begin{equation}
-		{\color{orange}\eta} ({\color{blue}T}(t,z),{\color{red}P}(t) | {\color{magenta}\theta_\eta}) = \cfrac{\sum_{i=1}^{3}{{\color{magenta}\beta_i}{\color{red}P}^{i-1}(t)} + \sum_{i=4}^{6}{{\color{magenta}\beta_i}\ln({\color{blue}T}(t,z))^{i-3}}}{1 + {\color{magenta}\beta_7}{\color{red}P}(t) + {\color{magenta}\beta_8} \ln({\color{blue}T}(t,z)) + {\color{magenta}\beta_9}\ln({\color{blue}T}(t,z))^2}
-	\end{equation}
-	%
-	%with parameters ${\color{magenta}\theta_\eta} = ({\color{magenta}\beta_1}, \dots, {\color{magenta}\beta_9})$ reported in Table \ref{tab: Viscosity_beta}
-	%\begin{table}[pos=h!]
-	%	\begin{center}
-		%		\caption{Viscosity: Parameters ${\color{magenta}\theta_\eta}$.}
-		%		\label{tab: Viscosity_beta}
-		%		\begin{tabular}{c c | c  c}
-			%			\hline
-			%			${\color{magenta}\beta_1}$	& -1.1461E-01	& ${\color{magenta}\beta_2}$	&  6.9784E-07	\\
-			%			${\color{magenta}\beta_3}$  &  3.9768E-10	& ${\color{magenta}\beta_4}$	&  6.3360E-02	\\
-			%			${\color{magenta}\beta_5}$	& -1.1660E-02	& ${\color{magenta}\beta_6}$	&  7.1426E-04	\\
-			%			${\color{magenta}\beta_7}$	&  6.5190E-06	& ${\color{magenta}\beta_8}$	& -3.5680E-01	\\
-			%			${\color{magenta}\beta_9}$	&  3.1800E-02	&								&				\\
-			%			\hline	
-			%		\end{tabular}
-		%	\end{center}
-	%\end{table}
-	%
-	\newpage\subsection{Measurement model} \label{subsec: Measurement model}
-	%The efficiency of the process (the yield) is calculated according to equation \ref{Model_measurment}.
-The yield is defined as the ratio between a difference of initial solute's mass in the solid phase ${\color{magenta}m_0}$, and an actual amount of solute in the same phase ${\color{blue}m}$, compared to the initial amount of the solute in the fixed bed ${\color{magenta}m_0}$.
-The yield can also be calculated based on the change of solutes concentration in the solid phase if the volume of the extractor ${\color{magenta}V}$ is constant.
-	%An output function ${\color{blue}y}(t)$ returns a yield curve that represents the fraction of the solute's mass over time.
-The yield is obtained by function ${\color{blue}g}({\color{blue}q}(t,z))$.
-Function ${\color{blue}g}({\color{blue}q}(t,z))$ corresponds to a 'measurement device' that allows to calculate the yield based on the state variable ${\color{blue}q}(t,z)$.
-	%
-	%\begin{align} 
-	%		\label{Model_measurment}
-	%		{\color{blue}y}(t) ={\color{blue}g}({\color{blue}q}(t,z)) &= \cfrac{ \left({\color{magenta}m_0} - {\color{blue}m}({\color{blue}q}(t,z)) \right) }{{\color{magenta}m_0}} = \cfrac{ {\color{magenta}V} \left({\color{magenta}q_0} - {\color{blue}q}(t,z) \right) }{{\color{magenta}V q_0}}
-	%\end{align}
-	%
-	%where ${\color{blue}q}(t,z)$ is concentration of solute in a solid phase and a temperature, respectively.
-${\color{magenta}m_0}$ is a initial mass of the solute in the solid phase, ${\color{magenta}q_0}$ is a  initial concentration of the solute in the solid phase, ${\color{magenta}V}$ is an extractor volume.
-	%
+	\todo[]{Add internal energy equation}
 

### 2023-03-09 SFE - EmptySpace/main_Opt_EmptySpace.m

@@ -11,8 +11,6 @@ import casadi.*
 DATA_set                = {'LUKE_T40_P200','LUKE_T50_P200','LUKE_T40_P300','LUKE_T50_P300'};
 Parameters_table        = readtable('Parameters.csv') ;        % Table with prameters
 
-DATA_K_OUT=nan(5,4);                                           % Store Parameters obatined from all fits (par num x num exper)
-
 %% Set time of the simulation
 PreparationTime         = 0;
 ExtractionTime          = 150;
@@ -104,6 +102,8 @@ Nx                      = 4*nstages+1;
 Nu                      = 3 + numel( Parameters_table{:,3} );
 Nk                      = numel(which_k)+1;
 
+DATA_K_OUT              = nan(Nk,numel(DATA_set));                               % Store Parameters obatined from all fits (par num x num exper)
+
 %% symbolic variables
 % Create symbolic variables
 x                       = MX.sym('x', Nx);
@@ -172,7 +172,7 @@ parfor ii=1:numel(DATA_set)
 
     % Descision variables
     k                       = OPT_solver.variable(Nk);
-    k_lu                    = [ [0;0.01;0.01;0;0] , [2;10;1;10;100] ];
+    k_lu                    = [ [0;0.01;0.01;0;0] , [2;10;1;10;inf] ];
     % Constraints
     for nk=1:Nk
         OPT_solver.subject_to( k_lu(nk,1) <= k(nk,:) <= k_lu(nk,2) );
@@ -183,8 +183,12 @@ parfor ii=1:numel(DATA_set)
     Parameters_sym       = MX(Parameters);           % Vector of paraneters in the form casadi vector
     % Decide which parameters are decision variabales
 
-    Parameters_sym(which_k) = k(1:4);
-    sigma = k(5);
+    Parameters_sym(which_k) = k(1:numel(which_k));
+
+    if numel(which_k) < Nk
+        sigma = k(5);
+    end
+
 
     % Store symbolic results of the simulation
     X = MX(Nx,N_Time+1);
@@ -200,19 +204,18 @@ parfor ii=1:numel(DATA_set)
     Yield_estimate_diff = diff(Yield_estimate);
 
     %% Create the cost function
[…]

### 2023-03-10 SFE-article/Article_Model_Parameters.tex
10.03

@@
 \usetikzlibrary{shapes.geometric,angles,quotes,calc}
+
+\usepackage[final]{pdfpages}
 
@@
 
-The quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates is given be equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_2}.
+The quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates is given be equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_3}.
 
@@
         \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
-        \cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \\
+        \cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} {EQ: CompressibleEuler_2} \\
         \cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T}{\partial z} \right)
-        \label{EQ: CompressibleEuler_2}
+        \label{EQ: CompressibleEuler_3}
     \end{align}  
@@
 
-\section{Results} \label{CH: Results}
+\subsection{Experimental work}
+\subfile{Sections/Experiments}
+
+\section{Results}
+\subfile{Sections/Results}
 
@@
 
-%\subsection{Bayes theorem} \label{CH: Bayes}
-%\subfile{Sections/Bayes_Theorem}
+\subsection{Bayes theorem} \label{CH: Bayes}
+\subfile{Sections/Bayes_Theorem}
+
+\clearpage
+\onecolumn
+\subsection{Solid density measurement} \label{CH: Solid_Density_Measurment}
+
+\begin{figure*}[b!]
+	%\centering 
+	\includegraphics[trim=0cm 6cm 0cm 0cm, clip,height=0.9\textheight]{Sections/ultraReportT5.pdf}
+	\caption{The result of solid density measurement}
+\end{figure*}
 

### 2023-03-10 SFE-article/Sections/Experiments.tex
10.03

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Experiments}

	The close the optimization problem given by set of equations \ref{EQ: Optimization_formulation_MLE}, it is require to know the dataset $Y(t)$. In this case, the dataset have been obtained by performing extraction of caraway oil from caraway seeds. The caraway seeds have been obtained from the company Caraway Finland\todo{Should be mentioned?} during 2022 growing season. The caraway seeds have been pre-treated with Retsch SM 300 cutting mill to decrease the particle size to 1mm and break the outer shell of the seeds. Later, the moisture content was analysed to ensure that it does not have a negative effect on the extraction process. An Infrared Moisture Analyser was used to investigate the sample. The moisture content after grinding was 4.83\%. The grind material density was measured by pyncometery and its result can be found in appendix \ref{CH: Solid_Density_Measurment}

	The unit used for the experimental work is 10 litre extractor \todo{Should Biorukki be mentioned?} with inner diameter around 15 cm and 60 cm height \todo{Double check dimension}. Four experiments have been performed in that unit at following operating conditions: $40^\circ C / 200$ bar, $50^\circ C / 200$ bar, $40^\circ C / 300$ bar and $50^\circ C / 300$ bar. 1 kg of grind material was weighted and placed in the extraction chamber. Due to some technical limitations, the amount of solid material fro extraction was selected to be 1 kg per batch, which is not sufficient to fill the whole chamber.

	After the material was loaded into chamber, the extractor is pre-heated to desired temperature. The next step is to close the outlet line coming out of the extractor and fill the extraction chamber with $CO_2$. The $CO_2$ is pumped and compressed until the operating pressure is achieved. When the operating temperature and pressure are obtained, the outlet in is open to allow the solvent flow through the system. The solvent extract essential oils from the fixed bed of solid material and the mixture $CO_2$-oil flow from the extractor to separator. The separator was operating at $50^\circ C$ and $50$ bar. At this condition the $CO_2$ is gasified and leave from the top, while oil stays in the liquid form and it is collected at the bottom of separator. Every 5 minutes, the oil is drained from the separator and its weight is measured. The amount of oil collect during a batch is an output of the experiment and it is used as data for parameter estimation. The extraction time for each batch was 150 minutes, counted from the opening of the extractor outlet port.

	The result of the experiment are presented in the table \ref{tab: Yield_data}.

	\begin{table}[H]
		\centering
		\begin{tabular}{c|cccc}
			& $40 ^\circ C / 200$ bar & $50 ^\circ C / 200$ bar & $40 ^\circ C / 300$ bar & $50 ^\circ C / 300$ bar \\ 
			Time min & Mass g                  & Mass g                  & Mass g                  & Mass g                  \\ \hline
			0        & 0.0                     & 0.0                     & 0.0                     & 0.0                     \\
			5        & 2.3                     & 1.8                     & 1.1                     & 1.2                     \\
			10       & 5.9                     & 5                       & 4.7                     & 4.5                     \\
			15       & 11.4                    & 8.6                     & 10.8                    & 11.3                    \\
			20       & 17.7                    & 13.7                    & 20.6                    & 20.6                    \\
			25       & 24.4                    & 18.3                    & 32.1                    & 30.6                    \\
			30       & 30.4                    & 22.3                    & 40.5                    & 37.8                    \\
			35       & 34.1                    & 26.4                    & 46.7                    & 43.3                    \\
			40       & 37.6                    & 30.2                    & 50.5                    & 47.5                    \\
			45       & 40.2                    & 33.8                    & 53.1                    & 50.8                    \\
			50       & 43.4                    & 37.3                    & 55.5                    & 53.7                    \\
			55       & 45.6                    & 40.9                    & 57.6                    & 56.5                    \\
			60       & 47.7                    & 44.2                    & 59.3                    & 58.1                    \\
			65       & 49.3                    & 46.8                    & 60.9                    & 59.6                    \\
			70       & 50.9                    & 49.1                    & 62.2                    & 61.1                    \\
			75       & 52.7                    & 50.9                    & 63.7                    & 62.7                    \\
			80       & 54.3                    & 52.6                    & 64.9                    & 64.4                    \\
			85       & 55.2                    & 54                      & 66.6                    & 65.8                    \\
			90       & 56.3                    & 55.4                    & 67.6                    & 66.7                    \\
			95       & 57.4                    & 56.6                    & 68.9                    & 67.4                    \\
			100      & 58.4                    & 57.8                    & 69.7                    & 68.2                    \\
			105      & 59.5                    & 58.6                    & 70.6                    & 69.1                    \\
			110      & 60.4                    & 59.8                    & 71.2                    & 70.1                    \\
			115      & 61.5                    & 60.9                    & 71.9                    & 70.9                    \\
			120      & 62.6                    & 62.1                    & 72.3                    & 71.6                    \\
			125      & 63.4                    & 63                      & 72.8                    & 72.3                    \\
			130      & 64.1                    & 64.1                    & 73.2                    & 72.9                    \\
			135      & 64.9                    & 65.1                    & 73.6                    & 73.5                    \\
			140      & 65.6                    & 66                      & 74                      & 74                      \\
			145      & 66.3                    & 66.9                    & 74.3                    & 74.5                    \\
			150      & 66.9                    & 67.7                    & 74.6                    & 74.9                   
		\end{tabular}
	\caption{Yield data}
	\label{tab: Yield_data}
	\end{table}

\end{document}

### 2023-03-10 SFE-article/Sections/Model.tex
10.03

@@
         			xlabel = {$c_f[kg/m^3]$},
-        			ylabel = {$\Gamma(c_f)[-]$}]
+        			ylabel = {$\gamma(c_f)[-]$}]
         			\addplot[
@@
 
-        {\color{blue} The heat equation was introduced in the previous chapter.
-The heat balance describe movement of the internal energy in the system.
+		\todo[inline]{Draft of new heat equation starts here. TODO: \\ Check if the heat cpacity of solid phase needs to be added \\ Elaborate why pressure is know}
+
+		\noindent\colorbox{pink}
+		{
+		\begin{minipage}{\columnwidth}
+			The heat equation was introduced in the previous chapter through equation \ref{EQ: CompressibleEuler_3} or
+
+			{\footnotesize
+			\begin{equation*}
+				\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} = -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T}{\partial z} \right)
+			\end{equation*}
+			}
+
+			For real gases the internal energy is defined as
+
+			{\footnotesize
+				\begin{equation}
+					de=C_vdT-\left[P-T\left(\cfrac{\partial P}{\partial T}\right)_{V_m}\right]dv_m
+					\label{EQ: internal_energy_def}
+				\end{equation} }
+
+			If a gas is consider to be perfectly caloric ($e=C_v T$), then the energy equation can be written in form of temperature.
+The perfectly caloric gas can be seen as the special case of a real gas, where the second term of the equation \ref{EQ: internal_energy_def} goes to zero.
+
 			For real gases it is complicated to write the heat balance in terms of temperature.
-Alternatively, the temperature can be obtained based on the equation of state if the internal energy and pressure are know.
-A roootfinder can be used to find a value of temperature, which satisfy the equation of state given values of internal energy and pressure.
-The temperature needs to be reconstructed from the internal energy in every time-step.
+Alternatively, the energy equation can be used in the form of internal energy, so as it is given by equation \ref{EQ: CompressibleEuler_3}.
+In such a case, the temperature (which is used as the input to some other functions) needs to be recover from the internal energy.
+A relation for the internal energy can be obtained from an equation of state.
+For Peng-Robinson, such a relation is given by equation \ref{EQ: internal_energy_PR}
+
+			{\footnotesize
+				\begin{equation}
+					e = C_vT + \cfrac{a\left(\alpha -T\cfrac{d \alpha}{dT}\right)}{2\sqrt{2}b} \ln \left[ \cfrac{1+b\left(1-\sqrt{2}\rho\right) }{1+b\left(1+\sqrt{2}\rho\right)} \right]
+					\label{EQ: internal_energy_PR}
+				\end{equation}
 			}
+
+			To solve equation \ref{EQ: internal_energy_PR}, values of temperature, pressure and density needs to be know.
+If an equation of state is introduce, then only 2 out 3 variables needs to be know as the third one can be calculated, this can be represented as follow
+
+			{\footnotesize
+			\begin{equation*}
+				e(t,z)=e(T(t,z),P(t),\rho(t,z))=e(T(t,z),P(t),\underbrace{\rho(T(t,z),P(t))}_{E.O.S.}) 
+			\end{equation*}
+			}
+
+			If the value of internal energy $e$ is know from time evolution of the energy equation (\ref{EQ: CompressibleEuler_3}), and pressure is know from measurement, then the temperature can be reconstructed.
+A roootfinder can be used to find a value of temperature, which minimize the difference between value of internal energy coming from the time evolution and the output from equation \ref{EQ: internal_energy_PR}.
+Such a procedure allow to find local temperature along spatial direction $z$ and needs to be repeated every time-step.
+
+		\end{minipage} }
+
+		\todo[inline]{Add short section about boundary conditions and comment on the used numerical methods}
 

### 2023-03-10 SFE-article/Sections/Parameter_estimation.tex
10.03

@@
 
-\subsection{Least squares estimation}
+\subsubsection{Least squares estimation}
 A least squares parameter estimation does not require prior knowledge of the distribution of unobservable errors, yield  unbiased estimates, and results in the minimum variance among all linear unbiased estimators.
@@
 \iffalse
-\subsection{Weighted sum of squares - Cumulative data}
+\subsubsection{Weighted sum of squares - Cumulative data}
 
@@
 
-\subsection{Maximum likelihood estimation}
+\subsubsection{Maximum likelihood estimation}
 
@@
 In effect, the methods selects those values of $\theta$ that are at least as likely to generate the observed sample as any other set of values of the parameters if the probability density of $y$ were to be extensively simulated through use of the probability density $p\left( y|\theta \right)$.
-In making a maximum likelihood estimate, we assume that the form of the probability density (\sout{only the $\theta$ need be determined}) and that all possible values of $\theta$ are equally likely before experimentation.
+In making a maximum likelihood estimate, we assume the form of the probability density and that all possible values of $\theta$ are equally likely before experimentation.
 \todo{Needed?}
@@
 			\begin{equation}
-				\begin{aligned}
+				\begin{aligned} \label{EQ: Optimization_formulation_MLE}
 					&\hat{\theta}_{MLE} &= \arg \max_{\sigma, \theta \in \Theta} \ln L = \arg \max_{\sigma,\theta \in \Theta} p(\theta|y) \\
@@
 
-		{\color{red}Based on the first order optimality condition,} the $\ln L$ can be maximized with respect to the vector $\theta$ by equating to zero the partial derivatives of $\ln L$ with respect to each of the parameters:
+		Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector $\theta$ by equating to zero the partial derivatives of $\ln L$ with respect to each of the parameters:
 

### 2023-03-10 SFE-article/Sections/Results.tex
10.03

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Results}

	Some results of the parameter estimations

	\begin{figure*}
		\centering
		\begin{subfigure}[b]{0.7\textwidth}
			\centering
			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Weighted_Yield_LUKE_T40_P200_F0.41_No_Delay.pdf}
			\caption{Experiment at $40^\circ C$ and $200$ bar}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.7\textwidth}
			\centering
			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Weighted_Yield_LUKE_T50_P200_F0.41_No_Delay.pdf}
			\caption{Experiment at $50^\circ C$ and $200$ bar}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.7\textwidth}
			\centering
			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Weighted_Yield_LUKE_T40_P300_F0.41_No_Delay.pdf}
			\caption{Experiment at $40^\circ C$ and $300$ bar}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.7\textwidth}
			\centering
			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Weighted_Yield_LUKE_T50_P300_F0.41_No_Delay.pdf}
			\caption{Experiment at $50^\circ C$ and $300$ bar}
		\end{subfigure}
		\caption{Results of parameter fitting, without estimation of the initial state}
	\end{figure*}

\end{document}

### 2023-03-10 SFE-article/Sections/Thermo.tex
10.03

@@
 
-    where $A$ and $B$ are parameters as defined in the appendix.
+    where $A$ and $B$ are parameters as defined in the appendix (\ref{CH: Thermodynamic_details}).
 The roots of the polynomial can be found iteratively or by Cardano formula.
@@
 			\centering
-			\includegraphics[trim = 1.5cm 4.0cm 2.5cm 10.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
-			\caption{Viscosity obtained based on different correlations ({\color{red}Decrease space between figures})} 
+			\includegraphics[trim = 1.5cm 11.5cm 2.5cm 10.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
+			\includegraphics[trim = 1.5cm 4.0cm 2.5cm 19.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
+			\caption{Viscosity obtained based on different correlations } 
             \label{fig: SFE_Properties_mu}

### 2023-03-10 SFE-article/Sections/Thermodynamic_details.tex
10.03

@@
 	{\footnotesize	
-	\begin{equation}\label{eq: Compressibility}
-		{\color{orange}Z}^3 - \left[1 - {\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]\right] {\color{orange}Z}^2 + \left[{\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] - 2{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] - 3{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]^2\right] {\color{orange}Z} = 0,
-	\end{equation} }
+	\begin{align}\label{eq: Compressibility}
+		&{\color{orange}Z}^3 - \left[1 - {\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]\right] {\color{orange}Z}^2 \\ \nonumber
+		&+ \left[{\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] - 2{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] - 3{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]^2\right] {\color{orange}Z} = 0
+	\end{align} }
 
@@
 Specifically, we have
-	\vskip-0.250cm
+
+	{\footnotesize
 	\begin{subequations} \label{eq: PR_AB}
@@
 		\end{align}
-	\end{subequations}
-	The quantity ${\color{orange}\alpha}\left[{\color{blue}T}\left(t,z\right)\right]= \left[1 + {\color{magenta}\kappa_{\text{CO}_2}} \left[1 - \sqrt{{\color{blue}T}\left(t,z\right) / {\color{magenta}T^c_{\text{CO}_2}}} \right] \right]^2$, with constant ${\color{magenta}\kappa_{\text{CO}_2}} = 0.37464 + 1.54226 {\color{magenta}\omega_{\text{CO}_2}} - 0.26992 {\color{magenta}\omega_{\text{CO}_2}}^2$, is a dimensionless correction term defined on the acentric factor ${\color{magenta}\omega_{\text{CO}_2}} = 0.239$ of $\text{CO}_2$ molecules.
+	\end{subequations}}
+
+	The quantity {\small${\color{orange}\alpha}\left[{\color{blue}T}\left(t,z\right)\right]= \left[1 + {\color{magenta}\kappa_{\text{CO}_2}} \left[1 - \sqrt{{\color{blue}T}\left(t,z\right) / {\color{magenta}T^c_{\text{CO}_2}}} \right] \right]^2$}, with constant ${\color{magenta}\kappa_{\text{CO}_2}} = 0.37464 + 1.54226 {\color{magenta}\omega_{\text{CO}_2}} - 0.26992 {\color{magenta}\omega_{\text{CO}_2}}^2$, is a dimensionless correction term defined on the acentric factor ${\color{magenta}\omega_{\text{CO}_2}} = 0.239$ of $\text{CO}_2$ molecules.
 \\
 
-	By denoting the physical constants as $\varphi_{Z} = \left(R,T^c_{\text{CO}_2},P^c_{\text{CO}_2},\kappa_{\text{CO}_2}\right)$, we obtain a spatio-temporal representation of the compressibility ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi_{Z}\right]$ with its complete set of functional dependencies and parameters.
+	By denoting the physical constants as {\small$\varphi_{Z} = \left(R,T^c_{\text{CO}_2},P^c_{\text{CO}_2},\kappa_{\text{CO}_2}\right)$}, we obtain a spatio-temporal representation of the compressibility ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi_{Z}\right]$ with its complete set of functional dependencies and parameters.
 \\
 
-	%\subsubsection{Density of the fluid phase} \label{subsubsec: Fluid density}
-	\noindent \textbf{Density of the fluid phase} \\
+	\subsubsection{Density of the fluid phase} \label{subsubsec: Fluid density}
+	%\noindent \textbf{Density of the fluid phase} \\
 
@@
 From an equation of state of the form ${\color{red}P}(t) {\color{orange}V_{\text{CO}_2}}\left[T(t,z),P(t)\right] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, we get
+
+	{\footnotesize
 	\begin{equation} \label{eq: Density}
 		{\color{orange}\rho_{\text{F}}} \left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid {\color{magenta}\varphi_{\rho_{\text{F}}}}\right] = \dfrac{{\color{red}P}(t) {\color{magenta}M_{\text{CO}_2}}}{{\color{magenta}R}{\color{blue}T}(t,z){\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid \varphi_{Z}\right]},
-	\end{equation}
+	\end{equation} }
+
 	where ${\color{magenta}M_{\text{CO}_2}}$ denotes the molar mass of $\text{CO}_2$ and ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ is the compressibility factor that solves Eq.
@@
 
-	%\subsubsection{Heat capacity of the fluid phase} \label{subsubsec: Fluid heat capacity}
-	\noindent\textbf{Heat capacity of the fluid phase} \\
+	\subsubsection{Heat capacity of the fluid phase} \label{subsubsec: Fluid heat capacity}
+%	\noindent\textbf{Heat capacity of the fluid phase} \\
 
 	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term {\color{red}REF}.
-In the following, we report only the main steps in the derivation of ${\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$: Step-by-step derivations using the Peng-Robinson's equation are given in Appendix {\color{red}REF}.
-\\
+In the following, we report only the main steps in the derivation of ${\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$: Step-by-step derivations using the Peng-Robinson's equation are given.
+\todo{Add step-by-step derivation} \\
 
 	At given temperature and pressure, for $\text{CO}_2$ we have
+
+	{\footnotesize
 	\begin{subequations}\begin{align}
@@
 } \eqref{eq: Cp_R}}  \label{eq: Cp_CO2}.
-	\end{align}\end{subequations}
+	\end{align}\end{subequations} }
+
 	${\color{orange}C^{\text{CO}_2}_v}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are the specific heat of $\text{CO}_2$ at constant volume and pressure, respectively.
@@
 
-	For $CO_2$ {\color{red}REF}, we have the ideal gas contribution to the specific heat at constant $P(t)$, as function of $T(t,z)$,
+	For $CO_2$ ()\todo[fancyline]{Add REF}, we have the ideal gas contribution to the specific heat at constant $P(t)$, as function of $T(t,z)$,
+
+	{\footnotesize
 	\begin{equation}
 		{\color{orange}C_p^{\text{I}}}\left[{\color{blue}T}(t,z),P(t)\right] = {\color{magenta}C_{P0}} + {\color{magenta}C_{P1}}T(t,z) + {\color{magenta}C_{P2}}{\color{blue}T}^2(t,z) + {\color{magenta}C_{P3}}{\color{blue}T}^3(t,z) \label{eq: Cp_I}
-	\end{equation}
+	\end{equation} }
+
 	where the coefficients of the expansion are ${\color{magenta}C_{P0}} = 4.728$, ${\color{magenta}C_{P1}} = 1.75 \times 10^{-3}$, ${\color{magenta}C_{P2}} = -1.34 \times 10^{-5}$, and ${\color{magenta}C_{P3}} = 4.10 \times 10^{-9}$.
 For the correction term ${\color{orange}C_p^{\text{R}}}\left[{\color{blue}T}(t,z){\color{red}P}(t)\right]$ at constant pressure $P(t)$, we have
-	\begin{equation}
-		{\color{orange}C_p^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] = \underbrace{{\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}_{\text{Eq.
-}\eqref{eq: CvR}} + {\color{blue}T}(t,z) \underbrace{\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}V_{\text{CO}_2}}(t,z)}}_{\text{Eq.
+
+	{\footnotesize	
+	\begin{align}
+		&{\color{orange}C_p^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] = \underbrace{{\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}_{\text{Eq.
+}\eqref{eq: CvR}} \nonumber \\
+		&+ {\color{blue}T}(t,z) \underbrace{\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}V_{\text{CO}_2}}(t,z)}}_{\text{Eq.
 } \eqref{eq: dPdT}} \underbrace{\left(\cfrac{\partial {\color{orange}V_{\text{CO}_2}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)}}_{\text{Eq.
@@
 \label{eq: Cp_R}
-	\end{equation}
+	\end{align} }
+
 	The braced terms are obtained from the chosen equation of state $P(t) V\left[T(t,z),P(t)\right] = Z\left[T(t,z),P(t)\right] R T(t,z)$. \\
@@
 	For the partial derivative of the volume with respect to temperature $T$ at constant pressure $P(t)$, we have
+
+	{\footnotesize
 	\begin{equation}
@@
 }\eqref{eq: dZdT}} \label{eq: dVdT}
-	\end{equation} 
+	\end{equation} }
+
 	with partial derivative of the compressibility factor with respect to temperature $T$ at constant pressure $P(t)$
+
+	{\footnotesize
 	\begin{equation}
 		\left(\cfrac{\partial{\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} = \left(\cfrac{\partial \dfrac{{\color{red}P}(t) {\color{orange}V_{\text{CO}_2}}\left[T(t,z),P(t)\right]}{{\color{magenta}R}{\color{blue}T}(t,z)}}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} \label{eq: dZdT}
-	\end{equation}
+	\end{equation} }
+
 	Similarly, for the partial derivative of the pressure with respect to temperature at constant volume, we have
+
+	{\footnotesize
 	\begin{equation}
 		\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}V_{\text{CO}_2}}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{magenta}V_{\text{CO}_2}}\left[T(t,z),P(t)\right]}}}{\partial{\color{blue}T}}\right)_{{\color{orange}V}(t,z)} \label{eq: dPdT}
-	\end{equation}
+	\end{equation} }
 
 	The residual specific heat at constant volume is obtained, by definition, by using the residual internal energy
+
+	{\footnotesize
 	\begin{equation}
@@
 \label{eq: CvR}
-	\end{equation}
+	\end{equation} }
 
-	By denoting the physical constants as $\varphi_{C_p^{\text{F}}} = \left({\color{magenta}R}, {\color{magenta}M_{\text{CO}_2}}, {\color{magenta}T^c_{\text{CO}_2}}, {\color{magenta}P^c_{\text{CO}_2}}, {\color{magenta}\omega_{\text{CO}_2}}\right)$, we get the spatio-temporal representation $C_p^{\text{F}}\left[T(t,z),P(t) \mid \varphi_{C_p^{\text{F}}}\right]$ of the specific heat of the fluid phase
+	By denoting the physical constants as $\varphi_{C_p^{\text{F}}} = \left({\color{magenta}R}, {\color{magenta}M_{\text{CO}_2}}, {\color{magenta}T^c_{\text{CO}_2}}, {\color{magenta}P^c_{\text{CO}_2}}, {\color{magenta}\omega_{\text{CO}_2}}\right)$, we get the spatio-temporal representation $C_p^{\text{F}}\left[T(t,z),P(t) \mid \varphi_{C_p^{\text{F}}}\right]$ of the specific heat of the fluid phase.
 

### 2023-03-10 SFE - EmptySpace/Plot_Fit.m

@@ -53,7 +53,7 @@
 
     subtitle([DATA,'_',mat2str(round([DATA_K_OUT(:,ii)],3))],'Interpreter','latex')
 
-    set(gcf,'PaperOrientation','landscape'); print(figure(ii),['MLE_Weighted_Yield_',DATA,'_F',mat2str(V_Flow),'_No_Delay.pdf'],'-dpdf','-bestfit'); close all
+    set(gcf,'PaperOrientation','landscape'); print(figure(ii),['Inital_state_2_Yield_',DATA,'_F',mat2str(V_Flow),'_No_Delay.pdf'],'-dpdf','-bestfit'); close all
 
     %%
 %{

### 2023-03-10 SFE - EmptySpace/Plot_Trend_Line.m

@@ -1,0 +1,30 @@
+RHO         = [840, 785, 910, 870];
+NAME        = {'$km[-]$', '$D_i[m^2/s]$', '$D_x[m^2/s]$', '$C_{sat}[kg/m^3]$', 'mSOL_s', 'max_ms'};
+
+%% Fit the parameters based as linear function of density
+
+figure(1)
+
+for jj=1:2
+    for ii=1:Nk
+        
+        [trendLine, SLine]   = polyfit(RHO, DATA_K_OUT(ii,:), jj );
+        p_est                = polyval(trendLine, RHO);
+        p_y                  = polyval(trendLine, linspace(min(RHO), max(RHO) ) );
+        
+        subplot(2,3,ii)
+        scatter(RHO, DATA_K_OUT(ii,:), 'filled')
+        hold on
+        plot(linspace(min(RHO), max(RHO) ),p_y,'LineWidth',2);
+        hold off
+    
+        title(['$R^2 = $', mat2str( round(power(corr2(DATA_K_OUT(ii,:), p_est),2),2) ) ])
+    
+        xlabel('$\rho~[kg/m^3]$')
+        ylabel(NAME{ii})
+    
+    end
+    
+    set(gcf,'PaperOrientation','landscape'); print(figure(1),['Inital_state_2_Trend_Lines_order_',mat2str(jj),'_No_Delay.pdf'],'-dpdf','-bestfit'); close all;
+
+end

### 2023-03-10 SFE-article/Sections/Results.tex
10.03

@@
 
+\begin{figure*}
+	\centering
+	\begin{subfigure}[b]{0.7\textwidth}
+		\centering
+		\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Inital_state_2_Yield_LUKE_T40_P200_F0.41_No_Delay}
+		\caption{Experiment at $40^\circ C$ and $200$ bar}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.7\textwidth}
+		\centering
+		\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Inital_state_2_Yield_LUKE_T50_P200_F0.41_No_Delay.pdf}
+		\caption{Experiment at $50^\circ C$ and $200$ bar}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.7\textwidth}
+		\centering
+		\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Inital_state_2_Yield_LUKE_T40_P300_F0.41_No_Delay.pdf}
+		\caption{Experiment at $40^\circ C$ and $300$ bar}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.7\textwidth}
+		\centering
+		\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Inital_state_2_Yield_LUKE_T50_P300_F0.41_No_Delay.pdf}
+		\caption{Experiment at $50^\circ C$ and $300$ bar}
+	\end{subfigure}
+	\caption{Results of parameter fitting, with estimation of the initial state}
+\end{figure*}
+
 \end{document}

### 2023-03-16 SFE - EmptySpace/main_Opt_EmptySpace.m
16.03

@@ -38,10 +38,10 @@ if numel(N_Sample) ~= numel(SAMPLE)
 end
 
 %% Specify parameters to estimate
-nstages                 = 150;
+nstages                 = 250;
 
 before  = 0.1;          nstagesbefore   = 1:floor(before*nstages);
-bed     = 0.2;        nstagesbed      = nstagesbefore(end)+1 : nstagesbefore(end) + floor(bed*nstages);
+bed     = 0.165;        nstagesbed      = nstagesbefore(end)+1 : nstagesbefore(end) + floor(bed*nstages);
 nstagesafter                            = nstagesbed(end)+1:nstages;
 
 bed_mask                = nan(nstages,1);
@@ -69,14 +69,14 @@ f                       = @(x, u) modelSFE_uniform_U(x, u, bed_mask);
 % Integrator
 F                       = buildIntegrator(f, [Nx,Nu] , timeStep_in_sec);
 
-V                       = 0.008;                                        % deafault = 0.01
+V                       = 0.010;                                        % deafault = 0.01
 r                       = 0.075;                                        % Radius of the extractor  [m3]
 L                       = V / pi / r^2;                                 % Total length of the extractor [m]
 L_nstages               = linspace(0,L,nstages);
 A                       = pi*r^2;                                       % Extractor cross-section
 epsi                    = 0.5;                                          % Fullness [-]
 
-V_Flow     = 0.41;
+V_Flow     = 0.39;
 
 parfor ii=1:numel(DATA_set)
 
@@ -99,7 +99,7 @@ parfor ii=1:numel(DATA_set)
 
     nlp_opts                    = struct;
     %nlp_opts.ipopt.max_iter     = 30;
-    nlp_opts.ipopt.max_cpu_time = 3600;
+    nlp_opts.ipopt.max_cpu_time = 4*3600;
     ocp_opts                    = {'nlp_opts', nlp_opts};
     OPT_solver.solver(             'ipopt'   , nlp_opts)
 
@@ -205,7 +205,7 @@ parfor ii=1:numel(DATA_set)
     Yield_estimate_diff = diff(Yield_estimate);
 
     %% Create the cost function
-    J       = (data-Yield_estimate_diff ) * diag(1) * (data-Yield_estimate_diff )';
[…]

### 2023-03-16 SFE - InternalEnergy/EnthalpyPlot.m

@@ -1,0 +1,48 @@
+clc, close all
+clear all
+
+%addpath('C:\dev\casadi-windows-matlabR2016a-v3.5.2');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
+import casadi.*
+
+Parameters_table        = readtable('Parameters.csv') ;        % Table with prameters
+Parameters_cell         = table2cell(Parameters_table(:,3));
+
+%%
+T_set               = linspace(34,100)+273;
+P_set               = linspace(74,300,200);
+
+data                = [combvec(T_set,P_set)'];
+
+h_data              = nan(numel(T_set)*numel(P_set),1);
+
+parfor i=1:length(data)
+    T               = data(i,1);
+    P               = data(i,2);
+
+    Z               = Compressibility( T, P,         Parameters_cell );
+    rho             = rhoPB_Comp(      T, P, Z,      Parameters_cell );
+    h               = SpecificEnthalpy(T, P, Z, rho, Parameters_cell );
+    h_data(i)       = h;        
+end
+
+%%
+[X,Y] = meshgrid(T_set,P_set);
+Z     = reshape(h_data,numel(T_set),numel(P_set))'*1e-3;
+
+%%
+figure(1);
+set(gcf,'PaperOrientation','landscape', 'visible','on')
+
+contourf(X,Y,Z, 50, 'EdgeColor', 'none'); colormap jet; axis square tight; colorbar;
+
+%xline((Parameters_cell{10}),':','color','w')
+%yline(Parameters_cell{11},':','color','w')
+
+hcb=colorbar;
+title(hcb,'Enthalpy~[kJ/kg]','Interpreter','latex');
+
+ylabel('Pressure [bar]')
+xlabel('Temperature [K]')
+
+print(gcf, '-dpdf', '-fillpage', 'Enthalpy.pdf'); close all

### 2023-03-16 SFE - InternalEnergy/Saturation_Concentration.m

@@ -1,0 +1,8 @@
+function [FLUID_SAT] = Saturation_Concentration(FLUID, C_SAT)
+
+    k = 2*C_SAT;            % Growth rate
+    L = 0.5*C_SAT;          % Location of midpoint
+    FLUID_SAT = 1 ./ (1 + exp( k .* ( FLUID - C_SAT ) ) );
+
+end
+

### 2023-03-16 SFE - InternalEnergy/modelSFE.m

@@ -1,0 +1,99 @@
+function xdot = modelSFE(x, p, mask)
+    % (t, x, u, parameters)
+    % Model with (F)luid, (S)olid, (T)emperature
+    % Di is a function of temperature (T), the function works with numbers,
+    % vectors of numbers and vectors of symbolic variables
+    % Rho (Peng-Robinson) are constant numbers
+
+    %% Load Paramters
+    T_u           =    p{1};
+    P_u           =    p{2};
+    V_u           =    p{3};
+
+    parameters    =    p(4:end);
+
+    nstages       =    parameters{1};
+    C0solid       =    parameters{2};     % Extractor initial concentration of extract
+    r             =    parameters{3};     % Extractor length (m)
+    epsi          =    parameters{4};     % Void bed fraction
+    dp            =    parameters{5};     % Diameter of the particle (m)
+    L             =    parameters{6};     % Length of the extractor (m)
+    rho_s         =    parameters{7};     %
+    km            =    parameters{8};
+    mi            =    parameters{9};
+
+    Di            =    parameters{44};      Di = Di * 1e-12;
+    Dx            =    parameters{45};      Dx = Dx * 1e-6;
+
+    nstages_index =    numel(mask);
+    
+    %% Properties of the bed
+    A             =     pi*r^2 ;       % Cross-section of the extractor (m^2)
+    rp            =     dp / 2;
+    lp2           =     (rp / 3)^2;
+   
+
+    %% States
+    FLUID         =    x(0*nstages_index+1:1*nstages_index);
+    SOLID         =    x(1*nstages_index+1:2*nstages_index);
+    TEMP          =    x(2*nstages_index+1:3*nstages_index);
+          
+    %Properties of the fluid in the extractor
+    Z             =     Compressibility(TEMP, P_u,   parameters);
+
+    RHO           =     rhoPB_Comp(     TEMP, P_u, Z,parameters);
+    
+    VELOCITY      =     V_u / A;
+
+    
+    %% Thermal Properties
+    CP            =     SpecificHeatComp(TEMP, P_u, Z, RHO,                 parameters);            % [kJ/kg/K]
+    CPRHOCP       =     cpRHOcp_Comp(    TEMP, P_u, Z, RHO, CP, epsi.*mask, parameters);
[…]

### 2023-03-16 SFE - InternalEnergy/modelSFE_uniform_U.m

@@ -1,0 +1,177 @@
+function xdot = modelSFE_uniform_U(x, p, mask)
+    % (t, x, u, parameters)
+    % Model with (F)luid, (S)olid, (T)emperature
+    % Di is a function of temperature (T), the function works with numbers,
+    % vectors of numbers and vectors of symbolic variables
+    % Rho (Peng-Robinson) are constant numbers
+
+    %% Load Paramters
+    T_u           =    p{1};
+    P_u           =    p{2};
+    F_u           =    p{3};
+
+    parameters    =    p(4:end);
+
+    nstages       =    parameters{1};
+    C0solid       =    parameters{2};     % Extractor initial concentration of extract
+    r             =    parameters{3};     % Extractor length (m)
+    epsi          =    parameters{4};     % Void bed fraction
+    dp            =    parameters{5};     % Diameter of the particle (m)
+    L             =    parameters{6};     % Length of the extractor (m)
+    rho_s         =    parameters{7};     %
+    km            =    parameters{8};
+    mi            =    parameters{9};
+
+    Di            =    parameters{44};      Di = Di * 1e-12;
+    Dx            =    parameters{45};      Dx = Dx * 1e-5;
+    C_SAT         =    parameters{47};
+
+    nstages_index =    numel(mask);
+    
+    %% Properties of the bed
+    A             =     pi*r^2 ;       % Cross-section of the extractor (m^2)
+    rp            =     dp / 2;
+    lp2           =     (rp / 3)^2;
+   
+
+    %% States
+    FLUID         =    x(0*nstages_index+1:1*nstages_index);
+    SOLID         =    x(1*nstages_index+1:2*nstages_index);
+    TEMP          =    x(2*nstages_index+1:3*nstages_index);
+    RHO_NS        =    x(3*nstages_index+1:4*nstages_index);
+    %VELOCITY_NS   =    x(4*nstages_index+1:5*nstages_index);
+    
+    %E_Inv         = (1 - epsi.*mask).^(-1);
+
+    %%
+
+    %PRESSURE      =     P_u * ones(nstages_index,1);
+    PRESSURE      =     Pressure_PR(TEMP,RHO_NS,parameters);
+      
[…]

### 2023-03-24 SFE-article/Article_Model_Parameters.tex
16.03
24.03

@@
 \subsection{Governing equations}
-The detail derivation of the governing equation can be found in the appendix (\ref{CH: Gouverning equations}) as well as in the work of \citet{Anderson1995}.
+The detail derivation of the governing equation can be found in the appendix \ref{CH: Gouverning equations} as well as in the work of \citet{Anderson1995}.
 Let's assume that any properties of the flow are unifrom across any given cross-section of an channel (or any device like an extractor).
@@
         \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
-        \cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} {EQ: CompressibleEuler_2} \\
+        \cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \label{EQ: CompressibleEuler_2} \\
         \cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T}{\partial z} \right)

### 2023-03-24 SFE-article/Sections/Model.tex
24.03

@@
 
-		\subsubsection{Heat balance} \label{CH: heat_balance} \todo{I will be back. The energy equation is not given as a in terms of temperature any more.}
+		\subsubsection{Heat balance} \label{CH: heat_balance}
 
+		\iffalse
 		 {\color{red}
@@
 
-		\todo[inline]{Draft of new heat equation starts here. TODO: \\ Check if the heat cpacity of solid phase needs to be added \\ Elaborate why pressure is know}
+%		\todo[inline]{Draft of new heat equation starts here. TODO: \\ Check if the heat cpacity of solid phase needs to be added \\ Elaborate why pressure is know}
+		\fi
 
-		\noindent\colorbox{pink}
-		{
-		\begin{minipage}{\columnwidth}
 			The heat equation was introduced in the previous chapter through equation \ref{EQ: CompressibleEuler_3} or
@@
 
-			For real gases it is complicated to write the heat balance in terms of temperature.
-Alternatively, the energy equation can be used in the form of internal energy, so as it is given by equation \ref{EQ: CompressibleEuler_3}.
+			For real gases it is complicated to write the heat balance in terms of temperature, but it be used directly in the form of internal energy, as it is given by equation \ref{EQ: CompressibleEuler_3}.
 In such a case, the temperature (which is used as the input to some other functions) needs to be recover from the internal energy.
 A relation for the internal energy can be obtained from an equation of state.
-For Peng-Robinson, such a relation is given by equation \ref{EQ: internal_energy_PR}
+For Peng-Robinson, such a relation is given by equation \ref{EQ: internal_energy_PR}.
 
@@
 			\begin{equation*}
-				e(t,z)=e(T(t,z),P(t),\rho(t,z))=e(T(t,z),P(t),\underbrace{\rho(T(t,z),P(t))}_{E.O.S.}) 
+				e(t,z)=e(T(t,z),P(t),\rho(t,z))=e( T(t,z), P(t), \rho(T(t,z),P(t)) ) 
 			\end{equation*}
@@
 
-		\end{minipage} }
+			Another way to express the energy equation is to introduce enthalpy $e = h - P_0 / \rho$. By introducing the definition of enthalpy, the energy equation becomes
+
+			{\footnotesize
+				\begin{equation}
+					\cfrac{\partial \left(\rho_f h A_f\right)}{\partial t} - \cfrac{\partial \left(P_0 A_f\right)}{\partial t} + \cfrac{\partial \left( \rho_f h A_f v \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
+				\end{equation}
+			}
+
+			The main advantage of this formulation is the presence of term $\partial P_0 / \partial t $, which allow to directly affect the system through the change of thermodynamic pressure (which is a control variable).\todo{ "For high pressures, the influence of the intermolecular forces on the enthalpy has to be taken into account, usually by applying a cubic equation of state.
+In most cases, these forces are attractive, so that additional energy is necessary to move the molecules away from each other, that is, to lower the density.
+If this energy is not added, the substance cools down when it is expanded" (\citet{Gmehling2019}).
+So, pressure reduction cause gas expansion and temperature drop.}
+			If an equation of state is known, the temperature can to be recovered from the enthalpy. The enthalpy is related to the pressure and temperature through the following equation:
+
+			{\footnotesize
+				\begin{equation}
+					h(t,z)=h(T(t,z),P(t),\rho(t,z))=h( T(t,z), P(t), \rho(T(t,z),P(t)) ) 
+					\label{EQ:Enthalpy_root}
+				\end{equation}
+			}
+
+			If the value of enthalpy is know from the time evolution and pressure can be measured, then the equation \ref{EQ:Enthalpy_root} can be solved for temperature to recover the temperature profile.
+By applying the departure functions to Peng-Robinson equation of state, the relation \ref{EQ:Enthalpy_root} can be expressed directly through equation \ref{EQ:Enthalpy_PR} as presented in \ref{CH:Enthalpy} or given by \citet{Gmehling2019}.
+
+			{\footnotesize
+				\begin{equation}
+					h_{T,P}-h_{T,P}^{\mathrm {ideal} }=RT_{C}\left[T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right]
+					\label{EQ:Enthalpy_PR}
+				\end{equation}
+			}
+
+			The equation \ref{EQ:Enthalpy_PR} requires an reference sate, which in this case is assumed to be $T_{ref}=298.15[K]$ and $P_{ref}=1.01325[bar]$.
 

### 2023-03-24 SFE-article/Sections/Thermo.tex
24.03

@@
 
-    where $a, b, \alpha$ are parameters defined as presented in the appendix.
+    where $a, b, \alpha$ are parameters defined as presented in the appendix \ref{subsubsec: Equation of state}.
 
-    The properties of the $CO_2$ presented as a function of operating conditions (temperature and pressure) are presented on fig. \ref{fig: SFE_Properties}
+    The properties of the $CO_2$ presented as a function of operating conditions (temperature and pressure) are presented on Figure \ref{fig: SFE_Properties}
 
@@
 
-    where $A$ and $B$ are parameters as defined in the appendix (\ref{CH: Thermodynamic_details}).
-The roots of the polynomial can be found iteratively or by Cardano formula.
-Depends on the operating conditions, one or two roots can be found.
-In one-phase region the fluid can be describe as gas, liquid or super-critical.
-In the two-phase region the gas-liquid mixture is present.
-The biggest root is assigned to the gas phase and smallest root corresponds to the liquid phase.
+    where $A$ and $B$ are parameters as defined in the appendix \ref{subsubsec: Equation of state}.
+The roots of the polynomial can be found iteratively or by the Cardano formula.
+One or three real roots can be found depending on the operating conditions.
+In a one-phase region, the fluid is described by one real root corresponding to the gas, liquid or supercritical phase.
+In the two-phase region, the gas-liquid mixture is present and has two roots.
+The biggest root is assigned to the gas phase, and the smallest root corresponds to the liquid phase.
 
-    The real gas effects are also visible on the density plot presented on the Figure \ref{fig: SFE_Properties_Density}. The density can change significantly depends on the operating conditions. 
+ 	The real gas effects are also visible on the density plot presented on the Figure \ref{fig: SFE_Properties_Density}.
+The density calculations are based on the compressibility factor, as explained in the appendix \ref{subsubsec: Fluid density}, and its value depends on the operating conditions.
+
     By analysing the compressibility and density plots more it can be noticed that very near to the critical point, the fluid can neither be called a liquid nor a gas and has a unique combination of gas-like and liquid-like properties.
@@
     The Figure \ref{fig: SFE_Properties_CP} show behaviour of the heat capacity of a supercritical fluid at constant pressure ($C_p$).
-The details of the calculations can be found in the appendix.
+The details of the calculations can be found in the appendix \ref{subsubsec: Fluid heat capacity}.
 In contrary to the density which varies monotonically, the specific heat shows very high levels in a narrow region.

### 2023-03-24 SFE-article/Sections/Thermodynamic_details.tex
24.03

@@
 
-	\todo[]{Add internal energy equation}
+	\subsubsection{Departure functions for enthalpy calculations} \label{CH:Enthalpy} \todo[]{Change to my text}
+
+	In thermodynamics, a departure function is defined for any thermodynamic property as the difference between the property as computed for an ideal gas and the property of the species as it exists in the real world, for a specified temperature T and pressure P.
+Common departure functions include those for enthalpy, entropy, and internal energy.
+
+	Departure functions are used to calculate real fluid extensive properties (i.e.
+properties which are computed as a difference between two states).
+A departure function gives the difference between the real state, at a finite volume or non-zero pressure and temperature, and the ideal state, usually at zero pressure or infinite volume and temperature.
+
+	For example, to evaluate enthalpy change between two points $h(V_1,T_1)$ and $h(V_2,T_2)$ we first compute the enthalpy departure function between volume $V_1$ and infinite volume at $T = T_1$, then add to that the ideal gas enthalpy change due to the temperature change from $T_1$ to $T_2$, then subtract the departure function value between $V_2$ and infinite volume.
+
+	Departure functions are computed by integrating a function which depends on an equation of state and its derivative. The general form the enthalpy equation is given by
+
+	{\footnotesize 
+		\begin{equation}
+			\frac{H^{\mathrm {ig} }-H}{RT} =\int_{V}^{\infty }\left[T\left({\frac{\partial Z}{\partial T}}\right)_{V}\right]{\frac{dV}{V}} + 1-Z
+		\end{equation}
+	}
+
+	The Peng–Robinson equation of state relates the three interdependent state properties pressure $P$, temperature $T$, and molar volume $V_m$.
+From the state properties ($P$, $V_m$, $T$), one may compute the departure function for enthalpy per mole (denoted $h$) as presented by \citet{Gmehling2019} or \citet{Elliott2011}:
+
+	{\footnotesize
+		\begin{equation}
+			h_{T,P}-h_{T,P}^{\mathrm {ideal} }=RT_{C}\left[T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right]
+		\end{equation}
+	}
 

### 2023-03-24 SFE - InternalEnergy/Plot_Fit.m

@@ -1,83 +1,51 @@
-    %figure('Visible','off')
-    figure(ii)
+figure(ii)
+subplot(2,2,1)
+hold on
+plot(Time  , xx_0(Nx,:)  ,'k'   )
+plot(Time  , xx_out(Nx,:),'r'   )
+plot(SAMPLE, data_org    ,'b--o')
+%plot(Time, 1e3 * (sum(xx_out(0*nstages+1:1*nstages,:) .* V_fluid) + sum(xx_out(1*nstages+1:2*nstages,:) .* V_solid)) + xx_out(Nx,:));
+hold off
 
-    h = tiledlayout(2,2);
+xlabel('Time [min]')
+ylabel('Yield [g]')
 
-    nexttile
-    %pbaspect([3 1 1])
-    hold on
-%    plot(Time, xx_0(end,:));
-    plot(Time, xx_out(end,:));
-    plot(SAMPLE, data_org,'o');
-    xline(PreparationTime,'--k')
-    ylim([0 80])
-    hold off
-    legend('$k_0$', '$k_{out}$', 'data', 'Location','northoutside')
-    legend('Orientation','horizontal')
-    legend('boxoff')
-    ylabel('CFD: y(t)','Interpreter','latex')
-    xlabel('Time [min]','Interpreter','latex')
+colorbar
 
-    nexttile
-    %pbaspect([3 1 1])
-    hold on
-%    plot(SAMPLE(1:end-1), diff(xx_0(end,N_Sample))   );
-    plot(SAMPLE(1:end-1), diff(xx_out(end,N_Sample)) );
-    plot(SAMPLE(1:end-1), diff(data_org),'o');
-    xline(PreparationTime,'--k')
-    hold off
-    ylim([0 15])
-    legend('$k_0$', '$k_{out}$', 'data', 'Location','northoutside')
-    legend('Orientation','horizontal')
-    legend('boxoff')
-    ylabel('PDF: norm $\frac{dy(t)}{dt}$','Interpreter','latex')
-    xlabel('Time [min]','Interpreter','latex')
+legend('Inital curve','Optimized curve','Data points','Location','northwest'); legend('boxoff')
 
-    nexttile
-    %pbaspect([3 1 1])
-    hold on
[…]

### 2023-03-24 SFE - InternalEnergy/Plot_Trend_Line.m

@@ -1,5 +1,5 @@
-RHO         = [840, 785, 910, 870];
-NAME        = {'$km[-]$', '$D_i[m^2/s]$', '$D_x[m^2/s]$', '$C_{sat}[kg/m^3]$', 'mSOL_s', 'max_ms'};
+RHO         = [840, 840, 785, 785, 910, 870];
+NAME        = {'$km[-]$', '$D_i[m^2/s]$', '$D_x[m^2/s]$', 'Mass in solid', 'Mass ratio'};
 
 %% Fit the parameters based as linear function of density
 
@@ -25,6 +25,6 @@ for jj=1:2
     
     end
     
-    set(gcf,'PaperOrientation','landscape'); print(figure(1),['Inital_state_2_Trend_Lines_order_',mat2str(jj),'_No_Delay.pdf'],'-dpdf','-bestfit'); close all;
+    set(gcf,'PaperOrientation','landscape'); print(figure(1),['Trend_Lines_order_',mat2str(jj),'.pdf'],'-dpdf','-bestfit'); close all;
 
 end

### 2023-03-24 SFE - InternalEnergy/modelSFE.m

@@ -12,8 +12,8 @@ function xdot = modelSFE(x, p, mask, dt)
 
     parameters    =     p(4:end);
 
-    nstages       =     parameters{1};
-    C0solid       =     parameters{2};     % Extractor initial concentration of extract
+    %nstages       =     parameters{1};
+    %C0solid       =     parameters{2};     % Extractor initial concentration of extract
     r             =     parameters{3};     % Extractor length (m)
     epsi          =     parameters{4};     % Void bed fraction
     dp            =     parameters{5};     % Diameter of the particle (m)
@@ -22,9 +22,9 @@ function xdot = modelSFE(x, p, mask, dt)
     km            =     parameters{8};
     mi            =     parameters{9};
 
-    Di            =     parameters{44};      Di = Di * 1e-12;
-    Dx            =     parameters{45};      Dx = Dx * 1e-5;
-    C_SAT         =     parameters{47};
+    Di            =     parameters{44};      Di = Di * 1e-14;
+    Dx            =     parameters{45};      Dx = Dx * 1e-6;
+    %C_SAT         =     parameters{47};
 
     nstages_index =     numel(mask);
     
@@ -49,12 +49,12 @@ function xdot = modelSFE(x, p, mask, dt)
     VELOCITY      =     Velocity(F_u, RHO, parameters);
     
     %% Thermal Properties
-    CP            =     SpecificHeatComp(TEMP, PRESSURE, Z, RHO,                 parameters);            % [kJ/kg/K]
-    CPRHOCP       =     cpRHOcp_Comp(    TEMP, PRESSURE, Z, RHO, CP, epsi.*mask, parameters);
-    KRHOCP        =     kRHOcp_Comp(     TEMP, PRESSURE, Z, RHO, CP, epsi.*mask, parameters);
+    %CP            =     SpecificHeatComp(TEMP, PRESSURE, Z, RHO,                 parameters);            % [kJ/kg/K]
+    %CPRHOCP       =     cpRHOcp_Comp(    TEMP, PRESSURE, Z, RHO, CP, epsi.*mask, parameters);
+    %KRHOCP        =     kRHOcp_Comp(     TEMP, PRESSURE, Z, RHO, CP, epsi.*mask, parameters);
 
     %% Saturation
[…]

### 2023-03-30 SFE-article/Sections/Results.tex
30.03

--- 2023-03-10 SFE-article/Sections/Results.tex
@@
 			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Weighted_Yield_LUKE_T40_P200_F0.41_No_Delay.pdf}
+			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
 			\caption{Experiment at $40^\circ C$ and $200$ bar}
@@
 			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Weighted_Yield_LUKE_T50_P200_F0.41_No_Delay.pdf}
+			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
 			\caption{Experiment at $50^\circ C$ and $200$ bar}
@@
 			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Weighted_Yield_LUKE_T40_P300_F0.41_No_Delay.pdf}
+			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
 			\caption{Experiment at $40^\circ C$ and $300$ bar}
@@
 			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Weighted_Yield_LUKE_T50_P300_F0.41_No_Delay.pdf}
+			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
 			\caption{Experiment at $50^\circ C$ and $300$ bar}
 		\end{subfigure}
-		\caption{Results of parameter fitting, without estimation of the initial state}
+		\caption{Results of parameter fitting, with estimation of the initial state}
+	\end{figure*}
+
+	\begin{figure*}
+	\centering
+	\begin{subfigure}[b]{0.85\textwidth}
+		\centering
+		\includegraphics[trim = 1cm 2cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
+		\caption{First order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.85\textwidth}
+		\centering
+		\includegraphics[trim = 1cm 2cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
+		\caption{Second order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
+	\end{subfigure}
+	\caption{Results of parameter fitting, with estimation of the initial state}
 \end{figure*}

### 2023-03-30 SFE - InternalEnergy/main_Fitting.m

@@ -9,16 +9,16 @@ Parameters_table        = readtable('Parameters.csv') ;        % Table with pram
 Parameters              = num2cell(Parameters_table{:,3});
 
 %% Load paramters
-DATA_set                = {'LUKE_T40_P200_org', 'LUKE_T50_P200', 'LUKE_T50_P200_org', 'LUKE_T40_P300_org', 'LUKE_T50_P300_org'};
+DATA_set                = {'LUKE_T40_P200', 'LUKE_T50_P200', 'LUKE_T40_P300_org', 'LUKE_T50_P300_org'};
 %DATA_set                = {'LUKE_T50_P300'};
 
 which_k                 = [8,  44, 45,          ];                          % Select which parameters are used for fitting
-k0                      = [1,  3 , 1 ,  77, 0.65];                          % Give inital value for each parameter
-Nk                      = numel(which_k)+2;                                 % Parameters within the model + m_max, m_ratio
-k_lu                    = [ [0;0;0;77;0] , [1;inf;inf;100;1] ];
+k0                      = [1,  3 , 1 ,  77, 0.65, 0.3];                          % Give inital value for each parameter
+Nk                      = numel(which_k)+3;                                 % Parameters within the model + m_max, m_ratio, sigma
+k_lu                    = [ [0;0;0;77;0;0] , [1;inf;inf;100;1;inf] ];
 
 Iteration_max           = 100;                                              % Maximum number of iterations for optimzer
-Time_max                = 6;                                              % Maximum time of optimization in [h]
+Time_max                = 36;                                               % Maximum time of optimization in [h]
 
 V_Flow                  = 0.4;                                              % Volumetric flow rate l/min
 
@@ -29,7 +29,7 @@ bed                     = 0.165;                                            % Pe
 % Set time of the simulation
 PreparationTime         = 0;
 ExtractionTime          = 150;
-timeStep                = 0.5;                                              % Minutes
+timeStep                = 0.1;                                              % Minutes
 SamplingTime            = 5;                                                % Minutes
 
 simulationTime          = PreparationTime + ExtractionTime;
[…]

### 2023-04-19 SFE-article/Article_Model_Parameters.tex
19.04

@@
 % Figure packages
-\usepackage{float}
+\usepackage{graphicx,float}
 \usepackage{adjustbox}
@@
 Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
-Given a system of partial differential equations, $F(t,x,\dot{x},\Theta,u)=0$, where $x$ represents state variables, $\Theta$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process.
+%Given a system of partial differential equations, $F(t,x,\dot{x},\Theta,u)=0$, where $x$ represents state variables, $\Theta$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process.
 The process model describes a partially filled extractor with a fixed bed, which work under constant operating conditions.
@@
 We apply the concept of quasi-one-dimensional flow to mimic the modelling of a two-dimensional case.
-In this work, a distributed-parameter model, based on \citet{Reverchon1996} is used to describe a fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent.
-The model parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient and saturation concentration are obtained from parameter estimation.
-The parameters are estimated based on four experiments performed at $40^\circ C$ and $50^\circ C$ at $200$ bar and $300$ bar.
+%In this work, a distributed-parameter model, based on \citet{Reverchon1996} is used to describe a fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent.
+The model parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient \textit{and saturation concentration} are obtained from parameter estimation.
+The parameters are estimated based on four experiments performed at $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar and $50^\circ C$/$300$ bar.
 Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
+We consider a system of partial differential equations, $F(t,x,\dot{x},\Theta,u)=0$, where $x$ denotes the state variables, $\Theta$ represents the parameters, and $u$ is the control variables.
+Our focus is on the supercritical extraction process, which involves a partially filled extractor with a fixed bed that operates under constant conditions.
+We assume the flow is uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
+To model this two-dimensional case, we use the concept of quasi-one-dimensional flow.
+To describe the fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent, we use a distributed-parameter model based on \citet{Reverchon1996}.
+This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and saturation concentration.
+We estimate these parameters from four experiments at different temperatures and pressures: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar.
+We obtain the parameter values using the maximum likelihood estimation method on yield data under the normal error assumption.
 
@@
 \section{Introduction}
-\subfile{Sections/introduction}
+%\subfile{Sections/introduction}
+\subfile{Sections/introduction_imp}
 
@@
 \subsection{Supercritical fluids} \label{CH: Thermodynamic}
-\subfile{Sections/Thermo}
+%\subfile{Sections/Thermo}
+\subfile{Sections/Thermo_imp}
 
@@
 \subsection{Governing equations}
-The detail derivation of the governing equation can be found in the appendix \ref{CH: Gouverning equations} as well as in the work of \citet{Anderson1995}.
-Let's assume that any properties of the flow are unifrom across any given cross-section of an channel (or any device like an extractor).
-Such a flow is called quasi-one-dimensional.
-The variation of the cross-section might be an result of its irregular shape (or partial filling of an extractor).
+The governing equation for a quasi-one-dimensional compressible flow in Cartesian coordinates can be found in the appendix \ref{CH: Gouverning equations} and in the work of \citet{Anderson1995}.
+Quasi-one-dimensional flow is a type of fluid flow that is characterized by the assumption that the flow properties remain uniform across any given cross-section of the flow.
+This assumption is made when there is a variation in the cross-sectional area of the flow channel, such as a irregular shape or partial filling of an extractor.
+In such cases, the flow is considered to be quasi-one-dimensional because the velocity and other flow properties are assumed to vary only in the direction of flow.
 
-The quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates is given be equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_3}.
+The quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates are given by equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_3}.
 
@@
 
-Based on governing equations, the small discontinuity in flow properties, shown on figure \ref{fig: Discontinuity_slow_flow}, can be analysed. The analysis follow the work of \citet{Schreier1982}.
+Based on governing equations, the small discontinuity (defined as $\delta$) in flow properties, shown on figure \ref{fig: Discontinuity_slow_flow}, can be analysed.
+The analysis follow the work of \citet{Schreier1982}.
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
 	\centering
@@
 			\draw (4.5,0) -- (4.5,2); 	% Bottom line
-		\node at (4,1.5) {$\rho$};
-		\node at (5.5,1.5) {$\rho+\delta\rho$};
+			\node at (4,1.5) {$\rho_f$};
+			\node at (5.5,1.5) {$\rho_f+\delta\rho_f$};
 			\node at (4,1.0) {$P$};
@@
 
-The discontinuity is presumed to be at rest relative and \todo[]{Fix the notation of pressure perturbation section to be coherent with governing equations}  the balance equations become
+The discontinuity is presumed to be at rest relative and the balance equations become
 
@@
 	\begin{align*}
-		&\rho \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 \\
+		&\rho_f \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 \\
 		&\delta P = \delta v \delta \rho_f
@@
 
-If the flow is presumed to be isentropic, $dP/d\rho = c^2$, so $V^2=c^2$, where $c$ is the speed of sound.
+If the flow is presumed to be isentropic, $dP/d\rho = c^2$, so $v^2=c^2$, where $c$ is the speed of sound.
 This can be interpreted that a small pressure wave propagates with the speed of sound relative to the flow.
@@
 \subsection{Low Mach number expansion}
-\subfile{Sections/Low_mach_number_expansion}
+%\subfile{Sections/Low_mach_number_expansion}
+\subfile{Sections/Low_mach_number_expansion_imp}
 

### 2023-04-19 SFE-article/Sections/Low_mach_number_expansion_imp.tex
19.04

--- 2023-03-09 SFE-article/Sections/Low_mach_number_expansion.tex
@@
 	As discussed by \citet{Lions2013}, the low Mach number equations are a subset of the fully compressible equations of motion (continuity, momentum and energy).
-Such a set of equations allow for large variations in gas density but it is consider to be acoustically incompressible.
-The low Mach number equations are preferred over the full compressible equations for low speed flow problems $\left( M_a = \frac{|V|}{\sqrt{ \partial P / \partial \rho }} \ll 1 \right)$ to avoids the need to resolve fast-moving acoustic signals.
-The equations are derived from the compressible equations based on the perturbation theory.
+Such a set of equations allow for large variations in gas density, but it is considered acoustically incompressible.
+Therefore, the low Mach number equations are preferred over the full compressible equations for low-speed flow problems $\left( M_a = \frac{|v|}{\sqrt{ \partial P / \partial \rho_f }} \ll 1 \right)$ to avoids the need to resolve fast-moving acoustic signals.
+The equations are derived from compressible equations based on the perturbation theory.
 The perturbation theory develops an expression for the desired solution in terms of a formal power series known as a perturbation series in some "small" parameter $\zeta$, that quantifies the deviation from the exactly solvable problem.
-The leading term in this power series is the solution of the exactly solvable problem, while further terms describe the deviation in the solution, due to the deviation from the initial problem.
+The leading term in this power series is the solution of the exactly solvable problem, while further terms describe the deviation in the solution due to the deviation from the initial problem.
 
-	The equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_2} describe the fully compressible equations of motion (respectively the transport of mass, momentum and energy) for quasi-one-dimensional case.
+	The equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_2} describe the fully compressible equations of motion (respectively, the transport of mass, momentum and energy) for the quasi-one-dimensional case.
 We rescale the time variable, considering finally
@@
 
-	The conservative non-dimensional equations of motion becomes
+	The conservative non-dimensional equations of motion become
 
@@
 			\cfrac{\partial \left( \rho_\zeta A_f v_\zeta \right) }{\partial t}	&+ \cfrac{\partial \left( \rho_\zeta v_\zeta A_f v_\zeta \right)}{\partial z} + \cfrac{A_f}{M_a^2} \cfrac{\partial P_\zeta}{\partial z} = 0\\
-			\cfrac{\partial \left( \rho_\zeta e_\zeta A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_\zeta e_\zeta v_\zeta A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_\zeta}{\partial z} \right) + P_\zeta \cfrac{\partial A_f v_\zeta}{\partial z} = 0
+			\cfrac{\partial \left( \rho_\zeta e_\zeta A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_\zeta e_\zeta v_\zeta A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_\zeta}{\partial z} \right) + P_\zeta \cfrac{\partial \left(A_f v_\zeta\right)}{\partial z} = 0
 		\end{align*}
@@
 
-	Let's define $\zeta=M_a^2$ and assume small Mach numbers, $M_a \ll 1$, then the kinetic energy, viscous work, and gravity work terms can be neglected in the energy equation since those terms are scaled by the square of the Mach number.
+	Let's define $\zeta=M_a^2$ and assume small Mach numbers, $M_a \ll 1$, then the kinetic energy, viscous work, and gravity work terms can be neglected in the energy equation since the square of the Mach number scales those terms.
 The inverse of Mach number squared remains in the momentum equations, suggesting singular behaviour.
@@
 
-	 By expanding performing power expansion on the continuity equation and taking the limit of $\zeta$ from the positive side we get
+	By expanding performing power expansion on the continuity equation and taking the limit of $\zeta$ from the positive side, we get
 
@@
 
-	The continuity equation become
+	The continuity equation becomes
 
@@
 
-	The form of the continuity equation stays the same. Considering the momentum equation, it can be seen that the inverse of Mach number squared remains which suggests singular behavior.
+	The form of the continuity equation stays the same. Considering the momentum equation, it can be seen that the inverse of Mach number squared remains, which suggests singular behaviour.
 
@@
 
-	The first two terms stays the same, but the third one become different in structure. By further investigation of the pressure term in the momentum equation it can be observed
+	The first two terms stay the same, but the third one becomes different in structure. By further investigation of the pressure term in the momentum equation, it can be observed.
 
@@
 	The simplification of the $P_0$ in the momentum equation comes from the fact that $P_0$ is independent of $z$.
-As it was presented above, the thermodynamical pressure moves with speed of sound, and any perturbation propagates instantaneously.
+As was presented above, the thermodynamical pressure moves with the speed of sound, and any perturbation propagates instantaneously.
 The term related to $P_2$ and higher order terms become zero at the limit of $M_a \rightarrow 0$.
-The momentum equation become
+The momentum equation becomes
 
@@
 
-	By expanding performing power expansion on the energy equation and taking the limit of $\zeta$ from the positive side we get
+	By expanding performing power expansion on the energy equation and taking the limit of $\zeta$ from the positive side, we get
 
@@
 		\begin{equation*}
-			\cfrac{\partial \left( \rho_0 e_0 A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_0 e_0 v_0 A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_0}{\partial z} \right) + P_0 \cfrac{\partial A_f v_0}{\partial z} = 0
+			\cfrac{\partial \left( \rho_0 e_0 A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_0 e_0 v_0 A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_0}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v_0\right)}{\partial z} = 0
 		\end{equation*}
@@
 			\cfrac{\partial \left( \rho_f A_f v \right) }{\partial t}	&+ \cfrac{\partial \left( \rho_f v A_f v \right)}{\partial z} + A_f \cfrac{\partial P_1}{\partial z} = 0\\
-			\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_f e v A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
+			\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_f e v A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v\right)}{\partial z} = 0
 		\end{align*}
@@
 		\begin{equation*}
-			 \rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) + e  \underbrace{ \left( \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f v A_f \right)}{\partial z} \right) }_{Continutiy}  - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
+			\rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) + e  \underbrace{ \left( \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f v A_f \right)}{\partial z} \right) }_{Continutiy}  - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v\right)}{\partial z} = 0
 		\end{equation*}
@@
 
-	The non-conservative form of the energy equation become
+	The non-conservative form of the energy equation becomes
 
@@
 		\begin{equation*}
-		\rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
+			\rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v\right)}{\partial z} = 0
 		\end{equation*}
@@
 
-	If the calorically perfect gas is assumed then $e=C_vT$, where $C_v$ is the constant specific heat. The energy equation can derived in terms of temperature $T$
+	If the calorically perfect gas is assumed, then $e=C_vT$, where $C_v$ is the constant specific heat. The energy equation can be derived in terms of temperature $T$.
 
@@
 		\begin{equation*}
-			\rho A_f C_v \left( \cfrac{\partial T }{\partial t} + v \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
+			\rho A_f C_v \left( \cfrac{\partial T }{\partial t} + v \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v\right)}{\partial z} = 0
 		\end{equation*}
@@
 
-	If isothermal case is assumed then, the energy equation becomes
+	If an isothermal case is assumed, then the energy equation becomes
 
@@
 		\begin{equation*}
-			\lim_{\Delta T \rightarrow 0_+} \rho A_f C_v \left( \cfrac{\partial T }{\partial t} + v \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
+			\lim_{\Delta T \rightarrow 0_+} \rho A_f C_v \left( \cfrac{\partial T }{\partial t} + v \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v\right)}{\partial z} = 0
 		\end{equation*}
@@
 		\begin{equation}
-			\cfrac{\partial A_f v}{\partial z} = 0
+			\cfrac{\partial \left(A_f v\right)}{\partial z} = 0
 			\label{EQ: Incompressibility_Condition_Ideal_IsoThermal}
@@
 
-		A general formulation the internal energy for a real gas is:
+	As presented by \citet{Elliott2011}, a general formulation of the internal energy for a real gas is:
 
@@
 		\begin{equation*}
-			de=C_vdT-\left[P-T\left(\cfrac{\partial P}{\partial T}\right)_{V_m}\right]dv_m
+			de=C_vdT-\left[P-T\left(\cfrac{\partial P}{\partial T}\right)_{v_m}\right]dv_m
 	\end{equation*} }
@@
 
-	The internal energy is a function of two intensive properties, in this case $T$ and $v_m=1/\rho_f$.
+	The internal energy is a function of two intensive properties, in this case, $T$ and $v_m=1/\rho_f$.
 But, in the case of an ideal gas, the equation of state is such that the second term in this equation is identically equal to zero.
@@
 		\begin{equation*}
-			\lim_{\Delta T, \Delta P \rightarrow 0_+ } \rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0 \rightarrow \cfrac{\partial A_f v}{\partial z} = 0
+			\lim_{\Delta T, \Delta P \rightarrow 0_+ } \rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v\right)}{\partial z} = 0 \rightarrow \cfrac{\partial \left(A_f v\right)}{\partial z} = 0
 		\end{equation*}
@@
 
-	It can be deduce that the continuity equation becomes $\frac{\partial \rho_f}{\partial t} = 0$ at constant temperature and pressure.
+	It can be deduced that the continuity equation becomes $\frac{\partial \rho_f}{\partial t} = 0$ at constant temperature and pressure.
 Moreover, the incompressibility condition $div(A_fV)=0$ is obtained.
 
-	Assuming an arbitrary function $\hat{P}$, which describe the total pressure, the dimensional momentum equation can be written as
+	Assuming an arbitrary function $\hat{P}$, which describes the total pressure, the dimensional momentum equation can be written as
 
@@
 		\begin{equation*}
-			V \underbrace{ \left( \cfrac{\partial \rho_f A_f}{\partial t} + \cfrac{\rho_f v A_f}{\partial z} \right) }_{Continuity~equation} + \rho_f A_f \cfrac{\partial v}{\partial t} + \rho_f v A_f \cfrac{\partial v}{\partial z} = - A_f \cfrac{\partial \hat{P}}{\partial z}
+			V \underbrace{ \left( \cfrac{\partial \left(\rho_f A_f\right)}{\partial t} + \cfrac{\left(\rho_f v A_f\right)}{\partial z} \right) }_{Continuity~equation} + \rho_f A_f \cfrac{\partial v}{\partial t} + \rho_f v A_f \cfrac{\partial v}{\partial z} = - A_f \cfrac{\partial \hat{P}}{\partial z}
 		\end{equation*}
@@
 
-	From the incompressibility conditions we can deduce that
+	From the incompressibility conditions, we can deduce that
 
@@
 		\begin{equation*}
-			\cfrac{\partial A_f v}{\partial z} = 0 \rightarrow A_f \cfrac{\partial v}{\partial z} = - v \cfrac{\partial A_f}{\partial z}
+			\cfrac{\partial \left(A_f v\right)}{\partial z} = 0 \rightarrow A_f \cfrac{\partial v}{\partial z} = - v \cfrac{\partial A_f}{\partial z}
 		\end{equation*}
@@
 
-	The final form of the momentum equation corresponds to the Bernoulli's principle
+	The final form of the momentum equation corresponds to Bernoulli's principle
 
@@
 
-	The Bernoulli's principle can be used to find the hydrodynamic pressure caused by varying cross-section at steady-state.
-Moreover, if the flow velocity is relatively low and so all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic.
+	Bernoulli's principle can be used to find the hydrodynamic pressure caused by varying cross-sections at steady-state.
+Moreover, if the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic.
 The effect of this is that $\partial \rho / \partial P = 0$.
@@
 So there is an infinite speed of sound, which makes the equations elliptic in nature.
-It can be deduced that at the isothermal conditions the density in the system propagates with the same speed as pressure due to the fact that they are both connected through the equation of state.
+It can be deduced that at the isothermal conditions, the density in the system propagates with the same speed as pressure since they are both connected through the equation of state.
 

### 2023-04-19 SFE-article/Sections/Thermo_imp.tex
19.04

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	A supercritical fluid (SCF) is a substance at a temperature and pressure above its critical point, where there are no distinct liquid and gas phases but below the pressure required to compress it into a solid. SCFs can move through porous solids like gases, which is faster than liquid transport through such materials. SCFs have a higher ability to dissolve materials like liquids or solids compared to gases. Near the critical point, small changes in pressure or temperature result in significant changes in density, allowing many properties of an SCF to be fine-tuned. By changing the pressure and temperature, the properties can be tuned to be more liquid-like or gas-like.

	Fluid properties can be divided into two kinds: equilibrium properties and transport properties. The equation of state can be used accurately to predict the equilibrium properties, such as density, enthalpy, vapour pressure, fugacity and fugacity coefficient, vapour-liquid equilibrium, and all kinds of excess properties.

	Supercritical $CO_2$'s thermodynamic properties, such as density, the local speed of sound, and specific heat capacity, vary significantly with slight changes in temperature and pressure due to real gas effects. The Peng-Robinson equation of state (P-R EOS) is used to calculate the thermodynamic properties by accounting for these real gas effects. The P-R EOS belongs to a specific class of thermodynamic models for modelling the pressure of a gas as a function of temperature and density. It can be written as a cubic function of the molar volume (of the density). Detail information about Peng-Robinson equation of state can be found in the work of \citet{Peng1976}, \citet{Elliott2011} or \citet{Pratt2001}. The P-R EOS is presented by equation \ref{EQ: PR}

	{\footnotesize
		\begin{equation}
			P = \cfrac{RT}{V_m - b} - \cfrac{a\alpha}{V_m^2 + 2bV_m - b^2}
			\label{EQ: PR}
		\end{equation}
	}

	The parameters $a, b, \alpha$ are parameters defined as presented in the appendix \ref{subsubsec: Equation of state}.

	The properties of $CO_2$  are presented as a function of operating conditions (temperature and pressure) in Figure \ref{fig: SFE_Properties}. At standard atmospheric pressure and temperature, $CO_2$  behaves as an ideal gas, and its compressibility factor equals unity. However, at high pressures and/or low temperatures, intermolecular forces between gas molecules become more significant, causing them to deviate from ideal behaviour. As a result, the compressibility factor can either be greater than or less than unity, depending on the magnitude of these forces. As presented in Figure \ref{fig: SFE_Properties_Compressibility}, the compressibility factor obtained from the Peng-Robinson equation of state varies strongly depending on the operating conditions. The compressibility factor can be obtained by solving the polynomial form of the P-R EOS given by \ref{EQ: PR_polynomial}.

	{\footnotesize
		\begin{equation}
			Z^3 - (1-B)Z^2+(A-2B-3B^2)Z -(AB-B^2-B^3) = 0
			\label{EQ: PR_polynomial}
		\end{equation}
	}

	where $A$ and $B$ are parameters as defined in the appendix \ref{subsubsec: Equation of state}. The roots of the polynomial can be found iteratively or by the Cardano formula. In a one-phase region, the fluid is described by one real root corresponding to the gas, liquid or supercritical phase. The gas-liquid mixture is present in the two-phase region, and two roots are found. The biggest root is assigned to the gas phase, and the smallest root corresponds to the liquid phase.

	The real gas effects are also visible on the density plot presented in Figure \ref{fig: SFE_Properties_Density}. The density calculations are based on the compressibility factor and its value depends on the operating conditions. The fluid's properties near the critical point are unique and combine gas-like and liquid-like properties. The details of calculations are explained in the appendix \ref{subsubsec: Fluid density}.

	Figure \ref{fig: SFE_Properties_CP} show the behaviour of the heat capacity of a supercritical fluid at constant pressure ($C_p$). The details of the calculations can be found in the appendix \ref{subsubsec: Fluid heat capacity}. Contrary to the density, which varies monotonically, the specific heat shows very high levels in a narrow region. In the subcritical region, the phase transition is associated with an effective spike in the heat capacity (i.e., the latent heat). Approaching the critical point, the latent heat falls to zero, which is accompanied by a gradual rise in heat capacity in the pure phases near phase transition. At the critical point, the latent heat is zero, but the heat capacity shows a diverging singularity. Beyond the critical point, there is no divergence, but rather a smooth peak in the heat capacity; the highest point of this peak identifies the Widom line (as discussed by \citet{Simeoni2010} and \citet{Banuti2019}).

	To determine the thermodynamic properties of a real gas, it is necessary to evaluate the departure function of the chosen equation of state for that property. As explained by \citet{Elliott2011}, the departure function is the difference between the actual value of a thermodynamic property of a real gas and its value if the gas were ideal under the same temperature and pressure conditions. The ideal gas serves as a reference state to which the properties of real gases are compared. The departure function is a measure of the extent to which a real gas deviates from ideal gas behaviour. The departure functions allow for the accurate calculation of thermodynamic properties for real gases.  %(10.1007/s10494-017-9872-4)

	\begin{figure*}[H]
		\begin{subfigure}[b]{0.95\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
			\caption{The compressibility factor based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_Compressibility}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.95\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/RHO.pdf}	
			\caption{The fluid density based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_Density}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.95\textwidth}
			\centering
			\includegraphics[trim = 2.9cm 7cm 3.cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
			\caption{The specific heat of the $CO_2$ based on the Peng-Robinson equation of state}
			\label{fig: SFE_Properties_CP}
		\end{subfigure}
		\caption{Properties of $CO_2$ based on the equation of state}
		\label{fig: SFE_Properties}
	\end{figure*}

	Transport properties such as viscosity and conductivity play a crucial role in engineering design for production, fluid transportation, and processing. However, as highlighted by \citet{Sheng1989}, developing a satisfactory theory for transport properties of real dense gases and liquids is a challenging task. This is due to the inherent difficulties involved in accurate measurements and the complexity involved in theoretical treatments.

	To address this issue, the correlations of transport coefficients are either empirical or based on some theoretical foundation. Chapman-Enskog's theory (presented in \citet{Chapman1991}) for transport properties of dense gases based on the distribution function is a popular theoretical approach. However, the Chapman-Enskog theory was developed for rigid spherical molecules and modifications are required to apply it to real gases. Many correlations have been proposed following the Chapman-Enskog theory in the form of reduced density and reduced temperature, such as those developed by \citet{Fenghour1998} and \citet{Laesecke2017} from the National Institute of Standards and Technology (NIST). A comparison of these correlations is presented in Figure \ref{fig: SFE_Properties_mu}.

	NIST has developed a viscosity formulation consisting of four contributions: (i) for the limit of zero density, (ii) for the initial density dependence, (iii) for the residual viscosity, and (iv) for the singularity of the viscosity at the critical point. The NIST correlation covers temperatures from 100 to 2000 $K$ for gaseous $CO_2$, and from 220 to 700 $K$ with pressures along the melting line up to 8000 $MPa$ for compressed and supercritical liquid states. These correlations and theories are essential in predicting transport properties for real gases and liquids and can assist in engineering design and analysis.

	\begin{figure*}[H]
		\centering
		\includegraphics[trim = 1.5cm 11.5cm 2.5cm 10.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
		\includegraphics[trim = 1.5cm 4.0cm 2.5cm 19.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
		\caption{Viscosity obtained based on different correlations } 
		\label{fig: SFE_Properties_mu}
	\end{figure*}

	Similarly, several correlations for thermal conductivity of $CO_2$ were compared in Figure \ref{fig: SFE_Properties_kt}. The presented figures show regions around the critical point where the singularity is present. Similarities between specific heat and thermal conductivity can be observed. The NIST correlation (\citet{Huber2016}) captures the singular behaviour of thermal conductivity around the critical point. The correlations are applicable for the temperature range from the triple point to 1100 $K$ and pressures up to 200 $MPa$.

	\begin{figure*}[H]
		\centering
		\includegraphics[trim = 1.5cm 2.5cm 1.5cm 2.0cm,clip,width=0.95\textwidth]{Figures/KT.pdf}	
		\caption{Thermal conductivity obtained based on different correlations }
		\label{fig: SFE_Properties_kt}
	\end{figure*}

\end{document}

### 2023-04-19 SFE-article/Sections/introduction_imp.tex
19.04

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	Over the years, the extraction of natural substances from solid materials and liquids using solvents has been a topic of significant interest for research and development. Supercritical fluids are particularly useful in extraction processes due to their pressure-dependent dissolving power and ability to exhibit both gas- and liquid-like properties, such as fluid-like density and gas-like diffusivity. Of the various supercritical fluids available, supercritical $CO_2$ is particularly attractive due to its nontoxic, non-flammable, and non-corrosive properties. Moreover, the critical point of $CO_2$ is relatively low ($73.8$ bar and $31 ^\circ C$) compared to other fluids, making it an excellent alternative to traditional extraction techniques.

	Different mathematical models have been proposed to describe the extraction of valuable compounds from a fixed biomass bed, as reviewed by \citet{Huang2012}. However, the selection of an appropriate extraction model should be based on the knowledge of the physical phenomena taking place in the operational unit. Each model has its own set of assumptions and describes different mass transfer mechanisms and equilibrium relationships.

	Based on an analogy to heat transfer, \citet{Reverchon1993} proposed a hot ball model to describe an extraction process from solid particles containing small quantities of solute, where solubility is not a limiting factor. \citet{Sovova1994} presented the Broken-and-Intact Cell model, which describes a system where the outer surfaces of particles have been mechanically interrupted, allowing easy access of solvent to the solute from the broken cells. In contrast, the solute from the intact cells is less accessible due to high mass transfer resistance.

	\citet{Reverchon1996} developed a model for fluid-solid extraction, where the oil is treated as a single component, and the extraction process is controlled by internal mass transfer resistance, neglecting external mass transfer. This model, however, does not consider the influence of axial dispersion or changes in density and flow rate along the bed. Our work assumes that the extraction process operates semi-continuously in a cylindrical vessel. The solvent is first brought to supercritical conditions, pumped through a fixed bed of finely chopped biomass, and the solute is extracted from the biomass. The solvent and solute are then separated in a flush drum, and the extract is collected. The feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) of the extractor can be measured and manipulated. In contrast, the vessel pressure ($P$) can be measured and manipulated, but the outlet temperature ($T_{out}$) can only be measured. Figure \ref{fig: SFE_drawing} depicts a simplified flow diagram.

	\begin{figure}[h!]
		\centering
		\includegraphics[width=0.95\columnwidth]{Figures/SFE_PFD_cropped.pdf}
		\caption{Process flow diagram ({\color{red}Font size}) }
		\label{fig: SFE_drawing}
	\end{figure}

\end{document}

### 2023-04-20 SFE-article/Sections/Cardano.tex
20.04

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	Following the work of \citet{Gmehling2019}, a cubic equation of state can be written a following form

	{\footnotesize
		\begin{equation}
			Z^3 + UZ^2+ SZ + T = 0
		\end{equation}
	}

	with Z as the compressibility factor. Using Cardano's formula, this type of equation can be solved analytically.
	With the abbreviations

	{\footnotesize
		\begin{equation*}
			P = \cfrac{3S-U^2}{3} \qquad Q = \cfrac{2U^3}{27}-\cfrac{US}{3} + T
		\end{equation*}
	}

	the discriminant can be determined to be

	{\footnotesize
		\begin{equation}
			D = \left( \cfrac{P}{3} \right)^3 + \left( \cfrac{Q}{2} \right)^2
		\end{equation}
	}

	For $D>0$, the equation of state has one real solution:

	{\footnotesize
		\begin{equation}
			Z = \left[ \sqrt{D} - \cfrac{Q}{2} \right]^{1/3} - \cfrac{P}{ 3 \left[ \sqrt{D}-\cfrac{Q}{2} \right]^{1/3} } - \cfrac{U}{3}
		\end{equation}
	}

	For $D<0$, there are three real solutions. With the abbreviations

	{\footnotesize
		\begin{equation*}
			\Theta = \sqrt{-\cfrac{P^3}{27}} \qquad \Phi = \arccos\left( \cfrac{-Q}{2\Theta} \right)
		\end{equation*}
	}

	they can be written as

	{\footnotesize
		\begin{align}
			Z_1 &= 2\Theta^(1/3) \cos \left( \cfrac{\Phi}{3} \right) - \cfrac{U}{3} \\
			Z_2 &= 2\Theta^(1/3) \cos \left( \cfrac{\Phi}{3} + \cfrac{2\pi}{3} \right) - \cfrac{U}{3} \\
			Z_3 &= 2\Theta^(1/3) \cos \left( \cfrac{\Phi}{3} + \cfrac{4\pi}{3} \right) - \cfrac{U}{3} 
		\end{align}
	}

	The largest and the smallest of the three values correspond to the vapor and to	the liquid solutions, respectively. The middle one has no physical meaning.

\end{document}

### 2023-04-20 SFE-article/Sections/Gouverning_equation_derivation.tex
08.03
09.03
10.03
16.03
20.04

--- 2023-02-16 SFE-report/Sections/Gouverning_equation_derivation.tex
@@
 
+	\label{CH: Gouverning equations}
+
 	\subsubsection{Mass continuity}
 
-	\label{CH: Gouverning equations}
-
+	Following the work of \citet{Anderson1995}, the governing equations for compressible fluid with non-uniform cross-section can be obtained.
 Let's assume that any properties of the flow are uniform across any given cross-section of an extractor.
@@
 The $A_f(z)$ is an arbitrary function, which describe change of the cross-section of an extractor.
-The function $A_f(z)$ can be defined as $A_f(z) = \textbf{A} \varepsilon(z)$, where $\varepsilon$ is the bed porosity and $\textbf{A}$ is the cross-section of an empty extractor.
+The function $A_f(z)$ can be defined as $A_f(z) = \textbf{A} \phi(z)$, where $\phi$ is the bed porosity and $\textbf{A}$ is the cross-section of an empty extractor.
 
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f \textbf{A} \varepsilon (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f \textbf{A} \varepsilon (z) V \right)}{\partial z} = 0
+			\cfrac{\partial \left( \rho_f \textbf{A} \phi (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f \textbf{A} \phi (z) V \right)}{\partial z} = 0
 		\end{equation}
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f \varepsilon (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f \varepsilon (z) V \right)}{\partial z} = 0
+			\cfrac{\partial \left( \rho_f \phi (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f \phi (z) V \right)}{\partial z} = 0
 		\end{equation}
@@
 
-	If so called superficial velocity is defined $u=\varepsilon V$, the mass continuity becomes
+	If so called superficial velocity is defined $u=\phi V$, the mass continuity becomes
 
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f \varepsilon (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f u \right)}{\partial z} = 0
+			\cfrac{\partial \left( \rho_f \phi (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f u \right)}{\partial z} = 0
 			\label{EQ: Mass_Continuity}
@@
 \ref{EQ: Continuity_integral_general} with additional terms on the right-hand side.
-The first term on the right-hand side describes that a substance goes from high density regions to low density regions and is based on the Fick's law ${\footnotesize\left( J_{diff} = D\cfrac{\partial C_f}{\partial z} \right)}$.
+The first term on the right-hand side describes that a substance goes from high density regions to low density regions and is based on the Fick's law $\left( J_{diff} = D_e^M\frac{\partial c_f}{\partial z} \right)$.
 The other term correspond for the mass transfer between solid and fluid phases, which is treated as a source term.
@@
 		\begin{equation}
-			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} C_f d\mathcal{V}_f + \iint_S C_f \textbf{V} \cdot \textbf{dS} = \iint_S J_{diff} \cdot \textbf{n}~\textbf{dS} + \cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_s} C_s d\mathcal{V}_s
+			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} c_f d\mathcal{V}_f + \iint_S c_f \textbf{V} \cdot \textbf{dS} = \iint_S J_{diff} \cdot \textbf{n}~\textbf{dS} + \cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_s} c_s d\mathcal{V}_s
 			\label{EQ: Integral_Mass_Species_general}
@@
 		\begin{align}
-			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} C_f d\mathcal{V}_f &= \cfrac{\partial}{\partial t}\left( C_f A_f dz \right) \\
-			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_s} C_s d\mathcal{V}_s &= \cfrac{\partial}{\partial t}\left( C_s A_s dz \right)
+			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} c_f d\mathcal{V}_f &= \cfrac{\partial}{\partial t}\left( c_f A_f dz \right) \\
+			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_s} c_s d\mathcal{V}_s &= \cfrac{\partial}{\partial t}\left( c_s A_s dz \right)
 		\end{align}
@@
 		\begin{equation}
-			\iint_S C_f \textbf{V} \cdot \textbf{dS} = C_f V dA_f + C_f A_f dV + V A_f dC_f 
+			\iint_S c_f \textbf{V} \cdot \textbf{dS} = c_f V dA_f + c_f A_f dV + V A_f dc_f 
 		\end{equation}
@@
 		\begin{equation}
-			\cfrac{\partial \left( C_f A_f \right)}{\partial t} + \cfrac{\partial \left( C_f A_f V \right)}{\partial x} = \cfrac{\partial \left( C_s A_s \right) }{\partial t} + \cfrac{\partial \left( J_{diff} A_f \right) }{\partial z}
+			\cfrac{\partial \left( c_f A_f \right)}{\partial t} + \cfrac{\partial \left( c_f A_f V \right)}{\partial z} = \cfrac{\partial \left( c_s A_s \right) }{\partial t} + \cfrac{\partial \left( J_{diff} A_f \right) }{\partial z}
 		\end{equation}
@@
 
-	By defining $A_f = A \cdot \varepsilon$, $A_s = A \cdot \left( 1-\varepsilon \right)$ and $u=V \cdot \varepsilon$, and assuming that $A$ is constant, the above equation becomes
+	By defining $A_f = A \cdot \phi$, $A_s = A \cdot \left( 1-\phi \right)$ and $u=V \cdot \phi$, and assuming that $A$ is constant, the above equation becomes
 
@@
 		\begin{equation}
-			\cfrac{\partial \left( C_f \varepsilon \right)}{\partial t} + \cfrac{\partial \left( C_f u\right)}{\partial x} = \cfrac{\partial \left( C_s (1-\varepsilon) \right) }{\partial t} + \cfrac{\partial \left( J_{diff} \varepsilon \right) }{\partial z}
+			\cfrac{\partial \left( c_f \phi \right)}{\partial t} + \cfrac{\partial \left( c_f u\right)}{\partial z} = \cfrac{\partial \left( c_s (1-\phi) \right) }{\partial t} + \cfrac{\partial \left( J_{diff} \phi \right) }{\partial z}
 		\end{equation}
@@
 
-	By expanding above equation, splitting variable and assuming that ${\footnotesize \cfrac{\partial \varepsilon}{\partial t}=0}$ we get
+	By assuming that ${\footnotesize \frac{\partial \phi}{\partial t}=0}$ and expanding $J_{diff}$, we get
 
@@
 		\begin{equation}
-			\cfrac{\partial C_f}{\partial t} + \cfrac{u}{\varepsilon} \cfrac{\partial C_f}{\partial z} + \cfrac{C_f}{\varepsilon} \cfrac{\partial u}{\partial z} = \cfrac{1-\varepsilon}{\varepsilon} \cfrac{\partial C_s}{\partial t} + \cfrac{D}{\varepsilon} \cfrac{\partial C_f}{\partial z} \cfrac{\partial \varepsilon}{\partial z} + \cfrac{\partial}{\partial z} \left( D \cfrac{\partial C_f}{\partial z} \right)
+			\cfrac{\partial c_f}{\partial t} + \cfrac{1}{\phi} \cfrac{\partial \left( c_f u\right)}{\partial z} = \cfrac{ (1-\phi)}{\phi} \cfrac{\partial c_s }{\partial t} + \cfrac{1}{\phi} \cfrac{\partial}{\partial z} \left( D_e^M \cfrac{\partial c_f}{\partial z} \right)
 		\end{equation}
@@
 
-	The equation can be further simplified if $\cfrac{\partial u}{\partial z} = \cfrac{\partial \varepsilon}{\partial z} = D = 0$, which corresponds to the assumptions of constant velocity along the bed( which might be a case of isothermal and low-mach number flow), constant porosity( which comes from the assumption of constant area for both solid and fluid phase) and no radial diffusion.
+	The equation can be further simplified if $\frac{\partial u}{\partial z} = \frac{\partial \phi}{\partial z} = D_e^M = 0$, which corresponds to the assumptions of constant velocity along the bed( which might be a case of isothermal and low-mach number flow), constant porosity( which comes from the assumption of constant area for both solid and fluid phase) and no radial diffusion.
 
@@
 		\begin{equation}
-			\cfrac{\partial C_f}{\partial t} + \cfrac{u}{\varepsilon} \cfrac{\partial C_f}{\partial z}  = \cfrac{1-\varepsilon}{\varepsilon} \cfrac{\partial C_s}{\partial t} 
+			\cfrac{\partial c_f}{\partial t} + \cfrac{u}{\phi} \cfrac{\partial c_f}{\partial z}  = \cfrac{1-\phi}{\phi} \cfrac{\partial c_s}{\partial t} 
 			\label{EQ: Simplified_Species_Conservation}
@@
 
-	The Eq. \ref{EQ: Conservative_Momentum} can be expanded further by assuming that $A_f = \textbf{A}\varepsilon$
+	The Eq. \ref{EQ: Conservative_Momentum} can be expanded further by assuming that $A_f = \textbf{A}\phi$
 
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f V \textbf{A} \varepsilon \right) }{\partial t} + \cfrac{\partial \left( \rho_f V^2 \textbf{A} \varepsilon \right) }{\partial z} = - 	\textbf{A} \varepsilon \cfrac{\partial P}{\partial t}
+			\cfrac{\partial \left( \rho_f V \textbf{A} \phi \right) }{\partial t} + \cfrac{\partial \left( \rho_f V^2 \textbf{A} \phi \right) }{\partial z} = - 	\textbf{A} \phi \cfrac{\partial P}{\partial t}
 		\end{equation}
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f V \varepsilon \right) }{\partial t} + \cfrac{\partial \left( \rho_f V^2 \varepsilon \right) }{\partial z} = - \varepsilon 	\cfrac{\partial P}{\partial t}
+			\cfrac{\partial \left( \rho_f V \phi \right) }{\partial t} + \cfrac{\partial \left( \rho_f V^2 \phi \right) }{\partial z} = - \phi 	\cfrac{\partial P}{\partial t}
 		\end{equation}
@@
 
-	If the superficial velocity $u=\varepsilon V$ is introduced, then the momentum conservation becomes
+	If the superficial velocity $u=\phi V$ is introduced, then the momentum conservation becomes
 
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f u \right)}{\partial z} + \cfrac{\partial \left( \rho_f u^2/\varepsilon \right) }{\partial z} = -\varepsilon \cfrac{\partial 	P}{\partial z}
+			\cfrac{\partial \left( \rho_f u \right)}{\partial z} + \cfrac{\partial \left( \rho_f u^2/\phi \right) }{\partial z} = -\phi \cfrac{\partial 	P}{\partial z}
 		\end{equation}
@@
 \ref{EQ: Non-conservative_Momentum} is stylistically the same as the general momentum conservation for one-dimensional flow with no-body forces.
-The momentum equation can be expressed in terms of superficial velocity $u=V\varepsilon$.
+The momentum equation can be expressed in terms of superficial velocity $u=V\phi$.
 
@@
 		\begin{equation}
-			\rho_f \cfrac{\partial \left(u / \varepsilon \right)}{\partial t} + \rho_f \cfrac{u}{\varepsilon} \cfrac{\partial \left( u / \varepsilon \right)}{\partial z} = - \cfrac{\partial P}{\partial z}
+			\rho_f \cfrac{\partial \left(u / \phi \right)}{\partial t} + \rho_f \cfrac{u}{\phi} \cfrac{\partial \left( u / \phi \right)}{\partial z} = - \cfrac{\partial P}{\partial z}
 		\end{equation}
@@
 		\begin{equation}
-			\cfrac{\rho_f}{\varepsilon} \cfrac{\partial u}{\partial t} + \rho_f u \cfrac{\partial \varepsilon^{-1}}{\partial t} + \rho_f \cfrac{u}{\varepsilon} \cfrac{1}{\varepsilon} \cfrac{\partial u}{\partial z} + \rho_f \cfrac{u}{\varepsilon} u \cfrac{\partial \varepsilon^{-1} }{\partial z} = - \cfrac{\partial P}{\partial z}
+			\cfrac{\rho_f}{\phi} \cfrac{\partial u}{\partial t} + \rho_f u \cfrac{\partial \phi^{-1}}{\partial t} + \rho_f \cfrac{u}{\phi} \cfrac{1}{\phi} \cfrac{\partial u}{\partial z} + \rho_f \cfrac{u}{\phi} u \cfrac{\partial \phi^{-1} }{\partial z} = - \cfrac{\partial P}{\partial z}
 		\end{equation}
@@
 
-	If the bed is not compressible and doesn't change its properties during the batch, then ${\footnotesize\cfrac{\partial \varepsilon}{\partial t}=0}$
+	If the bed is not compressible and doesn't change its properties during the batch, then ${\footnotesize\cfrac{\partial \phi}{\partial t}=0}$
 
@@
 		\begin{equation}
-			\cfrac{\rho_f}{\varepsilon} \left( \cfrac{\partial u}{\partial t} + \cfrac{u}{\varepsilon} \cfrac{\partial u}{\partial z} + u^2 \cfrac{\partial \varepsilon^{-1}}{\partial z} \right) = -\cfrac{\partial P}{\partial z}
+			\cfrac{\rho_f}{\phi} \left( \cfrac{\partial u}{\partial t} + \cfrac{u}{\phi} \cfrac{\partial u}{\partial z} + u^2 \cfrac{\partial \phi^{-1}}{\partial z} \right) = -\cfrac{\partial P}{\partial z}
 		\end{equation}
@@
 		\begin{equation}
-			\cfrac{\rho_f}{\varepsilon} \left( \cfrac{\partial u}{\partial t} + \cfrac{u}{\varepsilon} \cfrac{\partial u}{\partial z} \right) = -\cfrac{\partial P}{\partial z}
+			\cfrac{\rho_f}{\phi} \left( \cfrac{\partial u}{\partial t} + \cfrac{u}{\phi} \cfrac{\partial u}{\partial z} \right) = -\cfrac{\partial P}{\partial z}
 			\label{EQ: Non-conservative_Momentum_Const_Porosity}
@@
 
-	{TODO: \color{red}finish derivation of energy equation for real gas and introduce homogenous version of the energy equation}
+%	{TODO: \color{red}finish derivation of energy equation for real gas and introduce homogenous version of the energy equation}
 

### 2023-04-20 SFE-article/Sections/Model.tex
20.04

@@
 	\subsubsection{Continuity equation} \label{CH: Continuity}
-	The details of derivation can be found in the appendix \ref{CH: Gouverning equations}.
-The continuity equation for the fluid phase is given by equation \ref{EQ: CompressibleEuler_1}.
-If $A_f$ is specified to be a function of void fraction $A_f = A\varepsilon(z)$, where $\varepsilon$ is void fraction of the bed and $A$ is the cross-section of the empty extractor.
-The continuity equation become
+	The continuity equation for the fluid phase is derived in Appendix \ref{CH: Gouverning equations}.
+When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{magenta}\phi}(z)$ (where ${\color{magenta}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: \todo[]{assign color to v and u}
 
@@
 		\begin{equation*}
-			\cfrac{\partial \left( \rho_f \varepsilon \right)}{\partial t} + \cfrac{\partial \left( \rho_f v \varepsilon \right)}{\partial z} = 0
+			\frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{magenta}\phi})}{\partial t} + \frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) v A {\color{magenta}\phi})}{\partial {\color{blue}z}} = 0
 		\end{equation*}
@@
 
-	Assuming that the mass flow-rate is constant in time, the temporal derivative become zero and the spacial derivative can be integrated along $z$.
+	Assuming that the mass flow rate is constant in time, the temporal derivative becomes zero, and the spatial derivative can be integrated along ${\color{blue}z}$ as
 
@@
 		\begin{equation}
-			\int \cfrac{\partial \left( \rho_f v \varepsilon \right)}{\partial z} dz = 0 \rightarrow F=\rho_f v \varepsilon
+			\int \frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) v A {\color{magenta}\phi})}{\partial {\color{blue}z}} dz = 0 \rightarrow {\color{red}F}={\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) v A {\color{magenta}\phi}
 		\end{equation}
@@
 
-	where $F$ is a constant obtained from the integration and it is understood as the mass flux per unit area which is assumed to be constant along $z$.
-$F$ can treated as a control variable, which can change in time but it is constant in space.
-Such a assumption allows to find the velocity profile which satisfy the mass continuity based on $F, \varepsilon$ and $\rho_f$.
-The fluid density $\rho_f$ density is connected through equation of state with thermodynamical pressure, which is assumed to be constant along $z$ (due to the low-Mach number) and temperature \todo{Elaborate, the pressure is know (a control variable) and temperature can be found from energy equation}.
-The variation in density might be caused by the accumulation of the fluid \todo{Introduce relation between accumulation, pressure and energy equation} in the system (which happen instantaneously along $z$) or by temperature change.
-To simplify the dynamic of the system, it is assumed that $F=F(t)$ is a control variable and affects the whole system instantaneously.
+	Here, ${\color{red}F}$ is a constant obtained from the integration and is understood as the mass flux per unit area, which is assumed to be constant along ${\color{blue}z}$.
+To simplify the dynamics of the system, it is assumed that ${\color{red}F}={\color{red}F}(t)$ is a control variable and affects the whole system instantaneously.
+This assumption allows for finding the velocity profile that satisfies mass continuity based on ${\color{red}F}(t)$, ${\color{magenta}\phi}(z)$, and ${\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))$.
+
+	{\footnotesize
+	\begin{equation}
+		v = \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) A {\color{magenta}\phi}} 
+	\end{equation}
+	}
+
+	The fluid density ${\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be obtained from an equation of state if temperature and the thermodynamic pressure (assumed ${\color{red}P}(t)$ to be constant along ${\color{blue}z}$ due to the low-Mach number condition) are known.
+The variation in density may be caused by the fluid accumulation in the system (equivalent to pressure change), which occurs instantaneously along ${\color{blue}z}$ or by a temperature change.
+
+	Analogously, the superficial velocity mught be introduced to the model and defined as
+
+	{\footnotesize
+		\begin{equation}
+			u = v {\color{magenta}\phi} = \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) A }
+		\end{equation}
+	}
 
@@
 
-	The detail derivation of the mass balance equation for the fluid phase can be found in the appendix (\ref{CH: Gouverning equations}).
-The movement of the mobile pseudo-homogeneous phase (equation \ref{Model_fluid}) is considered only in the axial direction.
-The properties of the system in the radial direction are assumed to be uniform.
-In addition, it is considered that the boundary layer adjacent to the inner wall of the extractor does not exist.
-Therefore, the velocity profile is constant across any cross-section of the extractor perpendicular to the axial direction.
-As a result, the plug flow model \todo{Double check if we can call it a plug flow} can be introduced.
-The particle size distribution and the void fraction of the solid phase cab change along an extractor but they remain constant in time.
-Moreover, the thermodynamic pressure is considered to be constant along the device, as discussed above.
-The amount of solute in the solvent is considered negligible.
-Therefore, the fluid phase can be described as pseudo-homogenous, and its properties are assumed to be the same as the solvent.
-The mass balance for the fluid phase consists of convection, diffusion, and kinetic terms.
-
-	%The process model consists of three partial differential equations: two mass balance equations relative to the concentration of solute in the fixed solid phase and the mobile fluid phase, and the heat balance equation relative to the temperature of the fluid phase.
+	The detailed derivation of the mass balance equation for the fluid phase can be found in the appendix (\ref{CH: Gouverning equations}).
+The movement of the mobile pseudo-homogeneous phase (equation \ref{Model_fluid}) is considered only in the axial direction, while the properties of the system in the radial direction are assumed to be uniform.
+Additionally, the boundary layer adjacent to the inner wall of the extractor is neglected, resulting in a constant velocity profile across any cross-section of the extractor perpendicular to the axial direction.
+Although the particle size distribution and void fraction of the solid phase may change along the extractor, they are assumed to remain constant in time.
+Furthermore, the thermodynamic pressure is assumed to be constant along the device due to the Low-Mach number condition, as previously discussed.
+The amount of solute in the solvent is considered negligible, resulting in the fluid phase being described as pseudo-homogeneous, and its properties are assumed to be the same as the solvent.
+The mass balance equation for the fluid phase includes convection, diffusion, and kinetic terms.
 
 	{\footnotesize
-		\begin{align} 
+		\begin{equation}
 			\label{Model_fluid}
-			\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t} &	=  \underbrace{- \cfrac{u_s}{\varepsilon} \cfrac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} - \underbrace{ \cfrac{ {\color{blue}c_f}(t,z) }{\varepsilon} \cfrac{\partial {\color{blue}u}(t,z)}{\partial {\color{blue}z}}}_{\text{Convective term}} \nonumber \\
-			&+ \underbrace{ \cfrac{ {\color{orange}D^M_e} }{\varepsilon} \left[{\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t)\right] \cfrac{\partial^2 {\color{blue}c_f}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusive term}}
-			+ \underbrace{ \cfrac{1-{\color{magenta}\varepsilon}}{{\color{magenta}\varepsilon}} {\color{blue}r_e}(t,z) }_{\text{Kinetic term}}
-	\end{align} }
+			\frac{\partial {\color{blue}c_f}(t,z)}{\partial t}
+			+ \frac{1}{{\color{magenta}\phi}} \frac{\partial \left( {\color{blue}c_f}(t,z) u\right)}{\partial {\color{blue}z}}
+			= \frac{1-{\color{magenta}\phi}}{{\color{magenta}\phi}} {\color{blue}r_e}(t,z)
+			+ \frac{1}{{\color{magenta}\phi}} \frac{\partial}{\partial {\color{blue}z}} \left( {\color{orange}D^M_e} \frac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}} \right)
+		\end{equation}
+	}
 
-	where ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z), {\color{blue}T}(t,z)$ correspond to concentration of solute in the fluid phase, concentration of solute in the solid phase and the temperature, respectively.
+	Here, ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z),$ and ${\color{blue}T}(t,z)$ represent the concentration of solute in the fluid phase, concentration of solute in the solid phase, and temperature, respectively.
 ${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term.
-${\color{red}F}(t)$ is the mass flow rate, ${\color{red}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient and $u$ is the superficial velocity.
-\todo{Remove symbols which have been introduced before}
+${\color{red}F}(t)$ is the mass flow rate, ${\color{red}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient, and $u$ is the superficial velocity.
 
@@
 
-	Considering the solid phase to be fixed, the convection and diffusion terms in the corresponding mass balance (equation \ref{Model_solid}) are both assumed to be negligible or absent.
-Therefore, the only term present in this equation is the kinetic term (defined as presented in equation \ref{Model_kinetic_basic}), which links solid and fluid phases.
-A single pseudo-component is used to represent the extract collectively.
+	The solid phase is considered to be stationary, with negligible convection and diffusion terms in the mass balance equation (equation \ref{Model_solid}).
+Therefore, the only significant term in this equation is the kinetic term (as defined in equation \ref{Model_kinetic_basic}), which connects the solid and fluid phases.
+The extract is represented by a single pseudo-component to simplify the analysis.
 
@@
 
-	The kinetic term is based on two-film theory and follow work of \citet{Reverchon1996}.
+	%The kinetic term is based on two-film theory and follow work of \citet{Reverchon1996}.
 The mass transfer kinetic (equation \ref{Model_kinetic_basic}) consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.
 
-	As the solvent flows through the bed, the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to for an external fluid film around the solid particles through the solvent–solid matrix interactions.
+	The kinetic term in this study is based on the two-film theory proposed by \citet{Reverchon1996} and the mass transfer kinetic is given by equation \ref{Model_kinetic_basic}.
+This equation takes into account the overall diffusion coefficient and the concentration gradient, which acts as the driving force for the process.
+
+%	As the solvent flows through the bed, the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles through the solvent–solid matrix interactions.
 Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected.
@@
 The overall mass transfer coefficient can be introduced if the relation between the solute concentration in one phase and its equilibrium concentration is known.
+
+	As the solvent flows through the bed, $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles due to the solvent-solid matrix interactions.
+The effect of Knudsen diffusion is negligible in this process, as the mean free path of the molecule is much smaller than the pore diameter.
+The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
+Figure \ref{fig: SFE_Mechanism} illustrates the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as ${\color{blue}c_s}$ and the equilibrium concentrations at the solid-fluid interface are denoted as ${\color{blue}c_s^*}$ and ${\color{blue}c_P^*}$, respectively, for solid and fluid phases.
+The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{blue}c_{P}}$.
+As the solute diffuses through the pore, its concentration changes and reaches ${\color{blue}c_{Pf}}$ at the opening of the pore.
+The solute then diffuses through the film around the particle and reaches a concentration in the bulk ${\color{blue}c_f}$.
+The two-film theory describes the solid-fluid interface inside the pore.
+The overall mass transfer coefficient can be determined if the relation between the solute concentration in one phase and its equilibrium concentration is known.
 
@@
 					\label{Model_kinetic_no_sat}
-					{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} }\left({\color{blue}c_s}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
+					{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} }\left({\color{blue}c_s}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
 			\end{equation} }
 
-        The above model does not take into account the saturation of fluid, which can be introduced by multiplying the gradient by a function $\gamma(c_f)$ (equation \ref{EQ: C_sat_function}).
-$\gamma(c_f)$ describe the reverse logistic function, which is equal to unity below the $c_{sat}$, the saturation concentration, and equal to zero, above the $c_{sat}$.
-The $\gamma(c_f)$ for $c_{sat}=5$ is shown on figure \ref{fig: Gamma_function}.
-
-        {\footnotesize
-            \begin{equation}
-                \gamma(c_f) = \cfrac{1}{1+\exp ( -k_{sat} \left( c_f - c_{sat} \right) ) }
-                \label{EQ: C_sat_function}
-            \end{equation}
-        }
-
-        where $k_{sat}$ is the growth rate, and it is defined as $k_{sat} = 2c_{sat}$\todo{Explain why the growth rate is defined as it is}.
-
-        \begin{figure}[h!]
-        	\centering
-        	\begin{tikzpicture}
-
-        		\begin{axis}[
-        			legend style={draw=none},
-        			xmin = 0, xmax = 10,
-        			ymin = -0.5, ymax = 1.5,
-        			xlabel = {$c_f[kg/m^3]$},
-        			ylabel = {$\gamma(c_f)[-]$}]
-        			\addplot[
-        			domain = 0:10,
-        			samples = 100,
-        			smooth,
-        			thick,
-        			blue,
-        			] { 1 / (1 + exp( 2*5 .* ( x - 5 ) ) ) };
-        			\addplot[thick, samples=50, dashed, domain=0:1.5, black] coordinates {(5,-0.5)(5,1.5)};
-
-        			\addlegendentry{$\gamma(c_f)$}
-        			\addlegendentry{$c_{sat}$}
-        		\end{axis}
-
-        	\end{tikzpicture}
-        \caption{$\gamma(c_f)$ function under assumption of $c_{sat}=5 [kg/m^3]$}
-        \label{fig: Gamma_function}
-        \end{figure}
-
-        The final form of the extraction kinetic equation is given by equation \ref{Model_kinetic}.
-
-        {\footnotesize
-			\begin{equation}
-				\label{Model_kinetic}
-				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} } \gamma(c_f) \left({\color{blue}c_s}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
-		\end{equation} }
+        %\subfile{Sections/Saturation}
 
@@
 						\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} &= 
-						\underbrace{ -\cfrac{{\color{red}F}(t) {\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))}{{\color{magenta}A} 	[(1-{\color{magenta}\epsilon}){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{orange}C_p} ({\color{blue}T}(t,z),{\color{red}P}(t)) + {\color{magenta} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}}  }_{\text{Convection}} + \\
+						\underbrace{ -\cfrac{{\color{red}F}(t) {\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))}{{\color{magenta}A} 	[(1-{\color{magenta}\epsilon}){\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{orange}C_p} ({\color{blue}T}(t,z),{\color{red}P}(t)) + {\color{magenta} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}}  }_{\text{Convection}} + \\
 						& + \underbrace{ {\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{red}P}(t)) \cfrac{\partial^2 {\color{blue}T}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusion}}
@@
 
-			The heat equation was introduced in the previous chapter through equation \ref{EQ: CompressibleEuler_3} or
+			The heat equation was introduced in the previous chapter through equation \ref{EQ: CompressibleEuler_3} and in the appendix \ref{CH: Gouverning equations}
 
 			{\footnotesize
-			\begin{equation*}
-				\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} = -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T}{\partial z} \right)
-			\end{equation*}
+			\begin{align}
+				&\cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{blue}e}(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) A_f v {\color{blue}e}(t,z) \right)}{\partial {\color{blue}z}} \nonumber \\
+				&= -{\color{red}P}(t)\cfrac{\left( A_f v \right)}{\partial {\color{blue}z}} + \cfrac{\partial}{\partial {\color{blue}z}} \left( \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}} \right)
+			\end{align}
 			}
 
-			For real gases the internal energy is defined as
+			Following \citet{Elliott2011} or \citet{Gmehling2019}, a real gases internal energy definition can be obtained from the departure functions:
 
@@
 				\begin{equation}
-					de=C_vdT-\left[P-T\left(\cfrac{\partial P}{\partial T}\right)_{V_m}\right]dv_m
+					d{\color{blue}e}(t,z)=C_vd{\color{blue}T}-\left[{\color{red}P}(t)-{\color{blue}T}(t,z)\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}(t,z)}\right)_{v_m}\right]dv_m
 					\label{EQ: internal_energy_def}
@@
 
-			If a gas is consider to be perfectly caloric ($e=C_v T$), then the energy equation can be written in form of temperature.
+			where ${\color{blue}e}^{id}(t,z)$ is the internal energy of perfect gas.
+
+			If a gas is consider to be perfectly caloric (${\color{blue}e}(t,z)=C_v {\color{blue}T}(t,z)$), then the energy equation can be written in form of temperature.
 The perfectly caloric gas can be seen as the special case of a real gas, where the second term of the equation \ref{EQ: internal_energy_def} goes to zero.
 
-			For real gases it is complicated to write the heat balance in terms of temperature, but it be used directly in the form of internal energy, as it is given by equation \ref{EQ: CompressibleEuler_3}.
+			For real gases it is complicated to write the heat balance in terms of temperature, but it be can used directly in the form of internal energy, as it is given by equation \ref{EQ: CompressibleEuler_3}.
 In such a case, the temperature (which is used as the input to some other functions) needs to be recover from the internal energy.
 A relation for the internal energy can be obtained from an equation of state.
-For Peng-Robinson, such a relation is given by equation \ref{EQ: internal_energy_PR}.
+For Peng-Robinson, such a relation is given by equation \ref{EQ: internal_energy_PR} as presented by \citet{Elliott2011}.
+
+%			{\footnotesize
+%				\begin{equation}
+%					e = C_vT + \cfrac{a\left(\alpha -T\cfrac{d \alpha}{dT}\right)}{2\sqrt{2}b} \ln \left[ \cfrac{1+b\left(1-\sqrt{2}\rho\right) }{1+b\left(1+\sqrt{2}\rho\right)} \right]
+%					\label{EQ: internal_energy_PR}
+%				\end{equation}
+%			}
 
@@
 				\begin{equation}
-					e = C_vT + \cfrac{a\left(\alpha -T\cfrac{d \alpha}{dT}\right)}{2\sqrt{2}b} \ln \left[ \cfrac{1+b\left(1-\sqrt{2}\rho\right) }{1+b\left(1+\sqrt{2}\rho\right)} \right]
+					\cfrac{{\color{blue}e}(t,z)-{\color{blue}e}^{id}(t,z)}{R{\color{blue}T}(t,z)} = - \cfrac{A}{B\sqrt{8}} \cfrac{\kappa \sqrt{T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{Z+\left( 1+\sqrt{2} \right)B}{Z+\left( 1+\sqrt{2} \right)B} \right]
 					\label{EQ: internal_energy_PR}
@@
 			To solve equation \ref{EQ: internal_energy_PR}, values of temperature, pressure and density needs to be know.
-If an equation of state is introduce, then only 2 out 3 variables needs to be know as the third one can be calculated, this can be represented as follow
-
-			{\footnotesize
-			\begin{equation*}
-				e(t,z)=e(T(t,z),P(t),\rho(t,z))=e( T(t,z), P(t), \rho(T(t,z),P(t)) ) 
-			\end{equation*}
-			}
-
-			If the value of internal energy $e$ is know from time evolution of the energy equation (\ref{EQ: CompressibleEuler_3}), and pressure is know from measurement, then the temperature can be reconstructed.
-A roootfinder can be used to find a value of temperature, which minimize the difference between value of internal energy coming from the time evolution and the output from equation \ref{EQ: internal_energy_PR}.
-Such a procedure allow to find local temperature along spatial direction $z$ and needs to be repeated every time-step.
-
-			Another way to express the energy equation is to introduce enthalpy $e = h - P_0 / \rho$. By introducing the definition of enthalpy, the energy equation becomes
+If an equation of state is introduce, then only two out three variables needs to be know as the third one can be calculated, this can be represented as follow
 
@@
 			\begin{equation}
-					\cfrac{\partial \left(\rho_f h A_f\right)}{\partial t} - \cfrac{\partial \left(P_0 A_f\right)}{\partial t} + \cfrac{\partial \left( \rho_f h A_f v \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
+				{\color{blue}e}(t,z)={\color{blue}e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)))=e( {\color{blue}T}(t,z),{\color{red}P}(t), \rho({\color{blue}T}(t,z),{\color{red}P}(t)) )
 			\end{equation}
@@
 
-			The main advantage of this formulation is the presence of term $\partial P_0 / \partial t $, which allow to directly affect the system through the change of thermodynamic pressure (which is a control variable).\todo{ "For high pressures, the influence of the intermolecular forces on the enthalpy has to be taken into account, usually by applying a cubic equation of state.
+			If the value of internal energy ${\color{blue}e}(t,z)$ is know from time evolution of the energy equation (\ref{EQ: CompressibleEuler_3}), and pressure is know from measurement, then the temperature can be reconstructed.
+A roootfinder can be used to find a value of temperature, which minimize the difference between value of internal energy coming from the time evolution and the output from equation \ref{EQ: internal_energy_PR}.
+Such a procedure allow to find local temperature along spatial direction ${\color{blue}z}$ and needs to be repeated every time-step.
+
+			Another way to express the energy equation is to introduce enthalpy ${\color{blue}h}(t,z) = {\color{blue}e}(t,z) + {\color{red}P}(t) / \rho$.
+By introducing the definition of enthalpy, the energy equation becomes
+
+			{\footnotesize
+				\begin{align}
+					&\cfrac{\partial \left({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{blue}h}(t,z) A_f\right)}{\partial t} - \cfrac{\partial \left({\color{red}P}(t) A_f\right)}{\partial t} \nonumber \\
+					&+ \cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{blue}h}(t,z) A_f v \right)}{\partial {\color{blue}z}} - \cfrac{\partial}{\partial {\color{blue}z}} \left( k \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}} \right)
+				\end{align}
+			}
+
+			The main advantage of this formulation is the presence of term $\partial {\color{red}P}(t) / \partial t $, which allow to directly affect the system through the change of thermodynamic pressure (which is a control variable).\todo{ "For high pressures, the influence of the intermolecular forces on the enthalpy has to be taken into account, usually by applying a cubic equation of state.
 In most cases, these forces are attractive, so that additional energy is necessary to move the molecules away from each other, that is, to lower the density.
@@
 				\begin{equation}
-					h(t,z)=h(T(t,z),P(t),\rho(t,z))=h( T(t,z), P(t), \rho(T(t,z),P(t)) ) 
+					{\color{blue}h}(t,z)=h({\color{blue}T}(t,z),{\color{red}P}(t),{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)))=h( {\color{blue}T}(t,z),{\color{red}P}(t), \rho({\color{blue}T}(t,z),{\color{red}P}(t)) )
 					\label{EQ:Enthalpy_root}
@@
 				\begin{equation}
-					h_{T,P}-h_{T,P}^{\mathrm {ideal} }=RT_{C}\left[T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right]
+					{\color{blue}h}(t,z)-{\color{blue}h}(t,z)^{id}=R{\color{blue}T}(t,z) \left[T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right]
 					\label{EQ:Enthalpy_PR}
@@
 
-			The equation \ref{EQ:Enthalpy_PR} requires an reference sate, which in this case is assumed to be $T_{ref}=298.15[K]$ and $P_{ref}=1.01325[bar]$.
+			The equation \ref{EQ:Enthalpy_PR} requires an reference sate, which in this case is assumed to be $T_{ref}=298.15~[K]$ and $P_{ref}=1.01325~[bar]$.
 
@@
 %				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
-				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} \cfrac{F(t)}{\rho(t,z)} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] 	\\
+				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} \cfrac{{\color{red}P}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] ({\color{blue}c_f}(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] 	\\
 %				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
-				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= \cfrac{F(t)}{\rho(t,z)} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]
+				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= \cfrac{{\color{red}P}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] ({\color{blue}c_f}(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]
                 \label{Model_measurment_2}
@@
 			{\color{blue} In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases ($c(t,z)$ and $q(t,z)$, respectively), and the local temperature of the pseudo-homogeneous phase ($T(t,z)$).
-The controllable input variables are the mass flow-rate and temperature of the solvent in the feed ($F_\text{in}(t) = F(t)$ and $T_\text{in}(t) = T(t,z=0)$, respectively) and the pressure in the extractor ($P(t,z) = P(t)$).
+The controllable input variables are the mass flow-rate and temperature of the solvent in the feed ($F_\text{in}(t) = {\color{red}P}(t)$ and $T_\text{in}(t) = T(t,z=0)$, respectively) and the pressure in the extractor ($P(t,z) ={\color{red}P}(t)$).
 {\color{red}We also assume that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator ($Y(t)$).} The system is controllable by manipulating the flow-rate and temperature of CO2 in the feed, and the pressure in the extractor.

### 2023-04-20 SFE-article/Sections/Parameter_estimation.tex
20.04

@@
 	\begin{align}
-		\phi &= \cfrac{1}{2} \int_{0}^{t_f}  \left[ Y(t) - y(\theta,t) \right]^T \Gamma^{-1} \left[ Y(t) - y(\theta,t) \right] dt \\
-		\hat{\theta} &= \arg \min_{\theta \in \Theta} \phi
+		\gamma &= \cfrac{1}{2} \int_{0}^{t_f}  \left[ Y(t) - y(\theta,t) \right]^T \Gamma^{-1} \left[ Y(t) - y(\theta,t) \right] dt \\
+		\hat{\theta} &= \arg \min_{\theta \in \Theta} \gamma
 \end{align} }
-where $\Gamma$ is the covariance matrix (or perhaps a matrix of appropriate weights), $\hat{\theta}$ is the parameter estimate, $\Theta$ is the parameter space, and $\phi$ is the time integrated value of the error squared ("integral squared error").
+where $\Gamma$ is the covariance matrix (or perhaps a matrix of appropriate weights), $\hat{\theta}$ is the parameter estimate, $\Theta$ is the parameter space, and $\gamma$ is the time integrated value of the error squared ("integral squared error").
 If the observations are made at discrete instants of time, $t_i$, $i = 1,2,...,n$, the Markov criterion is to minimize:
@@
 	\begin{align}
-		\phi &= \cfrac{1}{2} \sum_{i=1}^{n} \left[ Y(t_i) - y(\theta,t_i) \right]^T \Gamma^{-1} \left[ Y(t_i) - y(\theta,t_i) \right] \\
-		\hat{\theta} &= \arg \min_{\theta \in \Theta} \phi
+		\gamma &= \cfrac{1}{2} \sum_{i=1}^{n} \left[ Y(t_i) - y(\theta,t_i) \right]^T \Gamma^{-1} \left[ Y(t_i) - y(\theta,t_i) \right] \\
+		\hat{\theta} &= \arg \min_{\theta \in \Theta} \gamma
 \end{align} }
 
-If $\Gamma$ is a diagonal matrix, $\phi$  becomes a "weighted least squares" criterion; if $\Gamma = \sigma^2 \textbf{I}$ where $\sigma$ is a standard deviation, $\phi$ is the "ordinary least squares" criterion.
+If $\Gamma$ is a diagonal matrix, $\gamma$  becomes a "weighted least squares" criterion; if $\Gamma = \sigma^2 \textbf{I}$ where $\sigma$ is a standard deviation, $\gamma$ is the "ordinary least squares" criterion.
 

### 2023-04-20 SFE-article/Sections/Saturation.tex
20.04

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\subsubsection{Saturation Concentration}

	The above model does not take into account the saturation of fluid, which can be introduced by multiplying the gradient by a function $\gamma(c_f)$ (equation \ref{EQ: C_sat_function}). $\gamma(c_f)$ describe the reverse logistic function, which is equal to unity below the $c_{sat}$, the saturation concentration, and equal to zero, above the $c_{sat}$. The $\gamma(c_f)$ for $c_{sat}=5$ is shown on figure \ref{fig: Gamma_function}.

	{\footnotesize
		\begin{equation}
			\gamma(c_f) = \cfrac{1}{1+\exp ( -k_{sat} \left( c_f - c_{sat} \right) ) }
			\label{EQ: C_sat_function}
			\end{equation}
	}

	where $k_{sat}$ is the growth rate, and it is defined as $k_{sat} = 2c_{sat}$\todo{Explain why the growth rate is defined as it is}.

	\begin{figure}[h!]
		\centering
			\begin{tikzpicture}

				\begin{axis}[
					legend style={draw=none},
					xmin = 0, xmax = 10,
					ymin = -0.5, ymax = 1.5,
					xlabel = {$c_f[kg/m^3]$},
					ylabel = {$\gamma(c_f)[-]$}]
					\addplot[
					domain = 0:10,
					samples = 100,
					smooth,
					thick,
					blue,
					] { 1 / (1 + exp( 2*5 .* ( x - 5 ) ) ) };
					\addplot[thick, samples=50, dashed, domain=0:1.5, black] coordinates {(5,-0.5)(5,1.5)};

					\addlegendentry{$\gamma(c_f)$}
					\addlegendentry{$c_{sat}$}
				\end{axis}

			\end{tikzpicture}
			\caption{$\gamma(c_f)$ function under assumption of $c_{sat}=5 [kg/m^3]$}
			\label{fig: Gamma_function}
	\end{figure}

	The final form of the extraction kinetic equation is given by equation \ref{Model_kinetic}.

	{\footnotesize
		\begin{equation}
			\label{Model_kinetic}
				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} } \gamma(c_f) \left({\color{blue}c_s}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
		\end{equation} }

\end{document}

### 2023-04-20 SFE-article/Sections/Thermodynamic_details.tex
20.04

@@
 	\subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}
-	We consider equations of state in the general form ${\color{red}P}(t) {\color{orange}V_{\text{CO}_2}}\left[T(t,z),P(t)\right] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, where ${\color{magenta}V_{\text{CO}_2}}$ denotes the molar volume of $\text{CO}_2$, ${\color{orange}Z}$ represents its compressibility factor, and $R$ is the universal gas constant.
+	We consider equations of state in the general form ${\color{red}P}(t) {\color{orange}v_m}\left[T(t,z),P(t)\right] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, where ${\color{magenta}v_m}$ denotes the molar volume of $\text{CO}_2$, ${\color{orange}Z}$ represents its compressibility factor, and $R$ is the universal gas constant.
 More specifically, we are interested in these equations because of the possibility to express the compressibility $Z$ as an explicit function of temperature and pressure.
@@
 Because temperature $T(t,z)$ of the fluid phase is a modelled variable, we allow for the density to vary along the bed and in time.
-From an equation of state of the form ${\color{red}P}(t) {\color{orange}V_{\text{CO}_2}}\left[T(t,z),P(t)\right] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, we get
+From an equation of state of the form ${\color{red}P}(t) {\color{orange}v_m}\left[T(t,z),P(t)\right] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, we get
 
@@
 }\eqref{eq: CvR}} \nonumber \\
-		&+ {\color{blue}T}(t,z) \underbrace{\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}V_{\text{CO}_2}}(t,z)}}_{\text{Eq.
-} \eqref{eq: dPdT}} \underbrace{\left(\cfrac{\partial {\color{orange}V_{\text{CO}_2}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)}}_{\text{Eq.
+		&+ {\color{blue}T}(t,z) \underbrace{\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)}}_{\text{Eq.
+} \eqref{eq: dPdT}} \underbrace{\left(\cfrac{\partial {\color{orange}v_m}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)}}_{\text{Eq.
 } \eqref{eq: dVdT}} - {\color{magenta}R}.
@@
 	\begin{equation}
-		\left( \cfrac{\partial {\color{orange}V_{\text{CO}_2}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)} = \cfrac{{\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] {\color{magenta}R}}{{\color{red}P}(t)} + \cfrac{{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{red}P}(t)} \underbrace{\left( \cfrac{\partial {\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)}}_{\text{Eq.
+		\left( \cfrac{\partial {\color{orange}v_m}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)} = \cfrac{{\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] {\color{magenta}R}}{{\color{red}P}(t)} + \cfrac{{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{red}P}(t)} \underbrace{\left( \cfrac{\partial {\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)}}_{\text{Eq.
 }\eqref{eq: dZdT}} \label{eq: dVdT}
@@
 	\begin{equation}
-		\left(\cfrac{\partial{\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} = \left(\cfrac{\partial \dfrac{{\color{red}P}(t) {\color{orange}V_{\text{CO}_2}}\left[T(t,z),P(t)\right]}{{\color{magenta}R}{\color{blue}T}(t,z)}}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} \label{eq: dZdT}
+		\left(\cfrac{\partial{\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} = \left(\cfrac{\partial \dfrac{{\color{red}P}(t) {\color{orange}v_m}\left[T(t,z),P(t)\right]}{{\color{magenta}R}{\color{blue}T}(t,z)}}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} \label{eq: dZdT}
 	\end{equation} }
@@
 	\begin{equation}
-		\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}V_{\text{CO}_2}}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{magenta}V_{\text{CO}_2}}\left[T(t,z),P(t)\right]}}}{\partial{\color{blue}T}}\right)_{{\color{orange}V}(t,z)} \label{eq: dPdT}
+		\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{magenta}v_m}\left[T(t,z),P(t)\right]}}}{\partial{\color{blue}T}}\right)_{{\color{orange}V}(t,z)} \label{eq: dPdT}
 	\end{equation} }
@@
 		\begin{equation}
-			\frac{H^{\mathrm {ig} }-H}{RT} =\int_{V}^{\infty }\left[T\left({\frac{\partial Z}{\partial T}}\right)_{V}\right]{\frac{dV}{V}} + 1-Z
+			\frac{h^{id}-h}{RT} =\int_{v_m}^{\infty }\left[T\left({\frac{\partial Z}{\partial T}}\right)_{v_m}\right]{\frac{dv_m}{v_m}} + 1-Z
 		\end{equation}
@@
 
-	The Peng–Robinson equation of state relates the three interdependent state properties pressure $P$, temperature $T$, and molar volume $V_m$.
-From the state properties ($P$, $V_m$, $T$), one may compute the departure function for enthalpy per mole (denoted $h$) as presented by \citet{Gmehling2019} or \citet{Elliott2011}:
+	The Peng–Robinson equation of state relates the three interdependent state properties pressure $P$, temperature $T$, and molar volume $v_m$.
+From the state properties ($P$, $v_m$, $T$), one may compute the departure function for enthalpy per mole (denoted $h$) as presented by \citet{Gmehling2019} or \citet{Elliott2011}:
 
@@
 		\begin{equation}
-			h_{T,P}-h_{T,P}^{\mathrm {ideal} }=RT_{C}\left[T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right]
+			h-h^{\mathrm {id} }=RT\left[T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right]
 		\end{equation}

### 2023-04-21 SFE-article/Sections/Model.tex
21.04

@@
 %				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
-				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} \cfrac{{\color{red}P}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] ({\color{blue}c_f}(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] 	\\
+				y(t) &= \int_{t_0}^{t_f} \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))} {\color{blue}c_f}(t,z) \biggr\rvert_{z=L} dt \\
 %				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
-				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= \cfrac{{\color{red}P}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))} \left[ \cfrac{kg}{s} \left( \cfrac{kg}{m^3} \right)^{-1} \right] ({\color{blue}c_f}(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]
+				\cfrac{dy}{dt} &= \qquad \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))} {\color{blue}c_f}(t,z) \biggr\rvert_{z=L} 
                 \label{Model_measurment_2}

### 2023-04-21 SFE-article/Sections/Parameter_estimation.tex
21.04

@@
 
-Conceptually, the unobservable error $\epsilon(t)$\todo[fancyline]{The same symbol as void fraction} is added to the deterministic model output, $y(t)$ (equation \ref{Model_measurment_1}), to give the observable dependent variable $Y(t)$ (for example results of an experiments).
-For discrete observations:
+The goal of parameter estimation is to obtain the "best" estimate of parameter set $\theta$ (which is a subset of the parameter space $\Theta$ containing all parameters of a model) based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$.
+Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, $y(t)$ (equation \ref{Model_measurment_1}), to give the observable dependent variable $Y(t)$ (for example results of an experiments).
+For discrete observations, this can be expressed as:
 
@@
 	\begin{equation*}
-		Y(t_i) = y(t_i) + \epsilon(t_i)
+		Y(t_i) = y(\theta, t_i) + \epsilon(t_i)
 \end{equation*} }
-and for continuos variables:
+
+For continuous variables, the equation is:
 
@@
 	\begin{equation*}
-		Y(t) = y(t) + \epsilon(t)
+		Y(t) = y(\theta, t) + \epsilon(t)
 \end{equation*} }
 
-%If the estimated parameter $\hat{\theta}$ replaces the model parameter $\theta$, the residue error is $\textbf{E} = Y(t) - \hat{Y}(t)$, where $\hat{Y}(t)$ is the predicted value of $Y_i$ at $y_i$. 
-The objective in parameter estimation is to obtain the "best" estimate of $\theta$ based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$.
-The above equation can be written in general form as:
-
-{\footnotesize
-	\begin{equation} \label{EQ: Measurment_noise}
-		Y(t_i) = y(\theta, t_i) + \epsilon(t_i)
-\end{equation}}
-
-where $\theta$ is set of parameters to be estimated from the data. $\theta$ is a subset of parameter space $\Theta$, which contain all parameters of the model.
-
-Because of the difficulty of obtaining analytical solutions to the deterministic process model, experiments have been arranged whereby the vector of derivatives $d Y(t_i)/dt$ is measured rather than $Y(t_i)$ itself.
-In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ (equation \ref{Model_measurment_2}) as follows:
+However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $dY(t_i)/dt$ is measured instead of $Y(t_i)$ itself.
+In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ (as shown in equation \ref{Model_measurment_2}) as follows:
 
@@
 
-If unobservable error in the first observation is designated as $\epsilon_1$, the second error observation $\epsilon_2'$ includes $\epsilon_1$ plus a random component introduced side from $\epsilon_1$, or $\epsilon_2' = \epsilon_1 + \epsilon_2$.
-The error in the third observation is $\epsilon_3' = \epsilon_1 + \epsilon_2 + \epsilon_3$, and so forth.
-\citet{Mandel1957} distinguished between the usually assumed type of independent measuring error in the dependent variable and a 'cumulative' or interval error in which each new observation includes the error of the previous observations.
-Cumulative errors, arising because of the fluctuations as a function of time in the process itself due to small changes in operating, are not independent - only the differences in measurement from one period to the next are independent.
+In the case where the error in the first observation is denoted as $\epsilon_1$, the error in the second observation $\epsilon_2'$ incorporates $\epsilon_1$ as well as an independent random component, given by $\epsilon_2' = \epsilon_1 + \epsilon_2$.
+Similarly, the error in the third observation is $\epsilon_3' = \epsilon_1 + \epsilon_2 + \epsilon_3$, and so on.
+\citet{Mandel1957}  made a distinction between the typically assumed independent measurement error in the dependent variable and a "cumulative" or interval error, in which each new observation encompasses the error of the previous ones.
+Cumulative errors arise from fluctuations in the process itself due to small variations in operating conditions and are not independent; only the differences in measurement from one period to the next are independent.
 
 \subsubsection{Least squares estimation}
-A least squares parameter estimation does not require prior knowledge of the distribution of unobservable errors, yield  unbiased estimates, and results in the minimum variance among all linear unbiased estimators.
-If the observations $ Y$ for the model responses are continuous functions of time from $t = 0$ to $t = t_f$, the Markov (or "rigorous least squares") criterion is to minimize:
+In statistics, least squares parameter estimation is a method used to estimate the parameters of a linear regression model.
+One of the benefits of this method is that it does not require any prior knowledge about the distribution of unobservable errors.
+Additionally, it yields unbiased estimates and results in the minimum variance among all linear unbiased estimators.
+
+If the model responses, represented by $Y$, are continuous functions of time from $t = 0$ to $t = t_f$, the Markov criterion, also known as "rigorous least squares," is used to minimize the integral squared error $\gamma$.
+This is achieved by minimizing the following expression:
 
@@
 \end{align} }
-where $\Gamma$ is the covariance matrix (or perhaps a matrix of appropriate weights), $\hat{\theta}$ is the parameter estimate, $\Theta$ is the parameter space, and $\gamma$ is the time integrated value of the error squared ("integral squared error").
-If the observations are made at discrete instants of time, $t_i$, $i = 1,2,...,n$, the Markov criterion is to minimize:
+
+Here, $\Gamma$ represents the covariance matrix or a matrix of appropriate weights, $\hat{\theta}$ is the parameter estimate, $\Theta$ is the parameter space, and $\gamma$ is the time-integrated value of the error squared.
+
+Alternatively, if the observations are made at discrete time intervals $t_i$, where $i = 1, 2, \dots, n$, the Markov criterion is to minimize the sum of squared errors, which is given by:
 
@@
 
-If $\Gamma$ is a diagonal matrix, $\gamma$  becomes a "weighted least squares" criterion; if $\Gamma = \sigma^2 \textbf{I}$ where $\sigma$ is a standard deviation, $\gamma$ is the "ordinary least squares" criterion.
+The parameter estimate, $\hat{\theta}$, is obtained by minimizing $\gamma$ over the parameter space $\Theta$.
+
+If the covariance matrix, $\Gamma$, is a diagonal matrix, the Markov criterion becomes a "weighted least squares" criterion.
+If $\Gamma = \sigma^2 \textbf{I}$, where $\sigma$ is a standard deviation and $\textbf{I}$ is the identity matrix, the Markov criterion becomes the "ordinary least squares" criterion.
 

### 2023-04-22 SFE-article/Sections/Experiments.tex
24.03
22.04

@@
 The moisture content after grinding was 4.83\%.
-The grind material density was measured by pyncometery and its result can be found in appendix \ref{CH: Solid_Density_Measurment}
+The grind material density was measured by pyncometery and its result can be found in appendix \ref{CH: Solid_Density_Measurment}.
+Moreover the porosity was calculated to be 0.5, as explained in appendix \ref{CH: Porosity}.
 
@@
 Four experiments have been performed in that unit at following operating conditions: $40^\circ C / 200$ bar, $50^\circ C / 200$ bar, $40^\circ C / 300$ bar and $50^\circ C / 300$ bar.
-1 kg of grind material was weighted and placed in the extraction chamber.
-Due to some technical limitations, the amount of solid material fro extraction was selected to be 1 kg per batch, which is not sufficient to fill the whole chamber.
+1 kg (or 1.6 litre) of grind material was weighted and placed in the extraction chamber.
+Due to technical limitations, the amount of solid material for extraction was selected to be 1 kg per batch, which is not sufficient to fill the whole chamber.
 
@@
 
-	\begin{table}[H]
+	\begin{table}[tbh!]
 		\centering
+		\adjustbox{max width=\columnwidth}{%
 		\begin{tabular}{c|cccc}
@@
 			0        & 0.0                     & 0.0                     & 0.0                     & 0.0                     \\
-			5        & 2.3                     & 1.8                     & 1.1                     & 1.2                     \\
-			10       & 5.9                     & 5                       & 4.7                     & 4.5                     \\
-			15       & 11.4                    & 8.6                     & 10.8                    & 11.3                    \\
-			20       & 17.7                    & 13.7                    & 20.6                    & 20.6                    \\
-			25       & 24.4                    & 18.3                    & 32.1                    & 30.6                    \\
-			30       & 30.4                    & 22.3                    & 40.5                    & 37.8                    \\
-			35       & 34.1                    & 26.4                    & 46.7                    & 43.3                    \\
-			40       & 37.6                    & 30.2                    & 50.5                    & 47.5                    \\
-			45       & 40.2                    & 33.8                    & 53.1                    & 50.8                    \\
-			50       & 43.4                    & 37.3                    & 55.5                    & 53.7                    \\
-			55       & 45.6                    & 40.9                    & 57.6                    & 56.5                    \\
-			60       & 47.7                    & 44.2                    & 59.3                    & 58.1                    \\
-			65       & 49.3                    & 46.8                    & 60.9                    & 59.6                    \\
-			70       & 50.9                    & 49.1                    & 62.2                    & 61.1                    \\
-			75       & 52.7                    & 50.9                    & 63.7                    & 62.7                    \\
-			80       & 54.3                    & 52.6                    & 64.9                    & 64.4                    \\
-			85       & 55.2                    & 54                      & 66.6                    & 65.8                    \\
-			90       & 56.3                    & 55.4                    & 67.6                    & 66.7                    \\
-			95       & 57.4                    & 56.6                    & 68.9                    & 67.4                    \\
-			100      & 58.4                    & 57.8                    & 69.7                    & 68.2                    \\
-			105      & 59.5                    & 58.6                    & 70.6                    & 69.1                    \\
-			110      & 60.4                    & 59.8                    & 71.2                    & 70.1                    \\
-			115      & 61.5                    & 60.9                    & 71.9                    & 70.9                    \\
-			120      & 62.6                    & 62.1                    & 72.3                    & 71.6                    \\
-			125      & 63.4                    & 63                      & 72.8                    & 72.3                    \\
-			130      & 64.1                    & 64.1                    & 73.2                    & 72.9                    \\
-			135      & 64.9                    & 65.1                    & 73.6                    & 73.5                    \\
-			140      & 65.6                    & 66                      & 74                      & 74                      \\
-			145      & 66.3                    & 66.9                    & 74.3                    & 74.5                    \\
-			150      & 66.9                    & 67.7                    & 74.6                    & 74.9                   
-		\end{tabular}
+			5        & 1.7                     & 1.8                     & 1.1                     & 1.2                     \\
+			10       & 5.7                     & 4.7                     & 4.7                     & 4.5                     \\
+			15       & 10.9                    & 9.5                     & 10.8                    & 11.3                    \\
+			20       & 17.8                    & 15.1                    & 20.6                    & 20.6                    \\
+			25       & 24.9                    & 21.3                    & 32.1                    & 30.6                    \\
+			30       & 30.3                    & 26.4                    & 40.5                    & 37.8                    \\
+			35       & 34.0                    & 29.8                    & 46.7                    & 43.3                    \\
+			40       & 37.5                    & 33.1                    & 50.5                    & 47.5                    \\
+			45       & 40.1                    & 35.6                    & 53.1                    & 50.8                    \\
+			50       & 43.3                    & 38.7                    & 55.5                    & 53.7                    \\
+			55       & 45.5                    & 41.5                    & 57.6                    & 56.5                    \\
+			60       & 47.6                    & 43.5                    & 59.3                    & 58.1                    \\
+			65       & 49.2                    & 45.9                    & 60.9                    & 59.6                    \\
+			70       & 50.8                    & 48.3                    & 62.2                    & 61.1                    \\
+			75       & 52.6                    & 50.8                    & 63.7                    & 62.7                    \\
+			80       & 54.2                    & 52.9                    & 64.9                    & 64.4                    \\
+			85       & 55.1                    & 55.3                    & 66.6                    & 65.8                    \\
+			90       & 56.2                    & 57.2                    & 67.6                    & 66.7                    \\
+			95       & 57.3                    & 58.3                    & 68.9                    & 67.4                    \\
+			100      & 58.3                    & 59.4                    & 69.7                    & 68.2                    \\
+			105      & 59.4                    & 60.4                    & 70.6                    & 69.1                    \\
+			110      & 60.2                    & 61.6                    & 71.2                    & 70.1                    \\
+			115      & 61.4                    & 62.7                    & 71.9                    & 70.9                    \\
+			120      & 62.5                    & 63.9                    & 72.3                    & 71.6                    \\
+			125      & 63.3                    & 64.7                    & 72.8                    & 72.3                    \\
+			130      & 64.0                    & 65.4                    & 73.2                    & 72.9                    \\
+			135      & 64.8                    & 65.9                    & 73.6                    & 73.5                    \\
+			140      & 65.5                    & 66.4                    & 74                      & 74                      \\
+			145      & 66.2                    & 67.1                    & 74.3                    & 74.5                    \\
+			150      & 66.8                    & 67.7                    & 74.6                    & 74.9                   
+		\end{tabular} }
 	\caption{Yield data}

### 2023-04-22 SFE-article/Sections/Porosity.tex
22.04

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	To calculate the porosity of the solid particles $\phi$, we can use the following formula:

    {\footnotesize
        \begin{equation}
            \phi = \dfrac{\text{Volume with pores} - \text{Volume without pores}}{\text{Volume with pores}}
        \end{equation}
    }

    We can first calculate the volume excluding the pore space using the true density of the material:

    {\footnotesize
        \begin{equation}
            \text{Volume excluding pores} = \dfrac{\text{mass}}{\text{true density}} = \dfrac{1\ \text{kg}}{1250\ \text{kg/m}^3} 0.0008\ \text{m}^3
        \end{equation}
    }

    We can then use the volume of the solid particles including the pore space and the volume excluding the pore space to calculate the porosity:

    {\footnotesize
        \begin{equation}
            \phi = \dfrac{\text{Volume with pores} - \text{Volume without pores}}{\text{Volume with pores}}   
        \end{equation}
    }

    Since 1 kg of solid particles occupies 1.6 L, which is equivalent to 0.0016 m³, we have:

    {\footnotesize
        \begin{equation}
            \phi = \dfrac{0.0016\ \text{m}^3 - 0.0008\ \text{m}^3}{0.0016\ \text{m}^3} = 0.5
        \end{equation}
    }

    Therefore, the porosity of the solid particles is 0.5, or 50\%. This means that half of the total volume of the solid particles is made up of pore space.

\end{document}

### 2023-04-22 SFE-article/Sections/Results.tex
22.04

@@
 	\label{CH: Results}
+
+    The parameter estimation problem was solved by fitting the process model to the dataset \ref{tab: Yield_data}.
+Each time-series was fitted to the model separately.
+As a result of fitting, the following parameters were obtained:
+
+    \begin{itemize}
+        \item Partition coefficient $k_m$
+        \item Internal Diffusion coefficient $D_i$
+        \item Axial Diffusion coefficient $D_e^M$
+        \item Standard Deviation $\sigma$
+    \end{itemize}
+
+    Moreover, the initial state estimation was performed together with parameter estimation.
+The concentration of solute is assumed to be constant and uniformly distributed.
+On the other hand, the solute concentration is assumed to not be uniform and not zero, which is common assumption.
+During the preparation period, when the operating conditions are achieved, the solute diffuses to the fluid phase in contact with the solid particles.
+Later, the solute in fluid phase is partially moved (if the pressure increase to the system the pump cause the movement of the fluid, even if the outlet valve is closed) to the region, where there is no solid phase.
+As a result, the distribution of solute in the fluid phase should be also estimated as it is unknown.
+Some conclusion can be drown from analysis of the initial part of each yield curve.
+It can be noticed, that each curve at the beginning has a curvature, which is not linear.
+In general sens, it can be said that a quadratic function could approximate initial part of each extraction curve.
+A function which after integration gives a quadratic-like result is a straight line.
+Based on that observation, the concentration of solute in fluid phase is assumed to be linearly distributed.
+The concentration of solute is assumed to be zero, at the outlet and reach maximum at beginning of the fixed bed.
+Such a formulation allows to fully describe the linear distribution of solute in the solid phase if the total mass of solute in the fluid phase is know, as explained in appendix \todo[]{Add chapter}.
+The total mass of solute in the fluid phase can be obtained from the total mass of solute $m_{total}$ and partition coefficient $\tau$, which is defined as
+
+    {\footnotesize
+    \begin{equation*}
+        \tau = \cfrac{\text{total mass of solute in the fluid phase}}{\text{total mass of solute in the system}} = \cfrac{m^0_{fluid}}{m_{total}}
+    \end{equation*}
+    }
+
+    Due to initial state estimation, two additional parameters are fitted
+
+    \begin{itemize}
+        \item Total mass of solute $m_{total}$
+        \item Partition coefficient $\tau$
+    \end{itemize}
 

### 2023-04-22 SFE-article/Article_Model_Parameters.tex
20.04
22.04
21.04

@@
 \begin{abstract}
-%Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ are the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output.
+%Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ is the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output.
 As an example, the supercritical extraction process is presented.
@@
 \begin{keywords}
-Supercritical extraction \sep Parameter estimation \sep Mathematical modelling
+Supercritical extraction \sep Parameter estimation \sep Mathematical modeling
 \end{keywords}
@@
 The governing equation for a quasi-one-dimensional compressible flow in Cartesian coordinates can be found in the appendix \ref{CH: Gouverning equations} and in the work of \citet{Anderson1995}.
-Quasi-one-dimensional flow is a type of fluid flow that is characterized by the assumption that the flow properties remain uniform across any given cross-section of the flow.
-This assumption is made when there is a variation in the cross-sectional area of the flow channel, such as a irregular shape or partial filling of an extractor.
+Quasi-one-dimensional flow is a fluid flow characterized by the assumption that the flow properties remain uniform across any given cross-section of the flow.
+This assumption is made when there is a variation in the cross-sectional area of the flow channel, such as an irregular shape or partial filling of an extractor.
 In such cases, the flow is considered to be quasi-one-dimensional because the velocity and other flow properties are assumed to vary only in the direction of flow.
@@
 
-Based on governing equations, the small discontinuity (defined as $\delta$) in flow properties, shown on figure \ref{fig: Discontinuity_slow_flow}, can be analysed.
-The analysis follow the work of \citet{Schreier1982}.
+Based on governing equations, the small discontinuity (defined as $\delta$) in flow properties, shown in Figure \ref{fig: Discontinuity_slow_flow}, can be analysed.
+The analysis follows the work of \citet{Schreier1982}.
 
-\begin{figure}[!ht]
+\begin{figure}[!h]
 	\centering
@@
 
-The discontinuity is presumed to be at rest relative and the balance equations become
+The discontinuity is presumed to be at rest relative, and the balance equations become
 
@@
 
-These relations are equally valid if the two regions are separated by a regions of finite width rather than a discontinuity.
+These relations are equally valid if the two regions are separated by a region of finite width rather than a discontinuity.
 
@@
 
-By combining momentum equation with above equation we get
+By combining the momentum equation with the above equation, we get
 
@@
 
-If the flow is presumed to be isentropic, $dP/d\rho = c^2$, so $v^2=c^2$, where $c$ is the speed of sound.
-This can be interpreted that a small pressure wave propagates with the speed of sound relative to the flow.
+Suppose the flow is presumed to be isentropic, $dP/d\rho = c^2$, so $v^2=c^2$, where $c$ is the speed of sound.
+This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow.
 
@@
 
+\subsection{Cardano's Formula} \label{CH: Cardano}
+\subfile{Sections/Cardano}
+
+\subsection{Porosity Calculations} \label{CH: Porosity}
+\subfile{Sections/Porosity}
+
 \clearpage
@@
 
-\begin{figure*}[b!]
+\begin{figure*}[!h]
 	%\centering 

### 2023-04-22 SFE-article/Sections/Bayes_Theorem.tex
08.03
21.04

--- 2023-01-24 SFE-report/Sections/Bayes_Theorem.tex
@@
 
-As discussed by \citet{Himmelblau1970}, the Bayesian approach to estimation make use of prior information.
+As discussed by \citet{Himmelblau1970}, the Bayesian approach to estimation makes use of prior information.
 Such prior knowledge can come from theoretical considerations, from the results of previous experiments, or from assumptions by the experimenter.
@@
 
-Consider a set of events or outcomes, $A_1,A_2,...,A_n$, and some other event $B$.
-Bayes' theorem states that the probability that event $A_i$ will occur, given that event $B$ has already occured, which will denoted by $P\{A_i|B\}$, is equal to the product of the probability that $A_i$ will occur regardless of whether $B$ will take place and the probability that $B$ will occur, given that $A_i$  has already taken place, divided by the probability of the occurrence of $B$:
+Consider a set of events or outcomes, $A_1, A_2,..., A_n$, and some other event $B$.
+Bayes' theorem states that the probability that event $A_i$ will occur, given that event, $B$ has already occurred, which will be denoted by $P\{A_i|B\}$, is equal to the product of the probability that $A_i$ will occur regardless of whether $B$ will take place and the probability that $B$ will occur, given that $A_i$  has already taken place, divided by the probability of the occurrence of $B$:
 
@@
 
-For continuous variable, Bayes' theorem can be more conveniently expressed in terms of the probability density function rather than the probabilities themselves.
+For a continuous variables, Bayes' theorem can be more conveniently expressed in terms of the probability density function rather than the probabilities themselves.
 Equation \ref{EQ: Bayes_discrit} can be expressed in terms of a set of observed values of the random variable $X$, the experimental data \textbf{x} and unknown parameter $\theta$ as
@@
 	\item It follows from the frequency theory of probability that: $0 \leq P \leq 1$
-	\item If the probability of occurrence of one event $A$ depends on whether or not event $B$ has occurred, the two events are termed \textit{dependent}; if the probability of occurrence of event $A$ does not depend on the occurrence of $B$, or the reverse, the two events are \textit{independent}.
+	\item If the probability of occurrence of one event $A$ depends on whether or not event $B$ has occurred, the two events are termed \textit{dependent}; if the probability of occurrence of event $A$ does not depend on the occurrence of $B$ or the reverse, the two events are \textit{independent}.
 	\item \textbf{Addition Rule}
-	If $A_1,A_2,...,A_n$ are mutually exclusive events, i.e., cannot occur at the same time, the probability of occurrence of just one of the events is equal to the sum of the probabilities of each $A_i$:
+	If $A_1, A_2,..., A_n$ are mutually exclusive events, i.e., cannot occur at the same time, the probability of occurrence of just one of the events is equal to the sum of the probabilities of each $A_i$:
 
@@
 
-	Also, if each event is equi-probable so that $P(A_i) = q$,
+	Also, if each event is equiprobable so that $P(A_i) = q$,
 
@@
 
-	In set theory, mutually exclusive event have no points in common. The union of the sets which represents the set of all elements that belong to
+	In set theory, mutually exclusive events have no points in common. The union of the sets which represents the set of all elements that belong to
 
@@
 
-	Two kind of probabilities enter Equation \ref{EQ: Probabiltiy_dependet_a} (or Equation \ref{EQ: Probabiltiy_dependet_b}): the absolute probability of event $B$ (or $A$) irrespective of whether or not $A$ (or $B$) has occurred, and that the conditional probability of event $A$ (or $B$) computed on the assumption that $B$ (or $B$) has occurred.
+	Two kinds of probabilities enter Equation \ref{EQ: Probabiltiy_dependet_a} (or Equation \ref{EQ: Probabiltiy_dependet_b}): the absolute probability of event $B$ (or $A$) irrespective of whether or not $A$ (or $B$) has occurred, and that the conditional probability of event $A$ (or $B$) computed on the assumption that $B$ (or $B$) has occurred.
 Equation \ref{EQ: Probabiltiy_independet_a} or \ref{EQ: Probabiltiy_independet_b} is special case of Equation \ref{EQ: Probabiltiy_dependet_a} or \ref{EQ: Probabiltiy_dependet_b}, because if the event are independent $P(A|B)=P(A)$.
@@
 
-	\item Another useful relationship for event which are not mutually exclusive is
+	\item Another useful relationship for events that are not mutually exclusive is
 

### 2023-04-22 SFE-article/Sections/Experiments.tex
21.04

@@
 
-	The close the optimization problem given by set of equations \ref{EQ: Optimization_formulation_MLE}, it is require to know the dataset $Y(t)$.
-In this case, the dataset have been obtained by performing extraction of caraway oil from caraway seeds.
-The caraway seeds have been obtained from the company Caraway Finland\todo{Should be mentioned?} during 2022 growing season.
+	The close the optimization problem given by a set of equations \ref{EQ: Optimization_formulation_MLE}, it is required to know the dataset $Y(t)$.
+In this case, the dataset has been obtained by performing the extraction of caraway oil from caraway seeds.
+The caraway seeds have been obtained from the company Caraway Finland\todo{Should be mentioned?} during the 2022 growing season.
 The caraway seeds have been pre-treated with Retsch SM 300 cutting mill to decrease the particle size to 1mm and break the outer shell of the seeds.
@@
 The moisture content after grinding was 4.83\%.
-The grind material density was measured by pyncometery and its result can be found in appendix \ref{CH: Solid_Density_Measurment}.
-Moreover the porosity was calculated to be 0.5, as explained in appendix \ref{CH: Porosity}.
+The grind material density was measured by pycnometer and its result can be found in appendix \ref{CH: Solid_Density_Measurment}.
+Moreover, the porosity was calculated to be 0.5, as explained in appendix \ref{CH: Porosity}.
 
-	The unit used for the experimental work is 10 litre extractor \todo{Should Biorukki be mentioned?} with inner diameter around 15 cm and 60 cm height \todo{Double check dimension}.
-Four experiments have been performed in that unit at following operating conditions: $40^\circ C / 200$ bar, $50^\circ C / 200$ bar, $40^\circ C / 300$ bar and $50^\circ C / 300$ bar.
-1 kg (or 1.6 litre) of grind material was weighted and placed in the extraction chamber.
+	The unit used for the experimental work is a 10-liter extractor \todo{Should Biorukki be mentioned?} with an inner diameter of around 15 cm and 60 cm height \todo{Double check dimension}.
+Four experiments have been performed in that unit at the following operating conditions: $40^\circ C / 200$ bar, $50^\circ C / 200$ bar, $40^\circ C / 300$ bar and $50^\circ C / 300$ bar.
+1 kg (or 1.6 liters) of grind material was weighed and placed in the extraction chamber.
 Due to technical limitations, the amount of solid material for extraction was selected to be 1 kg per batch, which is not sufficient to fill the whole chamber.
 
-	After the material was loaded into chamber, the extractor is pre-heated to desired temperature.
+	After the material was loaded into the chamber, the extractor is pre-heated to desired temperature.
 The next step is to close the outlet line coming out of the extractor and fill the extraction chamber with $CO_2$.
 The $CO_2$ is pumped and compressed until the operating pressure is achieved.
-When the operating temperature and pressure are obtained, the outlet in is open to allow the solvent flow through the system.
-The solvent extract essential oils from the fixed bed of solid material and the mixture $CO_2$-oil flow from the extractor to separator.
+When the operating temperature and pressure are obtained, the outlet in is open to allow the solvent to flow through the system.
+The solvent extracts essential oils from the fixed bed of solid material and the mixture $CO_2$-oil flow from the extractor to the separator.
 The separator was operating at $50^\circ C$ and $50$ bar.
-At this condition the $CO_2$ is gasified and leave from the top, while oil stays in the liquid form and it is collected at the bottom of separator.
-Every 5 minutes, the oil is drained from the separator and its weight is measured.
-The amount of oil collect during a batch is an output of the experiment and it is used as data for parameter estimation.
+At this condition, the gasified $CO_2$ leaves from the top, while oil stays in the liquid form and is collected at the bottom of the separator.
+Every 5 minutes, the oil is drained from the separator, and its weight is measured.
+The amount of oil collected during a batch is an output of the experiment and it is used as data for parameter estimation.
 The extraction time for each batch was 150 minutes, counted from the opening of the extractor outlet port.
 
-	The result of the experiment are presented in the table \ref{tab: Yield_data}.
+	The results of experiments are presented in the table \ref{tab: Yield_data}.
 

### 2023-04-22 SFE-article/Sections/Gouverning_equation_derivation.tex
21.04

@@
 Let's assume that any properties of the flow are uniform across any given cross-section of an extractor.
-The variation of the cross-section might be an result of partial filling of an extractor or its irregular shape.
-In reality, such a flow is two-dimensional, because with the area changing as a function of $z$, in actuality there will be flow-field variations in both directions.
-The assumption of quasi-one-dimensional flow dictates that the flow properties are function of $z$ only.
+The variation of the cross-section might result from the partial filling of an extractor or its irregular shape.
+In reality, such a flow is two-dimensional because the area changes as a function of $z$, and there is a flow-field variation in both directions.
+The assumption of quasi-one-dimensional flow dictates that the flow properties are a function of $z$ only.
 The equations described by quasi-one-dimensional assumption hold: (1) mass conservation, (2) Newton's second law, and (3) energy conservation.
-To ensure that these physical principles are satisfied the modified governing equation can be derived.	Let's start with the integral form of the continuity equation:
+The modified governing equation can be derived to ensure that these physical principles are satisfied.	Let's start with the integral form of the continuity equation:
 
@@
 		\end{tikzpicture}
-		\caption{Control volume for deriving partial differential equation for unsteady, quasi-one-dimensional flow}
+		\caption{Control volume for deriving the partial differential equation for unsteady, quasi-one-dimensional flow}
 		\label{fig: control_volume}
@@
 
-	This control volume is a slice of an extractor, where the infinitesimal thickens of the slice is $dz$.
-On the left side of the control volume, consistent with the quasi-one-dimensional assumptions, the density, velocity, pressure and internal energy denoted by $\rho_f$, $V$, $P$, and $e$, respectively, are uniform over the are $A$.
+	This control volume is a slice of an extractor, where the infinitesimal thickness of the slice is $dz$.
+On the left side of the control volume, consistent with the quasi-one-dimensional assumptions, the density, velocity, pressure, and internal energy denoted by $\rho_f$, $V$, $P$, and $e$, respectively, are uniform over the area $A$.
 Similarly, on the right side of the control volume, the density, velocity, pressure, and internal energy $\rho_f+d\rho_f$, $V+dV$, $P+dP$, and $e+de$, respectively, are uniform over the area available for fluid phase $A_f+dA_f$.
@@
 
-	where the minus sign on the leading term on the right-hand side is due to the vectors $\textbf{V}$ and $\textbf{dS}$ pointing in opposite directions over the left of the control volume, and hence the dot product is negative.
-Expending the triple product term
+	The minus sign on the leading term on the right-hand side is due to the vectors $\textbf{V}$ and $\textbf{dS}$ pointing in opposite directions over the left of the control volume, and hence the dot product is negative.
+Expanding the triple product term
 
@@
 	In the limit as $dz$ becomes very small, the terms involving products of the differential in Eq.
-\ref{EQ: Triple_Prod_Cont_Surf}, sych as $\rho_f dV dA_f,~d\rho_f dV dA_f$, go to zero much faster than those terms involving only one differential.
+\ref{EQ: Triple_Prod_Cont_Surf}, such as $\rho_f dV dA_f,~d\rho_f dV dA_f$, go to zero much faster than those terms involving only one differential.
 Hence, all terms involving products of differentials can be dropped, yielding in the limit as $dz$ becomes very small
@@
 
-	Above partial differential equation form of the continuity equation suitable for unsteady, quasi-one-dimensional flow.
-It ensures that mass is conserved for this mode of the flow.
-The $A_f(z)$ is an arbitrary function, which describe change of the cross-section of an extractor.
+	The above partial differential equation form of the continuity equation is suitable for unsteady, quasi-one-dimensional flow.
+It ensures that mass is conserved for this mode of flow.
+The $A_f(z)$ is an arbitrary function that describes a change in the cross-section of an extractor.
 The function $A_f(z)$ can be defined as $A_f(z) = \textbf{A} \phi(z)$, where $\phi$ is the bed porosity and $\textbf{A}$ is the cross-section of an empty extractor.
@@
 	}
-	The equation can be simplified by cancel out a constant $\textbf{A}$
+	The equation can be simplified by canceling out a constant $\textbf{A}$
 
@@
 
-	If so called superficial velocity is defined $u=\phi V$, the mass continuity becomes
+	If so-called superficial velocity is defined as $u=\phi V$, the mass continuity becomes
 
@@
 
-	The transport of a chemical species, in this case a solute, can be described by analogous equation to the Eq.
+	The transport of a chemical species, in this case, a solute, can be described by an analogous equation to the Eq.
 \ref{EQ: Continuity_integral_general} with additional terms on the right-hand side.
-The first term on the right-hand side describes that a substance goes from high density regions to low density regions and is based on the Fick's law $\left( J_{diff} = D_e^M\frac{\partial c_f}{\partial z} \right)$.
-The other term correspond for the mass transfer between solid and fluid phases, which is treated as a source term.
+The first term on the right-hand side describes that a substance goes from high-density regions to low-density regions and is based on the Fick's law $\left( J_{diff} = D_e^M\frac{\partial c_f}{\partial z} \right)$.
+The other term corresponds to the mass transfer between solid and fluid phases, which is treated as a source term.
 
@@
 
-	The surface integrals in the limit of $dz$ becomes
+	The surface integrals in the limit of $dz$ become
 
@@
 
-	The equation can be further simplified if $\frac{\partial u}{\partial z} = \frac{\partial \phi}{\partial z} = D_e^M = 0$, which corresponds to the assumptions of constant velocity along the bed( which might be a case of isothermal and low-mach number flow), constant porosity( which comes from the assumption of constant area for both solid and fluid phase) and no radial diffusion.
+	The equation can be further simplified if $\frac{\partial u}{\partial z} = \frac{\partial \phi}{\partial z} = D_e^M = 0$, which corresponds to the assumptions of constant velocity along the bed( which might be a case of isothermal and low-Mach number flow), constant porosity( which comes from the assumption of constant area for both solid and fluid phase) and no radial diffusion.
 
@@
 
-	Similarly to the mass conservation, the momentum conservation is derived for inviscid fluid with no body forces
+	Similarly to mass conservation, momentum conservation is derived for inviscid fluid with no body forces
 
@@
 \ref{fig: Forces_Momentum_Control_Volume}.
-Here, the $z$ components of the vector $PdS$ are shown on all four side of the control volume.
-Remember that $\textbf{dS}$ is assumed to points away from the control volume; hence  any $z$ component $\left( PdS \right)_z$ that acts toward the left (in the negative $z$ direction) is a negative quantity, and any $z$ component that acts toward the right (in the positive $z$ direction) is a positive quantity.
+Here, the $z$ components of the vector $PdS$ are shown on all four sides of the control volume.
+Remember that $\textbf{dS}$ is assumed to point away from the control volume; hence  any $z$ component $\left( PdS \right)_z$ that acts toward the left (in the negative $z$ direction) is a negative quantity.
+Any $z$ component that acts toward the right (in the positive $z$ direction) is a positive quantity.
 Also note that the $z$ component of $P\textbf{dS}$ acting on the top and the bottom inclined faces of the control volume in Fig.
-\ref{fig: Forces_Momentum_Control_Volume} can be expressed as the pressure $P$ acting on the component of the inclined are projected perpendicular to the $z$ direction, $dA_f/2$; hence, the contribution of each inclined face (top or bottom) to the pressure integral in Eq.
+\ref{fig: Forces_Momentum_Control_Volume} can be expressed as the pressure $P$ acting on the component of the inclined is projected perpendicular to the $z$ direction, $dA_f/2$; hence, the contribution of each inclined face (top or bottom) to the pressure integral in Eq.
 \ref{EQ: Momentum_Integral_Form} is $-P(dA_f/2)$.
@@
 
-	Cancelling like terms and ignoring products of differentials, equation above becomes in the limit $dz$ becoming  very small
+	Canceling like terms and ignoring products of differentials, the equation above becomes in the limit $dz$ becoming  very small
 
@@
 
-	Dividing above equation by $dz$ and taking the limit as $dz$ goes to zero, we obtain
+	Dividing the above equation by $dz$ and taking the limit as $dz$ goes to zero, we obtain
 
@@
 
-	Expanding the derivatives on the left-hand size of above equation and cancelling like terms, gives
+	Expanding the derivatives on the left-hand side of the above equation and canceling like terms, gives
 
@@
 
-	Dividing above equation by $A_f$ the non-conservative form of the momentum can be obtained
+	Dividing the above equation by $A_f$ the non-conservative form of the momentum can be obtained
 
@@
 
-	By expanding all the terms of equation above, we get
+	By expanding all the terms of the equation above, we get
 
@@
 
-	The Eq. \ref{EQ: Non-conservative_Momentum_Const_Porosity} represents non-conservative form of the momentum equation for quasi-one-dimensional flow with no body forces and constant porosity.
+	The Eq. \ref{EQ: Non-conservative_Momentum_Const_Porosity} represents the non-conservative form of the momentum equation for quasi-one-dimensional flow with no body forces and constant porosity.
 
@@
 
-	Neglecting products of differential and cancelling like terms, the above equation becomes
+	Neglecting products of differential and canceling like terms, the above equation becomes
 
@@
 
-	Expanding right-hand side and dividing by $A_f$, the above equation becomes
+	Expanding the right-hand side and dividing by $A_f$, the above equation becomes
 
@@
 
-	Equation \ref{EQ: Energy_equation_nonconservative} is the non-conservative for of the energy equation expressed in therms of internal energy, appropriate to unsteady quasi-one-dimensional flow.
+	Equation \ref{EQ: Energy_equation_nonconservative} is the non-conservative form of the energy equation expressed in terms of internal energy, appropriate to unsteady quasi-one-dimensional flow.
 The reason for obtaining the energy equation in the form of Eq.
-\ref{EQ: Energy_equation_nonconservative} is that, for a calorically perfect gas, it leads directly to a form of the energy equation in therms of temperature $T$.
+\ref{EQ: Energy_equation_nonconservative} is that, for a calorically perfect gas, it leads directly to a form of the energy equation in terms of temperature $T$.
 For calorically perfect gas ${\footnotesize e_f=C_vT}$
@@
 
-%	{TODO: \color{red}finish derivation of energy equation for real gas and introduce homogenous version of the energy equation}
+%	{TODO: \color{red}finish derivation of energy equation for real gas and introduce a homogenous version of the energy equation}
 

### 2023-04-22 SFE-article/Sections/Model.tex
21.04

@@
 	The continuity equation for the fluid phase is derived in Appendix \ref{CH: Gouverning equations}.
-When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{magenta}\phi}(z)$ (where ${\color{magenta}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: \todo[]{assign color to v and u}
+When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{magenta}\phi}(z)$ (where ${\color{magenta}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: \todo[]{assign a color to v and u}
 
@@
 
-	Analogously, the superficial velocity mught be introduced to the model and defined as
+	Analogously, the superficial velocity might be introduced to the model and defined as
 
@@
 
-	Here, ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z),$ and ${\color{blue}T}(t,z)$ represent the concentration of solute in the fluid phase, concentration of solute in the solid phase, and temperature, respectively.
+	Here, ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z),$ and ${\color{blue}T}(t,z)$ represent the concentration of solute in the fluid phase, the concentration of solute in the solid phase, and temperature, respectively.
 ${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term.
@@
 
-	The kinetic term in this study is based on the two-film theory proposed by \citet{Reverchon1996} and the mass transfer kinetic is given by equation \ref{Model_kinetic_basic}.
+	The kinetic term in this study is based on the two-film theory proposed by \citet{Reverchon1996}, and the mass transfer kinetic is given by equation \ref{Model_kinetic_basic}.
 This equation takes into account the overall diffusion coefficient and the concentration gradient, which acts as the driving force for the process.
@@
 Figure \ref{fig: SFE_Mechanism} illustrates the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as ${\color{blue}c_s}$ and the equilibrium concentrations at the solid-fluid interface are denoted as ${\color{blue}c_s^*}$ and ${\color{blue}c_P^*}$, respectively, for solid and fluid phases.
-The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{blue}c_{P}}$.
+The concentration of the solutes in the fluid phase in the center of the pore is denoted as ${\color{blue}c_{P}}$.
 As the solute diffuses through the pore, its concentration changes and reaches ${\color{blue}c_{Pf}}$ at the opening of the pore.
-The solute then diffuses through the film around the particle and reaches a concentration in the bulk ${\color{blue}c_f}$.
+The solute then diffuses through the film around the particle and reaches a concentration in bulk ${\color{blue}c_f}$.
 The two-film theory describes the solid-fluid interface inside the pore.
-The overall mass transfer coefficient can be determined if the relation between the solute concentration in one phase and its equilibrium concentration is known.
+The overall mass transfer coefficient can be determined if the relationship between the solute concentration in one phase and its equilibrium concentration is known.
 
@@
 
-		\citet{Bulley1984} suggest a process where the driving force for extraction is given by the difference between concentration of the solute in the bulk, ${\color{blue}c_f}$, and in the centre of the pore, ${\color{blue}c_P^*}$.
+		\citet{Bulley1984} suggests a process where the driving force for extraction is given by the difference between the concentration of the solute in bulk, ${\color{blue}c_f}$, and in the center of the pore, ${\color{blue}c_P^*}$.
 The concentration ${\color{blue}c_P^*}$ is in equilibrium with ${\color{blue}c_s}$ according to an equilibrium relationship.
@@
 
-		According to \citet{Bulley1984}, a linear equilibrium relationship (equation  \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{blue}c_f^*}(t,z)$ is based on concentration of the solute in the solid phase ${\color{blue}c_s}(t,z)$
+		According to \citet{Bulley1984}, a linear equilibrium relationship (equation  \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{blue}c_f^*}(t,z)$ is based on the concentration of the solute in the solid phase ${\color{blue}c_s}(t,z)$
 
@@
 
-			Following \citet{Elliott2011} or \citet{Gmehling2019}, a real gases internal energy definition can be obtained from the departure functions:
+			Following \citet{Elliott2011} or \citet{Gmehling2019}, a real gas internal energy definition can be obtained from the departure functions:
 
@@
 
-			If a gas is consider to be perfectly caloric (${\color{blue}e}(t,z)=C_v {\color{blue}T}(t,z)$), then the energy equation can be written in form of temperature.
+			If a gas is considered to be perfectly caloric (${\color{blue}e}(t,z)=C_v {\color{blue}T}(t,z)$), then the energy equation can be written in form of temperature.
 The perfectly caloric gas can be seen as the special case of a real gas, where the second term of the equation \ref{EQ: internal_energy_def} goes to zero.
 
-			For real gases it is complicated to write the heat balance in terms of temperature, but it be can used directly in the form of internal energy, as it is given by equation \ref{EQ: CompressibleEuler_3}.
-In such a case, the temperature (which is used as the input to some other functions) needs to be recover from the internal energy.
+			For real gases, it is complicated to write the heat balance in terms of temperature, but it be can be used directly in the form of internal energy, as it is given by equation \ref{EQ: CompressibleEuler_3}.
+In such a case, the temperature (which is used as the input to some other functions) needs to be recovered from the internal energy.
 A relation for the internal energy can be obtained from an equation of state.
@@
 
-			To solve equation \ref{EQ: internal_energy_PR}, values of temperature, pressure and density needs to be know.
-If an equation of state is introduce, then only two out three variables needs to be know as the third one can be calculated, this can be represented as follow
+			To solve equation \ref{EQ: internal_energy_PR}, values of temperature, pressure, and density need to be known.
+If an equation of state is introduced, then only two out of three variables need to be obtained as the third one can be calculated, this can be represented as follow
 
@@
 
-			If the value of internal energy ${\color{blue}e}(t,z)$ is know from time evolution of the energy equation (\ref{EQ: CompressibleEuler_3}), and pressure is know from measurement, then the temperature can be reconstructed.
-A roootfinder can be used to find a value of temperature, which minimize the difference between value of internal energy coming from the time evolution and the output from equation \ref{EQ: internal_energy_PR}.
+			If the value of internal energy ${\color{blue}e}(t,z)$ is known from the time evolution of the energy equation (\ref{EQ: CompressibleEuler_3}), and pressure is known from measurement, then the temperature can be reconstructed.
+A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution and the output from equation \ref{EQ: internal_energy_PR}.
 Such a procedure allow to find local temperature along spatial direction ${\color{blue}z}$ and needs to be repeated every time-step.
@@
 
-			The main advantage of this formulation is the presence of term $\partial {\color{red}P}(t) / \partial t $, which allow to directly affect the system through the change of thermodynamic pressure (which is a control variable).\todo{ "For high pressures, the influence of the intermolecular forces on the enthalpy has to be taken into account, usually by applying a cubic equation of state.
-In most cases, these forces are attractive, so that additional energy is necessary to move the molecules away from each other, that is, to lower the density.
+			The main advantage of this formulation is the presence of term $\partial {\color{red}P}(t) / \partial t $, which allows it to directly affect the system through the change of thermodynamic pressure (which is a control variable).\todo{ "For high pressures, the influence of the intermolecular forces on the enthalpy has to be taken into account, usually by applying a cubic equation of state.
+In most cases, these forces are attractive, so additional energy is necessary to move the molecules away from each other, that is, to lower the density.
 If this energy is not added, the substance cools down when it is expanded" (\citet{Gmehling2019}).
@@
 
-			If the value of enthalpy is know from the time evolution and pressure can be measured, then the equation \ref{EQ:Enthalpy_root} can be solved for temperature to recover the temperature profile.
+			If the value of enthalpy is known from the time evolution and pressure can be measured, then the equation \ref{EQ:Enthalpy_root} can be solved for the temperature to recover the temperature profile.
 By applying the departure functions to Peng-Robinson equation of state, the relation \ref{EQ:Enthalpy_root} can be expressed directly through equation \ref{EQ:Enthalpy_PR} as presented in \ref{CH:Enthalpy} or given by \citet{Gmehling2019}.
@@
 
-		\todo[inline]{Add short section about boundary conditions and comment on the used numerical methods}
+		\todo[inline]{Add a short section about boundary conditions and comment on the used numerical methods}
 
@@
 		The efficiency of the process (the yield) is calculated according to equations \ref{Model_measurment_1} to \ref{Model_measurment_2}, which evaluate the mass of solute at the exit of the extraction unit and sums it.
-The integral form of the measurement equation can be transformed into the differential form, and augmented with model equations to be solved simultaneously.
+The integral form of the measurement equation can be transformed into the differential form and augmented with model equations to be solved simultaneously.
 
@@
 
-		\iffalse
-
 		\subsubsection{State-space representation} \label{CH: State_space}
-		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}q_0}$.
-Moreover, it is considered that the initial temperature of the extractor in every place is equal to ${\color{magenta}T_0}$.
+		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}c_s_0}$.
+Moreover, it is considered that the initial temperature of the extractor in every place is equal to ${\color{magenta}h_0}$.
 Therefore, the initial conditions employed in the simulation are:
@@
 				\begin{align*}
-					{\color{blue}c}(t = 0, z) &= 0   \\
-					{\color{blue}q}(t = 0, z) &= {\color{magenta}q_0} \\
-					{\color{blue}T}(t = 0, z) &= {\color{magenta}T_0}
+					{\color{blue}c_f}(t = 0, z) &= 0   \\
+					{\color{blue}c_s}(t = 0, z) &= {\color{magenta}c_s_0} \\
+					{\color{blue}h}(t = 0, z) &= {\color{magenta}h_0}
 				\end{align*}
@@
 				\begin{bmatrix}
-					\cfrac{\partial {\color{blue}c}(t,z)}{\partial t}\\
-					\cfrac{\partial {\color{blue}q}(t,z)}{\partial t}\\
+					\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t}\\
+					\cfrac{\partial {\color{blue}c_s}(t,z)}{\partial t}\\
 					\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} 
@@
 				\begin{bmatrix}
-					{\color{blue}\phi_1} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)\\
-					{\color{blue}\phi_2} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)\\
-					{\color{blue}\phi_3} \left( {\color{blue}c}(t,z),{\color{blue}q}(t,z),{\color{blue}T}(t,z); {\color{magenta}\theta} \right)
-				\end{bmatrix} = {\color{blue}\phi} \left( t,z; {\color{magenta}\theta} \right) = \cfrac{\partial {\color{blue}\chi}(t,z)}{\partial t}
+					{\color{blue}\phi_1} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)\\
+					{\color{blue}\phi_2} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)\\
+					{\color{blue}\phi_3} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)
+				\end{bmatrix} = {\color{blue}\phi} \left( t,z; {\color{magenta}\Theta} \right) = \cfrac{\partial {\color{blue}\chi}(t,z)}{\partial t}
 		\end{align} }
@@
 The partial derivatives in $z$-direction are computed using a first-order and second-order finite difference approximation.
-The backward finite difference is used to approximate first-order derivative, while the central difference scheme is used to approximate second-order derivative.
+The backward finite difference is used to approximate the first-order derivative, while the central difference scheme is used to approximate the second-order derivative.
 The length of the fixed bed is divided into $N_z$ equally distributed points in $z$-direction.
@@
 						\\ \hline \\
-						\cfrac{d {\color{blue}T_1}(t)}{d t} 	  \\
+						\cfrac{d {\color{blue}h_1}(t)}{d t} 	  \\
 						\vdots 					  \\
-						\cfrac{d {\color{blue}T_{N_z}}(t)}{d t}
+						\cfrac{d {\color{blue}h_{N_z}}(t)}{d t}
 					\end{bmatrix}
@@
 					\underbrace{\begin{bmatrix}
-							{\color{blue}G_1} \left( {\color{blue}x}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
+							{\color{blue}G_1} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}p} \right)\\ 
 							\vdots\\ 
-							{\color{blue}G_{N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
+							{\color{blue}G_{N_z}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}p} \right)\\ 
 							\\ \hline \\ \\
-							{\color{blue}G_{N_z+1}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
+							{\color{blue}G_{N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
 							\vdots\\
@@
 							\\ \\ \hline \\ 
-							{\color{blue}G_{2N_z+1}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right) \\
+							{\color{blue}G_{2N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}p} \right) \\
 							\vdots\\
-							{\color{blue}G_{3N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)
+							{\color{blue}G_{3N_z}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}p} \right)
 					\end{bmatrix}}_{{\color{blue}G} \left( {\color{blue}x}(t); {\color{magenta}p} \right)} 
@@
 
-			where ${\color{blue}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{magenta}p} \in \mathbb{R}^{N_p =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of model parameters, $N_{u}$ is the number of control variables.
+			where ${\color{blue}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{magenta}p} \in \mathbb{R}^{N_p =  N_{\Theta} + N_u } $, $N_{\Theta}$ is the number of model parameters, $N_{u}$ is the number of control variables.
 
@@
 
-			\fi
-
 \end{document}

### 2023-04-22 SFE-article/Sections/Parameter_estimation.tex
21.04

@@
 The goal of parameter estimation is to obtain the "best" estimate of parameter set $\theta$ (which is a subset of the parameter space $\Theta$ containing all parameters of a model) based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$.
-Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, $y(t)$ (equation \ref{Model_measurment_1}), to give the observable dependent variable $Y(t)$ (for example results of an experiments).
+Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, $y(t)$ (equation \ref{Model_measurment_1}), to give the observable dependent variable $Y(t)$ (for example results of experiments).
 For discrete observations, this can be expressed as:
@@
 
-In the case where the error in the first observation is denoted as $\epsilon_1$, the error in the second observation $\epsilon_2'$ incorporates $\epsilon_1$ as well as an independent random component, given by $\epsilon_2' = \epsilon_1 + \epsilon_2$.
+When the error in the first observation is denoted as $\epsilon_1$, the error in the second observation $\epsilon_2'$ incorporates $\epsilon_1$ and an independent random component, given by $\epsilon_2' = \epsilon_1 + \epsilon_2$.
 Similarly, the error in the third observation is $\epsilon_3' = \epsilon_1 + \epsilon_2 + \epsilon_3$, and so on.
-\citet{Mandel1957}  made a distinction between the typically assumed independent measurement error in the dependent variable and a "cumulative" or interval error, in which each new observation encompasses the error of the previous ones.
-Cumulative errors arise from fluctuations in the process itself due to small variations in operating conditions and are not independent; only the differences in measurement from one period to the next are independent.
+\citet{Mandel1957}  distinguished between the typically assumed independent measurement error in the dependent variable and a "cumulative" or interval error, in which each new observation encompasses the error of the previous ones.
+Cumulative errors arise from fluctuations in the process due to small variations in operating conditions and are not independent; only the differences in measurement from one period to the next are independent.
 
@@
 In statistics, least squares parameter estimation is a method used to estimate the parameters of a linear regression model.
-One of the benefits of this method is that it does not require any prior knowledge about the distribution of unobservable errors.
+One of the benefits of this method is that it does not require prior knowledge about the distribution of unobservable errors.
 Additionally, it yields unbiased estimates and results in the minimum variance among all linear unbiased estimators.
 
-If the model responses, represented by $Y$, are continuous functions of time from $t = 0$ to $t = t_f$, the Markov criterion, also known as "rigorous least squares," is used to minimize the integral squared error $\gamma$.
+If the model responses, represented by $Y$, are continuous time functions from $t = 0$ to $t = t_f$, the Markov criterion, also known as "rigorous least squares," is used to minimize the integral squared error $\gamma$.
 This is achieved by minimizing the following expression:
@@
 
-One characteristic feature of certain special experiments is the use of the same batch of materials for the entire series of measurements.
+One characteristic feature of certain special experiments is the usage of the same batch of materials for the entire series of measurements.
 If unobservable error in the first observation is designated as $\epsilon_1$, the second error observation $\epsilon_2'$ includes $\epsilon_1$ plus a random component introduced side from $\epsilon_1$, or $\epsilon_2' = \epsilon_1 + \epsilon_2$.
@@
 \citet{Mandel1957} distinguished between the usually assumed type of independent measuring error in the dependent variable and a 'cumulative' or interval error in which each new observation includes the error of the previous observations.
-Cumulative errors, arising because of the fluctuations as a function of time in the process itself due to small changes in operating, are not independent - only the differences in measurement from one period to the next are independent.
-Thus, if we consider two model:
+Cumulative errors, arising because of the fluctuations as a function of time in the process due to small operating changes, are not independent - only the differences in measurement from one period to the next are independent.
+Thus, if we consider two models:
 
@@
 
-Maximum likelihood estimation (MLE) is a method of estimating the parameters of an assumed probability distribution, given some observed data.
-This is achieved by maximizing a likelihood function so that, under the assumed statistical model, the observed data is most probable.
+Maximum likelihood estimation (MLE) is a method of estimating the parameters of an assumed probability distribution given some observed data.
+This is achieved by maximizing a likelihood function so that the observed data is most probable under the assumed statistical model.
 The MLE has the desirable characteristics of asymptotic efficiency and normality.
@@
 
-The posterior probability density $p(\theta|y)$ can be expressed as the ratio of two probability densities if we make use of the analogue for continuous variables of Equation \ref{EQ: Probabiltiy_independet_b}:
+The posterior probability density $p(\theta|y)$ can be expressed as the ratio of two probability densities if we make use of the analog for continuous variables of Equation \ref{EQ: Probabiltiy_independet_b}:
 
@@
 We can get rid of the evidence term $p\left( y(t_n),...,y(t_1) \right)$ because it's constant with respect to the maximization.
-Moreover, if we are lacking a prior distribution over the quantity we want to estimate, then $p(\theta)$ can be omitted.
+Moreover, if we lack a prior distribution over the quantity we want to estimate, then $p(\theta)$ can be omitted.
 In such a case:
@@
 
-By collecting a values of $y$ and selecting the values of $\theta$ that maximize the likelihood function $L\left( \theta | y \right)$, a function described in chapter \ref{CH: Bayes} in connection with Bayes' theorem\todo{Is the reference it previous chapter needed?}.
+By collecting values of $y$ and selecting the values of $\theta$ that maximize the likelihood function $L\left( \theta | y \right)$, a function described in chapter \ref{CH: Bayes} in connection with Bayes' theorem\todo{Is the reference it previous chapter needed?}.
 Such estimators, $\hat{\theta}$, are known as maximum likelihood estimators.
-In effect, the methods selects those values of $\theta$ that are at least as likely to generate the observed sample as any other set of values of the parameters if the probability density of $y$ were to be extensively simulated through use of the probability density $p\left( y|\theta \right)$.
+In effect, the methods select those values of $\theta$ that are at least as likely to generate the observed sample as any other set of values of the parameters if the probability density of $y$ were to be extensively simulated through the use of the probability density $p\left( y|\theta \right)$.
 In making a maximum likelihood estimate, we assume the form of the probability density and that all possible values of $\theta$ are equally likely before experimentation.
@@
 
-		Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector $\theta$ by equating to zero the partial derivatives of $\ln L$ with respect to each of the parameters:
+		Based on the first-order optimality condition, the $\ln L$ can be maximized with respect to the vector $\theta$ by equating to zero the partial derivatives of $\ln L$ with respect to each of the parameters:
 
@@
 
-		It can be shown that as $n$ approaches infinity the maximum likelihood estimates have the desirable asymptotic properties:
+		It can be shown that as $n$ approaches infinity, the maximum likelihood estimates have the desirable asymptotic properties:
 
@@
 		Maximum likelihood estimates are not necessarily unbiased.
-Maximum likelihood estimates, however are efficient and, hence, consistent estimates.
+Maximum likelihood estimates, however, are efficient and consistent estimates.
 Furthermore, where a sufficient estimate can be obtained, the maximum likelihood method will obtain it.
@@
 Intuitively, this selects the parameter values that make the observed data most probable.
-The specific value $\hat{\theta}$ that maximizes the likelihood function $L$ is called the maximum likelihood estimate.
+The maximum likelihood estimate is the specific value $\hat{\theta}$ that maximizes the likelihood function $L$.
 
 		As already discussed, the prior information about the estimated parameters can be incorporated in to the maximum likelihood estimator to form a maximum a posteriori probability (MAP) estimate.
-MAP can be used to obtain a point estimate of an unobserved quantity on the basis of empirical data.
+MAP can be used to obtain a point estimate of an unobserved quantity based on empirical data.
 MAP estimation can therefore be seen as a regularization of maximum likelihood estimation.

### 2023-04-22 SFE-article/Sections/Porosity.tex
21.04

@@
 
-    We can first calculate the volume excluding the pore space using the true density of the material:
+    We can first calculate the volume, excluding the pore space, using the true density of the material:
 
@@
 
-    We can then use the volume of the solid particles including the pore space and the volume excluding the pore space to calculate the porosity:
+    We can then use the volume of the solid particles, including the pore space and the volume excluding the pore space, to calculate the porosity:
 
@@
 
-    Therefore, the porosity of the solid particles is 0.5, or 50\%. This means that half of the total volume of the solid particles is made up of pore space.
+    Therefore, the porosity of the solid particles is 0.5 or 50\%. This means that half of the total volume of the solid particles is made up of pore space.
 

### 2023-04-22 SFE-article/Sections/Results.tex
21.04

--- 2023-03-30 SFE-article/Sections/Results.tex
@@
 	\label{CH: Results}
+
+    The parameter estimation problem was solved by fitting the process model to the dataset \ref{tab: Yield_data}.
+Each time-series was fitted to the model separately.
+As a result of fitting, the following parameters were obtained:
+
+    \begin{itemize}
+        \item Partition coefficient $k_m$
+        \item Internal Diffusion coefficient $D_i$
+        \item Axial Diffusion coefficient $D_e^M$
+        \item Standard Deviation $\sigma$
+    \end{itemize}
+
+    Moreover, the initial state estimation was performed together with parameter estimation.
+The concentration of solute is assumed to be constant and uniformly distributed.
+On the other hand, the solute concentration is assumed not to be uniform and not zero, which is a common assumption.
+During the preparation period, when the operating conditions are achieved, the solute diffuses to the fluid phase in contact with the solid particles.
+Later, the solute in the fluid phase is partially moved (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed) to the region where there is no solid phase.
+As a result, the solute distribution in the fluid phase should also be estimated as it is unknown.
+Some conclusions can be drawn from the analysis of the initial part of each yield curve.
+It can be noticed that each curve at the beginning has a curvature, which is not linear.
+In a general sense, it can be said that a quadratic function could approximate the initial part of each extraction curve.
+A function that, after integration, gives a quadratic-like result is a straight line.
+Based on that observation, the solute concentration in the fluid phase is assumed to be linearly distributed.
+The solute concentration is assumed to be zero at the outlet and reach the maximum at the beginning of the fixed bed.
+Such a formulation allows to fully describe the linear distribution of solute in the solid phase if the total mass of solute in the fluid phase is known, as explained in appendix \todo[]{Add chapter}.
+The total mass of solute in the fluid phase can be obtained from the total mass of solute $m_{total}$ and partition coefficient $\tau$, which is defined as
+
+    {\footnotesize
+    \begin{equation*}
+        \tau = \cfrac{\text{total mass of solute in the fluid phase}}{\text{total mass of solute in the system}} = \cfrac{m^0_{fluid}}{m_{total}}
+    \end{equation*}
+    }
+
+    Due to initial state estimation, two additional parameters are fitted.
+
+    \begin{itemize}
+        \item Total mass of solute $m_{total}$
+        \item Partition coefficient $\tau$
+    \end{itemize}
 

### 2023-04-25 SFE-article/Article_Model_Parameters.tex
25.04

@@
 \usepackage{subcaption}
+
+\usepackage{csvsimple}
+
 \usepackage[bordercolor=gray!20,backgroundcolor=blue!10,linecolor=black,textsize=footnotesize,textwidth=1in]{todonotes}
@@
 Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
-We consider a system of partial differential equations, $F(t,x,\dot{x},\Theta,u)=0$, where $x$ denotes the state variables, $\Theta$ represents the parameters, and $u$ is the control variables.
+We consider a system of partial differential equations, $G(t,x,\dot{x},\Theta,u)=0$, where $x$ denotes the state variables, $\Theta$ represents the parameters, and $u$ is the control variables.
 Our focus is on the supercritical extraction process, which involves a partially filled extractor with a fixed bed that operates under constant conditions.
@@
 
+\subsection{Initial and boundary conditions} \label{CH: IC_BC}
+\subfile{Sections/IC_BC}
+
 \subsection{Porosity Calculations} \label{CH: Porosity}
@@
 	%\centering 
-	\includegraphics[trim=0cm 6cm 0cm 0cm, clip,height=0.9\textheight]{Sections/ultraReportT5.pdf}
+	\includegraphics[trim=0cm 6cm 0cm 0cm, clip,height=0.85\textheight]{Sections/ultraReportT5.pdf}
 	\caption{The result of solid density measurement}
 \end{figure*}
+
+{\footnotesize
+	\begin{equation*}
+		\rho_s^{ave} = \frac{1.2585+1.2582+1.2561+1.2546+1.2555}{5} = 1.25658 [g/cc]
+	\end{equation*}
+}
 

### 2023-04-25 SFE-article/Sections/Experiments.tex
25.04

@@
 
-	The close the optimization problem given by a set of equations \ref{EQ: Optimization_formulation_MLE}, it is required to know the dataset $Y(t)$.
-In this case, the dataset has been obtained by performing the extraction of caraway oil from caraway seeds.
-The caraway seeds have been obtained from the company Caraway Finland\todo{Should be mentioned?} during the 2022 growing season.
-The caraway seeds have been pre-treated with Retsch SM 300 cutting mill to decrease the particle size to 1mm and break the outer shell of the seeds.
-Later, the moisture content was analysed to ensure that it does not have a negative effect on the extraction process.
-An Infrared Moisture Analyser was used to investigate the sample.
-The moisture content after grinding was 4.83\%.
-The grind material density was measured by pycnometer and its result can be found in appendix \ref{CH: Solid_Density_Measurment}.
-Moreover, the porosity was calculated to be 0.5, as explained in appendix \ref{CH: Porosity}.
+	In order to solve the optimization problem presented in equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset $Y(t)$, which was obtained by extracting caraway oil from caraway seeds.
+To prepare the seeds for extraction, they were first pre-treated using a Retsch SM 300 cutting mill to reduce their particle size to 1mm and break their outer shell.
+The moisture content of the seeds was then determined using an Infrared Moisture Analyser, which revealed an average moisture content of 4.83\% in the solid particles after grinding.
+Next, the density of the solid material was measured using a pycnometer, which can be found in appendix \ref{CH: Solid_Density_Measurment}.
+Finally, the material's porosity was also calculated to be 0.5, as explained in appendix \ref{CH: Porosity}.
 
-	The unit used for the experimental work is a 10-liter extractor \todo{Should Biorukki be mentioned?} with an inner diameter of around 15 cm and 60 cm height \todo{Double check dimension}.
-Four experiments have been performed in that unit at the following operating conditions: $40^\circ C / 200$ bar, $50^\circ C / 200$ bar, $40^\circ C / 300$ bar and $50^\circ C / 300$ bar.
-1 kg (or 1.6 liters) of grind material was weighed and placed in the extraction chamber.
-Due to technical limitations, the amount of solid material for extraction was selected to be 1 kg per batch, which is not sufficient to fill the whole chamber.
+	The caraway seeds used in the experiments were obtained from Caraway Finland during the 2022 harvesting season.
+The experiments were conducted using a 10-litre extractor with an inner diameter of approximately 15 cm and a height of 60 cm, which was rented from VTT Bioruukki.
+Four experiments were performed under different operating conditions: $40^\circ C / 200$ bar, $50^\circ C / 200$ bar, $40^\circ C / 300$ bar, and $50^\circ C / 300$ bar.
+The volumetric flow rate used in all experiments was 0.4 litres per minute, with negligible variations.
+The amount of solid material used for extraction was 1 kg (or 1.6 litres), which was not enough to fill the entire extraction chamber.
 
-	After the material was loaded into the chamber, the extractor is pre-heated to desired temperature.
-The next step is to close the outlet line coming out of the extractor and fill the extraction chamber with $CO_2$.
-The $CO_2$ is pumped and compressed until the operating pressure is achieved.
-When the operating temperature and pressure are obtained, the outlet in is open to allow the solvent to flow through the system.
-The solvent extracts essential oils from the fixed bed of solid material and the mixture $CO_2$-oil flow from the extractor to the separator.
-The separator was operating at $50^\circ C$ and $50$ bar.
-At this condition, the gasified $CO_2$ leaves from the top, while oil stays in the liquid form and is collected at the bottom of the separator.
-Every 5 minutes, the oil is drained from the separator, and its weight is measured.
-The amount of oil collected during a batch is an output of the experiment and it is used as data for parameter estimation.
-The extraction time for each batch was 150 minutes, counted from the opening of the extractor outlet port.
+	After loading the material into the chamber, the extractor was pre-heated to the desired temperature.
+The outlet line was then closed, and the extraction chamber was filled with $CO_2$.
+The $CO_2$ was pumped and compressed until the desired operating pressure was reached.
+When the operating temperature and pressure were achieved, the outlet line was opened, allowing the solvent to flow through the system.
+The solvent extracted the essential oils from the solid material, and the resulting $CO_2$ and oil mixture flowed from the extractor to the separator.
+The separator operated at $50^\circ C$ and $50$ bar, with gaseous $CO_2$ exiting from the top and oil remaining at the bottom.
+The extraction time for each batch was 150 minutes, measured from the opening of the extractor outlet port.
+Every 5 minutes, the oil was drained from the separator, and its weight was measured.
+The resulting time series $Y(t)$ corresponds to the output of measurement equation \ref{Model_measurment_1} and can be used for parameter estimation.
 
@@
 
-	\begin{table}[tbh!]
+	\begin{table}[!h]
 		\centering

### 2023-04-25 SFE-article/Sections/IC_BC.tex
25.04

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}c_s^0}$. It is considered that the initial temperature of the extractor in every place is the same and described by ${\color{magenta}h^0}$.

	During the preparation period, when the operating conditions are achieved, the solute diffuses to the fluid phase in contact with the solid particles. Later, the solute in the fluid phase is partially moved (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed) to the region where there is no solid phase. As a result, the distribution of solutes mass in the fluid phase is assumed to not be uniform, and described by an arbitrary function $H=H(z)$. Some conclusions can be drawn from the analysis of the initial part of each yield curve. It can be noticed that each curve at the beginning has a curvature, which is not linear. In a general sense, it can be said that a quadratic function could approximate the initial part of each extraction curve. A function that, after integration, gives a quadratic-like result is a straight line. Based on that observation, the solute concentration in the fluid phase is assumed to be linearly distributed. The solute concentration is assumed to be zero at the outlet and reach the maximum at the beginning of the fixed bed. The graphical representation of the solute concentration in the fluid phase is shown in Figure \ref{fig: C_f_linear}.

	\begin{figure}[!h]
		\centering
		\begin{tikzpicture}[scale=2]
			\draw[->] (-2,0) -- (2,0) node[right] {z}; 
			\draw[->] (0,-1.5) -- (0,2) node[above] {$H(z)$};
%			\draw[->] (-2,1) -- (2,1);
%			\draw[->] (1,-1.5) -- (1,2);
			\draw[blue] (-1,2)  -- (2,-1);

			\node at (0,0) {\textbullet};
			\node[] at (0.2,0.1) {$z=0$};

			\node at (1,0) {\textbullet};
			\node[] at (1.2,0.1) {$z=L$};

			\node at (0,1) {\textbullet};
			%\node[] at (0.3,1) {$H=m$};

			\node[blue] at (1.3,0.5) {$H(z)=-m(z-b) + a$};
		\end{tikzpicture}
	\caption{The linear distribution of the solute concentration in the fluid phase}
	\label{fig: C_f_linear}
	\end{figure}

	As presented in Figure \ref{fig: C_f_linear}, the function $H$ is defined as

	{\footnotesize
	\begin{equation}
		H(z) = -m \left( z-b \right) + a
	\end{equation}
	}

	The function $H$ can be integrated over the integral from $a$ to $b$ to describe the total amount of solute in the fluid phase ($S$) in that interval.

	{\footnotesize
		\begin{equation}
			\int_{a}^{b} H(z) dz = S 
		\end{equation}
	}

	If parameter $a$ describe the beginning of the fixed bed, then $a=0$. Similarly, $b$ can be defined as the end of the fixed bed, then $b=L$. On range from $a=0$ to $b=L$ the result of this integral is know, and it is equal to

	{\footnotesize
		\begin{equation}
			S = m_{fluid}^0 = \int_{a=0}^{b=L} -m \left(x-L\right) dz
			\label{EQ: C_f_linear_int}
		\end{equation}
	}

	where $m_{fluid}^0$ is the total mass of solute in the fluid phase and $N$ is the number of intervals between $a$ and $b$.
	The right-hand side of the above equation can be evaluated

	{\footnotesize
		\begin{align}
			\int_{a=0}^{b=L} -m \left(x-L\right) dz &= -m \left( \int_{a=0}^{b=L} z dz - \int_{a=0}^{b=L} L dz \right) \nonumber \\
													&= -m \left(\frac{z^2}{2} \biggr\rvert_0^L - Lz \biggr\rvert_0^L   \right) \nonumber \\
													&= -m \left( \frac{L^2}{2} - L^2 \right) \nonumber \\
													&=  m \frac{L^2}{2}
													\label{EQ: C_f_linear_after_int}
		\end{align}
	}

	The parameter $m$ can be obtained by equating the left-hand side of Equation \ref{EQ: C_f_linear_int} and the right-hand side of Equation \ref{EQ: C_f_linear_after_int}

	{\footnotesize
		\begin{equation}
			m_{fluid}^0 = m \frac{L^2}{2} \rightarrow m = \frac{2m_{fluid}^0}{L^2}
		\end{equation}
	}

	As can be seen from the above equation, the linearly distributed concentration of solute in the fluid phase can be fully determined if parameters $a$, $b$ and $m_{fluid}^0$ are know. $m_{fluid}^0$ can be obtained from the total mass of the solute in the system at the initial time $m_{total}^0$ and the partition factor $\tau$.

	{\footnotesize
		\begin{equation*}
			\tau = \cfrac{\text{total mass of solute in the fluid phase}}{\text{total mass of solute in the system}} = \cfrac{m^0_{fluid}}{m^0_{total}}
		\end{equation*}
	}

	The initial conditions can be summarized as

	{\footnotesize
		\begin{subequations}
			\begin{align*}
				{\color{blue}c_f}(t = 0, z) &= H(z)   \\
				{\color{blue}c_s}(t = 0, z) &= {\color{magenta}c_{s0}} \\
				{\color{blue}h}(t = 0, z) &= {\color{magenta}h_0}
			\end{align*}
	\end{subequations} }

\end{document}

### 2023-04-25 SFE-article/Sections/Model.tex
25.04

@@
 	The continuity equation for the fluid phase is derived in Appendix \ref{CH: Gouverning equations}.
-When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{magenta}\phi}(z)$ (where ${\color{magenta}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: \todo[]{assign a color to v and u}
+When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{magenta}\phi}(z)$ (where ${\color{magenta}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: \todo[]{assign a color of v and u}
 
@@
 		\subsubsection{State-space representation} \label{CH: State_space}
-		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}c_s_0}$.
-Moreover, it is considered that the initial temperature of the extractor in every place is equal to ${\color{magenta}h_0}$.
+		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}c_{s0}}$.
+The fluid concentration is assumed to not be uniform, and as such it is described by a function $H=H(z)$.
+The further discussion on the distribution of concentration in the fluid phase can be found in appendix \todo[fancyline]{REF}.
+Moreover, it is considered that the initial temperature of the extractor in every place is the same and described by ${\color{magenta}h_0}$.
 Therefore, the initial conditions employed in the simulation are:
@@
 				\begin{align*}
-					{\color{blue}c_f}(t = 0, z) &= 0   \\
-					{\color{blue}c_s}(t = 0, z) &= {\color{magenta}c_s_0} \\
+					{\color{blue}c_f}(t = 0, z) &= H(z)   \\
+					{\color{blue}c_s}(t = 0, z) &= {\color{magenta}c_{s0}} \\
 					{\color{blue}h}(t = 0, z) &= {\color{magenta}h_0}

### 2023-04-25 SFE-article/Sections/Parameter_estimation.tex
25.04

--- 2023-04-21 SFE-article/Sections/Parameter_estimation.tex
@@
 However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $dY(t_i)/dt$ is measured instead of $Y(t_i)$ itself.
-In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ (as shown in equation \ref{Model_measurment_2}) as follows:
+In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ as shown below
 
 {\footnotesize
-	\begin{equation*}
+	\begin{equation}  \label{EQ: Measurment_noise}
 		\cfrac{d Y(t_i)}{dt} = \cfrac{dy(\theta, t_i)}{dt} + \epsilon(t_i)
-\end{equation*} }
+\end{equation} }
 
@@
 
-Examination of Equation \ref{EQ: Measurment_noise} shows that $ Y(t_i)$ depends only on $t_i$, $\theta$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement.
+Examination of Equation \ref{EQ: Measurment_noise} shows that $ d Y(t_i) / dt$ depends only on $t_i$, $\theta$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement.
 Consequently, we can write
@@
 		\end{equation} }
-
-		\todo{$x$ has not been defined}
 

### 2023-04-25 SFE-article/Sections/Results.tex
25.04

@@
 
-    The parameter estimation problem was solved by fitting the process model to the dataset \ref{tab: Yield_data}.
+    The parameter estimation problem was solved by fitting the process model to the dataset given in the table \ref{tab: Yield_data}.
 Each time-series was fitted to the model separately.
@@
     \begin{itemize}
-        \item Partition coefficient $k_m$
-        \item Internal Diffusion coefficient $D_i$
-        \item Axial Diffusion coefficient $D_e^M$
-        \item Standard Deviation $\sigma$
+        \item Partition coefficient:\qquad\quad\qquad$k_m$
+        \item Internal Diffusion coefficient: \quad$D_i$
+        \item Axial Diffusion coefficient: \qquad$D_e^M$
+        \item Standard Deviation: \qquad\qquad\quad$\sigma$
     \end{itemize}
@@
     Moreover, the initial state estimation was performed together with parameter estimation.
-The concentration of solute is assumed to be constant and uniformly distributed.
-On the other hand, the solute concentration is assumed not to be uniform and not zero, which is a common assumption.
+The concentration of solute in the solid phase is assumed to be constant and uniformly distributed.
+On the other hand, the solute concentration in the fluid phase is assumed not to be uniform and not zero.
 During the preparation period, when the operating conditions are achieved, the solute diffuses to the fluid phase in contact with the solid particles.
 Later, the solute in the fluid phase is partially moved (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed) to the region where there is no solid phase.
-As a result, the solute distribution in the fluid phase should also be estimated as it is unknown.
+As a result, the distribution of solutes mass in the fluid phase is assumed to not be uniform, and described by an arbitrary function $H=H(z)$.
 Some conclusions can be drawn from the analysis of the initial part of each yield curve.
@@
 The solute concentration is assumed to be zero at the outlet and reach the maximum at the beginning of the fixed bed.
-Such a formulation allows to fully describe the linear distribution of solute in the solid phase if the total mass of solute in the fluid phase is known, as explained in appendix \todo[]{Add chapter}.
-The total mass of solute in the fluid phase can be obtained from the total mass of solute $m_{total}$ and partition coefficient $\tau$, which is defined as
-
-    {\footnotesize
-    \begin{equation*}
-        \tau = \cfrac{\text{total mass of solute in the fluid phase}}{\text{total mass of solute in the system}} = \cfrac{m^0_{fluid}}{m_{total}}
-    \end{equation*}
-    }
+The details on the calculation are given in appendix \ref{CH: IC_BC}.
+The linear distribution can be defined if the total mass of solute $m_{total}$ and partition coefficient $\tau$ are know.
 
@@
     \begin{itemize}
-        \item Total mass of solute $m_{total}$
-        \item Partition coefficient $\tau$
+        \item Total mass of solute: \qquad\qquad\quad$m_{total}$
+        \item Partition coefficient: \qquad\qquad\quad$\tau$
     \end{itemize}
 
-	Some results of the parameter estimations
+	The parameter estimation was run as constrained optimization problem with following constraints:
 
-	\begin{figure*}
+	\begin{itemize}
+		\item $0  \leq k_m   \leq 1$
+		\item $0  \leq D_i   \leq +\infty$
+		\item $0  \leq D_e^M \leq +\infty$
+		\item $76 \leq m_{total} \leq 100$
+		\item $0  \leq \tau \leq 1$
+		\item $0  \leq \sigma \leq +\infty$
+	\end{itemize}
+
+	The results of the parameter estimation can be found in Table \ref{tab: Estimation_results}.
+
+	\begin{table}[H]
 		\centering
-		\begin{subfigure}[b]{0.7\textwidth}
+		\adjustbox{max width=\columnwidth}{%
+			\csvautotabular{Figures/Results_estimation/estimation.csv} }
+		\caption{Parameter estimation results}
+		\label{tab: Estimation_results}
+	\end{table}
+
+	The graphical representation of the original
+
+	\begin{figure*}[!h]
 		\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
+		\begin{subfigure}[b]{0.8\textwidth}
+			\centering
+			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
 			\caption{Experiment at $40^\circ C$ and $200$ bar}
@@
 		\hfill
-		\begin{subfigure}[b]{0.7\textwidth}
+		\begin{subfigure}[b]{0.8\textwidth}
 			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
+			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
 			\caption{Experiment at $50^\circ C$ and $200$ bar}
@@
 		\hfill
-		\begin{subfigure}[b]{0.7\textwidth}
+		\begin{subfigure}[b]{0.8\textwidth}
 			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
+			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
 			\caption{Experiment at $40^\circ C$ and $300$ bar}
@@
 		\hfill
-		\begin{subfigure}[b]{0.7\textwidth}
+		\begin{subfigure}[b]{0.8\textwidth}
 			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
+			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
 			\caption{Experiment at $50^\circ C$ and $300$ bar}
@@
 
-	\begin{figure*}
+	\begin{figure*}[!h]
 	\centering

### 2023-04-27 SFE-article/Article_Model_Parameters.tex
27.04

@@
 To describe the fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent, we use a distributed-parameter model based on \citet{Reverchon1996}.
-This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and saturation concentration.
-We estimate these parameters from four experiments at different temperatures and pressures: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar.
-We obtain the parameter values using the maximum likelihood estimation method on yield data under the normal error assumption.
+This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and an initial state estimate.
+We estimate these parameters by applying the maximum likelihood estimation method on yield data under the normal error assumption.
+The dataset comes from four experiments conducted at different operating conditions: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar.
 

### 2023-04-27 SFE-article/Sections/Results.tex
27.04

@@
 	\label{CH: Results}
+
+	To ensure the stability of the convergence while solving the partial differential equations, the Courant–Friedrichs–Lewy condition (given by equation) was applied.
+Based on the discretization step and the velocity, the Courant–Friedrichs–Lewy condition can be used to find.
+
+	{\footnotesize
+		\begin{equation*}
+			C = \cfrac{u\Delta t}{\Delta x} \leq C_{max} = 1
+		\end{equation*}
+	}
 
@@
 The concentration of solute in the solid phase is assumed to be constant and uniformly distributed.
-On the other hand, the solute concentration in the fluid phase is assumed not to be uniform and not zero.
-During the preparation period, when the operating conditions are achieved, the solute diffuses to the fluid phase in contact with the solid particles.
-Later, the solute in the fluid phase is partially moved (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed) to the region where there is no solid phase.
-As a result, the distribution of solutes mass in the fluid phase is assumed to not be uniform, and described by an arbitrary function $H=H(z)$.
+On the other hand, the solute concentration in the fluid phase should not follow the same assumption as the solid phase.
+During the preparation period the solute diffuses to the fluid phase in contact with the solid particles.
+Later, the solute in the fluid phase is partially moved (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed) along the extractor.
+As a result, the distribution of solutes mass in the fluid phase is assumed to not be uniform.
 Some conclusions can be drawn from the analysis of the initial part of each yield curve.
@@
 
-	The parameter estimation was run as constrained optimization problem with following constraints:
+	To ensure that parameters found by the optimizer do not reach unrealistic values, an additional set of inequality constraints is introduced.
+The lower and upper bounds for each parameter are given in Table \ref{tab:Constraints}.
 
-	\begin{itemize}
-		\item $0  \leq k_m   \leq 1$
-		\item $0  \leq D_i   \leq +\infty$
-		\item $0  \leq D_e^M \leq +\infty$
-		\item $76 \leq m_{total} \leq 100$
-		\item $0  \leq \tau \leq 1$
-		\item $0  \leq \sigma \leq +\infty$
-	\end{itemize}
+	\begin{table}[!h]
+		\begin{tabular}{ |l|c|c|c|c|c|c| } 
+			\hline
+			Parameter	&$k_m$ 	& $D_i$ 	& $D_e^M$ 	& $m_{total}$	& $\tau$ 	& $\sigma$ \\  \hline
+			Lower bound	&0	  	& 0 	  	& 0 		& 76 		 	& 0 	   	& 0 \\  \hline
+			Upper bound	&1 		& $+\infty$ & $+\infty$	& 100 			& 1 		& $+\infty$ \\
+			\hline
+		\end{tabular}
+	\caption{Constraints of the parameter estimation problem}
+	\label{tab:Constraints}
+	\end{table}
+
+	The parameter estimation problem requires an initial guess as an input to an optimization problem.
+To ensure that the solution is a global solution multiple initial points have been tested.
+The initial guesses for the parameter estimation problem are given in Table \ref{tab:InitialGuess}
+
+	\begin{table}[!h]
+		\begin{tabular}{ |l|c|c|c|c|c|c| } 
+			\hline
+			Parameter		&$k_m$ 	& $D_i$ 	& $D_e^M$ 	& $m_{total}$	& $\tau$ 	& $\sigma$ \\  \hline
+			Initial guess	&1	  	& 3 	  	& 1 		& 77 		 	& 0.65 	   	& 0.1 \\  
+			\hline
+		\end{tabular}
+		\caption{Constraints of the parameter estimation problem}
+		\label{tab:InitialGuess}
+	\end{table}
 
@@
 
-	\begin{table}[H]
+	\begin{table}[!h]
 		\centering

### 2023-04-27 SFE-article/Sections/Thermodynamic_details.tex
27.04

@@
 	\subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}
-	We consider equations of state in the general form ${\color{red}P}(t) {\color{orange}v_m}\left[T(t,z),P(t)\right] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, where ${\color{magenta}v_m}$ denotes the molar volume of $\text{CO}_2$, ${\color{orange}Z}$ represents its compressibility factor, and $R$ is the universal gas constant.
+	We consider equations of state in the general form ${\color{red}P}(t) {\color{orange}v_m}[T(t,z),P(t)] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, where ${\color{magenta}v_m}$ denotes the molar volume of $\text{CO}_2$, ${\color{orange}Z}$ represents its compressibility factor, and $R$ is the universal gas constant.
 More specifically, we are interested in these equations because of the possibility to express the compressibility $Z$ as an explicit function of temperature and pressure.
-This is the case when $Z$ is obtained as one of the physically meaningful roots of a polynomial equation, like the Peng-Robinson's and {\color{red} stuff with REFS to equations of state}.
-\\
+This is the case when $Z$ is obtained as one of the physically meaningful roots of a polynomial equation, like the Van der Waals's, Peng-Robinson's or Redlich–Kwong's equation of state.
+In this work the Peng-Robinson equation of state (\citet{Peng1976}) is used
 
-	In Peng-Robinson's equation, the compressibility ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ solves the third-order polynomial equation \todo{reference to Cardano formula}
+	In Peng-Robinson's equation fo state, the compressibility ${\color{orange}\overline{Z}}[{\color{blue}T}(t,z), {\color{red}P}(t)]$ solves the third-order polynomial equation given by equitation \ref{eq: Compressibility}.
+The polynomial equation can be solved by numerical methods like Newton-Raphson, or by applying Cardano formula.
+The Cardano formula is preferable in comparison to numerical root-finders, as it allows to obtain an analytical solution.
+The details of the Cardano formula are presented in appendix \ref{CH: Cardano}.
 
@@
 
-	\subsubsection{Departure functions for enthalpy calculations} \label{CH:Enthalpy} \todo[]{Change to my text}
+	\subsubsection{Departure functions for enthalpy calculations} \label{CH:Enthalpy}
 
-	In thermodynamics, a departure function is defined for any thermodynamic property as the difference between the property as computed for an ideal gas and the property of the species as it exists in the real world, for a specified temperature T and pressure P.
+	In thermodynamics, a departure function is a concept used to calculate the difference between a real fluid's thermodynamic properties and those of an ideal gas, given a specific temperature and pressure.
 Common departure functions include those for enthalpy, entropy, and internal energy.
+These functions are used to calculate extensive properties, which are properties computed as a difference between two states.
 
-	Departure functions are used to calculate real fluid extensive properties (i.e.
-properties which are computed as a difference between two states).
-A departure function gives the difference between the real state, at a finite volume or non-zero pressure and temperature, and the ideal state, usually at zero pressure or infinite volume and temperature.
+	For example, to evaluate the enthalpy change between two points, $h(V_1,T_1)$ and $h(V_2,T_2)$, we first calculate the enthalpy departure function between the initial volume $V_1$ and infinite volume at temperature $T_1$.
+We then add to that the ideal gas enthalpy change due to the temperature change from $T_1$ to $T_2$, and finally subtract the departure function value between the final volume $V_2$ and infinite volume.
 
-	For example, to evaluate enthalpy change between two points $h(V_1,T_1)$ and $h(V_2,T_2)$ we first compute the enthalpy departure function between volume $V_1$ and infinite volume at $T = T_1$, then add to that the ideal gas enthalpy change due to the temperature change from $T_1$ to $T_2$, then subtract the departure function value between $V_2$ and infinite volume.
-
-	Departure functions are computed by integrating a function which depends on an equation of state and its derivative. The general form the enthalpy equation is given by
+	Departure functions are computed by integrating a function that depends on an equation of state and its derivative. The general form of the enthalpy equation is given by:
 
@@
 	}
+
+	Here, $h^{id}$ represents the enthalpy of an ideal gas, $h$ is the enthalpy of a real fluid, $R$ is the universal gas constant, $T$ is temperature, $v_m$ is the molar volume, and $Z$ is the compressibility factor.
+
+	The integral in the equation is evaluated over the range of molar volumes from $v_m$ to infinity.
+The integral includes a term that depends on the derivative of the compressibility factor with respect to temperature, evaluated at the molar volume $v_m$.
+Finally, the term $1-Z$ is added to account for the deviation of the fluid's properties from those of an ideal gas.
 

### 2023-04-27 SFE - InternalEnergy/main_Fitting.m

@@ -1,4 +1,4 @@
-startup; datetime("now");
+startup; datetime("now")
 %p = Pushbullet(pushbullet_api);
 
 %addpath('C:\dev\casadi-windows-matlabR2016a-v3.5.2');
@@ -18,7 +18,7 @@ Nk                      = numel(which_k)+3;                                 % Pa
 k_lu                    = [ [0;0;0;76;0;0] , [1;inf;inf;100;1;inf] ];
 
 Iteration_max           = 100;                                              % Maximum number of iterations for optimzer
-Time_max                = 24;                                               % Maximum time of optimization in [h]
+Time_max                = 5*24;                                               % Maximum time of optimization in [h]
 
 V_Flow                  = 0.4;                                              % Volumetric flow rate l/min
 
@@ -29,7 +29,7 @@ bed                     = 0.165;                                            % Pe
 % Set time of the simulation
 PreparationTime         = 0;
 ExtractionTime          = 150;
-timeStep                = 0.25;                                             % Minutes
+timeStep                = 0.05;                                             % Minutes
 SamplingTime            = 5;                                                % Minutes
 
 simulationTime          = PreparationTime + ExtractionTime;
@@ -243,7 +243,7 @@ for i=1:numel(DATA_set)
     TT.(i+1)=round(DATA_K_OUT(:,i),5);
 end
 
-TT.Properties.VariableNames = ["$Parameter$",'$40[C] 200[bar]$',"$50[C] 200[bar]$","$40[C] 300[bar]$","$50[C] 300[bar]$"]
+TT.Properties.VariableNames = ["Parameter",'$40[C] 200[bar]$',"$50[C] 200[bar]$","$40[C] 300[bar]$","$50[C] 300[bar]$"];
 writetable(TT,'estimation.csv')
 
 %%  
@@ -283,12 +283,12 @@ for ii=1:numel(DATA_set)
         Parameters{which_k(i)}  = k0(i);
     end
 
-    msol_max                = k0(4);                                                % g of product in solid and fluid phase
+    msol_max                = k0(4);                                                             % g of product in solid and fluid phase
     mSol_ratio              = k0(5);
-    mSOL_s                  = msol_max*mSol_ratio;                                        % g of product in biomass
-    mSOL_f                  = msol_max*(1-mSol_ratio);                                    % g of biomass in fluid
[…]

### 2023-04-29 SFE-article/Sections/Model.tex
30.04

@@
 
-			Following \citet{Elliott2011} or \citet{Gmehling2019}, a real gas internal energy definition can be obtained from the departure functions:
+			Following \citet{Elliott2011} or \citet{Gmehling2019}, a real gas internal energy definition can be obtained from the departure functions, defined through equation \ref{EQ: internal_energy_def}.
+In thermodynamics, the departure function is a mathematical function that characterizes the deviation of a thermodynamic property of a real substance from that of an ideal gas at the same temperature and pressure.
+The departure function is typically defined as the difference between the value of a thermodynamic property for a real fluid and the corresponding value for an ideal gas at the same temperature and pressure.
+Common departure functions include those for enthalpy, entropy, and internal energy.
+They are typically computed by integrating a function that depends on the equation of state and its derivatives.
+More information on the departure functions can be found in appendix \ref{CH:Enthalpy}.
 
@@
 
-			The main advantage of this formulation is the presence of term $\partial {\color{red}P}(t) / \partial t $, which allows it to directly affect the system through the change of thermodynamic pressure (which is a control variable).\todo{ "For high pressures, the influence of the intermolecular forces on the enthalpy has to be taken into account, usually by applying a cubic equation of state.
-In most cases, these forces are attractive, so additional energy is necessary to move the molecules away from each other, that is, to lower the density.
-If this energy is not added, the substance cools down when it is expanded" (\citet{Gmehling2019}).
-So, pressure reduction cause gas expansion and temperature drop.}
-			If an equation of state is known, the temperature can to be recovered from the enthalpy. The enthalpy is related to the pressure and temperature through the following equation:
+			The main advantage of this formulation is the presence of term $\partial {\color{red}P}(t) / \partial t $, which allows it to directly affect the system through the change of thermodynamic pressure (which is a control variable).
+If an equation of state is known, the temperature can to be recovered from the enthalpy.
+The enthalpy is related to the pressure and temperature through the following equation:
 
@@
 
-		\todo[inline]{Add a short section about boundary conditions and comment on the used numerical methods}
+			As discussed by \citet{Gmehling2019}, special attention should be paid to high pressures systems, so the influence of the intermolecular forces on the enthalpy is taken into account.
+In most cases, these forces are attractive, so additional energy is necessary to move the molecules away from each other, that is, to lower the density.
+If this energy is not added, the substance cools down when it is expanded.
 
@@
 The fluid concentration is assumed to not be uniform, and as such it is described by a function $H=H(z)$.
-The further discussion on the distribution of concentration in the fluid phase can be found in appendix \todo[fancyline]{REF}.
+The further discussion on the distribution of concentration in the fluid phase can be found in appendix \ref{CH: IC_BC}.
 Moreover, it is considered that the initial temperature of the extractor in every place is the same and described by ${\color{magenta}h_0}$.
@@
 					\cfrac{\partial {\color{blue}c_s}(t,z)}{\partial t}\\
-					\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} 
+					\cfrac{\partial {\color{blue}h}(t,z)}{\partial t} \\
+					\cfrac{\partial {\color{blue}y}(t)}{\partial t} 
 				\end{bmatrix}
@@
 					{\color{blue}\phi_2} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)\\
-					{\color{blue}\phi_3} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)
+					{\color{blue}\phi_3} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right) \\
+					{\color{blue}\phi_4} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)
 				\end{bmatrix} = {\color{blue}\phi} \left( t,z; {\color{magenta}\Theta} \right) = \cfrac{\partial {\color{blue}\chi}(t,z)}{\partial t}
@@
 The length of the fixed bed is divided into $N_z$ equally distributed points in $z$-direction.
+To ensure the stability of the convergence while solving the partial differential equations, the Courant–Friedrichs–Lewy condition (given by equation) was applied.
+Based on the discretization step and the velocity, the Courant–Friedrichs–Lewy condition can be used to find.
+
+		{\footnotesize
+			\begin{equation*}
+				C = \cfrac{u\Delta t}{\Delta x} \leq C_{max} = 1
+			\end{equation*}
+		}
+
 		Each function ${\color{blue}\phi_i}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{blue}G}_{i\times N_z+1}$ to ${\color{blue}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation.
-The state-space model ${\color{blue}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{blue}x}}(t)$ (equation  \ref{discretization}).
+The state-space model ${\color{blue}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{blue}x}}(t)$.
 
@@
 						\vdots 					  \\
-						\cfrac{d {\color{blue}h_{N_z}}(t)}{d t}
+						\cfrac{d {\color{blue}h_{N_z}}(t)}{d t} \\
+						\\ \hline \\
+						\cfrac{d {\color{blue}t}(t)}{d t}
 					\end{bmatrix}
@@
 							\vdots\\
-							{\color{blue}G_{3N_z}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}p} \right)
+							{\color{blue}G_{3N_z}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}p} \right) \\ 
+							\\ \\ \hline \\
+							{\color{blue}G_{3N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}p} \right) 
 					\end{bmatrix}}_{{\color{blue}G} \left( {\color{blue}x}(t); {\color{magenta}p} \right)} 
@@
 
-			{\color{blue} In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases ($c(t,z)$ and $q(t,z)$, respectively), and the local temperature of the pseudo-homogeneous phase ($T(t,z)$).
-The controllable input variables are the mass flow-rate and temperature of the solvent in the feed ($F_\text{in}(t) = {\color{red}P}(t)$ and $T_\text{in}(t) = T(t,z=0)$, respectively) and the pressure in the extractor ($P(t,z) ={\color{red}P}(t)$).
-{\color{red}We also assume that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator ($Y(t)$).} The system is controllable by manipulating the flow-rate and temperature of CO2 in the feed, and the pressure in the extractor.
-}
+			In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases (${\color{blue}c_f}(t,z)$ and ${\color{blue}c_s}(t,z)$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{blue}h}(t,z)$).
+The controllable input variables are the mass flow-rate and temperature of the solvent in the feed ($F_\text{in}(t) = {\color{red}P}(t)$ and $h_\text{in}(t) = h(t,z=0)$, respectively) and the pressure in the extractor ($P(t,z) ={\color{red}P}(t)$).
+We extend the system state-space by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator ($Y(t)$).
+The system is controllable by manipulating the flow-rate and temperature (enthalpy) of $CO_2$ in the feed, and the pressure in the extractor.
 

### 2023-04-29 SFE-article/Sections/Parameter_estimation.tex
30.04

@@
 
-Maximum likelihood estimation (MLE) is a method of estimating the parameters of an assumed probability distribution, given some observed data.
-This is achieved by maximizing a likelihood function so that, under the assumed statistical model, the observed data is most probable.
-The MLE has the desirable characteristics of asymptotic efficiency and normality.
-Each time it has been associated with the (joint) normal distribution because of mathematical convenience.
-Consider the joint probability density function (the likelihood function) $p \left(\theta | y(t_1),y(t_2),...,y(t_n)\right)$ for parameter $\theta$.
-If a maximum of this function over all choices of $\theta$ can be found, the estimates so obtained are maximum likelihood estimates.
-The conditions at the maximum can be evolved incorporating prior information as follows.
+Maximum likelihood estimation (MLE) is a statistical method used to estimate the parameters of a probability distribution based on observed data.
+The MLE works by finding the values of the parameters that maximize the likelihood function, which is the probability of observing the given data for a given set of parameter values.
+The MLE has desirable properties such as asymptotic efficiency and normality.
+Although the MLE has often been associated with the normal distribution for mathematical convenience, it can be applied to a wide range of probability distributions.
 
-The posterior probability density $p(\theta|y)$ can be expressed as the ratio of two probability densities if we make use of the analogue for continuous variables of Equation \ref{EQ: Probabiltiy_independet_b}:
+To find the maximum likelihood estimates, we maximize the joint probability density function, or likelihood function, denoted as $p(\theta | y(t_1),y(t_2),...,y(t_n))$, where $\theta$ represents the parameters and $y(t_1),y(t_2),...,y(t_n)$ represent the observed data.
+The conditions at the maximum can be refined by incorporating prior information.
+The posterior probability density function $p(\theta|y)$ can be expressed as the ratio of two probability densities (\ref{EQ: Probabiltiy_independet_b}) using the continuous variable analogue of Bayes' theorem (details in appendix \ref{CH: Bayes}).
+In such a case the posteriori distribution is given by Equation \ref{EQ: Posterior_distribution}.
 
@@
 
-\todo[]{Notation is a bit unclear}The numerator of the right-hand side od Equation \ref{EQ: Posterior_distribution} using Equation \ref{EQ: Probabiltiy_dependet_a} becomes
+The numerator of the right-hand side od Equation \ref{EQ: Posterior_distribution} using Equation \ref{EQ: Probabiltiy_dependet_a} becomes
 
@@
 
-By collecting a values of $y$ and selecting the values of $\theta$ that maximize the likelihood function $L\left( \theta | y \right)$, a function described in chapter \ref{CH: Bayes} in connection with Bayes' theorem\todo{Is the reference it previous chapter needed?}.
-Such estimators, $\hat{\theta}$, are known as maximum likelihood estimators.
+%By collecting a values of $y$ and selecting the values of $\theta$ that maximize the likelihood function $L\left( \theta | y \right)$, an estimator $\hat{\theta}$ can be obtained.
+Such estimator, $\hat{\theta}$, is known as maximum likelihood estimator.
 In effect, the methods selects those values of $\theta$ that are at least as likely to generate the observed sample as any other set of values of the parameters if the probability density of $y$ were to be extensively simulated through use of the probability density $p\left( y|\theta \right)$.
@@
 		%where the lower case $y$'s and the number subscripts designate the value of the respective observation that is inserted into the probability density function. 
-		The likelihood function for the parameters based on several observations is the product of the individual functions if the observations are independent.
+		The likelihood function $L\left( \theta | y \right)$ for the parameters based on several observations is the product of the individual functions if the observations are independent.
 
@@
 					&& \dot{\theta} = 0 \\
-					&& y = y(x)
+					&& y = y(x) \\
+					&& \theta^{lb} \leq \theta \leq \theta^{ub}
 				\end{aligned}
 		\end{equation} }
+
+		where $\hat{\theta}$ is as maximum likelihood estimator, $\theta^{lb}$ define the minimal value of $\theta$ and $\theta^{ub}$ is the maximum value of $\theta$.
 
@@
 		Solution of Equations \ref{EQ: MLE_Basic_Solution} yield the desired estimates $\hat{\theta}$.
-For some models, these equations can be explicitly solved for $\hat{\theta}$ but in general no closed-form solution to the maximization problem is known or available, and an MLE can only be found via numerical optimization.
+For some models, these equations can be explicitly solved for $\hat{\theta}$ but in general no closed-form solution to the maximization problem is known or available, and an maximum likelihood estimator can only be found via numerical optimization.
 

### 2023-04-29 SFE-article/Sections/Results.tex
30.04

@@
 	\label{CH: Results}
-
-	To ensure the stability of the convergence while solving the partial differential equations, the Courant–Friedrichs–Lewy condition (given by equation) was applied.
-Based on the discretization step and the velocity, the Courant–Friedrichs–Lewy condition can be used to find.
-
-	{\footnotesize
-		\begin{equation*}
-			C = \cfrac{u\Delta t}{\Delta x} \leq C_{max} = 1
-		\end{equation*}
-	}
 
@@
 	\begin{table}[!h]
-		\begin{tabular}{ |l|c|c|c|c|c|c| } 
-			\hline
+		\begin{tabular}{ l|cccccc } 
 			Parameter	&$k_m$ 	& $D_i$ 	& $D_e^M$ 	& $m_{total}$	& $\tau$ 	& $\sigma$ \\  \hline
-			Lower bound	&0	  	& 0 	  	& 0 		& 76 		 	& 0 	   	& 0 \\  \hline
+			Lower bound	&0	  	& 0 	  	& 0 		& 76 		 	& 0 	   	& 0 \\ 
 			Upper bound	&1 		& $+\infty$ & $+\infty$	& 100 			& 1 		& $+\infty$ \\
-			\hline
 		\end{tabular}
@@
 	\begin{table}[!h]
-		\begin{tabular}{ |l|c|c|c|c|c|c| } 
-			\hline
+		\begin{tabular}{ l|cccccc } 
 			Parameter		&$k_m$ 	& $D_i$ 	& $D_e^M$ 	& $m_{total}$	& $\tau$ 	& $\sigma$ \\  \hline
 			Initial guess	&1	  	& 3 	  	& 1 		& 77 		 	& 0.65 	   	& 0.1 \\  
-			\hline
 		\end{tabular}
@@
 
-	The graphical representation of the original
+	The figure \ref{fig: estimation_results} show yield plots for each of experiments.
+The blue dot indicate the data point obtained as a measurement from the laboratory experiments.
+The black curve represents the yield curve obtained from the initial guess of the parameters.
+The blue curve correspond to yield curve obtained as a solution of the optimization problem.
 
@@
 		\caption{Results of parameter fitting, with estimation of the initial state}
+		\label{fig: estimation_results}
 	\end{figure*}

### 2023-05-03 SFE-article/Sections/Gouverning_equation_derivation.tex
03.05

@@
 	This control volume is a slice of an extractor, where the infinitesimal thickness of the slice is $dz$.
-On the left side of the control volume, consistent with the quasi-one-dimensional assumptions, the density, velocity, pressure, and internal energy denoted by $\rho_f$, $V$, $P$, and $e$, respectively, are uniform over the area $A$.
-Similarly, on the right side of the control volume, the density, velocity, pressure, and internal energy $\rho_f+d\rho_f$, $V+dV$, $P+dP$, and $e+de$, respectively, are uniform over the area available for fluid phase $A_f+dA_f$.
+On the left side of the control volume, consistent with the quasi-one-dimensional assumptions, the density, velocity, pressure, and internal energy denoted by $\rho_f$, $v$, $P$, and $e$, respectively, are uniform over the area $A$.
+Similarly, on the right side of the control volume, the density, velocity, pressure, and internal energy $\rho_f+d\rho_f$, $v+dv$, $P+dP$, and $e+de$, respectively, are uniform over the area available for fluid phase $A_f+dA_f$.
 Applied to the control volume in Fig.
@@
 		\begin{equation}
-			\iint_S \rho_f \textbf{V} \cdot \textbf{dS} = -\rho_f V A_f + (\rho_f+d\rho_f)(V+dV)(A_f+dA_f)
+			\iint_S \rho_f \textbf{V} \cdot \textbf{dS} = -\rho_f v A_f + (\rho_f+d\rho_f)(v+dv)(A_f+dA_f)
 		\end{equation}
@@
 		\begin{align}
-			&\iint_S \rho_f \textbf{V} \cdot \textbf{dS} = -\rho_f V A_f + \rho_f V A_f + \rho_f V dA_f + \rho_f A_f dV \nonumber \\ 
-			&+ \rho_f dV dA_f + V A_f d\rho_f + V d\rho_f dA + A_f d\rho_f dV + d\rho_f dV dA_f
+			&\iint_S \rho_f \textbf{V} \cdot \textbf{dS} = -\rho_f v A_f + \rho_f v A_f + \rho_f v dA_f + \rho_f A_f dv \nonumber \\ 
+			&+ \rho_f dv dA_f + v A_f d\rho_f + v d\rho_f dA + A_f d\rho_f dv + d\rho_f dv dA_f
 			\label{EQ: Triple_Prod_Cont_Surf}
@@
 	In the limit as $dz$ becomes very small, the terms involving products of the differential in Eq.
-\ref{EQ: Triple_Prod_Cont_Surf}, such as $\rho_f dV dA_f,~d\rho_f dV dA_f$, go to zero much faster than those terms involving only one differential.
+\ref{EQ: Triple_Prod_Cont_Surf}, such as $\rho_f dv dA_f,~d\rho_f dv dA_f$, go to zero much faster than those terms involving only one differential.
 Hence, all terms involving products of differentials can be dropped, yielding in the limit as $dz$ becomes very small
@@
 		\begin{equation}
-			\iint_S \rho_f \textbf{V} \cdot \textbf{dS} = \rho_f V dA_f + \rho_f A_f dV + V A_f d\rho_f 
+			\iint_S \rho_f \textbf{V} \cdot \textbf{dS} = \rho_f v dA_f + \rho_f A_f dv + v A_f d\rho_f 
 			\label{EQ: Cont_Simpl_Surf}
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_f A_f V \right)}{\partial z} = 0
+			\cfrac{\partial \left( \rho_f A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} = 0
 			\label{EQ: Conservative_continuity}
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f \textbf{A} \phi (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f \textbf{A} \phi (z) V \right)}{\partial z} = 0
+			\cfrac{\partial \left( \rho_f \textbf{A} \phi (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f \textbf{A} \phi (z) v \right)}{\partial z} = 0
 		\end{equation}
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f \phi (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f \phi (z) V \right)}{\partial z} = 0
+			\cfrac{\partial \left( \rho_f \phi (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f \phi (z) v \right)}{\partial z} = 0
 		\end{equation}
@@
 
-	If so-called superficial velocity is defined as $u=\phi V$, the mass continuity becomes
+	If so-called superficial velocity is defined as $u=\phi v$, the mass continuity becomes
 
@@
 		\begin{equation}
-			\iint_S c_f \textbf{V} \cdot \textbf{dS} = c_f V dA_f + c_f A_f dV + V A_f dc_f 
+			\iint_S c_f \textbf{V} \cdot \textbf{dS} = c_f v dA_f + c_f A_f dv + v A_f dc_f 
 		\end{equation}
@@
 		\begin{equation}
-			\iint_S J_{diff} \cdot \textbf{n}~\textbf{dS} = \iiint_{\mathcal{V}_f} \nabla J_{diff} dV_f = \nabla \iiint_{\mathcal{V}_f} J_{diff} dV_f = \nabla \left( J_{diff} A_f dz \right)
+			\iint_S J_{diff} \cdot \textbf{n}~\textbf{dS} = \iiint_{\mathcal{V}_f} \nabla J_{diff} dv_f = \nabla \iiint_{\mathcal{V}_f} J_{diff} dv_f = \nabla \left( J_{diff} A_f dz \right)
 		\end{equation}
@@
 		\begin{equation}
-			\cfrac{\partial \left( c_f A_f \right)}{\partial t} + \cfrac{\partial \left( c_f A_f V \right)}{\partial z} = \cfrac{\partial \left( c_s A_s \right) }{\partial t} + \cfrac{\partial \left( J_{diff} A_f \right) }{\partial z}
+			\cfrac{\partial \left( c_f A_f \right)}{\partial t} + \cfrac{\partial \left( c_f A_f v \right)}{\partial z} = \cfrac{\partial \left( c_s A_s \right) }{\partial t} + \cfrac{\partial \left( J_{diff} A_f \right) }{\partial z}
 		\end{equation}
@@
 		\begin{equation}
-			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} \left( \rho_f V_z \right) d\mathcal{V}_f + \iint_S \left( \rho_f V_z \textbf{V} \right) \textbf{dS} = \iint_S \left( P dS \right)_z
+			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} \left( \rho_f v_z \right) d\mathcal{V}_f + \iint_S \left( \rho_f v_z \textbf{V} \right) \textbf{dS} = \iint_S \left( P dS \right)_z
 			\label{EQ: Momentum_Integral_Form}
@@
 		\begin{equation}
-			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} \left( \rho_f V_z \right) d \mathcal{V}_f = \cfrac{\partial}{\partial t} \left( \rho_f V A_f dz \right)
+			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} \left( \rho_f v_z \right) d \mathcal{V}_f = \cfrac{\partial}{\partial t} \left( \rho_f v A_f dz \right)
 			\label{EQ: Force_Continuity_Monenmtum}
@@
 		\begin{equation}
-			\iint_S \left( \rho_f V_z \textbf{V} \right) dS = -\rho_f V^2 + \left( \rho_f + d \rho_f \right) \left( V+dV \right)^2 \left( A+dA \right)
+			\iint_S \left( \rho_f v_z \textbf{V} \right) dS = -\rho_f v^2 + \left( \rho_f + d \rho_f \right) \left( v+dv \right)^2 \left( A+dA \right)
 		\end{equation}
@@
 		\begin{align}
-			& \cfrac{\partial}{\partial t} \left( \rho_f V A_f dz \right) - \rho_f V^2 A_f + (\rho_f + d\rho_f)(V+dV)^2(A_f+dA_f)  \nonumber \\
+			& \cfrac{\partial}{\partial t} \left( \rho_f v A_f dz \right) - \rho_f v^2 A_f + (\rho_f + d\rho_f)(v+dv)^2(A_f+dA_f)  \nonumber \\
 			&= PA_f - (P+dP)(A+dA_f)+PdA_f
@@
 		\begin{equation}
-			\cfrac{\partial}{\partial t} \left( \rho_f V A_f dz \right) + d\left( \rho_f V^2 A_f \right) = -A dP
+			\cfrac{\partial}{\partial t} \left( \rho_f v A_f dz \right) + d\left( \rho_f v^2 A_f \right) = -A dP
 		\end{equation}
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f V A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_f V^2 A_f \right)}{\partial z} = -A_f \cfrac{\partial P}{\partial z}
+			\cfrac{\partial \left( \rho_f v A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_f v^2 A_f \right)}{\partial z} = -A_f \cfrac{\partial P}{\partial z}
 			\label{EQ: Conservative_Momentum}
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f V \textbf{A} \phi \right) }{\partial t} + \cfrac{\partial \left( \rho_f V^2 \textbf{A} \phi \right) }{\partial z} = - 	\textbf{A} \phi \cfrac{\partial P}{\partial t}
+			\cfrac{\partial \left( \rho_f v \textbf{A} \phi \right) }{\partial t} + \cfrac{\partial \left( \rho_f v^2 \textbf{A} \phi \right) }{\partial z} = - 	\textbf{A} \phi \cfrac{\partial P}{\partial t}
 		\end{equation}
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f V \phi \right) }{\partial t} + \cfrac{\partial \left( \rho_f V^2 \phi \right) }{\partial z} = - \phi 	\cfrac{\partial P}{\partial t}
+			\cfrac{\partial \left( \rho_f v \phi \right) }{\partial t} + \cfrac{\partial \left( \rho_f v^2 \phi \right) }{\partial z} = - \phi 	\cfrac{\partial P}{\partial t}
 		\end{equation}
@@
 \ref{EQ: Conservative_Momentum} represents the conservative form of the momentum equation for the quasi-one-dimensional flow.
-The equivalent non-conservative form can be obtained by multiplying the continuity equation by $V$ and subtracting it from Eq.
+The equivalent non-conservative form can be obtained by multiplying the continuity equation by $v$ and subtracting it from Eq.
 \ref{EQ: Conservative_Momentum}
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f V A_f \right)}{\partial t} - V\cfrac{ \partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\left( \rho_f V^2 A_f 	\right)}{\partial z} - V \cfrac{\left( \rho_f V A_f \right)}{\partial z} = -A_f \cfrac{\partial P}{\partial z}
+			\cfrac{\partial \left( \rho_f v A_f \right)}{\partial t} - V\cfrac{ \partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\left( \rho_f v^2 A_f 	\right)}{\partial z} - V \cfrac{\left( \rho_f v A_f \right)}{\partial z} = -A_f \cfrac{\partial P}{\partial z}
 		\end{equation}
@@
 		\begin{equation}
-			\rho_f A_f \cfrac{\partial V}{\partial t} + \rho_f A_f V \cfrac{\partial V}{\partial z} = -A_f \cfrac{\partial P}{\partial z}
+			\rho_f A_f \cfrac{\partial v}{\partial t} + \rho_f A_f v \cfrac{\partial v}{\partial z} = -A_f \cfrac{\partial P}{\partial z}
 		\end{equation}
@@
 		\begin{equation}
-			\rho_f \cfrac{\partial V}{\partial t} + \rho_f V \cfrac{\partial V}{\partial z} = -\cfrac{\partial P}{\partial z}
+			\rho_f \cfrac{\partial v}{\partial t} + \rho_f v \cfrac{\partial v}{\partial z} = -\cfrac{\partial P}{\partial z}
 			\label{EQ: Non-conservative_Momentum}
@@
 \ref{EQ: Non-conservative_Momentum} is stylistically the same as the general momentum conservation for one-dimensional flow with no-body forces.
-The momentum equation can be expressed in terms of superficial velocity $u=V\phi$.
+The momentum equation can be expressed in terms of superficial velocity $u=v\phi$.
 
@@
 		\begin{equation}
-			\cfrac{\partial}{\partial} \iiint_{\mathcal{V}_f} \rho_f \left( e_f + \cfrac{V^2}{2} \right) d\mathcal{V}_f + \iint_S \rho_f \left( e_f + \cfrac{V^2}{2} \right) \textbf{V} \cdot \textbf{dS} = - \iint_S \left( P\textbf{V} \right) \cdot \textbf{dS}
+			\cfrac{\partial}{\partial} \iiint_{\mathcal{V}_f} \rho_f \left( e_f + \cfrac{v^2}{2} \right) d\mathcal{V}_f + \iint_S \rho_f \left( e_f + \cfrac{v^2}{2} \right) \textbf{V} \cdot \textbf{dS} = - \iint_S \left( P\textbf{V} \right) \cdot \textbf{dS}
 			\label{EQ: Energy_equation_integral}
@@
 		\begin{align}
-			&\cfrac{\partial}{\partial t} \left[ \rho_f \left( e_f + \cfrac{V^2}{2} \right) A_f dz \right] - \rho_f \left( e_f + \cfrac{V^2}{2} \right) V A_f \nonumber \\
-			&+ \left( \rho_f + d\rho_f \right) \left[ e_f + de_f + \cfrac{\left( V + dV \right)^2}{2} \right] \left( V+fV \right) \left( A_f+dA_f \right) \nonumber \\
-			&= - \left[ -PVA_f + \left(P+dP\right) \left(V+dV\right) \left(A_f+dA_f\right) - 2\left( PV\cfrac{dA_f}{2} \right) \right]
+			&\cfrac{\partial}{\partial t} \left[ \rho_f \left( e_f + \cfrac{v^2}{2} \right) A_f dz \right] - \rho_f \left( e_f + \cfrac{v^2}{2} \right) v A_f \nonumber \\
+			&+ \left( \rho_f + d\rho_f \right) \left[ e_f + de_f + \cfrac{\left( v + dv \right)^2}{2} \right] \left( V+{\color{red}fV} \right) \left( A_f+dA_f \right) \nonumber \\
+			&= - \left[ -PvA_f + \left(P+dP\right) \left(v+dv\right) \left(A_f+dA_f\right) - 2\left( Pv\cfrac{dA_f}{2} \right) \right]
 		\end{align}
-	}
+	} \todo[]{Check fV}
 
@@
 		\begin{equation}
-			\cfrac{\partial}{\partial t} \left[ \rho_f \left( e_f + \cfrac{V^2}{2} \right) A_f dz \right] + d\left( \rho_f r_f A_f \right) + \cfrac{ \left( \rho_f V^3 A_f \right) }{2} = -d \left( P A_f V \right)
+			\cfrac{\partial}{\partial t} \left[ \rho_f \left( e_f + \cfrac{v^2}{2} \right) A_f dz \right] + d\left( \rho_f r_f A_f \right) + \cfrac{ \left( \rho_f v^3 A_f \right) }{2} = -d \left( P A_f v \right)
 		\end{equation}
@@
 		\begin{equation}
-			\cfrac{\partial}{\partial t} \left[ \rho_f \left( e_f + \cfrac{V^2}{2} \right) A_f dz \right] + d \left[ \rho_f \left( e_f \cfrac{V^2}{2} \right) VA_f \right] = - d\left( P A_f V \right)
+			\cfrac{\partial}{\partial t} \left[ \rho_f \left( e_f + \cfrac{v^2}{2} \right) A_f dz \right] + d \left[ \rho_f \left( e_f \cfrac{v^2}{2} \right) vA_f \right] = - d\left( P A_f v \right)
 		\end{equation}
@@
 		\begin{equation}
-			\cfrac{\partial \left[ \rho_f \left( e_f + V^2 / 2 \right) A \right]}{\partial t} + \cfrac{\partial \rho_f \left( e_f + V^2 / 2 \right)VA_f}{\partial z} = -\cfrac{\partial \left( P A_f V \right)}{\partial z}
+			\cfrac{\partial \left[ \rho_f \left( e_f + v^2 / 2 \right) A \right]}{\partial t} + \cfrac{\partial \rho_f \left( e_f + v^2 / 2 \right)vA_f}{\partial z} = -\cfrac{\partial \left( P A_f v \right)}{\partial z}
 			\label{EQ: Energy_equation_conservative_total}
@@
 
-	Equation \ref{EQ: Energy_equation_conservative_total} is the conservation form of the energy expressed in terms of the total energy $e~+~V^2/2$, appropriate for unsteady, quasi-one-dimensional flow.
+	Equation \ref{EQ: Energy_equation_conservative_total} is the conservation form of the energy expressed in terms of the total energy $e~+~v^2/2$, appropriate for unsteady, quasi-one-dimensional flow.
 The energy equation can be expressed in terms of internal energy if Eq.
-\ref{EQ: Conservative_Momentum} is multiplicated by $V$ and then subtracted from Eq.
+\ref{EQ: Conservative_Momentum} is multiplicated by $v$ and then subtracted from Eq.
 \ref{EQ: Energy_equation_conservative_total}
@@
 		\begin{equation}
-			\cfrac{\partial \left( \rho_f e_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f  e_f V A_f \right)}{\partial z} = -P \cfrac{\partial A_f V}{\partial z}
+			\cfrac{\partial \left( \rho_f e_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f  e_f v A_f \right)}{\partial z} = -P \cfrac{\partial A_f v}{\partial z}
 			\label{EQ: Energy_conservative_internal}
@@
 		\begin{equation}
-			\rho_f A_f \cfrac{\partial e_f}{\partial t} + \rho_f A_f V \cfrac{\partial e_f}{\partial z} = - P \cfrac{\partial (A_f V) }{\partial z}
+			\rho_f A_f \cfrac{\partial e_f}{\partial t} + \rho_f A_f v \cfrac{\partial e_f}{\partial z} = - P \cfrac{\partial (A_f v) }{\partial z}
 		\end{equation}
@@
 		\begin{equation}
-			\rho_f \cfrac{\partial e_f}{\partial t} + \rho_f V \cfrac{\partial e_f}{\partial z} = -P \cfrac{V}{A_f} \cfrac{\partial A_f}{\partial z}
+			\rho_f \cfrac{\partial e_f}{\partial t} + \rho_f v \cfrac{\partial e_f}{\partial z} = -P \cfrac{v}{A_f} \cfrac{\partial A_f}{\partial z}
 		\end{equation}
@@
 		\begin{equation}
-			\rho_f \cfrac{\partial e_f}{\partial t} + \rho_f V \cfrac{\partial e_f}{\partial z} = -P \cfrac{\partial V}{\partial z} - P V \cfrac{\partial (ln~A_f)}{\partial z}
+			\rho_f \cfrac{\partial e_f}{\partial t} + \rho_f v \cfrac{\partial e_f}{\partial z} = -P \cfrac{\partial v}{\partial z} - P V \cfrac{\partial (ln~A_f)}{\partial z}
 			\label{EQ: Energy_equation_nonconservative}
@@
 \ref{EQ: Energy_equation_nonconservative} is that, for a calorically perfect gas, it leads directly to a form of the energy equation in terms of temperature $T$.
-For calorically perfect gas ${\footnotesize e_f=C_vT}$
-
-	\hrule
-
-	{\footnotesize
-		\begin{equation}
-			\cfrac{\partial \left( \rho_f e_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f  e_f V A_f \right)}{\partial z} = -P \cfrac{\partial A_f V}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
-		\end{equation}
-	}
+%	
+%	For calorically perfect gas ${\footnotesize e_f=C_vT}$
+%	
+%	\hrule
+%	
+%	{\footnotesize
+%		\begin{equation}
+%			\cfrac{\partial \left( \rho_f e_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f  e_f v A_f \right)}{\partial z} = -P \cfrac{\partial A_f v}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
+%		\end{equation}
+%	}
 

### 2023-05-03 SFE-article/Sections/Model.tex
03.05

@@
 
-		\subsubsection{State-space representation} \label{CH: State_space}
+		\subsubsection{Initial and boundary conditions} 
 		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}c_{s0}}$.
@@
 
+		\subsubsection{State-space representation} \label{CH: State_space}
+
 		The process model can be written in a general form:
@@
 				\begin{bmatrix}
-					{\color{blue}\phi_1} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)\\
-					{\color{blue}\phi_2} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)\\
-					{\color{blue}\phi_3} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right) \\
-					{\color{blue}\phi_4} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)
-				\end{bmatrix} = {\color{blue}\phi} \left( t,z; {\color{magenta}\Theta} \right) = \cfrac{\partial {\color{blue}\chi}(t,z)}{\partial t}
+					{\color{blue}\bar{\phi_1}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)\\
+					{\color{blue}\bar{\phi_2}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)\\
+					{\color{blue}\bar{\phi_3}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right) \\
+					{\color{blue}\bar{\phi_4}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)
+				\end{bmatrix} = {\color{blue}\bar{\phi}} \left( t,z; {\color{magenta}\Theta} \right) = \cfrac{\partial {\color{blue}\chi}(t,z)}{\partial t}
 		\end{align} }
 
-		where ${\color{magenta}\theta}$ is a set of parameters present in the model, ${\color{blue}\phi}$ is a set of functions that correspond to state equations of the model, and ${\color{blue}\chi}$ is the state-space model.
+		where ${\color{magenta}\theta}$ is a set of parameters present in the model, ${\color{blue}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{blue}\chi}$ is the state-space model.
 
-		The method of lines is used to transform the process model equations into a set of ODEs denoted as ${\color{blue}G}({\color{blue}x}(t);{\color{magenta}p})$.
-The partial derivatives in $z$-direction are computed using a first-order and second-order finite difference approximation.
-The backward finite difference is used to approximate the first-order derivative, while the central difference scheme is used to approximate the second-order derivative.
-The length of the fixed bed is divided into $N_z$ equally distributed points in $z$-direction.
-To ensure the stability of the convergence while solving the partial differential equations, the Courant–Friedrichs–Lewy condition (given by equation) was applied.
-Based on the discretization step and the velocity, the Courant–Friedrichs–Lewy condition can be used to find.
-
-		{\footnotesize
-			\begin{equation*}
-				C = \cfrac{u\Delta t}{\Delta x} \leq C_{max} = 1
-			\end{equation*}
-		}
-
-		Each function ${\color{blue}\phi_i}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{blue}G}_{i\times N_z+1}$ to ${\color{blue}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation.
+		Each function ${\color{blue}\bar{\phi_i}}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{blue}G}_{i\times N_z+1}$ to ${\color{blue}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation.
 The state-space model ${\color{blue}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{blue}x}}(t)$.
@@
 
+			\subsubsection{Discretization methods}
+
+			The method of lines is used to transform the process model equations into a set of ODEs denoted as ${\color{blue}G}({\color{blue}x}(t);{\color{magenta}p})$.
+The partial derivatives in $z$-direction are computed using a first-order and second-order finite difference approximation.
+The backward finite difference is used to approximate the first-order derivative, while the central difference scheme is used to approximate the second-order derivative.
+The length of the fixed bed is divided into $N_z$ equally distributed points in $z$-direction.
+
+			As presented in Appendix \ref{CH: Gouverning equations}, all the governing can be written in the integral form using the Divergence Theorem.
+The integral equation states that the change rate of the integral of any quantity over an arbitrary control volume is given by the flux through the boundary of the control volume, with being the outer surface normal through the boundary.
+That quantity is neither produced nor consumed inside of the control volume and is hence conserved.
+For a derivative to be conservative, it must form a telescoping series.
+In other words, after the addition of all terms coming from the discretization over a grid, only the boundary terms should remain and the artificial interior points should cancel out.
+To ensure the mass conservation, the discretization is applied on the conservative form of the process model.
+
+			To ensure the stability of the convergence while solving the partial differential equations, the Courant–Friedrichs–Lewy condition (given by Equation \ref{EQ:CFL}) was applied.
+Based on the discretization step and the velocity, the Courant–Friedrichs–Lewy condition can be used to find.
+
+			{\footnotesize
+				\begin{equation}
+					C = \cfrac{u\Delta t}{\Delta x} \leq C_{max} = 1 
+					\label{EQ:CFL}
+				\end{equation}
+			}
+
+			where u is velocity, $\Delta t$	is a time step and $\Delta x$ is the space discretization.
+
 \end{document}

### 2023-05-03 SFE-article/Sections/Results.tex
03.05

@@
 	\begin{table}[!h]
-		\begin{tabular}{ l|cccccc } 
+		\centering
+		\adjustbox{max width=\columnwidth}{%
+		\begin{tabular}{ lcccccc }
+			\hline 
 			Parameter	&$k_m$ 	& $D_i$ 	& $D_e^M$ 	& $m_{total}$	& $\tau$ 	& $\sigma$ \\  \hline
 			Lower bound	&0	  	& 0 	  	& 0 		& 76 		 	& 0 	   	& 0 \\ 
-			Upper bound	&1 		& $+\infty$ & $+\infty$	& 100 			& 1 		& $+\infty$ \\
-		\end{tabular}
+			Upper bound	&1 		& $+\infty$ & $+\infty$	& 100 			& 1 		& $+\infty$ \\ \hline
+		\end{tabular} }
 	\caption{Constraints of the parameter estimation problem}
@@
 	\begin{table}[!h]
-		\begin{tabular}{ l|cccccc } 
+		\centering
+		\adjustbox{max width=\columnwidth}{%
+		\begin{tabular}{ lcccccc } 
+			\hline
 			Parameter		&$k_m$ 	& $D_i$ 	& $D_e^M$ 	& $m_{total}$	& $\tau$ 	& $\sigma$ \\  \hline
-			Initial guess	&1	  	& 3 	  	& 1 		& 77 		 	& 0.65 	   	& 0.1 \\  
-		\end{tabular}
+			Initial guess	&1	  	& 3 	  	& 1 		& 77 		 	& 0.65 	   	& 0.1 \\  \hline
+		\end{tabular} }
 		\caption{Constraints of the parameter estimation problem}
@@
 
-	The results of the parameter estimation can be found in Table \ref{tab: Estimation_results}.
-
-	\begin{table}[!h]
-		\centering
-		\adjustbox{max width=\columnwidth}{%
-			\csvautotabular{Figures/Results_estimation/estimation.csv} }
-		\caption{Parameter estimation results}
-		\label{tab: Estimation_results}
-	\end{table}
-
-	The figure \ref{fig: estimation_results} show yield plots for each of experiments.
-The blue dot indicate the data point obtained as a measurement from the laboratory experiments.
+	The figure \ref{fig: estimation_results} show yield curves for each of experiments.
+The blue dots indicate the data point obtained as a measurement from the laboratory experiments.
 The black curve represents the yield curve obtained from the initial guess of the parameters.
 The blue curve correspond to yield curve obtained as a solution of the optimization problem.
+The curves on the left hand-side of the Figure \ref{fig: estimation_results}, are the cumulative yield curves, which represents the cumulative amount of the oil collected during each experiment.
+The Figures on the right hand-side, represent the derivative of the cumulative yield curves.
+As explained in the chapter \ref{CH: Parameter_estimation}, the derivatives of the cumulative measurements are independent on the previous measurement and should be used for the parameter estimation.
 
@@
 
+	The results of the parameter estimation can be found in Table \ref{tab: Estimation_results}.
+As can be noticed, the optimizer found that the partition factor should be as high as possible and moved values of $k_m$ for each experiment to unity, which was chosen as the upper bound.
+
+	Values of the internal diffusion coefficients are distinguished for each experiment, with an increasing trend with respect to the fluid density.
+The order of magnitude of $D_i$ obtained from the optimization is similar to values found by other researcher (\todo[fancyline]{REF}).
+
+	\begin{table}[!h]
+		\centering
+		\adjustbox{max width=\columnwidth}{%
+			\csvautobooktabular{Figures/Results_estimation/estimation.csv} }
+		\caption{Parameter estimation results}
+		\label{tab: Estimation_results}
+	\end{table}
+
 	\begin{figure*}[!h]

### 2023-05-03 SFE-article/Sections/Thermodynamic_details.tex
03.05

@@
 	{\footnotesize
-	\begin{equation}
-		\left( \cfrac{\partial {\color{orange}v_m}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)} = \cfrac{{\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] {\color{magenta}R}}{{\color{red}P}(t)} + \cfrac{{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{red}P}(t)} \underbrace{\left( \cfrac{\partial {\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)}}_{\text{Eq.
+	\begin{align}
+		\left( \cfrac{\partial {\color{orange}v_m}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)} &= \cfrac{{\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] {\color{magenta}R}}{{\color{red}P}(t)} \nonumber \\
+		&+ \cfrac{{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{red}P}(t)} \underbrace{\left( \cfrac{\partial {\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)}}_{\text{Eq.
 }\eqref{eq: dZdT}} \label{eq: dVdT}
-	\end{equation} }
+	\end{align} }
 
@@
 	\begin{equation}
-		\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{magenta}v_m}\left[T(t,z),P(t)\right]}}}{\partial{\color{blue}T}}\right)_{{\color{orange}V}(t,z)} \label{eq: dPdT}
+		\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{magenta}v_m}\left[T(t,z),P(t)\right]}}}{\partial{\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} \label{eq: dPdT}
 	\end{equation} }
@@
 	\begin{equation}
-		{\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] = \left(\cfrac{\partial{\color{orange}U^{\text{R}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{orange}V}(t,z)}.
+		{\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] = \left(\cfrac{\partial{\color{orange}U^{\text{R}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)}.
 \label{eq: CvR}
@@
 
-	By denoting the physical constants as $\varphi_{C_p^{\text{F}}} = \left({\color{magenta}R}, {\color{magenta}M_{\text{CO}_2}}, {\color{magenta}T^c_{\text{CO}_2}}, {\color{magenta}P^c_{\text{CO}_2}}, {\color{magenta}\omega_{\text{CO}_2}}\right)$, we get the spatio-temporal representation $C_p^{\text{F}}\left[T(t,z),P(t) \mid \varphi_{C_p^{\text{F}}}\right]$ of the specific heat of the fluid phase.
+	By denoting the physical constants as $\varphi_{C_p^{\text{F}}} = ({\color{magenta}R}, {\color{magenta}M_{\text{CO}_2}},\\ {\color{magenta}T^c_{\text{CO}_2}}, {\color{magenta}P^c_{\text{CO}_2}}, {\color{magenta}\omega_{\text{CO}_2}})$, we get the spatio-temporal representation $C_p^{\text{F}}\left[T(t,z),P(t) \mid \varphi_{C_p^{\text{F}}}\right]$ of the specific heat of the fluid phase.
 

### 2023-05-03 SFE-article/Sections/Experiments.tex
03.05

@@
 Four experiments were performed under different operating conditions: $40^\circ C / 200$ bar, $50^\circ C / 200$ bar, $40^\circ C / 300$ bar, and $50^\circ C / 300$ bar.
-The volumetric flow rate used in all experiments was 0.4 litres per minute, with negligible variations.
+The volumetric flow rate used in all experiments was on average 0.4 litres per minute, with negligible variations (up to 5\%).
 The amount of solid material used for extraction was 1 kg (or 1.6 litres), which was not enough to fill the entire extraction chamber.
@@
 
-	The results of experiments are presented in the table \ref{tab: Yield_data}.
+	The results of experiments are presented in the Table \ref{tab: Yield_data}.
 
@@
 		\adjustbox{max width=\columnwidth}{%
-		\begin{tabular}{c|cccc}
+		\begin{tabular}{ccccc}
+			\hline
 			& $40 ^\circ C / 200$ bar & $50 ^\circ C / 200$ bar & $40 ^\circ C / 300$ bar & $50 ^\circ C / 300$ bar \\ 
@@
 			145      & 66.2                    & 67.1                    & 74.3                    & 74.5                    \\
-			150      & 66.8                    & 67.7                    & 74.6                    & 74.9                   
+			150      & 66.8                    & 67.7                    & 74.6                    & 74.9              		 \\ \hline     
 		\end{tabular} }

### 2023-05-03 SFE-article/Sections/Model.tex
03.05

@@
 
-		\subsubsection{Extraction yield} \label{CH: Yield} \todo{Give reference for measurement function}
+		\subsubsection{Extraction yield} \label{CH: Yield}
 
-		The efficiency of the process (the yield) is calculated according to equations \ref{Model_measurment_1} to \ref{Model_measurment_2}, which evaluate the mass of solute at the exit of the extraction unit and sums it.
-The integral form of the measurement equation can be transformed into the differential form and augmented with model equations to be solved simultaneously.
+		The efficiency of the process (the yield) is calculated according to equations \ref{Model_measurment_1} as presented by \citet{Sovova1994a}.
+The measurement equation evaluate the mass of solute at the outlet of the extraction unit and sums it.
+The integral form of the measurement equation (\ref{Model_measurment_1}) can be transformed into the differential form (\ref{Model_measurment_2}) and augmented with the process model.
 
@@
 			In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases (${\color{blue}c_f}(t,z)$ and ${\color{blue}c_s}(t,z)$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{blue}h}(t,z)$).
-The controllable input variables are the mass flow-rate and temperature of the solvent in the feed ($F_\text{in}(t) = {\color{red}P}(t)$ and $h_\text{in}(t) = h(t,z=0)$, respectively) and the pressure in the extractor ($P(t,z) ={\color{red}P}(t)$).
+The controllable input variables are the mass flow-rate and temperature of the solvent in the feed ($F_\text{in}(t) = {\color{red}P}(t)$ and $h_\text{in}(t) = {\color{red}h}(t,z=0)$, respectively) and the pressure in the extractor ($P(t,z) ={\color{red}P}(t)$).
 We extend the system state-space by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator ($Y(t)$).

### 2023-05-03 SFE-article/Sections/Results.tex
03.05

@@
 
-    The parameter estimation problem was solved by fitting the process model to the dataset given in the table \ref{tab: Yield_data}.
+    The parameter estimation problem was solved by fitting the process model to the dataset given in the Table \ref{tab: Yield_data}.
 Each time-series was fitted to the model separately.
@@
 The lower and upper bounds for each parameter are given in Table \ref{tab:Constraints}.
+The same Table contains the initial guesses for the optimizer.
+To ensure that the solution is a global solution multiple initial points have been tested.
 
@@
 			Lower bound		&0	  	& 0 	  	& 0 		& 76 		 	& 0 	   	& 0 \\ 
-			Upper bound	&1 		& $+\infty$ & $+\infty$	& 100 			& 1 		& $+\infty$ \\ \hline
+			Upper bound		&1 		& $+\infty$ & $+\infty$	& 100 			& 1 		& $+\infty$ \\ 
+			Initial guess	&1	  	& 3 	  	& 1 		& 77 		 	& 0.65 	   	& 0.1 \\  \hline
 		\end{tabular} }
@@
 
-	The parameter estimation problem requires an initial guess as an input to an optimization problem.
+%	The parameter estimation problem requires an initial guess as an input to an optimization problem.
 To ensure that the solution is a global solution multiple initial points have been tested.
@@
 
-	\begin{table}[!h]
-		\centering
-		\adjustbox{max width=\columnwidth}{%
-		\begin{tabular}{ lcccccc } 
-			\hline
-			Parameter		&$k_m$ 	& $D_i$ 	& $D_e^M$ 	& $m_{total}$	& $\tau$ 	& $\sigma$ \\  \hline
-			Initial guess	&1	  	& 3 	  	& 1 		& 77 		 	& 0.65 	   	& 0.1 \\  \hline
-		\end{tabular} }
-		\caption{Constraints of the parameter estimation problem}
-		\label{tab:InitialGuess}
-	\end{table}
+%	\begin{table}[!h]
+%		\centering
+%		\adjustbox{max width=\columnwidth}{%
+%		\begin{tabular}{ lcccccc } 
+%			\hline
+%			Parameter		&$k_m$ 	& $D_i$ 	& $D_e^M$ 	& $m_{total}$	& $\tau$ 	& $\sigma$ \\  \hline
+%			Initial guess	&1	  	& 3 	  	& 1 		& 77 		 	& 0.65 	   	& 0.1 \\  \hline
+%		\end{tabular} }
+%		\caption{Constraints of the parameter estimation problem}
+%		\label{tab:InitialGuess}
+%	\end{table}
 
@@
 
-	\begin{figure*}[!h]
-		\centering
-		\begin{subfigure}[b]{0.8\textwidth}
-			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
-			\caption{Experiment at $40^\circ C$ and $200$ bar}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.8\textwidth}
-			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
-			\caption{Experiment at $50^\circ C$ and $200$ bar}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.8\textwidth}
-			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
-			\caption{Experiment at $40^\circ C$ and $300$ bar}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{0.8\textwidth}
-			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
-			\caption{Experiment at $50^\circ C$ and $300$ bar}
-		\end{subfigure}
-		\caption{Results of parameter fitting, with estimation of the initial state}
-		\label{fig: estimation_results}
-	\end{figure*}
-
-	The results of the parameter estimation can be found in Table \ref{tab: Estimation_results}.
-As can be noticed, the optimizer found that the partition factor should be as high as possible and moved values of $k_m$ for each experiment to unity, which was chosen as the upper bound.
-
-	Values of the internal diffusion coefficients are distinguished for each experiment, with an increasing trend with respect to the fluid density.
-The order of magnitude of $D_i$ obtained from the optimization is similar to values found by other researcher (\todo[fancyline]{REF}).
-
 	\begin{table}[!h]
@@
 
-	\begin{figure*}[!h]
+	The results of the parameter estimation can be found in Table \ref{tab: Estimation_results}.
+As can be noticed, the optimizer found that the partition factor should be as high as possible and moved values of $k_m$ for each experiment to unity, which was chosen as the upper bound.
+
+	Values of the internal diffusion coefficients are distinguished for each experiment, with an increasing trend with respect to the fluid density.
+The order of magnitude of $D_i$ obtained from the optimization is similar to values found by other researchers.
+\citet{Reverchon1996} performed the parameter estimation for the extraction process of sage oil from seeds and reported $D_i \approx 6e-13$.
+
+	The axial diffusion coefficient obtained from the optimizer seems to be quite high if compared to the internal diffusion coefficients.
+Nevertheless, the values of $D_e^M$ have similar order of magnitude as reported in literature, for example \citet{ReisVasco2000}.
+The relatively high values of the axial diffusion coefficients might be justified by taking into account low values of flow rate used in all the experiments.
+
+	As the total amount of the oil present in the system is unknown, and as such it has been obtained from the optimizer.
+Given the dataset and the process model, the optimizer found that all most all the oil was extracted out of the seeds and that the best fit is obtained if the total mass of the oil reach a lower bound equal to 76 g.
+
+	As explained above, and in Appendix \ref{CH: IC_BC}, the linear distribution of can be fully determined if the parameter $\tau$ is known.
+The split ratio for experiments conducted at $40 ^\circ C$ / 300 bar and $50 ^\circ C$ / 300 bar are similar to each other and close to 0.64.
+The experiments performed at $40 ^\circ C$ / 200 bar and $50 ^\circ C$ / 200 bar have $\tau$ equals to $0.69$ and $0.74$, respectively.
+
+	The noise present in each dataset is quantified by parameter $\sigma$.
+It can be observed dataset obtained at $40 ^\circ C$ / 200 bar, $50 ^\circ C$ / 200 bar and $40 ^\circ C$ / 300 bar have similar value of $\sigma\approx0.34$.
+The visual investigation of the dataset obtained at $50 ^\circ C$ / 300 bar allow to explain higher value of $\sigma$ for this dataset.
+This dataset have higher deviation of the data points from the simulated curve.
+
+		\begin{figure}[!h]
 		\centering
-	\begin{subfigure}[b]{0.85\textwidth}
+		\begin{subfigure}[b]{\columnwidth}
 			\centering
-		\includegraphics[trim = 1cm 2cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
+			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
+			\caption{Experiment at $40^\circ C$ and $200$ bar}
+		\end{subfigure}
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
+			\caption{Experiment at $50^\circ C$ and $200$ bar}
+		\end{subfigure}
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
+			\caption{Experiment at $40^\circ C$ and $300$ bar}
+		\end{subfigure}
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
+			\caption{Experiment at $50^\circ C$ and $300$ bar}
+		\end{subfigure}
+		\caption{Results of parameter fitting, with estimation of the initial state}
+		\label{fig: estimation_results}
+	\end{figure}
+
+	The results obtained from the parameter estimation are used to develop a generalized process model.
+This model expresses the parameters $D_i$ and $D_e^M$ as functions of the operating conditions, such as temperature (T), pressure (P), and flow rate (F).
+Since the experiments were performed under varying temperature and pressure, the influence of these variables is taken into account.
+To simplify the problem, the correlations are written as functions of fluid density rather than temperature and pressure.
+
+	While the experimental procedure and device can affect $\tau$ and $\sigma$, these parameters are not further considered.
+They are used only to define the initial conditions and are not included in the process model.
+Additionally, since the optimizer found that $k_m$ and $m_{total}$ have the same value, they are assumed to be constants and not considered further.
+
+	The other two parameters ($D_i$ and $D_e^M$) are subject to regression to obtain correlations in terms of density.
+Figure \ref{fig:Regression} shows the first- and second-order polynomials used to fit $D_i$ and $D_e^M$ as a function of fluid density.
+Interestingly, these two parameters exhibit opposite behavior.
+The internal diffusion coefficient increases with increasing fluid density, whereas the axial diffusion coefficient decreases.
+
+	\begin{figure}[!h]
+	\centering
+	\begin{subfigure}[b]{\columnwidth}
+		\centering
+		\includegraphics[trim = 10.5cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
 		\caption{First order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
 	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.85\textwidth}
+	\begin{subfigure}[b]{\columnwidth}
 		\centering
-		\includegraphics[trim = 1cm 2cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
+		\includegraphics[trim = 10.5cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
 		\caption{Second order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
@@
 	\caption{Results of parameter fitting, with estimation of the initial state} 
-	\end{figure*}
+	\label{fig:Regression}
+	\end{figure}
 

### 2023-05-04 SFE-article/Article_Model_Parameters.tex
03.05
04.05

@@
 \section{Conclusions}
+In this work, a dataset obtained from experiments conducted at various temperature and pressure was utilized for parameter estimation to develop a process model.
+The model showed good agreement with experimental yield curves for the extraction of caraway oil from caraway seeds.
+Linear and non-linear regression techniques were employed to establish correlations for the internal diffusion coefficient and axial diffusion coefficient in terms of fluid density.
+These correlations allowed for the generalization of the process model to a range of operating conditions, specifically temperature ranging from $40^\circ C$ to $50^\circ C$, pressure ranging from 200 bar to 300 bar, and flow rate of 0.4 l/min (with flow variations up to 5\%).
+The generalized model can be used to evaluate the impact of different operating conditions on the extraction yield or for economic analysis of the extraction process.
 
@@
 
-\subsection{Porosity Calculations} \label{CH: Porosity}
-\subfile{Sections/Porosity}
-
-\clearpage
-\onecolumn
 \subsection{Solid density measurement} \label{CH: Solid_Density_Measurment}
 
-\begin{figure*}[!h]
-	%\centering 
-	\includegraphics[trim=0cm 6cm 0cm 0cm, clip,height=0.85\textheight]{Sections/ultraReportT5.pdf}
+\begin{figure}[!h]
+	\centering 
+	\includegraphics[trim=2cm 6cm 4cm 0cm, clip,width=\columnwidth]{Sections/ultraReportT5.pdf}
 	\caption{The result of solid density measurement}
-\end{figure*}
+\end{figure}
 
@@
 }
+
+\subsection{Porosity Calculations} \label{CH: Porosity}
+\subfile{Sections/Porosity}
 

### 2023-05-04 SFE-article/Sections/Results.tex
04.05

@@
 Interestingly, these two parameters exhibit opposite behavior.
-The internal diffusion coefficient increases with increasing fluid density, whereas the axial diffusion coefficient decreases.
 
@@
 		\caption{First order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
+		\label{fig:Regression_1}
 	\end{subfigure}
@@
 		\caption{Second order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
+		\label{fig:Regression_2}
 	\end{subfigure}
@@
 
+	The results of the linear regression applied to $D_i$ and $D_e^M$ are presented in Figure \ref{fig:Regression_1}.
+It can be observed that the internal diffusion coefficient increases with increasing fluid density, while the axial diffusion coefficient decreases.
+
+	The increase in the density of the supercritical fluid can lead to an increase in the solubility of the solute and, consequently, an increase in the concentration gradient.
+This increased concentration gradient drives the solute to diffuse more rapidly through the matrix of the solid particles, resulting in an increase in the internal mass transfer coefficient.
+However, the effect of increased solubility on the internal mass transfer coefficient is greater than the resistance coming from higher density, resulting in an overall increase in the internal mass transfer coefficient with density.
+
+	The behaviour of the axial diffusion coefficient can be explained through Graham’s Law of Diffusion, which states that the rate of diffusion of a molecule is inversely proportional to the square root of its density under given conditions of temperature and pressure.
+This means that denser media slow down the axial diffusion rate of molecules.
+
+	{\color{red}IDEAL I SHOULD SUPPORT THIS EXPLANATION WITH SOME REFERENCES}
+
+	Figure \ref{fig:Regression_1} show the result of fitting a second-order polynomial in density space.
+It can be observed that the fit obtained from quadratic functions seems to be represent both dataset better.
+
 \end{document}

### 2023-05-04 SFE-article/Sections/Thermodynamic_details.tex
04.05

@@
 
-	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term {\color{red}REF}.
-In the following, we report only the main steps in the derivation of ${\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$: Step-by-step derivations using the Peng-Robinson's equation are given.
-\todo{Add step-by-step derivation} \\
-
-	At given temperature and pressure, for $\text{CO}_2$ we have
+	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}.
+In the following, we report only the main steps in the derivation of ${\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$:
 

### 2023-05-04 SFE - InternalEnergy/main_Fitting.m

@@ -12,10 +12,10 @@ Parameters              = num2cell(Parameters_table{:,3});
 DATA_set                = {'LUKE_T40_P200', 'LUKE_T50_P200', 'LUKE_T40_P300_org', 'LUKE_T50_P300_org'};
 %DATA_set                = {'LUKE_T50_P300'};
 
-which_k                 = [8,  44, 45, 47               ];                          % Select which parameters are used for fitting
-k0                      = [1,  3 , 1 ,  3, 76, 0.65, 0.3];                     % Give inital value for each parameter
+which_k                 = [8,  44, 45, 47               ];                  % Select which parameters are used for fitting
+k0                      = [0.01,  30 , 1 ,  3, 100, 0.65, 0.3];                  % Give inital value for each parameter
 Nk                      = numel(which_k)+3;                                 % Parameters within the model + m_max, m_ratio, sigma
-k_lu                    = [ [0;0;0;0;70;0;0] , [1;inf;inf;inf;100;1;inf] ];
+k_lu                    = [ [0;0;0;0;80;0;0] , [1;inf;inf;inf;150;1;inf] ];
 
 Iteration_max           = 100;                                              % Maximum number of iterations for optimzer
 Time_max                = 5*24;                                               % Maximum time of optimization in [h]

### 2023-05-05 SFE-article/Article_Model_Parameters.tex
05.05

--- 2023-04-27 SFE-article/Article_Model_Parameters.tex
@@
 
-\subsection{Governing equations}
+\subsection{Governing equations} \label{CH:Governing_equations_chapter}
 The governing equation for a quasi-one-dimensional compressible flow in Cartesian coordinates can be found in the appendix \ref{CH: Gouverning equations} and in the work of \citet{Anderson1995}.
@@
 
-\subsection{Low Mach number expansion}
+\subsection{Low Mach number expansion} \label{CH:Low_Mach_chapter}
 %\subfile{Sections/Low_mach_number_expansion}
@@
 
-\section{Conclusions}
+\section{Conclusions} \label{CH: Conclusion}
+In this study, a process model was developed through parameter estimation using a dataset obtained from experiments conducted at various temperature and pressure.
+The model was found to have good agreement with experimental yield curves for the extraction of caraway oil from caraway seeds.
+To establish correlations for the internal and axial diffusion coefficients in terms of fluid density, both linear and non-linear regression techniques were utilized.
+These correlations facilitated the generalization of the process model to a range of operating conditions, specifically for temperatures ranging from $40^\circ C$ to $50^\circ C$, pressures ranging from 200 bar to 300 bar, and flow rates of 0.4 l/min (with flow variations of up to 5\%).
+The generalized model can be employed to investigate the impact of different operating conditions on the extraction yield, or for economic analysis of the extraction process.
 

### 2023-05-05 SFE-article/Sections/introduction_imp.tex
05.05

@@
 
-	Over the years, the extraction of natural substances from solid materials and liquids using solvents has been a topic of significant interest for research and development.
-Supercritical fluids are particularly useful in extraction processes due to their pressure-dependent dissolving power and ability to exhibit both gas- and liquid-like properties, such as fluid-like density and gas-like diffusivity.
-Of the various supercritical fluids available, supercritical $CO_2$ is particularly attractive due to its nontoxic, non-flammable, and non-corrosive properties.
-Moreover, the critical point of $CO_2$ is relatively low ($73.8$ bar and $31 ^\circ C$) compared to other fluids, making it an excellent alternative to traditional extraction techniques.
+	In recent years, the use of solvents for extracting natural substances from solid materials and liquids has been an area of significant interest for research and development.
+Supercritical fluids, which exhibit both gas- and liquid-like properties, have proven particularly useful in extraction processes due to their pressure-dependent dissolving power.
+Supercritical $CO_2$, in particular, is attractive because it is nontoxic, non-flammable, and non-corrosive.
+Furthermore, its critical point is relatively low compared to other fluids, making it a suitable alternative to traditional extraction techniques.
 
-	Different mathematical models have been proposed to describe the extraction of valuable compounds from a fixed biomass bed, as reviewed by \citet{Huang2012}.
-However, the selection of an appropriate extraction model should be based on the knowledge of the physical phenomena taking place in the operational unit.
+	Various mathematical models have been proposed to describe the extraction of valuable compounds from a fixed biomass bed.
+However, selecting an appropriate extraction model requires understanding the physical phenomena occurring in the operational unit.
 Each model has its own set of assumptions and describes different mass transfer mechanisms and equilibrium relationships.
 
-	Based on an analogy to heat transfer, \citet{Reverchon1993} proposed a hot ball model to describe an extraction process from solid particles containing small quantities of solute, where solubility is not a limiting factor.
-\citet{Sovova1994} presented the Broken-and-Intact Cell model, which describes a system where the outer surfaces of particles have been mechanically interrupted, allowing easy access of solvent to the solute from the broken cells.
+	One model proposed by \citet{Reverchon1993} is the hot ball model, which is based on an analogy to heat transfer and describes an extraction process from solid particles containing small quantities of solute where solubility is not a limiting factor.
+Another model, called the Broken-and-Intact Cell model, was presented by \citet{Sovova1994}.
+This model describes a system where the outer surfaces of particles have been mechanically interrupted, allowing easy access of solvent to the solute from the broken cells.
 In contrast, the solute from the intact cells is less accessible due to high mass transfer resistance.
@@
 	\citet{Reverchon1996} developed a model for fluid-solid extraction, where the oil is treated as a single component, and the extraction process is controlled by internal mass transfer resistance, neglecting external mass transfer.
-This model, however, does not consider the influence of axial dispersion or changes in density and flow rate along the bed.
+However, this model does not consider the influence of axial dispersion or changes in density and flow rate along the bed.
+
+	In this work, we derive basic governing equations and combine them with the kinetic model suggested by \citet{Reverchon1996} to obtain a general model for the extraction process of the oil from the caraway seed.
+This model simplifies some of the physical behavior to obtain a control-oriented model.
 Our work assumes that the extraction process operates semi-continuously in a cylindrical vessel.
@@
 The solvent and solute are then separated in a flush drum, and the extract is collected.
-The feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) of the extractor can be measured and manipulated.
-In contrast, the vessel pressure ($P$) can be measured and manipulated, but the outlet temperature ($T_{out}$) can only be measured.
+The feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) of the extractor can be measured and manipulated, while the vessel pressure ($P$) can also be measured and manipulated.
+However, the outlet temperature ($T_{out}$) can only be measured.
 Figure \ref{fig: SFE_drawing} depicts a simplified flow diagram.
@@
 
+	The purpose of this study is to develop a process model for the extraction of natural substances from solid materials and liquids using supercritical fluids, specifically supercritical $CO_2$.
+To achieve this, the model parameters are estimated based on thermodynamic relations and a set of experiments conducted at various conditions.
+The maximum likelihood estimator is used to solve the parameter estimation problem, and the obtained parameters are subjected to regression to derive correlations.
+These correlations enable the process model to be generalized across a range of temperatures (40 to $50^\circ C$) and pressures (200 to 300 bars).
+
+	The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties.
+Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations, which are derived under the assumption of Low-Mach number in Chapter \ref{CH:Low_Mach_chapter}.
+The simplified balance equations are combined with the extraction kinetic equation to develop the process model in Chapter \ref{CH: Extraction_model}.
+The maximum likelihood technique is presented in Chapter \ref{CH: Parameter_estimation} and is then combined with the process model.
+The dataset obtained from laboratory experiments is used to close the optimization problem in Chapter \ref{CH: Experiments}.
+Finally, Chapters \ref{CH: Results} and \ref{CH: Conclusion} discuss the results of the parameter estimations and simulation results.
+
 \end{document}

### 2023-05-07 SFE-article/Article_Model_Parameters.tex
07.05

@@
 % ---------------------------------------------------------------
-% Make margins bigger to fit annotations. TO be removed later
-\paperwidth=\dimexpr \paperwidth + 6cm\relax
-\oddsidemargin=\dimexpr\oddsidemargin + 3cm\relax
-\evensidemargin=\dimexpr\evensidemargin + 3cm\relax
+% Make margins bigger to fit annotations. Use 1, 2 and 3. TO be removed later
+%\paperwidth=\dimexpr \paperwidth + 6cm\relax
+%\oddsidemargin=\dimexpr\oddsidemargin + 3cm\relax
+%\evensidemargin=\dimexpr\evensidemargin + 3cm\relax
 %\marginparwidth=\dimexpr \marginparwidth + 3cm\relax
@@
 
+% TODO package
 \usepackage[bordercolor=gray!20,backgroundcolor=blue!10,linecolor=black,textsize=footnotesize,textwidth=1in]{todonotes}
@@
 
-\shortauthors{A, B, C}
+\shortauthors{OS, PO}
 
@@
 \cormark[1]
-%\credit{a}
+\credit{a}
 
-%\author[1]{Pekka Oinas}[orcid=0000-0002-0183-5558]
-%\credit{b}
+\author[1]{Pekka Oinas}[orcid=0000-0002-0183-5558]
+\credit{b}
 
@@
 Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
-We consider a system of partial differential equations, $G(t,x,\dot{x},\Theta,u)=0$, where $x$ denotes the state variables, $\Theta$ represents the parameters, and $u$ is the control variables.
-Our focus is on the supercritical extraction process, which involves a partially filled extractor with a fixed bed that operates under constant conditions.
-We assume the flow is uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
-To model this two-dimensional case, we use the concept of quasi-one-dimensional flow.
-To describe the fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent, we use a distributed-parameter model based on \citet{Reverchon1996}.
-This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and an initial state estimate.
-We estimate these parameters by applying the maximum likelihood estimation method on yield data under the normal error assumption.
+A system of partial differential equations, $G(t,x,\dot{x},\Theta,u)=0$ is considered, where $x$ denotes the state variables, $\Theta$ represents the parameters, and $u$ is the control variables.
+The system $G(t,x,\dot{x},\Theta,u)=0$ describe the supercritical extraction process, which involves a partially filled extractor with a fixed bed that operates under constant conditions.
+It is assumed that the flow is uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
+To model this two-dimensional case, the concept of quasi-one-dimensional flow is applied.
+To describe the fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent, we use the distributed-parameter model $G(t,x,\dot{x},\Theta,u)=0$ based on \citet{Reverchon1996}.
+This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, saturation concentration, and an initial state estimate.
+These parameters are estimated from the Peng-Robinson equation of state and by applying the maximum likelihood estimation method on yield data under the normal error assumption.
 The dataset comes from four experiments conducted at different operating conditions: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar.
@@
 \subsection{Governing equations} \label{CH:Governing_equations_chapter}
-The governing equation for a quasi-one-dimensional compressible flow in Cartesian coordinates can be found in the appendix \ref{CH: Gouverning equations} and in the work of \citet{Anderson1995}.
+The governing equation for a quasi-one-dimensional compressible flow in Cartesian coordinates can be found in the Appendix \ref{CH: Gouverning equations} and in the work of \citet{Anderson1995}.
 Quasi-one-dimensional flow is a fluid flow characterized by the assumption that the flow properties remain uniform across any given cross-section of the flow.
@@
 
-The quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates are given by equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_3}.
+The quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates are given by Equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_3}.
 
@@
 \section{Conclusions} \label{CH: Conclusion}
-In this study, a process model was developed through parameter estimation using a dataset obtained from experiments conducted at various temperature and pressure.
+In this study, a process model was developed by performing parameter estimation using a dataset obtained from experiments conducted at various temperature and pressure levels.
 The model was found to have good agreement with experimental yield curves for the extraction of caraway oil from caraway seeds.
+However, it was noticed that the simulation results overshoot the dataset, which may be explained to the presence of losses in the real system, such as some amount of the solute sticking to the inner walls of pipes.
+Another possible reason could be the need for a more complex mass transfer mechanism than the extraction kinetic presented in this work.
+For example, the Broken-and-Intact Cell model suggested by \citet{Sovova2017} formulated a general SFE model that includes the solute-matrix interaction.
+This model allows for solute diffusion from intact cells to the region of broken cells, and the equilibrium is established at the particle surface between the broken cells and fluid phase.
+Such a mechanism gives more flexibility to the process model to adapt to a dataset.
+
 To establish correlations for the internal and axial diffusion coefficients in terms of fluid density, both linear and non-linear regression techniques were utilized.
 These correlations facilitated the generalization of the process model to a range of operating conditions, specifically for temperatures ranging from $40^\circ C$ to $50^\circ C$, pressures ranging from 200 bar to 300 bar, and flow rates of 0.4 l/min (with flow variations of up to 5\%).
-The generalized model can be employed to investigate the impact of different operating conditions on the extraction yield, or for economic analysis of the extraction process.
+The dependencies given by these correlations can be justified by the influence of the solubility and Graham's Law of Diffusion, as suggested above.
+
+The generalized model can be used to study the impact of different operating conditions on the extraction yield or for economic analysis of the extraction process.
 
@@
 \subfile{Sections/Porosity}
+
+\subsection{Concentration profiles} \label{CH: Profiles}
+\subfile{Sections/Profiles}
 

### 2023-05-07 SFE-article/Sections/Gouverning_equation_derivation.tex
05.05
07.05

@@
 
-	\hrule
-
 	\subsubsection{Energy conservation}
@@
 			&\cfrac{\partial}{\partial t} \left[ \rho_f \left( e_f + \cfrac{v^2}{2} \right) A_f dz \right] - \rho_f \left( e_f + \cfrac{v^2}{2} \right) v A_f \nonumber \\
-			&+ \left( \rho_f + d\rho_f \right) \left[ e_f + de_f + \cfrac{\left( v + dv \right)^2}{2} \right] \left( V+{\color{red}fV} \right) \left( A_f+dA_f \right) \nonumber \\
+			&+ \left( \rho_f + d\rho_f \right) \left[ e_f + de_f + \cfrac{\left( v + dv \right)^2}{2} \right] \left( V+dV \right) \left( A_f+dA_f \right) \nonumber \\
 			&= - \left[ -PvA_f + \left(P+dP\right) \left(v+dv\right) \left(A_f+dA_f\right) - 2\left( Pv\cfrac{dA_f}{2} \right) \right]
 		\end{align}
-	} \todo[]{Check fV}
+	} %\todo[]{Check fV}
 

### 2023-05-07 SFE-article/Sections/Model.tex
05.05
07.05

@@
 	The continuity equation for the fluid phase is derived in Appendix \ref{CH: Gouverning equations}.
-When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{magenta}\phi}(z)$ (where ${\color{magenta}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: \todo[]{assign a color of v and u}
+When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{magenta}\phi}(z)$ (where ${\color{magenta}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}
 
@@
 	}
+
+	{\color{red}assign a color of v and u}
 
@@
 	The detailed derivation of the mass balance equation for the fluid phase can be found in the appendix (\ref{CH: Gouverning equations}).
-The movement of the mobile pseudo-homogeneous phase (equation \ref{Model_fluid}) is considered only in the axial direction, while the properties of the system in the radial direction are assumed to be uniform.
+The movement of the mobile pseudo-homogeneous phase (Equation \ref{Model_fluid}) is considered only in the axial direction, while the properties of the system in the radial direction are assumed to be uniform.
 Additionally, the boundary layer adjacent to the inner wall of the extractor is neglected, resulting in a constant velocity profile across any cross-section of the extractor perpendicular to the axial direction.
@@
 
-	The solid phase is considered to be stationary, with negligible convection and diffusion terms in the mass balance equation (equation \ref{Model_solid}).
-Therefore, the only significant term in this equation is the kinetic term (as defined in equation \ref{Model_kinetic_basic}), which connects the solid and fluid phases.
+	The solid phase is considered to be stationary, with negligible convection and diffusion terms in the mass balance equation (Equation \ref{Model_solid}).
+Therefore, the only significant term in this equation is the kinetic term (as defined in Equation \ref{Model_kinetic_basic}), which connects the solid and fluid phases.
 The extract is represented by a single pseudo-component to simplify the analysis.
@@
 	%The kinetic term is based on two-film theory and follow work of \citet{Reverchon1996}.
-The mass transfer kinetic (equation \ref{Model_kinetic_basic}) consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.
+The mass transfer kinetic (Equation \ref{Model_kinetic_basic}) consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.
 
-	The kinetic term in this study is based on the two-film theory proposed by \citet{Reverchon1996}, and the mass transfer kinetic is given by equation \ref{Model_kinetic_basic}.
+	The kinetic term in this study is based on the two-film theory proposed by \citet{Reverchon1996}, and the mass transfer kinetic is given by Equation \ref{Model_kinetic_basic}.
 This equation takes into account the overall diffusion coefficient and the concentration gradient, which acts as the driving force for the process.
@@
 
-        %\subfile{Sections/Saturation}
+        \subfile{Saturation}
 
@@
 		 {\color{red}
-			The heat balance (equation \ref{Model_heat}) consists of the convective and diffusive terms.
+			The heat balance (Equation \ref{Model_heat}) consists of the convective and diffusive terms.
 It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases.
@@
 
-		{\color{blue} The heat balance (equation \ref{Model_heat}), is based on \citet{Srinivasan2012}, and consists of convective and diffusive terms.
+		{\color{blue} The heat balance (Equation \ref{Model_heat}), is based on \citet{Srinivasan2012}, and consists of convective and diffusive terms.
 It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases.
@@
 
-			The heat equation was introduced in the previous chapter through equation \ref{EQ: CompressibleEuler_3} and in the appendix \ref{CH: Gouverning equations}
+			The heat equation was introduced in the previous chapter through Equation \ref{EQ: CompressibleEuler_3} and in the appendix \ref{CH: Gouverning equations}
 
@@
 
-			Following \citet{Elliott2011} or \citet{Gmehling2019}, a real gas internal energy definition can be obtained from the departure functions, defined through equation \ref{EQ: internal_energy_def}.
+			Following \citet{Elliott2011} or \citet{Gmehling2019}, a real gas internal energy definition can be obtained from the departure functions, defined through Equation \ref{EQ: internal_energy_def}.
 In thermodynamics, the departure function is a mathematical function that characterizes the deviation of a thermodynamic property of a real substance from that of an ideal gas at the same temperature and pressure.
@@
 			If a gas is considered to be perfectly caloric (${\color{blue}e}(t,z)=C_v {\color{blue}T}(t,z)$), then the energy equation can be written in form of temperature.
-The perfectly caloric gas can be seen as the special case of a real gas, where the second term of the equation \ref{EQ: internal_energy_def} goes to zero.
+The perfectly caloric gas can be seen as the special case of a real gas, where the second term of the Equation \ref{EQ: internal_energy_def} goes to zero.
 
-			For real gases, it is complicated to write the heat balance in terms of temperature, but it be can be used directly in the form of internal energy, as it is given by equation \ref{EQ: CompressibleEuler_3}.
+			For real gases, it is complicated to write the heat balance in terms of temperature, but it be can be used directly in the form of internal energy, as it is given by Equation \ref{EQ: CompressibleEuler_3}.
 In such a case, the temperature (which is used as the input to some other functions) needs to be recovered from the internal energy.
 A relation for the internal energy can be obtained from an equation of state.
-For Peng-Robinson, such a relation is given by equation \ref{EQ: internal_energy_PR} as presented by \citet{Elliott2011}.
+For Peng-Robinson, such a relation is given by Equation \ref{EQ: internal_energy_PR} as presented by \citet{Elliott2011}.
 
@@
 
-			To solve equation \ref{EQ: internal_energy_PR}, values of temperature, pressure, and density need to be known.
+			To solve Equation \ref{EQ: internal_energy_PR}, values of temperature, pressure, and density need to be known.
 If an equation of state is introduced, then only two out of three variables need to be obtained as the third one can be calculated, this can be represented as follow
@@
 			If the value of internal energy ${\color{blue}e}(t,z)$ is known from the time evolution of the energy equation (\ref{EQ: CompressibleEuler_3}), and pressure is known from measurement, then the temperature can be reconstructed.
-A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution and the output from equation \ref{EQ: internal_energy_PR}.
+A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution and the output from Equation \ref{EQ: internal_energy_PR}.
 Such a procedure allow to find local temperature along spatial direction ${\color{blue}z}$ and needs to be repeated every time-step.
@@
 
-			If the value of enthalpy is known from the time evolution and pressure can be measured, then the equation \ref{EQ:Enthalpy_root} can be solved for the temperature to recover the temperature profile.
-By applying the departure functions to Peng-Robinson equation of state, the relation \ref{EQ:Enthalpy_root} can be expressed directly through equation \ref{EQ:Enthalpy_PR} as presented in \ref{CH:Enthalpy} or given by \citet{Gmehling2019}.
+			If the value of enthalpy is known from the time evolution and pressure can be measured, then the Equation \ref{EQ:Enthalpy_root} can be solved for the temperature to recover the temperature profile.
+By applying the departure functions to Peng-Robinson equation of state, the relation \ref{EQ:Enthalpy_root} can be expressed directly through Equation \ref{EQ:Enthalpy_PR} as presented in \ref{CH:Enthalpy} or given by \citet{Gmehling2019}.
 
@@
 
-			The equation \ref{EQ:Enthalpy_PR} requires an reference sate, which in this case is assumed to be $T_{ref}=298.15~[K]$ and $P_{ref}=1.01325~[bar]$.
+			The Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which in this case is assumed to be $T_{ref}=298.15~[K]$ and $P_{ref}=1.01325~[bar]$.
 
@@
 						\\ \hline \\
-						\cfrac{d {\color{blue}t}(t)}{d t}
+						\cfrac{d {\color{blue}y}(t)}{d t}
 					\end{bmatrix}
@@
 
-			To ensure the stability of the convergence while solving the partial differential equations, the Courant–Friedrichs–Lewy condition (given by Equation \ref{EQ:CFL}) was applied.
+%			To ensure the stability of the convergence while solving the partial differential equations, the Courant–Friedrichs–Lewy condition (given by Equation \ref{EQ:CFL}) was applied.
 Based on the discretization step and the velocity, the Courant–Friedrichs–Lewy condition can be used to find.
-
-			{\footnotesize
-				\begin{equation}
-					C = \cfrac{u\Delta t}{\Delta x} \leq C_{max} = 1 
-					\label{EQ:CFL}
-				\end{equation}
-			}
-
-			where u is velocity, $\Delta t$	is a time step and $\Delta x$ is the space discretization.
+%			
+%			{\footnotesize
+%				\begin{equation}
+%					C = \cfrac{u\Delta t}{\Delta x} \leq C_{max} = 1 
+%					\label{EQ:CFL}
+%				\end{equation}
+%			}
+%			
+%			where u is velocity, $\Delta t$	is a time step and $\Delta x$ is the space discretization.
 

### 2023-05-07 SFE-article/Sections/Parameter_estimation.tex
05.05
07.05

@@
 The goal of parameter estimation is to obtain the "best" estimate of parameter set $\theta$ (which is a subset of the parameter space $\Theta$ containing all parameters of a model) based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$.
-Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, $y(t)$ (equation \ref{Model_measurment_1}), to give the observable dependent variable $Y(t)$ (for example results of an experiments).
+Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, $y(t)$ (Equation \ref{Model_measurment_1}), to give the observable dependent variable $Y(t)$ (for example results of an experiments).
 For discrete observations, this can be expressed as:
@@
 
+\iffalse
 \subsubsection{Least squares estimation}
@@
 
-\iffalse
 \subsubsection{Weighted sum of squares - Cumulative data}
@@
 
-\subsubsection{Maximum likelihood estimation}
+%\subsubsection{Maximum likelihood estimation}
 
@@
 The conditions at the maximum can be refined by incorporating prior information.
-The posterior probability density function $p(\theta|y)$ can be expressed as the ratio of two probability densities (\ref{EQ: Probabiltiy_independet_b}) using the continuous variable analogue of Bayes' theorem (details in appendix \ref{CH: Bayes}).
+The posterior probability density function $p(\theta|y)$ can be expressed as the ratio of two probability densities (\ref{EQ: Probabiltiy_independet_b}) using the continuous variable analogue of Bayes' theorem (details in Appendix \ref{CH: Bayes}).
 In such a case the posteriori distribution is given by Equation \ref{EQ: Posterior_distribution}.

### 2023-05-07 SFE-article/Sections/Profiles.tex
07.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	The time evolution of concentration profiles along the extractor for each dataset is presented on Figure \ref{fig: estimation_results_profiles}. The concentration profiles use the parameters obtained from the parameter estimation. The plots on the left hand-side show the fluid phase concentration, while the plots on the right-hand side present the concentration in the solid phase.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 1.4cm 1.9cm 11cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
			\caption{Experiment at $40^\circ C$ and $200$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 1.4cm 1.9cm 11cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
			\caption{Experiment at $50^\circ C$ and $200$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 1.4cm 1.9cm 11cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
			\caption{Experiment at $40^\circ C$ and $300$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 1.4cm 1.9cm 11cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
			\caption{Experiment at $50^\circ C$ and $300$ bar}
		\end{subfigure}
		\caption{Concentration profiles after solving the parameter estimation problem}
		\label{fig: estimation_results_profiles}
	\end{figure}

\end{document}

### 2023-05-07 SFE-article/Sections/Results.tex
07.05

@@
         \item Axial Diffusion coefficient: \qquad$D_e^M$
+        \item Saturation concentration: \quad\qquad$C_{sat}$
         \item Standard Deviation: \qquad\qquad\quad$\sigma$
@@
 During the preparation period the solute diffuses to the fluid phase in contact with the solid particles.
-Later, the solute in the fluid phase is partially moved (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed) along the extractor.
-As a result, the distribution of solutes mass in the fluid phase is assumed to not be uniform.
+Later, the solute in the fluid phase is partially moved along the extractor (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed).
+As a result, the distribution of solute mass in the fluid phase is assumed to not be uniform.
 Some conclusions can be drawn from the analysis of the initial part of each yield curve.
@@
 The lower and upper bounds for each parameter are given in Table \ref{tab:Constraints}.
-The same Table contains the initial guesses for the optimizer.
-To ensure that the solution is a global solution multiple initial points have been tested.
+To ensure that the solution is a global solution multiple initial points have been tested but presented results come from the initial guess given also in Table \ref{tab:Constraints}.
 
@@
 		\adjustbox{max width=\columnwidth}{%
-		\begin{tabular}{ lcccccc }
+		\begin{tabular}{ lccccccc }
 			\hline 
-			Parameter		&$k_m$ 	& $D_i$ 	& $D_e^M$ 	& $m_{total}$	& $\tau$ 	& $\sigma$ \\  \hline
-			Lower bound		&0	  	& 0 	  	& 0 		& 76 		 	& 0 	   	& 0 \\ 
-			Upper bound		&1 		& $+\infty$ & $+\infty$	& 100 			& 1 		& $+\infty$ \\ 
-			Initial guess	&1	  	& 3 	  	& 1 		& 77 		 	& 0.65 	   	& 0.1 \\  \hline
+			Parameter		&$k_m$[-] 	& $D_i$[m/s$^2$] 	& $D_e^M$[m/s$^2$]	& $C_{sat}$ [kg/m$^3$] 	& $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
+			Lower bound		&0	  		& 0 	  			& 0 				&	0					& 80 		 		& 0 	   		& 0 \\ 
+			Upper bound		&1 			& $+\infty$ 		& $+\infty$			&	$+\infty$			& 150 				& 1 			& $+\infty$ \\ 
+			Initial guess	&1	  		& 3 	  			& 1 				&	3					& 80 		 		& 0.65 	   		& 0.1 \\  \hline
 		\end{tabular} }
@@
 
-	The figure \ref{fig: estimation_results} show yield curves for each of experiments.
+	Figure \ref{fig: estimation_results} show yield curves for each of experiments.
 The blue dots indicate the data point obtained as a measurement from the laboratory experiments.
@@
 The curves on the left hand-side of the Figure \ref{fig: estimation_results}, are the cumulative yield curves, which represents the cumulative amount of the oil collected during each experiment.
-The Figures on the right hand-side, represent the derivative of the cumulative yield curves.
+The plots on the right hand-side, represent the derivative of the cumulative yield curves.
 As explained in the chapter \ref{CH: Parameter_estimation}, the derivatives of the cumulative measurements are independent on the previous measurement and should be used for the parameter estimation.
@@
 			\csvautobooktabular{Figures/Results_estimation/estimation.csv} }
-		\caption{Parameter estimation results}
+		\caption{Parameter estimation results rounded to fifth decimal place}
 		\label{tab: Estimation_results}
@@
 
-	The results of the parameter estimation can be found in Table \ref{tab: Estimation_results}.
+	The results of parameter estimation can be found in Table \ref{tab: Estimation_results} and the concentration profiles, which correspond for the optimized solution for each experiments, are presented on Figure \ref{fig: estimation_results_profiles} in Appendix \ref{CH: Profiles}.
 As can be noticed, the optimizer found that the partition factor should be as high as possible and moved values of $k_m$ for each experiment to unity, which was chosen as the upper bound.
 
-	Values of the internal diffusion coefficients are distinguished for each experiment, with an increasing trend with respect to the fluid density.
+	Values of the internal diffusion coefficients are distinguished for each experiment, which grows as the fluid density increase.
 The order of magnitude of $D_i$ obtained from the optimization is similar to values found by other researchers.
@@
 
+	The further spifflication of the process model can be introduced based on $C_{sat}$ results.
+Values of saturation concentrations are at the level of 1e5 which is an internal upper bound of the optimizer used if $+\infty$ indicates the upper bound.
+This suggest that solvent hasn't reach the saturation concentration and the process model can be simplified by replacing $\gamma(c_f)$ function with unity.
+
 	As the total amount of the oil present in the system is unknown, and as such it has been obtained from the optimizer.
-Given the dataset and the process model, the optimizer found that all most all the oil was extracted out of the seeds and that the best fit is obtained if the total mass of the oil reach a lower bound equal to 76 g.
+Given the dataset and the process model, the optimizer found that the best fit is obtained if the total mass of the oil reach a lower bound equal to 80 g.
+The lower bound was estimated by round up of the biggest value of collected cumulative amount of the extraction product.
+As the same raw material was used in all experiments, the same initial amount of solute is assumed for all the cases.
 
 	As explained above, and in Appendix \ref{CH: IC_BC}, the linear distribution of can be fully determined if the parameter $\tau$ is known.
-The split ratio for experiments conducted at $40 ^\circ C$ / 300 bar and $50 ^\circ C$ / 300 bar are similar to each other and close to 0.64.
-The experiments performed at $40 ^\circ C$ / 200 bar and $50 ^\circ C$ / 200 bar have $\tau$ equals to $0.69$ and $0.74$, respectively.
+The split ratio for experiments conducted at $40 ^\circ C$ / 300 bar and $50 ^\circ C$ / 300 bar are similar to each other and close to 0.65.
+The experiments performed at $40 ^\circ C$ / 200 bar and $50 ^\circ C$ / 200 bar have $\tau$ equals to $0.70$ and $0.75$, respectively.
 
 	The noise present in each dataset is quantified by parameter $\sigma$.
-It can be observed dataset obtained at $40 ^\circ C$ / 200 bar, $50 ^\circ C$ / 200 bar and $40 ^\circ C$ / 300 bar have similar value of $\sigma\approx0.34$.
-The visual investigation of the dataset obtained at $50 ^\circ C$ / 300 bar allow to explain higher value of $\sigma$ for this dataset.
-This dataset have higher deviation of the data points from the simulated curve.
+It can be observed dataset obtained at $40 ^\circ C$ / 200 bar and $50 ^\circ C$ / 200 bar have similar value of $\sigma\approx0.36$.
+The visual investigation of the datasets obtained at $40 ^\circ C$ / 300 bar and $50 ^\circ C$ / 300 bar allow to explain higher values of $\sigma$ for both dataset.
+Both datasets have higher deviation of the data points from the simulated curve.
 
@@
 			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
 			\caption{Experiment at $40^\circ C$ and $200$ bar}
@@
 			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
 			\caption{Experiment at $50^\circ C$ and $200$ bar}
@@
 			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
 			\caption{Experiment at $40^\circ C$ and $300$ bar}
@@
 			\centering
-			\includegraphics[trim = 3cm 11cm 2.5cm 2.1cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
 			\caption{Experiment at $50^\circ C$ and $300$ bar}
@@
 	The results obtained from the parameter estimation are used to develop a generalized process model.
-This model expresses the parameters $D_i$ and $D_e^M$ as functions of the operating conditions, such as temperature (T), pressure (P), and flow rate (F).
+The model generalization is performed by introducing correlations which link the estimated parameters and the operating conditions.
 Since the experiments were performed under varying temperature and pressure, the influence of these variables is taken into account.
 To simplify the problem, the correlations are written as functions of fluid density rather than temperature and pressure.
-
-	While the experimental procedure and device can affect $\tau$ and $\sigma$, these parameters are not further considered.
-They are used only to define the initial conditions and are not included in the process model.
-Additionally, since the optimizer found that $k_m$ and $m_{total}$ have the same value, they are assumed to be constants and not considered further.
+Since the optimizer found that $k_m$, $m_{total}$ and $C_{sat}$ don't change with the density variations, they are assumed to be constants and not considered further.
 
@@
 Figure \ref{fig:Regression} shows the first- and second-order polynomials used to fit $D_i$ and $D_e^M$ as a function of fluid density.
-Interestingly, these two parameters exhibit opposite behavior.
 
@@
 		\centering
-		\includegraphics[trim = 10.5cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
-		\caption{First order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
+		\includegraphics[trim = 11.7cm 14cm 2.3cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
+		\caption{First-order polynomial regression of fitted parameters ($D_i$ and $D_e^M$) as a function of fluid density $\rho_f$}
 		\label{fig:Regression_1}
@@
 		\centering
-		\includegraphics[trim = 10.5cm 11cm 2.5cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
-		\caption{Second order polynomial regression of fitted parameters as a function of fluid density $\rho_f$}
+		\includegraphics[trim = 11.7cm 14cm 2.3cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
+		\caption{Second-order polynomial regression of fitted parameters ($D_i$ and $D_e^M$) as a function of fluid density $\rho_f$}
 		\label{fig:Regression_2}
 	\end{subfigure}
-	\caption{Results of parameter fitting, with estimation of the initial state} 
+	\caption{Regression of $D_i$ and $D_e^M$} 
 	\label{fig:Regression}
@@
 	The increase in the density of the supercritical fluid can lead to an increase in the solubility of the solute and, consequently, an increase in the concentration gradient.
-This increased concentration gradient drives the solute to diffuse more rapidly through the matrix of the solid particles, resulting in an increase in the internal mass transfer coefficient.
-However, the effect of increased solubility on the internal mass transfer coefficient is greater than the resistance coming from higher density, resulting in an overall increase in the internal mass transfer coefficient with density.
+This increased concentration gradient drives the solute to diffuse more rapidly through the matrix of the solid particles, resulting in an increased internal mass transfer coefficient.
+However, the effect of increased solubility on the internal mass transfer coefficient outweighs the resistance from higher density, resulting in an overall increase in the internal mass transfer coefficient with density.
+The same behaviour can be observed in Figure \ref{fig: estimation_results}, where plots on the right-hand side exhibit a peak.
+The higher the peak, the greater the increase in solute concentration in the fluid phase, which can be explained by higher solubility.
 
@@
 
-	Figure \ref{fig:Regression_1} show the result of fitting a second-order polynomial in density space.
+	Figure \ref{fig:Regression_2} show the result of fitting a second-order polynomial in density space.
 It can be observed that the fit obtained from quadratic functions seems to be represent both dataset better.
 
+	The experimental procedure and the used device can influence the values of $\tau$ and $\sigma$.
+Therefore, seeking a general expression for the initial state that is solely a function of operating conditions may not be sufficient to fully describe the relationship between these parameters.
+However, if first- and second-order regressions are applied to $\tau$ and $\sigma$, some general conclusions about the trend can be drawn.
+The results of the regression applied to $\tau$ and $\sigma$ are presented in Figure \ref{fig:Regression_tau_simga}.
+
+	\begin{figure}[!h]
+		\centering
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 18.8cm 8cm 2.5cm 7.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
+			\includegraphics[trim = 4cm 2cm 17.5cm 13.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
+			\caption{First order polynomial regression of fitted parameters ($\tau$ and $\sigma$) as a function of fluid density $\rho_f$}
+			\label{fig:Regression_3}
+		\end{subfigure}
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 18.8cm 8cm 2.5cm 7.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
+			\includegraphics[trim = 4cm 2cm 17.5cm 13.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
+			\caption{Second order polynomial regression of fitted parameters ($\tau$ and $\sigma$) as a function of fluid density $\rho_f$}
+			\label{fig:Regression_4}
+		\end{subfigure}
+		\caption{Regression of $\tau$ and $\sigma$} 
+		\label{fig:Regression_tau_simga}
+	\end{figure}
+
+	As can be seen from Figure \ref{fig:Regression_tau_simga} , the $\tau$ seems to decrease as the fluid density increase.
+The standard deviation increases as the fluid density increase.
+As mentioned above, these results should be used with caution due to uninvestigated influence of the equipment on the extraction results.
+
 \end{document}

### 2023-05-07 SFE-article/Sections/Saturation.tex
07.05

@@
 
-	where $k_{sat}$ is the growth rate, and it is defined as $k_{sat} = 2c_{sat}$\todo{Explain why the growth rate is defined as it is}.
+	where $k_{sat}$ is the growth rate, and it is defined as $k_{sat} = 4$.
+The growth rate corresponds for the shape of the $\gamma(c_f)$ function.
+The bigger value of the $k_{sat}$ the steeper the function is.
+In the limit when $ k_{sat}\rightarrow+\infty$ become a step function.
+If the growth rate is to high, the gradient of the $\gamma$ function become high, or goes to infinity, which might cause difficulties for a gradient-based optimizer.
 
@@
 					blue,
-					] { 1 / (1 + exp( 2*5 .* ( x - 5 ) ) ) };
+					] { 1 / (1 + exp( 4 .* ( x - 5 ) ) ) };
 					\addplot[thick, samples=50, dashed, domain=0:1.5, black] coordinates {(5,-0.5)(5,1.5)};

### 2023-05-07 SFE-article/Sections/Thermo_imp.tex
07.05

@@
 Detail information about Peng-Robinson equation of state can be found in the work of \citet{Peng1976}, \citet{Elliott2011} or \citet{Pratt2001}.
-The P-R EOS is presented by equation \ref{EQ: PR}
+The P-R EOS is presented by Equation \ref{EQ: PR}
 
@@
 
-	The parameters $a, b, \alpha$ are parameters defined as presented in the appendix \ref{subsubsec: Equation of state}.
+	The parameters $a, b, \alpha$ are parameters defined as presented in the Appendix \ref{subsubsec: Equation of state}.
 
@@
 As presented in Figure \ref{fig: SFE_Properties_Compressibility}, the compressibility factor obtained from the Peng-Robinson equation of state varies strongly depending on the operating conditions.
-The compressibility factor can be obtained by solving the polynomial form of the P-R EOS given by \ref{EQ: PR_polynomial}.
+The compressibility factor can be obtained by solving the polynomial form of the P-R EOS given by Equation \ref{EQ: PR_polynomial}.
 
@@
 
-	where $A$ and $B$ are parameters as defined in the appendix \ref{subsubsec: Equation of state}.
+	where $A$ and $B$ are parameters as defined in the Appendix \ref{subsubsec: Equation of state}.
 The roots of the polynomial can be found iteratively or by the Cardano formula.
@@
 The fluid's properties near the critical point are unique and combine gas-like and liquid-like properties.
-The details of calculations are explained in the appendix \ref{subsubsec: Fluid density}.
+The details of calculations are explained in the Appendix \ref{subsubsec: Fluid density}.
 
 	Figure \ref{fig: SFE_Properties_CP} show the behaviour of the heat capacity of a supercritical fluid at constant pressure ($C_p$).
-The details of the calculations can be found in the appendix \ref{subsubsec: Fluid heat capacity}.
+The details of the calculations can be found in the Appendix \ref{subsubsec: Fluid heat capacity}.
 Contrary to the density, which varies monotonically, the specific heat shows very high levels in a narrow region.

### 2023-05-07 SFE-article/Sections/Thermodynamic_details.tex
07.05

@@
 	\subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}
-	We consider equations of state in the general form ${\color{red}P}(t) {\color{orange}v_m}[T(t,z),P(t)] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, where ${\color{magenta}v_m}$ denotes the molar volume of $\text{CO}_2$, ${\color{orange}Z}$ represents its compressibility factor, and $R$ is the universal gas constant.
-More specifically, we are interested in these equations because of the possibility to express the compressibility $Z$ as an explicit function of temperature and pressure.
-This is the case when $Z$ is obtained as one of the physically meaningful roots of a polynomial equation, like the Van der Waals's, Peng-Robinson's or Redlich–Kwong's equation of state.
-In this work the Peng-Robinson equation of state (\citet{Peng1976}) is used
+	In this study, the influence of real gas effects are introduced through ${\color{red}P}(t) {\color{orange}v_m}[T(t,z),P(t)] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, where ${\color{orange}v_m}$ represents the molar volume of $\text{CO}_2$, ${\color{orange}Z}$ denotes its compressibility factor, and $R$ is the universal gas constant.
+The main advantage of using compressibility in calculations is to express it as an explicit function of temperature and pressure.
+This is possible when $Z$ is obtained as one of the physically meaningful roots of a polynomial equation, such as the Van der Waals, Peng-Robinson, or Redlich-Kwong equation of state.
+In this study, the Peng-Robinson equation of state (\citet{Peng1976}) was selected.
 
-	In Peng-Robinson's equation fo state, the compressibility ${\color{orange}\overline{Z}}[{\color{blue}T}(t,z), {\color{red}P}(t)]$ solves the third-order polynomial equation given by equitation \ref{eq: Compressibility}.
-The polynomial equation can be solved by numerical methods like Newton-Raphson, or by applying Cardano formula.
-The Cardano formula is preferable in comparison to numerical root-finders, as it allows to obtain an analytical solution.
-The details of the Cardano formula are presented in appendix \ref{CH: Cardano}.
+	In the Peng-Robinson equation of state, the compressibility ${\color{orange}\overline{Z}}[{\color{blue}T}(t,z), {\color{red}P}(t)]$ solves the third-order polynomial equation shown in Equation \ref{eq: Compressibility}.
+Numerical methods such as Newton-Raphson can be used to solve the polynomial equation, but the Cardano formula is preferred as it yields an analytical solution.
+Further details regarding the Cardano formula can be found in Appendix \ref{CH: Cardano}.
 
@@
 
-	where ${\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are functions of time and space defined on the attraction parameter, ${\color{orange}a}\left[{\color{blue}T}(t,z)\right] = {\color{magenta}a^c_{\text{CO}_2}}{\color{orange}\alpha}\left[{\color{blue}T}(t,z)\right]$ with ${\color{magenta}a^c_{\text{CO}_2}} \approx 0.45724 {{\color{magenta}R}^2{\color{magenta}T^c_{\text{CO}_2}}^2}/{{\color{magenta}P^c_{\text{CO}_2}}}$, and the repulsion parameter, ${\color{magenta}b_{\text{CO}_2}} \approx 0.07780 {{\color{magenta}R}{\color{magenta}T^c_{\text{CO}_2}}}/{{\color{magenta}P^c_{\text{CO}_2}}}$, both functions of the critical temperature ${\color{magenta}T^c_{\text{CO}_2}}$ and pressure ${\color{magenta}P^c_{\text{CO}_2}}$.
-Specifically, we have
+	where ${\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are functions of time and space defined on the attraction parameter, ${\color{orange}a}\left[{\color{blue}T}(t,z)\right] = {\color{magenta}a^c}{\color{orange}\alpha}\left[{\color{blue}T}(t,z)\right]$ with ${\color{magenta}a^c} \approx 0.45724 {{\color{magenta}R}^2{\color{magenta}T^c}^2}/{{\color{magenta}P^c}}$, and the repulsion parameter, ${\color{magenta}b} \approx 0.07780 {{\color{magenta}R}{\color{magenta}T^c}}/{{\color{magenta}P^c}}$, both functions of the critical temperature ${\color{magenta}T^c}$ and pressure ${\color{magenta}P^c}$.
 
@@
 		\begin{align} 
-			{\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]	& = \dfrac{{\color{orange}\alpha}\left[T\left(t,z\right)\right]{\color{magenta}a^c_{\text{CO}_2}}{\color{red}P}(t)}{{\color{magenta}R}^2{\color{blue}T}^2(t,z)};													\label{eq: PR_A}\\
-			{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]	& = \dfrac{{\color{magenta}b_{\text{CO}_2}}{\color{red}P}(t)}{{\color{magenta}R}{\color{blue}T}(t,z)}	\label{eq: PR_B}.
+			{\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]	& = \dfrac{{\color{orange}\alpha}\left[T\left(t,z\right)\right]{\color{magenta}a^c}{\color{red}P}(t)}{{\color{magenta}R}^2{\color{blue}T}^2(t,z)};													\label{eq: PR_A}\\
+			{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]	& = \dfrac{{\color{magenta}b}{\color{red}P}(t)}{{\color{magenta}R}{\color{blue}T}(t,z)}	\label{eq: PR_B}.
 		\end{align}
@@
 
-	The quantity {\small${\color{orange}\alpha}\left[{\color{blue}T}\left(t,z\right)\right]= \left[1 + {\color{magenta}\kappa_{\text{CO}_2}} \left[1 - \sqrt{{\color{blue}T}\left(t,z\right) / {\color{magenta}T^c_{\text{CO}_2}}} \right] \right]^2$}, with constant ${\color{magenta}\kappa_{\text{CO}_2}} = 0.37464 + 1.54226 {\color{magenta}\omega_{\text{CO}_2}} - 0.26992 {\color{magenta}\omega_{\text{CO}_2}}^2$, is a dimensionless correction term defined on the acentric factor ${\color{magenta}\omega_{\text{CO}_2}} = 0.239$ of $\text{CO}_2$ molecules.
-\\
+	The quantity ${\color{orange}\alpha}\left[{\color{blue}T}\left(t,z\right)\right]$ is a dimensionless correction term that depends on the temperature ${\color{blue}T}\left(t,z\right)$ and a constant ${\color{magenta}\kappa}$.
+The constant ${\color{magenta}\kappa}$ is given by the formula ${\color{magenta}\kappa} = 0.37464 + 1.54226 {\color{magenta}\omega} - 0.26992 {\color{magenta}\omega^2}$, where ${\color{magenta}\omega}$ is the acentric factor of $\text{CO}_2$ molecules and is equal to 0.239.
 
-	By denoting the physical constants as {\small$\varphi_{Z} = \left(R,T^c_{\text{CO}_2},P^c_{\text{CO}_2},\kappa_{\text{CO}_2}\right)$}, we obtain a spatio-temporal representation of the compressibility ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi_{Z}\right]$ with its complete set of functional dependencies and parameters.
-\\
+%	Using the physical constants $\varphi_{Z} = \left(R,T^c_{CO_2},P^c{CO_2},\kappa{CO_2}\right)$, we can represent the compressibility ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi{Z}\right]$ as a function of temperature and pressure with their complete set of functional dependencies and parameters.
 
@@
 
-	The density $\rho_{\text{F}}$ of the fluid phase is assumed to be equal to the density of solvent, at given temperature and pressure.
-Because temperature $T(t,z)$ of the fluid phase is a modelled variable, we allow for the density to vary along the bed and in time.
-From an equation of state of the form ${\color{red}P}(t) {\color{orange}v_m}\left[T(t,z),P(t)\right] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, we get
+	The density of the fluid phase, denoted by $\rho_{\text{F}}$, is assumed to be equal to the density of the solvent at a given temperature and pressure.
+Since the temperature $T(t,z)$ of the fluid phase is a modelled variable, the density can vary both along the bed and in time.
+Using an equation of state in the form of ${\color{red}P}(t) {\color{orange}v_m}\left[T(t,z),P(t)\right] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, the following expression for the density can be obtained:
 
@@
 		\begin{equation} \label{eq: Density}
-		{\color{orange}\rho_{\text{F}}} \left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid {\color{magenta}\varphi_{\rho_{\text{F}}}}\right] = \dfrac{{\color{red}P}(t) {\color{magenta}M_{\text{CO}_2}}}{{\color{magenta}R}{\color{blue}T}(t,z){\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid \varphi_{Z}\right]},
-	\end{equation} }
+			{\color{orange}\rho_{\text{F}}} \left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid {\color{magenta}\varphi_{\rho_{\text{F}}}}\right] = \frac{{\color{red}P}(t) {\color{magenta}M_{CO_2}}}{{\color{magenta}R}{\color{blue}T}(t,z){\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid \varphi{Z}\right]},
+	\end{equation}}
 
-	where ${\color{magenta}M_{\text{CO}_2}}$ denotes the molar mass of $\text{CO}_2$ and ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ is the compressibility factor that solves Eq.
+	where ${\color{magenta}M_{CO_2}}$ denotes the molar mass of $CO_2$, and ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ is the compressibility factor that solves Eq.
 \eqref{eq: Compressibility}.
-The density of the fluid is thus a function of space and time, due to its dependence on temperature and pressure, and it is expressed in terms of the set of physical constants $\varphi_{\rho_\text{F}} = \left({\color{magenta}R}, {\color{magenta}M_{\text{CO}_2}}, {\color{magenta}T^c_{\text{CO}_2}}, {\color{magenta}P^c_{\text{CO}_2}}, {\color{magenta}\omega_{\text{CO}_2}}\right)$.
-\\
+This means that the density of the fluid depends on both space and time, due to its dependence on temperature and pressure.
+%	, and it can be expressed in terms of a set of physical constants, denoted by $\varphi{\rho_\text{F}} = \left({\color{magenta}R}, {\color{magenta}M_{CO_2}}, {\color{magenta}T^c{CO_2}}, {\color{magenta}P^c{CO_2}}, {\color{magenta}\omega{\text{CO}_2}}\right)$.
 
@@
 	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}.
-In the following, we report only the main steps in the derivation of ${\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$:
+The main steps in the derivation of ${\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are presented below:
 
@@
 
-	For $CO_2$ ()\todo[fancyline]{Add REF}, we have the ideal gas contribution to the specific heat at constant $P(t)$, as function of $T(t,z)$,
+	For $CO_2$, the ideal gas contribution to the specific heat at constant $P(t)$, as function of $T(t,z)$ is given by,
 
@@
 
-	where the coefficients of the expansion are ${\color{magenta}C_{P0}} = 4.728$, ${\color{magenta}C_{P1}} = 1.75 \times 10^{-3}$, ${\color{magenta}C_{P2}} = -1.34 \times 10^{-5}$, and ${\color{magenta}C_{P3}} = 4.10 \times 10^{-9}$.
+	where the coefficients ({\color{red}REF}) of the expansion are ${\color{magenta}C_{P0}} = 4.728$, ${\color{magenta}C_{P1}} = 1.75 \times 10^{-3}$, ${\color{magenta}C_{P2}} = -1.34 \times 10^{-5}$, and ${\color{magenta}C_{P3}} = 4.10 \times 10^{-9}$.
 For the correction term ${\color{orange}C_p^{\text{R}}}\left[{\color{blue}T}(t,z){\color{red}P}(t)\right]$ at constant pressure $P(t)$, we have
@@
 
-	Similarly, for the partial derivative of the pressure with respect to temperature at constant volume, we have
+	Similarly, for the partial derivative of the pressure with respect to temperature at constant volume is :
 
@@
 
-	By denoting the physical constants as $\varphi_{C_p^{\text{F}}} = ({\color{magenta}R}, {\color{magenta}M_{\text{CO}_2}},\\ {\color{magenta}T^c_{\text{CO}_2}}, {\color{magenta}P^c_{\text{CO}_2}}, {\color{magenta}\omega_{\text{CO}_2}})$, we get the spatio-temporal representation $C_p^{\text{F}}\left[T(t,z),P(t) \mid \varphi_{C_p^{\text{F}}}\right]$ of the specific heat of the fluid phase.
+	%By denoting the physical constants as $\varphi_{C_p^{\text{F}}} = ({\color{magenta}R}, {\color{magenta}M},\\ {\color{magenta}T^c}, {\color{magenta}P^c}, {\color{magenta}\omega})$, we get the spatio-temporal representation \\$C_p^{\text{F}}\left[T(t,z),P(t) \mid \varphi_{C_p^{\text{F}}}\right]$ of the specific heat of the fluid phase.
 

### 2023-05-07 SFE-article/Sections/introduction_imp.tex
07.05

@@
 
-	In this work, we derive basic governing equations and combine them with the kinetic model suggested by \citet{Reverchon1996} to obtain a general model for the extraction process of the oil from the caraway seed.
+	In this work, the basic governing equations are derived and combine them with the kinetic model suggested by \citet{Reverchon1996} to obtain a general model for the extraction process of the oil from the caraway seed.
 This model simplifies some of the physical behavior to obtain a control-oriented model.
-Our work assumes that the extraction process operates semi-continuously in a cylindrical vessel.
+It is assumed that the extraction process operates semi-continuously in a cylindrical vessel.
 The solvent is first brought to supercritical conditions, pumped through a fixed bed of finely chopped biomass, and the solute is extracted from the biomass.
@@
 However, the outlet temperature ($T_{out}$) can only be measured.
-Figure \ref{fig: SFE_drawing} depicts a simplified flow diagram.
+Figure \ref{fig: SFE_drawing} shows a simplified flow diagram.
 

### 2023-05-07 SFE - InternalEnergy/Plot_Trend_Line.m

@@ -13,21 +13,21 @@ for jj=1:2
         p_est                = polyval(trendLine, RHO);
         p_y                  = polyval(trendLine, linspace(min(RHO), max(RHO) ) );
         
-        subplot(2,4,ii)
+        subplot(3,3,ii)
         scatter(RHO, DATA_K_OUT(ii,:), 'filled')
         hold on
         plot(linspace(min(RHO), max(RHO) ),p_y,'LineWidth',2);
         hold off
 
         if jj==1
-            pp=sprintf('%s=$(%6.4g) \\rho + (%6.4g)$',NAME{ii},trendLine');
+            pp=sprintf('%s=$(%6.4g) \\rho + (%6.4g)$\n',NAME{ii},trendLine');
         else
-            pp=sprintf('%s=$(%6.4g) \\rho^2 + (%6.4g) \\rho + (%6.4g)$',NAME{ii},trendLine');
+            pp=sprintf('%s=$(%6.4g) \\rho^2 + (%6.4g) \\rho + (%6.4g)$\n',NAME{ii},trendLine');
         end
 
         oo = sprintf('$R^2 = %g$\n', round(power(corr2(DATA_K_OUT(ii,:), p_est),2),2) ) ;
     
-        title( [oo,pp], 'FontSize', 6)
+        title( [oo,pp], 'FontSize', 8)
     
         xlabel('$\rho~[kg/m^3]$','Interpreter','latex')
         ylabel(NAME{ii},'Interpreter','latex')

### 2023-05-08 SFE-article/Sections/Results.tex
08.05

@@
 		\end{tabular} }
-	\caption{Constraints of the parameter estimation problem}
+	\caption{Constraints and initial guess of the parameter estimation problem}
 	\label{tab:Constraints}
@@
 
+	To prove that the obtained solution is a global solution, the parameter estimation problem was run from multiple initial conditions.
+The Appendix \ref{CH: Profiles_2}, contain a solution of the optimization solution and corresponding figures.
+
 \end{document}

### 2023-05-08 SFE - InternalEnergy/main_Fitting.m

@@ -13,12 +13,12 @@ DATA_set                = {'LUKE_T40_P200', 'LUKE_T50_P200', 'LUKE_T40_P300_org'
 %DATA_set                = {'LUKE_T50_P300'};
 
 which_k                 = [8,  44, 45, 47               ];                  % Select which parameters are used for fitting
-k0                      = [1,  3 , 1 ,  10, 80, 0.65, 0.3];                  % Give inital value for each parameter
+k0                      = [0.01,  3 , 1 ,  1, 100, 0.65, 0.4];                  % Give inital value for each parameter
 Nk                      = numel(which_k)+3;                                 % Parameters within the model + m_max, m_ratio, sigma
 k_lu                    = [ [0;0;0;0;80;0;0] , [1;inf;inf;inf;150;1;inf] ];
 
 Iteration_max           = 100;                                              % Maximum number of iterations for optimzer
-Time_max                = 5*24;                                               % Maximum time of optimization in [h]
+Time_max                = 2*24;                                               % Maximum time of optimization in [h]
 
 V_Flow                  = 0.4;                                              % Volumetric flow rate l/min
 

### 2023-05-12 SFE-article/Sections/Model.tex
12.05

@@
 		\begin{equation*}
-			\frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{magenta}\phi})}{\partial t} + \frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) v A {\color{magenta}\phi})}{\partial {\color{blue}z}} = 0
+			\frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{magenta}\phi})}{\partial t} + \frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v A {\color{magenta}\phi})}{\partial {\color{blue}z}} = 0
 		\end{equation*}
@@
 		\begin{equation}
-			\int \frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) v A {\color{magenta}\phi})}{\partial {\color{blue}z}} dz = 0 \rightarrow {\color{red}F}={\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) v A {\color{magenta}\phi}
+			\int \frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v A {\color{magenta}\phi})}{\partial {\color{blue}z}} dz = 0 \rightarrow {\color{red}F}={\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v A {\color{magenta}\phi}
 		\end{equation}
@@
 To simplify the dynamics of the system, it is assumed that ${\color{red}F}={\color{red}F}(t)$ is a control variable and affects the whole system instantaneously.
-This assumption allows for finding the velocity profile that satisfies mass continuity based on ${\color{red}F}(t)$, ${\color{magenta}\phi}(z)$, and ${\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))$.
+This assumption allows for finding the velocity profile that satisfies mass continuity based on ${\color{red}F}(t)$, ${\color{magenta}\phi}(z)$, and ${\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))$.
 
@@
 	\begin{equation}
-		v = \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) A {\color{magenta}\phi}} 
+		v = \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) A {\color{magenta}\phi}} 
 	\end{equation}
@@
 
-	The fluid density ${\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be obtained from an equation of state if temperature and the thermodynamic pressure (assumed ${\color{red}P}(t)$ to be constant along ${\color{blue}z}$ due to the low-Mach number condition) are known.
+	The fluid density ${\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))$ can be obtained from an equation of state if temperature and the thermodynamic pressure (assumed ${\color{blue}P}(t)$ to be constant along ${\color{blue}z}$ due to the low-Mach number condition) are known.
 The variation in density may be caused by the fluid accumulation in the system (equivalent to pressure change), which occurs instantaneously along ${\color{blue}z}$ or by a temperature change.
@@
 		\begin{equation}
-			u = v {\color{magenta}\phi} = \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) A }
+			u = v {\color{magenta}\phi} = \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) A }
 		\end{equation}
@@
 ${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term.
-${\color{red}F}(t)$ is the mass flow rate, ${\color{red}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient, and $u$ is the superficial velocity.
+${\color{red}F}(t)$ is the mass flow rate, ${\color{blue}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))$ is the fluid density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient, and $u$ is the superficial velocity.
 
@@
 				\begin{equation} \label{Model_kinetic_basic}
-					{\color{blue}r_e}(t,z) = \cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} }\left({\color{blue}c_s}(t,z) - {\color{blue}c_P^*}(t,z) \right)
+					{\color{blue}r_e}(t,z) = \cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{blue}P}(t))}{{\color{magenta} \mu l^2} }\left({\color{blue}c_s}(t,z) - {\color{blue}c_P^*}(t,z) \right)
 			\end{equation} }
@@
 				\begin{align} \label{Linear_equilibirum}
-					{\color{blue}c}(t,z) &= {\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t)) \allowbreak {\color{blue}q^*}(t,z)
+					{\color{blue}c}(t,z) &= {\color{orange}k_p}({\color{blue}T}(t,z),{\color{blue}P}(t)) \allowbreak {\color{blue}q^*}(t,z)
 			\end{align} }
 
-			The volumetric partition coefficient ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
-According to \citet{Spiro2007}, the term ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ can be expressed as the function of mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$.
+			The volumetric partition coefficient ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{blue}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
+According to \citet{Spiro2007}, the term ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{blue}P}(t))$ can be expressed as the function of mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$.
 
@@
 				\begin{align}
-					{\color{orange}k_m}({\color{blue}T}(t,z)) = \cfrac{{\color{orange}k_p}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{magenta}\rho_s}}{{\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}
+					{\color{orange}k_m}({\color{blue}T}(t,z)) = \cfrac{{\color{orange}k_p}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{magenta}\rho_s}}{{\color{orange}\rho}({\color{blue}T}(t,z),{\color{blue}P}(t))}
 			\end{align} }
@@
 					\label{Model_kinetic_no_sat}
-					{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} }\left({\color{blue}c_s}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
+					{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{blue}P}(t))}{{\color{magenta} \mu l^2} }\left({\color{blue}c_s}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))}  {\color{blue}c_f}(t,z) \right)
 			\end{equation} }
@@
 The pseudo-homogenous phase is assumed to flow only in the axial direction.
-The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ because the solid phase is stationary.
+The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{blue}P}(t))$ because the solid phase is stationary.
 Therefore, this factor can be understood as the fraction of the fluid's total heat through convection.
@@
 						\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} &= 
-						\underbrace{ -\cfrac{{\color{red}F}(t) {\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))}{{\color{magenta}A} 	[(1-{\color{magenta}\epsilon}){\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{orange}C_p} ({\color{blue}T}(t,z),{\color{red}P}(t)) + {\color{magenta} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}}  }_{\text{Convection}} + \\
-						& + \underbrace{ {\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{red}P}(t)) \cfrac{\partial^2 {\color{blue}T}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusion}}
+						\underbrace{ -\cfrac{{\color{red}F}(t) {\color{orange}C_p}({\color{blue}T}(t,z),{\color{blue}P}(t))}{{\color{magenta}A} 	[(1-{\color{magenta}\epsilon}){\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{orange}C_p} ({\color{blue}T}(t,z),{\color{blue}P}(t)) + {\color{magenta} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}}  }_{\text{Convection}} + \\
+						& + \underbrace{ {\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{blue}P}(t)) \cfrac{\partial^2 {\color{blue}T}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusion}}
 					\end{split}
@@
 
-		where $ {\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient, ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{red}P}(t))$ is the fluid's specific heat, ${\color{magenta}C_{ps}}$ is the specific heat of the solid phase, ${\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{red}F}(t))$ is the axial heat diffusion coefficient.
+		where $ {\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient, ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{blue}P}(t))$ is the fluid's specific heat, ${\color{magenta}C_{ps}}$ is the specific heat of the solid phase, ${\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{red}F}(t))$ is the axial heat diffusion coefficient.
 
@@
 			\begin{align}
-				&\cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{blue}e}(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) A_f v {\color{blue}e}(t,z) \right)}{\partial {\color{blue}z}} \nonumber \\
-				&= -{\color{red}P}(t)\cfrac{\left( A_f v \right)}{\partial {\color{blue}z}} + \cfrac{\partial}{\partial {\color{blue}z}} \left( \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}} \right)
+				&\cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{blue}e}(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) A_f v {\color{blue}e}(t,z) \right)}{\partial {\color{blue}z}} \nonumber \\
+				&= -{\color{blue}P}(t)\cfrac{\left( A_f v \right)}{\partial {\color{blue}z}} + \cfrac{\partial}{\partial {\color{blue}z}} \left( \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}} \right)
 			\end{align}
@@
 				\begin{equation}
-					d{\color{blue}e}(t,z)=C_vd{\color{blue}T}-\left[{\color{red}P}(t)-{\color{blue}T}(t,z)\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}(t,z)}\right)_{v_m}\right]dv_m
+					d{\color{blue}e}(t,z)=C_vd{\color{blue}T}-\left[{\color{blue}P}(t)-{\color{blue}T}(t,z)\left(\cfrac{\partial {\color{blue}P}(t)}{\partial {\color{blue}T}(t,z)}\right)_{v_m}\right]dv_m
 					\label{EQ: internal_energy_def}
@@
 			\begin{equation}
-				{\color{blue}e}(t,z)={\color{blue}e}({\color{blue}T}(t,z),{\color{red}P}(t),{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)))=e( {\color{blue}T}(t,z),{\color{red}P}(t), \rho({\color{blue}T}(t,z),{\color{red}P}(t)) )
+				{\color{blue}e}(t,z)={\color{blue}e}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)))=e( {\color{blue}T}(t,z),{\color{blue}P}(t), \rho({\color{blue}T}(t,z),{\color{blue}P}(t)) )
 			\end{equation}
@@
 
-			Another way to express the energy equation is to introduce enthalpy ${\color{blue}h}(t,z) = {\color{blue}e}(t,z) + {\color{red}P}(t) / \rho$.
+			Another way to express the energy equation is to introduce enthalpy ${\color{blue}h}(t,z) = {\color{blue}e}(t,z) + {\color{blue}P}(t) / \rho$.
 By introducing the definition of enthalpy, the energy equation becomes
@@
 			{\footnotesize
-				\begin{align}
-					&\cfrac{\partial \left({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{blue}h}(t,z) A_f\right)}{\partial t} - \cfrac{\partial \left({\color{red}P}(t) A_f\right)}{\partial t} \nonumber \\
-					&+ \cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{blue}h}(t,z) A_f v \right)}{\partial {\color{blue}z}} - \cfrac{\partial}{\partial {\color{blue}z}} \left( k \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}} \right)
+				\begin{align} \label{EQ:Enthalpy_equation}
+					&\cfrac{\partial \left({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{blue}h}(t,z) A_f\right)}{\partial t} - \cfrac{\partial \left({\color{blue}P}(t) A_f\right)}{\partial t} \nonumber \\
+					&+ \cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{blue}h}(t,z) A_f v \right)}{\partial {\color{blue}z}} - \cfrac{\partial}{\partial {\color{blue}z}} \left( k \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}} \right)
 				\end{align}
@@
 
-			The main advantage of this formulation is the presence of term $\partial {\color{red}P}(t) / \partial t $, which allows it to directly affect the system through the change of thermodynamic pressure (which is a control variable).
+			The main advantage of this formulation is the presence of term $\partial {\color{blue}P}(t) / \partial t $, which allows it to directly affect the system through the change of thermodynamic pressure (which is a control variable).
 If an equation of state is known, the temperature can to be recovered from the enthalpy.
@@
 				\begin{equation}
-					{\color{blue}h}(t,z)=h({\color{blue}T}(t,z),{\color{red}P}(t),{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)))=h( {\color{blue}T}(t,z),{\color{red}P}(t), \rho({\color{blue}T}(t,z),{\color{red}P}(t)) )
+					{\color{blue}h}(t,z)=h({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)))=h( {\color{blue}T}(t,z),{\color{blue}P}(t), \rho({\color{blue}T}(t,z),{\color{blue}P}(t)) )
 					\label{EQ:Enthalpy_root}
@@
 
+		\subsubsection{Pressure term} \label{CH: Pressure}
+
+		The pressure term in the energy equation, given by Equation \ref{EQ:Enthalpy_equation}, describes the change of the thermodynamic pressure with respect to time.
+As explained in Chapters \ref{CH: Gouverning equations} and \ref{CH:Low_Mach_chapter}, at low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound.
+Under such conditions, the term $\partial P/\partial t$ can be approximated by an ordinary differential equation, which describes the instantaneous change of pressure in the system.
+The pressure in the system is considered a state variable, while the pressure in the new time-step is considered a control variable.
+
+		{\footnotesize
+			\begin{equation}
+				\frac{\partial {\color{blue}P}(t)}{\partial t} \approx \frac{{\color{blue}P}(t) - {\color{red}P_{in}}(t) }{\Delta t}
+		\end{equation}}
+
+		Such a simplified equation takes into account the pressure change in the energy balance, but the dynamics are simplified and do not consider the effects of pressure losses.
+In a real system, the pressure change dynamics would depend on the pump used in the system, as well as the back-pressure regulator used to control the outlet valve.
+
 		\subsubsection{Extraction yield} \label{CH: Yield}
@@
 %				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
-				y(t) &= \int_{t_0}^{t_f} \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))} {\color{blue}c_f}(t,z) \biggr\rvert_{z=L} dt \\
+				y(t) &= \int_{t_0}^{t_f} \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))} {\color{blue}c_f}(t,z) \biggr\rvert_{z=L} dt \\
 %				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
-				\cfrac{dy}{dt} &= \qquad \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t))} {\color{blue}c_f}(t,z) \biggr\rvert_{z=L} 
+				\cfrac{dy}{dt} &= \qquad \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))} {\color{blue}c_f}(t,z) \biggr\rvert_{z=L} 
                 \label{Model_measurment_2}
@@
 			In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases (${\color{blue}c_f}(t,z)$ and ${\color{blue}c_s}(t,z)$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{blue}h}(t,z)$).
-The controllable input variables are the mass flow-rate and temperature of the solvent in the feed ($F_\text{in}(t) = {\color{red}P}(t)$ and $h_\text{in}(t) = {\color{red}h}(t,z=0)$, respectively) and the pressure in the extractor ($P(t,z) ={\color{red}P}(t)$).
+The controllable input variables are the mass flow-rate and temperature of the solvent in the feed ($F_\text{in}(t) = {\color{blue}P}(t)$ and $h_\text{in}(t) = {\color{red}h}(t,z=0)$, respectively) and the pressure in the extractor ($P(t,z) ={\color{blue}P}(t)$).
 We extend the system state-space by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator ($Y(t)$).

### 2023-05-26 SFE-article/Article_Model_Parameters.tex
08.05
12.05
26.05

@@
 Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
-A system of partial differential equations, $G(t,x,\dot{x},\Theta,u)=0$ is considered, where $x$ denotes the state variables, $\Theta$ represents the parameters, and $u$ is the control variables.
-The system $G(t,x,\dot{x},\Theta,u)=0$ describe the supercritical extraction process, which involves a partially filled extractor with a fixed bed that operates under constant conditions.
+The aim of this study was to investigate the supercritical extraction process of the caraway oil from caraway seeds from a partially filled extractor with a fixed bed that was operated under multiple constant operating conditions.
+The dataset collected from the experiments consists of four experiments conducted at different operating conditions: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar.
+To describe the fluid-solid extraction process with $CO_2$ as a solvent, a distributed-parameter model is used.
 It is assumed that the flow is uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
 To model this two-dimensional case, the concept of quasi-one-dimensional flow is applied.
-To describe the fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent, we use the distributed-parameter model $G(t,x,\dot{x},\Theta,u)=0$ based on \citet{Reverchon1996}.
 This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, saturation concentration, and an initial state estimate.
 These parameters are estimated from the Peng-Robinson equation of state and by applying the maximum likelihood estimation method on yield data under the normal error assumption.
-The dataset comes from four experiments conducted at different operating conditions: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar.
 
@@
 \begin{keywords}
-Supercritical extraction \sep Parameter estimation \sep Mathematical modeling
+Supercritical extraction \sep Parameter estimation \sep Mathematical modelling
 \end{keywords}
@@
 {\footnotesize
-	\begin{equation*}
+	\begin{equation} \label{EQ: Pressure_Velocity}
 		\cfrac{d v}{d \rho_f} = - \cfrac{d v}{dP} \cfrac{d P}{d \rho_f} = -\cfrac{1}{\rho v} \cfrac{dP}{d\rho_f} = -\cfrac{v}{\rho_f}
-	\end{equation*}
+	\end{equation}
 }
@@
 
+\clearpage
+\subsection{Solution of the parameter estimation starting from another initial guess} \label{CH: Profiles_2}
+\subfile{Sections/Parameter_estimation_solution_from_another_IG}
+
 \iffalse

### 2023-05-26 SFE-article/Sections/Thermo_imp.tex
26.05

@@
 	\begin{figure*}[H]
-		\begin{subfigure}[b]{0.95\textwidth}
+		\begin{subfigure}[b]{0.31\textwidth}
 			\centering
-			\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
+			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
 			\caption{The compressibility factor based on the Peng-Robinson equation of state}
@@
 		\hfill
-		\begin{subfigure}[b]{0.95\textwidth}
+		\begin{subfigure}[b]{0.31\textwidth}
 			\centering
-			\includegraphics[trim = 2.9cm 7cm 3cm 7cm,clip,width=\textwidth]{Figures/RHO.pdf}	
+			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/RHO.pdf}	
 			\caption{The fluid density based on the Peng-Robinson equation of state}
@@
 		\hfill
-		\begin{subfigure}[b]{0.95\textwidth}
+		\begin{subfigure}[b]{0.31\textwidth}
 			\centering
-			\includegraphics[trim = 2.9cm 7cm 3.cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
+			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
 			\caption{The specific heat of the $CO_2$ based on the Peng-Robinson equation of state}

### 2023-05-26 SFE - MegaFit/main_Fitting_MegaFit.m

@@ -1,5 +1,6 @@
-startup; datetime("now");  delete(gcp('nocreate'));
-%p = Pushbullet(pushbullet_api);
+startup; datetime("now")
+delete(gcp('nocreate'));
+% %p = Pushbullet(pushbullet_api);
 
 %addpath('C:\dev\casadi-windows-matlabR2016a-v3.5.2');
 addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
@@ -13,13 +14,13 @@ DATA_set                = {'LUKE_T40_P200', 'LUKE_T50_P200', 'LUKE_T40_P300_org'
 %DATA_set                = {'LUKE_T50_P300'};
 
 which_k                 = [    8, 44, 45, 47                  ];            % Select which parameters are used for fitting
-k0                      = [ 0.01,  3,  1, 1,  80,  0.65,  0.4 ];            % Give inital value for each parameter
+k0                      = [  0.1,  3,  1, 1,  80,  0.65,   0.4];            % Give inital value for each parameter
 k_lu                    = [ [  0;  0;  0; 0;  80;     0;     0], ...
                           [  inf;inf;inf;inf;150;     1;   inf]];
 Nk                      = numel(which_k)+3;                                 % Parameters within the model + m_max, m_ratio, sigma
 
-Iteration_max           = 5;                                                % Maximum number of iterations for optimzer
-Time_max                = 1.0;                                              % Maximum time of optimization in [h]
+Iteration_max           = 50;                                               % Maximum number of iterations for optimzer
+Time_max                = 12.0;                                              % Maximum time of optimization in [h]
 
 V_Flow                  = 0.4;                                              % Volumetric flow rate l/min
 
@@ -30,7 +31,7 @@ bed                     = 0.165;                                            % Pe
 % Set time of the simulation
 PreparationTime         = 0;
 ExtractionTime          = 150;
-timeStep                = 5;                                                % Minutes
+timeStep                = 2.5;                                                % Minutes
 SamplingTime            = 5;                                                % Minutes
 
 simulationTime          = PreparationTime + ExtractionTime;
@@ -59,7 +60,8 @@ OPT_solver                  = casadi.Opti();
 
 nlp_opts                    = struct;
[…]

### 2023-05-26 SFE-article/Sections/Thermo_imp.tex
26.05

@@
 
-	\begin{figure*}[H]
+	\begin{figure}[!h]
 		\centering
-		\includegraphics[trim = 1.5cm 11.5cm 2.5cm 10.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
-		\includegraphics[trim = 1.5cm 4.0cm 2.5cm 19.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
+		\includegraphics[trim = 1.5cm 12.0cm 14cm 10.0cm,clip,width=\columnwidth]{Figures/MU.pdf}	
+		\includegraphics[trim = 1.5cm 4.0cm  14cm 19.0cm,clip,width=\columnwidth]{Figures/MU.pdf}	
 		\caption{Viscosity obtained based on different correlations } 
 		\label{fig: SFE_Properties_mu}
-	\end{figure*}
+	\end{figure}
 
@@
 		\centering
-		\includegraphics[trim = 1.5cm 2.5cm 1.5cm 2.0cm,clip,width=0.95\textwidth]{Figures/KT.pdf}	
+		\includegraphics[trim = 1.5cm 14.25cm 14cm 2.0cm,clip,width=0.49\textwidth]{Figures/KT.pdf}	
+		\includegraphics[trim = 1.5cm 2.8cm 14cm 13.75cm,clip,width=0.49\textwidth]{Figures/KT.pdf}	
 		\caption{Thermal conductivity obtained based on different correlations }

### 2023-05-26 SFE-article/Article_Model_Parameters.tex
26.05

@@
 This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow.
-
-\subsection{Low Mach number expansion} \label{CH:Low_Mach_chapter}
-%\subfile{Sections/Low_mach_number_expansion}
-\subfile{Sections/Low_mach_number_expansion_imp}
+Moreover, if the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic which leads to $\partial \rho / \partial P \approx 0$.
+In other words, the small changes in pressure due to flow velocity changes do not change the density.
+This has a secondary effect -- the speed of sound in the fluid is $\partial P/\partial \rho = \infty$ in this instance.
+So there is an infinite speed of sound, which makes the equations elliptic in nature.
+It can be deduced that at the isothermal conditions, the density in the system propagates with the same speed as pressure since they are both connected through the equation of state.
+The details of the Mach-number analysis are presented in Appendix \ref{CH:Low_Mach_chapter}.
 
@@
 \subfile{Sections/Thermodynamic_details}
+
 \subsection{Governing equations}
 \subfile{Sections/Gouverning_equation_derivation}
+
+\subsection{Low Mach number expansion} \label{CH:Low_Mach_chapter}
+%\subfile{Sections/Low_mach_number_expansion}
+\subfile{Sections/Low_mach_number_expansion_imp}
 

### 2023-05-31 SFE-article/Sections/Thermo_imp.tex

--- 2023-05-26 SFE-article/Sections/Thermo_imp.tex
@@
 			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
-			\caption{The specific heat of the $CO_2$ based on the Peng-Robinson equation of state}
+			\caption{The specific heat of $CO_2$ based on the Peng-Robinson equation of state}
 			\label{fig: SFE_Properties_CP}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.31\textwidth}
+			\centering
+			\includegraphics[trim = 0cm 0cm 0cm 0cm,clip,width=\textwidth]{Figures/Enthalpy.pdf}	
+			\caption{The enthalpy of $CO_2$ based on the Peng-Robinson equation of state (\color{red}FONT SIZE)}
+			\label{fig: SFE_Properties_h}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.31\textwidth}
+			\centering
+			\includegraphics[trim = 1.5cm 4.0cm  14cm 19.0cm,clip,width=\textwidth]{Figures/MU.pdf}
+			\caption{Thermal conductivity obtained based on Laesecke correlation}
+			\label{fig: SFE_Properties_Viscosity}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.31\textwidth}
+			\centering
+			\includegraphics[trim = 2.5cm 2.8cm 14.3cm 21.4cm,clip,width=\textwidth]{Figures/KT.pdf}	
+			\caption{Thermal conductivity obtained based on Huber correlation}
+			\label{fig: SFE_Properties_Thermal}
 		\end{subfigure}
@@
 Many correlations have been proposed following the Chapman-Enskog theory in the form of reduced density and reduced temperature, such as those developed by \citet{Fenghour1998} and \citet{Laesecke2017} from the National Institute of Standards and Technology (NIST).
-A comparison of these correlations is presented in Figure \ref{fig: SFE_Properties_mu}.
+A comparison of these correlations is presented in Figure \ref{fig: SFE_Properties_Viscosity}.
 
@@
 
-	\begin{figure*}[H]
-		\centering
-		\includegraphics[trim = 1.5cm 11.5cm 2.5cm 10.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
-		\includegraphics[trim = 1.5cm 4.0cm 2.5cm 19.0cm,clip,width=\textwidth]{Figures/MU.pdf}	
-		\caption{Viscosity obtained based on different correlations } 
-		\label{fig: SFE_Properties_mu}
-	\end{figure*}
-
-	Similarly, several correlations for thermal conductivity of $CO_2$ were compared in Figure \ref{fig: SFE_Properties_kt}.
+	Similarly, several correlations for thermal conductivity of $CO_2$ were compared in Figure \ref{fig: SFE_Properties_Thermal}.
 The presented figures show regions around the critical point where the singularity is present.
@@
 
-	\begin{figure*}[H]
-		\centering
-		\includegraphics[trim = 1.5cm 2.5cm 1.5cm 2.0cm,clip,width=0.95\textwidth]{Figures/KT.pdf}	
-		\caption{Thermal conductivity obtained based on different correlations }
-		\label{fig: SFE_Properties_kt}
-	\end{figure*}
-
 \end{document}

### 2023-06-20 SFE-article/Sections/Results.tex
20.06

@@
         \item Partition coefficient:\qquad\quad\qquad$k_m$
-        \item Internal Diffusion coefficient: \quad$D_i$
-        \item Axial Diffusion coefficient: \qquad$D_e^M$
-        \item Saturation concentration: \quad\qquad$C_{sat}$
-        \item Standard Deviation: \qquad\qquad\quad$\sigma$
+        \item Internal diffusion coefficient: \quad$D_i$
+        \item Axial diffusion coefficient: \qquad$D_e^M$
+        \item Limiting concentration: \quad\qquad$C_{lim}$
+        \item Standard deviation: \qquad\qquad\quad$\sigma$
     \end{itemize}
@@
 			\hline 
-			Parameter		&$k_m$[-] 	& $D_i$[m/s$^2$] 	& $D_e^M$[m/s$^2$]	& $C_{sat}$ [kg/m$^3$] 	& $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
+			Parameter		&$k_m$[-] 	& $D_i$[m/s$^2$] 	& $D_e^M$[m/s$^2$]	& $C_{lim}$ [kg/m$^3$] 	& $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
 			Lower bound		&0	  		& 0 	  			& 0 				&	0					& 80 		 		& 0 	   		& 0 \\ 
@@
 
-	The further spifflication of the process model can be introduced based on $C_{sat}$ results.
+	The further spifflication of the process model can be introduced based on $C_{lim}$ results.
 Values of saturation concentrations are at the level of 1e5 which is an internal upper bound of the optimizer used if $+\infty$ indicates the upper bound.
@@
 To simplify the problem, the correlations are written as functions of fluid density rather than temperature and pressure.
-Since the optimizer found that $k_m$, $m_{total}$ and $C_{sat}$ don't change with the density variations, they are assumed to be constants and not considered further.
+Since the optimizer found that $k_m$, $m_{total}$ and $C_{lim}$ don't change with the density variations, they are assumed to be constants and not considered further.
 

### 2023-06-20 SFE-article/Sections/Saturation.tex
20.06

@@
 
-	\subsubsection{Saturation Concentration}
+	\subsubsection{Concentration limit}
 
-	The above model does not take into account the saturation of fluid, which can be introduced by multiplying the gradient by a function $\gamma(c_f)$ (equation \ref{EQ: C_sat_function}).
-$\gamma(c_f)$ describe the reverse logistic function, which is equal to unity below the $c_{sat}$, the saturation concentration, and equal to zero, above the $c_{sat}$.
+	To mimic that not all solute might be obtained at specific operating conditions, the coefficient $\gamma$ is introduced to limit the available oil.
+The $\gamma(c_s)$ describe the reverse logistic function, which is equal to unity above the $c_{lim}$, the saturation concentration, and equal to zero, below the $c_{lim}$.
+The $\gamma$ parameter multiply the solute concentration term in solid phase in the concentration gradient.
+As the concentration of solute decrease, it can reach the limiting value $c_{lim}$ when the $\gamma$ goes to zero and stop the extraction from the solid.
 	The $\gamma(c_f)$ for $c_{sat}=5$ is shown on figure \ref{fig: Gamma_function}.
@@
 		\begin{equation}
-			\gamma(c_f) = \cfrac{1}{1+\exp ( -k_{sat} \left( c_f - c_{sat} \right) ) }
+			\gamma(c_s) = \cfrac{1}{1+\exp ( -k_{sat} \left( c_s - c_{lim} \right) ) }
 			\label{EQ: C_sat_function}
@@
 
-	where $k_{sat}$ is the growth rate, and it is defined as $k_{sat} = 4$.
-The growth rate corresponds for the shape of the $\gamma(c_f)$ function.
+	where $k_{lim}$ describe the curvature of the $\gamma$ function, and it is defined as $k_{lim} = 1$.
 The bigger value of the $k_{sat}$ the steeper the function is.
-In the limit when $ k_{sat}\rightarrow+\infty$ become a step function.
+In the limit when $ k_{lim}\rightarrow+\infty$ become a step function.
 If the growth rate is to high, the gradient of the $\gamma$ function become high, or goes to infinity, which might cause difficulties for a gradient-based optimizer.
@@
 					legend style={draw=none},
-					xmin = 0, xmax = 10,
+					xmin = 0, xmax = 100,
 					ymin = -0.5, ymax = 1.5,
@@
 					\addplot[
-					domain = 0:10,
+					domain = 0:100,
 					samples = 100,
@@
 					blue,
-					] { 1 / (1 + exp( 4 .* ( x - 5 ) ) ) };
-					\addplot[thick, samples=50, dashed, domain=0:1.5, black] coordinates {(5,-0.5)(5,1.5)};
+					] { 1 / (1 + exp( 1 * ( 50 - x ) ) ) };
+					\addplot[thick, samples=50, dashed, domain=0:1.5, black] coordinates {(50,-0.5)(50,1.5)};
 
-					\addlegendentry{$\gamma(c_f)$}
-					\addlegendentry{$c_{sat}$}
+					\addlegendentry{$\gamma(c_s)$}
+					\addlegendentry{$c_{lim}$}
 				\end{axis}
@@
 			\end{tikzpicture}
-			\caption{$\gamma(c_f)$ function under assumption of $c_{sat}=5 [kg/m^3]$}
+			\caption{$\gamma(c_s)$ function under assumption of $c_{lim}=50~[kg/m^3]$}
 			\label{fig: Gamma_function}
@@
 			\label{Model_kinetic}
-				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} } \gamma(c_f) \left({\color{blue}c_s}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
+				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} } \left({\color{blue}c_s}(t,z) \gamma(c_s) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
 		\end{equation} }

### 2023-06-20 SFE-article/Sections/Thermo_imp.tex
20.06

@@
 	Supercritical $CO_2$'s thermodynamic properties, such as density, the local speed of sound, and specific heat capacity, vary significantly with slight changes in temperature and pressure due to real gas effects.
-The Peng-Robinson equation of state (P-R EOS) is used to calculate the thermodynamic properties by accounting for these real gas effects.
+The Peng-Robinson equation of state (P-R EOS) is used to calculate the thermodynamic properties by accounting for these real gas effects are presented Appendix \ref{subsubsec: Equation of state}.
 The P-R EOS belongs to a specific class of thermodynamic models for modelling the pressure of a gas as a function of temperature and density.
-It can be written as a cubic function of the molar volume (of the density).
-Detail information about Peng-Robinson equation of state can be found in the work of \citet{Peng1976}, \citet{Elliott2011} or \citet{Pratt2001}.
-The P-R EOS is presented by Equation \ref{EQ: PR}
 
-	{\footnotesize
-		\begin{equation}
-			P = \cfrac{RT}{V_m - b} - \cfrac{a\alpha}{V_m^2 + 2bV_m - b^2}
-			\label{EQ: PR}
-		\end{equation}
-	}
-
-	The parameters $a, b, \alpha$ are parameters defined as presented in the Appendix \ref{subsubsec: Equation of state}.
+	To determine the thermodynamic properties of a real gas, it is necessary to evaluate the departure function of the chosen equation of state for that property.
+As explained by \citet{Elliott2011}, the departure function is the difference between the actual value of a thermodynamic property of a real gas and its value if the gas were ideal under the same temperature and pressure conditions.
+The ideal gas serves as a reference state to which the properties of real gases are compared.
+The departure function is a measure of the extent to which a real gas deviates from ideal gas behaviour.
+The departure functions allow for the accurate calculation of thermodynamic properties for real gases.
+%(10.1007/s10494-017-9872-4)
 
@@
 As presented in Figure \ref{fig: SFE_Properties_Compressibility}, the compressibility factor obtained from the Peng-Robinson equation of state varies strongly depending on the operating conditions.
-The compressibility factor can be obtained by solving the polynomial form of the P-R EOS given by Equation \ref{EQ: PR_polynomial}.
-
-	{\footnotesize
-		\begin{equation}
-			Z^3 - (1-B)Z^2+(A-2B-3B^2)Z -(AB-B^2-B^3) = 0
-			\label{EQ: PR_polynomial}
-		\end{equation}
-	}
-
-	where $A$ and $B$ are parameters as defined in the Appendix \ref{subsubsec: Equation of state}.
-The roots of the polynomial can be found iteratively or by the Cardano formula.
-In a one-phase region, the fluid is described by one real root corresponding to the gas, liquid or supercritical phase.
-The gas-liquid mixture is present in the two-phase region, and two roots are found.
-The biggest root is assigned to the gas phase, and the smallest root corresponds to the liquid phase.
 
@@
 The density calculations are based on the compressibility factor and its value depends on the operating conditions.
-The fluid's properties near the critical point are unique and combine gas-like and liquid-like properties.
+The fluid properties near the critical point are unique and combine gas-like and liquid-like properties.
 The details of calculations are explained in the Appendix \ref{subsubsec: Fluid density}.
@@
 Beyond the critical point, there is no divergence, but rather a smooth peak in the heat capacity; the highest point of this peak identifies the Widom line (as discussed by \citet{Simeoni2010} and \citet{Banuti2019}).
-
-	To determine the thermodynamic properties of a real gas, it is necessary to evaluate the departure function of the chosen equation of state for that property.
-As explained by \citet{Elliott2011}, the departure function is the difference between the actual value of a thermodynamic property of a real gas and its value if the gas were ideal under the same temperature and pressure conditions.
-The ideal gas serves as a reference state to which the properties of real gases are compared.
-The departure function is a measure of the extent to which a real gas deviates from ideal gas behaviour.
-The departure functions allow for the accurate calculation of thermodynamic properties for real gases.
-%(10.1007/s10494-017-9872-4)
 
@@
 However, the Chapman-Enskog theory was developed for rigid spherical molecules and modifications are required to apply it to real gases.
-Many correlations have been proposed following the Chapman-Enskog theory in the form of reduced density and reduced temperature, such as those developed by \citet{Fenghour1998} and \citet{Laesecke2017} from the National Institute of Standards and Technology (NIST).
-A comparison of these correlations is presented in Figure \ref{fig: SFE_Properties_Viscosity}.
+Many correlations have been proposed following the Chapman-Enskog theory in the form of reduced density and reduced temperature, such as those developed by \citet{Fenghour1998}, and \citet{Laesecke2017} from the National Institute of Standards and Technology (NIST).
+The correlation of \citet{Laesecke2017} is presented in Figure \ref{fig: SFE_Properties_Viscosity}.
 
@@
 
-	Similarly, several correlations for thermal conductivity of $CO_2$ were compared in Figure \ref{fig: SFE_Properties_Thermal}.
+%	Similarly, several correlations for thermal conductivity of $CO_2$ were compared in Figure \ref{fig: SFE_Properties_Thermal}.
 The presented figures show regions around the critical point where the singularity is present.
@@
 
+	Similarly, the NIST developed the correlation, which describe the behaviour of thermal diffusivity of $CO_2$.
+The work of \citet{Huber2016} captures the singular behaviour of thermal conductivity around the critical point.
+The correlation is applicable for the temperature range from the triple point to 1100 $K$ and pressures up to 200 $MPa$.
+Figure \ref{fig: SFE_Properties_Thermal}.
+The presented figure show regions around the critical point where the singularity is present.
+
 \end{document}

### 2023-06-20 SFE-article/Sections/Thermodynamic_details.tex
20.06

@@
 	\subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}
-	In this study, the influence of real gas effects are introduced through ${\color{red}P}(t) {\color{orange}v_m}[T(t,z),P(t)] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, where ${\color{orange}v_m}$ represents the molar volume of $\text{CO}_2$, ${\color{orange}Z}$ denotes its compressibility factor, and $R$ is the universal gas constant.
+	In this study, the influence of real gas effects are introduced through ${\color{red}P}(t) {\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t)) = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, where ${\color{orange}v_m}$ represents the molar volume of $CO_2$, ${\color{orange}Z}$ denotes its compressibility factor, and $R$ is the universal gas constant.
 The main advantage of using compressibility in calculations is to express it as an explicit function of temperature and pressure.
-This is possible when $Z$ is obtained as one of the physically meaningful roots of a polynomial equation, such as the Van der Waals, Peng-Robinson, or Redlich-Kwong equation of state.
-In this study, the Peng-Robinson equation of state (\citet{Peng1976}) was selected.
+It can be written as a cubic function of the molar volume (of the density).
+Detail information about Peng-Robinson equation of state can be found in the work of \citet{Peng1976}, \citet{Elliott2011} or \citet{Pratt2001}.
+The P-R EOS is presented by Equation \ref{EQ: PR}.
 
-	In the Peng-Robinson equation of state, the compressibility ${\color{orange}\overline{Z}}[{\color{blue}T}(t,z), {\color{red}P}(t)]$ solves the third-order polynomial equation shown in Equation \ref{eq: Compressibility}.
+	{\footnotesize
+		\begin{equation}
+			{\color{red}P}(t) = \cfrac{{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t)) - {\color{magenta}b}} - \cfrac{{\color{magenta}a^c}{\color{orange}\alpha}\left({\color{blue}T}(t,z)\right)}{{\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t))^2 + 2{\color{magenta}b}{\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t)) - {\color{magenta}b}^2}
+			\label{EQ: PR}
+		\end{equation}
+	}
+
+	The Equation \ref{EQ: PR} can be also written as the third-order polynomial equation shown in Equation \ref{eq: Compressibility}.
 Numerical methods such as Newton-Raphson can be used to solve the polynomial equation, but the Cardano formula is preferred as it yields an analytical solution.
@@
 		\begin{align} 
-			{\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]	& = \dfrac{{\color{orange}\alpha}\left[T\left(t,z\right)\right]{\color{magenta}a^c}{\color{red}P}(t)}{{\color{magenta}R}^2{\color{blue}T}^2(t,z)};													\label{eq: PR_A}\\
+			{\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]	& = \dfrac{{\color{orange}\alpha}\left[{\color{blue}T}\left(t,z\right)\right]{\color{magenta}a^c}{\color{red}P}(t)}{{\color{magenta}R}^2{\color{blue}T}^2(t,z)};													\label{eq: PR_A}\\
 			{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]	& = \dfrac{{\color{magenta}b}{\color{red}P}(t)}{{\color{magenta}R}{\color{blue}T}(t,z)}	\label{eq: PR_B}.
@@
 	The quantity ${\color{orange}\alpha}\left[{\color{blue}T}\left(t,z\right)\right]$ is a dimensionless correction term that depends on the temperature ${\color{blue}T}\left(t,z\right)$ and a constant ${\color{magenta}\kappa}$.
-The constant ${\color{magenta}\kappa}$ is given by the formula ${\color{magenta}\kappa} = 0.37464 + 1.54226 {\color{magenta}\omega} - 0.26992 {\color{magenta}\omega^2}$, where ${\color{magenta}\omega}$ is the acentric factor of $\text{CO}_2$ molecules and is equal to 0.239.
+The constant ${\color{magenta}\kappa}$ is given by the formula ${\color{magenta}\kappa} = 0.37464 + 1.54226 {\color{magenta}\omega} - 0.26992 {\color{magenta}\omega^2}$, where ${\color{magenta}\omega}$ is the acentric factor of $CO_2$ molecules and is equal to 0.239.
 
 %	Using the physical constants $\varphi_{Z} = \left(R,T^c_{CO_2},P^c{CO_2},\kappa{CO_2}\right)$, we can represent the compressibility ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi{Z}\right]$ as a function of temperature and pressure with their complete set of functional dependencies and parameters.
+
+	%	The compressibility factor can be obtained by solving the polynomial form of the P-R EOS given by Equation \ref{EQ: PR_polynomial}.
+
+	%	{\footnotesize
+		%		\begin{equation}
+			%			Z^3 - (1-B)Z^2+(A-2B-3B^2)Z -(AB-B^2-B^3) = 0
+			%			\label{EQ: PR_polynomial}
+			%		\end{equation}
+		%	}
+	%	
+	In a one-phase region, the fluid is described by one real root corresponding to the gas, liquid or supercritical phase.
+The gas-liquid mixture is present in the two-phase region, and two roots are found.
+The biggest root is assigned to the gas phase, and the smallest root corresponds to the liquid phase.
 
@@
 This means that the density of the fluid depends on both space and time, due to its dependence on temperature and pressure.
-%	, and it can be expressed in terms of a set of physical constants, denoted by $\varphi{\rho_\text{F}} = \left({\color{magenta}R}, {\color{magenta}M_{CO_2}}, {\color{magenta}T^c{CO_2}}, {\color{magenta}P^c{CO_2}}, {\color{magenta}\omega{\text{CO}_2}}\right)$.
+%	, and it can be expressed in terms of a set of physical constants, denoted by $\varphi{\rho_\text{F}} = \left({\color{magenta}R}, {\color{magenta}M_{CO_2}}, {\color{magenta}T^c{CO_2}}, {\color{magenta}P^c{CO_2}}, {\color{magenta}\omega{CO_2}}\right)$.
 
@@
 	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}.
-The main steps in the derivation of ${\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are presented below:
+The main steps in the derivation of ${\color{orange}C^{CO_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are presented below:
 
@@
 	\begin{subequations}\begin{align}
-			{\color{orange}C^{\text{CO}_2}_v}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] & = {\color{orange}C_v^{\text{I}}}\left[{\color{blue}T}(t,z),P(t)\right] + {\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] \label{eq: Cv_CO2}; \\
-			{\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] & = \underbrace{{\color{orange}C_p^{\text{I}}}\left[{\color{blue}T}(t,z),P(t)\right]}_{\text{Eq.
+			{\color{orange}C^{CO_2}_v}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] & = {\color{orange}C_v^{\text{I}}}\left[{\color{blue}T}(t,z),P(t)\right] + {\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] \label{eq: Cv_CO2}; \\
+			{\color{orange}C^{CO_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] & = \underbrace{{\color{orange}C_p^{\text{I}}}\left[{\color{blue}T}(t,z),P(t)\right]}_{\text{Eq.
 } \eqref{eq: Cp_I}} + \underbrace{{\color{orange}C_p^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}_{\text{Eq.
@@
 
-	${\color{orange}C^{\text{CO}_2}_v}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}C^{\text{CO}_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are the specific heat of $\text{CO}_2$ at constant volume and pressure, respectively.
+	${\color{orange}C^{CO_2}_v}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}C^{CO_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are the specific heat of $CO_2$ at constant volume and pressure, respectively.
 ${\color{orange}C_v^{\text{I}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}C_p^{\text{I}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$, with ${\color{orange}C_p^{\text{I}}}({\color{blue}T}(t,z)) - {\color{orange}C_v^{\text{I}}}({\color{blue}T}(t,z)) = {\color{magenta}R}$, are the specific heat of an ideal gas at constant volume and pressure.

### 2023-06-20 SFE-article/Sections/introduction_imp.tex
26.05
20.06

@@
 
-	In recent years, the use of solvents for extracting natural substances from solid materials and liquids has been an area of significant interest for research and development.
-Supercritical fluids, which exhibit both gas- and liquid-like properties, have proven particularly useful in extraction processes due to their pressure-dependent dissolving power.
-Supercritical $CO_2$, in particular, is attractive because it is nontoxic, non-flammable, and non-corrosive.
+	The present study focuses on extracting essential oil from the caraway (Carum carvi L.) seeds with supercritical fluid extraction and the modelling of that process.
+Caraway is a biennial plant belonging to the Apiaceae family.
+It is widespread in Asia, Europe, and North Africa.
+The essential oil obtained from caraway finds its potential application as a fragrance ingredient in perfumes, liquors, and toothpaste.
+As presented by \citet{Hromis2015}, the dried caraway contains nearly~2.8–5\% essential oil, from which the main compounds are carvone, pinene, camphene, limonene, and carveol.
+
+	The economic feasibility of the process is crucial when selecting appropriate technology.
+Conventional processes are frequently used for essential oil extraction, such as distillation and organic solvent extraction.
+The distillation process is carried out at a high temperature, which causes thermal degradation of thermolabile compounds.
+Considering that, alternatives techniques like supercritical fluid extraction gained popularity for extraction.
+Supercritical $CO_2$, in particular, is attractive due to its unique properties such as inflammable, non-toxic, low critical temperature and non-corrosive.
 Furthermore, its critical point is relatively low compared to other fluids, making it a suitable alternative to traditional extraction techniques.
+The supercritical fluids exhibit both gas- and liquid-like properties so pressure-depended dissolving power can be adjusted by operating conditions.
 
@@
 		\centering
-		\includegraphics[width=0.95\columnwidth]{Figures/SFE_PFD_cropped.pdf}
-		\caption{Process flow diagram ({\color{red}Font size}) }
+		\includegraphics[trim = 5cm 12cm 8cm 6cm, clip,width=\columnwidth]{Figures/PFD.pdf}
+		\caption{Process flow diagram}
 		\label{fig: SFE_drawing}
@@
 	The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties.
-Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations, which are derived under the assumption of Low-Mach number in Chapter \ref{CH:Low_Mach_chapter}.
+Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations, which are derived under the assumption of Low-Mach number.
 The simplified balance equations are combined with the extraction kinetic equation to develop the process model in Chapter \ref{CH: Extraction_model}.

### 2023-06-20 SFE - MegaFit/main_Fitting_MegaFit.m

@@ -13,8 +13,8 @@ Parameters_sym          = MX(cell2mat(Parameters));
 %% Create the solver
 OPT_solver                  = casadi.Opti();
 
-Iteration_max               = 0;                                            % Maximum number of iterations for optimzer
-Time_max                    = 4.0;                                          % Maximum time of optimization in [h]
+Iteration_max               = 3000;                                          % Maximum number of iterations for optimzer
+Time_max                    = 72.0;                                          % Maximum time of optimization in [h]
 
 nlp_opts                    = struct;
 nlp_opts.ipopt.max_iter     = Iteration_max;
@@ -23,16 +23,16 @@ nlp_opts.ipopt.max_cpu_time = Time_max*3600;
 ocp_opts                    = {'nlp_opts', nlp_opts};
 OPT_solver.solver(             'ipopt'   , nlp_opts)
 
-which_k                 = [     8, 44, 45,          ];                      % Select which parameters are used for fitting
-k0                      = [     1,  3,  1, 0.8,  0.4];                      % Give inital value for each parameter
-k_lu                    = [ [0.05;  0;  0;   0;    0], ...
-    [  100; inf;inf;   1; inf]];
+which_k                 = [     8, 44, 45, 47            ];                      % Select which parameters are used for fitting
+k0                      = [     1,  3,  1, 0.9, 0.7,  0.2];                      % Give inital value for each parameter
+k_lu                    = [ [0.05;  0;  0;   0;   0;    0], ...
+                          [  inf; inf;inf;   1;   1; inf]];
 Nk                      = numel(which_k)+2;                                 % Parameters within the model + (m_max), m_ratio, sigma
 
-m_total                 = 90;
+%m_total                 = 90;
 
-%sat                     = OPT_solver.variable(2);
-%                          OPT_solver.subject_to( 0 <= sat <= 1 );
+m_total                 = OPT_solver.variable(1);
+                          OPT_solver.subject_to( 80 <= m_total <= 150 );
 
 %% Load paramters
 DATA_set                = {'LUKE_T40_P200', 'LUKE_T50_P200', 'LUKE_T40_P300_org', 'LUKE_T50_P300_org'};
[…]

### 2023-06-20 SFE - MegaFit/modelSFE.m

@@ -24,7 +24,7 @@ function xdot = modelSFE(x, p, mask, dt)
 
     Di            =     parameters{44};      Di = Di * 1e-14;
     Dx            =     parameters{45};      Dx = Dx * 1e-6;
-    %C_SAT         =     parameters{47};
+    C_SAT         =     parameters{47};
 
     nstages_index =     numel(mask);
     
@@ -57,8 +57,8 @@ function xdot = modelSFE(x, p, mask, dt)
     KRHOCP        =     kRHOcp_Comp(     TEMP, PRESSURE, Z, RHO, CP, epsi.*mask, parameters);
 
     %% Saturation
-    %Colid_percentage_left = 1 - (SOLID./C0solid);
-    Sat_coe       =     1;%Saturation_Concentration(Colid_percentage_left, C_SAT); % Inverse logistic is used to control saturation. Close to saturation point, the Sat_coe goes to zero.
+    Colid_percentage_left = 1 - (SOLID./C0solid);
+    Sat_coe       =     Saturation_Concentration(Colid_percentage_left, C_SAT, km); % Inverse logistic is used to control saturation. Close to saturation point, the Sat_coe goes to zero.
 
     %% BC
     %Cf_0          =     if_else(F_u == 0, FLUID(1), 0);
@@ -97,20 +97,22 @@ function xdot = modelSFE(x, p, mask, dt)
 
     dPdt          = backward_diff_1_order(P_u, PRESSURE, [], dt)*1e2;
    
+    re = (1 ./ mi ./ lp2 .* Di)  .* ( SOLID .* Sat_coe - FLUID );
+
     %%
 
     xdot = [
     
     %--------------------------------------------------------------------
     % Concentration of extract in fluid phase | 0
-   - 1            ./  ( 1 - epsi .* mask ) .* d_cons_CF_dz                                                                     + ...
-    Dx            ./  ( 1 - epsi .* mask ) .* d2Cfdz2                                                                          + ...
-    (epsi.*mask)  ./  ( 1 - epsi .* mask ) .* (1 ./ mi ./ lp2 .* Di)  .* ( SOLID .* Sat_coe - FLUID ./ km ) ;
+   - 1            ./  ( 1 - epsi .* mask ) .* d_cons_CF_dz   + ...
+    Dx            ./  ( 1 - epsi .* mask ) .* d2Cfdz2        + ...
+    (epsi.*mask)  ./  ( 1 - epsi .* mask ) .* re;
     %zeros(nstages_index,1);
 
[…]

### 2023-06-21 SFE-article/Article_Model_Parameters.tex
20.06
21.06

@@
 To describe the fluid-solid extraction process with $CO_2$ as a solvent, a distributed-parameter model is used.
+To reduce the number of spatial dimensions, the concept of quasi-one-dimensional flow is applied.
 It is assumed that the flow is uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
-To model this two-dimensional case, the concept of quasi-one-dimensional flow is applied.
 This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, saturation concentration, and an initial state estimate.
@@
 \subsection{Governing equations} \label{CH:Governing_equations_chapter}
-The governing equation for a quasi-one-dimensional compressible flow in Cartesian coordinates can be found in the Appendix \ref{CH: Gouverning equations} and in the work of \citet{Anderson1995}.
+The governing equation \footnote{For the sake of clarity of the process model, different colors have been used in the equations to indicate: 
+	{\color{red}control variables},
+	{\color{blue}state variables},
+	{\color{orange}variables} and
+	{\color{magenta}parameters}.} for a quasi-one-dimensional compressible flow in Cartesian coordinates can be found in the Appendix \ref{CH: Gouverning equations} and in the work of \citet{Anderson1995}.
 Quasi-one-dimensional flow is a fluid flow characterized by the assumption that the flow properties remain uniform across any given cross-section of the flow.
@@
 		\label{EQ: CompressibleEuler_1}
-		\cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
-		\cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \label{EQ: CompressibleEuler_2} \\
-		\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T}{\partial z} \right)
+		\cfrac{\partial \left( {\color{orange}\rho_f} {\color{magenta}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{orange}\rho_f} {\color{magenta}A_f}(z) v \right)}{\partial z} &= 0 \\
+		\cfrac{\partial \left( {\color{orange}\rho_f} v {\color{magenta}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{orange}\rho_f} {\color{magenta}A_f}(z) v^2 \right)}{\partial z} &= -{\color{magenta}A_f}(z) \cfrac{\partial {\color{blue}P}}{\partial z} \label{EQ: CompressibleEuler_2} \\
+		\cfrac{\partial \left( {\color{orange}\rho_f} {\color{blue}e} {\color{magenta}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{orange}\rho_f} {\color{magenta}A_f}(z) v {\color{blue}e}\right)}{\partial z} &= -{\color{blue}P}\cfrac{\left( {\color{magenta}A_f}(z) v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial {\color{blue}T}}{\partial z} \right)
 		\label{EQ: CompressibleEuler_3}
@@
 
-where $\rho_f$ is the density of the fluid, $A_f$ is the function which describe change of the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
+where ${\color{orange}\rho_f}$ is the density of the fluid, ${\color{magenta}A_f}(z)$ is the function which describe change of the cross-section, $v$ is the velocity, ${\color{blue}P}$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
 
@@
 			\draw (4.5,0) -- (4.5,2); 	% Bottom line
-			\node at (4,1.5) {$\rho_f$};
-			\node at (5.5,1.5) {$\rho_f+\delta\rho_f$};
+			\node at (4,1.5) {${\color{orange}\rho_f}$};
+			\node at (5.5,1.5) {${\color{orange}\rho_f}+\delta{\color{orange}\rho_f}$};
 			\node at (4,1.0) {$P$};
-			\node at (5.5,1.0) {$P+\delta P$};
+			\node at (5.5,1.0) {${\color{blue}P}+\delta {\color{blue}P}$};
 			\node at (4,0.5) {$T$};
-			\node at (5.5,0.5) {$T+\delta T$};
+			\node at (5.5,0.5) {${\color{blue}T}+\delta {\color{blue}T}$};
 			\node at (1,1.0) {$v \rightarrow$};
@@
 	\begin{align*}
-		&\rho_f \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 \\
-		&\delta P = \delta v \delta \rho_f
+		&{\color{orange}\rho_f} \delta v + v \delta {\color{orange}\rho_f} + \delta {\color{orange}\rho_f} \delta v = 0 \\
+		&\delta {\color{blue}P} = \delta v \delta {\color{orange}\rho_f}
 	\end{align*}
@@
 	\begin{equation*}
-		\lim_{\rho_f v \rightarrow 0} \rho_f \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 / \delta \rho_f \rightarrow \cfrac{d v}{d \rho_f} = - \cfrac{v}{\rho_f}
+		\lim_{{\color{orange}\rho_f} v \rightarrow 0} {\color{orange}\rho_f} \delta v + v \delta {\color{orange}\rho_f} + \delta {\color{orange}\rho_f} \delta v = 0 / \delta {\color{orange}\rho_f} \rightarrow \cfrac{d v}{d {\color{orange}\rho_f}} = - \cfrac{v}{{\color{orange}\rho_f}}
 	\end{equation*}
@@
 	\begin{equation} \label{EQ: Pressure_Velocity}
-		\cfrac{d v}{d \rho_f} = - \cfrac{d v}{dP} \cfrac{d P}{d \rho_f} = -\cfrac{1}{\rho v} \cfrac{dP}{d\rho_f} = -\cfrac{v}{\rho_f}
+		\cfrac{d v}{d {\color{orange}\rho_f}} = - \cfrac{d v}{d{\color{blue}P}} \cfrac{d P}{d {\color{orange}\rho_f}} = -\cfrac{1}{\rho v} \cfrac{d{\color{blue}P}}{d{\color{orange}\rho_f}} = -\cfrac{v}{{\color{orange}\rho_f}}
 	\end{equation}
@@
 
-Suppose the flow is presumed to be isentropic, $dP/d\rho = c^2$, so $v^2=c^2$, where $c$ is the speed of sound.
+Suppose the flow is presumed to be isentropic, $d{\color{blue}P}/d{\color{orange}\rho_f} = c^2$, so $v^2=c^2$, where $c$ is the speed of sound.
 This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow.
-Moreover, if the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic which leads to $\partial \rho / \partial P \approx 0$.
+Moreover, if the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic which leads to $\partial {\color{orange}\rho_f} / \partial {\color{blue}P} \approx 0$.
 In other words, the small changes in pressure due to flow velocity changes do not change the density.
-This has a secondary effect -- the speed of sound in the fluid is $\partial P/\partial \rho = \infty$ in this instance.
+This has a secondary effect -- the speed of sound in the fluid is $\partial {\color{blue}P}/\partial {\color{orange}\rho_f} = \infty$ in this instance.
 So there is an infinite speed of sound, which makes the equations elliptic in nature.
@@
 
+\subsection{Maximum Likelihood} \label{CH: ML}
+\subfile{Sections/Likelihood}
+
 \subsection{Solid density measurement} \label{CH: Solid_Density_Measurment}
@@
 
-\clearpage
-\subsection{Solution of the parameter estimation starting from another initial guess} \label{CH: Profiles_2}
-\subfile{Sections/Parameter_estimation_solution_from_another_IG}
+%\subsection{Solution of the parameter estimation starting from another initial guess} \label{CH: Profiles_2}
+%\subfile{Sections/Parameter_estimation_solution_from_another_IG}
 

### 2023-06-21 SFE-article/Sections/Model.tex
21.06

@@
 
-	For the sake of clarity of the process model, different colors have been used in the equations to indicate: 
-	{\color{red}control variables},
-	{\color{blue}state variables},
-	{\color{orange}variables} and
-	{\color{magenta}parameters}.
-
 	\subsubsection{Continuity equation} \label{CH: Continuity}
-	The continuity equation for the fluid phase is derived in Appendix \ref{CH: Gouverning equations}.
-When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{magenta}\phi}(z)$ (where ${\color{magenta}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}
+	 %When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{magenta}\phi}(z)$ (where ${\color{magenta}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}
+	The discussed above quasi-one-dimensional assumption was used to derive the continuity equation for the fluid phase as presented in Appendix \ref{CH: Gouverning equations}.
+The cross-section change is taken into account by void fraction ${\color{magenta}\phi}(z)$, which depends on the spatial dimension.
+The equation \ref{EQ: Continuity_differential} shows the differential form, of the continuity equation:
 
 	{\footnotesize
-		\begin{equation*}
-			\frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{magenta}\phi})}{\partial t} + \frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v A {\color{magenta}\phi})}{\partial {\color{blue}z}} = 0
-		\end{equation*}
+		\begin{equation} \label{EQ: Continuity_differential}
+			\frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{magenta}\phi}(z))}{\partial t} + \frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v {\color{magenta}A\phi}(z))}{\partial {\color{blue}z}} = 0
+		\end{equation}
 	}
+	where ${\color{magenta} A}$ is the total cross-section of the extractor.
 
@@
 		\begin{equation}
-			\int \frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v A {\color{magenta}\phi})}{\partial {\color{blue}z}} dz = 0 \rightarrow {\color{red}F}={\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v A {\color{magenta}\phi}
+			\int \frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v {\color{magenta}A \phi}(z) )}{\partial {\color{blue}z}} dz = 0 \rightarrow {\color{red}F}={\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v {\color{magenta}A\phi}(z)
 		\end{equation}
@@
 	\begin{equation}
-		v = \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) A {\color{magenta}\phi}} 
+		v = \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{magenta}A\phi}(z)} 
 	\end{equation}
@@
 		\begin{equation}
-			u = v {\color{magenta}\phi} = \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) A }
+			u = v {\color{magenta}\phi}(z) = \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{magenta} A} }
 		\end{equation}
@@
 			\frac{\partial {\color{blue}c_f}(t,z)}{\partial t}
-			+ \frac{1}{{\color{magenta}\phi}} \frac{\partial \left( {\color{blue}c_f}(t,z) u\right)}{\partial {\color{blue}z}}
-			= \frac{1-{\color{magenta}\phi}}{{\color{magenta}\phi}} {\color{blue}r_e}(t,z)
-			+ \frac{1}{{\color{magenta}\phi}} \frac{\partial}{\partial {\color{blue}z}} \left( {\color{orange}D^M_e} \frac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}} \right)
+			+ \frac{1}{{\color{magenta}\phi}(z)} \frac{\partial \left( {\color{blue}c_f}(t,z) u\right)}{\partial {\color{blue}z}}
+			= \frac{1-{\color{magenta}\phi}(z)}{{\color{magenta}\phi}(z)} {\color{blue}r_e}(t,z)
+			+ \frac{1}{{\color{magenta}\phi}(z)} \frac{\partial}{\partial {\color{blue}z}} \left( {\color{orange}D^M_e} \frac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}} \right)
 		\end{equation}
@@
 	Here, ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z),$ and ${\color{blue}T}(t,z)$ represent the concentration of solute in the fluid phase, the concentration of solute in the solid phase, and temperature, respectively.
-${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term.
-${\color{red}F}(t)$ is the mass flow rate, ${\color{blue}P}(t)$ is the pressure, ${\color{magenta}\epsilon}$ is the void fraction of the bed, ${\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))$ is the fluid density, ${\color{magenta}\rho_s}$ is the solids density, ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient, and $u$ is the superficial velocity.
+${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term, ${\color{red}F}(t)$ is the mass flow rate and ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient.
 
@@
 				\begin{equation}
-					d{\color{blue}e}(t,z)=C_vd{\color{blue}T}-\left[{\color{blue}P}(t)-{\color{blue}T}(t,z)\left(\cfrac{\partial {\color{blue}P}(t)}{\partial {\color{blue}T}(t,z)}\right)_{v_m}\right]dv_m
+					d{\color{blue}e}(t,z)=C_vd{\color{blue}T}-\left[{\color{blue}P}(t)-{\color{blue}T}(t,z)\left(\cfrac{\partial {\color{blue}P}(t)}{\partial {\color{blue}T}(t,z)}\right)_{{\color{orange}v_m}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}\right]d{\color{orange}v_m}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)
 					\label{EQ: internal_energy_def}
@@
 
-			{\footnotesize
+			{\scriptsize
 				\begin{equation}
-					\cfrac{{\color{blue}e}(t,z)-{\color{blue}e}^{id}(t,z)}{R{\color{blue}T}(t,z)} = - \cfrac{A}{B\sqrt{8}} \cfrac{\kappa \sqrt{T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{Z+\left( 1+\sqrt{2} \right)B}{Z+\left( 1+\sqrt{2} \right)B} \right]
+					\begin{aligned}
+					&\cfrac{{\color{blue}e}(t,z)-{\color{blue}e}^{id}(t,z)}{R{\color{blue}T}(t,z)} = \\
+					& - \cfrac{{\color{orange}A}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{{\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)\sqrt{8}} \cfrac{{\color{magenta}\kappa} \sqrt{\color{magenta}T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)} \right]
 					\label{EQ: internal_energy_PR}
+				\end{aligned}
 			\end{equation}
@@
 			\begin{equation}
-				{\color{blue}e}(t,z)={\color{blue}e}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)))=e( {\color{blue}T}(t,z),{\color{blue}P}(t), \rho({\color{blue}T}(t,z),{\color{blue}P}(t)) )
+				{\color{blue}e}(t,z)={\color{blue}e}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)))=e( {\color{blue}T}(t,z),{\color{blue}P}(t), {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) )
 			\end{equation}
@@
 
-			If the value of internal energy ${\color{blue}e}(t,z)$ is known from the time evolution of the energy equation (\ref{EQ: CompressibleEuler_3}), and pressure is known from measurement, then the temperature can be reconstructed.
+			If the value of internal energy ${\color{blue}e}(t,z)$ is known from the time evolution of the energy Equation \ref{EQ: CompressibleEuler_3}, and pressure is known from measurement, then the temperature can be reconstructed.
 A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution and the output from Equation \ref{EQ: internal_energy_PR}.
@@
 
-			Another way to express the energy equation is to introduce enthalpy ${\color{blue}h}(t,z) = {\color{blue}e}(t,z) + {\color{blue}P}(t) / \rho$.
+			Another way to express the energy equation is to introduce enthalpy ${\color{blue}h}(t,z) = {\color{blue}e}(t,z) + {\color{blue}P}(t) / {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))$.
 By introducing the definition of enthalpy, the energy equation becomes
@@
 				\begin{equation}
-					{\color{blue}h}(t,z)=h({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)))=h( {\color{blue}T}(t,z),{\color{blue}P}(t), \rho({\color{blue}T}(t,z),{\color{blue}P}(t)) )
+					{\color{blue}h}(t,z)={\color{blue}h}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)))={\color{blue}h}( {\color{blue}T}(t,z),{\color{blue}P}(t), {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) )
 					\label{EQ:Enthalpy_root}
@@
 
-			{\footnotesize
+			{\scriptsize
 				\begin{equation}
-					{\color{blue}h}(t,z)-{\color{blue}h}(t,z)^{id}=R{\color{blue}T}(t,z) \left[T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right]
+					\begin{aligned}
+					&{\color{blue}h}(t,z)-{\color{blue}h}(t,z)^{id}={\color{magenta}R}{\color{blue}T}(t,z) \\
+					& \left[{\color{magenta}T_r}(Z-1)-2.078(1+{\color{magenta}\kappa} ){\sqrt {\alpha }}\ln \left(\cfrac{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}\right)\right]
 					\label{EQ:Enthalpy_PR}
+				\end{aligned}
 			\end{equation}				
@@
 %				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
-				y(t) &= \int_{t_0}^{t_f} \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))} {\color{blue}c_f}(t,z) \biggr\rvert_{z=L} dt \\
+				{\color{blue}y}(t) &= \int_{t_0}^{t_f} \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))} {\color{blue}c_f}(t,z) \biggr\rvert_{z=L} dt \\
 %				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
-				\cfrac{dy}{dt} &= \qquad \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))} {\color{blue}c_f}(t,z) \biggr\rvert_{z=L} 
+				\cfrac{d{\color{blue}y}(t)}{dt} &= \qquad \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))} {\color{blue}c_f}(t,z) \biggr\rvert_{z=L} 
                 \label{Model_measurment_2}
@@
 
-		where ${\color{magenta}\theta}$ is a set of parameters present in the model, ${\color{blue}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{blue}\chi}$ is the state-space model.
+		where ${\color{magenta}\Theta}$ is a paramter space consisting of model parameters ${\color{magenta}\theta}$ and controls ${\color{red}u}$, ${\color{blue}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{blue}\chi}$ is the state-space model.
 
-		Each function ${\color{blue}\bar{\phi_i}}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{blue}G}_{i\times N_z+1}$ to ${\color{blue}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation.
+		Each function ${\color{blue}\bar{\phi_i}}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{orange}G}_{i\times N_z+1}$ to ${\color{orange}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation.
 The state-space model ${\color{blue}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{blue}x}}(t)$.
@@
 					\underbrace{\begin{bmatrix}
-							{\color{blue}G_1} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}p} \right)\\ 
+							{\color{orange}G_1} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right)\\ 
 							\vdots\\ 
-							{\color{blue}G_{N_z}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}p} \right)\\ 
+							{\color{orange}G_{N_z}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right)\\ 
 							\\ \hline \\ \\
-							{\color{blue}G_{N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
+							{\color{orange}G_{N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right)\\ 
 							\vdots\\
-							{\color{blue}G_{2N_z}} \left( {\color{blue}c}(t),{\color{blue}q}(t),{\color{blue}T}(t); {\color{magenta}p} \right)\\ 
+							{\color{orange}G_{2N_z}} \left( {\color{blue}c}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right)\\ 
 							\\ \\ \hline \\ 
-							{\color{blue}G_{2N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}p} \right) \\
+							{\color{orange}G_{2N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right) \\
 							\vdots\\
-							{\color{blue}G_{3N_z}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}p} \right) \\ 
+							{\color{orange}G_{3N_z}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right) \\ 
 							\\ \\ \hline \\
-							{\color{blue}G_{3N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}p} \right) 
-					\end{bmatrix}}_{{\color{blue}G} \left( {\color{blue}x}(t); {\color{magenta}p} \right)} 
+							{\color{orange}G_{3N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right) 
+					\end{bmatrix}}_{{\color{orange}G} \left( {\color{blue}x}(t); {\color{magenta}\Theta} \right)} 
 			\end{align*} }
 
-			where ${\color{blue}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{magenta}p} \in \mathbb{R}^{N_p =  N_{\Theta} + N_u } $, $N_{\Theta}$ is the number of model parameters, $N_{u}$ is the number of control variables.
+			where ${\color{blue}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{magenta}\Theta} \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of model parameters, $N_{u}$ is the number of control variables.
 
 			In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases (${\color{blue}c_f}(t,z)$ and ${\color{blue}c_s}(t,z)$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{blue}h}(t,z)$).
-The controllable input variables are the mass flow-rate and temperature of the solvent in the feed ($F_\text{in}(t) = {\color{blue}P}(t)$ and $h_\text{in}(t) = {\color{red}h}(t,z=0)$, respectively) and the pressure in the extractor ($P(t,z) ={\color{blue}P}(t)$).
-We extend the system state-space by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator ($Y(t)$).
+The controllable input variables are the mass flow-rate and temperature of the solvent in the feed and the pressure in the extractor.
+We extend the system state-space by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator (${\color{blue}Y}(t)$).
 The system is controllable by manipulating the flow-rate and temperature (enthalpy) of $CO_2$ in the feed, and the pressure in the extractor.
@@
 
-			The method of lines is used to transform the process model equations into a set of ODEs denoted as ${\color{blue}G}({\color{blue}x}(t);{\color{magenta}p})$.
+			The method of lines is used to transform the process model equations into a set of ODEs denoted as ${\color{orange}G}({\color{blue}x}(t);{\color{magenta}\Theta})$.
 The partial derivatives in $z$-direction are computed using a first-order and second-order finite difference approximation.

### 2023-06-21 SFE-article/Sections/Parameter_estimation.tex
21.06

--- 2023-04-29 SFE-article/Sections/Parameter_estimation.tex
@@
 
-The goal of parameter estimation is to obtain the "best" estimate of parameter set $\theta$ (which is a subset of the parameter space $\Theta$ containing all parameters of a model) based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$.
-Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, $y(t)$ (equation \ref{Model_measurment_1}), to give the observable dependent variable $Y(t)$ (for example results of an experiments).
+	The goal of parameter estimation is to obtain the "best" estimate of parameter set ${\color{magenta} \theta}$ (which is a subset of the parameter space ${\color{magenta}\Theta}$ containing all parameters of a model) based on the continuous observations ${\color{blue}Y}(t)$ or the discrete observations ${\color{blue}Y}(t_i)$.
+Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, ${\color{blue}y}(t)$ (Equation \ref{Model_measurment_1}), to give the observable dependent variable ${\color{blue}Y}(t)$ (for example results of an experiments).
 For discrete observations, this can be expressed as:
@@
 		\begin{equation*}
-		Y(t_i) = y(\theta, t_i) + \epsilon(t_i)
+			{\color{blue}Y}(t_i) = {\color{blue}y}({\color{magenta} \theta}, t_i) + \epsilon(t_i)
 	\end{equation*} }
@@
 		\begin{equation*}
-		Y(t) = y(\theta, t) + \epsilon(t)
+			{\color{blue}Y}(t) = {\color{blue}y}({\color{magenta} \theta}, t) + \epsilon(t)
 	\end{equation*} }
 
-However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $dY(t_i)/dt$ is measured instead of $Y(t_i)$ itself.
-In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ as shown below
+	However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $d{\color{blue}Y}(t_i)/dt$ is measured instead of ${\color{blue}Y}(t_i)$ itself.
+In such cases, it is assumed that the unobservable error is added to the deterministic derivative $d{\color{blue}y}({\color{magenta} \theta}, t_i)/dt$ as shown below
 
@@
 		\begin{equation}  \label{EQ: Measurment_noise}
-		\cfrac{d Y(t_i)}{dt} = \cfrac{dy(\theta, t_i)}{dt} + \epsilon(t_i)
+			\cfrac{d {\color{blue}Y}(t_i)}{dt} = \cfrac{d{\color{blue}y}({\color{magenta} \theta}, t_i)}{dt} + \epsilon(t_i)
 	\end{equation} }
@@
 
-\subsubsection{Least squares estimation}
-In statistics, least squares parameter estimation is a method used to estimate the parameters of a linear regression model.
-One of the benefits of this method is that it does not require any prior knowledge about the distribution of unobservable errors.
-Additionally, it yields unbiased estimates and results in the minimum variance among all linear unbiased estimators.
-
-If the model responses, represented by $Y$, are continuous functions of time from $t = 0$ to $t = t_f$, the Markov criterion, also known as "rigorous least squares," is used to minimize the integral squared error $\gamma$.
-This is achieved by minimizing the following expression:
-
-{\footnotesize
-	\begin{align}
-		\gamma &= \cfrac{1}{2} \int_{0}^{t_f} \left[ Y(t) - y(\theta,t) \right]^T \Gamma^{-1} \left[ Y(t) - y(\theta,t) \right] dt \\
-		\hat{\theta} &= \arg \min_{\theta \in \Theta} \gamma
-\end{align} }
-
-Here, $\Gamma$ represents the covariance matrix or a matrix of appropriate weights, $\hat{\theta}$ is the parameter estimate, $\Theta$ is the parameter space, and $\gamma$ is the time-integrated value of the error squared.
-
-Alternatively, if the observations are made at discrete time intervals $t_i$, where $i = 1, 2, \dots, n$, the Markov criterion is to minimize the sum of squared errors, which is given by:
-
-{\footnotesize
-	\begin{align}
-		\gamma &= \cfrac{1}{2} \sum_{i=1}^{n} \left[ Y(t_i) - y(\theta,t_i) \right]^T \Gamma^{-1} \left[ Y(t_i) - y(\theta,t_i) \right] \\
-		\hat{\theta} &= \arg \min_{\theta \in \Theta} \gamma
-\end{align} }
-
-The parameter estimate, $\hat{\theta}$, is obtained by minimizing $\gamma$ over the parameter space $\Theta$.
-
-If the covariance matrix, $\Gamma$, is a diagonal matrix, the Markov criterion becomes a "weighted least squares" criterion.
-If $\Gamma = \sigma^2 \textbf{I}$, where $\sigma$ is a standard deviation and $\textbf{I}$ is the identity matrix, the Markov criterion becomes the "ordinary least squares" criterion.
-
-\iffalse
-\subsubsection{Weighted sum of squares - Cumulative data}
-
-One characteristic feature of certain special experiments is the use of the same batch of materials for the entire series of measurements.
-If unobservable error in the first observation is designated as $\epsilon_1$, the second error observation $\epsilon_2'$ includes $\epsilon_1$ plus a random component introduced side from $\epsilon_1$, or $\epsilon_2' = \epsilon_1 + \epsilon_2$.
-The error in the third observation is $\epsilon_3' = \epsilon_1 + \epsilon_2 + \epsilon_3$, and so forth.
-\citet{Mandel1957} distinguished between the usually assumed type of independent measuring error in the dependent variable and a 'cumulative' or interval error in which each new observation includes the error of the previous observations.
-Cumulative errors, arising because of the fluctuations as a function of time in the process itself due to small changes in operating, are not independent - only the differences in measurement from one period to the next are independent.
-Thus, if we consider two model:
-
-{\footnotesize
-	\begin{flalign*}
-		&{\normalsize \text{Model A - independent error:} } &&\nonumber \\
-		Y(t_i) &= y(\theta, t_i) + \epsilon_i  \qquad i = 1,2,...,n&& \\
-		&{\normalsize \text{Model B - cumulative data:}} && \nonumber \\
-		Y(t_j) - Y(t_{j-1}) &= y(\theta, t_j) - y(\theta, t_{j-1}) + \epsilon_j, \quad j = 1,2,...,n&& \\
-		&{\normalsize \text{or}} && \nonumber \\
-		Y(t_i) = \sum_{j=1}^{i} &\left( Y(t_j) - Y(t_{j-1}) \right) = \sum_{j=1}^{i} \left( y(\theta, t_j) - y(\theta, t_{j-1}) \right) + \sum_{j=1}^{i} \epsilon_j &&
-\end{flalign*} }
-
-in which $\epsilon_i$ are independent random variables with $\mathbb{E}\{\epsilon_i\}$ and Var$\{\epsilon_i\} = \sigma_1^2$, a constant.
-The $\epsilon_j$ are also random independent variables because they represent differences such as $\epsilon_3' - \epsilon_2' = \left( \epsilon_1 + \epsilon_2 + \epsilon_3 \right) - \left( \epsilon_1 + \epsilon_2 \right) = \epsilon_3$.
-We assume that $\mathbb{E}\{\epsilon_j\}$ and Var$\{\epsilon_i\} = \sigma_1^2\left(y_j - y_{j-1}\right)$; i.e., the variance of $\epsilon_j$ can be a function of the test interval.
-The experimental point tend to stay on one side of the regression line of the best fit for Model B.
-
-The unbiased estimate of the Model B is obtained by minimizing the weighted sum of squares:
-
-{\footnotesize
-	\begin{equation*}
-		\hat{\theta} = \arg \min_{\theta \in \Theta} \sum_{j=1}^{n} \cfrac{ \left[ \left( Y(t_j) - Y(t_{j-1}) \right) - \left( y(\theta, t_j) - y(\theta, t_{j-1}) \right) \right]^2  }{y(\theta, t_j) - y(\theta, t_{j-1})}
-\end{equation*} }
-
-\fi
-
-\subsubsection{Maximum likelihood estimation}
-
 	Maximum likelihood estimation (MLE) is a statistical method used to estimate the parameters of a probability distribution based on observed data.
@@
 Although the MLE has often been associated with the normal distribution for mathematical convenience, it can be applied to a wide range of probability distributions.
-
-To find the maximum likelihood estimates, we maximize the joint probability density function, or likelihood function, denoted as $p(\theta | y(t_1),y(t_2),...,y(t_n))$, where $\theta$ represents the parameters and $y(t_1),y(t_2),...,y(t_n)$ represent the observed data.
-The conditions at the maximum can be refined by incorporating prior information.
-The posterior probability density function $p(\theta|y)$ can be expressed as the ratio of two probability densities (\ref{EQ: Probabiltiy_independet_b}) using the continuous variable analogue of Bayes' theorem (details in appendix \ref{CH: Bayes}).
-In such a case the posteriori distribution is given by Equation \ref{EQ: Posterior_distribution}.
+The derivation of the likelihood function under assumption of the Gaussian distribution is presented in the Appendix \ref{CH: ML}.
+The final form of the objective function is presented by Equation \ref{EQ: Objective_function}:
 
 	{\footnotesize
-	\begin{align} \label{EQ: Posterior_distribution}
-		p\left( \theta| y(t_n),...,y(t_1) \right) = \cfrac{p\left( \theta, y(t_n),...,y(t_1) \right)}{p\left( y(t_n),...,y(t_1) \right)}
-\end{align} }
-
-The numerator of the right-hand side od Equation \ref{EQ: Posterior_distribution} using Equation \ref{EQ: Probabiltiy_dependet_a} becomes
-
-{\footnotesize
-	\begin{equation}
-		\begin{split}
-			p\left( \theta,y(t_n),...,y(t_1) \right) &= p\left( y(t_n)|\theta,y(t_{n-1}),...,y(t_1) \right) \\ &\cdot p\left( \theta,y(t_{n-1}),...,y(t_1) \right)
-		\end{split}
-\end{equation} }
-
-These operations can be continued repetitively until we get
-
-{\footnotesize
-	\begin{equation}
-		p\left( \theta, y(t_n),...,y(t_1) \right) = p\left( \theta \right) \prod_{i=1}^{n} p\left( y(t_i)|\theta, y(t_{i-1}),...,y(t_1) \right)
-\end{equation} }
-
-Examination of Equation \ref{EQ: Measurment_noise} shows that $ d Y(t_i) / dt$ depends only on $t_i$, $\theta$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement.
-Consequently, we can write
-
-{\footnotesize
-	\begin{equation}
-		p\left( y(t_i)|\theta, y(t_{i-1}),...,y(t_1) \right) = p\left( y(t_i)|\theta \right)
-\end{equation} }
-
-provided Equation \ref{EQ: Measurment_noise} is observed as a constraint. The desired joint conditional probability function is thus
-
-{\footnotesize
-	\begin{equation}
-		p\left( \theta| y(t_n),...,y(t_1) \right) = \cfrac{p\left( \theta \right) \prod_{i=1}^{n} p\left( y(t_i)|\theta \right) }{p\left( y(t_n),...,y(t_1) \right)}
-\end{equation} }
-
-We can get rid of the evidence term $p\left( y(t_n),...,y(t_1) \right)$ because it's constant with respect to the maximization.
-Moreover, if we are lacking a prior distribution over the quantity we want to estimate, then $p(\theta)$ can be omitted.
-In such a case:
-
-{\footnotesize
-	\begin{equation}
-		p\left( \theta| y(t_n),...,y(t_1) \right) = \prod_{i=1}^{n} p\left( y(t_i)|\theta \right) = \prod_{i=1}^{n} L\left( \theta|y(t_i) \right) 
-\end{equation} }
-
-%By collecting a values of $y$ and selecting the values of $\theta$ that maximize the likelihood function $L\left( \theta | y \right)$, an estimator $\hat{\theta}$ can be obtained.
-Such estimator, $\hat{\theta}$, is known as maximum likelihood estimator.
-In effect, the methods selects those values of $\theta$ that are at least as likely to generate the observed sample as any other set of values of the parameters if the probability density of $y$ were to be extensively simulated through use of the probability density $p\left( y|\theta \right)$.
-In making a maximum likelihood estimate, we assume the form of the probability density and that all possible values of $\theta$ are equally likely before experimentation.
-\todo{Needed?}
-
-%The likelihood function for the parameters given one observation is just the probability density in which the observation is regarded as a fixed number and the parameters as the variables:
-%
-%{\footnotesize
-	%	\begin{equation}
-		%		p\left( \theta| y(t_i) \right) = L\left( \theta|y_{t_i} \right) = p\left( y(t_i)| \theta \right)
-		%\end{equation} }
-		%where the lower case $y$'s and the number subscripts designate the value of the respective observation that is inserted into the probability density function. 
-		The likelihood function $L\left( \theta | y \right)$ for the parameters based on several observations is the product of the individual functions if the observations are independent.
-
-		{\footnotesize 
-			\begin{multline}
-				L\left( \theta|y(t_n),...,y(t_1) \right) = \prod_{i=1}^{n} L\left( \theta|y(t_i) \right) \\
-				= p\left( y(t_1)| \theta \right)p\left( y(t_2)| \theta \right) ... p\left( y(t_n)| \theta \right)
-		\end{multline} }
-
-		In choosing as estimates of $\theta$ the values that maximize $L$ for the given values $\left( y(t_i) \right)$, it turns out that it is more convenient to work with the $\ln L$ than with $L$ itself:
-
-		{\footnotesize 
-			\begin{equation}
-				\ln L = \ln p \left( y(t_1)| \theta \right) + \ln p\left( y(t_2)| \theta \right) + ... + \ln p \left( y(t_n)| \theta \right) = \sum_{i=1}^{n} \ln p\left( y(t_i); \theta \right)
-		\end{equation} }
-
-		By assuming that the conditional distribution of $\bar{Y}_i$, given $y_i$, is normal, then we form the likelihood function based on the probability density:
-
-		{\footnotesize
-			\begin{align} \label{EQ: MLE_Norm}
-				p\left(  \theta, \sigma | y(t_n),...,y(t_1) \right) &= \prod_{i=1}^{n} \cfrac{1}{\sqrt{2 \pi} \sigma } \exp \left[ \cfrac{1}{2  \sigma } \left( Y(t_i) - y(\theta , t_i) \right)^2 \right] \nonumber \\
-				L\left( \theta, \sigma | y(t_n),...,y(t_1) \right) &= \prod_{i=1}^{n} \cfrac{1}{\sqrt{2 \pi} \sigma } \exp \left[ \cfrac{1}{2  \sigma } \left( Y(t_i) - y(\theta , t_i) \right)^2 \right]
-		\end{align}}
-		where $\sigma$ is the variance
-
-		%In Equation \ref{EQ: MLE_Norm} the parameters are the variables, and the values of $Y$ and $x$ are given. Then
-		By taking the natural logarithm of the Equation \ref{EQ: MLE_Norm}, the final form of the objective function can be obtained:
-
-		{\footnotesize
-			\begin{equation}
-				\ln L = -\cfrac{n}{2} \left( \ln \sqrt{2 \pi} + \ln \sigma^2 \right)
-				- \cfrac{ \sum_{i=1}^{n} \left[  Y(t_i) - y(\theta , t_i) \right]^2 }{2 \sigma^2}
+		\begin{equation} \label{EQ: Objective_function}
+			\ln L = -\cfrac{n}{2} \left( \ln \sqrt{2 \pi} + \ln {\color{magenta} \sigma}^2 \right)
+			- \cfrac{ \sum_{i=1}^{n} \left[  \cfrac{d {\color{blue}Y}(t_i)}{dt} - \cfrac{d{\color{blue}y}({\color{magenta} \theta}, t_i)}{dt} \right]^2 }{2 {\color{magenta} \sigma}^2}
 		\end{equation}
@@
 			\begin{aligned} \label{EQ: Optimization_formulation_MLE}
-					&\hat{\theta}_{MLE} &= \arg \max_{\sigma, \theta \in \Theta} \ln L = \arg \max_{\sigma,\theta \in \Theta} p(\theta|y) \\
+				&\hat{{\color{magenta} \theta}}_{MLE} &= \arg \max_{{\color{magenta} \sigma}, {\color{magenta} \theta} \in \Theta} \ln L = \arg \max_{{\color{magenta} \sigma},{\color{magenta} \theta} \in \Theta} p({\color{magenta} \theta}|{\color{blue}y}) \\
 				&\text{subject to}
-					& \dot{x} = f(t,x,\theta) \\
-					&& \dot{\theta} = 0 \\
-					&& y = y(x) \\
-					&& \theta^{lb} \leq \theta \leq \theta^{ub}
+				& \dot{ {\color{blue}x} } = {\color{blue}G}({\color{blue} x}(t);{\color{magenta} \theta}) \\
+				&& {\color{magenta} \dot{\theta}} = 0 \\
+				&& {\color{blue}y} = {\color{blue}y}(t) \\
+				&& {\color{magenta} \theta}^{lb} \leq {\color{magenta} \theta} \leq {\color{magenta} \theta}^{ub}
 			\end{aligned}
@@
 
-		where $\hat{\theta}$ is as maximum likelihood estimator, $\theta^{lb}$ define the minimal value of $\theta$ and $\theta^{ub}$ is the maximum value of $\theta$.
+	where $\hat{{\color{magenta} \theta}}$ is as maximum likelihood estimator, ${\color{magenta} \theta}^{lb}$ define the minimal value of ${\color{magenta} \theta}$ and ${\color{magenta} \theta}^{ub}$ is the maximum value of ${\color{magenta} \theta}$.
 
-		Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector $\theta$ by equating to zero the partial derivatives of $\ln L$ with respect to each of the parameters:
+	Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector ${\color{magenta} \theta}$ by equating to zero the partial derivatives of $\ln L$ with respect to each of the parameters:
 
@@
 		\begin{align}\label{EQ: MLE_Basic_Solution}
-				\cfrac{\partial \ln L}{\partial \theta} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( y(t_i) | \theta \right) }{\partial \theta} = 0 
+			\cfrac{\partial \ln L}{\partial {\color{magenta} \theta}} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( y(t_i) | {\color{magenta} \theta} \right) }{\partial {\color{magenta} \theta}} = 0 
 	\end{align} }
 
-		Solution of Equations \ref{EQ: MLE_Basic_Solution} yield the desired estimates $\hat{\theta}$.
-For some models, these equations can be explicitly solved for $\hat{\theta}$ but in general no closed-form solution to the maximization problem is known or available, and an maximum likelihood estimator can only be found via numerical optimization.
-
-		\iffalse
-
-		It can be shown that as $n$ approaches infinity the maximum likelihood estimates have the desirable asymptotic properties:
-
-		\begin{enumerate}[label=(\arabic*)]
-			\item {\footnotesize $\lim\limits_{n \rightarrow \infty} \mathbb{E}\{\hat{\theta}\} = \theta$ }
-			\item {\footnotesize $\left[ \sqrt{n}\left( \hat{\theta} - \theta \right) \right]$ } is normally distributed
-		\end{enumerate}
-		and for the case of two parameters:
-
-		\begin{enumerate}[resume,label=(\arabic*)]
-			\item {\footnotesize $\lim\limits_{n \rightarrow \infty} \text{Var}\{\hat{\theta}\} = \cfrac{1}{n} \left[ \mathbb{E} \left\{ \left( \cfrac{\partial \ln p}{\partial \theta} \right)^2 \right\} \right]^{-1} \cfrac{1}{1-\rho^2_{\hat{\theta}}} $ } \label{Assumption_MLE}
-		\end{enumerate}
-
-		where $\rho^2_{\hat{\theta}}$ is the matrix of correlation coefficients.
-
-		Maximum likelihood estimates are not necessarily unbiased.
-Maximum likelihood estimates, however are efficient and, hence, consistent estimates.
-Furthermore, where a sufficient estimate can be obtained, the maximum likelihood method will obtain it.
-Finally, if $\hat{\theta}$ is a maximum likelihood estimator of $\theta$, the $f\left( \hat{\theta} \right)$ is a maximum likelihood estimator of $f\left( \theta \right)$, a function of $\theta$.
-
-		\hrule
-
-		%Under the assumption of normality, the lack of prior knowledge about the parameters $\theta^0$ and known initial conditions $y_0$.
-Intuitively, this selects the parameter values that make the observed data most probable.
-The specific value $\hat{\theta}$ that maximizes the likelihood function $L$ is called the maximum likelihood estimate.
-
-		As already discussed, the prior information about the estimated parameters can be incorporated in to the maximum likelihood estimator to form a maximum a posteriori probability (MAP) estimate.
-MAP can be used to obtain a point estimate of an unobserved quantity on the basis of empirical data.
-MAP estimation can therefore be seen as a regularization of maximum likelihood estimation.
-The relationship between MAP and MLE can be obtained from the Bayes' rule:
-
-		{\footnotesize
-			\begin{equation} 
-				\begin{split} \label{EQ: MAP_probability}
-					{\bf \hat{\theta}_{\text{MAP}}} &= \arg\max_{\sigma, \theta \in \Theta} p(\theta | y) \\
-					&= \arg\max_{\sigma, \theta \in \Theta} \frac{p(y | \theta) p(\theta)}{p(y)} \\
-					&= \arg\max_{\sigma, \theta \in \Theta} p(y | \theta) p(\theta) \\
-					&= \arg\max_{\sigma, \theta \in \Theta} \ln(p(y | \theta) p(\theta)) \\
-					&= \arg\max_{\sigma, \theta \in \Theta} \ln p(y | \theta) + \ln p(\theta)
-				\end{split}
-		\end{equation} }
-
-		We assume the normal distribution of random samples, with identical variance and the prior distribution of $\theta$ given by $\mathcal{N}(\theta^0,\,\sigma_\theta^{2})$.
-The function to be maximized can be written as
-
-		{\footnotesize
-			\begin{equation} \label{EQ: MAP_L2}
-				\begin{aligned}
-					&\arg\max_{\sigma, \theta \in \Theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 }{2\sigma^2}}
-					+ \ln \prod_{j=0}^{p} \frac{1}{\sigma_\theta\sqrt{2\pi}}e^{-\frac{ \left( \theta - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]  \\
-					= &\arg\max_{\sigma, \theta \in \Theta} \left[- \sum_{i=1}^{n} {\frac{\left( Y(t_i) - y\left( \theta, t_i \right) \right)^2}{2\sigma^2}}
-					- \sum_{j=0}^{p} {\frac{\left( \theta - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]\\
-					= &\arg\min_{\sigma, \theta \in \Theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2
-					+ \frac{\sigma^2}{\sigma_\theta^2} \sum_{j=0}^{p} \left( \theta - \theta^0 \right)^2 \right] \\
-					= &\arg\min_{\sigma, \theta \in \Theta} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 + \lambda_{L2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^0 \right)^2 \right]
-				\end{aligned}
-		\end{equation} }
-
-		In Equation \ref{EQ: MAP_L2} some of the constants (with respect to $\theta$) were dropped and factored to simplify the expression.
-We can adjust the amount of regularization we want by changing $\lambda_{L2}$.
-Equivalently, we can adjust how much we want to weight the priors carry on the coefficients ($\theta$).
-If we have a very small variance (large $\lambda_{L2}$) then the coefficients will be very close to 0; if we have a large variance (small $\lambda_{L2}$) then the coefficients will not be affected much (similar to as if we didn't have any regularization).
-
-		Let's assume that the prior distribution of parameter $\theta$ is given by the Laplace distribution. The likelihood function can defined as follow:
-
-		{\footnotesize
-			\begin{equation} \label{EQ: MAP_L1}
-				\begin{aligned}
-					&\arg\max_{\sigma, \theta \in \Theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 }{2\sigma^2}}
-					+ \ln \prod_{j=0}^{p} \frac{1}{2b}e^{-\frac{ | \theta - \theta^0 | }{\sigma_\theta}} \right]  \\
-					= &\arg\max_{\sigma, \theta \in \Theta} \left[- \sum_{i=1}^{n} {\frac{\left( Y(t_i) - y\left( \theta, t_i \right) \right)^2}{2\sigma^2}}
-					- \sum_{j=0}^{p} {\frac{ | \theta - \theta^0 | }{\sigma_\theta}} \right]\\
-					= &\arg\min_{\sigma, \theta \in \Theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2
-					+ \frac{\sigma^2}{\sigma_\theta} \sum_{j=0}^{p} | \theta - \theta^0 | \right] \\
-					= &\arg\min_{\sigma, \theta \in \Theta} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 + \lambda_{L1} \sum_{j=0}^{p} | \theta - \theta^0 | \right]
-				\end{aligned}
-		\end{equation} }
-
-		The Laplacean prior act as $L1$-type of regularization on the optimization problem.
-Instead of preventing any of the coefficients from being too large (due to the squaring), $L1$ promotes sparsity.
-Due to the sparsity some of the parameters can be zero out, and eventually removed from the model.
-$L1$ is more robust to outliers than $L2$.
-
-		If the cost function is given by Equations \ref{EQ: MAP_L2} or \ref{EQ: MAP_L1}, then the optimization problem can be formulated as follow:
-
-		{\footnotesize
-			\begin{equation}
-				\begin{aligned}
-					&\hat{\theta}_{MAP} &= \arg\max_{\sigma, \theta \in \Theta} \ln p(y | \theta) + \ln p(\theta) \\
-					&\text{subject to}
-					& \dot{x} = f(t,x,\theta) \\
-					&& \dot{\theta} = 0 \\
-					&& y = g(x)
-				\end{aligned}
-		\end{equation} }
-
-		\hrule
-		If the cost function to be maximized is given be Equation \ref{EQ: MAP_probability} and constrained by Equation \ref{EQ: Measurment_noise}, then the method of Lagrange multipliers can be used to convert a constrained problem into a form such that the derivative test of an unconstrained problem can be applied.
-The Lagrange function ($L^*$) can be defined as $\ln(L)$ plus the Lagrangian multipliers $\lambda(t_i)$ times the constraint function
-
-		{\footnotesize
-			\begin{equation} \label{EQ: MLE_Lagrangian}
-				\begin{split}
-					L^* \equiv \ln p\left( \theta \right) + \sum_{i=1}^{n} \left\{ \ln p(y(t_i)|\theta) \right. \\
-					\left. + \lambda^T \cdot {\color{red} \left[ Y(t_i) - y\left( \theta,t_i \right) - \epsilon(t_i) \right] } \right\} \\ - \ln \left[ p\left( y \right) \right]
-				\end{split}
-		\end{equation}}
-
-		By assumption of the relation of Equation \ref{EQ: Measurment_noise}
-
-		{\footnotesize
-			\begin{equation} \label{EQ: Noise_prob}
-				p\left( y(t_i) | \theta,y_0 \right) = p\left( \epsilon(t_i) \right)
-		\end{equation} }
-
-		and specially
-
-		{\footnotesize
-			\begin{equation} \label{EQ: Noise_prob_norm}
-				p\left( \epsilon(t_i) \right) = \cfrac{1}{ (2\pi)^{v/2} |\Gamma(t_i)|^{1/2} } \exp \left[ -\cfrac{1}{2}\epsilon^T(t_i) \left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \right]
-		\end{equation} }
-		where $|\Gamma|$ is the det$~\Gamma$, and $\Gamma$ is the covariance matrix of $\epsilon$, i.e., of the response.
-
-		After Equation \ref{EQ: Noise_prob} is substituted into Equation \ref{EQ: MLE_Lagrangian}, and $L^*$ can be differentiated with respect to each of the estimates and $\epsilon(t_i)$.
-{\color{red}Based on the first order optimality conditions}, the resulting expression is equated to zero:
-
-		{\footnotesize
-			\begin{subequations} \label{EQ: MLE_Lag_diff}
-				\begin{alignat}{2}
-					%\cfrac{\partial L^*}{\partial y_0} &= \cfrac{\partial}{\partial y_0} \ln p(\theta,y_0) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial y_0} y(\theta ,t_i) = 0^T \\
-					\cfrac{\partial L^*}{\partial \theta} &= \cfrac{\partial}{\partial \theta} \ln p(\theta) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial \theta} y(\theta,t_i) =0 \\
-					\cfrac{\partial L^*}{\partial \epsilon(t_i)} &= \cfrac{\partial}{\partial \epsilon(t_i)} \ln p(\epsilon(t_i)) - \lambda^T(t_i) = 0^T
-				\end{alignat}
-		\end{subequations} }
-
-		Substitution of Equation \ref{EQ: Noise_prob_norm} into the last Equation of \ref{EQ: MLE_Lag_diff} makes it possible to solve for $\lambda(t_i)$:
-
-		{\footnotesize
-			\begin{align}
-				\lambda(t_i) &= -\left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \nonumber \\
-				&= -\left( \Gamma(t_i) \right)^{-1} \left[ Y(t_i) - y(\theta,t_i) \right]
-		\end{align} }
-
-		and to eliminate $\lambda(t_i)$ from the first equation of \ref{EQ: MLE_Lag_diff}.
-
-		For convenience we shall define a new column vector $\theta^*$ in which all the elements of $\theta$ are arranged as follows:
-
-		{\footnotesize
-			\begin{equation}
-				\theta^* = \begin{bmatrix}
-					\theta_{1,1} & \theta_{1,2} & \cdots & \theta_{1,v} & \theta_{2,1} & \cdots & \theta_{2,v} & \cdots & \theta_{v,v}
-				\end{bmatrix}^T	
-		\end{equation} }
-
-		Finally, we assume that and $\theta^*$ are distributed by a joint normal distribution and that the prior distribution are, respectively
-
-		{\footnotesize
-			\begin{subequations} \label{EQ: MLE_Priors}
-				\begin{align}
-					&p\left( \theta^* \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{\theta^*}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( \theta^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} \left( \theta^* - \theta^{*(0)} \right) \right]
-					%&p\left( y_0 \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{y_0}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( y_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} \left( y_0 - y_0^{(0)} \right) \right] 
-				\end{align}
-		\end{subequations} }
-		where $\Omega$'s are the respective covariance matrices for $\theta^*$ and $y_0$, and the subscript $(0)$ designates the prior estimated of $\theta^*$ and $y_0$.
-If we assume that $\theta^*$ and $y_0$ are independent
-
-		%{\footnotesize
-			%	\begin{equation}
-				%		\ln p(\theta^*,y_0) = \ln p(\theta^*) + \ln p(y_0)
-				%\end{equation} }
-
-				Introduction of the prior distributions, Equations \ref{EQ: MLE_Priors}, plus the expression for $\lambda(t_i)$ into the first two equations of \ref{EQ: MLE_Lag_diff} gives the final equations from which the estimators of $\theta^*$ and $y_0$ can be obtained:
-
-				{\footnotesize
-					\begin{subequations} 
-						\begin{flalign}
-							%			&-\left( \hat{y}_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} + \sum_{i=1}^{n}\left[ Y(t_i) - y\left( \hat{\theta}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \cdot \cfrac{\partial}{\partial y_0} y\left( \hat{\theta}, \hat{y}, t_i \right) = 0^T  &&\\
-							&-\left( \hat{\theta}^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} + \sum_{i=1}^{n}\left[ Y(t_i) - y\left( \hat{\theta}, t_i \right) \right]^T \Gamma^{-1}(t_i) \cdot \cfrac{\partial}{\partial \theta^*} y\left( \hat{\theta}, t_i \right) = 0^T &&
-						\end{flalign}
-				\end{subequations} }
-				where the overlay caret denotes estimated parameters.
-
-				Note that under the assumption that the elements of $\Omega$ are essentially infinite (prior knowledge is diffuse), the elements of $\Omega^{-1}$ are zero, the equations for the maximum likelihood estimates coincide with those for the least squares estimates, and the same calculations for precision in the estimates apply.
-
-				%For some models, these equations can be explicitly solved for $\hat{\theta}^*$ and $\hat{y}$ but in general no closed-form solution to the maximization problem is known or available, and an MLE can only be found via numerical optimization.
-Under the assumption of normality, the lack of prior knowledge about the parameters $\theta^0$ and known initial conditions $y_0$, the optimization problem is defined as follow:
-				%
-				%{\footnotesize
-					%\begin{equation}
-					%	\hat{\theta}_{MLE} = \arg \max_{\theta \in \Theta} L = \arg \max_{\theta \in \Theta} p(\theta|y)
-					%\end{equation} }
-					%
-					%Intuitively, this selects the parameter values that make the observed data most probable.
-The specific value $\hat{\theta}$ that maximizes the likelihood function $L$ is called the maximum likelihood estimate.
-Further, if the function $\hat{\theta}:\mathbb{R}\rightarrow\Theta$ so defined is measurable, then it is called the maximum likelihood estimator.
-					%
-					%If the random samples $y(t_1)$, $y(t_2)$,...,$y(t_n)$ come from a normal distribution with unknown mean $\hat{\theta}$ and variance $\sigma^2$, then the joint probability function can be written as
-					%
-					%{\footnotesize
-						%\begin{equation}
-						%	p(\theta|y(t_i)) = \cfrac{1}{\sqrt{2\pi\sigma}}\exp\left[-\cfrac{ \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}\right]
-						%\end{equation} }
-						%
-						%Then the likelihood function is defined as follow:
-						%
-						%{\footnotesize
-							%\begin{equation} 
-							%	L =\prod\limits_{i=1}^n p(\theta|y(t_i)) = (2\pi\sigma)^{-n/2}\exp\left[-\cfrac{1}{2\sigma}\sum\limits_{i=1}^n \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2\right]
-							%\end{equation} }
-							%
-							%By taking the ln of the likelihood function, the final form of the cost function is obtained:
-							%
-							%{\footnotesize
-								%\begin{equation} 
-								%	\ln L=-\cfrac{n}{2}\ln\sigma-\cfrac{n}{2}\ln(2\pi)-\cfrac{\sum\limits_{i=1}^n \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}
-								%\end{equation} }
-								%
-								%\subsection{Maximum a posteriori estimation}
-								%
-								%As already discussed, the prior information about the estimated parameters can be incorporated in to the maximum likelihood estimator to form a maximum a posteriori probability (MAP) estimate.
-MAP can be used to obtain a point estimate of an unobserved quantity on the basis of empirical data.
-MAP estimation can therefore be seen as a regularization of maximum likelihood estimation.
-MLE and MAP can be connected by Bayes' rule:
-								%
-								%{\footnotesize
-									%\begin{equation} 
-									%	\begin{split}
-										%		{\bf \hat{\theta}_{\text{MAP}}} &= \arg\max_{\sigma, \theta \in \Theta} p(\theta | y) \\
-										%		&= \arg\max_{\sigma, \theta \in \Theta} \frac{p(y | \theta) p(\theta)}{p(y)} \\
-										%		&= \arg\max_{\sigma, \theta \in \Theta} p(y | \theta) p(\theta) \\
-										%		&= \arg\max_{\sigma, \theta \in \Theta} \ln(p(y | \theta) p(\theta)) \\
-										%		&= \arg\max_{\sigma, \theta \in \Theta} \ln p(y | \theta) + \ln p(\theta)
-										%	\end{split}
-									%\end{equation} }
-									%
-									%Notice that we can get rid of the evidence term $P(y)$ because it's constant with respect to the maximization and also take the ln of the inner function because it's monotonically increasing.
-									%
-									%We assume the normal distribution of random samples, with identical variance and the prior distribution of $\theta$ given by $\mathcal{N}(\theta^0,\,\sigma_\theta^{2})$.
-The likelihood function to be maximized can be written as
-									%
-									%{\footnotesize
-										%\begin{equation} \label{EQ: MAP_L2}
-										%	\begin{split}
-											%	&\arg\max_{\sigma, \theta \in \Theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2 }{2\sigma^2}}
-											%	+ \ln \prod_{j=0}^{p} \frac{1}{\sigma_\theta\sqrt{2\pi}}e^{-\frac{ \left( \hat{\theta} - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]  \\
-											%	&= \arg\max_{\sigma, \theta \in \Theta} \left[- \sum_{i=1}^{n} {\frac{\left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma^2}}
-											%	- \sum_{j=0}^{p} {\frac{\left( \hat{\theta} - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]\\
-											%	&= \arg\min_{\bf \theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2
-											%	+ \frac{\sigma^2}{\sigma_\theta^2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^0 \right)^2 \right] \\
-											%	&= \arg\min_{\bf \theta} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2 + \lambda_{L2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^0 \right)^2 \right]
-											%	\end{split}
-										%\end{equation} }
-										%
-										%Notice that we dropped some of the constants (with respect to $\theta$) and factored to simplify the expression.
-You can see this is the same expression as Equation \ref{EQ: MAP_L2} (L2 Regularization) with $\lambda_{L2}$.
-We can adjust the amount of regularization we want by changing $\lambda_{L2}$.
-Equivalently, we can adjust how much we want to weight the priors carry on the coefficients ($\theta$).
-If we have a very small variance (large $\lambda_{L2}$) then the coefficients will be very close to 0; if we have a large variance (small $\lambda_{L2}$) then the coefficients will not be affected much (similar to as if we didn't have any regularization).
-
-	\fi
+	Solution of Equations \ref{EQ: MLE_Basic_Solution} yield the desired estimates $\hat{{\color{magenta} \theta}}$.
+For some models, these equations can be explicitly solved for $\hat{{\color{magenta} \theta}}$ but in general no closed-form solution to the maximization problem is known or available, and an maximum likelihood estimator can only be found via numerical optimization.
 

### 2023-06-21 SFE-article/Sections/Saturation.tex
21.06

--- 2023-04-20 SFE-article/Sections/Saturation.tex
@@
 
-	\subsubsection{Saturation Concentration}
+	\subsubsection{Concentration limit}
 
-	The above model does not take into account the saturation of fluid, which can be introduced by multiplying the gradient by a function $\gamma(c_f)$ (equation \ref{EQ: C_sat_function}).
-$\gamma(c_f)$ describe the reverse logistic function, which is equal to unity below the $c_{sat}$, the saturation concentration, and equal to zero, above the $c_{sat}$.
-The $\gamma(c_f)$ for $c_{sat}=5$ is shown on figure \ref{fig: Gamma_function}.
+	To mimic that not all solute might be obtained at specific operating conditions, the coefficient ${\color{orange} \gamma}$ is introduced to limit the available oil.
+The ${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ describe the reverse logistic function, which is equal to unity above the ${\color{magenta} c_{lim}}$, the saturation concentration, and equal to zero, below the ${\color{magenta} c_{lim}}$.
+The ${\color{orange} \gamma}$ parameter multiply the solute concentration term in solid phase in the concentration gradient.
+As the concentration of solute decrease, it can reach the limiting value ${\color{magenta} c_{lim}}$ when the ${\color{orange} \gamma}$ goes to zero and stop the extraction from the solid.
 
@@
 		\begin{equation}
-			\gamma(c_f) = \cfrac{1}{1+\exp ( -k_{sat} \left( c_f - c_{sat} \right) ) }
+			{\color{orange} \gamma}({\color{blue} c_s} (t,z)) = \cfrac{1}{1+\exp \left( -{\color{magenta} k_{lim}} \left( {\color{blue} c_s} (t,z) - {\color{magenta} c_{lim}} \right) \right) }
 			\label{EQ: C_sat_function}
@@
 
-	where $k_{sat}$ is the growth rate, and it is defined as $k_{sat} = 2c_{sat}$\todo{Explain why the growth rate is defined as it is}.
+	where ${\color{magenta} k_{lim}}$ describe the curvature of the $\gamma$ function, and it is defined as ${\color{magenta} k_{lim}} = 1$.
+%In the limit when $ {\color{magenta} k_{lim}}\rightarrow+\infty$ become a step function.
+If the ${\color{magenta} k_{lim}}$ is to high, the gradient of the ${\color{orange} \gamma}$ function become high, or goes to infinity, which might cause difficulties for a gradient-based optimizer.
+	The ${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ gamma function is visualised on \ref{fig: Gamma_function}.
 
@@
 					legend style={draw=none},
-					xmin = 0, xmax = 10,
+					xmin = 0, xmax = 100,
 					ymin = -0.5, ymax = 1.5,
-					xlabel = {$c_f[kg/m^3]$},
-					ylabel = {$\gamma(c_f)[-]$}]
+					xlabel = {${\color{blue} c_s}(t,z)[kg/m^3]$},
+					ylabel = {${\color{orange} \gamma}({\color{blue} c_s}(t,z))[-]$}]
 					\addplot[
-					domain = 0:10,
+					domain = 0:100,
 					samples = 100,
@@
 					blue,
-					] { 1 / (1 + exp( 2*5 .* ( x - 5 ) ) ) };
-					\addplot[thick, samples=50, dashed, domain=0:1.5, black] coordinates {(5,-0.5)(5,1.5)};
+					] { 1 / (1 + exp( 1 * ( 50 - x ) ) ) };
+					\addplot[thick, samples=50, dashed, domain=0:1.5, black] coordinates {(50,-0.5)(50,1.5)};
 
-					\addlegendentry{$\gamma(c_f)$}
-					\addlegendentry{$c_{sat}$}
+					\addlegendentry{${\color{orange} \gamma}({\color{blue} c_s} (t,z))$}
+					\addlegendentry{${\color{magenta} c_{lim}}$}
 				\end{axis}
@@
 			\end{tikzpicture}
-			\caption{$\gamma(c_f)$ function under assumption of $c_{sat}=5 [kg/m^3]$}
+			\caption{${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ function under assumption of ${\color{magenta} c_{lim}}=50~[kg/m^3]$}
 			\label{fig: Gamma_function}
@@
 
-	{\footnotesize
+	{\scriptsize
 		\begin{equation}
 			\label{Model_kinetic}
-				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} } \gamma(c_f) \left({\color{blue}c_s}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
+				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} } \left({\color{blue}{\color{blue} c_s} }(t,z) {\color{orange} \gamma}({\color{blue} c_s} (t,z)) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
 		\end{equation} }

### 2023-06-21 SFE-article/Sections/Thermodynamic_details.tex
21.06

@@
 	\subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}
-	In this study, the influence of real gas effects are introduced through ${\color{red}P}(t) {\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t)) = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, where ${\color{orange}v_m}$ represents the molar volume of $CO_2$, ${\color{orange}Z}$ denotes its compressibility factor, and $R$ is the universal gas constant.
+	In this study, the influence of real gas effects are introduced through ${\color{red}P}(t) {\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t)) = {\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right){\color{magenta}R}{\color{blue}T}(t,z)$, where ${\color{orange}v_m}$ represents the molar volume of $CO_2$, ${\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ denotes its compressibility factor, and $R$ is the universal gas constant.
 The main advantage of using compressibility in calculations is to express it as an explicit function of temperature and pressure.
@@
 
-	The Equation \ref{EQ: PR} can be also written as the third-order polynomial equation shown in Equation \ref{eq: Compressibility}.
-Numerical methods such as Newton-Raphson can be used to solve the polynomial equation, but the Cardano formula is preferred as it yields an analytical solution.
+	The Equation \ref{EQ: PR} can be also written as the third-order given by Equation \ref{eq: Compressibility}.
+Numerical methods such as Newton-Raphson can be used to solve the polynomial equation to obtain the compressibility ${\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ at given temperature and pressure.
+Alternatively, the Cardano formula can be used to get the closed form solution of the Equation \ref{eq: Compressibility}.
 Further details regarding the Cardano formula can be found in Appendix \ref{CH: Cardano}.
@@
 	{\footnotesize	
-	\begin{align}\label{eq: Compressibility}
-		&{\color{orange}Z}^3 - \left[1 - {\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]\right] {\color{orange}Z}^2 \\ \nonumber
-		&+ \left[{\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] - 2{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] - 3{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]^2\right] {\color{orange}Z} = 0
-	\end{align} }
+	\begin{equation}\label{eq: Compressibility}
+	\begin{aligned}
+		&{\color{orange}Z}^3 - \left(1 - {\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)\right) {\color{orange}Z}^2 \\
+		&+ \left({\color{orange}A}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) - 2{\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) - 3{\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)^2\right) {\color{orange}Z} = 0
+	\end{aligned} \end{equation} }
 
-	where ${\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are functions of time and space defined on the attraction parameter, ${\color{orange}a}\left[{\color{blue}T}(t,z)\right] = {\color{magenta}a^c}{\color{orange}\alpha}\left[{\color{blue}T}(t,z)\right]$ with ${\color{magenta}a^c} \approx 0.45724 {{\color{magenta}R}^2{\color{magenta}T^c}^2}/{{\color{magenta}P^c}}$, and the repulsion parameter, ${\color{magenta}b} \approx 0.07780 {{\color{magenta}R}{\color{magenta}T^c}}/{{\color{magenta}P^c}}$, both functions of the critical temperature ${\color{magenta}T^c}$ and pressure ${\color{magenta}P^c}$.
+	where ${\color{orange}A}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ are functions of time and space defined on the attraction parameter, ${\color{orange}a}\left({\color{blue}T}(t,z)\right) = {\color{magenta}a^c}{\color{orange}\alpha}\left({\color{blue}T}(t,z)\right)$ with ${\color{magenta}a^c} \approx 0.45724 {{\color{magenta}R}^2{\color{magenta}T_c}^2}/{{\color{magenta}P_c}}$, and the repulsion parameter, ${\color{magenta}b} \approx 0.07780 {{\color{magenta}R}{\color{magenta}T_c}}/{{\color{magenta}P_c}}$, both functions of the critical temperature ${\color{magenta}T_c}$ and pressure ${\color{magenta}P_c}$.
 
@@
 		\begin{align} 
-			{\color{orange}A}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]	& = \dfrac{{\color{orange}\alpha}\left[{\color{blue}T}\left(t,z\right)\right]{\color{magenta}a^c}{\color{red}P}(t)}{{\color{magenta}R}^2{\color{blue}T}^2(t,z)};													\label{eq: PR_A}\\
-			{\color{orange}B}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]	& = \dfrac{{\color{magenta}b}{\color{red}P}(t)}{{\color{magenta}R}{\color{blue}T}(t,z)}	\label{eq: PR_B}.
+			{\color{orange}A}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)	& = \dfrac{{\color{orange}\alpha}\left({\color{blue}T}\left(t,z\right)\right){\color{magenta}a^c}{\color{red}P}(t)}{{\color{magenta}R}^2{\color{blue}T}^2(t,z)};													\label{eq: PR_A}\\
+			{\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)	& = \dfrac{{\color{magenta}b}{\color{red}P}(t)}{{\color{magenta}R}{\color{blue}T}(t,z)}	\label{eq: PR_B}.
 		\end{align}
@@
 
-	The quantity ${\color{orange}\alpha}\left[{\color{blue}T}\left(t,z\right)\right]$ is a dimensionless correction term that depends on the temperature ${\color{blue}T}\left(t,z\right)$ and a constant ${\color{magenta}\kappa}$.
+	The quantity ${\color{orange}\alpha}\left({\color{blue}T}\left(t,z\right)\right)$ is a dimensionless correction term that depends on the temperature ${\color{blue}T}\left(t,z\right)$ and a constant ${\color{magenta}\kappa}$.
 The constant ${\color{magenta}\kappa}$ is given by the formula ${\color{magenta}\kappa} = 0.37464 + 1.54226 {\color{magenta}\omega} - 0.26992 {\color{magenta}\omega^2}$, where ${\color{magenta}\omega}$ is the acentric factor of $CO_2$ molecules and is equal to 0.239.
 
-%	Using the physical constants $\varphi_{Z} = \left(R,T^c_{CO_2},P^c{CO_2},\kappa{CO_2}\right)$, we can represent the compressibility ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi{Z}\right]$ as a function of temperature and pressure with their complete set of functional dependencies and parameters.
+%	Using the physical constants $\varphi_{Z} = \left(R,T_c_{CO_2},P_c{CO_2},\kappa{CO_2}\right)$, we can represent the compressibility ${\color{orange}\overline{Z}}\left({\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi{Z}\right)$ as a function of temperature and pressure with their complete set of functional dependencies and parameters.
 
@@
 
-	The density of the fluid phase, denoted by $\rho_{\text{F}}$, is assumed to be equal to the density of the solvent at a given temperature and pressure.
-Since the temperature $T(t,z)$ of the fluid phase is a modelled variable, the density can vary both along the bed and in time.
-Using an equation of state in the form of ${\color{red}P}(t) {\color{orange}v_m}\left[T(t,z),P(t)\right] = {\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)$, the following expression for the density can be obtained:
+	The density of the fluid phase, denoted by ${\color{orange}\rho_f}$, is assumed to be equal to the density of the solvent at a given temperature and pressure.
+Since the temperature ${\color{blue}T}(t,z)$ of the fluid phase is a modelled variable, the density can vary both along the bed and in time.
+Using the definition of compressibility, the following expression for the density can be obtained:
 
@@
 		\begin{equation} \label{eq: Density}
-			{\color{orange}\rho_{\text{F}}} \left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid {\color{magenta}\varphi_{\rho_{\text{F}}}}\right] = \frac{{\color{red}P}(t) {\color{magenta}M_{CO_2}}}{{\color{magenta}R}{\color{blue}T}(t,z){\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z),{\color{red}P}(t) \mid \varphi{Z}\right]},
+			{\color{orange}\rho_f} \left({\color{blue}T}(t,z),{\color{red}P}(t) \right) = \frac{{\color{red}P}(t) {\color{magenta}M_{CO_2}}}{{\color{magenta}R}{\color{blue}T}(t,z){\color{orange}Z}\left({\color{blue}T}(t,z),{\color{red}P}(t) \right)},
 	\end{equation}}
 
-	where ${\color{magenta}M_{CO_2}}$ denotes the molar mass of $CO_2$, and ${\color{orange}\overline{Z}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ is the compressibility factor that solves Eq.
+	where ${\color{magenta}M_{CO_2}}$ denotes the molar mass of $CO_2$, and ${\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ is the compressibility factor that solves Eq.
 \eqref{eq: Compressibility}.
 This means that the density of the fluid depends on both space and time, due to its dependence on temperature and pressure.
-%	, and it can be expressed in terms of a set of physical constants, denoted by $\varphi{\rho_\text{F}} = \left({\color{magenta}R}, {\color{magenta}M_{CO_2}}, {\color{magenta}T^c{CO_2}}, {\color{magenta}P^c{CO_2}}, {\color{magenta}\omega{CO_2}}\right)$.
+%	, and it can be expressed in terms of a set of physical constants, denoted by $\varphi{\rho_\text{F}} = \left({\color{magenta}R}, {\color{magenta}M_{CO_2}}, {\color{magenta}T_c{CO_2}}, {\color{magenta}P_c{CO_2}}, {\color{magenta}\omega{CO_2}}\right)$.
 
@@
 	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}.
-The main steps in the derivation of ${\color{orange}C^{CO_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are presented below:
+The main steps in the derivation of ${\color{orange}C^{CO_2}_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ are presented below:
 
@@
 	\begin{subequations}\begin{align}
-			{\color{orange}C^{CO_2}_v}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] & = {\color{orange}C_v^{\text{I}}}\left[{\color{blue}T}(t,z),P(t)\right] + {\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] \label{eq: Cv_CO2}; \\
-			{\color{orange}C^{CO_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] & = \underbrace{{\color{orange}C_p^{\text{I}}}\left[{\color{blue}T}(t,z),P(t)\right]}_{\text{Eq.
-} \eqref{eq: Cp_I}} + \underbrace{{\color{orange}C_p^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}_{\text{Eq.
+			{\color{orange}C^{CO_2}_v}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) & = {\color{orange}C_v^{\text{I}}}\left({\color{blue}T}(t,z),P(t)\right) + {\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) \label{eq: Cv_CO2}; \\
+			{\color{orange}C^{CO_2}_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) & = \underbrace{{\color{orange}C_p^{\text{I}}}\left({\color{blue}T}(t,z),P(t)\right)}_{\text{Eq.
+} \eqref{eq: Cp_I}} + \underbrace{{\color{orange}C_p^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}_{\text{Eq.
 } \eqref{eq: Cp_R}}  \label{eq: Cp_CO2}.
@@
 
-	${\color{orange}C^{CO_2}_v}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}C^{CO_2}_p}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ are the specific heat of $CO_2$ at constant volume and pressure, respectively.
-${\color{orange}C_v^{\text{I}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}C_p^{\text{I}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$, with ${\color{orange}C_p^{\text{I}}}({\color{blue}T}(t,z)) - {\color{orange}C_v^{\text{I}}}({\color{blue}T}(t,z)) = {\color{magenta}R}$, are the specific heat of an ideal gas at constant volume and pressure.
-${\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]$ and ${\color{orange}C_p^{\text{R}}}({\color{blue}T}(t,z), {\color{red}P}(t))$ are the correction terms.
+	${\color{orange}C^{CO_2}_v}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}C^{CO_2}_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ are the specific heat of $CO_2$ at constant volume and pressure, respectively.
+${\color{orange}C_v^{\text{I}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}C_p^{\text{I}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$, with ${\color{orange}C_p^{\text{I}}}({\color{blue}T}(t,z)) - {\color{orange}C_v^{\text{I}}}({\color{blue}T}(t,z)) = {\color{magenta}R}$, are the specific heat of an ideal gas at constant volume and pressure.
+${\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}C_p^{\text{R}}}({\color{blue}T}(t,z), {\color{red}P}(t))$ are the correction terms.
 \\
 
-	For $CO_2$, the ideal gas contribution to the specific heat at constant $P(t)$, as function of $T(t,z)$ is given by,
+	For $CO_2$, the ideal gas contribution to the specific heat at constant ${\color{red}P}(t)$, as function of ${\color{blue}T}(t,z)$ is given by,
 
@@
 	\begin{equation}
-		{\color{orange}C_p^{\text{I}}}\left[{\color{blue}T}(t,z),P(t)\right] = {\color{magenta}C_{P0}} + {\color{magenta}C_{P1}}T(t,z) + {\color{magenta}C_{P2}}{\color{blue}T}^2(t,z) + {\color{magenta}C_{P3}}{\color{blue}T}^3(t,z) \label{eq: Cp_I}
+		{\color{orange}C_p^{\text{I}}}\left({\color{blue}T}(t,z),P(t)\right) = {\color{magenta}C_{P0}} + {\color{magenta}C_{P1}}T(t,z) + {\color{magenta}C_{P2}}{\color{blue}T}^2(t,z) + {\color{magenta}C_{P3}}{\color{blue}T}^3(t,z) \label{eq: Cp_I}
 	\end{equation} }
@@
 	where the coefficients ({\color{red}REF}) of the expansion are ${\color{magenta}C_{P0}} = 4.728$, ${\color{magenta}C_{P1}} = 1.75 \times 10^{-3}$, ${\color{magenta}C_{P2}} = -1.34 \times 10^{-5}$, and ${\color{magenta}C_{P3}} = 4.10 \times 10^{-9}$.
-For the correction term ${\color{orange}C_p^{\text{R}}}\left[{\color{blue}T}(t,z){\color{red}P}(t)\right]$ at constant pressure $P(t)$, we have
+For the correction term ${\color{orange}C_p^{\text{R}}}\left({\color{blue}T}(t,z){\color{red}P}(t)\right)$ at constant pressure ${\color{red}P}(t)$, we have
 
@@
 	\begin{align}
-		&{\color{orange}C_p^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] = \underbrace{{\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}_{\text{Eq.
+		&{\color{orange}C_p^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) = \underbrace{{\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}_{\text{Eq.
 }\eqref{eq: CvR}} \nonumber \\
 		&+ {\color{blue}T}(t,z) \underbrace{\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)}}_{\text{Eq.
-} \eqref{eq: dPdT}} \underbrace{\left(\cfrac{\partial {\color{orange}v_m}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)}}_{\text{Eq.
+} \eqref{eq: dPdT}} \underbrace{\left(\cfrac{\partial {\color{orange}v_m}\left({\color{blue}T}(t,z),{\color{red}P}(t)\right)}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)}}_{\text{Eq.
 } \eqref{eq: dVdT}} - {\color{magenta}R}.
@@
 
-	The braced terms are obtained from the chosen equation of state $P(t) V\left[T(t,z),P(t)\right] = Z\left[T(t,z),P(t)\right] R T(t,z)$. \\
+%	The braced terms are obtained from the chosen equation of state and the compressibility definition ${\color{red}P}(t) {\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t)) = {\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right){\color{magenta}R}{\color{blue}T}(t,z)$.
+\\
 
@@
 	\begin{align}
-		\left( \cfrac{\partial {\color{orange}v_m}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)} &= \cfrac{{\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right] {\color{magenta}R}}{{\color{red}P}(t)} \nonumber \\
-		&+ \cfrac{{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{red}P}(t)} \underbrace{\left( \cfrac{\partial {\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)}}_{\text{Eq.
+		\left( \cfrac{\partial {\color{orange}v_m}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)} &= \cfrac{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) {\color{magenta}R}}{{\color{red}P}(t)} \nonumber \\
+		&+ \cfrac{{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{red}P}(t)} \underbrace{\left( \cfrac{\partial {\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)}}_{\text{Eq.
 }\eqref{eq: dZdT}} \label{eq: dVdT}
@@
 
-	with partial derivative of the compressibility factor with respect to temperature $T$ at constant pressure $P(t)$
+	with partial derivative of the compressibility factor with respect to temperature ${\color{blue}T}$ at constant pressure ${\color{blue}P}(t)$
 
@@
 	\begin{equation}
-		\left(\cfrac{\partial{\color{orange}Z}\left[{\color{blue}T}(t,z), {\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} = \left(\cfrac{\partial \dfrac{{\color{red}P}(t) {\color{orange}v_m}\left[T(t,z),P(t)\right]}{{\color{magenta}R}{\color{blue}T}(t,z)}}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} \label{eq: dZdT}
+		\left(\cfrac{\partial{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} = \left(\cfrac{\partial \dfrac{{\color{red}P}(t) {\color{orange}v_m}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{{\color{magenta}R}{\color{blue}T}(t,z)}}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} \label{eq: dZdT}
 	\end{equation} }
@@
 	\begin{equation}
-		\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{magenta}v_m}\left[T(t,z),P(t)\right]}}}{\partial{\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} \label{eq: dPdT}
+		\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{orange}v_m}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}}}{\partial{\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} \label{eq: dPdT}
 	\end{equation} }
@@
 	\begin{equation}
-		{\color{orange}C_v^{\text{R}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right] = \left(\cfrac{\partial{\color{orange}U^{\text{R}}}\left[{\color{blue}T}(t,z),{\color{red}P}(t)\right]}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)}.
+		{\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z),{\color{red}P}(t)\right) = \left(\cfrac{\partial{\color{orange}U^{\text{R}}}\left({\color{blue}T}(t,z),{\color{red}P}(t)\right)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)}.
 \label{eq: CvR}
@@
 
-	%By denoting the physical constants as $\varphi_{C_p^{\text{F}}} = ({\color{magenta}R}, {\color{magenta}M},\\ {\color{magenta}T^c}, {\color{magenta}P^c}, {\color{magenta}\omega})$, we get the spatio-temporal representation \\$C_p^{\text{F}}\left[T(t,z),P(t) \mid \varphi_{C_p^{\text{F}}}\right]$ of the specific heat of the fluid phase.
+	%By denoting the physical constants as $\varphi_{C_p^{\text{F}}} = ({\color{magenta}R}, {\color{magenta}M},\\ {\color{magenta}T_c}, {\color{magenta}P_c}, {\color{magenta}\omega})$, we get the spatio-temporal representation \\$C_p^{\text{F}}\left(T(t,z),P(t) \mid \varphi_{C_p^{\text{F}}}\right)$ of the specific heat of the fluid phase.
 
@@
 		\begin{equation}
-			\frac{h^{id}-h}{RT} =\int_{v_m}^{\infty }\left[T\left({\frac{\partial Z}{\partial T}}\right)_{v_m}\right]{\frac{dv_m}{v_m}} + 1-Z
+			\frac{h^{id}-h}{RT} =\int_{v_m}^{\infty }\left(T\left({\frac{\partial Z}{\partial T}}\right)_{v_m}\right){\frac{dv_m}{v_m}} + 1-Z
 		\end{equation}
@@
 		\begin{equation}
-			h-h^{\mathrm {id} }=RT\left[T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right]
+			h-h^{\mathrm {id} }=RT\left(T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right)
 		\end{equation}

### 2023-06-27 SFE-article/Article_Model_Parameters.tex
27.06

@@
 Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
-The aim of this study was to investigate the supercritical extraction process of the caraway oil from caraway seeds from a partially filled extractor with a fixed bed that was operated under multiple constant operating conditions.
+This study aimed to investigate the supercritical extraction process of the caraway oil from caraway seeds from a partially filled extractor with a fixed bed operated under multiple constant operating conditions.
 The dataset collected from the experiments consists of four experiments conducted at different operating conditions: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar.
-To describe the fluid-solid extraction process with $CO_2$ as a solvent, a distributed-parameter model is used.
-To reduce the number of spatial dimensions, the concept of quasi-one-dimensional flow is applied.
-It is assumed that the flow is uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
+A distributed-parameter model is used to describe the fluid-solid extraction process with $CO_2$ as a solvent.
+The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
+The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
 This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, saturation concentration, and an initial state estimate.
@@
 The quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates are given by Equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_3}.
+The derivation of these Equations are presented in Appendix \ref{CH: Gouverning equations}.
 
@@
 	\begin{equation} \label{EQ: Pressure_Velocity}
-		\cfrac{d v}{d {\color{orange}\rho_f}} = - \cfrac{d v}{d{\color{blue}P}} \cfrac{d P}{d {\color{orange}\rho_f}} = -\cfrac{1}{\rho v} \cfrac{d{\color{blue}P}}{d{\color{orange}\rho_f}} = -\cfrac{v}{{\color{orange}\rho_f}}
+		\cfrac{d v}{d {\color{orange}\rho_f}} = - \cfrac{d v}{d{\color{blue}P}} \cfrac{d {\color{blue}P}}{d {\color{orange}\rho_f}} = -\cfrac{1}{\rho v} \cfrac{d{\color{blue}P}}{d{\color{orange}\rho_f}} = -\cfrac{v}{{\color{orange}\rho_f}}
 	\end{equation}

### 2023-06-27 SFE-article/Sections/Experiments.tex
07.05
27.06

@@
 
-	In order to solve the optimization problem presented in equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset $Y(t)$, which was obtained by extracting caraway oil from caraway seeds.
+	In order to solve the optimization problem presented in Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset ${\color{blue}Y}(t)$, which was obtained by extracting caraway oil from caraway seeds.
 To prepare the seeds for extraction, they were first pre-treated using a Retsch SM 300 cutting mill to reduce their particle size to 1mm and break their outer shell.
@@
 
-	After loading the material into the chamber, the extractor was pre-heated to the desired temperature.
+	After loading the material into the extraction chamber, the extractor was pre-heated to the desired temperature.
 The outlet line was then closed, and the extraction chamber was filled with $CO_2$.
@@
 The solvent extracted the essential oils from the solid material, and the resulting $CO_2$ and oil mixture flowed from the extractor to the separator.
-The separator operated at $50^\circ C$ and $50$ bar, with gaseous $CO_2$ exiting from the top and oil remaining at the bottom.
+The separator operated at $50^\circ C$ and $50$ bar.
+The gaseous $CO_2$ exited from the top and was recycled to the $CO_2$ storage tank.
+The oil stayed at the bottom of the separator in the liquid form.
 The extraction time for each batch was 150 minutes, measured from the opening of the extractor outlet port.
 Every 5 minutes, the oil was drained from the separator, and its weight was measured.
-The resulting time series $Y(t)$ corresponds to the output of measurement equation \ref{Model_measurment_1} and can be used for parameter estimation.
+The resulting time series ${\color{blue}Y}(t)$ corresponds to the output of measurement Equation \ref{Model_measurment_1} and can be used for parameter estimation.
 
 	The results of experiments are presented in the Table \ref{tab: Yield_data}.
+
+%	\begin{table}[!h]
+%		\centering
+%		\adjustbox{max width=\columnwidth}{%
+%		\begin{tabular}{ccccc}
+%			\hline
+%			& $40 ^\circ C / 200$ bar & $50 ^\circ C / 200$ bar & $40 ^\circ C / 300$ bar & $50 ^\circ C / 300$ bar \\ 
+%			Time min & Mass g                  & Mass g                  & Mass g                  & Mass g                  \\ \hline
+%			0        & 0.0                     & 0.0                     & 0.0                     & 0.0                     \\
+%			5        & 1.7                     & 1.8                     & 1.1                     & 1.2                     \\
+%			10       & 5.7                     & 4.7                     & 4.7                     & 4.5                     \\
+%			15       & 10.9                    & 9.5                     & 10.8                    & 11.3                    \\
+%			20       & 17.8                    & 15.1                    & 20.6                    & 20.6                    \\
+%			25       & 24.9                    & 21.3                    & 32.1                    & 30.6                    \\
+%			30       & 30.3                    & 26.4                    & 40.5                    & 37.8                    \\
+%			35       & 34.0                    & 29.8                    & 46.7                    & 43.3                    \\
+%			40       & 37.5                    & 33.1                    & 50.5                    & 47.5                    \\
+%			45       & 40.1                    & 35.6                    & 53.1                    & 50.8                    \\
+%			50       & 43.3                    & 38.7                    & 55.5                    & 53.7                    \\
+%			55       & 45.5                    & 41.5                    & 57.6                    & 56.5                    \\
+%			60       & 47.6                    & 43.5                    & 59.3                    & 58.1                    \\
+%			65       & 49.2                    & 45.9                    & 60.9                    & 59.6                    \\
+%			70       & 50.8                    & 48.3                    & 62.2                    & 61.1                    \\
+%			75       & 52.6                    & 50.8                    & 63.7                    & 62.7                    \\
+%			80       & 54.2                    & 52.9                    & 64.9                    & 64.4                    \\
+%			85       & 55.1                    & 55.3                    & 66.6                    & 65.8                    \\
+%			90       & 56.2                    & 57.2                    & 67.6                    & 66.7                    \\
+%			95       & 57.3                    & 58.3                    & 68.9                    & 67.4                    \\
+%			100      & 58.3                    & 59.4                    & 69.7                    & 68.2                    \\
+%			105      & 59.4                    & 60.4                    & 70.6                    & 69.1                    \\
+%			110      & 60.2                    & 61.6                    & 71.2                    & 70.1                    \\
+%			115      & 61.4                    & 62.7                    & 71.9                    & 70.9                    \\
+%			120      & 62.5                    & 63.9                    & 72.3                    & 71.6                    \\
+%			125      & 63.3                    & 64.7                    & 72.8                    & 72.3                    \\
+%			130      & 64.0                    & 65.4                    & 73.2                    & 72.9                    \\
+%			135      & 64.8                    & 65.9                    & 73.6                    & 73.5                    \\
+%			140      & 65.5                    & 66.4                    & 74                      & 74                      \\
+%			145      & 66.2                    & 67.1                    & 74.3                    & 74.5                    \\
+%			150      & 66.8                    & 67.7                    & 74.6                    & 74.9              		 \\ \hline     
+%		\end{tabular} }
+%	\caption{Yield data}
+%	\label{tab: Yield_data}
+%	\end{table}
 
@@
 		\adjustbox{max width=\columnwidth}{%
-		\begin{tabular}{ccccc}
-			\hline
-			& $40 ^\circ C / 200$ bar & $50 ^\circ C / 200$ bar & $40 ^\circ C / 300$ bar & $50 ^\circ C / 300$ bar \\ 
-			Time min & Mass g                  & Mass g                  & Mass g                  & Mass g                  \\ \hline
-			0        & 0.0                     & 0.0                     & 0.0                     & 0.0                     \\
-			5        & 1.7                     & 1.8                     & 1.1                     & 1.2                     \\
-			10       & 5.7                     & 4.7                     & 4.7                     & 4.5                     \\
-			15       & 10.9                    & 9.5                     & 10.8                    & 11.3                    \\
-			20       & 17.8                    & 15.1                    & 20.6                    & 20.6                    \\
-			25       & 24.9                    & 21.3                    & 32.1                    & 30.6                    \\
-			30       & 30.3                    & 26.4                    & 40.5                    & 37.8                    \\
-			35       & 34.0                    & 29.8                    & 46.7                    & 43.3                    \\
-			40       & 37.5                    & 33.1                    & 50.5                    & 47.5                    \\
-			45       & 40.1                    & 35.6                    & 53.1                    & 50.8                    \\
-			50       & 43.3                    & 38.7                    & 55.5                    & 53.7                    \\
-			55       & 45.5                    & 41.5                    & 57.6                    & 56.5                    \\
-			60       & 47.6                    & 43.5                    & 59.3                    & 58.1                    \\
-			65       & 49.2                    & 45.9                    & 60.9                    & 59.6                    \\
-			70       & 50.8                    & 48.3                    & 62.2                    & 61.1                    \\
-			75       & 52.6                    & 50.8                    & 63.7                    & 62.7                    \\
-			80       & 54.2                    & 52.9                    & 64.9                    & 64.4                    \\
-			85       & 55.1                    & 55.3                    & 66.6                    & 65.8                    \\
-			90       & 56.2                    & 57.2                    & 67.6                    & 66.7                    \\
-			95       & 57.3                    & 58.3                    & 68.9                    & 67.4                    \\
-			100      & 58.3                    & 59.4                    & 69.7                    & 68.2                    \\
-			105      & 59.4                    & 60.4                    & 70.6                    & 69.1                    \\
-			110      & 60.2                    & 61.6                    & 71.2                    & 70.1                    \\
-			115      & 61.4                    & 62.7                    & 71.9                    & 70.9                    \\
-			120      & 62.5                    & 63.9                    & 72.3                    & 71.6                    \\
-			125      & 63.3                    & 64.7                    & 72.8                    & 72.3                    \\
-			130      & 64.0                    & 65.4                    & 73.2                    & 72.9                    \\
-			135      & 64.8                    & 65.9                    & 73.6                    & 73.5                    \\
-			140      & 65.5                    & 66.4                    & 74                      & 74                      \\
-			145      & 66.2                    & 67.1                    & 74.3                    & 74.5                    \\
-			150      & 66.8                    & 67.7                    & 74.6                    & 74.9              		 \\ \hline     
-		\end{tabular} }
-	\caption{Yield data}
+			\csvautobooktabular{Figures/Results_estimation/Dataset.csv} }
+		\caption{Yield data; cumulative amount of solute [g] collected every 5 min}
 		\label{tab: Yield_data}

### 2023-06-27 SFE-article/Sections/Model.tex
27.06

@@
 	 %When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{magenta}\phi}(z)$ (where ${\color{magenta}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}
-	The discussed above quasi-one-dimensional assumption was used to derive the continuity equation for the fluid phase as presented in Appendix \ref{CH: Gouverning equations}.
+	The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function ${\color{magenta}A_f}(z) = {\color{magenta}A_f\phi}(z)$ to take into account the change of the cross-section available for the fluid.
 The cross-section change is taken into account by void fraction ${\color{magenta}\phi}(z)$, which depends on the spatial dimension.
@@
 
-			The heat equation was introduced in the previous chapter through Equation \ref{EQ: CompressibleEuler_3} and in the appendix \ref{CH: Gouverning equations}
+			The heat equation was introduced in the previous chapter through Equation \ref{EQ: CompressibleEuler_3}, in the appendix \ref{CH: Gouverning equations}  as well as through Equation \ref{EQ: Heat_internal}
 
 			{\footnotesize
-			\begin{align}
+			\begin{align} \label{EQ: Heat_internal}
 				&\cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{blue}e}(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) A_f v {\color{blue}e}(t,z) \right)}{\partial {\color{blue}z}} \nonumber \\
@@
 
-			If a gas is considered to be perfectly caloric (${\color{blue}e}(t,z)=C_v {\color{blue}T}(t,z)$), then the energy equation can be written in form of temperature.
-The perfectly caloric gas can be seen as the special case of a real gas, where the second term of the Equation \ref{EQ: internal_energy_def} goes to zero.
+			Suppose a gas is considered to be perfectly caloric (${\color{blue}e}(t,z)={\color{magenta}C_v} {\color{blue}T}(t,z)$), then the energy equation can be written explicitly in the form of temperature.
+The perfectly caloric gas can be seen as the special case of a real gas, where the second term of Equation \ref{EQ: internal_energy_def} goes to zero and the heat capacity ${\color{magenta}C_v}$ is constant.
 
 			For real gases, it is complicated to write the heat balance in terms of temperature, but it be can be used directly in the form of internal energy, as it is given by Equation \ref{EQ: CompressibleEuler_3}.
-In such a case, the temperature (which is used as the input to some other functions) needs to be recovered from the internal energy.
+In such a case, the temperature needs to be recovered from the internal energy.
 A relation for the internal energy can be obtained from an equation of state.
@@
 
-			To solve Equation \ref{EQ: internal_energy_PR}, values of temperature, pressure, and density need to be known.
-If an equation of state is introduced, then only two out of three variables need to be obtained as the third one can be calculated, this can be represented as follow
+			To solve Equation \ref{EQ: internal_energy_PR}, temperature, pressure, and density values need to be known.
+If an equation of state is introduced, then only two out of three variables need to be obtained as the third one can be calculated; this can be represented as follow
 
@@
 			If the value of internal energy ${\color{blue}e}(t,z)$ is known from the time evolution of the energy Equation \ref{EQ: CompressibleEuler_3}, and pressure is known from measurement, then the temperature can be reconstructed.
-A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution and the output from Equation \ref{EQ: internal_energy_PR}.
+A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution (Equation \ref{EQ: Heat_internal}) and the output from Equation \ref{EQ: internal_energy_PR}.
 Such a procedure allow to find local temperature along spatial direction ${\color{blue}z}$ and needs to be repeated every time-step.
@@
 				\begin{equation}
-					\begin{aligned}
-					&{\color{blue}h}(t,z)-{\color{blue}h}(t,z)^{id}={\color{magenta}R}{\color{blue}T}(t,z) \\
-					& \left[{\color{magenta}T_r}(Z-1)-2.078(1+{\color{magenta}\kappa} ){\sqrt {\alpha }}\ln \left(\cfrac{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}\right)\right]
+					\begin{split}
+					{\color{blue}h}(t,z)-{\color{blue}h}(t,z)^{id}={\color{magenta}R}{\color{blue}T}(t,z) \left[{\color{magenta}T_r}({\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)-1) \right.
+\\
+					\left.
+-2.078(1+{\color{magenta}\kappa} ){\sqrt { {\color{orange}\alpha}\left({\color{blue}T}(t,z)\right) } } \ln \left(\cfrac{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}\right)\right]
 					\label{EQ:Enthalpy_PR}
-				\end{aligned}
+				\end{split}
 			\end{equation}				
@@
 As explained in Chapters \ref{CH: Gouverning equations} and \ref{CH:Low_Mach_chapter}, at low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound.
-Under such conditions, the term $\partial P/\partial t$ can be approximated by an ordinary differential equation, which describes the instantaneous change of pressure in the system.
+Under such conditions, the term $\partial {\color{blue}P}/\partial t$ can be approximated by an ordinary differential equation, which describes the instantaneous change of pressure in the system.
 The pressure in the system is considered a state variable, while the pressure in the new time-step is considered a control variable.

### 2023-06-27 SFE-article/Sections/Parameter_estimation.tex
27.06

@@
 	The goal of parameter estimation is to obtain the "best" estimate of parameter set ${\color{magenta} \theta}$ (which is a subset of the parameter space ${\color{magenta}\Theta}$ containing all parameters of a model) based on the continuous observations ${\color{blue}Y}(t)$ or the discrete observations ${\color{blue}Y}(t_i)$.
-Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, ${\color{blue}y}(t)$ (Equation \ref{Model_measurment_1}), to give the observable dependent variable ${\color{blue}Y}(t)$ (for example results of an experiments).
+Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, ${\color{blue}y}(t)$ (Equation \ref{Model_measurment_1}), to give the observable dependent variable ${\color{blue}Y}(t)$ (for example results of an experiment).
 For discrete observations, this can be expressed as:
@@
 Although the MLE has often been associated with the normal distribution for mathematical convenience, it can be applied to a wide range of probability distributions.
-The derivation of the likelihood function under assumption of the Gaussian distribution is presented in the Appendix \ref{CH: ML}.
+The derivation of the likelihood function under the assumption of the Gaussian distribution is presented in Appendix \ref{CH: ML}.
 The final form of the objective function is presented by Equation \ref{EQ: Objective_function}:
@@
 
-	Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector ${\color{magenta} \theta}$ by equating to zero the partial derivatives of $\ln L$ with respect to each of the parameters:
+	Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector ${\color{magenta} \theta}$ and equating to zero the partial derivatives of $\ln L$:
 
@@
 		\begin{align}\label{EQ: MLE_Basic_Solution}
-			\cfrac{\partial \ln L}{\partial {\color{magenta} \theta}} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( y(t_i) | {\color{magenta} \theta} \right) }{\partial {\color{magenta} \theta}} = 0 
+			\cfrac{\partial \ln L}{\partial {\color{magenta} \theta}} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( {\color{blue}y}(t_i) | {\color{magenta} \theta} \right) }{\partial {\color{magenta} \theta}} = 0
 	\end{align} }
@@
 	Solution of Equations \ref{EQ: MLE_Basic_Solution} yield the desired estimates $\hat{{\color{magenta} \theta}}$.
-For some models, these equations can be explicitly solved for $\hat{{\color{magenta} \theta}}$ but in general no closed-form solution to the maximization problem is known or available, and an maximum likelihood estimator can only be found via numerical optimization.
+For some models, these equations can be explicitly solved for $\hat{{\color{magenta} \theta}}$ but in general, no closed-form solution to the maximization problem is known or available, and a maximum likelihood estimator can only be found via numerical optimization.
 

### 2023-06-27 SFE-article/Sections/Results.tex
27.06

@@
         \item Axial diffusion coefficient: \qquad$D_e^M$
-        \item Limiting concentration: \quad\qquad$C_{lim}$
-        \item Standard deviation: \qquad\qquad\quad$\sigma$
+        \item Decay curvature coefficient:\qquad$\Upsilon$
+        \item Standard deviation:\qquad\qquad\quad~$\sigma$
     \end{itemize}
@@
     Moreover, the initial state estimation was performed together with parameter estimation.
-The concentration of solute in the solid phase is assumed to be constant and uniformly distributed.
+The initial solute concentration in the solid phase is assumed to be uniformly distributed.
 On the other hand, the solute concentration in the fluid phase should not follow the same assumption as the solid phase.
-During the preparation period the solute diffuses to the fluid phase in contact with the solid particles.
+During the preparation period, the solute diffuses to the fluid phase in contact with the solid particles.
 Later, the solute in the fluid phase is partially moved along the extractor (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed).
-As a result, the distribution of solute mass in the fluid phase is assumed to not be uniform.
-Some conclusions can be drawn from the analysis of the initial part of each yield curve.
+As a result, the distribution of solute mass in the fluid phase is assumed not to be uniform.
+Some conclusions can be drawn from the analysis of the initial part of each yield curve obtained from the laboratory.
 It can be noticed that each curve at the beginning has a curvature, which is not linear.
-In a general sense, it can be said that a quadratic function could approximate the initial part of each extraction curve.
+Generally, a quadratic function could approximate the initial part of each extraction curve.
 A function that, after integration, gives a quadratic-like result is a straight line.
@@
 The details on the calculation are given in appendix \ref{CH: IC_BC}.
-The linear distribution can be defined if the total mass of solute $m_{total}$ and partition coefficient $\tau$ are know.
+The linear distribution can be defined if the total mass of solute $m_{total}$ and partition coefficient $\tau$ are known.
 
@@
 			\hline 
-			Parameter		&$k_m$[-] 	& $D_i$[m/s$^2$] 	& $D_e^M$[m/s$^2$]	& $C_{lim}$ [kg/m$^3$] 	& $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
+			Parameter		&$k_m$[-] 	& $D_i$[m/s$^2$] 	& $D_e^M$[m/s$^2$]	& $\Upsilon$ [m$^3$/kg] & $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
 			Lower bound		&0	  		& 0 	  			& 0 				&	0					& 80 		 		& 0 	   		& 0 \\ 
-			Upper bound		&1 			& $+\infty$ 		& $+\infty$			&	$+\infty$			& 150 				& 1 			& $+\infty$ \\ 
-			Initial guess	&1	  		& 3 	  			& 1 				&	3					& 80 		 		& 0.65 	   		& 0.1 \\  \hline
+			Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			&	100					& 150 				& 1 			& $+\infty$ \\ 
+			Initial guess	&1e5 		& 3 	  			& 1 				&	0					& 80 		 		& 0.65 	   		& 0.1 \\  \hline
 		\end{tabular} }
@@
 	The results of parameter estimation can be found in Table \ref{tab: Estimation_results} and the concentration profiles, which correspond for the optimized solution for each experiments, are presented on Figure \ref{fig: estimation_results_profiles} in Appendix \ref{CH: Profiles}.
-As can be noticed, the optimizer found that the partition factor should be as high as possible and moved values of $k_m$ for each experiment to unity, which was chosen as the upper bound.
+As can be noticed, the optimizer found that the partition factor should be as high as possible.
+Such a behaviour suggest that the solvent is far from the saturation, and the model can be simplified.
+The model reduction can be introduced by considering the limit of the concentration gradient
+
+	{\footnotesize
+	\begin{equation*}
+		\begin{split}
+			&\lim_{k_m \rightarrow \infty} \left({\color{blue}{\color{blue} c_s} }(t,z)  - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)  = \\
+			&= \left({\color{blue}{\color{blue} c_s} }(t,z)  - \cfrac{{\color{magenta}\rho_s}}{\infty{\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right) = \left({\color{blue}{\color{blue} c_s} }(t,z) - 0 \right)
+		\end{split}
+	\end{equation*} }
 

### 2023-06-27 SFE-article/Sections/Saturation.tex
27.06

--- 2023-05-07 SFE-article/Sections/Saturation.tex
@@
 
-	\subsubsection{Saturation Concentration}
+	\subsubsection{Uneven distribution of the solute in the solid phase}
 
-	The above model does not take into account the saturation of fluid, which can be introduced by multiplying the gradient by a function $\gamma(c_f)$ (equation \ref{EQ: C_sat_function}).
-$\gamma(c_f)$ describe the reverse logistic function, which is equal to unity below the $c_{sat}$, the saturation concentration, and equal to zero, above the $c_{sat}$.
-The $\gamma(c_f)$ for $c_{sat}=5$ is shown on figure \ref{fig: Gamma_function}.
+%	To mimic that not all solute might be obtained at specific operating conditions, the coefficient ${\color{orange} \gamma}$ is introduced to limit the available oil.
+The ${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ describe the reverse logistic function, which is equal to unity above the ${\color{magenta} c_{lim}}$, the saturation concentration, and equal to zero, below the ${\color{magenta} c_{lim}}$.
+The ${\color{orange} \gamma}$ parameter multiply the solute concentration term in solid phase in the concentration gradient.
+As the concentration of solute decrease, it can reach the limiting value ${\color{magenta} c_{lim}}$ when the ${\color{orange} \gamma}$ goes to zero and stop the extraction from the solid.
+%			
+%	{\footnotesize
+%		\begin{equation}
+%			{\color{orange} \gamma}({\color{blue} c_s} (t,z)) = \cfrac{1}{1+\exp \left( -{\color{magenta} k_{lim}} \left( {\color{blue} c_s} (t,z) - {\color{magenta} c_{lim}} \right) \right) }
+%			\label{EQ: C_sat_function}
+%			\end{equation}
+%	}
+%			
+%	where ${\color{magenta} k_{lim}}$ describe the curvature of the $\gamma$ function, and it is defined as ${\color{magenta} k_{lim}} = 1$.
+%In the limit when $ {\color{magenta} k_{lim}}\rightarrow+\infty$ become a step function.
+If the ${\color{magenta} k_{lim}}$ is to high, the gradient of the ${\color{orange} \gamma}$ function become high, or goes to infinity, which might cause difficulties for a gradient-based optimizer.
+%	The ${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ gamma function is visualised on \ref{fig: Gamma_function}.
+%			
+%	\begin{figure}[h!]
+%		\centering
+%			\begin{tikzpicture}
+%					
+%				\begin{axis}[
+%					legend style={draw=none},
+%					xmin = 0, xmax = 100,
+%					ymin = -0.5, ymax = 1.5,
+%					xlabel = {${\color{blue} c_s}(t,z)[kg/m^3]$},
+%					ylabel = {${\color{orange} \gamma}({\color{blue} c_s}(t,z))[-]$}]
+%					\addplot[
+%					domain = 0:100,
+%					samples = 100,
+%					smooth,
+%					thick,
+%					blue,
+%					] { 1 / (1 + exp( 1 * ( 50 - x ) ) ) };
+%					\addplot[thick, samples=50, dashed, domain=0:1.5, black] coordinates {(50,-0.5)(50,1.5)};
+%					
+%					\addlegendentry{${\color{orange} \gamma}({\color{blue} c_s} (t,z))$}
+%					\addlegendentry{${\color{magenta} c_{lim}}$}
+%				\end{axis}
+%					
+%			\end{tikzpicture}
+%			\caption{${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ function under assumption of ${\color{magenta} c_{lim}}=50~[kg/m^3]$}
+%			\label{fig: Gamma_function}
+%	\end{figure}
+
+	Following the idea of the Broken-and-Intact Cell (BIC) model presented by \citet{Sovova2017}, the coefficient ${\color{orange} \gamma}$ is introduced to limit the available oil.
+The ${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ describes the decay function, which is equal to unity and slowly decays when the amount of the solute in the solid phase decrease.
+Similarly to the BIC model, this can be explained if oil is assumed to be contained in the cells, a part of which is open because the cell walls were broken by grinding, and the rest remains intact.
+The ${\color{orange} \gamma}$ parameter multiply the internal diffusion term to indicate that the diffusion of the solute from a particle's core takes more time compared to the diffusion of the solute located close to the outer surface.
 
@@
 		\begin{equation}
-			\gamma(c_f) = \cfrac{1}{1+\exp ( -k_{sat} \left( c_f - c_{sat} \right) ) }
-			\label{EQ: C_sat_function}
-			\end{equation}
-	}
+			{\color{orange} \gamma}({\color{blue} c_s} (t,z)) = \exp\left( {\color{magenta}\Upsilon} \left( 1-\cfrac{{\color{blue} c_s} (t,z) }{{\color{magenta}c_{s0}}} \right) \right) \label{EQ: C_sat_function}
+		\end{equation} }
 
-	where $k_{sat}$ is the growth rate, and it is defined as $k_{sat} = 4$.
-The growth rate corresponds for the shape of the $\gamma(c_f)$ function.
-The bigger value of the $k_{sat}$ the steeper the function is.
-In the limit when $ k_{sat}\rightarrow+\infty$ become a step function.
-If the growth rate is to high, the gradient of the $\gamma$ function become high, or goes to infinity, which might cause difficulties for a gradient-based optimizer.
+	where the ${\color{magenta}\Upsilon}$ describe the curvature of the decay function. The final form of the extraction kinetic equation is given by equation \ref{Model_kinetic}.
 
-	\begin{figure}[h!]
-		\centering
-			\begin{tikzpicture}
-
-				\begin{axis}[
-					legend style={draw=none},
-					xmin = 0, xmax = 10,
-					ymin = -0.5, ymax = 1.5,
-					xlabel = {$c_f[kg/m^3]$},
-					ylabel = {$\gamma(c_f)[-]$}]
-					\addplot[
-					domain = 0:10,
-					samples = 100,
-					smooth,
-					thick,
-					blue,
-					] { 1 / (1 + exp( 4 .* ( x - 5 ) ) ) };
-					\addplot[thick, samples=50, dashed, domain=0:1.5, black] coordinates {(5,-0.5)(5,1.5)};
-
-					\addlegendentry{$\gamma(c_f)$}
-					\addlegendentry{$c_{sat}$}
-				\end{axis}
-
-			\end{tikzpicture}
-			\caption{$\gamma(c_f)$ function under assumption of $c_{sat}=5 [kg/m^3]$}
-			\label{fig: Gamma_function}
-	\end{figure}
-
-	The final form of the extraction kinetic equation is given by equation \ref{Model_kinetic}.
-
-	{\footnotesize
+	{\scriptsize
 		\begin{equation}
 			\label{Model_kinetic}
-				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t))}{{\color{magenta} \mu l^2} } \gamma(c_f) \left({\color{blue}c_s}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
+				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t)) {\color{orange} \gamma}({\color{blue} c_s} (t,z)) }{{\color{magenta} \mu l^2} } \left({\color{blue}{\color{blue} c_s} }(t,z)  - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
 		\end{equation} }

### 2023-06-27 SFE-article/Sections/Thermo_imp.tex
27.06

@@
 	Supercritical $CO_2$'s thermodynamic properties, such as density, the local speed of sound, and specific heat capacity, vary significantly with slight changes in temperature and pressure due to real gas effects.
-The Peng-Robinson equation of state (P-R EOS) is used to calculate the thermodynamic properties by accounting for these real gas effects are presented Appendix \ref{subsubsec: Equation of state}.
+The Peng-Robinson equation of state (P-R EOS) is used to calculate the thermodynamic properties by accounting for these real gas effects are presented in Appendix \ref{subsubsec: Equation of state}.
 The P-R EOS belongs to a specific class of thermodynamic models for modelling the pressure of a gas as a function of temperature and density.
@@
 The ideal gas serves as a reference state to which the properties of real gases are compared.
-The departure function is a measure of the extent to which a real gas deviates from ideal gas behaviour.
+The departure function measures the extent to which a real gas deviates from ideal gas behaviour.
 The departure functions allow for the accurate calculation of thermodynamic properties for real gases.
@@
 However, at high pressures and/or low temperatures, intermolecular forces between gas molecules become more significant, causing them to deviate from ideal behaviour.
-As a result, the compressibility factor can either be greater than or less than unity, depending on the magnitude of these forces.
+As a result, the compressibility factor can be greater than or less than unity, depending on the magnitude of these forces.
 As presented in Figure \ref{fig: SFE_Properties_Compressibility}, the compressibility factor obtained from the Peng-Robinson equation of state varies strongly depending on the operating conditions.
@@
 	The real gas effects are also visible on the density plot presented in Figure \ref{fig: SFE_Properties_Density}.
-The density calculations are based on the compressibility factor and its value depends on the operating conditions.
+The density calculations are based on the compressibility factor, and its value depends on the operating conditions.
 The fluid properties near the critical point are unique and combine gas-like and liquid-like properties.
@@
 	Figure \ref{fig: SFE_Properties_CP} show the behaviour of the heat capacity of a supercritical fluid at constant pressure ($C_p$).
-The details of the calculations can be found in the Appendix \ref{subsubsec: Fluid heat capacity}.
+The details of the calculations can be found in Appendix \ref{subsubsec: Fluid heat capacity}.
 Contrary to the density, which varies monotonically, the specific heat shows very high levels in a narrow region.
@@
 At the critical point, the latent heat is zero, but the heat capacity shows a diverging singularity.
-Beyond the critical point, there is no divergence, but rather a smooth peak in the heat capacity; the highest point of this peak identifies the Widom line (as discussed by \citet{Simeoni2010} and \citet{Banuti2019}).
+Beyond the critical point, there is no divergence, but rather a peak in the heat capacity; the highest point of this peak identifies the Widom line (as discussed by \citet{Simeoni2010} and \citet{Banuti2019}).
 

### 2023-06-27 SFE - MegaFit/Plot_Fit.m

@@ -4,9 +4,10 @@ hold on
 plot(Time  , xx_0(Nx,:)  ,'k'    , 'LineWidth',2)
 plot(Time  , xx_out(Nx,:),'r'    , 'LineWidth',2)
 plot(SAMPLE, data_org    ,'bo'   , 'LineWidth',2)
-%plot(Time, 1e3 * (sum(xx_out(0*nstages+1:1*nstages,:) .* V_fluid) + sum(xx_out(1*nstages+1:2*nstages,:) .* V_solid)) + xx_out(Nx,:));
+plot(Time, 1e3 * (sum(xx_out(0*nstages+1:1*nstages,:) .* V_fluid) + sum(xx_out(1*nstages+1:2*nstages,:) .* V_solid)) + xx_out(Nx,:));
 hold off
 
+ylim([0 m_total+5])
 xlabel('Time [min]')
 ylabel('Yield [g]')
 

### 2023-06-27 SFE - MegaFit/Saturation_Concentration.m

@@ -1,7 +1,7 @@
-function [FLUID_SAT] = Saturation_Concentration(SOLID, C_SAT, km)
+function [FLUID_SAT] = Saturation_Concentration(SOLID, shape, km)
 
-    k = 25;            % Growth rate
+    %k = shape;                         % Growth rate
     %L = 0.5*C_SAT;          % Location of midpoint
-    FLUID_SAT = km ./ (1 + exp( k .* ( SOLID - C_SAT ) ) );
-
+    %FLUID_SAT = km ./ (1 + exp( shape .* ( SOLID - C_SAT ) ) );
+    FLUID_SAT = km .* exp( -shape .* ( SOLID ) );
 end

### 2023-06-27 SFE - MegaFit/main_Fitting_MegaFit.m

@@ -8,31 +8,27 @@ import casadi.*
 
 Parameters_table        = readtable('Parameters.csv') ;        % Table with prameters
 Parameters              = num2cell(Parameters_table{:,3});
-Parameters_sym          = MX(cell2mat(Parameters));
 
 %% Create the solver
-OPT_solver                  = casadi.Opti();
-
-Iteration_max               = 3000;                                          % Maximum number of iterations for optimzer
-Time_max                    = 72.0;                                          % Maximum time of optimization in [h]
+Iteration_max               = 1000;                                         % Maximum number of iterations for optimzer
+Time_max                    = 5.0;                                          % Maximum time of optimization in [h]
 
 nlp_opts                    = struct;
 nlp_opts.ipopt.max_iter     = Iteration_max;
 nlp_opts.ipopt.max_cpu_time = Time_max*3600;
+nlp_opts.ipopt.acceptable_tol  = 1e-4;
+nlp_opts.ipopt.acceptable_iter = 5;
 
-ocp_opts                    = {'nlp_opts', nlp_opts};
-OPT_solver.solver(             'ipopt'   , nlp_opts)
-
-which_k                 = [     8, 44, 45, 47            ];                      % Select which parameters are used for fitting
-k0                      = [     1,  3,  1, 0.9, 0.7,  0.2];                      % Give inital value for each parameter
-k_lu                    = [ [0.05;  0;  0;   0;   0;    0], ...
-                          [  inf; inf;inf;   1;   1; inf]];
+which_k                 = [     8, 44,   45,  48            ];              % Select which parameters are used for fitting
+k0                      = [  1000,  3,    1,   0,   1,  0.05];              % Give inital value for each parameter
+k_lu                    = [ [0.01;  0;    0;   0;   0;    0 ], ...
+                          [   inf; inf; inf; 100;   1; inf] ];
 Nk                      = numel(which_k)+2;                                 % Parameters within the model + (m_max), m_ratio, sigma
 
-%m_total                 = 90;
+m_total                 = 80;
 
[…]

### 2023-06-27 SFE - MegaFit/modelSFE.m

@@ -24,7 +24,8 @@ function xdot = modelSFE(x, p, mask, dt)
 
     Di            =     parameters{44};      Di = Di * 1e-14;
     Dx            =     parameters{45};      Dx = Dx * 1e-6;
-    C_SAT         =     parameters{47};
+    %SAT           =     parameters{47};
+    shape         =     parameters{48};
 
     nstages_index =     numel(mask);
     
@@ -57,8 +58,9 @@ function xdot = modelSFE(x, p, mask, dt)
     KRHOCP        =     kRHOcp_Comp(     TEMP, PRESSURE, Z, RHO, CP, epsi.*mask, parameters);
 
     %% Saturation
-    Colid_percentage_left = 1 - (SOLID./C0solid);
-    Sat_coe       =     Saturation_Concentration(Colid_percentage_left, C_SAT, km); % Inverse logistic is used to control saturation. Close to saturation point, the Sat_coe goes to zero.
+    Csolid_percentage_left = 1 - (SOLID./C0solid);
+    Csolid_percentage_left(find(~mask)) = 0;                                              % inserte zeros instead of NAN in pleces where there is no bed
+    Sat_coe       =     Saturation_Concentration(Csolid_percentage_left, shape, Di); % Inverse logistic is used to control saturation. Close to saturation point, the Sat_coe goes to zero.
 
     %% BC
     %Cf_0          =     if_else(F_u == 0, FLUID(1), 0);
@@ -97,8 +99,8 @@ function xdot = modelSFE(x, p, mask, dt)
 
     dPdt          = backward_diff_1_order(P_u, PRESSURE, [], dt)*1e2;
    
-    re = (1 ./ mi ./ lp2 .* Di)  .* ( SOLID .* Sat_coe - FLUID );
-
+    re            = (Sat_coe ./ mi ./ lp2)  .* ( SOLID - FLUID .* rho_s ./ RHO ./ km );
+    
     %%
 
     xdot = [

### 2023-06-27 SFE-article/Sections/Results.tex
27.06

@@
 
-	The further spifflication of the process model can be introduced based on $C_{lim}$ results.
-Values of saturation concentrations are at the level of 1e5 which is an internal upper bound of the optimizer used if $+\infty$ indicates the upper bound.
-This suggest that solvent hasn't reach the saturation concentration and the process model can be simplified by replacing $\gamma(c_f)$ function with unity.
+	The $\Upsilon$ coefficient
 

### 2023-06-28 SFE-article/Sections/Results.tex
28.06

@@
 			\hline 
-			Parameter		&$k_m$[-] 	& $D_i$[m/s$^2$] 	& $D_e^M$[m/s$^2$]	& $\Upsilon$ [m$^3$/kg] & $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
+			Parameter		&$k_m$[-] 	& $D_i$[$m^2/s$] 	& $D_e^M$[$m^2/s$]	& $\Upsilon$ [m$^3$/kg] & $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
 			Lower bound		&0	  		& 0 	  			& 0 				&	0					& 80 		 		& 0 	   		& 0 \\ 
@@
 The plots on the right hand-side, represent the derivative of the cumulative yield curves.
-As explained in the chapter \ref{CH: Parameter_estimation}, the derivatives of the cumulative measurements are independent on the previous measurement and should be used for the parameter estimation.
+As explained in the Chapter \ref{CH: Parameter_estimation}, the derivatives of the cumulative measurements are independent on the previous measurement and should be used for the parameter estimation.
 
@@
 	The results of parameter estimation can be found in Table \ref{tab: Estimation_results} and the concentration profiles, which correspond for the optimized solution for each experiments, are presented on Figure \ref{fig: estimation_results_profiles} in Appendix \ref{CH: Profiles}.
+
+	\begin{figure}[!h]
+		\centering
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
+			\caption{Experiment at $40^\circ C$ and $200$ bar}
+		\end{subfigure}
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
+			\caption{Experiment at $50^\circ C$ and $200$ bar}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
+			\caption{Experiment at $40^\circ C$ and $300$ bar}
+		\end{subfigure}
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
+			\caption{Experiment at $50^\circ C$ and $300$ bar}
+		\end{subfigure}
+		\caption{Results of parameter fitting, with estimation of the initial state}
+		\label{fig: estimation_results}
+	\end{figure}
+
 	As can be noticed, the optimizer found that the partition factor should be as high as possible.
@@
 
-	Values of the internal diffusion coefficients are distinguished for each experiment, which grows as the fluid density increase.
+	Values of the internal diffusion coefficients are distinguished for each experiment.
 The order of magnitude of $D_i$ obtained from the optimization is similar to values found by other researchers.
 \citet{Reverchon1996} performed the parameter estimation for the extraction process of sage oil from seeds and reported $D_i \approx 6e-13$.
+The $\gamma$ (Equation \ref{EQ: C_sat_function}) coefficient multiply the reference value of $D_i$ to take into consideration that solute inside of a particle is harder to obtain than the solute close to the outer surface, as explained before.
+The Figure \ref{fig:Di_upsilon_res} shows how the internal diffusivity as a function of the solute's concentration in the solid phase.
+It can be observed that the obtained values of $D_i$ increase as the density increase.
+This behaviour can be explained by an increase in solubility when the density grow.
+\citet{Shojaie2010}, proved that the carvone (which is one of the main components of caraway oil) solubility increase together with pressure increase and decrease when temperature increase.
+
+	\begin{figure}
+		\centering
+		\includegraphics[trim = 2cm 0.4cm 2cm 0.5cm, clip, width=\columnwidth]{/Results_estimation/D_i_Uppsilon_results.pdf}
+		\caption{The dependence of the internal diffusion coefficient on the solutes concentration in the solid phase}
+		\label{fig:Di_upsilon_res}
+	\end{figure}
 
@@
 The relatively high values of the axial diffusion coefficients might be justified by taking into account low values of flow rate used in all the experiments.
-
-	The $\Upsilon$ coefficient
 
@@
 Both datasets have higher deviation of the data points from the simulated curve.
-
-	\begin{figure}[!h]
-		\centering
-		\begin{subfigure}[b]{\columnwidth}
-			\centering
-			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
-			\caption{Experiment at $40^\circ C$ and $200$ bar}
-		\end{subfigure}
-		\begin{subfigure}[b]{\columnwidth}
-			\centering
-			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
-			\caption{Experiment at $50^\circ C$ and $200$ bar}
-		\end{subfigure}
-		\begin{subfigure}[b]{\columnwidth}
-			\centering
-			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
-			\caption{Experiment at $40^\circ C$ and $300$ bar}
-		\end{subfigure}
-		\begin{subfigure}[b]{\columnwidth}
-			\centering
-			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
-			\caption{Experiment at $50^\circ C$ and $300$ bar}
-		\end{subfigure}
-		\caption{Results of parameter fitting, with estimation of the initial state}
-		\label{fig: estimation_results}
-	\end{figure}
 
@@
 
-	The results of the linear regression applied to $D_i$ and $D_e^M$ are presented in Figure \ref{fig:Regression_1}.
-It can be observed that the internal diffusion coefficient increases with increasing fluid density, while the axial diffusion coefficient decreases.
-
-	The increase in the density of the supercritical fluid can lead to an increase in the solubility of the solute and, consequently, an increase in the concentration gradient.
-This increased concentration gradient drives the solute to diffuse more rapidly through the matrix of the solid particles, resulting in an increased internal mass transfer coefficient.
-However, the effect of increased solubility on the internal mass transfer coefficient outweighs the resistance from higher density, resulting in an overall increase in the internal mass transfer coefficient with density.
-The same behaviour can be observed in Figure \ref{fig: estimation_results}, where plots on the right-hand side exhibit a peak.
-The higher the peak, the greater the increase in solute concentration in the fluid phase, which can be explained by higher solubility.
-
-	The behaviour of the axial diffusion coefficient can be explained through Graham’s Law of Diffusion, which states that the rate of diffusion of a molecule is inversely proportional to the square root of its density under given conditions of temperature and pressure.
-This means that denser media slow down the axial diffusion rate of molecules.
-
-	{\color{red}IDEAL I SHOULD SUPPORT THIS EXPLANATION WITH SOME REFERENCES}
-
-	Figure \ref{fig:Regression_2} show the result of fitting a second-order polynomial in density space.
-It can be observed that the fit obtained from quadratic functions seems to be represent both dataset better.
-
-	The experimental procedure and the used device can influence the values of $\tau$ and $\sigma$.
-Therefore, seeking a general expression for the initial state that is solely a function of operating conditions may not be sufficient to fully describe the relationship between these parameters.
-However, if first- and second-order regressions are applied to $\tau$ and $\sigma$, some general conclusions about the trend can be drawn.
-The results of the regression applied to $\tau$ and $\sigma$ are presented in Figure \ref{fig:Regression_tau_simga}.
-
-	\begin{figure}[!h]
-		\centering
-		\begin{subfigure}[b]{\columnwidth}
-			\centering
-			\includegraphics[trim = 18.8cm 8cm 2.5cm 7.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
-			\includegraphics[trim = 4cm 2cm 17.5cm 13.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
-			\caption{First order polynomial regression of fitted parameters ($\tau$ and $\sigma$) as a function of fluid density $\rho_f$}
-			\label{fig:Regression_3}
-		\end{subfigure}
-		\begin{subfigure}[b]{\columnwidth}
-			\centering
-			\includegraphics[trim = 18.8cm 8cm 2.5cm 7.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
-			\includegraphics[trim = 4cm 2cm 17.5cm 13.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
-			\caption{Second order polynomial regression of fitted parameters ($\tau$ and $\sigma$) as a function of fluid density $\rho_f$}
-			\label{fig:Regression_4}
-		\end{subfigure}
-		\caption{Regression of $\tau$ and $\sigma$} 
-		\label{fig:Regression_tau_simga}
-	\end{figure}
-
-	As can be seen from Figure \ref{fig:Regression_tau_simga} , the $\tau$ seems to decrease as the fluid density increase.
-The standard deviation increases as the fluid density increase.
-As mentioned above, these results should be used with caution due to uninvestigated influence of the equipment on the extraction results.
-
-	To prove that the obtained solution is a global solution, the parameter estimation problem was run from multiple initial conditions.
-The Appendix \ref{CH: Profiles_2}, contain a solution of the optimization solution and corresponding figures.
-
 \end{document}

### 2023-06-28 SFE - MegaFit/mtcombvec.m

@@ -1,0 +1,29 @@
+function c = mtcombvec(varargin)
+% my own implementation of combvec for use in octave or without matlab nnet library
+% 
+% takes args of column-vectors, produces all combinations thereof
+%
+
+% copyright (c) 2018 Michael Tesch, tesch1@gmail.com
+% released under the Apache 2.0 Open Source license.
+
+if length(varargin)==0
+    c = [];
+    return
+end
+
+c = varargin{1};
+
+for i=2:length(varargin)
+    % make sure varargin{i} isn't more than 2d matrix
+    if length(size(varargin{i}))>2
+        error(sprintf('parameters must be 2d matrices (check arg %d)', i));
+    end
+    c = mtextend(c, varargin{i});
+end
+
+function cc = mtextend(old, new)
+mm = size(old,2);
+nn = size(new,2);
+cc = repmat(old, 1, nn);
+cc = [cc ; repmat(new, 1, mm)];

### 2023-06-28 SFE-article/Sections/Model.tex
29.06

@@
 					\cfrac{\partial {\color{blue}h}(t,z)}{\partial t} \\
+					\cfrac{\partial {\color{blue}P}(t,z)}{\partial t} \\
 					\cfrac{\partial {\color{blue}y}(t)}{\partial t} 
@@
 					{\color{blue}\bar{\phi_3}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right) \\
-					{\color{blue}\bar{\phi_4}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)
+					{\color{blue}\bar{\phi_4}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)\\
+					{\color{blue}\bar{\phi_5}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)
 				\end{bmatrix} = {\color{blue}\bar{\phi}} \left( t,z; {\color{magenta}\Theta} \right) = \cfrac{\partial {\color{blue}\chi}(t,z)}{\partial t}
@@
 						\\ \hline \\
+						\cfrac{d {\color{blue}P}(t)}{d t} \\
+						\\ \hline \\
 						\cfrac{d {\color{blue}y}(t)}{d t}
@@
 							\\ \\ \hline \\
-							{\color{orange}G_{3N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right) 
+							{\color{orange}G_{3N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right) \\
+							\\ \\ \hline \\
+							{\color{orange}G_{3N_z+2}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right) 
 					\end{bmatrix}}_{{\color{orange}G} \left( {\color{blue}x}(t); {\color{magenta}\Theta} \right)} 

### 2023-06-28 SFE-article/Sections/Results.tex
29.06

@@
 		\end{subfigure}
-		\caption{Results of parameter fitting, with estimation of the initial state}
+		\caption{Results of parameter estimation}
 		\label{fig: estimation_results}
@@
 
-	As can be noticed, the optimizer found that the partition factor should be as high as possible.
+	Based on the Table \ref{tab: Estimation_results}, the optimizer found optimal values of the partition factors at relatively high.
 Such a behaviour suggest that the solvent is far from the saturation, and the model can be simplified.
@@
 The $\gamma$ (Equation \ref{EQ: C_sat_function}) coefficient multiply the reference value of $D_i$ to take into consideration that solute inside of a particle is harder to obtain than the solute close to the outer surface, as explained before.
-The Figure \ref{fig:Di_upsilon_res} shows how the internal diffusivity as a function of the solute's concentration in the solid phase.
+The curvature of the $\gamma$ function is described by a $\Upsilon$.
+The higher the value of $D_i \times \gamma$, the higher
+
 	It can be observed that the obtained values of $D_i$ increase as the density increase.
@@
 \citet{Shojaie2010}, proved that the carvone (which is one of the main components of caraway oil) solubility increase together with pressure increase and decrease when temperature increase.
+$D_i$ and $\Upsilon$ can be related directly to
 
-	\begin{figure}
+		\begin{figure*}[!h]
 		\centering
-		\includegraphics[trim = 2cm 0.4cm 2cm 0.5cm, clip, width=\columnwidth]{/Results_estimation/D_i_Uppsilon_results.pdf}
+		\begin{subfigure}[b]{0.32\textwidth}
+			\centering
+			\includegraphics[trim = 10.5cm 14cm 10cm 1.5cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
+			\caption{Experiment at $40^\circ C$ and $200$ bar}
+		\end{subfigure}
+		\begin{subfigure}[b]{0.32\textwidth}
+			\centering
+			\includegraphics[trim = 3cm 8cm 17.7cm 7.7cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
+			\caption{Experiment at $50^\circ C$ and $200$ bar}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.32\textwidth}
+			\includegraphics[trim = 2cm 0.4cm 2cm 0.9cm, clip, width=\columnwidth]{/Results_estimation/D_i_Uppsilon_results.pdf}
 			\caption{The dependence of the internal diffusion coefficient on the solutes concentration in the solid phase}
 			\label{fig:Di_upsilon_res}
-	\end{figure}
+		\end{subfigure}
+		\caption{Results of parameter estimation}
+		%\label{fig: estimation_results}
+	\end{figure*}
+
+	The Figure \ref{fig:Di_upsilon_res} shows how the internal diffusivity as a function of the solute's concentration in the solid phase.
 
@@
 
-	\begin{figure}[!h]
-	\centering
-	\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[trim = 11.7cm 14cm 2.3cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
-		\caption{First-order polynomial regression of fitted parameters ($D_i$ and $D_e^M$) as a function of fluid density $\rho_f$}
-		\label{fig:Regression_1}
-	\end{subfigure}
-	\begin{subfigure}[b]{\columnwidth}
-		\centering
-		\includegraphics[trim = 11.7cm 14cm 2.3cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_2.pdf}
-		\caption{Second-order polynomial regression of fitted parameters ($D_i$ and $D_e^M$) as a function of fluid density $\rho_f$}
-		\label{fig:Regression_2}
-	\end{subfigure}
-	\caption{Regression of $D_i$ and $D_e^M$} 
-	\label{fig:Regression}
-	\end{figure}
+%	\begin{figure}[!h]
+%		\centering
+%		\includegraphics[trim = 11.7cm 14cm 2.3cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
+%		\caption{Second-order polynomial regression of fitted parameters ($D_i$ and $D_e^M$) as a function of fluid density $\rho_f$}
+%		\label{fig:Regression_2}
+%	\end{figure}
 

### 2023-06-28 SFE-article/Sections/Thermo_imp.tex
29.06

@@
 	\begin{figure*}[H]
-		\begin{subfigure}[b]{0.31\textwidth}
+		\begin{subfigure}[b]{0.32\textwidth}
 			\centering
-			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
-			\caption{The compressibility factor based on the Peng-Robinson equation of state}
+			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
+			\caption{The compressibility factor}
 			\label{fig: SFE_Properties_Compressibility}
@@
 		\hfill
-		\begin{subfigure}[b]{0.31\textwidth}
+		\begin{subfigure}[b]{0.32\textwidth}
 			\centering
-			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/RHO.pdf}	
-			\caption{The fluid density based on the Peng-Robinson equation of state}
+			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/RHO.pdf}	
+			\caption{The density}
 			\label{fig: SFE_Properties_Density}
@@
 		\hfill
-		\begin{subfigure}[b]{0.31\textwidth}
+		\begin{subfigure}[b]{0.32\textwidth}
 			\centering
-			\includegraphics[trim = 2.9cm 8cm 18cm 7cm,clip,width=\textwidth]{Figures/CP.pdf}	
-			\caption{The specific heat of $CO_2$ based on the Peng-Robinson equation of state}
+			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/CP.pdf}	
+			\caption{The specific heat}
 			\label{fig: SFE_Properties_CP}
@@
 		\hfill
-		\begin{subfigure}[b]{0.31\textwidth}
+		\begin{subfigure}[b]{0.32\textwidth}
 			\centering
-			\includegraphics[trim = 0cm 0cm 0cm 0cm,clip,width=\textwidth]{Figures/Enthalpy.pdf}	
-			\caption{The enthalpy of $CO_2$ based on the Peng-Robinson equation of state (\color{red}FONT SIZE)}
+			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/Enthalpy.pdf}	
+			\caption{The enthalpy}
 			\label{fig: SFE_Properties_h}
@@
 		\hfill
-		\begin{subfigure}[b]{0.31\textwidth}
+		\begin{subfigure}[b]{0.32\textwidth}
 			\centering
-			\includegraphics[trim = 1.5cm 4.0cm  14cm 19.0cm,clip,width=\textwidth]{Figures/MU.pdf}
-			\caption{Thermal conductivity obtained based on Laesecke correlation}
+			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/MU.pdf}
+			\caption{Viscosity}
 			\label{fig: SFE_Properties_Viscosity}
@@
 		\hfill
-		\begin{subfigure}[b]{0.31\textwidth}
+		\begin{subfigure}[b]{0.32\textwidth}
 			\centering
-			\includegraphics[trim = 2.5cm 2.8cm 14.3cm 21.4cm,clip,width=\textwidth]{Figures/KT.pdf}	
-			\caption{Thermal conductivity obtained based on Huber correlation}
+			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/KT.pdf}	
+			\caption{Thermal conductivity}
 			\label{fig: SFE_Properties_Thermal}
 		\end{subfigure}
-		\caption{Properties of $CO_2$ based on the equation of state}
+		\caption{Properties of $CO_2$ based on the equation of state and correlations}
 		\label{fig: SFE_Properties}

### 2023-06-28 SFE - MegaFit/Compressibility_Cardano.m

@@ -1,0 +1,44 @@
+function Z = Compressibility_Cardano(T,P,theta)
+    %% Parameters
+    Tc      = theta{10};         % Critical temperature [K]
+    Pc      = theta{11};         % Critical pressure [bar]
+    R       = 83.1447;           % Universal gas constant, [m3-bar/K-mol]
+    kappa   = 0.2250;
+    MW      = theta{14};         % Molar mass [g/mol]       
+    
+    CPA =  1.98E+01;
+    CPB =  7.34E-02;
+    CPC = -5.60E-05;
+    CPD =  1.72E-08;
+
+    %% Reference state %TODO: Add a function to calulate the properties of the reference state
+    TREF = 298.15;   % K
+    PREF = 0.101325; % MPa
+
+    Delta_CP_IG_REF = -41.81755442;
+    
+    %% Recalculate the Peng Robinson parameters
+    Tr = T ./ Tc;
+    Pr = P ./ Pc;
+    %alpha = (1 + kappa .* (1 - sqrt(Tr))).^2;
+    
+    m     = 0.37464 + 1.54226*kappa - 0.26992 * kappa^2;
+    alpha = ( 1 + m .* ( 1 - Tr.^0.5 ) ).^2;
+
+    a = 0.45724 .* R.^2 .* Tc.^2 *alpha ./ Pc;
+    b = 0.0777961 .* R    .* Tc         ./ Pc;
+
+    %A = a .* alpha .* P ./ R.^2 ./ T.^2;
+    A = 0.45723553.*alpha.*Pr./Tr.^2;
+    B = b .* P ./ R ./ T;
+
+    UC = - (1 - B)              ;
+    SC =   (A - 2.*B - 3.*B.^2) ;
+    TC = - ( A .* B - B.^2 - B.^3);
+
+    PC = (3.*SC - UC.^2) ./ 3;
+    QC = (2.*UC.^3 ./ 27) - UC.*SC./3 + TC;
+
+    DC = (PC./3).^3 + (QC./2).^2;
+    
+end

### 2023-06-28 SFE - MegaFit/EnthalpyPlot.m

@@ -6,55 +6,188 @@ Parameters_table        = readtable('Parameters.csv') ;        % Table with pram
 Parameters_cell         = table2cell(Parameters_table(:,3));
 
 %%
-T_set               = linspace(34,100, 100)+273;
-P_set               = linspace(74,300, 100);
+T_set               = linspace(34, 137, 100)+273;
+P_set               = linspace(74, 300, 100);
 
-data                = [mtcombvec(T_set,P_set)'];
+[p,q]               = meshgrid(T_set,P_set);
+data                = [p(:) q(:)];
 
 h_data              = nan(numel(T_set)*numel(P_set),1);
+Z_data              = nan(numel(T_set)*numel(P_set),1);
+rho_data            = nan(numel(T_set)*numel(P_set),1);
+cp_data             = nan(numel(T_set)*numel(P_set),1);
+mu_data             = nan(numel(T_set)*numel(P_set),1);
+k_data              = nan(numel(T_set)*numel(P_set),1);
 
 numIterations       = length(data);
 
-parpool(6)
+f                   = waitbar(0, 'Starting');
 
-ppm = ParforProgressbar(numIterations);
-
-parfor i=1:numIterations
-    T               = data(i,1)
-    P               = data(i,2)
+for i=1:numIterations
+    T               = data(i,1);
+    P               = data(i,2);
 
     Z               = Compressibility( T, P,         Parameters_cell );
     rho             = rhoPB_Comp(      T, P, Z,      Parameters_cell );
-    tic
     h               = SpecificEnthalpy(T, P, Z, rho, Parameters_cell );
-    toc
-    h_data(i)       = h;        
+    Cp              = SpecificHeatComp(T, P, Z, rho, Parameters_cell );
+    mu              = Viscosity(T,rho);
+    k               = HeatConductivity_Comp(T, rho);
 
-    pause(100/numIterations);
-    % increment counter to track progress
-    ppm.increment();
+    Z_data(i)       = Z;
+    rho_data(i)     = rho;
[…]

### 2023-06-28 SFE - MegaFit/HeatConductivity_Comp.m

@@ -77,7 +77,7 @@ k = ( A1 + A2.*rho + A3.*(rho.^2) + A4.*(rho.^3).*(T.^3) + A5.*(rho.^4) + A6.*T 
 
     fk = Function('fk',{T,rho}, {k});
 
-    k = fk(t,RHO);
+    k = full(fk(t,RHO));
 
     %k = Delta_k;
 

### 2023-06-28 SFE - MegaFit/SpecificHeatComp.m

@@ -1,4 +1,4 @@
-function Cv = SpecificHeatComp(T, P, Z, RHO, theta)
+function Cp = SpecificHeatComp(T, P, Z, RHO, theta)
 
     % Specific heat equations
     % https://cheguide.com/specific_heat_ratio.html

### 2023-06-28 SFE - MegaFit/plot_Di_Upsilon.m

@@ -7,7 +7,7 @@ hold off
 legend({'$40^\circ C / 200 bar$', '$50^\circ C / 200 bar$', '$40^\circ C / 300 bar$', '$50^\circ C / 300 bar$'}, 'Location','northwest')
 legend('boxoff')
 xlabel('$c_s [kg/m^3]$')
-ylabel('$D_i [m^2/s]$')
+ylabel('$D_i \gamma [m^2/s]$')
 fontsize(24,"points")
 set(gcf,'PaperOrientation','landscape'); print(figure(1),['D_i_Uppsilon_results.pdf'],'-dpdf','-bestfit');
 close all;

### 2023-08-01 SFE-article/Article_Model_Parameters.tex
01.08

@@
 \usetikzlibrary{shapes.geometric,angles,quotes,calc}
+
+\usepackage{placeins}
 
@@
 \section{Conclusions} \label{CH: Conclusion}
-In this study, a process model was developed by performing parameter estimation using a dataset obtained from experiments conducted at various temperature and pressure levels.
-The model was found to have good agreement with experimental yield curves for the extraction of caraway oil from caraway seeds.
-However, it was noticed that the simulation results overshoot the dataset, which may be explained to the presence of losses in the real system, such as some amount of the solute sticking to the inner walls of pipes.
-Another possible reason could be the need for a more complex mass transfer mechanism than the extraction kinetic presented in this work.
-For example, the Broken-and-Intact Cell model suggested by \citet{Sovova2017} formulated a general SFE model that includes the solute-matrix interaction.
-This model allows for solute diffusion from intact cells to the region of broken cells, and the equilibrium is established at the particle surface between the broken cells and fluid phase.
-Such a mechanism gives more flexibility to the process model to adapt to a dataset.
 
-To establish correlations for the internal and axial diffusion coefficients in terms of fluid density, both linear and non-linear regression techniques were utilized.
-These correlations facilitated the generalization of the process model to a range of operating conditions, specifically for temperatures ranging from $40^\circ C$ to $50^\circ C$, pressures ranging from 200 bar to 300 bar, and flow rates of 0.4 l/min (with flow variations of up to 5\%).
-The dependencies given by these correlations can be justified by the influence of the solubility and Graham's Law of Diffusion, as suggested above.
-
-The generalized model can be used to study the impact of different operating conditions on the extraction yield or for economic analysis of the extraction process.
+This study presented basic aspects regarding the process parameters for obtaining caraway extracts using supercritical $CO_2$ at different operating conditions.
+A first-principle process model was developed based on governing equations and simplified using the Low-Mach number approximation.
+The values of unknown parameters in the process model were obtained by parameter estimation.
+The yield data from the experiments were compared against the yield data generated by the model.
+The IPOPT solver was used to solve the maximum likelihood estimation.
+The process model was found to have good agreement with experimental yield curves.
+Later, the parameters found for each experiment were combined to obtain more general relationships.
+The correlations for $D_i$, $\Upsilon$ and $D_e^M$ are presented as a function of $\rho$ or $R_e$.
+It should be noted that obtained correlations have been prepared with a limited amount of data.
+These correlations can be used to study the impact of different operating conditions on the extraction yield by different methods, such as sensitivity analysis.
+Moreover, the generalized model could be useful in finding the optimal operating conditions with respect to the process economy.
 

### 2023-08-01 SFE-article/Sections/Model.tex
01.08

@@
 		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}c_{s0}}$.
-The fluid concentration is assumed to not be uniform, and as such it is described by a function $H=H(z)$.
-The further discussion on the distribution of concentration in the fluid phase can be found in appendix \ref{CH: IC_BC}.
+On the other hand, the solute concentration in the fluid phase should not follow the same assumption as the solid phase.
+During the preparation period, the solute diffuses to the fluid phase in contact with the solid particles.
+Later, the solute in the fluid phase is partially moved along the extractor (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed).
+As a result, the distribution of solute mass in the fluid phase is assumed not to be uniform.
+Some conclusions can be drawn from the analysis of the initial part of each yield curve obtained from the laboratory (Figure \ref{fig: estimation_results}).
+It can be noticed that each curve at the beginning has a curvature, which is not linear.
+Generally, a quadratic function could approximate the initial part of each extraction curve.
+A function that, after integration, gives a quadratic-like result is a straight line.
+Based on that observation, the solute concentration in the fluid phase is assumed to be linearly distributed.
+The solute concentration is assumed to be zero at the outlet and reach the maximum at the beginning of the fixed bed.
+The details on the calculation are given in Appendix \ref{CH: IC_BC}.
+The linear distribution $H(z)$ can be defined if the total mass of solute $m_{total}$ and initial mass ratio between solid and fluid phases $\tau$ are known.
 		Moreover, it is considered that the initial temperature of the extractor in every place is the same and described by ${\color{magenta}h_0}$.

### 2023-08-01 SFE-article/Sections/Parameter_estimation.tex
01.08

@@
 
+	As a result of fitting, the following parameters are obtained:
+
+	\begin{itemize}
+		\item Partition coefficient:\qquad\quad\qquad$k_m$
+		\item Internal diffusion coefficient: \quad$D_i^R$
+		\item Axial diffusion coefficient: \qquad$D_e^M$
+		\item Decay coefficient:\qquad\qquad\qquad$\Upsilon$
+		\item Standard deviation:\qquad\qquad\quad~$\sigma^2$
+		\item Total mass of solute: \qquad\quad\quad$m_{total}$
+		\item Initial mass ratio: \qquad\qquad\qquad$\tau$
+	\end{itemize}
+
+	To ensure that parameters found by the optimizer do not reach unrealistic values, an additional set of inequality constraints is introduced.
+The initial guess for each optimization, the lower and upper bounds for each parameter are given in Table \ref{tab:Constraints}.
+
+ 	\begin{table}[h]
+		\adjustbox{max width=\columnwidth}{%
+			\begin{tabular}{ lccccccc }
+				\hline 
+				Parameter		&$k_m$[-] 	& $D_i^R$[$m^2/s$] 	& $D_e^M$[$m^2/s$]	& $\Upsilon$ [m$^3$/kg] & $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
+				Lower bound		&0	  		& 0 	  			& 0 				&	0					& 80 		 		& 0 	   		& 0 \\ 
+				Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			&	100					& 150 				& 1 			& $+\infty$ \\ 
+				Initial guess	&1e5 		& 3 	  			& 1 				&	0					& 80 		 		& 0.65 	   		& 0.1 \\  \hline
+		\end{tabular} }
+		\caption{Constraints and initial guess}
+		\label{tab:Constraints}
+	\end{table}
+
 \end{document}

### 2023-08-01 SFE-article/Sections/Results.tex
01.08

@@
 
-    The parameter estimation problem was solved by fitting the process model to the dataset given in the Table \ref{tab: Yield_data}.
-Each time-series was fitted to the model separately.
-As a result of fitting, the following parameters were obtained:
-
-    \begin{itemize}
-        \item Partition coefficient:\qquad\quad\qquad$k_m$
-        \item Internal diffusion coefficient: \quad$D_i$
-        \item Axial diffusion coefficient: \qquad$D_e^M$
-        \item Decay curvature coefficient:\qquad$\Upsilon$
-        \item Standard deviation:\qquad\qquad\quad~$\sigma$
-    \end{itemize}
-
-    Moreover, the initial state estimation was performed together with parameter estimation.
-The initial solute concentration in the solid phase is assumed to be uniformly distributed.
-On the other hand, the solute concentration in the fluid phase should not follow the same assumption as the solid phase.
-During the preparation period, the solute diffuses to the fluid phase in contact with the solid particles.
-Later, the solute in the fluid phase is partially moved along the extractor (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed).
-As a result, the distribution of solute mass in the fluid phase is assumed not to be uniform.
-Some conclusions can be drawn from the analysis of the initial part of each yield curve obtained from the laboratory.
-It can be noticed that each curve at the beginning has a curvature, which is not linear.
-Generally, a quadratic function could approximate the initial part of each extraction curve.
-A function that, after integration, gives a quadratic-like result is a straight line.
-Based on that observation, the solute concentration in the fluid phase is assumed to be linearly distributed.
-The solute concentration is assumed to be zero at the outlet and reach the maximum at the beginning of the fixed bed.
-The details on the calculation are given in appendix \ref{CH: IC_BC}.
-The linear distribution can be defined if the total mass of solute $m_{total}$ and partition coefficient $\tau$ are known.
-
-    Due to initial state estimation, two additional parameters are fitted.
-
-    \begin{itemize}
-        \item Total mass of solute: \qquad\qquad\quad$m_{total}$
-        \item Partition coefficient: \qquad\qquad\quad$\tau$
-    \end{itemize}
-
-	To ensure that parameters found by the optimizer do not reach unrealistic values, an additional set of inequality constraints is introduced.
-The lower and upper bounds for each parameter are given in Table \ref{tab:Constraints}.
-To ensure that the solution is a global solution multiple initial points have been tested but presented results come from the initial guess given also in Table \ref{tab:Constraints}.
-
-	\begin{table}[!h]
-		\centering
-		\adjustbox{max width=\columnwidth}{%
-		\begin{tabular}{ lccccccc }
-			\hline 
-			Parameter		&$k_m$[-] 	& $D_i$[$m^2/s$] 	& $D_e^M$[$m^2/s$]	& $\Upsilon$ [m$^3$/kg] & $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
-			Lower bound		&0	  		& 0 	  			& 0 				&	0					& 80 		 		& 0 	   		& 0 \\ 
-			Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			&	100					& 150 				& 1 			& $+\infty$ \\ 
-			Initial guess	&1e5 		& 3 	  			& 1 				&	0					& 80 		 		& 0.65 	   		& 0.1 \\  \hline
-		\end{tabular} }
-	\caption{Constraints and initial guess of the parameter estimation problem}
-	\label{tab:Constraints}
-	\end{table}
-
-%	The parameter estimation problem requires an initial guess as an input to an optimization problem.
-To ensure that the solution is a global solution multiple initial points have been tested.
-The initial guesses for the parameter estimation problem are given in Table \ref{tab:InitialGuess}
-
-%	\begin{table}[!h]
-%		\centering
-%		\adjustbox{max width=\columnwidth}{%
-%		\begin{tabular}{ lcccccc } 
-%			\hline
-%			Parameter		&$k_m$ 	& $D_i$ 	& $D_e^M$ 	& $m_{total}$	& $\tau$ 	& $\sigma$ \\  \hline
-%			Initial guess	&1	  	& 3 	  	& 1 		& 77 		 	& 0.65 	   	& 0.1 \\  \hline
-%		\end{tabular} }
-%		\caption{Constraints of the parameter estimation problem}
-%		\label{tab:InitialGuess}
-%	\end{table}
-
-	Figure \ref{fig: estimation_results} show yield curves for each of experiments.
+    The parameter estimation problem was solved by fitting the process model to the dataset given in the Figure \ref{fig: estimation_results}.
+Each time-series present was fitted to the model separately.
 The blue dots indicate the data point obtained as a measurement from the laboratory experiments.
 The black curve represents the yield curve obtained from the initial guess of the parameters.
-The blue curve correspond to yield curve obtained as a solution of the optimization problem.
-The curves on the left hand-side of the Figure \ref{fig: estimation_results}, are the cumulative yield curves, which represents the cumulative amount of the oil collected during each experiment.
-The plots on the right hand-side, represent the derivative of the cumulative yield curves.
+The red curve correspond to yield curve obtained as a solution of the optimization problem.
+Every sub-figure is made of two figure of which one represent the cumulative yield, and the second one shows the derivative of the cumulative yield.
 As explained in the Chapter \ref{CH: Parameter_estimation}, the derivatives of the cumulative measurements are independent on the previous measurement and should be used for the parameter estimation.
+    The parameters obtained from solving the optimization problem can be found in Table \ref{tab: Estimation_results}.
 
-	\begin{table}[!h]
-		\centering
-		\adjustbox{max width=\columnwidth}{%
-			\csvautobooktabular{Figures/Results_estimation/estimation.csv} }
-		\caption{Parameter estimation results rounded to fifth decimal place}
-		\label{tab: Estimation_results}
-	\end{table}
-
-	The results of parameter estimation can be found in Table \ref{tab: Estimation_results} and the concentration profiles, which correspond for the optimized solution for each experiments, are presented on Figure \ref{fig: estimation_results_profiles} in Appendix \ref{CH: Profiles}.
-
-	\begin{figure}[!h]
+    \begin{figure*}[!h]
     	\centering
@@
     	\label{fig: estimation_results}
-	\end{figure}
+    \end{figure*}
 
-	Based on the Table \ref{tab: Estimation_results}, the optimizer found optimal values of the partition factors at relatively high.
+	 %and the concentration profiles, which correspond for the optimized solution for each experiments, are presented on Figure \ref{fig: estimation_results_profiles} in Appendix \ref{CH: Profiles}.
+
+	\begin{table}[!h]
+		\centering
+		\adjustbox{max width=\columnwidth}{%
+			\csvautobooktabular{Figures/Results_estimation/estimation_2.csv} }
+		\caption{Parameter estimation results rounded to fifth decimal place}
+		\label{tab: Estimation_results}
+	\end{table}
+
+	As shown in the Table \ref{tab: Estimation_results}, the optimizer found optimal values of the partition factors ${\color{orange}k_m}$ at relatively high levels.
 Such a behaviour suggest that the solvent is far from the saturation, and the model can be simplified.
@@
 	Values of the internal diffusion coefficients are distinguished for each experiment.
-The order of magnitude of $D_i$ obtained from the optimization is similar to values found by other researchers.
-\citet{Reverchon1996} performed the parameter estimation for the extraction process of sage oil from seeds and reported $D_i \approx 6e-13$.
-The $\gamma$ (Equation \ref{EQ: C_sat_function}) coefficient multiply the reference value of $D_i$ to take into consideration that solute inside of a particle is harder to obtain than the solute close to the outer surface, as explained before.
-The curvature of the $\gamma$ function is described by a $\Upsilon$.
-The higher the value of $D_i \times \gamma$, the higher
+The order of magnitude of ${\color{orange}D_i^R}$ obtained from the optimization is similar to values found by other researchers.
+\citet{Reverchon1996} performed the parameter estimation for the extraction process of sage oil from seeds and reported ${\color{magenta}D_i^R} \approx 6\times 10^{-13}[m^2/s]$.
+Figure \ref{fig: results_DI} represent the ${\color{orange}D_i^R}$ as the function of density.
+As the internal diffusion coefficient describes the diffusion inside of a particle, it is independent of external factors such as a fluid velocity around that particle.
+In such a case, the internal diffusion depends only on local conditions given by temperature and pressure, which defines the physical properties of a stagnant fluid inside of pores of a particle—considering that the internal diffusion can be represented as a function of the density of the fluid, which is uniquely defined at a given temperature and pressure in the one-phase region.
+The linear trend in Figure \ref{fig: results_DI} suggests that ${\color{orange}D_i^R}$ increases with fluid density.
 
-	It can be observed that the obtained values of $D_i$ increase as the density increase.
-This behaviour can be explained by an increase in solubility when the density grow.
-\citet{Shojaie2010}, proved that the carvone (which is one of the main components of caraway oil) solubility increase together with pressure increase and decrease when temperature increase.
-$D_i$ and $\Upsilon$ can be related directly to
+	Similarly to the internal diffusion coefficient, the obtained values ${\color{orange}\Upsilon}$ can be represented as a function of the local operating conditions, or by uniquely defined physical properties such as density.
+Figure \ref{fig: results_upsilon} shows that of ${\color{orange}\Upsilon}$ grows with density.
+This can be explained if the solubility increases as the density grows.
+\citet{Shojaie2010}, showed that the solubility of carvone (one of the main components of caraway oil) rises together with pressure increase and decreases when temperature increases.
 
-		\begin{figure*}[!h]
+	The Figure \ref{fig:Di_upsilon_res} shows how the internal diffusivity ${\color{orange}D_i}$ (Equation \ref{EQ: C_sat_function}) as a function of the solute concentration in the solid phase at different operating conditions.
+The higher the density, the higher solubility according to \citet{Shojaie2010}, which results in higher values of the internal diffusion coefficient and larger curvature of ${\color{orange}D_i}$ function.
+
+		\begin{figure}[!h]
 		\centering
-		\begin{subfigure}[b]{0.32\textwidth}
+		\begin{subfigure}[b]{0.49\columnwidth}
 			\centering
 			\includegraphics[trim = 10.5cm 14cm 10cm 1.5cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
-			\caption{Experiment at $40^\circ C$ and $200$ bar}
+			\caption{Dependency of ${\color{orange}D_i}$}
+			\label{fig: results_DI}
 		\end{subfigure}
-		\begin{subfigure}[b]{0.32\textwidth}
+		\begin{subfigure}[b]{0.49\columnwidth}
 			\centering
 			\includegraphics[trim = 3cm 8cm 17.7cm 7.7cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
-			\caption{Experiment at $50^\circ C$ and $200$ bar}
+			\caption{Dependency of ${\color{orange}\Upsilon}$}
+			\label{fig: results_upsilon}
 		\end{subfigure}
 		\hfill
-		\begin{subfigure}[b]{0.32\textwidth}
-			\includegraphics[trim = 2cm 0.4cm 2cm 0.9cm, clip, width=\columnwidth]{/Results_estimation/D_i_Uppsilon_results.pdf}
-			\caption{The dependence of the internal diffusion coefficient on the solutes concentration in the solid phase}
+		\begin{subfigure}[b]{0.49\columnwidth}
+			\includegraphics[trim = 1.0cm 0cm 3cm 0cm, clip, width=\columnwidth]{/Results_estimation/D_i_Uppsilon_results.pdf}
+			\caption{Dependency of ${\color{orange}D^R_i}$}
 			\label{fig:Di_upsilon_res}
 		\end{subfigure}
+		\begin{subfigure}[b]{0.49\columnwidth}
+			\centering
+			\includegraphics[trim = 19.0cm 13.8cm 3.5cm 1.0cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_D_e.pdf}
+			\caption{Dependency of ${\color{orange}D^M_e}$}
+			\label{fig: results_De}
+		\end{subfigure}
 		\caption{Results of parameter estimation}
-		%\label{fig: estimation_results}
-	\end{figure*}
+		\label{fig: estimation_results_DI_GAMMA}
+	\end{figure}
 
-	The Figure \ref{fig:Di_upsilon_res} shows how the internal diffusivity as a function of the solute's concentration in the solid phase.
-
-	The axial diffusion coefficient obtained from the optimizer seems to be quite high if compared to the internal diffusion coefficients.
-Nevertheless, the values of $D_e^M$ have similar order of magnitude as reported in literature, for example \citet{ReisVasco2000}.
-The relatively high values of the axial diffusion coefficients might be justified by taking into account low values of flow rate used in all the experiments.
+	The axial diffusion coefficient obtained from the optimizer seems is relatively high if compared to the internal diffusion coefficients.
+The values of ${\color{orange}D_e^M}$ have similar order of magnitude as reported in literature( \citet{ReisVasco2000}).
+%The relatively high values of the axial diffusion coefficients might be justified by taking into account low values of flow rate used in all the experiments.
+	The axial diffusion can be further analysed by defining the Pecelt number (${\color{orange}P_e} = v \times {\color{magenta}d_p} / {\color{orange}D_e^M} $) and the Reynolds number (${\color{orange}R_e} = v \times {\color{magenta}d_p} / {\color{orange}\mu} $), where ${\color{magenta}d_p}=0.15~[m]$ is the characteristic dimension defined to be the extractor diameter and $\mu$ is the fluid viscosity.
+%The obtained Pecelt numbers have the order of magnitude of $1 \times 10^{8}$, which suggest that diffusion is negligible, and advection dominates mass transport.
+	The obtained Pecelt numbers are $P_e \gg 1$, which suggest that mass diffusion is negligible, and advection dominates mass transport.
+An idea to consider a relationship between the Peclet (indirectly the mass diffusion coefficient) and Reynolds numbers has been proposed by \citet{Chung1968}.
+	The Figure \ref{fig: results_De} shows that the obtained values of the mass diffusion coefficient increase almost linearly with increment of the Reynolds number.
 
@@
 
-	As explained above, and in Appendix \ref{CH: IC_BC}, the linear distribution of can be fully determined if the parameter $\tau$ is known.
-The split ratio for experiments conducted at $40 ^\circ C$ / 300 bar and $50 ^\circ C$ / 300 bar are similar to each other and close to 0.65.
-The experiments performed at $40 ^\circ C$ / 200 bar and $50 ^\circ C$ / 200 bar have $\tau$ equals to $0.70$ and $0.75$, respectively.
+	The inital state estimation resulted in values of $\tau$ in range from 0.69 to 0.76.
+These values are relatively similar to each other.
+It can be concluded that in the used experimental set-up around 30\% of the solute was extracted to the fluid phase during the preparation period.
 
-	The noise present in each dataset is quantified by parameter $\sigma$.
-It can be observed dataset obtained at $40 ^\circ C$ / 200 bar and $50 ^\circ C$ / 200 bar have similar value of $\sigma\approx0.36$.
-The visual investigation of the datasets obtained at $40 ^\circ C$ / 300 bar and $50 ^\circ C$ / 300 bar allow to explain higher values of $\sigma$ for both dataset.
-Both datasets have higher deviation of the data points from the simulated curve.
+	The noise present in each dataset is quantified by parameter $\sigma^2$.
+It can be observed dataset obtained at $40 ^\circ C$ / 200 bar and $30 ^\circ C$ / 300 bar have similar value of $\sigma^2\approx0.07$.
+The slightly better results were obtained for the experiment at $50 ^\circ C$ / 300 bar, when $\sigma^2\approx0.05$.
+The most noisy dataset corresponds to $50 ^\circ C$ / 200 bar, when $\sigma^2\approx0.12$.
+All values of $\sigma^2$ are relatively low, which suggest the mathematical model is capable to mimic the physical system up to the noise coming from the experiment.
 
-	The results obtained from the parameter estimation are used to develop a generalized process model.
+	%The results obtained from the parameter estimation are used to develop a generalized process model.
 The model generalization is performed by introducing correlations which link the estimated parameters and the operating conditions.
@@
 To simplify the problem, the correlations are written as functions of fluid density rather than temperature and pressure.
-Since the optimizer found that $k_m$, $m_{total}$ and $C_{lim}$ don't change with the density variations, they are assumed to be constants and not considered further.
-
-	The other two parameters ($D_i$ and $D_e^M$) are subject to regression to obtain correlations in terms of density.
-Figure \ref{fig:Regression} shows the first- and second-order polynomials used to fit $D_i$ and $D_e^M$ as a function of fluid density.
+Since the optimizer found that ${\color{orange}k_m}$, $m_{total}$ and $C_{lim}$ don't change with the density variations, they are assumed to be constants and not considered further.
 
@@
 %		\includegraphics[trim = 11.7cm 14cm 2.3cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
-%		\caption{Second-order polynomial regression of fitted parameters ($D_i$ and $D_e^M$) as a function of fluid density $\rho_f$}
+%		\caption{Second-order polynomial regression of fitted parameters (${\color{orange}D_i^R}$ and ${\color{orange}D_e^M}$) as a function of fluid density $\rho_f$}
 %		\label{fig:Regression_2}

### 2023-08-01 SFE-article/Sections/Saturation.tex
01.08

@@
 
-	Following the idea of the Broken-and-Intact Cell (BIC) model presented by \citet{Sovova2017}, the coefficient ${\color{orange} \gamma}$ is introduced to limit the available oil.
-The ${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ describes the decay function, which is equal to unity and slowly decays when the amount of the solute in the solid phase decrease.
-Similarly to the BIC model, this can be explained if oil is assumed to be contained in the cells, a part of which is open because the cell walls were broken by grinding, and the rest remains intact.
-The ${\color{orange} \gamma}$ parameter multiply the internal diffusion term to indicate that the diffusion of the solute from a particle's core takes more time compared to the diffusion of the solute located close to the outer surface.
+	Following the idea of the Broken-and-Intact Cell (BIC) model presented by \citet{Sovova2017}, the internal diffusion coefficient ${\color{orange}D_i}$ is consider to be a product of the reference value of ${\color{orange}D_i^R}$ and the exponential decay function ${\color{orange} \gamma}$, as given by Equation \ref{EQ: C_sat_function}.
 
@@
 		\begin{equation}
-			{\color{orange} \gamma}({\color{blue} c_s} (t,z)) = \exp\left( {\color{magenta}\Upsilon} \left( 1-\cfrac{{\color{blue} c_s} (t,z) }{{\color{magenta}c_{s0}}} \right) \right) \label{EQ: C_sat_function}
+			{\color{orange}D_i} = {\color{orange}D_i^R} {\color{orange} \gamma}({\color{blue} c_s} (t,z)) = {\color{orange}D_i^R} \exp\left( {\color{magenta}\Upsilon} \left( 1-\cfrac{{\color{blue} c_s} (t,z) }{{\color{magenta}c_{s0}}} \right) \right) \label{EQ: C_sat_function}
 		\end{equation} }
@@
 			\label{Model_kinetic}
-				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t)) {\color{orange} \gamma}({\color{blue} c_s} (t,z)) }{{\color{magenta} \mu l^2} } \left({\color{blue}{\color{blue} c_s} }(t,z)  - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
+				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i^R}({\color{blue}T}(t,z), {\color{red}P}(t)) {\color{orange} \gamma}({\color{blue} c_s} (t,z)) }{{\color{magenta} \mu l^2} } \left({\color{blue}{\color{blue} c_s} }(t,z)  - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
 		\end{equation} }
 
+	Such a formulation limits the availability of the solute in the solid phase.
+Similarly to the BIC model, this can be explained if oil is assumed to be contained in the cells, a part of which is open because the cell walls were broken by grinding, and the rest remains intact.
+The diffusion of the solute from a particle's core takes more time compared to the diffusion of the solute located close to the outer surface, considering that the internal diffusion coefficient decay as the concentration of the solute in the solid decrease.
+As the value of the ${\color{blue}c_s}$ decrease over time, the exponential term approach unity and $\lim_{ {\color{blue}c_s} \rightarrow 0} {\color{orange}D_i} =  {\color{orange}D_i^R}$.
+${\color{orange}D_i^R}$ can be interpreted as the internal diffusion coefficient at vanishing gradient.
+
 \end{document}

### 2023-08-01 SFE-article/Sections/Thermo_imp.tex
01.08

@@
 			\centering
-			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
-			\caption{The compressibility factor}
+			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
+			\caption{Compressibility factor}
 			\label{fig: SFE_Properties_Compressibility}
@@
 			\centering
-			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/RHO.pdf}	
-			\caption{The density}
+			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/RHO.pdf}	
+			\caption{Density}
 			\label{fig: SFE_Properties_Density}
@@
 			\centering
-			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/CP.pdf}	
-			\caption{The specific heat}
+			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/CP.pdf}	
+			\caption{Specific heat}
 			\label{fig: SFE_Properties_CP}
@@
 			\centering
-			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/Enthalpy.pdf}	
-			\caption{The enthalpy}
+			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/Enthalpy.pdf}	
+			\caption{Enthalpy}
 			\label{fig: SFE_Properties_h}
@@
 			\centering
-			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/MU.pdf}
+			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/MU.pdf}
 			\caption{Viscosity}
@@
 			\centering
-			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/KT.pdf}	
+			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/KT.pdf}	
 			\caption{Thermal conductivity}

### 2023-08-01 SFE - MegaFit/axial_diffusion_Chung.m

@@ -1,0 +1,70 @@
+startup
+
+import casadi.*
+
+Parameters_table        = readtable('Parameters.csv') ;        % Table with prameters
+Parameters              = num2cell(Parameters_table{:,3});
+
+DATA_set                = {'LUKE_T40_P200', 'LUKE_T50_P200', 'LUKE_T40_P300_org', 'LUKE_T50_P300_org'};
+
+V_Flow                  = 0.4;                                              % Volumetric flow rate l/mi
+r                       = Parameters{3};                                    % Radius of the extractor  [m]
+epsi                    = Parameters{4};                                    % Fullness [-]
+L                       = Parameters{6};                                    % Total length of the extractor [m]
+
+RE = []; RHO = []; MU = []; V = []; D_L = [];
+
+for ii=1:numel(DATA_set)
+    % Dataset
+    DATA                = DATA_set{ii};
+    LabResults          = xlsread([DATA,'.xlsx']);
+
+    T                   = LabResults(1,1)+273.15;
+    P                   = LabResults(1,2);
+
+    Z                   = Compressibility( T, P,         Parameters );
+    rho                 = rhoPB_Comp(      T, P, Z,      Parameters );
+    RHO = [RHO,rho];
+
+    F                   = V_Flow * rho * 1e-3 / 60 ;
+
+    v                   = Velocity(F,rho,Parameters);
+    V  = [V,v];
+
+    mu                  = Viscosity(T,rho);
+    MU = [MU,mu];
+
+    dp = 0.15;
+
+    Re                  = dp * v * rho * epsi / mu;
+    RE = [RE,Re];
+
+    d_L                 = 2*0.001*v/(0.2+0.011*Re^0.48);
+    D_L = [D_L, d_L];
+
+end
+
+DATA_estimated = readtable('estimation.csv');
+D_L_estimated  = DATA_estimated{3,2:end};
+
+[trendLine, SLine]   = polyfit(RE, D_L_estimated, 1 );
+p_est                = polyval(trendLine, RE);
+p_y                  = polyval(trendLine, linspace(min(RE), max(RE) ) );
+
+subplot(3,3,3)
+scatter(RE, D_L_estimated, 'filled')
+hold on
+plot(linspace(min(RE), max(RE) ),p_y,'LineWidth',2);
+hold off
+
[…]

### 2023-08-01 SFE - MegaFit/corr2.m

@@ -1,0 +1,7 @@
+function [r] = corr2(a,b)
+    
+    a = a - mean(a);
+    b = b - mean(b);
+    r = sum(sum(a.*b))/sqrt(sum(sum(a.*a))*sum(sum(b.*b)));
+
+end

### 2023-08-01 SFE - MegaFit/main_Fitting_MegaFit.m

@@ -294,7 +294,7 @@ end
 
 %format shortE
 
-NAME = {'$k_m[-]$', '$D_i[m^2/s] \times 1e-14$', '$D_e^M[m^2/s] \times 1e-6$', '$\Upsilon[-]$', '$\tau[-]$', '$\sigma[-]$'};
+NAME = {'$k_m[-]$', '$D_i[m^2/s] \times 10^{-14}$', '$D_e^M[m^2/s] \times 10^{-6}$', '$\Upsilon[-]$', '$\tau[-]$', '$\sigma[-]$'};
 name = {'km', 'Di', 'De', 'Upsilon', 'tau', 'sigma'};
 Title = {'T40P200', 'T50P200', 'T40P300', 'T50P300'};
 
@@ -512,7 +512,6 @@ for xoxo=1:1%numel(XOXO)
 end
 
 %%
-
 Plot_Trend_Line
 plot_Di_Upsilon
 

### 2023-08-01 SFE - MegaFit/mtcombvec.m

@@ -1,29 +1,0 @@
-function c = mtcombvec(varargin)
-% my own implementation of combvec for use in octave or without matlab nnet library
-% 
-% takes args of column-vectors, produces all combinations thereof
-%
-
-% copyright (c) 2018 Michael Tesch, tesch1@gmail.com
-% released under the Apache 2.0 Open Source license.
-
-if length(varargin)==0
-    c = [];
-    return
-end
-
-c = varargin{1};
-
-for i=2:length(varargin)
-    % make sure varargin{i} isn't more than 2d matrix
-    if length(size(varargin{i}))>2
-        error(sprintf('parameters must be 2d matrices (check arg %d)', i));
-    end
-    c = mtextend(c, varargin{i});
-end
-
-function cc = mtextend(old, new)
-mm = size(old,2);
-nn = size(new,2);
-cc = repmat(old, 1, nn);
-cc = [cc ; repmat(new, 1, mm)];

### 2023-08-06 SFE-article/Article_Model_Parameters.tex
06.08

@@
 
-\author[1]{Oliwer Sliczniuk*}[orcid=0000-0003-2593-5956]
+\author[1]{Oliwer Sliczniuk}[orcid=0000-0003-2593-5956]
 \ead{oliwer.sliczniuk@aalto.fi}
@@
 Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
-This study aimed to investigate the supercritical extraction process of the caraway oil from caraway seeds from a partially filled extractor with a fixed bed operated under multiple constant operating conditions.
-The dataset collected from the experiments consists of four experiments conducted at different operating conditions: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar.
+This study aimed to investigate the supercritical extraction process of the caraway oil from caraway seeds.
+The extraction was performed in a partially filled extractor with a fixed bed operated under multiple constant operating conditions.
+The dataset collected from four experiments consists of four experiments conducted at different operating conditions: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar.
 A distributed-parameter model is used to describe the fluid-solid extraction process with $CO_2$ as a solvent.
@@
 
-where ${\color{orange}\rho_f}$ is the density of the fluid, ${\color{magenta}A_f}(z)$ is the function which describe change of the cross-section, $v$ is the velocity, ${\color{blue}P}$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
+where ${\color{orange}\rho_f}$ is the density of the fluid, ${\color{magenta}A_f}(z)$ is the function which describe change of the cross-section, $v$ is the velocity, ${\color{blue}P}$ is the total pressure, ${\color{blue}e}$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
 
@@
 			\node at (5.5,1.5) {${\color{orange}\rho_f}+\delta{\color{orange}\rho_f}$};
-			\node at (4,1.0) {$P$};
+			\node at (4,1.0) {${\color{blue}P}$};
 			\node at (5.5,1.0) {${\color{blue}P}+\delta {\color{blue}P}$};
-			\node at (4,0.5) {$T$};
+			\node at (4,0.5) {${\color{blue}T}$};
 			\node at (5.5,0.5) {${\color{blue}T}+\delta {\color{blue}T}$};
@@
 
-This study presented basic aspects regarding the process parameters for obtaining caraway extracts using supercritical $CO_2$ at different operating conditions.
+This study presented basic aspects regarding the laboratory work for obtaining caraway extracts using supercritical $CO_2$ at different operating conditions.
 A first-principle process model was developed based on governing equations and simplified using the Low-Mach number approximation.
+Based on the literature review, the extraction kinetic model was selected.
 The values of unknown parameters in the process model were obtained by parameter estimation.
@@
 Later, the parameters found for each experiment were combined to obtain more general relationships.
-The correlations for $D_i$, $\Upsilon$ and $D_e^M$ are presented as a function of $\rho$ or $R_e$.
+The correlations for ${\color{orange}D_i^R}$, ${\color{orange}\Upsilon}$ and ${\color{orange}D_e^M}$ are presented as a function of ${\color{orange}\rho}$ or ${\color{orange}R_e}$.
 It should be noted that obtained correlations have been prepared with a limited amount of data.
-These correlations can be used to study the impact of different operating conditions on the extraction yield by different methods, such as sensitivity analysis.
+These correlations can be used to study qualitatively the impact of different operating conditions on the extraction yield by different methods, such as sensitivity analysis.
 Moreover, the generalized model could be useful in finding the optimal operating conditions with respect to the process economy.

### 2023-08-06 SFE-article/Sections/Results.tex
06.08

@@
     The parameter estimation problem was solved by fitting the process model to the dataset given in the Figure \ref{fig: estimation_results}.
-Each time-series present was fitted to the model separately.
+Each time-series was fitted to the model separately.
 The blue dots indicate the data point obtained as a measurement from the laboratory experiments.
@@
 Every sub-figure is made of two figure of which one represent the cumulative yield, and the second one shows the derivative of the cumulative yield.
-As explained in the Chapter \ref{CH: Parameter_estimation}, the derivatives of the cumulative measurements are independent on the previous measurement and should be used for the parameter estimation.
+As explained in Chapter \ref{CH: Parameter_estimation}, the derivatives of the cumulative measurements are independent on the previous measurement and should be used for the parameter estimation.
     The parameters obtained from solving the optimization problem can be found in Table \ref{tab: Estimation_results}.
@@
 
-	Values of the internal diffusion coefficients are distinguished for each experiment.
+	Values of the reference internal diffusion coefficients are distinguished for each experiment.
 The order of magnitude of ${\color{orange}D_i^R}$ obtained from the optimization is similar to values found by other researchers.
@@
 Figure \ref{fig: results_DI} represent the ${\color{orange}D_i^R}$ as the function of density.
-As the internal diffusion coefficient describes the diffusion inside of a particle, it is independent of external factors such as a fluid velocity around that particle.
-In such a case, the internal diffusion depends only on local conditions given by temperature and pressure, which defines the physical properties of a stagnant fluid inside of pores of a particle—considering that the internal diffusion can be represented as a function of the density of the fluid, which is uniquely defined at a given temperature and pressure in the one-phase region.
+As the reference internal diffusion coefficient describes the diffusion inside of a particle, it is independent of external factors such as a fluid velocity around that particle.
+The reference internal diffusion depends only on local conditions given by temperature and pressure, which defines the physical properties of a stagnant fluid inside of pores of a particle—considering that the reference internal diffusion can be represented as a function of the density of the fluid, which is uniquely defined at a given temperature and pressure in the one-phase region.
 The linear trend in Figure \ref{fig: results_DI} suggests that ${\color{orange}D_i^R}$ increases with fluid density.
 
-	Similarly to the internal diffusion coefficient, the obtained values ${\color{orange}\Upsilon}$ can be represented as a function of the local operating conditions, or by uniquely defined physical properties such as density.
+	Similarly to the internal diffusion coefficient, the obtained values of ${\color{orange}\Upsilon}$ depends only on temperature and pressure, or by uniquely defined physical properties such as density.
 Figure \ref{fig: results_upsilon} shows that of ${\color{orange}\Upsilon}$ grows with density.
@@
 			\centering
-			\includegraphics[trim = 10.5cm 14cm 10cm 1.5cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
+			\includegraphics[trim = 11.2cm 13.7cm 11cm 1.0cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
 			\caption{Dependency of ${\color{orange}D_i}$}
@@
 			\centering
-			\includegraphics[trim = 3cm 8cm 17.7cm 7.7cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
+			\includegraphics[trim = 3.5cm 7.7cm 18.7cm 7.3cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
 			\caption{Dependency of ${\color{orange}\Upsilon}$}
@@
 
-	The axial diffusion coefficient obtained from the optimizer seems is relatively high if compared to the internal diffusion coefficients.
-The values of ${\color{orange}D_e^M}$ have similar order of magnitude as reported in literature( \citet{ReisVasco2000}).
-%The relatively high values of the axial diffusion coefficients might be justified by taking into account low values of flow rate used in all the experiments.
-	The axial diffusion can be further analysed by defining the Pecelt number (${\color{orange}P_e} = v \times {\color{magenta}d_p} / {\color{orange}D_e^M} $) and the Reynolds number (${\color{orange}R_e} = v \times {\color{magenta}d_p} / {\color{orange}\mu} $), where ${\color{magenta}d_p}=0.15~[m]$ is the characteristic dimension defined to be the extractor diameter and $\mu$ is the fluid viscosity.
-%The obtained Pecelt numbers have the order of magnitude of $1 \times 10^{8}$, which suggest that diffusion is negligible, and advection dominates mass transport.
-	The obtained Pecelt numbers are $P_e \gg 1$, which suggest that mass diffusion is negligible, and advection dominates mass transport.
-An idea to consider a relationship between the Peclet (indirectly the mass diffusion coefficient) and Reynolds numbers has been proposed by \citet{Chung1968}.
-	The Figure \ref{fig: results_De} shows that the obtained values of the mass diffusion coefficient increase almost linearly with increment of the Reynolds number.
+	The axial diffusion coefficient obtained from the optimizer is relatively high compared to the internal diffusion coefficients.
+The values of ${\color{orange}D_e^M}$ have a similar order of magnitude as reported in the literature (\citet{ReisVasco2000}).
+%The relatively high values of the axial diffusion coefficients might be justified by taking into account the low values of the flow rate used in all the experiments.
+	The axial diffusion can be further analyzed by defining the Pecelt number (${\color{orange}P_e} = v \times {\color{magenta}d_p} / {\color{orange}D_e^M} $) and the Reynolds number (${\color{orange}R_e} = v \times {\color{magenta}d_p} / {\color{orange}\mu} $), where ${\color{magenta}d_p}=0.15~[m]$ is the characteristic dimension defined to be the extractor diameter and $\mu$ is the fluid viscosity.
+%The obtained Pecelt numbers have the order of magnitude of $1 \times 10^{8}$, which suggests that diffusion is negligible and advection dominates mass transport.
+	The obtained Pecelt numbers are ${\color{orange}P_e} \gg 1$, which suggests that mass diffusion is negligible and advection dominates mass transport.
+This observation suggests that the process model could be further simplified by neglecting the diffusion term.
+Nevertheless, such a simplification has not been introduced in this work.
+	\citet{Chung1968} presented an idea for a relationship between the Peclet (indirectly the mass diffusion coefficient) and Reynolds numbers.
+By modifying the idea of \citet{Chung1968}, a direct relation between the diffusion coefficient and the Reynolds number is used in the work as shown in Figure \ref{fig: results_De}.
+The obtained values of the mass diffusion coefficient increase almost linearly with the increment of the Reynolds number, which is in agreement with the observation that the advection dominates the diffusion.
 
-	As the total amount of the oil present in the system is unknown, and as such it has been obtained from the optimizer.
-Given the dataset and the process model, the optimizer found that the best fit is obtained if the total mass of the oil reach a lower bound equal to 80 g.
-The lower bound was estimated by round up of the biggest value of collected cumulative amount of the extraction product.
-As the same raw material was used in all experiments, the same initial amount of solute is assumed for all the cases.
+	As the total amount of oil present in the system is unknown, and as such, it has been obtained from the optimizer.
+Given the dataset and the process model, the optimizer found that the best fit is obtained if the total mass of the oil reaches a lower bound equal to 80 g.
+The lower bound was estimated by rounding up the biggest value of the collected cumulative amount of the extraction product.
+As the same raw material was used in all experiments, the same initial amount of solute was assumed for all the cases.
 
-	The inital state estimation resulted in values of $\tau$ in range from 0.69 to 0.76.
+	The initial state estimation resulted in values of $\tau$ in the range from 0.69 to 0.76.
 These values are relatively similar to each other.
-It can be concluded that in the used experimental set-up around 30\% of the solute was extracted to the fluid phase during the preparation period.
+In the equipment used in this experiment, around 30\% of the solute was extracted to the fluid phase during the preparation period.
 
-	The noise present in each dataset is quantified by parameter $\sigma^2$.
+	The noise present in each dataset is quantified by the parameter $\sigma^2$.
 It can be observed dataset obtained at $40 ^\circ C$ / 200 bar and $30 ^\circ C$ / 300 bar have similar value of $\sigma^2\approx0.07$.
-The slightly better results were obtained for the experiment at $50 ^\circ C$ / 300 bar, when $\sigma^2\approx0.05$.
-The most noisy dataset corresponds to $50 ^\circ C$ / 200 bar, when $\sigma^2\approx0.12$.
-All values of $\sigma^2$ are relatively low, which suggest the mathematical model is capable to mimic the physical system up to the noise coming from the experiment.
+The slightly better results were obtained for the experiment at $50 ^\circ C$ / 300 bar when $\sigma^2\approx0.05$.
+The noisiest dataset corresponds to $50 ^\circ C$ / 200 bar when $\sigma^2\approx0.12$.
+All values of $\sigma^2$ are relatively low, suggesting the mathematical model can mimic the physical system up to the noise coming from the experiment.
 

### 2023-08-06 SFE - MegaFit/Plot_Trend_Line.m

@@ -25,7 +25,7 @@ for jj=1:2
             pp=sprintf('%s=$(%6.4g) \\rho^2 + (%6.4g) \\rho + (%6.4g)$\n',NAME{ii},trendLine');
         end
 
-        oo = sprintf('$R^2 = %g$\n', round(power(corr2(DATA_K_OUT(ii,:), p_est),2),2) ) ;
+        %oo = sprintf('$R^2 = %g$\n', round(power(corr2(DATA_K_OUT(ii,:), p_est),2),2) ) ;
     
         title( [oo,pp], 'FontSize', 8)
     

### 2023-08-08 SFE_article_Parameter_Estimation/Sections/Experiments.tex
08.08

--- 2023-06-27 SFE-article/Sections/Experiments.tex
@@
 
-	In order to solve the optimization problem presented in Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset ${\color{blue}Y}(t)$, which was obtained by extracting caraway oil from caraway seeds.
+	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset ${\color{blue}Y}(t)$, which was obtained by extracting caraway oil from caraway seeds.
 To prepare the seeds for extraction, they were first pre-treated using a Retsch SM 300 cutting mill to reduce their particle size to 1mm and break their outer shell.
@@
 
-	The results of experiments are presented in the Table \ref{tab: Yield_data}.
+	%The results of experiments are presented in the Table \ref{tab: Yield_data}.
 
@@
 %		\adjustbox{max width=\columnwidth}{%
-%		\begin{tabular}{ccccc}
-%			\hline
-%			& $40 ^\circ C / 200$ bar & $50 ^\circ C / 200$ bar & $40 ^\circ C / 300$ bar & $50 ^\circ C / 300$ bar \\ 
-%			Time min & Mass g                  & Mass g                  & Mass g                  & Mass g                  \\ \hline
-%			0        & 0.0                     & 0.0                     & 0.0                     & 0.0                     \\
-%			5        & 1.7                     & 1.8                     & 1.1                     & 1.2                     \\
-%			10       & 5.7                     & 4.7                     & 4.7                     & 4.5                     \\
-%			15       & 10.9                    & 9.5                     & 10.8                    & 11.3                    \\
-%			20       & 17.8                    & 15.1                    & 20.6                    & 20.6                    \\
-%			25       & 24.9                    & 21.3                    & 32.1                    & 30.6                    \\
-%			30       & 30.3                    & 26.4                    & 40.5                    & 37.8                    \\
-%			35       & 34.0                    & 29.8                    & 46.7                    & 43.3                    \\
-%			40       & 37.5                    & 33.1                    & 50.5                    & 47.5                    \\
-%			45       & 40.1                    & 35.6                    & 53.1                    & 50.8                    \\
-%			50       & 43.3                    & 38.7                    & 55.5                    & 53.7                    \\
-%			55       & 45.5                    & 41.5                    & 57.6                    & 56.5                    \\
-%			60       & 47.6                    & 43.5                    & 59.3                    & 58.1                    \\
-%			65       & 49.2                    & 45.9                    & 60.9                    & 59.6                    \\
-%			70       & 50.8                    & 48.3                    & 62.2                    & 61.1                    \\
-%			75       & 52.6                    & 50.8                    & 63.7                    & 62.7                    \\
-%			80       & 54.2                    & 52.9                    & 64.9                    & 64.4                    \\
-%			85       & 55.1                    & 55.3                    & 66.6                    & 65.8                    \\
-%			90       & 56.2                    & 57.2                    & 67.6                    & 66.7                    \\
-%			95       & 57.3                    & 58.3                    & 68.9                    & 67.4                    \\
-%			100      & 58.3                    & 59.4                    & 69.7                    & 68.2                    \\
-%			105      & 59.4                    & 60.4                    & 70.6                    & 69.1                    \\
-%			110      & 60.2                    & 61.6                    & 71.2                    & 70.1                    \\
-%			115      & 61.4                    & 62.7                    & 71.9                    & 70.9                    \\
-%			120      & 62.5                    & 63.9                    & 72.3                    & 71.6                    \\
-%			125      & 63.3                    & 64.7                    & 72.8                    & 72.3                    \\
-%			130      & 64.0                    & 65.4                    & 73.2                    & 72.9                    \\
-%			135      & 64.8                    & 65.9                    & 73.6                    & 73.5                    \\
-%			140      & 65.5                    & 66.4                    & 74                      & 74                      \\
-%			145      & 66.2                    & 67.1                    & 74.3                    & 74.5                    \\
-%			150      & 66.8                    & 67.7                    & 74.6                    & 74.9              		 \\ \hline     
-%		\end{tabular} }
-%	\caption{Yield data}
+%			\csvautobooktabular{Figures/Results_estimation/Dataset.csv} }
+%		\caption{Yield data; cumulative amount of solute [g] collected every 5 min}
 %		\label{tab: Yield_data}
@@
 
-	\begin{table}[!h]
-		\centering
-		\adjustbox{max width=\columnwidth}{%
-			\csvautobooktabular{Figures/Results_estimation/Dataset.csv} }
-		\caption{Yield data; cumulative amount of solute [g] collected every 5 min}
-		\label{tab: Yield_data}
-	\end{table}
-
 \end{document}

### 2023-08-08 SFE_article_Parameter_Estimation/Sections/Likelihood.tex
08.08

--- 2023-01-24 SFE-report/Sections/Parameter_estimation.tex
@@
 
-Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, $y(t)$, to give the observable dependent variable $Y(t)$, for example the experimental process output.
-For discrete observations:
+	Maximum likelihood estimation (MLE) is a statistical method used to estimate the parameters of a probability distribution based on observed data.
+The MLE works by finding the values of the parameters that maximize the likelihood function, which is the probability of observing the given data for a given set of parameter values.
+The MLE has desirable properties such as asymptotic efficiency and normality.
+Although the MLE has often been associated with the normal distribution for mathematical convenience, it can be applied to a wide range of probability distributions.
 
-{\footnotesize
-	\begin{equation}
-		Y(t_i) = y(t_i) + \epsilon(t_i)
-\end{equation} }
-and for continuos variables:
-
-{\footnotesize
-	\begin{equation}
-		Y(t) = y(t) + \epsilon(t)
-\end{equation} }
-
-%If the estimated parameter $\hat{\theta}$ replaces the model parameter $\theta$, the residue error is $\textbf{E} = Y(t) - \hat{Y}(t)$, where $\hat{Y}(t)$ is the predicted value of $Y_i$ at $y_i$. 
-The objective in parameter estimation is to obtain the "best" estimate of $\theta$ based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$. 
-\sout{
-	We assume that $x(t)$ is given \textit{a priori} (for example as a solution of process model) but $\theta$ is to be estimated over the time interval $0 \leq t \leq t_n$ from discrete observation described by the following relation:}
-
-{\footnotesize
-	\begin{equation}
-		Y(t_i) = \textbf{h}(t_i)y(t_i) + \boldsymbol{\epsilon}(t_i) \qquad 1 \leq i \leq n
-\end{equation} }
-\sout{where $ Y(t_i)$ is an $n \times 1$ column vector, $\textbf{h}(t_i)$ is an $n \times v$ matrix given \textit{a priori}, and $ \boldsymbol{\epsilon} (t_i)$ is an $n \times 1$ column vector ("noise" vector) whose elements are the unobservable errors.
-The above equation can be written in general form as:}
-
-{\footnotesize
-	\begin{equation} \label{EQ: Measurment_noise}
-		Y(t_i) = y(\theta, t_i) + \epsilon(t_i)
-\end{equation}}
-where $y$ is the output model, which is a function of $\theta$ and time $t_i$.
-
-Because of the difficulty of obtaining analytical solutions to the deterministic process model, experiments have been arranged whereby the vector of derivatives $d Y(t_i)/dt$ is measured rather than $Y(t_i)$ itself.
-In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ as follows:
-
-{\footnotesize
-	\begin{equation}
-		\cfrac{d Y(t_i)}{dt} = \cfrac{dy(\theta, t_i)}{dt} + \epsilon(t_i)
-\end{equation} }
-
-\subsection{Least squares estimation}
-A least squares parameter estimation does not require prior knowledge of the distribution of unobservable errors, yield  unbiased estimates, \sout{that is, $ \mathbb{E}\{\hat{Y}(t) = y(t) \} $,} and results in the minimum variance among all linear unbiased estimators.
-If the observations $ Y$ for the model responses are continuous functions of time from $t = 0$ to $t = t_f$, the Markov (or "rigorous least squares") criterion is to minimize:
-
-{\footnotesize
-	\begin{align}
-		\phi &= \cfrac{1}{2} \int_{0}^{t_f}  \left[ Y(t) - y(\theta,t) \right]^T \Gamma^{-1} \left[ Y(t) - y(\theta,t) \right] dt \\
-		\hat{\theta} &= \arg \min_{\theta \in \Theta} \phi
-\end{align} }
-where $\Gamma$ is the covariance matrix (or perhaps a matrix of appropriate weights), $\hat{\theta}$ is the parameter estimate, $\Theta$ is the parameter space, and $\phi$ is the time integrated value of the error squared ("integral squared error").
-If the observations are made at discrete instants of time, $t_i$, $i = 1,2,...,n$, the Markov criterion is to minimize:
-
-{\footnotesize
-	\begin{align}
-		\phi &= \cfrac{1}{2} \sum_{i=1}^{n} \left[ Y(t_i) - y(\theta,t_i) \right]^T \Gamma^{-1} \left[ Y(t_i) - y(\theta,t_i) \right] \\
-		\hat{\theta} &= \arg \min_{\theta \in \Theta} \phi
-\end{align} }
-
-If $\Gamma$ is a diagonal matrix, $\phi$  becomes a "weighted least squares" criterion; if $\Gamma = \sigma^2 \textbf{I}$ where $\sigma$ is a standard deviation., $\phi$ is the "ordinary least squares" criterion.
-
-\subsection{Weighted sum of squares - Cumulative data}
-
-One characteristic feature of certain special experiments is the use of the same batch of materials for the entire series of measurements.
-If unobservable error in the first observation is designated as $\epsilon_1$, the second error observation $\epsilon_2'$ includes $\epsilon_1$ plus a random component introduced side from $\epsilon_1$, or $\epsilon_2' = \epsilon_1 + \epsilon_2$.
-The error in the third observation is $\epsilon_3' = \epsilon_1 + \epsilon_2 + \epsilon_3$, and so forth.
-\citet{Mandel1957} distinguished between the usually assumed type of independent measuring error in the dependent variable and a 'cumulative' or interval error in which each new observation includes the error of the previous observations.
-Cumulative errors, arising because of the fluctuations as a function of time in the process itself due to small changes in operating, are not independent - only the differences in measurement from one period to the next are independent.
-Thus, if we consider two model:
-
-{\footnotesize
-	\begin{flalign*}
-		&{\normalsize \text{Model A - independent error:} } &&\nonumber \\
-		Y(t_i) &= y(\theta, t_i) + \epsilon_i  \qquad i = 1,2,...,n&& \\
-		&{\normalsize \text{Model B - cumulative data:}} && \nonumber \\
-		Y(t_j) - Y(t_{j-1}) &= y(\theta, t_j) - y(\theta, t_{j-1}) + \epsilon_j, \quad j = 1,2,...,n&& \\
-		&{\normalsize \text{or}} && \nonumber \\
-		Y(t_i) = \sum_{j=1}^{i} &\left( Y(t_j) - Y(t_{j-1}) \right) = \sum_{j=1}^{i} \left( y(\theta, t_j) - y(\theta, t_{j-1}) \right) + \sum_{j=1}^{i} \epsilon_j &&
-\end{flalign*} }
-
-in which $\epsilon_i$ are independent random variables with $\mathbb{E}\{\epsilon_i\}$ and Var$\{\epsilon_i\} = \sigma_1^2$, a constant.
-The $\epsilon_j$ are also random independent variables because they represent differences such as $\epsilon_3' - \epsilon_2' = \left( \epsilon_1 + \epsilon_2 + \epsilon_3 \right) - \left( \epsilon_1 + \epsilon_2 \right) = \epsilon_3$.
-We assume that $\mathbb{E}\{\epsilon_j\}$ and Var$\{\epsilon_i\} = \sigma_1^2\left(y_j - y_{j-1}\right)$; i.e., the variance of $\epsilon_j$ can be a function of the test interval.
-The experimental point tend to stay on one side of the regression line of the best fit for Model B.
-
-The \sout{best} unbiased estimate of the Model B is obtained by minimizing the weighted sum of squares:
-
-{\footnotesize
-	\begin{equation*}
-		\hat{\theta} = \arg \min_{\theta \in \Theta} \sum_{j=1}^{n} \cfrac{ \left[ \left( Y(t_j) - Y(t_{j-1}) \right) - \left( y(\theta, t_j) - y(\theta, t_{j-1}) \right) \right]^2  }{y(\theta, t_j) - y(\theta, t_{j-1})}
-\end{equation*} }
-
-\subsection{Maximum likelihood estimation}
-
-Maximum likelihood estimation (MLE) is a method of estimating the parameters of an assumed probability distribution, given some observed data.
-This is achieved by maximizing a likelihood function so that, under the assumed statistical model, the observed data is most probable.
-The MLE has the desirable characteristics of asymptotic efficiency and normality.
-Each time it has been associated with the (joint) normal distribution because of mathematical convenience.
-Consider the joint probability density function (the likelihood function) $p(\theta |y)$ for random sample $y = y(t_1),y(t_2),...,y(t_n)$, parameter $\theta$.
-If a maximum of this function over all choices of $\theta$ can be found, the estimates so obtained are maximum likelihood estimates.
-The conditions at the maximum can be evolved incorporating prior information as follows.
-
-The posterior probability density $p(\theta|y)$ can be expressed as the ratio of two probability densities if we make use of the analogue for continuous variables of Equation \ref{EQ: Probabiltiy_independet_b}:
+	To find the maximum likelihood estimates, we maximize the joint probability density function, or likelihood function, denoted as $p(\theta | y(t_1),y(t_2),...,y(t_n))$, where $\theta$ represents the parameters and $y(t_1),y(t_2),...,y(t_n)$ represent the observed data.
+The conditions at the maximum can be refined by incorporating prior information.
+The posterior probability density function $p(\theta|y)$ can be expressed as the ratio of two probability densities (\ref{EQ: Probabiltiy_independet_b}) using the continuous variable analogue of Bayes' theorem (details in Appendix \ref{CH: Bayes}).
+In such a case the posteriori distribution is given by Equation \ref{EQ: Posterior_distribution}.
 
@@
 
-Examination of Equation \ref{EQ: Measurment_noise} shows that $ Y(t_i)$ depends only on $t_i$, $\theta$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement.
+	Examination of Equation \ref{EQ: Measurment_noise} shows that $ d Y(t_i) / dt$ depends only on $t_i$, $\theta$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement.
 Consequently, we can write
@@
 
-By collecting a random sample of values of the random variable $y$ and selecting the values of $\theta$ that maximize the likelihood function $L\left( \theta | y \right)$, a function described in chapter \ref{CH: Bayes} in connection with Bayes' theorem.
-Such estimators, $\hat{\theta}$, are known as maximum likelihood estimators.
-In effect, the methods selects those values of $\theta$ that are at least as likely to generate the observed sample as any other set of values of the parameters if the probability density of the random variable $y$ were to be extensively simulated through use of the probability density $p\left( y|\theta \right)$.
-In making a maximum likelihood estimate, we assume that the form of the probability density (\sout{only the $\theta$ need be determined}) and that all possible values of $\theta$ are equally likely before experimentation.
-
-%The likelihood function for the parameters given one observation is just the probability density in which the observation is regarded as a fixed number and the parameters as the variables:
-%
-%{\footnotesize
-	%	\begin{equation}
-		%		p\left( \theta| y(t_i) \right) = L\left( \theta|y_{t_i} \right) = p\left( y(t_i)| \theta \right)
-		%\end{equation} }
-		%where the lower case $y$'s and the number subscripts designate the value of the respective observation that is inserted into the probability density function. 
-		The likelihood function for the parameters based on several observations is the product of the individual functions if the observations are independent.
+	The likelihood function $L\left( \theta | y \right)$ for the parameters based on several observations is the product of the individual functions if the observations are independent.
 
@@
 		\begin{equation}
-				\ln L = -n \ln \sqrt{2 \pi} - \cfrac{n}{2} \ln \sigma
+			\ln L = -\cfrac{n}{2} \left( \ln \sqrt{2 \pi} + \ln \sigma^2 \right)
 			- \cfrac{ \sum_{i=1}^{n} \left[  Y(t_i) - y(\theta , t_i) \right]^2 }{2 \sigma^2}
@@
 	}
+
+	\iffalse
 
@@
 		\begin{equation}
-				\begin{aligned}
+			\begin{aligned} \label{EQ: Optimization_formulation_MLE}
 				&\hat{\theta}_{MLE} &= \arg \max_{\sigma, \theta \in \Theta} \ln L = \arg \max_{\sigma,\theta \in \Theta} p(\theta|y) \\
@@
 				&& \dot{\theta} = 0 \\
-					&& y = g(x)
+				&& y = y(x) \\
+				&& \theta^{lb} \leq \theta \leq \theta^{ub}
 			\end{aligned}
@@
 
-		{\color{red}Based on the first order optimality condition,} the $\ln L$ can be maximized with respect to the vector $\theta$ by equating to zero the partial derivatives of $\ln L$ with respect to each of the parameters:
+	where $\hat{\theta}$ is as maximum likelihood estimator, $\theta^{lb}$ define the minimal value of $\theta$ and $\theta^{ub}$ is the maximum value of $\theta$.
+
+	Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector $\theta$ by equating to zero the partial derivatives of $\ln L$ with respect to each of the parameters:
 
@@
 	Solution of Equations \ref{EQ: MLE_Basic_Solution} yield the desired estimates $\hat{\theta}$.
-For some models, these equations can be explicitly solved for $\hat{\theta}$ but in general no closed-form solution to the maximization problem is known or available, and an MLE can only be found via numerical optimization.
+For some models, these equations can be explicitly solved for $\hat{\theta}$ but in general no closed-form solution to the maximization problem is known or available, and an maximum likelihood estimator can only be found via numerical optimization.
 
-		\sout{By carrying out this operation, under fairly unrestrictive conditions,} 
 			It can be shown that as $n$ approaches infinity the maximum likelihood estimates have the desirable asymptotic properties:
@@
 
+											\fi
+
 										\end{document}

### 2023-08-08 SFE_article_Parameter_Estimation/Sections/Parameter_estimation_solution_from_another_IG.tex
08.08

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	Tables \ref{tab:Constraints_2}, \ref{tab: Estimation_results_2} and Figures \ref{fig: estimation_results_2}, \ref{fig:Regression-2}, \ref{fig:Regression_tau_simga_2} and \ref{fig: estimation_results_profiles_2} describe the solution of the parameter estimation problem solved from another initial solution.

	\begin{table}[!h]
		\centering
		\adjustbox{max width=\columnwidth}{%
			\begin{tabular}{ lccccccc }
				\hline 
				Parameter		&$k_m$[-] 	& $D_i$[m/s$^2$] 	& $D_e^M$[m/s$^2$]	& $C_{sat}$ [kg/m$^3$] 	& $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
				Lower bound		&0	  		& 0 	  			& 0 				&	0					& 80 		 		& 0 	   		& 0 \\ 
				Upper bound		&1 			& $+\infty$ 		& $+\infty$			&	$+\infty$			& 150 				& 1 			& $+\infty$ \\ 
				Initial guess	&0.01  		& 3 	  			& 1 				&	1					& 100 		 		& 0.65 	   		& 0.4 \\  \hline
		\end{tabular} }
		\caption{Constraints and initial guess of the parameter estimation problem}
		\label{tab:Constraints_2}
	\end{table}

	\begin{table}[!h]
		\centering
		\adjustbox{max width=\columnwidth}{%
			\csvautobooktabular{Figures/Results_estimation/estimation_2.csv} }
		\caption{Parameter estimation results rounded to fifth decimal place}
		\label{tab: Estimation_results_2}
	\end{table}

	\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200_2.pdf}
			\caption{Experiment at $40^\circ C$ and $200$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200_2.pdf}
			\caption{Experiment at $50^\circ C$ and $200$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org_2.pdf}
			\caption{Experiment at $40^\circ C$ and $300$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org_2.pdf}
			\caption{Experiment at $50^\circ C$ and $300$ bar}
		\end{subfigure}
		\caption{Results of parameter fitting, with estimation of the initial state}
		\label{fig: estimation_results_2}
	\end{figure}

	\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 11.7cm 14cm 2.3cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1_2.pdf}
			\caption{First-order polynomial regression of fitted parameters ($D_i$ and $D_e^M$) as a function of fluid density $\rho_f$}
			\label{fig:Regression_12}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 11.7cm 14cm 2.3cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_2_2.pdf}
			\caption{Second-order polynomial regression of fitted parameters ($D_i$ and $D_e^M$) as a function of fluid density $\rho_f$}
			\label{fig:Regression_22}
		\end{subfigure}
		\caption{Regression of $D_i$ and $D_e^M$} 
		\label{fig:Regression-2}
	\end{figure}

	\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 18.8cm 8cm 2.5cm 7.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_1_2.pdf}
			\includegraphics[trim = 4cm 2cm 17.5cm 13.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_1_2.pdf}
			\caption{First order polynomial regression of fitted parameters ($\tau$ and $\sigma$) as a function of fluid density $\rho_f$}
			\label{fig:Regression_32}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 18.8cm 8cm 2.5cm 7.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_2_2.pdf}
			\includegraphics[trim = 4cm 2cm 17.5cm 13.6cm,clip,width=0.49\textwidth]{/Results_estimation/Trend_Lines_order_2_2.pdf}
			\caption{Second order polynomial regression of fitted parameters ($\tau$ and $\sigma$) as a function of fluid density $\rho_f$}
			\label{fig:Regression_42}
		\end{subfigure}
		\caption{Regression of $\tau$ and $\sigma$} 
		\label{fig:Regression_tau_simga_2}
	\end{figure}

	\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 1.4cm 1.9cm 11cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200_2.pdf}
			\caption{Experiment at $40^\circ C$ and $200$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 1.4cm 1.9cm 11cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200_2.pdf}
			\caption{Experiment at $50^\circ C$ and $200$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 1.4cm 1.9cm 11cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org_2.pdf}
			\caption{Experiment at $40^\circ C$ and $300$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 1.4cm 1.9cm 11cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org_2.pdf}
			\caption{Experiment at $50^\circ C$ and $300$ bar}
		\end{subfigure}
		\caption{Concentration profiles after solving the parameter estimation problem}
		\label{fig: estimation_results_profiles_2}
	\end{figure}

\end{document}

### 2023-08-08 SFE_article_Parameter_Estimation/Sections/Saturation.tex
08.08

--- 2023-08-01 SFE-article/Sections/Saturation.tex
@@
 
-	where the ${\color{magenta}\Upsilon}$ describe the curvature of the decay function. The final form of the extraction kinetic equation is given by equation \ref{Model_kinetic}.
+	where the ${\color{magenta}\Upsilon}$ describe the curvature of the decay function. The final form of the extraction kinetic Equation is given by equation \ref{Model_kinetic}.
 
@@
 
+	Alternatively, the decay function ${\color{orange}\gamma}$ can be consider with respect to the Shrinking Core model presented by \citet{Goto1996}, where the particle radius change as the amount of solute in the solid phase decrease.
+As the particle size decrease due to dissolution, the diffusion path increase which makes the diffusion slower and reduce the value of a diffusion coefficient.
+The same analogy can be apply to the Equation \ref{EQ: C_sat_function} to explain the change of the diffusion coefficient.
+
 \end{document}

### 2023-08-08 SFE_article_Parameter_Estimation/Sections/introduction_imp.tex
08.08

--- 2023-06-20 SFE-article/Sections/introduction_imp.tex
@@
 
-	The present study focuses on extracting essential oil from the caraway (Carum carvi L.) seeds with supercritical fluid extraction and the modelling of that process.
+	The present study focuses on extracting essential oil from the caraway (Carum carvi L.) seeds with supercritical fluid extraction and modelling that process.
 Caraway is a biennial plant belonging to the Apiaceae family.
@@
 
-	The economic feasibility of the process is crucial when selecting appropriate technology.
-Conventional processes are frequently used for essential oil extraction, such as distillation and organic solvent extraction.
-The distillation process is carried out at a high temperature, which causes thermal degradation of thermolabile compounds.
-Considering that, alternatives techniques like supercritical fluid extraction gained popularity for extraction.
+	The economic feasibility of the process is crucial when selecting the appropriate technology.
+Conventional processes, such as distillation and organic solvent extraction, are frequently used for essential oil extraction.
+The distillation process is carried out at a high temperature, which causes thermal degradation of thermolabile compounds—considering that alternative techniques like supercritical fluid extraction gained popularity for extraction.
 Supercritical $CO_2$, in particular, is attractive due to its unique properties such as inflammable, non-toxic, low critical temperature and non-corrosive.
 Furthermore, its critical point is relatively low compared to other fluids, making it a suitable alternative to traditional extraction techniques.
-The supercritical fluids exhibit both gas- and liquid-like properties so pressure-depended dissolving power can be adjusted by operating conditions.
+The supercritical fluids exhibit both gas- and liquid-like properties so that operating conditions can adjust pressure-depended dissolving power.
 
@@
 	One model proposed by \citet{Reverchon1993} is the hot ball model, which is based on an analogy to heat transfer and describes an extraction process from solid particles containing small quantities of solute where solubility is not a limiting factor.
-Another model, called the Broken-and-Intact Cell model, was presented by \citet{Sovova1994}.
+Another model, the Broken-and-Intact Cell model, was presented by \citet{Sovova1994}.
 This model describes a system where the outer surfaces of particles have been mechanically interrupted, allowing easy access of solvent to the solute from the broken cells.
@@
 
-	In this work, the basic governing equations are derived and combine them with the kinetic model suggested by \citet{Reverchon1996} to obtain a general model for the extraction process of the oil from the caraway seed.
-This model simplifies some of the physical behavior to obtain a control-oriented model.
+	In this work, the fundamental governing equations are derived and combined with the kinetic model suggested by \citet{Reverchon1996} to obtain a general model for the oil extraction process from the caraway seed.
+This model simplifies some of the physical behaviour to obtain a control-oriented model.
 It is assumed that the extraction process operates semi-continuously in a cylindrical vessel.
@@
 
-	The purpose of this study is to develop a process model for the extraction of natural substances from solid materials and liquids using supercritical fluids, specifically supercritical $CO_2$.
+	This study aims to develop a process model for extracting natural substances from solid materials and liquids using supercritical fluids, specifically supercritical $CO_2$.
 To achieve this, the model parameters are estimated based on thermodynamic relations and a set of experiments conducted at various conditions.
@@
 	The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties.
-Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations, which are derived under the assumption of Low-Mach number.
+Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations derived under the Low-Mach number assumption.
 The simplified balance equations are combined with the extraction kinetic equation to develop the process model in Chapter \ref{CH: Extraction_model}.
 The maximum likelihood technique is presented in Chapter \ref{CH: Parameter_estimation} and is then combined with the process model.
-The dataset obtained from laboratory experiments is used to close the optimization problem in Chapter \ref{CH: Experiments}.
-Finally, Chapters \ref{CH: Results} and \ref{CH: Conclusion} discuss the results of the parameter estimations and simulation results.
+The dataset obtained from laboratory experiments closes the optimization problem in Chapter \ref{CH: Experiments}.
+Finally, the parameter estimations and simulation results are discussed in Chapters \ref{CH: Results} and \ref{CH: Conclusion}
 

### 2023-08-08 SFE_Presentation_Sensitivity_Analysis/wcce11.tex
08.08

\documentclass[8pt]{beamer}

\usetheme[progressbar=frametitle]{metropolis}
\setbeamercolor{background canvas}{bg=white}

\usepackage{appendixnumberbeamer}

\usepackage{booktabs}
\usepackage[scale=2]{ccicons}

\usepackage{pgfplots}
\usepgfplotslibrary{dateplot}

\usepackage{xspace}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}

\usepackage{lineno,hyperref}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{pdfpages}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{csvsimple}
\usepackage{smartdiagram}
\usesmartdiagramlibrary{additions}
\usepackage[export]{adjustbox}
\usepackage[document]{ragged2e}

\usepackage{amsbsy}
\newcommand*{\claps}[1]{\hbox to 0pt{\hss#1\hss}}
\newcommand*{\mat}[1]{\boldsymbol{\mathrm{#1}}}
\newcommand*{\subdims}[3]{\clap{\raisebox{#1}[0pt][0pt]{$\scriptstyle(#2 \times #3)$}}}
\fboxrule=1pt

\usepackage{soul}
\newcommand{\mathcolorbox}[2]{\colorbox{#1}{$\displaystyle #2$}}

\title{Sensitivity analysis of a control-oriented model of supercritical extraction}
\subtitle{}
% \date{\today}
\date{05.06.2023}
\author{Oliwer Sliczniuk}
\institute{Aalto University, Finland}

\titlegraphic{\includegraphics[trim = 8.5cm 7cm 8.5cm 7cm,clip,width=2cm]{Figures/logo.png} }

\begin{document}

	\begin{frame}
		\titlepage 
	\end{frame}

%	\begin{frame}{Contents}
%		\begin{enumerate}
%			\item Introduction to the process
%			\item Process model and assumptions
%			\item Methodology - forward sensitivity analysis
%			\item Simulation results
%			\item Sensitivity analysis results
%		\end{enumerate}
%	\end{frame}

	\begin{frame}[fragile]{SFE}
		What are advantages of supercritical fluid extraction?
		\begin{itemize}
			\item $CO_2$ non-flammable and non-toxic
			\item properties of $CO_2$ can be 'tuned' with operating conditions
			\item the critical point of $CO_2$ is easily accessible 
			\item high selectivity
			\item easy separation of the solvent (if there is no co-solvent)
		\end{itemize}

		\begin{figure}[!h]
			\centering
			\includegraphics[trim = 2.5cm 8cm 18cm 7cm,clip,width=0.31\textwidth]{Figures/Compressibility.pdf}
			\includegraphics[trim = 2.5cm 8cm 18cm 7cm,clip,width=0.31\textwidth]{Figures/RHO.pdf}
			\includegraphics[trim = 2.5cm 8cm 18cm 7cm,clip,width=0.31\textwidth]{Figures/CP.pdf}
			\caption{Properties of $CO_2$}
			\label{fig:SFE_drawing}
		\end{figure}

	\end{frame}

%	\begin{frame}[fragile]{$CO_2$ properties}
%		\begin{figure}[!h]
%			\centering
%			\includegraphics[trim = 2.5cm 8cm 2.5cm 7cm,clip,width=0.8\textwidth]{Figures/Compressibility.pdf}
%			\includegraphics[trim = 2.5cm 8cm 2.5cm 7cm,clip,width=0.8\textwidth]{Figures/RHO.pdf}
%			\includegraphics[trim = 2.5cm 8cm 2.5cm 7cm,clip,width=0.8\textwidth]{Figures/CP.pdf}
%			\caption{Properties of $CO_2$}
%			\label{fig:SFE_drawing}
%		\end{figure} 
%	\end{frame}

%	\section{Model description}

%	\begin{frame}[fragile]{SFE}
%		\begin{figure}[!h]
%			\centering
%			\includegraphics[trim = 5cm 0cm 5cm 0cm,clip,height=0.70\textheight]{Figures/SFE_Diagram.pdf}
%			\caption{Schematic representation of SFE process}
%		\end{figure} 
%	\end{frame}

	\begin{frame}[fragile]{SFE - assumptions}
		\begin{minipage}[b]{0.475\textwidth}
			\begin{figure}[!h]
				\centering
				\includegraphics[trim = 5cm 0cm 5cm 0cm,clip,width=\textwidth]{Figures/SFE_Diagram.pdf}
				\caption{Schematic representation of SFE process}
			\end{figure} 
		\end{minipage}
		\hfill \vrule \hfill
		\begin{minipage}[b]{0.475\textwidth}
			Assumptions:
			\begin{itemize}
				\item Quasi-one-dimensional model
				\item Negligible external diffusion
				\item Low-Mach number assumption
				\item No pressure drop
				\item Pseudo-single component
				\item Negligible thermal properties of solid phase
				\item Uniform distribution of the particles
				\item Varying void fraction along the extractor
			\end{itemize}
	\end{minipage}
	\end{frame}

	\begin{frame}{Model of an extractor}

		{\tiny\begin{align*}
		\intertext{(1) Fluid phase mass balance [1]}
				&\frac{\partial {\color{blue}c_f}(t,z)}{\partial t}
				+ \underbrace{\frac{1}{{\color{magenta}\phi}} \frac{\partial \left( {\color{blue}c_f}(t,z) u\right)}{\partial {\color{blue}z}}}_{Convection}
				= \underbrace{\frac{1-{\color{magenta}\phi}}{{\color{magenta}\phi}} {\color{blue}r_e}(t,z) }_{Kinetic}
				+ \underbrace{\frac{1}{{\color{magenta}\phi}} \frac{\partial}{\partial {\color{blue}z}} \left( \mathcolorbox{yellow}{D^M_e} \frac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}} \right) }_{Diffusion}
				\\
				%		\end{align*}}
		\intertext{(2) Solid phase mass balance [1]}
		%		{\scriptsize\begin{align*}
				&\cfrac{\partial \textcolor{blue}{c_s}(t,z)}{\partial t} = - \underbrace{{\color{blue}r_e}(t,z)}_{Kinetic}\\
				%		\end{align*}}
		\intertext{(3) Heat balance [2]}
		%		{\scriptsize\begin{align*}
				&\cfrac{\partial \left({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{red}P}(t)) {\color{blue}h}(t,z) A_f\right)}{\partial t} - \cfrac{\partial \left({\color{red}P}(t) A_f\right)}{\partial t} = 
				\underbrace{- \cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{blue}h}(t,z) A_f v \right)}{\partial {\color{blue}z}} }_{Convection}
				+ \underbrace{\cfrac{\partial}{\partial {\color{blue}z}} \left( k \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}} \right)}_{Diffusion}\\
%		\intertext{(4) Pressure}
%				&\cfrac{\partial \textcolor{blue}{P}(t)}{\partial t} = \cfrac{P(t)-P(t-1)}{\partial t}\\
%
				\\ \hline
		\intertext{Extraction kinetic [1]}
				{\color{blue}r_e}(t,z) &= -\cfrac{ \mathcolorbox{yellow}{D_i} } {{\color{magenta} \mu l^2} }\left({\color{blue}c_s}(t,z) \mathcolorbox{yellow}{k_m}  - {\color{blue}c_f}(t,z) \right)
		\intertext{Output function [3]}
		%		{\scriptsize\begin{align*}
				\textcolor{blue}{y}(t) &= \textcolor{blue}{g}(x(t)) = \int_{0}^{t_f} \textcolor{red}{Q}(t)  \textcolor{blue}{c_f}(t,z) |_{z = L} dt =
				\int_{0}^{t_f} \textcolor{red}{u}(t)  \textcolor{green}{A} \textcolor{blue}{c_f}(t,z) |_{z = L} dt =
				\iff \cfrac{ \partial \textcolor{blue}{y}(t)}{\partial t} = \textcolor{red}{u}(t) A \textcolor{blue}{c_f}(t,z) |_{z = L}\\
	 	\intertext{Equation of state - Peng-Robinson}
		%		{\scriptsize\begin{align*}
				 \textcolor{orange}{P} & \left( \textcolor{blue}{T}(t,z), \textcolor{blue}{\rho}(t,z) \right) = \frac{R \textcolor{blue}{T}(t,z) }{\textcolor{blue}{v}(t,z)-b} - \frac{a}{\textcolor{blue}{v}(t,z)(\textcolor{blue}{v}(t,z)+b)+b(\textcolor{blue}{v}(t,z)-b)}; \quad \textcolor{blue}{v}(t,z) = \cfrac{1}{ \textcolor{blue}{\rho}(t,z) }
		\end{align*}}
	\hrule
	\Tiny{[1] E. Reverchon, Mathematical modeling of supercritical extraction of sage oil, AIChE J 42 (6), 1996}\\
	\Tiny{[2] John D. Anderson. Computational fluid dynamics the basic with applications. McGraw-Hill, 1995}\\
	\Tiny{[3] H. Sovova, R. Komers, J. Kucuera, and J. Jezu. Supercritical carbon dioxide extraction of caraway essential oil. Chemical Engineering Science, 1994}
	\end{frame}

	\begin{frame}[fragile]{Model discretization}
		\footnotesize{
			\begin{align*}
				\cfrac{d x(t)}{d t} &= 
				\begin{bmatrix}
					\cfrac{d c_{f_1}(t)}{d t}   	\\
					\vdots					   		\\
					\cfrac{d c_{f_{N_z}}(t)}{d t} 	\\
					\cfrac{d c_{s_1}(t)}{d t}   	\\
					\vdots					   		\\
					\cfrac{d c_{s_{N_z}}(t)}{d t}	\\
					\cfrac{d h_1(t)}{d t} 	   		\\
					\vdots 					   		\\
					\cfrac{d h_{N_z}(t)}{d t} 		\\
					\cfrac{d P(t)}{dt}				\\
					\cfrac{d y(t)}{dt}
				\end{bmatrix}
				=
				\begin{bmatrix}
					F_1 \left(c_f(t),c_s(t),T(t), y(t); \Theta \right)\\ 
					\vdots\\ 
					F_{N_z} \left(c_f(t),c_s(t),T(t), y(t); \Theta \right)\\ \\
					F_{N_z+1} \left(c_f(t),c_s(t),T(t), y(t); \Theta \right)\\
					\vdots\\
					F_{2N_z} \left(c_f(t),c_s(t),T(t), y(t); \Theta \right)\\ \\
					F_{2N_z+1} \left(c_f(t),c_s(t),T(t), y(t); \Theta \right) \\
					\vdots\\
					F_{3N_z} \left(c_f(t),c_s(t),T(t), y(t); \Theta \right) \\ \\
					F_{3N_z+1} \left(c_f(t),c_s(t),T(t), y(t); \Theta \right) \\ \\
					F_{3N_z+2} \left(c_f(t),c_s(t),T(t), y(t); \Theta \right) 
				\end{bmatrix}
				= F \left( t; \Theta \right)
		\end{align*} }\\
		where $x \in \mathbb{R}^{N_x = 3N_z+2} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $
	\end{frame}

%	\begin{frame}[fragile]{Parameter estimation}
%		\small{
%			Maximum likelihood estimation [4] is used to define the objective function of the parameter estimation problem
%			
%			{\footnotesize
%				\begin{equation}
%					\ln L = -\cfrac{n}{2} \left( \ln \sqrt{2 \pi} + \ln \mathcolorbox{yellow}{\sigma^2} \right)
%					- \cfrac{ \sum_{i=1}^{n} \left[  Y(t_i) - y(\theta , t_i) \right]^2 }{2 \mathcolorbox{yellow}{\sigma^2}}
%				\end{equation}
%			}
%			
%			The parameter estimation problem can be formulated as follow:
%			
%			{\footnotesize
%				\begin{equation*}
%					\begin{aligned} \label{EQ: Optimization_formulation_MLE}
%						&\hat{\theta}_{MLE} &= \arg \max_{\sigma, \theta \in \Theta} \ln L = \arg \max_{\sigma,\theta \in \Theta} p(\theta|y) \\
%						&\text{subject to}
%						& \dot{x} = f(t,x,\theta) \\
%						&& \dot{\theta} = 0 \\
%						&& \theta^{lb} \leq \theta \leq \theta^{ub}
%					\end{aligned}
%			\end{equation*} }
%			
%			If the measurement is 'cumulative', then each new observation includes the error of the previous observations, but the differences in measurement from one period to the next are independent. In such a case, the measurement data should be redefined as:
%			
%			{\footnotesize
%				\begin{align*}
%					Y(t_i) = \sum_{j=1}^{i} \left( Y(t_j) - Y(t_{j-1}) \right) = \sum_{j=1}^{i} \left( y(\theta, t_j) - y(\theta, t_{j-1}) \right) + \sum_{j=1}^{i} \epsilon_j 
%			\end{align*} }
%			
%			in which $\epsilon_j$ are independent random variables with $\mathbb{E}\{\epsilon_j\}$ and Var$\{\epsilon_i\} = \sigma^2$, a constant. 
%		}
%	
%		\hrule
%		\Tiny{[4] David Mautner Himmelblau. Process analysis by statistical methods, 1970.}
%	\end{frame}

	\begin{frame}[fragile]{Results of the simulation}
		\begin{figure}[!h]
			\centering
			\begin{subfigure}[b]{0.49\textwidth}
				\centering
				\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{Figures/Fitting_LUKE_T40_P200.pdf}
				\caption{Experiment at $40^\circ C$ and $200$ bar}
			\end{subfigure}
			\hfill
			\begin{subfigure}[b]{0.49\textwidth}
				\centering
				\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{Figures/Fitting_LUKE_T50_P200.pdf}
				\caption{Experiment at $50^\circ C$ and $200$ bar}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\centering
				\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{Figures/Fitting_LUKE_T40_P300_org.pdf}
				\caption{Experiment at $40^\circ C$ and $300$ bar}
			\end{subfigure}
			\hfill
			\begin{subfigure}[b]{0.49\textwidth}
				\centering
				\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{Figures/Fitting_LUKE_T50_P300_org.pdf}
				\caption{Experiment at $50^\circ C$ and $300$ bar}
			\end{subfigure}
%			\begin{subfigure}[b]{0.60\textwidth}
%				\hspace*{-1.2cm}
%				\centering
%				\includegraphics[trim = 3cm 14cm 2.3cm 1cm,clip,width=\textwidth]{Figures/Trend_Lines_order_2.pdf}
%				\caption{Second-order polynomial regression of fitted parameters ($k_m$, $D_i$ and $D_e^M$) as a function of fluid density $\rho_f$}
%			\end{subfigure}
%			\hfill
%			\begin{subfigure}[b]{0.39\textwidth}
%				\begin{minipage}[t]{\textwidth}
%						\vspace*{-1.2cm}
%						\centering
%						\adjustbox{max width=\columnwidth}{%
%							\csvautobooktabular{Figures/estimation.csv} }
%				\end{minipage}
%				\caption{Parameter estimation results rounded to fifth decimal place}
%			\end{subfigure}
		\end{figure}
	\end{frame}

%	\section{Sensitivity Analysis}

	\begin{frame}[fragile]{Sensitivity Analysis}
		Local derivative-based methods involve taking the partial derivative of the output with respect to an input parameter. In sensitivity analysis the original system of equations is solved simultaneously with $\frac{\partial \textcolor{blue}{F}(x(t);\Theta)}{\partial \Theta}$, where $\Theta$ is a vector of all the parameters and the control variables.

		\small{
			\begin{align*}
				Z &= \cfrac{\partial x(t,\Theta)}{\partial \Theta} \nonumber \\
				\dot{Z}  &= \cfrac{\partial Z(t,\Theta)}{\partial t} = \cfrac{\partial }{\partial t} \left( \cfrac{\partial x(t,\Theta)}{\partial \Theta} \right) = \cfrac{\partial }{\partial \Theta} \left( \cfrac{\partial x(t,\Theta)}{\partial t} \right) = \cfrac{d F(x(t);\Theta)}{d \Theta} \\
				\cfrac{d F(x(t);\Theta)}{d \Theta} &=  \cfrac{\partial F(x(t);\Theta)}{\partial x(t)} \cfrac{\partial x(t)}{\partial \Theta} + \cfrac{\partial F(x(t);\Theta)}{\partial \Theta}  \\
				& = J_x(x(t);\Theta)S(x(t);\Theta) + J_\Theta(x(t);\Theta)
			\end{align*}
			%		}
		%		\tiny{
			%		\[
			%		\framebox[1.2cm]{\claps{\raisebox{0pt}[1.0cm][1.0cm]{$\mat {\cfrac{d F(x(t);\Theta)}{dp}} $}}\subdims{-1.5cm} {N_x} {N_p}} =
			%		\framebox[2.0cm]{\claps{\raisebox{0pt}[1.0cm][1.0cm]{$\mat J_x$}}\subdims{-1.5cm} {N_x} {N_x}} \ 
			%		\framebox[1.2cm]{\claps{\raisebox{0pt}[1.0cm][1.0cm]{$\mat S$}}  \subdims{-1.5cm} {N_x} {N_p}} + 
			%		\framebox[1.2cm]{\claps{\raisebox{0pt}[1.0cm][1.0cm]{$\mat J_p$}}\subdims{-1.5cm} {N_x} {N_p}}
			%		\]}
	}
	\tiny{
		\[
		\framebox[1.2cm]{\claps{\raisebox{0pt}[1.0cm][1.0cm]{$ {\cfrac{d F(x(t);\Theta)}{d\Theta}} $}}\subdims{-1.5cm} {N_x} {N_\Theta}} =
		\framebox[2.0cm]{\claps{\raisebox{0pt}[1.0cm][1.0cm]{$ {\cfrac{\partial F(x(t);\Theta)}{\partial x(t)}} $} }\subdims{-1.5cm} {N_x} {N_x}} \ 
		\framebox[1.2cm]{\claps{\raisebox{0pt}[1.0cm][1.0cm]{$ {\cfrac{\partial x(t)}{\partial \Theta}}$}}  \subdims{-1.5cm} {N_x} {N_\Theta}} + 
		\framebox[1.2cm]{\claps{\raisebox{0pt}[1.0cm][1.0cm]{$ {\cfrac{\partial F(x(t);\Theta)}{\partial \Theta}}$}}\subdims{-1.5cm} {N_x} {N_\Theta}}
		\]}

	\vspace*{0.5cm}
	\hrule
	\Tiny{[4] T. Maly, L. R. Petzold, Numerical methods and software for sensitivity analysis of differential-algebraic systems, Applied Numerical Mathematics 20 (1-2), 1996 }

	\end{frame}

	\begin{frame}[fragile]{Results of the sensitivity analysis - Internal diffusion}
		\begin{figure}[h]
			\centering
			\includegraphics[trim = 2cm 2cm 2cm 1cm,clip,width=0.9\textwidth,center]{Figures/D_iT50P200.pdf}	
			\caption{$50^\circ C,~200~bar$}
		\end{figure}
	\end{frame}
%	
%	\begin{frame}[fragile]{Results of the sensitivity analysis - Partition factor}
%		\begin{figure}[h]
%			\centering
%			\includegraphics[trim = 2cm 2cm 2cm 2cm,clip,width=0.9\textwidth,center]{Figures/k_m_all_long.pdf}	
%			\caption{$40-50^\circ C,~200-300~bar$}
%		\end{figure}
%	\end{frame}

	\begin{frame}[fragile]{Results of the sensitivity analysis - Flow-rate}
		\begin{figure}[h]
			\centering
			\includegraphics[trim = 2cm 2cm 2cm 1cm,clip,width=0.9\textwidth,center]{Figures/FT50P200.pdf}	
			\caption{$50^\circ C,~200~bar$}
		\end{figure}
	\end{frame}

	\begin{frame}[fragile]{Results of the sensitivity analysis - Flow-rate}
		\begin{figure}[h]
			\centering
			\includegraphics[trim = 2cm 2cm 2cm 2cm,clip,width=0.9\textwidth,center]{Figures/F_all.pdf}	
			\caption{$40-50^\circ C,~200-300~bar$}
		\end{figure}
	\end{frame}

	\begin{frame}[fragile]{Conclusion}
		The forward sensitivity analysis allows to 
		\begin{itemize}
			\item better understanding of the analysed model
			\item evaluated an influence of controls and parameters 
			\item identify sensitive and none-sensitive parameters
			\item spot modelling errors 
		\end{itemize}

	\end{frame}

\end{document}

### 2023-08-08 SFE_Sensitivity_Analysis/Integrator_SS.m

@@ -1,37 +1,0 @@
-function Results = Integrator_SS(Time, x0, S, p, Sdot, parameters)
-    import casadi.*
-
-    Results = nan(length(S),length(Time));
-    Results(:,1) = x0;
-    
-    timeStep_in_seconds = Time(2)-Time(1);
-    
-    dae = struct('x', S, 'p', p, 'ode', Sdot);
-
-    MyIntegrator = 'rk';
-
-    opts = struct();
-    opts.tf = timeStep_in_seconds;
-    %opts.monitor = '1';
-    %opts.nonlinear_solver_iteration = 'functional';
-    %opts.abstol  = 1e-10;
-    %opts.reltol  = 1e-8;
-
-    I = casadi.integrator('I', MyIntegrator, dae, opts);
-
-    %% Integrator
-    for i=1:(length(Time)-1)
-        
-        Q = Results(:,i);
-
-        res = I('x0', Q, 'p', parameters(i,:) );
-        Results(:,i+1) = full(res.xf.');
-
-        if(mod(Time(i)/Time(end),0.2)==0)
-                fprintf("Finished: %g [%%]\n",[i/length(Time)*100])
-        end
-
-    end
-
-
-end

### 2023-08-08 SFE_Sensitivity_Analysis/SpecificHeatComp.m

@@ -1,86 +1,0 @@
-function Cp = SpecificHeatComp(T, P, Z, RHO, theta)
-
-    % Specific heat equations
-    % https://cheguide.com/specific_heat_ratio.html
-   
-    % The article with specific heat plots, to compare
-    % https://www.sciencedirect.com/science/article/abs/pii/S0017931014006577
-
-    %% Parameters
-    Tc      = theta{10};         % Critical temperature [K]
-    Pc      = theta{11};         % Critical pressure [bar]
-    R       = 83.1447;    % Universal gas constant, [m3-bar/K-mol]
-    kappa   = 0.2250;
-    MW      = theta{14};         % Molar mass [g/mol]       
-    CP_0    = theta{17};     
-    CP_A    = theta{18};       
-    CP_B    = theta{19};       
-    CP_C    = theta{20};       
-    CP_D    = theta{21};
-    
-    %% Recalculate the Peng Robinson parameters
-    Tr = T ./ Tc;
-    Pr = P ./ Pc;
-    %alpha = (1 + kappa .* (1 - sqrt(Tr))).^2;
-    
-    m     = 0.37464 + 1.54226*kappa - 0.26992 * kappa^2;
-    alpha = ( 1 + m .* ( 1 - Tr.^0.5 ) ).^2;
-
-    a = 0.45724 .* R.^2 .* Tc.^2 *alpha ./ Pc;
-    b = 0.0777961 .* R    .* Tc           ./ Pc;
-
-    %A = a .* alpha .* P ./ R.^2 ./ T.^2;
-    A = 0.45723553.*alpha.*Pr./Tr.^2;
-    B = b .* P ./ R ./ T;
-
-    v = 1./RHO*MW*1e6;
-    
-    %% Derivatives
-    
-    %  (δP/ δV)_T = -RT/(v - b)² + 2a(v + b)/[v(v + b) + b(v - b)]²
-    dPdV = -R.*T./(v-b).^2 + 2.*a.*(v+b)./(v.*(v+b) + b.*(v-b)).^2;
-    
[…]

### 2023-08-08 SFE_Sensitivity_Analysis/compressibility_beta.m

@@ -1,44 +1,0 @@
-function beta = compressibility_beta(T,P,RHO,theta)
-    
-    %% Parameters
-    Tc      = theta{10};         % Critical temperature [K]
-    Pc      = theta{11};         % Critical pressure [bar]
-    R       = 83.1447;    % Universal gas constant, [m3-bar/K-mol]
-    kappa   = 0.2250;
-    MW      = theta{14};         % Molar mass [g/mol]
-    CP_0    = theta{17};
-    CP_A    = theta{18};
-    CP_B    = theta{19};
-    CP_C    = theta{20};
-    CP_D    = theta{21};
-    
-    %% Recalculate the Peng Robinson parameters
-    Tr = T ./ Tc;
-    Pr = P ./ Pc;
-    %alpha = (1 + kappa .* (1 - sqrt(Tr))).^2;
-    
-    m     = 0.37464 + 1.54226*kappa - 0.26992 * kappa^2;
-    alpha = ( 1 + m .* ( 1 - Tr.^0.5 ) ).^2;
-    
-    a = 0.45724 .* R.^2 .* Tc.^2 *alpha ./ Pc;
-    b = 0.0777961 .* R    .* Tc           ./ Pc;
-    
-    %A = a .* alpha .* P ./ R.^2 ./ T.^2;
-    A = 0.45723553.*alpha.*Pr./Tr.^2;
-    B = b .* P ./ R ./ T;
-    
-    v = 1./RHO*MW*1e6;
-    
-    %% Derivatives
-    
-    %  (δP/ δV)_T = -RT/(v - b)² + 2a(v + b)/[v(v + b) + b(v - b)]²
-    dPdV = -R.*T./(v-b).^2 + 2.*a.*(v+b)./(v.*(v+b) + b.*(v-b)).^2;
-    
-
-    %%
-
-    dVdP = 1/dPdV;
-
-    beta = -1./v .* dVdP ;
-
-end

### 2023-08-08 SFE_Sensitivity_Analysis/kRHOcp_Comp.m

@@ -1,16 +1,0 @@
-function krhocp = kRHOcp_Comp(T, P, Z, RHO, CP, epsi, theta)
-
-    % http://www.ffrc.fi/FlameDays_2009/3B/HankalinPaper.pdf
-    
-    %epsi     = theta{4};                                    % Void bed fraction    
-    rhoSolid = theta{7};                                    % Density of solid
-    cpSolid  = theta{24} * 1e3;                            %  [kJ/kg/K] -> [J/kg/K]
-
-    k_solid  = 0.18;         % thermal conductivity of solid particles W/m/K - Some engineering and thermal properties of black cumin(Nigella sativaL.) seeds | 10.1111/j.1365-2621.2007.01561.x
-    
-    k_fluid = HeatConductivity_Comp(T, RHO) * 10^-3;        % mili W/m/K -> W/m/K
-    cpFluid = CP;                                    % [J/kg/K]
-    
-    krhocp = ( (1-epsi) .* k_fluid + epsi .* k_solid ) ./ (cpFluid .* (1-epsi) .* RHO + cpSolid .* epsi .* rhoSolid);
-
-end

### 2023-08-08 SFE_Sensitivity_Analysis/modelSFE.m

@@ -1,268 +1,0 @@
-function xdot = modelSFE(x, p, mask)
-    % (t, x, u, parameters)
-    % Model with (F)luid, (S)olid, (T)emperature
-    % Di is a function of temperature (T), the function works with numbers,
-    % vectors of numbers and vectors of symbolic variables
-    % Rho (Peng-Robinson) are constant numbers
-
-    %% Load Paramters
-    T_u           =    p{1};
-    P_u           =    p{2};
-    F_u           =    p{3};
-
-    parameters    =    p(4:end);
-
-    nstages       =    parameters{1};
-    C0solid       =    parameters{2};     % Extractor initial concentration of extract
-    r             =    parameters{3};     % Extractor length (m)
-    epsi          =    parameters{4};     % Void bed fraction
-    dp            =    parameters{5};     % Diameter of the particle (m)
-    L             =    parameters{6};     % Length of the extractor (m)
-    rho_s         =    parameters{7};     %
-    km            =    parameters{8};
-    mi            =    parameters{9};
-
-    Di            =    parameters{44};      Di = Di * 1e-12;
-    Dx            =    parameters{45};      Dx = Dx * 1e-6;
-
-    nstages_index =    numel(mask);
-    
-    %% Properties of the bed
-    A             =     pi*r^2 ;       % Cross-section of the extractor (m^2)
-    rp            =     dp / 2;
-    lp2           =     (rp / 3)^2;
-   
-
-    %% States
-    FLUID         =    x(0*nstages_index+1:1*nstages_index);
-    SOLID         =    x(1*nstages_index+1:2*nstages_index);
-    TEMP          =    x(2*nstages_index+1:3*nstages_index);
-    %RHO_NS        =    x(3*nstages_index+1:4*nstages_index);
-    %VELOCITY_NS   =    x(4*nstages_index+1:5*nstages_index);
-    
-    E_Inv         = (1 - epsi.*mask).^(-1);
-
-    %%
-
-    PRESSURE      =    P_u * ones(nstages_index,1);
-    %PRESSURE      = Pressure_PR(TEMP,RHO_NS,parameters);
-      
-    %Properties of the fluid in the extractor
-    Z             =     Compressibility(TEMP, PRESSURE,   parameters);
-
-    RHO           =     rhoPB_Comp(     TEMP, PRESSURE, Z,parameters);
-    %RHO           = RHO_NS;
-
[…]

### 2023-08-08 SFE_Sensitivity_Analysis/plot_fitting.m

@@ -1,72 +1,0 @@
-function [] = plot_fitting(DATA, Time_in_sec, RHO, F, g, x0, KOUT, which_parameter, N_Delay, N_Sample, theta, print_mode)
-
-    Time = 0:numel(Time_in_sec);
-    
-    for i = 1:numel(DATA)
-    
-        subplot(2,2,i)
-
-        set(gcf,'Units','inches');
-        screenposition = get(gcf,'Position');
-        set(gcf,...
-            'PaperPosition',[0 0 screenposition(3:4)],...
-            'PaperSize',[screenposition(3:4)], ...
-            'renderer','OpenGL');
-        set(gca,'TickLabelInterpreter','latex')
-
-        load(DATA{i});
-
-        %T0homog   = 50 + 273.15;                             % Extractor initial temperature (pseudo-homogeneous)
-        feedTemp  = T0homog      * ones(1,length(Time_in_sec));  % Kelvin
-        feedPress = feedPress(1) * ones(1,length(Time_in_sec));  % Bars
-
-        feedFlow  = 0.4 * RHO(i) * 1e-3 / 60 * ones(1,length(Time_in_sec));  % l/min -> kg/min -> Kg / sec
-        
-        %% Inital values
-
-        uu = [feedTemp', feedPress', feedFlow'];
-
-        for k=1:1%numel(DATA)
-    
-            %[uu(1,:), KOUT(:,k)']
-    
-            %% Simulate system with estiamted parameter
-            [yy_out, tt_out, xx_out] = simulateSystem_ParameterEstimation(F, g, x0, uu, KOUT(:,i));
-    
-            yy_out_D = [ zeros(1,N_Delay) yy_out(1:end-N_Delay)];
-
-            %legend_name = sprintf('km = %g, Di = %g, \\sigma = %g', KOUT(:,k)');
-
-            hold on
-%            plot(Time, yy_out_D, 'LineWidth',1, 'DisplayName',legend_name);
-            %plot(Time(1:N_Sample:end), data, 'o','MarkerSize',2)
-            plot(Time, yy_out_D, 'LineWidth',1);
-            plot(Time(1:N_Sample:end), data ,'o')
-            hold off
-            
-        end
-
-        xlim([0,Time(end)])
-        ylim([-10,110])
-
-        yline(50,'--')
-        xline(50,'--')
-
-        yline(75,'--')
-        xline(100,'--')
-
[…]

### 2023-08-24 SFE_article_Sensitivity_Analysis/Article_Model_Parameters.tex
24.08

--- 2023-08-06 SFE-article/Article_Model_Parameters.tex
@@
 % ===================================================
-\title[mode=title]{Parameter estimation}                      
-\shorttitle{Parameter estimation}
+\title[mode=title]{Sensitivity Analysis}                      
+\shorttitle{Sensitivity Analysis}
 
@@
 \begin{abstract}
-%Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ is the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output.
-As an example, the supercritical extraction process is presented.
-The impact of mass flow rate, pressure, and inlet temperature on the model's output is discussed.
-The sensitivity analysis results prove that the considered variables can affect the extraction's yield and be used as control variables in optimization problems.
-Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
-%Given a system of partial differential equations, $F(t,x,\dot{x},\Theta,u)=0$, where $x$ represents state variables, $\Theta$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process.
-The process model describes a partially filled extractor with a fixed bed, which work under constant operating conditions.
-We assume that the flow is uniform across any cross-section, although the area available for the fluid phase can change along the extractor.
-We apply the concept of quasi-one-dimensional flow to mimic the modelling of a two-dimensional case.
-%In this work, a distributed-parameter model, based on \citet{Reverchon1996} is used to describe a fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent.
-The model parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient \textit{and saturation concentration} are obtained from parameter estimation.
-The parameters are estimated based on four experiments performed at $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar and $50^\circ C$/$300$ bar.
-Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
-This study aimed to investigate the supercritical extraction process of the caraway oil from caraway seeds.
-The extraction was performed in a partially filled extractor with a fixed bed operated under multiple constant operating conditions.
-The dataset collected from four experiments consists of four experiments conducted at different operating conditions: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar.
-A distributed-parameter model is used to describe the fluid-solid extraction process with $CO_2$ as a solvent.
+This study aimed to investigate the supercritical extraction process of caraway oil from caraway seeds.
+The extraction was performed in a partially filled extractor with a fixed bed operated under multiple operating conditions.
+A distributed-parameter model describes the fluid-solid extraction process with $CO_2$ as a solvent.
 The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
 The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
-This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, saturation concentration, and an initial state estimate.
-These parameters are estimated from the Peng-Robinson equation of state and by applying the maximum likelihood estimation method on yield data under the normal error assumption.
+The local sensitivity analysis investigates the influence of infinitely small changes in the inlet temperature, pressure, and flow rate on the extraction yield.
 
@@
 
-\subsection{Parameter estimation} \label{CH: Parameter_estimation}
-\subfile{Sections/Parameter_estimation}
+\subsection{Sensitivity Analysis} \label{CH: Sensitivity_Analysis}
+\subfile{Sections/Sensitivity_Analysis}
 
-\subsection{Experimental work}
-\subfile{Sections/Experiments}
+%\subsection{Experimental work}
+%\subfile{Sections/Experiments}
 
 \section{Results}
-\subfile{Sections/Results}
+\subfile{Sections/Results_Sensitivity}
 
 \section{Conclusions} \label{CH: Conclusion}
-
-This study presented basic aspects regarding the laboratory work for obtaining caraway extracts using supercritical $CO_2$ at different operating conditions.
-A first-principle process model was developed based on governing equations and simplified using the Low-Mach number approximation.
-Based on the literature review, the extraction kinetic model was selected.
-The values of unknown parameters in the process model were obtained by parameter estimation.
-The yield data from the experiments were compared against the yield data generated by the model.
-The IPOPT solver was used to solve the maximum likelihood estimation.
-The process model was found to have good agreement with experimental yield curves.
-Later, the parameters found for each experiment were combined to obtain more general relationships.
-The correlations for ${\color{orange}D_i^R}$, ${\color{orange}\Upsilon}$ and ${\color{orange}D_e^M}$ are presented as a function of ${\color{orange}\rho}$ or ${\color{orange}R_e}$.
-It should be noted that obtained correlations have been prepared with a limited amount of data.
-These correlations can be used to study qualitatively the impact of different operating conditions on the extraction yield by different methods, such as sensitivity analysis.
-Moreover, the generalized model could be useful in finding the optimal operating conditions with respect to the process economy.
 
@@
 
-\subsection{Maximum Likelihood} \label{CH: ML}
-\subfile{Sections/Likelihood}
+%\subsection{Maximum Likelihood} \label{CH: ML}
+%\subfile{Sections/Likelihood}
 
@@
 
-\subsection{Concentration profiles} \label{CH: Profiles}
-\subfile{Sections/Profiles}
+%\subsection{Concentration profiles} \label{CH: Profiles}
+%\subfile{Sections/Profiles}
 

### 2023-08-24 SFE_article_Sensitivity_Analysis/Sections/Model.tex
24.08

--- 2023-08-01 SFE-article/Sections/Model.tex
@@
 The cross-section change is taken into account by void fraction ${\color{magenta}\phi}(z)$, which depends on the spatial dimension.
-The equation \ref{EQ: Continuity_differential} shows the differential form, of the continuity equation:
+The Equation \ref{EQ: Continuity_differential} shows the differential form of the continuity equation:
 
@@
 
-	{\color{red}assign a color of v and u}
+	%{\color{red}assign a color of v and u}
 
@@
 	The detailed derivation of the mass balance equation for the fluid phase can be found in the appendix (\ref{CH: Gouverning equations}).
-The movement of the mobile pseudo-homogeneous phase (Equation \ref{Model_fluid}) is considered only in the axial direction, while the properties of the system in the radial direction are assumed to be uniform.
+The movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}) is considered only in the axial direction, while the properties of the system in the radial direction are assumed to be uniform.
 Additionally, the boundary layer adjacent to the inner wall of the extractor is neglected, resulting in a constant velocity profile across any cross-section of the extractor perpendicular to the axial direction.
@@
 The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
-Figure \ref{fig: SFE_Mechanism} illustrates the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as ${\color{blue}c_s}$ and the equilibrium concentrations at the solid-fluid interface are denoted as ${\color{blue}c_s^*}$ and ${\color{blue}c_P^*}$, respectively, for solid and fluid phases.
-The concentration of the solutes in the fluid phase in the center of the pore is denoted as ${\color{blue}c_{P}}$.
-As the solute diffuses through the pore, its concentration changes and reaches ${\color{blue}c_{Pf}}$ at the opening of the pore.
+Figure \ref{fig: SFE_Mechanism} illustrates the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as ${\color{blue}c_s}$ and the equilibrium concentrations at the solid-fluid interface are denoted as ${\color{blue}c_s^*}$ and ${\color{blue}c_p^*}$, respectively, for solid and fluid phases.
+The concentration of the solutes in the fluid phase in the center of the pore is denoted as ${\color{blue}c_{p}}$.
+As the solute diffuses through the pore, its concentration changes and reaches ${\color{blue}c_{pf}}$ at the opening of the pore.
 The solute then diffuses through the film around the particle and reaches a concentration in bulk ${\color{blue}c_f}$.
@@
 			\centering
-			%	\includegraphics[trim  = 6cm 0cm 3cm 0cm,clip,width=\linewidth]{Figures/SFE_draft.png}
-			\includegraphics[trim = 5.8cm 1.1cm 6cm 3cm,clip,width=\columnwidth]{Figures/SFE_draft.pdf}	
+			\includegraphics[trim = 45cm 0cm 60cm 20cm,clip,width=\columnwidth]{Figures/SFE_PFD.drawio.png}	
 			\caption{The extraction mechanism}
@@
 
-		\citet{Bulley1984} suggests a process where the driving force for extraction is given by the difference between the concentration of the solute in bulk, ${\color{blue}c_f}$, and in the center of the pore, ${\color{blue}c_P^*}$.
-The concentration ${\color{blue}c_P^*}$ is in equilibrium with ${\color{blue}c_s}$ according to an equilibrium relationship.
-The rate of extraction is thus ${\color{blue}r_\text{e}}\left({\color{blue}c_f} - {\color{blue}c^*_P}({\color{blue}c_s})\right)$.
+		\citet{Bulley1984} suggests a process where the driving force for extraction is given by the difference between the concentration of the solute in bulk, ${\color{blue}c_f}$, and in the center of the pore, ${\color{blue}c_p^*}$.
+The concentration ${\color{blue}c_p^*}$ is in equilibrium with ${\color{blue}c_s}$ according to an equilibrium relationship.
+The rate of extraction is thus ${\color{blue}r_\text{e}}\left({\color{blue}c_f} - {\color{blue}c^*_p}({\color{blue}c_s})\right)$.
 
-		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between ${\color{blue}c_s}$ and ${\color{blue}c_P^*}$.
-${\color{blue}c_P^*}$ is determined by an equilibrium relationship with ${\color{blue}c_f}$ and the extraction rate is ${\color{blue}r_\text{e}}\left({\color{blue}c_s} - {\color{blue}c^*_P}({\color{blue}c_f})\right)$ or more precisely
+		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between ${\color{blue}c_s}$ and ${\color{blue}c_p^*}$.
+${\color{blue}c_p^*}$ is determined by an equilibrium relationship with ${\color{blue}c_f}$ and the extraction rate is ${\color{blue}r_\text{e}}\left({\color{blue}c_s} - {\color{blue}c^*_p}({\color{blue}c_f})\right)$ or more precisely
 
@@
 
-			The Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which in this case is assumed to be $T_{ref}=298.15~[K]$ and $P_{ref}=1.01325~[bar]$.
+			The Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which in this case is assumed to be ${\color{magenta}T_{ref}}=298.15~[K]$ and ${\color{magenta}P_{ref}}=1.01325~[bar]$.
 
@@
 		Such a simplified equation takes into account the pressure change in the energy balance, but the dynamics are simplified and do not consider the effects of pressure losses.
-In a real system, the pressure change dynamics would depend on the pump used in the system, as well as the back-pressure regulator used to control the outlet valve.
+In a real system, the dynamics of pressure change would depend on a pump used in an extraction system, as well as a back-pressure regulator used to control an outlet valve.
 
@@
 
-		The efficiency of the process (the yield) is calculated according to equations \ref{Model_measurment_1} as presented by \citet{Sovova1994a}.
+		The efficiency of the process (the yield) is calculated according to Equation \ref{Model_measurment_1} as presented by \citet{Sovova1994a}.
 The measurement equation evaluate the mass of solute at the outlet of the extraction unit and sums it.
@@
 On the other hand, the solute concentration in the fluid phase should not follow the same assumption as the solid phase.
-During the preparation period, the solute diffuses to the fluid phase in contact with the solid particles.
-Later, the solute in the fluid phase is partially moved along the extractor (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed).
-As a result, the distribution of solute mass in the fluid phase is assumed not to be uniform.
+Every SFE system needs some time to reach the desired operating conditions but the solute diffuses from solid phase to the fluid phase already at the preparation stage.
+For instance, a pump introduce more and more fluid to the extractor to increase the pressure, which makes the fluid present already in that vessel to moves internally hence the solute in the fluid phase is non-uniformly distributed.
 Some conclusions can be drawn from the analysis of the initial part of each yield curve obtained from the laboratory (Figure \ref{fig: estimation_results}).
@@
 The controllable input variables are the mass flow-rate and temperature of the solvent in the feed and the pressure in the extractor.
-We extend the system state-space by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator (${\color{blue}Y}(t)$).
+Additionally, the pressure change is augumented with the state-space and denoted as ${\color{blue}P}(t)$.
+			The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator (${\color{blue}Y}(t)$).
 The system is controllable by manipulating the flow-rate and temperature (enthalpy) of $CO_2$ in the feed, and the pressure in the extractor.

### 2023-08-24 SFE_article_Sensitivity_Analysis/Sections/Parameter_estimation.tex
24.08

--- 2023-08-01 SFE-article/Sections/Parameter_estimation.tex
@@
 
-	The goal of parameter estimation is to obtain the "best" estimate of parameter set ${\color{magenta} \theta}$ (which is a subset of the parameter space ${\color{magenta}\Theta}$ containing all parameters of a model) based on the continuous observations ${\color{blue}Y}(t)$ or the discrete observations ${\color{blue}Y}(t_i)$.
+	Not all the parameters present in a process model can be estimated from the theoretical considerations.
+The goal of parameter estimation is to obtain the "best" estimate of unknown parameters ${\color{magenta} \theta}$ (which is a subset of the parameter space ${\color{magenta}\Theta}$ containing all parameters of a model) based on the continuous observations ${\color{blue}Y}(t)$ or the discrete observations ${\color{blue}Y}(t_i)$.
 Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, ${\color{blue}y}(t)$ (Equation \ref{Model_measurment_1}), to give the observable dependent variable ${\color{blue}Y}(t)$ (for example results of an experiment).

### 2023-08-24 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
24.08

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Results}

	The sensitivity equations were solved simultaneously with the original process model. The focus of this work is to investigate the influence of inlet temperature, pressure and mass flow-rate on the state-space as wall as on the extraction yield.

	The increase of the mass-flow rate affects the whole system simultaneously in the spatial direction. The change in mass flow-rate makes the fluid moves faster, but its thermodynamic state is not affected. As the result, the  Figure \ref{fig:Sensitivty_F_P} show no change in pressure during the simulation.

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 3cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/P_F.pdf}
    	\caption{The effect of $F$ change on $P$}
    	\label{fig:Sensitivty_F_P}
    \end{figure}

    Similarly, the energy in the system (defined as $\rho \times h$) is not affected as presented on Figure \ref{fig:Sensitivty_F_H}.

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 3cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.pdf}
    	\caption{The effect of $F$ change on $\rho \times h$}
    	\label{fig:Sensitivty_F_H}
    \end{figure}

    The increase in the mass flow-rate affects the concentration gradient and accelerate the extraction kinetic. The acceleration

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 3cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.pdf}
    	\caption{The effect of $F$ change on $C_s$}
    	\label{fig:Sensitivty_F_CS}
    \end{figure}

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 3cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.pdf}
    	\caption{The effect of $F$ change on $C_f$}
    	\label{fig:Sensitivty_F_CF}
    \end{figure}

\end{document}

### 2023-08-24 SFE_article_Sensitivity_Analysis/Sections/Sensitivity_Analysis.tex
24.08

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	Local derivative-based methods involve taking the partial derivative of the output with respect to an input parameter. This set of derivatives is known as sensitivity equations, and it is solved simultaneously with the process model. The purpose of the sensitivity analysis is to investigate how responsive the solution is for the perturbation of the parameter ${\color{magenta}p}$. According to \citet{Dickinson1976}, the sensitivity analysis can be used to determine the influence of the uncertainty on the solution of the original system. Another purpose is to distinguish sensitive parameters from insensitive ones, which might be helpful for model reduction. Finally, from a control engineering point of view, the sensitivity analysis allows to sort the control variables with respect to the level of effort required to change the model's output.

	As presented in the work of \citet{Maly1996}, the sensitivity analysis equations(${\color{blue}\dot{Z}}$) are developed by taking the total derivative of the original system ${\color{blue}F}({\color{blue}x}(t);{\color{magenta}p})$ with respect to ${\color{magenta}p}$.

	{\footnotesize
		\begin{align}
			%		\label{SA_def}
			{\color{orange}Z}({\color{blue}x}(t);{\color{magenta}p}) &= \cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}p}}
	\end{align} }

	As the process model depends on time $t$, parameters $p$ and initial conditions, each parameter's sensitivity also depend on time $t$. Therefore, the new system of equations can be obtained by taking derivatives with respect to time $t$ and applying the chain rule.

	{\footnotesize
		\begin{equation} \label{SA_dt} 
			{\color{blue}\dot{Z}}({\color{blue}x}(t);{\color{magenta}p})  = \cfrac{d {\color{orange}Z}(x(t);{\color{magenta}p})}{d t} = \cfrac{\partial }{\partial t} \left( \cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}p}} \right) = \cfrac{\partial }{\partial {\color{magenta}p}} \left( \cfrac{\partial {\color{blue}x}(t)}{\partial t} \right) = \cfrac{d {\color{blue}F}({\color{blue}x}(t);{\color{magenta}p})}{d {\color{magenta}p}} 
	\end{equation} }

	By applying the definition of the total derivative to the equation \ref{SA_dt}, the sensitivity equation can be obtained.

	{\footnotesize
		\begin{align}		
			\label{SA_eq_full}\cfrac{d {\color{blue}F}({\color{blue}x}(t);{\color{magenta}p})}{d {\color{magenta}p}} &=  \underbrace{ \cfrac{\partial {\color{blue}F}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x}(t)} }_{{\color{blue}J_x}({\color{blue}x}(t);{\color{magenta}p})} \underbrace{\cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}p}} }_{{\color{blue}S}({\color{blue}x}(t);{\color{magenta}p})} + \underbrace{ \cfrac{\partial {\color{blue}F}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p}} }_{{\color{blue}J_p}({\color{blue}x}(t);{\color{magenta}p})}
	\end{align} }

	The sensitivity equation \ref{SA_eq_full} is solved simultaneously with the original system. This equation is made of three terms: jacobian ${\color{blue}J_x}({\color{blue}x}(t);{\color{magenta}p})$, sensitivity matrix ${\color{blue}S}({\color{blue}x}(t);{\color{magenta}p})$ and jacobian ${\color{blue}J_p}({\color{blue}x}(t);{\color{magenta}p})$. The jacobian ${\color{blue}J_x}({\color{blue}x}(t);{\color{magenta}p})$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${\color{blue}J_x}(n_x,n_x)$ is the derivative of process model equations ${\color{blue}F}_{n_x}({\color{blue}x}(t);{\color{magenta}p})$ with respect to the state variable $x_{n_p}$.

	{\footnotesize
		\begin{align}
			\begingroup % keep the change local
			\setlength\arraycolsep{2pt}
			{\color{blue}J_x}({\color{blue}x}(t);{\color{magenta}p})=\begin{pmatrix}
				\cfrac{\partial {\color{blue}F_{1}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{1}}(t)} & \cfrac{\partial {\color{blue}F_{1}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{2}}(t)} & \cdots & \cfrac{\partial {\color{blue}F_{1}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{N_x}}(t)}\\
				\cfrac{\partial {\color{blue}F_{2}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{1}}(t)} & \cfrac{\partial {\color{blue}F_{2}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{2}}(t)} & \cdots & \cfrac{\partial {\color{blue}F_{2}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{N_x}}(t)}\\
				\vdots & \vdots & \ddots & \vdots\\ 
				\cfrac{\partial {\color{blue}F_{N_x}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{1}}(t)} & \cfrac{\partial {\color{blue}F_{N_x}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{2}}(t)} & \cdots & \cfrac{\partial {\color{blue}F_{N_x}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{N_x}}(t)}\\
			\end{pmatrix}
			\endgroup
	\end{align} }

	The sensitivity matrix ${\color{blue}S}({\color{blue}x}(t);{\color{magenta}p})$ represents the matrix of equations of size $N_x \times N_p$, where each equation ${\color{blue}S}(n_x,n_p)$ is the derivative of the state variable $x_{n_x}$ with respect to the parameter $p_{n_p}$.

	{\footnotesize
		\begin{equation}
			\begin{split}
				{\color{blue}S}({\color{blue}x}(t);{\color{magenta}p}) & = 
				\begingroup % keep the change local
				\setlength\arraycolsep{2pt}
				\begin{pmatrix}
					{\color{blue}s_{({1,1})}} & {\color{blue}s_{({1,2})}} & \cdots & {\color{blue}s_{({1,N_p})}}\\
					{\color{blue}s_{({2,1})}} & {\color{blue}s_{({2,2})}} & \cdots & {\color{blue}s_{({2,N_p})}}\\
					\vdots & \vdots & \ddots & \vdots\\
					{\color{blue}s_{({N_x,1})}} & {\color{blue}s_{({N_x,2})}} & \cdots & {\color{blue}s_{({N_x,N_p})}}\\
				\end{pmatrix}
				\endgroup
				=\\
				&=
				\begingroup % keep the change local
				\setlength\arraycolsep{2pt}
				\begin{pmatrix}
					\cfrac{d {\color{blue}x_{1}}(t)}{d {\color{magenta}p_{1}}} 	& \cfrac{d {\color{blue}x_{1}}(t)}{d {\color{magenta}p_{2}}}     & \cdots & \cfrac{d {\color{blue}x_{1}}(t)}{d {\color{magenta}p_{N_p}}}\\
					\cfrac{d {\color{blue}x_{2}}(t)}{d {\color{magenta}p_{1}}} 	& \cfrac{d {\color{blue}x_{2}}(t)}{d {\color{magenta}p_{2}}}     & \cdots & \cfrac{d {\color{blue}x_{2}}(t)}{d {\color{magenta}p_{N_p}}}\\
					\vdots					 	    & \vdots 					   	  & \ddots & \vdots\\
					\cfrac{d {\color{blue}x_{N_x}}(t)}{d {\color{magenta}p_{1}}} 	& \cfrac{d {\color{blue}x_{N_x}}(t)}{d {\color{magenta}p_{2}}}     & \cdots & \cfrac{d {\color{blue}x_{N_x}}(t)}{d {\color{magenta}p_{N_p}}}
				\end{pmatrix} 
				\endgroup
			\end{split}
	\end{equation} }

	The jacobian ${\color{blue}J_p}({\color{blue}x}(t);{\color{magenta}p})$ represents the matrix of equations of size $N_x \times N_p$, where each equation ${\color{blue}J_p}(n_x,n_p)$ is the direct derivative of the process model equation $F_{n_x}$ with respect to the parameter $p_{n_p}$.

	{\footnotesize
		\begin{align}
			{\color{blue}J_p}({\color{blue}x}(t);{\color{magenta}p}) & =
			\begingroup % keep the change local
			\setlength\arraycolsep{2pt}
			\begin{pmatrix}
				\cfrac{\partial {\color{blue}F_{1}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{1}}} & \cfrac{\partial {\color{blue}F_{1}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{2}}} & \cdots & \cfrac{\partial {\color{blue}F_{1}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{N_p}}}\\
				\cfrac{\partial {\color{blue}F_{2}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{1}}} & \cfrac{\partial {\color{blue}F_{2}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{2}}} & \cdots & \cfrac{\partial {\color{blue}F_{2}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{N_p}}}\\
				\vdots & \vdots & \ddots & \vdots\\
				\cfrac{\partial {\color{blue}F_{N_x}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{1}}} & \cfrac{\partial {\color{blue}F_{N_x}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{2}}} & \cdots & \cfrac{\partial {\color{blue}F_{N_x}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{N_p}}}
			\end{pmatrix}
			\endgroup
	\end{align}}

	The combined system containing the original set of equations ${\color{blue}F}({\color{blue}x}(t);{\color{magenta}p})$ and sensitivity equations can be formulated as ${\color{blue}\textbf{F}}\left({\color{blue}x}(t);{\color{magenta}p}\right)$. The size of ${\color{blue}\textbf{F}}\left({\color{blue}x}(t);{\color{magenta}p}\right)$ is equal to $N_s = N_x(N_p + 1)$.

	{\footnotesize
		\begin{align}
			{\color{blue}\textbf{F}}\left({\color{blue}x}(t);{\color{magenta}p}\right) = 
			\begin{bmatrix}
				{\color{blue}F}({\color{blue}x}(t);{\color{magenta}p})\\
				{\color{blue}J_x}({\color{blue}x}(t);{\color{magenta}p}){\color{blue}S}({\color{blue}x}(t);{\color{magenta}p}) + {\color{blue}J_p}({\color{blue}x}(t);{\color{blue}p})
			\end{bmatrix}
	\end{align} }

	The initial conditions are described as

	{\footnotesize
		\begin{align}
			{\color{blue}\textbf{F}}\left({\color{blue}x}(t_0);{\color{magenta}p}\right)  = 
			\begin{bmatrix} {\color{blue}x}(t_0),			& 
				\cfrac{ \text{d}{\color{blue}x}(t_0) }{ d{\color{magenta}p_1} },		& 
				\cdots,					 	&
				\cfrac{ d{\color{blue}x}(t_0) }{ d{\color{magenta}p_{N_p}} } 
			\end{bmatrix}^T
	\end{align} }

	In a similar way, the sensitivity analysis of the output function can be performed with respect to parameters ${\color{magenta}p}$. The output function ${\color{blue}g}({\color{blue}x}(t))$ returns ${\color{blue}y}(t)$. By taking a total derivative of ${\color{blue}y}(t)$ with respect to ${\color{magenta}p}$, the new sensitivity equation can be found.

	{\footnotesize
		\begin{align}
			\cfrac{d {\color{blue}y}(t)}{d{\color{magenta}p}} = \cfrac{d {\color{blue}g}({\color{blue}x}(t))}{d{\color{magenta}p}} = \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x}(t)} \cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}p}} + \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{magenta}p}}
	\end{align} }

	The ${\color{blue}g}({\color{blue}x}(t))$ itself is independent of the parameters, but it dependents on ${\color{blue}x}(t)$, which is the function of ${\color{magenta}p}$. In such a case the sensitivity equation for the output becomes

	{\footnotesize
		\begin{equation} \label{EQ:Output_sens_full}
			\cfrac{d {\color{blue}g}({\color{blue}x}(t))}{d {\color{magenta}p}} = \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x}(t)} \cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}p}} + 0 = \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x}(t)}  {\color{blue}S}({\color{blue}x}(t);{\color{magenta}p}) = 
		\end{equation}

		\begin{equation} 
			= \begingroup % keep the change local
			\setlength\arraycolsep{2pt}
			\begin{pmatrix}
				\cfrac{\partial {\color{blue}g_{1}}({\color{blue}x}(t))}{\partial {\color{blue}x_{1}}} & \cfrac{\partial {\color{blue}g_{1}}({\color{blue}x}(t))}{\partial {\color{blue}x_{2}}} & \cdots & \cfrac{\partial {\color{blue}g_{1}}({\color{blue}x}(t))}{\partial {\color{blue}x_{N_x}}}\\
				\cfrac{\partial {\color{blue}g_{2}}({\color{blue}x}(t))}{\partial {\color{blue}x_{1}}} & \cfrac{\partial {\color{blue}g_{2}}({\color{blue}x}(t))}{\partial {\color{blue}x_{2}}} & \cdots & \cfrac{\partial {\color{blue}g_{2}}({\color{blue}x}(t))}{\partial {\color{blue}x_{N_x}}}\\
				\vdots & \vdots & \ddots & \vdots\\
				\cfrac{\partial {\color{blue}g_{N_g}}({\color{blue}x}(t))}{\partial {\color{blue}x_{1}}} & \cfrac{\partial {\color{blue}g_{N_g}}({\color{blue}x}(t))}{\partial {\color{blue}x_{2}}} & \cdots & \cfrac{\partial {\color{blue}g_{N_g}}({\color{blue}}(t))}{\partial {\color{blue}x_{N_x}}}
			\end{pmatrix}
			\begin{pmatrix}
				{\color{blue}s_{({1,1})}} & {\color{blue}s_{({1,2})}} & \cdots & {\color{blue}s_{({1,N_p})}}\\
				{\color{blue}s_{({2,1})}} & {\color{blue}s_{({2,2})}} & \cdots & {\color{blue}s_{({2,N_p})}}\\
				\vdots & \vdots & \ddots & \vdots\\
				{\color{blue}s_{({N_x,1})}} & {\color{blue}s_{({N_x,2})}} & \cdots & {\color{blue}s_{({N_x,N_p})}}\\
			\end{pmatrix}
			\endgroup
	\end{equation} }

%	Keeping in mind that the output function returns only one value, the sensitivity equation of the output (\ref{EQ:Output_sens_full}) becomes:
%	
%	{\footnotesize
%		\begin{equation} \label{EQ:Output_sens_short}
%			\begin{split}
%				& \left( \cfrac{d {\color{blue}y}({\color{blue}x}(t))}{d {\color{magenta}p_{1}}}, \cfrac{d {\color{blue}y}({\color{blue}x}(t))}{d {\color{magenta}p_{2}}}, \cdots, \cfrac{d {\color{blue}y}({\color{blue}x}(t))}{d {\color{magenta}p_{N_p}}} \right)  = \\
%				& =  \left( \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x_{1}}}, \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x_{2}}}, \cdots, \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x_{N_x}}} \right)
%				\begingroup % keep the change local
%				\setlength\arraycolsep{2pt}
%				\begin{pmatrix}
%					{\color{blue}s_{({1,1})}} & {\color{blue}s_{({1,2})}} & \cdots & {\color{blue}s_{({1,N_p})}}\\
%					{\color{blue}s_{({2,1})}} & {\color{blue}s_{({2,2})}} & \cdots & {\color{blue}s_{({2,N_p})}}\\
%					\vdots & \vdots & \ddots & \vdots\\
%					{\color{blue}s_{({N_x,1})}} & {\color{blue}s_{({N_x,2})}} & \cdots & {\color{blue}s_{({N_x,N_p})}}\\
%				\end{pmatrix} \endgroup
%			\end{split}
%	\end{equation} }

\end{document}

### 2023-08-24 SFE_article_Sensitivity_Analysis/Sections/Thermodynamic_details.tex
24.08

--- 2023-06-21 SFE-article/Sections/Thermodynamic_details.tex
@@
 
-	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}.
-The main steps in the derivation of ${\color{orange}C^{CO_2}_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ are presented below:
+	%The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}.
+The main steps in the derivation of ${\color{orange}C_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ are presented below:
+	Following the work of \citet{Pratt2001}, it is assumed that the specific heat can be obtained as a sum of ideal gas contribution and a residual correction for non-ideal behaviour, as given by Equations \ref{eq: Cv_CO2} and \ref{eq: Cp_CO2}.
 
@@
 	\begin{subequations}\begin{align}
-			{\color{orange}C^{CO_2}_v}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) & = {\color{orange}C_v^{\text{I}}}\left({\color{blue}T}(t,z),P(t)\right) + {\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) \label{eq: Cv_CO2}; \\
-			{\color{orange}C^{CO_2}_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) & = \underbrace{{\color{orange}C_p^{\text{I}}}\left({\color{blue}T}(t,z),P(t)\right)}_{\text{Eq.
+			{\color{orange}C_v}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) & = {\color{orange}C_v^{\text{I}}}\left({\color{blue}T}(t,z),P(t)\right) + {\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) \label{eq: Cv_CO2}; \\
+			{\color{orange}C_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) & = \underbrace{{\color{orange}C_p^{\text{I}}}\left({\color{blue}T}(t,z),P(t)\right)}_{\text{Eq.
 } \eqref{eq: Cp_I}} + \underbrace{{\color{orange}C_p^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}_{\text{Eq.
@@
 
-	${\color{orange}C^{CO_2}_v}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}C^{CO_2}_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ are the specific heat of $CO_2$ at constant volume and pressure, respectively.
-${\color{orange}C_v^{\text{I}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}C_p^{\text{I}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$, with ${\color{orange}C_p^{\text{I}}}({\color{blue}T}(t,z)) - {\color{orange}C_v^{\text{I}}}({\color{blue}T}(t,z)) = {\color{magenta}R}$, are the specific heat of an ideal gas at constant volume and pressure.
-${\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}C_p^{\text{R}}}({\color{blue}T}(t,z), {\color{red}P}(t))$ are the correction terms.
-\\
+	${\color{orange}C_v}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}C_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ are the specific heat of $CO_2$ at constant volume and pressure, respectively.
 
+	The ideal-gas contribution ${\color{orange}C_v^{\text{I}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}C_p^{\text{I}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$, can be obtained based on heat-capacity data applicable to gases at low pressure.
 For $CO_2$, the ideal gas contribution to the specific heat at constant ${\color{red}P}(t)$, as function of ${\color{blue}T}(t,z)$ is given by,
@@
 	where the coefficients ({\color{red}REF}) of the expansion are ${\color{magenta}C_{P0}} = 4.728$, ${\color{magenta}C_{P1}} = 1.75 \times 10^{-3}$, ${\color{magenta}C_{P2}} = -1.34 \times 10^{-5}$, and ${\color{magenta}C_{P3}} = 4.10 \times 10^{-9}$.
-For the correction term ${\color{orange}C_p^{\text{R}}}\left({\color{blue}T}(t,z){\color{red}P}(t)\right)$ at constant pressure ${\color{red}P}(t)$, we have
+
+	The correction term ${\color{orange}C_p^{\text{R}}}\left({\color{blue}T}(t,z){\color{red}P}(t)\right)$ at constant pressure ${\color{red}P}(t)$, can be defined by introducing  ${\color{orange}C_p^{\text{I}}}({\color{blue}T}(t,z)) - {\color{orange}C_v^{\text{I}}}({\color{blue}T}(t,z)) = {\color{magenta}R}$ and using the definition of ${\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z){\color{red}P}(t)\right)$.
+The general form of the correction term is given by Equation \ref{eq: Cp_R}
 
@@
 
-	For the partial derivative of the volume with respect to temperature $T$ at constant pressure $P(t)$, we have
+	For the partial derivative of the volume with respect to temperature ${\color{blue}T}(t,z)$ at constant pressure ${\color{red}P}(t)$, we have
 
@@
 
-	with partial derivative of the compressibility factor with respect to temperature ${\color{blue}T}$ at constant pressure ${\color{blue}P}(t)$
+	with partial derivative of the compressibility factor with respect to temperature ${\color{blue}T}(t,z)$ at constant pressure ${\color{blue}P}(t)$
 
@@
 	\begin{equation}
-		{\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z),{\color{red}P}(t)\right) = \left(\cfrac{\partial{\color{orange}U^{\text{R}}}\left({\color{blue}T}(t,z),{\color{red}P}(t)\right)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)}.
-\label{eq: CvR}
+		{\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z),{\color{red}P}(t)\right) = \left(\cfrac{\partial{\color{orange}U^{\text{R}}}\left({\color{blue}T}(t,z),{\color{red}P}(t)\right)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} \label{eq: CvR}
 	\end{equation} }

### 2023-09-02 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
02.09

@@
 
+	\subsection{Flow-rate}
+
 	The increase of the mass-flow rate affects the whole system simultaneously in the spatial direction.
 The change in mass flow-rate makes the fluid moves faster, but its thermodynamic state is not affected.
-As the result, the  Figure \ref{fig:Sensitivty_F_P} show no change in pressure during the simulation.
+As the result, Figure \ref{fig:Sensitivty_F_P} show no change in pressure during the simulation.
 
@@
     	\centering
-    	\includegraphics[trim = 3cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/P_F.pdf}
+    	\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/P_F.pdf}
     	\caption{The effect of $F$ change on $P$}
@@
     Similarly, the energy in the system (defined as $\rho \times h$) is not affected as presented on Figure \ref{fig:Sensitivty_F_H}.
+As pressure and temperature are not affected by the increase in the mass flow-rate, the fluid density $\rho$ and enthalpy $h$ are insensitive to flow-rate change.
 
@@
     	\centering
-    	\includegraphics[trim = 3cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.pdf}
+    	\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.pdf}
     	\caption{The effect of $F$ change on $\rho \times h$}
@@
 
-    The increase in the mass flow-rate affects the concentration gradient and accelerate the extraction kinetic. The acceleration
+    The increase in the mass flow rate affects the concentration gradient and accelerates the extraction kinetics.
+Negative sensitivities in Figure \ref{fig:Sensitivty_F_CS} present the faster extraction rate.
+Negative values of $dc_s/dF$ can be interpreted as a 'faster' mass loss from the solid phase, which means the extraction efficiency improves.
+At the beginning of the extraction process, the change in the flow rate has a minimal effect on the extraction process (represented by close to zero sensitivities), due to the high concentration gradient, which leads the extraction kinetic.
+Later, the increment of the mass flow rate accelerates the extraction kinetic and sensitivities along the decrease to minimum values.
+Over time, the amount of solute in the solid phase decreases, and eventually, the extraction kinetic becomes limited by the concentration gradient.
+This behaviour is represented by sensitivities, which asymptotically go to zero.
+The asymptotic movement of sensitivities can be explained by the fact that the increase in the flow rate does not affect the extraction if all the solute has been removed from the solid phase.
 
@@
     	\centering
-    	\includegraphics[trim = 3cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.pdf}
+    	\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.pdf}
     	\caption{The effect of $F$ change on $C_s$}
@@
 
+    Figure \ref{fig:Sensitivty_F_CF} shows how the concentration of solute in the fluid phase is affected by the flow-rate increment.
+Initially, sensitivities are close to zero, which indicates very little system response.
+The flow-rate growth affects the ${\color{blue}C_f}(z,t)$ by increasing the velocity of the solute across the system, which also increases the concentration gradient.
+As a result, the positive sensitivities appear in the system and form a front, which moves from the inlet to the outlet of the extractor.
+Because the larger amount of solute moves faster across the system, the total amount of solute in both phases decreases faster, which eventually causes negative sensitivities to appear in the system.
+The negative sensitivities form the second front, which moves across the extractor.
+Eventually, the negative sensitivities asymptotically go to zero.
+
     \begin{figure}[h!]
     	\centering
-    	\includegraphics[trim = 3cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.pdf}
+    	\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.pdf}
     	\caption{The effect of $F$ change on $C_f$}
@@
 
+    Figure \ref{fig:Sensitivty_F_y} shows how the flow-rate increment changes the extraction yield.
+Initially, the sensitivity curve stays flat, which is caused by the fact that the fixed bed does not occupy the whole volume of the extractor, and the fluid needs some time to flow through the empty part of the extractor to reach its outlet.
+When the solute in the fluid phase reaches the outlet of the extractor, then system response can be observed.
+The $dy/dF$ starts to increase, and positive value of sensitivity indicates an improvement in the process efficiency, hence the yield increment.
+Over time, the sensitivity reaches its maximum and diminishes due to decreasing concentration gradient.
+The $dy/dF$ asymptotically goes to zero because the amount of solute in the fluid phase becomes a limiting factor of the extraction process, and the flow-rate increment has less effect on the extraction yield.
+
+    \begin{figure}[h!]
+    	\centering
+    	\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_F.pdf}
+    	\caption{The effect of $F$ change on $y(t)$}
+    	\label{fig:Sensitivty_F_y}
+    \end{figure}
+
+    \subsection{Pressure}
+
 \end{document}

### 2023-09-02 SFE_article_Sensitivity_Analysis/Sections/Sensitivity_Analysis.tex
02.09

@@
 				{\color{blue}S}({\color{blue}x}(t);{\color{magenta}p}) & = 
-				\begingroup % keep the change local
-				\setlength\arraycolsep{2pt}
-				\begin{pmatrix}
-					{\color{blue}s_{({1,1})}} & {\color{blue}s_{({1,2})}} & \cdots & {\color{blue}s_{({1,N_p})}}\\
-					{\color{blue}s_{({2,1})}} & {\color{blue}s_{({2,2})}} & \cdots & {\color{blue}s_{({2,N_p})}}\\
-					\vdots & \vdots & \ddots & \vdots\\
-					{\color{blue}s_{({N_x,1})}} & {\color{blue}s_{({N_x,2})}} & \cdots & {\color{blue}s_{({N_x,N_p})}}\\
-				\end{pmatrix}
-				\endgroup
-				=\\
-				&=
+%				\begingroup % keep the change local
+%				\setlength\arraycolsep{2pt}
+%				\begin{pmatrix}
+%					{\color{blue}s_{({1,1})}} & {\color{blue}s_{({1,2})}} & \cdots & {\color{blue}s_{({1,N_p})}}\\
+%					{\color{blue}s_{({2,1})}} & {\color{blue}s_{({2,2})}} & \cdots & {\color{blue}s_{({2,N_p})}}\\
+%					\vdots & \vdots & \ddots & \vdots\\
+%					{\color{blue}s_{({N_x,1})}} & {\color{blue}s_{({N_x,2})}} & \cdots & {\color{blue}s_{({N_x,N_p})}}\\
+%				\end{pmatrix}
+%				\endgroup
+%				=\\
+%				&=
 				\begingroup % keep the change local
@@
 
-	The ${\color{blue}g}({\color{blue}x}(t))$ itself is independent of the parameters, but it dependents on ${\color{blue}x}(t)$, which is the function of ${\color{magenta}p}$.
+%	The ${\color{blue}g}({\color{blue}x}(t))$ itself is independent of the parameters, but it dependents on ${\color{blue}x}(t)$, which is the function of ${\color{magenta}p}$.
 In such a case the sensitivity equation for the output becomes
-
-	{\footnotesize
-		\begin{equation} \label{EQ:Output_sens_full}
-			\cfrac{d {\color{blue}g}({\color{blue}x}(t))}{d {\color{magenta}p}} = \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x}(t)} \cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}p}} + 0 = \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x}(t)}  {\color{blue}S}({\color{blue}x}(t);{\color{magenta}p}) =
-		\end{equation}
-
-		\begin{equation} 
-			= \begingroup % keep the change local
-			\setlength\arraycolsep{2pt}
-			\begin{pmatrix}
-				\cfrac{\partial {\color{blue}g_{1}}({\color{blue}x}(t))}{\partial {\color{blue}x_{1}}} & \cfrac{\partial {\color{blue}g_{1}}({\color{blue}x}(t))}{\partial {\color{blue}x_{2}}} & \cdots & \cfrac{\partial {\color{blue}g_{1}}({\color{blue}x}(t))}{\partial {\color{blue}x_{N_x}}}\\
-				\cfrac{\partial {\color{blue}g_{2}}({\color{blue}x}(t))}{\partial {\color{blue}x_{1}}} & \cfrac{\partial {\color{blue}g_{2}}({\color{blue}x}(t))}{\partial {\color{blue}x_{2}}} & \cdots & \cfrac{\partial {\color{blue}g_{2}}({\color{blue}x}(t))}{\partial {\color{blue}x_{N_x}}}\\
-				\vdots & \vdots & \ddots & \vdots\\
-				\cfrac{\partial {\color{blue}g_{N_g}}({\color{blue}x}(t))}{\partial {\color{blue}x_{1}}} & \cfrac{\partial {\color{blue}g_{N_g}}({\color{blue}x}(t))}{\partial {\color{blue}x_{2}}} & \cdots & \cfrac{\partial {\color{blue}g_{N_g}}({\color{blue}}(t))}{\partial {\color{blue}x_{N_x}}}
-			\end{pmatrix}
-			\begin{pmatrix}
-				{\color{blue}s_{({1,1})}} & {\color{blue}s_{({1,2})}} & \cdots & {\color{blue}s_{({1,N_p})}}\\
-				{\color{blue}s_{({2,1})}} & {\color{blue}s_{({2,2})}} & \cdots & {\color{blue}s_{({2,N_p})}}\\
-				\vdots & \vdots & \ddots & \vdots\\
-				{\color{blue}s_{({N_x,1})}} & {\color{blue}s_{({N_x,2})}} & \cdots & {\color{blue}s_{({N_x,N_p})}}\\
-			\end{pmatrix}
-			\endgroup
-	\end{equation} }
+%	
+%	{\footnotesize
+%		\begin{equation} \label{EQ:Output_sens_full}
+%			\cfrac{d {\color{blue}g}({\color{blue}x}(t))}{d {\color{magenta}p}} = \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x}(t)} \cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}p}} + 0 = \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x}(t)}  {\color{blue}S}({\color{blue}x}(t);{\color{magenta}p}) =
+%		\end{equation} 
+%		
+%		\begin{equation} 
+%			= \begingroup % keep the change local
+%			\setlength\arraycolsep{2pt}
+%			\begin{pmatrix}
+%				\cfrac{\partial {\color{blue}g_{1}}({\color{blue}x}(t))}{\partial {\color{blue}x_{1}}} & \cfrac{\partial {\color{blue}g_{1}}({\color{blue}x}(t))}{\partial {\color{blue}x_{2}}} & \cdots & \cfrac{\partial {\color{blue}g_{1}}({\color{blue}x}(t))}{\partial {\color{blue}x_{N_x}}}\\
+%				\cfrac{\partial {\color{blue}g_{2}}({\color{blue}x}(t))}{\partial {\color{blue}x_{1}}} & \cfrac{\partial {\color{blue}g_{2}}({\color{blue}x}(t))}{\partial {\color{blue}x_{2}}} & \cdots & \cfrac{\partial {\color{blue}g_{2}}({\color{blue}x}(t))}{\partial {\color{blue}x_{N_x}}}\\
+%				\vdots & \vdots & \ddots & \vdots\\
+%				\cfrac{\partial {\color{blue}g_{N_g}}({\color{blue}x}(t))}{\partial {\color{blue}x_{1}}} & \cfrac{\partial {\color{blue}g_{N_g}}({\color{blue}x}(t))}{\partial {\color{blue}x_{2}}} & \cdots & \cfrac{\partial {\color{blue}g_{N_g}}({\color{blue}}(t))}{\partial {\color{blue}x_{N_x}}}
+%			\end{pmatrix}
+%			\begin{pmatrix}
+%				{\color{blue}s_{({1,1})}} & {\color{blue}s_{({1,2})}} & \cdots & {\color{blue}s_{({1,N_p})}}\\
+%				{\color{blue}s_{({2,1})}} & {\color{blue}s_{({2,2})}} & \cdots & {\color{blue}s_{({2,N_p})}}\\
+%				\vdots & \vdots & \ddots & \vdots\\
+%				{\color{blue}s_{({N_x,1})}} & {\color{blue}s_{({N_x,2})}} & \cdots & {\color{blue}s_{({N_x,N_p})}}\\
+%			\end{pmatrix}
+%			\endgroup
+%	\end{equation} }
 

### 2023-09-11 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
11.09

@@
 The focus of this work is to investigate the influence of inlet temperature, pressure and mass flow-rate on the state-space as wall as on the extraction yield.
+The process model and parameters have been discussed in {\color{red}article 1}.
+The process model was calibrated on set of experiments obtained at different operating conditions, $40^\circ C$ - $50^\circ C$ and 200 bar - 300 bar.
+The sensitivity analysis has been performed under assumption that the system operates are $45^\circ C$ and 250 bar.
 
@@
 
+    As discussed in Chapter \ref{CH:Governing_equations_chapter}, a small pressure wave propagates with the speed of sound relative to the flow.
+If the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic which leads to $\partial {\color{blue}P}/\partial {\color{orange}\rho_f} = \infty$.
+The Low Mach-number assumption leads to instant pressure propagation along the system.
+It allows to consider one value of pressure for the whole system as all the changes occur in the machine simultaneously.
+Figure \ref{fig:Sensitivty_P_P} represents a step function, which indicate the pressure change in the system.
+
+    \begin{figure}[h!]
+    	\centering
+    	\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/P_P.pdf}
+    	\caption{The effect of $P$ change on $P$ in the system}
+    	\label{fig:Sensitivty_P_P}
+    \end{figure}
+
+	As a result of the Low Mach-number assumption and the pressure change, the temperature and density changes happen along the system simultaneously.
+As presented by Equation \ref{EQ:Enthalpy_equation}, the pressure change affect the quantity $h \times \rho_f$ directly through $\frac{\partial ({\color{blue}P}(t) A_f)}{\partial t}$, which leads to a step-change presented in Figure \ref{fig:Sensitivty_P_H}.
+Depending on the configuration of the system, two cases are possible.
+As the total energy in the extractor has changed, there might be a difference between the fluid inside the equipment and the inlet temperature(defined as a boundary condition).
+If the Dirichlet boundary condition is applied, the inlet temperature is kept at the pre-defined value and might differ from the temperature in the extractor.
+In such a case, the temperature difference will cause the heat front to propagate along the system.
+Alternatively, the Neumann boundary condition can be applied to ensure that the temperature inside the extractor and at its inlet is the same.
+In the case of this work, the second approach was chosen to simplify the discussion.
+
+    \begin{figure}[h!]
+    	\centering
+    	\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P.pdf}
+    	\caption{The effect of $P$ change on $(h \times \rho_f)$ in the system}
+    	\label{fig:Sensitivty_P_H}
+    \end{figure}
+
+	The pressure change affects the mass transfer in two ways.
+As given in Chapter \ref{CH: Continuity}, the velocity is inversely proportional to the density, hence the higher density of the fluid leads to the lower velocity and the residence time.
+The second way is given by the relationships, which connect the pressure and the extraction kinetic term.
+As presented in {\color{red}article 1}, the $D_i^R$ increase with the fluid density, which leads to higher extraction rate.
+The cumulative effect of the pressure change can be observed in Figure \ref{fig:Sensitivty_P_CS}.
+The
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.pdf}
+		\caption{The effect of $P$ change on $C_s$}
+		\label{fig:Sensitivty_P_CS}
+	\end{figure}
+
 \end{document}

### 2023-09-13 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
13.09

@@
 The process model was calibrated on set of experiments obtained at different operating conditions, $40^\circ C$ - $50^\circ C$ and 200 bar - 300 bar.
-The sensitivity analysis has been performed under assumption that the system operates are $45^\circ C$ and 250 bar.
+The sensitivity analysis has been performed under assumption that the system operates are $45^\circ C$ and 250 bar and 0.4 l/min.
 
@@
     	\centering
-    	\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/P_F.pdf}
+    	\includegraphics[trim = 1.5cm 1cm 0.5cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_F.pdf}
     	\caption{The effect of $F$ change on $P$}
@@
     	\centering
-    	\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.pdf}
+    	\includegraphics[trim = 1.5cm 1cm 0.5cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.pdf}
     	\caption{The effect of $F$ change on $\rho \times h$}
@@
     	\centering
-    	\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.pdf}
+    	\includegraphics[trim = 1.5cm 1cm 0.5cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.pdf}
     	\caption{The effect of $F$ change on $C_s$}
@@
     	\centering
-    	\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.pdf}
+    	\includegraphics[trim = 1.5cm 1cm 0.5cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.pdf}
     	\caption{The effect of $F$ change on $C_f$}
@@
 The $dy/dF$ asymptotically goes to zero because the amount of solute in the fluid phase becomes a limiting factor of the extraction process, and the flow-rate increment has less effect on the extraction yield.
+To show how $dy / dF$ converges to zero, the simulation time was expanded.
 
@@
     	\centering
-    	\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_F.pdf}
+    	\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_F.pdf}
     	\caption{The effect of $F$ change on $y(t)$}
@@
     	\centering
-    	\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/P_P.pdf}
+    	\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_P.pdf}
     	\caption{The effect of $P$ change on $P$ in the system}
@@
 
-	As a result of the Low Mach-number assumption and the pressure change, the temperature and density changes happen along the system simultaneously.
-As presented by Equation \ref{EQ:Enthalpy_equation}, the pressure change affect the quantity $h \times \rho_f$ directly through $\frac{\partial ({\color{blue}P}(t) A_f)}{\partial t}$, which leads to a step-change presented in Figure \ref{fig:Sensitivty_P_H}.
+	As a result of the Low Mach-number assumption and the pressure deviation, the temperature and density change along the system simultaneously.
+According to Equation \ref{EQ:Enthalpy_equation}, the pressure change affect the quantity $h \times \rho_f$ directly through $\partial ({\color{blue}P}(t) A_f) / \partial t$, which leads to a step-change presented in Figure \ref{fig:Sensitivty_P_H}.
 Depending on the configuration of the system, two cases are possible.
@@
 If the Dirichlet boundary condition is applied, the inlet temperature is kept at the pre-defined value and might differ from the temperature in the extractor.
-In such a case, the temperature difference will cause the heat front to propagate along the system.
+In such a case, the temperature difference will cause the heat front to propagate through the system.
 Alternatively, the Neumann boundary condition can be applied to ensure that the temperature inside the extractor and at its inlet is the same.
@@
     	\centering
-    	\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P.pdf}
+    	\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P.pdf}
     	\caption{The effect of $P$ change on $(h \times \rho_f)$ in the system}
@@
 	The pressure change affects the mass transfer in two ways.
-As given in Chapter \ref{CH: Continuity}, the velocity is inversely proportional to the density, hence the higher density of the fluid leads to the lower velocity and the residence time.
+As given in Chapter \ref{CH: Continuity}, the velocity is inversely proportional to the density; hence, the higher density of the fluid leads to a lower velocity and larger residence time.
 The second way is given by the relationships, which connect the pressure and the extraction kinetic term.
-As presented in {\color{red}article 1}, the $D_i^R$ increase with the fluid density, which leads to higher extraction rate.
+As presented in {\color{red}article 1}, the $D_i^R$ increases with the fluid density, which leads to a higher extraction rate.
 The cumulative effect of the pressure change can be observed in Figure \ref{fig:Sensitivty_P_CS}.
-The
+The sensitivity plot shows a uniform decay of sensitivities along the fixed bed.
+The negative values of sensitivities suggest a faster extraction rate.
+No matter the location of the sensitivity in the bed, the general behaviour stays the same.
+Every sensitivity starts with zero and decreases to a minimum value.
+After the extremum, the sensitivities asymptotically increase to zero.
 
@@
 		\centering
-		\includegraphics[trim = 2cm 0cm 0cm 0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.pdf}
+		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.pdf}
 		\caption{The effect of $P$ change on $C_s$}
@@
 
+	The corresponding response of the pressure change on the solute concentration in the fluid phase is presented in Figure \ref{fig:Sensitivty_P_CF}.
+As discussed above, the pressure change directly affects the extraction kinetics.
+Figure \ref{fig:Sensitivty_P_CS} is characterized by negative sensitivities, which suggest a higher extraction rate due to pressure change.
+It is expected to observe an increase of solute in the fluid phase due to a higher extraction rate.
+That increase of the solute in the fluid phase is visible in Figure \ref{fig:Sensitivty_P_CF} as positive sensitivities, which forms a front moving along the extractor.
+As the extraction is faster, more solute goes to the fluid phase, explaining the hot spot in the Figure.
+Then, the solute flows along the system, where there are no solid particles, and the diffusion effect becomes noticeable.
+After the positive sensitivities, a small front of negative sensitivities can be observed.
+Due to higher extraction rate, more solute has been extracted at the beginning of the extraction time, which means that there is less solute to extract later, and that effect is visible in Figure \ref{fig:Sensitivty_P_CF} as a negative sensitivities.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.pdf}
+		\caption{The effect of $P$ change on $C_f$}
+		\label{fig:Sensitivty_P_CF}
+	\end{figure}
+
+	The effect of the pressure increase on the extraction yield is presented in Figure \ref{fig:Sensitivty_P_y}.
+The initial flat curve is related to a delay in the system caused by empty space in the extractor, through which the solvent with solute needs to flow to reach the outlet.
+Later, the positive sensitivity is present and indicates an increase in yield.
+The $dy / dP$ reaches a maximum and starts to decrease due to the lower amount of the solute left in the solid phase compared with the case before the pressure increment.
+The sensitivity decreases to negative values, reaches a minimum, and eventually goes zero.
+To show how $dy / dP$ converges to zero, the simulation time was expanded.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_P.pdf}
+		\caption{The effect of $P$ change on $y(t)$}
+		\label{fig:Sensitivty_P_y}
+	\end{figure}
+
+	\subsection{Inlet temperature}
+
+	The influence of the inlet temperature on the supercritical extraction differs from the two presented cases because the disturbance does not affect the whole system instantaneously but propagates through the system.
+As the fluid with modified temperature flows along the system, it gradually affects the mass transfer.
+One assumption is that inlet temperature does not affect the pressure, and because of that, a horizontal line is present in Figure \ref{fig:Sensitivty_P_T}.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_T_{in}.pdf}
+		\caption{The effect of $T_{in}$ change on $P$ in the system}
+		\label{fig:Sensitivty_P_T}
+	\end{figure}
+
+	The propagation of the heat front is presented in Figure \ref{fig:Sensitivty_T_H}.
+The inlet value of $(h\times \rho_f)$ is calculated based on the given value of the inlet temperature( Dirichlet boundary condition) and given pressure.
+The deviation in $T_{in}$ affects $(h\times \rho_f)$ at the inlet, which propagates according to the governing equations.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_T_{in}.pdf}
+		\caption{The effect of $T_{in}$ change on $(h \times \rho_f)$ in the system}
+		\label{fig:Sensitivty_T_H}
+	\end{figure}
+
+	Figure \ref{fig:Sensitivty_T_CS} shows how the concentration of the solute in the solid phase is affected by the inlet temperature change.
+Initially, the sensitivities are zero along the fixed bed because the heat front needs time to propagate to the fixed bed.
+As the propagation is not instantaneous, the non-uniform distribution of sensitivities along the fixed bed is visible.
+All the sensitivities start to grow and reach maxima.
+As presented in {\color{red}article 1}, the value of $D_i^R$ diminishes when the density decreases.
+It is expected to observe positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, which indicates a slower extraction rate.
+When the concentration gradient becomes a limiting factor, the sensitivities decrease.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_T_{in}.pdf}
+		\caption{The effect of $T_{in}$ change on $C_s$ in the system}
+		\label{fig:Sensitivty_T_CS}
+	\end{figure}
+
+	The influence of the inlet temperature on the solute in the fluid phase is shown in Figure \ref{fig:Sensitivty_T_CF}.
+At the start, all the sensitivities stay at zero because of idle time.
+When the fluid at a new temperature reaches the solid particles, it affects the mass transfer, which later affects the amount of the solute in the fluid phase.
+As a response to the slower extraction rate suggested by positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, the 'hot spot' with negative sensitivities is visible in Figure \ref{fig:Sensitivty_T_CF}.
+An effect of the diffusion can be observed in the section without the fixed bed where the front made of sensitivities becomes blurry.
+After the sensitivities reach minima, they grow and reach positive values.
+This behavior can be explained by considering that the heat front slowed the mass transfer, and more of the solute stayed in the solid phase.
+That leads to a higher concentration gradient in the later time of the extraction if compared to the situation without the inlet temperature deviation.
+The higher concentration gradient causes the increase of the $dc_f/dT_{in}$.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_T_{in}.pdf}
+		\caption{The effect of $T_{in}$ change on $C_f$ in the system}
+		\label{fig:Sensitivty_T_CF}
+	\end{figure}
+
+	Figure \ref{fig:Sensitivty_T_y} shows how the inlet temperature increment changes the extraction yield.
+Initially, the sensitivity curve stays flat, which is caused by the fact that the fixed bed does not occupy the whole volume of the extractor, and the fluid needs some time to flow through the empty part of the extractor to reach its outlet.
+When the solute in the fluid phase reaches the outlet of the extractor, then system response can be observed.
+The $dy/dT_{in}$ starts to decrease, and the negative sensitivity value indicates a worsened process efficiency.
+Over time, the sensitivity reaches its minimum and increases due to a higher concentration gradient (if compared to the case without the disturbance).
+The sensitivity reaches a positive maximum and decreases again due to lower reduced extraction kinetic and decreased concentration gradient.
+The $dy/dT_{in}$ becomes negative again, and eventually the sensitivity curve flattens.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_T_{in}.pdf}
+		\caption{The effect of $T_{in}$ change on $y(t)$ in the system}
+		\label{fig:Sensitivty_T_y}
+	\end{figure}
+
 \end{document}

### 2023-09-13 SFE_SEnsitivity_Analysis/main_Sensitivity_Analysis.m

@@ -2,8 +2,8 @@ startup;
 delete(gcp('nocreate'));
 % %p = Pushbullet(pushbullet_api);
 
-addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
-%addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
 import casadi.*
 
 Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
@@ -20,8 +20,8 @@ bed                     = 0.165;                                            % Pe
 
 % Set time of the simulation
 PreparationTime         = 0;
-ExtractionTime          = 400;
-timeStep                = 1.0;                                              % Minutes
+ExtractionTime          = 250;
+timeStep                = 0.01;                                             % Minutes
 SamplingTime            = 5;                                                % Minutes
 
 simulationTime          = PreparationTime + ExtractionTime;
@@ -143,11 +143,15 @@ Parameters_init_time   = [uu repmat(cell2mat(Parameters),1,N_Time)'];
 name_v = {'T_{in}', 'P', 'F'};
 
 My_Font = 24;
+My_Font_cont = 8;
+num_levels = 100;
 
 for ii = 1:3
+
+        %% Sensitivities calculations
         Parameters{8} = ii;
         Parameters_init_time   = [uu repmat(cell2mat(Parameters),1,N_Time)'];
-        [S,p,Sdot]              = Sensitivity(x, xdot, u, [ii] );
+        [S,p,Sdot]              = Sensitivity(x, xdot, u, ii );
 
         % Initial conditions
         x0_SA                   = [ x0; zeros(length(S)-length(xdot),1) ];
@@ -156,11 +160,14 @@ for ii = 1:3
         Results = Integrator_SS(Time*60, x0_SA, S, p, Sdot, Parameters_init_time);
         Res = Results(Nx+1:end,:);
 
+        %% Sensitivities plot - normal scale
         %subplot(3,2,1)
[…]

### 2023-09-14 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
14.09

@@
 The process model was calibrated on set of experiments obtained at different operating conditions, $40^\circ C$ - $50^\circ C$ and 200 bar - 300 bar.
-The sensitivity analysis has been performed under assumption that the system operates are $45^\circ C$ and 250 bar and 0.4 l/min.
+The sensitivity analysis has been performed under assumption that the system operates are $45^\circ C$, 250 bar, 0.4 l/min and the simulation was performed with the time step of 0.01 [min].
 
@@
 The change in mass flow-rate makes the fluid moves faster, but its thermodynamic state is not affected.
-As the result, Figure \ref{fig:Sensitivty_F_P} show no change in pressure during the simulation.
+\todo{Change the description} As the result, Figure \ref{fig:Sensitivty_F_P} show no change in pressure during the simulation.
 
@@
 As pressure and temperature are not affected by the increase in the mass flow-rate, the fluid density $\rho$ and enthalpy $h$ are insensitive to flow-rate change.
+\todo{Change the description}
 

### 2023-09-14 SFE_SEnsitivity_Analysis/main_Sensitivity_Analysis.m

@@ -2,8 +2,8 @@ startup;
 delete(gcp('nocreate'));
 % %p = Pushbullet(pushbullet_api);
 
-%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
-addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+%addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
 import casadi.*
 
 Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
@@ -146,7 +146,7 @@ My_Font = 24;
 My_Font_cont = 8;
 num_levels = 100;
 
-for ii = 1:3
+for ii = 3
 
         %% Sensitivities calculations
         Parameters{8} = ii;

### 2023-09-18 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
18.09

--- 2023-09-13 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
@@
 The process model was calibrated on set of experiments obtained at different operating conditions, $40^\circ C$ - $50^\circ C$ and 200 bar - 300 bar.
-The sensitivity analysis has been performed under assumption that the system operates are $45^\circ C$ and 250 bar and 0.4 l/min.
+The sensitivity analysis has been performed under assumption that the system operates are $45^\circ C$, 250 bar, 0.4 l/min and the simulation was performed with the time step of 0.01 [min] and 400 equally distributed points in the spatial direction.
 
@@
 
-	The increase of the mass-flow rate affects the whole system simultaneously in the spatial direction.
-The change in mass flow-rate makes the fluid moves faster, but its thermodynamic state is not affected.
-As the result, Figure \ref{fig:Sensitivty_F_P} show no change in pressure during the simulation.
+	The increase in the mass-flow rate affects the whole system simultaneously in the spatial direction.
+The change in mass flow-rate makes the fluid move faster and does not directly affect the thermodynamic state of the fluid.
+As a result, Figure \ref{fig:Sensitivty_F_P} shows no change in pressure during the simulation.
 
@@
     	\centering
-    	\includegraphics[trim = 1.5cm 1cm 0.5cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_F.pdf}
+    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_F.pdf}
     	\caption{The effect of $F$ change on $P$}
@@
 
-    Similarly, the energy in the system (defined as $\rho \times h$) is not affected as presented on Figure \ref{fig:Sensitivty_F_H}.
-As pressure and temperature are not affected by the increase in the mass flow-rate, the fluid density $\rho$ and enthalpy $h$ are insensitive to flow-rate change.
+    A change in flow rate has a direct impact on the kinetic energy of the fluid, as defined by the spatial derivative $\frac{\partial \left( {\color{orange}\rho_f}{\color{blue}h} A_f v \right)}{\partial {\color{blue}z}}$.
+The consequence of Equation \ref{EQ:Velocity} is the instantaneous change of the velocity field in the system, which means that the spatial derivative equals zero.
+Because ${\color{blue}h}$ represents an enthalpy but not a total enthalpy, it does not contain the kinetic energy contribution.
+Consequently, under conditions where the thermodynamic state remains constant, specifically with constant temperature and pressure, Figure \ref{fig:Sensitivty_F_H} demonstrates no significant deviation.
+
+    The flow rate change affects the fluid inside the system, but appropriate boundary conditions must be set.
+If Dirichlet boundary conditions are used, a numerical mismatch between boundary conditions and the computational domain might occur due to different ways of computing them.
+The system's enthalpy is computed based on time evolution of governing equations, while the enthalpy at the inlet is computed based on inlet temperature and pressure.
+A small numerical mismatch between these values would be presented in the system as a difference in enthalpy, which propagates along the spatial domain.
+To ensure that the fluid at the inlet and the fluid inside of the computational domain are defined in the same way, Neumann boundary conditions are used in this analysis.
 
@@
     	\centering
-    	\includegraphics[trim = 1.5cm 1cm 0.5cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.pdf}
+    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.pdf}
     	\caption{The effect of $F$ change on $\rho \times h$}
@@
 
-    The increase in the mass flow rate affects the concentration gradient and accelerates the extraction kinetics.
-Negative sensitivities in Figure \ref{fig:Sensitivty_F_CS} present the faster extraction rate.
-Negative values of $dc_s/dF$ can be interpreted as a 'faster' mass loss from the solid phase, which means the extraction efficiency improves.
-At the beginning of the extraction process, the change in the flow rate has a minimal effect on the extraction process (represented by close to zero sensitivities), due to the high concentration gradient, which leads the extraction kinetic.
-Later, the increment of the mass flow rate accelerates the extraction kinetic and sensitivities along the decrease to minimum values.
+   An increase in the mass flow rate impacts the concentration gradient and accelerates the extraction kinetics.
+Negative sensitivities in Figure \ref{fig:Sensitivty_F_CS} indicate a faster extraction rate.
+Negative values of $dc_s/dF$ can be interpreted as a 'faster' loss of mass from the solid phase, signifying an improvement in extraction efficiency.
+At the beginning of the extraction process, changes in the flow rate have a minimal effect on the extraction process, as evidenced by sensitivities that are close to zero.
+This is due to the dominance of the high concentration gradient, which leads the extraction kinetic.
+As time progresses, the increase in the mass flow rate accelerates the extraction kinetics, causing the sensitivities to decrease towards their minimum values.
 Over time, the amount of solute in the solid phase decreases, and eventually, the extraction kinetic becomes limited by the concentration gradient.
-This behaviour is represented by sensitivities, which asymptotically go to zero.
-The asymptotic movement of sensitivities can be explained by the fact that the increase in the flow rate does not affect the extraction if all the solute has been removed from the solid phase.
+This behavior is represented in the sensitivities, which asymptotically approach zero.
+The asymptotic movement of sensitivities can be explained by the fact that an increase in the flow rate does not impact the extraction process when all the solute has been removed from the solid phase.
 
@@
     	\centering
-    	\includegraphics[trim = 1.5cm 1cm 0.5cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.pdf}
+    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.pdf}
     	\caption{The effect of $F$ change on $C_s$}
@@
 
-    Figure \ref{fig:Sensitivty_F_CF} shows how the concentration of solute in the fluid phase is affected by the flow-rate increment.
-Initially, sensitivities are close to zero, which indicates very little system response.
-The flow-rate growth affects the ${\color{blue}C_f}(z,t)$ by increasing the velocity of the solute across the system, which also increases the concentration gradient.
-As a result, the positive sensitivities appear in the system and form a front, which moves from the inlet to the outlet of the extractor.
-Because the larger amount of solute moves faster across the system, the total amount of solute in both phases decreases faster, which eventually causes negative sensitivities to appear in the system.
-The negative sensitivities form the second front, which moves across the extractor.
-Eventually, the negative sensitivities asymptotically go to zero.
+    Figure \ref{fig:Sensitivty_F_CF} illustrates how the concentration of solute in the fluid phase responds to an increase in the flow rate.
+Initially, sensitivities are close to zero, indicating a minimal system response.
+The growth in flow rate affects ${\color{blue}C_f}(z,t)$ by increasing the velocity, consequently elevating the concentration gradient.
+As a result, positive sensitivities emerge within the system, forming a front that progresses from the inlet to the outlet of the extractor.
+The positive front indicates that the larger amount of solute moves faster across the system, which leads to faster decrease of the total amount of solute in both phases.
+This reduced amount of solute in the solid phase restricts the extraction rate due to a diminishment of the concentration gradient.
+This limitation leads to the formation of a front composed of negative sensitivities, which advances through the extractor.
+The negative front indicates that the solute concentration in the fluid phase becomes lower than before the flow rate increment.
+Eventually, the negative sensitivities asymptotically approach zero.
 
@@
     	\centering
-    	\includegraphics[trim = 1.5cm 1cm 0.5cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.pdf}
+    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.pdf}
     	\caption{The effect of $F$ change on $C_f$}
@@
 
-    Figure \ref{fig:Sensitivty_F_y} shows how the flow-rate increment changes the extraction yield.
-Initially, the sensitivity curve stays flat, which is caused by the fact that the fixed bed does not occupy the whole volume of the extractor, and the fluid needs some time to flow through the empty part of the extractor to reach its outlet.
-When the solute in the fluid phase reaches the outlet of the extractor, then system response can be observed.
-The $dy/dF$ starts to increase, and positive value of sensitivity indicates an improvement in the process efficiency, hence the yield increment.
-Over time, the sensitivity reaches its maximum and diminishes due to decreasing concentration gradient.
-The $dy/dF$ asymptotically goes to zero because the amount of solute in the fluid phase becomes a limiting factor of the extraction process, and the flow-rate increment has less effect on the extraction yield.
-To show how $dy / dF$ converges to zero, the simulation time was expanded.
+    Figure \ref{fig:Sensitivty_F_y} illustrates how the increase in flow rate affects the extraction yield.
+Initially, the sensitivity curve remains flat.
+This occurs because the fixed bed doesn't occupy the entire volume of the extractor, requiring some time for the fluid to flow through the empty portion of the extractor to reach its outlet.
+It's only when the solute in the fluid phase reaches the extractor's outlet that we can measure and observe the system response.
+At this point, $dy/dF$ begins to increase.
+The positive sensitivity value indicates an improvement in process efficiency, resulting in an increased yield.
+As time progresses, the sensitivity reaches its maximum and then diminishes due to a decreasing concentration gradient.
+Eventually, $dy/dF$ asymptotically approaches zero.
+This happens because the amount of solute in the fluid phase becomes a limiting factor in the extraction process, and the increase in flow rate has a reduced impact on the extraction yield.
+The simulation time was extended to demonstrate the convergence of $dy/dF$ toward zero.
 
@@
     	\centering
-    	\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_F.pdf}
+    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_F.pdf}
     	\caption{The effect of $F$ change on $y(t)$}
@@
     	\centering
-    	\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_P.pdf}
+    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_P.pdf}
     	\caption{The effect of $P$ change on $P$ in the system}
@@
     	\centering
-    	\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P.pdf}
+    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P.pdf}
     	\caption{The effect of $P$ change on $(h \times \rho_f)$ in the system}
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.pdf}
+		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.pdf}
 		\caption{The effect of $P$ change on $C_s$}
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.pdf}
+		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.pdf}
 		\caption{The effect of $P$ change on $C_f$}
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_P.pdf}
+		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_P.pdf}
 		\caption{The effect of $P$ change on $y(t)$}
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_T_{in}.pdf}
+		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_T_{in}.pdf}
 		\caption{The effect of $T_{in}$ change on $P$ in the system}
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_T_{in}.pdf}
+		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_T_{in}.pdf}
 		\caption{The effect of $T_{in}$ change on $(h \times \rho_f)$ in the system}
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_T_{in}.pdf}
+		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_T_{in}.pdf}
 		\caption{The effect of $T_{in}$ change on $C_s$ in the system}
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_T_{in}.pdf}
+		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_T_{in}.pdf}
 		\caption{The effect of $T_{in}$ change on $C_f$ in the system}
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.8cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_T_{in}.pdf}
+		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_T_{in}.pdf}
 		\caption{The effect of $T_{in}$ change on $y(t)$ in the system}

### 2023-09-18 SFE_SEnsitivity_Analysis/SimulateSystemEuler.m

@@ -1,9 +1,9 @@
 function xout = SimulateSystemEuler(f,x0,p,dt)
 
-    addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
+    %addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
     import casadi.*
 
-    N = 1;
+    N = 10;
     Nx = size(x0,1);
     xout = zeros(Nx,N+1);  
     xout(:,1) = x0;

### 2023-09-18 SFE_SEnsitivity_Analysis/main_Sensitivity_Analysis.m

@@ -2,8 +2,8 @@ startup;
 delete(gcp('nocreate'));
 % %p = Pushbullet(pushbullet_api);
 
-addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
-%addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
 import casadi.*
 
 Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters

### 2023-09-19 SFE_article_Sensitivity_Analysis/Article_Model_Parameters.tex
19.09

@@
 
+In this study, the method of local sensitivity analysis was introduced to explore the dynamics of the supercritical extraction system, which consists of a set of partial differential equations.
+The aim was to investigate how variations in key control variables influence the behavior of the system.
+The automatic differentiation technique was implemented to obtain the sensitivity equations for each control variable.
+The sensitivity equations evaluate the influence of control variables on the state-space consisting of the concentration of the solute in solid and liquid phases, the fluid's enthalpy density, system pressure, and extraction yield.
+Then, the sensitivity equations are solved simultaneously with the original process to obtain the time evolution of the sensitivity curves.
+Later, the time evolution of the sensitivity curves was analyzed to understand better the process model.
+
+The first parameter to investigate was the flow-rate
+
 % ===================================================

### 2023-09-19 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
19.09

@@
 	The sensitivity equations were solved simultaneously with the original process model.
-The focus of this work is to investigate the influence of inlet temperature, pressure and mass flow-rate on the state-space as wall as on the extraction yield.
+This work investigates the influence of inlet temperature, pressure, and mass flow rate on the state space and the extraction yield.
 The process model and parameters have been discussed in {\color{red}article 1}.
 The process model was calibrated on set of experiments obtained at different operating conditions, $40^\circ C$ - $50^\circ C$ and 200 bar - 300 bar.
-The sensitivity analysis has been performed under assumption that the system operates are $45^\circ C$, 250 bar, 0.4 l/min and the simulation was performed with the time step of 0.01 [min] and 400 equally distributed points in the spatial direction.
+The sensitivity analysis has been performed under the assumption that the system operates are $45^\circ C$, 250 bar, 0.4 l/min.
+The simulation was performed with the time step of 0.01 [min] and 400 equally distributed points in the spatial direction.
 
@@
 
-    As discussed in Chapter \ref{CH:Governing_equations_chapter}, a small pressure wave propagates with the speed of sound relative to the flow.
-If the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic which leads to $\partial {\color{blue}P}/\partial {\color{orange}\rho_f} = \infty$.
-The Low Mach-number assumption leads to instant pressure propagation along the system.
-It allows to consider one value of pressure for the whole system as all the changes occur in the machine simultaneously.
-Figure \ref{fig:Sensitivty_P_P} represents a step function, which indicate the pressure change in the system.
+    As discussed in Chapter \ref{CH:Governing_equations_chapter}, a small pressure wave propagates at the speed of sound relative to the flow.
+If the flow velocity is relatively low, all pressure changes are hydrodynamic (resulting from velocity motion) rather than thermodynamic.
+The Low Mach-number assumption enables instant pressure propagation throughout the system.
+This assumption allows to consider a single pressure value for the entire system, as all changes occur simultaneously within the machine.
+Figure \ref{fig:Sensitivty_P_P} illustrates a step function representing the pressure change in the system.
 
@@
 
-	As a result of the Low Mach-number assumption and the pressure deviation, the temperature and density change along the system simultaneously.
-According to Equation \ref{EQ:Enthalpy_equation}, the pressure change affect the quantity $h \times \rho_f$ directly through $\partial ({\color{blue}P}(t) A_f) / \partial t$, which leads to a step-change presented in Figure \ref{fig:Sensitivty_P_H}.
+	As a result of the Low Mach-number assumption and the pressure deviation, temperature and density change simultaneously along the system.
+According to Equation \ref{EQ:Enthalpy_equation}, the pressure change directly affects the quantity $h \times \rho_f$ through $\partial ({\color{blue}P}(t) A_f) / \partial t$, leading to the step change presented in Figure \ref{fig:Sensitivty_P_H}.
 Depending on the configuration of the system, two cases are possible.
-As the total energy in the extractor has changed, there might be a difference between the fluid inside the equipment and the inlet temperature(defined as a boundary condition).
-If the Dirichlet boundary condition is applied, the inlet temperature is kept at the pre-defined value and might differ from the temperature in the extractor.
+Since the total energy in the extractor has changed, there may be a difference between the fluid inside the equipment and the inlet temperature, defined as a boundary condition.
+If Dirichlet boundary conditions are applied, the inlet temperature is maintained at the predefined value and may differ from the temperature in the extractor.
 In such a case, the temperature difference will cause the heat front to propagate through the system.
-Alternatively, the Neumann boundary condition can be applied to ensure that the temperature inside the extractor and at its inlet is the same.
-In the case of this work, the second approach was chosen to simplify the discussion.
+Alternatively, Neumann boundary conditions can be applied to ensure that the temperature inside the extractor matches that at its inlet.
+In this work, the second approach was chosen to simplify the discussion.
 
@@
 	The corresponding response of the pressure change on the solute concentration in the fluid phase is presented in Figure \ref{fig:Sensitivty_P_CF}.
-As discussed above, the pressure change directly affects the extraction kinetics.
-Figure \ref{fig:Sensitivty_P_CS} is characterized by negative sensitivities, which suggest a higher extraction rate due to pressure change.
-It is expected to observe an increase of solute in the fluid phase due to a higher extraction rate.
-That increase of the solute in the fluid phase is visible in Figure \ref{fig:Sensitivty_P_CF} as positive sensitivities, which forms a front moving along the extractor.
-As the extraction is faster, more solute goes to the fluid phase, explaining the hot spot in the Figure.
-Then, the solute flows along the system, where there are no solid particles, and the diffusion effect becomes noticeable.
-After the positive sensitivities, a small front of negative sensitivities can be observed.
-Due to higher extraction rate, more solute has been extracted at the beginning of the extraction time, which means that there is less solute to extract later, and that effect is visible in Figure \ref{fig:Sensitivty_P_CF} as a negative sensitivities.
+As discussed earlier, the pressure change directly influences the extraction kinetics.
+Figure \ref{fig:Sensitivty_P_CS} is characterized by negative sensitivities, suggesting a higher extraction rate due to the pressure change.
+Consequently, an increase in solute concentration in the fluid phase is expected.
+This increase in solute concentration in the fluid phase is visible in Figure \ref{fig:Sensitivty_P_CF} as positive sensitivities, forming a front that moves along the extractor.
+As the extraction process accelerates, more solute enters the fluid phase, explaining the "hot spot" in the Figure.
+Subsequently, the solute flows through the system where there are no solid particles, and the diffusion effect becomes noticeable.
+Following the positive sensitivities, a small front of negative sensitivities can be observed.
+Due to the higher extraction rate, more solute has been extracted at the beginning of the extraction process, resulting in less solute available for extraction later.
+This effect is reflected in Figure \ref{fig:Sensitivty_P_CF} as negative sensitivities.
+Eventually, the negative sensitivities approach zero.
 
@@
 
-	The effect of the pressure increase on the extraction yield is presented in Figure \ref{fig:Sensitivty_P_y}.
-The initial flat curve is related to a delay in the system caused by empty space in the extractor, through which the solvent with solute needs to flow to reach the outlet.
-Later, the positive sensitivity is present and indicates an increase in yield.
-The $dy / dP$ reaches a maximum and starts to decrease due to the lower amount of the solute left in the solid phase compared with the case before the pressure increment.
-The sensitivity decreases to negative values, reaches a minimum, and eventually goes zero.
-To show how $dy / dP$ converges to zero, the simulation time was expanded.
+	The impact of pressure increase on extraction yield is depicted in Figure \ref{fig:Sensitivty_P_y}.
+The initial flat curve reflects a system delay, caused by the empty space within the extractor that the solvent with solute must traverse to reach the outlet.
+Next, a positive sensitivity starts to rise, which indicates an increase in yield.
+$dy / dP$ reaches its maximum and then declines due to a lower amount of solute remaining in the solid phase compared to the initial pressure conditions.
+This sensitivity eventually dips into negative values, hits a minimum point, and ultimately converges to zero.
+The simulation duration was extended to demonstrate the convergence of $dy / dP$ towards zero.
 
@@
 
-	The influence of the inlet temperature on the supercritical extraction differs from the two presented cases because the disturbance does not affect the whole system instantaneously but propagates through the system.
-As the fluid with modified temperature flows along the system, it gradually affects the mass transfer.
-One assumption is that inlet temperature does not affect the pressure, and because of that, a horizontal line is present in Figure \ref{fig:Sensitivty_P_T}.
+	The impact of the inlet temperature on supercritical extraction differs from the two cases presented earlier because the disturbance does not instantaneously affect the entire system; instead, it propagates through the system.
+As the fluid with the modified temperature flows along the system, it gradually influences the mass transfer parameters.
+One important assumption is that the inlet temperature does not affect the pressure, and as a result, a horizontal line is present in Figure \ref{fig:Sensitivty_P_T}.
 
@@
 	The propagation of the heat front is presented in Figure \ref{fig:Sensitivty_T_H}.
-The inlet value of $(h\times \rho_f)$ is calculated based on the given value of the inlet temperature( Dirichlet boundary condition) and given pressure.
-The deviation in $T_{in}$ affects $(h\times \rho_f)$ at the inlet, which propagates according to the governing equations.
+Initially, the system was uniformly set to the same temperature.
+The temperatures at the inlet and outlet boundaries are predefined (Dirichlet boundary conditions) and consistent with those inside the system.
+The inlet value of $(h\times \rho_f)$ is calculated based on the provided inlet temperature and given pressure.
+Any deviation in $T_{in}$ affects $(h\times \rho_f)$ at the inlet, which subsequently propagates according to the governing equations.
 
@@
 
-	Figure \ref{fig:Sensitivty_T_CS} shows how the concentration of the solute in the solid phase is affected by the inlet temperature change.
-Initially, the sensitivities are zero along the fixed bed because the heat front needs time to propagate to the fixed bed.
-As the propagation is not instantaneous, the non-uniform distribution of sensitivities along the fixed bed is visible.
-All the sensitivities start to grow and reach maxima.
-As presented in {\color{red}article 1}, the value of $D_i^R$ diminishes when the density decreases.
-It is expected to observe positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, which indicates a slower extraction rate.
-When the concentration gradient becomes a limiting factor, the sensitivities decrease.
+	Figure \ref{fig:Sensitivty_T_CS} illustrates how the change in inlet temperature affects the concentration of solute in the solid phase.
+Initially, the sensitivities are zero along the fixed bed because the heat front requires time to propagate to the fixed bed.
+Since this propagation is not instantaneous, a non-uniform distribution of sensitivities along the fixed bed becomes evident.
+All the sensitivities gradually increase until they reach their respective maxima.
+As presented in {\color{red}article 1}, the value of $D_i^R$ decreases as density decreases.
+Therefore, it is expected to observe positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, indicating a slower extraction rate.
+When the concentration gradient becomes the limiting factor, the sensitivities start to decrease to zero.
 
@@
 
-	The influence of the inlet temperature on the solute in the fluid phase is shown in Figure \ref{fig:Sensitivty_T_CF}.
-At the start, all the sensitivities stay at zero because of idle time.
-When the fluid at a new temperature reaches the solid particles, it affects the mass transfer, which later affects the amount of the solute in the fluid phase.
-As a response to the slower extraction rate suggested by positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, the 'hot spot' with negative sensitivities is visible in Figure \ref{fig:Sensitivty_T_CF}.
-An effect of the diffusion can be observed in the section without the fixed bed where the front made of sensitivities becomes blurry.
-After the sensitivities reach minima, they grow and reach positive values.
-This behavior can be explained by considering that the heat front slowed the mass transfer, and more of the solute stayed in the solid phase.
-That leads to a higher concentration gradient in the later time of the extraction if compared to the situation without the inlet temperature deviation.
-The higher concentration gradient causes the increase of the $dc_f/dT_{in}$.
+	The influence of inlet temperature on solute concentration in the fluid phase is depicted in Figure \ref{fig:Sensitivty_T_CF}.
+Initially, all the sensitivities remain at zero due to an idle period.
+When the fluid at the new temperature reaches the solid particles, it affects mass transfer, subsequently influencing the amount of solute in the fluid phase.
+In response to the slower extraction rate indicated by positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, a 'hot spot' with negative sensitivities becomes visible in Figure \ref{fig:Sensitivty_T_CF}.
+The effect of diffusion is observable in the section without the fixed bed, where the front composed of sensitivities becomes blurred.
+After reaching their minima, the sensitivities increase and attain positive values.
+This behavior can be explained by considering that the heat front slowed mass transfer, causing more solute to remain in the solid phase.
+This, in turn, leads to a higher concentration gradient in the later stages of extraction compared to the scenario without the inlet temperature deviation.
+The higher concentration gradient results in an increase in $dc_f/dT_{in}$.
 
@@
 
-	Figure \ref{fig:Sensitivty_T_y} shows how the inlet temperature increment changes the extraction yield.
-Initially, the sensitivity curve stays flat, which is caused by the fact that the fixed bed does not occupy the whole volume of the extractor, and the fluid needs some time to flow through the empty part of the extractor to reach its outlet.
-When the solute in the fluid phase reaches the outlet of the extractor, then system response can be observed.
-The $dy/dT_{in}$ starts to decrease, and the negative sensitivity value indicates a worsened process efficiency.
-Over time, the sensitivity reaches its minimum and increases due to a higher concentration gradient (if compared to the case without the disturbance).
-The sensitivity reaches a positive maximum and decreases again due to lower reduced extraction kinetic and decreased concentration gradient.
-The $dy/dT_{in}$ becomes negative again, and eventually the sensitivity curve flattens.
+	Figure \ref{fig:Sensitivty_T_y} depicts how an increase in inlet temperature alters the extraction yield.
+Initially, the sensitivity curve remains flat.
+It is because the fixed bed doesn't occupy the entire volume of the extractor and the fluid requires some time to flow through the empty portion of the extractor to reach its outlet.
+It's only when the solute in the fluid phase reaches the extractor's outlet a system response can be observed.
+At this point, $dy/dT_{in}$ begins to decrease, and the negative sensitivity value indicates a decrease in process efficiency.
+Over time, the sensitivity reaches its minimum and then increases due to a higher concentration gradient compared to the case without the disturbance.
+The sensitivity reaches a positive maximum and then declines again due to reduced extraction kinetics and a decreased concentration gradient.
+$dy/dT_{in}$ becomes negative once more, eventually resulting in a flattening of the sensitivity curve.
+The flattening of the yield curve suggest that the mass transfer parameters limits the extraction rate and the residual solute in the solid phase become difficult to obtain.
 

### 2023-09-27 SFE_article_Sensitivity_Analysis/Article_Model_Parameters.tex
27.09

--- 2023-08-24 SFE_article_Sensitivity_Analysis/Article_Model_Parameters.tex
@@
 
+The sensitivity analysis is a tool to understand the parametric dependence of dynamic behavior and its suitability in inferring mechanisms of the dynamic behavior of the analyzed system.
+The mathematical formulation involves derivative-based local sensitivity analysis of the solution of an inverse problem with respect to perturbations of parameters.
+The local method is based only on considering all parameters as constants (those independent of time or location), and then the sensitivity coefficients are estimated by solving a variational system simultaneously with the original system.
+The sensitivity equations can be obtained in various ways, but in the case of this work, the automatic differentiation technique was implemented to obtain the sensitivity equations.
+By identifying which parameters are influential at specific time points during the simulation, local sensitivity analysis can yield valuable information for guiding the design of experiments, the process modeling, or the model reduction.
+The local sensitivity analysis techniques consider the sensitivities at only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions unless the discussed system is a linear system.
+
+In this study, the local sensitivity analysis method was introduced to explore the dynamics of the supercritical extraction system, which consists of a set of partial differential equations.
+The sensitivity equations evaluate the influence of control variables such as flow rate, pressure, and inlet temperature on the state-space consisting of the concentration of the solute in solid and liquid phases, the fluid's enthalpy density, system pressure, and extraction yield.
+Every change in the control variables leads to a state-space change, eventually affecting the process performance.
+This information can be utilized to identify which control variables influence the extraction yield the most.
+The control with high sensitivities on the extraction should be further investigated to find optimal operating conditions.
+
 % ===================================================

### 2023-09-27 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
27.09

@@
 
-    A change in flow rate has a direct impact on the kinetic energy of the fluid, as defined by the spatial derivative $\frac{\partial \left( {\color{orange}\rho_f}{\color{blue}h} A_f v \right)}{\partial {\color{blue}z}}$.
+    A change in flow rate is defined by the spatial derivative $\frac{\partial \left( {\color{orange}\rho_f}{\color{blue}h} A_f v \right)}{\partial {\color{blue}z}}$.
 The consequence of Equation \ref{EQ:Velocity} is the instantaneous change of the velocity field in the system, which means that the spatial derivative equals zero.
 Because ${\color{blue}h}$ represents an enthalpy but not a total enthalpy, it does not contain the kinetic energy contribution.
-Consequently, under conditions where the thermodynamic state remains constant, specifically with constant temperature and pressure, Figure \ref{fig:Sensitivty_F_H} demonstrates no significant deviation.
+Consequences of the modelling assumptions are that ${\color{blue}h}$ and ${\color{orange}\rho_f}$ change only if a pressure or temperature change directly.
+As the result, Figure \ref{fig:Sensitivty_F_H} demonstrates no significant deviation.
 

### 2023-09-28 SFE_article_Sensitivity_Analysis/Article_Model_Parameters.tex
28.09

@@
 The sensitivity equations can be obtained in various ways, but in the case of this work, the automatic differentiation technique was implemented to obtain the sensitivity equations.
-By identifying which parameters are influential at specific time points during the simulation, local sensitivity analysis can yield valuable information for guiding the design of experiments, the process modeling, or the model reduction.
+By identifying which parameters are influential at each period of the simulation, local sensitivity analysis can yield valuable information for guiding the design of experiments, the process modeling, or the model reduction.
 The local sensitivity analysis techniques consider the sensitivities at only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions unless the discussed system is a linear system.
@@
 This information can be utilized to identify which control variables influence the extraction yield the most.
-The control with high sensitivities on the extraction should be further investigated to find optimal operating conditions.
+The controls with high sensitivities on the extraction can be used to investigated to find optimal operating conditions from economic point of view.
 

### 2023-09-28 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
28.09

@@
 
-    A change in flow rate is defined by the spatial derivative $\frac{\partial \left( {\color{orange}\rho_f}{\color{blue}h} A_f v \right)}{\partial {\color{blue}z}}$.
+    A flow rate change is defined by the spatial derivative $\frac{\partial \left( {\color{orange}\rho_f}{\color{blue}h} A_f v \right)}{\partial {\color{blue}z}}$.
 The consequence of Equation \ref{EQ:Velocity} is the instantaneous change of the velocity field in the system, which means that the spatial derivative equals zero.
-Because ${\color{blue}h}$ represents an enthalpy but not a total enthalpy, it does not contain the kinetic energy contribution.
-Consequences of the modelling assumptions are that ${\color{blue}h}$ and ${\color{orange}\rho_f}$ change only if a pressure or temperature change directly.
+It's important to note that ${\color{blue}h}$ represents enthalpy but not total enthalpy, thus excluding kinetic energy contribution.
+As a consequence of our modelling assumptions, changes in ${\color{blue}h}$ and ${\color{orange}\rho_f}$ only occur in response to direct change in pressure or temperature.
 As the result, Figure \ref{fig:Sensitivty_F_H} demonstrates no significant deviation.
@@
     The flow rate change affects the fluid inside the system, but appropriate boundary conditions must be set.
-If Dirichlet boundary conditions are used, a numerical mismatch between boundary conditions and the computational domain might occur due to different ways of computing them.
-The system's enthalpy is computed based on time evolution of governing equations, while the enthalpy at the inlet is computed based on inlet temperature and pressure.
-A small numerical mismatch between these values would be presented in the system as a difference in enthalpy, which propagates along the spatial domain.
-To ensure that the fluid at the inlet and the fluid inside of the computational domain are defined in the same way, Neumann boundary conditions are used in this analysis.
+When utilizing Dirichlet boundary conditions, it's crucial to be aware of potential numerical discrepancies stemming from the differing methods used to compute them.
+The system's enthalpy is determined through the time evolution of governing equations, while the inlet's enthalpy depends on the inlet temperature and pressure.
+A minor numerical mismatch between these values may manifest as an enthalpy difference propagating along the spatial domain.
+To ensure consistency between the fluid at the inlet and inside the computational domain, this analysis employs Neumann boundary conditions.
 
@@
 
-   An increase in the mass flow rate impacts the concentration gradient and accelerates the extraction kinetics.
-Negative sensitivities in Figure \ref{fig:Sensitivty_F_CS} indicate a faster extraction rate.
-Negative values of $dc_s/dF$ can be interpreted as a 'faster' loss of mass from the solid phase, signifying an improvement in extraction efficiency.
-At the beginning of the extraction process, changes in the flow rate have a minimal effect on the extraction process, as evidenced by sensitivities that are close to zero.
+   An increase in the mass flow rate impacts the concentration gradient and the extraction kinetics as presented in Figure \ref{fig:Sensitivty_F_CS} .
+At the beginning of the extraction process, changes in the flow rate have a minimal effect on the extraction process, as showed by sensitivities that are close to zero.
 This is due to the dominance of the high concentration gradient, which leads the extraction kinetic.
-As time progresses, the increase in the mass flow rate accelerates the extraction kinetics, causing the sensitivities to decrease towards their minimum values.
+As time progresses, the increase in the mass flow rate have greater influence on the extraction kinetics, causing the sensitivities to decrease towards their minimum values.
+Negative sensitivities indicate a faster extraction rate.
 Over time, the amount of solute in the solid phase decreases, and eventually, the extraction kinetic becomes limited by the concentration gradient.
@@
 The growth in flow rate affects ${\color{blue}C_f}(z,t)$ by increasing the velocity, consequently elevating the concentration gradient.
-As a result, positive sensitivities emerge within the system, forming a front that progresses from the inlet to the outlet of the extractor.
+As a result, positive sensitivities emerge within the system, forming a front that progresses in the direction of flow.
 The positive front indicates that the larger amount of solute moves faster across the system, which leads to faster decrease of the total amount of solute in both phases.
@@
 Depending on the configuration of the system, two cases are possible.
-Since the total energy in the extractor has changed, there may be a difference between the fluid inside the equipment and the inlet temperature, defined as a boundary condition.
+Since the total energy in the extractor has changed, there may be a difference between the fluid inside the equipment and the boundary conditions at the inlet.
 If Dirichlet boundary conditions are applied, the inlet temperature is maintained at the predefined value and may differ from the temperature in the extractor.

### 2023-10-02 SFE_article_Parameter_Estimation/Article_Model_Parameters.tex
02.10

--- 2023-08-06 SFE-article/Article_Model_Parameters.tex
@@
 The extraction was performed in a partially filled extractor with a fixed bed operated under multiple constant operating conditions.
-The dataset collected from four experiments consists of four experiments conducted at different operating conditions: $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar, and $50^\circ C$/$300$ bar.
-A distributed-parameter model is used to describe the fluid-solid extraction process with $CO_2$ as a solvent.
+The dataset collected from four experiments consists of four experiments conducted at different operating conditions: $40~^\circ C$ / $200$ bar, $50~^\circ C$ / $200$ bar, $40~^\circ C$ / $300$ bar, and $50~^\circ C$ / $300$ bar.
+A distributed-parameter model is used to describe the fluid-solid extraction process with carbon dioxide as a solvent.
 The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
@@
 \subsection{Governing equations} \label{CH:Governing_equations_chapter}
-The governing equation \footnote{For the sake of clarity of the process model, different colors have been used in the equations to indicate: 
-	{\color{red}control variables},
-	{\color{blue}state variables},
-	{\color{orange}variables} and
-	{\color{magenta}parameters}.} for a quasi-one-dimensional compressible flow in Cartesian coordinates can be found in the Appendix \ref{CH: Gouverning equations} and in the work of \citet{Anderson1995}.
+%\footnote{For the sake of clarity of the process model, different colors have been used in the equations to indicate: 
+%	{\color{red}control variables},
+%	{\color{black}state variables},
+%	{\color{black}variables} and
+%	{\color{black}parameters}.} 
+	The governing equation for a quasi-one-dimensional compressible flow in Cartesian coordinates can be found in the Appendix \ref{CH: Gouverning equations} and in the work of \citet{Anderson1995}.
 Quasi-one-dimensional flow is a fluid flow characterized by the assumption that the flow properties remain uniform across any given cross-section of the flow.
@@
 		\label{EQ: CompressibleEuler_1}
-		\cfrac{\partial \left( {\color{orange}\rho_f} {\color{magenta}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{orange}\rho_f} {\color{magenta}A_f}(z) v \right)}{\partial z} &= 0 \\
-		\cfrac{\partial \left( {\color{orange}\rho_f} v {\color{magenta}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{orange}\rho_f} {\color{magenta}A_f}(z) v^2 \right)}{\partial z} &= -{\color{magenta}A_f}(z) \cfrac{\partial {\color{blue}P}}{\partial z} \label{EQ: CompressibleEuler_2} \\
-		\cfrac{\partial \left( {\color{orange}\rho_f} {\color{blue}e} {\color{magenta}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{orange}\rho_f} {\color{magenta}A_f}(z) v {\color{blue}e}\right)}{\partial z} &= -{\color{blue}P}\cfrac{\left( {\color{magenta}A_f}(z) v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial {\color{blue}T}}{\partial z} \right)
+		\cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v \right)}{\partial z} &= 0 \\
+		\cfrac{\partial \left( {\color{black}\rho_f} v {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v^2 \right)}{\partial z} &= -{\color{black}A_f}(z) \cfrac{\partial {\color{black}P}}{\partial z} \label{EQ: CompressibleEuler_2} \\
+		\cfrac{\partial \left( {\color{black}\rho_f} {\color{black}e} {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v {\color{black}e}\right)}{\partial z} &= -{\color{black}P}\cfrac{\left( {\color{black}A_f}(z) v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial {\color{black}T}}{\partial z} \right)
 		\label{EQ: CompressibleEuler_3}
@@
 
-where ${\color{orange}\rho_f}$ is the density of the fluid, ${\color{magenta}A_f}(z)$ is the function which describe change of the cross-section, $v$ is the velocity, ${\color{blue}P}$ is the total pressure, ${\color{blue}e}$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
+where ${\color{black}\rho_f}$ is the density of the fluid, ${\color{black}A_f}(z)$ is the function which describe change of the cross-section, $v$ is the velocity, ${\color{black}P}$ is the total pressure, ${\color{black}e}$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
 
@@
 			\draw (4.5,0) -- (4.5,2); 	% Bottom line
-			\node at (4,1.5) {${\color{orange}\rho_f}$};
-			\node at (5.5,1.5) {${\color{orange}\rho_f}+\delta{\color{orange}\rho_f}$};
-			\node at (4,1.0) {${\color{blue}P}$};
-			\node at (5.5,1.0) {${\color{blue}P}+\delta {\color{blue}P}$};
-			\node at (4,0.5) {${\color{blue}T}$};
-			\node at (5.5,0.5) {${\color{blue}T}+\delta {\color{blue}T}$};
+			\node at (4,1.5) {${\color{black}\rho_f}$};
+			\node at (5.5,1.5) {${\color{black}\rho_f}+\delta{\color{black}\rho_f}$};
+			\node at (4,1.0) {${\color{black}P}$};
+			\node at (5.5,1.0) {${\color{black}P}+\delta {\color{black}P}$};
+			\node at (4,0.5) {${\color{black}T}$};
+			\node at (5.5,0.5) {${\color{black}T}+\delta {\color{black}T}$};
 			\node at (1,1.0) {$v \rightarrow$};
@@
 	\begin{align*}
-		&{\color{orange}\rho_f} \delta v + v \delta {\color{orange}\rho_f} + \delta {\color{orange}\rho_f} \delta v = 0 \\
-		&\delta {\color{blue}P} = \delta v \delta {\color{orange}\rho_f}
+		&{\color{black}\rho_f} \delta v + v \delta {\color{black}\rho_f} + \delta {\color{black}\rho_f} \delta v = 0 \\
+		&\delta {\color{black}P} = \delta v \delta {\color{black}\rho_f}
 	\end{align*}
@@
 	\begin{equation*}
-		\lim_{{\color{orange}\rho_f} v \rightarrow 0} {\color{orange}\rho_f} \delta v + v \delta {\color{orange}\rho_f} + \delta {\color{orange}\rho_f} \delta v = 0 / \delta {\color{orange}\rho_f} \rightarrow \cfrac{d v}{d {\color{orange}\rho_f}} = - \cfrac{v}{{\color{orange}\rho_f}}
+		\lim_{{\color{black}\rho_f} v \rightarrow 0} {\color{black}\rho_f} \delta v + v \delta {\color{black}\rho_f} + \delta {\color{black}\rho_f} \delta v = 0 / \delta {\color{black}\rho_f} \rightarrow \cfrac{d v}{d {\color{black}\rho_f}} = - \cfrac{v}{{\color{black}\rho_f}}
 	\end{equation*}
@@
 	\begin{equation} \label{EQ: Pressure_Velocity}
-		\cfrac{d v}{d {\color{orange}\rho_f}} = - \cfrac{d v}{d{\color{blue}P}} \cfrac{d {\color{blue}P}}{d {\color{orange}\rho_f}} = -\cfrac{1}{\rho v} \cfrac{d{\color{blue}P}}{d{\color{orange}\rho_f}} = -\cfrac{v}{{\color{orange}\rho_f}}
+		\cfrac{d v}{d {\color{black}\rho_f}} = - \cfrac{d v}{d{\color{black}P}} \cfrac{d {\color{black}P}}{d {\color{black}\rho_f}} = -\cfrac{1}{\rho v} \cfrac{d{\color{black}P}}{d{\color{black}\rho_f}} = -\cfrac{v}{{\color{black}\rho_f}}
 	\end{equation}
@@
 
-Suppose the flow is presumed to be isentropic, $d{\color{blue}P}/d{\color{orange}\rho_f} = c^2$, so $v^2=c^2$, where $c$ is the speed of sound.
+Suppose the flow is presumed to be isentropic, $d{\color{black}P}/d{\color{black}\rho_f} = c^2$, so $v^2=c^2$, where $c$ is the speed of sound.
 This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow.
-Moreover, if the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic which leads to $\partial {\color{orange}\rho_f} / \partial {\color{blue}P} \approx 0$.
+Moreover, if the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic which leads to $\partial {\color{black}\rho_f} / \partial {\color{black}P} \approx 0$.
 In other words, the small changes in pressure due to flow velocity changes do not change the density.
-This has a secondary effect -- the speed of sound in the fluid is $\partial {\color{blue}P}/\partial {\color{orange}\rho_f} = \infty$ in this instance.
+%This has a secondary effect -- the speed of sound in the fluid is $\partial {\color{black}P}/\partial {\color{black}\rho_f} = \infty$ in this instance.
 So there is an infinite speed of sound, which makes the equations elliptic in nature.
@@
 
-This study presented basic aspects regarding the laboratory work for obtaining caraway extracts using supercritical $CO_2$ at different operating conditions.
-A first-principle process model was developed based on governing equations and simplified using the Low-Mach number approximation.
-Based on the literature review, the extraction kinetic model was selected.
+This study presented basic aspects regarding the laboratory work for obtaining caraway extracts using supercritical carbon dioxide at different operating conditions.
+A first-principle process model was developed based on governing equations.
+Based on the literature review, the extraction kinetic model was selected and combined with the general mass balance equations.
 The values of unknown parameters in the process model were obtained by parameter estimation.
@@
 Later, the parameters found for each experiment were combined to obtain more general relationships.
-The correlations for ${\color{orange}D_i^R}$, ${\color{orange}\Upsilon}$ and ${\color{orange}D_e^M}$ are presented as a function of ${\color{orange}\rho}$ or ${\color{orange}R_e}$.
+The correlations for diffusion and decay coefficients are presented as a function of fluid density or Reynolds number.
 It should be noted that obtained correlations have been prepared with a limited amount of data.
@@
 
-\subsection{Low Mach number expansion} \label{CH:Low_Mach_chapter}
+%\subsection{Low Mach number expansion} \label{CH:Low_Mach_chapter}
 %\subfile{Sections/Low_mach_number_expansion}
-\subfile{Sections/Low_mach_number_expansion_imp}
-
-\subsection{Bayes theorem} \label{CH: Bayes}
-\subfile{Sections/Bayes_Theorem}
+%\subfile{Sections/Low_mach_number_expansion_imp}
 
@@
 
-\subsection{Maximum Likelihood} \label{CH: ML}
+%\subsection{Bayes theorem} \label{CH: Bayes}
+%\subfile{Sections/Bayes_Theorem}
+
+\subsection{Maximum likelihood} \label{CH: ML}
 \subfile{Sections/Likelihood}
@@
 \subsection{Solid density measurement} \label{CH: Solid_Density_Measurment}
+
+Figure \ref{fig:density_cal} shows results of density measurement performed with pycnometer.
 
@@
 	\caption{The result of solid density measurement}
+	\label{fig:density_cal}
 \end{figure}
@@
 
-\subsection{Porosity Calculations} \label{CH: Porosity}
+\subsection{Porosity calculations} \label{CH: Porosity}
 \subfile{Sections/Porosity}
 
-\subsection{Concentration profiles} \label{CH: Profiles}
-\subfile{Sections/Profiles}
+%\subsection{Concentration profiles} \label{CH: Profiles}
+%\subfile{Sections/Profiles}
 

### 2023-10-02 SFE_article_Parameter_Estimation/Sections/Experiments.tex
02.10

@@
 
-	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset ${\color{blue}Y}(t)$, which was obtained by extracting caraway oil from caraway seeds.
+	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset ${\color{black}Y}(t)$, which was obtained by extracting caraway oil from caraway seeds.
 To prepare the seeds for extraction, they were first pre-treated using a Retsch SM 300 cutting mill to reduce their particle size to 1mm and break their outer shell.
 The moisture content of the seeds was then determined using an Infrared Moisture Analyser, which revealed an average moisture content of 4.83\% in the solid particles after grinding.
-Next, the density of the solid material was measured using a pycnometer, which can be found in appendix \ref{CH: Solid_Density_Measurment}.
-Finally, the material's porosity was also calculated to be 0.5, as explained in appendix \ref{CH: Porosity}.
+Next, the density of the solid material was measured using a pycnometer, which can be found in Appendix \ref{CH: Solid_Density_Measurment}.
+Finally, the material's porosity was also calculated to be 0.5, as explained in Appendix \ref{CH: Porosity}.
 
-	The caraway seeds used in the experiments were obtained from Caraway Finland during the 2022 harvesting season.
-The experiments were conducted using a 10-litre extractor with an inner diameter of approximately 15 cm and a height of 60 cm, which was rented from VTT Bioruukki.
-Four experiments were performed under different operating conditions: $40^\circ C / 200$ bar, $50^\circ C / 200$ bar, $40^\circ C / 300$ bar, and $50^\circ C / 300$ bar.
+	The caraway seeds used in the experiments were obtained during the 2022 harvesting season.
+The experiments were conducted using a 10-litre extractor with an inner diameter of approximately 15 cm and a height of 60 cm.
+Four experiments were performed under different operating conditions: $40~^\circ C$ / 200 bar, $50~^\circ C$ / 200 bar, $40~^\circ C$ / 300 bar, and $50~^\circ C$ / 300 bar.
 The volumetric flow rate used in all experiments was on average 0.4 litres per minute, with negligible variations (up to 5\%).
@@
 Every 5 minutes, the oil was drained from the separator, and its weight was measured.
-The resulting time series ${\color{blue}Y}(t)$ corresponds to the output of measurement Equation \ref{Model_measurment_1} and can be used for parameter estimation.
+The resulting time series ${\color{black}Y}(t)$ corresponds to the output of measurement Equation \ref{Model_measurment_1} and can be used for parameter estimation.
 

### 2023-10-02 SFE_article_Parameter_Estimation/Sections/IC_BC.tex
08.08
02.10

--- 2023-04-25 SFE-article/Sections/IC_BC.tex
@@
 
-	It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}c_s^0}$.
-It is considered that the initial temperature of the extractor in every place is the same and described by ${\color{magenta}h^0}$.
+	It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{black}c_s^0}$.
+It is considered that the initial temperature of the extractor in every place is the same and described by ${\color{black}h^0}$.
 
@@
 
-			\node[blue] at (1.3,0.5) {$H(z)=-m(z-b) + a$};
+			\node[black] at (1.3,0.5) {$H(z)=-m(z-b) + a$};
 		\end{tikzpicture}
@@
 	As can be seen from the above equation, the linearly distributed concentration of solute in the fluid phase can be fully determined if parameters $a$, $b$ and $m_{fluid}^0$ are know.
-$m_{fluid}^0$ can be obtained from the total mass of the solute in the system at the initial time $m_{total}^0$ and the partition factor $\tau$.
+$m_{fluid}^0$ can be obtained from the total mass of the solute in the system at the initial time $m_{total}^0$ and the initial mass ratio $\tau$.
 
@@
 			\begin{align*}
-				{\color{blue}c_f}(t = 0, z) &= H(z)   \\
-				{\color{blue}c_s}(t = 0, z) &= {\color{magenta}c_{s0}} \\
-				{\color{blue}h}(t = 0, z) &= {\color{magenta}h_0}
+				{\color{black}c_f}(t = 0, z) &= H(z)   \\
+				{\color{black}c_s}(t = 0, z) &= {\color{black}c_{s0}} \\
+				{\color{black}h}(t = 0, z) &= {\color{black}h_0}
 			\end{align*}

### 2023-10-02 SFE_article_Parameter_Estimation/Sections/Model.tex
02.10

--- 2023-08-24 SFE_article_Sensitivity_Analysis/Sections/Model.tex
@@
 	\subsubsection{Continuity equation} \label{CH: Continuity}
-	 %When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{magenta}\phi}(z)$ (where ${\color{magenta}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}
-	The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function ${\color{magenta}A_f}(z) = {\color{magenta}A_f\phi}(z)$ to take into account the change of the cross-section available for the fluid.
-The cross-section change is taken into account by void fraction ${\color{magenta}\phi}(z)$, which depends on the spatial dimension.
+	 %When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{black}\phi}(z)$ (where ${\color{black}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}
+	The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function ${\color{black}A_f}(z) = {\color{black}A_f\phi}(z)$ to take into account the change of the cross-section available for the fluid.
+The cross-section change is taken into account by void fraction ${\color{black}\phi}(z)$, which depends on the spatial dimension.
 The Equation \ref{EQ: Continuity_differential} shows the differential form of the continuity equation:
@@
 		\begin{equation} \label{EQ: Continuity_differential}
-			\frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{magenta}\phi}(z))}{\partial t} + \frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v {\color{magenta}A\phi}(z))}{\partial {\color{blue}z}} = 0
+			\frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}\phi}(z))}{\partial t} + \frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A\phi}(z))}{\partial {\color{black}z}} = 0
 		\end{equation}
 	}
-	where ${\color{magenta} A}$ is the total cross-section of the extractor.
+	where ${\color{black} A}$ is the total cross-section of the extractor.
 
-	%{\color{red}assign a color of v and u}
+	%{\color{black}assign a color of v and u}
 
-	Assuming that the mass flow rate is constant in time, the temporal derivative becomes zero, and the spatial derivative can be integrated along ${\color{blue}z}$ as
+	Assuming that the mass flow rate is constant in time, the temporal derivative becomes zero, and the spatial derivative can be integrated along ${\color{black}z}$ as
 
@@
 		\begin{equation}
-			\int \frac{\partial ({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v {\color{magenta}A \phi}(z) )}{\partial {\color{blue}z}} dz = 0 \rightarrow {\color{red}F}={\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) v {\color{magenta}A\phi}(z)
+			\int \frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A \phi}(z) )}{\partial {\color{black}z}} dz = 0 \rightarrow {\color{black}F}={\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A\phi}(z)
 		\end{equation}
@@
 
-	Here, ${\color{red}F}$ is a constant obtained from the integration and is understood as the mass flux per unit area, which is assumed to be constant along ${\color{blue}z}$.
-To simplify the dynamics of the system, it is assumed that ${\color{red}F}={\color{red}F}(t)$ is a control variable and affects the whole system instantaneously.
-This assumption allows for finding the velocity profile that satisfies mass continuity based on ${\color{red}F}(t)$, ${\color{magenta}\phi}(z)$, and ${\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))$.
+	Here, ${\color{black}F}$ is a constant obtained from the integration and is understood as the mass flux per unit area, which is assumed to be constant along ${\color{black}z}$.
+To simplify the dynamics of the system, it is assumed that ${\color{black}F}={\color{black}F}(t)$ is a control variable and affects the whole system instantaneously.
+This assumption allows for finding the velocity profile that satisfies mass continuity based on ${\color{black}F}(t)$, ${\color{black}\phi}(z)$, and ${\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$.
 
@@
 	\begin{equation}
-		v = \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{magenta}A\phi}(z)} 
+		v = \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}A\phi}(z)} 
 	\end{equation}
@@
 
-	The fluid density ${\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))$ can be obtained from an equation of state if temperature and the thermodynamic pressure (assumed ${\color{blue}P}(t)$ to be constant along ${\color{blue}z}$ due to the low-Mach number condition) are known.
-The variation in density may be caused by the fluid accumulation in the system (equivalent to pressure change), which occurs instantaneously along ${\color{blue}z}$ or by a temperature change.
+	The fluid density ${\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$ can be obtained from an equation of state if temperature and the thermodynamic pressure (assumed ${\color{black}P}(t)$ to be constant along ${\color{black}z}$ due to the low-Mach number condition) are known.
+The variation in density may be caused by the fluid accumulation in the system (equivalent to pressure change), which occurs instantaneously along ${\color{black}z}$ or by a temperature change.
 
@@
 		\begin{equation}
-			u = v {\color{magenta}\phi}(z) = \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{magenta} A} }
+			u = v {\color{black}\phi}(z) = \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black} A} }
 		\end{equation}
@@
 
-	The detailed derivation of the mass balance equation for the fluid phase can be found in the appendix (\ref{CH: Gouverning equations}).
+	The detailed derivation of the mass balance equation for the fluid phase can be found in the Appendix \ref{CH: Gouverning equations}.
 The movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}) is considered only in the axial direction, while the properties of the system in the radial direction are assumed to be uniform.
@@
 			\label{Model_fluid}
-			\frac{\partial {\color{blue}c_f}(t,z)}{\partial t}
-			+ \frac{1}{{\color{magenta}\phi}(z)} \frac{\partial \left( {\color{blue}c_f}(t,z) u\right)}{\partial {\color{blue}z}}
-			= \frac{1-{\color{magenta}\phi}(z)}{{\color{magenta}\phi}(z)} {\color{blue}r_e}(t,z)
-			+ \frac{1}{{\color{magenta}\phi}(z)} \frac{\partial}{\partial {\color{blue}z}} \left( {\color{orange}D^M_e} \frac{\partial {\color{blue}c_f}(t,z)}{\partial {\color{blue}z}} \right)
+			\frac{\partial {\color{black}c_f}(t,z)}{\partial t}
+			+ \frac{1}{{\color{black}\phi}(z)} \frac{\partial \left( {\color{black}c_f}(t,z) u\right)}{\partial {\color{black}z}}
+			= \frac{1-{\color{black}\phi}(z)}{{\color{black}\phi}(z)} {\color{black}r_e}(t,z)
+			+ \frac{1}{{\color{black}\phi}(z)} \frac{\partial}{\partial {\color{black}z}} \left( {\color{black}D^M_e} \frac{\partial {\color{black}c_f}(t,z)}{\partial {\color{black}z}} \right)
 		\end{equation}
@@
 
-	Here, ${\color{blue}c_f}(t,z), {\color{blue}c_s}(t,z),$ and ${\color{blue}T}(t,z)$ represent the concentration of solute in the fluid phase, the concentration of solute in the solid phase, and temperature, respectively.
-${\color{blue}r_e}(t,z)$ is a mass transfer kinetic term, ${\color{red}F}(t)$ is the mass flow rate and ${\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient.
+	Here, ${\color{black}c_f}(t,z), {\color{black}c_s}(t,z),$ and ${\color{black}T}(t,z)$ represent the concentration of solute in the fluid phase, the concentration of solute in the solid phase, and temperature, respectively.
+${\color{black}r_e}(t,z)$ is a mass transfer kinetic term, ${\color{black}F}(t)$ is the mass flow rate and ${\color{black}D^M_e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}F}(t))$ is the axial mass diffusion coefficient.
 
@@
 			%		{\scriptsize\begin{align*}
-					\cfrac{\partial {\color{blue}c_s}(t,z)}{\partial t} = \underbrace{ {\color{blue}r_e}(t,z) }_{\text{Kinetics}}
+					\cfrac{\partial {\color{black}c_s}(t,z)}{\partial t} = \underbrace{ {\color{black}r_e}(t,z) }_{\text{Kinetics}}
 			\end{equation} }
@@
 The graphical representation of the mass transfer mechanism is shown in Figure \ref{fig: SFE_Mechanism}.
-The mean solute concentration in the solid phase is denoted as ${\color{blue}c_s}$.
-At the solid-fluid interface, the equilibrium concentrations are given as ${\color{blue}c_s^*}$ and ${\color{blue}c_P^*}$, respectively for solid and fluid phases.
-The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{blue}c_{P}}$.
-As the solute diffuses through the pore, its concentration changes and reaches ${\color{blue}c_{Pf}}$ at the opening of the pore.
-The solute diffuses through the film around the particle and reaches a concentration in the bulk ${\color{blue}c_f}$.
+The mean solute concentration in the solid phase is denoted as ${\color{black}c_s}$.
+At the solid-fluid interface, the equilibrium concentrations are given as ${\color{black}c_s^*}$ and ${\color{black}c_P^*}$, respectively for solid and fluid phases.
+The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{black}c_{P}}$.
+As the solute diffuses through the pore, its concentration changes and reaches ${\color{black}c_{Pf}}$ at the opening of the pore.
+The solute diffuses through the film around the particle and reaches a concentration in the bulk ${\color{black}c_f}$.
 It can be assumed that the two-film theory describes the solid-fluid interface inside the pore.
@@
 The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
-Figure \ref{fig: SFE_Mechanism} illustrates the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as ${\color{blue}c_s}$ and the equilibrium concentrations at the solid-fluid interface are denoted as ${\color{blue}c_s^*}$ and ${\color{blue}c_p^*}$, respectively, for solid and fluid phases.
-The concentration of the solutes in the fluid phase in the center of the pore is denoted as ${\color{blue}c_{p}}$.
-As the solute diffuses through the pore, its concentration changes and reaches ${\color{blue}c_{pf}}$ at the opening of the pore.
-The solute then diffuses through the film around the particle and reaches a concentration in bulk ${\color{blue}c_f}$.
+Figure \ref{fig: SFE_Mechanism} illustrates the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as ${\color{black}c_s}$ and the equilibrium concentrations at the solid-fluid interface are denoted as ${\color{black}c_s^*}$ and ${\color{black}c_p^*}$, respectively, for solid and fluid phases.
+The concentration of the solutes in the fluid phase in the center of the pore is denoted as ${\color{black}c_{p}}$.
+As the solute diffuses through the pore, its concentration changes and reaches ${\color{black}c_{pf}}$ at the opening of the pore.
+The solute then diffuses through the film around the particle and reaches a concentration in bulk ${\color{black}c_f}$.
 The two-film theory describes the solid-fluid interface inside the pore.
@@
 
-		\citet{Bulley1984} suggests a process where the driving force for extraction is given by the difference between the concentration of the solute in bulk, ${\color{blue}c_f}$, and in the center of the pore, ${\color{blue}c_p^*}$.
-The concentration ${\color{blue}c_p^*}$ is in equilibrium with ${\color{blue}c_s}$ according to an equilibrium relationship.
-The rate of extraction is thus ${\color{blue}r_\text{e}}\left({\color{blue}c_f} - {\color{blue}c^*_p}({\color{blue}c_s})\right)$.
+		\citet{Bulley1984} suggests a process where the driving force for extraction is given by the difference between the concentration of the solute in bulk, ${\color{black}c_f}$, and in the center of the pore, ${\color{black}c_p^*}$.
+The concentration ${\color{black}c_p^*}$ is in equilibrium with ${\color{black}c_s}$ according to an equilibrium relationship.
+The rate of extraction is thus ${\color{black}r_\text{e}}\left({\color{black}c_f} - {\color{black}c^*_p}({\color{black}c_s})\right)$.
 
-		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between ${\color{blue}c_s}$ and ${\color{blue}c_p^*}$.
-${\color{blue}c_p^*}$ is determined by an equilibrium relationship with ${\color{blue}c_f}$ and the extraction rate is ${\color{blue}r_\text{e}}\left({\color{blue}c_s} - {\color{blue}c^*_p}({\color{blue}c_f})\right)$ or more precisely
+		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between ${\color{black}c_s}$ and ${\color{black}c_p^*}$.
+${\color{black}c_p^*}$ is determined by an equilibrium relationship with ${\color{black}c_f}$ and the extraction rate is ${\color{black}r_\text{e}}\left({\color{black}c_s} - {\color{black}c^*_p}({\color{black}c_f})\right)$ or more precisely
 
@@
 				\begin{equation} \label{Model_kinetic_basic}
-					{\color{blue}r_e}(t,z) = \cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{blue}P}(t))}{{\color{magenta} \mu l^2} }\left({\color{blue}c_s}(t,z) - {\color{blue}c_P^*}(t,z) \right)
+					{\color{black}r_e}(t,z) = \cfrac{{\color{black}D_i}({\color{black}T}(t,z), {\color{black}P}(t))}{{\color{black} \mu l^2} }\left({\color{black}c_s}(t,z) - {\color{black}c_P^*}(t,z) \right)
 			\end{equation} }
 
-		where ${\color{magenta}\mu}$ is sphericity, ${\color{magenta}l}$ a characteristic dimension of particles and can be defined as ${\color{magenta}l} = {\color{magenta}r}/3$, ${\color{magenta}r}$ is the mean particle radius, ${\color{magenta}\rho_s}$ is the solid density, ${\color{orange}D_i}({\color{blue}T}(t,z))$ corresponds to the overall diffusion coefficient and ${\color{blue}c_P^*}(t,z)$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).
+		where ${\color{black}\mu}$ is sphericity, ${\color{black}l}$ a characteristic dimension of particles and can be defined as ${\color{black}l} = {\color{black}r}/3$, ${\color{black}r}$ is the mean particle radius, ${\color{black}\rho_s}$ is the solid density, ${\color{black}D_i}({\color{black}T}(t,z))$ corresponds to the overall diffusion coefficient and ${\color{black}c_P^*}(t,z)$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).
 
-		According to \citet{Bulley1984}, a linear equilibrium relationship (equation  \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{blue}c_f^*}(t,z)$ is based on the concentration of the solute in the solid phase ${\color{blue}c_s}(t,z)$
+		According to \citet{Bulley1984}, a linear equilibrium relationship (equation  \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{black}c_f^*}(t,z)$ is based on the concentration of the solute in the solid phase ${\color{black}c_s}(t,z)$
 
@@
 				\begin{align} \label{Linear_equilibirum}
-					{\color{blue}c}(t,z) &= {\color{orange}k_p}({\color{blue}T}(t,z),{\color{blue}P}(t)) \allowbreak {\color{blue}q^*}(t,z)
+					{\color{black}c}(t,z) &= {\color{black}k_p}({\color{black}T}(t,z),{\color{black}P}(t)) \allowbreak {\color{black}q^*}(t,z)
 			\end{align} }
 
-			The volumetric partition coefficient ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{blue}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
-According to \citet{Spiro2007}, the term ${\color{orange}k_p}({\color{blue}T}(t,z),{\color{blue}P}(t))$ can be expressed as the function of mass partition factor ${\color{orange}k_m}({\color{blue}T}(t,z))$.
+			The volumetric partition coefficient ${\color{black}k_p}({\color{black}T}(t,z),{\color{black}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
+According to \citet{Spiro2007}, the term ${\color{black}k_p}({\color{black}T}(t,z),{\color{black}P}(t))$ can be expressed as the function of mass partition factor ${\color{black}k_m}({\color{black}T}(t,z))$.
 
@@
 				\begin{align}
-					{\color{orange}k_m}({\color{blue}T}(t,z)) = \cfrac{{\color{orange}k_p}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{magenta}\rho_s}}{{\color{orange}\rho}({\color{blue}T}(t,z),{\color{blue}P}(t))}
+					{\color{black}k_m}({\color{black}T}(t,z)) = \cfrac{{\color{black}k_p}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}\rho_s}}{{\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}
 			\end{align} }
@@
 					\label{Model_kinetic_no_sat}
-					{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{blue}P}(t))}{{\color{magenta} \mu l^2} }\left({\color{blue}c_s}(t,z) - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))}  {\color{blue}c_f}(t,z) \right)
+					{\color{black}r_e}(t,z) = -\cfrac{{\color{black}D_i}({\color{black}T}(t,z), {\color{black}P}(t))}{{\color{black} \mu l^2} }\left({\color{black}c_s}(t,z) - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right)
 			\end{equation} }
@@
 		\iffalse
-		 {\color{red}
+		 {\color{black}
 			The heat balance (Equation \ref{Model_heat}) consists of the convective and diffusive terms.
@@
 The pseudo-homogenous phase is assumed to flow only in the axial direction.
-The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{blue}P}(t))$ because the solid phase is stationary.
+The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid ${\color{black}C_p}({\color{black}T}(t,z),{\color{black}P}(t))$ because the solid phase is stationary.
 Therefore, this factor can be understood as the fraction of the fluid's total heat through convection.
@@
 
-		{\color{blue} The heat balance (Equation \ref{Model_heat}), is based on \citet{Srinivasan2012}, and consists of convective and diffusive terms.
+		{\color{black} The heat balance (Equation \ref{Model_heat}), is based on \citet{Srinivasan2012}, and consists of convective and diffusive terms.
 It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases.
 It is considered that there is no heat loss through the walls, and there is no heat generation in the system.
-The temperature of the extractor can be changed only by manipulating the temperature of the inlet stream ${\color{red}T_{Inlet}}(t)$.
+The temperature of the extractor can be changed only by manipulating the temperature of the inlet stream ${\color{black}T_{Inlet}}(t)$.
 			}
@@
 					\begin{split}
-						\cfrac{\partial {\color{blue}T}(t,z)}{\partial t} &= 
-						\underbrace{ -\cfrac{{\color{red}F}(t) {\color{orange}C_p}({\color{blue}T}(t,z),{\color{blue}P}(t))}{{\color{magenta}A} 	[(1-{\color{magenta}\epsilon}){\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{orange}C_p} ({\color{blue}T}(t,z),{\color{blue}P}(t)) + {\color{magenta} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}}  }_{\text{Convection}} + \\
-						& + \underbrace{ {\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{blue}P}(t)) \cfrac{\partial^2 {\color{blue}T}(t,z)}{\partial {\color{blue}z^2}} }_{\text{Diffusion}}
+						\cfrac{\partial {\color{black}T}(t,z)}{\partial t} &= 
+						\underbrace{ -\cfrac{{\color{black}F}(t) {\color{black}C_p}({\color{black}T}(t,z),{\color{black}P}(t))}{{\color{black}A} 	[(1-{\color{black}\epsilon}){\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}C_p} ({\color{black}T}(t,z),{\color{black}P}(t)) + {\color{black} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial {\color{black}T}(t,z)}{\partial {\color{black}z}}  }_{\text{Convection}} + \\
+						& + \underbrace{ {\color{black}D^T_e}({\color{black}T}(t,z),{\color{black}P}(t)) \cfrac{\partial^2 {\color{black}T}(t,z)}{\partial {\color{black}z^2}} }_{\text{Diffusion}}
 					\end{split}
@@
 
-		where $ {\color{orange}D^M_e}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{red}F}(t))$ is the axial mass diffusion coefficient, ${\color{orange}C_p}({\color{blue}T}(t,z),{\color{blue}P}(t))$ is the fluid's specific heat, ${\color{magenta}C_{ps}}$ is the specific heat of the solid phase, ${\color{orange}D^T_e}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{red}F}(t))$ is the axial heat diffusion coefficient.
+		where $ {\color{black}D^M_e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}F}(t))$ is the axial mass diffusion coefficient, ${\color{black}C_p}({\color{black}T}(t,z),{\color{black}P}(t))$ is the fluid's specific heat, ${\color{black}C_{ps}}$ is the specific heat of the solid phase, ${\color{black}D^T_e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}F}(t))$ is the axial heat diffusion coefficient.
 
@@
 			\begin{align} \label{EQ: Heat_internal}
-				&\cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{blue}e}(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) A_f v {\color{blue}e}(t,z) \right)}{\partial {\color{blue}z}} \nonumber \\
-				&= -{\color{blue}P}(t)\cfrac{\left( A_f v \right)}{\partial {\color{blue}z}} + \cfrac{\partial}{\partial {\color{blue}z}} \left( \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}} \right)
+				&\cfrac{\partial \left( {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}e}(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) A_f v {\color{black}e}(t,z) \right)}{\partial {\color{black}z}} \nonumber \\
+				&= -{\color{black}P}(t)\cfrac{\left( A_f v \right)}{\partial {\color{black}z}} + \cfrac{\partial}{\partial {\color{black}z}} \left( \cfrac{\partial {\color{black}T}(t,z)}{\partial {\color{black}z}} \right)
 			\end{align}
@@
 				\begin{equation}
-					d{\color{blue}e}(t,z)=C_vd{\color{blue}T}-\left[{\color{blue}P}(t)-{\color{blue}T}(t,z)\left(\cfrac{\partial {\color{blue}P}(t)}{\partial {\color{blue}T}(t,z)}\right)_{{\color{orange}v_m}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}\right]d{\color{orange}v_m}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)
+					d{\color{black}e}(t,z)=C_vd{\color{black}T}-\left[{\color{black}P}(t)-{\color{black}T}(t,z)\left(\cfrac{\partial {\color{black}P}(t)}{\partial {\color{black}T}(t,z)}\right)_{{\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}\right]d{\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)
 					\label{EQ: internal_energy_def}
@@
 
-			where ${\color{blue}e}^{id}(t,z)$ is the internal energy of perfect gas.
+			where ${\color{black}e}^{id}(t,z)$ is the internal energy of perfect gas.
 
-			Suppose a gas is considered to be perfectly caloric (${\color{blue}e}(t,z)={\color{magenta}C_v} {\color{blue}T}(t,z)$), then the energy equation can be written explicitly in the form of temperature.
-The perfectly caloric gas can be seen as the special case of a real gas, where the second term of Equation \ref{EQ: internal_energy_def} goes to zero and the heat capacity ${\color{magenta}C_v}$ is constant.
+			Suppose a gas is considered to be perfectly caloric (${\color{black}e}(t,z)={\color{black}C_v} {\color{black}T}(t,z)$), then the energy equation can be written explicitly in the form of temperature.
+The perfectly caloric gas can be seen as the special case of a real gas, where the second term of Equation \ref{EQ: internal_energy_def} goes to zero and the heat capacity ${\color{black}C_v}$ is constant.
 
@@
 					\begin{aligned}
-					&\cfrac{{\color{blue}e}(t,z)-{\color{blue}e}^{id}(t,z)}{R{\color{blue}T}(t,z)} = \\
-					& - \cfrac{{\color{orange}A}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{{\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)\sqrt{8}} \cfrac{{\color{magenta}\kappa} \sqrt{\color{magenta}T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)} \right]
+					&\cfrac{{\color{black}e}(t,z)-{\color{black}e}^{id}(t,z)}{R{\color{black}T}(t,z)} = \\
+					& - \cfrac{{\color{black}A}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)\sqrt{8}} \cfrac{{\color{black}\kappa} \sqrt{\color{black}T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)} \right]
 					\label{EQ: internal_energy_PR}
@@
 			\begin{equation}
-				{\color{blue}e}(t,z)={\color{blue}e}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)))=e( {\color{blue}T}(t,z),{\color{blue}P}(t), {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) )
+				{\color{black}e}(t,z)={\color{black}e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)))=e( {\color{black}T}(t,z),{\color{black}P}(t), {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) )
 			\end{equation}
@@
 
-			If the value of internal energy ${\color{blue}e}(t,z)$ is known from the time evolution of the energy Equation \ref{EQ: CompressibleEuler_3}, and pressure is known from measurement, then the temperature can be reconstructed.
+			If the value of internal energy ${\color{black}e}(t,z)$ is known from the time evolution of the energy Equation \ref{EQ: CompressibleEuler_3}, and pressure is known from measurement, then the temperature can be reconstructed.
 A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution (Equation \ref{EQ: Heat_internal}) and the output from Equation \ref{EQ: internal_energy_PR}.
-Such a procedure allow to find local temperature along spatial direction ${\color{blue}z}$ and needs to be repeated every time-step.
+Such a procedure allow to find local temperature along spatial direction ${\color{black}z}$ and needs to be repeated every time-step.
 
-			Another way to express the energy equation is to introduce enthalpy ${\color{blue}h}(t,z) = {\color{blue}e}(t,z) + {\color{blue}P}(t) / {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))$.
+			Another way to express the energy equation is to introduce enthalpy ${\color{black}h}(t,z) = {\color{black}e}(t,z) + {\color{black}P}(t) / {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$.
 By introducing the definition of enthalpy, the energy equation becomes
@@
 				\begin{align} \label{EQ:Enthalpy_equation}
-					&\cfrac{\partial \left({\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{blue}h}(t,z) A_f\right)}{\partial t} - \cfrac{\partial \left({\color{blue}P}(t) A_f\right)}{\partial t} \nonumber \\
-					&+ \cfrac{\partial \left( {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) {\color{blue}h}(t,z) A_f v \right)}{\partial {\color{blue}z}} - \cfrac{\partial}{\partial {\color{blue}z}} \left( k \cfrac{\partial {\color{blue}T}(t,z)}{\partial {\color{blue}z}} \right)
+					&\cfrac{\partial \left({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}h}(t,z) A_f\right)}{\partial t} - \cfrac{\partial \left({\color{black}P}(t) A_f\right)}{\partial t} \nonumber \\
+					&+ \cfrac{\partial \left( {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}h}(t,z) A_f v \right)}{\partial {\color{black}z}} - \cfrac{\partial}{\partial {\color{black}z}} \left( k \cfrac{\partial {\color{black}T}(t,z)}{\partial {\color{black}z}} \right)
 				\end{align}
@@
 
-			The main advantage of this formulation is the presence of term $\partial {\color{blue}P}(t) / \partial t $, which allows it to directly affect the system through the change of thermodynamic pressure (which is a control variable).
+			The main advantage of this formulation is the presence of term $\partial {\color{black}P}(t) / \partial t $, which allows it to directly affect the system through the change of thermodynamic pressure (which is a control variable).
 If an equation of state is known, the temperature can to be recovered from the enthalpy.
@@
 				\begin{equation}
-					{\color{blue}h}(t,z)={\color{blue}h}({\color{blue}T}(t,z),{\color{blue}P}(t),{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)))={\color{blue}h}( {\color{blue}T}(t,z),{\color{blue}P}(t), {\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t)) )
+					{\color{black}h}(t,z)={\color{black}h}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)))={\color{black}h}( {\color{black}T}(t,z),{\color{black}P}(t), {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) )
 					\label{EQ:Enthalpy_root}
@@
 					\begin{split}
-					{\color{blue}h}(t,z)-{\color{blue}h}(t,z)^{id}={\color{magenta}R}{\color{blue}T}(t,z) \left[{\color{magenta}T_r}({\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)-1) \right.
+					{\color{black}h}(t,z)-{\color{black}h}(t,z)^{id}={\color{black}R}{\color{black}T}(t,z) \left[{\color{black}T_r}({\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)-1) \right.
 \\
 					\left.
--2.078(1+{\color{magenta}\kappa} ){\sqrt { {\color{orange}\alpha}\left({\color{blue}T}(t,z)\right) } } \ln \left(\cfrac{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}\right)\right]
+-2.078(1+{\color{black}\kappa} ){\sqrt { {\color{black}\alpha}\left({\color{black}T}(t,z)\right) } } \ln \left(\cfrac{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}\right)\right]
 					\label{EQ:Enthalpy_PR}
@@
 
-			The Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which in this case is assumed to be ${\color{magenta}T_{ref}}=298.15~[K]$ and ${\color{magenta}P_{ref}}=1.01325~[bar]$.
+			The Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which in this case is assumed to be ${\color{black}T_{ref}}=298.15~[K]$ and ${\color{black}P_{ref}}=1.01325~[bar]$.
 
@@
 		The pressure term in the energy equation, given by Equation \ref{EQ:Enthalpy_equation}, describes the change of the thermodynamic pressure with respect to time.
-As explained in Chapters \ref{CH: Gouverning equations} and \ref{CH:Low_Mach_chapter}, at low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound.
-Under such conditions, the term $\partial {\color{blue}P}/\partial t$ can be approximated by an ordinary differential equation, which describes the instantaneous change of pressure in the system.
+As explained in Chapters \ref{CH:Governing_equations_chapter}, at Low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound.
+Under such conditions, the term $\partial {\color{black}P}/\partial t$ can be approximated by an ordinary differential equation, which describes the instantaneous change of pressure in the system.
 The pressure in the system is considered a state variable, while the pressure in the new time-step is considered a control variable.
@@
 			\begin{equation}
-				\frac{\partial {\color{blue}P}(t)}{\partial t} \approx \frac{{\color{blue}P}(t) - {\color{red}P_{in}}(t) }{\Delta t}
+				\frac{\partial {\color{black}P}(t)}{\partial t} \approx \frac{{\color{black}P}(t) - {\color{black}P_{in}}(t) }{\Delta t}
 		\end{equation}}
@@
 %				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
-				{\color{blue}y}(t) &= \int_{t_0}^{t_f} \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))} {\color{blue}c_f}(t,z) \biggr\rvert_{z=L} dt \\
+				{\color{black}y}(t) &= \int_{t_0}^{t_f} \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))} {\color{black}c_f}(t,z) \biggr\rvert_{z=L} dt \\
 %				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
-				\cfrac{d{\color{blue}y}(t)}{dt} &= \qquad \cfrac{{\color{red}F}(t)}{{\color{orange}\rho_f}({\color{blue}T}(t,z),{\color{blue}P}(t))} {\color{blue}c_f}(t,z) \biggr\rvert_{z=L} 
+				\cfrac{d{\color{black}y}(t)}{dt} &= \qquad \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))} {\color{black}c_f}(t,z) \biggr\rvert_{z=L} 
                 \label{Model_measurment_2}
@@
 		\subsubsection{Initial and boundary conditions} 
-		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}c_{s0}}$.
+		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{black}c_{s0}}$.
 On the other hand, the solute concentration in the fluid phase should not follow the same assumption as the solid phase.
@@
 The linear distribution $H(z)$ can be defined if the total mass of solute $m_{total}$ and initial mass ratio between solid and fluid phases $\tau$ are known.
-		Moreover, it is considered that the initial temperature of the extractor in every place is the same and described by ${\color{magenta}h_0}$.
+		Moreover, it is considered that the initial temperature of the extractor in every place is the same and described by ${\color{black}h_0}$.
 Therefore, the initial conditions employed in the simulation are:
@@
 				\begin{align*}
-					{\color{blue}c_f}(t = 0, z) &= H(z)   \\
-					{\color{blue}c_s}(t = 0, z) &= {\color{magenta}c_{s0}} \\
-					{\color{blue}h}(t = 0, z) &= {\color{magenta}h_0}
+					{\color{black}c_f}(t = 0, z) &= H(z)   \\
+					{\color{black}c_s}(t = 0, z) &= {\color{black}c_{s0}} \\
+					{\color{black}h}(t = 0, z) &= {\color{black}h_0}
 				\end{align*}
@@
 				\begin{bmatrix}
-					\cfrac{\partial {\color{blue}c_f}(t,z)}{\partial t}\\
-					\cfrac{\partial {\color{blue}c_s}(t,z)}{\partial t}\\
-					\cfrac{\partial {\color{blue}h}(t,z)}{\partial t} \\
-					\cfrac{\partial {\color{blue}P}(t,z)}{\partial t} \\
-					\cfrac{\partial {\color{blue}y}(t)}{\partial t} 
+					\cfrac{\partial {\color{black}c_f}(t,z)}{\partial t}\\
+					\cfrac{\partial {\color{black}c_s}(t,z)}{\partial t}\\
+					\cfrac{\partial {\color{black}h}(t,z)}{\partial t} \\
+					\cfrac{\partial {\color{black}P}(t,z)}{\partial t} \\
+					\cfrac{\partial {\color{black}y}(t)}{\partial t} 
 				\end{bmatrix}
@@
 				\begin{bmatrix}
-					{\color{blue}\bar{\phi_1}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)\\
-					{\color{blue}\bar{\phi_2}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)\\
-					{\color{blue}\bar{\phi_3}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right) \\
-					{\color{blue}\bar{\phi_4}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)\\
-					{\color{blue}\bar{\phi_5}} \left( {\color{blue}c_f}(t,z),{\color{blue}c_s}(t,z),{\color{blue}h}(t,z); {\color{magenta}\Theta} \right)
-				\end{bmatrix} = {\color{blue}\bar{\phi}} \left( t,z; {\color{magenta}\Theta} \right) = \cfrac{\partial {\color{blue}\chi}(t,z)}{\partial t}
+					{\color{black}\bar{\phi_1}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
+					{\color{black}\bar{\phi_2}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
+					{\color{black}\bar{\phi_3}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right) \\
+					{\color{black}\bar{\phi_4}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
+					{\color{black}\bar{\phi_5}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)
+				\end{bmatrix} = {\color{black}\bar{\phi}} \left( t,z; {\color{black}\Theta} \right) = \cfrac{\partial {\color{black}\chi}(t,z)}{\partial t}
 		\end{align} }
 
-		where ${\color{magenta}\Theta}$ is a paramter space consisting of model parameters ${\color{magenta}\theta}$ and controls ${\color{red}u}$, ${\color{blue}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{blue}\chi}$ is the state-space model.
+		where ${\color{black}\Theta}$ is a paramter space consisting of model parameters ${\color{black}\theta}$ and controls ${\color{black}u}$, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.
 
-		Each function ${\color{blue}\bar{\phi_i}}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{orange}G}_{i\times N_z+1}$ to ${\color{orange}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation.
-The state-space model ${\color{blue}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{blue}x}}(t)$.
+		Each function ${\color{black}\bar{\phi_i}}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{black}G}_{i\times N_z+1}$ to ${\color{black}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation.
+The state-space model ${\color{black}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{black}x}}(t)$.
 
@@
 				\begin{align*} \label{discretization}
-					\dot{{\color{blue}x}}(t) &= \cfrac{d {\color{blue}x}(t)}{d t} = 
+					\dot{{\color{black}x}}(t) &= \cfrac{d {\color{black}x}(t)}{d t} = 
 					\begin{bmatrix}
-						\cfrac{d {\color{blue}c_{f,1}}(t)}{d t} 	  \\
+						\cfrac{d {\color{black}c_{f,1}}(t)}{d t} 	  \\
 						\vdots					  \\
-						\cfrac{d {\color{blue}c_{f,N_z}}(t)}{d t} \\
+						\cfrac{d {\color{black}c_{f,N_z}}(t)}{d t} \\
 						\\ \hline \\
-						\cfrac{d {\color{blue}c_{s,1}}(t)}{d t} 	  \\
+						\cfrac{d {\color{black}c_{s,1}}(t)}{d t} 	  \\
 						\vdots					  \\
-						\cfrac{d {\color{blue}c_{s,N_z}}(t)}{d t} \\
+						\cfrac{d {\color{black}c_{s,N_z}}(t)}{d t} \\
 						\\ \hline \\
-						\cfrac{d {\color{blue}h_1}(t)}{d t} 	  \\
+						\cfrac{d {\color{black}h_1}(t)}{d t} 	  \\
 						\vdots 					  \\
-						\cfrac{d {\color{blue}h_{N_z}}(t)}{d t} \\
+						\cfrac{d {\color{black}h_{N_z}}(t)}{d t} \\
 						\\ \hline \\
-						\cfrac{d {\color{blue}P}(t)}{d t} \\
+						\cfrac{d {\color{black}P}(t)}{d t} \\
 						\\ \hline \\
-						\cfrac{d {\color{blue}y}(t)}{d t}
+						\cfrac{d {\color{black}y}(t)}{d t}
 					\end{bmatrix}
@@
 					\underbrace{\begin{bmatrix}
-							{\color{orange}G_1} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right)\\ 
+							{\color{black}G_1} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right)\\ 
 							\vdots\\ 
-							{\color{orange}G_{N_z}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right)\\ 
+							{\color{black}G_{N_z}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right)\\ 
 							\\ \hline \\ \\
-							{\color{orange}G_{N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right)\\ 
+							{\color{black}G_{N_z+1}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right)\\ 
 							\vdots\\
-							{\color{orange}G_{2N_z}} \left( {\color{blue}c}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right)\\ 
+							{\color{black}G_{2N_z}} \left( {\color{black}c}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right)\\ 
 							\\ \\ \hline \\ 
-							{\color{orange}G_{2N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right) \\
+							{\color{black}G_{2N_z+1}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right) \\
 							\vdots\\
-							{\color{orange}G_{3N_z}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right) \\ 
+							{\color{black}G_{3N_z}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right) \\ 
 							\\ \\ \hline \\
-							{\color{orange}G_{3N_z+1}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right) \\
+							{\color{black}G_{3N_z+1}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right) \\
 							\\ \\ \hline \\
-							{\color{orange}G_{3N_z+2}} \left( {\color{blue}c_f}(t),{\color{blue}c_s}(t),{\color{blue}h}(t); {\color{magenta}\Theta} \right) 
-					\end{bmatrix}}_{{\color{orange}G} \left( {\color{blue}x}(t); {\color{magenta}\Theta} \right)} 
+							{\color{black}G_{3N_z+2}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right) 
+					\end{bmatrix}}_{{\color{black}G} \left( {\color{black}x}(t); {\color{black}\Theta} \right)} 
 			\end{align*} }
 
-			where ${\color{blue}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{magenta}\Theta} \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of model parameters, $N_{u}$ is the number of control variables.
+			where ${\color{black}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{black}\Theta} \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of model parameters, $N_{u}$ is the number of control variables.
 
-			In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases (${\color{blue}c_f}(t,z)$ and ${\color{blue}c_s}(t,z)$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{blue}h}(t,z)$).
+			In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases (${\color{black}c_f}(t,z)$ and ${\color{black}c_s}(t,z)$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{black}h}(t,z)$).
 The controllable input variables are the mass flow-rate and temperature of the solvent in the feed and the pressure in the extractor.
-Additionally, the pressure change is augumented with the state-space and denoted as ${\color{blue}P}(t)$.
-			The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator (${\color{blue}Y}(t)$).
+Additionally, the pressure change is augumented with the state-space and denoted as ${\color{black}P}(t)$.
+			The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator (${\color{black}Y}(t)$).
 The system is controllable by manipulating the flow-rate and temperature (enthalpy) of $CO_2$ in the feed, and the pressure in the extractor.
@@
 
-			The method of lines is used to transform the process model equations into a set of ODEs denoted as ${\color{orange}G}({\color{blue}x}(t);{\color{magenta}\Theta})$.
+			The method of lines is used to transform the process model equations into a set of ODEs denoted as ${\color{black}G}({\color{black}x}(t);{\color{black}\Theta})$.
 The partial derivatives in $z$-direction are computed using a first-order and second-order finite difference approximation.

### 2023-10-02 SFE_article_Parameter_Estimation/Sections/Results.tex
02.10

--- 2023-08-06 SFE-article/Sections/Results.tex
@@
     		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
-    		\caption{Experiment at $40^\circ C$ and $200$ bar}
+    		\caption{Experiment at $40~^\circ C$ and 200 bar}
     	\end{subfigure}
@@
     		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
-    		\caption{Experiment at $50^\circ C$ and $200$ bar}
+    		\caption{Experiment at $50~^\circ C$ and 200 bar}
     	\end{subfigure}
@@
     		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
-    		\caption{Experiment at $40^\circ C$ and $300$ bar}
+    		\caption{Experiment at $40~^\circ C$ and 300 bar}
     	\end{subfigure}
@@
     		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
-    		\caption{Experiment at $50^\circ C$ and $300$ bar}
+    		\caption{Experiment at $50~^\circ C$ and 300 bar}
     	\end{subfigure}
@@
 		\adjustbox{max width=\columnwidth}{%
-			\csvautobooktabular{Figures/Results_estimation/estimation_2.csv} }
-		\caption{Parameter estimation results rounded to fifth decimal place}
+			\csvautobooktabular[separator=comma, table head = \toprule & $40~^\circ C$ & $50~^\circ C$ & $40~^\circ C$ & $50~^\circ C$ \\ & $200~bar$ & $200~bar$ & $300~bar$ & $300~bar$ \\\midrule]{Figures/Results_estimation/estimation_2.csv} }
+		\caption{Parameter estimation results}
 		\label{tab: Estimation_results}
@@
 
-	As shown in the Table \ref{tab: Estimation_results}, the optimizer found optimal values of the partition factors ${\color{orange}k_m}$ at relatively high levels.
+	As shown in the Table \ref{tab: Estimation_results}, the optimizer found optimal values of the partition factors ${\color{black}k_m}$ at relatively high levels.
 Such a behaviour suggest that the solvent is far from the saturation, and the model can be simplified.
@@
 		\begin{split}
-			&\lim_{k_m \rightarrow \infty} \left({\color{blue}{\color{blue} c_s} }(t,z)  - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)  = \\
-			&= \left({\color{blue}{\color{blue} c_s} }(t,z)  - \cfrac{{\color{magenta}\rho_s}}{\infty{\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right) = \left({\color{blue}{\color{blue} c_s} }(t,z) - 0 \right)
+			&\lim_{k_m \rightarrow \infty} \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right)  = \\
+			&= \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{\infty{\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right) = \left({\color{black}{\color{black} c_s} }(t,z) - 0 \right)
 		\end{split}
@@
 	Values of the reference internal diffusion coefficients are distinguished for each experiment.
-The order of magnitude of ${\color{orange}D_i^R}$ obtained from the optimization is similar to values found by other researchers.
-\citet{Reverchon1996} performed the parameter estimation for the extraction process of sage oil from seeds and reported ${\color{magenta}D_i^R} \approx 6\times 10^{-13}[m^2/s]$.
-Figure \ref{fig: results_DI} represent the ${\color{orange}D_i^R}$ as the function of density.
+The order of magnitude of ${\color{black}D_i^R}$ obtained from the optimization is similar to values found by other researchers.
+\citet{Reverchon1996} performed the parameter estimation for the extraction process of sage oil from seeds and reported ${\color{black}D_i^R} \approx 6\cdot 10^{-13}[m^2/s]$.
+Figure \ref{fig: results_DI} represent the ${\color{black}D_i^R}$ as the function of density.
 As the reference internal diffusion coefficient describes the diffusion inside of a particle, it is independent of external factors such as a fluid velocity around that particle.
 The reference internal diffusion depends only on local conditions given by temperature and pressure, which defines the physical properties of a stagnant fluid inside of pores of a particle—considering that the reference internal diffusion can be represented as a function of the density of the fluid, which is uniquely defined at a given temperature and pressure in the one-phase region.
-The linear trend in Figure \ref{fig: results_DI} suggests that ${\color{orange}D_i^R}$ increases with fluid density.
+The linear trend in Figure \ref{fig: results_DI} suggests that ${\color{black}D_i^R}$ increases with fluid density.
 
-	Similarly to the internal diffusion coefficient, the obtained values of ${\color{orange}\Upsilon}$ depends only on temperature and pressure, or by uniquely defined physical properties such as density.
-Figure \ref{fig: results_upsilon} shows that of ${\color{orange}\Upsilon}$ grows with density.
+	Similarly to the internal diffusion coefficient, the obtained values of ${\color{black}\Upsilon}$ depends only on temperature and pressure, or by uniquely defined physical properties such as density.
+Figure \ref{fig: results_upsilon} shows that of ${\color{black}\Upsilon}$ grows with density.
 This can be explained if the solubility increases as the density grows.
@@
 
-	The Figure \ref{fig:Di_upsilon_res} shows how the internal diffusivity ${\color{orange}D_i}$ (Equation \ref{EQ: C_sat_function}) as a function of the solute concentration in the solid phase at different operating conditions.
-The higher the density, the higher solubility according to \citet{Shojaie2010}, which results in higher values of the internal diffusion coefficient and larger curvature of ${\color{orange}D_i}$ function.
+	The Figure \ref{fig:Di_upsilon_res} shows how the internal diffusivity ${\color{black}D_i}$ (Equation \ref{EQ: C_sat_function}) as a function of the solute concentration in the solid phase at different operating conditions.
+The higher the density, the higher solubility according to \citet{Shojaie2010}, which results in higher values of the internal diffusion coefficient and larger curvature of ${\color{black}D_i}$ function.
 
@@
 			\includegraphics[trim = 11.2cm 13.7cm 11cm 1.0cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
-			\caption{Dependency of ${\color{orange}D_i}$}
+			\caption{Dependency of ${\color{black}D_i}$}
 			\label{fig: results_DI}
@@
 			\includegraphics[trim = 3.5cm 7.7cm 18.7cm 7.3cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
-			\caption{Dependency of ${\color{orange}\Upsilon}$}
+			\caption{Dependency of ${\color{black}\Upsilon}$}
 			\label{fig: results_upsilon}
@@
 			\includegraphics[trim = 1.0cm 0cm 3cm 0cm, clip, width=\columnwidth]{/Results_estimation/D_i_Uppsilon_results.pdf}
-			\caption{Dependency of ${\color{orange}D^R_i}$}
+			\caption{Dependency of ${\color{black}D^R_i}$}
 			\label{fig:Di_upsilon_res}
@@
 			\includegraphics[trim = 19.0cm 13.8cm 3.5cm 1.0cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_D_e.pdf}
-			\caption{Dependency of ${\color{orange}D^M_e}$}
+			\caption{Dependency of ${\color{black}D^M_e}$}
 			\label{fig: results_De}
@@
 	The axial diffusion coefficient obtained from the optimizer is relatively high compared to the internal diffusion coefficients.
-The values of ${\color{orange}D_e^M}$ have a similar order of magnitude as reported in the literature (\citet{ReisVasco2000}).
+The values of ${\color{black}D_e^M}$ have a similar order of magnitude as reported in the literature (\citet{ReisVasco2000}).
 %The relatively high values of the axial diffusion coefficients might be justified by taking into account the low values of the flow rate used in all the experiments.
-	The axial diffusion can be further analyzed by defining the Pecelt number (${\color{orange}P_e} = v \times {\color{magenta}d_p} / {\color{orange}D_e^M} $) and the Reynolds number (${\color{orange}R_e} = v \times {\color{magenta}d_p} / {\color{orange}\mu} $), where ${\color{magenta}d_p}=0.15~[m]$ is the characteristic dimension defined to be the extractor diameter and $\mu$ is the fluid viscosity.
+	The axial diffusion can be further analyzed by defining the Peclet number $\left( {\color{black}Pe} = \frac{v d_p}{D_e^M} \right)$ and the Reynolds number $\left( {\color{black}Re} = \frac{v d_p}{\mu} \right)$, where ${\color{black}d_p}=0.15~[m]$ is the characteristic dimension defined to be the extractor diameter and $\mu$ is the fluid viscosity.
 %The obtained Pecelt numbers have the order of magnitude of $1 \times 10^{8}$, which suggests that diffusion is negligible and advection dominates mass transport.
-	The obtained Pecelt numbers are ${\color{orange}P_e} \gg 1$, which suggests that mass diffusion is negligible and advection dominates mass transport.
+	The obtained Pecelt numbers are ${\color{black}Pe} \gg 1$, which suggests that mass diffusion is negligible and advection dominates mass transport.
 This observation suggests that the process model could be further simplified by neglecting the diffusion term.
@@
 	The noise present in each dataset is quantified by the parameter $\sigma^2$.
-It can be observed dataset obtained at $40 ^\circ C$ / 200 bar and $30 ^\circ C$ / 300 bar have similar value of $\sigma^2\approx0.07$.
-The slightly better results were obtained for the experiment at $50 ^\circ C$ / 300 bar when $\sigma^2\approx0.05$.
-The noisiest dataset corresponds to $50 ^\circ C$ / 200 bar when $\sigma^2\approx0.12$.
+It can be observed dataset obtained at $40~^\circ C$ / 200 bar and $30~^\circ C$ / 300 bar have similar value of $\sigma^2\approx0.07$.
+The slightly better results were obtained for the experiment at $50~^\circ C$ / 300 bar when $\sigma^2\approx0.05$.
+The noisiest dataset corresponds to $50~^\circ C$ / 200 bar when $\sigma^2\approx0.12$.
 All values of $\sigma^2$ are relatively low, suggesting the mathematical model can mimic the physical system up to the noise coming from the experiment.
@@
 To simplify the problem, the correlations are written as functions of fluid density rather than temperature and pressure.
-Since the optimizer found that ${\color{orange}k_m}$, $m_{total}$ and $C_{lim}$ don't change with the density variations, they are assumed to be constants and not considered further.
+Since the optimizer found that ${\color{black}k_m}$, $m_{total}$ and $C_{lim}$ don't change with the density variations, they are assumed to be constants and not considered further.
 
@@
 %		\includegraphics[trim = 11.7cm 14cm 2.3cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
-%		\caption{Second-order polynomial regression of fitted parameters (${\color{orange}D_i^R}$ and ${\color{orange}D_e^M}$) as a function of fluid density $\rho_f$}
+%		\caption{Second-order polynomial regression of fitted parameters (${\color{black}D_i^R}$ and ${\color{black}D_e^M}$) as a function of fluid density $\rho_f$}
 %		\label{fig:Regression_2}

### 2023-10-02 SFE_article_Parameter_Estimation/Sections/Thermo_imp.tex
02.10

--- 2023-08-01 SFE-article/Sections/Thermo_imp.tex
@@
 	Fluid properties can be divided into two kinds: equilibrium properties and transport properties.
-The equation of state can be used accurately to predict the equilibrium properties, such as density, enthalpy, vapour pressure, fugacity and fugacity coefficient, vapour-liquid equilibrium, and all kinds of excess properties.
+The equation of state can be used accurately to predict the equilibrium properties, such as fluid density, enthalpy, vapour pressure, fugacity and fugacity coefficient, vapour-liquid equilibrium, and all kinds of excess properties.
 
-	Supercritical $CO_2$'s thermodynamic properties, such as density, the local speed of sound, and specific heat capacity, vary significantly with slight changes in temperature and pressure due to real gas effects.
+	Supercritical $CO_2$'s thermodynamic properties, such as density or specific heat capacity, vary significantly with slight changes in temperature and pressure due to real gas effects.
 The Peng-Robinson equation of state (P-R EOS) is used to calculate the thermodynamic properties by accounting for these real gas effects are presented in Appendix \ref{subsubsec: Equation of state}.
@@
 	NIST has developed a viscosity formulation consisting of four contributions: (i) for the limit of zero density, (ii) for the initial density dependence, (iii) for the residual viscosity, and (iv) for the singularity of the viscosity at the critical point.
-The NIST correlation covers temperatures from 100 to 2000 $K$ for gaseous $CO_2$, and from 220 to 700 $K$ with pressures along the melting line up to 8000 $MPa$ for compressed and supercritical liquid states.
+The NIST correlation covers temperatures from 100 to 2000 K for gaseous $CO_2$, and from 220 to 700 K with pressures along the melting line up to 8000 MPa for compressed and supercritical liquid states.
 These correlations and theories are essential in predicting transport properties for real gases and liquids and can assist in engineering design and analysis.
@@
 The work of \citet{Huber2016} captures the singular behaviour of thermal conductivity around the critical point.
-The correlation is applicable for the temperature range from the triple point to 1100 $K$ and pressures up to 200 $MPa$.
+The correlation is applicable for the temperature range from the triple point to 1100 K and pressures up to 200 MPa.
 Figure \ref{fig: SFE_Properties_Thermal}.

### 2023-10-02 SFE_article_Parameter_Estimation/Sections/Thermodynamic_details.tex
02.10

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Thermodynamic_details}

	\subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}
	In this study, the influence of real gas effects are introduced through ${\color{black}P}(t) {\color{black}v_m}({\color{black}T}(t,z),{\color{black}P}(t)) = {\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right){\color{black}R}{\color{black}T}(t,z)$, where ${\color{black}v_m}$ represents the molar volume of $CO_2$, ${\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ denotes its compressibility factor, and $R$ is the universal gas constant. The main advantage of using compressibility in calculations is to express it as an explicit function of temperature and pressure. It can be written as a cubic function of the molar volume (of the density). Detail information about Peng-Robinson equation of state can be found in the work of \citet{Peng1976}, \citet{Elliott2011} or \citet{Pratt2001}. The P-R EOS is presented by Equation \ref{EQ: PR}.

	{\footnotesize
		\begin{equation}
			{\color{black}P}(t) = \cfrac{{\color{black}R}{\color{black}T}(t,z)}{{\color{black}v_m}({\color{black}T}(t,z),{\color{black}P}(t)) - {\color{black}b}} - \cfrac{{\color{black}a^c}{\color{black}\alpha}\left({\color{black}T}(t,z)\right)}{{\color{black}v_m}({\color{black}T}(t,z),{\color{black}P}(t))^2 + 2{\color{black}b}{\color{black}v_m}({\color{black}T}(t,z),{\color{black}P}(t)) - {\color{black}b}^2}
			\label{EQ: PR}
		\end{equation}
	}

	The Equation \ref{EQ: PR} can be also written as the third-order given by Equation \ref{eq: Compressibility}. Numerical methods such as Newton-Raphson can be used to solve the polynomial equation to obtain the compressibility ${\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ at given temperature and pressure. Alternatively, the Cardano formula can be used to get the closed form solution of the Equation \ref{eq: Compressibility}. Further details regarding the Cardano formula can be found in Appendix \ref{CH: Cardano}.

	{\footnotesize	
	\begin{equation}\label{eq: Compressibility}
	\begin{aligned}
		&{\color{black}Z}^3 - \left(1 - {\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)\right) {\color{black}Z}^2 \\
		&+ \left({\color{black}A}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) - 2{\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) - 3{\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)^2\right) {\color{black}Z} = 0
	\end{aligned} \end{equation} }

	where ${\color{black}A}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ and ${\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ are functions of time and space defined on the attraction parameter, ${\color{black}a}\left({\color{black}T}(t,z)\right) = {\color{black}a^c}{\color{black}\alpha}\left({\color{black}T}(t,z)\right)$ with ${\color{black}a^c} \approx 0.45724 {{\color{black}R}^2{\color{black}T_c}^2}/{{\color{black}P_c}}$, and the repulsion parameter, ${\color{black}b} \approx 0.07780 {{\color{black}R}{\color{black}T_c}}/{{\color{black}P_c}}$, both functions of the critical temperature ${\color{black}T_c}$ and pressure ${\color{black}P_c}$.

	{\footnotesize
	\begin{subequations} \label{eq: PR_AB}
		\begin{align} 
			{\color{black}A}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)	& = \dfrac{{\color{black}\alpha}\left({\color{black}T}\left(t,z\right)\right){\color{black}a^c}{\color{black}P}(t)}{{\color{black}R}^2{\color{black}T}^2(t,z)};													\label{eq: PR_A}\\
			{\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)	& = \dfrac{{\color{black}b}{\color{black}P}(t)}{{\color{black}R}{\color{black}T}(t,z)}	\label{eq: PR_B}.
		\end{align}
	\end{subequations}}

	The quantity ${\color{black}\alpha}\left({\color{black}T}\left(t,z\right)\right)$ is a dimensionless correction term that depends on the temperature ${\color{black}T}\left(t,z\right)$ and a constant ${\color{black}\kappa}$. The constant ${\color{black}\kappa}$ is given by the formula ${\color{black}\kappa} = 0.37464 + 1.54226 {\color{black}\omega} - 0.26992 {\color{black}\omega^2}$, where ${\color{black}\omega}$ is the acentric factor of $CO_2$ molecules and is equal to 0.239.

%	Using the physical constants $\varphi_{Z} = \left(R,T_c_{CO_2},P_c{CO_2},\kappa{CO_2}\right)$, we can represent the compressibility ${\color{black}\overline{Z}}\left({\color{black}T}(t,z), {\color{black}P}(t) \mid \varphi{Z}\right)$ as a function of temperature and pressure with their complete set of functional dependencies and parameters.

	%	The compressibility factor can be obtained by solving the polynomial form of the P-R EOS given by Equation \ref{EQ: PR_polynomial}.

	%	{\footnotesize
		%		\begin{equation}
			%			Z^3 - (1-B)Z^2+(A-2B-3B^2)Z -(AB-B^2-B^3) = 0
			%			\label{EQ: PR_polynomial}
			%		\end{equation}
		%	}
	%	
	In a one-phase region, the fluid is described by one real root corresponding to the gas, liquid or supercritical phase. The gas-liquid mixture is present in the two-phase region, and two roots are found. The biggest root is assigned to the gas phase, and the smallest root corresponds to the liquid phase.

	\subsubsection{Density of the fluid phase} \label{subsubsec: Fluid density}
	%\noindent \textbf{Density of the fluid phase} \\

	The density of the fluid phase, denoted by ${\color{black}\rho_f}$, is assumed to be equal to the density of the solvent at a given temperature and pressure. Since the temperature ${\color{black}T}(t,z)$ of the fluid phase is a modelled variable, the density can vary both along the bed and in time. Using the definition of compressibility, the following expression for the density can be obtained:

	{\footnotesize
		\begin{equation} \label{eq: Density}
			{\color{black}\rho_f} \left({\color{black}T}(t,z),{\color{black}P}(t) \right) = \frac{{\color{black}P}(t) {\color{black}M_{CO_2}}}{{\color{black}R}{\color{black}T}(t,z){\color{black}Z}\left({\color{black}T}(t,z),{\color{black}P}(t) \right)},
	\end{equation}}

	where ${\color{black}M_{CO_2}}$ denotes the molar mass of $CO_2$, and ${\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ is the compressibility factor that solves Eq. \eqref{eq: Compressibility}. This means that the density of the fluid depends on both space and time, due to its dependence on temperature and pressure.
%	, and it can be expressed in terms of a set of physical constants, denoted by $\varphi{\rho_\text{F}} = \left({\color{black}R}, {\color{black}M_{CO_2}}, {\color{black}T_c{CO_2}}, {\color{black}P_c{CO_2}}, {\color{black}\omega{CO_2}}\right)$.

	\subsubsection{Heat capacity of the fluid phase} \label{subsubsec: Fluid heat capacity}
%	\noindent\textbf{Heat capacity of the fluid phase} \\

	%The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}. The main steps in the derivation of ${\color{black}C_p}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ are presented below: 
	Following the work of \citet{Pratt2001}, it is assumed that the specific heat can be obtained as a sum of ideal gas contribution and a residual correction for non-ideal behaviour, as given by Equations \ref{eq: Cv_CO2} and \ref{eq: Cp_CO2}.

	{\footnotesize
	\begin{subequations}\begin{align}
			{\color{black}C_v}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) & = {\color{black}C_v^{\text{I}}}\left({\color{black}T}(t,z),P(t)\right) + {\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) \label{eq: Cv_CO2}; \\ 
			{\color{black}C_p}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) & = \underbrace{{\color{black}C_p^{\text{I}}}\left({\color{black}T}(t,z),P(t)\right)}_{\text{Eq. } \eqref{eq: Cp_I}} + \underbrace{{\color{black}C_p^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}_{\text{Eq. } \eqref{eq: Cp_R}}  \label{eq: Cp_CO2}.
	\end{align}\end{subequations} }

	${\color{black}C_v}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ and ${\color{black}C_p}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ are the specific heat of $CO_2$ at constant volume and pressure, respectively.

	The ideal-gas contribution ${\color{black}C_v^{\text{I}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ and ${\color{black}C_p^{\text{I}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$, can be obtained based on heat-capacity data applicable to gases at low pressure. For $CO_2$, the ideal gas contribution to the specific heat at constant ${\color{black}P}(t)$, as function of ${\color{black}T}(t,z)$ is given by,

	{\footnotesize
	\begin{equation}
		{\color{black}C_p^{\text{I}}}\left({\color{black}T}(t,z),P(t)\right) = {\color{black}C_{P0}} + {\color{black}C_{P1}}T(t,z) + {\color{black}C_{P2}}{\color{black}T}^2(t,z) + {\color{black}C_{P3}}{\color{black}T}^3(t,z) \label{eq: Cp_I}
	\end{equation} }

	where the coefficients ({\color{black}REF}) of the expansion are ${\color{black}C_{P0}} = 4.728$, ${\color{black}C_{P1}} = 1.75 \times 10^{-3}$, ${\color{black}C_{P2}} = -1.34 \times 10^{-5}$, and ${\color{black}C_{P3}} = 4.10 \times 10^{-9}$.

	The correction term ${\color{black}C_p^{\text{R}}}\left({\color{black}T}(t,z){\color{black}P}(t)\right)$ at constant pressure ${\color{black}P}(t)$, can be defined by introducing  ${\color{black}C_p^{\text{I}}}({\color{black}T}(t,z)) - {\color{black}C_v^{\text{I}}}({\color{black}T}(t,z)) = {\color{black}R}$ and using the definition of ${\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z){\color{black}P}(t)\right)$. The general form of the correction term is given by Equation \ref{eq: Cp_R}

	{\footnotesize	
	\begin{align}
		&{\color{black}C_p^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) = \underbrace{{\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}_{\text{Eq. }\eqref{eq: CvR}} \nonumber \\
		&+ {\color{black}T}(t,z) \underbrace{\left(\cfrac{\partial {\color{black}P}(t)}{\partial {\color{black}T}}\right)_{{\color{black}v_m}(t,z)}}_{\text{Eq. } \eqref{eq: dPdT}} \underbrace{\left(\cfrac{\partial {\color{black}v_m}\left({\color{black}T}(t,z),{\color{black}P}(t)\right)}{\partial {\color{black}T}}\right)_{{\color{black}P}(t)}}_{\text{Eq. } \eqref{eq: dVdT}} - {\color{black}R}. \label{eq: Cp_R} 
	\end{align} }

%	The braced terms are obtained from the chosen equation of state and the compressibility definition ${\color{black}P}(t) {\color{black}v_m}({\color{black}T}(t,z),{\color{black}P}(t)) = {\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right){\color{black}R}{\color{black}T}(t,z)$. \\

	For the partial derivative of the volume with respect to temperature ${\color{black}T}(t,z)$ at constant pressure ${\color{black}P}(t)$, we have

	{\footnotesize
	\begin{align}
		\left( \cfrac{\partial {\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{\partial {\color{black}T}} \right)_{{\color{black}P}(t)} &= \cfrac{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) {\color{black}R}}{{\color{black}P}(t)} \nonumber \\
		&+ \cfrac{{\color{black}R}{\color{black}T}(t,z)}{{\color{black}P}(t)} \underbrace{\left( \cfrac{\partial {\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{\partial {\color{black}T}} \right)_{{\color{black}P}(t)}}_{\text{Eq. }\eqref{eq: dZdT}} \label{eq: dVdT}
	\end{align} }

	with partial derivative of the compressibility factor with respect to temperature ${\color{black}T}(t,z)$ at constant pressure ${\color{black}P}(t)$

	{\footnotesize
	\begin{equation}
		\left(\cfrac{\partial{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{\partial {\color{black}T}}\right)_{{\color{black}P}(t)} = \left(\cfrac{\partial \dfrac{{\color{black}P}(t) {\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}R}{\color{black}T}(t,z)}}{\partial {\color{black}T}}\right)_{{\color{black}P}(t)} \label{eq: dZdT}
	\end{equation} }

	Similarly, for the partial derivative of the pressure with respect to temperature at constant volume is :

	{\footnotesize
	\begin{equation}
		\left(\cfrac{\partial {\color{black}P}(t)}{\partial {\color{black}T}}\right)_{{\color{black}v_m}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{black}Z}{\color{black}R}{\color{black}T}(t,z)}{{\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}}}{\partial{\color{black}T}}\right)_{{\color{black}v_m}(t,z)} \label{eq: dPdT}
	\end{equation} }

	The residual specific heat at constant volume is obtained, by definition, by using the residual internal energy

	{\footnotesize
	\begin{equation}
		{\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z),{\color{black}P}(t)\right) = \left(\cfrac{\partial{\color{black}U^{\text{R}}}\left({\color{black}T}(t,z),{\color{black}P}(t)\right)}{\partial {\color{black}T}}\right)_{{\color{black}v_m}(t,z)} \label{eq: CvR}
	\end{equation} }

	%By denoting the physical constants as $\varphi_{C_p^{\text{F}}} = ({\color{black}R}, {\color{black}M},\\ {\color{black}T_c}, {\color{black}P_c}, {\color{black}\omega})$, we get the spatio-temporal representation \\$C_p^{\text{F}}\left(T(t,z),P(t) \mid \varphi_{C_p^{\text{F}}}\right)$ of the specific heat of the fluid phase.

	\subsubsection{Departure functions for enthalpy calculations} \label{CH:Enthalpy}

	In thermodynamics, a departure function is a concept used to calculate the difference between a real fluid's thermodynamic properties and those of an ideal gas, given a specific temperature and pressure. Common departure functions include those for enthalpy, entropy, and internal energy. These functions are used to calculate extensive properties, which are properties computed as a difference between two states.

	For example, to evaluate the enthalpy change between two points, $h(V_1,T_1)$ and $h(V_2,T_2)$, we first calculate the enthalpy departure function between the initial volume $V_1$ and infinite volume at temperature $T_1$. We then add to that the ideal gas enthalpy change due to the temperature change from $T_1$ to $T_2$, and finally subtract the departure function value between the final volume $V_2$ and infinite volume.

	Departure functions are computed by integrating a function that depends on an equation of state and its derivative. The general form of the enthalpy equation is given by:

	{\footnotesize
		\begin{equation}
			\frac{h^{id}-h}{RT} =\int_{v_m}^{\infty }\left(T\left({\frac{\partial Z}{\partial T}}\right)_{v_m}\right){\frac{dv_m}{v_m}} + 1-Z
		\end{equation}
	}

	Here, $h^{id}$ represents the enthalpy of an ideal gas, $h$ is the enthalpy of a real fluid, $R$ is the universal gas constant, $T$ is temperature, $v_m$ is the molar volume, and $Z$ is the compressibility factor.

	The integral in the equation is evaluated over the range of molar volumes from $v_m$ to infinity. The integral includes a term that depends on the derivative of the compressibility factor with respect to temperature, evaluated at the molar volume $v_m$. Finally, the term $1-Z$ is added to account for the deviation of the fluid's properties from those of an ideal gas.

	The Peng–Robinson equation of state relates the three interdependent state properties pressure $P$, temperature $T$, and molar volume $v_m$. From the state properties ($P$, $v_m$, $T$), one may compute the departure function for enthalpy per mole (denoted $h$) as presented by \citet{Gmehling2019} or \citet{Elliott2011}:

	{\footnotesize
		\begin{equation}
			h-h^{\mathrm {id} }=RT\left(T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right)
		\end{equation}
	}

\end{document}

### 2023-10-02 SFE_article_Parameter_Estimation/Sections/introduction_imp.tex
02.10

@@
 The distillation process is carried out at a high temperature, which causes thermal degradation of thermolabile compounds—considering that alternative techniques like supercritical fluid extraction gained popularity for extraction.
-Supercritical $CO_2$, in particular, is attractive due to its unique properties such as inflammable, non-toxic, low critical temperature and non-corrosive.
+Supercritical carbon dioxide, in particular, is attractive due to its unique properties such as inflammable, non-toxic, low critical temperature and non-corrosive.
 Furthermore, its critical point is relatively low compared to other fluids, making it a suitable alternative to traditional extraction techniques.
@@
 	\citet{Reverchon1996} developed a model for fluid-solid extraction, where the oil is treated as a single component, and the extraction process is controlled by internal mass transfer resistance, neglecting external mass transfer.
-However, this model does not consider the influence of axial dispersion or changes in density and flow rate along the bed.
+However, this model does not consider the influence of axial dispersion or changes in fluid density and flow rate along the bed.
 
@@
 The maximum likelihood estimator is used to solve the parameter estimation problem, and the obtained parameters are subjected to regression to derive correlations.
-These correlations enable the process model to be generalized across a range of temperatures (40 to $50^\circ C$) and pressures (200 to 300 bars).
+These correlations enable the process model to be generalized across a range of temperatures (40 to $50~^\circ C$) and pressures (200 to 300 bar).
 

### 2023-10-03 SFE_article_Parameter_Estimation/Article_Model_Parameters.tex
03.10

@@
 This study aimed to investigate the supercritical extraction process of the caraway oil from caraway seeds.
-The extraction was performed in a partially filled extractor with a fixed bed operated under multiple constant operating conditions.
-The dataset collected from four experiments consists of four experiments conducted at different operating conditions: $40~^\circ C$ / $200$ bar, $50~^\circ C$ / $200$ bar, $40~^\circ C$ / $300$ bar, and $50~^\circ C$ / $300$ bar.
 A distributed-parameter model is used to describe the fluid-solid extraction process with carbon dioxide as a solvent.
@@
 The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
-This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, saturation concentration, and an initial state estimate.
-These parameters are estimated from the Peng-Robinson equation of state and by applying the maximum likelihood estimation method on yield data under the normal error assumption.
+This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and an initial state estimate.
+The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
+The missing parameters which describe the extraction kinetic are obtained by solving the maximum likelihood estimation on experimental yield data under the normal error assumption.
+A set of laboratory experiments was performed in a partially filled extractor with a fixed bed operated under multiple constant operating conditions: $40~^\circ C$ / $200$ bar, $50~^\circ C$ / $200$ bar, $40~^\circ C$ / $300$ bar, and $50~^\circ C$ / $300$ bar.
 

### 2023-10-03 SFE_article_Parameter_Estimation/Sections/Thermodynamic_details.tex
03.10

@@
 
-	where the coefficients ({\color{black}REF}) of the expansion are ${\color{black}C_{P0}} = 4.728$, ${\color{black}C_{P1}} = 1.75 \times 10^{-3}$, ${\color{black}C_{P2}} = -1.34 \times 10^{-5}$, and ${\color{black}C_{P3}} = 4.10 \times 10^{-9}$.
+	where the coefficients of the expansion are ${\color{black}C_{P0}} = 22.26$, ${\color{black}C_{P1}} = 5.981 \times 10^{-2}$, ${\color{black}C_{P2}} = -3.501 \times 10^{-5}$, and ${\color{black}C_{P3}} = 7.469 \times 10^{-9}$, as given by \citet{Kyle1999}.
 

### 2023-10-03 SFE_article_Parameter_Estimation/Sections/introduction_imp.tex
03.10

@@
 		\centering
-		\includegraphics[trim = 5cm 12cm 8cm 6cm, clip,width=\columnwidth]{Figures/PFD.pdf}
+		\includegraphics[width=\columnwidth]{Figures/PFD.drawio.pdf}
 		\caption{Process flow diagram}
@@
 	The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties.
-Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations derived under the Low-Mach number assumption.
-The simplified balance equations are combined with the extraction kinetic equation to develop the process model in Chapter \ref{CH: Extraction_model}.
+Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations.
+The balance equations are combined with the extraction kinetic equation to develop the process model in Chapter \ref{CH: Extraction_model}.
 The maximum likelihood technique is presented in Chapter \ref{CH: Parameter_estimation} and is then combined with the process model.
-The dataset obtained from laboratory experiments closes the optimization problem in Chapter \ref{CH: Experiments}.
+Chapter \ref{CH: Experiments} describes the experimental work and the data collected from experiments are used to estimate missing parameters related to the extraction kinetic.
 Finally, the parameter estimations and simulation results are discussed in Chapters \ref{CH: Results} and \ref{CH: Conclusion}

### 2023-10-03 SFE_SEnsitivity_Analysis/SpecificHeatComp.m

@@ -12,7 +12,7 @@ function Cp = SpecificHeatComp(T, P, Z, RHO, theta)
     R       = 83.1447;           % Universal gas constant, [m3-bar/K-mol]
     kappa   = 0.2250;
     MW      = theta{14};         % Molar mass [g/mol]       
-    CP_0    = theta{17};     
+    
     CP_A    = theta{18};       
     CP_B    = theta{19};       
     CP_C    = theta{20};       
@@ -67,7 +67,7 @@ function Cp = SpecificHeatComp(T, P, Z, RHO, theta)
     d2adT2 = a*m*(1+m).*sqrt(Tc./T)./(2.*T.*Tc);
 
     %% Heat Capacity - Ideal gas
-    Cp_Ideal = CP_0 * (CP_A + CP_B.*T + CP_C.*T.^2 + CP_D.*T.^3);
+    Cp_Ideal = CP_A + CP_B.*T + CP_C.*T.^2 + CP_D.*T.^3;
     Cv_Ideal = Cp_Ideal - R/10;
 
     %% Heat Capacity - correction for real gasses

### 2023-10-05 SFE_article_Parameter_Estimation/Article_Model_Parameters.tex
05.10

@@
 % Figure packages
-\usepackage{graphicx,float}
+\usepackage{graphicx}
+\usepackage{float}
+\restylefloat{table}
 \usepackage{adjustbox}
@@
 The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
+The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
 This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and an initial state estimate.
-The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
-The missing parameters which describe the extraction kinetic are obtained by solving the maximum likelihood estimation on experimental yield data under the normal error assumption.
+The missing model parameters are obtained by solving the maximum likelihood estimation based on experimental yield data under the normal error assumption.
 A set of laboratory experiments was performed in a partially filled extractor with a fixed bed operated under multiple constant operating conditions: $40~^\circ C$ / $200$ bar, $50~^\circ C$ / $200$ bar, $40~^\circ C$ / $300$ bar, and $50~^\circ C$ / $300$ bar.
@@
 \subsection{Thermodynamic}
+\subfile{Sections/Qubic_EOS}
 \subfile{Sections/Thermodynamic_details}

### 2023-10-05 SFE_article_Parameter_Estimation/Sections/Qubic_EOS.tex
05.10

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	%\label{CH: Thermodynamic_details}

	%subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}

	An equation of state (EoS) is an algebraic relation between P, $v_m$, and T. Cubic equations of state are a specific class of thermodynamic models for modeling the pressure of a gas as a function of temperature and density and which can be rewritten as a cubic function of the molar volume. In general, the general cubic equation of state has a number of degrees of freedom equal to 2 + the number of components in the system (total flow rate, temperature, pressure and N-1 mole fractions). In some cases (primarily inlets to units), this is increased by 1 due to the removal of a constraint on the sum of mole fractions.

	Equations of state are generally applied in the fields of physical chemistry and chemical engineering, particularly in the modeling of vapor–liquid equilibrium and chemical engineering process design. Following the work of \citet{Poling2001}, the general cubic equation of state is represented by the following equations:

	{\footnotesize
	\begin{equation} \label{EQ: General_Qubic}
		P = \frac{RT}{v_m-b} - \frac{\Theta \left( v_m - \eta \right)}{\left( v_m - b \right) \left(v_m^2 + \delta v_m + \epsilon \right) }
	\end{equation}
	}

	where, depending upon the model, the parameters $\Theta,~b,~\delta,~\epsilon$ may be constants, including zero, or they may vary with $T$ and / or composition. Thus, the distinctions among cubic EoS models for pure components are which of the parameters in Equation \ref{EQ: General_Qubic} are nonzero and how they are made to vary with $T$. A common notation for EOS is to use $\Theta(T)=a\alpha(T)$, where $\alpha(T_c) = 1$. Tables \ref{tab:Popular_Cubic_EoS} and \ref{tab:Popular_Cubic_EoS_alpha} give relations among the Equation \ref{EQ: General_Qubic} parameters for several common cubic EoS.

	\begin{table}[h!]
		\centering
		\adjustbox{width=\columnwidth}{%
			\begin{tabular}{|c| c c c|} 
				\hline
				Eos & $\delta$ & $\epsilon$ & $\theta$ \\
				\hline
				van der Waals (1890) & 0 & 0 & a \\
				Redlich and Kwong (1949) & b & 0 & $a / T^{0.5}$ \\
				Peng and Robinson (1976) \cite{Peng1976} & 2b & $-b^2$ & $a\alpha(T_r) $ \\
				\hline
		\end{tabular} }
		\caption{Parameters for Popular Cubic EoS}
		\label{tab:Popular_Cubic_EoS}
	\end{table}

	\begin{table}[h!]
		\centering
		\adjustbox{width=\columnwidth}{%
			\begin{tabular}{|c| c|} 
				\hline
				Eos & $\alpha(T_r)$ \\
				\hline
				van der Waals (1890) & 1 \\
				Redlich and Kwong (1949) & $1/\sqrt{T_r}$ \\
				Peng and Robinson (1976) \cite{Peng1976} & $[1+(0.37464 + 1.54226 \omega - 0.2699\omega^2)(1-\sqrt{T_r})]^2$ \\
				\hline
		\end{tabular} }
		\caption{Parameters for Popular Cubic EoS}
		\label{tab:Popular_Cubic_EoS_alpha}
	\end{table}

	Equation \ref{EQ: General_Qubic} can be written to obtain the compressibility as given by Equation \ref{EQ:Comp_EOS}.

	{\footnotesize
	\begin{equation} \label{EQ:Comp_EOS}
		Z = \frac{v_m}{v_m-b} - \frac{\left( \Theta /RT \right) v_m \left( v_m - \eta \right) }{\left( v_m - b \right) \left(v_m^2 + \delta v_m + \epsilon \right)}
	\end{equation}
	}

	When it is rewritten as the form to be solved when T and P are specified and Z is to be found analytically, it is

\end{document}

### 2023-10-05 SFE_article_Parameter_Estimation/Sections/Thermo_imp.tex
03.10
05.10

@@
 Near the critical point, small changes in pressure or temperature result in significant changes in density, allowing many properties of an SCF to be fine-tuned.
-By changing the pressure and temperature, the properties can be tuned to be more liquid-like or gas-like.
+By changing the pressure and temperature, the properties of carbon dioxide can be tuned to be more liquid-like or gas-like.
 
@@
 The Peng-Robinson equation of state (P-R EOS) is used to calculate the thermodynamic properties by accounting for these real gas effects are presented in Appendix \ref{subsubsec: Equation of state}.
-The P-R EOS belongs to a specific class of thermodynamic models for modelling the pressure of a gas as a function of temperature and density.
+The P-R EOS belongs to a specific class of thermodynamic models for modelling the pressure of a solvent as a function of temperature and density and which can be rewritten as a cubic function of the molar volume.
 
 	To determine the thermodynamic properties of a real gas, it is necessary to evaluate the departure function of the chosen equation of state for that property.
-As explained by \citet{Elliott2011}, the departure function is the difference between the actual value of a thermodynamic property of a real gas and its value if the gas were ideal under the same temperature and pressure conditions.
+As explained by \citet{Elliott2011}, the departure function describe the difference between the actual value of a thermodynamic property of a real gas and its value if the gas were ideal under the same temperature and pressure conditions.
 The ideal gas serves as a reference state to which the properties of real gases are compared.
@@
 The fluid properties near the critical point are unique and combine gas-like and liquid-like properties.
-The details of calculations are explained in the Appendix \ref{subsubsec: Fluid density}.
+The details of calculations are explained in Appendix \ref{subsubsec: Fluid density}.
 
@@
 Beyond the critical point, there is no divergence, but rather a peak in the heat capacity; the highest point of this peak identifies the Widom line (as discussed by \citet{Simeoni2010} and \citet{Banuti2019}).
+
+	Figure \ref{fig: SFE_Properties_h} represent how the specific enthalpy change with the operating conditions. The details of calculations are discussed in Appendix \ref{CH:Enthalpy}.
 
@@
 The correlation is applicable for the temperature range from the triple point to 1100 K and pressures up to 200 MPa.
-Figure \ref{fig: SFE_Properties_Thermal}.
-The presented figure show regions around the critical point where the singularity is present.
+Figure \ref{fig: SFE_Properties_Thermal} shows how the thermal conductivity of carbon dioxide change depending on the operating conditions.
 

### 2023-10-05 SFE_article_Parameter_Estimation/Sections/Qubic_EOS.tex
05.10

@@
 
-	%\label{CH: Thermodynamic_details}
+	\label{CH: Thermodynamic_details}
 
-	%subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}
+	subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}
 
-	An equation of state (EoS) is an algebraic relation between P, $v_m$, and T.
-Cubic equations of state are a specific class of thermodynamic models for modeling the pressure of a gas as a function of temperature and density and which can be rewritten as a cubic function of the molar volume.
-In general, the general cubic equation of state has a number of degrees of freedom equal to 2 + the number of components in the system (total flow rate, temperature, pressure and N-1 mole fractions).
-In some cases (primarily inlets to units), this is increased by 1 due to the removal of a constraint on the sum of mole fractions.
+	A cubic equation of state is a mathematical model used in the field of thermodynamics and fluid dynamics to describe the behavior of real gases and liquids.
+It is named "cubic" because it is characterized by a third-degree polynomial equation that relates the pressure, volume, and temperature of a substance.
+These equations are essential tools for understanding the phase behavior, properties, and thermodynamic processes of real substances, making them invaluable in various engineering and scientific applications.
+The cubic equation of state accounts for the deviations from ideal gas behavior, which is particularly important at high pressures and low temperatures, where real gases show significant departures from ideal behavior.
 
-	Equations of state are generally applied in the fields of physical chemistry and chemical engineering, particularly in the modeling of vapor–liquid equilibrium and chemical engineering process design.
-Following the work of \citet{Poling2001}, the general cubic equation of state is represented by the following equations:
+	The general cubic equation of state is typically written in the following form:
 
 	{\footnotesize
-	\begin{equation} \label{EQ: General_Qubic}
-		P = \frac{RT}{v_m-b} - \frac{\Theta \left( v_m - \eta \right)}{\left( v_m - b \right) \left(v_m^2 + \delta v_m + \epsilon \right) }
+	\begin{equation}
+		P = \frac{RT}{v_m-b} - \frac{a\alpha}{v_m^2 - ubv_m + wb^2}
 	\end{equation}
@@
 
-	where, depending upon the model, the parameters $\Theta,~b,~\delta,~\epsilon$ may be constants, including zero, or they may vary with $T$ and / or composition.
-Thus, the distinctions among cubic EoS models for pure components are which of the parameters in Equation \ref{EQ: General_Qubic} are nonzero and how they are made to vary with $T$.
-A common notation for EOS is to use $\Theta(T)=a\alpha(T)$, where $\alpha(T_c) = 1$.
-Tables \ref{tab:Popular_Cubic_EoS} and \ref{tab:Popular_Cubic_EoS_alpha} give relations among the Equation \ref{EQ: General_Qubic} parameters for several common cubic EoS.
+	Where P is the pressure of the substance, $v_m$ is the molar volume (volume per mole) of the substance, T is the absolute temperature of the substance., u and w are integers that differ rom an equation to another, R is the universal gas constant, a and b are substance-specific parameters known as the Van der Waals constants and $\omega$ is an acentric factor.
+
+	The Van der Waals constants, a and b, are empirical values that depend on the specific substance being modeled.
+These constants account for the molecular interactions (attractive forces represented by a) and the finite size of gas molecules (excluded volume represented by b).
+For different substances, a and b will have different values based on experimental data.
+
+	Several variations of the cubic equation of state exist, including the Van der Waals equation and the Redlich-Kwong equation, each with its own set of parameters and assumptions.
+Tables \ref{tab:Popular_Cubic_EoS} show parameters for popular cubic EoS.
 
@@
 		\adjustbox{width=\columnwidth}{%
-			\begin{tabular}{|c| c c c|} 
+			\begin{tabular}{|c| c c c c|} 
 				\hline
-				Eos & $\delta$ & $\epsilon$ & $\theta$ \\
+				EoS & u & w & a & b\\
 				\hline
-				van der Waals (1890) & 0 & 0 & a \\
-				Redlich and Kwong (1949) & b & 0 & $a / T^{0.5}$ \\
-				Peng and Robinson (1976) \cite{Peng1976} & 2b & $-b^2$ & $a\alpha(T_r) $ \\
+				van der Waals  & 0 & 0 & $\frac{27}{64} \frac{R^2T_c^2}{P_c}$ & $\frac{RT_c}{8P_c}$ \\
+				Redlich and Kwong & 1 & 0 & $0.42748 \frac{R^2T_c^{2.5}}{P_c}$ & $\frac{0.08664RT_c}{P_c}$ \\
+				Soave & 1 & 0 & $0.42748 \frac{R^2T_c^2}{P_c}$ & $\frac{0.08664RT_c}{P_c}$ \\
+				Peng and Robinson \cite{Peng1976} & 2 & -1 & $0.45724 \frac{R^2T_c^2}{P_c}$ & $\frac{0.07780T_c}{P_c}$\\
 				\hline
@@
 		\adjustbox{width=\columnwidth}{%
-			\begin{tabular}{|c| c|} 
+			\begin{tabular}{|c| c c|} 
 				\hline
-				Eos & $\alpha(T_r)$ \\
+				EoS & $\alpha$ & f($\omega$)\\
 				\hline
-				van der Waals (1890) & 1 \\
-				Redlich and Kwong (1949) & $1/\sqrt{T_r}$ \\
-				Peng and Robinson (1976) \cite{Peng1976} & $[1+(0.37464 + 1.54226 \omega - 0.2699\omega^2)(1-\sqrt{T_r})]^2$ \\
+				van der Waals  & - & - \\
+				Redlich and Kwong & $\frac{1}{\sqrt{T_r}}$ & - \\
+				Soave & $\left[ 1 + f(\omega) \left( 1-\sqrt{T_r} \right) \right]^2$ & 0.48+1.574$\omega$-0.176$\omega^2$\\
+				Peng and Robinson \cite{Peng1976} & $\left[ 1 + f(\omega) \left( 1-\sqrt{T_r} \right) \right]^2$ & 0.37464+1.54226$\omega$-0.26992$\omega^2$ \\
 				\hline
@@
 
-	Equation \ref{EQ: General_Qubic} can be written to obtain the compressibility as given by Equation \ref{EQ:Comp_EOS}.
+	The general cubic equation of state can be written in polynomial as presented by Equation \ref{EQ:Compressibility_Polynomial}.
+In a one-phase region, the fluid is described by one real root corresponding to the gas, liquid or supercritical phase.
+The gas-liquid mixture is present in the two-phase region, and two roots are found.
+The biggest root is assigned to the gas phase, and the smallest root corresponds to the liquid phase.
 
 	{\footnotesize
-	\begin{equation} \label{EQ:Comp_EOS}
-		Z = \frac{v_m}{v_m-b} - \frac{\left( \Theta /RT \right) v_m \left( v_m - \eta \right) }{\left( v_m - b \right) \left(v_m^2 + \delta v_m + \epsilon \right)}
+		\begin{equation}
+			\label{EQ:Compressibility_Polynomial}
+			Z^3 - (1+B-uB)Z^2+(A+wB^2-uB-uB^2)Z - AB - wB^2 - wB^3 = 0
+	\end{equation} }
+
+	where $A=\frac{a\alpha P}{R^2T^2}$ and $B=\frac{bP}{RT}$.
+
+	If the Peng-Robinson equation of state \citet{Peng1976} is used, the polynomial equation becomes
+
+	{\footnotesize
+	\begin{equation}
+		\label{EQ:Peng_Robinson_Polynomial}
+		Z^3 - (1-B)Z^2+(A-2B-3B^2)Z -(AB-B^2-B^3) = 0
+	\end{equation} }
+
+	For an ideal gas the compressibility factor is $Z = 1$ per definition.
+In many real world applications requirements for accuracy demand that deviations from ideal gas behaviour, i.e., real gas behaviour, be taken into account.
+The value of $Z$ generally increases with pressure and decreases with temperature.
+At high pressures molecules are colliding more often.
+This allows repulsive forces between molecules to have a noticeable effect, making the molar volume of the real gas ($v_m$) greater than the molar volume of the corresponding ideal gas $\left( \left(v_m\right)_{ideal~gas} = \frac{RT}{P} \right)$, which causes Z to exceed one.
+When pressures are lower, the molecules are free to move.
+In this case attractive forces dominate, making Z < 1.
+The closer the gas is to its critical point or its boiling point, the more Z deviates from the ideal case.
+
+	Numerical methods such as Newton-Raphson can be used to solve the polynomial equation to obtain the compressibility ${\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ at given temperature and pressure.
+Alternatively, the Cardano formula can be used to get the closed form solution of the Equation \ref{EQ:Compressibility_Polynomial}.
+Further details regarding the Cardano formula can be found in Appendix \ref{CH: Cardano}.
+
+	\subsubsection{Density of the fluid phase} \label{subsubsec: Fluid density}
+
+	The density of the fluid can be calculated from the real gas equation $\rho = \frac{P}{RTZ} \frac{1}{m_{CO2}}$.
+The local temperature can be obtain from the time evolution of governing equations, the pressure is consider to be constant along the system to be a know at any time.
+The local compressibility factor can be also computed if the local temperature and pressure are know.
+To obtain the density in terms of mass, molar mass of the solvent is taken into account.
+
+	\subsubsection{Heat capacity of the fluid phase} \label{subsubsec: Fluid heat capacity}
+	%	\noindent\textbf{Heat capacity of the fluid phase} \\
+
+	%The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}.
+The main steps in the derivation of ${\color{black}C_p}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ are presented below:
+	Following the work of \citet{Pratt2001}, it is assumed that the specific heat can be obtained as a sum of ideal gas contribution and a residual correction for non-ideal behaviour, as given by Equations \ref{eq: Cv_CO2} and \ref{eq: Cp_CO2}.
+
+	{\footnotesize
+		\begin{subequations}\begin{align}
+				{\color{black}C_v}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) & = {\color{black}C_v^{\text{I}}}\left({\color{black}T}(t,z),P(t)\right) + {\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) \label{eq: Cv_CO2}; \\
+				{\color{black}C_p}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) & = \underbrace{{\color{black}C_p^{\text{I}}}\left({\color{black}T}(t,z),P(t)\right)}_{\text{Eq.
+} \eqref{eq: Cp_I}} + \underbrace{{\color{black}C_p^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}_{\text{Eq.
+} \eqref{eq: Cp_R}}  \label{eq: Cp_CO2}.
+	\end{align}\end{subequations} }
+
+	${\color{black}C_v}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ and ${\color{black}C_p}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ are the specific heat of $CO_2$ at constant volume and pressure, respectively.
+
+	The ideal-gas contribution ${\color{black}C_v^{\text{I}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ and ${\color{black}C_p^{\text{I}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$, can be obtained based on heat-capacity data applicable to gases at low pressure.
+For $CO_2$, the ideal gas contribution to the specific heat at constant ${\color{black}P}(t)$, as function of ${\color{black}T}(t,z)$ is given by,
+
+	{\footnotesize
+		\begin{equation}
+			{\color{black}C_p^{\text{I}}}\left({\color{black}T}(t,z),P(t)\right) = {\color{black}C_{P0}} + {\color{black}C_{P1}}T(t,z) + {\color{black}C_{P2}}{\color{black}T}^2(t,z) + {\color{black}C_{P3}}{\color{black}T}^3(t,z) \label{eq: Cp_I}
+	\end{equation} }
+
+	where the coefficients of the expansion are ${\color{black}C_{P0}} = 22.26$, ${\color{black}C_{P1}} = 5.981 \times 10^{-2}$, ${\color{black}C_{P2}} = -3.501 \times 10^{-5}$, and ${\color{black}C_{P3}} = 7.469 \times 10^{-9}$, as given by \citet{Kyle1999}.
+
+	The correction term ${\color{black}C_p^{\text{R}}}\left({\color{black}T}(t,z){\color{black}P}(t)\right)$ at constant pressure ${\color{black}P}(t)$, can be defined by introducing  ${\color{black}C_p^{\text{I}}}({\color{black}T}(t,z)) - {\color{black}C_v^{\text{I}}}({\color{black}T}(t,z)) = {\color{black}R}$ and using the definition of ${\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z){\color{black}P}(t)\right)$.
+The general form of the correction term is given by Equation \ref{eq: Cp_R}
+
+	{\footnotesize	
+		\begin{align}
+			&{\color{black}C_p^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) = \underbrace{{\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}_{\text{Eq.
+}\eqref{eq: CvR}} \nonumber \\
+			&+ {\color{black}T}(t,z) \underbrace{\left(\cfrac{\partial {\color{black}P}(t)}{\partial {\color{black}T}}\right)_{{\color{black}v_m}(t,z)}}_{\text{Eq.
+} \eqref{eq: dPdT}} \underbrace{\left(\cfrac{\partial {\color{black}v_m}\left({\color{black}T}(t,z),{\color{black}P}(t)\right)}{\partial {\color{black}T}}\right)_{{\color{black}P}(t)}}_{\text{Eq.
+} \eqref{eq: dVdT}} - {\color{black}R}.
+\label{eq: Cp_R}
+	\end{align} }
+
+	%	The braced terms are obtained from the chosen equation of state and the compressibility definition ${\color{black}P}(t) {\color{black}v_m}({\color{black}T}(t,z),{\color{black}P}(t)) = {\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right){\color{black}R}{\color{black}T}(t,z)$.
+\\
+
+	For the partial derivative of the volume with respect to temperature ${\color{black}T}(t,z)$ at constant pressure ${\color{black}P}(t)$, we have
+
+	{\footnotesize
+		\begin{align}
+			\left( \cfrac{\partial {\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{\partial {\color{black}T}} \right)_{{\color{black}P}(t)} &= \cfrac{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) {\color{black}R}}{{\color{black}P}(t)} \nonumber \\
+			&+ \cfrac{{\color{black}R}{\color{black}T}(t,z)}{{\color{black}P}(t)} \underbrace{\left( \cfrac{\partial {\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{\partial {\color{black}T}} \right)_{{\color{black}P}(t)}}_{\text{Eq.
+}\eqref{eq: dZdT}} \label{eq: dVdT}
+	\end{align} }
+
+	with partial derivative of the compressibility factor with respect to temperature ${\color{black}T}(t,z)$ at constant pressure ${\color{black}P}(t)$
+
+	{\footnotesize
+		\begin{equation}
+			\left(\cfrac{\partial{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{\partial {\color{black}T}}\right)_{{\color{black}P}(t)} = \left(\cfrac{\partial \dfrac{{\color{black}P}(t) {\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}R}{\color{black}T}(t,z)}}{\partial {\color{black}T}}\right)_{{\color{black}P}(t)} \label{eq: dZdT}
+	\end{equation} }
+
+	Similarly, for the partial derivative of the pressure with respect to temperature at constant volume is :
+
+	{\footnotesize
+		\begin{equation}
+			\left(\cfrac{\partial {\color{black}P}(t)}{\partial {\color{black}T}}\right)_{{\color{black}v_m}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{black}Z}{\color{black}R}{\color{black}T}(t,z)}{{\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}}}{\partial{\color{black}T}}\right)_{{\color{black}v_m}(t,z)} \label{eq: dPdT}
+	\end{equation} }
+
+	The residual specific heat at constant volume is obtained, by definition, by using the residual internal energy
+
+	{\footnotesize
+		\begin{equation}
+			{\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z),{\color{black}P}(t)\right) = \left(\cfrac{\partial{\color{black}U^{\text{R}}}\left({\color{black}T}(t,z),{\color{black}P}(t)\right)}{\partial {\color{black}T}}\right)_{{\color{black}v_m}(t,z)} \label{eq: CvR}
+	\end{equation} }
+
+	\subsubsection{Departure functions for enthalpy calculations} \label{CH:Enthalpy}
+
+	In thermodynamics, a departure function is a concept used to calculate the difference between a real fluid's thermodynamic properties and those of an ideal gas, given a specific temperature and pressure.
+Common departure functions include those for enthalpy, entropy, and internal energy.
+These functions are used to calculate extensive properties, which are properties computed as a difference between two states.
+
+	To evaluate the enthalpy change between two points, $h(V_1,T_1)$ and $h(V_2,T_2)$, the enthalpy departure function between the initial volume $V_1$ and infinite volume at temperature $T_1$ is calculated.
+Then it is added to that the ideal gas enthalpy change due to the temperature change from $T_1$ to $T_2$, and finally subtract the departure function value between the final volume $V_2$ and infinite volume.
+
+	Departure functions are computed by integrating a function that depends on an equation of state and its derivative. The general form of the enthalpy equation is given by:
+
+	{\footnotesize
+		\begin{equation}
+			\frac{h^{id}-h}{RT} =\int_{v_m}^{\infty }\left(T\left({\frac{\partial Z}{\partial T}}\right)_{v_m}\right){\frac{dv_m}{v_m}} + 1-Z
 		\end{equation}
@@
 
-	When it is rewritten as the form to be solved when T and P are specified and Z is to be found analytically, it is
+	Here, $h^{id}$ represents the enthalpy of an ideal gas, $h$ is the enthalpy of a real fluid, $R$ is the universal gas constant, $T$ is temperature, $v_m$ is the molar volume, and $Z$ is the compressibility factor.
+
+	The integral in the equation is evaluated over the range of molar volumes from $v_m$ to infinity.
+The integral includes a term that depends on the derivative of the compressibility factor with respect to temperature, evaluated at the molar volume $v_m$.
+Finally, the term $1-Z$ is added to account for the deviation of the fluid's properties from those of an ideal gas.
+
+	The Peng–Robinson equation of state relates the three interdependent state properties pressure $P$, temperature $T$, and molar volume $v_m$.
+From the state properties ($P$, $v_m$, $T$), one may compute the departure function for enthalpy per mole (denoted $h$) as presented by \citet{Gmehling2019} or \citet{Elliott2011}:
+
+	{\footnotesize
+		\begin{equation}
+			h-h^{\mathrm {id} }=RT_c\left[T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right]
+		\end{equation}
+	}
 

### 2023-10-06 SFE_article_Parameter_Estimation/Sections/Qubic_EOS.tex
06.10

@@
 
-	subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}
+	\subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}
 
-	A cubic equation of state is a mathematical model used in the field of thermodynamics and fluid dynamics to describe the behavior of real gases and liquids.
-It is named "cubic" because it is characterized by a third-degree polynomial equation that relates the pressure, volume, and temperature of a substance.
-These equations are essential tools for understanding the phase behavior, properties, and thermodynamic processes of real substances, making them invaluable in various engineering and scientific applications.
-The cubic equation of state accounts for the deviations from ideal gas behavior, which is particularly important at high pressures and low temperatures, where real gases show significant departures from ideal behavior.
-
-	The general cubic equation of state is typically written in the following form:
+	A cubic equation of state serves as a mathematical model utilized in thermodynamics and fluid dynamics to depict the behavior of real gases and liquids.
+Its name, "cubic," from its characteristic feature—a third-degree polynomial equation that correlates the pressure, volume, and temperature of a substance.
+These equations constitute tools for comprehending the phase behavior, properties, and thermodynamic processes of actual substances, across various engineering and scientific applications.
+The cubic equation of state take into account deviations from ideal gas behavior, which are particularly important at high pressures and low temperatures, where real gases do not follow assumption of ideal gas.
 
@@
 
-	Where P is the pressure of the substance, $v_m$ is the molar volume (volume per mole) of the substance, T is the absolute temperature of the substance., u and w are integers that differ rom an equation to another, R is the universal gas constant, a and b are substance-specific parameters known as the Van der Waals constants and $\omega$ is an acentric factor.
+	In this equation, P denotes the pressure of the substance, $v_m$ represents the molar volume (volume per mole) of the substance, T stands for the absolute temperature of the substance, u and w are integers that vary from one equation to another, R symbolizes the universal gas constant, and a and b serve as substance-specific parameters known as Van der Waals constants.
+Additionally, $\omega$ denotes an acentric factor.
 
-	The Van der Waals constants, a and b, are empirical values that depend on the specific substance being modeled.
-These constants account for the molecular interactions (attractive forces represented by a) and the finite size of gas molecules (excluded volume represented by b).
-For different substances, a and b will have different values based on experimental data.
+	The Van der Waals constants, a and b, constitute empirical values contingent upon the particular substance being modeled.
+These constants factor in molecular interactions (represented by 'a') and the finite size of gas molecules (indicated by 'b').
+Different substances will possess distinct values for 'a' and 'b' based on experimental data.
 
@@
 
-	The general cubic equation of state can be written in polynomial as presented by Equation \ref{EQ:Compressibility_Polynomial}.
-In a one-phase region, the fluid is described by one real root corresponding to the gas, liquid or supercritical phase.
-The gas-liquid mixture is present in the two-phase region, and two roots are found.
-The biggest root is assigned to the gas phase, and the smallest root corresponds to the liquid phase.
+	The general cubic equation of state can be represented as a polynomial, as indicated in Equation \ref{EQ:Compressibility_Polynomial}.
+In a one-phase region, the fluid is characterized by a single real root, corresponding to the gas, liquid, or supercritical phase.
+In the two-phase region, a gas-liquid mixture exists, and two roots are identified.
+The larger root corresponds to the gas phase, while the smaller root pertains to the liquid phase.
 
@@
 
-	If the Peng-Robinson equation of state \citet{Peng1976} is used, the polynomial equation becomes
+	If the Peng-Robinson equation of state [\cite{Peng1976}] is used, the polynomial equation becomes
 
@@
 
-	For an ideal gas the compressibility factor is $Z = 1$ per definition.
-In many real world applications requirements for accuracy demand that deviations from ideal gas behaviour, i.e., real gas behaviour, be taken into account.
-The value of $Z$ generally increases with pressure and decreases with temperature.
-At high pressures molecules are colliding more often.
-This allows repulsive forces between molecules to have a noticeable effect, making the molar volume of the real gas ($v_m$) greater than the molar volume of the corresponding ideal gas $\left( \left(v_m\right)_{ideal~gas} = \frac{RT}{P} \right)$, which causes Z to exceed one.
-When pressures are lower, the molecules are free to move.
-In this case attractive forces dominate, making Z < 1.
-The closer the gas is to its critical point or its boiling point, the more Z deviates from the ideal case.
+	For an ideal gas, the compressibility factor is defined as $Z = 1$.
+In many real-world applications, deviations from ideal gas behavior, needs to be taken into account to have a precise model describing a physical phenomena.
+The value of $Z$ typically increases with pressure and decreases with temperature.
+At elevated pressures, molecules collide more frequently, allowing repulsive forces between molecules to influence the molar volume of the real gas ($v_m$) to surpass that of the corresponding ideal gas $\left( \left(v_m\right)_{ideal~gas} = \frac{RT}{P} \right)$, resulting in $Z$ exceeding one.
+Analogously, at lower pressures, molecules move freely, with attractive forces predominating, leading to $Z < 1$.
 
@@
 
-	%The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}.
-The main steps in the derivation of ${\color{black}C_p}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ are presented below:
-	Following the work of \citet{Pratt2001}, it is assumed that the specific heat can be obtained as a sum of ideal gas contribution and a residual correction for non-ideal behaviour, as given by Equations \ref{eq: Cv_CO2} and \ref{eq: Cp_CO2}.
+	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state,  under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}:
+
+	{\footnotesize
+	\begin{align}
+		C_v &= C_v^{id} + C_v^R \\
+		C_p &= C_p^{id} + C_p^R
+	\end{align}}
+
+	The ideal-gas contribution is found using heat-capacity data applicable to gases at very low pressures, which are available in many thermodynamics textbooks in the polynomial form, such as $C_p^{id}(T) = A + BT + CT^2 + DT^3$.
+
+	where the coefficients of the expansion are ${\color{black}C_{P0}} = 22.26$, ${\color{black}C_{P1}} = 5.981 \times 10^{-2}$, ${\color{black}C_{P2}} = -3.501 \times 10^{-5}$, and ${\color{black}C_{P3}} = 7.469 \times 10^{-9}$, as given by \citet{Kyle1999}.
+
+	To calculate the residual contribution, we use the standard equation found in many textbooksr4•6 l for the residual internal energy derived from the Peng-Robinson equation of state
+
+	%Following the work of \citet{Pratt2001}, it is assumed that the specific heat can be obtained as a sum of ideal gas contribution and a residual correction for non-ideal behaviour, as given by Equations \ref{eq: Cv_CO2} and \ref{eq: Cp_CO2}.
 

### 2023-10-08 SFE_article_Parameter_Estimation/Article_Model_Parameters.tex
05.10
08.10

@@
 The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
-This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and an initial state estimate.
-The missing model parameters are obtained by solving the maximum likelihood estimation based on experimental yield data under the normal error assumption.
+This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient.
+The missing model parameters and the initial state are obtained by solving the maximum likelihood estimation based on experimental yield data under the normal error assumption.
 A set of laboratory experiments was performed in a partially filled extractor with a fixed bed operated under multiple constant operating conditions: $40~^\circ C$ / $200$ bar, $50~^\circ C$ / $200$ bar, $40~^\circ C$ / $300$ bar, and $50~^\circ C$ / $300$ bar.
@@
 \subfile{Sections/Qubic_EOS}
-\subfile{Sections/Thermodynamic_details}
+%\subfile{Sections/Thermodynamic_details}
 

### 2023-10-08 SFE_article_Parameter_Estimation/Sections/Model.tex
08.10

@@
 Although the particle size distribution and void fraction of the solid phase may change along the extractor, they are assumed to remain constant in time.
-Furthermore, the thermodynamic pressure is assumed to be constant along the device due to the Low-Mach number condition, as previously discussed.
+Furthermore, the thermodynamic pressure is assumed to be constant along the device as presented by Equation \ref{EQ: Pressure_Velocity}.
 The amount of solute in the solvent is considered negligible, resulting in the fluid phase being described as pseudo-homogeneous, and its properties are assumed to be the same as the solvent.
@@
 			If the value of enthalpy is known from the time evolution and pressure can be measured, then the Equation \ref{EQ:Enthalpy_root} can be solved for the temperature to recover the temperature profile.
-By applying the departure functions to Peng-Robinson equation of state, the relation \ref{EQ:Enthalpy_root} can be expressed directly through Equation \ref{EQ:Enthalpy_PR} as presented in \ref{CH:Enthalpy} or given by \citet{Gmehling2019}.
+An equation for the enthalpy change for Peng-Robinson EoS can be expressed through Equation \ref{EQ:Enthalpy_PR}.
+More details can be found in Appendix \ref{CH:Enthalpy} or given by \citet{Gmehling2019}.
 
@@
 Under such conditions, the term $\partial {\color{black}P}/\partial t$ can be approximated by an ordinary differential equation, which describes the instantaneous change of pressure in the system.
-The pressure in the system is considered a state variable, while the pressure in the new time-step is considered a control variable.
+The pressure (P) in the system is considered a state variable, while the pressure in the new time-step ($P_{in}$) is considered a control variable.
 
@@
 Every SFE system needs some time to reach the desired operating conditions but the solute diffuses from solid phase to the fluid phase already at the preparation stage.
-For instance, a pump introduce more and more fluid to the extractor to increase the pressure, which makes the fluid present already in that vessel to moves internally hence the solute in the fluid phase is non-uniformly distributed.
+For instance, a pump introduce more fluid to the extractor to increase the pressure, which makes the fluid present already in that vessel to moves internally hence the solute in the fluid phase is non-uniformly distributed.
 Some conclusions can be drawn from the analysis of the initial part of each yield curve obtained from the laboratory (Figure \ref{fig: estimation_results}).

### 2023-10-08 SFE_article_Parameter_Estimation/Sections/Saturation.tex
08.10

@@
 
-%	To mimic that not all solute might be obtained at specific operating conditions, the coefficient ${\color{orange} \gamma}$ is introduced to limit the available oil.
-The ${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ describe the reverse logistic function, which is equal to unity above the ${\color{magenta} c_{lim}}$, the saturation concentration, and equal to zero, below the ${\color{magenta} c_{lim}}$.
-The ${\color{orange} \gamma}$ parameter multiply the solute concentration term in solid phase in the concentration gradient.
-As the concentration of solute decrease, it can reach the limiting value ${\color{magenta} c_{lim}}$ when the ${\color{orange} \gamma}$ goes to zero and stop the extraction from the solid.
+%	To mimic that not all solute might be obtained at specific operating conditions, the coefficient ${\color{black} \gamma}$ is introduced to limit the available oil.
+The ${\color{black} \gamma}({\color{black} c_s} (t,z))$ describe the reverse logistic function, which is equal to unity above the ${\color{black} c_{lim}}$, the saturation concentration, and equal to zero, below the ${\color{black} c_{lim}}$.
+The ${\color{black} \gamma}$ parameter multiply the solute concentration term in solid phase in the concentration gradient.
+As the concentration of solute decrease, it can reach the limiting value ${\color{black} c_{lim}}$ when the ${\color{black} \gamma}$ goes to zero and stop the extraction from the solid.
 %			
@@
 %		\begin{equation}
-%			{\color{orange} \gamma}({\color{blue} c_s} (t,z)) = \cfrac{1}{1+\exp \left( -{\color{magenta} k_{lim}} \left( {\color{blue} c_s} (t,z) - {\color{magenta} c_{lim}} \right) \right) }
+%			{\color{black} \gamma}({\color{black} c_s} (t,z)) = \cfrac{1}{1+\exp \left( -{\color{black} k_{lim}} \left( {\color{black} c_s} (t,z) - {\color{black} c_{lim}} \right) \right) }
 %			\label{EQ: C_sat_function}
@@
 %			
-%	where ${\color{magenta} k_{lim}}$ describe the curvature of the $\gamma$ function, and it is defined as ${\color{magenta} k_{lim}} = 1$.
-%In the limit when $ {\color{magenta} k_{lim}}\rightarrow+\infty$ become a step function.
-If the ${\color{magenta} k_{lim}}$ is to high, the gradient of the ${\color{orange} \gamma}$ function become high, or goes to infinity, which might cause difficulties for a gradient-based optimizer.
-%	The ${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ gamma function is visualised on \ref{fig: Gamma_function}.
+%	where ${\color{black} k_{lim}}$ describe the curvature of the $\gamma$ function, and it is defined as ${\color{black} k_{lim}} = 1$.
+%In the limit when $ {\color{black} k_{lim}}\rightarrow+\infty$ become a step function.
+If the ${\color{black} k_{lim}}$ is to high, the gradient of the ${\color{black} \gamma}$ function become high, or goes to infinity, which might cause difficulties for a gradient-based optimizer.
+%	The ${\color{black} \gamma}({\color{black} c_s} (t,z))$ gamma function is visualised on \ref{fig: Gamma_function}.
 %			
@@
 %					ymin = -0.5, ymax = 1.5,
-%					xlabel = {${\color{blue} c_s}(t,z)[kg/m^3]$},
-%					ylabel = {${\color{orange} \gamma}({\color{blue} c_s}(t,z))[-]$}]
+%					xlabel = {${\color{black} c_s}(t,z)[kg/m^3]$},
+%					ylabel = {${\color{black} \gamma}({\color{black} c_s}(t,z))[-]$}]
 %					\addplot[
@@
 %					
-%					\addlegendentry{${\color{orange} \gamma}({\color{blue} c_s} (t,z))$}
-%					\addlegendentry{${\color{magenta} c_{lim}}$}
+%					\addlegendentry{${\color{black} \gamma}({\color{black} c_s} (t,z))$}
+%					\addlegendentry{${\color{black} c_{lim}}$}
 %				\end{axis}
@@
 %			\end{tikzpicture}
-%			\caption{${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ function under assumption of ${\color{magenta} c_{lim}}=50~[kg/m^3]$}
+%			\caption{${\color{black} \gamma}({\color{black} c_s} (t,z))$ function under assumption of ${\color{black} c_{lim}}=50~[kg/m^3]$}
 %			\label{fig: Gamma_function}
@@
 
-	Following the idea of the Broken-and-Intact Cell (BIC) model presented by \citet{Sovova2017}, the internal diffusion coefficient ${\color{orange}D_i}$ is consider to be a product of the reference value of ${\color{orange}D_i^R}$ and the exponential decay function ${\color{orange} \gamma}$, as given by Equation \ref{EQ: C_sat_function}.
+	Following the idea of the Broken-and-Intact Cell (BIC) model presented by \citet{Sovova2017}, the internal diffusion coefficient ${\color{black}D_i}$ is consider to be a product of the reference value of ${\color{black}D_i^R}$ and the exponential decay function ${\color{black} \gamma}$, as given by Equation \ref{EQ: C_sat_function}.
 
@@
 		\begin{equation}
-			{\color{orange}D_i} = {\color{orange}D_i^R} {\color{orange} \gamma}({\color{blue} c_s} (t,z)) = {\color{orange}D_i^R} \exp\left( {\color{magenta}\Upsilon} \left( 1-\cfrac{{\color{blue} c_s} (t,z) }{{\color{magenta}c_{s0}}} \right) \right) \label{EQ: C_sat_function}
+			{\color{black}D_i} = {\color{black}D_i^R} {\color{black} \gamma}({\color{black} c_s} (t,z)) = {\color{black}D_i^R} \exp\left( {\color{black}\Upsilon} \left( 1-\cfrac{{\color{black} c_s} (t,z) }{{\color{black}c_{s0}}} \right) \right) \label{EQ: C_sat_function}
 		\end{equation} }
 
-	where the ${\color{magenta}\Upsilon}$ describe the curvature of the decay function. The final form of the extraction kinetic Equation is given by equation \ref{Model_kinetic}.
+	where the ${\color{black}\Upsilon}$ describe the curvature of the decay function. The final form of the extraction kinetic Equation is given by Equation \ref{Model_kinetic}.
 
@@
 			\label{Model_kinetic}
-				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i^R}({\color{blue}T}(t,z), {\color{red}P}(t)) {\color{orange} \gamma}({\color{blue} c_s} (t,z)) }{{\color{magenta} \mu l^2} } \left({\color{blue}{\color{blue} c_s} }(t,z)  - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
+				{\color{black}r_e}(t,z) = -\cfrac{{\color{black}D_i^R}({\color{black}T}(t,z), {\color{black}P}(t)) {\color{black} \gamma}({\color{black} c_s} (t,z)) }{{\color{black} \mu l^2} } \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right)
 		\end{equation} }
@@
 The diffusion of the solute from a particle's core takes more time compared to the diffusion of the solute located close to the outer surface, considering that the internal diffusion coefficient decay as the concentration of the solute in the solid decrease.
-As the value of the ${\color{blue}c_s}$ decrease over time, the exponential term approach unity and $\lim_{ {\color{blue}c_s} \rightarrow 0} {\color{orange}D_i} =  {\color{orange}D_i^R}$.
-${\color{orange}D_i^R}$ can be interpreted as the internal diffusion coefficient at vanishing gradient.
+As the value of the ${\color{black}c_s}$ decrease over time, the exponential term approach unity and $\lim_{ {\color{black}c_s} \rightarrow 0} {\color{black}D_i} =  {\color{black}D_i^R}$.
+${\color{black}D_i^R}$ can be interpreted as the internal diffusion coefficient at vanishing gradient.
 
-	Alternatively, the decay function ${\color{orange}\gamma}$ can be consider with respect to the Shrinking Core model presented by \citet{Goto1996}, where the particle radius change as the amount of solute in the solid phase decrease.
+	Alternatively, the decay function ${\color{black}\gamma}$ can be consider with respect to the Shrinking Core model presented by \citet{Goto1996}, where the particle radius change as the amount of solute in the solid phase decrease.
 As the particle size decrease due to dissolution, the diffusion path increase which makes the diffusion slower and reduce the value of a diffusion coefficient.

### 2023-10-10 SFE_article_Parameter_Estimation/Article_Model_Parameters.tex
10.10

@@
 A first-principle process model was developed based on governing equations.
-Based on the literature review, the extraction kinetic model was selected and combined with the general mass balance equations.
+As a result of the literature review, the extraction kinetic model was selected and combined with the general mass balance equations.
 The values of unknown parameters in the process model were obtained by parameter estimation.
-The yield data from the experiments were compared against the yield data generated by the model.
+The yield data from the experiments were compared against the yield generated by the model.
 The IPOPT solver was used to solve the maximum likelihood estimation.
@@
 
-\iffalse
-\newpage
-\begin{table*}[p]
-		\caption{Notation}
-		\label{tab::symbols}
-		\begin{tabular}{ |c|l|c| } 
-			\hline
-			Symbol 		& 	Description 							& Unit 						\\ \hline
-			$A$			&	cross-section							& $m^2$ 					\\ \hline
-			$c$			&	concentration in fluid phase			& $kg ~ m^{-3}$				\\ \hline
-			$Cp$		&	specific heat of the fluid				& $J ~ mol^{-1} ~ K^{-1}$ 	\\ \hline
-			$Cp_s$		&	specific heat of the solid				& $J ~ mol^{-1} ~ K^{-1}$ 	\\ \hline
-			$D_e^M$		&	axial mass diffusion coefficient		& $m^2 ~ s^{-1}$			\\ \hline
-			$D_e^T$		&	axial heat diffusion coefficient		& $m^2 ~ s^{-1}$			\\ \hline
-			$Di$		&	internal diffusion coefficient			& $m^2 ~ s^{-1}$			\\ \hline
-			$dp$		&	particle diameter						& $m$						\\ \hline
-			$F(t)$		&	mass flow-rate							& $kg ~ s^{-1}$				\\ \hline
-			$km$		&	partition coefficient					& $[-]$						\\ \hline
-			$k^T$		&	thermal conductivity					& $W ~ m^{-1} ~ K^{-1}$		\\ \hline
-			$l$			&	characteristic dimension				& $m$						\\ \hline
-			$L$			&	total length of the bed					& $m$						\\ \hline
-			$m$			&	mass of the oil in solid phase			& $kg$						\\ \hline
-			$m_0$		&	initial mass of the oil in solid phase	& $kg$						\\ \hline
-			$M_{CO_2}$	&	molecular mass of CO2					& $mol ~ kg^{-1}$			\\ \hline
-			$Np$		&	number of model parameters and control variables & $[-]$			\\ \hline
-			$N_{\theta}$&	number of model parameters				& $[-]$						\\ \hline
-			$Nu$		&	number of control variables				& $[-]$						\\ \hline
-			$Nz$		&	number of grid points in z-direction	& $[-]$						\\ \hline
-			$p$			&	vector of model parameters and control variables	& $[-]$			\\ \hline
-			$P(t)$		&	pressure								& $bar$						\\ \hline
-			$Pe$		&	Peclet's number							& $[-]$						\\ \hline
-			$q$			&	concentration in solid phase			& $kg ~ m^{-3}$				\\ \hline
-			$R$			&	gas constant							& $J ~ K^{-1} ~ mol^{-1}$	\\ \hline
-			$Re$		&	Reynolds number							& $[-]$						\\ \hline
-			$t$			&	time									& $s$						\\ \hline
-			$T$			&	temperature								& $K$						\\ \hline
-			$T_0$		&	initial temperature						& $K$						\\ \hline
-			$V$			&	volume of the extractor					& $m^3$						\\ \hline
-			$y$			&	yield	 								& $[-]$						\\ \hline
-			$z$			&	length									& $m$						\\ \hline
-			$Z$			&	compressibility	factor					& $[-]$						\\ \hline
-			$\epsilon$	&	void fraction							& $[-]$						\\ \hline
-			$\rho$		&	density of the fluid					& $kg ~ m^{-3}$				\\ \hline
-			$\rho_s$	&	solid density							& $kg ~ m^{-3}$				\\ \hline
-			$\mu$		&	shape coefficient						& $[-]$						\\ \hline
-			$\theta$	&	vector of model parameters				& $[-]$						\\ \hline
-			$\eta$		&	viscosity								& $cP$						\\ \hline				
-						& 											&							\\ \hline			
-		 	Subscript	& 											&							\\ \hline
-			$0$			&	initial conditions						& $[-]$						\\ \hline
-			$^*$		&	equilibrium conditions					& $[-]$						\\ \hline							
-		\end{tabular}
-\end{table*}
-\fi
 \end{document}

### 2023-10-10 SFE_article_Parameter_Estimation/Sections/Results.tex
10.10

@@
 	\label{CH: Results}
+
+	 %and the concentration profiles, which correspond for the optimized solution for each experiments, are presented on Figure \ref{fig: estimation_results_profiles} in Appendix \ref{CH: Profiles}.
 
@@
 	 The parameters obtained from solving the optimization problem can be found in Table \ref{tab: Estimation_results}.
-
-    \begin{figure*}[!h]
-    	\centering
-    	\begin{subfigure}[b]{\columnwidth}
-    		\centering
-    		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
-    		\caption{Experiment at $40~^\circ C$ and 200 bar}
-    	\end{subfigure}
-    	\begin{subfigure}[b]{\columnwidth}
-    		\centering
-    		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
-    		\caption{Experiment at $50~^\circ C$ and 200 bar}
-    	\end{subfigure}
-    	\hfill
-    	\begin{subfigure}[b]{\columnwidth}
-    		\centering
-    		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
-    		\caption{Experiment at $40~^\circ C$ and 300 bar}
-    	\end{subfigure}
-    	\begin{subfigure}[b]{\columnwidth}
-    		\centering
-    		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
-    		\caption{Experiment at $50~^\circ C$ and 300 bar}
-    	\end{subfigure}
-    	\caption{Results of parameter estimation}
-    	\label{fig: estimation_results}
-    \end{figure*}
-
-	 %and the concentration profiles, which correspond for the optimized solution for each experiments, are presented on Figure \ref{fig: estimation_results_profiles} in Appendix \ref{CH: Profiles}.
 
@@
 	The Figure \ref{fig:Di_upsilon_res} shows how the internal diffusivity ${\color{black}D_i}$ (Equation \ref{EQ: C_sat_function}) as a function of the solute concentration in the solid phase at different operating conditions.
-The higher the density, the higher solubility according to \citet{Shojaie2010}, which results in higher values of the internal diffusion coefficient and larger curvature of ${\color{black}D_i}$ function.
+The higher the density, the higher solubility according to \citet{Shojaie2010}, which results in higher values of the internal diffusion coefficient and steeper curvature of ${\color{black}D_i}$ function.
 
@@
 This observation suggests that the process model could be further simplified by neglecting the diffusion term.
-Nevertheless, such a simplification has not been introduced in this work.
 	\citet{Chung1968} presented an idea for a relationship between the Peclet (indirectly the mass diffusion coefficient) and Reynolds numbers.
@@
 	The initial state estimation resulted in values of $\tau$ in the range from 0.69 to 0.76.
-These values are relatively similar to each other.
-In the equipment used in this experiment, around 30\% of the solute was extracted to the fluid phase during the preparation period.
+In the equipment used in this experiment, around 25\%-30\% of the solute was extracted to the fluid phase during the preparation period.
 
@@
 The noisiest dataset corresponds to $50~^\circ C$ / 200 bar when $\sigma^2\approx0.12$.
-All values of $\sigma^2$ are relatively low, suggesting the mathematical model can mimic the physical system up to the noise coming from the experiment.
+All values of $\sigma^2$ are relatively low, suggesting the mathematical model can mimic the physical system.
 

### 2023-10-11 SFE_article_Sensitivity_Analysis/Article_Model_Parameters.tex
11.10

@@
 \begin{keywords}
-Supercritical extraction \sep Parameter estimation \sep Mathematical modelling
+Supercritical extraction \sep Sensitivity analysis \sep Mathematical modelling
 \end{keywords}
@@
 \subsection{Governing equations} \label{CH:Governing_equations_chapter}
-The governing equation \footnote{For the sake of clarity of the process model, different colors have been used in the equations to indicate: 
-	{\color{red}control variables},
-	{\color{blue}state variables},
-	{\color{orange}variables} and
-	{\color{magenta}parameters}.} for a quasi-one-dimensional compressible flow in Cartesian coordinates can be found in the Appendix \ref{CH: Gouverning equations} and in the work of \citet{Anderson1995}.
-Quasi-one-dimensional flow is a fluid flow characterized by the assumption that the flow properties remain uniform across any given cross-section of the flow.
-This assumption is made when there is a variation in the cross-sectional area of the flow channel, such as an irregular shape or partial filling of an extractor.
-In such cases, the flow is considered to be quasi-one-dimensional because the velocity and other flow properties are assumed to vary only in the direction of flow.
-
-The quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates are given by Equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_3}.
-The derivation of these Equations are presented in Appendix \ref{CH: Gouverning equations}.
-
-{\footnotesize
-	\begin{align}
-		\label{EQ: CompressibleEuler_1}
-		\cfrac{\partial \left( {\color{orange}\rho_f} {\color{magenta}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{orange}\rho_f} {\color{magenta}A_f}(z) v \right)}{\partial z} &= 0 \\
-		\cfrac{\partial \left( {\color{orange}\rho_f} v {\color{magenta}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{orange}\rho_f} {\color{magenta}A_f}(z) v^2 \right)}{\partial z} &= -{\color{magenta}A_f}(z) \cfrac{\partial {\color{blue}P}}{\partial z} \label{EQ: CompressibleEuler_2} \\
-		\cfrac{\partial \left( {\color{orange}\rho_f} {\color{blue}e} {\color{magenta}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{orange}\rho_f} {\color{magenta}A_f}(z) v {\color{blue}e}\right)}{\partial z} &= -{\color{blue}P}\cfrac{\left( {\color{magenta}A_f}(z) v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial {\color{blue}T}}{\partial z} \right)
-		\label{EQ: CompressibleEuler_3}
-	\end{align}  
-}
-
-where ${\color{orange}\rho_f}$ is the density of the fluid, ${\color{magenta}A_f}(z)$ is the function which describe change of the cross-section, $v$ is the velocity, ${\color{blue}P}$ is the total pressure, ${\color{blue}e}$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
-
-Based on governing equations, the small discontinuity (defined as $\delta$) in flow properties, shown in Figure \ref{fig: Discontinuity_slow_flow}, can be analysed.
-The analysis follows the work of \citet{Schreier1982}.
-
-\begin{figure}[!h]
-	\centering
-	\resizebox{0.95\columnwidth}{!}{%
-		\begin{tikzpicture}[]
-			\draw (0,2) -- (9,2);	% Top line
-			\draw (0,0) -- (9,0); 	% Bottom line
-			\draw (4.5,0) -- (4.5,2); 	% Bottom line
-			\node at (4,1.5) {${\color{orange}\rho_f}$};
-			\node at (5.5,1.5) {${\color{orange}\rho_f}+\delta{\color{orange}\rho_f}$};
-			\node at (4,1.0) {${\color{blue}P}$};
-			\node at (5.5,1.0) {${\color{blue}P}+\delta {\color{blue}P}$};
-			\node at (4,0.5) {${\color{blue}T}$};
-			\node at (5.5,0.5) {${\color{blue}T}+\delta {\color{blue}T}$};
-			\node at (1,1.0) {$v \rightarrow$};
-			\node at (8,1.0) {$v + \delta v \rightarrow$};
-	\end{tikzpicture} }
-	\caption{Small discontinuity in one-dimensional flow}
-	\label{fig: Discontinuity_slow_flow}
-\end{figure}
-
-The discontinuity is presumed to be at rest relative, and the balance equations become
-
-{\footnotesize
-	\begin{align*}
-		&{\color{orange}\rho_f} \delta v + v \delta {\color{orange}\rho_f} + \delta {\color{orange}\rho_f} \delta v = 0 \\
-		&\delta {\color{blue}P} = \delta v \delta {\color{orange}\rho_f}
-	\end{align*}
-}
-
-These relations are equally valid if the two regions are separated by a region of finite width rather than a discontinuity.
-
-{\footnotesize
-	\begin{equation*}
-		\lim_{{\color{orange}\rho_f} v \rightarrow 0} {\color{orange}\rho_f} \delta v + v \delta {\color{orange}\rho_f} + \delta {\color{orange}\rho_f} \delta v = 0 / \delta {\color{orange}\rho_f} \rightarrow \cfrac{d v}{d {\color{orange}\rho_f}} = - \cfrac{v}{{\color{orange}\rho_f}}
-	\end{equation*}
-}
-
-By combining the momentum equation with the above equation, we get
-
-{\footnotesize
-	\begin{equation} \label{EQ: Pressure_Velocity}
-		\cfrac{d v}{d {\color{orange}\rho_f}} = - \cfrac{d v}{d{\color{blue}P}} \cfrac{d {\color{blue}P}}{d {\color{orange}\rho_f}} = -\cfrac{1}{\rho v} \cfrac{d{\color{blue}P}}{d{\color{orange}\rho_f}} = -\cfrac{v}{{\color{orange}\rho_f}}
-	\end{equation}
-}
-
-Suppose the flow is presumed to be isentropic, $d{\color{blue}P}/d{\color{orange}\rho_f} = c^2$, so $v^2=c^2$, where $c$ is the speed of sound.
-This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow.
-Moreover, if the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic which leads to $\partial {\color{orange}\rho_f} / \partial {\color{blue}P} \approx 0$.
-In other words, the small changes in pressure due to flow velocity changes do not change the density.
-This has a secondary effect -- the speed of sound in the fluid is $\partial {\color{blue}P}/\partial {\color{orange}\rho_f} = \infty$ in this instance.
-So there is an infinite speed of sound, which makes the equations elliptic in nature.
-It can be deduced that at the isothermal conditions, the density in the system propagates with the same speed as pressure since they are both connected through the equation of state.
-The details of the Mach-number analysis are presented in Appendix \ref{CH:Low_Mach_chapter}.
+\subfile{Sections/Gouverning_equation}
 
@@
 
-\clearpage \appendix \label{appendix}
-\section{Appendix} 
-\subsection{Thermodynamic}
-\subfile{Sections/Thermodynamic_details}
+%\clearpage \appendix \label{appendix}
+%\section{Appendix} 
+%\subsection{Thermodynamic}
+%\subfile{Sections/Qubic_EOS}
 
-\subsection{Governing equations}
-\subfile{Sections/Gouverning_equation_derivation}
+%\subsection{Governing equations}
+%\subfile{Sections/Gouverning_equation_derivation}
 
-\subsection{Low Mach number expansion} \label{CH:Low_Mach_chapter}
+%\subsection{Low Mach number expansion} \label{CH:Low_Mach_chapter}
 %\subfile{Sections/Low_mach_number_expansion}
-\subfile{Sections/Low_mach_number_expansion_imp}
+%\subfile{Sections/Low_mach_number_expansion_imp}
 
-\subsection{Bayes theorem} \label{CH: Bayes}
-\subfile{Sections/Bayes_Theorem}
+%\subsection{Bayes theorem} \label{CH: Bayes}
+%\subfile{Sections/Bayes_Theorem}
 
-\subsection{Cardano's Formula} \label{CH: Cardano}
-\subfile{Sections/Cardano}
+%\subsection{Cardano's Formula} \label{CH: Cardano}
+%\subfile{Sections/Cardano}
 
-\subsection{Initial and boundary conditions} \label{CH: IC_BC}
-\subfile{Sections/IC_BC}
+%\subsection{Initial and boundary conditions} \label{CH: IC_BC}
+%\subfile{Sections/IC_BC}
 
@@
 
-\subsection{Solid density measurement} \label{CH: Solid_Density_Measurment}
+%\subsection{Solid density measurement} \label{CH: Solid_Density_Measurment}
 
-\begin{figure}[!h]
-	\centering 
-	\includegraphics[trim=2cm 6cm 4cm 0cm, clip,width=\columnwidth]{Sections/ultraReportT5.pdf}
-	\caption{The result of solid density measurement}
-\end{figure}
+%\begin{figure}[!h]
+%	\centering 
+%	\includegraphics[trim=2cm 6cm 4cm 0cm, clip,width=\columnwidth]{Sections/ultraReportT5.pdf}
+%	\caption{The result of solid density measurement}
+%\end{figure}
 
-{\footnotesize
-	\begin{equation*}
-		\rho_s^{ave} = \frac{1.2585+1.2582+1.2561+1.2546+1.2555}{5} = 1.25658 [g/cc]
-	\end{equation*}
-}
+%{\footnotesize
+%	\begin{equation*}
+%		\rho_s^{ave} = \frac{1.2585+1.2582+1.2561+1.2546+1.2555}{5} = 1.25658 [g/cc]
+%	\end{equation*} }
 
-\subsection{Porosity Calculations} \label{CH: Porosity}
-\subfile{Sections/Porosity}
+%\subsection{Porosity Calculations} \label{CH: Porosity}
+%\subfile{Sections/Porosity}
 

### 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Gouverning_equation.tex
11.10

--- 2023-10-10 SFE_article_Parameter_Estimation/Article_Model_Parameters.tex
@@
-% ---------------------------------------------------------------
-% Preamble
-% ---------------------------------------------------------------
-%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}
-\documentclass[a4paper,fleqn]{cas-dc}
-%\documentclass[a4paper]{cas-dc}
-%\documentclass[a4paper]{cas-sc}
-% ---------------------------------------------------------------
-% Make margins bigger to fit annotations. Use 1, 2 and 3. TO be removed later
-%\paperwidth=\dimexpr \paperwidth + 6cm\relax
-%\oddsidemargin=\dimexpr\oddsidemargin + 3cm\relax
-%\evensidemargin=\dimexpr\evensidemargin + 3cm\relax
-%\marginparwidth=\dimexpr \marginparwidth + 3cm\relax
-% -------------------------------------------------------------------- 
-% Packages
-% --------------------------------------------------------------------
-% Figure packages
-\usepackage{graphicx}
-\usepackage{float}
-\restylefloat{table}
-\usepackage{adjustbox}
-% Text, input, formatting, and language-related packages
-\usepackage[T1]{fontenc}
-\usepackage{subcaption}
+\documentclass[../Article_Model_Parameters.tex]{subfiles}
+\graphicspath{{\subfix{../Figures/}}}
+\begin{document}
 
-\usepackage{csvsimple}
-
-% TODO package
-\usepackage[bordercolor=gray!20,backgroundcolor=blue!10,linecolor=black,textsize=footnotesize,textwidth=1in]{todonotes}
-\setlength{\marginparwidth}{1in}
-% \usepackage[utf8]{inputenc}
-% \usepackage[nomath]{lmodern}
-
-% Margin and formatting specifications
-%\usepackage[authoryear]{natbib}
-\usepackage[sort]{natbib}
-\setcitestyle{square,numbers}
-
- %\bibliographystyle{cas-model2-names}
-
-\usepackage{setspace}
-\usepackage{subfiles} % Best loaded last in the preamble
-
-% \usepackage[authoryear,longnamesfirst]{natbib}
-
-% Math packages
-\usepackage{amsmath, amsthm, amssymb, amsfonts, bm, nccmath, mathdots, mathtools, bigints, ulem}
-
-\usepackage{tikz}
-\usepackage{pgfplots}
-\usetikzlibrary{shapes.geometric,angles,quotes,calc}
-
-\usepackage{placeins}
-
-\usepackage[final]{pdfpages}
-
-% --------------------------------------------------------------------
-% Packages Configurations
-\usepackage{enumitem}
-% --------------------------------------------------------------------
-% (General) General configurations and fixes
-\AtBeginDocument{\setlength{\FullWidth}{\textwidth}}	% Solves els-cas caption positioning issue
-\setlength{\parindent}{20pt}
-%\doublespacing
-% --------------------------------------------------------------------
-% Other Definitions
-% --------------------------------------------------------------------
-\graphicspath{{Figures/}}
-% --------------------------------------------------------------------
-% Environments
-% --------------------------------------------------------------------
-% ...
-
-% --------------------------------------------------------------------
-% Commands
-% --------------------------------------------------------------------
-
-% ==============================================================
-% ========================== DOCUMENT ==========================
-% ==============================================================
-\begin{document} 
-%  --------------------------------------------------------------------
-
-% ===================================================
-% METADATA
-% ===================================================
-\title[mode=title]{Parameter estimation}                      
-\shorttitle{Parameter estimation}
-
-\shortauthors{OS, PO}
-
-\author[1]{Oliwer Sliczniuk}[orcid=0000-0003-2593-5956]
-\ead{oliwer.sliczniuk@aalto.fi}
-\cormark[1]
-\credit{a}
-
-\author[1]{Pekka Oinas}[orcid=0000-0002-0183-5558]
-\credit{b}
-
-%\author[1]{Francesco Corona}[orcid=0000-0002-3615-1359]
-%\credit{c}
-
-\address[1]{Aalto University, School of Chemical Engineering, Espoo, 02150, Finland}
-%\address[2]{2}
-
-\cortext[cor1]{Corresponding author}
-
-% ===================================================
-% ABSTRACT
-% ===================================================
-\begin{abstract}
-%Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ is the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output.
-As an example, the supercritical extraction process is presented.
-The impact of mass flow rate, pressure, and inlet temperature on the model's output is discussed.
-The sensitivity analysis results prove that the considered variables can affect the extraction's yield and be used as control variables in optimization problems.
-Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
-%Given a system of partial differential equations, $F(t,x,\dot{x},\Theta,u)=0$, where $x$ represents state variables, $\Theta$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process.
-The process model describes a partially filled extractor with a fixed bed, which work under constant operating conditions.
-We assume that the flow is uniform across any cross-section, although the area available for the fluid phase can change along the extractor.
-We apply the concept of quasi-one-dimensional flow to mimic the modelling of a two-dimensional case.
-%In this work, a distributed-parameter model, based on \citet{Reverchon1996} is used to describe a fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent.
-The model parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient \textit{and saturation concentration} are obtained from parameter estimation.
-The parameters are estimated based on four experiments performed at $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar and $50^\circ C$/$300$ bar.
-Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
-This study aimed to investigate the supercritical extraction process of the caraway oil from caraway seeds.
-A distributed-parameter model is used to describe the fluid-solid extraction process with carbon dioxide as a solvent.
-The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
-The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
-The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
-This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient.
-The missing model parameters and the initial state are obtained by solving the maximum likelihood estimation based on experimental yield data under the normal error assumption.
-A set of laboratory experiments was performed in a partially filled extractor with a fixed bed operated under multiple constant operating conditions: $40~^\circ C$ / $200$ bar, $50~^\circ C$ / $200$ bar, $40~^\circ C$ / $300$ bar, and $50~^\circ C$ / $300$ bar.
-
-\end{abstract}
-
-\begin{keywords}
-Supercritical extraction \sep Parameter estimation \sep Mathematical modelling
-\end{keywords}
-
-% ===================================================
-% TITLE
-% ===================================================
-\maketitle
-
-% ===================================================
-% Section: Introduction
-% ===================================================\section{Introduction}
-
-\section{Introduction}
-%\subfile{Sections/introduction}
-\subfile{Sections/introduction_imp}
-
-\section{Materials and methods} \label{CH: Materials and methods}
-
-\subsection{Supercritical fluids} \label{CH: Thermodynamic}
-%\subfile{Sections/Thermo}
-\subfile{Sections/Thermo_imp}
-
-%\clearpage
-%\subfile{Sections/Materials_and_methods}
-
-\subsection{Governing equations} \label{CH:Governing_equations_chapter}
 	%\footnote{For the sake of clarity of the process model, different colors have been used in the equations to indicate: 
@@
 
-\subsection{Extraction model} \label{CH: Extraction_model}
-\subfile{Sections/Model}
-
-%\newpage
-%\section{Bayes theorem} \label{CH: Bayes}
-%\subfile{Sections/Bayes_Theorem}
-%\clearpage
-
-\subsection{Parameter estimation} \label{CH: Parameter_estimation}
-\subfile{Sections/Parameter_estimation}
-
-\subsection{Experimental work}
-\subfile{Sections/Experiments}
-
-\section{Results}
-\subfile{Sections/Results}
-
-\section{Conclusions} \label{CH: Conclusion}
-
-This study presented basic aspects regarding the laboratory work for obtaining caraway extracts using supercritical carbon dioxide at different operating conditions.
-A first-principle process model was developed based on governing equations.
-As a result of the literature review, the extraction kinetic model was selected and combined with the general mass balance equations.
-The values of unknown parameters in the process model were obtained by parameter estimation.
-The yield data from the experiments were compared against the yield generated by the model.
-The IPOPT solver was used to solve the maximum likelihood estimation.
-The process model was found to have good agreement with experimental yield curves.
-Later, the parameters found for each experiment were combined to obtain more general relationships.
-The correlations for diffusion and decay coefficients are presented as a function of fluid density or Reynolds number.
-It should be noted that obtained correlations have been prepared with a limited amount of data.
-These correlations can be used to study qualitatively the impact of different operating conditions on the extraction yield by different methods, such as sensitivity analysis.
-Moreover, the generalized model could be useful in finding the optimal operating conditions with respect to the process economy.
-
-% ===================================================
-% Bibliography
-% ===================================================
-%% Loading bibliography style file
-\clearpage
-%\bibliographystyle{model1-num-names}
-\bibliographystyle{unsrtnat}
-\bibliography{mybibfile}
-
-\clearpage \appendix \label{appendix}
-\section{Appendix} 
-\subsection{Thermodynamic}
-\subfile{Sections/Qubic_EOS}
-%\subfile{Sections/Thermodynamic_details}
-
-\subsection{Governing equations}
-\subfile{Sections/Gouverning_equation_derivation}
-
-%\subsection{Low Mach number expansion} \label{CH:Low_Mach_chapter}
-%\subfile{Sections/Low_mach_number_expansion}
-%\subfile{Sections/Low_mach_number_expansion_imp}
-
-\subsection{Cardano's Formula} \label{CH: Cardano}
-\subfile{Sections/Cardano}
-
-\subsection{Initial and boundary conditions} \label{CH: IC_BC}
-\subfile{Sections/IC_BC}
-
-%\subsection{Bayes theorem} \label{CH: Bayes}
-%\subfile{Sections/Bayes_Theorem}
-
-\subsection{Maximum likelihood} \label{CH: ML}
-\subfile{Sections/Likelihood}
-
-\subsection{Solid density measurement} \label{CH: Solid_Density_Measurment}
-
-Figure \ref{fig:density_cal} shows results of density measurement performed with pycnometer.
-
-\begin{figure}[!h]
-	\centering 
-	\includegraphics[trim=2cm 6cm 4cm 0cm, clip,width=\columnwidth]{Sections/ultraReportT5.pdf}
-	\caption{The result of solid density measurement}
-	\label{fig:density_cal}
-\end{figure}
-
-{\footnotesize
-	\begin{equation*}
-		\rho_s^{ave} = \frac{1.2585+1.2582+1.2561+1.2546+1.2555}{5} = 1.25658 [g/cc]
-	\end{equation*}
-}
-
-\subsection{Porosity calculations} \label{CH: Porosity}
-\subfile{Sections/Porosity}
-
-%\subsection{Concentration profiles} \label{CH: Profiles}
-%\subfile{Sections/Profiles}
-
-%\subsection{Solution of the parameter estimation starting from another initial guess} \label{CH: Profiles_2}
-%\subfile{Sections/Parameter_estimation_solution_from_another_IG}
-
 \end{document}

### 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Likelihood.tex
11.10

--- 2023-08-08 SFE_article_Parameter_Estimation/Sections/Likelihood.tex
@@
 The conditions at the maximum can be refined by incorporating prior information.
-The posterior probability density function $p(\theta|y)$ can be expressed as the ratio of two probability densities (\ref{EQ: Probabiltiy_independet_b}) using the continuous variable analogue of Bayes' theorem (details in Appendix \ref{CH: Bayes}).
-In such a case the posteriori distribution is given by Equation \ref{EQ: Posterior_distribution}.
+The posterior probability density function $p(\theta|y)$ can be expressed as the ratio of two probability densities %(\ref{EQ: Probabiltiy_independet_b})
+	 using the continuous variable analogue of Bayes' theorem %(details in Appendix \ref{CH: Bayes})
+	 . In such a case the posteriori distribution is given by Equation \ref{EQ: Posterior_distribution}.
 
@@
 
-	The numerator of the right-hand side od Equation \ref{EQ: Posterior_distribution} using Equation \ref{EQ: Probabiltiy_dependet_a} becomes
+	The numerator of the right-hand side od Equation \ref{EQ: Posterior_distribution} becomes %using Equation \ref{EQ: Probabiltiy_dependet_a} becomes
 

### 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Parameter_estimation.tex
11.10

@@
 	Not all the parameters present in a process model can be estimated from the theoretical considerations.
-The goal of parameter estimation is to obtain the "best" estimate of unknown parameters ${\color{magenta} \theta}$ (which is a subset of the parameter space ${\color{magenta}\Theta}$ containing all parameters of a model) based on the continuous observations ${\color{blue}Y}(t)$ or the discrete observations ${\color{blue}Y}(t_i)$.
-Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, ${\color{blue}y}(t)$ (Equation \ref{Model_measurment_1}), to give the observable dependent variable ${\color{blue}Y}(t)$ (for example results of an experiment).
+The goal of parameter estimation is to obtain the "best" estimate of unknown parameters ${\color{black} \theta}$ (which is a subset of the parameter space ${\color{black}\Theta}$ containing all parameters of a model) based on the continuous observations ${\color{black}Y}(t)$ or the discrete observations ${\color{black}Y}(t_i)$.
+Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, ${\color{black}y}(t)$ (Equation \ref{Model_measurment_1}), to give the observable dependent variable ${\color{black}Y}(t)$ (for example results of an experiment).
 For discrete observations, this can be expressed as:
@@
 		\begin{equation*}
-			{\color{blue}Y}(t_i) = {\color{blue}y}({\color{magenta} \theta}, t_i) + \epsilon(t_i)
+			{\color{black}Y}(t_i) = {\color{black}y}({\color{black} \theta}, t_i) + \epsilon(t_i)
 	\end{equation*} }
@@
 		\begin{equation*}
-			{\color{blue}Y}(t) = {\color{blue}y}({\color{magenta} \theta}, t) + \epsilon(t)
+			{\color{black}Y}(t) = {\color{black}y}({\color{black} \theta}, t) + \epsilon(t)
 	\end{equation*} }
 
-	However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $d{\color{blue}Y}(t_i)/dt$ is measured instead of ${\color{blue}Y}(t_i)$ itself.
-In such cases, it is assumed that the unobservable error is added to the deterministic derivative $d{\color{blue}y}({\color{magenta} \theta}, t_i)/dt$ as shown below
+	However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $d{\color{black}Y}(t_i)/dt$ is measured instead of ${\color{black}Y}(t_i)$ itself.
+In such cases, it is assumed that the unobservable error is added to the deterministic derivative $d{\color{black}y}({\color{black} \theta}, t_i)/dt$ as shown below
 
@@
 		\begin{equation}  \label{EQ: Measurment_noise}
-			\cfrac{d {\color{blue}Y}(t_i)}{dt} = \cfrac{d{\color{blue}y}({\color{magenta} \theta}, t_i)}{dt} + \epsilon(t_i)
+			\cfrac{d {\color{black}Y}(t_i)}{dt} = \cfrac{d{\color{black}y}({\color{black} \theta}, t_i)}{dt} + \epsilon(t_i)
 	\end{equation} }
@@
 		\begin{equation} \label{EQ: Objective_function}
-			\ln L = -\cfrac{n}{2} \left( \ln \sqrt{2 \pi} + \ln {\color{magenta} \sigma}^2 \right)
-			- \cfrac{ \sum_{i=1}^{n} \left[  \cfrac{d {\color{blue}Y}(t_i)}{dt} - \cfrac{d{\color{blue}y}({\color{magenta} \theta}, t_i)}{dt} \right]^2 }{2 {\color{magenta} \sigma}^2}
+			\ln L = -\cfrac{n}{2} \left( \ln \sqrt{2 \pi} + \ln {\color{black} \sigma}^2 \right)
+			- \cfrac{ \sum_{i=1}^{n} \left[  \cfrac{d {Y}(t_i)}{dt} - \cfrac{d{\color{black}y}({\color{black} \theta}, t_i)}{dt} \right]^2 }{2 {\color{black} \sigma}^2}
 		\end{equation}
@@
 			\begin{aligned} \label{EQ: Optimization_formulation_MLE}
-				&\hat{{\color{magenta} \theta}}_{MLE} &= \arg \max_{{\color{magenta} \sigma}, {\color{magenta} \theta} \in \Theta} \ln L = \arg \max_{{\color{magenta} \sigma},{\color{magenta} \theta} \in \Theta} p({\color{magenta} \theta}|{\color{blue}y}) \\
+				&\hat{{\color{black} \theta}}_{MLE} &= \arg \max_{{\color{black} \sigma}, {\color{black} \theta} \in \Theta} \ln L = \arg \max_{{\color{black} \sigma},{\color{black} \theta} \in \Theta} p({\color{black} \theta}|{\color{black}y}) \\
 				&\text{subject to}
-				& \dot{ {\color{blue}x} } = {\color{blue}G}({\color{blue} x}(t);{\color{magenta} \theta}) \\
-				&& {\color{magenta} \dot{\theta}} = 0 \\
-				&& {\color{blue}y} = {\color{blue}y}(t) \\
-				&& {\color{magenta} \theta}^{lb} \leq {\color{magenta} \theta} \leq {\color{magenta} \theta}^{ub}
+				& \dot{ {\color{black}x} } = {\color{black}G}({\color{black} x}(t);{\color{black} \theta}) \\
+				&& {\color{black} \dot{\theta}} = 0 \\
+				&& {\color{black}y} = {\color{black}y}(t) \\
+				&& {\color{black} \theta}^{lb} \leq {\color{black} \theta} \leq {\color{black} \theta}^{ub}
 			\end{aligned}
@@
 
-	where $\hat{{\color{magenta} \theta}}$ is as maximum likelihood estimator, ${\color{magenta} \theta}^{lb}$ define the minimal value of ${\color{magenta} \theta}$ and ${\color{magenta} \theta}^{ub}$ is the maximum value of ${\color{magenta} \theta}$.
+	where $\hat{{\color{black} \theta}}$ is as maximum likelihood estimator, ${\color{black} \theta}^{lb}$ define the minimal value of ${\color{black} \theta}$ and ${\color{black} \theta}^{ub}$ is the maximum value of ${\color{black} \theta}$.
 
-	Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector ${\color{magenta} \theta}$ and equating to zero the partial derivatives of $\ln L$:
+	Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector ${\color{black} \theta}$ and equating to zero the partial derivatives of $\ln L$:
 
@@
 		\begin{align}\label{EQ: MLE_Basic_Solution}
-			\cfrac{\partial \ln L}{\partial {\color{magenta} \theta}} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( {\color{blue}y}(t_i) | {\color{magenta} \theta} \right) }{\partial {\color{magenta} \theta}} = 0
+			\cfrac{\partial \ln L}{\partial {\color{black} \theta}} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( {\color{black}y}(t_i) | {\color{black} \theta} \right) }{\partial {\color{black} \theta}} = 0 
 	\end{align} }
 
-	Solution of Equations \ref{EQ: MLE_Basic_Solution} yield the desired estimates $\hat{{\color{magenta} \theta}}$.
-For some models, these equations can be explicitly solved for $\hat{{\color{magenta} \theta}}$ but in general, no closed-form solution to the maximization problem is known or available, and a maximum likelihood estimator can only be found via numerical optimization.
+	Solution of Equations \ref{EQ: MLE_Basic_Solution} yield the desired estimates $\hat{{\color{black} \theta}}$.
+For some models, these equations can be explicitly solved for $\hat{{\color{black} \theta}}$ but in general, no closed-form solution to the maximization problem is known or available, and a maximum likelihood estimator can only be found via numerical optimization.
 

### 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
11.10

@@
 When the fluid at the new temperature reaches the solid particles, it affects mass transfer, subsequently influencing the amount of solute in the fluid phase.
-In response to the slower extraction rate indicated by positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, a 'hot spot' with negative sensitivities becomes visible in Figure \ref{fig:Sensitivty_T_CF}.
+In response to the slower extraction rate indicated by positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, a section with negative sensitivities becomes visible in Figure \ref{fig:Sensitivty_T_CF}.
 The effect of diffusion is observable in the section without the fixed bed, where the front composed of sensitivities becomes blurred.

### 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Sensitivity_Analysis.tex
11.10

@@
 This set of derivatives is known as sensitivity equations, and it is solved simultaneously with the process model.
-The purpose of the sensitivity analysis is to investigate how responsive the solution is for the perturbation of the parameter ${\color{magenta}p}$.
+The purpose of the sensitivity analysis is to investigate how responsive the solution is for the perturbation of the parameter ${p}$.
 According to \citet{Dickinson1976}, the sensitivity analysis can be used to determine the influence of the uncertainty on the solution of the original system.
@@
 
-	As presented in the work of \citet{Maly1996}, the sensitivity analysis equations(${\color{blue}\dot{Z}}$) are developed by taking the total derivative of the original system ${\color{blue}F}({\color{blue}x}(t);{\color{magenta}p})$ with respect to ${\color{magenta}p}$.
+	As presented in the work of \citet{Maly1996}, the sensitivity analysis equations(${\dot{Z}}$) are developed by taking the total derivative of the original system ${F}({x}(t);{p})$ with respect to ${p}$.
 
@@
 			%		\label{SA_def}
-			{\color{orange}Z}({\color{blue}x}(t);{\color{magenta}p}) &= \cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}p}}
+			{Z}({x}(t);{p}) &= \cfrac{\partial {x}(t)}{\partial {p}}
 	\end{align} }
@@
 		\begin{equation} \label{SA_dt} 
-			{\color{blue}\dot{Z}}({\color{blue}x}(t);{\color{magenta}p})  = \cfrac{d {\color{orange}Z}(x(t);{\color{magenta}p})}{d t} = \cfrac{\partial }{\partial t} \left( \cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}p}} \right) = \cfrac{\partial }{\partial {\color{magenta}p}} \left( \cfrac{\partial {\color{blue}x}(t)}{\partial t} \right) = \cfrac{d {\color{blue}F}({\color{blue}x}(t);{\color{magenta}p})}{d {\color{magenta}p}}
+			{\dot{Z}}({x}(t);{p})  = \cfrac{d {Z}(x(t);{p})}{d t} = \cfrac{\partial }{\partial t} \left( \cfrac{\partial {x}(t)}{\partial {p}} \right) = \cfrac{\partial }{\partial {p}} \left( \cfrac{\partial {x}(t)}{\partial t} \right) = \cfrac{d {F}({x}(t);{p})}{d {p}}
 	\end{equation} }
@@
 		\begin{align}		
-			\label{SA_eq_full}\cfrac{d {\color{blue}F}({\color{blue}x}(t);{\color{magenta}p})}{d {\color{magenta}p}} &=  \underbrace{ \cfrac{\partial {\color{blue}F}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x}(t)} }_{{\color{blue}J_x}({\color{blue}x}(t);{\color{magenta}p})} \underbrace{\cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}p}} }_{{\color{blue}S}({\color{blue}x}(t);{\color{magenta}p})} + \underbrace{ \cfrac{\partial {\color{blue}F}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p}} }_{{\color{blue}J_p}({\color{blue}x}(t);{\color{magenta}p})}
+			\label{SA_eq_full}\cfrac{d {F}({x}(t);{p})}{d {p}} &=  \underbrace{ \cfrac{\partial {F}({x}(t);{p})}{\partial {x}(t)} }_{{J_x}({x}(t);{p})} \underbrace{\cfrac{\partial {x}(t)}{\partial {p}} }_{{S}({x}(t);{p})} + \underbrace{ \cfrac{\partial {F}({x}(t);{p})}{\partial {p}} }_{{J_p}({x}(t);{p})}
 	\end{align} }
@@
 	The sensitivity equation \ref{SA_eq_full} is solved simultaneously with the original system.
-This equation is made of three terms: jacobian ${\color{blue}J_x}({\color{blue}x}(t);{\color{magenta}p})$, sensitivity matrix ${\color{blue}S}({\color{blue}x}(t);{\color{magenta}p})$ and jacobian ${\color{blue}J_p}({\color{blue}x}(t);{\color{magenta}p})$.
-The jacobian ${\color{blue}J_x}({\color{blue}x}(t);{\color{magenta}p})$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${\color{blue}J_x}(n_x,n_x)$ is the derivative of process model equations ${\color{blue}F}_{n_x}({\color{blue}x}(t);{\color{magenta}p})$ with respect to the state variable $x_{n_p}$.
+This equation is made of three terms: jacobian ${J_x}({x}(t);{p})$, sensitivity matrix ${S}({x}(t);{p})$ and jacobian ${J_p}({x}(t);{p})$.
+The jacobian ${J_x}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${J_x}(n_x,n_x)$ is the derivative of process model equations ${F}_{n_x}({x}(t);{p})$ with respect to the state variable $x_{n_p}$.
 
@@
 			\setlength\arraycolsep{2pt}
-			{\color{blue}J_x}({\color{blue}x}(t);{\color{magenta}p})=\begin{pmatrix}
-				\cfrac{\partial {\color{blue}F_{1}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{1}}(t)} & \cfrac{\partial {\color{blue}F_{1}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{2}}(t)} & \cdots & \cfrac{\partial {\color{blue}F_{1}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{N_x}}(t)}\\
-				\cfrac{\partial {\color{blue}F_{2}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{1}}(t)} & \cfrac{\partial {\color{blue}F_{2}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{2}}(t)} & \cdots & \cfrac{\partial {\color{blue}F_{2}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{N_x}}(t)}\\
+			{J_x}({x}(t);{p})=\begin{pmatrix}
+				\cfrac{\partial {F_{1}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {F_{1}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {F_{1}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
+				\cfrac{\partial {F_{2}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {F_{2}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {F_{2}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
 				\vdots & \vdots & \ddots & \vdots\\ 
-				\cfrac{\partial {\color{blue}F_{N_x}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{1}}(t)} & \cfrac{\partial {\color{blue}F_{N_x}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{2}}(t)} & \cdots & \cfrac{\partial {\color{blue}F_{N_x}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{blue}x_{N_x}}(t)}\\
+				\cfrac{\partial {F_{N_x}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {F_{N_x}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {F_{N_x}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
 			\end{pmatrix}
@@
 
-	The sensitivity matrix ${\color{blue}S}({\color{blue}x}(t);{\color{magenta}p})$ represents the matrix of equations of size $N_x \times N_p$, where each equation ${\color{blue}S}(n_x,n_p)$ is the derivative of the state variable $x_{n_x}$ with respect to the parameter $p_{n_p}$.
+	The sensitivity matrix ${S}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_p$, where each equation ${S}(n_x,n_p)$ is the derivative of the state variable $x_{n_x}$ with respect to the parameter $p_{n_p}$.
 
@@
 			\begin{split}
-				{\color{blue}S}({\color{blue}x}(t);{\color{magenta}p}) & = 
+				{S}({x}(t);{p}) & = 
 %				\begingroup % keep the change local
@@
 %				\begin{pmatrix}
-%					{\color{blue}s_{({1,1})}} & {\color{blue}s_{({1,2})}} & \cdots & {\color{blue}s_{({1,N_p})}}\\
-%					{\color{blue}s_{({2,1})}} & {\color{blue}s_{({2,2})}} & \cdots & {\color{blue}s_{({2,N_p})}}\\
+%					{s_{({1,1})}} & {s_{({1,2})}} & \cdots & {s_{({1,N_p})}}\\
+%					{s_{({2,1})}} & {s_{({2,2})}} & \cdots & {s_{({2,N_p})}}\\
 %					\vdots & \vdots & \ddots & \vdots\\
-%					{\color{blue}s_{({N_x,1})}} & {\color{blue}s_{({N_x,2})}} & \cdots & {\color{blue}s_{({N_x,N_p})}}\\
+%					{s_{({N_x,1})}} & {s_{({N_x,2})}} & \cdots & {s_{({N_x,N_p})}}\\
 %				\end{pmatrix}
@@
 				\begin{pmatrix}
-					\cfrac{d {\color{blue}x_{1}}(t)}{d {\color{magenta}p_{1}}} 	& \cfrac{d {\color{blue}x_{1}}(t)}{d {\color{magenta}p_{2}}}     & \cdots & \cfrac{d {\color{blue}x_{1}}(t)}{d {\color{magenta}p_{N_p}}}\\
-					\cfrac{d {\color{blue}x_{2}}(t)}{d {\color{magenta}p_{1}}} 	& \cfrac{d {\color{blue}x_{2}}(t)}{d {\color{magenta}p_{2}}}     & \cdots & \cfrac{d {\color{blue}x_{2}}(t)}{d {\color{magenta}p_{N_p}}}\\
+					\cfrac{d {x_{1}}(t)}{d {p_{1}}} 	& \cfrac{d {x_{1}}(t)}{d {p_{2}}}     & \cdots & \cfrac{d {x_{1}}(t)}{d {p_{N_p}}}\\
+					\cfrac{d {x_{2}}(t)}{d {p_{1}}} 	& \cfrac{d {x_{2}}(t)}{d {p_{2}}}     & \cdots & \cfrac{d {x_{2}}(t)}{d {p_{N_p}}}\\
 					\vdots					 	    & \vdots 					   	  & \ddots & \vdots\\
-					\cfrac{d {\color{blue}x_{N_x}}(t)}{d {\color{magenta}p_{1}}} 	& \cfrac{d {\color{blue}x_{N_x}}(t)}{d {\color{magenta}p_{2}}}     & \cdots & \cfrac{d {\color{blue}x_{N_x}}(t)}{d {\color{magenta}p_{N_p}}}
+					\cfrac{d {x_{N_x}}(t)}{d {p_{1}}} 	& \cfrac{d {x_{N_x}}(t)}{d {p_{2}}}     & \cdots & \cfrac{d {x_{N_x}}(t)}{d {p_{N_p}}}
 				\end{pmatrix} 
@@
 
-	The jacobian ${\color{blue}J_p}({\color{blue}x}(t);{\color{magenta}p})$ represents the matrix of equations of size $N_x \times N_p$, where each equation ${\color{blue}J_p}(n_x,n_p)$ is the direct derivative of the process model equation $F_{n_x}$ with respect to the parameter $p_{n_p}$.
+	The jacobian ${J_p}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_p$, where each equation ${J_p}(n_x,n_p)$ is the direct derivative of the process model equation $F_{n_x}$ with respect to the parameter $p_{n_p}$.
 
@@
 		\begin{align}
-			{\color{blue}J_p}({\color{blue}x}(t);{\color{magenta}p}) & =
+			{J_p}({x}(t);{p}) & =
 			\begingroup % keep the change local
@@
 			\begin{pmatrix}
-				\cfrac{\partial {\color{blue}F_{1}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{1}}} & \cfrac{\partial {\color{blue}F_{1}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{2}}} & \cdots & \cfrac{\partial {\color{blue}F_{1}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{N_p}}}\\
-				\cfrac{\partial {\color{blue}F_{2}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{1}}} & \cfrac{\partial {\color{blue}F_{2}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{2}}} & \cdots & \cfrac{\partial {\color{blue}F_{2}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{N_p}}}\\
+				\cfrac{\partial {F_{1}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {F_{1}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {F_{1}}({x}(t);{p})}{\partial {p_{N_p}}}\\
+				\cfrac{\partial {F_{2}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {F_{2}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {F_{2}}({x}(t);{p})}{\partial {p_{N_p}}}\\
 				\vdots & \vdots & \ddots & \vdots\\
-				\cfrac{\partial {\color{blue}F_{N_x}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{1}}} & \cfrac{\partial {\color{blue}F_{N_x}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{2}}} & \cdots & \cfrac{\partial {\color{blue}F_{N_x}}({\color{blue}x}(t);{\color{magenta}p})}{\partial {\color{magenta}p_{N_p}}}
+				\cfrac{\partial {F_{N_x}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {F_{N_x}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {F_{N_x}}({x}(t);{p})}{\partial {p_{N_p}}}
 			\end{pmatrix}
@@
 
-	The combined system containing the original set of equations ${\color{blue}F}({\color{blue}x}(t);{\color{magenta}p})$ and sensitivity equations can be formulated as ${\color{blue}\textbf{F}}\left({\color{blue}x}(t);{\color{magenta}p}\right)$.
-The size of ${\color{blue}\textbf{F}}\left({\color{blue}x}(t);{\color{magenta}p}\right)$ is equal to $N_s = N_x(N_p + 1)$.
+	The combined system containing the original set of equations ${F}({x}(t);{p})$ and sensitivity equations can be formulated as ${\textbf{F}}\left({x}(t);{p}\right)$.
+The size of ${\textbf{F}}\left({x}(t);{p}\right)$ is equal to $N_s = N_x(N_p + 1)$.
 
@@
 		\begin{align}
-			{\color{blue}\textbf{F}}\left({\color{blue}x}(t);{\color{magenta}p}\right) = 
+			{\textbf{F}}\left({x}(t);{p}\right) = 
 			\begin{bmatrix}
-				{\color{blue}F}({\color{blue}x}(t);{\color{magenta}p})\\
-				{\color{blue}J_x}({\color{blue}x}(t);{\color{magenta}p}){\color{blue}S}({\color{blue}x}(t);{\color{magenta}p}) + {\color{blue}J_p}({\color{blue}x}(t);{\color{blue}p})
+				{F}({x}(t);{p})\\
+				{J_x}({x}(t);{p}){S}({x}(t);{p}) + {J_p}({x}(t);{p})
 			\end{bmatrix}
@@
 		\begin{align}
-			{\color{blue}\textbf{F}}\left({\color{blue}x}(t_0);{\color{magenta}p}\right)  = 
-			\begin{bmatrix} {\color{blue}x}(t_0),			& 
-				\cfrac{ \text{d}{\color{blue}x}(t_0) }{ d{\color{magenta}p_1} },		& 
+			{\textbf{F}}\left({x}(t_0);{p}\right)  = 
+			\begin{bmatrix} {x}(t_0),			& 
+				\cfrac{ \text{d}{x}(t_0) }{ d{p_1} },		& 
 				\cdots,					 	&
-				\cfrac{ d{\color{blue}x}(t_0) }{ d{\color{magenta}p_{N_p}} } 
+				\cfrac{ d{x}(t_0) }{ d{p_{N_p}} } 
 			\end{bmatrix}^T
@@
 
-	In a similar way, the sensitivity analysis of the output function can be performed with respect to parameters ${\color{magenta}p}$.
-The output function ${\color{blue}g}({\color{blue}x}(t))$ returns ${\color{blue}y}(t)$.
-By taking a total derivative of ${\color{blue}y}(t)$ with respect to ${\color{magenta}p}$, the new sensitivity equation can be found.
+	In a similar way, the sensitivity analysis of the output function can be performed with respect to parameters ${p}$.
+The output function ${g}({x}(t))$ returns ${y}(t)$.
+By taking a total derivative of ${y}(t)$ with respect to ${p}$, the new sensitivity equation can be found.
 
@@
 		\begin{align}
-			\cfrac{d {\color{blue}y}(t)}{d{\color{magenta}p}} = \cfrac{d {\color{blue}g}({\color{blue}x}(t))}{d{\color{magenta}p}} = \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x}(t)} \cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}p}} + \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{magenta}p}}
+			\cfrac{d {y}(t)}{d{p}} = \cfrac{d {g}({x}(t))}{d{p}} = \cfrac{\partial {g}({x}(t))}{\partial {x}(t)} \cfrac{\partial {x}(t)}{\partial {p}} + \cfrac{\partial {g}({x}(t))}{\partial {p}}
 	\end{align} }
 
-%	The ${\color{blue}g}({\color{blue}x}(t))$ itself is independent of the parameters, but it dependents on ${\color{blue}x}(t)$, which is the function of ${\color{magenta}p}$.
-In such a case the sensitivity equation for the output becomes
+%	The ${g}({x}(t))$ itself is independent of the parameters, but it dependents on ${x}(t)$, which is the function of ${p}$. In such a case the sensitivity equation for the output becomes
 %	
@@
 %		\begin{equation} \label{EQ:Output_sens_full}
-%			\cfrac{d {\color{blue}g}({\color{blue}x}(t))}{d {\color{magenta}p}} = \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x}(t)} \cfrac{\partial {\color{blue}x}(t)}{\partial {\color{magenta}p}} + 0 = \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x}(t)}  {\color{blue}S}({\color{blue}x}(t);{\color{magenta}p}) =
+%			\cfrac{d {g}({x}(t))}{d {p}} = \cfrac{\partial {g}({x}(t))}{\partial {x}(t)} \cfrac{\partial {x}(t)}{\partial {p}} + 0 = \cfrac{\partial {g}({x}(t))}{\partial {x}(t)}  {S}({x}(t);{p}) = 
 %		\end{equation} 
@@
 %			\begin{pmatrix}
-%				\cfrac{\partial {\color{blue}g_{1}}({\color{blue}x}(t))}{\partial {\color{blue}x_{1}}} & \cfrac{\partial {\color{blue}g_{1}}({\color{blue}x}(t))}{\partial {\color{blue}x_{2}}} & \cdots & \cfrac{\partial {\color{blue}g_{1}}({\color{blue}x}(t))}{\partial {\color{blue}x_{N_x}}}\\
-%				\cfrac{\partial {\color{blue}g_{2}}({\color{blue}x}(t))}{\partial {\color{blue}x_{1}}} & \cfrac{\partial {\color{blue}g_{2}}({\color{blue}x}(t))}{\partial {\color{blue}x_{2}}} & \cdots & \cfrac{\partial {\color{blue}g_{2}}({\color{blue}x}(t))}{\partial {\color{blue}x_{N_x}}}\\
+%				\cfrac{\partial {g_{1}}({x}(t))}{\partial {x_{1}}} & \cfrac{\partial {g_{1}}({x}(t))}{\partial {x_{2}}} & \cdots & \cfrac{\partial {g_{1}}({x}(t))}{\partial {x_{N_x}}}\\
+%				\cfrac{\partial {g_{2}}({x}(t))}{\partial {x_{1}}} & \cfrac{\partial {g_{2}}({x}(t))}{\partial {x_{2}}} & \cdots & \cfrac{\partial {g_{2}}({x}(t))}{\partial {x_{N_x}}}\\
 %				\vdots & \vdots & \ddots & \vdots\\
-%				\cfrac{\partial {\color{blue}g_{N_g}}({\color{blue}x}(t))}{\partial {\color{blue}x_{1}}} & \cfrac{\partial {\color{blue}g_{N_g}}({\color{blue}x}(t))}{\partial {\color{blue}x_{2}}} & \cdots & \cfrac{\partial {\color{blue}g_{N_g}}({\color{blue}}(t))}{\partial {\color{blue}x_{N_x}}}
+%				\cfrac{\partial {g_{N_g}}({x}(t))}{\partial {x_{1}}} & \cfrac{\partial {g_{N_g}}({x}(t))}{\partial {x_{2}}} & \cdots & \cfrac{\partial {g_{N_g}}({}(t))}{\partial {x_{N_x}}}
 %			\end{pmatrix}
 %			\begin{pmatrix}
-%				{\color{blue}s_{({1,1})}} & {\color{blue}s_{({1,2})}} & \cdots & {\color{blue}s_{({1,N_p})}}\\
-%				{\color{blue}s_{({2,1})}} & {\color{blue}s_{({2,2})}} & \cdots & {\color{blue}s_{({2,N_p})}}\\
+%				{s_{({1,1})}} & {s_{({1,2})}} & \cdots & {s_{({1,N_p})}}\\
+%				{s_{({2,1})}} & {s_{({2,2})}} & \cdots & {s_{({2,N_p})}}\\
 %				\vdots & \vdots & \ddots & \vdots\\
-%				{\color{blue}s_{({N_x,1})}} & {\color{blue}s_{({N_x,2})}} & \cdots & {\color{blue}s_{({N_x,N_p})}}\\
+%				{s_{({N_x,1})}} & {s_{({N_x,2})}} & \cdots & {s_{({N_x,N_p})}}\\
 %			\end{pmatrix}
@@
 %			\begin{split}
-%				& \left( \cfrac{d {\color{blue}y}({\color{blue}x}(t))}{d {\color{magenta}p_{1}}}, \cfrac{d {\color{blue}y}({\color{blue}x}(t))}{d {\color{magenta}p_{2}}}, \cdots, \cfrac{d {\color{blue}y}({\color{blue}x}(t))}{d {\color{magenta}p_{N_p}}} \right)  = \\
-%				& =  \left( \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x_{1}}}, \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x_{2}}}, \cdots, \cfrac{\partial {\color{blue}g}({\color{blue}x}(t))}{\partial {\color{blue}x_{N_x}}} \right)
+%				& \left( \cfrac{d {y}({x}(t))}{d {p_{1}}}, \cfrac{d {y}({x}(t))}{d {p_{2}}}, \cdots, \cfrac{d {y}({x}(t))}{d {p_{N_p}}} \right)  = \\
+%				& =  \left( \cfrac{\partial {g}({x}(t))}{\partial {x_{1}}}, \cfrac{\partial {g}({x}(t))}{\partial {x_{2}}}, \cdots, \cfrac{\partial {g}({x}(t))}{\partial {x_{N_x}}} \right)
 %				\begingroup % keep the change local
@@
 %				\begin{pmatrix}
-%					{\color{blue}s_{({1,1})}} & {\color{blue}s_{({1,2})}} & \cdots & {\color{blue}s_{({1,N_p})}}\\
-%					{\color{blue}s_{({2,1})}} & {\color{blue}s_{({2,2})}} & \cdots & {\color{blue}s_{({2,N_p})}}\\
+%					{s_{({1,1})}} & {s_{({1,2})}} & \cdots & {s_{({1,N_p})}}\\
+%					{s_{({2,1})}} & {s_{({2,2})}} & \cdots & {s_{({2,N_p})}}\\
 %					\vdots & \vdots & \ddots & \vdots\\
-%					{\color{blue}s_{({N_x,1})}} & {\color{blue}s_{({N_x,2})}} & \cdots & {\color{blue}s_{({N_x,N_p})}}\\
+%					{s_{({N_x,1})}} & {s_{({N_x,2})}} & \cdots & {s_{({N_x,N_p})}}\\
 %				\end{pmatrix} \endgroup

### 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Thermodynamic_details.tex
11.10

@@
 	\subsubsection{Equation of state and properties of the fluid phase} \label{subsubsec: Equation of state}
-	In this study, the influence of real gas effects are introduced through ${\color{red}P}(t) {\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t)) = {\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right){\color{magenta}R}{\color{blue}T}(t,z)$, where ${\color{orange}v_m}$ represents the molar volume of $CO_2$, ${\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ denotes its compressibility factor, and $R$ is the universal gas constant.
+	In this study, the influence of real gas effects are introduced through ${\color{black}P}(t) {\color{black}v_m}({\color{black}T}(t,z),{\color{black}P}(t)) = {\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right){\color{black}R}{\color{black}T}(t,z)$, where ${\color{black}v_m}$ represents the molar volume of $CO_2$, ${\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ denotes its compressibility factor, and $R$ is the universal gas constant.
 The main advantage of using compressibility in calculations is to express it as an explicit function of temperature and pressure.
@@
 		\begin{equation}
-			{\color{red}P}(t) = \cfrac{{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t)) - {\color{magenta}b}} - \cfrac{{\color{magenta}a^c}{\color{orange}\alpha}\left({\color{blue}T}(t,z)\right)}{{\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t))^2 + 2{\color{magenta}b}{\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t)) - {\color{magenta}b}^2}
+			{\color{black}P}(t) = \cfrac{{\color{black}R}{\color{black}T}(t,z)}{{\color{black}v_m}({\color{black}T}(t,z),{\color{black}P}(t)) - {\color{black}b}} - \cfrac{{\color{black}a^c}{\color{black}\alpha}\left({\color{black}T}(t,z)\right)}{{\color{black}v_m}({\color{black}T}(t,z),{\color{black}P}(t))^2 + 2{\color{black}b}{\color{black}v_m}({\color{black}T}(t,z),{\color{black}P}(t)) - {\color{black}b}^2}
 			\label{EQ: PR}
@@
 	The Equation \ref{EQ: PR} can be also written as the third-order given by Equation \ref{eq: Compressibility}.
-Numerical methods such as Newton-Raphson can be used to solve the polynomial equation to obtain the compressibility ${\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ at given temperature and pressure.
+Numerical methods such as Newton-Raphson can be used to solve the polynomial equation to obtain the compressibility ${\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ at given temperature and pressure.
 Alternatively, the Cardano formula can be used to get the closed form solution of the Equation \ref{eq: Compressibility}.
@@
 	\begin{aligned}
-		&{\color{orange}Z}^3 - \left(1 - {\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)\right) {\color{orange}Z}^2 \\
-		&+ \left({\color{orange}A}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) - 2{\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) - 3{\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)^2\right) {\color{orange}Z} = 0
+		&{\color{black}Z}^3 - \left(1 - {\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)\right) {\color{black}Z}^2 \\
+		&+ \left({\color{black}A}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) - 2{\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) - 3{\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)^2\right) {\color{black}Z} = 0
 	\end{aligned} \end{equation} }
 
-	where ${\color{orange}A}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ are functions of time and space defined on the attraction parameter, ${\color{orange}a}\left({\color{blue}T}(t,z)\right) = {\color{magenta}a^c}{\color{orange}\alpha}\left({\color{blue}T}(t,z)\right)$ with ${\color{magenta}a^c} \approx 0.45724 {{\color{magenta}R}^2{\color{magenta}T_c}^2}/{{\color{magenta}P_c}}$, and the repulsion parameter, ${\color{magenta}b} \approx 0.07780 {{\color{magenta}R}{\color{magenta}T_c}}/{{\color{magenta}P_c}}$, both functions of the critical temperature ${\color{magenta}T_c}$ and pressure ${\color{magenta}P_c}$.
+	where ${\color{black}A}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ and ${\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ are functions of time and space defined on the attraction parameter, ${\color{black}a}\left({\color{black}T}(t,z)\right) = {\color{black}a^c}{\color{black}\alpha}\left({\color{black}T}(t,z)\right)$ with ${\color{black}a^c} \approx 0.45724 {{\color{black}R}^2{\color{black}T_c}^2}/{{\color{black}P_c}}$, and the repulsion parameter, ${\color{black}b} \approx 0.07780 {{\color{black}R}{\color{black}T_c}}/{{\color{black}P_c}}$, both functions of the critical temperature ${\color{black}T_c}$ and pressure ${\color{black}P_c}$.
 
@@
 		\begin{align} 
-			{\color{orange}A}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)	& = \dfrac{{\color{orange}\alpha}\left({\color{blue}T}\left(t,z\right)\right){\color{magenta}a^c}{\color{red}P}(t)}{{\color{magenta}R}^2{\color{blue}T}^2(t,z)};													\label{eq: PR_A}\\
-			{\color{orange}B}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)	& = \dfrac{{\color{magenta}b}{\color{red}P}(t)}{{\color{magenta}R}{\color{blue}T}(t,z)}	\label{eq: PR_B}.
+			{\color{black}A}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)	& = \dfrac{{\color{black}\alpha}\left({\color{black}T}\left(t,z\right)\right){\color{black}a^c}{\color{black}P}(t)}{{\color{black}R}^2{\color{black}T}^2(t,z)};													\label{eq: PR_A}\\
+			{\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)	& = \dfrac{{\color{black}b}{\color{black}P}(t)}{{\color{black}R}{\color{black}T}(t,z)}	\label{eq: PR_B}.
 		\end{align}
@@
 
-	The quantity ${\color{orange}\alpha}\left({\color{blue}T}\left(t,z\right)\right)$ is a dimensionless correction term that depends on the temperature ${\color{blue}T}\left(t,z\right)$ and a constant ${\color{magenta}\kappa}$.
-The constant ${\color{magenta}\kappa}$ is given by the formula ${\color{magenta}\kappa} = 0.37464 + 1.54226 {\color{magenta}\omega} - 0.26992 {\color{magenta}\omega^2}$, where ${\color{magenta}\omega}$ is the acentric factor of $CO_2$ molecules and is equal to 0.239.
+	The quantity ${\color{black}\alpha}\left({\color{black}T}\left(t,z\right)\right)$ is a dimensionless correction term that depends on the temperature ${\color{black}T}\left(t,z\right)$ and a constant ${\color{black}\kappa}$.
+The constant ${\color{black}\kappa}$ is given by the formula ${\color{black}\kappa} = 0.37464 + 1.54226 {\color{black}\omega} - 0.26992 {\color{black}\omega^2}$, where ${\color{black}\omega}$ is the acentric factor of $CO_2$ molecules and is equal to 0.239.
 
-%	Using the physical constants $\varphi_{Z} = \left(R,T_c_{CO_2},P_c{CO_2},\kappa{CO_2}\right)$, we can represent the compressibility ${\color{orange}\overline{Z}}\left({\color{blue}T}(t,z), {\color{red}P}(t) \mid \varphi{Z}\right)$ as a function of temperature and pressure with their complete set of functional dependencies and parameters.
+%	Using the physical constants $\varphi_{Z} = \left(R,T_c_{CO_2},P_c{CO_2},\kappa{CO_2}\right)$, we can represent the compressibility ${\color{black}\overline{Z}}\left({\color{black}T}(t,z), {\color{black}P}(t) \mid \varphi{Z}\right)$ as a function of temperature and pressure with their complete set of functional dependencies and parameters.
 
@@
 
-	The density of the fluid phase, denoted by ${\color{orange}\rho_f}$, is assumed to be equal to the density of the solvent at a given temperature and pressure.
-Since the temperature ${\color{blue}T}(t,z)$ of the fluid phase is a modelled variable, the density can vary both along the bed and in time.
+	The density of the fluid phase, denoted by ${\color{black}\rho_f}$, is assumed to be equal to the density of the solvent at a given temperature and pressure.
+Since the temperature ${\color{black}T}(t,z)$ of the fluid phase is a modelled variable, the density can vary both along the bed and in time.
 Using the definition of compressibility, the following expression for the density can be obtained:
@@
 		\begin{equation} \label{eq: Density}
-			{\color{orange}\rho_f} \left({\color{blue}T}(t,z),{\color{red}P}(t) \right) = \frac{{\color{red}P}(t) {\color{magenta}M_{CO_2}}}{{\color{magenta}R}{\color{blue}T}(t,z){\color{orange}Z}\left({\color{blue}T}(t,z),{\color{red}P}(t) \right)},
+			{\color{black}\rho_f} \left({\color{black}T}(t,z),{\color{black}P}(t) \right) = \frac{{\color{black}P}(t) {\color{black}M_{CO_2}}}{{\color{black}R}{\color{black}T}(t,z){\color{black}Z}\left({\color{black}T}(t,z),{\color{black}P}(t) \right)},
 	\end{equation}}
 
-	where ${\color{magenta}M_{CO_2}}$ denotes the molar mass of $CO_2$, and ${\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ is the compressibility factor that solves Eq.
+	where ${\color{black}M_{CO_2}}$ denotes the molar mass of $CO_2$, and ${\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ is the compressibility factor that solves Eq.
 \eqref{eq: Compressibility}.
 This means that the density of the fluid depends on both space and time, due to its dependence on temperature and pressure.
-%	, and it can be expressed in terms of a set of physical constants, denoted by $\varphi{\rho_\text{F}} = \left({\color{magenta}R}, {\color{magenta}M_{CO_2}}, {\color{magenta}T_c{CO_2}}, {\color{magenta}P_c{CO_2}}, {\color{magenta}\omega{CO_2}}\right)$.
+%	, and it can be expressed in terms of a set of physical constants, denoted by $\varphi{\rho_\text{F}} = \left({\color{black}R}, {\color{black}M_{CO_2}}, {\color{black}T_c{CO_2}}, {\color{black}P_c{CO_2}}, {\color{black}\omega{CO_2}}\right)$.
 
@@
 	%The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state, again under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}.
-The main steps in the derivation of ${\color{orange}C_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ are presented below:
+The main steps in the derivation of ${\color{black}C_p}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ are presented below:
 	Following the work of \citet{Pratt2001}, it is assumed that the specific heat can be obtained as a sum of ideal gas contribution and a residual correction for non-ideal behaviour, as given by Equations \ref{eq: Cv_CO2} and \ref{eq: Cp_CO2}.
@@
 	\begin{subequations}\begin{align}
-			{\color{orange}C_v}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) & = {\color{orange}C_v^{\text{I}}}\left({\color{blue}T}(t,z),P(t)\right) + {\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) \label{eq: Cv_CO2}; \\
-			{\color{orange}C_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) & = \underbrace{{\color{orange}C_p^{\text{I}}}\left({\color{blue}T}(t,z),P(t)\right)}_{\text{Eq.
-} \eqref{eq: Cp_I}} + \underbrace{{\color{orange}C_p^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}_{\text{Eq.
+			{\color{black}C_v}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) & = {\color{black}C_v^{\text{I}}}\left({\color{black}T}(t,z),P(t)\right) + {\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) \label{eq: Cv_CO2}; \\
+			{\color{black}C_p}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) & = \underbrace{{\color{black}C_p^{\text{I}}}\left({\color{black}T}(t,z),P(t)\right)}_{\text{Eq.
+} \eqref{eq: Cp_I}} + \underbrace{{\color{black}C_p^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}_{\text{Eq.
 } \eqref{eq: Cp_R}}  \label{eq: Cp_CO2}.
@@
 
-	${\color{orange}C_v}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}C_p}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ are the specific heat of $CO_2$ at constant volume and pressure, respectively.
+	${\color{black}C_v}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ and ${\color{black}C_p}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ are the specific heat of $CO_2$ at constant volume and pressure, respectively.
 
-	The ideal-gas contribution ${\color{orange}C_v^{\text{I}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$ and ${\color{orange}C_p^{\text{I}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)$, can be obtained based on heat-capacity data applicable to gases at low pressure.
-For $CO_2$, the ideal gas contribution to the specific heat at constant ${\color{red}P}(t)$, as function of ${\color{blue}T}(t,z)$ is given by,
+	The ideal-gas contribution ${\color{black}C_v^{\text{I}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ and ${\color{black}C_p^{\text{I}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$, can be obtained based on heat-capacity data applicable to gases at low pressure.
+For $CO_2$, the ideal gas contribution to the specific heat at constant ${\color{black}P}(t)$, as function of ${\color{black}T}(t,z)$ is given by,
 
@@
 	\begin{equation}
-		{\color{orange}C_p^{\text{I}}}\left({\color{blue}T}(t,z),P(t)\right) = {\color{magenta}C_{P0}} + {\color{magenta}C_{P1}}T(t,z) + {\color{magenta}C_{P2}}{\color{blue}T}^2(t,z) + {\color{magenta}C_{P3}}{\color{blue}T}^3(t,z) \label{eq: Cp_I}
+		{\color{black}C_p^{\text{I}}}\left({\color{black}T}(t,z),P(t)\right) = {\color{black}C_{P0}} + {\color{black}C_{P1}}T(t,z) + {\color{black}C_{P2}}{\color{black}T}^2(t,z) + {\color{black}C_{P3}}{\color{black}T}^3(t,z) \label{eq: Cp_I}
 	\end{equation} }
 
-	where the coefficients ({\color{red}REF}) of the expansion are ${\color{magenta}C_{P0}} = 4.728$, ${\color{magenta}C_{P1}} = 1.75 \times 10^{-3}$, ${\color{magenta}C_{P2}} = -1.34 \times 10^{-5}$, and ${\color{magenta}C_{P3}} = 4.10 \times 10^{-9}$.
+	where the coefficients of the expansion are ${\color{black}C_{P0}} = 22.26$, ${\color{black}C_{P1}} = 5.981 \times 10^{-2}$, ${\color{black}C_{P2}} = -3.501 \times 10^{-5}$, and ${\color{black}C_{P3}} = 7.469 \times 10^{-9}$, as given by \citet{Kyle1999}.
 
-	The correction term ${\color{orange}C_p^{\text{R}}}\left({\color{blue}T}(t,z){\color{red}P}(t)\right)$ at constant pressure ${\color{red}P}(t)$, can be defined by introducing  ${\color{orange}C_p^{\text{I}}}({\color{blue}T}(t,z)) - {\color{orange}C_v^{\text{I}}}({\color{blue}T}(t,z)) = {\color{magenta}R}$ and using the definition of ${\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z){\color{red}P}(t)\right)$.
+	The correction term ${\color{black}C_p^{\text{R}}}\left({\color{black}T}(t,z){\color{black}P}(t)\right)$ at constant pressure ${\color{black}P}(t)$, can be defined by introducing  ${\color{black}C_p^{\text{I}}}({\color{black}T}(t,z)) - {\color{black}C_v^{\text{I}}}({\color{black}T}(t,z)) = {\color{black}R}$ and using the definition of ${\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z){\color{black}P}(t)\right)$.
 The general form of the correction term is given by Equation \ref{eq: Cp_R}
@@
 	\begin{align}
-		&{\color{orange}C_p^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) = \underbrace{{\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}_{\text{Eq.
+		&{\color{black}C_p^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) = \underbrace{{\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}_{\text{Eq.
 }\eqref{eq: CvR}} \nonumber \\
-		&+ {\color{blue}T}(t,z) \underbrace{\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)}}_{\text{Eq.
-} \eqref{eq: dPdT}} \underbrace{\left(\cfrac{\partial {\color{orange}v_m}\left({\color{blue}T}(t,z),{\color{red}P}(t)\right)}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)}}_{\text{Eq.
-} \eqref{eq: dVdT}} - {\color{magenta}R}.
+		&+ {\color{black}T}(t,z) \underbrace{\left(\cfrac{\partial {\color{black}P}(t)}{\partial {\color{black}T}}\right)_{{\color{black}v_m}(t,z)}}_{\text{Eq.
+} \eqref{eq: dPdT}} \underbrace{\left(\cfrac{\partial {\color{black}v_m}\left({\color{black}T}(t,z),{\color{black}P}(t)\right)}{\partial {\color{black}T}}\right)_{{\color{black}P}(t)}}_{\text{Eq.
+} \eqref{eq: dVdT}} - {\color{black}R}.
 \label{eq: Cp_R}
@@
 
-%	The braced terms are obtained from the chosen equation of state and the compressibility definition ${\color{red}P}(t) {\color{orange}v_m}({\color{blue}T}(t,z),{\color{red}P}(t)) = {\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right){\color{magenta}R}{\color{blue}T}(t,z)$.
+%	The braced terms are obtained from the chosen equation of state and the compressibility definition ${\color{black}P}(t) {\color{black}v_m}({\color{black}T}(t,z),{\color{black}P}(t)) = {\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right){\color{black}R}{\color{black}T}(t,z)$.
 \\
 
-	For the partial derivative of the volume with respect to temperature ${\color{blue}T}(t,z)$ at constant pressure ${\color{red}P}(t)$, we have
+	For the partial derivative of the volume with respect to temperature ${\color{black}T}(t,z)$ at constant pressure ${\color{black}P}(t)$, we have
 
@@
 	\begin{align}
-		\left( \cfrac{\partial {\color{orange}v_m}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)} &= \cfrac{{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right) {\color{magenta}R}}{{\color{red}P}(t)} \nonumber \\
-		&+ \cfrac{{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{red}P}(t)} \underbrace{\left( \cfrac{\partial {\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{\partial {\color{blue}T}} \right)_{{\color{red}P}(t)}}_{\text{Eq.
+		\left( \cfrac{\partial {\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{\partial {\color{black}T}} \right)_{{\color{black}P}(t)} &= \cfrac{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) {\color{black}R}}{{\color{black}P}(t)} \nonumber \\
+		&+ \cfrac{{\color{black}R}{\color{black}T}(t,z)}{{\color{black}P}(t)} \underbrace{\left( \cfrac{\partial {\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{\partial {\color{black}T}} \right)_{{\color{black}P}(t)}}_{\text{Eq.
 }\eqref{eq: dZdT}} \label{eq: dVdT}
@@
 
-	with partial derivative of the compressibility factor with respect to temperature ${\color{blue}T}(t,z)$ at constant pressure ${\color{blue}P}(t)$
+	with partial derivative of the compressibility factor with respect to temperature ${\color{black}T}(t,z)$ at constant pressure ${\color{black}P}(t)$
 
@@
 	\begin{equation}
-		\left(\cfrac{\partial{\color{orange}Z}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} = \left(\cfrac{\partial \dfrac{{\color{red}P}(t) {\color{orange}v_m}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}{{\color{magenta}R}{\color{blue}T}(t,z)}}{\partial {\color{blue}T}}\right)_{{\color{red}P}(t)} \label{eq: dZdT}
+		\left(\cfrac{\partial{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{\partial {\color{black}T}}\right)_{{\color{black}P}(t)} = \left(\cfrac{\partial \dfrac{{\color{black}P}(t) {\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}R}{\color{black}T}(t,z)}}{\partial {\color{black}T}}\right)_{{\color{black}P}(t)} \label{eq: dZdT}
 	\end{equation} }
@@
 	\begin{equation}
-		\left(\cfrac{\partial {\color{red}P}(t)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{orange}Z}{\color{magenta}R}{\color{blue}T}(t,z)}{{\color{orange}v_m}\left({\color{blue}T}(t,z), {\color{red}P}(t)\right)}}}{\partial{\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} \label{eq: dPdT}
+		\left(\cfrac{\partial {\color{black}P}(t)}{\partial {\color{black}T}}\right)_{{\color{black}v_m}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{black}Z}{\color{black}R}{\color{black}T}(t,z)}{{\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}}}{\partial{\color{black}T}}\right)_{{\color{black}v_m}(t,z)} \label{eq: dPdT}
 	\end{equation} }
@@
 	\begin{equation}
-		{\color{orange}C_v^{\text{R}}}\left({\color{blue}T}(t,z),{\color{red}P}(t)\right) = \left(\cfrac{\partial{\color{orange}U^{\text{R}}}\left({\color{blue}T}(t,z),{\color{red}P}(t)\right)}{\partial {\color{blue}T}}\right)_{{\color{orange}v_m}(t,z)} \label{eq: CvR}
+		{\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z),{\color{black}P}(t)\right) = \left(\cfrac{\partial{\color{black}U^{\text{R}}}\left({\color{black}T}(t,z),{\color{black}P}(t)\right)}{\partial {\color{black}T}}\right)_{{\color{black}v_m}(t,z)} \label{eq: CvR}
 	\end{equation} }
 
-	%By denoting the physical constants as $\varphi_{C_p^{\text{F}}} = ({\color{magenta}R}, {\color{magenta}M},\\ {\color{magenta}T_c}, {\color{magenta}P_c}, {\color{magenta}\omega})$, we get the spatio-temporal representation \\$C_p^{\text{F}}\left(T(t,z),P(t) \mid \varphi_{C_p^{\text{F}}}\right)$ of the specific heat of the fluid phase.
+	%By denoting the physical constants as $\varphi_{C_p^{\text{F}}} = ({\color{black}R}, {\color{black}M},\\ {\color{black}T_c}, {\color{black}P_c}, {\color{black}\omega})$, we get the spatio-temporal representation \\$C_p^{\text{F}}\left(T(t,z),P(t) \mid \varphi_{C_p^{\text{F}}}\right)$ of the specific heat of the fluid phase.
 
@@
 
-	For example, to evaluate the enthalpy change between two points, $h(V_1,T_1)$ and $h(V_2,T_2)$, we first calculate the enthalpy departure function between the initial volume $V_1$ and infinite volume at temperature $T_1$.
-We then add to that the ideal gas enthalpy change due to the temperature change from $T_1$ to $T_2$, and finally subtract the departure function value between the final volume $V_2$ and infinite volume.
+	To evaluate the enthalpy change between two points, $h(V_1,T_1)$ and $h(V_2,T_2)$, the enthalpy departure function between the initial volume $V_1$ and infinite volume at temperature $T_1$ is calculated.
+Then it is added to that the ideal gas enthalpy change due to the temperature change from $T_1$ to $T_2$, and finally subtract the departure function value between the final volume $V_2$ and infinite volume.
 

### 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Experiments.tex
11.10

--- 2023-10-02 SFE_article_Parameter_Estimation/Sections/Experiments.tex
@@
 
-	%The results of experiments are presented in the Table \ref{tab: Yield_data}.
-
-%	\begin{table}[!h]
-%		\centering
-%		\adjustbox{max width=\columnwidth}{%
-%			\csvautobooktabular{Figures/Results_estimation/Dataset.csv} }
-%		\caption{Yield data; cumulative amount of solute [g] collected every 5 min}
-%		\label{tab: Yield_data}
-%	\end{table}
+	\begin{figure}[!h]
+		\centering
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
+			\caption{Experiment at $40~^\circ C$ and 200 bar}
+		\end{subfigure}
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
+			\caption{Experiment at $50~^\circ C$ and 200 bar}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
+			\caption{Experiment at $40~^\circ C$ and 300 bar}
+		\end{subfigure}
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
+			\caption{Experiment at $50~^\circ C$ and 300 bar}
+		\end{subfigure}
+		\caption{Results of parameter estimation}
+		\label{fig: estimation_results}
+	\end{figure}
 

### 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Gouverning_equation_derivation.tex
11.10

--- 2023-05-07 SFE-article/Sections/Gouverning_equation_derivation.tex
@@
 The assumption of quasi-one-dimensional flow dictates that the flow properties are a function of $z$ only.
-The equations described by quasi-one-dimensional assumption hold: (1) mass conservation, (2) Newton's second law, and (3) energy conservation.
-The modified governing equation can be derived to ensure that these physical principles are satisfied.	Let's start with the integral form of the continuity equation:
+The integral form of the continuity equation is:
 
@@
 
-	We apply this equation to the shaded control volume shown in Fig. \ref{fig: control_volume}.
+	We apply this equation to the shaded control volume shown in Figure \ref{fig: control_volume}.
 
@@
 
-	This control volume is a slice of an extractor, where the infinitesimal thickness of the slice is $dz$.
 	 On the left side of the control volume, consistent with the quasi-one-dimensional assumptions, the density, velocity, pressure, and internal energy denoted by $\rho_f$, $v$, $P$, and $e$, respectively, are uniform over the area $A$.
 Similarly, on the right side of the control volume, the density, velocity, pressure, and internal energy $\rho_f+d\rho_f$, $v+dv$, $P+dP$, and $e+de$, respectively, are uniform over the area available for fluid phase $A_f+dA_f$.
-Applied to the control volume in Fig.
-\ref{fig: control_volume}, the volume integral in Eq.
-\ref{EQ: Continuity_integral_general} becomes, in the limit as $dz$ becomes very small,
+Applied to the control volume in Figure \ref{fig: control_volume}, the volume integral in Equation \ref{EQ: Continuity_integral_general} becomes, in the limit as $dz$ becomes very small,
 
@@
 
-	where $A~dz$ is the volume of the control volume in the limit of $dz$ becoming vanishingly small. The surface integral in Eq. \ref{EQ: Continuity_integral_general} becomes
+	where $A~dz$ is the volume of the control volume in the limit of $dz$ becoming vanishingly small. The surface integral in Equation \ref{EQ: Continuity_integral_general} becomes
 
@@
 
-	In the limit as $dz$ becomes very small, the terms involving products of the differential in Eq.
-\ref{EQ: Triple_Prod_Cont_Surf}, such as $\rho_f dv dA_f,~d\rho_f dv dA_f$, go to zero much faster than those terms involving only one differential.
+	In the limit as $dz$ becomes very small, the terms involving products of the differential in Equation \ref{EQ: Triple_Prod_Cont_Surf}, such as $\rho_f dv dA_f,~d\rho_f dv dA_f$, go to zero much faster than those terms involving only one differential.
 Hence, all terms involving products of differentials can be dropped, yielding in the limit as $dz$ becomes very small
@@
 	The above partial differential equation form of the continuity equation is suitable for unsteady, quasi-one-dimensional flow.
-It ensures that mass is conserved for this mode of flow.
-The $A_f(z)$ is an arbitrary function that describes a change in the cross-section of an extractor.
-The function $A_f(z)$ can be defined as $A_f(z) = \textbf{A} \phi(z)$, where $\phi$ is the bed porosity and $\textbf{A}$ is the cross-section of an empty extractor.
+The $A_f(z)$ is an arbitrary function that describes a change in the extractor's cross-section and can be defined as $A_f(z) = \textbf{A} \phi(z)$, where $\phi$ is the bed porosity and $\textbf{A}$ is the cross-section of an empty extractor.
 
@@
 
-	\hrule
-
 	\subsubsection{Transport of a species}
 
-	The transport of a chemical species, in this case, a solute, can be described by an analogous equation to the Eq.
-\ref{EQ: Continuity_integral_general} with additional terms on the right-hand side.
-The first term on the right-hand side describes that a substance goes from high-density regions to low-density regions and is based on the Fick's law $\left( J_{diff} = D_e^M\frac{\partial c_f}{\partial z} \right)$.
+	The transport of a solute, can be described by an analogous equation to the Equation \ref{EQ: Continuity_integral_general} with additional terms on the right-hand side.
+The first term on the right-hand side describes diffusional movement of species and is based on the Fick's law $\left( J_{diff} = D_e^M\frac{\partial c_f}{\partial z} \right)$.
 The other term corresponds to the mass transfer between solid and fluid phases, which is treated as a source term.
@@
 
-	By substituting the equations derived above into Eq. \ref{EQ: Integral_Mass_Species_general} we obtain
+	By substituting the equations derived above into Equation \ref{EQ: Integral_Mass_Species_general} we obtain
 
@@
 
-	The Eq. \ref{EQ: Simplified_Species_Conservation} is equivalent to the equation presented by \citet{Reverchon1996}.
-
-	\hrule
+	The Equation \ref{EQ: Simplified_Species_Conservation} is equivalent to the equation presented by \citet{Reverchon1996}.
 
@@
 
-	We the momentum conservation to the shaded control volume in Fig.
-\ref{fig: control_volume}, the integrals on the left side are evaluated in the same manner as discussed above in the regard to the continuity equation.
+	We the momentum conservation to the shaded control volume in Figure \ref{fig: control_volume}, the integrals on the left side are evaluated in the same manner as discussed above in the regard to the continuity equation.
 That is,
@@
 
-	The evaluation of the pressure force term on the right side of Eq.
-\ref{EQ: Momentum_Integral_Form} can be understood based on the Fig.
-\ref{fig: Forces_Momentum_Control_Volume}.
+	The evaluation of the pressure force term on the right side of Equation \ref{EQ: Momentum_Integral_Form} can be understood based on the Figure \ref{fig: Forces_Momentum_Control_Volume}.
 Here, the $z$ components of the vector $PdS$ are shown on all four sides of the control volume.
@@
 Any $z$ component that acts toward the right (in the positive $z$ direction) is a positive quantity.
-Also note that the $z$ component of $P\textbf{dS}$ acting on the top and the bottom inclined faces of the control volume in Fig.
-\ref{fig: Forces_Momentum_Control_Volume} can be expressed as the pressure $P$ acting on the component of the inclined is projected perpendicular to the $z$ direction, $dA_f/2$; hence, the contribution of each inclined face (top or bottom) to the pressure integral in Eq.
-\ref{EQ: Momentum_Integral_Form} is $-P(dA_f/2)$.
-All together, the right-hand side of Eq.
-\ref{EQ: Momentum_Integral_Form} is expressed as follows:
+Also note that the $z$ component of $P\textbf{dS}$ acting on the top and the bottom inclined faces of the control volume in Figure \ref{fig: Forces_Momentum_Control_Volume} can be expressed as the pressure $P$ acting on the component of the inclined is projected perpendicular to the $z$ direction, $dA_f/2$; hence, the contribution of each inclined face (top or bottom) to the pressure integral in Equation \ref{EQ: Momentum_Integral_Form} is $-P(dA_f/2)$.
+All together, the right-hand side of Equation \ref{EQ: Momentum_Integral_Form} is expressed as follows:
 
@@
 
-	Substituting Eqs. \ref{EQ: Force_Continuity_Monenmtum} to \ref{EQ: Force_Integral_Varying_Cross_Section} into Eq. \ref{EQ: Momentum_Integral_Form}, we have
+	Substituting Eqs. \ref{EQ: Force_Continuity_Monenmtum} to \ref{EQ: Force_Integral_Varying_Cross_Section} into Equation \ref{EQ: Momentum_Integral_Form}, we have
 
@@
 
-	The Eq. \ref{EQ: Conservative_Momentum} can be expanded further by assuming that $A_f = \textbf{A}\phi$
+	The Equation \ref{EQ: Conservative_Momentum} can be expanded further by assuming that $A_f = \textbf{A}\phi$
 
@@
 
-	Eq.
-\ref{EQ: Conservative_Momentum} represents the conservative form of the momentum equation for the quasi-one-dimensional flow.
-The equivalent non-conservative form can be obtained by multiplying the continuity equation by $v$ and subtracting it from Eq.
-\ref{EQ: Conservative_Momentum}
+	Equation \ref{EQ: Conservative_Momentum} represents the conservative form of the momentum equation for the quasi-one-dimensional flow.
+The equivalent non-conservative form can be obtained by multiplying the continuity equation by $v$ and subtracting it from Equation \ref{EQ: Conservative_Momentum}
 
@@
 
-	The Eq.
-\ref{EQ: Non-conservative_Momentum} is stylistically the same as the general momentum conservation for one-dimensional flow with no-body forces.
+	The Equation \ref{EQ: Non-conservative_Momentum} is stylistically the same as the general momentum conservation for one-dimensional flow with no-body forces.
 The momentum equation can be expressed in terms of superficial velocity $u=v\phi$.
@@
 
-	The Eq. \ref{EQ: Non-conservative_Momentum_Const_Porosity} represents the non-conservative form of the momentum equation for quasi-one-dimensional flow with no body forces and constant porosity.
+	The Equation \ref{EQ: Non-conservative_Momentum_Const_Porosity} represents the non-conservative form of the momentum equation for quasi-one-dimensional flow with no body forces and constant porosity.
 
@@
 
-	Applied to the shaded control volume in Fig.
-\ref{fig: control_volume}, and keeping in mind the pressure forces shown in Fig.
-\ref{fig: Forces_Momentum_Control_Volume}, Eq.
-\ref{EQ: Energy_equation_integral} becomes
+	Applied to the shaded control volume in Figure \ref{fig: control_volume}, and keeping in mind the pressure forces shown in Figure \ref{fig: Forces_Momentum_Control_Volume}, Equation \ref{EQ: Energy_equation_integral} becomes
 
@@
 	Equation \ref{EQ: Energy_equation_conservative_total} is the conservation form of the energy expressed in terms of the total energy $e~+~v^2/2$, appropriate for unsteady, quasi-one-dimensional flow.
-The energy equation can be expressed in terms of internal energy if Eq.
-\ref{EQ: Conservative_Momentum} is multiplicated by $v$ and then subtracted from Eq.
-\ref{EQ: Energy_equation_conservative_total}
+The energy equation can be expressed in terms of internal energy if Equation \ref{EQ: Conservative_Momentum} is multiplicated by $v$ and then subtracted from Equation \ref{EQ: Energy_equation_conservative_total}
 
@@
 	Equation \ref{EQ: Energy_equation_nonconservative} is the non-conservative form of the energy equation expressed in terms of internal energy, appropriate to unsteady quasi-one-dimensional flow.
-The reason for obtaining the energy equation in the form of Eq.
-\ref{EQ: Energy_equation_nonconservative} is that, for a calorically perfect gas, it leads directly to a form of the energy equation in terms of temperature $T$.
+The reason for obtaining the energy equation in the form of Equation \ref{EQ: Energy_equation_nonconservative} is that, for a calorically perfect gas, it leads directly to a form of the energy equation in terms of temperature $T$.
 %	

### 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Model.tex
11.10

@@
 	 %When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{black}\phi}(z)$ (where ${\color{black}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}
-	The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function ${\color{black}A_f}(z) = {\color{black}A_f\phi}(z)$ to take into account the change of the cross-section available for the fluid.
-The cross-section change is taken into account by void fraction ${\color{black}\phi}(z)$, which depends on the spatial dimension.
+	The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function ${\color{black}A_f}(z) = {\color{black}A\phi}(z)$ to take into account the change of the cross-section available for the fluid.
 The Equation \ref{EQ: Continuity_differential} shows the differential form of the continuity equation:
@@
 	}
-	where ${\color{black} A}$ is the total cross-section of the extractor.
+	where ${\color{black} A}$ is the total cross-section of the extractor and ${\color{black}\phi}(z)$ describe porosity along the extractor.
 
@@
 
-	The detailed derivation of the mass balance equation for the fluid phase can be found in the Appendix \ref{CH: Gouverning equations}.
-The movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}) is considered only in the axial direction, while the properties of the system in the radial direction are assumed to be uniform.
+	The detailed derivation of the mass balance equation for the fluid phase can be found in Appendix \ref{CH: Gouverning equations}.
+The movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}) is considered only in the axial direction due to quasi-one-dimensional assumptions, which take into account variation of the void fraction.
+Furthermore, the thermodynamic pressure is assumed to be constant along the device as presented by Equation \ref{EQ: Pressure_Velocity}.
 Additionally, the boundary layer adjacent to the inner wall of the extractor is neglected, resulting in a constant velocity profile across any cross-section of the extractor perpendicular to the axial direction.
-Although the particle size distribution and void fraction of the solid phase may change along the extractor, they are assumed to remain constant in time.
-Furthermore, the thermodynamic pressure is assumed to be constant along the device as presented by Equation \ref{EQ: Pressure_Velocity}.
 The amount of solute in the solvent is considered negligible, resulting in the fluid phase being described as pseudo-homogeneous, and its properties are assumed to be the same as the solvent.
@@
 
-	Here, ${\color{black}c_f}(t,z), {\color{black}c_s}(t,z),$ and ${\color{black}T}(t,z)$ represent the concentration of solute in the fluid phase, the concentration of solute in the solid phase, and temperature, respectively.
-${\color{black}r_e}(t,z)$ is a mass transfer kinetic term, ${\color{black}F}(t)$ is the mass flow rate and ${\color{black}D^M_e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}F}(t))$ is the axial mass diffusion coefficient.
+	${\color{black}c_f}(t,z)$ represents the concentration of solute in the fluid phase, , ${\color{black}r_e}(t,z)$ is a mass transfer kinetic term, and ${\color{black}D^M_e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}F}(t))$ is the axial mass diffusion coefficient.
 
@@
 			\label{Model_solid}
-			%		{\scriptsize\begin{align*}
+			%		{\scriptsize\begin{equation}
 					\cfrac{\partial {\color{black}c_s}(t,z)}{\partial t} = \underbrace{ {\color{black}r_e}(t,z) }_{\text{Kinetics}}
@@
 Therefore, this factor can be understood as the fraction of the fluid's total heat through convection.
-On the other hand, the axial heat diffusion is calculated based on the definition of thermal diffusivity for the fluid, as explained in the appendix.
+On the other hand, the axial heat diffusion is calculated based on the definition of thermal diffusivity for the fluid, as explained in Appendix.
 }
@@
 
-			The heat equation was introduced in the previous chapter through Equation \ref{EQ: CompressibleEuler_3}, in the appendix \ref{CH: Gouverning equations}  as well as through Equation \ref{EQ: Heat_internal}
+			The heat governing equation describe the evolution of the energy in the system and it is given by \ref{EQ: Heat_internal}.
+The derivation of the heat equation can be found in Appendix \ref{CH: Gouverning equations}.
 
@@
 
+			The departure function is a mathematical function that characterizes the deviation of a thermodynamic property (enthalpy, entropy, and internal energy) of a real substance from that of an ideal gas at the same temperature and pressure.
+The departure function is typically defined as the difference between the value of a thermodynamic property for a real fluid and the corresponding value for an ideal gas at the same temperature and pressure.
+They are typically computed by integrating a function that depends on the equation of state and its derivatives.
 Following \citet{Elliott2011} or \citet{Gmehling2019}, a real gas internal energy definition can be obtained from the departure functions, defined through Equation \ref{EQ: internal_energy_def}.
-In thermodynamics, the departure function is a mathematical function that characterizes the deviation of a thermodynamic property of a real substance from that of an ideal gas at the same temperature and pressure.
-The departure function is typically defined as the difference between the value of a thermodynamic property for a real fluid and the corresponding value for an ideal gas at the same temperature and pressure.
-Common departure functions include those for enthalpy, entropy, and internal energy.
-They are typically computed by integrating a function that depends on the equation of state and its derivatives.
-More information on the departure functions can be found in appendix \ref{CH:Enthalpy}.
+More information on the departure functions can be found in Appendix \ref{CH:Enthalpy}.
 
@@
 			The main advantage of this formulation is the presence of term $\partial {\color{black}P}(t) / \partial t $, which allows it to directly affect the system through the change of thermodynamic pressure (which is a control variable).
-If an equation of state is known, the temperature can to be recovered from the enthalpy.
 The enthalpy is related to the pressure and temperature through the following equation:
@@
 			If the value of enthalpy is known from the time evolution and pressure can be measured, then the Equation \ref{EQ:Enthalpy_root} can be solved for the temperature to recover the temperature profile.
-By applying the departure functions to Peng-Robinson equation of state, the relation \ref{EQ:Enthalpy_root} can be expressed directly through Equation \ref{EQ:Enthalpy_PR} as presented in \ref{CH:Enthalpy} or given by \citet{Gmehling2019}.
+For the Peng-Robinson EoS, the enthalpy can be defined by Equation \ref{EQ:Enthalpy_PR}.
+More details can be found in Appendix \ref{CH:Enthalpy} or given by \citet{Gmehling2019}.
 
@@
 
-			As discussed by \citet{Gmehling2019}, special attention should be paid to high pressures systems, so the influence of the intermolecular forces on the enthalpy is taken into account.
+			As discussed by \citet{Gmehling2019}, the influence of the intermolecular forces on the enthalpy is needs to taken into account in high pressures systems.
 In most cases, these forces are attractive, so additional energy is necessary to move the molecules away from each other, that is, to lower the density.
@@
 		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{black}c_{s0}}$.
-On the other hand, the solute concentration in the fluid phase should not follow the same assumption as the solid phase.
 Every SFE system needs some time to reach the desired operating conditions but the solute diffuses from solid phase to the fluid phase already at the preparation stage.
-For instance, a pump introduce more and more fluid to the extractor to increase the pressure, which makes the fluid present already in that vessel to moves internally hence the solute in the fluid phase is non-uniformly distributed.
+For instance, a pump introduce more fluid to the extractor to increase the pressure, which makes the fluid present already in that vessel to moves internally hence the solute in the fluid phase is non-uniformly distributed.
 Some conclusions can be drawn from the analysis of the initial part of each yield curve obtained from the laboratory (Figure \ref{fig: estimation_results}).
-It can be noticed that each curve at the beginning has a curvature, which is not linear.
-Generally, a quadratic function could approximate the initial part of each extraction curve.
+It can be noticed that each curve at the beginning has a non-linear curvature.
+A quadratic function could approximate the initial part of each extraction curve.
 A function that, after integration, gives a quadratic-like result is a straight line.
@@
 		{\footnotesize
-			\begin{subequations}
-				\begin{align*}
-					{\color{black}c_f}(t = 0, z) &= H(z)   \\
-					{\color{black}c_s}(t = 0, z) &= {\color{black}c_{s0}} \\
-					{\color{black}h}(t = 0, z) &= {\color{black}h_0}
-				\end{align*}
-		\end{subequations} }
+				\begin{equation*}
+					{\color{black}c_f}(t = 0, z) = H(z) \quad {\color{black}c_s}(t = 0, z) = {\color{black}c_{s0}} \quad {\color{black}h}(t = 0, z) = {\color{black}h_0}
+				\end{equation*} }
 
@@
 
-		where ${\color{black}\Theta}$ is a paramter space consisting of model parameters ${\color{black}\theta}$ and controls ${\color{black}u}$, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.
+		where ${\color{black}\Theta}$ is a paramter space, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.
 
-		Each function ${\color{black}\bar{\phi_i}}$ is transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{black}G}_{i\times N_z+1}$ to ${\color{black}G}_{(i+1)\times N_z}$, where $i$ corresponds to the process model equation.
+		Function ${\color{black}\bar{\phi}}$ are transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{black}G}$.
 The state-space model ${\color{black}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{black}x}}(t)$.

### 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Saturation.tex
11.10

--- 2023-10-08 SFE_article_Parameter_Estimation/Sections/Saturation.tex
@@
 	Such a formulation limits the availability of the solute in the solid phase.
-Similarly to the BIC model, this can be explained if oil is assumed to be contained in the cells, a part of which is open because the cell walls were broken by grinding, and the rest remains intact.
-The diffusion of the solute from a particle's core takes more time compared to the diffusion of the solute located close to the outer surface, considering that the internal diffusion coefficient decay as the concentration of the solute in the solid decrease.
+Similarly to the BIC model, if solute is assumed to be contained in the cells, a part of which is open because the cell walls were broken by grinding, and the rest remains intact.
+The diffusion of the solute from a particle's core takes more time compared to the diffusion of the solute located close to the outer surface.
+Considering that the internal diffusion coefficient decay as the concentration of the solute in the solid decrease.
 As the value of the ${\color{black}c_s}$ decrease over time, the exponential term approach unity and $\lim_{ {\color{black}c_s} \rightarrow 0} {\color{black}D_i} =  {\color{black}D_i^R}$.

### 2023-10-31 SFE_article_Parameter_Estimation/Sections/Results.tex
31.10

@@
 		\adjustbox{max width=\columnwidth}{%
-			\csvautobooktabular[separator=comma, table head = \toprule & $40~^\circ C$ & $50~^\circ C$ & $40~^\circ C$ & $50~^\circ C$ \\ & $200~bar$ & $200~bar$ & $300~bar$ & $300~bar$ \\\midrule]{Figures/Results_estimation/estimation_2.csv} }
+			\csvautobooktabular[separator=comma, table head = \toprule & $40~^\circ C$ & $50~^\circ C$ & $40~^\circ C$ & $50~^\circ C$ \\ & $200~bar$ & $200~bar$ & $300~bar$ & $300~bar$ \\\midrule]{Figures/Results_estimation/estimation.csv} }
 		\caption{Parameter estimation results}
@@
 			\centering
-			\includegraphics[trim = 11.2cm 13.7cm 11cm 1.0cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
+			\includegraphics[trim = 10.5cm 14.0cm 10.0cm 1.0cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
 			\caption{Dependency of ${\color{black}D_i}$}
@@
 			\centering
-			\includegraphics[trim = 3.5cm 7.7cm 18.7cm 7.3cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
+			\includegraphics[trim = 3.0cm 7.9cm 17.7cm 7.7cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
 			\caption{Dependency of ${\color{black}\Upsilon}$}
@@
 		\begin{subfigure}[b]{0.49\columnwidth}
-			\includegraphics[trim = 1.0cm 0cm 3cm 0cm, clip, width=\columnwidth]{/Results_estimation/D_i_Uppsilon_results.pdf}
+			\includegraphics[trim = 1.0cm 0cm 2.0cm 0cm, clip, width=\columnwidth]{/Results_estimation/D_i_Uppsilon_results.pdf}
 			\caption{Dependency of ${\color{black}D^R_i}$}
@@
 			\centering
-			\includegraphics[trim = 19.0cm 13.8cm 3.5cm 1.0cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_D_e.pdf}
+			\includegraphics[trim = 18.0cm 14.0cm 2.5cm 1.0cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_RE_order_1.pdf}
 			\caption{Dependency of ${\color{black}D^M_e}$}

### 2023-10-31 SFE_SEnsitivity_Analysis/Decay_Function_Coe.m

@@ -1,5 +1,5 @@
 function [Upsilon] = Decay_Function_Coe(rho)
 
-    Upsilon  = 0.0117 .* rho - 9.176;
+    Upsilon  = 0.01138 .* rho - 8.723;
 
 end

### 2023-10-31 SFE_SEnsitivity_Analysis/modelSFE.m

@@ -68,12 +68,11 @@ function xdot = modelSFE(x, p, mask, dt)
     %Cf_0          =     if_else(F_u == 0, FLUID(1), 0);
     Cf_0          =     0;
     Cf_B          =     FLUID(nstages_index);
-
-    T_0 = if_else( mode == 2, TEMP(1), T_u );                                             % If the sensitivity of P is consider, then set the input T as equal to the T insdie of the extractor
+                                                                                          % If the sensitivity of P and F is consider, then set the input T as equal to the T insdie of the extractor
                                                                                           % to avoid different T at the inlet and inside of the extractor
-    %T_0           =     TEMP(1);
-    T_0 = if_else( mode == 3, TEMP(1), T_u );
-
+    %T_0 = if_else( mode == 1, T_u, TEMP(1));
+    T_0 = TEMP(1);
+    
     T_B           =     TEMP(nstages_index);
 
     Z_0           =     Compressibility(T_0, PRESSURE,     parameters);
@@ -87,8 +86,8 @@ function xdot = modelSFE(x, p, mask, dt)
 
     H_0           =     SpecificEnthalpy(T_0, PRESSURE, Z_0, rho_0, parameters );   
 
-    %enthalpy_rho_0 = rho_0 .* H_0;
-    enthalpy_rho_0 = if_else( mode == 3, ENTHALPY_RHO(1), rho_0 .* H_0 );
+    %enthalpy_rho_0 = if_else( mode == 1, rho_0 .* H_0, ENTHALPY_RHO(1) );
+    enthalpy_rho_0 = rho_0 .* H_0;
     
     %% Derivatives
 

### 2023-11-01 SFE_Economic_Optimization/Heat_Exchanger_estimation.m
01.11

@@ -1,4 +1,4 @@
-function [T_w_out, T_c_out, Cost] = Heat_Exchanger_estimation(T_out_compressor, feedPress, Parameters)
+function [T_w_out, T_c_out, Cost] = Heat_Exchanger_estimation(T_out_compressor, P, Parameters)
 
     % epsilon-NTU method is used to determin the outlet temperatures if the
     % heat transfer area, inner daimeter of the inner diamter of tube, 
@@ -7,8 +7,8 @@ function [T_w_out, T_c_out, Cost] = Heat_Exchanger_estimation(T_out_compressor, 
     % streams (temperature, flow rate and heat capacity). Later the heat
     % exchnager cost is estimated.
 
-    Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
-    Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model 
+    Parameters_table        = readtable('Parameters.csv') ;                 % Table with prameters
+    Parameters              = num2cell(Parameters_table{:,3});              % Parameters within the model 
 
     %% Heat exchnager properties
     D_i     = 4.094e-2;       % m - inner diamter of tube
@@ -30,7 +30,7 @@ function [T_w_out, T_c_out, Cost] = Heat_Exchanger_estimation(T_out_compressor, 
     Deo     = D_o - D_io;
 
     %% fluid outside - water
-    F_c     = 0.5;        % kg/s
+    F_c     = 0.75;        % kg/s
     
     T_c_in  = 50+273;       % C
 
@@ -53,21 +53,20 @@ function [T_w_out, T_c_out, Cost] = Heat_Exchanger_estimation(T_out_compressor, 
     %% fluid inside - co2
     F_w     = 0.6;    % kg/s % TODO: get the F from the simulation
     T_w_in  = T_out_compressor;      % C
-    feedPress = feedPress;
-
+    
     % properties of co2 at the highest T
-    Z_in     = Compressibility( T_w_in, feedPress,               Parameters );
-    rho_in   = rhoPB_Comp(      T_w_in, feedPress, Z_in,         Parameters );
-    CP_in    = SpecificHeatComp(T_w_in, feedPress, Z_in, rho_in, Parameters );         % [J/kg/K]
-    k_in     = HeatConductivity_Comp(T_w_in, rho_in)*1e-3;                             % [ 10^-3 (W / m * K) ] -> (W / m * K)
[…]

### 2023-11-01 SFE_Economic_Optimization/main_Economic_Optimization.m

@@ -91,13 +91,13 @@ F                       = buildIntegrator(f, [Nx,Nu] , timeStep_in_sec);
 
 %% Set operating conditions
 feedPress               = 200;                                                          % pressure in the extractor [bar]
-massFlow                = 0.06;                                                         % mass flow rate in kg/s
+massFlow                = 0.02;                                                         % mass flow rate in kg/s
 
 %% compressor
-T_out_compressor        = Pump_estimation(10+273, 70, feedPress, massFlow, Parameters);
+[T_out_compressor, W_com, Comp_cost] = Pump_estimation(10+273, 70, feedPress, massFlow, Parameters);
 
 %% heat exchanger
-[T_w_out, T_c_out]      = Heat_Exchanger_estimation(T_out_compressor, feedPress, Parameters);
+[T_w_out, T_c_out, HX_cost] = Heat_Exchanger_estimation(T_out_compressor, feedPress, Parameters);
 T0homog                 = full(T_w_out);                           
 
 %% Extractor
@@ -114,10 +114,11 @@ feedFlow                = massFlow * ones(1,length(Time_in_sec));               
 
 uu                      = [feedTemp', feedPress', feedFlow'];
 
-%% 260 < Re < 320
+%% Re range: 584(40C, 300bar) < 631(50C, 300bar) < 718(40C 200bar) < 795(50C, 200bar) for empty pipe acc to Aspen
 VELOCITY                = Velocity(massFlow, rho, Parameters);
 mu                      = Viscosity(T0homog, rho);
-Re                      = (2*r) .* rho .* (VELOCITY .* epsi) ./ mu;
+Re                      = (2*r) .* VELOCITY ./ (mu / rho);
+keyboard
 
 %% Set inital state and inital conditions
 msol_max                = m_total;                                                      % g of product in solid and fluid phase

### 2023-11-01 SFE_Parameter_Estimation/main_Fitting_MegaFit.m

@@ -371,9 +371,8 @@ for ii=1:numel(DATA_set)
 
     %
     mu = Viscosity(T0homog,rho);
-    dp = 0.15;
     VELOCITY      =     Velocity(feedFlow(1), rho, Parameters);
-    Re = dp .* VELOCITY .* rho .* epsi ./ mu;
+    Re 		  = (2*r) .* VELOCITY ./ (mu / rho);
     RE = [RE, Re];
 
     % Solve for the inital guess

### 2023-11-01 SFE_SEnsitivity_Analysis/main_Sensitivity_Analysis.m

@@ -20,8 +20,8 @@ bed                     = 0.165;                                            % Pe
 
 % Set time of the simulation
 PreparationTime         = 0;
-ExtractionTime          = 250;
-timeStep                = 1;                                              % Minutes
+ExtractionTime          = 2000;
+timeStep                = 1;                                                % Minutes
 SamplingTime            = 5;                                                % Minutes
 
 simulationTime          = PreparationTime + ExtractionTime;

### 2023-11-04 SFE_article_Economic_Optimization/template_Article.tex
04.11

\documentclass[]{article}

%opening
\title{Cost calculations}
\author{}

\begin{document}

\maketitle

\begin{abstract}
Summery of the cost calculations
\end{abstract}

\section{Intro}

The estimation of operating and capital costs is an important facet of process design and optimization. In the absence of firm bids or valid historical records, you can locate charts, tables, and equations that provide cost estimates from a wide variety of sources based on given values of the design variables.

\section{Cost index method}

When using purchase cost estimates from an earlier date, an estimate of the cost at the later date is made by multiplying the cost from an earlier date by the ratio of a cost index, $I$, at that later date to a base cost index, $I_{base}$, that corresponds to the date that applies to the purchase cost:

{\footnotesize
\begin{equation}
	Cost = Base~Cost \left(\frac{I}{I_{base}}\right)
	\end{equation}}

The indexes most commonly considered by chemical engineers are: The Chemical Engineering (CE) Plant Cost Index, The Marshall \& Swift (MS) Equipment Cost Index, The Nelson-Farrar (NF) Refinery Construction Cost Index and The Engineering News-Record (ENR) Construction Cost Index.

The CE and NF indexes pertain to the entire processing plant, taking into account labor and materials to fabricate the equipment, deliver it, and install it. However, the NF index is restricted to the petroleum industry whereas the CE index pertains to an average of all chemical processing industries. The ENR index, which is a more general index that pertains to the average of all industrial construction, is a composite of the costs of structural steel, lumber, concrete, and labor. The MS index pertains to an all-industry average equipment purchase cost. However, the MS index is accompanied by a more useful process industries average equipment cost index, averaged mainly for the chemicals, petroleum products, paper, and rubber industries. The CE and NF indexes also provide cost indexes for only the purchase cost of several categories of processing equipment, including heat exchangers, pumps and compressors, and machinery

\section{Compressor/Pump}

\section{Heat exchanger}

\section{Extractor}

\end{document}

### 2023-11-04 SFE_Economic_Optimization/main_Economic_Optimization.m

@@ -2,8 +2,8 @@ startup;
 delete(gcp('nocreate'));
 % %p = Pushbullet(pushbullet_api);
 
-%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
-addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+%addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
 import casadi.*
 
 Parameters_table        = readtable('Parameters.csv') ;                                 % Table with prameters
@@ -98,9 +98,12 @@ massFlow                = 0.02;                                                 
 
 %% heat exchanger
 [T_w_out, T_c_out, HX_cost] = Heat_Exchanger_estimation(T_out_compressor, feedPress, Parameters);
-T0homog                 = full(T_w_out);                           
+T0homog                     = full(T_w_out);            
 
 %% Extractor
+[Extractor_cost]        = Extractor_estimation(feedPress,Parameters);
+
+%% Controls
 Z                       = Compressibility( T0homog, feedPress,         Parameters );
 rho                     = rhoPB_Comp(      T0homog, feedPress, Z,      Parameters );
 

### 2023-11-14 SFE_Design_of_Experiment/Notes/template_Scrartcl.tex
14.11

\documentclass[]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}

%opening
\title{Optimal design of experiment}
\author{Oliwer Sliczniuk}

\begin{document}

\maketitle

\begin{abstract}
Notes about the optimal design of an experiment
\end{abstract}

\section{What information do we have?}

\begin{itemize}
	\item Process model: $\dot{x}=f(t,x,p)$
	\item Measurement equation: $\dot{y}=g(x)$
	\item Likelihood function with respect to the dataset
	\item Parameter estimation
	\item Sensitivity equations: $\dot{S} = J_x \dot{x} + J_p$
\end{itemize}

\section{Maximum likelihood}
Let $y^s$ be the vector of all experimental results (random vector) to be used to estimate $p$, and $y^m(p)$. The vector of the corresponding quantities computed by the model $\dot{x}=f(t,x,p)$. For a parallel model, the parameters of which are to be estimated from measurements of an output vector $\dot{y}=g(x)$. We shall call any
oplimizer of $j$, i.e. any $\hat{p}$ that corresponds to an optimal value of the cost function $j$, an estimate of $p$ in the sense of $j$.

The vector $\hat{p}_{ml}$ will be a maximum-likelihood estimate if it maximizes the cost function

\begin{equation}
	j_{ml} = \pi_y (y^s|p) 
\end{equation}

If $p$ were fixed, $\pi_y(y^s|p)$ would be the probability density of the random vector $y^s$ being generated by a model with parameters $p$. Here, to the contrary, $y^s$ is fixed and corresponds to the observations. Considered as a function of $p$, $\pi_y(y^s|p)$ is then called the likelihood of $y^s$. The maximum-likelihood method looks for the value of the parameter vector $p$ that gives the highest likelihood to the observed data. In practice, it is often easier to look for $\hat{p}_{ml}$ by maximizing the log-likelihood function which yields the same estimate since the logarithm function is monotonically increasing.

\begin{equation}
	j_{ml} = \ln ( \pi_y (y^s|p) )
\end{equation}

Assume that the observed outputs satisfy

\begin{equation}
	y(t_i) = y^m(t_i, p^*) + \epsilon_i, \qquad i=1,...,n_t
\end{equation}

where the vector $y^m(t_i. p^*)$ is the output of a deterministic model, $p^*$ is the true value of the parameter vector and $\epsilon_i$ belongs to a sequence of independent random variables with probability density $\pi_{\epsilon}(\epsilon_i)$. Since the $\epsilon_i$ are independent

\begin{equation}
	\pi_{\epsilon}(\epsilon_1, \epsilon_2, ..., \epsilon_{n_t}) = \prod_{i=1}^{n_t} \pi_{\epsilon_i}(\epsilon_i)
\end{equation}

Consider the output error

\begin{equation}
	e^y(t_i, p) = y(t_i) - y^m(t_i, p)
\end{equation}

For the true value of the parameters, it satisfies $e^y(t_i, p^*)=\epsilon_i$. and, since $y^m$ is deterministic, $\pi_{y_i} (y^s(t_i)|p) = \pi_{\epsilon_i} (e^y(t_i)|p)$. The likelihood of the $n_t$ observations can therefore be written as

\begin{equation}
	 \pi_y (y^s|p) = \prod_{i=1}^{n_t} \pi_{\epsilon_i}(e^y(t_i,p)) =  \prod_{i=1}^{n_t} \pi_{\epsilon_i}(y(t_i) - y^m(t_i, p))
\end{equation}

If the noise is assumed to follow the normal distribution:

\begin{equation}
	\pi_y (y^s|p) = \prod_{i=1}^{n_t} \frac{1}{ \sqrt{2\pi\sigma_i^2} } \exp \left( -\frac{1}{2} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_i} \right) \right)
\end{equation}

The associated log-likelihood can be written as

\begin{equation}
	\ln (\pi_y (y^s|p)) = (\text{term independent of p}) - \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{ij}^2} \right)
\end{equation}

Its gradient is thus

\begin{equation}
	\frac{\partial}{\partial p} \ln (\pi_y (y^s|p)) =  \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{ij}^2} \frac{\partial y^m(t_i, p)}{\partial p} \right)
\end{equation}

\section{Fisher information}

The Fisher information is a way of measuring the amount of information that an observable random variable carries about an unknown parameter of a distribution that models the random variable. The Fisher information matrix is used to calculate the covariance matrices associated with maximum-likelihood estimates.

The Fisher information matrix can be calculated as

\begin{align}
	F(p) &= \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial \ln (\pi_y (y^s|p))}{\partial p} \frac{\partial \ln (\pi_y (y^s|p))}{\partial p}^T \right] \\
	&= \mathop{\mathbb{E}}_{y^s|p} \left[ \sum_{k=1}^{n_t} \left( \frac{y(t_k) - y^m(t_k, p)}{\sigma_{t_k}^2} \frac{\partial y^m(t_k, p)}{\partial p} \right) \times  \sum_{i=1}^{n_t} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p^T} \right) \right]
\end{align}

Since

\begin{equation}
	\mathop{\mathbb{E}}_{y^s|p} \left[ \left( y(t_i) - y^m(t_k, p) \right) \left( y(t_i) - y^m(t_i, p) \right) \right] = \sigma_{t_i}^2 \delta_{ik}
\end{equation}

one gets

\begin{equation}
	F(p) = \sum_{i=1}^{n_t} \left( \frac{1}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p} \frac{\partial y^m(t_i, p)}{\partial p^T} \right)
\end{equation}

\section{Cramer-Rao inequality}

Let $\hat{p}$ be an (absolutely) unbiased estimator $p^*$, i.e. such that which amounts to saying that if it were possible to replicate the same experiment and
estimate $\hat{p}$ an infinite number of times, the mean of the estimates would coincide with the true value. Let $P$ be the covariance matrix of this estimator. Since $\hat{p}$ is unbiased, $P$ can be written as

\begin{equation}
	P = \mathop{\mathbb{E}}_{y^s|p^*} \left[ \left( \hat{p}(y^s) - p^* \right) \left( \hat{p}(y^s) - p^* \right)^T \right]
\end{equation}

which quantifies how the estimates are spread around the true value $p^*$. One would like the estimates to be as concentrated as possible around this true value, of course. An estimator $\hat{p}_1$ with covariance matrix $P_1$ is said to be more efficient than an estimator $\hat{p}_2$ with covariance matrix $P_2$ if $P_1 < P_2$, that is if $P_2 - P_1$ is positive-definite (i.e.if all the eigenvalues of $P_2-P_1$ arc strictly positive). Since estimators with high efficiency are desirable, a natural request is to make P as small as possible. The Cramer-Rao inequality provides a lower bound to what can be achieved.

Under the hypotheses that:

\begin{itemize}
	\item the set of all data vectors $y^s$ with $\pi_y(y^s|p) > 0$ does not depend on $p$
	\item $\frac{\partial \pi_y(y^s|p)}{\partial p_i}~\left(i=1,2,...,n_p\right)$ is absolutely integrable
	\item $\mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial \ln (\pi_y (y^s|p))}{\partial p} \frac{\partial \ln (\pi_y (y^s|p))}{\partial p^T} \right]$ exists and is invertible
\end{itemize}

the covariance of any absolutely unbiased estimator satisfies

\begin{equation}
	P \geq F^{-1}(p^*)
\end{equation}

In other words, the precision to which we can estimate $p$ is fundamentally limited by the Fisher information of the likelihood function.

\section{Experiment design}

The experimental procedure for the collection of the numerical data to be used to estimate the parameters of a given model depends on qualitative choices made at various steps of the modelling. In particular, the tools presented in the previous chapters allow one to choose:

\begin{itemize}
	\item a set of model structures to be considered
	\item location of sensors and actuators to guarantee identifiability (and distinguishably if several rival structures exist)
	\item an estimator and a characterization of parameter uncertainly
\end{itemize}

Once these choices have been made, the experimenter still has some freedom to specify the quantitative experimental conditions (such as temperature, pressure, sampling times, shape of inputs, etc.). Experiment design aims at determining experimental conditions adapted to the final purpose of the modelling. It is a crucial step, for a badly designed experiment may ruin any attempt at analysing the data collected from the system.

Assume that the i'th scalar observation can be written as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ (the i'th support point) describes the experimental conditions (e.g., measurement time, shape of input...) under which the i'th observation is to be collected. When $n_t$ such observations are taken, the concatenation of the vectors $\xi_i$'s yields the $\Xi = (\xi_1, \xi_2,..., \xi_{n_t})$, which characterizes all experimental conditions to be optimized. To make experiment design realistic, it is necessary to take a number of constraints into account, e.g. on the duration of the experiments, the energy or amplitude of the inputs, the minimum time between samples. Let $\bar{\Xi}$ be the set of all feasible values for $\Xi$.

The definition of a cost function $j$ then permits optimal experiment design to be cast as a constrained optimization problem, where the optimal experiment $\Xi^*$ is defined by

\begin{equation}
	\Xi^* = \arg~\underset{\Xi \in \bar{\Xi}}{\text{opt}}~j\left(\Xi\right)
\end{equation}

Evaluation of the cost function $j$ must be simple enough to allow easy optimization. For that reason, classical oplimality criteria correspond to a scalar function of the Fisher information matrix $F(p,\Xi)$

\begin{equation}
	j(\Xi) = \phi\left[ F(p, \Xi) \right]
\end{equation}

Under the hypotheses mentioned above, the distribution of the maximum likelihood estimator is asymptotically Gaussian $\mathop{\mathbb{N}} (p^*, F^{-1}([^*, \Xi])) $ when the number of measurements tends to infinity. Minimizing $j(\Xi)$ then amounts to minimizing a scalar easure of the asymptotic covariance matrix of the parameters.

A rather general class of optimality criteria employs the following family of cost functions

\begin{align}
	\phi_k(F) &= \left[\frac{1}{n_p} \text{trace}\left( QF^{-1}Q^T \right)^k \right]^{1/k} \quad &if \det F \neq 0 \nonumber \\
	\phi_k(F) &= \infty \quad &if \det F = 0
\end{align}

where $Q$ is a weighting matrix. The special case $k = 1$ corresponds to the L-optimality cost function,

\begin{equation}
	j_L(\Xi) = \text{trace} \left[ Q^TQF^{-1}(p,\Xi) \right]
\end{equation}

and choosing $Q = \textbf{I}_{n_p}$ then corresponds to the A-optimality cost function. An A-optimal experiment minimizes the sum of the squares of the lengths or the axes of asymptotic confidence ellipsoids. Choosing $Q$ diagonal, with $[Q]_{ii} = 1/p_i$ corresponds to C-optimality, which is connected with the relative precision of estimates. Taking Q to be a row vector leads to c-optimality. Taking $Q = \textbf{I}_{n_p}$ and $k = \infty$ corresponds to E-optimality; E-optimal design maximizes the smallest eigenvalues of the Fisher information matrix and thus minimizes the length of the largest axis of the asymptotic confidence ellipsoids. The most widely used optimality criterion has $k = 0$, $Q = \textbf{I}_{n_p}$ , requiring minimization of $\det F^{-1}(p, \Xi)$, or, equivalently, maximization of

\begin{equation}
	j_D(\Xi) = \det F(p, \Xi)
\end{equation}

A D-optimal experiment minimizes the volume of the asymptotic confidence ellipsoids for the parameters.

\begin{figure}[h]
	\centering
	\includegraphics[width=8cm]{DOE_conditions.jpg}
\end{figure}

\end{document}

### 2023-12-03 SFE_Design_of_Experiment/Notes/template_Scrartcl.tex
03.10

@@
 \usepackage{graphicx}
+\usepackage{tikz}
 
@@
 \section{Maximum likelihood}
-Let $y^s$ be the vector of all experimental results (random vector) to be used to estimate $p$, and $y^m(p)$.
+Let $y^s$ be the vector of all experimental results (random vector) to be used to estimate $p$ and $y^m(p)$.
 The vector of the corresponding quantities computed by the model $\dot{x}=f(t,x,p)$.
 For a parallel model, the parameters of which are to be estimated from measurements of an output vector $\dot{y}=g(x)$.
-We shall call any
-oplimizer of $j$, i.e. any $\hat{p}$ that corresponds to an optimal value of the cost function $j$, an estimate of $p$ in the sense of $j$.
+We shall call any optimizer of $j$, i.e., any $\hat{p}$ that corresponds to an optimal value of the cost function $j$, an estimate of $p$ in the sense of $j$.
 
-The vector $\hat{p}_{ml}$ will be a maximum-likelihood estimate if it maximizes the cost function
+The vector $\hat{p}_{ml}$ will be a maximum-likelihood estimate if it maximizes the cost function:
 
@@
 
-If $p$ were fixed, $\pi_y(y^s|p)$ would be the probability density of the random vector $y^s$ being generated by a model with parameters $p$.
+If $p$ were fixed, $\pi_y(y^s|p)$ would be the probability density of the random vector $y^s$ generated by a model with parameters $p$.
 Here, to the contrary, $y^s$ is fixed and corresponds to the observations.
 Considered as a function of $p$, $\pi_y(y^s|p)$ is then called the likelihood of $y^s$.
-The maximum-likelihood method looks for the value of the parameter vector $p$ that gives the highest likelihood to the observed data.
-In practice, it is often easier to look for $\hat{p}_{ml}$ by maximizing the log-likelihood function which yields the same estimate since the logarithm function is monotonically increasing.
+The maximum-likelihood method looks for the parameter vector $p$ value that gives the observed data the highest likelihood.
+In practice, it is often easier to look for $\hat{p}_{ml}$ by maximizing the log-likelihood function, yielding the same estimate since the logarithm function is monotonically increasing.
 
@@
 where the vector $y^m(t_i.
-p^*)$ is the output of a deterministic model, $p^*$ is the true value of the parameter vector and $\epsilon_i$ belongs to a sequence of independent random variables with probability density $\pi_{\epsilon}(\epsilon_i)$.
+p^*)$ is the output of a deterministic model, $p^*$ is the true value of the parameter vector, and $\epsilon_i$ belongs to a sequence of independent random variables with probability density $\pi_{\epsilon}(\epsilon_i)$.
 Since the $\epsilon_i$ are independent
@@
 and, since $y^m$ is deterministic, $\pi_{y_i} (y^s(t_i)|p) = \pi_{\epsilon_i} (e^y(t_i)|p)$.
-The likelihood of the $n_t$ observations can therefore be written as
+The likelihood of the $n_t$ observations can be written as
 
@@
 \begin{equation}
-	\pi_y (y^s|p) = \prod_{i=1}^{n_t} \frac{1}{ \sqrt{2\pi\sigma_i^2} } \exp \left( -\frac{1}{2} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_i} \right) \right)
+	\pi_y (y^s|p) = \prod_{i=1}^{n_t} \frac{1}{ \sqrt{2\pi\sigma_{t_i}^2} } \exp \left( -\frac{1}{2} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}} \right) \right)
 \end{equation}
@@
 \begin{equation}
-	\ln (\pi_y (y^s|p)) = (\text{term independent of p}) - \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{ij}^2} \right)
+	\ln (\pi_y (y^s|p)) = (\text{term independent of p}) - \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \right)
 \end{equation}
@@
 \begin{equation}
-	\frac{\partial}{\partial p} \ln (\pi_y (y^s|p)) =  \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{ij}^2} \frac{\partial y^m(t_i, p)}{\partial p} \right)
+	\frac{\partial}{\partial p} \ln (\pi_y (y^s|p)) =  \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p} \right)
 \end{equation}
@@
 The Fisher information is a way of measuring the amount of information that an observable random variable carries about an unknown parameter of a distribution that models the random variable.
-The Fisher information matrix is used to calculate the covariance matrices associated with maximum-likelihood estimates.
-
-The Fisher information matrix can be calculated as
+The Fisher information is related to the second derivative (or the curvature) of the log-likelihood function with respect to the parameter.
+This relationship provides a measure of how "sensitive" the likelihood is to changes in the parameter value.
+The Fisher information matrix can be calculated as follow.
 
 \begin{align}
-	F(p) &= \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial \ln (\pi_y (y^s|p))}{\partial p} \frac{\partial \ln (\pi_y (y^s|p))}{\partial p}^T \right] \\
+	F(p) &= - \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial^2 \ln (\pi_y (y^s|p))}{\partial p \partial p^T} \right] = \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial \ln (\pi_y (y^s|p))}{\partial p} \frac{\partial \ln (\pi_y (y^s|p))}{\partial p^T} \right] \\
 	&= \mathop{\mathbb{E}}_{y^s|p} \left[ \sum_{k=1}^{n_t} \left( \frac{y(t_k) - y^m(t_k, p)}{\sigma_{t_k}^2} \frac{\partial y^m(t_k, p)}{\partial p} \right) \times  \sum_{i=1}^{n_t} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p^T} \right) \right]
@@
 	F(p) = \sum_{i=1}^{n_t} \left( \frac{1}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p} \frac{\partial y^m(t_i, p)}{\partial p^T} \right)
+\end{equation}
+
+If every experiment at time $t_i$ is independent and characterized by its own $\sigma_{t_i}$, then the Fisher information matrix can be presented in the more compact way:
+
+\begin{equation}
+	F(p) = \frac{\partial y^m(t, p)}{\partial p} \text{diag}\left(\frac{1}{\sigma_{t}^2}\right) \frac{\partial y^m(t, p)}{\partial p^T} 
 \end{equation}
@@
 In other words, the precision to which we can estimate $p$ is fundamentally limited by the Fisher information of the likelihood function.
+Based on the Cramer-Rao inequality, the Fisher information matrix can used to calculate the covariance matrices associated with maximum-likelihood estimates.
 
-\section{Experiment design}
+\section{Optimal experimental design}
 
-The experimental procedure for the collection of the numerical data to be used to estimate the parameters of a given model depends on qualitative choices made at various steps of the modelling.
-In particular, the tools presented in the previous chapters allow one to choose:
+The optimal design of experiments (DOE) is a statistical concept that refers to the process of planning an experiment, which allow parameters to be estimated without bias and with minimum variance.
+Optimal design ensures that the experiment can provide the most informative data possible.
+This often involves balancing the study of main effects and interactions between factors.
+Moreover, by efficiently planning experiments, optimal design aims to reduce the overall resources required, such as time, materials, and manpower.
 
-\begin{itemize}
-	\item a set of model structures to be considered
-	\item location of sensors and actuators to guarantee identifiability (and distinguishably if several rival structures exist)
-	\item an estimator and a characterization of parameter uncertainly
-\end{itemize}
+The methodology for data to estimate the parameters of a specific model is influenced by a series of qualitative decisions made throughout the experimental and modelling process, such as: a model structure, a location of sensors or an equipment.
+Once these choices have been made, the experimenter still has some freedom to specify the quantitative experimental conditions (such as temperature, pressure, sampling times, etc.).
+Experiment design aims to determine experimental conditions adapted to the final purpose of the modeling.
 
-Once these choices have been made, the experimenter still has some freedom to specify the quantitative experimental conditions (such as temperature, pressure, sampling times, shape of inputs, etc.).
-Experiment design aims at determining experimental conditions adapted to the final purpose of the modelling.
-It is a crucial step, for a badly designed experiment may ruin any attempt at analysing the data collected from the system.
-
-Assume that the i'th scalar observation can be written as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ (the i'th support point) describes the experimental conditions (e.g., measurement time, shape of input...) under which the i'th observation is to be collected.
+%Assume that the i'th scalar observation can be written as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ (the i'th support point) describes the experimental conditions (e.g., measurement time, the shape of input, etc.) under which the i'th observation is to be collected.
 When $n_t$ such observations are taken, the concatenation of the vectors $\xi_i$'s yields the $\Xi = (\xi_1, \xi_2,..., \xi_{n_t})$, which characterizes all experimental conditions to be optimized.
-To make experiment design realistic, it is necessary to take a number of constraints into account, e.g.
-on the duration of the experiments, the energy or amplitude of the inputs, the minimum time between samples.
+To make the experiment design realistic, it is necessary to consider several constraints, e.g., the experiments' duration, the inlet stream's temperature, and the minimum time between samples.
 Let $\bar{\Xi}$ be the set of all feasible values for $\Xi$.
 
-The definition of a cost function $j$ then permits optimal experiment design to be cast as a constrained optimization problem, where the optimal experiment $\Xi^*$ is defined by
+Let's consider that each scalar observation in our study can be expressed as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ representing the specific experimental conditions (such as the timing of measurements, operating conditions, etc.) under which the i'th observation is gathered.
+When collecting $n_t$ such observations, the assembly of these $\xi_i$ vectors forms the matrix $\Xi = (\xi_1, \xi_2,..., \xi_{n_t})$, which combine all the experimental conditions that need optimization.
+In order to align the design of the experiment with practical realities, it's important to take into account various constraints, such as the total duration of the experiments, the maximum temperature of the inlet stream, and the minimum interval between sampling events.
+The set of all possible combinations for $\bar{\Xi}$ that adhere to these constraints is denoted as $\Xi$.
+
+%The definition of a cost function $j$ then permits the optimal experiment design to be cast as a constrained optimization problem, where the optimal experiment $\Xi^*$ is defined by
+
+The formulation of a cost function $j$ allows for the framing of optimal experiment design as a problem of constrained optimization. In this context, the optimal experiment, denoted as $\Xi^*$:
 
@@
 
-Evaluation of the cost function $j$ must be simple enough to allow easy optimization.
-For that reason, classical oplimality criteria correspond to a scalar function of the Fisher information matrix $F(p,\Xi)$
+The cost function should describe the amount of information from an experiment.
+For that purpose it can be assumed a function $\phi$ can be related to the Fisher information obtained an arbitrary operating conditions.
 
@@
 
-Under the hypotheses mentioned above, the distribution of the maximum likelihood estimator is asymptotically Gaussian $\mathop{\mathbb{N}} (p^*, F^{-1}([^*, \Xi])) $ when the number of measurements tends to infinity.
-Minimizing $j(\Xi)$ then amounts to minimizing a scalar easure of the asymptotic covariance matrix of the parameters.
+%Under the hypotheses mentioned above, the distribution of the maximum likelihood estimator is asymptotically Gaussian $\mathop{\mathbb{N}} (p^*, F^{-1}([^*, \Xi])) $ when the number of measurements tends to infinity.
+Minimizing $j(\Xi)$ then amounts to minimizing a scalar measure of the asymptotic covariance matrix of the parameters.
 
-A rather general class of optimality criteria employs the following family of cost functions
+A general class of optimality criteria for DOE is given by
 
@@
 A D-optimal experiment minimizes the volume of the asymptotic confidence ellipsoids for the parameters.
+The graphical representation of the different optimality conditions is shown in Figure \ref{fig:score_fun}.
 
-\begin{figure}[h]
+\begin{figure}[!h]
 	\centering
-	\includegraphics[width=8cm]{DOE_conditions.jpg}
+	\resizebox{0.4\textwidth}{!}{%
+	\begin{tikzpicture}
+		% Ellipse parameters
+		\def\ellipsecenter{(3,3)}
+		\def\ellipseA{(0.75,5.25)} % End point for A-optimality arrow
+		\def\ellipseB{(5.13,5.13)} % End point for E-optimality arrow
+		\def\ellipseC{(4,1.2)}      % End point for D-optimality arrow
+
+		% Draw the rotated ellipse
+		\draw[fill=gray!10, draw=black, rotate around={45:\ellipsecenter}] \ellipsecenter ellipse (3cm and 1cm);
+
+		% Draw the dashed rectangle
+		\draw[dashed] (0.75,0.75) rectangle (5.25,5.25);
+
+		% Draw the arrows and label them with adjustable positions
+		\draw [-latex] \ellipsecenter -- \ellipseA node[yshift=-4cm, xshift=2.5cm,rotate around={-45:\ellipsecenter}] {A-optimality};
+		\draw [-latex] \ellipsecenter -- \ellipseB node[yshift=0cm, xshift=-3.9cm,rotate around={45:\ellipsecenter}] {E-optimality};
+		\draw [-latex] \ellipseC -- (2,2) node[yshift=-1cm, xshift=2cm] {D-optimality};
+
+		% Draw axes
+		\draw[thick,->] (0,0) -- (6,0) node[below] {$p_1$};
+		\draw[thick,->] (0,0) -- (0,6) node[left] {$p_2$};
+	\end{tikzpicture}
+	}%
+	\caption{Graphical representation of score functions}
+	\label{fig:score_fun}
 \end{figure}

### 2023-12-03 SFE_article_Parameter_Estimation/Sections/Experiments.tex
03.10

@@
 
-	%The results of experiments are presented in the Table \ref{tab: Yield_data}.
-
-%	\begin{table}[!h]
-%		\centering
-%		\adjustbox{max width=\columnwidth}{%
-%			\csvautobooktabular{Figures/Results_estimation/Dataset.csv} }
-%		\caption{Yield data; cumulative amount of solute [g] collected every 5 min}
-%		\label{tab: Yield_data}
-%	\end{table}
+	\begin{figure}[!h]
+		\centering
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
+			\caption{Experiment at $40~^\circ C$ and 200 bar}
+		\end{subfigure}
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
+			\caption{Experiment at $50~^\circ C$ and 200 bar}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300.pdf}
+			\caption{Experiment at $40~^\circ C$ and 300 bar}
+		\end{subfigure}
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300.pdf}
+			\caption{Experiment at $50~^\circ C$ and 300 bar}
+		\end{subfigure}
+		\caption{Results of parameter estimation}
+		\label{fig: estimation_results}
+	\end{figure}
 

### 2023-12-03 SFE_article_Parameter_Estimation/Supercritical_fluid_extraction_of_essential_oil_from_caraway.tex
03.10

--- 2023-10-10 SFE_article_Parameter_Estimation/Article_Model_Parameters.tex
@@
 
+\usepackage{numprint}
+
 % --------------------------------------------------------------------
@@
 % ===================================================
-\title[mode=title]{Parameter estimation}                      
-\shorttitle{Parameter estimation}
+\title[mode=title]{Supercritical fluid extraction of essential oil from caraway seeds: experiments, modelling, and parameter estimation}                      
+\shorttitle{Supercritical fluid extraction of essential oil from caraway seeds: experiments, modelling, and parameter estimation}
 
@@
 
-%\author[1]{Francesco Corona}[orcid=0000-0002-3615-1359]
-%\credit{c}
-
 \address[1]{Aalto University, School of Chemical Engineering, Espoo, 02150, Finland}
@@
 \begin{abstract}
-%Given a system of partial differential equations, $F(t,x,\dot{x},p,u)=0$, where $x$ represents state variables, $p$ is the parameters, and $u$ are control variables, the process model is simultaneously solved for both $x_i$ and a set of sensitivity functions, $dx_i/dp_j$, overall times $t$.These sensitivity functions measure the influence of the parameter change on the model's output.
-As an example, the supercritical extraction process is presented.
-The impact of mass flow rate, pressure, and inlet temperature on the model's output is discussed.
-The sensitivity analysis results prove that the considered variables can affect the extraction's yield and be used as control variables in optimization problems.
-Moreover, the local sensitivity analysis results are analyzed from a phenomenological point of view to enhance understanding of the process model.
-%Given a system of partial differential equations, $F(t,x,\dot{x},\Theta,u)=0$, where $x$ represents state variables, $\Theta$ are the parameters, and $u$ are control variables, we describe the supercritical extraction process.
-The process model describes a partially filled extractor with a fixed bed, which work under constant operating conditions.
-We assume that the flow is uniform across any cross-section, although the area available for the fluid phase can change along the extractor.
-We apply the concept of quasi-one-dimensional flow to mimic the modelling of a two-dimensional case.
-%In this work, a distributed-parameter model, based on \citet{Reverchon1996} is used to describe a fluid-solid extraction process of caraway oil from caraway seeds with $CO_2$ as a solvent.
-The model parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient \textit{and saturation concentration} are obtained from parameter estimation.
-The parameters are estimated based on four experiments performed at $40^\circ C$/$200$ bar, $50^\circ C$/$200$ bar, $40^\circ C$/$300$ bar and $50^\circ C$/$300$ bar.
-Given yield data, the model-based parameter estimation uses the maximum likelihood estimation method under assumption of normal error.
-This study aimed to investigate the supercritical extraction process of the caraway oil from caraway seeds.
-A distributed-parameter model is used to describe the fluid-solid extraction process with carbon dioxide as a solvent.
+This study investigated the supercritical extraction process of caraway oil from caraway seeds.
+A distributed-parameter model describes the fluid-solid extraction process.
 The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
@@
 The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
-This model requires parameters such as partition factor, internal diffusion coefficient, axial diffusion coefficient.
-The missing model parameters and the initial state are obtained by solving the maximum likelihood estimation based on experimental yield data under the normal error assumption.
+Key model parameters included partition factor internal and axial diffusion coefficients.
+These parameters and the initial state were determined using maximum likelihood estimation from experimental data, assuming normal error.
 A set of laboratory experiments was performed in a partially filled extractor with a fixed bed operated under multiple constant operating conditions: $40~^\circ C$ / $200$ bar, $50~^\circ C$ / $200$ bar, $40~^\circ C$ / $300$ bar, and $50~^\circ C$ / $300$ bar.
@@
 \section{Introduction}
-%\subfile{Sections/introduction}
 \subfile{Sections/introduction_imp}
@@
 \subsection{Supercritical fluids} \label{CH: Thermodynamic}
-%\subfile{Sections/Thermo}
 \subfile{Sections/Thermo_imp}
 
-%\clearpage
-%\subfile{Sections/Materials_and_methods}
-
 \subsection{Governing equations} \label{CH:Governing_equations_chapter}
-%\footnote{For the sake of clarity of the process model, different colors have been used in the equations to indicate: 
-%	{\color{red}control variables},
-%	{\color{black}state variables},
-%	{\color{black}variables} and
-%	{\color{black}parameters}.} 
 	The governing equation for a quasi-one-dimensional compressible flow in Cartesian coordinates can be found in the Appendix \ref{CH: Gouverning equations} and in the work of \citet{Anderson1995}.
@@
 In other words, the small changes in pressure due to flow velocity changes do not change the density.
-%This has a secondary effect -- the speed of sound in the fluid is $\partial {\color{black}P}/\partial {\color{black}\rho_f} = \infty$ in this instance.
-So there is an infinite speed of sound, which makes the equations elliptic in nature.
-It can be deduced that at the isothermal conditions, the density in the system propagates with the same speed as pressure since they are both connected through the equation of state.
-The details of the Mach-number analysis are presented in Appendix \ref{CH:Low_Mach_chapter}.
 
@@
 \subfile{Sections/Model}
-
-%\newpage
-%\section{Bayes theorem} \label{CH: Bayes}
-%\subfile{Sections/Bayes_Theorem}
-%\clearpage
 
@@
 \subfile{Sections/Qubic_EOS}
-%\subfile{Sections/Thermodynamic_details}
 
@@
 \subfile{Sections/Gouverning_equation_derivation}
-
-%\subsection{Low Mach number expansion} \label{CH:Low_Mach_chapter}
-%\subfile{Sections/Low_mach_number_expansion}
-%\subfile{Sections/Low_mach_number_expansion_imp}
 
@@
 \subfile{Sections/IC_BC}
-
-%\subsection{Bayes theorem} \label{CH: Bayes}
-%\subfile{Sections/Bayes_Theorem}
 
@@
 
-%\subsection{Concentration profiles} \label{CH: Profiles}
-%\subfile{Sections/Profiles}
-
-%\subsection{Solution of the parameter estimation starting from another initial guess} \label{CH: Profiles_2}
-%\subfile{Sections/Parameter_estimation_solution_from_another_IG}
-
 \end{document}

### 2023-12-03 SFE_Design_of_Experiment/Sensitivity.m

@@ -1,4 +1,4 @@
-function [S,p,Sdot] = Sensitivity(x,xdot,theta,which_theta)
+function [S,p,Sdot] = Sensitivity(x, xdot, theta, which_theta)
 
     %addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
     import casadi.*

### 2023-12-03 SFE_Design_of_Experiment/main_Experiment_Design.m

@@ -10,12 +10,13 @@ Parameters_table        = readtable('Parameters.csv') ;                     % Ta
 Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
 
 %% Create the solver
-Iteration_max               = 50;                                            % Maximum number of iterations for optimzer
-Time_max                    = 12.0;                                           % Maximum time of optimization in [h]
+Iteration_max               = 100;                                            % Maximum number of iterations for optimzer
+Time_max                    = 24.0;                                           % Maximum time of optimization in [h]
 
 nlp_opts                    = struct;
 nlp_opts.ipopt.max_iter     = Iteration_max;
 nlp_opts.ipopt.max_cpu_time = Time_max*3600;
+nlp_opts.ipopt.hessian_approximation ='limited-memory';
 %nlp_opts.ipopt.acceptable_tol  = 1e-4;
 %nlp_opts.ipopt.acceptable_iter = 5;
 
@@ -34,9 +35,10 @@ bed                     = 0.165;                                            % Pe
 
 % Set time of the simulation
 PreparationTime         = 0;
-ExtractionTime          = 200; 
-timeStep                = 1;                                               % Minutes
-SamplingTime            = 50;                                              % Minutes
+ExtractionTime          = 120;
+timeStep                = 2.5;                                              % Minutes
+SamplingTime            = 5;                                                % Minutes
+OP_change_Time          = 10;                                               % Minutes
 
 simulationTime          = PreparationTime + ExtractionTime;
 
@@ -44,8 +46,18 @@ timeStep_in_sec         = timeStep * 60;                                    % Se
 Time_in_sec             = (timeStep:timeStep:simulationTime)*60;            % Seconds
 Time                    = [0 Time_in_sec/60];                               % Minutes
 
-N_Time                  = length(Time_in_sec);        
-N_Sample                = SamplingTime:SamplingTime:ExtractionTime;
[…]

### 2023-12-03 SFE_Design_of_Experiment/test_direct_jacob.m

@@ -6,22 +6,28 @@ delete(gcp('nocreate'));
 addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
 import casadi.*
 
-Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
-Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
+numeEval = 108;
+
+parfor ii=1:numeEval
+
+Parameters_table                = readtable('Parameters.csv') ;                     % Table with prameters
+Parameters                      = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
 
 %% Create the solver
-Iteration_max               = 50;                                            % Maximum number of iterations for optimzer
-Time_max                    = 20.0;                                           % Maximum time of optimization in [h]
+Iteration_max                   = 150;                                            % Maximum number of iterations for optimzer
+Time_max                        = 24.0;                                          % Maximum time of optimization in [h]
 
-nlp_opts                    = struct;
-nlp_opts.ipopt.max_iter     = Iteration_max;
-nlp_opts.ipopt.max_cpu_time = Time_max*3600;
-%nlp_opts.ipopt.acceptable_tol  = 1e-4;
+nlp_opts                        = struct;
+nlp_opts.ipopt.max_iter         = Iteration_max;
+nlp_opts.ipopt.max_cpu_time     = Time_max*3600;
+nlp_opts.ipopt.hessian_approximation ='limited-memory';
+nlp_opts.ipopt.tol              = 1e-5;
+nlp_opts.ipopt.acceptable_tol   = 1e-3;
 %nlp_opts.ipopt.acceptable_iter = 5;
 
-OPT_solver                  = casadi.Opti();
-ocp_opts                    = {'nlp_opts', nlp_opts};
-OPT_solver.solver(             'ipopt'   , nlp_opts)
+OPT_solver                      = casadi.Opti();
+ocp_opts                        = {'nlp_opts', nlp_opts};
+OPT_solver.solver(                  'ipopt'   , nlp_opts)
 
 %% Load paramters
 m_total                 = 80;
[…]

### 2023-12-07 SFE_Design_of_Experiment/Notes/template_Scrartcl.tex
07.12

@@
 \section{Maximum likelihood}
-Let $y^s$ be the vector of all experimental results (random vector) to be used to estimate $p$ and $y^m(p)$.
+Let $y^s$ be the vector of all experimental results (random vector) to be used to estimate parameters $p$ and model output $y^m(p)$.
 The vector of the corresponding quantities computed by the model $\dot{x}=f(t,x,p)$.
@@
 
-If the noise is assumed to follow the normal distribution:
+If the noise is assumed to follow the normal distribution with the standard deviation $\sigma$, which is known from the parameter estimation:
 
 \begin{equation}
-	\pi_y (y^s|p) = \prod_{i=1}^{n_t} \frac{1}{ \sqrt{2\pi\sigma_{t_i}^2} } \exp \left( -\frac{1}{2} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}} \right) \right)
+	\pi_y (y^s|p) = \prod_{i=1}^{n_t} \frac{1}{ \sqrt{2\pi\sigma_{t_i}^2} } \exp \left( -\frac{1}{2} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}} \right)^2 \right)
 \end{equation}
@@
 \begin{equation}
-	\ln (\pi_y (y^s|p)) = (\text{term independent of p}) - \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \right)
+	\ln (\pi_y (y^s|p)) = (\text{term independent of p}) - \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}} \right)^2
 \end{equation}
@@
 \begin{equation}
-	\frac{\partial}{\partial p} \ln (\pi_y (y^s|p)) =  \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p} \right)
+	\frac{\partial}{\partial p} \ln (\pi_y (y^s|p)) =  \sum_{i=1}^{n_t}  \left[ \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \right) \frac{\partial y^m(t_i, p)}{\partial p} \right]
 \end{equation}
@@
 
-Since
+Considering the mismatch between the dataset and the model output, the expectation becomes $\mathop{\mathbb{E}}_{y^s|p} \left[ \left( y(t_i) - y^m(t_k, p) \right) \right] = \mathop{\mathbb{E}}_{y^s|p} \left[ \epsilon_i^2 \right]$.
+For $i=k$, the expectation of $\epsilon_i$ is the variance of the noise $\sigma_{t_i}^2$.
+Analogously, the expectation becomes 0 if $i \neq k$ because the expectation of the noise $\epsilon_i$ is zero and the measurements are independent at different times.
 
@@
 
-one gets
+where $\delta_{ik}$ represents the Kronecker delta. Given the property of the Kronecker delta, the double summation in the Fisher Information matrix reduces to a single summation:
 
@@
 \begin{equation}
-	F(p) = \frac{\partial y^m(t, p)}{\partial p} \text{diag}\left(\frac{1}{\sigma_{t}^2}\right) \frac{\partial y^m(t, p)}{\partial p^T} 
+	F(p) = \frac{\partial y^m(t, p)}{\partial p} \begin{bmatrix}
+		\frac{1}{\sigma_{t_1}^2} & 0 & 0\\
+		0 & \ddots & 0 \\
+		0 & 0 & \frac{1}{\sigma_{t_{n_t}}^2} 
+	\end{bmatrix}\ \frac{\partial y^m(t, p)}{\partial p^T} 
 \end{equation}
@@
 
-Let $\hat{p}$ be an (absolutely) unbiased estimator $p^*$, i.e. such that which amounts to saying that if it were possible to replicate the same experiment and
-estimate $\hat{p}$ an infinite number of times, the mean of the estimates would coincide with the true value.
+Let $\hat{p}$ be an (absolutely) unbiased estimator $p^*$, i.e.
+such that it were possible to replicate the same experiment and estimate $\hat{p}$ an infinite number of times, the mean of the estimates would coincide with the true value.
 Let $P$ be the covariance matrix of this estimator.
@@
 which quantifies how the estimates are spread around the true value $p^*$.
-One would like the estimates to be as concentrated as possible around this true value, of course.
+One would like the estimates to be as concentrated as possible around this true value.
 An estimator $\hat{p}_1$ with covariance matrix $P_1$ is said to be more efficient than an estimator $\hat{p}_2$ with covariance matrix $P_2$ if $P_1 < P_2$, that is if $P_2 - P_1$ is positive-definite (i.e.if all the eigenvalues of $P_2-P_1$ arc strictly positive).
@@
 
+\section{Problem formulation}
+
+The optimal design of experiment technique is used extend the experiment discussed in ${\color{red}article~1}$, where supercritical extraction from caraway seeds has been discussed.
+In this work, the extraction has been performed at multiple operating conditions, such that the temperature, pressure and flow-rate were constant during each batch.
+Later, the results from all the experiments are combined and correlations for extraction kinetic parameters are presented.
+In this work, the optimal design of experiment is used to design an experiment to validate these correlations.
+The model parameters and the sampling time are the same as in ${\color{red}article~1}$ to mimic the original system.
+It is assumed that the flow-rate is constant, because the effect of the flow-rate has not been deeply investigated.
+The inlet temperature can be controlled by a controller
+
+\begin{equation}
+	\begin{aligned} 
+		&\hat{{\color{black} \theta}}_{MLE} &= \arg \max_{{\color{black} \sigma}, {\color{black} \theta} \in \Theta} \ln L = \arg \max_{{\color{black} \sigma},{\color{black} \theta} \in \Theta} p({\color{black} \theta}|{\color{black}y}) \\
+		&\text{subject to}
+		& \dot{ {\color{black}x} } = {\color{black}G}({\color{black} x}(t);{\color{black} \theta}) \\
+		&& {\color{black} \dot{\theta}} = 0 \\
+		&& {\color{black}y} = {\color{black}y}(t) \\
+		&& {\color{black} \theta}^{lb} \leq {\color{black} \theta} \leq {\color{black} \theta}^{ub}
+	\end{aligned}
+\end{equation}
+
 \end{document}

### 2023-12-14 SFE_Design_of_Experiment/Notes/template_Scrartcl.tex
14.12

@@
 \usepackage{tikz}
+\usepackage{subcaption}
 
@@
 \begin{align}
-	F(p) &= - \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial^2 \ln (\pi_y (y^s|p))}{\partial p \partial p^T} \right] = \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial \ln (\pi_y (y^s|p))}{\partial p} \frac{\partial \ln (\pi_y (y^s|p))}{\partial p^T} \right] \\
-	&= \mathop{\mathbb{E}}_{y^s|p} \left[ \sum_{k=1}^{n_t} \left( \frac{y(t_k) - y^m(t_k, p)}{\sigma_{t_k}^2} \frac{\partial y^m(t_k, p)}{\partial p} \right) \times  \sum_{i=1}^{n_t} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p^T} \right) \right]
+	F(p) &= - \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial^2 \ln (\pi_y (y^s|p))}{\partial p \partial p^T} \right] = \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial \ln (\pi_y (y^s|p))}{\partial p} \frac{\partial \ln (\pi_y (y^s|p))}{\partial p^T} \right] \nonumber \\
+	&= \mathop{\mathbb{E}}_{y^s|p} \left[ \sum_{k=1}^{n_t} \left( \frac{y(t_k) - y^m(t_k, p)}{\sigma_{t_k}^2} \frac{\partial y^m(t_k, p)}{\partial p} \right) \times  \sum_{i=1}^{n_t} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p^T} \right) \right] \nonumber \\
+	&= \mathop{\mathbb{E}}_{y^s|p} \left[ \sum_{k=1}^{n_t} \sum_{i=1}^{n_t} \left[ \left( \frac{y(t_k) - y^m(t_k, p)}{\sigma_{t_k}^2} \frac{\partial y^m(t_k, p)}{\partial p} \right) \times \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p^T} \right) \right] \right] \nonumber \\
+	&= \sum_{k=1}^{n_t} \sum_{i=1}^{n_t} \mathop{\mathbb{E}}_{y^s|p} \left[ \left( \frac{y(t_k) - y^m(t_k, p)}{\sigma_{t_k}^2} \frac{\partial y^m(t_k, p)}{\partial p} \right) \times \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p^T} \right) \right] \nonumber \\
+	&= \sum_{k=1}^{n_t} \sum_{i=1}^{n_t} \frac{1}{\sigma_{t_k}^2} \frac{\partial y^m(t_k, p)}{\partial p} \frac{1}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p^T} \mathop{\mathbb{E}}_{y^s|p} \left[ \left( y(t_k) - y^m(t_k, p) \right) \times \left( y(t_i) - y^m(t_i, p) \right) \right]
 \end{align}
 
-Considering the mismatch between the dataset and the model output, the expectation becomes $\mathop{\mathbb{E}}_{y^s|p} \left[ \left( y(t_i) - y^m(t_k, p) \right) \right] = \mathop{\mathbb{E}}_{y^s|p} \left[ \epsilon_i^2 \right]$.
+Considering the mismatch between the dataset and the model output, the expectation $\mathop{\mathbb{E}}_{y^s|p}$ can be redefined as $\mathop{\mathbb{E}}_{y^s|p} \left[ \left( y(t_i) - y^m(t_i, p) \right) \left( y(t_k) - y^m(t_k, p) \right) \right] = \mathop{\mathbb{E}}_{y^s|p} \left[ \epsilon_i \epsilon_k \right]$.
 For $i=k$, the expectation of $\epsilon_i$ is the variance of the noise $\sigma_{t_i}^2$.
-Analogously, the expectation becomes 0 if $i \neq k$ because the expectation of the noise $\epsilon_i$ is zero and the measurements are independent at different times.
+Analogously, the expectation becomes 0 if $i \neq k$ because the measurement noises are independent at different times.
 
@@
 
-The optimal design of experiment technique is used extend the experiment discussed in ${\color{red}article~1}$, where supercritical extraction from caraway seeds has been discussed.
-In this work, the extraction has been performed at multiple operating conditions, such that the temperature, pressure and flow-rate were constant during each batch.
-Later, the results from all the experiments are combined and correlations for extraction kinetic parameters are presented.
-In this work, the optimal design of experiment is used to design an experiment to validate these correlations.
-The model parameters and the sampling time are the same as in ${\color{red}article~1}$ to mimic the original system.
-It is assumed that the flow-rate is constant, because the effect of the flow-rate has not been deeply investigated.
-The inlet temperature can be controlled by a controller
+The optimal design of the experiment technique is used to extend the experiment discussed in $({\color{red}article~1})$, where supercritical extraction from caraway seeds has been discussed.
+The presented extraction was performed under multiple operating conditions, such that the temperature, pressure, and flow rate were constant during each batch.
+Later, the experiments' results are combined, and correlations for extraction kinetic parameters are presented.
+In this work, the optimal design of the experiment is used to design an experiment to validate these correlations.
+The model parameters, the extraction time (150 minutes), and the sampling time (5 minutes) are the same as in $({\color{red}article~1})$ to mimic the original system.
+It is assumed that the flow rate is constant because the effect of the flow rate has not been deeply investigated in the previous work of the authors (${\color{red}articl~1}$).
+The pressure is assumed to be constant during the whole experiment.
+The initial temperature ($T^0$) of the extractor and the inlet temperature ($T^{in}$) are decision variables in the optimization.
+It is considered that the initial state is isothermal, so $T^0=T^{in}(t=0)$.
+The inlet temperature is changed every 5 minutes, and considered to be constant inside of this time period.
+Considering that the residence time in the extractor is around 20-25 minutes (depending on the operating conditions), it is assumed that there is no change in the inlet temperature in the last 25 minutes of extraction, so the extractor becomes isothermal at the end of the experiment.
+The lower ($40^\circ C$) and upper ($50^\circ C$) bounds for the temperature are limits of the previous experiments (${\color{red}article~1}$).
+The general formulation of the optimal design of experiment problem is presented below.
 
@@
 	\begin{aligned} 
-		&\hat{{\color{black} \theta}}_{MLE} &= \arg \max_{{\color{black} \sigma}, {\color{black} \theta} \in \Theta} \ln L = \arg \max_{{\color{black} \sigma},{\color{black} \theta} \in \Theta} p({\color{black} \theta}|{\color{black}y}) \\
+		&\Xi^* &= \arg \min_{ T^0, T^{in} \in \Xi} -j_D(\Xi,y)  \\
 		&\text{subject to}
-		& \dot{ {\color{black}x} } = {\color{black}G}({\color{black} x}(t);{\color{black} \theta}) \\
-		&& {\color{black} \dot{\theta}} = 0 \\
-		&& {\color{black}y} = {\color{black}y}(t) \\
-		&& {\color{black} \theta}^{lb} \leq {\color{black} \theta} \leq {\color{black} \theta}^{ub}
+		& \dot{x} = f(x,t,\theta;\Xi) \\
+		&& \dot{y} = g(x(t)) \\
+		&& 40^\circ C \leq T^{in}(t) \leq 50^\circ C \\
+		&& T^{0} = T^{in}(t=0) \\
 	\end{aligned}
@@
 
+The non-linear optimization problem is solved by applying single-shooting to obtain the trajectory under assumption of piece-wise constant controls.
+The CasADi framework is used as the interface for the IPOPT solver.
+Each simulation problem is solved multiple time starting from different initial points and the solution with the best score is consider as the optimal solution.
+
+\section{Results and discussion}
+The D-optimal Design of the Experiment is used to define the way to run the experiment to validate the hypothesis presented in $({\color{red}article~1})$, which are the correlations for $D_i$ and $\Gamma$.
+It is assumed that the experiment is performed on the same equipment as in the previous work, so all the properties of the machine and the biomass stay the same.
+The flow rate and the pressure are considered to be constant during the whole experiment.
+In the previous work, the pressure range was from 200 bar to 300 bar; in this experiment, the pressure is assumed to be 250 bar.
+The initial and the inlet temperatures are found by solving the optimization problem.
+The optimization problem was solved 69 times, starting from random initial conditions between $40^\circ C$ and $50^\circ C$.
+Figure \ref{fig:monet_carlo_P250} summarize solutions to all the optimization problem.
+The x-axis corresponds to the initial value of the D-optimal score, while the y-axis represents the D-optimal score's final value.
+As the optimization problem is formulated as the minimization, the lowest negative value is considered the best.
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.80\textwidth, trim = 0cm 0cm 0cm 0cm, clip]{Multiple_shot_DOE_P250.pdf}
+	\caption{Comparison between initial and optimal solutions}
+	\label{fig:monet_carlo_P250}
+\end{figure}
+
+Based on Figure \ref{fig:monet_carlo_P250}, five best results were selected and the the corresponding inlet temperatures are presented on Figure \ref{fig:Best_T_in_P250}.
+Corresponding outlet temperatures are presented in Figure \ref{fig:Best_T_out_P250}.
+The inlet and outlet temperature profiles difference from each other due to thermal diffusion.
+For all five cases, the inlet profiles overlap with each other.
+
+\begin{figure}[!h]
+	\centering
+	\begin{subfigure}[h]{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth,trim = 0cm 0cm 0cm 0cm, clip]{Best_T_in_P250.pdf}
+		\caption{Inlet temperature profile}
+		\label{fig:Best_T_in_P250}
+	\end{subfigure}%
+	~ 
+	\begin{subfigure}[h]{0.5\textwidth}
+		\centering
+		\includegraphics[width=\textwidth,trim = 0cm 0cm 0cm 0cm, clip]{Best_T_out_P250.pdf}
+		\caption{Outlet temperature profile}
+		\label{fig:Best_T_out_P250}
+	\end{subfigure}
+	\caption{Temperature profiles}
+	\label{fig:DOE_results}
+\end{figure}
+
+It can be observed that all the results are very similar to each other and represent the same pattern.
+The optimizer found that the best score, given the assumptions explained above, can be obtained by the square waves.
+This pattern is characterized by periods where the temperature remains constant at a particular value, followed by sudden and steep changes to a new constant value.
+In this graph, the temperature alternates between roughly $313$ K and $323$ K.
+
+At the beginning of the experiment, the temperature rapidly rises to $323$ K and stays flat at this high level for about 20 minutes, indicating that the supercritical $CO_2$ has reached a stable temperature.
+Following this period, there is a sharp decline to a lower stable temperature of around $313$ K, where it again remains constant for a similar duration.
+After maintaining the lower temperature, the pattern repeats itself with another sharp increase back to $323$ K, followed by a period of stability and then another drop.
+
 \end{document}

### 2023-12-14 SFE_Design_of_Experiment/modelSFE.m

@@ -47,11 +47,11 @@ function xdot = modelSFE(x, p, mask, dt)
     Z             =     Compressibility(TEMP, PRESSURE,    parameters);
 
     RHO           =     rhoPB_Comp(     TEMP, PRESSURE, Z, parameters);   
-    VELOCITY      =     Velocity(F_u, mean(RHO), parameters) .* ones(nstages_index,1);
+    VELOCITY      =     Velocity(F_u, mean([RHO(2:19:end)]), parameters) .* ones(nstages_index,1);
     
     %% Thermal Properties
     CP            =     SpecificHeatComp(TEMP, PRESSURE, Z, RHO,                 parameters);            % [kJ/kg/K]
-    CPRHOCP       =     cpRHOcp_Comp(    TEMP, PRESSURE, Z, RHO, CP, epsi.*mask, parameters);
+    %CPRHOCP       =     cpRHOcp_Comp(    TEMP, PRESSURE, Z, RHO, CP, epsi.*mask, parameters);
     KRHOCP        =     kRHOcp_Comp(     TEMP, PRESSURE, Z, RHO, CP, epsi.*mask, parameters);
 
     %% Extraction kientic
@@ -65,7 +65,7 @@ function xdot = modelSFE(x, p, mask, dt)
     Sat_coe       =     Saturation_Concentration(Csolid_percentage_left, shape, Di);        % Inverse logistic is used to control saturation. Close to saturation point, the Sat_coe goes to zero.
 
     %% BC
-    %Cf_0          =     if_else(F_u == 0, FLUID(1), 0);
+    
     Cf_0          =     0;
     Cf_B          =     FLUID(nstages_index);
                                                                                             % If the sensitivity of P and F is consider, then set the input T as equal to the T inside of the extractor
@@ -75,14 +75,11 @@ function xdot = modelSFE(x, p, mask, dt)
     T_B           =     TEMP(nstages_index);
 
     Z_0           =     Compressibility(T_0, PRESSURE,     parameters);
-    %Z_B           =     Compressibility(T_B, PRESSURE,     parameters);
-
+    
     rho_0         =     rhoPB_Comp(     T_0, P_u, Z_0, parameters);
-    %rho_B         =     rhoPB_Comp(     T_B, PRESSURE, Z_B, parameters);
-
-    u_0           =     Velocity(F_u, rho_0, parameters);
[…]

### 2023-12-14 SFE_Design_of_Experiment/test_direct_jacob.m

@@ -6,23 +6,24 @@ delete(gcp('nocreate'));
 addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
 import casadi.*
 
-numeEval = 6;
+excel_file = 'output_P250.xls';
+numeEval = 69;
 
-for ii=1:numeEval
+parfor ii=61:numeEval
 
 Parameters_table                = readtable('Parameters.csv') ;             % Table with prameters
 Parameters                      = num2cell(Parameters_table{:,3});          % Parameters within the model + (m_max), m_ratio, sigma
 
 %% Create the solver
-Iteration_max                   = 200;                                        % Maximum number of iterations for optimzer
-Time_max                        = 24.0;                                     % Maximum time of optimization in [h]
+Iteration_max                   = 100;                                       % Maximum number of iterations for optimzer
+Time_max                        = 12.0;                                      % Maximum time of optimization in [h]
 
 nlp_opts                        = struct;
 nlp_opts.ipopt.max_iter         = Iteration_max;
 nlp_opts.ipopt.max_cpu_time     = Time_max*3600;
 nlp_opts.ipopt.hessian_approximation ='limited-memory';
-%nlp_opts.ipopt.tol              = 1e-5;
-%nlp_opts.ipopt.acceptable_tol   = 1e-3;
+nlp_opts.ipopt.tol              = 1e-6;
+nlp_opts.ipopt.acceptable_tol   = 1e-4;
 %nlp_opts.ipopt.acceptable_iter = 5;
 
 OPT_solver                      = casadi.Opti();
@@ -41,8 +42,9 @@ bed                     = 0.165;                                            % Pe
 % Set time of the simulation
 PreparationTime         = 0;
 ExtractionTime          = 150;
-DeadTime                = 30;
-timeStep                = 2.5;                                              % Minutes
+DeadTime                = 25;
+timeStep                = 1;                                                % Minutes
+timeShited              = 0;                                                % Minutes
[…]

### 2024-01-12 SFE_article_Sensitivity_Analysis/Article_Model_Parameters.tex
12.01

@@
 \subfile{Sections/introduction_imp}
+This study aims to analyse the influence of the operating conditions on the supercritical extraction process described in {\color{red}article 1}.
+To achieve this, The local sensitivity analysis methods is applied to obtain the sensitivity equations.
+The influence of mass-flow rate, pressure and the inlet temperature are considered.
+
+\subfile{Sections/Literature_Review}
+
+The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties.
+Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations.
+The balance equations are combined with the extraction kinetic equation to develop the process model in Chapter \ref{CH: Extraction_model}.
+The derivative-based local sensitivity analysis is presented in Chapter \ref{CH: Sensitivity_Analysis} and is then combined with the process model.
+Finally, the sensitivity plots are discussed in Chapters \ref{CH: Results} and \ref{CH: Conclusion}.
 

### 2024-01-12 SFE_article_Sensitivity_Analysis/Sections/Literature_Review.tex
12.01

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	Sensitivity analysis is the study of how the uncertainty in the output of a mathematical model or system (numerical or otherwise) can be divided and allocated to different sources of uncertainty in its inputs or model parameters. As a mathematical model can be complex and consists of multiple parameters, a method to evaluate the relation between inputs and outputs, such a technique is called sensitivity analysis. There are a large number of approaches to performing a sensitivity analysis, which include but it is not limited to the following methods:

	\begin{itemize}
		\item One-at-a-time method
		\item Derivative-based local methods
		\item Variance-based methods
	\end{itemize}

	\citet{Fiori_2007} applied the sensitivity analysis to supercritical extraction process. The sensitivity calculations were performed by varying the parameters within their confidence interval and observing how the model results change, which allows to establish the effect of the uncertainties on model predictions. The sensitivity analysis revealed that two parameters are particularly important for the extraction process: the particle diameter and the internal mass transfer coefficient. The effect of changing some operative conditions is also investigated, underlining how the solvent flow rate and the seed milling affect the extraction process.

	\citet{Santos2000}, in their work considered a diffusive model for semi-continuous isothermal and isobaric extraction process using supercritical carbon dioxide. The parametric sensitivity analysis by means of a factorial design in two levels was considered. The model parameters were disturbed and their main effects analysed, so that it is possible to propose strategies for high performance operation. The parametric sensitivity analysis was carried out by applying disturbances of 10\% in the values of the normal operation conditions.

	\citet{Hatami2024} deploed two distinct strategies for sensitivity analysis. The first strategy applies uniform fluctuations to technical and economic parameters, while the second employs actual parameter ranges for fluctuation. The combination of these two strategies provide insights into both the sensitivity of net present value (NPV) to the unit relative change in each factor and the maximum potential of each factor to influence NPV.

	\citet{Poletto1996} provided a general dimensionless model was developed for a sensitivity analysis of the supercritical extraction process of vegetable oils and essential oils. Two dimensionless parameters, a dimensionless partition coefficient, and a dimensionless characteristic time, appeared as the most important parameters to monitor the evolution of the extraction process. The sensitivity calculations were performed by varying the parameters and analysis the model response.

\end{document}

### 2024-01-12 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
12.01

@@
 The process model was calibrated on set of experiments obtained at different operating conditions, $40^\circ C$ - $50^\circ C$ and 200 bar - 300 bar.
-The sensitivity analysis has been performed under the assumption that the system operates are $45^\circ C$, 250 bar, 0.4 l/min.
-The simulation was performed with the time step of 0.01 [min] and 400 equally distributed points in the spatial direction.
+The sensitivity analysis has been performed under the assumption that the system operates are $45^\circ C$, 250 bar and 0.4 l/min.
 
@@
     The flow rate change affects the fluid inside the system, but appropriate boundary conditions must be set.
-When utilizing Dirichlet boundary conditions, it's crucial to be aware of potential numerical discrepancies stemming from the differing methods used to compute them.
+When utilizing Dirichlet boundary conditions, it's crucial to be aware of potential numerical artifacts from the differing methods used to compute them.
 The system's enthalpy is determined through the time evolution of governing equations, while the inlet's enthalpy depends on the inlet temperature and pressure.
@@
 This reduced amount of solute in the solid phase restricts the extraction rate due to a diminishment of the concentration gradient.
-This limitation leads to the formation of a front composed of negative sensitivities, which advances through the extractor.
+This limitation leads to the formation of a front composed of negative sensitivities, which propagate through the extractor.
 The negative front indicates that the solute concentration in the fluid phase becomes lower than before the flow rate increment.
@@
 Alternatively, Neumann boundary conditions can be applied to ensure that the temperature inside the extractor matches that at its inlet.
-In this work, the second approach was chosen to simplify the discussion.
+In this work, the second approach was chosen.
 

### 2024-01-12 SFE_article_Sensitivity_Analysis/Sections/introduction_imp.tex
12.01

--- 2023-10-03 SFE_article_Parameter_Estimation/Sections/introduction_imp.tex
@@
 Furthermore, its critical point is relatively low compared to other fluids, making it a suitable alternative to traditional extraction techniques.
-The supercritical fluids exhibit both gas- and liquid-like properties so that operating conditions can adjust pressure-depended dissolving power.
+The supercritical fluids exhibit both gas- and liquid-like properties so that operating conditions can adjust the dissolving power.
 
@@
 	One model proposed by \citet{Reverchon1993} is the hot ball model, which is based on an analogy to heat transfer and describes an extraction process from solid particles containing small quantities of solute where solubility is not a limiting factor.
+
 	Another model, the Broken-and-Intact Cell model, was presented by \citet{Sovova1994}.
@@
 
-	This study aims to develop a process model for extracting natural substances from solid materials and liquids using supercritical fluids, specifically supercritical $CO_2$.
-To achieve this, the model parameters are estimated based on thermodynamic relations and a set of experiments conducted at various conditions.
-The maximum likelihood estimator is used to solve the parameter estimation problem, and the obtained parameters are subjected to regression to derive correlations.
-These correlations enable the process model to be generalized across a range of temperatures (40 to $50~^\circ C$) and pressures (200 to 300 bar).
-
-	The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties.
-Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations.
-The balance equations are combined with the extraction kinetic equation to develop the process model in Chapter \ref{CH: Extraction_model}.
-The maximum likelihood technique is presented in Chapter \ref{CH: Parameter_estimation} and is then combined with the process model.
-Chapter \ref{CH: Experiments} describes the experimental work and the data collected from experiments are used to estimate missing parameters related to the extraction kinetic.
-Finally, the parameter estimations and simulation results are discussed in Chapters \ref{CH: Results} and \ref{CH: Conclusion}
-
 \end{document}

### 2024-01-15 SFE_article_Sensitivity_Analysis/Article_Model_Parameters.tex
15.01

@@
 \subfile{Sections/introduction_imp}
-This study aims to analyse the influence of the operating conditions on the supercritical extraction process described in {\color{red}article 1}.
-To achieve this, The local sensitivity analysis methods is applied to obtain the sensitivity equations.
-The influence of mass-flow rate, pressure and the inlet temperature are considered.
 

### 2024-01-15 SFE_article_Sensitivity_Analysis/Sections/Literature_Review.tex
15.01

@@
 
+	This study aims to analyse the influence of changes in operating conditions on the supercritical extraction process described in {\color{red}article 1}.
+The emphasis is put on the effect of to mass-flow rate, pressure and the inlet temperature.
+The relation between input and output are obtained by applying a sensitivity analysis on the process model.
 Sensitivity analysis is the study of how the uncertainty in the output of a mathematical model or system (numerical or otherwise) can be divided and allocated to different sources of uncertainty in its inputs or model parameters.
-As a mathematical model can be complex and consists of multiple parameters, a method to evaluate the relation between inputs and outputs, such a technique is called sensitivity analysis.
-There are a large number of approaches to performing a sensitivity analysis, which include but it is not limited to the following methods:
+There are many sensitivity analysis methods which include but are not limited to those listed below:
 
@@
 
-	\citet{Fiori_2007} applied the sensitivity analysis to supercritical extraction process.
+	Different supercritical extraction models were analyzed using sensitivity analysis.
+One example of such work is \citet{Fiori_2007}.
 The sensitivity calculations were performed by varying the parameters within their confidence interval and observing how the model results change, which allows to establish the effect of the uncertainties on model predictions.
 The sensitivity analysis revealed that two parameters are particularly important for the extraction process: the particle diameter and the internal mass transfer coefficient.
-The effect of changing some operative conditions is also investigated, underlining how the solvent flow rate and the seed milling affect the extraction process.
+The effect of changing some operative conditions was also investigated, underlining how the solvent flow rate and the seed milling affect the extraction process.
 
-	\citet{Santos2000}, in their work considered a diffusive model for semi-continuous isothermal and isobaric extraction process using supercritical carbon dioxide.
-The parametric sensitivity analysis by means of a factorial design in two levels was considered.
-The model parameters were disturbed and their main effects analysed, so that it is possible to propose strategies for high performance operation.
+	\citet{Santos2000}, in their work considered a model of supercritical extraction process for semi-continuous isothermal and isobaric extraction process using carbon dioxide as a solvent.
 The parametric sensitivity analysis was carried out by applying disturbances of 10\% in the values of the normal operation conditions.
 
-	\citet{Hatami2024} deploed two distinct strategies for sensitivity analysis.
-The first strategy applies uniform fluctuations to technical and economic parameters, while the second employs actual parameter ranges for fluctuation.
-The combination of these two strategies provide insights into both the sensitivity of net present value (NPV) to the unit relative change in each factor and the maximum potential of each factor to influence NPV.
+	\citet{Hatami2024} used a one-factor-at-a-time sensitivity analysis to assess the response of NPV concerning variations in both technical and economic variables.
+Their findings shows that the most influential factors on NPV include the price of the extract, the interest rate, the dynamic time of SFE, and the project lifetime.
 
 	\citet{Poletto1996} provided a general dimensionless model was developed for a sensitivity analysis of the supercritical extraction process of vegetable oils and essential oils.
-Two dimensionless parameters, a dimensionless partition coefficient, and a dimensionless characteristic time, appeared as the most important parameters to monitor the evolution of the extraction process.
+A dimensionless partition coefficient, and a dimensionless characteristic time, appeared as the most important parameters to monitor the evolution of the extraction process.
 The sensitivity calculations were performed by varying the parameters and analysis the model response.

### 2024-01-15 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
15.01

@@
 
-	The sensitivity equations were solved simultaneously with the original process model.
 	This work investigates the influence of inlet temperature, pressure, and mass flow rate on the state space and the extraction yield.
@@
 The process model was calibrated on set of experiments obtained at different operating conditions, $40^\circ C$ - $50^\circ C$ and 200 bar - 300 bar.
-The sensitivity analysis has been performed under the assumption that the system operates are $45^\circ C$, 250 bar and 0.4 l/min.
+The sensitivity analysis has been performed under the assumption that the system operates are $45^\circ C$, 250 bar and 0.4 l/min, which is the middle of the range of operating conditions.
 

### 2024-01-15 SFE_article_Sensitivity_Analysis/Sections/Sensitivity_Analysis.tex
15.01

@@
 The purpose of the sensitivity analysis is to investigate how responsive the solution is for the perturbation of the parameter ${p}$.
-According to \citet{Dickinson1976}, the sensitivity analysis can be used to determine the influence of the uncertainty on the solution of the original system.
-Another purpose is to distinguish sensitive parameters from insensitive ones, which might be helpful for model reduction.
+As discussed by \citet{Dickinson1976}, the sensitivity analysis can be used to determine the influence of the uncertainty on the solution of the original system.
+A sensitivity analysis can be used to distinguish sensitive parameters from insensitive ones, which might be helpful for model reduction.
 Finally, from a control engineering point of view, the sensitivity analysis allows to sort the control variables with respect to the level of effort required to change the model's output.
 
-	As presented in the work of \citet{Maly1996}, the sensitivity analysis equations(${\dot{Z}}$) are developed by taking the total derivative of the original system ${F}({x}(t);{p})$ with respect to ${p}$.
+	As presented in the work of \citet{Maly1996}, the sensitivity analysis equations(${\dot{Z}}$) are developed by taking the total derivative of the state vector $x$ with respect to parameters $p$, where $p$ is a subset of $\theta$.
 
@@
 			%		\label{SA_def}
-			{Z}({x}(t);{p}) &= \cfrac{\partial {x}(t)}{\partial {p}}
+			{Z}({x}(t);{p}) &= \cfrac{d {x}(t)}{d {p}}
 	\end{align} }
 
-	As the process model depends on time $t$, parameters $p$ and initial conditions, each parameter's sensitivity also depend on time $t$.
-Therefore, the new system of equations can be obtained by taking derivatives with respect to time $t$ and applying the chain rule.
+	The new system of equations can be obtained by taking derivatives of $Z$ with respect to time $t$ and applying the chain rule.
 
@@
 		\begin{equation} \label{SA_dt} 
-			{\dot{Z}}({x}(t);{p})  = \cfrac{d {Z}(x(t);{p})}{d t} = \cfrac{\partial }{\partial t} \left( \cfrac{\partial {x}(t)}{\partial {p}} \right) = \cfrac{\partial }{\partial {p}} \left( \cfrac{\partial {x}(t)}{\partial t} \right) = \cfrac{d {F}({x}(t);{p})}{d {p}}
+			{\dot{Z}}({x}(t);{p})  = \cfrac{d {Z}(x(t);{p})}{d t} = \cfrac{d}{d t} \left( \cfrac{d {x}(t)}{d {p}} \right) = \cfrac{d }{d {p}} \left( \cfrac{d {x}(t)}{d t} \right) = \cfrac{d {G}({x}(t);{p})}{d {p}}
 	\end{equation} }
 
-	By applying the definition of the total derivative to the equation \ref{SA_dt}, the sensitivity equation can be obtained.
+	By applying the definition of the total derivative to the Equation \ref{SA_dt}, the sensitivity equation can be obtained.
 
@@
 		\begin{align}		
-			\label{SA_eq_full}\cfrac{d {F}({x}(t);{p})}{d {p}} &=  \underbrace{ \cfrac{\partial {F}({x}(t);{p})}{\partial {x}(t)} }_{{J_x}({x}(t);{p})} \underbrace{\cfrac{\partial {x}(t)}{\partial {p}} }_{{S}({x}(t);{p})} + \underbrace{ \cfrac{\partial {F}({x}(t);{p})}{\partial {p}} }_{{J_p}({x}(t);{p})}
+			\label{SA_eq_full}\cfrac{d {G}({x}(t);{p})}{d {p}} &=  \underbrace{ \cfrac{\partial {G}({x}(t);{p})}{\partial {x}(t)} }_{{J_x}({x}(t);{p})} \underbrace{\cfrac{\partial {x}(t)}{\partial {p}} }_{{S}({x}(t);{p})} + \underbrace{ \cfrac{\partial {G}({x}(t);{p})}{\partial {p}} }_{{J_p}({x}(t);{p})}
 	\end{align} }
 
-	The sensitivity equation \ref{SA_eq_full} is solved simultaneously with the original system.
-This equation is made of three terms: jacobian ${J_x}({x}(t);{p})$, sensitivity matrix ${S}({x}(t);{p})$ and jacobian ${J_p}({x}(t);{p})$.
-The jacobian ${J_x}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${J_x}(n_x,n_x)$ is the derivative of process model equations ${F}_{n_x}({x}(t);{p})$ with respect to the state variable $x_{n_p}$.
+	The sensitivity Equation \ref{SA_eq_full} is solved simultaneously with the original syste and is made of three terms: jacobian ${J_x}({x}(t);{p})$, sensitivity matrix ${S}({x}(t);{p})$ and jacobian ${J_p}({x}(t);{p})$.
+The jacobian ${J_x}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${J_x}(n_x,n_x)$ is the derivative of process model equations ${G}_{n_x}({x}(t);{p})$ with respect to the state variable $x_{n_p}$.
 
@@
 			{J_x}({x}(t);{p})=\begin{pmatrix}
-				\cfrac{\partial {F_{1}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {F_{1}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {F_{1}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
-				\cfrac{\partial {F_{2}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {F_{2}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {F_{2}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
+				\cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
+				\cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
 				\vdots & \vdots & \ddots & \vdots\\ 
-				\cfrac{\partial {F_{N_x}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {F_{N_x}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {F_{N_x}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
+				\cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
 			\end{pmatrix}
@@
 				\begin{pmatrix}
-					\cfrac{d {x_{1}}(t)}{d {p_{1}}} 	& \cfrac{d {x_{1}}(t)}{d {p_{2}}}     & \cdots & \cfrac{d {x_{1}}(t)}{d {p_{N_p}}}\\
-					\cfrac{d {x_{2}}(t)}{d {p_{1}}} 	& \cfrac{d {x_{2}}(t)}{d {p_{2}}}     & \cdots & \cfrac{d {x_{2}}(t)}{d {p_{N_p}}}\\
+					\cfrac{\partial {x_{1}}(t)}{\partial {p_{1}}} 	& \cfrac{\partial {x_{1}}(t)}{d {p_{2}}}     & \cdots & \cfrac{d {x_{1}}(t)}{\partial {p_{N_p}}}\\
+					\cfrac{\partial {x_{2}}(t)}{\partial {p_{1}}} 	& \cfrac{\partial {x_{2}}(t)}{d {p_{2}}}     & \cdots & \cfrac{d {x_{2}}(t)}{\partial {p_{N_p}}}\\
 					\vdots					 	    & \vdots 					   	  & \ddots & \vdots\\
-					\cfrac{d {x_{N_x}}(t)}{d {p_{1}}} 	& \cfrac{d {x_{N_x}}(t)}{d {p_{2}}}     & \cdots & \cfrac{d {x_{N_x}}(t)}{d {p_{N_p}}}
+					\cfrac{\partial {x_{N_x}}(t)}{\partial {p_{1}}} 	& \cfrac{\partial {x_{N_x}}(t)}{d {p_{2}}}     & \cdots & \cfrac{\partial {x_{N_x}}(t)}{d {p_{N_p}}}
 				\end{pmatrix} 
@@
 
-	The jacobian ${J_p}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_p$, where each equation ${J_p}(n_x,n_p)$ is the direct derivative of the process model equation $F_{n_x}$ with respect to the parameter $p_{n_p}$.
+	The jacobian ${J_p}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_p$, where each equation ${J_p}(n_x,n_p)$ is the partial derivative of the process model equation $F_{n_x}$ with respect to the parameter $p_{n_p}$.
 
@@
 			\begin{pmatrix}
-				\cfrac{\partial {F_{1}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {F_{1}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {F_{1}}({x}(t);{p})}{\partial {p_{N_p}}}\\
-				\cfrac{\partial {F_{2}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {F_{2}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {F_{2}}({x}(t);{p})}{\partial {p_{N_p}}}\\
+				\cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {p_{N_p}}}\\
+				\cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {p_{N_p}}}\\
 				\vdots & \vdots & \ddots & \vdots\\
-				\cfrac{\partial {F_{N_x}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {F_{N_x}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {F_{N_x}}({x}(t);{p})}{\partial {p_{N_p}}}
+				\cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {p_{N_p}}}
 			\end{pmatrix}
@@
 
-	The combined system containing the original set of equations ${F}({x}(t);{p})$ and sensitivity equations can be formulated as ${\textbf{F}}\left({x}(t);{p}\right)$.
-The size of ${\textbf{F}}\left({x}(t);{p}\right)$ is equal to $N_s = N_x(N_p + 1)$.
+	The combined system containing the original set of equations ${G}({x}(t);{p})$ and sensitivity equations can be formulated as ${\textbf{G}}\left({x}(t);{p}\right)$.
+The size of ${\textbf{G}}\left({x}(t);{p}\right)$ is equal to $N_s = N_x(N_p + 1)$.
 
@@
 		\begin{align}
-			{\textbf{F}}\left({x}(t);{p}\right) = 
+			{\textbf{G}}\left({x}(t);{p}\right) = 
 			\begin{bmatrix}
-				{F}({x}(t);{p})\\
+				{G}({x}(t);{p})\\
 				{J_x}({x}(t);{p}){S}({x}(t);{p}) + {J_p}({x}(t);{p})
@@
 		\begin{align}
-			{\textbf{F}}\left({x}(t_0);{p}\right)  = 
+			{\textbf{G}}\left({x}(t_0);{p}\right)  = 
 			\begin{bmatrix} {x}(t_0),			& 

### 2024-01-19 SFE_article_Sensitivity_Analysis/Article_Model_Parameters.tex
19.01

@@
 The mathematical formulation involves derivative-based local sensitivity analysis of the solution of an inverse problem with respect to perturbations of parameters.
-The local method is based only on considering all parameters as constants (those independent of time or location), and then the sensitivity coefficients are estimated by solving a variational system simultaneously with the original system.
-The sensitivity equations can be obtained in various ways, but in the case of this work, the automatic differentiation technique was implemented to obtain the sensitivity equations.
-By identifying which parameters are influential at each period of the simulation, local sensitivity analysis can yield valuable information for guiding the design of experiments, the process modeling, or the model reduction.
+The local method is based only on considering all parameters as constants (those independent of time or location), and then the sensitivity equations are estimated by solving a variational system simultaneously with the original system.
+The sensitivity equations can be obtained in various ways, but the automatic differentiation technique was implemented to obtain the sensitivity equations in this work.
+By identifying which parameters are influential at each period of the simulation, local sensitivity analysis can yield valuable information for guiding the process modelling, the design of experiments or the model reduction.
 The local sensitivity analysis techniques consider the sensitivities at only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions unless the discussed system is a linear system.
@@
 This information can be utilized to identify which control variables influence the extraction yield the most.
-The controls with high sensitivities on the extraction can be used to investigated to find optimal operating conditions from economic point of view.
+The controls with high sensitivities on the extraction can be used to investigate to find optimal operating conditions from an economic point of view.
 

### 2024-01-19 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
19.01

--- 2024-01-12 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
@@
 
-	The sensitivity equations were solved simultaneously with the original process model.
 	This work investigates the influence of inlet temperature, pressure, and mass flow rate on the state space and the extraction yield.
 The process model and parameters have been discussed in {\color{red}article 1}.
-The process model was calibrated on set of experiments obtained at different operating conditions, $40^\circ C$ - $50^\circ C$ and 200 bar - 300 bar.
+The process model was calibrated on the set of experiments obtained at different operating conditions, $40$ - $50^\circ C$ and 200 - 300 bar.
 The sensitivity analysis has been performed under the assumption that the system operates are $45^\circ C$, 250 bar and 0.4 l/min.
 
-	\subsection{Flow-rate}
+	\subsection{Flow rate}
 
-	The increase in the mass-flow rate affects the whole system simultaneously in the spatial direction.
-The change in mass flow-rate makes the fluid move faster and does not directly affect the thermodynamic state of the fluid.
+	The increase in the mass-flow rate affects the system simultaneously along the spatial direction by increasing the velocity but without affecting the thermodynamic state of the fluid.
 As a result, Figure \ref{fig:Sensitivty_F_P} shows no change in pressure during the simulation.
@@
 
-    A flow rate change is defined by the spatial derivative $\frac{\partial \left( {\color{orange}\rho_f}{\color{blue}h} A_f v \right)}{\partial {\color{blue}z}}$.
-The consequence of Equation \ref{EQ:Velocity} is the instantaneous change of the velocity field in the system, which means that the spatial derivative equals zero.
-It's important to note that ${\color{blue}h}$ represents enthalpy but not total enthalpy, thus excluding kinetic energy contribution.
-As a consequence of our modelling assumptions, changes in ${\color{blue}h}$ and ${\color{orange}\rho_f}$ only occur in response to direct change in pressure or temperature.
-As the result, Figure \ref{fig:Sensitivty_F_H} demonstrates no significant deviation.
+    It's important to note that $h$ represents enthalpy but not total enthalpy, thus excluding kinetic energy contribution.
+As a consequence of the modelling assumptions, changes in $h$ and $\rho_f$ occur only in response to direct change in pressure or temperature, which is demonstrated by no significant deviation of $h \times \rho_f$ in Figure \ref{fig:Sensitivty_F_H}.
 
-    The flow rate change affects the fluid inside the system, but appropriate boundary conditions must be set.
-When utilizing Dirichlet boundary conditions, it's crucial to be aware of potential numerical artifacts from the differing methods used to compute them.
-The system's enthalpy is determined through the time evolution of governing equations, while the inlet's enthalpy depends on the inlet temperature and pressure.
+    %When utilizing Dirichlet boundary conditions, it's crucial to be aware of potential numerical artefacts from the differing methods used to compute them.
+The system's enthalpy is determined through the time evolution of governing equations, while the inlet's enthalpy depends on the inlet temperature and pressure, which are the controls.
 A minor numerical mismatch between these values may manifest as an enthalpy difference propagating along the spatial domain.
@@
 
-   An increase in the mass flow rate impacts the concentration gradient and the extraction kinetics as presented in Figure \ref{fig:Sensitivty_F_CS} .
-At the beginning of the extraction process, changes in the flow rate have a minimal effect on the extraction process, as showed by sensitivities that are close to zero.
-This is due to the dominance of the high concentration gradient, which leads the extraction kinetic.
+   Figure \ref{fig:Sensitivty_F_CS} shows how the flow rate affects the concentration of the solute in the solid phase.
+At the beginning of the extraction process, the flow rate have a low impact on the extraction process due to the dominance of the concentration gradient in the kinetic regime.
+The corresponding sensitivities are close to zero.
 As time progresses, the increase in the mass flow rate have greater influence on the extraction kinetics, causing the sensitivities to decrease towards their minimum values.
 Negative sensitivities indicate a faster extraction rate.
-Over time, the amount of solute in the solid phase decreases, and eventually, the extraction kinetic becomes limited by the concentration gradient.
-This behavior is represented in the sensitivities, which asymptotically approach zero.
+Eventually, the amount of solute in the solid phase decreases, and the extraction kinetic becomes limited by the concentration gradient.
+This behaviour is represented by sensitivities, which increase from their minimal values and asymptotically approach to zero.
 The asymptotic movement of sensitivities can be explained by the fact that an increase in the flow rate does not impact the extraction process when all the solute has been removed from the solid phase.
@@
 Initially, sensitivities are close to zero, indicating a minimal system response.
-The growth in flow rate affects ${\color{blue}C_f}(z,t)$ by increasing the velocity, consequently elevating the concentration gradient.
+The growth in flow rate affects $C_f(z,t)$ indirectly by increasing the velocity and consequently elevating the concentration gradient.
 As a result, positive sensitivities emerge within the system, forming a front that progresses in the direction of flow.
-The positive front indicates that the larger amount of solute moves faster across the system, which leads to faster decrease of the total amount of solute in both phases.
-This reduced amount of solute in the solid phase restricts the extraction rate due to a diminishment of the concentration gradient.
-This limitation leads to the formation of a front composed of negative sensitivities, which propagate through the extractor.
+The positive front indicates that the larger amount of solute moves faster across the system.
+When the amount of the solute in the solid phase becomes a limiting factor, then the concentration gradient diminishes and slows down the extraction kinetics.
+The corresponding sensitivities form a front composed of negative sensitivities propagating through the extractor.
 The negative front indicates that the solute concentration in the fluid phase becomes lower than before the flow rate increment.
-Eventually, the negative sensitivities asymptotically approach zero.
+Eventually, the negative sensitivities start to increase and asymptotically approach zero.
 
@@
 Initially, the sensitivity curve remains flat.
-This occurs because the fixed bed doesn't occupy the entire volume of the extractor, requiring some time for the fluid to flow through the empty portion of the extractor to reach its outlet.
-It's only when the solute in the fluid phase reaches the extractor's outlet that we can measure and observe the system response.
-At this point, $dy/dF$ begins to increase.
-The positive sensitivity value indicates an improvement in process efficiency, resulting in an increased yield.
-As time progresses, the sensitivity reaches its maximum and then diminishes due to a decreasing concentration gradient.
+This occurs because the fixed bed doesn't occupy the entire volume of the extractor.
+Hence, some time is required for the fluid to flow through the empty portion of the extractor to reach its outlet.
+Only when the solute in the fluid phase reaches the extractor's outlet can the yield be measured.
+After the idle time, the system response can be observed as the increment of  $dy/dF$.
+The positive sensitivity value indicates improved process efficiency, increasing yield.
+As time progresses, the sensitivity reaches its maximum and diminishes due to a decreasing concentration gradient.
 Eventually, $dy/dF$ asymptotically approaches zero.
-This happens because the amount of solute in the fluid phase becomes a limiting factor in the extraction process, and the increase in flow rate has a reduced impact on the extraction yield.
-The simulation time was extended to demonstrate the convergence of $dy/dF$ toward zero.
+This happens because the amount of solute in the fluid phase becomes a limiting factor, and the process is in the diffusion regime.
+%The simulation time was extended to demonstrate the convergence of $dy/dF$ toward zero.
 
@@
 If the flow velocity is relatively low, all pressure changes are hydrodynamic (resulting from velocity motion) rather than thermodynamic.
-The Low Mach-number assumption enables instant pressure propagation throughout the system.
-This assumption allows to consider a single pressure value for the entire system, as all changes occur simultaneously within the machine.
+The Low Mach-number assumption leads to instant propagation of the thermodynamic pressure throughout the system.
+This assumption allows considering a single pressure value for the entire system, as all changes occur simultaneously within the machine.
 Figure \ref{fig:Sensitivty_P_P} illustrates a step function representing the pressure change in the system.
@@
 
-	As a result of the Low Mach-number assumption and the pressure deviation, temperature and density change simultaneously along the system.
-According to Equation \ref{EQ:Enthalpy_equation}, the pressure change directly affects the quantity $h \times \rho_f$ through $\partial ({\color{blue}P}(t) A_f) / \partial t$, leading to the step change presented in Figure \ref{fig:Sensitivty_P_H}.
+	According to Equation \ref{EQ:Enthalpy_equation}, the pressure change directly affects the quantity $h \times \rho_f$ through $\partial (P(t) A_f) / \partial t$, leading to the step change along the whole system, as presented in Figure \ref{fig:Sensitivty_P_H}.
 Depending on the configuration of the system, two cases are possible.
-Since the total energy in the extractor has changed, there may be a difference between the fluid inside the equipment and the boundary conditions at the inlet.
 If Dirichlet boundary conditions are applied, the inlet temperature is maintained at the predefined value and may differ from the temperature in the extractor.
@@
 As given in Chapter \ref{CH: Continuity}, the velocity is inversely proportional to the density; hence, the higher density of the fluid leads to a lower velocity and larger residence time.
-The second way is given by the relationships, which connect the pressure and the extraction kinetic term.
-As presented in {\color{red}article 1}, the $D_i^R$ increases with the fluid density, which leads to a higher extraction rate.
+The second way is given by the correlations, which connect the pressure and the extraction kinetic parameters as presented in {\color{red}article 1}, the $D_i^R$ increases with the fluid density, which leads to a higher extraction rate.
 The cumulative effect of the pressure change can be observed in Figure \ref{fig:Sensitivty_P_CS}.
-The sensitivity plot shows a uniform decay of sensitivities along the fixed bed.
+The sensitivity plot shows a close-to-uniform decay of sensitivities along the fixed bed.
 The negative values of sensitivities suggest a faster extraction rate.
-No matter the location of the sensitivity in the bed, the general behaviour stays the same.
+No matter the location of the sensitivity measure in the bed, the general behaviour stays the same.
 Every sensitivity starts with zero and decreases to a minimum value.
@@
 
-	The corresponding response of the pressure change on the solute concentration in the fluid phase is presented in Figure \ref{fig:Sensitivty_P_CF}.
-As discussed earlier, the pressure change directly influences the extraction kinetics.
+	The deviation in the solute concentration in the fluid phase caused by the pressure change is presented in Figure \ref{fig:Sensitivty_P_CF}.
+As discussed earlier, the pressure change directly influences the extraction kinetics parameters.
 Figure \ref{fig:Sensitivty_P_CS} is characterized by negative sensitivities, suggesting a higher extraction rate due to the pressure change.
@@
 As the extraction process accelerates, more solute enters the fluid phase, explaining the "hot spot" in the Figure.
-Subsequently, the solute flows through the system where there are no solid particles, and the diffusion effect becomes noticeable.
-Following the positive sensitivities, a small front of negative sensitivities can be observed.
-Due to the higher extraction rate, more solute has been extracted at the beginning of the extraction process, resulting in less solute available for extraction later.
+Subsequently, the solute flows through the system without solid particles, and the diffusion effect becomes noticeable.
+After the front of positive sensitivities, a small front of negative sensitivities can be observed.
+Due to the higher extraction rate, more solute is extracted at the beginning of the extraction process, resulting in less solute being available for extraction later.
 This effect is reflected in Figure \ref{fig:Sensitivty_P_CF} as negative sensitivities.
@@
 	The impact of pressure increase on extraction yield is depicted in Figure \ref{fig:Sensitivty_P_y}.
-The initial flat curve reflects a system delay, caused by the empty space within the extractor that the solvent with solute must traverse to reach the outlet.
-Next, a positive sensitivity starts to rise, which indicates an increase in yield.
-$dy / dP$ reaches its maximum and then declines due to a lower amount of solute remaining in the solid phase compared to the initial pressure conditions.
-This sensitivity eventually dips into negative values, hits a minimum point, and ultimately converges to zero.
+The initial flat curve reflects a system delay caused by the empty space within the extractor that the fluid phase needs to flow through.
+The first observed deviation is a small negative sensitivity, which can be related to a lower fluid phase velocity.
+Keeping the same mass flow rate and increasing the density (by increasing the pressure) decreases the velocity.
+Next, the sensitivity rises, which indicates an increase in yield.
+$dy / dP$ reaches its positive maximum and then declines due to a limited amount of solute remaining in the solid phase.
+The sensitivity curve draws into negative values, reach a minimum point, and converges to zero.
 The simulation duration was extended to demonstrate the convergence of $dy / dP$ towards zero.
@@
 
-	The impact of the inlet temperature on supercritical extraction differs from the two cases presented earlier because the disturbance does not instantaneously affect the entire system; instead, it propagates through the system.
-As the fluid with the modified temperature flows along the system, it gradually influences the mass transfer parameters.
+	The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through the system.
+As the fluid with the modified temperature flows along the system, it gradually modifies the mass transfer parameters.
 One important assumption is that the inlet temperature does not affect the pressure, and as a result, a horizontal line is present in Figure \ref{fig:Sensitivty_P_T}.
@@
 
-	The propagation of the heat front is presented in Figure \ref{fig:Sensitivty_T_H}.
-Initially, the system was uniformly set to the same temperature.
-The temperatures at the inlet and outlet boundaries are predefined (Dirichlet boundary conditions) and consistent with those inside the system.
-The inlet value of $(h\times \rho_f)$ is calculated based on the provided inlet temperature and given pressure.
-Any deviation in $T_{in}$ affects $(h\times \rho_f)$ at the inlet, which subsequently propagates according to the governing equations.
+	The heat front propagation is presented in Figure \ref{fig:Sensitivty_T_H}.
+The initial system had constant temperature along the whole spatial domain.
+The inlet temperature is a control represented by the Dirichlet boundary condition.
+The inlet $(h\times \rho_f)$ inside the spatial domain is calculated based on the initial inlet temperature and given pressure.
+Any deviation in $T_{in}$ affects $(h\times \rho_f)$ at the inlet, propagating according to the governing equations.
 
@@
 	Figure \ref{fig:Sensitivty_T_CS} illustrates how the change in inlet temperature affects the concentration of solute in the solid phase.
+As presented in {\color{red}article 1}, the value of $D_i^R$ decreases as density decreases.
+Therefore, it is expected to observe positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, indicating a slower extraction rate.
 Initially, the sensitivities are zero along the fixed bed because the heat front requires time to propagate to the fixed bed.
 Since this propagation is not instantaneous, a non-uniform distribution of sensitivities along the fixed bed becomes evident.
-All the sensitivities gradually increase until they reach their respective maxima.
-As presented in {\color{red}article 1}, the value of $D_i^R$ decreases as density decreases.
-Therefore, it is expected to observe positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, indicating a slower extraction rate.
-When the concentration gradient becomes the limiting factor, the sensitivities start to decrease to zero.
+All the sensitivities gradually increase until they reach their maxima.
+When the concentration gradient becomes the limiting factor, the sensitivities start to decrease.
 
@@
 	The influence of inlet temperature on solute concentration in the fluid phase is depicted in Figure \ref{fig:Sensitivty_T_CF}.
-Initially, all the sensitivities remain at zero due to an idle period.
-When the fluid at the new temperature reaches the solid particles, it affects mass transfer, subsequently influencing the amount of solute in the fluid phase.
-In response to the slower extraction rate indicated by positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, a section with negative sensitivities becomes visible in Figure \ref{fig:Sensitivty_T_CF}.
-The effect of diffusion is observable in the section without the fixed bed, where the front composed of sensitivities becomes blurred.
-After reaching their minima, the sensitivities increase and attain positive values.
-This behavior can be explained by considering that the heat front slowed mass transfer, causing more solute to remain in the solid phase.
-This, in turn, leads to a higher concentration gradient in the later stages of extraction compared to the scenario without the inlet temperature deviation.
-The higher concentration gradient results in an increase in $dc_f/dT_{in}$.
+Initially, all the sensitivities remain at zero due to the idle period.
+As the fluid with elevated temperature flows through the fixed bed, the internal mass transfer slows down, resulting in negative sensitivities.
+The diffusion effect is observable in the empty section, where the front composed of sensitivities becomes blurry.
+After reaching their minima, the sensitivities increase and reach slightly positive values.
+This behaviour can be explained by considering that the heat front slowed mass transfer, causing more solute to remain in the solid phase.
 
@@
 Initially, the sensitivity curve remains flat.
-It is because the fixed bed doesn't occupy the entire volume of the extractor and the fluid requires some time to flow through the empty portion of the extractor to reach its outlet.
-It's only when the solute in the fluid phase reaches the extractor's outlet a system response can be observed.
-At this point, $dy/dT_{in}$ begins to decrease, and the negative sensitivity value indicates a decrease in process efficiency.
-Over time, the sensitivity reaches its minimum and then increases due to a higher concentration gradient compared to the case without the disturbance.
-The sensitivity reaches a positive maximum and then declines again due to reduced extraction kinetics and a decreased concentration gradient.
-$dy/dT_{in}$ becomes negative once more, eventually resulting in a flattening of the sensitivity curve.
-The flattening of the yield curve suggest that the mass transfer parameters limits the extraction rate and the residual solute in the solid phase become difficult to obtain.
+This is because the fixed bed doesn't occupy the entire volume of the extractor, and the fluid requires some time to flow through the empty portion of the extractor.
+The first observed response of the system is a small increment of the $dy/dT_{in}$ caused by an increment of the velocity( which is inversely proportional to the fluid density).
+After the small positive peak, the sensitivity curve begins to decrease.
+The negative value of the sensitivity indicates a lower process efficiency.
+Over time, the sensitivity reaches its minimum and then increases due to a higher concentration gradient than in the case without the disturbance.
+Eventually, the $dy/dT_{in}$ curve flattens around a negative value.
+The flattening of the yield curve suggests that the mass transfer parameters limit the extraction rate, and the residual solute in the solid phase becomes difficult to obtain.
+The simulation time was extend to show how the sensitivity plot flatten.
 

### 2024-01-20 SFE_article_Sensitivity_Analysis/Sections/Literature_Review.tex
20.01

@@
 
-	This study aims to analyse the influence of changes in operating conditions on the supercritical extraction process described in {\color{red}article 1}.
-The emphasis is put on the effect of to mass-flow rate, pressure and the inlet temperature.
-The relation between input and output are obtained by applying a sensitivity analysis on the process model.
-Sensitivity analysis is the study of how the uncertainty in the output of a mathematical model or system (numerical or otherwise) can be divided and allocated to different sources of uncertainty in its inputs or model parameters.
-There are many sensitivity analysis methods which include but are not limited to those listed below:
+	This study aims to analyze the influence of changes in operating conditions on the supercritical extraction process described in {\color{red}article 1}.
+The emphasis is put on the effect of the mass flow rate, pressure, and the inlet temperature.
+The relation between input and output is obtained by applying a sensitivity analysis.
+Sensitivity analysis examines the impact of varying inputs or model parameters on the uncertainty of a mathematical model or system's output.
+The aim is to understand and to allocat the source of uncertainty in the output to the corresponding inputs or parameters.
+There are many sensitivity analysis methods, which include but are not limited to those listed below:
 
@@
 One example of such work is \citet{Fiori_2007}.
-The sensitivity calculations were performed by varying the parameters within their confidence interval and observing how the model results change, which allows to establish the effect of the uncertainties on model predictions.
-The sensitivity analysis revealed that two parameters are particularly important for the extraction process: the particle diameter and the internal mass transfer coefficient.
+The sensitivity calculations were performed by varying the parameters within their confidence interval and observing how the model results changed.
+This allows to establish the effect of the uncertainties on model predictions.
+The sensitivity analysis revealed that the particle diameter and the internal mass transfer coefficient are significant for the extraction process.
 The effect of changing some operative conditions was also investigated, underlining how the solvent flow rate and the seed milling affect the extraction process.
 
-	\citet{Santos2000}, in their work considered a model of supercritical extraction process for semi-continuous isothermal and isobaric extraction process using carbon dioxide as a solvent.
+	\citet{Santos2000}, in their work, considered a model of supercritical extraction process for semi-continuous isothermal and isobaric extraction process using carbon dioxide as a solvent.
 The parametric sensitivity analysis was carried out by applying disturbances of 10\% in the values of the normal operation conditions.
@@
 	\citet{Hatami2024} used a one-factor-at-a-time sensitivity analysis to assess the response of NPV concerning variations in both technical and economic variables.
-Their findings shows that the most influential factors on NPV include the price of the extract, the interest rate, the dynamic time of SFE, and the project lifetime.
+Their findings show that the most influential factors on NPV include the price of the extract, the interest rate, the dynamic time of SFE, and the project lifetime.
 
-	\citet{Poletto1996} provided a general dimensionless model was developed for a sensitivity analysis of the supercritical extraction process of vegetable oils and essential oils.
-A dimensionless partition coefficient, and a dimensionless characteristic time, appeared as the most important parameters to monitor the evolution of the extraction process.
-The sensitivity calculations were performed by varying the parameters and analysis the model response.
+	\citet{Poletto1996} provided a general dimensionless model for the supercritical extraction process of vegetable and essential oils and applied a sensitivity analysis.
+They found that a dimensionless partition coefficient and a dimensionless characteristic time appeared as the most important parameters of the extraction process.
+The sensitivity calculations were performed by varying the parameters and analyzing the model response.
 

### 2024-01-20 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
20.01

@@
 The process model was calibrated on the set of experiments obtained at different operating conditions, $40$ - $50^\circ C$ and 200 - 300 bar.
-The sensitivity analysis has been performed under the assumption that the system operates are $45^\circ C$, 250 bar and 0.4 l/min.
+The sensitivity analysis has been performed assuming that the system operates at $45^\circ C$, 250 bar and 0.4 l/min.
 
@@
 
-    It's important to note that $h$ represents enthalpy but not total enthalpy, thus excluding kinetic energy contribution.
-As a consequence of the modelling assumptions, changes in $h$ and $\rho_f$ occur only in response to direct change in pressure or temperature, which is demonstrated by no significant deviation of $h \times \rho_f$ in Figure \ref{fig:Sensitivty_F_H}.
+	It is important to note that $h$ represents enthalpy but not total enthalpy, thus excluding kinetic energy.
+As a consequence of the modelling assumptions, changes in $h$ and $\rho$ occur in response to changes in pressure or temperature, which explains no deviation of $h \times \rho$ in Figure \ref{fig:Sensitivty_F_H}.
 
@@
     	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.pdf}
-    	\caption{The effect of $F$ change on $\rho \times h$}
+    	\caption{The effect of $F$ change on $h \times \rho$}
     	\label{fig:Sensitivty_F_H}
@@
 
-   Figure \ref{fig:Sensitivty_F_CS} shows how the flow rate affects the concentration of the solute in the solid phase.
-At the beginning of the extraction process, the flow rate have a low impact on the extraction process due to the dominance of the concentration gradient in the kinetic regime.
+   Figure \ref{fig:Sensitivty_F_CS} shows how the flow rate affects the solute concentration in the solid phase.
+At the beginning of the extraction process, the flow rate has a low impact on the extraction process due to the dominance of the concentration gradient in the kinetic regime.
 The corresponding sensitivities are close to zero.
-As time progresses, the increase in the mass flow rate have greater influence on the extraction kinetics, causing the sensitivities to decrease towards their minimum values.
+As time progresses, the increment in the mass flow rate has a greater influence on the extraction kinetics, causing the sensitivities to decrease towards their minimum values.
 Negative sensitivities indicate a faster extraction rate.
-Eventually, the amount of solute in the solid phase decreases, and the extraction kinetic becomes limited by the concentration gradient.
+Eventually, the amount of solute in the solid phase decreases, and the concentration gradient limits the extraction kinetic.
 This behaviour is represented by sensitivities, which increase from their minimal values and asymptotically approach to zero.
-The asymptotic movement of sensitivities can be explained by the fact that an increase in the flow rate does not impact the extraction process when all the solute has been removed from the solid phase.
+In extreme cases, when all the solutes have been removed from the solid phase, the concentration gradient is zero, independent of the mass flow rate, which explains the asymptotic behaviour.
 
@@
 This happens because the amount of solute in the fluid phase becomes a limiting factor, and the process is in the diffusion regime.
-%The simulation time was extended to demonstrate the convergence of $dy/dF$ toward zero.
 
@@
 This assumption allows considering a single pressure value for the entire system, as all changes occur simultaneously within the machine.
-Figure \ref{fig:Sensitivty_P_P} illustrates a step function representing the pressure change in the system.
+Figure \ref{fig:Sensitivty_P_P} illustrates a step function representing the pressure change.
 
@@
 
-	According to Equation \ref{EQ:Enthalpy_equation}, the pressure change directly affects the quantity $h \times \rho_f$ through $\partial (P(t) A_f) / \partial t$, leading to the step change along the whole system, as presented in Figure \ref{fig:Sensitivty_P_H}.
+	According to Equation \ref{EQ:Enthalpy_equation}, the pressure change directly affects the quantity $h \times \rho$ through $\partial (P(t) A_f) / \partial t$, leading to the step change along the whole system, as presented in Figure \ref{fig:Sensitivty_P_H}.
 Depending on the configuration of the system, two cases are possible.
@@
     	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P.pdf}
-    	\caption{The effect of $P$ change on $(h \times \rho_f)$ in the system}
+    	\caption{The effect of $P$ change on $(h \times \rho)$ in the system}
     	\label{fig:Sensitivty_P_H}
@@
 	The pressure change affects the mass transfer in two ways.
-As given in Chapter \ref{CH: Continuity}, the velocity is inversely proportional to the density; hence, the higher density of the fluid leads to a lower velocity and larger residence time.
-The second way is given by the correlations, which connect the pressure and the extraction kinetic parameters as presented in {\color{red}article 1}, the $D_i^R$ increases with the fluid density, which leads to a higher extraction rate.
-The cumulative effect of the pressure change can be observed in Figure \ref{fig:Sensitivty_P_CS}.
+As discussed in Chapter \ref{CH: Continuity}, the velocity is inversely proportional to the density; hence, the higher density of the fluid leads to a lower velocity and larger residence time.
+The changes in the thermodynamic state of the fluid affect the extraction kinetic parameters, which are defined by correlations presented in {\color{red}article 1}.
+For example, the $D_i^R$ increases with the fluid density, which leads to a higher extraction rate.
+The cumulative effect of the pressure change on the solute concentration in the solid phase can be observed in Figure \ref{fig:Sensitivty_P_CS}.
 The sensitivity plot shows a close-to-uniform decay of sensitivities along the fixed bed.
@@
 	The deviation in the solute concentration in the fluid phase caused by the pressure change is presented in Figure \ref{fig:Sensitivty_P_CF}.
-As discussed earlier, the pressure change directly influences the extraction kinetics parameters.
-Figure \ref{fig:Sensitivty_P_CS} is characterized by negative sensitivities, suggesting a higher extraction rate due to the pressure change.
+As discussed earlier, the sensitivities related to the solute concentration in the solid phase are characterized by negative sensitivities, suggesting a higher extraction rate due to the pressure change.
 Consequently, an increase in solute concentration in the fluid phase is expected.
-This increase in solute concentration in the fluid phase is visible in Figure \ref{fig:Sensitivty_P_CF} as positive sensitivities, forming a front that moves along the extractor.
-As the extraction process accelerates, more solute enters the fluid phase, explaining the "hot spot" in the Figure.
-Subsequently, the solute flows through the system without solid particles, and the diffusion effect becomes noticeable.
-After the front of positive sensitivities, a small front of negative sensitivities can be observed.
-Due to the higher extraction rate, more solute is extracted at the beginning of the extraction process, resulting in less solute being available for extraction later.
-This effect is reflected in Figure \ref{fig:Sensitivty_P_CF} as negative sensitivities.
-Eventually, the negative sensitivities approach zero.
+This increase in solute concentration in the fluid phase is visible in Figure \ref{fig:Sensitivty_P_CF} as positive sensitivities, which form a front that moves along the extractor.
+Due to the diffusion effect, the front changes its pattern in the empty section and becomes more spread.
+Accelerating the extraction rate since the beginning of the extraction process leads to a faster decrease in the concentration gradient.
+This effect is reflected in Figure \ref{fig:Sensitivty_P_CF} as the front of the negative sensitivities, which follows the positive front.
+Eventually, the negative sensitivities approach zero when the concentration gradient goes to zero.
 
@@
 As the fluid with the modified temperature flows along the system, it gradually modifies the mass transfer parameters.
-One important assumption is that the inlet temperature does not affect the pressure, and as a result, a horizontal line is present in Figure \ref{fig:Sensitivty_P_T}.
+One important assumption is that the inlet temperature change does not affect the pressure, which explains a horizontal line in Figure \ref{fig:Sensitivty_P_T}.
 
@@
 The initial system had constant temperature along the whole spatial domain.
-The inlet temperature is a control represented by the Dirichlet boundary condition.
-The inlet $(h\times \rho_f)$ inside the spatial domain is calculated based on the initial inlet temperature and given pressure.
-Any deviation in $T_{in}$ affects $(h\times \rho_f)$ at the inlet, propagating according to the governing equations.
+The inlet temperature is a control characterized by the Dirichlet boundary condition.
+The boundary value of $(h\times \rho)$ is calculated based on two controls which can be manipulated: inlet temperature and given pressure.
+Any deviation in $T_{in}$ affects $(h\times \rho)$ at the inlet, propagating according to the governing equations.
 
@@
 		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_T_{in}.pdf}
-		\caption{The effect of $T_{in}$ change on $(h \times \rho_f)$ in the system}
+		\caption{The effect of $T_{in}$ change on $(h \times \rho)$ in the system}
 		\label{fig:Sensitivty_T_H}
@@
 Therefore, it is expected to observe positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, indicating a slower extraction rate.
-Initially, the sensitivities are zero along the fixed bed because the heat front requires time to propagate to the fixed bed.
+Initially, the sensitivities are zero along the fixed bed because the heat front requires time to reach the fixed bed.
 Since this propagation is not instantaneous, a non-uniform distribution of sensitivities along the fixed bed becomes evident.
-All the sensitivities gradually increase until they reach their maxima.
-When the concentration gradient becomes the limiting factor, the sensitivities start to decrease.
+All the sensitivities gradually increase until they reach their maximum.
+When the concentration gradient becomes the limiting factor, the sensitivities decrease.
 
@@
 Initially, all the sensitivities remain at zero due to the idle period.
-As the fluid with elevated temperature flows through the fixed bed, the internal mass transfer slows down, resulting in negative sensitivities.
+As the fluid with elevated temperature flows through the fixed bed, the internal mass transfer slows down (the $D_i^R$ is proportional to density as presented in {\color{red}article 1}), resulting in negative sensitivities.
 The diffusion effect is observable in the empty section, where the front composed of sensitivities becomes blurry.
@@
 	Figure \ref{fig:Sensitivty_T_y} depicts how an increase in inlet temperature alters the extraction yield.
-Initially, the sensitivity curve remains flat.
-This is because the fixed bed doesn't occupy the entire volume of the extractor, and the fluid requires some time to flow through the empty portion of the extractor.
+Initially, the sensitivity curve remains flat due to the idle time.
 The first observed response of the system is a small increment of the $dy/dT_{in}$ caused by an increment of the velocity( which is inversely proportional to the fluid density).
@@
 The flattening of the yield curve suggests that the mass transfer parameters limit the extraction rate, and the residual solute in the solid phase becomes difficult to obtain.
-The simulation time was extend to show how the sensitivity plot flatten.
+The simulation time was extended to show how the sensitivity plot flattened.
 

### 2024-01-20 SFE_article_Sensitivity_Analysis/Sections/Sensitivity_Analysis.tex
20.01

@@
 	Local derivative-based methods involve taking the partial derivative of the output with respect to an input parameter.
-This set of derivatives is known as sensitivity equations, and it is solved simultaneously with the process model.
-The purpose of the sensitivity analysis is to investigate how responsive the solution is for the perturbation of the parameter ${p}$.
+This set of derivatives, known as sensitivity equations, is solved simultaneously with the process model.
+The sensitivity analysis aims to investigate how responsive the solution is for the perturbation of the parameter ${p}$.
 As discussed by \citet{Dickinson1976}, the sensitivity analysis can be used to determine the influence of the uncertainty on the solution of the original system.
 A sensitivity analysis can be used to distinguish sensitive parameters from insensitive ones, which might be helpful for model reduction.
-Finally, from a control engineering point of view, the sensitivity analysis allows to sort the control variables with respect to the level of effort required to change the model's output.
+Finally, from a control engineering point of view, the sensitivity analysis allows sorting the control variables with respect to the level of effort required to change the model's output.
 
@@
 
-	By applying the definition of the total derivative to the Equation \ref{SA_dt}, the sensitivity equation can be obtained.
+	The sensitivity equation can be obtained by applying the definition of the total derivative to the Equation \ref{SA_dt}.
 
@@
 
-	The sensitivity Equation \ref{SA_eq_full} is solved simultaneously with the original syste and is made of three terms: jacobian ${J_x}({x}(t);{p})$, sensitivity matrix ${S}({x}(t);{p})$ and jacobian ${J_p}({x}(t);{p})$.
+	The sensitivity Equation \ref{SA_eq_full} is solved simultaneously with the original system and is made of three terms: jacobian ${J_x}({x}(t);{p})$, sensitivity matrix ${S}({x}(t);{p})$ and jacobian ${J_p}({x}(t);{p})$.
 The jacobian ${J_x}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${J_x}(n_x,n_x)$ is the derivative of process model equations ${G}_{n_x}({x}(t);{p})$ with respect to the state variable $x_{n_p}$.
@@
 
-	In a similar way, the sensitivity analysis of the output function can be performed with respect to parameters ${p}$.
+	The sensitivity analysis of the output function can be performed with respect to parameters ${p}$.
 The output function ${g}({x}(t))$ returns ${y}(t)$.

### 2024-01-21 SFE_article_Design_of_Experiment/Article_Design_of_Experiment.tex
21.01

--- 2024-01-19 SFE_article_Sensitivity_Analysis/Article_Model_Parameters.tex
@@
 % ===================================================
-\title[mode=title]{Sensitivity Analysis}                      
-\shorttitle{Sensitivity Analysis}
+\title[mode=title]{Optimal design of experiment}                      
+\shorttitle{Optimal design of experiment}
 
@@
 The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
-The local sensitivity analysis investigates the influence of infinitely small changes in the inlet temperature, pressure, and flow rate on the extraction yield.
+The optimal design of experiment problem is solved to find an experimental strategy for validating the correlations between extraction kinetic parameters and the operating conditions.
+This work proposes two experimental strategies: one that only manipulates the inlet temperature and the second that manipulate only the pressure.
 
@@
 \begin{keywords}
-Supercritical extraction \sep Sensitivity analysis \sep Mathematical modelling
+Supercritical extraction \sep Optimal design of experiment \sep Mathematical modelling \sep Optimization \sep Fisher information
 \end{keywords}
@@
 
-\subsection{Sensitivity Analysis} \label{CH: Sensitivity_Analysis}
-\subfile{Sections/Sensitivity_Analysis}
+\subsection{Design of experiment} \label{CH: Optimal_design_of_experiment}
+\subfile{Sections/Optimal_design_of_experiment}
 
@@
 \section{Results}
-\subfile{Sections/Results_Sensitivity}
+%\subfile{Sections/Results_Sensitivity}
 
 \section{Conclusions} \label{CH: Conclusion}
-
-The sensitivity analysis is a tool to understand the parametric dependence of dynamic behavior and its suitability in inferring mechanisms of the dynamic behavior of the analyzed system.
-The mathematical formulation involves derivative-based local sensitivity analysis of the solution of an inverse problem with respect to perturbations of parameters.
-The local method is based only on considering all parameters as constants (those independent of time or location), and then the sensitivity equations are estimated by solving a variational system simultaneously with the original system.
-The sensitivity equations can be obtained in various ways, but the automatic differentiation technique was implemented to obtain the sensitivity equations in this work.
-By identifying which parameters are influential at each period of the simulation, local sensitivity analysis can yield valuable information for guiding the process modelling, the design of experiments or the model reduction.
-The local sensitivity analysis techniques consider the sensitivities at only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions unless the discussed system is a linear system.
-
-In this study, the local sensitivity analysis method was introduced to explore the dynamics of the supercritical extraction system, which consists of a set of partial differential equations.
-The sensitivity equations evaluate the influence of control variables such as flow rate, pressure, and inlet temperature on the state-space consisting of the concentration of the solute in solid and liquid phases, the fluid's enthalpy density, system pressure, and extraction yield.
-Every change in the control variables leads to a state-space change, eventually affecting the process performance.
-This information can be utilized to identify which control variables influence the extraction yield the most.
-The controls with high sensitivities on the extraction can be used to investigate to find optimal operating conditions from an economic point of view.
 

### 2024-01-21 SFE_article_Design_of_Experiment/Sections/IC_BC.tex
21.01

--- 2023-10-02 SFE_article_Parameter_Estimation/Sections/IC_BC.tex
@@
-\documentclass[../Article_Model_Parameters.tex]{subfiles}
+\documentclass[../Article_Design_of_Experiment.tex]{subfiles}
 \graphicspath{{\subfix{../Figures/}}}
@@
 
-	During the preparation period, when the operating conditions are achieved, the solute diffuses to the fluid phase in contact with the solid particles.
+	During the preparation period, the solute diffuses to the fluid phase in contact with the solid particles although the operating conditions are not obtained yet.
 Later, the solute in the fluid phase is partially moved (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed) to the region where there is no solid phase.

### 2024-01-21 SFE_article_Design_of_Experiment/Sections/Literature_Review.tex
21.01

--- 2024-01-20 SFE_article_Sensitivity_Analysis/Sections/Literature_Review.tex
@@
 The relation between input and output is obtained by applying a sensitivity analysis.
-Sensitivity analysis examines the impact of varying inputs or model parameters on the uncertainty of a mathematical model or system's output.
-The aim is to understand and to allocat the source of uncertainty in the output to the corresponding inputs or parameters.
+Sensitivity analysis examines the impact of varying inputs or model parameters on the system's output.
+The aim is to understand and to allocate the source of uncertainty in the output to the corresponding inputs or parameters.
 There are many sensitivity analysis methods, which include but are not limited to those listed below:
@@
 	Different supercritical extraction models were analyzed using sensitivity analysis.
-One example of such work is \citet{Fiori_2007}.
-The sensitivity calculations were performed by varying the parameters within their confidence interval and observing how the model results changed.
-This allows to establish the effect of the uncertainties on model predictions.
+\citet{Fiori_2007}, performed the sensitivity calculations by varying the parameters within their confidence interval and observing how the model results changed.
+This allows to evaluate the effect of the uncertainties on model predictions.
 The sensitivity analysis revealed that the particle diameter and the internal mass transfer coefficient are significant for the extraction process.

### 2024-01-21 SFE_article_Design_of_Experiment/Sections/Low_mach_number_expansion.tex
21.01

--- 2023-03-09 SFE-article/Sections/Low_mach_number_expansion.tex
@@
 Such a set of equations allow for large variations in gas density but it is consider to be acoustically incompressible.
-The low Mach number equations are preferred over the full compressible equations for low speed flow problems $\left( M_a = \frac{|V|}{\sqrt{ \partial P / \partial \rho }} \ll 1 \right)$ to avoids the need to resolve fast-moving acoustic signals.
+The low Mach number equations are preferred over the full compressible equations for low speed flow problems $\left( M_a = \frac{|v|}{\sqrt{ \partial P / \partial \rho_f }} \ll 1 \right)$ to avoids the need to resolve fast-moving acoustic signals.
 The equations are derived from the compressible equations based on the perturbation theory.
@@
 		\begin{equation*}
-			 \rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) + e  \underbrace{ \left( \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f v A_f \right)}{\partial z} \right) }_{Continutiy}  - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
+			 \rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) + e  \underbrace{ \left( \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f v A_f \right)}{\partial z} \right) }_{Continutiy}  - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v\right)}{\partial z} = 0
 		\end{equation*}
@@
 		\begin{equation*}
-		\rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f v}{\partial z} = 0
+		\rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v\right)}{\partial z} = 0
 		\end{equation*}
@@
 
+	\todo[]{Add REF}
+
 	Assuming constant temperature and pressure along space and in time:

### 2024-01-21 SFE_article_Design_of_Experiment/Sections/Low_mach_number_expansion_imp.tex
21.01

--- 2023-04-19 SFE-article/Sections/Low_mach_number_expansion_imp.tex
@@
 
-	The equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_2} describe the fully compressible equations of motion (respectively, the transport of mass, momentum and energy) for the quasi-one-dimensional case.
+	The Equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_2} describe the fully compressible equations of motion (respectively, the transport of mass, momentum and energy) for the quasi-one-dimensional case.
 We rescale the time variable, considering finally
@@
 
-	In one-dimensional case, the equation \ref{EQ: Incompressibility_Condition_Ideal_IsoThermal} become equivalent of $\text{div} ( A_f v) = 0$, which known as the incompressibility condition (\citet{Lions2013}).
+	In one-dimensional case, the Equation \ref{EQ: Incompressibility_Condition_Ideal_IsoThermal} become equivalent of $\text{div} ( A_f v) = 0$, which known as the incompressibility condition (\citet{Lions2013}).
 
@@
 	It can be deduced that the continuity equation becomes $\frac{\partial \rho_f}{\partial t} = 0$ at constant temperature and pressure.
-Moreover, the incompressibility condition $div(A_fV)=0$ is obtained.
+Moreover, the incompressibility condition $div(A_fv)=0$ is obtained.
 

### 2024-01-21 SFE_article_Design_of_Experiment/Sections/Optimal_design_of_experiment.tex
21.01

--- 2023-12-03 SFE_Design_of_Experiment/Notes/template_Scrartcl.tex
@@
-\documentclass[]{scrartcl}
-
-\usepackage{amsmath,amssymb}
-\usepackage{graphicx}
-\usepackage{tikz}
-
-%opening
-\title{Optimal design of experiment}
-\author{Oliwer Sliczniuk}
-
+\documentclass[../Article_Design_of_Experiment.tex]{subfiles}
+\graphicspath{{\subfix{../Figures/}}}
 \begin{document}
 
-\maketitle
+	The design of experiments (DOE) also known as experiment design or experimental design, is the design of any task that aims to describe and explain the variation of information under conditions that are hypothesized to reflect the variation.
+The term is generally associated with experiments in which the design introduces conditions that directly affect the variation, but may also refer to the design of quasi-experiments, in which natural conditions that influence the variation are selected for observation.
 
-\begin{abstract}
-Notes about the optimal design of an experiment
-\end{abstract}
-
-\section{What information do we have?}
-
-\begin{itemize}
-	\item Process model: $\dot{x}=f(t,x,p)$
-	\item Measurement equation: $\dot{y}=g(x)$
-	\item Likelihood function with respect to the dataset
-	\item Parameter estimation
-	\item Sensitivity equations: $\dot{S} = J_x \dot{x} + J_p$
-\end{itemize}
-
-\section{Maximum likelihood}
-Let $y^s$ be the vector of all experimental results (random vector) to be used to estimate $p$ and $y^m(p)$.
-The vector of the corresponding quantities computed by the model $\dot{x}=f(t,x,p)$.
+	\subsubsection{Maximum likelihood}
+	%Let $Y$ be the vector of all experimental results (random vector) to be used to estimate parameters $p$ (where $p$ is the subset of parameter space $\Theta$) and model output $y(p)$.
+The vector of the corresponding quantities computed by the model $\dot{x}(t)=G(x(t);p)$.
 For a parallel model, the parameters of which are to be estimated from measurements of an output vector $\dot{y}=g(x)$.
@@
 
+	{\footnotesize
 	\begin{equation}
-	j_{ml} = \pi_y (y^s|p) 
-\end{equation}
+		j_{ml}(p) = \pi_y (Y|p) 
+	\end{equation} }
 
-If $p$ were fixed, $\pi_y(y^s|p)$ would be the probability density of the random vector $y^s$ generated by a model with parameters $p$.
-Here, to the contrary, $y^s$ is fixed and corresponds to the observations.
-Considered as a function of $p$, $\pi_y(y^s|p)$ is then called the likelihood of $y^s$.
+	If $p$ were fixed, $\pi_y(Y|p)$ would be the probability density of the random vector $Y$ generated by a model with parameters $p$.
+Here, to the contrary, $Y$ is fixed and corresponds to the observations.
+Considered as a function of $p$, $\pi_y(Y|p)$ is then called the likelihood of $Y$.
 The maximum-likelihood method looks for the parameter vector $p$ value that gives the observed data the highest likelihood.
@@
 
+	{\footnotesize
 	\begin{equation}
-	j_{ml} = \ln ( \pi_y (y^s|p) )
-\end{equation}
+		j_{ml}(p) = \ln ( \pi_y (Y|p) )
+	\end{equation} }
 
@@
 
+	{\footnotesize
 	\begin{equation}
-	y(t_i) = y^m(t_i, p^*) + \epsilon_i, \qquad i=1,...,n_t
-\end{equation}
+		Y(t_i) = y(t_i, p^*) + \epsilon_i, \qquad i=1,...,n_t
+	\end{equation} }
 
-where the vector $y^m(t_i.
-p^*)$ is the output of a deterministic model, $p^*$ is the true value of the parameter vector, and $\epsilon_i$ belongs to a sequence of independent random variables with probability density $\pi_{\epsilon}(\epsilon_i)$.
+	where the vector $y(t_i, p^*)$ is the output of a deterministic model, $p^*$ is the true value of the parameter vector, and $\epsilon_i$ belongs to a sequence of independent random variables with probability density $\pi_{\epsilon}(\epsilon_i)$.
 Since the $\epsilon_i$ are independent
 
+	{\footnotesize
 	\begin{equation}
 		\pi_{\epsilon}(\epsilon_1, \epsilon_2, ..., \epsilon_{n_t}) = \prod_{i=1}^{n_t} \pi_{\epsilon_i}(\epsilon_i)
-\end{equation}
+	\end{equation} }
 
@@
 
+	{\footnotesize
 	\begin{equation}
-	e^y(t_i, p) = y(t_i) - y^m(t_i, p)
-\end{equation}
+		e^y(t_i, p) = Y(t_i) - y(t_i, p)
+	\end{equation} }
 
 	For the true value of the parameters, it satisfies $e^y(t_i, p^*)=\epsilon_i$.
-and, since $y^m$ is deterministic, $\pi_{y_i} (y^s(t_i)|p) = \pi_{\epsilon_i} (e^y(t_i)|p)$.
+and, since $y$ is deterministic, $\pi_{y_i} (Y(t_i)|p) = \pi_{\epsilon_i} (e^Y(t_i)|p)$.
 The likelihood of the $n_t$ observations can be written as
 
+	{\footnotesize
 	\begin{equation}
-	\pi_y (y^s|p) = \prod_{i=1}^{n_t} \pi_{\epsilon_i}(e^y(t_i,p)) =  \prod_{i=1}^{n_t} \pi_{\epsilon_i}(y(t_i) - y^m(t_i, p))
-\end{equation}
+		\pi_y (Y|p) = \prod_{i=1}^{n_t} \pi_{\epsilon_i}(e^y(t_i,p)) =  \prod_{i=1}^{n_t} \pi_{\epsilon_i}(Y(t_i) - y(t_i, p))
+	\end{equation} }
 
-If the noise is assumed to follow the normal distribution:
+	If the noise is assumed to follow the normal distribution with the standard deviation $\sigma$, which is known from the parameter estimation:
 
+	{\footnotesize
 	\begin{equation}
-	\pi_y (y^s|p) = \prod_{i=1}^{n_t} \frac{1}{ \sqrt{2\pi\sigma_{t_i}^2} } \exp \left( -\frac{1}{2} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}} \right) \right)
-\end{equation}
+		\pi_y (Y|p) = \prod_{i=1}^{n_t} \frac{1}{ \sqrt{2\pi\sigma_{t_i}^2} } \exp \left( -\frac{1}{2} \left( \frac{Y(t_i) - y(t_i, p)}{\sigma_{t_i}} \right)^2 \right)
+	\end{equation} }
 
@@
 
+	{\footnotesize
 	\begin{equation}
-	\ln (\pi_y (y^s|p)) = (\text{term independent of p}) - \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \right)
-\end{equation}
+		\ln (\pi_y (Y|p)) = (\text{term independent of p}) - \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{Y(t_i) - y(t_i, p)}{\sigma_{t_i}} \right)^2
+	\end{equation} }
 
@@
 
+	{\footnotesize
 	\begin{equation}
-	\frac{\partial}{\partial p} \ln (\pi_y (y^s|p)) =  \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p} \right)
-\end{equation}
+		\frac{\partial}{\partial p} \ln (\pi_y (Y|p)) =  \sum_{i=1}^{n_t}  \left[ \left( \frac{Y(t_i) - y(t_i, p)}{\sigma_{t_i}^2} \right) \frac{\partial y(t_i, p)}{\partial p} \right]
+	\end{equation} }
 
-\section{Fisher information}
+	\subsubsection{Fisher information}
 
@@
 
-\begin{align}
-	F(p) &= - \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial^2 \ln (\pi_y (y^s|p))}{\partial p \partial p^T} \right] = \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial \ln (\pi_y (y^s|p))}{\partial p} \frac{\partial \ln (\pi_y (y^s|p))}{\partial p^T} \right] \\
-	&= \mathop{\mathbb{E}}_{y^s|p} \left[ \sum_{k=1}^{n_t} \left( \frac{y(t_k) - y^m(t_k, p)}{\sigma_{t_k}^2} \frac{\partial y^m(t_k, p)}{\partial p} \right) \times  \sum_{i=1}^{n_t} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p^T} \right) \right]
-\end{align}
+	{\scriptsize
+	\begin{equation}
+		\begin{aligned}
+		&\text{FIM(p)} = - \mathop{\mathbb{E}}_{Y|p} \left[ \frac{\partial^2 \ln (\pi_y (Y|p))}{\partial p \partial p^\top} \right] = \mathop{\mathbb{E}}_{Y|p} \left[ \frac{\partial \ln (\pi_y (Y|p))}{\partial p} \frac{\partial \ln (\pi_y (Y|p))}{\partial p^\top} \right] \nonumber \\
+		&= \mathop{\mathbb{E}}_{Y|p} \left[ \sum_{k=1}^{n_t} \left( \frac{Y(t_k) - y(t_k, p)}{\sigma_{t_k}^2} \frac{\partial y(t_k, p)}{\partial p} \right) \times  \sum_{i=1}^{n_t} \left( \frac{Y(t_i) - y(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y(t_i, p)}{\partial p^\top} \right) \right] \nonumber \\
+		&= \mathop{\mathbb{E}}_{Y|p} \left[ \sum_{k=1}^{n_t} \sum_{i=1}^{n_t} \left[ \left( \frac{Y(t_k) - y(t_k, p)}{\sigma_{t_k}^2} \frac{\partial y(t_k, p)}{\partial p} \right) \times \left( \frac{Y(t_i) - y(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y(t_i, p)}{\partial p^\top} \right) \right] \right] \nonumber \\
+		&= \sum_{k=1}^{n_t} \sum_{i=1}^{n_t} \mathop{\mathbb{E}}_{Y|p} \left[ \left( \frac{Y(t_k) - y(t_k, p)}{\sigma_{t_k}^2} \frac{\partial y(t_k, p)}{\partial p} \right) \times \left( \frac{Y(t_i) - y(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y(t_i, p)}{\partial p^\top} \right) \right] \nonumber \\
+		&= \sum_{k=1}^{n_t} \sum_{i=1}^{n_t} \frac{1}{\sigma_{t_k}^2} \frac{\partial y(t_k, p)}{\partial p} \frac{1}{\sigma_{t_i}^2} \frac{\partial y(t_i, p)}{\partial p^\top} \mathop{\mathbb{E}}_{Y|p} \left[ \left( Y(t_k) - y(t_k, p) \right) \times \left( Y(t_i) - y(t_i, p) \right) \right]
+	\end{aligned} 
+	\end{equation} }
 
-Since
+	Considering the mismatch between the dataset and the model output, the expectation $\mathop{\mathbb{E}}_{Y|p}$ can be redefined as $\mathop{\mathbb{E}}_{Y|p} \left[ \left( Y(t_i) - y(t_i, p) \right) \left( Y(t_k) - y(t_k, p) \right) \right] = \mathop{\mathbb{E}}_{Y|p} \left[ \epsilon_i \epsilon_k \right]$.
+For $i=k$, the expectation of $\epsilon_i$ is the variance of the noise $\sigma_{t_i}^2$.
+Analogously, the expectation becomes 0 if $i \neq k$ because the measurement noises are independent at different times.
 
+	{\footnotesize
 	\begin{equation}
-	\mathop{\mathbb{E}}_{y^s|p} \left[ \left( y(t_i) - y^m(t_k, p) \right) \left( y(t_i) - y^m(t_i, p) \right) \right] = \sigma_{t_i}^2 \delta_{ik}
-\end{equation}
+		\mathop{\mathbb{E}}_{Y|p} \left[ \left( Y(t_i) - y(t_k, p) \right) \left( Y(t_i) - y(t_i, p) \right) \right] = \sigma_{t_i}^2 \delta_{ik}
+	\end{equation} }
 
-one gets
+	where $\delta_{ik}$ represents the Kronecker delta. Given the property of the Kronecker delta, the double summation in the Fisher Information matrix reduces to a single summation:
 
+	{\footnotesize
 	\begin{equation}
-	F(p) = \sum_{i=1}^{n_t} \left( \frac{1}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p} \frac{\partial y^m(t_i, p)}{\partial p^T} \right)
-\end{equation}
+		\text{FIM(p)} = \sum_{i=1}^{n_t} \left( \frac{1}{\sigma_{t_i}^2} \frac{\partial y(t_i, p)}{\partial p} \frac{\partial y(t_i, p)}{\partial p^\top} \right)
+	\end{equation} }
 
@@
 
+	{\footnotesize
 	\begin{equation}
-	F(p) = \frac{\partial y^m(t, p)}{\partial p} \text{diag}\left(\frac{1}{\sigma_{t}^2}\right) \frac{\partial y^m(t, p)}{\partial p^T} 
-\end{equation}
+		\text{\text{FIM(p)}} = \frac{\partial y(t, p)}{\partial p} \begin{bmatrix}
+			\frac{1}{\sigma_{t_1}^2} & 0 & 0\\
+			0 & \ddots & 0 \\
+			0 & 0 & \frac{1}{\sigma_{t_{n_t}}^2} 
+		\end{bmatrix}\ \frac{\partial y(t, p)}{\partial p^\top} 
+	\end{equation} }
 
-\section{Cramer-Rao inequality}
+	\subsubsection{Cramer-Rao inequality}
 
-Let $\hat{p}$ be an (absolutely) unbiased estimator $p^*$, i.e. such that which amounts to saying that if it were possible to replicate the same experiment and
-estimate $\hat{p}$ an infinite number of times, the mean of the estimates would coincide with the true value.
+	Let $\hat{p}$ be an (absolutely) unbiased estimator $p^*$, i.e.
+such that it were possible to replicate the same experiment and estimate $\hat{p}$ an infinite number of times, the mean of the estimates would coincide with the true value.
 Let $P$ be the covariance matrix of this estimator.
@@
 
+	{\footnotesize
 	\begin{equation}
-	P = \mathop{\mathbb{E}}_{y^s|p^*} \left[ \left( \hat{p}(y^s) - p^* \right) \left( \hat{p}(y^s) - p^* \right)^T \right]
-\end{equation}
+		\Sigma = \mathop{\mathbb{E}}_{Y|p^*} \left[ \left( \hat{p}(Y) - p^* \right) \left( \hat{p}(Y) - p^* \right)^\top \right]
+	\end{equation} }
 
 	which quantifies how the estimates are spread around the true value $p^*$.
-One would like the estimates to be as concentrated as possible around this true value, of course.
-An estimator $\hat{p}_1$ with covariance matrix $P_1$ is said to be more efficient than an estimator $\hat{p}_2$ with covariance matrix $P_2$ if $P_1 < P_2$, that is if $P_2 - P_1$ is positive-definite (i.e.if all the eigenvalues of $P_2-P_1$ arc strictly positive).
+One would like the estimates to be as concentrated as possible around this true value.
+An estimator $\hat{p}_1$ with covariance matrix $\Sigma_1$ is said to be more efficient than an estimator $\hat{p}_2$ with covariance matrix $\Sigma_2$ if $\Sigma_1 < \Sigma_2$, that is if $\Sigma_2 - \Sigma_1$ is positive-definite (i.e.if all the eigenvalues of $\Sigma_2-\Sigma_1$ arc strictly positive).
 Since estimators with high efficiency are desirable, a natural request is to make P as small as possible.
@@
 	\begin{itemize}
-	\item the set of all data vectors $y^s$ with $\pi_y(y^s|p) > 0$ does not depend on $p$
-	\item $\frac{\partial \pi_y(y^s|p)}{\partial p_i}~\left(i=1,2,...,n_p\right)$ is absolutely integrable
-	\item $\mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial \ln (\pi_y (y^s|p))}{\partial p} \frac{\partial \ln (\pi_y (y^s|p))}{\partial p^T} \right]$ exists and is invertible
+		\item the set of all data vectors $Y$ with $\pi_y(Y|p) > 0$ does not depend on $p$
+		\item $\frac{\partial \pi_y(Y|p)}{\partial p_i}~\left(i=1,2,...,n_p\right)$ is absolutely integrable
+		\item $\mathop{\mathbb{E}}_{Y|p} \left[ \frac{\partial \ln (\pi_y (Y|p))}{\partial p} \frac{\partial \ln (\pi_y (Y|p))}{\partial p^\top} \right]$ exists and is invertible
 	\end{itemize}
@@
 
+	{\footnotesize
 	\begin{equation}
-	P \geq F^{-1}(p^*)
-\end{equation}
+		\Sigma \geq \text{FIM(p)}^{-1}(p^*)
+	\end{equation} }
 
@@
 
-\section{Optimal experimental design}
+	\subsubsection{Optimal experimental design}
 
@@
 
+	{\footnotesize
 	\begin{equation}
 		\Xi^* = \arg~\underset{\Xi \in \bar{\Xi}}{\text{opt}}~j\left(\Xi\right)
-\end{equation}
+	\end{equation} }
 
@@
 
+	{\footnotesize
 	\begin{equation}
-	j(\Xi) = \phi\left[ F(p, \Xi) \right]
-\end{equation}
+		j(\Xi) = \phi\left[ \text{FIM(p)}(p, \Xi) \right]
+	\end{equation} }
 
@@
 
+	{\footnotesize
 	\begin{align}
-	\phi_k(F) &= \left[\frac{1}{n_p} \text{trace}\left( QF^{-1}Q^T \right)^k \right]^{1/k} \quad &if \det F \neq 0 \nonumber \\
-	\phi_k(F) &= \infty \quad &if \det F = 0
-\end{align}
+		\phi_k(\text{FIM(p)}) &= \left[\frac{1}{n_p} \text{trace}\left( Q\text{FIM(p)}^{-1}Q^\top \right)^k \right]^{1/k} \quad &\text{if} \det F \neq 0 \nonumber \\
+		\phi_k(\text{FIM(p)}) &= \infty \quad &\text{if} \det F = 0
+	\end{align} }
 
@@
 
+	{\footnotesize
 	\begin{equation}
-	j_L(\Xi) = \text{trace} \left[ Q^TQF^{-1}(p,\Xi) \right]
-\end{equation}
+		j_L(\Xi) = \text{trace} \left[ Q^\top Q\text{FIM}^{-1}(p,\Xi) \right]
+	\end{equation} }
 
@@
 Taking $Q = \textbf{I}_{n_p}$ and $k = \infty$ corresponds to E-optimality; E-optimal design maximizes the smallest eigenvalues of the Fisher information matrix and thus minimizes the length of the largest axis of the asymptotic confidence ellipsoids.
-The most widely used optimality criterion has $k = 0$, $Q = \textbf{I}_{n_p}$ , requiring minimization of $\det F^{-1}(p, \Xi)$, or, equivalently, maximization of
+The most widely used optimality criterion has $k = 0$, $Q = \textbf{I}_{n_p}$ , requiring minimization of $\det \text{FIM}^{-1}(p, \Xi)$, or, equivalently, maximization of
 
+	{\footnotesize
 	\begin{equation}
-	j_D(\Xi) = \det F(p, \Xi)
-\end{equation}
+		j_D(\Xi) = \det \text{FIM}(p, \Xi)
+	\end{equation} }
 
@@
 
+	\subsubsection{Problem formulation}
+
+	The optimal design of the experiment technique is used to extend the experiment discussed in $({\color{red}article~1})$, where supercritical extraction from caraway seeds has been discussed.
+The presented extraction was performed under multiple operating conditions, such that the temperature, pressure, and flow rate were constant during each batch.
+Later, the experiments' results are combined, and correlations for extraction kinetic parameters are presented.
+In this work, the optimal design of the experiment is used to design an experiment to validate these correlations.
+The model parameters, the extraction time (150 minutes), and the sampling time (5 minutes) are the same as in $({\color{red}article~1})$ to mimic the original system.
+It is assumed that the flow rate is constant because the effect of the flow rate has not been deeply investigated in the previous work of the authors (${\color{red}articl~1}$).
+The pressure is assumed to be constant during the whole experiment.
+The initial temperature ($T^0$) of the extractor and the inlet temperature ($T^{in}$) are decision variables in the optimization.
+It is considered that the initial state is isothermal, so $T^0=T^{in}(t=0)$.
+The inlet temperature is changed every 5 minutes, and considered to be constant inside of this time period.
+Considering that the residence time in the extractor is around 20-25 minutes (depending on the operating conditions), it is assumed that there is no change in the inlet temperature in the last 25 minutes of extraction, so the extractor becomes isothermal at the end of the experiment.
+The lower ($40^\circ C$) and upper ($50^\circ C$) bounds for the temperature are limits of the previous experiments (${\color{red}article~1}$).
+The general formulation of the optimal design of experiment problem is presented below.
+
+	{\footnotesize
+	\begin{equation}
+		\begin{aligned} 
+			&\Xi^* &= \arg \min_{ T^0, T^{in} \in \Xi} -j_D(\Xi,y)  \\
+			&\text{subject to}
+			& \dot{x} = f(x,t,\theta;\Xi) \\
+			&& \dot{y} = g(x(t)) \\
+			&& 40^\circ C \leq T^{in}(t) \leq 50^\circ C \\
+			&& T^{0} = T^{in}(t=0) \\
+		\end{aligned}
+	\end{equation} }
+
+	The non-linear optimization problem is solved by applying single-shooting to obtain the trajectory under assumption of piece-wise constant controls.
+The CasADi framework is used as the interface for the IPOPT solver.
+Each simulation problem is solved multiple time starting from different initial points and the solution with the best score is consider as the optimal solution.
 \end{document}

### 2024-01-21 SFE_article_Design_of_Experiment/Sections/Porosity.tex
21.01

--- 2023-04-22 SFE-article/Sections/Porosity.tex
@@
         \begin{equation}
-            \text{Volume excluding pores} = \dfrac{\text{mass}}{\text{true density}} = \dfrac{1\ \text{kg}}{1250\ \text{kg/m}^3} 0.0008\ \text{m}^3
+            \text{Volume excluding pores} = \dfrac{\text{mass}}{\text{true density}} = \dfrac{1\ \text{kg}}{1256.58\ \text{kg/m}^3} 0.0007958\ \text{m}^3
         \end{equation}
@@
         \begin{equation}
-            \phi = \dfrac{0.0016\ \text{m}^3 - 0.0008\ \text{m}^3}{0.0016\ \text{m}^3} = 0.5
+            \phi = \dfrac{0.0016\ \text{m}^3 - 0.0007958\ \text{m}^3}{0.0016\ \text{m}^3} = 0.5026
         \end{equation}
@@
 
-    Therefore, the porosity of the solid particles is 0.5 or 50\%. This means that half of the total volume of the solid particles is made up of pore space.
+    Therefore, the porosity of the solid particles is 0.5026 or 50.26\%. This means that half of the total volume of the solid particles is made up of pore space.
 

### 2024-01-21 SFE_article_Design_of_Experiment/Sections/Qubic_EOS.tex
21.01

--- 2023-10-06 SFE_article_Parameter_Estimation/Sections/Qubic_EOS.tex
@@
 
-	A cubic equation of state serves as a mathematical model utilized in thermodynamics and fluid dynamics to depict the behavior of real gases and liquids.
-Its name, "cubic," from its characteristic feature—a third-degree polynomial equation that correlates the pressure, volume, and temperature of a substance.
+	A cubic equation of state serves as a mathematical model to describe the behavior of real gases and liquids through a third-degree polynomial equation that correlates the pressure, volume, and temperature of a substance.
 These equations constitute tools for comprehending the phase behavior, properties, and thermodynamic processes of actual substances, across various engineering and scientific applications.
@@
 	\begin{equation}
-		P = \frac{RT}{v_m-b} - \frac{a\alpha}{v_m^2 - ubv_m + wb^2}
+		P = \frac{RT}{v_m-b} - \frac{\Phi}{v_m^2 - ubv_m + wb^2}
 	\end{equation}
@@
 
-	In this equation, P denotes the pressure of the substance, $v_m$ represents the molar volume (volume per mole) of the substance, T stands for the absolute temperature of the substance, u and w are integers that vary from one equation to another, R symbolizes the universal gas constant, and a and b serve as substance-specific parameters known as Van der Waals constants.
-Additionally, $\omega$ denotes an acentric factor.
+	In this equation, P denotes the pressure of the substance, $v_m$ represents the molar volume of the substance, T stands for the absolute temperature of the substance, u and w are integers that vary from one equation to another, R symbolizes the universal gas constant, and a and b serve as substance-specific parameters known as Van der Waals constants.
+$\omega$ denotes an acentric factor and $\Phi=a\alpha$.
 
@@
 These constants factor in molecular interactions (represented by 'a') and the finite size of gas molecules (indicated by 'b').
-Different substances will possess distinct values for 'a' and 'b' based on experimental data.
 
-	Several variations of the cubic equation of state exist, including the Van der Waals equation and the Redlich-Kwong equation, each with its own set of parameters and assumptions.
-Tables \ref{tab:Popular_Cubic_EoS} show parameters for popular cubic EoS.
+	Several variations of the cubic equation of state exist each with its own set of parameters and assumptions. Tables \ref{tab:Popular_Cubic_EoS} show parameters for popular cubic EoS.
 
@@
 
-	where $A=\frac{a\alpha P}{R^2T^2}$ and $B=\frac{bP}{RT}$.
+	where $A=\frac{\Phi P}{R^2T^2}$ and $B=\frac{bP}{RT}$.
 
@@
 
-	For an ideal gas, the compressibility factor is defined as $Z = 1$.
-In many real-world applications, deviations from ideal gas behavior, needs to be taken into account to have a precise model describing a physical phenomena.
+	For an ideal gas, the compressibility factor is defined as $Z = 1$, but to describe real-life physical phenomena, the deviation of Z needs to be consider.
 The value of $Z$ typically increases with pressure and decreases with temperature.
 At elevated pressures, molecules collide more frequently, allowing repulsive forces between molecules to influence the molar volume of the real gas ($v_m$) to surpass that of the corresponding ideal gas $\left( \left(v_m\right)_{ideal~gas} = \frac{RT}{P} \right)$, resulting in $Z$ exceeding one.
-Analogously, at lower pressures, molecules move freely, with attractive forces predominating, leading to $Z < 1$.
+At lower pressures, molecules move freely, with attractive forces predominating, leading to $Z < 1$.
 
 	Numerical methods such as Newton-Raphson can be used to solve the polynomial equation to obtain the compressibility ${\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ at given temperature and pressure.
-Alternatively, the Cardano formula can be used to get the closed form solution of the Equation \ref{EQ:Compressibility_Polynomial}.
-Further details regarding the Cardano formula can be found in Appendix \ref{CH: Cardano}.
+Alternatively, the closed form solution can by obtained by Cardano formula.
+Details regarding the Cardano formula can be found in Appendix \ref{CH: Cardano}.
 
@@
 
-	To calculate the residual contribution, we use the standard equation found in many textbooksr4•6 l for the residual internal energy derived from the Peng-Robinson equation of state
-
-	%Following the work of \citet{Pratt2001}, it is assumed that the specific heat can be obtained as a sum of ideal gas contribution and a residual correction for non-ideal behaviour, as given by Equations \ref{eq: Cv_CO2} and \ref{eq: Cp_CO2}.
+	The residual component of the specific heat can obtained from general relation between $C_v$ and $C_p$ as given by \citet{Poling2001}.
 
 	{\footnotesize
-		\begin{subequations}\begin{align}
-				{\color{black}C_v}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) & = {\color{black}C_v^{\text{I}}}\left({\color{black}T}(t,z),P(t)\right) + {\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) \label{eq: Cv_CO2}; \\
-				{\color{black}C_p}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) & = \underbrace{{\color{black}C_p^{\text{I}}}\left({\color{black}T}(t,z),P(t)\right)}_{\text{Eq.
-} \eqref{eq: Cp_I}} + \underbrace{{\color{black}C_p^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}_{\text{Eq.
-} \eqref{eq: Cp_R}}  \label{eq: Cp_CO2}.
-	\end{align}\end{subequations} }
+	\begin{equation} \label{EQ:CP_residual}
+		C_p^R = C_v^R + T\left(\frac{\partial P}{\partial T}\right)_{v_m} \left(\frac{\partial v_m}{\partial T}\right)_P - R
+	\end{equation}}
 
-	${\color{black}C_v}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ and ${\color{black}C_p}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ are the specific heat of $CO_2$ at constant volume and pressure, respectively.
+	The effects of pressure and temperature for liquids are not great, but both $C_p$ and $C_v$ diverge at the critical point of a pure fluid.
+In the neighborhood of the critical, $\left(\frac{\partial P}{\partial v_m}\right)_T$ approaches zero, so $C_p$ increases much faster than $C_v$.
+At both high and low densities, the differences are small, but for $T_r$ near unity, they increase rapidly as the critical density is approached.
+At fixed density in this region, $C_p$ actually decreases as T increases.
 
-	The ideal-gas contribution ${\color{black}C_v^{\text{I}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ and ${\color{black}C_p^{\text{I}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$, can be obtained based on heat-capacity data applicable to gases at low pressure.
-For $CO_2$, the ideal gas contribution to the specific heat at constant ${\color{black}P}(t)$, as function of ${\color{black}T}(t,z)$ is given by,
+	The term $\left(\frac{\partial P}{\partial T}\right)_{v_m}$ can be obtain by direct differentiation of P-R EoS
 
@@
 	\begin{equation}
-			{\color{black}C_p^{\text{I}}}\left({\color{black}T}(t,z),P(t)\right) = {\color{black}C_{P0}} + {\color{black}C_{P1}}T(t,z) + {\color{black}C_{P2}}{\color{black}T}^2(t,z) + {\color{black}C_{P3}}{\color{black}T}^3(t,z) \label{eq: Cp_I}
-	\end{equation} }
+		\left(\frac{\partial P}{\partial T}\right)_{v_m} = \frac{R}{v_m - b} - \frac{\frac{d \Phi}{dT}}{\left[v_m(v_m+b)+b(v_m-b)\right]^2}
+	\end{equation}}
 
-	where the coefficients of the expansion are ${\color{black}C_{P0}} = 22.26$, ${\color{black}C_{P1}} = 5.981 \times 10^{-2}$, ${\color{black}C_{P2}} = -3.501 \times 10^{-5}$, and ${\color{black}C_{P3}} = 7.469 \times 10^{-9}$, as given by \citet{Kyle1999}.
+	where $\left(\frac{\partial \Phi}{\partial T}\right)_{v_m} = \frac{-f(\omega)a}{\sqrt{TT_c}(1 + f(\omega)( 1 - \sqrt{T/T_c}))}$
 
-	The correction term ${\color{black}C_p^{\text{R}}}\left({\color{black}T}(t,z){\color{black}P}(t)\right)$ at constant pressure ${\color{black}P}(t)$, can be defined by introducing  ${\color{black}C_p^{\text{I}}}({\color{black}T}(t,z)) - {\color{black}C_v^{\text{I}}}({\color{black}T}(t,z)) = {\color{black}R}$ and using the definition of ${\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z){\color{black}P}(t)\right)$.
-The general form of the correction term is given by Equation \ref{eq: Cp_R}
+	The term $\left(\frac{\partial v_m}{\partial T}\right)_P = \frac{R}{P} \left(T \left(\frac{\partial Z}{\partial T}\right)_P + Z \right)$
+
+	The term $\left(\frac{\partial Z}{\partial T}\right)_P$ can be defined as below
+
+	{\footnotesize
+	\begin{equation}
+		\left(\frac{\partial Z}{\partial T}\right)_P = \frac{ \left(\frac{\partial A}{\partial T}\right)_P (B-Z) + \left( \frac{\partial B}{\partial T} \right)_P \left( 6BZ+2Z-3B^2-2B+A-Z^2 \right)}{3Z^2 + 2(B-1)Z + (A-2B-3B^2)}
+	\end{equation}}
 
@@
 	\begin{align}
-			&{\color{black}C_p^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) = \underbrace{{\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}_{\text{Eq.
-}\eqref{eq: CvR}} \nonumber \\
-			&+ {\color{black}T}(t,z) \underbrace{\left(\cfrac{\partial {\color{black}P}(t)}{\partial {\color{black}T}}\right)_{{\color{black}v_m}(t,z)}}_{\text{Eq.
-} \eqref{eq: dPdT}} \underbrace{\left(\cfrac{\partial {\color{black}v_m}\left({\color{black}T}(t,z),{\color{black}P}(t)\right)}{\partial {\color{black}T}}\right)_{{\color{black}P}(t)}}_{\text{Eq.
-} \eqref{eq: dVdT}} - {\color{black}R}.
-\label{eq: Cp_R}
-	\end{align} }
+		\left(\frac{\partial A}{\partial T}\right)_P &= (P/(RT)^2)(\frac{d \Phi}{dT} - 2a/T) \\
+		\left(\frac{\partial B}{\partial T}\right)_P &= -bP/(RT^2)
+	\end{align}}
 
-	%	The braced terms are obtained from the chosen equation of state and the compressibility definition ${\color{black}P}(t) {\color{black}v_m}({\color{black}T}(t,z),{\color{black}P}(t)) = {\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right){\color{black}R}{\color{black}T}(t,z)$.
-\\
-
-	For the partial derivative of the volume with respect to temperature ${\color{black}T}(t,z)$ at constant pressure ${\color{black}P}(t)$, we have
-
-	{\footnotesize
-		\begin{align}
-			\left( \cfrac{\partial {\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{\partial {\color{black}T}} \right)_{{\color{black}P}(t)} &= \cfrac{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right) {\color{black}R}}{{\color{black}P}(t)} \nonumber \\
-			&+ \cfrac{{\color{black}R}{\color{black}T}(t,z)}{{\color{black}P}(t)} \underbrace{\left( \cfrac{\partial {\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{\partial {\color{black}T}} \right)_{{\color{black}P}(t)}}_{\text{Eq.
-}\eqref{eq: dZdT}} \label{eq: dVdT}
-	\end{align} }
-
-	with partial derivative of the compressibility factor with respect to temperature ${\color{black}T}(t,z)$ at constant pressure ${\color{black}P}(t)$
+	The first component of Equation \ref{EQ:CP_residual} from definition of $C_v = \left(\frac{\partial U^R}{\partial T}\right)_{v_m}$, where $U^R$ represents internal energy.
+In case of Pen-Robinson $U^R$ equals to
 
@@
 	\begin{equation}
-			\left(\cfrac{\partial{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{\partial {\color{black}T}}\right)_{{\color{black}P}(t)} = \left(\cfrac{\partial \dfrac{{\color{black}P}(t) {\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}R}{\color{black}T}(t,z)}}{\partial {\color{black}T}}\right)_{{\color{black}P}(t)} \label{eq: dZdT}
-	\end{equation} }
+		U^R = \frac{T \frac{d^2 \Phi}{dT^2}}{b \sqrt{8}} \ln \left( \frac{Z+B\left(1+\sqrt{2}\right)}{Z+B\left(1-\sqrt{2}\right)} \right)
+	\end{equation}}
 
-	Similarly, for the partial derivative of the pressure with respect to temperature at constant volume is :
+	As given by \citet{Pratt2001}, for Peng-Robinson EoS the term $\frac{d^2 \Phi}{dT^2}$ is defined as follow
 
@@
 	\begin{equation}
-			\left(\cfrac{\partial {\color{black}P}(t)}{\partial {\color{black}T}}\right)_{{\color{black}v_m}(t,z)} = \left( \cfrac{\partial{\dfrac{{\color{black}Z}{\color{black}R}{\color{black}T}(t,z)}{{\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}}}{\partial{\color{black}T}}\right)_{{\color{black}v_m}(t,z)} \label{eq: dPdT}
-	\end{equation} }
-
-	The residual specific heat at constant volume is obtained, by definition, by using the residual internal energy
-
-	{\footnotesize
-		\begin{equation}
-			{\color{black}C_v^{\text{R}}}\left({\color{black}T}(t,z),{\color{black}P}(t)\right) = \left(\cfrac{\partial{\color{black}U^{\text{R}}}\left({\color{black}T}(t,z),{\color{black}P}(t)\right)}{\partial {\color{black}T}}\right)_{{\color{black}v_m}(t,z)} \label{eq: CvR}
+		\frac{d^2\Phi}{dT^2} = \frac{af(\omega)\sqrt{\frac{T_c}{T}} \left( 1+ f\left(\omega\right) \right)}{2TT_c}
 	\end{equation} }
@@
 
-	In thermodynamics, a departure function is a concept used to calculate the difference between a real fluid's thermodynamic properties and those of an ideal gas, given a specific temperature and pressure.
-Common departure functions include those for enthalpy, entropy, and internal energy.
+	In thermodynamics, a departure function is a concept used to calculate the difference between a real fluid's thermodynamic properties (enthalpy, entropy, or internal energy) and those of an ideal gas, given a specific temperature and pressure.
 These functions are used to calculate extensive properties, which are properties computed as a difference between two states.
@@
 The integral includes a term that depends on the derivative of the compressibility factor with respect to temperature, evaluated at the molar volume $v_m$.
-Finally, the term $1-Z$ is added to account for the deviation of the fluid's properties from those of an ideal gas.
+Finally, the term $1-Z$ is added to account for the deviation of the fluid's properties from an ideal state.
 
-	The Peng–Robinson equation of state relates the three interdependent state properties pressure $P$, temperature $T$, and molar volume $v_m$.
+	The Peng–Robinson EoS relates the three interdependent state properties pressure $P$, temperature $T$, and molar volume $v_m$.
 From the state properties ($P$, $v_m$, $T$), one may compute the departure function for enthalpy per mole (denoted $h$) as presented by \citet{Gmehling2019} or \citet{Elliott2011}:

### 2024-01-21 SFE_article_Design_of_Experiment/Sections/Sensitivity_Analysis.tex
21.01

--- 2024-01-20 SFE_article_Sensitivity_Analysis/Sections/Sensitivity_Analysis.tex
@@
 
-	As presented in the work of \citet{Maly1996}, the sensitivity analysis equations(${\dot{Z}}$) are developed by taking the total derivative of the state vector $x$ with respect to parameters $p$, where $p$ is a subset of $\theta$.
+	As presented in the work of \citet{Maly1996}, the sensitivity analysis equations(${\dot{Z}}$) are developed by taking the total derivative of the state vector $x$ with respect to parameters $p$, where $p$ is a subset of the parameter space $\theta$.
 
@@
 
-	The sensitivity matrix ${S}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_p$, where each equation ${S}(n_x,n_p)$ is the derivative of the state variable $x_{n_x}$ with respect to the parameter $p_{n_p}$.
+	The sensitivity matrix ${S}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_p$, where each subequation ${S}(n_x,n_p)$ is the derivative of the state variable $x_{n_x}$ with respect to the parameter $p_{n_p}$.
 
@@
 
-	The jacobian ${J_p}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_p$, where each equation ${J_p}(n_x,n_p)$ is the partial derivative of the process model equation $F_{n_x}$ with respect to the parameter $p_{n_p}$.
+	The jacobian ${J_p}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_p$, where each subequation ${J_p}(n_x,n_p)$ is the partial derivative of the process model equation $F_{n_x}$ with respect to the parameter $p_{n_p}$.
 

### 2024-01-21 SFE_article_Sensitivity_Analysis/Article_Sensitivity_Analsysis.tex
21.01

--- 2024-01-19 SFE_article_Sensitivity_Analysis/Article_Model_Parameters.tex
@@
 
-The sensitivity analysis is a tool to understand the parametric dependence of dynamic behavior and its suitability in inferring mechanisms of the dynamic behavior of the analyzed system.
-The mathematical formulation involves derivative-based local sensitivity analysis of the solution of an inverse problem with respect to perturbations of parameters.
-The local method is based only on considering all parameters as constants (those independent of time or location), and then the sensitivity equations are estimated by solving a variational system simultaneously with the original system.
+The sensitivity analysis is a tool to understand the parametric dependence in the dynamic behaviour of the analysed system.
+The presented formulation involves derivative-based local sensitivity analysis of the model solution with respect to selected parameters and controls.
 The sensitivity equations can be obtained in various ways, but the automatic differentiation technique was implemented to obtain the sensitivity equations in this work.
 By identifying which parameters are influential at each period of the simulation, local sensitivity analysis can yield valuable information for guiding the process modelling, the design of experiments or the model reduction.
-The local sensitivity analysis techniques consider the sensitivities at only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions unless the discussed system is a linear system.
+The local sensitivity analysis techniques consider the sensitivities at only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions unless the discussed system is a linear model.
 
@@
 Every change in the control variables leads to a state-space change, eventually affecting the process performance.
+
+Similarities between Figures \ref{fig:Sensitivty_F_y}, \ref{fig:Sensitivty_P_y} and \ref{fig:Sensitivty_T_y} can observed, although the sources of disturbances are different.
+All the plots stay initially plat, and this is because the extraction kinetic is mainly controlled by the concentration gradient.
+The largest sensitivity deviations are observed in the second extraction phase, which is mainly controlled by the internal mass transfer.
+These deviations are strongly related to the fluid velocity and the correlations used to connect the extraction kinetic parameters.
+As correlations used in this work are linear functions of the fluid density( {\color{red} article 1}), Figures \ref{fig:Sensitivty_P_y} and \ref{fig:Sensitivty_T_y} are characterised by the opposite changes in the fluid density, which leads to the sensitivity plots with similar shape but opposite sign.
+In the third extraction phase, the concentration gradient and the internal diffusion coefficient decrease with the solute concentration in the solid phase( it is more difficult to extract the solute from the particle core than from the outer shell).
+It is important to note that the local-sensitivity methods obtain the discussed results, which can be obtained at different operating conditions.
+
 This information can be utilized to identify which control variables influence the extraction yield the most.

### 2024-01-22 SFE_article_Design_of_Experiment/Sections/Literature_Review.tex
22.01

@@
 
-	This study aims to analyze the influence of changes in operating conditions on the supercritical extraction process described in {\color{red}article 1}.
-The emphasis is put on the effect of the mass flow rate, pressure, and the inlet temperature.
-The relation between input and output is obtained by applying a sensitivity analysis.
-Sensitivity analysis examines the impact of varying inputs or model parameters on the system's output.
-The aim is to understand and to allocate the source of uncertainty in the output to the corresponding inputs or parameters.
-There are many sensitivity analysis methods, which include but are not limited to those listed below:
+	The design of experiments (DOE) also known as experiment design or experimental design, is the design of any task that aims to describe and explain the variation of information under conditions that are hypothesized to reflect the variation.
+The term is generally associated with experiments in which the design introduces conditions that directly affect the variation, but may also refer to the design of quasi-experiments, in which natural conditions that influence the variation are selected for observation.
 
-	\begin{itemize}
-		\item One-at-a-time method
-		\item Derivative-based local methods
-		\item Variance-based methods
-	\end{itemize}
+	\citet{Oinas1992} presents how the experimental design methods can be applied for analyzing mass transfer and reaction in stirred gas—liquid and gas—liquid—solid reactors.
+In this work a sequential approach to experimentation is suggested.
+First preliminary set of 8 2-level experiments ($2^8$ factorial design) were performed.
+The identifiability of the parameters was then considered and some reparametrisations done.
+The precision of the parameter values were further improved with D-optimal experiments.
 
-	Different supercritical extraction models were analyzed using sensitivity analysis.
-\citet{Fiori_2007}, performed the sensitivity calculations by varying the parameters within their confidence interval and observing how the model results changed.
-This allows to evaluate the effect of the uncertainties on model predictions.
-The sensitivity analysis revealed that the particle diameter and the internal mass transfer coefficient are significant for the extraction process.
-The effect of changing some operative conditions was also investigated, underlining how the solvent flow rate and the seed milling affect the extraction process.
+	\citet{Kassama2008} used the response surface methodology with the central composite rotatetable design (CCRD) model.
+The goal of this work was to optimize parameters for supercritical carbon dioxide extraction of lycopene ($C_{40}H_{56}$) from dried tomato skin.
+The CCRD consisting of three-factored factorial design with two levels was used in this study.
+The factors used were temperature of the extraction chamber (40 and 70 $^\circ C$), pressure of the extraction fluid (25 and 45 MPa), and modifier concentration (5 and 15\%).
+A second-degree polynomial equation was developed from a response surface analysis for all trans-lycopene yield and the highest yield was predicted at 62 $^\circ C$, 45 MPa (450 bar) and 14\% temperature, pressure and modifier concentration, respectively and the recovery of all trans-lycopene was 33\%.
 
-	\citet{Santos2000}, in their work, considered a model of supercritical extraction process for semi-continuous isothermal and isobaric extraction process using carbon dioxide as a solvent.
-The parametric sensitivity analysis was carried out by applying disturbances of 10\% in the values of the normal operation conditions.
-
-	\citet{Hatami2024} used a one-factor-at-a-time sensitivity analysis to assess the response of NPV concerning variations in both technical and economic variables.
-Their findings show that the most influential factors on NPV include the price of the extract, the interest rate, the dynamic time of SFE, and the project lifetime.
-
-	\citet{Poletto1996} provided a general dimensionless model for the supercritical extraction process of vegetable and essential oils and applied a sensitivity analysis.
-They found that a dimensionless partition coefficient and a dimensionless characteristic time appeared as the most important parameters of the extraction process.
-The sensitivity calculations were performed by varying the parameters and analyzing the model response.
+	\citet{Abrahamsson2016} selected extraction conditions based on a symmetrical full factorial design of experiments with three factors and three levels.
+The factors were pressure ranging from 15 to 30 MPa, temperature from 313 to 353 K and compressed $CO_2$ pump volumetric flow rate from 0.5 to 1.5 mL/min, with three replicates at the center point (22.5 MPa, 333 K, 1 mL/min) thus resulting in a total of 29 extractions.
+By including all of the 29 experiments for the model calibration, a more robust estimates of parameters were obtained.
 

### 2024-01-22 SFE_article_Design_of_Experiment/Sections/Optimal_design_of_experiment.tex
22.01

@@
 
-	The design of experiments (DOE) also known as experiment design or experimental design, is the design of any task that aims to describe and explain the variation of information under conditions that are hypothesized to reflect the variation.
-The term is generally associated with experiments in which the design introduces conditions that directly affect the variation, but may also refer to the design of quasi-experiments, in which natural conditions that influence the variation are selected for observation.
+	\subsubsection{Maximum likelihood}
 
-	\subsubsection{Maximum likelihood}
-	%Let $Y$ be the vector of all experimental results (random vector) to be used to estimate parameters $p$ (where $p$ is the subset of parameter space $\Theta$) and model output $y(p)$.
-The vector of the corresponding quantities computed by the model $\dot{x}(t)=G(x(t);p)$.
-For a parallel model, the parameters of which are to be estimated from measurements of an output vector $\dot{y}=g(x)$.
-We shall call any optimizer of $j$, i.e., any $\hat{p}$ that corresponds to an optimal value of the cost function $j$, an estimate of $p$ in the sense of $j$.
-
-	The vector $\hat{p}_{ml}$ will be a maximum-likelihood estimate if it maximizes the cost function:
+	Following the work of \citet{Walter2010}, the vector $\hat{p}_{ml}$ will be a maximum-likelihood estimate if it maximizes the cost function:
 
@@
 
-	If $p$ were fixed, $\pi_y(Y|p)$ would be the probability density of the random vector $Y$ generated by a model with parameters $p$.
-Here, to the contrary, $Y$ is fixed and corresponds to the observations.
+	If $p$ were fixed, $\pi_y(Y|p)$ would be the probability density of the random vector $Y$ generated by a model with parameters $p$ and observations $Y$.
 Considered as a function of $p$, $\pi_y(Y|p)$ is then called the likelihood of $Y$.
@@
 
-	where the vector $y(t_i, p^*)$ is the output of a deterministic model, $p^*$ is the true value of the parameter vector, and $\epsilon_i$ belongs to a sequence of independent random variables with probability density $\pi_{\epsilon}(\epsilon_i)$.
+	where the vector $y(t_i, p^*)$ is the output of a deterministic model, $p^*$ is the true value of the parameter vector, and the error $\epsilon_i$ belongs to a sequence of independent random variables with probability density $\pi_{\epsilon}(\epsilon_i)$.
 Since the $\epsilon_i$ are independent
@@
 	{\footnotesize
-	\begin{equation}
+	\begin{equation} \label{EQ:Error_measurment}
 		e^y(t_i, p) = Y(t_i) - y(t_i, p)
@@
 	For the true value of the parameters, it satisfies $e^y(t_i, p^*)=\epsilon_i$.
-and, since $y$ is deterministic, $\pi_{y_i} (Y(t_i)|p) = \pi_{\epsilon_i} (e^Y(t_i)|p)$.
+and, since $y$ is deterministic, $\pi_{y_i} (Y(t_i)|p) = \pi_{\epsilon_i} (e^y(t_i),p)$.
 The likelihood of the $n_t$ observations can be written as
@@
 
-	Considering the mismatch between the dataset and the model output, the expectation $\mathop{\mathbb{E}}_{Y|p}$ can be redefined as $\mathop{\mathbb{E}}_{Y|p} \left[ \left( Y(t_i) - y(t_i, p) \right) \left( Y(t_k) - y(t_k, p) \right) \right] = \mathop{\mathbb{E}}_{Y|p} \left[ \epsilon_i \epsilon_k \right]$.
+	Considering the mismatch between the dataset and the model output, the Equation \ref{EQ:Error_measurment} can be used too redefine the expectation $\mathop{\mathbb{E}}_{Y|p}$ as $\mathop{\mathbb{E}}_{Y|p} \left[ \left( Y(t_i) - y(t_i, p) \right) \left( Y(t_k) - y(t_k, p) \right) \right] = \mathop{\mathbb{E}}_{Y|p} \left[ \epsilon_i \epsilon_k \right]$.
 For $i=k$, the expectation of $\epsilon_i$ is the variance of the noise $\sigma_{t_i}^2$.
@@
 such that it were possible to replicate the same experiment and estimate $\hat{p}$ an infinite number of times, the mean of the estimates would coincide with the true value.
-Let $P$ be the covariance matrix of this estimator.
-Since $\hat{p}$ is unbiased, $P$ can be written as
+Let $\Sigma$ be the covariance matrix of this estimator.
+Since $\hat{p}$ is unbiased, $\Sigma$ can be written as
 
@@
 
-	In other words, the precision to which we can estimate $p$ is fundamentally limited by the Fisher information of the likelihood function.
+	In other words, the precision to which we can estimate $p$ is limited by the Fisher information of the likelihood function.
 Based on the Cramer-Rao inequality, the Fisher information matrix can used to calculate the covariance matrices associated with maximum-likelihood estimates.
@@
 
-	Let's consider that each scalar observation in our study can be expressed as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ representing the specific experimental conditions (such as the timing of measurements, operating conditions, etc.) under which the i'th observation is gathered.
+	Let's consider that each scalar observation in a study can be expressed as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ representing the specific experimental conditions (such as the timing of measurements, operating conditions, etc.) under which the i'th observation is gathered.
 When collecting $n_t$ such observations, the assembly of these $\xi_i$ vectors forms the matrix $\Xi = (\xi_1, \xi_2,..., \xi_{n_t})$, which combine all the experimental conditions that need optimization.
@@
 	The cost function should describe the amount of information from an experiment.
-For that purpose it can be assumed a function $\phi$ can be related to the Fisher information obtained an arbitrary operating conditions.
+For that purpose it can be assumed a function $\kappa$ can be related to the Fisher information obtained an arbitrary operating conditions.
 
@@
 	\begin{equation}
-		j(\Xi) = \phi\left[ \text{FIM(p)}(p, \Xi) \right]
+		j(\Xi) = \kappa\left[ \text{FIM}(p, \Xi) \right]
 	\end{equation} }
@@
 	\begin{align}
-		\phi_k(\text{FIM(p)}) &= \left[\frac{1}{n_p} \text{trace}\left( Q\text{FIM(p)}^{-1}Q^\top \right)^k \right]^{1/k} \quad &\text{if} \det F \neq 0 \nonumber \\
-		\phi_k(\text{FIM(p)}) &= \infty \quad &\text{if} \det F = 0
+		\kappa_k(\text{FIM(p)}) &= \left[\frac{1}{n_p} \text{trace}\left( Q\text{FIM}()^{-1}Q^\top \right)^k \right]^{1/k} \quad &\text{if} \det \text{FIM} \neq 0 \nonumber \\
+		\kappa_k(\text{FIM(p)}) &= \infty \quad &\text{if} \det \text{FIM} = 0
 	\end{align} }

### 2024-01-22 SFE_Design_of_Experiment/test_direct_jacob.m

@@ -6,17 +6,17 @@ delete(gcp('nocreate'));
 addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
 import casadi.*
 
-excel_file = 'output_change_In_T_and_P.xls';
+excel_file = 'output_T45.xls';
 numeEval = 69;
 
-parfor ii=1:numeEval
+parfor ii=7:numeEval
 
 Parameters_table                = readtable('Parameters.csv') ;             % Table with prameters
 Parameters                      = num2cell(Parameters_table{:,3});          % Parameters within the model + (m_max), m_ratio, sigma
 
 %% Create the solver
-Iteration_max                   = 200;                                       % Maximum number of iterations for optimzer
-Time_max                        = 24.0;                                      % Maximum time of optimization in [h]
+Iteration_max                   = 100;                                       % Maximum number of iterations for optimzer
+Time_max                        = 12.0;                                      % Maximum time of optimization in [h]
 
 nlp_opts                        = struct;
 nlp_opts.ipopt.max_iter         = Iteration_max;
@@ -46,8 +46,7 @@ DeadTime                = 25;
 timeStep                = 1;                                                % Minutes
 timeShited              = 0;                                                % Minutes
 SamplingTime            = 5;                                                % Minutes
-T_change_Time           = 5;                                                % Minutes
-P_change_Time           = 30;                                                % Minutes
+OP_change_Time          = 15;                                               % Minutes
 
 simulationTime          = PreparationTime + ExtractionTime;
 
@@ -57,8 +56,7 @@ Time                    = [0 Time_in_sec/60];                               % Mi
 
 N_Time                  = length(Time_in_sec);
 SAMPLE                  = SamplingTime:SamplingTime:ExtractionTime;
[…]

### 2024-01-24 SFE_article_Design_of_Experiment/Article_Design_of_Experiment.tex
24.01

@@
 % ===================================================
-\title[mode=title]{Optimal design of experiment}                      
-\shorttitle{Optimal design of experiment}
+\title[mode=title]{Optimal design of experiments}                      
+\shorttitle{Optimal design of experiments}
 
@@
 The balance equations are combined with the extraction kinetic equation to develop the process model in Chapter \ref{CH: Extraction_model}.
-The derivative-based local sensitivity analysis is presented in Chapter \ref{CH: Sensitivity_Analysis} and is then combined with the process model.
+The general formulation of model-based the optimal design of experiments is presented in Chapter \ref{CH: Optimal_design_of_experiment}.
 Finally, the sensitivity plots are discussed in Chapters \ref{CH: Results} and \ref{CH: Conclusion}.
@@
 \section{Results}
-%\subfile{Sections/Results_Sensitivity}
+\subfile{Sections/Results_DOE}
 

### 2024-01-24 SFE_article_Design_of_Experiment/Sections/Literature_Review.tex
24.01

@@
 
+	\citet{Espie1989} presented the case of the continuous yeast fermenter, in which a stream containing an organic substrate is fed to a well-stirred tank, and a model is sought to describe the substrate and biomass consumption.
+Optimal dynamic experiments are initially designed to select the best model from a set of candidate models, then to produce improved parameter estimates for the remaining model.
+
 \end{document}

### 2024-01-24 SFE_article_Design_of_Experiment/Sections/Model.tex
21.01
24.01

--- 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Model.tex
@@
 	{\footnotesize
-		\begin{equation}
+		\begin{equation} \label{EQ:Velocity}
 			\int \frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A \phi}(z) )}{\partial {\color{black}z}} dz = 0 \rightarrow {\color{black}F}={\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A\phi}(z)
@@
 %				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
-				\cfrac{d{\color{black}y}(t)}{dt} &= \qquad \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))} {\color{black}c_f}(t,z) \biggr\rvert_{z=L} 
+				\cfrac{d{\color{black}y}(t)}{dt} = g(x(t)) &= \qquad \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))} {\color{black}c_f}(t,z) \biggr\rvert_{z=L} 
                 \label{Model_measurment_2}
@@
 The controllable input variables are the mass flow-rate and temperature of the solvent in the feed and the pressure in the extractor.
-Additionally, the pressure change is augumented with the state-space and denoted as ${\color{black}P}(t)$.
+Additionally, the pressure change is augmented with the state-space and denoted as ${\color{black}P}(t)$.
 			The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator (${\color{black}Y}(t)$).

### 2024-01-24 SFE_article_Design_of_Experiment/Sections/Optimal_design_of_experiment.tex
24.01

@@
 		\begin{aligned}
-		&\text{FIM(p)} = - \mathop{\mathbb{E}}_{Y|p} \left[ \frac{\partial^2 \ln (\pi_y (Y|p))}{\partial p \partial p^\top} \right] = \mathop{\mathbb{E}}_{Y|p} \left[ \frac{\partial \ln (\pi_y (Y|p))}{\partial p} \frac{\partial \ln (\pi_y (Y|p))}{\partial p^\top} \right] \nonumber \\
+		&\mathcal{F}(p) = - \mathop{\mathbb{E}}_{Y|p} \left[ \frac{\partial^2 \ln (\pi_y (Y|p))}{\partial p \partial p^\top} \right] = \mathop{\mathbb{E}}_{Y|p} \left[ \frac{\partial \ln (\pi_y (Y|p))}{\partial p} \frac{\partial \ln (\pi_y (Y|p))}{\partial p^\top} \right] \nonumber \\
 		&= \mathop{\mathbb{E}}_{Y|p} \left[ \sum_{k=1}^{n_t} \left( \frac{Y(t_k) - y(t_k, p)}{\sigma_{t_k}^2} \frac{\partial y(t_k, p)}{\partial p} \right) \times  \sum_{i=1}^{n_t} \left( \frac{Y(t_i) - y(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y(t_i, p)}{\partial p^\top} \right) \right] \nonumber \\
@@
 	\begin{equation}
-		\text{FIM(p)} = \sum_{i=1}^{n_t} \left( \frac{1}{\sigma_{t_i}^2} \frac{\partial y(t_i, p)}{\partial p} \frac{\partial y(t_i, p)}{\partial p^\top} \right)
+		\mathcal{F}(p) = \sum_{i=1}^{n_t} \left( \frac{1}{\sigma_{t_i}^2} \frac{\partial y(t_i, p)}{\partial p} \frac{\partial y(t_i, p)}{\partial p^\top} \right)
 	\end{equation} }
@@
 	\begin{equation}
-		\text{\text{FIM(p)}} = \frac{\partial y(t, p)}{\partial p} \begin{bmatrix}
+		\mathcal{F}(p) = \frac{\partial y(t, p)}{\partial p} \begin{bmatrix}
 			\frac{1}{\sigma_{t_1}^2} & 0 & 0\\
@@
 	\begin{equation}
-		\Sigma \geq \text{FIM(p)}^{-1}(p^*)
+		\Sigma \geq \mathcal{F}^{-1}(p^*)
 	\end{equation} }
@@
 	\begin{equation}
-		j(\Xi) = \kappa\left[ \text{FIM}(p, \Xi) \right]
+		j(\Xi) = \kappa\left[ \mathcal{F}(p, \Xi) \right]
 	\end{equation} }
@@
 	\begin{align}
-		\kappa_k(\text{FIM(p)}) &= \left[\frac{1}{n_p} \text{trace}\left( Q\text{FIM}()^{-1}Q^\top \right)^k \right]^{1/k} \quad &\text{if} \det \text{FIM} \neq 0 \nonumber \\
-		\kappa_k(\text{FIM(p)}) &= \infty \quad &\text{if} \det \text{FIM} = 0
+		\kappa_k(\mathcal{F}(p)) &= \left[\frac{1}{n_p} \text{trace}\left( Q\mathcal{F}^{-1}(p, \Xi) Q^\top \right)^k \right]^{1/k} \quad &\text{if} \det \mathcal{F} \neq 0 \nonumber \\
+		\kappa_k(\mathcal{F}(p)) &= \infty \quad &\text{if} \det \mathcal{F} = 0
 	\end{align} }
@@
 	\begin{equation}
-		j_L(\Xi) = \text{trace} \left[ Q^\top Q\text{FIM}^{-1}(p,\Xi) \right]
+		j_L(\Xi) = \text{trace} \left[ Q^\top Q\mathcal{F}^{-1}(p,\Xi) \right]
 	\end{equation} }
@@
 Taking $Q = \textbf{I}_{n_p}$ and $k = \infty$ corresponds to E-optimality; E-optimal design maximizes the smallest eigenvalues of the Fisher information matrix and thus minimizes the length of the largest axis of the asymptotic confidence ellipsoids.
-The most widely used optimality criterion has $k = 0$, $Q = \textbf{I}_{n_p}$ , requiring minimization of $\det \text{FIM}^{-1}(p, \Xi)$, or, equivalently, maximization of
+The most widely used optimality criterion has $k = 0$, $Q = \textbf{I}_{n_p}$ , requiring minimization of $\det \mathcal{F}^{-1}(p, \Xi)$, or, equivalently, maximization of
 
@@
 	\begin{equation}
-		j_D(\Xi) = \det \text{FIM}(p, \Xi)
+		j_D(\Xi) = \det \mathcal{F}(p, \Xi)
 	\end{equation} }
@@
 
-	The optimal design of the experiment technique is used to extend the experiment discussed in $({\color{red}article~1})$, where supercritical extraction from caraway seeds has been discussed.
+	The optimal design of experiments technique is used to extend the experimental procedure discussed in $({\color{red}article~1})$, where supercritical extraction from caraway seeds has been discussed.
 The presented extraction was performed under multiple operating conditions, such that the temperature, pressure, and flow rate were constant during each batch.
@@
 In this work, the optimal design of the experiment is used to design an experiment to validate these correlations.
+The Fisher information is computed with respect to correlations for $D_i$ and $\Upsilon$, which gives in total fours parameters.
 The model parameters, the extraction time (150 minutes), and the sampling time (5 minutes) are the same as in $({\color{red}article~1})$ to mimic the original system.
 It is assumed that the flow rate is constant because the effect of the flow rate has not been deeply investigated in the previous work of the authors (${\color{red}articl~1}$).
-The pressure is assumed to be constant during the whole experiment.
-The initial temperature ($T^0$) of the extractor and the inlet temperature ($T^{in}$) are decision variables in the optimization.
+In this work, two cases are considered.
+
+	In the first one, the initial temperature ($T^0$) of the extractor and the inlet temperature ($T^{in}$) are decision variables in the optimization.
+At the same time, the pressure is assumed to be constant during the whole experiment.
 It is considered that the initial state is isothermal, so $T^0=T^{in}(t=0)$.
-The inlet temperature is changed every 5 minutes, and considered to be constant inside of this time period.
-Considering that the residence time in the extractor is around 20-25 minutes (depending on the operating conditions), it is assumed that there is no change in the inlet temperature in the last 25 minutes of extraction, so the extractor becomes isothermal at the end of the experiment.
+The inlet temperature is changed every 5 minutes and is considered constant inside this time period (piecewise constant controls).
+The residence time in the extractor is approximately 20-25 minutes (depending on the operating conditions).
+It is assumed that there is no change in the inlet temperature in the last 25 minutes of extraction, so the extractor becomes isothermal at the end of the experiment.
 The lower ($40^\circ C$) and upper ($50^\circ C$) bounds for the temperature are limits of the previous experiments (${\color{red}article~1}$).
-The general formulation of the optimal design of experiment problem is presented below.
+The general formulation of the optimal design of the experiment problem is presented below.
 
@@
 		\begin{aligned} 
-			&\Xi^* &= \arg \min_{ T^0, T^{in} \in \Xi} -j_D(\Xi,y)  \\
+			&\Xi^* &= \arg \min_{ T^0, T^{in} \in \Xi} \int_{t_0}^{t_f} - \ln j_D(\Xi,y(g(x(t)))) dt  \\
 			&\text{subject to}
-			& \dot{x} = f(x,t,\theta;\Xi) \\
+			& \dot{x} = G(x,t,\theta;\Xi) \\
 			&& \dot{y} = g(x(t)) \\
 			&& 40^\circ C \leq T^{in}(t) \leq 50^\circ C \\
+			&& P(t) = 250 \text{bar} \\
 			&& T^{0} = T^{in}(t=0) \\
+			&& t_0=0~[min] \\
+			&& t_f=150~[min] \\
 		\end{aligned}
@@
 
-	The non-linear optimization problem is solved by applying single-shooting to obtain the trajectory under assumption of piece-wise constant controls.
-The CasADi framework is used as the interface for the IPOPT solver.
-Each simulation problem is solved multiple time starting from different initial points and the solution with the best score is consider as the optimal solution.
+	The second experiment strategy uses pressure as the decision variable.
+Contrary to the previous cases, the pressure change affects the temperature inside the extractor.
+It is expected to observe the heat front propagation along the system if the inlet temperature is kept at a constant value (for example, using a heat exchanger).
+Such a configuration leads to a more complex system response than in the first case.
+In contrary to the real system, the model assumes instantaneous pressure change.
+Depressurization in experimental systems is a rapid process, and such a simplification is acceptable.
+The pressure build-up is a slower process than the depressurization and requires more effort from the experimenter.
+To take it into account, it is assumed that the pressure can be changed less frequently than the inlet temperature in the previous case.
+The model parameters, the extraction time (150 minutes) and the sampling time (5 minutes), stay the same, but the pressure changes every 15 minutes (compared to 5 minutes in the first case).
+Initially, the extractor is kept at a constant temperature of $45 ^\circ C$, which is in the middle of the previously investigated domain.
+The inlet temperature is also kept at $45^\circ C$.
+The state constraints are included to ensure the pressure manipulation does not move the extractor temperature outside the confidence interval.
+The pressure can be manipulated in the range from $200$ bar to $300$ bar.
+The general formulation of the optimal design of the experiment problem is presented below.
+
+	{\footnotesize
+		\begin{equation}
+			\begin{aligned} 
+				&\Xi^* &= \arg \min_{ P \in \Xi} \int_{t_0}^{t_f} - \ln j_D(\Xi,y(g(x(t)))) dt  \\
+				&\text{subject to}
+				& \dot{x} = G(x,t,\theta;\Xi) \\
+				&& \dot{y} = g(x(t)) \\
+				&& 200 \text{bar} \leq P(t) \leq 300 \text{bar} \\
+				&& 40^\circ C \leq T(t,x) \leq 50^\circ C \\
+				&& T^{in} = 45 ^\circ C \\
+				&& t_0=0~[min] \\
+				&& t_f=150~[min] \\
+			\end{aligned}
+	\end{equation} }
+
 \end{document}

### 2024-01-24 SFE_article_Design_of_Experiment/Sections/Results_DOE.tex
24.01

\documentclass[../Article_Design_of_Experiment.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Results}

	Both non-linear optimization problems are solved by applying a single-shooting technique to obtain the trajectory under the assumption of piece-wise constant controls. The CasADi framework is used as the interface for the IPOPT solver. Each simulation problem is solved multiple times, starting from different initial points, and the solution with the best score is considered the optimal solution.

	The first optimization problem was solved 69 times, starting from random initial guesses for the inlet temperature profile. The initial and final values of the objective function for each optimization are presented in Figure \ref{fig:DOE_T_OBJ}. It can be observed that multiple local minima are presented in the Figure. The global solution is selected from all the local solutions as the smallest local minima.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 3cm 1cm 0.5cm 2cm,clip,width=\columnwidth]{/Results_sensitivity/Multiple_shot_DOE_P250.pdf}
		\caption{Solution to the first DOE}
		\label{fig:DOE_T_OBJ}
	\end{figure}

	The inlet temperature profile, which corresponds to the solution of the first optimization problem, is presented in Figure \ref{fig:DOE_T_IN}. The general shape of the inlet temperature profile is similar to a square wave, with the second wave being wider than the first. The maximum and the minimum values correspond to the upper and the lower constraints for the inlet temperature. The similarity with a bang-bang controller should be mentioned, although the second wave has two intermediate values between the bounds.

	Figure \ref{fig:DOE_T_OUT} shows the temperature profile at outlet of the extractor. The outlet profile differs from the inlet profile due to heat diffusion.

	\begin{figure}[h!]
		\centering
		\begin{subfigure}[b]{0.49\columnwidth}
			\centering
			\includegraphics[trim = 1cm 1cm 2.5cm 2.0cm,clip,width=\columnwidth]{/Results_sensitivity/Best_T_in_P250.pdf}
			\caption{Inlet temperature profile}
			\label{fig:DOE_T_IN}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.49\columnwidth}
			\centering
			\includegraphics[trim = 1cm 1cm 2.5cm 2.0cm,clip,width=\columnwidth]{/Results_sensitivity/Best_T_out_P250.pdf}
			\caption{Outlet temperature profile}
			\label{fig:DOE_T_OUT}
		\end{subfigure}
		\caption{Global solution to the first optimization problem}
		\label{fig:DOE_T}
	\end{figure}

\end{document}

### 2024-01-28 SFE_DOE_Model_Discriminant/Reconstruct_T_from_enthalpy.m
29.01

@@ -1,0 +1,54 @@
+function [T] = Reconstruct_T_from_enthalpy(h, P, theta)
+
+    %addpath('C:\dev\casadi-windows-matlabR2016a-v3.5.2');
+    %addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi');
+    import casadi.*
+
+    if class(P)=="double"
+         % Create symbolic temperature
+        T_s             = MX.sym('T_s'  ,length(h)    ,1);
+    
+        % Based on symbolic T and know P calulate symbolic enthalpy h
+        Z               = Compressibility( T_s, P,         theta );
+        rho             = rhoPB_Comp(      T_s, P, Z,      theta );
+        h_sym           = rho.*SpecificEnthalpy(T_s, P, Z, rho, theta);
+        
+        % Create function which compare the difference between symbolic h and
+        % real h
+        H               = h - h_sym;
+        
+        % Set a rootfinder to make the difference between h and h_sym goes to
+        % zero
+        g               = Function('g',{T_s},{H});
+        G               = rootfinder('G','newton',g);
+        
+        % Guess value of T and use rootfinder
+        T               = G(40+273);
+
+    else
+
+        % Create symbolic temperature
+        THETA           = MX.sym('THETA',length(theta)  );
+        H_s             = MX.sym('H_s'  ,length(h)      );
+        P_s             = MX.sym('P_s'  ,length(P)      );
+        T_s             = MX.sym('T_s'  ,length(h)    ,1);
+    
+        % Based on symbolic T and know P calulate symbolic enthalpy h
+        Z               = Compressibility( T_s, P_s,         THETA );
+        rho             = rhoPB_Comp(      T_s, P_s, Z,      THETA );
+        h_sym           = rho.*SpecificEnthalpy(T_s, P_s, Z, rho, THETA );
+        
+        % Create function which compare the difference between symbolic h and
+        % real h
+        H               = H_s - h_sym;
+        
+        % Set a rootfinder to make the difference between h and h_sym goes to
+        % zero
+        g               = Function('g',{T_s,P_s,H_s,THETA},{H});
+        G               = rootfinder('G','newton',g);
+        
+        % Guess value of T and use rootfinder
+        T               = G(40+273, P, h, theta);
+        
+    end
+end

### 2024-01-28 SFE_DOE_Model_Discriminant/modelSFE_BIC.m

@@ -1,0 +1,138 @@
+function xdot = modelSFE(x, p, mask, dt)
+    % (t, x, u, parameters)
+    % Model with (F)luid, (S)olid, (T)emperature
+    % Di is a function of temperature (T), the function works with numbers,
+    % vectors of numbers and vectors of symbolic variables
+    % Rho (Peng-Robinson) are constant numbers
+
+    %% Load Paramters
+    T_u           =     p{1};
+    P_u           =     p{2};
+    F_u           =     p{3};
+
+    parameters    =     p(4:end);
+
+    %nstages       =     parameters{1};
+    %C0solid       =     parameters{2};     % Extractor initial concentration of extract
+%    r             =     parameters{3};     % Extractor length (m)
+    epsi          =     parameters{4};     % Void bed fraction
+    dp            =     parameters{5};     % Diameter of the particle (m)
+    L             =     parameters{6};     % Length of the extractor (m)
+%    rho_s         =     parameters{7};     %
+%    mode          =     parameters{8};
+%    mi            =     parameters{9};
+
+    K1            =     parameters{44};     
+    K2            =     parameters{45};      
+    Di1           =     parameters{46};
+    Di2           =     parameters{47};
+
+    nstages_index =     numel(mask);
+    
+    %% Properties of the bed
+%    A             =     pi*r^2 ;       % Cross-section of the extractor (m^2)
+%    rp            =     dp / 2;
+%    lp2           =     (rp / 3)^2;
+
+    %% States
+    FLUID         =     x(0*nstages_index+1:1*nstages_index);
+    SOLID_B       =     x(1*nstages_index+1:2*nstages_index);
+    SOLID_I       =     x(2*nstages_index+1:3*nstages_index);
+    ENTHALPY_RHO  =     x(3*nstages_index+1:4*nstages_index);
+    PRESSURE      =     x(4*nstages_index+1);
+
+    TEMP          =     Reconstruct_T_from_enthalpy(ENTHALPY_RHO, PRESSURE, parameters);
+      
+    %Properties of the fluid in the extractor
+    Z             =     Compressibility(TEMP, PRESSURE,    parameters);
+
+    RHO           =     rhoPB_Comp(     TEMP, PRESSURE, Z, parameters);   
+    VELOCITY      =     Velocity(F_u, mean([RHO(2:19:end)]), parameters) .* ones(nstages_index,1);
+    
+    %% Thermal Properties
[…]

### 2024-02-06 SFE_DOE_Model_Discriminant/Notes/template_Scrartcl.tex
29.01
06.02

--- 2023-12-03 SFE_Design_of_Experiment/Notes/template_Scrartcl.tex
@@
 \usepackage{tikz}
+\usepackage{subcaption}
 
 %opening
-\title{Optimal design of experiment}
+\title{Optimal design of experiment for model discrimination}
 \author{Oliwer Sliczniuk}
@@
 \begin{abstract}
-Notes about the optimal design of an experiment
+Notes about the optimal model discrimination
 \end{abstract}
@@
 
-\section{Maximum likelihood}
-Let $y^s$ be the vector of all experimental results (random vector) to be used to estimate $p$ and $y^m(p)$.
-The vector of the corresponding quantities computed by the model $\dot{x}=f(t,x,p)$.
-For a parallel model, the parameters of which are to be estimated from measurements of an output vector $\dot{y}=g(x)$.
-We shall call any optimizer of $j$, i.e., any $\hat{p}$ that corresponds to an optimal value of the cost function $j$, an estimate of $p$ in the sense of $j$.
+\section{Model discrimination}
 
-The vector $\hat{p}_{ml}$ will be a maximum-likelihood estimate if it maximizes the cost function:
+Let's consider two probability distributions $p(y_1)$ and $p(y_2)$ where each represents the Gaussian probability density function for a model.
 
 \begin{equation}
-	j_{ml} = \pi_y (y^s|p) 
+	p(Y|y_1) = \prod_{i=1}^{n_t} \frac{1}{\sqrt{2\pi\sigma_1^2}} \exp \left( \frac{\sum \left(Y - y_1(t,x,p)\right)^2}{2\sigma_1^2} \right)
 \end{equation}
 
-If $p$ were fixed, $\pi_y(y^s|p)$ would be the probability density of the random vector $y^s$ generated by a model with parameters $p$.
-Here, to the contrary, $y^s$ is fixed and corresponds to the observations.
-Considered as a function of $p$, $\pi_y(y^s|p)$ is then called the likelihood of $y^s$.
-The maximum-likelihood method looks for the parameter vector $p$ value that gives the observed data the highest likelihood.
-In practice, it is often easier to look for $\hat{p}_{ml}$ by maximizing the log-likelihood function, yielding the same estimate since the logarithm function is monotonically increasing.
+If the ratio of two probability distributions is considered to indicate the measure of similarity, then $\ln \left(\frac{p(Y|y_1)}{p(Y|y_2)}\right)$ becomes a measure of the odds in favour of choosing hypothesis $H_1$ ($p(Y|y_1)$ is a true model) over hypothesis $H_2$ ($p(Y|y_2)$ is a true model).
+Alternatively, the ratio can be interpreted as the information in favour of hypothesis $H_1$ as opposed to the hypothesis $H_2$.
+The so-called 'weight of evidence' or expected information in favour of choosing $H_1$ over $H_2$ can be defined through the Kullback–Leibler divergence and is represented by:
 
 \begin{equation}
-	j_{ml} = \ln ( \pi_y (y^s|p) )
+	I(1:2) = \int_{-\infty}^{\infty} p(Y|y_1) \ln \left(\frac{p(Y|y_1)}{p(Y|y_2)}\right) dY 
 \end{equation}
 
-Assume that the observed outputs satisfy
+The above equation can be written more explicitly as
+
+\begin{align}
+	I(1:2) &= \int_{-\infty}^{\infty} p(Y|y_1) \left[ \sum_{i=1}^{n_t} \left( \ln\left( \frac{\sigma_2}{\sigma_1} \right) - \frac{(Y_i - y_{1i})^2}{2\sigma_1^2} + \frac{(Y_i - y_{2i})^2}{2\sigma_2^2}\right) \right] dY \nonumber \\
+	&= \sum_{i=1}^{n_t} \int_{-\infty}^{\infty} \left( p(Y|y_1) \ln\left(\frac{\sigma_2}{\sigma_1}\right) \right) dY - \sum_{i=1}^{n_t} \int_{-\infty}^{\infty} \left( p(Y|y_1) \frac{(Y_i-y_{1i})^2}{2\sigma_1^2} \right) dY \nonumber \\
+	&+ \sum_{i=1}^{n_t} \int_{-\infty}^{\infty} \left( p(Y|y_1) \frac{(Y_i-y_{2i})^2}{2\sigma_2^2}  \right) dY
+\end{align}
+
+As the expected error is constant for all the measurements: $\mathbb{E}[(Y_i-y_{1i})^2]=\mathbb{E}[\sigma_1^2]$, which simplifies the equation:
+
+\begin{align}
+	I(1:2) &= \sum_{i=1}^{n_t} \int_{-\infty}^{\infty} \left( p(Y|y_1) \ln \left(\frac{\sigma_2}{\sigma_1} \right) \right) dY - \sum_{i=1}^{n_t} \int_{-\infty}^{\infty} \left( \frac{1}{2} p(Y|y_1) \right) dY \nonumber \\
+	&+ \sum_{i=1}^{n_t} \int_{-\infty}^{\infty} \left( p(Y|y_1) \frac{(Y_i-y_{2i})^2}{2\sigma_2^2}  \right) dY
+\end{align}
+
+The first two terms can be simplified by taking a constant in front of integrals and by noticing that $\int p(x) dx = 1$.
 
 \begin{equation}
-	y(t_i) = y^m(t_i, p^*) + \epsilon_i, \qquad i=1,...,n_t
+	I(1:2) = n_t \ln \left(\frac{\sigma_2}{\sigma_1} \right) - \frac{n_t}{2} + \sum_{i=1}^{n_t} \frac{1}{2\sigma_2^2} \int_{-\infty}^{\infty} \left( p(Y|y_1) \left( Y_i^2 - 2Y_iy_{2i} + y_{2i}^2 \right)  \right) dY
 \end{equation}
 
-where the vector $y^m(t_i.
-p^*)$ is the output of a deterministic model, $p^*$ is the true value of the parameter vector, and $\epsilon_i$ belongs to a sequence of independent random variables with probability density $\pi_{\epsilon}(\epsilon_i)$.
-Since the $\epsilon_i$ are independent
+\begin{align}
+	I(1:2) &= n_t \ln \left(\frac{\sigma_2}{\sigma_1} \right) - \frac{n_t}{2} + \sum_{i=1}^{n_t} \frac{1}{2\sigma_2^2} \int_{-\infty}^{\infty} \left( p(Y|y_1) \times Y_i^2  \right) dY \nonumber \\ 
+	&-\sum_{i=1}^{n_t} \frac{2y_{2i}}{2\sigma_2^2} \underbrace{\int_{-\infty}^{\infty} \left( p(Y|y_1) \times Y_i  \right) dY}_{\text{expected value} = y_{1i} } +\sum_{i=1}^{n_t} \frac{y_{2i}^2}{2\sigma_2^2} \underbrace{\int_{-\infty}^{\infty} p(Y|y_1) dY}_{=1}
+\end{align}
+
+The remaining integral can be solved by recognizing that $\sigma^2 = \int_{-\infty}^{\infty} X^2 p(X) dX - \mathbb{E}[(X)]^2$, which leads to $\int_{-\infty}^{\infty} Y_i^2 p(Y|y_{1i}) dY = y_{1i}^2 + \sigma_1^2$.
+
+The final form of the Kullback–Leibler divergence becomes:
+
+\begin{align}
+	I(1:2) &= n_t \ln \left(\frac{\sigma_2}{\sigma_1} \right) - \frac{n_t}{2} + \sum_{i=1}^{n_t} \frac{y_{1i}^2 + \sigma_1^2}{2\sigma_2^2} \sum_{i=1}^{n_t} \frac{2y_{2i}y_{1i}}{2\sigma_2^2} +\sum_{i=1}^{n_t}  \frac{y_{2i}^2}{2\sigma_2^2} \nonumber \\
+	&= n_t \ln \left(\frac{\sigma_2}{\sigma_1} \right) - \frac{n_t}{2} + \frac{n_t}{2\sigma_1^2} + \sum_{i=1}^{n_t} \frac{1}{\sigma_2^2} \left( y_{1i} - y_{2i} \right)^2 \\
+	I(2:1) &= n_t \ln \left(\frac{\sigma_1}{\sigma_2} \right) - \frac{n_t}{2} + \frac{n_t}{2\sigma_2^2} + \sum_{i=1}^{n_t} \frac{1}{2\sigma_1^2} \left( y_{1i} - y_{2i} \right)^2
+\end{align}
+
+While Kulback-Liebler divergence is a statistical distance, it is not a metric on the space of probability distributions.
+While metrics are symmetric and generalize linear distance, satisfying the triangle inequality, divergences are asymmetric in general and generalize squared distance.
+In general, $I(1:2)\neq I(2:1)$.
+By taking into account that the Kullbacl-Liebler divergence is additive for independent distribution, the function J for model discrimination can be defined as
+
+\begin{align}
+	J(1,2) &= I(1:2) + I(2:1) = \int_{-\infty}^{\infty} [p(Y|y_2) - p(Y|y_1)] \ln \frac{p(Y|y_1)}{p(Y|y_2)} dy \nonumber \\
+	&= \frac{n_t(\sigma_1^2-\sigma_2^2)}{2\sigma_1^2\sigma_2^2} + \frac{\sigma_1^2+\sigma_2^2}{2\sigma_1\sigma_2}\times \sum_{i=1}^{n_t} \left( y_{1i}-y_{2i} \right)^2
+\end{align}
+
+The first term of J is independent of changes in $y_{1}$ and $y_{2}$, while the second term is equivalent to the sum of squared differences between two model outputs.
+By maximizing J, the $y_1$ and $y_2$ are spread apart.
+Although both models were fitted with the same dataset, they employ structurally different extraction kinetic terms.
+These structural differences lead to different outputs, particularly in regions not covered by the dataset.
+In this work, both models can be manipulated by flow rate, inlet temperature and pressure to find the dynamic operating conditions such that model outputs that differ from each other the most.
+The optimization problem can be formulated as follow
 
 \begin{equation}
-	\pi_{\epsilon}(\epsilon_1, \epsilon_2, ..., \epsilon_{n_t}) = \prod_{i=1}^{n_t} \pi_{\epsilon_i}(\epsilon_i)
+	\begin{aligned} \label{EQ: Optimization_formulation_MLE}
+		\hat{{\color{black} \theta}}_{MLE} = &\arg \max_{F, T_{in}, P} J(y_1(t,x_1,u), y_2(t,x_2,u)) \\
+		 \textrm{s.t.} \quad \dot{x}_1 &= {\color{black}G_1}(x_1(t);u) \\
+		 \dot{x}_2 &= {\color{black}G_2}(x_2(t);u) \\
+		 y_1 &= g_1(t,x_1) \\
+		 y_2 &= g_2(t,x_2) \\
+		 1.67 \times 10^{-5} &\leq F \leq 6.67 \times 10^{-5}  \\
+		 30^\circ C &\leq T_{in} \leq 40^\circ C \\
+		 100~\text{bar} &\leq T_{in} \leq 200~\text{bar}
+	\end{aligned}
 \end{equation}
 
-Consider the output error
-
-\begin{equation}
-	e^y(t_i, p) = y(t_i) - y^m(t_i, p)
-\end{equation}
-
-For the true value of the parameters, it satisfies $e^y(t_i, p^*)=\epsilon_i$.
-and, since $y^m$ is deterministic, $\pi_{y_i} (y^s(t_i)|p) = \pi_{\epsilon_i} (e^y(t_i)|p)$.
-The likelihood of the $n_t$ observations can be written as
-
-\begin{equation}
-	\pi_y (y^s|p) = \prod_{i=1}^{n_t} \pi_{\epsilon_i}(e^y(t_i,p)) =  \prod_{i=1}^{n_t} \pi_{\epsilon_i}(y(t_i) - y^m(t_i, p))
-\end{equation}
-
-If the noise is assumed to follow the normal distribution:
-
-\begin{equation}
-	\pi_y (y^s|p) = \prod_{i=1}^{n_t} \frac{1}{ \sqrt{2\pi\sigma_{t_i}^2} } \exp \left( -\frac{1}{2} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}} \right) \right)
-\end{equation}
-
-The associated log-likelihood can be written as
-
-\begin{equation}
-	\ln (\pi_y (y^s|p)) = (\text{term independent of p}) - \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \right)
-\end{equation}
-
-Its gradient is thus
-
-\begin{equation}
-	\frac{\partial}{\partial p} \ln (\pi_y (y^s|p)) =  \frac{1}{2} \sum_{i=1}^{n_t}  \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p} \right)
-\end{equation}
-
-\section{Fisher information}
-
-The Fisher information is a way of measuring the amount of information that an observable random variable carries about an unknown parameter of a distribution that models the random variable.
-The Fisher information is related to the second derivative (or the curvature) of the log-likelihood function with respect to the parameter.
-This relationship provides a measure of how "sensitive" the likelihood is to changes in the parameter value.
-The Fisher information matrix can be calculated as follow.
-
-\begin{align}
-	F(p) &= - \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial^2 \ln (\pi_y (y^s|p))}{\partial p \partial p^T} \right] = \mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial \ln (\pi_y (y^s|p))}{\partial p} \frac{\partial \ln (\pi_y (y^s|p))}{\partial p^T} \right] \\
-	&= \mathop{\mathbb{E}}_{y^s|p} \left[ \sum_{k=1}^{n_t} \left( \frac{y(t_k) - y^m(t_k, p)}{\sigma_{t_k}^2} \frac{\partial y^m(t_k, p)}{\partial p} \right) \times  \sum_{i=1}^{n_t} \left( \frac{y(t_i) - y^m(t_i, p)}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p^T} \right) \right]
-\end{align}
-
-Since
-
-\begin{equation}
-	\mathop{\mathbb{E}}_{y^s|p} \left[ \left( y(t_i) - y^m(t_k, p) \right) \left( y(t_i) - y^m(t_i, p) \right) \right] = \sigma_{t_i}^2 \delta_{ik}
-\end{equation}
-
-one gets
-
-\begin{equation}
-	F(p) = \sum_{i=1}^{n_t} \left( \frac{1}{\sigma_{t_i}^2} \frac{\partial y^m(t_i, p)}{\partial p} \frac{\partial y^m(t_i, p)}{\partial p^T} \right)
-\end{equation}
-
-If every experiment at time $t_i$ is independent and characterized by its own $\sigma_{t_i}$, then the Fisher information matrix can be presented in the more compact way:
-
-\begin{equation}
-	F(p) = \frac{\partial y^m(t, p)}{\partial p} \text{diag}\left(\frac{1}{\sigma_{t}^2}\right) \frac{\partial y^m(t, p)}{\partial p^T} 
-\end{equation}
-
-\section{Cramer-Rao inequality}
-
-Let $\hat{p}$ be an (absolutely) unbiased estimator $p^*$, i.e. such that which amounts to saying that if it were possible to replicate the same experiment and
-estimate $\hat{p}$ an infinite number of times, the mean of the estimates would coincide with the true value.
-Let $P$ be the covariance matrix of this estimator.
-Since $\hat{p}$ is unbiased, $P$ can be written as
-
-\begin{equation}
-	P = \mathop{\mathbb{E}}_{y^s|p^*} \left[ \left( \hat{p}(y^s) - p^* \right) \left( \hat{p}(y^s) - p^* \right)^T \right]
-\end{equation}
-
-which quantifies how the estimates are spread around the true value $p^*$.
-One would like the estimates to be as concentrated as possible around this true value, of course.
-An estimator $\hat{p}_1$ with covariance matrix $P_1$ is said to be more efficient than an estimator $\hat{p}_2$ with covariance matrix $P_2$ if $P_1 < P_2$, that is if $P_2 - P_1$ is positive-definite (i.e.if all the eigenvalues of $P_2-P_1$ arc strictly positive).
-Since estimators with high efficiency are desirable, a natural request is to make P as small as possible.
-The Cramer-Rao inequality provides a lower bound to what can be achieved.
-
-Under the hypotheses that:
-
-\begin{itemize}
-	\item the set of all data vectors $y^s$ with $\pi_y(y^s|p) > 0$ does not depend on $p$
-	\item $\frac{\partial \pi_y(y^s|p)}{\partial p_i}~\left(i=1,2,...,n_p\right)$ is absolutely integrable
-	\item $\mathop{\mathbb{E}}_{y^s|p} \left[ \frac{\partial \ln (\pi_y (y^s|p))}{\partial p} \frac{\partial \ln (\pi_y (y^s|p))}{\partial p^T} \right]$ exists and is invertible
-\end{itemize}
-
-the covariance of any absolutely unbiased estimator satisfies
-
-\begin{equation}
-	P \geq F^{-1}(p^*)
-\end{equation}
-
-In other words, the precision to which we can estimate $p$ is fundamentally limited by the Fisher information of the likelihood function.
-Based on the Cramer-Rao inequality, the Fisher information matrix can used to calculate the covariance matrices associated with maximum-likelihood estimates.
-
-\section{Optimal experimental design}
-
-The optimal design of experiments (DOE) is a statistical concept that refers to the process of planning an experiment, which allow parameters to be estimated without bias and with minimum variance.
-Optimal design ensures that the experiment can provide the most informative data possible.
-This often involves balancing the study of main effects and interactions between factors.
-Moreover, by efficiently planning experiments, optimal design aims to reduce the overall resources required, such as time, materials, and manpower.
-
-The methodology for data to estimate the parameters of a specific model is influenced by a series of qualitative decisions made throughout the experimental and modelling process, such as: a model structure, a location of sensors or an equipment.
-Once these choices have been made, the experimenter still has some freedom to specify the quantitative experimental conditions (such as temperature, pressure, sampling times, etc.).
-Experiment design aims to determine experimental conditions adapted to the final purpose of the modeling.
-
-%Assume that the i'th scalar observation can be written as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ (the i'th support point) describes the experimental conditions (e.g., measurement time, the shape of input, etc.) under which the i'th observation is to be collected.
-When $n_t$ such observations are taken, the concatenation of the vectors $\xi_i$'s yields the $\Xi = (\xi_1, \xi_2,..., \xi_{n_t})$, which characterizes all experimental conditions to be optimized.
-To make the experiment design realistic, it is necessary to consider several constraints, e.g., the experiments' duration, the inlet stream's temperature, and the minimum time between samples.
-Let $\bar{\Xi}$ be the set of all feasible values for $\Xi$.
-
-Let's consider that each scalar observation in our study can be expressed as $y(\xi_i)$, where the $n_\xi$-dimensional vector $\xi_i$ representing the specific experimental conditions (such as the timing of measurements, operating conditions, etc.) under which the i'th observation is gathered.
-When collecting $n_t$ such observations, the assembly of these $\xi_i$ vectors forms the matrix $\Xi = (\xi_1, \xi_2,..., \xi_{n_t})$, which combine all the experimental conditions that need optimization.
-In order to align the design of the experiment with practical realities, it's important to take into account various constraints, such as the total duration of the experiments, the maximum temperature of the inlet stream, and the minimum interval between sampling events.
-The set of all possible combinations for $\bar{\Xi}$ that adhere to these constraints is denoted as $\Xi$.
-
-%The definition of a cost function $j$ then permits the optimal experiment design to be cast as a constrained optimization problem, where the optimal experiment $\Xi^*$ is defined by
-
-The formulation of a cost function $j$ allows for the framing of optimal experiment design as a problem of constrained optimization. In this context, the optimal experiment, denoted as $\Xi^*$:
-
-\begin{equation}
-	\Xi^* = \arg~\underset{\Xi \in \bar{\Xi}}{\text{opt}}~j\left(\Xi\right)
-\end{equation}
-
-The cost function should describe the amount of information from an experiment.
-For that purpose it can be assumed a function $\phi$ can be related to the Fisher information obtained an arbitrary operating conditions.
-
-\begin{equation}
-	j(\Xi) = \phi\left[ F(p, \Xi) \right]
-\end{equation}
-
-%Under the hypotheses mentioned above, the distribution of the maximum likelihood estimator is asymptotically Gaussian $\mathop{\mathbb{N}} (p^*, F^{-1}([^*, \Xi])) $ when the number of measurements tends to infinity.
-Minimizing $j(\Xi)$ then amounts to minimizing a scalar measure of the asymptotic covariance matrix of the parameters.
-
-A general class of optimality criteria for DOE is given by
-
-\begin{align}
-	\phi_k(F) &= \left[\frac{1}{n_p} \text{trace}\left( QF^{-1}Q^T \right)^k \right]^{1/k} \quad &if \det F \neq 0 \nonumber \\
-	\phi_k(F) &= \infty \quad &if \det F = 0
-\end{align}
-
-where $Q$ is a weighting matrix. The special case $k = 1$ corresponds to the L-optimality cost function,
-
-\begin{equation}
-	j_L(\Xi) = \text{trace} \left[ Q^TQF^{-1}(p,\Xi) \right]
-\end{equation}
-
-and choosing $Q = \textbf{I}_{n_p}$ then corresponds to the A-optimality cost function.
-An A-optimal experiment minimizes the sum of the squares of the lengths or the axes of asymptotic confidence ellipsoids.
-Choosing $Q$ diagonal, with $[Q]_{ii} = 1/p_i$ corresponds to C-optimality, which is connected with the relative precision of estimates.
-Taking Q to be a row vector leads to c-optimality.
-Taking $Q = \textbf{I}_{n_p}$ and $k = \infty$ corresponds to E-optimality; E-optimal design maximizes the smallest eigenvalues of the Fisher information matrix and thus minimizes the length of the largest axis of the asymptotic confidence ellipsoids.
-The most widely used optimality criterion has $k = 0$, $Q = \textbf{I}_{n_p}$ , requiring minimization of $\det F^{-1}(p, \Xi)$, or, equivalently, maximization of
-
-\begin{equation}
-	j_D(\Xi) = \det F(p, \Xi)
-\end{equation}
-
-A D-optimal experiment minimizes the volume of the asymptotic confidence ellipsoids for the parameters.
-The graphical representation of the different optimality conditions is shown in Figure \ref{fig:score_fun}.
-
-\begin{figure}[!h]
-	\centering
-	\resizebox{0.4\textwidth}{!}{%
-	\begin{tikzpicture}
-		% Ellipse parameters
-		\def\ellipsecenter{(3,3)}
-		\def\ellipseA{(0.75,5.25)} % End point for A-optimality arrow
-		\def\ellipseB{(5.13,5.13)} % End point for E-optimality arrow
-		\def\ellipseC{(4,1.2)}      % End point for D-optimality arrow
-
-		% Draw the rotated ellipse
-		\draw[fill=gray!10, draw=black, rotate around={45:\ellipsecenter}] \ellipsecenter ellipse (3cm and 1cm);
-
-		% Draw the dashed rectangle
-		\draw[dashed] (0.75,0.75) rectangle (5.25,5.25);
-
-		% Draw the arrows and label them with adjustable positions
-		\draw [-latex] \ellipsecenter -- \ellipseA node[yshift=-4cm, xshift=2.5cm,rotate around={-45:\ellipsecenter}] {A-optimality};
-		\draw [-latex] \ellipsecenter -- \ellipseB node[yshift=0cm, xshift=-3.9cm,rotate around={45:\ellipsecenter}] {E-optimality};
-		\draw [-latex] \ellipseC -- (2,2) node[yshift=-1cm, xshift=2cm] {D-optimality};
-
-		% Draw axes
-		\draw[thick,->] (0,0) -- (6,0) node[below] {$p_1$};
-		\draw[thick,->] (0,0) -- (0,6) node[left] {$p_2$};
-	\end{tikzpicture}
-	}%
-	\caption{Graphical representation of score functions}
-	\label{fig:score_fun}
-\end{figure}
+By employing the dynamic operating conditions determined by the optimization to the real system and comparing the result of a new experiment with responses from both models, the model discrimination can be concluded.
 

### 2024-02-06 SFE_article_Parameter_Estimation - Chamomile/Sections/Experiments.tex
06.02

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Experiments}

	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile seeds. The experiments were performed by \citet{Povh2001}. To prepare the seeds for extraction, they were first pre-treated using a knife mill (TECNAL, model TE 340) to reduce their particle size. The mean
	particle diameter was determined by the Sauter equation and is equal to $0.3\times 10^{-3}$m. The actual density of the chamomile particles was measured through helium pycnometry at the Institute of Chemistry IQ/Unicamp's Analytical Facilities. The bulk density of the bed was computed based on the feed's mass and the extractor's volume. The total porosity of the bed, including the particles, was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$.

	%The moisture content of the seeds was then determined using an Infrared Moisture Analyser, which revealed an average moisture content of 4.83\% in the solid particles after grinding. Next, the density of the solid material was measured using a pycnometer, which can be found in Appendix \ref{CH: Solid_Density_Measurment}. Finally, the material's porosity was also calculated to be 0.5, as explained in Appendix \ref{CH: Porosity}.

	The experiments were conducted using an extractor with diameter of $3.96\times 10^{-2}$ m and length $16.55\times 10^{-2}$ m. Twelve experiments were performed under different but constant in time operating conditions: $30-40^\circ C$, $100 - 200$ bar, and $1.33-6.66 \times 10^{-5}$ kg/s. The amount of solid material used for extraction was $75\times 10^{-3}$ kg, which was sufficient to fill the whole vessel. Samples were collected every 30 min for the first 3 h and every hour afterwards up to 10 h.

	%After loading the material into the extraction chamber, the extractor was pre-heated to the desired temperature. The outlet line was then closed, and the extraction chamber was filled with $CO_2$. The $CO_2$ was pumped and compressed until the desired operating pressure was reached. When the operating temperature and pressure were achieved, the outlet line was opened, allowing the solvent to flow through the system. The solvent extracted the essential oils from the solid material, and the resulting $CO_2$ and oil mixture flowed from the extractor to the separator. The separator operated at $50^\circ C$ and $50$ bar. The gaseous $CO_2$ exited from the top and was recycled to the $CO_2$ storage tank. The oil stayed at the bottom of the separator in the liquid form. The extraction time for each batch was 150 minutes, measured from the opening of the extractor outlet port. Every 5 minutes, the oil was drained from the separator, and its weight was measured. The resulting time series ${\color{black}Y}(t)$ corresponds to the output of measurement Equation \ref{Model_measurment_1} and can be used for parameter estimation.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
			\caption{Experiment at $40~^\circ C$ and 200 bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
			\caption{Experiment at $50~^\circ C$ and 200 bar}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300.pdf}
			\caption{Experiment at $40~^\circ C$ and 300 bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300.pdf}
			\caption{Experiment at $50~^\circ C$ and 300 bar}
		\end{subfigure}
		\caption{Results of parameter estimation}
		\label{fig: estimation_results}
	\end{figure}

\end{document}

### 2024-02-06 SFE_article_Parameter_Estimation - Chamomile/Sections/Model.tex
06.02

--- 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Model.tex
@@
 				\begin{align} \label{EQ:Enthalpy_equation}
-					&\cfrac{\partial \left({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}h}(t,z) A_f\right)}{\partial t} - \cfrac{\partial \left({\color{black}P}(t) A_f\right)}{\partial t} \nonumber \\
-					&+ \cfrac{\partial \left( {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}h}(t,z) A_f v \right)}{\partial {\color{black}z}} - \cfrac{\partial}{\partial {\color{black}z}} \left( k \cfrac{\partial {\color{black}T}(t,z)}{\partial {\color{black}z}} \right)
+					\cfrac{\partial \left({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}h}(t,z) A_f\right)}{\partial t} &= - \cfrac{\partial \left( {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}h}(t,z) A_f v \right)}{\partial {\color{black}z}}  \nonumber \\
+					& + \cfrac{\partial \left({\color{black}P}(t) A_f\right)}{\partial t} + \cfrac{\partial}{\partial {\color{black}z}} \left( k \cfrac{\partial {\color{black}T}(t,z)}{\partial {\color{black}z}} \right)
 				\end{align}
@@
 		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{black}c_{s0}}$.
-Every SFE system needs some time to reach the desired operating conditions but the solute diffuses from solid phase to the fluid phase already at the preparation stage.
-For instance, a pump introduce more fluid to the extractor to increase the pressure, which makes the fluid present already in that vessel to moves internally hence the solute in the fluid phase is non-uniformly distributed.
-Some conclusions can be drawn from the analysis of the initial part of each yield curve obtained from the laboratory (Figure \ref{fig: estimation_results}).
-It can be noticed that each curve at the beginning has a non-linear curvature.
-A quadratic function could approximate the initial part of each extraction curve.
-A function that, after integration, gives a quadratic-like result is a straight line.
-Based on that observation, the solute concentration in the fluid phase is assumed to be linearly distributed.
-The solute concentration is assumed to be zero at the outlet and reach the maximum at the beginning of the fixed bed.
-The details on the calculation are given in Appendix \ref{CH: IC_BC}.
-The linear distribution $H(z)$ can be defined if the total mass of solute $m_{total}$ and initial mass ratio between solid and fluid phases $\tau$ are known.
+As the residence time is much shorter than the sampling time, the initial state estimate for the concentration of the solute in the fluid phase would be not reliable.
+Considering that it is assumed that the $c_f0=0$.
 Moreover, it is considered that the initial temperature of the extractor in every place is the same and described by ${\color{black}h_0}$.
@@
 		{\footnotesize
-				\begin{equation*}
-					{\color{black}c_f}(t = 0, z) = H(z) \quad {\color{black}c_s}(t = 0, z) = {\color{black}c_{s0}} \quad {\color{black}h}(t = 0, z) = {\color{black}h_0}
-				\end{equation*} }
+				\begin{align*}
+					&{\color{black}c_f}(t = 0, z) = 0 & {\color{black}c_s}(t = 0, z) = {\color{black}c_{s0}} & &{\color{black}h}(t = 0, z) = {\color{black}h_0} \\
+					&\frac{\partial c_f(t,z=L)}{\partial x} = 0 & {\color{black}c_s}(t = 0, z) = {\color{black}c_{s0}} & &\frac{\partial h(t,z=L)}{\partial x} = 0
+				\end{align*} }
 

### 2024-02-06 SFE_article_Parameter_Estimation - Chamomile/Sections/Parameter_estimation.tex
06.02

--- 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Parameter_estimation.tex
@@
 		\begin{equation} \label{EQ: Objective_function}
-			\ln L = -\cfrac{n}{2} \left( \ln \sqrt{2 \pi} + \ln {\color{black} \sigma}^2 \right)
+			\ln L = -\cfrac{n}{2}  \ln \sqrt{2 \pi \sigma^2} 
 			- \cfrac{ \sum_{i=1}^{n} \left[  \cfrac{d {Y}(t_i)}{dt} - \cfrac{d{\color{black}y}({\color{black} \theta}, t_i)}{dt} \right]^2 }{2 {\color{black} \sigma}^2}
@@
 		\item Internal diffusion coefficient: \quad$D_i^R$
-		\item Axial diffusion coefficient: \qquad$D_e^M$
+		%\item Axial diffusion coefficient: \qquad$D_e^M$
 		\item Decay coefficient:\qquad\qquad\qquad$\Upsilon$
 		\item Standard deviation:\qquad\qquad\quad~$\sigma^2$
-		\item Total mass of solute: \qquad\quad\quad$m_{total}$
-		\item Initial mass ratio: \qquad\qquad\qquad$\tau$
 	\end{itemize}
@@
 				\hline 
-				Parameter		&$k_m$[-] 	& $D_i^R$[$m^2/s$] 	& $D_e^M$[$m^2/s$]	& $\Upsilon$ [m$^3$/kg] & $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
-				Lower bound		&0	  		& 0 	  			& 0 				&	0					& 80 		 		& 0 	   		& 0 \\ 
-				Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			&	100					& 150 				& 1 			& $+\infty$ \\ 
-				Initial guess	&1e5 		& 3 	  			& 1 				&	0					& 80 		 		& 0.65 	   		& 0.1 \\  \hline
+				Parameter		&$k_m$[-] 	& $D_i^R\times10^{-13}$[$m^2/s$] 	& $D_e^M$[$m^2/s$]	& $\Upsilon$ [m$^3$/kg] & $\sigma$[-] \\  \hline
+				Lower bound		&0	  		& 0 	  			& 0 				& 0 	   		& 0 \\ 
+				Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			& $+\infty$ 	& $+\infty$\\ 
+				Initial guesses	&0.1-10		& $0.1-10$ 			& 0 		   		& 0.1-10		& 0.01 \\  \hline
 		\end{tabular} }

### 2024-02-06 SFE_article_Parameter_Estimation - Chamomile/Sections/introduction_imp.tex
06.02

--- 2023-10-03 SFE_article_Parameter_Estimation/Sections/introduction_imp.tex
@@
 	This study aims to develop a process model for extracting natural substances from solid materials and liquids using supercritical fluids, specifically supercritical $CO_2$.
-To achieve this, the model parameters are estimated based on thermodynamic relations and a set of experiments conducted at various conditions.
+To achieve this, the solvent properties are estimated based on thermodynamic relations and the extraction kinetic parameters estimated based on a set of experiments conducted at various conditions.
 The maximum likelihood estimator is used to solve the parameter estimation problem, and the obtained parameters are subjected to regression to derive correlations.
@@
 The maximum likelihood technique is presented in Chapter \ref{CH: Parameter_estimation} and is then combined with the process model.
-Chapter \ref{CH: Experiments} describes the experimental work and the data collected from experiments are used to estimate missing parameters related to the extraction kinetic.
+Chapter \ref{CH: Experiments} describes the experimental work and the data collected from experiments, which are used to estimate missing parameters related to the extraction kinetic.
 Finally, the parameter estimations and simulation results are discussed in Chapters \ref{CH: Results} and \ref{CH: Conclusion}

### 2024-02-06 SFE_article_Parameter_Estimation - Chamomile/Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
06.02

--- 2023-12-03 SFE_article_Parameter_Estimation/Supercritical_fluid_extraction_of_essential_oil_from_caraway.tex
@@
 % ===================================================
-\title[mode=title]{Supercritical fluid extraction of essential oil from caraway seeds: experiments, modelling, and parameter estimation}                      
-\shorttitle{Supercritical fluid extraction of essential oil from caraway seeds: experiments, modelling, and parameter estimation}
+\title[mode=title]{Supercritical fluid extraction of essential oil from chamomile seeds: experiments, modelling, and parameter estimation}                      
+\shorttitle{Supercritical fluid extraction of essential oil from chamomile seeds: experiments, modelling, and parameter estimation}
 
@@
 \begin{abstract}
-This study investigated the supercritical extraction process of caraway oil from caraway seeds.
+This study investigated the supercritical extraction process of chamomile oil from chamomile seeds.
 A distributed-parameter model describes the fluid-solid extraction process.
@@
 The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
-Key model parameters included partition factor internal and axial diffusion coefficients.
-These parameters and the initial state were determined using maximum likelihood estimation from experimental data, assuming normal error.
-A set of laboratory experiments was performed in a partially filled extractor with a fixed bed operated under multiple constant operating conditions: $40~^\circ C$ / $200$ bar, $50~^\circ C$ / $200$ bar, $40~^\circ C$ / $300$ bar, and $50~^\circ C$ / $300$ bar.
+Key model parameters included partition factor internal and axial diffusion coefficients were determined using maximum likelihood estimation from experimental data, assuming normal error.
+A set of laboratory experiments was performed in under multiple constant operating conditions: $30 - 40~^\circ C$, $100 - 200$ bar, and $1.33-6.66 \times 10^{-5}$ kg/s.
 
@@
 
-This study presented basic aspects regarding the laboratory work for obtaining caraway extracts using supercritical carbon dioxide at different operating conditions.
+This study presented basic aspects regarding the laboratory work for obtaining chamomile extracts using supercritical carbon dioxide at different operating conditions.
 A first-principle process model was developed based on governing equations.
@@
 
-\subsection{Initial and boundary conditions} \label{CH: IC_BC}
-\subfile{Sections/IC_BC}
+%\subsection{Initial and boundary conditions} \label{CH: IC_BC}
+%\subfile{Sections/IC_BC}
 
@@
 
-\subsection{Solid density measurement} \label{CH: Solid_Density_Measurment}
+%\subsection{Solid density measurement} \label{CH: Solid_Density_Measurment}
 
-Figure \ref{fig:density_cal} shows results of density measurement performed with pycnometer.
+%Figure \ref{fig:density_cal} shows results of density measurement performed with pycnometer.
 
-\begin{figure}[!h]
-	\centering 
-	\includegraphics[trim=2cm 6cm 4cm 0cm, clip,width=\columnwidth]{Sections/ultraReportT5.pdf}
-	\caption{The result of solid density measurement}
-	\label{fig:density_cal}
-\end{figure}
+%\begin{figure}[!h]
+%	\centering 
+%	\includegraphics[trim=2cm 6cm 4cm 0cm, clip,width=\columnwidth]{Sections/ultraReportT5.pdf}
+%	\caption{The result of solid density measurement}
+%	\label{fig:density_cal}
+%\end{figure}
 
-{\footnotesize
-	\begin{equation*}
-		\rho_s^{ave} = \frac{1.2585+1.2582+1.2561+1.2546+1.2555}{5} = 1.25658 [g/cc]
-	\end{equation*}
-}
+%{\footnotesize
+%	\begin{equation*}
+%		\rho_s^{ave} = \frac{1.2585+1.2582+1.2561+1.2546+1.2555}{5} = 1.25658 [g/cc]
+%	\end{equation*}
+%}
 
-\subsection{Porosity calculations} \label{CH: Porosity}
-\subfile{Sections/Porosity}
+%\subsection{Porosity calculations} \label{CH: Porosity}
+%\subfile{Sections/Porosity}
 

### 2024-02-12 SFE_article_Parameter_Estimation - Chamomile/Sections/Experiments.tex
12.02

@@
 
-	\begin{figure}[!h]
-		\centering
-		\begin{subfigure}[b]{\columnwidth}
-			\centering
-			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
-			\caption{Experiment at $40~^\circ C$ and 200 bar}
-		\end{subfigure}
-		\begin{subfigure}[b]{\columnwidth}
-			\centering
-			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
-			\caption{Experiment at $50~^\circ C$ and 200 bar}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[b]{\columnwidth}
-			\centering
-			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300.pdf}
-			\caption{Experiment at $40~^\circ C$ and 300 bar}
-		\end{subfigure}
-		\begin{subfigure}[b]{\columnwidth}
-			\centering
-			\includegraphics[trim = 2cm 10.5cm 2.5cm 1.7cm,clip,width=0.99\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300.pdf}
-			\caption{Experiment at $50~^\circ C$ and 300 bar}
-		\end{subfigure}
-		\caption{Results of parameter estimation}
-		\label{fig: estimation_results}
-	\end{figure}
-
 \end{document}

### 2024-02-12 SFE_article_Parameter_Estimation - Chamomile/Sections/Parameter_estimation.tex
12.02

@@
 		\begin{equation} \label{EQ: Objective_function}
-			\ln L = -\cfrac{n}{2}  \ln \sqrt{2 \pi \sigma^2} 
+			\ln L = -\cfrac{n}{2}  \ln \left(2 \pi \sigma^2\right) 
 			- \cfrac{ \sum_{i=1}^{n} \left[  \cfrac{d {Y}(t_i)}{dt} - \cfrac{d{\color{black}y}({\color{black} \theta}, t_i)}{dt} \right]^2 }{2 {\color{black} \sigma}^2}
@@
 
-	where $\hat{{\color{black} \theta}}$ is as maximum likelihood estimator, ${\color{black} \theta}^{lb}$ define the minimal value of ${\color{black} \theta}$ and ${\color{black} \theta}^{ub}$ is the maximum value of ${\color{black} \theta}$.
+	where $\hat{{\color{black} \theta}}$ is as maximum likelihood estimator, ${\color{black} \theta}^{lb}$ define the minimal value of ${\color{black} \theta}$, ${\color{black} \theta}^{ub}$ is the maximum value of ${\color{black} \theta}$ and $\sigma$ represents the standard deviation of the residuals (errors) between the observed data points and the model outputs.
 
@@
 		\item Internal diffusion coefficient: \quad$D_i^R$
-		%\item Axial diffusion coefficient: \qquad$D_e^M$
+		\item Axial diffusion coefficient: \qquad$D_e^M$
 		\item Decay coefficient:\qquad\qquad\qquad$\Upsilon$
-		\item Standard deviation:\qquad\qquad\quad~$\sigma^2$
+		%\item Standard deviation:\qquad\qquad\quad~$\sigma^2$
 	\end{itemize}
@@
 				\hline 
-				Parameter		&$k_m$[-] 	& $D_i^R\times10^{-13}$[$m^2/s$] 	& $D_e^M$[$m^2/s$]	& $\Upsilon$ [m$^3$/kg] & $\sigma$[-] \\  \hline
-				Lower bound		&0	  		& 0 	  			& 0 				& 0 	   		& 0 \\ 
-				Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			& $+\infty$ 	& $+\infty$\\ 
-				Initial guesses	&0.1-10		& $0.1-10$ 			& 0 		   		& 0.1-10		& 0.01 \\  \hline
+				Parameter		&$k_m$[-] 	& $D_i^R\times10^{-13}$[$m^2/s$] 	& $D_e^M\times10^{-12}$[$m^2/s$]	& $\Upsilon$ [m$^3$/kg] \\  \hline
+				Lower bound		&0	  		& 0 	  			& 0 				& 0 	   		\\ 
+				Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			& $+\infty$ 	\\ 
+				Initial guesses	&0.1-10		& $0.1-10$ 			& 0.1-10   			& 0.1-10		\\  \hline
 		\end{tabular} }

### 2024-02-12 SFE_article_Parameter_Estimation - Chamomile/Sections/Results_Chamomile.tex
12.02

\documentclass[../Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Results}

	The parameter estimation problem was solved multiple time for different initial guesses. Each time-series was fitted to the model separately. First, the model with linear extraction kinetic only was fitted to the dataset. The Figure show the result of parameter estimation for dataset 1, which corresponds to the following operating conditions: 313 K, 100 bar and 6.57$\times 10^{-5}$ kg/s.

	\begin{figure}[!h]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_Space_Linear_Dataset_1.png}
		\caption{Parameter space for the linear extraction kinetic model and the experiment 1}
		\label{fig: Fit_1_linear}
	\end{figure}

	In case of the linear kinetic two parameter are unknown, namely partition coefficient $k_m$ and the internal diffusion coefficient $D_i$. Figure \ref{fig: Fit_1_linear} shows the parameter space and corresponding values of the cost function. As the cost function is to be minimized, the lowest value of $-\ln(L)$ indicate the best fit. A black stripe around $D_i \approx 0.2)$ can be observed. That stripe indicate existence of optimal value of the $D_i$. In direction of $k_m$, the cost function is almost flat, which suggest that any value of $k_m$ above approximately 0.1 is equally good for fitting. If $k_m$ can be arbitrary point, then it can grow to the infinity. The optimizer found optimal values of the partition factors at relatively high levels. Such a behaviour suggest that the solvent is far from the saturation, and the model can be simplified. The model reduction can be introduced by considering the limit of $k_m$ in the extraction kinetic term:

	{\footnotesize
		\begin{equation*}
			\begin{split}
				&\lim_{k_m \rightarrow \infty} \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right)  = \\
				&= \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{\infty{\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right) = \left({\color{black}{\color{black} c_s} }(t,z) - 0 \right)
			\end{split}
	\end{equation*} }

	The extraction model can be modified to account for the reduced kinetic term and the axial diffusion. In such a configuration just two parameters are unknown, namely internal diffusion coefficient $D_i$ and axial diffusion coefficient $D_e^M$. Figure \ref{fig: Fit_1_Di_Dx} shows the parameter space and corresponding values of the cost function.

	\begin{figure}[!h]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_Space_Di_Dx_Dataset_1.png}
		\caption{Parameter space for the reduced linear extraction kinetic model with and the experiment 1}
		\label{fig: Fit_1_Di_Dx}
	\end{figure}

	Similarly to the previous case, the optimal value of $D_i$ exist, but a unique value for the $D_e^M$ cannot be determined. A little influence of the axial diffusion coefficient can be observed on Figure \ref{fig: Fit_1_Di_Dx} in a width range of values. By selecting $D_e^M$ such it has a low value, the axial diffusion term can be reduced and removed from the model without lost of generality.

	I both cases discussed above, none of the results of the fitting was not sufficient due to high or to low extraction kinetic. Following the idea behind the Broken-and-Intact and Shrinking Core models (presented in Chapter \ref{CH: Gamma_Function}), the gamma function is introduced to account for the decaying extraction kinetic. The proposed correction factor is combined with the reduced linear model, which leads to a two-parameter ($D_i^R$ and $\Upsilon$) defined by Equation \ref{Model_kinetic}. The Figure \ref{fig: Fit_1_Di_Dx} shows the parameter space with and the corresponding values of the cost function.

	\begin{figure}[!h]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
		\caption{Parameter space for the modified extraction model and experiment 1}
		\label{fig: Fit_1_Di_Gamma}
	\end{figure}

	The parameter space of the modified model is characterized by the unique minimum value, which corresponds to the solution of the parameter estimation problem for the experiment 1. The red circle shows the minimum value of the cost function found by the optimizer.

	The remaining experiments are fitted to the modified extraction model in the same way. The results of the parameter estimation for experiments at constant flow rate of $6.67\times 10^{-5}$ [kg/s] and constant temperature of 313 [K] are presented in Figure \ref{fig: Fit_1_4_Di_Dx}.

	\begin{figure}[!h]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and constant temperature of 313 [K]}
		\label{fig: Fit_1_4_Di_Dx}
	\end{figure}

	\begin{figure}[!h]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and constant temperature of 303 [K]}
		\label{fig: Fit_5_8_Di_Dx}
	\end{figure}

	\begin{figure}[!h]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
		\caption{Results of parameter estimation for experiments at $3.34\times 10^{-5}$ [kg/s]}
		\label{fig: Fit_9_12_Di_Dx}
	\end{figure}

\end{document}

### 2024-02-12 SFE_article_Parameter_Estimation - Chamomile/Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
12.02

@@
 \section{Results}
-\subfile{Sections/Results}
+\subfile{Sections/Results_Chamomile}
 
@@
 
-This study presented basic aspects regarding the laboratory work for obtaining chamomile extracts using supercritical carbon dioxide at different operating conditions.
+%This study presented basic aspects regarding the laboratory work for obtaining chamomile extracts using supercritical carbon dioxide at different operating conditions.
 A first-principle process model was developed based on governing equations.

### 2024-02-12 SFE_Parameter_Estimation_Chamomile/main_Parameter_Estimation_Chamomile.m

@@ -2,44 +2,53 @@ startup;
 delete(gcp('nocreate'));
 % %p = Pushbullet(pushbullet_api);
 
-addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
-%addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
 import casadi.*
 
+excel_file = 'Chamomile_Di_Gamma_org.xls';
+rng(69)
+
+%%
 Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
 Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
 
 LabResults              = xlsread('wpd_datasets.xlsx');
 
-Iteration_max           = 30;                                           % Maximum number of iterations for optimzer
-Time_max                = 12;                                             % Maximum time of optimization in [h]
+N_trial                 = 1;
+Iteration_max           = 20;                                              % Maximum number of iterations for optimzer
+Time_max                = 12;                                               % Maximum time of optimization in [h]
 
 nlp_opts                    = struct;
 nlp_opts.ipopt.max_iter     = Iteration_max;
 nlp_opts.ipopt.max_cpu_time = Time_max*3600;
-nlp_opts.ipopt.hessian_approximation ='limited-memory';
+nlp_opts.ipopt.acceptable_tol     = 1e-4;
+nlp_opts.ipopt.tol      = 1e-6;
+%nlp_opts.ipopt.hessian_approximation ='limited-memory';
 
-which_k                 = [     8,   44,   45,   46        ];              % Select which parameters are used for fitting
-k_lu                    = [ [   0;    0;    0;    0;   0   ], ...
-                          [   inf;  inf;  inf;  inf; inf ] ];
-Nk                      = numel(which_k)+1;                                   % Parameters within the model + sigma
-
-N_trial = 10;
+which_k                 = [      44,   46];              % Select which parameters are used for fitting
+k_lu                    = [ [     0;    0], ...
+                            [   inf;  inf] ];
[…]

### 2024-02-12 SFE_Parameter_Estimation_Chamomile/modelSFE.m

@@ -19,14 +19,13 @@ function xdot = modelSFE(x, p, mask, dt)
     dp            =     parameters{5};     % Diameter of the particle (m)
     L             =     parameters{6};     % Length of the extractor (m)
     rho_s         =     parameters{7};     %
-    km            =     parameters{8};
-    %km            =     1e5;
     mi            =     parameters{9};
 
-    Di            =     parameters{44}*1e-14;      
-    Dx            =     parameters{45}*1e-8;      
-    SAT           =     parameters{46};
-    %shape         =     parameters{52};
+    %km            =     parameters{8} ;
+    Di            =     parameters{44}* 1e-13;      
+    %Dx            =     parameters{45}* 1e-12;      
+    Dx            =     1e-15;      
+    gamma         =     parameters{46};
 
     nstages_index =     numel(mask);
     
@@ -62,7 +61,7 @@ function xdot = modelSFE(x, p, mask, dt)
     %% Saturation
     Csolid_percentage_left = 1 - (SOLID./C0solid);
     Csolid_percentage_left(find(~mask)) = 0;                                                % inserte zeros instead of NAN in pleces where there is no bed
-    Sat_coe       =     Saturation_Concentration(Csolid_percentage_left, SAT, Di);        % Inverse logistic is used to control saturation. Close to saturation point, the Sat_coe goes to zero.
+    Sat_coe       =     Saturation_Concentration(Csolid_percentage_left, gamma, Di);        % Inverse logistic is used to control saturation. Close to saturation point, the Sat_coe goes to zero.
 
     %% BC
     
@@ -99,7 +98,8 @@ function xdot = modelSFE(x, p, mask, dt)
 
     dPdt          = backward_diff_1_order(P_u, PRESSURE, [], dt)*1e2;
    
-    re            = (Sat_coe ./ mi ./ lp2)  .* ( SOLID - FLUID .* rho_s ./ RHO ./ km );
+    %re            = (Di ./ mi ./ lp2)  .* ( SOLID  );
+    re            = (Sat_coe ./ mi ./ lp2)  .* ( SOLID );
     
     %% model
     xdot = [

### 2024-02-13 SFE_article_Parameter_Estimation - Chamomile/Sections/Parameter_estimation.tex
13.02

@@
 				\hline 
-				Parameter		&$k_m$[-] 	& $D_i^R\times10^{-13}$[$m^2/s$] 	& $D_e^M\times10^{-12}$[$m^2/s$]	& $\Upsilon$ [m$^3$/kg] \\  \hline
+				Parameter		&$k_m$[-] 	& $D_i^R\times10^{-13}$[$m^2/s$] 	& $D_e^M\times10^{-12}$[$m^2/s$]	& $\Upsilon$ [-] \\  \hline
 				Lower bound		&0	  		& 0 	  			& 0 				& 0 	   		\\ 

### 2024-02-13 SFE_article_Parameter_Estimation - Chamomile/Sections/Results_Chamomile.tex
13.02

@@
 By selecting $D_e^M$ such it has a low value, the axial diffusion term can be reduced and removed from the model without lost of generality.
+The model reduction is in agreement with the work of \citet{Rahimi2011}, who worked with the same dataset and obtained Peclet numbers in the range from 290 to 400.
+Such a high values if Pe suggest that the advection term dominates the mass transfer and the axial diffusion is negligible.
 
@@
 The red circle shows the minimum value of the cost function found by the optimizer.
+The remaining experiments are fitted to the modified extraction model and results are presented in Figure \ref{fig: Fit_Di_Gamma}.
+The obtained results show good agreement for almost all the experiments.
 
-	The remaining experiments are fitted to the modified extraction model in the same way.
-The results of the parameter estimation for experiments at constant flow rate of $6.67\times 10^{-5}$ [kg/s] and constant temperature of 313 [K] are presented in Figure \ref{fig: Fit_1_4_Di_Dx}.
-
-	\begin{figure}[!h]
+	\begin{figure}
+		\centering
+		\begin{subfigure}[b]{\columnwidth}
 			\centering
 			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
-		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and constant temperature of 313 [K]}
-		\label{fig: Fit_1_4_Di_Dx}
+			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 313 [K]}
+			\label{fig: Fit_1_4_Di_Gamma}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
+			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 303 [K]}
+			\label{fig: Fit_5_8_Di_Gamma}
+		\end{subfigure}
+		\hfil
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
+			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
+			\label{fig: Fit_9_12_Di_Gamma}
+		\end{subfigure}
+		\caption{Parameter estimation results}
+		\label{fig: Fit_Di_Gamma}
 	\end{figure}
 
-	\begin{figure}[!h]
+	The results from the parameter estimation are further combined to obtain general correlations, which can be used for modelling of the extraction process at dynamically changing operating conditions.
+The traditional approach for finding correlations by combining Reynolds, Schmidt and Sherwood numbers is not used here because the axial diffusion rate was considered to be negligible.
+The proposed correlations shows linear trend between obtained parameters and the Reynolds number $\left(Re = \frac{\rho_f u d_p}{\mu}\right)$, as shown in Figure \ref{fig: Correlations}.
+
+	\begin{figure}
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
-		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and constant temperature of 303 [K]}
-		\label{fig: Fit_5_8_Di_Dx}
-	\end{figure}
-
-	\begin{figure}[!h]
+		\begin{subfigure}[b]{\columnwidth}
 			\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
-		\caption{Results of parameter estimation for experiments at $3.34\times 10^{-5}$ [kg/s]}
-		\label{fig: Fit_9_12_Di_Dx}
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Di_Re.png}
+			\caption{Linear regression $D_i^R$}
+			\label{fig: Correlations_Di_Re}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Gamma_Re.png}
+			\caption{Linear regression $\Upsilon$}
+			\label{fig: Correlations_Gamma_Re}
+		\end{subfigure}
+		\caption{Parameter estimation results}
+		\label{fig: Correlations}
 	\end{figure}

### 2024-02-13 SFE_article_Parameter_Estimation - Chamomile/Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
13.02

@@
 % ===================================================
-\title[mode=title]{Supercritical fluid extraction of essential oil from chamomile seeds: experiments, modelling, and parameter estimation}                      
-\shorttitle{Supercritical fluid extraction of essential oil from chamomile seeds: experiments, modelling, and parameter estimation}
+\title[mode=title]{Supercritical fluid extraction of essential oil from chamomile seeds: modelling, and parameter estimation}                      
+\shorttitle{Supercritical fluid extraction of essential oil from chamomile seeds: modelling, and parameter estimation}
 
@@
 Key model parameters included partition factor internal and axial diffusion coefficients were determined using maximum likelihood estimation from experimental data, assuming normal error.
-A set of laboratory experiments was performed in under multiple constant operating conditions: $30 - 40~^\circ C$, $100 - 200$ bar, and $1.33-6.66 \times 10^{-5}$ kg/s.
+A set of laboratory experiments was performed in under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s.
 

### 2024-02-13 SFE_Parameter_Estimation_Chamomile/Fit_Correlations.m

@@ -1,0 +1,45 @@
+startup;
+delete(gcp('nocreate'));
+
+AA = xlsread('Regression.xlsx');
+DI = [0.701472275, 1.331443055, 2.239307889, 2.711813187, 1.32629228, 1.485504345, 1.73827467, 2.59502961, 0.48656241, 1.363499511, 0.72227, 0.756214019];
+GG = [4.274825704, 2.189390368, 2.552240039, 1.365163176, 2.830760407, 2.573487374, 1.642279591, 1.906200052, 4.287215235, 2.723682117, 3.82240, 3.35589348];
+RE = [0.4632, 0.3783, 0.3029, 0.2619, 0.3579, 0.3140, 0.2635, 0.2323, 0.1787, 0.1160, 0.1889, 0.1512];
+FF = [6.67, 6.67, 6.67, 6.67, 6.67, 6.67, 6.67, 6.67, 3.33, 3.33, 3.33, 3.33];
+
+%%
+x1 = RE(1:8) ; y1 = GG(1:8);
+x2 = RE(9:12); y2 = GG(9:12);
+
+[mdl1,stuff1] = fit(x1',y1','poly1');
+[mdl2,stuff2] = fit(x2',y2','poly1');
+
+p1 = coeffvalues(mdl1);
+p2 = coeffvalues(mdl2);
+
+xtest  = linspace(0.1,0.5);
+ytest1 = polyval(p1,xtest);
+ytest2 = polyval(p2,xtest);
+
+hold on
+plt1 = plot(x1,y1,'ko', 'LineWidth',2);
+plt2 = plot(x2,y2,'kd', 'LineWidth',2);
+plot(xtest,ytest1, 'LineWidth',2);
+plot(xtest,ytest2, 'LineWidth',2);
+%yline(0, 'k', 'LineWidth',2);
+hold off
+
+text(0.3, 4.0, sprintf('~$D_i = %.3f \\cdot Re + %.3f$ \n $R^2=%.3f$',[p1, stuff1.rsquare]))
+text(0.15, 6.0, sprintf('$~D_i = %.3f \\cdot Re + %.3f$ \n $R^2=%.3f$',[p2, stuff2.rsquare]))
+
+legend([plt1(1),plt2(1)],'$3.33\times 10^{-5}[kg/s]$','$6.67\times 10^{-5}[kg/s]$','Location','best');
+legend box off
+
+%ylabel('$D_i^R \times 10^{-13} [m^2/s]$')
[…]

### 2024-02-15 SFE_article_Parameter_Estimation - Chamomile/Sections/Results_Chamomile.tex
15.02

--- 2024-02-12 SFE_article_Parameter_Estimation - Chamomile/Sections/Results_Chamomile.tex
@@
 
-	The parameter estimation problem was solved multiple time for different initial guesses.
-Each time-series was fitted to the model separately.
-First, the model with linear extraction kinetic only was fitted to the dataset.
-The Figure show the result of parameter estimation for dataset 1, which corresponds to the following operating conditions: 313 K, 100 bar and 6.57$\times 10^{-5}$ kg/s.
+	The parameter estimation problem was solved multiple times for different initial guesses.
+Each time series was fitted to the model separately.
+First, the model with linear extraction kinetics was the only one fitted to the dataset.
+The Figure shows the parameter estimation result for dataset 1, corresponding to the following operating conditions: $40^\circ C$, 100 bar and 6.67$\times 10^{-5}$ kg/s.
 
@@
 
-	In case of the linear kinetic two parameter are unknown, namely partition coefficient $k_m$ and the internal diffusion coefficient $D_i$.
-Figure \ref{fig: Fit_1_linear} shows the parameter space and corresponding values of the cost function.
+	In the case of the model with linear kinetic, two parameters are unknown, namely the partition coefficient $k_m$ and the internal diffusion coefficient $D_i$.
+Figure \ref{fig: Fit_1_linear} shows the cost function's parameter space and corresponding values.
 As the cost function is to be minimized, the lowest value of $-\ln(L)$ indicate the best fit.
-A black stripe around $D_i \approx 0.2)$ can be observed.
-That stripe indicate existence of optimal value of the $D_i$.
-In direction of $k_m$, the cost function is almost flat, which suggest that any value of $k_m$ above approximately 0.1 is equally good for fitting.
-If $k_m$ can be arbitrary point, then it can grow to the infinity.
-The optimizer found optimal values of the partition factors at relatively high levels.
-Such a behaviour suggest that the solvent is far from the saturation, and the model can be simplified.
+A black vertical stripe at $D_i \approx 0.2$ can be observed.
+That stripe indicates the existence of the optimal value of the $D_i$.
+In the direction of $k_m$, the cost function is almost flat, which suggests that any value of $k_m$ above 0.1 fits the data equally well.
+If $k_m$ can be an arbitrary point, then it can grow to infinity, which suggests that the solvent is far from the saturation, and the model can be simplified.
 The model reduction can be introduced by considering the limit of $k_m$ in the extraction kinetic term:
@@
 	The extraction model can be modified to account for the reduced kinetic term and the axial diffusion.
-In such a configuration just two parameters are unknown, namely internal diffusion coefficient $D_i$ and axial diffusion coefficient $D_e^M$.
+In such a configuration, two parameters are unknown: internal diffusion coefficient $D_i$ and axial diffusion coefficient $D_e^M$.
 Figure \ref{fig: Fit_1_Di_Dx} shows the parameter space and corresponding values of the cost function.
@@
 
-	Similarly to the previous case, the optimal value of $D_i$ exist, but a unique value for the $D_e^M$ cannot be determined.
-A little influence of the axial diffusion coefficient can be observed on Figure \ref{fig: Fit_1_Di_Dx} in a width range of values.
-By selecting $D_e^M$ such it has a low value, the axial diffusion term can be reduced and removed from the model without lost of generality.
+	Similarly to the previous case, the optimal value of $D_i$ exists, but a unique value for the $D_e^M$ cannot be determined.
+A little influence of the axial diffusion coefficient can be observed in Figure \ref{fig: Fit_1_Di_Dx} in a width range of values.
+By selecting $D_e^M$, which has a low value, the axial diffusion term can be reduced and removed from the model without losing generality.
+Similar was drawn by \citet{Rahimi2011}, who worked with the same dataset and obtained Peclet numbers from 290 to 400.
+Such high values of the Peclet number suggest that the advection term dominates the mass transfer, and the axial diffusion is negligible.
 
-	I both cases discussed above, none of the results of the fitting was not sufficient due to high or to low extraction kinetic.
+	In both cases discussed above, none of the fitting results were satisfactory.
 Following the idea behind the Broken-and-Intact and Shrinking Core models (presented in Chapter \ref{CH: Gamma_Function}), the gamma function is introduced to account for the decaying extraction kinetic.
-The proposed correction factor is combined with the reduced linear model, which leads to a two-parameter ($D_i^R$ and $\Upsilon$) defined by Equation \ref{Model_kinetic}.
-The Figure \ref{fig: Fit_1_Di_Dx} shows the parameter space with and the corresponding values of the cost function.
+The proposed correction factor is combined with the reduced linear model, which leads to a new two-parameter ($D_i^R$ and $\Upsilon$) model defined by Equation \ref{Model_kinetic}.
+Figure \ref{fig: Fit_1_Di_Dx} shows the parameter space with and the corresponding values of the cost function.
 
@@
 
-	The parameter space of the modified model is characterized by the unique minimum value, which corresponds to the solution of the parameter estimation problem for the experiment 1.
+	The parameter space of the modified model is characterized by the unique minimum value, which corresponds to the solution of the parameter estimation problem for experiment 1.
 The red circle shows the minimum value of the cost function found by the optimizer.
-
-	The remaining experiments are fitted to the modified extraction model in the same way.
-The results of the parameter estimation for experiments at constant flow rate of $6.67\times 10^{-5}$ [kg/s] and constant temperature of 313 [K] are presented in Figure \ref{fig: Fit_1_4_Di_Dx}.
+The remaining experiments are fitted to the modified extraction model, and results are presented in Figure \ref{fig: Fit_Di_Gamma}.
+The obtained results show good agreement with experimental data.
 
@@
 		\centering
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
 			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
-		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and constant temperature of 313 [K]}
-		\label{fig: Fit_1_4_Di_Dx}
+			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
+			\label{fig: Fit_1_4_Di_Gamma}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
+			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
+			\label{fig: Fit_5_8_Di_Gamma}
+		\end{subfigure}
+		\hfil
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
+			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
+			\label{fig: Fit_9_12_Di_Gamma}
+		\end{subfigure}
+		\caption{Parameter estimation results}
+		\label{fig: Fit_Di_Gamma}
 	\end{figure}
+
+	The estimated parameters describe the decaying rate of internal diffusion coefficient $D_i$ according to Equation \ref{EQ: C_sat_function}.
+The internal diffusion coefficient is assumed to decrease as it is more difficult for a solute particle to diffuse from a particle core than the particle of a solute located next to the surface.
+The obtained decaying patterns are present in Figure \ref{fig: Gamma_function}.
+It can be noticed from the plot that a higher internal diffusion coefficient characterises the high-pressure fluid.
+This is in agreement with the work of \citet{Giddings1968}, \citet{Gurdial1989} and \citet{Machida2011} who analysed the solvation power of a solvent and correlated it with physical properties of $CO_2$.
+The Hildebrand solubility parameter was used to measure the cohesive energy density of a substance.
+\citet{Giddings1968} proposed a correlation for a solubility parameter $\delta_H[\text{MPa}^{1/2}] = 1.25 P_c^{1/2}\rho_r$, where $P_c$ and $\rho_r$ are critical pressure and reduced density respectively.
+\citet{Marcus2006} derived a similar correlation from the Van der Waals equation of state: $\delta_H[\text{MPa}^{1/2}] = 2.79 P_c^{1/4}T_r^{1/4}\rho_r$.
+Figure \ref{fig: Gamma_function} shows that fluid characterised by a higher solubility factor has larger values of internal diffusion coefficient.
+The relation between $\delta_H$ and $D_i$ should only be treated as an indicator because the system is non-ideal, and external factors such as fluid velocity are not considered.
 
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
-		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and constant temperature of 303 [K]}
-		\label{fig: Fit_5_8_Di_Dx}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Gamma_function.png}
+		\caption{The decaying internal diffusion coefficient}
+		\label{fig: Gamma_function}
 	\end{figure}
+
+	The parameter estimation results are combined to analyse the relationship between the obtained parameters and the operating conditions.
+This work does not apply the traditional approach for finding correlations by combining Reynolds, Schmidt and Sherwood numbers because the axial diffusion was considered negligible.
+Instead, the Reynolds number $\left(Re = \frac{(2r) \cdot \rho_f \cdot u}{\mu}\right)$ is used solely as an independent variable as shown in Figure \ref{fig: Correlations}.
+Using the Reynolds number has the advantage of considering the influence of all the control variables (temperature, pressure and flow rate), which means it can be uniquely defined by selecting operating conditions.
+	Two data clusters can be distinguished in Figures \ref{fig: Correlations_Di_Re} and \ref{fig: Correlations_Gamma_Re}, where each cluster corresponds to a different mass flow rate.
+Even though a linear trend characterises both correlations, correlations related to $D_i^R$ decrease with Re while the correlations related to $\Upsilon$ increase with Re.
+Higher fluid density and corresponding mass transfer resistance can explain the decrease of the $D_i^R$ along each line.
+On the other hand, the increase in $\Upsilon$ correlations can be justified by higher solubility.
+The Hildebrand solubility factor is mainly a function of fluid density, which is also present in the the Reynolds number hence $\Upsilon$ can be correlated with Re.
 
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
-		\caption{Results of parameter estimation for experiments at $3.34\times 10^{-5}$ [kg/s]}
-		\label{fig: Fit_9_12_Di_Dx}
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Di_Re.png}
+			\caption{Linear regression $D_i^R = f(Re)$}
+			\label{fig: Correlations_Di_Re}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Gamma_Re.png}
+			\caption{Linear regression $\Upsilon = f(Re)$}
+			\label{fig: Correlations_Gamma_Re}
+		\end{subfigure}
+		\caption{Parameter estimation results}
+		\label{fig: Correlations}
 	\end{figure}

### 2024-02-22 SFE_article_Parameter_Estimation - Chamomile/Sections/Experiments.tex
22.02

@@
 
-	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile seeds.
+	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers.
 The experiments were performed by \citet{Povh2001}.
-To prepare the seeds for extraction, they were first pre-treated using a knife mill (TECNAL, model TE 340) to reduce their particle size.
+To prepare the flowers for extraction, they were first pre-treated using a knife mill (TECNAL, model TE 340) to reduce their particle size.
 The mean
@@
 
-	%The moisture content of the seeds was then determined using an Infrared Moisture Analyser, which revealed an average moisture content of 4.83\% in the solid particles after grinding.
+	%The moisture content of the flowers was then determined using an Infrared Moisture Analyser, which revealed an average moisture content of 4.83\% in the solid particles after grinding.
 Next, the density of the solid material was measured using a pycnometer, which can be found in Appendix \ref{CH: Solid_Density_Measurment}.
@@
 	The experiments were conducted using an extractor with diameter of $3.96\times 10^{-2}$ m and length $16.55\times 10^{-2}$ m.
-Twelve experiments were performed under different but constant in time operating conditions: $30-40^\circ C$, $100 - 200$ bar, and $1.33-6.66 \times 10^{-5}$ kg/s.
+Twelve experiments were performed under different but constant in time operating conditions: $30-40^\circ C$, $100 - 200$ bar, and $1.33-6.67 \times 10^{-5}$ kg/s.
 The amount of solid material used for extraction was $75\times 10^{-3}$ kg, which was sufficient to fill the whole vessel.

### 2024-02-22 SFE_article_Parameter_Estimation - Chamomile/Sections/Model.tex
22.02

@@
 	 %When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{black}\phi}(z)$ (where ${\color{black}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}
-	The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function ${\color{black}A_f}(z) = {\color{black}A\phi}(z)$ to take into account the change of the cross-section available for the fluid.
+
+	%The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function ${\color{black}A_f}(z) = {\color{black}A\phi}(z)$ to take into account the change of the cross-section available for the fluid.
 The Equation \ref{EQ: Continuity_differential} shows the differential form of the continuity equation:
+
+	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is refined by incorporating a function ${\color{black}A_f}(z) = {\color{black}A\phi}(z)$.
+This modification accounts for the variability in the cross-sectional area available for fluid flow.
+Equation \ref{EQ: Continuity_differential} presents this adaptation in the differential form of the continuity equation, capturing the dynamics of the flow as it responds to changes in the cross-section.
 
@@
 
-	The detailed derivation of the mass balance equation for the fluid phase can be found in Appendix \ref{CH: Gouverning equations}.
-The movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}) is considered only in the axial direction due to quasi-one-dimensional assumptions, which take into account variation of the void fraction.
-Furthermore, the thermodynamic pressure is assumed to be constant along the device as presented by Equation \ref{EQ: Pressure_Velocity}.
-Additionally, the boundary layer adjacent to the inner wall of the extractor is neglected, resulting in a constant velocity profile across any cross-section of the extractor perpendicular to the axial direction.
-The amount of solute in the solvent is considered negligible, resulting in the fluid phase being described as pseudo-homogeneous, and its properties are assumed to be the same as the solvent.
-The mass balance equation for the fluid phase includes convection, diffusion, and kinetic terms.
+	The comprehensive derivation of the mass balance equation for the fluid phase is detailed in Appendix \ref{CH: Gouverning equations}.
+This equation accounts for the movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}), which is constrained to the axial direction due to the quasi-one-dimensional approach that considers changes in the void fraction.
+It is also predicated on the assumption that the thermodynamic pressure remains constant throughout the device, as illustrated by Equation \ref{EQ: Pressure_Velocity}.
+The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall, leading to a uniform velocity profile across any cross-section perpendicular to the axial direction.
+Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself.
+The mass balance equation thus encompasses convection, diffusion, and kinetic terms to accurately represent the fluid phase's behaviour.
 
@@
 
-	${\color{black}c_f}(t,z)$ represents the concentration of solute in the fluid phase, , ${\color{black}r_e}(t,z)$ is a mass transfer kinetic term, and ${\color{black}D^M_e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}F}(t))$ is the axial mass diffusion coefficient.
+	${\color{black}c_f}(t,z)$ represents the concentration of solute in the fluid phase, , ${\color{black}r_e}(t,z)$ is a mass transfer kinetic term, and ${\color{black}D^M_e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}F}(t))$ is the axial diffusion coefficient.
 
@@
 
-	The solid phase is considered to be stationary, with negligible convection and diffusion terms in the mass balance equation (Equation \ref{Model_solid}).
+	The solid phase is considered to be stationary, without convection and diffusion terms in the mass balance equation (Equation \ref{Model_solid}).
 Therefore, the only significant term in this equation is the kinetic term (as defined in Equation \ref{Model_kinetic_basic}), which connects the solid and fluid phases.
@@
 As the solute diffuses through the pore, its concentration changes and reaches ${\color{black}c_{pf}}$ at the opening of the pore.
-The solute then diffuses through the film around the particle and reaches a concentration in bulk ${\color{black}c_f}$.
+The solute then diffuses through the film around the particle and reaches bulk concentration ${\color{black}c_f}$.
 The two-film theory describes the solid-fluid interface inside the pore.
@@
 
-			For real gases, it is complicated to write the heat balance in terms of temperature, but it be can be used directly in the form of internal energy, as it is given by Equation \ref{EQ: CompressibleEuler_3}.
+			For real gases, it is complicated to write the heat balance in terms of temperature, but it can be used directly in the form of internal energy, as it is given by Equation \ref{EQ: CompressibleEuler_3}.
 In such a case, the temperature needs to be recovered from the internal energy.
@@
 A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution (Equation \ref{EQ: Heat_internal}) and the output from Equation \ref{EQ: internal_energy_PR}.
-Such a procedure allow to find local temperature along spatial direction ${\color{black}z}$ and needs to be repeated every time-step.
+Such a procedure allows to find a local temperature along spatial direction ${\color{black}z}$ and needs to be repeated every time-step.
 
@@
 As the residence time is much shorter than the sampling time, the initial state estimate for the concentration of the solute in the fluid phase would be not reliable.
-Considering that it is assumed that the $c_f0=0$.
+Considering that it is assumed that the $c_{f0}=0$.
 Moreover, it is considered that the initial temperature of the extractor in every place is the same and described by ${\color{black}h_0}$.
@@
 			In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases (${\color{black}c_f}(t,z)$ and ${\color{black}c_s}(t,z)$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{black}h}(t,z)$).
-The controllable input variables are the mass flow-rate and temperature of the solvent in the feed and the pressure in the extractor.
-Additionally, the pressure change is augumented with the state-space and denoted as ${\color{black}P}(t)$.
-			The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase and it can be measured after the separator (${\color{black}Y}(t)$).
-The system is controllable by manipulating the flow-rate and temperature (enthalpy) of $CO_2$ in the feed, and the pressure in the extractor.
+The controllable input variables are the mass flow rate and temperature of the solvent in the feed and the pressure in the extractor.
+Additionally, the pressure change is augmented with the state-space and denoted as ${\color{black}P}(t)$.
+			The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase, and it can be measured after the separator (${\color{black}Y}(t)$).
+The system is controllable by manipulating the flow rate and temperature (enthalpy) of $CO_2$ in the feed and the pressure in the extractor.
 
@@
 The integral equation states that the change rate of the integral of any quantity over an arbitrary control volume is given by the flux through the boundary of the control volume, with being the outer surface normal through the boundary.
-That quantity is neither produced nor consumed inside of the control volume and is hence conserved.
+That quantity is neither produced nor consumed inside the control volume and is conserved.
 For a derivative to be conservative, it must form a telescoping series.
-In other words, after the addition of all terms coming from the discretization over a grid, only the boundary terms should remain and the artificial interior points should cancel out.
-To ensure the mass conservation, the discretization is applied on the conservative form of the process model.
+In other words, after the addition of all terms coming from the discretization over a grid, only the boundary terms should remain, and the artificial interior points should cancel out.
+To ensure mass conservation, discretization is applied to the conservative form of the process model.
 

### 2024-02-22 SFE_article_Parameter_Estimation - Chamomile/Sections/Parameter_estimation.tex
22.02

@@
 
-	Not all the parameters present in a process model can be estimated from the theoretical considerations.
+	Only some of the parameters in a process model can be estimated from the theoretical considerations.
 The goal of parameter estimation is to obtain the "best" estimate of unknown parameters ${\color{black} \theta}$ (which is a subset of the parameter space ${\color{black}\Theta}$ containing all parameters of a model) based on the continuous observations ${\color{black}Y}(t)$ or the discrete observations ${\color{black}Y}(t_i)$.
@@
 	In the case where the error in the first observation is denoted as $\epsilon_1$, the error in the second observation $\epsilon_2'$ incorporates $\epsilon_1$ as well as an independent random component, given by $\epsilon_2' = \epsilon_1 + \epsilon_2$.
-Similarly, the error in the third observation is $\epsilon_3' = \epsilon_1 + \epsilon_2 + \epsilon_3$, and so on.
+Similarly, the error in the third observation is $\epsilon_3' = \epsilon_1 + \epsilon_2 + \epsilon_3$, etc.
 \citet{Mandel1957}  made a distinction between the typically assumed independent measurement error in the dependent variable and a "cumulative" or interval error, in which each new observation encompasses the error of the previous ones.
-Cumulative errors arise from fluctuations in the process itself due to small variations in operating conditions and are not independent; only the differences in measurement from one period to the next are independent.
+Cumulative errors arise from fluctuations in the process due to small variations in operating conditions and are not independent; only the differences in measurement from one period to the next are independent.
 
@@
 
-	Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector ${\color{black} \theta}$ and equating to zero the partial derivatives of $\ln L$:
-
-	{\footnotesize
-		\begin{align}\label{EQ: MLE_Basic_Solution}
-			\cfrac{\partial \ln L}{\partial {\color{black} \theta}} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( {\color{black}y}(t_i) | {\color{black} \theta} \right) }{\partial {\color{black} \theta}} = 0 
-	\end{align} }
-
-	Solution of Equations \ref{EQ: MLE_Basic_Solution} yield the desired estimates $\hat{{\color{black} \theta}}$.
-For some models, these equations can be explicitly solved for $\hat{{\color{black} \theta}}$ but in general, no closed-form solution to the maximization problem is known or available, and a maximum likelihood estimator can only be found via numerical optimization.
-
-	As a result of fitting, the following parameters are obtained:
-
-	\begin{itemize}
-		\item Partition coefficient:\qquad\quad\qquad$k_m$
-		\item Internal diffusion coefficient: \quad$D_i^R$
-		\item Axial diffusion coefficient: \qquad$D_e^M$
-		\item Decay coefficient:\qquad\qquad\qquad$\Upsilon$
-		%\item Standard deviation:\qquad\qquad\quad~$\sigma^2$
-	\end{itemize}
-
-	To ensure that parameters found by the optimizer do not reach unrealistic values, an additional set of inequality constraints is introduced.
-The initial guess for each optimization, the lower and upper bounds for each parameter are given in Table \ref{tab:Constraints}.
+	The initial guess for each decision variable, as well as the lower and upper bounds are given in Table \ref{tab:Constraints}.
 
@@
 
+	%Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector ${\color{black} \theta}$ and equating to zero the partial derivatives of $\ln L$:
+
+	%{\footnotesize
+	%	\begin{align}\label{EQ: MLE_Basic_Solution}
+	%		\cfrac{\partial \ln L}{\partial {\color{black} \theta}} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( {\color{black}y}(t_i) | {\color{black} \theta} \right) }{\partial {\color{black} \theta}} = 0 
+	%\end{align} }
+
+	Solution of Equations \ref{EQ: Optimization_formulation_MLE} yield the desired estimates $\hat{{\color{black} \theta}}$.
+For some models, these equations can be explicitly solved for $\hat{{\color{black} \theta}}$ but in general, no closed-form solution to the maximization problem is known or available, and a maximum likelihood estimator can only be found via numerical optimization.
+
+	%The decision variables are:
+
+	%\begin{itemize}
+	%	\item Partition coefficient:\qquad\quad\qquad$k_m$
+	%	\item Internal diffusion coefficient: \quad$D_i^R$
+	%	\item Axial diffusion coefficient: \qquad$D_e^M$
+	%	\item Decay coefficient:\qquad\qquad\qquad$\Upsilon$
+	%	%\item Standard deviation:\qquad\qquad\quad~$\sigma^2$
+	%\end{itemize}
+
+	%To ensure that parameters found by the optimizer do not reach unrealistic values, an additional set of inequality constraints is introduced.
+The initial guess for each optimization, the lower and upper bounds for each parameter are given in Table \ref{tab:Constraints}.
+
 \end{document}

### 2024-02-22 SFE_article_Parameter_Estimation - Chamomile/Sections/Results_Chamomile.tex
22.02

@@
 
-	The parameter estimation problem was solved multiple times for different initial guesses.
-Each time series was fitted to the model separately.
-First, the model with linear extraction kinetics was the only one fitted to the dataset.
-The Figure shows the parameter estimation result for dataset 1, corresponding to the following operating conditions: $40^\circ C$, 100 bar and 6.67$\times 10^{-5}$ kg/s.
+	To solve the parameter estimation problem, the single shooting method was used to transform the boundary-value problem into the initial value problem and to formulate the non-linear programming problem.
+This non-linear optimization task was tackled using the CasADi framework (\citet{Andersson2018}).
+Each time series was fitted separately to the model with the linear extraction kinetics (Equation \ref{Model_kinetic_no_sat}).
+The initial value problem was solved multiple times with varying initial guesses to identify the global minimum.
+Within the model context characterized by linear kinetics, two parameters remain to be determined: the partition coefficient $k_m$ and the internal diffusion coefficient $D_i$.
 
@@
 
-	In the case of the model with linear kinetic, two parameters are unknown, namely the partition coefficient $k_m$ and the internal diffusion coefficient $D_i$.
-Figure \ref{fig: Fit_1_linear} shows the cost function's parameter space and corresponding values.
+	Figure \ref{fig: Fit_1_linear} shows the parameter space and corresponding values of the cost function for experiment 1 ($40^\circ C$, 100 bar and 6.67$\times 10^{-5}$ kg/s).
 As the cost function is to be minimized, the lowest value of $-\ln(L)$ indicate the best fit.
@@
 				&\lim_{k_m \rightarrow \infty} \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right)  = \\
-				&= \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{\infty{\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right) = \left({\color{black}{\color{black} c_s} }(t,z) - 0 \right)
+				&= \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{\rho_s}{\infty \cdot \rho(T(t,z),P(t))}  {c_f}(t,z) \right) = \left(c_s(t,z) - 0 \right)
 			\end{split}
@@
 
-	The extraction model can be modified to account for the reduced kinetic term and the axial diffusion.
-In such a configuration, two parameters are unknown: internal diffusion coefficient $D_i$ and axial diffusion coefficient $D_e^M$.
-Figure \ref{fig: Fit_1_Di_Dx} shows the parameter space and corresponding values of the cost function.
+	The extraction model can be adapted to incorporate adjustments for the reduced kinetic term and axial diffusion.
+In this revised setup, two parameters remain undetermined: the internal diffusion coefficient $D_i$ and the axial diffusion coefficient $D_e^M$.
+Figure \ref{fig: Fit_1_Di_Dx} illustrates the parameter space and associated cost function values.
 
@@
 	Similarly to the previous case, the optimal value of $D_i$ exists, but a unique value for the $D_e^M$ cannot be determined.
-A little influence of the axial diffusion coefficient can be observed in Figure \ref{fig: Fit_1_Di_Dx} in a width range of values.
-By selecting $D_e^M$, which has a low value, the axial diffusion term can be reduced and removed from the model without losing generality.
-Similar was drawn by \citet{Rahimi2011}, who worked with the same dataset and obtained Peclet numbers from 290 to 400.
+Figure \ref{fig: Fit_1_Di_Dx} illustrates the minimal impact of the axial diffusion coefficient, where a broad range of $D_e^M$ yields identical cost function values.
+By selecting a low value $D_e^M$, the axial diffusion terms can be reduced or eliminated from the model without compromising its generality.
+This observation aligns with the findings of \citet{Rahimi2011}, who analysed the same dataset and reported Peclet numbers ranging between 290 and 400.
 Such high values of the Peclet number suggest that the advection term dominates the mass transfer, and the axial diffusion is negligible.
 
-	In both cases discussed above, none of the fitting results were satisfactory.
-Following the idea behind the Broken-and-Intact and Shrinking Core models (presented in Chapter \ref{CH: Gamma_Function}), the gamma function is introduced to account for the decaying extraction kinetic.
-The proposed correction factor is combined with the reduced linear model, which leads to a new two-parameter ($D_i^R$ and $\Upsilon$) model defined by Equation \ref{Model_kinetic}.
-Figure \ref{fig: Fit_1_Di_Dx} shows the parameter space with and the corresponding values of the cost function.
+	In both scenarios previously discussed, the fitting outcomes were not deemed satisfactory.
+Building upon the concepts underlying the Broken-and-Intact and Shrinking Core models (detailed in Chapter \ref{CH: Gamma_Function}), a gamma function is introduced to capture the diminishing extraction kinetics.
+The correction factor is combined with the simplified linear model, resulting in a two-parameter model ($D_i^R$ and $\Upsilon$) as given by Equation \ref{Model_kinetic}.
+Figure \ref{fig: Fit_1_Di_Gamma} shows the parameter space and the corresponding cost function values.
 
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=0.98\columnwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
 		\caption{Parameter space for the modified extraction model and experiment 1}
@@
 
-	The parameter space of the modified model is characterized by the unique minimum value, which corresponds to the solution of the parameter estimation problem for experiment 1.
-The red circle shows the minimum value of the cost function found by the optimizer.
+	The parameter space for the revised model exhibits a distinct minimum value corresponding to the solution of the parameter estimation problem for experiment 1.
+The red circle highlights the minimum value of the cost function found by the optimizer.
 The remaining experiments are fitted to the modified extraction model, and results are presented in Figure \ref{fig: Fit_Di_Gamma}.
@@
 		\end{subfigure}
-		\hfil
+			\end{figure}%
+		\begin{figure}[h!]\ContinuedFloat
 		\begin{subfigure}[b]{\columnwidth}
@@
 
-	The estimated parameters describe the decaying rate of internal diffusion coefficient $D_i$ according to Equation \ref{EQ: C_sat_function}.
-The internal diffusion coefficient is assumed to decrease as it is more difficult for a solute particle to diffuse from a particle core than the particle of a solute located next to the surface.
-The obtained decaying patterns are present in Figure \ref{fig: Gamma_function}.
-It can be noticed from the plot that a higher internal diffusion coefficient characterises the high-pressure fluid.
-This is in agreement with the work of \citet{Giddings1968}, \citet{Gurdial1989} and \citet{Machida2011} who analysed the solvation power of a solvent and correlated it with physical properties of $CO_2$.
-The Hildebrand solubility parameter was used to measure the cohesive energy density of a substance.
-\citet{Giddings1968} proposed a correlation for a solubility parameter $\delta_H[\text{MPa}^{1/2}] = 1.25 P_c^{1/2}\rho_r$, where $P_c$ and $\rho_r$ are critical pressure and reduced density respectively.
-\citet{Marcus2006} derived a similar correlation from the Van der Waals equation of state: $\delta_H[\text{MPa}^{1/2}] = 2.79 P_c^{1/4}T_r^{1/4}\rho_r$.
-Figure \ref{fig: Gamma_function} shows that fluid characterised by a higher solubility factor has larger values of internal diffusion coefficient.
-The relation between $\delta_H$ and $D_i$ should only be treated as an indicator because the system is non-ideal, and external factors such as fluid velocity are not considered.
+	The estimated parameters describe the diminishing trend of the internal diffusion coefficient $D_i$, as delineated by Equation \ref{EQ: C_sat_function}.
+It is hypothesized that the internal diffusion coefficient decreases because solute particles face greater difficulty diffusing from the core of a particle than from positions closer to the surface.
+Decay patterns under various operational conditions, depicted in Figure \ref{fig: Gamma_function}, show that the internal diffusion coefficient is notably higher in fluids under high pressure.
+This observation aligns with the findings of \citet{Giddings1968}, \citet{Gurdial1989}, and \citet{Machida2011}, who explored the solvation capability of solvents and its correlation with the physical properties of $CO_2$ by calculating the Hildebrand solubility parameter $\delta_H$.
+\citet{Giddings1968} introduced a correlation for the solubility parameter $\delta_H[\text{MPa}^{1/2}] = 1.25 P_c^{1/2}\rho_r$, with $P_c$ and $\rho_r$ representing the critical pressure and reduced density, respectively.
+Similarly, \citet{Marcus2006} formulated a correlation based on the Van der Waals equation of state: $\delta_H[\text{MPa}^{1/2}] = 2.79 P_c^{1/4}T_r^{1/4}\rho_r$.
+As Figure \ref{fig: Gamma_function} shows, fluids with higher solubility factors exhibit greater internal diffusion coefficients.
+However, the relationship between $\delta_H$ and $D_i$ should be considered indicative rather than definitive due to the non-ideal nature of the system and the omission of external factors such as fluid velocity.
 
@@
 	The parameter estimation results are combined to analyse the relationship between the obtained parameters and the operating conditions.
-This work does not apply the traditional approach for finding correlations by combining Reynolds, Schmidt and Sherwood numbers because the axial diffusion was considered negligible.
-Instead, the Reynolds number $\left(Re = \frac{(2r) \cdot \rho_f \cdot u}{\mu}\right)$ is used solely as an independent variable as shown in Figure \ref{fig: Correlations}.
+Unlike traditional methods that employ a combination of Reynolds, Schmidt, and Sherwood numbers to find correlations—omitted here due to the insignificance of axial diffusion—the approach in this study leverages the Reynolds number $\left(Re = \frac{(2r) \cdot \rho_f \cdot u}{\mu}\right)$ as the sole independent variable.
 Using the Reynolds number has the advantage of considering the influence of all the control variables (temperature, pressure and flow rate), which means it can be uniquely defined by selecting operating conditions.
-	Two data clusters can be distinguished in Figures \ref{fig: Correlations_Di_Re} and \ref{fig: Correlations_Gamma_Re}, where each cluster corresponds to a different mass flow rate.
-Even though a linear trend characterises both correlations, correlations related to $D_i^R$ decrease with Re while the correlations related to $\Upsilon$ increase with Re.
-Higher fluid density and corresponding mass transfer resistance can explain the decrease of the $D_i^R$ along each line.
-On the other hand, the increase in $\Upsilon$ correlations can be justified by higher solubility.
-The Hildebrand solubility factor is mainly a function of fluid density, which is also present in the the Reynolds number hence $\Upsilon$ can be correlated with Re.
+
+	In Figures \ref{fig: Correlations_Di_Re} and \ref{fig: Correlations_Gamma_Re}, two distinct data clusters emerge, each corresponding to a different mass flow rate.
+Despite the linear trends observed in both sets of correlations, the correlations for $D_i^R$ exhibit a decline with increasing Re, whereas those for $\Upsilon$ show an upward trend with Re.
+The decrease in $D_i^R$ across each data line can be attributed to higher fluid density and increased mass transfer resistance.
+Conversely, the rise in $\Upsilon$ correlations may be explained by enhanced solubility.
+The Hildebrand solubility factor and the Reynolds number are proportional to the fluid density; hence, $\Upsilon$ can be correlated with Re.
 

### 2024-02-22 SFE_article_Parameter_Estimation - Chamomile/Sections/introduction_imp.tex
22.02

--- 2023-10-03 SFE_article_Parameter_Estimation/Sections/introduction_imp.tex
@@
 
-	The present study focuses on extracting essential oil from the caraway (Carum carvi L.) seeds with supercritical fluid extraction and modelling that process.
+	This study investigates the extraction of essential oil from chamomile flowers (Matricaria chamomilla L.) via supercritical fluid extraction techniques and modelling of this process.
+Chamomile is a medicinal herb widely cultivated in southern and eastern Europe—such as Germany, Hungary, France, and Russia.
+It can be found outside of Europe in Brazil as discussed by \citet{Singh2011}.
+This plant is distinguished by its hollow, bright gold cones, housing disc or tubular florets and surrounded by about fifteen white ray or ligulate florets.
+Chamomile has been used for its medicinal benefits, serving as an anti-inflammatory, antioxidant, mild astringent, and healing remedy.
+Chamomile's aqueous extract is widely used as a gentle sedative to calm nerves and mitigate anxiety, hysteria, nightmares, insomnia, and other sleep-related conditions, according to \citet{Srivastava2009}.
+\citet{Orav2010} reported that oil yields from dried chamomile samples ranged from 0.7 to 6.7 mL kg$^{-1}$.
+Notably, the highest yields of essential oil, between 6.1 and 6.7 mL kg$^{-1}$, were derived from chamomile sourced from Latvia and Ukraine, while chamomile from Armenia exhibited a lower oil content of 0.7 mL kg$^{-1}$.
+
+	%The present study focuses on extracting essential oil from the chamomile flowers with supercritical fluid extraction and modelling that process.
 Caraway is a biennial plant belonging to the Apiaceae family.
-It is widespread in Asia, Europe, and North Africa.
+It is widespread in Asia, Europe, and North Afri``ca.
 The essential oil obtained from caraway finds its potential application as a fragrance ingredient in perfumes, liquors, and toothpaste.
@@
 
-	The economic feasibility of the process is crucial when selecting the appropriate technology.
+	%The economic feasibility of the process is crucial when selecting the appropriate technology.
 Conventional processes, such as distillation and organic solvent extraction, are frequently used for essential oil extraction.
 The distillation process is carried out at a high temperature, which causes thermal degradation of thermolabile compounds—considering that alternative techniques like supercritical fluid extraction gained popularity for extraction.
-Supercritical carbon dioxide, in particular, is attractive due to its unique properties such as inflammable, non-toxic, low critical temperature and non-corrosive.
+Supercritical carbon dioxide, in particular, is attractive due to its unique properties such as being inflammable, non-toxic, low critical temperature, and non-corrosive.
 Furthermore, its critical point is relatively low compared to other fluids, making it a suitable alternative to traditional extraction techniques.
-The supercritical fluids exhibit both gas- and liquid-like properties so that operating conditions can adjust pressure-depended dissolving power.
+The supercritical fluids exhibit both gas- and liquid-like properties so that operating conditions can adjust the dissolving power.
 
-	Various mathematical models have been proposed to describe the extraction of valuable compounds from a fixed biomass bed.
+	%Various mathematical models have been proposed to describe the extraction of valuable compounds from a fixed biomass bed.
 However, selecting an appropriate extraction model requires understanding the physical phenomena occurring in the operational unit.
@@
 
-	One model proposed by \citet{Reverchon1993} is the hot ball model, which is based on an analogy to heat transfer and describes an extraction process from solid particles containing small quantities of solute where solubility is not a limiting factor.
-Another model, the Broken-and-Intact Cell model, was presented by \citet{Sovova1994}.
+	%One model proposed by \citet{Reverchon1993} is the hot ball model, which is based on an analogy to heat transfer and describes an extraction process from solid particles containing small quantities of solute where solubility is not a limiting factor.
+
+	%Another model, the Broken-and-Intact Cell model, was presented by \citet{Sovova1994}.
 This model describes a system where the outer surfaces of particles have been mechanically interrupted, allowing easy access of solvent to the solute from the broken cells.
@@
 
-	\citet{Reverchon1996} developed a model for fluid-solid extraction, where the oil is treated as a single component, and the extraction process is controlled by internal mass transfer resistance, neglecting external mass transfer.
+	%\citet{Reverchon1996} developed a model for fluid-solid extraction, where the oil is treated as a single component, and the extraction process is controlled by internal mass transfer resistance, neglecting external mass transfer.
 However, this model does not consider the influence of axial dispersion or changes in fluid density and flow rate along the bed.
 
-	In this work, the fundamental governing equations are derived and combined with the kinetic model suggested by \citet{Reverchon1996} to obtain a general model for the oil extraction process from the caraway seed.
+	%In this work, the fundamental governing equations are derived and combined with the kinetic model suggested by \citet{Reverchon1996} to obtain a general model for the oil extraction process from the chamomile flower.
 This model simplifies some of the physical behaviour to obtain a control-oriented model.
@@
 
+	Evaluating the economic viability of the process is essential when choosing the suitable technology for essential oil extraction.
+Traditional methods, such as distillation and organic solvent extraction, are commonly employed but come with drawbacks.
+Distillation, for example, involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds.
+This limitation has led to the increased popularity of alternative techniques like supercritical fluid extraction.
+Supercritical carbon dioxide is particularly appealing due to its distinctive properties: it's inflammable, non-toxic, has a low critical temperature, and is non-corrosive.
+Moreover, its relatively low critical point, compared to other fluids, positions it as an advantageous alternative to conventional extraction methods.
+Supercritical fluids are capable of exhibiting both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.
+
+	The literature offers a variety of mathematical models aimed at detailing the extraction of valuable compounds from a fixed biomass bed.
+Selecting a fitting model necessitates a deep understanding of the physical processes at play within the operational unit, as each model is built on specific assumptions and outlines distinct mass transfer mechanisms and equilibrium dynamics.
+
+	One model proposed by \citet{Reverchon1993} is the hot ball model, which is based on an analogy to heat transfer and describes an extraction process from solid particles containing small quantities of solute where solubility is not a limiting factor.
+
+	The Broken-and-Intact Cell model, proposed by \citet{Sovova1994}, assumes that external surfaces of particles are mechanically disrupted, allowing the solvent's access to the solute in broken cells, while the solute in intact cells remains less accessible due to higher mass transfer resistance.
+
+	\citet{Reverchon1996} formulated a fluid-solid extraction model where the solute is treated as a single component, governed by internal mass transfer resistance and omitting the effects of external mass transfer, axial dispersion, and variations in fluid density and flow rate throughout the bed.
+
+	This work builds upon the linear kinetic model suggested by \citet{Reverchon1996}, deriving fundamental governing equations to develop a comprehensive model for the chamomile oil extraction process.
+This model aims for control-oriented simplicity, assuming a semi-continuous operation within a cylindrical vessel.
+The process involves supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract.
+Parameters such as the feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) are adjustable and measurable, as is the vessel pressure ($P$), whereas the outlet temperature ($T_{out}$) can only be monitored.
+A simplified flow diagram is presented in Figure \ref{fig: SFE_drawing}, illustrating the process setup.
+
 	\begin{figure}[h!]
@@
 
-	This study aims to develop a process model for extracting natural substances from solid materials and liquids using supercritical fluids, specifically supercritical $CO_2$.
-To achieve this, the model parameters are estimated based on thermodynamic relations and a set of experiments conducted at various conditions.
+	%This study aims to develop a process model for extracting natural substances from solid materials and liquids using supercritical fluids, specifically supercritical $CO_2$.
+To achieve this, the solvent properties are estimated based on thermodynamic relations, and the extraction kinetic parameters are estimated based on a set of experiments conducted under various conditions.
 The maximum likelihood estimator is used to solve the parameter estimation problem, and the obtained parameters are subjected to regression to derive correlations.
@@
 
-	The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties.
+	%The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties.
 Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations.
@@
 The maximum likelihood technique is presented in Chapter \ref{CH: Parameter_estimation} and is then combined with the process model.
-Chapter \ref{CH: Experiments} describes the experimental work and the data collected from experiments are used to estimate missing parameters related to the extraction kinetic.
-Finally, the parameter estimations and simulation results are discussed in Chapters \ref{CH: Results} and \ref{CH: Conclusion}
+Chapter \ref{CH: Experiments} describes the experimental work and the data collected from experiments, which are used to estimate missing parameters related to the extraction kinetics.
+Finally, the parameter estimations and simulation results are discussed in Chapters \ref{CH: Results} and \ref{CH: Conclusion}.
+
+	This study focuses on creating a process model for the extraction of natural substances from solid materials using supercritical fluids, with a particular emphasis on supercritical $CO_2$.
+The approach involves estimating the solvent properties through thermodynamic relationships and determining the extraction kinetic parameters via a series of experiments conducted under a variety of conditions.
+The maximum likelihood estimator method is employed to address the parameter estimation challenge, with the derived parameters subsequently used to establish correlations.
+These correlations are instrumental in extending the applicability of the process model across different temperatures (30 to 40$^\circ C$) and pressures (100 to 200 bar).
+
+	The organization of the study is as follows: Chapter \ref{CH: Thermodynamic} offers an overview of supercritical fluids, aiming to acquaint the reader with their unique properties.
+Chapter \ref{CH:Governing_equations_chapter} outlines the fundamental balance equations.
+These equations are then integrated with the extraction kinetic equation in Chapter \ref{CH: Extraction_model} to formulate the process model.
+Chapter \ref{CH: Parameter_estimation} introduces the maximum likelihood estimation technique, which is subsequently applied within the context of the process model.
+Chapter \ref{CH: Experiments} details the experimental procedures and the data acquisition necessary for estimating the kinetic parameters related to the extraction process.
+The study culminates in Chapters \ref{CH: Results} and \ref{CH: Conclusion}, where the parameter estimations and simulation outcomes are thoroughly analysed and discussed.
 

### 2024-02-22 SFE_article_Parameter_Estimation - Chamomile/Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
22.02

@@
 % ===================================================
-\title[mode=title]{Supercritical fluid extraction of essential oil from chamomile seeds: modelling, and parameter estimation}                      
-\shorttitle{Supercritical fluid extraction of essential oil from chamomile seeds: modelling, and parameter estimation}
+\title[mode=title]{Supercritical fluid extraction of essential oil from chamomile flowers: modelling, and parameter estimation}                      
+\shorttitle{Supercritical fluid extraction of essential oil from chamomile flowers: modelling, and parameter estimation}
 
@@
 \begin{abstract}
-This study investigated the supercritical extraction process of chamomile oil from chamomile seeds.
+This study investigated the supercritical extraction process of chamomile extract from chamomile flowers.
 A distributed-parameter model describes the fluid-solid extraction process.
@@
 The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
-Key model parameters included partition factor internal and axial diffusion coefficients were determined using maximum likelihood estimation from experimental data, assuming normal error.
-A set of laboratory experiments was performed in under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s.
+Model parameters, including the partition factor, internal diffusion coefficient, axial diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data, with the assumption of normally distributed errors.
+A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s.
 
@@
 \subsection{Governing equations} \label{CH:Governing_equations_chapter}
-	The governing equation for a quasi-one-dimensional compressible flow in Cartesian coordinates can be found in the Appendix \ref{CH: Gouverning equations} and in the work of \citet{Anderson1995}.
-Quasi-one-dimensional flow is a fluid flow characterized by the assumption that the flow properties remain uniform across any given cross-section of the flow.
-This assumption is made when there is a variation in the cross-sectional area of the flow channel, such as an irregular shape or partial filling of an extractor.
-In such cases, the flow is considered to be quasi-one-dimensional because the velocity and other flow properties are assumed to vary only in the direction of flow.
+	The governing equations for quasi-one-dimensional compressible flow in Cartesian coordinates are detailed in Appendix \ref{CH: Gouverning equations} and are based on the foundational work by \citet{Anderson1995}.
+Quasi-one-dimensional flow refers to a fluid flow scenario where it's assumed that flow properties are uniformly distributed across any given cross-section.
+This simplification is typically applied in situations where the flow channel's cross-sectional area changes, such as through irregular shapes or partial fillings of an extractor.
+In these instances, the flow is considered quasi-one-dimensional because it's presumed that velocity and other flow properties change solely along the flow direction.
 
-The quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates are given by Equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_3}.
-The derivation of these Equations are presented in Appendix \ref{CH: Gouverning equations}.
+	The set of quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates are encapsulated by Equations \ref{EQ: CompressibleEuler_1} through \ref{EQ: CompressibleEuler_3}.
+The formulation of these equations is elaborated upon in Appendix \ref{CH: Gouverning equations}, providing a mathematical foundation for analyzing flow dynamics under the assumed conditions.
 
@@
 
-These relations are equally valid if the two regions are separated by a region of finite width rather than a discontinuity.
+These relations are equally valid if both regions are separated by a region of finite width rather than a discontinuity.
 
@@
 
+The low Mach number condition leads to the incompressible condition: $\nabla \cdot \mathbf {u} =0$, which is valid for constant density (strict incompressible) or varying density flow.
+The restraint allows for the removal of acoustic waves, but also allows for large perturbations in density and/or temperature.
+The assumption is that the flow remains within a Mach number limit (normally less than 0.3) for any solution using such a constraint to be valid.
+In 1-D case the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.
+
 \subsection{Extraction model} \label{CH: Extraction_model}
@@
 
-%This study presented basic aspects regarding the laboratory work for obtaining chamomile extracts using supercritical carbon dioxide at different operating conditions.
-A first-principle process model was developed based on governing equations.
-As a result of the literature review, the extraction kinetic model was selected and combined with the general mass balance equations.
-The values of unknown parameters in the process model were obtained by parameter estimation.
-The yield data from the experiments were compared against the yield generated by the model.
-The IPOPT solver was used to solve the maximum likelihood estimation.
-The process model was found to have good agreement with experimental yield curves.
-Later, the parameters found for each experiment were combined to obtain more general relationships.
-The correlations for diffusion and decay coefficients are presented as a function of fluid density or Reynolds number.
-It should be noted that obtained correlations have been prepared with a limited amount of data.
-These correlations can be used to study qualitatively the impact of different operating conditions on the extraction yield by different methods, such as sensitivity analysis.
-Moreover, the generalized model could be useful in finding the optimal operating conditions with respect to the process economy.
+The article presents a comprehensive study on supercritical fluid extraction of essential oil from chamomile flowers, focusing on developing and applying a distributed-parameter model to describe the fluid-solid extraction process.
+By employing the concept of quasi-one-dimensional flow, the study simplifies the spatial dimensions of the extraction process, ensuring uniform flow across any cross-section while allowing for variations in the area available for the fluid phase.
+The physical properties of the solvent are estimated using the Peng-Robinson equation of state, and key model parameters are determined through maximum likelihood estimation based on experimental data, considering normally distributed errors.
+
+Laboratory experiments were conducted under various conditions to validate the model's effectiveness.
+The model parameters, such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data.
+The parameter space exploration revealed that while some parameters could be determined with a high degree of confidence, others, like the axial diffusion coefficient, had a low impact on the model's output.
+
+The Reynolds number and Hildebrand solubility parameter were used to analyse the obtained parameters further.
+The linear correlations between parameters and the Reynolds numbers are presented.
+$D_i^R$ coefficient decreases with the Reynolds number due to higher fluids density and the corresponding mass transfer resistance, while $\Upsilon$ increases due to increased Hildebrand parameter.
+It should be noted that outside of the confidence region, the parameters can become negative, which might reverse the direction of the mass transfer.
+
+The presented model might be used as a first approximation and for generating first estimates of the parameters for data correlation.
+The presented model can be further used with presented correlations to introduce an extraction model with dynamically changing operating conditions for multiple purposes such as techno-economic analysis, optimal design of experiments, or yield maximisation.
 

### 2024-02-28 SFE_article_Parameter_Estimation - Chamomile/Sections/Results_Chamomile.tex
28.02

@@
 
+	A more general relationship can be obtained by applying multiple linear regression instead of linear regression.
+The clusters in Figure \ref{fig: Correlations} are close to parallel, suggesting that a plane would combine all the data points.
+The Reynolds number and flow rate act as independent variables for $D_i^R$ and $\Upsilon$ as presented in Figure \ref{fig: Correlations_surface}.
+
+	\begin{figure}[!h]
+		\centering
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Di_Re_F.png}
+			\caption{Multiple linear regression $D_i^R = f(Re, F)$}
+			\label{fig: Correlations_Di_Re_F}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Gamma_Re_F.png}
+			\caption{Multiple linear regression $\Upsilon = f(Re, F)$}
+			\label{fig: Correlations_Gamma_Re_F}
+		\end{subfigure}
+		\caption{Parameter estimation results}
+		\label{fig: Correlations_surface}
+	\end{figure}
+
 \end{document}

### 2024-02-28 SFE_article_Parameter_Estimation - Chamomile/Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
28.02

@@
 
-Laboratory experiments were conducted under various conditions to validate the model's effectiveness.
+Laboratory experiments were conducted under various conditions to validate the model.
 The model parameters, such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data.
 The parameter space exploration revealed that while some parameters could be determined with a high degree of confidence, others, like the axial diffusion coefficient, had a low impact on the model's output.
+The identification of the low impact parameters lead to model reduction
 
@@
 $D_i^R$ coefficient decreases with the Reynolds number due to higher fluids density and the corresponding mass transfer resistance, while $\Upsilon$ increases due to increased Hildebrand parameter.
-It should be noted that outside of the confidence region, the parameters can become negative, which might reverse the direction of the mass transfer.
+It should be noted that outside of the confidence region, the parameters can become negative, which might reverse the direction of the mass transfer and leads to unfeasible solution.
 
-The presented model might be used as a first approximation and for generating first estimates of the parameters for data correlation.
-The presented model can be further used with presented correlations to introduce an extraction model with dynamically changing operating conditions for multiple purposes such as techno-economic analysis, optimal design of experiments, or yield maximisation.
+The presented model can be further used with presented correlations to introduce an extraction model with dynamically changing operating conditions for multiple purposes such as yield maximisation, techno-economic analysis, or optimal design of experiments.
 

### 2024-02-28 SFE_Sensitivity_Analysis_Chamomile/Diffusion.m

@@ -1,8 +1,8 @@
-function D = Diffusion(RE, parameters)
+function D = Diffusion(Re, F, parameters)
 
     a = parameters{44};
     b = parameters{45};
 
-    D =  a.* RE + b;
+    D =  -0.131 - 8.337 .* Re + 0.687 * (F * 10^5);
     
 end

### 2024-02-28 SFE_Sensitivity_Analysis_Chamomile/Fit_Correlations.m

@@ -42,7 +42,7 @@ hold off
 text(0.35, 2.0, sprintf('$~ D_i^R = %.3f \\cdot Re + %.3f$ \n $R^2=%.3f$',[p1, stuff1.rsquare]))
 text(0.15, -1.0, sprintf('$~ D_i^R = %.3f \\cdot Re + %.3f$ \n $R^2=%.3f$',[p2, stuff2.rsquare]))
 
-legend([plt1(1),plt2(1)],'$3.33\times 10^{-5}[kg/s]$','$6.67\times 10^{-5}[kg/s]$','Location','best');
+legend([plt1(1),plt2(1)],'$6.67\times 10^{-5}[kg/s]$','$3.33\times 10^{-5}[kg/s]$','Location','best');
 legend box off
 
 ylabel('$D_i^R \times 10^{-13} [m^2/s]$')
@@ -50,15 +50,15 @@ ylabel('$D_i^R \times 10^{-13} [m^2/s]$')
 xlabel('Re [-]')
 set(gca,'FontSize',12)
 
-exportgraphics(figure(1), ['Correlation_Di_Re.png'], "Resolution",300);
-close all
+%exportgraphics(figure(1), ['Correlation_Di_Re.png'], "Resolution",300);
+%close all
 
 %% gamma function plot
 %{\
 C0 = 1;
 XX = C0:-0.01:0;
 
-%subplot(3,1,3)
+figure()
 for ii=1:12
 
     %RE_temp = sort(RE, 'descend');
@@ -82,3 +82,71 @@ set(gca,'FontSize',42)
 %exportgraphics(figure(1), ['Gamma_function.png'], "Resolution",300);
 %close all
 %}
+
+%% Fit a surface in RE and F space
+
+figure()
+[ml3, sf3] = fit([RHO', FF'],DI','poly11');
+h3 = plot(ml3, [RHO', FF'],DI');
+set(h3,'linestyle','none');
+alpha(.5)
+
+p3 = coeffvalues(ml3);
+text(-0.25, 2.7, 0.1, sprintf('$D_i^R = %.3f %.3f \\cdot Re + %.3f \\cdot F$ \n $R^2 = %.3f $',[p3, sf3.rsquare]))
+xlabel('Re[-]',Position=[0.12, 0.5, 0.7])
[…]

### 2024-03-12 SFE_article_Parameter_Estimation - Chamomile/Sections/Results_Chamomile.tex
12.03

--- 2024-02-22 SFE_article_Parameter_Estimation - Chamomile/Sections/Results_Chamomile.tex
@@
 Within the model context characterized by linear kinetics, two parameters remain to be determined: the partition coefficient $k_m$ and the internal diffusion coefficient $D_i$.
-
-	\begin{figure}[!h]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_Space_Linear_Dataset_1.png}
-		\caption{Parameter space for the linear extraction kinetic model and the experiment 1}
-		\label{fig: Fit_1_linear}
-	\end{figure}
 
@@
 
-	\begin{figure}[!h]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_Space_Di_Dx_Dataset_1.png}
-		\caption{Parameter space for the reduced linear extraction kinetic model with and the experiment 1}
-		\label{fig: Fit_1_Di_Dx}
-	\end{figure}
-
 	Similarly to the previous case, the optimal value of $D_i$ exists, but a unique value for the $D_e^M$ cannot be determined.
@@
 	In both scenarios previously discussed, the fitting outcomes were not deemed satisfactory.
-Building upon the concepts underlying the Broken-and-Intact and Shrinking Core models (detailed in Chapter \ref{CH: Gamma_Function}), a gamma function is introduced to capture the diminishing extraction kinetics.
+Building upon the concepts underlying the Broken-and-Intact and Shrinking Core models (detailed in Chapter \ref{CH: Gamma_Function}), the gamma function is introduced to capture the decreasing extraction kinetics.
 The correction factor is combined with the simplified linear model, resulting in a two-parameter model ($D_i^R$ and $\Upsilon$) as given by Equation \ref{Model_kinetic}.
 Figure \ref{fig: Fit_1_Di_Gamma} shows the parameter space and the corresponding cost function values.
-
-	\begin{figure}[!h]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=0.98\columnwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
-		\caption{Parameter space for the modified extraction model and experiment 1}
-		\label{fig: Fit_1_Di_Gamma}
-	\end{figure}
 
@@
 
-	\begin{figure}[!h]
+	\begin{figure*}[!h]
 		\centering
-		\begin{subfigure}[b]{\columnwidth}
+		\begin{subfigure}{0.3\textwidth}
 			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
 			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
@@
 		\hfill
-		\begin{subfigure}[b]{\columnwidth}
+		\begin{subfigure}{0.3\textwidth}
 			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
 			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
@@
 		\end{subfigure}
-			\end{figure}%
-		\begin{figure}[h!]\ContinuedFloat
-		\begin{subfigure}[b]{\columnwidth}
+		\hfill
+		\begin{subfigure}{0.3\textwidth}
 			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
 			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
@@
 		\label{fig: Fit_Di_Gamma}
-	\end{figure}
+	\end{figure*}
 
+	\begin{figure*}[!h]
+		\centering
+		\begin{subfigure}{0.24\textwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Correlation_Di_Re.png}
+			\caption{Linear regression $D_i^R = f(Re)$}
+			\label{fig: Correlations_Di_Re}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.24\textwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Correlation_Gamma_Re.png}
+			\caption{Linear regression $\Upsilon = f(Re)$}
+			\label{fig: Correlations_Gamma_Re}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.24\textwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Di_Re_F.png}
+			\caption{Multiple linear regression $D_i^R = f(Re, F)$}
+			\label{fig: Correlations_Di_Re_F}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.24\textwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Gamma_Re_F.png}
+			\caption{Multiple linear regression $\Upsilon = f(Re, F)$}
+			\label{fig: Correlations_Gamma_Re_F}
+		\end{subfigure}
+		\caption{Parameter estimation results}
+		%\label{fig: Correlations_surface}
+	\end{figure*}
+
+	\iffalse
 	The estimated parameters describe the diminishing trend of the internal diffusion coefficient $D_i$, as delineated by Equation \ref{EQ: C_sat_function}.
@@
 
+	\fi	
 	The parameter estimation results are combined to analyse the relationship between the obtained parameters and the operating conditions.
@@
 The decrease in $D_i^R$ across each data line can be attributed to higher fluid density and increased mass transfer resistance.
-Conversely, the rise in $\Upsilon$ correlations may be explained by enhanced solubility.
+%Conversely, the rise in $\Upsilon$ correlations may be explained by enhanced solubility.
 The Hildebrand solubility factor and the Reynolds number are proportional to the fluid density; hence, $\Upsilon$ can be correlated with Re.
 
-	\begin{figure}[!h]
+	A more general relationship can be obtained by applying multiple linear regression instead of linear regression.
+The clusters in Figure \ref{fig: Correlations_Di_Re}  and \ref{fig: Correlations_Gamma_Re} are close to parallel, suggesting that a plane would combine all the data points.
+The Reynolds number and flow rate act as independent variables for $D_i^R$ and $\Upsilon$ as presented in Figures \ref{fig: Correlations_Di_Re_F} and \ref{fig: Correlations_Gamma_Re_F}.
+The presented correlations are valid in the whole range of investigated operating conditions.
+
+	The correlations are later used against the original dataset to show that the correlations can reproduce the results with satisfactory accuracy.
+Figure \ref{fig: Fit_Di_Gamma_correlation} shows the results of the simulations with incorporated correlations.
+A good agreement between simulation results and the dataset can be observed.
+If Figures \ref{fig: Fit_Di_Gamma} and \ref{fig: Fit_Di_Gamma_correlation} are compared, a decrease in the accuracy of simulations can be observed.
+Such a behaviour is expected due the bias–variance trade-off, which describes the relationship between a model's complexity and the accuracy of its predictions.
+
+	\begin{figure*}[!h]
 		\centering
-		\begin{subfigure}[b]{\columnwidth}
+		\begin{subfigure}{0.3\textwidth}
 			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Di_Re.png}
-			\caption{Linear regression $D_i^R = f(Re)$}
-			\label{fig: Correlations_Di_Re}
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_1_4_correlation.png}
+			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
+			\label{fig: Fit_1_4_Di_Gamma_correlation}
 		\end{subfigure}
 		\hfill
-		\begin{subfigure}[b]{\columnwidth}
+		\begin{subfigure}{0.3\textwidth}
 			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Gamma_Re.png}
-			\caption{Linear regression $\Upsilon = f(Re)$}
-			\label{fig: Correlations_Gamma_Re}
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_5_8_correlation.png}
+			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
+			\label{fig: Fit_5_8_Di_Gamma_correlation}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.3\textwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_9_12_correlation.png}
+			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
+			\label{fig: Fit_9_12_Di_Gamma_correlation}
 		\end{subfigure}
 		\caption{Parameter estimation results}
-		\label{fig: Correlations}
-	\end{figure}
+		\label{fig: Fit_Di_Gamma_correlation}
+	\end{figure*}
 

### 2024-03-12 SFE_article_Parameter_Estimation - Chamomile/Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
12.03

@@
 
+\begin{figure*}[!b]
+	\centering
+	\begin{subfigure}{0.3\textwidth}
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Parameter_Space_Linear_Dataset_1.png}
+		\caption{Parameter space for the linear extraction kinetic model and the experiment 1}
+		\label{fig: Fit_1_linear}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{0.3\textwidth}
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Parameter_Space_Di_Dx_Dataset_1.png}
+		\caption{Parameter space for the reduced linear extraction kinetic model with axial diffusion and the experiment 1}
+		\label{fig: Fit_1_Di_Dx}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{0.3\textwidth}
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
+		\caption{Parameter space for the modified extraction model and experiment 1}
+		\label{fig: Fit_1_Di_Gamma}
+	\end{subfigure}
+	\caption{Parameter estimation results}
+	%\label{fig: Fit_Di_Gamma}
+\end{figure*}
+
 \subsection{Experimental work}
@@
 The parameter space exploration revealed that while some parameters could be determined with a high degree of confidence, others, like the axial diffusion coefficient, had a low impact on the model's output.
-The identification of the low impact parameters lead to model reduction
+The identification of the low-impact parameters leads to model reduction
 
-The Reynolds number and Hildebrand solubility parameter were used to analyse the obtained parameters further.
-The linear correlations between parameters and the Reynolds numbers are presented.
-$D_i^R$ coefficient decreases with the Reynolds number due to higher fluids density and the corresponding mass transfer resistance, while $\Upsilon$ increases due to increased Hildebrand parameter.
-It should be noted that outside of the confidence region, the parameters can become negative, which might reverse the direction of the mass transfer and leads to unfeasible solution.
+This work introduced a set of correlations to find a general relationship between parameters and the independent variables, which can be determined by operating conditions.
+The obtained correlations were introduced into the model and tested against the dataset.
+The results show good agreement between the simulation results and all the data points.
 
-The presented model can be further used with presented correlations to introduce an extraction model with dynamically changing operating conditions for multiple purposes such as yield maximisation, techno-economic analysis, or optimal design of experiments.
+The presented model can be further used with the presented correlations to introduce an extraction model with dynamically changing operating conditions for multiple purposes, such as yield maximisation, techno-economic analysis, or optimal experiments design.
 

### 2024-03-12 SFE_Parameter_Estimation_Chamomile/Fit_Correlations.m

@@ -3,8 +3,8 @@ delete(gcp('nocreate'));
 
 %%
 AA = xlsread('Regression.xlsx');
-DI = [0.701472275, 1.331443055, 2.239307889, 2.711813187, 1.32629228, 1.485504345, 1.73827467, 2.59502961, 0.48656241, 1.363499511, 0.72227, 0.756214019];
-GG = [4.274825704, 2.189390368, 2.552240039, 1.365163176, 2.830760407, 2.573487374, 1.642279591, 1.906200052, 4.287215235, 2.723682117, 3.82240, 3.35589348];
+DI = [0.71383013	1.076801997	2.179470155	2.475532632	1.390707877	1.336111172	1.882954204	2.457886055	0.564935512	1.542106938	0.835725102	0.87349666];
+GG = [4.229739602	3.091520556	2.359538225	1.132795818	2.204975712	2.739220425	1.868538631	1.69935869	3.452308202	1.995905641	3.012676539	2.596460037];
 RE = [0.4632, 0.3783, 0.3029, 0.2619, 0.3579, 0.3140, 0.2635, 0.2323, 0.1787, 0.1160, 0.1889, 0.1512];
 TT = [313, 313, 313, 313, 303, 303, 303, 303, 303, 303, 313, 313];
 Tr = TT ./ 304;
@@ -28,6 +28,7 @@ xtest  = linspace(0.1,0.5);
 ytest1 = polyval(p1,xtest);
 ytest2 = polyval(p2,xtest);
 
+%{\
 hold on
 plt1 = plot(x1,y1,'ko', 'LineWidth',2);
 plt2 = plot(x2,y2,'kd', 'LineWidth',2);
@@ -39,10 +40,10 @@ hold off
 %text(0.3, 4.0, sprintf('~$~\\Upsilon = %.3f \\cdot + Re %.3f$ \n $R^2=%.3f$',[p1, stuff1.rsquare]))
 %text(0.15, 6.0, sprintf('~$~ \\Upsilon = %.3f \\cdot Re + %.3f$ \n $R^2=%.3f$',[p2, stuff2.rsquare]))
 
-text(0.35, 2.0, sprintf('$~ D_i^R = %.3f \\cdot Re + %.3f$ \n $R^2=%.3f$',[p1, stuff1.rsquare]))
[…]

### 2024-03-12 SFE_Parameter_Estimation_Chamomile/main_Parameter_Estimation_Chamomile.m

@@ -6,17 +6,17 @@ delete(gcp('nocreate'));
 addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
 import casadi.*
 
-excel_file = 'Chamomile_Di_Gamma_org.xls';
+excel_file = 'Chamomile_Di_Gamma_2.xls';
 rng(69)
 
 %%
 Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
 Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
 
-LabResults              = xlsread('wpd_datasets.xlsx');
+LabResults              = xlsread('dataset_2.xlsx');
 
 N_trial                 = 1;
-Iteration_max           = 20;                                              % Maximum number of iterations for optimzer
+Iteration_max           = 15;                                              % Maximum number of iterations for optimzer
 Time_max                = 12;                                               % Maximum time of optimization in [h]
 
 nlp_opts                    = struct;
@@ -39,7 +39,7 @@ DI = [0.701472275, 1.331443055, 2.239307889, 2.711813187, 1.32629228, 1.48550434
 GG = [4.274825704, 2.189390368, 2.552240039, 1.365163176, 2.830760407, 2.573487374, 1.642279591, 1.906200052, 4.287215235, 2.723682117, 3.82240, 3.35589348];
 
 %% Load paramters
-m_total                 = 3.5;
+m_total                 = 3.0;
 
 % Bed geometry
 before                  = 0.04;                                             % Precentage of length before which is empty
@@ -58,7 +58,7 @@ Time                    = [0 Time_in_sec/60];                               % Mi
 
 N_Time                  = length(Time_in_sec);
 
-SAMPLE                  = LabResults(21:34,1);
+SAMPLE                  = LabResults(6:19,1);
 
 % Check if the number of data points is the same for both the dataset and the simulation
 N_Sample                = [];
@@ -144,16 +144,19 @@ m_fluid                 = G(L_bed_after_nstages)*( L_bed_after_nstages(2) ); % L
[…]

### 2024-03-12 SFE_Parameter_Estimation_Chamomile/plot_Fitting_Results.m

@@ -1,14 +1,14 @@
 startup;
 delete(gcp('nocreate'));
 
-addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
-%addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
 import casadi.*
 
 %%
 AA = xlsread('Regression.xlsx');
-DI = [0.701472275, 1.331443055, 2.239307889, 2.711813187, 1.32629228, 1.485504345, 1.73827467, 2.59502961, 0.48656241, 1.363499511, 0.72227, 0.756214019];
-GG = [4.274825704, 2.189390368, 2.552240039, 1.365163176, 2.830760407, 2.573487374, 1.642279591, 1.906200052, 4.287215235, 2.723682117, 3.82240, 3.35589348];
+DI = [0.71383013	1.076801997	2.179470155	2.475532632	1.390707877	1.336111172	1.882954204	2.457886055	0.564935512	1.542106938	0.835725102	0.87349666];
+GG = [4.229739602	3.091520556	2.359538225	1.132795818	2.204975712	2.739220425	1.868538631	1.69935869	3.452308202	1.995905641	3.012676539	2.596460037];
 RE = [0.4632, 0.3783, 0.3029, 0.2619, 0.3579, 0.3140, 0.2635, 0.2323, 0.1787, 0.1160, 0.1889, 0.1512];
 TT = [313, 313, 313, 313, 303, 303, 303, 303, 303, 303, 313, 313];
 Tr = TT ./ 304;
@@ -18,12 +18,12 @@ RHO= [630, 691, 793, 840, 772, 802, 856, 891, 772, 891, 691, 793];
 Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
 Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
 
-LabResults              = xlsread('wpd_datasets.xlsx');
+LabResults              = xlsread('dataset_2.xlsx');
 
 which_k                 = [44, 46];
 
 %% Load paramters
-m_total                 = 3.5;
+m_total                 = 3.0;
 
 % Bed geometry
 before                  = 0.04;                                             % Precentage of length before which is empty
[…]

### 2024-03-13 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
13.03

--- 2024-02-22 SFE_article_Parameter_Estimation - Chamomile/Sections/Model.tex
@@
 				\begin{equation} \label{Model_kinetic_basic}
-					{\color{black}r_e}(t,z) = \cfrac{{\color{black}D_i}({\color{black}T}(t,z), {\color{black}P}(t))}{{\color{black} \mu l^2} }\left({\color{black}c_s}(t,z) - {\color{black}c_P^*}(t,z) \right)
+					{\color{black}r_e}(t,z) = \cfrac{{\color{black}D_i}({\color{black}T}(t,z), {\color{black}P}(t), F(t))}{{\color{black} \mu l^2} }\left({\color{black}c_s}(t,z) - {\color{black}c_P^*}(t,z) \right)
 			\end{equation} }
@@
 					\label{Model_kinetic_no_sat}
-					{\color{black}r_e}(t,z) = -\cfrac{{\color{black}D_i}({\color{black}T}(t,z), {\color{black}P}(t))}{{\color{black} \mu l^2} }\left({\color{black}c_s}(t,z) - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right)
+					{\color{black}r_e}(t,z) = -\cfrac{{\color{black}D_i}({\color{black}T}(t,z), {\color{black}P}(t), F(t))}{{\color{black} \mu l^2} }\left({\color{black}c_s}(t,z) - \cfrac{{\color{black}\rho_s}c_f(t,z)}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))}   \right)
 			\end{equation} }
@@
 
+		\iffalse	
 		\subsubsection{Heat balance} \label{CH: heat_balance}
 
-		\iffalse
 		 {\color{black}
@@
 %		\todo[inline]{Draft of new heat equation starts here. TODO: \\ Check if the heat cpacity of solid phase needs to be added \\ Elaborate why pressure is know}
-		\fi
 
@@
 
+  		\fi
+
 		\subsubsection{Extraction yield} \label{CH: Yield}
@@
 Considering that it is assumed that the $c_{f0}=0$.
-Moreover, it is considered that the initial temperature of the extractor in every place is the same and described by ${\color{black}h_0}$.
+Moreover, it is considered that the extractor is isothermal and described by ${\color{black}h_0}$.
 Therefore, the initial conditions employed in the simulation are:
@@
 
-		\subsubsection{State-space representation} \label{CH: State_space}
+		\subsubsection{Discretization methods}
 
-		The process model can be written in a general form:
-
-		{\footnotesize
-			\begin{align}
-				\begin{bmatrix}
-					\cfrac{\partial {\color{black}c_f}(t,z)}{\partial t}\\
-					\cfrac{\partial {\color{black}c_s}(t,z)}{\partial t}\\
-					\cfrac{\partial {\color{black}h}(t,z)}{\partial t} \\
-					\cfrac{\partial {\color{black}P}(t,z)}{\partial t} \\
-					\cfrac{\partial {\color{black}y}(t)}{\partial t} 
-				\end{bmatrix}
-				& =
-				\begin{bmatrix}
-					{\color{black}\bar{\phi_1}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
-					{\color{black}\bar{\phi_2}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
-					{\color{black}\bar{\phi_3}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right) \\
-					{\color{black}\bar{\phi_4}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
-					{\color{black}\bar{\phi_5}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)
-				\end{bmatrix} = {\color{black}\bar{\phi}} \left( t,z; {\color{black}\Theta} \right) = \cfrac{\partial {\color{black}\chi}(t,z)}{\partial t}
-		\end{align} }
-
-		where ${\color{black}\Theta}$ is a paramter space, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.
-
-		Function ${\color{black}\bar{\phi}}$ are transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{black}G}$.
-The state-space model ${\color{black}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{black}x}}(t)$.
+		The method of lines is used to transform the process model equations into a set of ODEs denoted as ${\color{black}G}({\color{black}x}(t);{\color{black}\Theta})$.
+The partial derivatives in $z$-direction are computed using a first-order and second-order finite difference approximation.
+The backward finite difference is used to approximate the first-order derivative, while the central difference scheme is used to approximate the second-order derivative.
+The length of the fixed bed is divided into $N_z$ equally distributed points in $z$-direction.
+The state-space model after the discretization is represented by $\dot{{\color{black}x}}(t)$.
 
@@
 
-			where ${\color{black}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{black}\Theta} \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of model parameters, $N_{u}$ is the number of control variables.
-
-			In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases (${\color{black}c_f}(t,z)$ and ${\color{black}c_s}(t,z)$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{black}h}(t,z)$).
-The controllable input variables are the mass flow rate and temperature of the solvent in the feed and the pressure in the extractor.
-Additionally, the pressure change is augmented with the state-space and denoted as ${\color{black}P}(t)$.
-			The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase, and it can be measured after the separator (${\color{black}Y}(t)$).
-The system is controllable by manipulating the flow rate and temperature (enthalpy) of $CO_2$ in the feed and the pressure in the extractor.
-
-			\subsubsection{Discretization methods}
-
-			The method of lines is used to transform the process model equations into a set of ODEs denoted as ${\color{black}G}({\color{black}x}(t);{\color{black}\Theta})$.
-The partial derivatives in $z$-direction are computed using a first-order and second-order finite difference approximation.
-The backward finite difference is used to approximate the first-order derivative, while the central difference scheme is used to approximate the second-order derivative.
-The length of the fixed bed is divided into $N_z$ equally distributed points in $z$-direction.
+		where ${\color{black}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{black}\Theta} \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters, $N_{u}$ is the number of control variables.
 
@@
 To ensure mass conservation, discretization is applied to the conservative form of the process model.
+
+		\iffalse
+		\subsubsection{State-space representation} \label{CH: State_space}
+
+		The process model can be written in a general form:
+
+		{\footnotesize
+			\begin{align}
+				\begin{bmatrix}
+					\cfrac{\partial {\color{black}c_f}(t,z)}{\partial t}\\
+					\cfrac{\partial {\color{black}c_s}(t,z)}{\partial t}\\
+					\cfrac{\partial {\color{black}h}(t,z)}{\partial t} \\
+					\cfrac{\partial {\color{black}P}(t,z)}{\partial t} \\
+					\cfrac{\partial {\color{black}y}(t)}{\partial t} 
+				\end{bmatrix}
+				& =
+				\begin{bmatrix}
+					{\color{black}\bar{\phi_1}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
+					{\color{black}\bar{\phi_2}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
+					{\color{black}\bar{\phi_3}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right) \\
+					{\color{black}\bar{\phi_4}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
+					{\color{black}\bar{\phi_5}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)
+				\end{bmatrix} = {\color{black}\bar{\phi}} \left( t,z; {\color{black}\Theta} \right) = \cfrac{\partial {\color{black}\chi}(t,z)}{\partial t}
+		\end{align} }
+
+		where ${\color{black}\Theta}$ is a paramter space, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.
+
+		\fi
+
+		%Function ${\color{black}\bar{\phi}}$ are transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{black}G}$.
+		%The state-space model ${\color{black}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{black}x}}(t)$.
+
+		In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases (${\color{black}c_f}(t,z)$ and ${\color{black}c_s}(t,z)$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{black}h}(t,z)$).
+The controllable input variables are the mass flow rate and temperature of the solvent in the feed and the pressure in the extractor.
+Additionally, the pressure change is augmented with the state-space and denoted as ${\color{black}P}(t)$.
+		The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase, and it can be measured after the separator (${\color{black}Y}(t)$).
+The system is controllable by manipulating the flow rate and temperature (enthalpy) of $CO_2$ in the feed and the pressure in the extractor.
 

### 2024-03-13 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Results_Chamomile.tex
13.03

--- 2024-03-12 SFE_article_Parameter_Estimation - Chamomile/Sections/Results_Chamomile.tex
@@
 	\label{CH: Results}
+
+	\begin{figure*}[!h]
+		\centering
+		\begin{subfigure}{0.3\textwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
+			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
+			\label{fig: Fit_1_4_Di_Gamma}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.3\textwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
+			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
+			\label{fig: Fit_5_8_Di_Gamma}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.3\textwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
+			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
+			\label{fig: Fit_9_12_Di_Gamma}
+		\end{subfigure}
+		\caption{Parameter estimation results}
+		\label{fig: Fit_Di_Gamma}
+	\end{figure*}
 
@@
 
-	\begin{figure*}[!h]
-		\centering
-		\begin{subfigure}{0.3\textwidth}
-			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
-			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
-			\label{fig: Fit_1_4_Di_Gamma}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}{0.3\textwidth}
-			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
-			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
-			\label{fig: Fit_5_8_Di_Gamma}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}{0.3\textwidth}
-			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
-			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
-			\label{fig: Fit_9_12_Di_Gamma}
-		\end{subfigure}
-		\caption{Parameter estimation results}
-		\label{fig: Fit_Di_Gamma}
-	\end{figure*}
-
-	\begin{figure*}[!h]
-		\centering
-		\begin{subfigure}{0.24\textwidth}
-			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Correlation_Di_Re.png}
-			\caption{Linear regression $D_i^R = f(Re)$}
-			\label{fig: Correlations_Di_Re}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}{0.24\textwidth}
-			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Correlation_Gamma_Re.png}
-			\caption{Linear regression $\Upsilon = f(Re)$}
-			\label{fig: Correlations_Gamma_Re}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}{0.24\textwidth}
-			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Di_Re_F.png}
-			\caption{Multiple linear regression $D_i^R = f(Re, F)$}
-			\label{fig: Correlations_Di_Re_F}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}{0.24\textwidth}
-			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Gamma_Re_F.png}
-			\caption{Multiple linear regression $\Upsilon = f(Re, F)$}
-			\label{fig: Correlations_Gamma_Re_F}
-		\end{subfigure}
-		\caption{Parameter estimation results}
-		%\label{fig: Correlations_surface}
-	\end{figure*}
-
 	\iffalse
@@
 	\fi
+
 	The parameter estimation results are combined to analyse the relationship between the obtained parameters and the operating conditions.
@@
 Using the Reynolds number has the advantage of considering the influence of all the control variables (temperature, pressure and flow rate), which means it can be uniquely defined by selecting operating conditions.
+
+	\begin{figure}[!h]
+		\centering
+		\begin{subfigure}{0.48\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Di_Re.png}
+			\caption{Linear regression $D_i^R = f(Re)$}
+			\label{fig: Correlations_Di_Re}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.48\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Gamma_Re.png}
+			\caption{Linear regression $\Upsilon = f(Re)$}
+			\label{fig: Correlations_Gamma_Re}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.48\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Di_Re_F.png}
+			\caption{Multiple linear regression $D_i^R = f(Re, F)$}
+			\label{fig: Correlations_Di_Re_F}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.48\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Gamma_Re_F.png}
+			\caption{Multiple linear regression $\Upsilon = f(Re, F)$}
+			\label{fig: Correlations_Gamma_Re_F}
+		\end{subfigure}
+		\caption{Parameter estimation results}
+		%\label{fig: Correlations_surface}
+	\end{figure}
 
@@
 
-	\begin{figure*}[!h]
-		\centering
-		\begin{subfigure}{0.3\textwidth}
-			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_1_4_correlation.png}
-			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
-			\label{fig: Fit_1_4_Di_Gamma_correlation}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}{0.3\textwidth}
-			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_5_8_correlation.png}
-			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
-			\label{fig: Fit_5_8_Di_Gamma_correlation}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}{0.3\textwidth}
-			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_9_12_correlation.png}
-			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
-			\label{fig: Fit_9_12_Di_Gamma_correlation}
-		\end{subfigure}
-		\caption{Parameter estimation results}
-		\label{fig: Fit_Di_Gamma_correlation}
-	\end{figure*}
-
 \end{document}

### 2024-03-13 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Saturation.tex
13.03

--- 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Saturation.tex
@@
 
-	\subsubsection{Uneven distribution of the solute in the solid phase}
+	\subsubsection{Uneven distribution of the solute in the solid phase} \label{CH: Gamma_Function}
 
@@
 			\label{Model_kinetic}
-				{\color{black}r_e}(t,z) = -\cfrac{{\color{black}D_i^R}({\color{black}T}(t,z), {\color{black}P}(t)) {\color{black} \gamma}({\color{black} c_s} (t,z)) }{{\color{black} \mu l^2} } \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right)
+				{\color{black}r_e}(t,z) = -\cfrac{{\color{black}D_i^R}({\color{black}T}(t,z), {\color{black}P}(t), F(t)) {\color{black} \gamma}({\color{black} c_s} (t,z)) }{{\color{black} \mu l^2} } \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}c_f(t,z)}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  \right)
 		\end{equation} }

### 2024-03-13 SFE_article_Parameter_Estimation_short - Chamomile/Sections/introduction_imp.tex
13.03

--- 2024-02-22 SFE_article_Parameter_Estimation - Chamomile/Sections/introduction_imp.tex
@@
 Chamomile's aqueous extract is widely used as a gentle sedative to calm nerves and mitigate anxiety, hysteria, nightmares, insomnia, and other sleep-related conditions, according to \citet{Srivastava2009}.
-\citet{Orav2010} reported that oil yields from dried chamomile samples ranged from 0.7 to 6.7 mL kg$^{-1}$.
-Notably, the highest yields of essential oil, between 6.1 and 6.7 mL kg$^{-1}$, were derived from chamomile sourced from Latvia and Ukraine, while chamomile from Armenia exhibited a lower oil content of 0.7 mL kg$^{-1}$.
+\citet{Orav2010} reported that oil yields from dried chamomile samples ranged from 0.7 to 6.7 mL/kg.
+Notably, the highest yields of essential oil, between 6.1 and 6.7 mL/kg, were derived from chamomile sourced from Latvia and Ukraine, while chamomile from Armenia exhibited a lower oil content of 0.7 mL/kg.
 
@@
 
-	The organization of the study is as follows: Chapter \ref{CH: Thermodynamic} offers an overview of supercritical fluids, aiming to acquaint the reader with their unique properties.
+	%The organization of the study is as follows: Chapter \ref{CH: Thermodynamic} offers an overview of supercritical fluids, aiming to acquaint the reader with their unique properties. 
 	Chapter \ref{CH:Governing_equations_chapter} outlines the fundamental balance equations.

### 2024-03-13 SFE_article_Parameter_Estimation_short - Chamomile/Short_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
13.03

--- 2024-03-12 SFE_article_Parameter_Estimation - Chamomile/Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
@@
 
-\subsection{Supercritical fluids} \label{CH: Thermodynamic}
-\subfile{Sections/Thermo_imp}
+%\subsection{Supercritical fluids} \label{CH: Thermodynamic}
+%\subfile{Sections/Thermo_imp}
 
@@
 
-The low Mach number condition leads to the incompressible condition: $\nabla \cdot \mathbf {u} =0$, which is valid for constant density (strict incompressible) or varying density flow.
+The low Mach number condition leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow.
 The restraint allows for the removal of acoustic waves, but also allows for large perturbations in density and/or temperature.
@@
 \section{Conclusions} \label{CH: Conclusion}
+
+\begin{figure*}[!h]
+	\centering
+	\begin{subfigure}{0.3\textwidth}
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_1_4_correlation.png}
+		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
+		\label{fig: Fit_1_4_Di_Gamma_correlation}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{0.3\textwidth}
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_5_8_correlation.png}
+		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
+		\label{fig: Fit_5_8_Di_Gamma_correlation}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{0.3\textwidth}
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_9_12_correlation.png}
+		\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
+		\label{fig: Fit_9_12_Di_Gamma_correlation}
+	\end{subfigure}
+	\caption{Parameter estimation results}
+	\label{fig: Fit_Di_Gamma_correlation}
+\end{figure*}
 

### 2024-03-14 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
14.03

@@
 Considering that it is assumed that the $c_{f0}=0$.
-Moreover, it is considered that the extractor is isothermal and described by ${\color{black}h_0}$.
-Therefore, the initial conditions employed in the simulation are:
+Moreover, it is considered that the extractor is isothermal %and described by ${\color{black}h_0}$.
+		Therefore, the initial and boundary conditions employed in the simulation are:
 
+		\begin{comment}
 		{\footnotesize
@@
 					&\frac{\partial c_f(t,z=L)}{\partial x} = 0 & {\color{black}c_s}(t = 0, z) = {\color{black}c_{s0}} & &\frac{\partial h(t,z=L)}{\partial x} = 0
+				\end{align*} }
+		\end{comment}
+
+			{\footnotesize
+				\begin{align*}
+					&{\color{black}c_f}(t = 0, z) = 0 & {\color{black}c_s}(t = 0, z) = {\color{black}c_{s0}} &{c_f}(t, z=0) = 0 \\
+					&\frac{\partial c_f(t,z=0,L)}{\partial x} = 0 & c_s(t, z=0,L) = {\color{black}c_{s0}} &y(0) = 0
 			\end{align*} }
@@
 
+		\begin{comment}
 		{\footnotesize
@@
 		\end{align*} }
+	\end{comment}
 
-		where ${\color{black}x} \in \mathbb{R}^{N_x = 3N_z} $ and ${\color{black}\Theta} \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters, $N_{u}$ is the number of control variables.
+		{\footnotesize
+			\begin{align*} \label{discretization}
+				\dot{{\color{black}x}}(t) &= \cfrac{d {\color{black}x}(t)}{d t} = 
+				\begin{bmatrix}
+					\cfrac{d {\color{black}c_{f,1}}(t)}{d t} 	  \\
+					\vdots					  \\
+					\cfrac{d {\color{black}c_{f,N_z}}(t)}{d t} \\
+					\\ \hline \\
+					\cfrac{d {\color{black}c_{s,1}}(t)}{d t} 	  \\
+					\vdots					  \\
+					\cfrac{d {\color{black}c_{s,N_z}}(t)}{d t} \\
+					%\\ \hline \\
+					%\cfrac{d {\color{black}P}(t)}{d t} \\
+					\\ \hline \\
+					\cfrac{d {\color{black}y}(t)}{d t}
+				\end{bmatrix}
+				=
+				\underbrace{\begin{bmatrix}
+						{\color{black}G_1} \left( {\color{black}c_f}(t),{\color{black}c_s}(t); {\color{black}\Theta} \right)\\ 
+						\vdots\\ 
+						{\color{black}G_{N_z}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t); {\color{black}\Theta} \right)\\ 
+						\\ \hline \\ \\
+						{\color{black}G_{N_z+1}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t); {\color{black}\Theta} \right)\\ 
+						\vdots\\
+						{\color{black}G_{2N_z}} \left( {\color{black}c}(t),{\color{black}c_s}(t); {\color{black}\Theta} \right)\\ 
+						%\\ \\ \hline \\ 
+						%{\color{black}G_{2N_z+1}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t); {\color{black}\Theta} \right) \\
+						\\ \\ \hline \\
+						{\color{black}G_{2N_z+2}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t); {\color{black}\Theta} \right) 
+				\end{bmatrix}}_{{\color{black}G} \left( {\color{black}x}(t); {\color{black}\Theta} \right)} 
+		\end{align*} }
+
+		where ${\color{black}x} \in \mathbb{R}^{N_x = 2N_z+1} $ and ${\color{black}\Theta} \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters, $N_{u}$ is the number of control variables.
 
@@
 
-		In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases (${\color{black}c_f}(t,z)$ and ${\color{black}c_s}(t,z)$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{black}h}(t,z)$).
+		%In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases (${\color{black}c_f}(t,z)$ and ${\color{black}c_s}(t,z)$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{black}h}(t,z)$).
 The controllable input variables are the mass flow rate and temperature of the solvent in the feed and the pressure in the extractor.
 Additionally, the pressure change is augmented with the state-space and denoted as ${\color{black}P}(t)$.
-		The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase, and it can be measured after the separator (${\color{black}Y}(t)$).
+		%The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase, and it can be measured after the separator (${\color{black}Y}(t)$).
 The system is controllable by manipulating the flow rate and temperature (enthalpy) of $CO_2$ in the feed and the pressure in the extractor.

### 2024-03-14 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Qubic_EOS.tex
14.03

--- 2024-01-21 SFE_article_Design_of_Experiment/Sections/Qubic_EOS.tex
@@
-\documentclass[../Article_Design_of_Experiment.tex]{subfiles}
+\documentclass[../Article_Model_Parameters.tex]{subfiles}
 \graphicspath{{\subfix{../Figures/}}}
@@
 				Soave & $\left[ 1 + f(\omega) \left( 1-\sqrt{T_r} \right) \right]^2$ & 0.48+1.574$\omega$-0.176$\omega^2$\\
-				Peng and Robinson \cite{Peng1976} & $\left[ 1 + f(\omega) \left( 1-\sqrt{T_r} \right) \right]^2$ & 0.37464+1.54226$\omega$-0.26992$\omega^2$ \\
+				Peng and Robinson (\citet{Peng1976}) & $\left[ 1 + f(\omega) \left( 1-\sqrt{T_r} \right) \right]^2$ & 0.37464+1.54226$\omega$-0.26992$\omega^2$ \\
 				\hline
@@
 
-	If the Peng-Robinson equation of state [\cite{Peng1976}] is used, the polynomial equation becomes
+	If the Peng-Robinson equation of state (\citet{Peng1976}) is used, the polynomial equation becomes
 
@@
 
+	\begin{comment}
 	\subsubsection{Heat capacity of the fluid phase} \label{subsubsec: Fluid heat capacity}
@@
 
+	\end{comment}
+
 \end{document}

### 2024-03-14 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Results_Chamomile.tex
14.03

@@
 			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
-			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
+			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s]}% and temperature of 40 $[^\circ C]$}
 			\label{fig: Fit_1_4_Di_Gamma}
@@
 			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
-			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
+			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s]}% and temperature of 30 $[^\circ C]$}
 			\label{fig: Fit_5_8_Di_Gamma}

### 2024-03-14 SFE_article_Parameter_Estimation_short - Chamomile/Sections/introduction_imp.tex
14.03

@@
 This limitation has led to the increased popularity of alternative techniques like supercritical fluid extraction.
-Supercritical carbon dioxide is particularly appealing due to its distinctive properties: it's inflammable, non-toxic, has a low critical temperature, and is non-corrosive.
+Supercritical carbon dioxide is particularly appealing due to its distinctive properties: it's inflammable, non-toxic, and is non-corrosive.
 Moreover, its relatively low critical point, compared to other fluids, positions it as an advantageous alternative to conventional extraction methods.
@@
 	%The organization of the study is as follows: Chapter \ref{CH: Thermodynamic} offers an overview of supercritical fluids, aiming to acquaint the reader with their unique properties. 
-	Chapter \ref{CH:Governing_equations_chapter} outlines the fundamental balance equations.
+	%Chapter \ref{CH:Governing_equations_chapter} outlines the fundamental balance equations.
 These equations are then integrated with the extraction kinetic equation in Chapter \ref{CH: Extraction_model} to formulate the process model.

### 2024-03-14 SFE_article_Parameter_Estimation_short - Chamomile/Short_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
14.03

@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Parameter_Space_Linear_Dataset_1.png}
-		\caption{Parameter space for the linear extraction kinetic model and the experiment 1}
+		\caption{Parameter space: the linear kinetic model}
 		\label{fig: Fit_1_linear}
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Parameter_Space_Di_Dx_Dataset_1.png}
-		\caption{Parameter space for the reduced linear extraction kinetic model with axial diffusion and the experiment 1}
+		\caption{Parameter space: the reduced linear kinetic model with axial diffusion}
 		\label{fig: Fit_1_Di_Dx}
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
-		\caption{Parameter space for the modified extraction model and experiment 1}
+		\caption{Parameter space: the modified model}
 		\label{fig: Fit_1_Di_Gamma}
 	\end{subfigure}
-	\caption{Parameter estimation results}
+	\caption{Parameter estimation results for experiment 1}
 	%\label{fig: Fit_Di_Gamma}
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_1_4_correlation.png}
-		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
+		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s]}% and temperature of 40 $[^\circ C]$}
 		\label{fig: Fit_1_4_Di_Gamma_correlation}
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_5_8_correlation.png}
-		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
+		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s]}% and temperature of 30 $[^\circ C]$}
 		\label{fig: Fit_5_8_Di_Gamma_correlation}
@@
 %% Loading bibliography style file
-\clearpage
+%\clearpage
 %\bibliographystyle{model1-num-names}

### 2024-03-19 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Experiments.tex
14.03
19.03

--- 2024-02-22 SFE_article_Parameter_Estimation - Chamomile/Sections/Experiments.tex
@@
 	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers.
-The experiments were performed by \citet{Povh2001}.
+The experiments were performed by \citet{Povh2001} and \citet{Rahimi2011}.
 To prepare the flowers for extraction, they were first pre-treated using a knife mill (TECNAL, model TE 340) to reduce their particle size.
-The mean
-	particle diameter was determined by the Sauter equation and is equal to $0.3\times 10^{-3}$m.
+The Sauter equation determined the mean particle diameter and is equal to $0.3\times 10^{-3}$m.
 The actual density of the chamomile particles was measured through helium pycnometry at the Institute of Chemistry IQ/Unicamp's Analytical Facilities.
@@
 
-	The experiments were conducted using an extractor with diameter of $3.96\times 10^{-2}$ m and length $16.55\times 10^{-2}$ m.
+	The experiments were conducted using an extractor with a diameter of $3.96\times 10^{-2}$ m and a length $16.55\times 10^{-2}$ m.
 Twelve experiments were performed under different but constant in time operating conditions: $30-40^\circ C$, $100 - 200$ bar, and $1.33-6.67 \times 10^{-5}$ kg/s.

### 2024-03-19 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
19.03

@@
 
-	Assuming that the mass flow rate is constant in time, the temporal derivative becomes zero, and the spatial derivative can be integrated along ${\color{black}z}$ as
+	Assuming that the mass flow rate is constant in time, the temporal derivative becomes the mass flux F, and the spatial derivative can be integrated along ${\color{black}z}$ as
 
@@
 		\begin{equation}
-			\int \frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A \phi}(z) )}{\partial {\color{black}z}} dz = 0 \rightarrow {\color{black}F}={\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A\phi}(z)
+			\int \frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A \phi}(z) )}{\partial {\color{black}z}} dz = F \rightarrow {\color{black}F}={\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A\phi}(z)
 		\end{equation}
@@
 
-	Here, ${\color{black}F}$ is a constant obtained from the integration and is understood as the mass flux per unit area, which is assumed to be constant along ${\color{black}z}$.
 	To simplify the dynamics of the system, it is assumed that ${\color{black}F}={\color{black}F}(t)$ is a control variable and affects the whole system instantaneously.
@@
 
-	The fluid density ${\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$ can be obtained from an equation of state if temperature and the thermodynamic pressure (assumed ${\color{black}P}(t)$ to be constant along ${\color{black}z}$ due to the low-Mach number condition) are known.
+	The fluid density ${\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$ can be obtained from an equation of state (Appendix \ref{CH: EOS}) if temperature and the thermodynamic pressure (assumed ${\color{black}P}(t)$ to be constant along ${\color{black}z}$ due to the low-Mach number condition) are known.
 The variation in density may be caused by the fluid accumulation in the system (equivalent to pressure change), which occurs instantaneously along ${\color{black}z}$ or by a temperature change.
@@
 Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself.
-The mass balance equation thus encompasses convection, diffusion, and kinetic terms to accurately represent the fluid phase's behaviour.
+Thus, The mass balance equation encompasses convection, diffusion, and kinetic terms to represent the fluid phase's behaviour accurately.
 
@@
 		The efficiency of the process (the yield) is calculated according to Equation \ref{Model_measurment_1} as presented by \citet{Sovova1994a}.
-The measurement equation evaluate the mass of solute at the outlet of the extraction unit and sums it.
+The measurement equation evaluates the solute's mass at the extraction unit's outlet and sums it up.
 The integral form of the measurement equation (\ref{Model_measurment_1}) can be transformed into the differential form (\ref{Model_measurment_2}) and augmented with the process model.
@@
 Considering that it is assumed that the $c_{f0}=0$.
-Moreover, it is considered that the extractor is isothermal %and described by ${\color{black}h_0}$.
+Moreover, it is considered that the extractor is isothermal.
+%and described by ${\color{black}h_0}$.
 		Therefore, the initial and boundary conditions employed in the simulation are:
@@
 				\begin{align*}
-					&{\color{black}c_f}(t = 0, z) = 0 & {\color{black}c_s}(t = 0, z) = {\color{black}c_{s0}} &{c_f}(t, z=0) = 0 \\
-					&\frac{\partial c_f(t,z=0,L)}{\partial x} = 0 & c_s(t, z=0,L) = {\color{black}c_{s0}} &y(0) = 0
+					&{\color{black}c_f}(t = 0, z) = 0 && c_s(t = 0, z) = {\color{black}c_{s0}} && {c_f}(t, z=0) = 0 \\
+					&\frac{\partial c_f(t,z=L)}{\partial x} = 0 && c_s(t, z=\{0,L\}) = 0 && y(0) = 0
 			\end{align*} }
@@
 The integral equation states that the change rate of the integral of any quantity over an arbitrary control volume is given by the flux through the boundary of the control volume, with being the outer surface normal through the boundary.
-That quantity is neither produced nor consumed inside the control volume and is conserved.
+That quantity is conserved and neither produced nor consumed inside the control volume.
 For a derivative to be conservative, it must form a telescoping series.
 In other words, after the addition of all terms coming from the discretization over a grid, only the boundary terms should remain, and the artificial interior points should cancel out.
-To ensure mass conservation, discretization is applied to the conservative form of the process model.
+Discretization is applied to the conservative form of the process model to ensure mass conservation.
 

### 2024-03-19 SFE_article_Parameter_Estimation_short - Chamomile/Sections/introduction_imp.tex
19.03

@@
 
-	This study investigates the extraction of essential oil from chamomile flowers (Matricaria chamomilla L.) via supercritical fluid extraction techniques and modelling of this process.
+	This study investigates the extraction of essential oil from chamomile flowers (Matricaria chamomilla L.) via supercritical fluid extraction techniques and the modelling of this process.
 Chamomile is a medicinal herb widely cultivated in southern and eastern Europe—such as Germany, Hungary, France, and Russia.
@@
 This limitation has led to the increased popularity of alternative techniques like supercritical fluid extraction.
-Supercritical carbon dioxide is particularly appealing due to its distinctive properties: it's inflammable, non-toxic, and is non-corrosive.
-Moreover, its relatively low critical point, compared to other fluids, positions it as an advantageous alternative to conventional extraction methods.
+Supercritical carbon dioxide is particularly appealing due to its distinctive properties: it is inflammable, non-toxic, and is non-corrosive.
+Moreover, compared to other fluids, its relatively low critical point positions it as an advantageous alternative to conventional extraction methods.
 Supercritical fluids are capable of exhibiting both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.
 
-	The literature offers a variety of mathematical models aimed at detailing the extraction of valuable compounds from a fixed biomass bed.
+	The literature offers various mathematical models to detail the extraction of valuable compounds from a fixed biomass bed.
 Selecting a fitting model necessitates a deep understanding of the physical processes at play within the operational unit, as each model is built on specific assumptions and outlines distinct mass transfer mechanisms and equilibrium dynamics.
@@
 The process involves supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract.
-Parameters such as the feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) are adjustable and measurable, as is the vessel pressure ($P$), whereas the outlet temperature ($T_{out}$) can only be monitored.
-A simplified flow diagram is presented in Figure \ref{fig: SFE_drawing}, illustrating the process setup.
+Parameters such as the pressure ($P$), feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) are adjustable and measurable, while the outlet temperature ($T_{out}$) and the amount of product at the outlet can only be monitored.
+Figure \ref{fig: SFE_drawing} presents a simplified flow diagram illustrating the process setup.
 
@@
 The maximum likelihood estimator method is employed to address the parameter estimation challenge, with the derived parameters subsequently used to establish correlations.
-These correlations are instrumental in extending the applicability of the process model across different temperatures (30 to 40$^\circ C$) and pressures (100 to 200 bar).
+These correlations are instrumental in extending the applicability of the process model across different temperatures (30 to 40$^\circ C$), pressures (100 to 200 bar) and flow rates (3.33 to 6.67 $\times 10^{-5}$ kg/s).
 

### 2024-03-19 SFE_article_Parameter_Estimation_short - Chamomile/Short_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
19.03

@@
 
-	The set of quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates are encapsulated by Equations \ref{EQ: CompressibleEuler_1} through \ref{EQ: CompressibleEuler_3}.
+	The set of quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates are described by Equations \ref{EQ: CompressibleEuler_1} through \ref{EQ: CompressibleEuler_3}.
 The formulation of these equations is elaborated upon in Appendix \ref{CH: Gouverning equations}, providing a mathematical foundation for analyzing flow dynamics under the assumed conditions.
@@
 		\cfrac{\partial \left( {\color{black}\rho_f} v {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v^2 \right)}{\partial z} &= -{\color{black}A_f}(z) \cfrac{\partial {\color{black}P}}{\partial z} \label{EQ: CompressibleEuler_2} \\
-		\cfrac{\partial \left( {\color{black}\rho_f} {\color{black}e} {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v {\color{black}e}\right)}{\partial z} &= -{\color{black}P}\cfrac{\left( {\color{black}A_f}(z) v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial {\color{black}T}}{\partial z} \right)
+		\cfrac{\partial \left( {\color{black}\rho_f} {\color{black}e} {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v {\color{black}e}\right)}{\partial z} &= -{\color{black}P}\cfrac{\left( {\color{black}A_f}(z) v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial {\color{black}T}}{\partial z} \right)
 		\label{EQ: CompressibleEuler_3}
@@
 This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow.
-Moreover, if the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic which leads to $\partial {\color{black}\rho_f} / \partial {\color{black}P} \approx 0$.
-In other words, the small changes in pressure due to flow velocity changes do not change the density.
+If the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic, which leads to $\partial {\color{black}\rho_f} / \partial {\color{black}P} \approx 0$.
+The small changes in pressure due to flow velocity changes do not change the density.
 
@@
 The restraint allows for the removal of acoustic waves, but also allows for large perturbations in density and/or temperature.
-The assumption is that the flow remains within a Mach number limit (normally less than 0.3) for any solution using such a constraint to be valid.
-In 1-D case the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.
+The assumption is that the flow remains within a Mach number limit (usually less than 0.3) for any solution using such a constraint to be valid.
+In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.
 
@@
 \section{Appendix}
-\subsection{Thermodynamic}
-\subfile{Sections/Qubic_EOS}
 
@@
 \subfile{Sections/Gouverning_equation_derivation}
+
+\subsection{Thermodynamic}
+\subfile{Sections/Qubic_EOS} \label{CH: EOS}
 

### 2024-03-19 SFE_article_Sensitivity_Analysis - Chamomile/Article_Sensitivity_Analsysis-Chamomile.tex
19.03

--- 2024-01-21 SFE_article_Sensitivity_Analysis/Article_Sensitivity_Analsysis.tex
@@
 \begin{abstract}
-This study aimed to investigate the supercritical extraction process of caraway oil from caraway seeds.
-The extraction was performed in a partially filled extractor with a fixed bed operated under multiple operating conditions.
-A distributed-parameter model describes the fluid-solid extraction process with $CO_2$ as a solvent.
+This study aimed to investigate the supercritical extraction process of caraway oil from chamomile flowers.
+The distributed-parameter model describes the fluid-solid extraction process.
 The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
 The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
+The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
+A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s.
+Sensitivity analyses play a crucial role in assessing the robustness of the findings or conclusions based on mathematical model.
 The local sensitivity analysis investigates the influence of infinitely small changes in the inlet temperature, pressure, and flow rate on the extraction yield.
@@
 
-The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties.
+%The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties.
 Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations.

### 2024-03-19 SFE_article_Sensitivity_Analysis - Chamomile/Sections/Literature_Review.tex
19.03

--- 2024-01-20 SFE_article_Sensitivity_Analysis/Sections/Literature_Review.tex
@@
-\documentclass[../Article_Model_Parameters.tex]{subfiles}
+\documentclass[../Article_Sensitivity_Analsysis.tex]{subfiles}
 \graphicspath{{\subfix{../Figures/}}}

### 2024-03-19 SFE_article_Sensitivity_Analysis - Chamomile/Sections/Results_Sensitivity.tex
19.03

--- 2024-01-20 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
@@
 The process model and parameters have been discussed in {\color{red}article 1}.
-The process model was calibrated on the set of experiments obtained at different operating conditions, $40$ - $50^\circ C$ and 200 - 300 bar.
-The sensitivity analysis has been performed assuming that the system operates at $45^\circ C$, 250 bar and 0.4 l/min.
+The process model was calibrated on the set of experiments obtained at different operating conditions, $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s.
+The sensitivity analysis has been performed assuming that the system operates at $35^\circ C$, 150 bar and 5 $\times 10^{-5}$ kg/s.
 
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_F.pdf}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_F.png}
 		\caption{The effect of $F$ change on $P$}
@@
     	\centering
-    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.pdf}
+    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.png}
     	\caption{The effect of $F$ change on $h \times \rho$}
@@
     	\centering
-    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.pdf}
+    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.png}
     	\caption{The effect of $F$ change on $C_s$}
@@
     	\centering
-    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.pdf}
+    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.png}
     	\caption{The effect of $F$ change on $C_f$}
@@
     	\centering
-    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_F.pdf}
+    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_F.png}
     	\caption{The effect of $F$ change on $y(t)$}
@@
     	\centering
-    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_P.pdf}
+    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_P.png}
     	\caption{The effect of $P$ change on $P$ in the system}
@@
     	\centering
-    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P.pdf}
+    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P.png}
     	\caption{The effect of $P$ change on $(h \times \rho)$ in the system}
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.pdf}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.png}
 		\caption{The effect of $P$ change on $C_s$}
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.pdf}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.png}
 		\caption{The effect of $P$ change on $C_f$}
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_P.pdf}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_P.png}
 		\caption{The effect of $P$ change on $y(t)$}
@@
 	The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through the system.
+
+	The Figure \ref{fig:Sensitivty_P_T} for the system pressure response shows a flat curve, indicating an invariant behavior of pressure in response to inlet temperature changes throughout the time.
+This uniformity is expected, as explained in the Chapter XXX.
+The pressure of the modelled system is controlled and maintained independently of the inlet temperature variations.
+	%The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through the system.
 As the fluid with the modified temperature flows along the system, it gradually modifies the mass transfer parameters.
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_T_{in}.pdf}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_T_{in}.png}
 		\caption{The effect of $T_{in}$ change on $P$ in the system}
@@
 
-	The heat front propagation is presented in Figure \ref{fig:Sensitivty_T_H}.
-The initial system had constant temperature along the whole spatial domain.
-The inlet temperature is a control characterized by the Dirichlet boundary condition.
+	The inlet temperature is characterized by the Dirichlet boundary condition.
 The boundary value of $(h\times \rho)$ is calculated based on two controls which can be manipulated: inlet temperature and given pressure.
 Any deviation in $T_{in}$ affects $(h\times \rho)$ at the inlet, propagating according to the governing equations.
+	Figure \ref{fig:Sensitivty_T_H} showcases the sensitivity of the fluid enthalpy to the inlet temperature over both time and the length of the extraction bed.
+The heat front propagation from the inlet of the extractor to its outlet.
+The fluid entering the extraction bed will have its enthalpy most influenced by the inlet conditions.
+As the fluid progresses through the bed, the enthalpy change sensitivity affects the whole system gradually.
+Over time, the system's gradual approach to a new thermal steady state and the sensitivities becomes zero.
+
+	%The heat front propagation is presented in Figure \ref{fig:Sensitivty_T_H}. The initial system had constant temperature along the whole spatial domain.
 
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_T_{in}.pdf}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_T_{in}.png}
 		\caption{The effect of $T_{in}$ change on $(h \times \rho)$ in the system}
@@
 
-	Figure \ref{fig:Sensitivty_T_CS} illustrates how the change in inlet temperature affects the concentration of solute in the solid phase.
+	Figure \ref{fig:Sensitivty_T_CS} shows the curve depicts an initial sharp increase (positive sign of the sensitivities) in the solute concentration in the solid phase as a function of time, which then asymptotically approaches a stable value before increasing again towards the end of the period.
+Although $D_i^R$ decrease with the fluid's density, the $\Upsilon$ increases, which explains the system responses.
+This suggests that an increase in inlet temperature initially slow down the mass transfer of solutes from the solid phase to the supercritical fluid, hence the concentration of the solute in the solid phase increases.
+Over time, this effect stabilizes, which could indicate the exhaustion of easily extractable solutes.
+	%Figure \ref{fig:Sensitivty_T_CS} illustrates how the change in inlet temperature affects the concentration of solute in the solid phase.
 As presented in {\color{red}article 1}, the value of $D_i^R$ decreases as density decreases.
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_T_{in}.pdf}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_T_{in}.png}
 		\caption{The effect of $T_{in}$ change on $C_s$ in the system}
@@
 
-	The influence of inlet temperature on solute concentration in the fluid phase is depicted in Figure \ref{fig:Sensitivty_T_CF}.
+	The Figure \ref{fig:Sensitivty_T_CF} represents the sensitivity of the concentration of solutes in the fluid phase over a period of 600 minutes as a result of changes in the inlet temperature.
 Initially, all the sensitivities remain at zero due to the idle period.
 As the fluid with elevated temperature flows through the fixed bed, the internal mass transfer slows down (the $D_i^R$ is proportional to density as presented in {\color{red}article 1}), resulting in negative sensitivities.
-The diffusion effect is observable in the empty section, where the front composed of sensitivities becomes blurry.
-After reaching their minima, the sensitivities increase and reach slightly positive values.
-This behaviour can be explained by considering that the heat front slowed mass transfer, causing more solute to remain in the solid phase.
+The negative sensitivities can be explained by considering that the heat front slowed mass transfer, causing more solute to remain in the solid phase.
+After reaching their minima, the sensitivities increase and reach positive values.
+Later the sensitivities starts to increase due higher concentration gradient if compared to before the temperature change.
+Eventually, the system response stabilize around a constant value when the extraction kinetics become a limiting factor.
 
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_T_{in}.pdf}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_T_{in}.png}
 		\caption{The effect of $T_{in}$ change on $C_f$ in the system}
@@
 		\centering
-		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_T_{in}.pdf}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_T_{in}.png}
 		\caption{The effect of $T_{in}$ change on $y(t)$ in the system}

### 2024-03-19 SFE_Sensitivity_Analysis_Chamomile/Diffusion.m

@@ -2,7 +2,8 @@ function D = Diffusion(Re, F, parameters)
 
     a = parameters{44};
     b = parameters{45};
+    c = parameters{46};
 
-    D =  -0.131 - 8.337 .* Re + 0.687 * (F * 10^5);
+    D =  a -  b * Re + c  * F * 10^5;
     
 end

### 2024-03-19 SFE_Sensitivity_Analysis_Chamomile/main_Sensitivity_Analysis_Chamomile.m

@@ -25,7 +25,7 @@ bed                     = 0.92;                                              % P
 % Set time of the simulation
 PreparationTime         = 0;
 ExtractionTime          = 300;
-timeStep                = 0.1;                                                % Minutes
+timeStep                = 0.5;                                                % Minutes
 
 simulationTime          = PreparationTime + ExtractionTime;
 
@@ -112,9 +112,9 @@ m_fluid                 = [zeros(1,numel(nstagesbefore)) m_fluid];
 C0fluid                 = m_fluid * 1e-3 ./ V_fluid';
 
 %% Set operating conditions
-T0homog                 = LabResults(1,which_dataset+1);                    % K
-feedPress               = LabResults(2,which_dataset+1) * 10;               % MPa -> bar
-Flow                    = LabResults(3,which_dataset+1) * 1e-5 ;            % kg/s
+T0homog                 = 35+273;                    % K
+feedPress               = 150;               % MPa -> bar
+Flow                    = 5 * 1e-5 ;            % kg/s
 
 Z                       = Compressibility( T0homog, feedPress,         Parameters );
 rho                     = rhoPB_Comp(      T0homog, feedPress, Z,      Parameters );
@@ -159,7 +159,7 @@ name_p = {'CF'    , 'CS'  , 'H'             , 'P'      , 'Y' };
 My_Font = 14;
 num_levels = 100;
 
-for ii = 1:3
+for ii = 1:3        
 
         %% Sensitivities calculations
         Parameters{8} = ii;
@@ -175,6 +175,7 @@ for ii = 1:3
 
         %% Sensitivities plot 
         for ind=0:2
+            figure()
             imagesc(Time, L_nstages, Res(ind*nstages+1:(ind+1)*nstages,:)); cb = colorbar; colormap turbo;
 
             hold on
@@ -187,7 +188,7 @@ for ii = 1:3
             cb.Label.Rotation = 0; % to rotate the text
             xlabel('Time [min]'); ylabel('Length [m]'); 
             set(gca,'FontSize',My_Font)
-
+            
             exportgraphics(figure(1),[name_p{ind+1},'_',name_v{ii},'.png'], "Resolution",300);
             close all;
         end
@@ -195,9 +196,10 @@ for ii = 1:3
         %% Sensitivities plot - P and y
         indx = 0;
         for ind = 4:-1:3
+            figure()
             hold on
[…]

### 2024-03-20 SFE_article_Sensitivity_Analysis - Chamomile/Sections/Results_Sensitivity.tex
20.03

@@
 	The increase in the mass-flow rate affects the system simultaneously along the spatial direction by increasing the velocity but without affecting the thermodynamic state of the fluid.
-As a result, Figure \ref{fig:Sensitivty_F_P} shows no change in pressure during the simulation.
+As a result, Figure \ref{fig:Sensitivty_F_P} indicates that the system's pressure remains unaffected by changes in the flow rate.
 
@@
 
-   Figure \ref{fig:Sensitivty_F_CS} shows how the flow rate affects the solute concentration in the solid phase.
+   Figure \ref{fig:Sensitivty_F_CS} represents the sensitivity of solute concentration in the solid phase to changes in the mass flow rate.
+In an extraction process, it is expected that as the mass flow rate increases, the concentration of solute in the solid phase would decrease more quickly due to the increased concentration gradient.
+The improved extraction efficiency is indicated by negative sensitivities, as the loss of the solute from the solid phase is faster.
+Eventually, the amount of solute in the solid phase decreases, and the concentration gradient limits the extraction kinetic.
+This behaviour is represented by sensitivities, which increase from their minimal values and asymptotically approach to zero.
+In extreme cases, when all the solutes have been removed from the solid phase, the concentration gradient is zero, independent of the mass flow rate, which explains the asymptotic behaviour.
+
+   %Figure \ref{fig:Sensitivty_F_CS} shows how the flow rate affects the solute concentration in the solid phase.
 At the beginning of the extraction process, the flow rate has a low impact on the extraction process due to the dominance of the concentration gradient in the kinetic regime.
@@
 Negative sensitivities indicate a faster extraction rate.
-Eventually, the amount of solute in the solid phase decreases, and the concentration gradient limits the extraction kinetic.
-This behaviour is represented by sensitivities, which increase from their minimal values and asymptotically approach to zero.
-In extreme cases, when all the solutes have been removed from the solid phase, the concentration gradient is zero, independent of the mass flow rate, which explains the asymptotic behaviour.
 
@@
 
-    Figure \ref{fig:Sensitivty_F_CF} illustrates how the concentration of solute in the fluid phase responds to an increase in the flow rate.
+    Figure \ref{fig:Sensitivty_F_CF} shows how the concentration of solute in the fluid phase responds to an increase in the flow rate.
 Initially, sensitivities are close to zero, indicating a minimal system response.
@@
 
-    Figure \ref{fig:Sensitivty_F_y} illustrates how the increase in flow rate affects the extraction yield.
-Initially, the sensitivity curve remains flat.
-This occurs because the fixed bed doesn't occupy the entire volume of the extractor.
-Hence, some time is required for the fluid to flow through the empty portion of the extractor to reach its outlet.
-Only when the solute in the fluid phase reaches the extractor's outlet can the yield be measured.
-After the idle time, the system response can be observed as the increment of  $dy/dF$.
-The positive sensitivity value indicates improved process efficiency, increasing yield.
-As time progresses, the sensitivity reaches its maximum and diminishes due to a decreasing concentration gradient.
+    In Figure \ref{fig:Sensitivty_F_y}, the curve's shape reveals the time-dependent sensitivity of extraction yield to mass flow rate variations.
+The curve peaks and then falls, indicating a transient behavior in extraction efficiency.
+Initially, there's a negligible response, suggesting that changes in mass flow rate have little to no immediate impact on yield.
+As time progresses, however, yield becomes increasingly sensitive to the flow rate, reaching a peak sensitivity.
+Beyond this peak, the sensitivity decreases, which might reflect a saturation point in the extraction process where further increases in mass flow rate do not translate to increased yield, possibly due to limitations in solute diffusion rates from the solid matrix and decreasing concentration gradient.
 Eventually, $dy/dF$ asymptotically approaches zero.
@@
 
-	The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through the system.
+	The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through it.
 
-	The Figure \ref{fig:Sensitivty_P_T} for the system pressure response shows a flat curve, indicating an invariant behavior of pressure in response to inlet temperature changes throughout the time.
-This uniformity is expected, as explained in the Chapter XXX.
-The pressure of the modelled system is controlled and maintained independently of the inlet temperature variations.
+	The Figure \ref{fig:Sensitivty_P_T} shows the system pressure response.
+A flat curve indicates an invariant behavior of pressure in response to inlet temperature changes throughout the time.
+The pressure in the modelled system is controlled and maintained independently of the inlet temperature variations as a results of the assumptions as explained in the Chapter X.
 	%The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through the system.
@@
 
-	The inlet temperature is characterized by the Dirichlet boundary condition.
+	The inlet enthalpy is characterized by the Dirichlet boundary condition.
 The boundary value of $(h\times \rho)$ is calculated based on two controls which can be manipulated: inlet temperature and given pressure.
@@
 	Figure \ref{fig:Sensitivty_T_H} showcases the sensitivity of the fluid enthalpy to the inlet temperature over both time and the length of the extraction bed.
+The fluid entering the extraction bed will have its enthalpy directly influenced by the boundary conditions.
 The heat front propagation from the inlet of the extractor to its outlet.
-The fluid entering the extraction bed will have its enthalpy most influenced by the inlet conditions.
-As the fluid progresses through the bed, the enthalpy change sensitivity affects the whole system gradually.
-Over time, the system's gradual approach to a new thermal steady state and the sensitivities becomes zero.
+As the fluid progresses through the bed, the enthalpy change affects the whole system gradually.
+Over time, the system's approach to a new thermal steady state and the sensitivities becomes zero.
 
@@
 
-	Figure \ref{fig:Sensitivty_T_CS} shows the curve depicts an initial sharp increase (positive sign of the sensitivities) in the solute concentration in the solid phase as a function of time, which then asymptotically approaches a stable value before increasing again towards the end of the period.
-Although $D_i^R$ decrease with the fluid's density, the $\Upsilon$ increases, which explains the system responses.
-This suggests that an increase in inlet temperature initially slow down the mass transfer of solutes from the solid phase to the supercritical fluid, hence the concentration of the solute in the solid phase increases.
+	Figure \ref{fig:Sensitivty_T_CS} shows the curve depicts an initial increase (the positive sign of the sensitivities) in the solute concentration in the solid phase as a function of time, which later asymptotically approaches a stable value before decreasing again towards the end of the period.
+Although $D_i^R$ decreases with the fluid's density, the $\Upsilon$ increases, which explains the system responses.
+This suggests that an increase in temperature slows the mass transfer of solutes from the solid phase to the supercritical fluid; hence, the solute concentration in the solid phase increases.
 Over time, this effect stabilizes, which could indicate the exhaustion of easily extractable solutes.

### 2024-03-21 SFE_article_Sensitivity_Analysis - Chamomile/Sections/Results_Sensitivity.tex
21.03

@@
 
-   Figure \ref{fig:Sensitivty_F_CS} represents the sensitivity of solute concentration in the solid phase to changes in the mass flow rate.
-In an extraction process, it is expected that as the mass flow rate increases, the concentration of solute in the solid phase would decrease more quickly due to the increased concentration gradient.
-The improved extraction efficiency is indicated by negative sensitivities, as the loss of the solute from the solid phase is faster.
-Eventually, the amount of solute in the solid phase decreases, and the concentration gradient limits the extraction kinetic.
-This behaviour is represented by sensitivities, which increase from their minimal values and asymptotically approach to zero.
-In extreme cases, when all the solutes have been removed from the solid phase, the concentration gradient is zero, independent of the mass flow rate, which explains the asymptotic behaviour.
+   Figure \ref{fig:Sensitivty_F_CS} visualizes the local sensitivity of the solute concentration in the solid phase to changes in the mass flow rate during a supercritical fluid extraction process.
+It is postulated that with an increase in the mass flow rate, the driving force for mass transfer—the concentration gradient—becomes more pronounced, leading to an accelerated decrease in solute concentration within the solid matrix.
+This is exhibited by the negative sensitivity values: the solute is depleted more rapidly from the solid phase with higher mass flow rates.
+The most significant sensitivity is seen at the process commencement, particularly at the column inlet (top left corner with bright colours), where the concentration of solute is highest, and the effect of mass flow rate on extraction is most pronounced.
+
+   As the extraction progresses, the sensitivity values become less negative, moving towards zero, depicted by the gradient transitioning to cooler colors towards the bottom of the figure.
+This gradual change corresponds to the decreasing concentration of the solute in the solid phase, which results in a diminishing concentration gradient and, consequently, a reduction in the rate of extraction.
+The sensitivity approaching zero suggests that the driving force for mass transfer is decreasing as the solute is being depleted.
+
+   The asymptotic approach to zero sensitivity indicates a physical plateau in the extraction process, where further increases in mass flow rate no longer enhance the extraction efficiency.
+In practical terms, this asymptotic behavior signifies the approach towards an extraction endpoint where the remaining solute concentration in the solid phase is minimal and becomes less dependent on the mass flow rate.
+At this stage, other factors, such as diffusion within the solid matrix or equilibrium limitations, may limit the extraction rate.
+
+   In the most extreme cases, depicted by the uniform regions in the plot, the solute has been effectively exhausted, and the remaining traces in the solid phase are no longer influenced by changes in the mass flow rate.
+This stage represents the final equilibrium, where the concentration gradient effectively drops to zero, rendering the mass flow rate inconsequential for the extraction of the remaining solute.
+At this juncture, the system has reached its thermodynamic limit, and the efficiency of extraction cannot be enhanced by merely increasing the flow rate.
+This underscores the importance of optimizing the mass flow rate at the beginning and throughout the extraction process to ensure efficient solute recovery before reaching this terminal stage.
 
@@
 
-    Figure \ref{fig:Sensitivty_F_CF} shows how the concentration of solute in the fluid phase responds to an increase in the flow rate.
+    The Figure \ref{fig:Sensitivty_F_CF} depicts the sensitivity of the solute concentration in the fluid phase to the flow rate within a supercritical fluid extraction system.
+This sensitivity analysis reveals how the solute's behavior in the fluid phase is influenced by variations in the flow rate over the course of the extraction process, as depicted by both time and the length of the extraction column.
+
+    In the initial phase of the extraction, the sensitivities near the inlet are negligible, as shown by the colors being close to zero.
+This indicates a minimal initial response to changes in the flow rate, which could be due to the presence of an high concentration gradient, allowing the fluid phase to rapidly reach solute regardless of the flow rate.
+
+    As the extraction progresses, positive sensitivities emerge along the length of the extractor, indicated by the concentration front that develops and moves along the flow direction.
+This front represents the increased movement of the solute with the fluid phase as the flow rate increases, suggesting an enhanced mass transfer due to the elevated velocity of the supercritical fluid.
+This velocity increase augments the concentration gradient, thus encouraging a more efficient solute migration from the solid to the fluid phase.
+
+    Following the positive front, there is an emergence of a front characterized by negative sensitivities.
+This trend illustrates a diminishing solute concentration in the fluid phase, and it reflects a point in the extraction where the solute availability in the solid phase becomes a limiting factor; the depletion of solute reduces the concentration gradient, thereby decelerating the extraction rate.
+
+    Toward the end of the extraction process, the sensitivities are shown to increase from their negative values towards zero.
+This asymptotic approach suggests that the system is reaching a kinetic regime where further increases in the flow rate have a low impact on the solute concentration in the fluid phase.
+This behavior reflects a physical limit where the remaining solute in the solid phase is insufficient to sustain a high concentration in the fluid phase, regardless of the flow rate.
+It indicates a terminal phase of the extraction process where the available solute has been largely exhausted, and the system response to changes in flow rate is inherently constrained by the depletion of extractable material.
+
+    %Figure \ref{fig:Sensitivty_F_CF} shows how the concentration of solute in the fluid phase responds to an increase in the flow rate.
 Initially, sensitivities are close to zero, indicating a minimal system response.
@@
 
-    In Figure \ref{fig:Sensitivty_F_y}, the curve's shape reveals the time-dependent sensitivity of extraction yield to mass flow rate variations.
+	The Figure \ref{fig:Sensitivty_F_y} depicts the sensitivity of the extraction yield to variations in mass flow rate  as a function of time.
+The curve’s initial rise to a peak followed by a decline conveys the dynamic relationship between the mass flow rate and the extraction yield within the supercritical extraction process.
+
+	In the early phase, the sensitivity is minimal, denoting that adjustments to the mass flow rate have a negligible influence on the yield.
+This can be attributed to the initial phase of the extraction, where the mass transport mechanisms are mainly controlled by a high concentration gradient.
+
+	As the process evolves, the curve's ascent to its apex signifies a period during which the extraction yield becomes increasingly sensitive to the mass flow rate.
+This is likely due to the mass flow rate enhancing the convective transport of solute, maximizing the extraction efficiency.
+At this stage, the solute transfer from the solid to the fluid phase is most responsive to changes in flow rate.
+
+	However, the curve’s descent past the peak suggests a diminishing return on sensitivity with further increases in mass flow rate.
+The decrease indicates a transitional phase where the extraction process likely encounters diffusion limitations or a depletion of readily extractable solute.
+The concentration gradient, which drives the mass transfer, may be reduced due to the depletion of solute in the solid phase, or the system may be experiencing diffusive resistances that limit the rate at which solute can be delivered to the fluid phase.
+
+	The asymptotic approach to zero sensitivity towards the end of the curve reflects a regime where the yield is no longer significantly influenced by the mass flow rate.
+At this juncture, the extraction process has likely exhausted the available solute, and any further increase in mass flow rate does not result in a proportional increase in yield.
+The extraction system has reached a point of saturation or equilibrium where the mass transfer is limited by factors other than flow rate, such as the intrinsic properties of the solute or the matrix, indicating that the system has achieved as much extraction as is practically feasible under the given conditions.
+
+	The curve captures the non-linear and transient nature of the extraction yield's response to the mass flow rate, underscoring the importance of optimizing flow rates over the duration of the extraction to maximize yield.
+It also highlights the multifaceted dependencies and constraints inherent in supercritical fluid extraction processes, such as mass transfer rates, solute availability, and diffusion limitations.
+
+    %In Figure \ref{fig:Sensitivty_F_y}, the curve's shape reveals the time-dependent sensitivity of extraction yield to mass flow rate variations.
 The curve peaks and then falls, indicating a transient behavior in extraction efficiency.
@@
     According to Equation \ref{EQ:Enthalpy_equation}, the pressure change directly affects the quantity $h \times \rho$ through $\partial (P(t) A_f) / \partial t$, leading to the step change along the whole system, as presented in Figure \ref{fig:Sensitivty_P_H}.
+The uniform response across the entire extraction column length and time, represented by the homogeneously dark red color, indicates that the entire system experiences an immediate and uniform change in enthalpy density in response to pressure changes.
+This is consistent with the physical expectation that pressure changes should equilibrate rapidly throughout the fluid phase due to the high compressibility of supercritical fluids.
+
+    Regarding the boundary conditions, by applying the Dirichlet boundary conditions( mean setting a fixed temperature at the system boundary) can leads to a possible thermal gradient within the system if the initial temperatures differ.
+In contrast, Neumann boundary conditions would dictate that the heat flux at the boundaries be held constant, ensuring temperature uniformity between the inlet and the rest of the extractor.
+In case of this work, the Neumann boundary conditions have been applied, as indicated by the uniform response in enthalpy density, implying that there is no temperature gradient caused by a heat front propagating through the system.
+Instead, the temperature within the extractor is instantaneously and evenly matched to that at the inlet.
+
+	%According to Equation \ref{EQ:Enthalpy_equation}, the pressure change directly affects the quantity $h \times \rho$ through $\partial (P(t) A_f) / \partial t$, leading to the step change along the whole system, as presented in Figure \ref{fig:Sensitivty_P_H}.
 Depending on the configuration of the system, two cases are possible.
@@
 
-	The pressure change affects the mass transfer in two ways.
+    The provided figure showcases the sensitivity of the solute concentration in the solid phase with respect to changes in pressure throughout a fixed bed in a supercritical fluid extraction process.
+
+    As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely related to its density, which suggests that with higher fluid density—often associated with increased pressure—the velocity decreases.
+This leads to an extended residence time of the fluid within the system.
+The lower velocity afforded by increased pressure allows for a longer interaction between the solute and the solvent, potentially a higher concentration of solute in the fluid phase.
+
+    Simultaneously, pressure changes alter the fluid's thermodynamic state, affecting the extraction process's kinetics.
+These changes are characterized by correlations ({\color{red}article 1}), such as the increase of the diffusion coefficient $D_i^R$ with fluid density.
+A higher $D_i^R$ indicates enhanced mass transfer capabilities, contributing to an increased rate of extraction.
+
+    Figure \ref{fig:Sensitivty_P_CS} captures these dual effects on the solute concentration within the solid matrix.
+Initially, the system response is low due to a high concentration gradient.
+When the concentration gradient starts to diminish, high sensitivities reveal that changes in pressure have a more pronounced effect.
+This is consistent with the fluid's higher density and lower velocity, resulting in more effective mass transfer from the solid to the fluid phase.
+
+    Over time, the pressure change has a lower effect and the sensitivities decay.
+This trend signifies that the impact of pressure on solute concentration is diminishing, likely due to the depletion of the solute in the solid phase over time.
+The decreasing concentration gradient suggests that the solute availability becomes a limiting factor in the extraction process.
+
+    Eventually, sensitivities asymptotically approach zero.
+The solute concentration in the solid phase has been reduced, and further changes in pressure do not influence the remaining concentration.
+This behaviour reflects that in the later extraction phase, the kinetics of extraction are dominated by the reduced availability of the solute rather than the conditions of the supercritical fluid.
+
+	%The pressure change affects the mass transfer in two ways.
 As discussed in Chapter \ref{CH: Continuity}, the velocity is inversely proportional to the density; hence, the higher density of the fluid leads to a lower velocity and larger residence time.
@@
 The sensitivity plot shows a close-to-uniform decay of sensitivities along the fixed bed.
-The negative values of sensitivities suggest a faster extraction rate.
-No matter the location of the sensitivity measure in the bed, the general behaviour stays the same.
-Every sensitivity starts with zero and decreases to a minimum value.
 After the extremum, the sensitivities asymptotically increase to zero.
@@
 
-	The deviation in the solute concentration in the fluid phase caused by the pressure change is presented in Figure \ref{fig:Sensitivty_P_CF}.
+	Figure \ref{fig:Sensitivty_P_CF} shows the sensitivity of the solute concentration in the fluid phase as a function of pressure changes throughout the supercritical extraction column's length and over the extraction process's duration.
+An increase in pressure typically enhances the solute's solubility, resulting in its heightened presence in the supercritical fluid, which is seen as a leading front moving through the system.
+Due to the diffusion effect, the gradient becomes more dispersed in regions beyond the fixed bed.
+Following this, the formation of a trailing front characterized by decreasing sensitivities can be observed.
+This trailing front can be explained by the decrease in the concentration gradient as the solute is increasingly extracted and the available concentration within the solid phase diminishes.
+As seen in the figure, sensitivities are declining towards zero.
+This asymptotic trend suggests the driving force for the mass transfer—the concentration gradient—has been minimized, and changes in pressure no longer significantly impact the solute concentration in the fluid phase.
+
+	%The deviation in the solute concentration in the fluid phase caused by the pressure change is presented in Figure \ref{fig:Sensitivty_P_CF}.
 As discussed earlier, the sensitivities related to the solute concentration in the solid phase are characterized by negative sensitivities, suggesting a higher extraction rate due to the pressure change.
@@
 
-	The impact of pressure increase on extraction yield is depicted in Figure \ref{fig:Sensitivty_P_y}.
+	Figure \ref{fig:Sensitivty_P_y} illustrates the temporal evolution of the extraction yield's sensitivity to changes in pressure within a supercritical fluid extraction system.
+
+	Initially, the curve displays an almost flat profile, suggesting a latency in the system's response to pressure changes.
+A minor initial decrease in sensitivity, indicated by a slight dip below zero, may arise due to a decrease in the velocity of the fluid phase.
+For a constant mass flow rate, an increase in fluid density due to heightened pressure results in a lower fluid velocity, potentially leading to this reduced sensitivity.
+
+	As the process continues, the curve ascends sharply, indicating a positive yield response to pressure.
+This increase in sensitivity can be associated with the enhanced solubility and mass transfer capabilities imparted by higher pressures, improving the rate at which solute is extracted into the fluid phase.
+The peak in dy/dP reflects the most responsive period of the system, where pressure changes are highly effective in improving yield.
+
+	Beyond the peak, the sensitivity declines, converging towards zero.
+This descending curve represents a depletion phase: as the available solute in the solid phase diminishes, the potential for further increasing the yield through pressure alone is reduced.
+The remaining solute concentration becomes a limiting factor, and the mass transfer driving force, initially augmented by pressure, no longer plays a dominant role.
+
+	%The impact of pressure increase on extraction yield is depicted in Figure \ref{fig:Sensitivty_P_y}.
 The initial flat curve reflects a system delay caused by the empty space within the extractor that the fluid phase needs to flow through.

### 2024-03-26 SFE_article_Sensitivity_Analysis - Chamomile/Sections/Results_Sensitivity.tex
26.03

@@
 
-	The Figure \ref{fig:Sensitivty_P_T} shows the system pressure response.
+	Figure \ref{fig:Sensitivty_P_T} presents the sensitivity of the system's pressure response to changes in the inlet temperature over time during a supercritical fluid extraction process.
+The flat curve, hovering at zero, indicates a system where the pressure does not exhibit any response to changes in the inlet temperature throughout the entire operation period.
+In other words, the extraction system maintains a constant pressure regardless of any fluctuations in the temperature of the fluid entering the system.
+The invariance in pressure displayed in the Figure \ref{fig:Sensitivty_P_T} corroborates the model assumptions discussed in the Chapter X, where the pressure is assumed to be a control variable.
+
+	%The Figure \ref{fig:Sensitivty_P_T} shows the system pressure response.
 A flat curve indicates an invariant behavior of pressure in response to inlet temperature changes throughout the time.
 The pressure in the modelled system is controlled and maintained independently of the inlet temperature variations as a results of the assumptions as explained in the Chapter X.
+
 	%The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through the system.
@@
 
-	The inlet enthalpy is characterized by the Dirichlet boundary condition.
+	Figure \ref{fig:Sensitivty_T_H} displays the sensitivity of the fluid enthalpy density to changes in the inlet temperature across the extraction bed over time.
+Given that the Dirichlet boundary conditions are applied to the system, any alteration in inlet temperature will have an immediate and localized effect on the enthalpy density at the entrance of the extraction column on the fluids enthalpy.
+This alteration results in a heat front propagation from the inlet to the outlet of the extractor as presented on the Figure \ref{fig:Sensitivty_T_H}.
+As time progresses, the impact of the inlet temperature on enthalpy diminish and the sensitivities converging towards zero.
+This convergence suggests that the system is reaching a new thermal equilibrium.
+The uniformity of the enthalpy at later times implies that the initial temperature perturbations have equilibrated throughout the bed, and the system has adapted to the new inlet temperature condition.
+
+	%The inlet enthalpy is characterized by the Dirichlet boundary condition.
 The boundary value of $(h\times \rho)$ is calculated based on two controls which can be manipulated: inlet temperature and given pressure.
 Any deviation in $T_{in}$ affects $(h\times \rho)$ at the inlet, propagating according to the governing equations.
-	Figure \ref{fig:Sensitivty_T_H} showcases the sensitivity of the fluid enthalpy to the inlet temperature over both time and the length of the extraction bed.
+	%Figure \ref{fig:Sensitivty_T_H} showcases the sensitivity of the fluid enthalpy to the inlet temperature over both time and the length of the extraction bed.
 The fluid entering the extraction bed will have its enthalpy directly influenced by the boundary conditions.
@@
 
-	Figure \ref{fig:Sensitivty_T_CS} shows the curve depicts an initial increase (the positive sign of the sensitivities) in the solute concentration in the solid phase as a function of time, which later asymptotically approaches a stable value before decreasing again towards the end of the period.
+	Figure \ref{fig:Sensitivty_T_CS} shows the temporal and spatial sensitivity of the solute concentration in the solid phase to changes in the inlet temperature during a supercritical fluid extraction process.
+The positive sensitivities observed suggest that the solute concentration in the solid phase increases with rising inlet temperature.
+This initial increase could be attributed to a reduction in solute solubility in the supercritical fluid at higher temperatures or a slowdown in mass transfer kinetics.
+As presented in {\color{red}article 1}, a rise in temperature at constant pressure would increase solute diffusivity $D_i^R$ in supercritical fluids; however, the increase in concentration in the solid phase indicates other dominating factors, such as changes in solubility described by the solubility parameter ($\Upsilon$), which might decrease, thereby reducing the extraction rate.
+
+	As the extraction progresses, the sensitivities flatten out and then decrease.
+Towards the end of the extraction period, the sensitivities approach a positive constant, implying that the effect of inlet temperature on the concentration of the solute in the solid phase becomes negligible.
+This behaviour can be explained if it assumed that the extraction kinetic slowed because at the high temperature, which leads to higher concentration gradient in the later part of the process.
+The reduced availability of extractable solute in the later part of the process corresponds to the diminishing of the sensitivity.
+
+	%Figure \ref{fig:Sensitivty_T_CS} shows the curve depicts an initial increase (the positive sign of the sensitivities) in the solute concentration in the solid phase as a function of time, which later asymptotically approaches a stable value before decreasing again towards the end of the period.
 Although $D_i^R$ decreases with the fluid's density, the $\Upsilon$ increases, which explains the system responses.
@@
 Over time, this effect stabilizes, which could indicate the exhaustion of easily extractable solutes.
+
 	%Figure \ref{fig:Sensitivty_T_CS} illustrates how the change in inlet temperature affects the concentration of solute in the solid phase.
@@
 	The Figure \ref{fig:Sensitivty_T_CF} represents the sensitivity of the concentration of solutes in the fluid phase over a period of 600 minutes as a result of changes in the inlet temperature.
+In the initial phase of the process, indicated by the area where sensitivities are at or near zero, there is a lack of response, likely reflecting an idle period or delay as the system adjusts to the new inlet temperature.
+This could represent the time needed for the thermal front to propagate through the system and influence the solubility and mass transfer rates of the solutes.
+As the warmer fluid begins to interact with the solid phase, the negative sensitivities are observed.
+These negative values imply a decrease in solute concentration within the fluid phase, which might be attributed to a reduced diffusion coefficient ($D_i^R$) due to increased fluid viscosity at higher temperatures, or possibly due to a change in the solubility ($\Upsilon$) of the solute with temperature.
+If the solubility decreases with temperature for the given solute, an increase in temperature could indeed result in a lower solute concentration in the fluid phase.
+Later the sensitivities starts to increase due higher concentration gradient if compared to before the temperature change.
+Towards the end of the time period, the figure shows the sensitivities stabilizing at a constant value.
+Eventually, the system response stabilize around a constant value when the extraction kinetics become a limiting factor.
+
+	%The Figure \ref{fig:Sensitivty_T_CF} represents the sensitivity of the concentration of solutes in the fluid phase over a period of 600 minutes as a result of changes in the inlet temperature.
 Initially, all the sensitivities remain at zero due to the idle period.
@@
 
-	Figure \ref{fig:Sensitivty_T_y} depicts how an increase in inlet temperature alters the extraction yield.
+	Figure \ref{fig:Sensitivty_T_y} shows the time-dependent response of the extraction yield's sensitivity to changes in the inlet temperature.
+Initially, there is no change in yield as the heat front needs to propagate the along the system.
+That delayed response, cause the yield sensitivity to stay flat at the beginning of the extraction.
+
+	As the system starts responding, a small increase in sensitivity can be observed, which indicates a transient enhancement in yield.
+This is due to the velocity of the fluid, which is inversely proportional to density.
+The sensitivity peak comes from the fact that the fluid moves faster across the system, while the mass transfer kinetic is mainly driven by high concentration gradient.
+
+	Subsequently, the sensitivity curve descends into negative territory, suggesting that the increased inlet temperature eventually reduces the extraction efficiency.
+As explained above, due to complex relation between temperature and various mass transfer parameters, including the solubility of different compounds and the diffusivity within the supercritical fluid, the temperature increase might have a negatively affected on the extraction efficiency.
+The minimum point reached by the sensitivity curve implies a period where the yield is affected the most by the temperature increase.
+
+	Afterward, the curve's gradual ascent towards zero reflects a stabilizing effect.
+The curve eventually flattens out, maintaining a slightly negative sensitivity, suggesting that while the system has reached a new quasi-steady state.
+The overall yield remains slightly compromised compared to the baseline.
+At this point, the extraction process is limited by availability of the solute in the solid particles.	This extended simulation offers a comprehensive view of how inlet temperature variations can impact the extraction yield over time.
+
+	%Figure \ref{fig:Sensitivty_T_y} depicts how an increase in inlet temperature alters the extraction yield.
 Initially, the sensitivity curve remains flat due to the idle time.

### 2024-04-08 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
08.04

@@
 	\subsubsection{Continuity equation} \label{CH: Continuity}
-	 %When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{black}\phi}(z)$ (where ${\color{black}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}
+	 %When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction $\phi$ (where ${\color{black}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}
 
-	%The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function ${\color{black}A_f}(z) = {\color{black}A\phi}(z)$ to take into account the change of the cross-section available for the fluid.
+	%The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function $A_f = A\phi$ to take into account the change of the cross-section available for the fluid.
 The Equation \ref{EQ: Continuity_differential} shows the differential form of the continuity equation:
 
-	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is refined by incorporating a function ${\color{black}A_f}(z) = {\color{black}A\phi}(z)$.
+	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is refined by incorporating a function $A_f = A\phi$.
 This modification accounts for the variability in the cross-sectional area available for fluid flow.
@@
 		\begin{equation} \label{EQ: Continuity_differential}
-			\frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}\phi}(z))}{\partial t} + \frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A\phi}(z))}{\partial {\color{black}z}} = 0
+			\frac{\partial (\rho_f \phi)}{\partial t} + \frac{\partial (\rho_f v A\phi)}{\partial {\color{black}z}} = 0
 		\end{equation}
 	}
-	where ${\color{black} A}$ is the total cross-section of the extractor and ${\color{black}\phi}(z)$ describe porosity along the extractor.
+	where ${\color{black} A}$ is the total cross-section of the extractor and $\phi$ describe porosity along the extractor.
 
@@
 
-	Assuming that the mass flow rate is constant in time, the temporal derivative becomes the mass flux F, and the spatial derivative can be integrated along ${\color{black}z}$ as
+	Assuming that the mass flow rate is constant in time, the temporal derivative becomes the mass flux F, and the spatial derivative can be integrated along $z$ as
 
@@
 		\begin{equation}
-			\int \frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A \phi}(z) )}{\partial {\color{black}z}} dz = F \rightarrow {\color{black}F}={\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A\phi}(z)
+			\int \frac{\partial (\rho_f v A \phi )}{\partial {\color{black}z}} dz = F \rightarrow {\color{black}F}=\rho_f v A\phi
 		\end{equation}
@@
 
-	To simplify the dynamics of the system, it is assumed that ${\color{black}F}={\color{black}F}(t)$ is a control variable and affects the whole system instantaneously.
-This assumption allows for finding the velocity profile that satisfies mass continuity based on ${\color{black}F}(t)$, ${\color{black}\phi}(z)$, and ${\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$.
+	To simplify the dynamics of the system, it is assumed that ${\color{black}F}=F$ is a control variable and affects the whole system instantaneously.
+This assumption allows for finding the velocity profile that satisfies mass continuity based on $F$, $\phi$, and $\rho_f$.
 
@@
 	\begin{equation}
-		v = \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}A\phi}(z)} 
+		v = \cfrac{F}{\rho_f A\phi} 
 	\end{equation}
@@
 
-	The fluid density ${\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$ can be obtained from an equation of state (Appendix \ref{CH: EOS}) if temperature and the thermodynamic pressure (assumed ${\color{black}P}(t)$ to be constant along ${\color{black}z}$ due to the low-Mach number condition) are known.
+	The fluid density $\rho_f$ can be obtained from an equation of state (Appendix \ref{CH: EOS}) if temperature and the thermodynamic pressure (assumed ${\color{black}P}(t)$ to be constant along ${\color{black}z}$ due to the low-Mach number condition) are known.
 The variation in density may be caused by the fluid accumulation in the system (equivalent to pressure change), which occurs instantaneously along ${\color{black}z}$ or by a temperature change.
@@
 		\begin{equation}
-			u = v {\color{black}\phi}(z) = \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black} A} }
+			u = v \phi = \cfrac{F}{\rho_f {\color{black} A} }
 		\end{equation}
@@
 This equation accounts for the movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}), which is constrained to the axial direction due to the quasi-one-dimensional approach that considers changes in the void fraction.
-It is also predicated on the assumption that the thermodynamic pressure remains constant throughout the device, as illustrated by Equation \ref{EQ: Pressure_Velocity}.
+It is also assumed that the thermodynamic pressure remains constant throughout the device, as illustrated by Equation \ref{EQ: Pressure_Velocity}.
 The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall, leading to a uniform velocity profile across any cross-section perpendicular to the axial direction.
 Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself.
-Thus, The mass balance equation encompasses convection, diffusion, and kinetic terms to represent the fluid phase's behaviour accurately.
+Thus, the mass balance equation encompasses convection, diffusion, and kinetic terms to represent the fluid phase behaviour accurately.
 
@@
 			\label{Model_fluid}
-			\frac{\partial {\color{black}c_f}(t,z)}{\partial t}
-			+ \frac{1}{{\color{black}\phi}(z)} \frac{\partial \left( {\color{black}c_f}(t,z) u\right)}{\partial {\color{black}z}}
-			= \frac{1-{\color{black}\phi}(z)}{{\color{black}\phi}(z)} {\color{black}r_e}(t,z)
-			+ \frac{1}{{\color{black}\phi}(z)} \frac{\partial}{\partial {\color{black}z}} \left( {\color{black}D^M_e} \frac{\partial {\color{black}c_f}(t,z)}{\partial {\color{black}z}} \right)
+			\frac{\partial c_f}{\partial t}
+			+ \frac{1}{\phi} \frac{\partial \left( c_f u\right)}{\partial {\color{black}z}}
+			= \frac{1-\phi}{\phi} r_e
+			+ \frac{1}{\phi} \frac{\partial}{\partial {\color{black}z}} \left( {\color{black}D^M_e} \frac{\partial c_f}{\partial {\color{black}z}} \right)
 		\end{equation}
@@
 
-	${\color{black}c_f}(t,z)$ represents the concentration of solute in the fluid phase, , ${\color{black}r_e}(t,z)$ is a mass transfer kinetic term, and ${\color{black}D^M_e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}F}(t))$ is the axial diffusion coefficient.
+	$c_f$ represents the concentration of solute in the fluid phase, , $r_e$ is a mass transfer kinetic term, and ${\color{black}D^M_e}(T(t,z),{\color{black}P}(t),F)$ is the axial diffusion coefficient.
 
@@
 			%		{\scriptsize\begin{equation}
-					\cfrac{\partial {\color{black}c_s}(t,z)}{\partial t} = \underbrace{ {\color{black}r_e}(t,z) }_{\text{Kinetics}}
+					\cfrac{\partial c_s}{\partial t} = \underbrace{ r_e }_{\text{Kinetics}}
 			\end{equation} }
@@
 
-%	As the solvent flows through the bed, the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles through the solvent–solid matrix interactions.
+%	As the solvent flows through the bed, the CO$_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles through the solvent–solid matrix interactions.
 Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected.
@@
 
-	As the solvent flows through the bed, $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles due to the solvent-solid matrix interactions.
-The effect of Knudsen diffusion is negligible in this process, as the mean free path of the molecule is much smaller than the pore diameter.
+	As the solvent flows through the bed, CO$_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles due to the solvent-solid matrix interactions.
 The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
@@
 				\begin{equation} \label{Model_kinetic_basic}
-					{\color{black}r_e}(t,z) = \cfrac{{\color{black}D_i}({\color{black}T}(t,z), {\color{black}P}(t), F(t))}{{\color{black} \mu l^2} }\left({\color{black}c_s}(t,z) - {\color{black}c_P^*}(t,z) \right)
+					r_e = \cfrac{{\color{black}D_i}(T(t,z), {\color{black}P}(t), F(t))}{{\color{black} \mu l^2} }\left(c_s - {\color{black}c_P^*}(t,z) \right)
 			\end{equation} }
 
-		where ${\color{black}\mu}$ is sphericity, ${\color{black}l}$ a characteristic dimension of particles and can be defined as ${\color{black}l} = {\color{black}r}/3$, ${\color{black}r}$ is the mean particle radius, ${\color{black}\rho_s}$ is the solid density, ${\color{black}D_i}({\color{black}T}(t,z))$ corresponds to the overall diffusion coefficient and ${\color{black}c_P^*}(t,z)$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).
+		where ${\color{black}\mu}$ is sphericity, ${\color{black}l}$ a characteristic dimension of particles and can be defined as ${\color{black}l} = {\color{black}r}/3$, ${\color{black}r}$ is the mean particle radius, ${\color{black}\rho_s}$ is the solid density, ${\color{black}D_i}(T(t,z))$ corresponds to the overall diffusion coefficient and ${\color{black}c_P^*}(t,z)$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).
 
-		According to \citet{Bulley1984}, a linear equilibrium relationship (equation  \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{black}c_f^*}(t,z)$ is based on the concentration of the solute in the solid phase ${\color{black}c_s}(t,z)$
+		According to \citet{Bulley1984}, a linear equilibrium relationship (equation  \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{black}c_f^*}(t,z)$ is based on the concentration of the solute in the solid phase $c_s$
 
@@
 				\begin{align} \label{Linear_equilibirum}
-					{\color{black}c}(t,z) &= {\color{black}k_p}({\color{black}T}(t,z),{\color{black}P}(t)) \allowbreak {\color{black}q^*}(t,z)
+					{\color{black}c}(t,z) &= {\color{black}k_p}(T(t,z),{\color{black}P}(t)) \allowbreak {\color{black}q^*}(t,z)
 			\end{align} }
 
-			The volumetric partition coefficient ${\color{black}k_p}({\color{black}T}(t,z),{\color{black}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
-According to \citet{Spiro2007}, the term ${\color{black}k_p}({\color{black}T}(t,z),{\color{black}P}(t))$ can be expressed as the function of mass partition factor ${\color{black}k_m}({\color{black}T}(t,z))$.
+			The volumetric partition coefficient ${\color{black}k_p}(T(t,z),{\color{black}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
+According to \citet{Spiro2007}, the term ${\color{black}k_p}(T(t,z),{\color{black}P}(t))$ can be expressed as the function of mass partition factor ${\color{black}k_m}(T(t,z))$.
 
@@
 				\begin{align}
-					{\color{black}k_m}({\color{black}T}(t,z)) = \cfrac{{\color{black}k_p}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}\rho_s}}{{\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}
+					{\color{black}k_m}(T(t,z)) = \cfrac{{\color{black}k_p}(T(t,z),{\color{black}P}(t)) {\color{black}\rho_s}}{{\color{black}\rho}(T(t,z),{\color{black}P}(t))}
 			\end{align} }
@@
 					\label{Model_kinetic_no_sat}
-					{\color{black}r_e}(t,z) = -\cfrac{{\color{black}D_i}({\color{black}T}(t,z), {\color{black}P}(t), F(t))}{{\color{black} \mu l^2} }\left({\color{black}c_s}(t,z) - \cfrac{{\color{black}\rho_s}c_f(t,z)}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))}   \right)
+					r_e = -\cfrac{{\color{black}D_i}(T(t,z), {\color{black}P}(t), F(t))}{{\color{black} \mu l^2} }\left(c_s - \cfrac{{\color{black}\rho_s}c_f(t,z)}{{\color{black}k_m}(T(t,z))\rho_f}   \right)
 			\end{equation} }
@@
 The pseudo-homogenous phase is assumed to flow only in the axial direction.
-The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid ${\color{black}C_p}({\color{black}T}(t,z),{\color{black}P}(t))$ because the solid phase is stationary.
+The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid ${\color{black}C_p}(T(t,z),{\color{black}P}(t))$ because the solid phase is stationary.
 Therefore, this factor can be understood as the fraction of the fluid's total heat through convection.
@@
 					\begin{split}
-						\cfrac{\partial {\color{black}T}(t,z)}{\partial t} &= 
-						\underbrace{ -\cfrac{{\color{black}F}(t) {\color{black}C_p}({\color{black}T}(t,z),{\color{black}P}(t))}{{\color{black}A} 	[(1-{\color{black}\epsilon}){\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}C_p} ({\color{black}T}(t,z),{\color{black}P}(t)) + {\color{black} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial {\color{black}T}(t,z)}{\partial {\color{black}z}}  }_{\text{Convection}} + \\
-						& + \underbrace{ {\color{black}D^T_e}({\color{black}T}(t,z),{\color{black}P}(t)) \cfrac{\partial^2 {\color{black}T}(t,z)}{\partial {\color{black}z^2}} }_{\text{Diffusion}}
+						\cfrac{\partial T(t,z)}{\partial t} &= 
+						\underbrace{ -\cfrac{F {\color{black}C_p}(T(t,z),{\color{black}P}(t))}{{\color{black}A} 	[(1-{\color{black}\epsilon})\rho_f {\color{black}C_p} (T(t,z),{\color{black}P}(t)) + {\color{black} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial T(t,z)}{\partial {\color{black}z}}  }_{\text{Convection}} + \\
+						& + \underbrace{ {\color{black}D^T_e}(T(t,z),{\color{black}P}(t)) \cfrac{\partial^2 T(t,z)}{\partial {\color{black}z^2}} }_{\text{Diffusion}}
 					\end{split}
@@
 
-		where $ {\color{black}D^M_e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}F}(t))$ is the axial mass diffusion coefficient, ${\color{black}C_p}({\color{black}T}(t,z),{\color{black}P}(t))$ is the fluid's specific heat, ${\color{black}C_{ps}}$ is the specific heat of the solid phase, ${\color{black}D^T_e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}F}(t))$ is the axial heat diffusion coefficient.
+		where $ {\color{black}D^M_e}(T(t,z),{\color{black}P}(t),F)$ is the axial mass diffusion coefficient, ${\color{black}C_p}(T(t,z),{\color{black}P}(t))$ is the fluid's specific heat, ${\color{black}C_{ps}}$ is the specific heat of the solid phase, ${\color{black}D^T_e}(T(t,z),{\color{black}P}(t),F)$ is the axial heat diffusion coefficient.
 
@@
 			\begin{align} \label{EQ: Heat_internal}
-				&\cfrac{\partial \left( {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}e}(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) A_f v {\color{black}e}(t,z) \right)}{\partial {\color{black}z}} \nonumber \\
-				&= -{\color{black}P}(t)\cfrac{\left( A_f v \right)}{\partial {\color{black}z}} + \cfrac{\partial}{\partial {\color{black}z}} \left( \cfrac{\partial {\color{black}T}(t,z)}{\partial {\color{black}z}} \right)
+				&\cfrac{\partial \left( \rho_f e(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e(t,z) \right)}{\partial {\color{black}z}} \nonumber \\
+				&= -{\color{black}P}(t)\cfrac{\left( A_f v \right)}{\partial {\color{black}z}} + \cfrac{\partial}{\partial {\color{black}z}} \left( \cfrac{\partial T(t,z)}{\partial {\color{black}z}} \right) 
 			\end{align}
@@
 				\begin{equation}
-					d{\color{black}e}(t,z)=C_vd{\color{black}T}-\left[{\color{black}P}(t)-{\color{black}T}(t,z)\left(\cfrac{\partial {\color{black}P}(t)}{\partial {\color{black}T}(t,z)}\right)_{{\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}\right]d{\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)
+					de(t,z)=C_vdT-\left[{\color{black}P}(t)-T(t,z)\left(\cfrac{\partial {\color{black}P}(t)}{\partial T(t,z)}\right)_{{\color{black}v_m}\left(T(t,z), {\color{black}P}(t)\right)}\right]d{\color{black}v_m}\left(T(t,z), {\color{black}P}(t)\right)
 					\label{EQ: internal_energy_def}
@@
 
-			where ${\color{black}e}^{id}(t,z)$ is the internal energy of perfect gas.
+			where $e^{id}(t,z)$ is the internal energy of perfect gas.
 
-			Suppose a gas is considered to be perfectly caloric (${\color{black}e}(t,z)={\color{black}C_v} {\color{black}T}(t,z)$), then the energy equation can be written explicitly in the form of temperature.
+			Suppose a gas is considered to be perfectly caloric ($e(t,z)={\color{black}C_v} T(t,z)$), then the energy equation can be written explicitly in the form of temperature.
 The perfectly caloric gas can be seen as the special case of a real gas, where the second term of Equation \ref{EQ: internal_energy_def} goes to zero and the heat capacity ${\color{black}C_v}$ is constant.
@@
 					\begin{aligned}
-					&\cfrac{{\color{black}e}(t,z)-{\color{black}e}^{id}(t,z)}{R{\color{black}T}(t,z)} = \\
-					& - \cfrac{{\color{black}A}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)\sqrt{8}} \cfrac{{\color{black}\kappa} \sqrt{\color{black}T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)} \right]
+					&\cfrac{e(t,z)-e^{id}(t,z)}{RT(t,z)} = \\
+					& - \cfrac{{\color{black}A}\left(T(t,z), {\color{black}P}(t)\right)}{{\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)\sqrt{8}} \cfrac{{\color{black}\kappa} \sqrt{\color{black}T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)} \right]
 					\label{EQ: internal_energy_PR}
@@
 			\begin{equation}
-				{\color{black}e}(t,z)={\color{black}e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)))=e( {\color{black}T}(t,z),{\color{black}P}(t), {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) )
+				e(t,z)=e(T(t,z),{\color{black}P}(t),\rho_f)=e( T(t,z),{\color{black}P}(t), \rho_f ) 
 			\end{equation}
@@
 
-			If the value of internal energy ${\color{black}e}(t,z)$ is known from the time evolution of the energy Equation \ref{EQ: CompressibleEuler_3}, and pressure is known from measurement, then the temperature can be reconstructed.
+			If the value of internal energy $e(t,z)$ is known from the time evolution of the energy Equation \ref{EQ: CompressibleEuler_3}, and pressure is known from measurement, then the temperature can be reconstructed.
 A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution (Equation \ref{EQ: Heat_internal}) and the output from Equation \ref{EQ: internal_energy_PR}.
@@
 
-			Another way to express the energy equation is to introduce enthalpy ${\color{black}h}(t,z) = {\color{black}e}(t,z) + {\color{black}P}(t) / {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$.
+			Another way to express the energy equation is to introduce enthalpy ${\color{black}h}(t,z) = e(t,z) + {\color{black}P}(t) / \rho_f$.
 By introducing the definition of enthalpy, the energy equation becomes
@@
 				\begin{align} \label{EQ:Enthalpy_equation}
-					\cfrac{\partial \left({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}h}(t,z) A_f\right)}{\partial t} &= - \cfrac{\partial \left( {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}h}(t,z) A_f v \right)}{\partial {\color{black}z}}  \nonumber \\
-					& + \cfrac{\partial \left({\color{black}P}(t) A_f\right)}{\partial t} + \cfrac{\partial}{\partial {\color{black}z}} \left( k \cfrac{\partial {\color{black}T}(t,z)}{\partial {\color{black}z}} \right)
+					\cfrac{\partial \left(\rho_f {\color{black}h}(t,z) A_f\right)}{\partial t} &= - \cfrac{\partial \left( \rho_f {\color{black}h}(t,z) A_f v \right)}{\partial {\color{black}z}}  \nonumber \\
+					& + \cfrac{\partial \left({\color{black}P}(t) A_f\right)}{\partial t} + \cfrac{\partial}{\partial {\color{black}z}} \left( k \cfrac{\partial T(t,z)}{\partial {\color{black}z}} \right)
 				\end{align}
@@
 				\begin{equation}
-					{\color{black}h}(t,z)={\color{black}h}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)))={\color{black}h}( {\color{black}T}(t,z),{\color{black}P}(t), {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) )
+					{\color{black}h}(t,z)={\color{black}h}(T(t,z),{\color{black}P}(t),\rho_f)={\color{black}h}( T(t,z),{\color{black}P}(t), \rho_f ) 
 					\label{EQ:Enthalpy_root}
@@
 					\begin{split}
-					{\color{black}h}(t,z)-{\color{black}h}(t,z)^{id}={\color{black}R}{\color{black}T}(t,z) \left[{\color{black}T_r}({\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)-1) \right.
-\\
+					{\color{black}h}(t,z)-{\color{black}h}(t,z)^{id}={\color{black}R}T(t,z) \left[{\color{black}T_r}({\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)-1) \right. \\
 					\left.
--2.078(1+{\color{black}\kappa} ){\sqrt { {\color{black}\alpha}\left({\color{black}T}(t,z)\right) } } \ln \left(\cfrac{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}\right)\right]
+-2.078(1+{\color{black}\kappa} ){\sqrt { {\color{black}\alpha}\left(T(t,z)\right) } } \ln \left(\cfrac{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)}\right)\right]
 					\label{EQ:Enthalpy_PR}
@@
 %				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
-				{\color{black}y}(t) &= \int_{t_0}^{t_f} \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))} {\color{black}c_f}(t,z) \biggr\rvert_{z=L} dt \\
+				{\color{black}y}(t) &= \int_{t_0}^{t_f} \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} dt \\
 %				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
-				\cfrac{d{\color{black}y}(t)}{dt} &= \qquad \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))} {\color{black}c_f}(t,z) \biggr\rvert_{z=L} 
+				\cfrac{d{\color{black}y}(t)}{dt} &= \qquad \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} 
                 \label{Model_measurment_2}
@@
 				\begin{bmatrix}
-					\cfrac{\partial {\color{black}c_f}(t,z)}{\partial t}\\
-					\cfrac{\partial {\color{black}c_s}(t,z)}{\partial t}\\
+					\cfrac{\partial c_f}{\partial t}\\
+					\cfrac{\partial c_s}{\partial t}\\
 					\cfrac{\partial {\color{black}h}(t,z)}{\partial t} \\
@@
 				\begin{bmatrix}
-					{\color{black}\bar{\phi_1}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
-					{\color{black}\bar{\phi_2}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
-					{\color{black}\bar{\phi_3}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right) \\
-					{\color{black}\bar{\phi_4}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
-					{\color{black}\bar{\phi_5}} \left( {\color{black}c_f}(t,z),{\color{black}c_s}(t,z),{\color{black}h}(t,z); {\color{black}\Theta} \right)
+					{\color{black}\bar{\phi_1}} \left( c_f,c_s,{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
+					{\color{black}\bar{\phi_2}} \left( c_f,c_s,{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
+					{\color{black}\bar{\phi_3}} \left( c_f,c_s,{\color{black}h}(t,z); {\color{black}\Theta} \right) \\
+					{\color{black}\bar{\phi_4}} \left( c_f,c_s,{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
+					{\color{black}\bar{\phi_5}} \left( c_f,c_s,{\color{black}h}(t,z); {\color{black}\Theta} \right)
 				\end{bmatrix} = {\color{black}\bar{\phi}} \left( t,z; {\color{black}\Theta} \right) = \cfrac{\partial {\color{black}\chi}(t,z)}{\partial t}
@@
 
-		%In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases (${\color{black}c_f}(t,z)$ and ${\color{black}c_s}(t,z)$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{black}h}(t,z)$).
+		%In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases ($c_f$ and $c_s$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{black}h}(t,z)$).
 The controllable input variables are the mass flow rate and temperature of the solvent in the feed and the pressure in the extractor.
@@
 		%The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase, and it can be measured after the separator (${\color{black}Y}(t)$).
-The system is controllable by manipulating the flow rate and temperature (enthalpy) of $CO_2$ in the feed and the pressure in the extractor.
+The system is controllable by manipulating the flow rate and temperature (enthalpy) of CO$_2$ in the feed and the pressure in the extractor.
 

### 2024-04-08 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Results_Chamomile.tex
08.04

@@
 			\begin{split}
-				&\lim_{k_m \rightarrow \infty} \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right)  = \\
+				&\lim_{k_m \rightarrow \infty} \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}(T(t,z)){\color{black}\rho}(T(t,z),{\color{black}P}(t))}  c_f \right)  = \\
 				&= \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{\rho_s}{\infty \cdot \rho(T(t,z),P(t))}  {c_f}(t,z) \right) = \left(c_s(t,z) - 0 \right)
@@
 Decay patterns under various operational conditions, depicted in Figure \ref{fig: Gamma_function}, show that the internal diffusion coefficient is notably higher in fluids under high pressure.
-This observation aligns with the findings of \citet{Giddings1968}, \citet{Gurdial1989}, and \citet{Machida2011}, who explored the solvation capability of solvents and its correlation with the physical properties of $CO_2$ by calculating the Hildebrand solubility parameter $\delta_H$.
+This observation aligns with the findings of \citet{Giddings1968}, \citet{Gurdial1989}, and \citet{Machida2011}, who explored the solvation capability of solvents and its correlation with the physical properties of CO$_2$ by calculating the Hildebrand solubility parameter $\delta_H$.
 \citet{Giddings1968} introduced a correlation for the solubility parameter $\delta_H[\text{MPa}^{1/2}] = 1.25 P_c^{1/2}\rho_r$, with $P_c$ and $\rho_r$ representing the critical pressure and reduced density, respectively.

### 2024-04-08 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Saturation.tex
19.03
08.04

--- 2023-10-11 SFE_article_Sensitivity_Analysis/Sections/Saturation.tex
@@
 
-	\subsubsection{Uneven distribution of the solute in the solid phase}
+	\subsubsection{Uneven solute's distribution in the solid phase} \label{CH: Gamma_Function}
 
@@
 			\label{Model_kinetic}
-				{\color{black}r_e}(t,z) = -\cfrac{{\color{black}D_i^R}({\color{black}T}(t,z), {\color{black}P}(t)) {\color{black} \gamma}({\color{black} c_s} (t,z)) }{{\color{black} \mu l^2} } \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right)
+				r_e = -\cfrac{{\color{black}D_i^R}(T(t,z), {\color{black}P}(t), F(t)) {\color{black} \gamma}({\color{black} c_s} (t,z)) }{{\color{black} \mu l^2} } \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}c_f(t,z)}{{\color{black}k_m}(T(t,z)){\color{black}\rho}(T(t,z),{\color{black}P}(t))}  \right)
 		\end{equation} }

### 2024-04-08 SFE_article_Parameter_Estimation_short - Chamomile/Sections/introduction_imp.tex
08.04

@@
 Parameters such as the pressure ($P$), feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) are adjustable and measurable, while the outlet temperature ($T_{out}$) and the amount of product at the outlet can only be monitored.
-Figure \ref{fig: SFE_drawing} presents a simplified flow diagram illustrating the process setup.
+Figure \ref{fig: SFE_drawing} presents a simplified process flow diagram.
 
@@
 
-	This study focuses on creating a process model for the extraction of natural substances from solid materials using supercritical fluids, with a particular emphasis on supercritical $CO_2$.
+	This study focuses on creating a process model for the extraction of natural substances from solid materials using supercritical fluids, with a particular emphasis on supercritical CO$_2$.
 The approach involves estimating the solvent properties through thermodynamic relationships and determining the extraction kinetic parameters via a series of experiments conducted under a variety of conditions.
 The maximum likelihood estimator method is employed to address the parameter estimation challenge, with the derived parameters subsequently used to establish correlations.
-These correlations are instrumental in extending the applicability of the process model across different temperatures (30 to 40$^\circ C$), pressures (100 to 200 bar) and flow rates (3.33 to 6.67 $\times 10^{-5}$ kg/s).
+These correlations are instrumental in extending the applicability of the process model across different temperatures (30 to 40$~^\circ \text{C}$), pressures (100 to 200 bar) and flow rates (3.33 to 6.67 $\times 10^{-5}$ kg/s).
 

### 2024-04-08 SFE_article_Parameter_Estimation_short - Chamomile/Short_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
08.04

@@
 \begin{abstract}
-This study investigated the supercritical extraction process of chamomile extract from chamomile flowers.
+This study investigates the supercritical extraction process of essential oil from chamomile flowers.
+Essential oils of chamomile are used extensively for medicinal purposes.
+Many different products of chamomile have been developed, the most popular of which is in the form of herbal tea.
 A distributed-parameter model describes the fluid-solid extraction process.
@@
 \subsection{Governing equations} \label{CH:Governing_equations_chapter}
-	The governing equations for quasi-one-dimensional compressible flow in Cartesian coordinates are detailed in Appendix \ref{CH: Gouverning equations} and are based on the foundational work by \citet{Anderson1995}.
-Quasi-one-dimensional flow refers to a fluid flow scenario where it's assumed that flow properties are uniformly distributed across any given cross-section.
+	The governing equations based on the work of \citet{Anderson1995} for quasi-one-dimensional compressible flow in Cartesian coordinates are presented in Appendix \ref{CH: Gouverning equations}.
+Quasi-one-dimensional flow refers to a fluid flow scenario assuming that flow properties are uniformly distributed across any given cross-section.
 This simplification is typically applied in situations where the flow channel's cross-sectional area changes, such as through irregular shapes or partial fillings of an extractor.
-In these instances, the flow is considered quasi-one-dimensional because it's presumed that velocity and other flow properties change solely along the flow direction.
+According to this assumption, velocity and other flow properties change solely in the flow direction.
 
-	The set of quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates are described by Equations \ref{EQ: CompressibleEuler_1} through \ref{EQ: CompressibleEuler_3}.
+	The set of quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}.
 The formulation of these equations is elaborated upon in Appendix \ref{CH: Gouverning equations}, providing a mathematical foundation for analyzing flow dynamics under the assumed conditions.
@@
 		\label{EQ: CompressibleEuler_1}
-		\cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v \right)}{\partial z} &= 0 \\
-		\cfrac{\partial \left( {\color{black}\rho_f} v {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v^2 \right)}{\partial z} &= -{\color{black}A_f}(z) \cfrac{\partial {\color{black}P}}{\partial z} \label{EQ: CompressibleEuler_2} \\
-		\cfrac{\partial \left( {\color{black}\rho_f} {\color{black}e} {\color{black}A_f}(z) \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f} {\color{black}A_f}(z) v {\color{black}e}\right)}{\partial z} &= -{\color{black}P}\cfrac{\left( {\color{black}A_f}(z) v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial {\color{black}T}}{\partial z} \right)
+		\cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
+		\cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial {\color{black}P}}{\partial z} \label{EQ: CompressibleEuler_2} \\
+		\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -{\color{black}P}\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
 		\label{EQ: CompressibleEuler_3}
@@
 
-where ${\color{black}\rho_f}$ is the density of the fluid, ${\color{black}A_f}(z)$ is the function which describe change of the cross-section, $v$ is the velocity, ${\color{black}P}$ is the total pressure, ${\color{black}e}$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
+where $\rho_f$ is the density of the fluid, $A_f$ is the function which describe change of the cross-section, $v$ is the velocity, ${\color{black}P}$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
 
@@
 			\draw (4.5,0) -- (4.5,2); 	% Bottom line
-			\node at (4,1.5) {${\color{black}\rho_f}$};
-			\node at (5.5,1.5) {${\color{black}\rho_f}+\delta{\color{black}\rho_f}$};
+			\node at (4,1.5) {$\rho_f$};
+			\node at (5.5,1.5) {$\rho_f+\delta\rho_f$};
 			\node at (4,1.0) {${\color{black}P}$};
 			\node at (5.5,1.0) {${\color{black}P}+\delta {\color{black}P}$};
-			\node at (4,0.5) {${\color{black}T}$};
-			\node at (5.5,0.5) {${\color{black}T}+\delta {\color{black}T}$};
+			\node at (4,0.5) {$T$};
+			\node at (5.5,0.5) {$T+\delta T$};
 			\node at (1,1.0) {$v \rightarrow$};
@@
 	\begin{align*}
-		&{\color{black}\rho_f} \delta v + v \delta {\color{black}\rho_f} + \delta {\color{black}\rho_f} \delta v = 0 \\
-		&\delta {\color{black}P} = \delta v \delta {\color{black}\rho_f}
+		&\rho_f \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 \\
+		&\delta {\color{black}P} = \delta v \delta \rho_f
 	\end{align*}
@@
 	\begin{equation*}
-		\lim_{{\color{black}\rho_f} v \rightarrow 0} {\color{black}\rho_f} \delta v + v \delta {\color{black}\rho_f} + \delta {\color{black}\rho_f} \delta v = 0 / \delta {\color{black}\rho_f} \rightarrow \cfrac{d v}{d {\color{black}\rho_f}} = - \cfrac{v}{{\color{black}\rho_f}}
+		\lim_{\rho_f v \rightarrow 0} \rho_f \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 / \delta \rho_f \rightarrow \cfrac{d v}{d \rho_f} = - \cfrac{v}{\rho_f}
 	\end{equation*}
@@
 	\begin{equation} \label{EQ: Pressure_Velocity}
-		\cfrac{d v}{d {\color{black}\rho_f}} = - \cfrac{d v}{d{\color{black}P}} \cfrac{d {\color{black}P}}{d {\color{black}\rho_f}} = -\cfrac{1}{\rho v} \cfrac{d{\color{black}P}}{d{\color{black}\rho_f}} = -\cfrac{v}{{\color{black}\rho_f}}
+		\cfrac{d v}{d \rho_f} = - \cfrac{d v}{d{\color{black}P}} \cfrac{d {\color{black}P}}{d \rho_f} = -\cfrac{1}{\rho v} \cfrac{d{\color{black}P}}{d\rho_f} = -\cfrac{v}{\rho_f}
 	\end{equation}
@@
 
-Suppose the flow is presumed to be isentropic, $d{\color{black}P}/d{\color{black}\rho_f} = c^2$, so $v^2=c^2$, where $c$ is the speed of sound.
+Suppose the flow is presumed to be isentropic, $d{\color{black}P}/d\rho_f = c^2$, so $v^2=c^2$, where $c$ is the speed of sound.
 This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow.
-If the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic, which leads to $\partial {\color{black}\rho_f} / \partial {\color{black}P} \approx 0$.
+If the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic, which leads to $\partial \rho_f / \partial {\color{black}P} \approx 0$.
 The small changes in pressure due to flow velocity changes do not change the density.

### 2024-04-09 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Experiments.tex
08.04
09.04

--- 2024-02-22 SFE_article_Parameter_Estimation - Chamomile/Sections/Experiments.tex
@@
 
-	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers.
-The experiments were performed by \citet{Povh2001}.
+	%In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers.
+The experiments were performed by \citet{Povh2001} and \citet{Rahimi2011}.
 To prepare the flowers for extraction, they were first pre-treated using a knife mill (TECNAL, model TE 340) to reduce their particle size.
-The mean
-	particle diameter was determined by the Sauter equation and is equal to $0.3\times 10^{-3}$m.
+The Sauter equation determined the mean particle diameter and is equal to $0.3\times 10^{-3}$m.
 The actual density of the chamomile particles was measured through helium pycnometry at the Institute of Chemistry IQ/Unicamp's Analytical Facilities.
@@
 
-	The experiments were conducted using an extractor with diameter of $3.96\times 10^{-2}$ m and length $16.55\times 10^{-2}$ m.
-Twelve experiments were performed under different but constant in time operating conditions: $30-40^\circ C$, $100 - 200$ bar, and $1.33-6.67 \times 10^{-5}$ kg/s.
-The amount of solid material used for extraction was $75\times 10^{-3}$ kg, which was sufficient to fill the whole vessel.
-Samples were collected every 30 min for the first 3 h and every hour afterwards up to 10 h.
+	The experiments were conducted using an a semi-batch extractor with diameter of 3.96 [cm] and length of 16.55 [cm].
+Twelve experiments were performed under different operating conditions: $30-40^\circ C$, $100 - 200$ [bar], and $0.05 - 0.24$ [kg/h].
+The amount of solid material used for extraction was $75$ [g], which was sufficient to fill the whole vessel.
+The bulk density of the bed was computed based on the feed's mass and the extractor's volume.
+The total porosity of the bed, including the particles, was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$.
 
 	%After loading the material into the extraction chamber, the extractor was pre-heated to the desired temperature.
-The outlet line was then closed, and the extraction chamber was filled with $CO_2$.
-The $CO_2$ was pumped and compressed until the desired operating pressure was reached.
+The outlet line was then closed, and the extraction chamber was filled with CO$_2$.
+The CO$_2$ was pumped and compressed until the desired operating pressure was reached.
 When the operating temperature and pressure were achieved, the outlet line was opened, allowing the solvent to flow through the system.
-The solvent extracted the essential oils from the solid material, and the resulting $CO_2$ and oil mixture flowed from the extractor to the separator.
+The solvent extracted the essential oils from the solid material, and the resulting CO$_2$ and oil mixture flowed from the extractor to the separator.
 The separator operated at $50^\circ C$ and $50$ bar.
-The gaseous $CO_2$ exited from the top and was recycled to the $CO_2$ storage tank.
+The gaseous CO$_2$ exited from the top and was recycled to the CO$_2$ storage tank.
 The oil stayed at the bottom of the separator in the liquid form.

### 2024-04-09 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
09.04

@@
 		\begin{equation} \label{EQ: Continuity_differential}
-			\frac{\partial (\rho_f \phi)}{\partial t} + \frac{\partial (\rho_f v A\phi)}{\partial {\color{black}z}} = 0
+			\frac{\partial (\rho_f \phi)}{\partial t} + \frac{\partial (\rho_f v A\phi)}{\partial z} = 0
 		\end{equation}
 	}
-	where ${\color{black} A}$ is the total cross-section of the extractor and $\phi$ describe porosity along the extractor.
+	where $A$ is the total cross-section of the extractor and $\phi$ describe porosity along the extractor.
 
@@
 		\begin{equation}
-			\int \frac{\partial (\rho_f v A \phi )}{\partial {\color{black}z}} dz = F \rightarrow {\color{black}F}=\rho_f v A\phi
+			\int \frac{\partial (\rho_f v A \phi )}{\partial z} dz = F \rightarrow F=\rho_f v A\phi
 		\end{equation}
@@
 
-	To simplify the dynamics of the system, it is assumed that ${\color{black}F}=F$ is a control variable and affects the whole system instantaneously.
-This assumption allows for finding the velocity profile that satisfies mass continuity based on $F$, $\phi$, and $\rho_f$.
+	To simplify the system's dynamics, it is assumed that $F$ is a control variable and affects the whole system instantaneously, which allows finding the velocity profile that satisfies mass continuity based on $F$, $\phi$, and $\rho_f$.
 
@@
 
-	The fluid density $\rho_f$ can be obtained from an equation of state (Appendix \ref{CH: EOS}) if temperature and the thermodynamic pressure (assumed ${\color{black}P}(t)$ to be constant along ${\color{black}z}$ due to the low-Mach number condition) are known.
-The variation in density may be caused by the fluid accumulation in the system (equivalent to pressure change), which occurs instantaneously along ${\color{black}z}$ or by a temperature change.
-
-	Analogously, the superficial velocity might be introduced to the model and defined as
+	Similarly, the superficial velocity might be introduced.
 
@@
 		\begin{equation}
-			u = v \phi = \cfrac{F}{\rho_f {\color{black} A} }
+			u = v \phi = \cfrac{F}{\rho_f A }
 		\end{equation}
 	}
+
+	The fluid density $\rho_f$ can be obtained from an equation of state (Appendix \ref{CH: EOS}) if temperature and thermodynamic pressure are known along $z$.
+The variation in fluid density may occurs due to pressure or a inlet temperature changes.
 
@@
 			\frac{\partial c_f}{\partial t}
-			+ \frac{1}{\phi} \frac{\partial \left( c_f u\right)}{\partial {\color{black}z}}
+			+ \frac{1}{\phi} \frac{\partial \left( c_f u\right)}{\partial z}
 			= \frac{1-\phi}{\phi} r_e
-			+ \frac{1}{\phi} \frac{\partial}{\partial {\color{black}z}} \left( {\color{black}D^M_e} \frac{\partial c_f}{\partial {\color{black}z}} \right)
+			+ \frac{1}{\phi} \frac{\partial}{\partial z} \left( D^M_e \frac{\partial c_f}{\partial z} \right)
 		\end{equation}
@@
 
-	$c_f$ represents the concentration of solute in the fluid phase, , $r_e$ is a mass transfer kinetic term, and ${\color{black}D^M_e}(T(t,z),{\color{black}P}(t),F)$ is the axial diffusion coefficient.
+	$c_f$ represents the concentration of solute in the fluid phase, $r_e$ is a mass transfer kinetic term, and $D^M_e$ is the axial diffusion coefficient.
 
@@
 Therefore, the only significant term in this equation is the kinetic term (as defined in Equation \ref{Model_kinetic_basic}), which connects the solid and fluid phases.
-The extract is represented by a single pseudo-component to simplify the analysis.
+The extract is represented by a single pseudo-component for simplicity.
 
@@
 The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
-Figure \ref{fig: SFE_Mechanism} illustrates the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as ${\color{black}c_s}$ and the equilibrium concentrations at the solid-fluid interface are denoted as ${\color{black}c_s^*}$ and ${\color{black}c_p^*}$, respectively, for solid and fluid phases.
-The concentration of the solutes in the fluid phase in the center of the pore is denoted as ${\color{black}c_{p}}$.
-As the solute diffuses through the pore, its concentration changes and reaches ${\color{black}c_{pf}}$ at the opening of the pore.
-The solute then diffuses through the film around the particle and reaches bulk concentration ${\color{black}c_f}$.
+Figure \ref{fig: SFE_Mechanism} illustrates the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as $c_s$ and the equilibrium concentrations at the solid-fluid interface are denoted as $c_s^*$ and $c_p^*$, respectively, for solid and fluid phases.
+The concentration of the solutes in the fluid phase in the center of the pore is denoted as $c_p$.
+As the solute diffuses through the pore, its concentration changes and reaches $c_{pf}$ at the opening of the pore.
+The solute then diffuses through the film around the particle and reaches bulk concentration $c_f$.
 The two-film theory describes the solid-fluid interface inside the pore.
@@
 
-		\citet{Bulley1984} suggests a process where the driving force for extraction is given by the difference between the concentration of the solute in bulk, ${\color{black}c_f}$, and in the center of the pore, ${\color{black}c_p^*}$.
-The concentration ${\color{black}c_p^*}$ is in equilibrium with ${\color{black}c_s}$ according to an equilibrium relationship.
-The rate of extraction is thus ${\color{black}r_\text{e}}\left({\color{black}c_f} - {\color{black}c^*_p}({\color{black}c_s})\right)$.
+		\citet{Bulley1984} suggests a process where the driving force for extraction is given by the difference between the concentration of the solute in bulk, $c_f$, and in the center of the pore, $c_p^*$.
+The concentration $c_p^*$ is in equilibrium with $c_s$ according to an equilibrium relationship.
+The rate of extraction is thus $r_e\left(c_f - c^*_p(c_s)\right)$.
 
-		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between ${\color{black}c_s}$ and ${\color{black}c_p^*}$.
-${\color{black}c_p^*}$ is determined by an equilibrium relationship with ${\color{black}c_f}$ and the extraction rate is ${\color{black}r_\text{e}}\left({\color{black}c_s} - {\color{black}c^*_p}({\color{black}c_f})\right)$ or more precisely
+		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$.
+$c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate is $r_e\left(c_s - c^*_p(c_f)\right)$ or more precisely
 
@@
 				\begin{equation} \label{Model_kinetic_basic}
-					r_e = \cfrac{{\color{black}D_i}(T(t,z), {\color{black}P}(t), F(t))}{{\color{black} \mu l^2} }\left(c_s - {\color{black}c_P^*}(t,z) \right)
+					r_e = \cfrac{D_i}{\mu l^2 }\left(c_s - c_p^* \right)
 			\end{equation} }
 
-		where ${\color{black}\mu}$ is sphericity, ${\color{black}l}$ a characteristic dimension of particles and can be defined as ${\color{black}l} = {\color{black}r}/3$, ${\color{black}r}$ is the mean particle radius, ${\color{black}\rho_s}$ is the solid density, ${\color{black}D_i}(T(t,z))$ corresponds to the overall diffusion coefficient and ${\color{black}c_P^*}(t,z)$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).
+		where $\mu$ is sphericity, $l$ a characteristic dimension of particles and can be defined as $l = r/3$, $r$ is the mean particle radius, $\rho_s$ is the solid density, $D_i$ corresponds to the overall diffusion coefficient and $c_P^*$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).
 
-		According to \citet{Bulley1984}, a linear equilibrium relationship (equation  \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{black}c_f^*}(t,z)$ is based on the concentration of the solute in the solid phase $c_s$
+		According to \citet{Bulley1984}, a linear equilibrium relationship (Equation  \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase $c_f^*$ is based on the concentration of the solute in the solid phase $c_s$.
 
@@
 				\begin{align} \label{Linear_equilibirum}
-					{\color{black}c}(t,z) &= {\color{black}k_p}(T(t,z),{\color{black}P}(t)) \allowbreak {\color{black}q^*}(t,z)
+					c_f^* &= k_p c_s
 			\end{align} }
 
-			The volumetric partition coefficient ${\color{black}k_p}(T(t,z),{\color{black}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
-According to \citet{Spiro2007}, the term ${\color{black}k_p}(T(t,z),{\color{black}P}(t))$ can be expressed as the function of mass partition factor ${\color{black}k_m}(T(t,z))$.
+			The volumetric partition coefficient $k_p$ acts as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
+According to \citet{Spiro2007}, $k_p$ can be expressed through the mass partition coefficient $k_m$.
 
@@
 				\begin{align}
-					{\color{black}k_m}(T(t,z)) = \cfrac{{\color{black}k_p}(T(t,z),{\color{black}P}(t)) {\color{black}\rho_s}}{{\color{black}\rho}(T(t,z),{\color{black}P}(t))}
+					k_m = \cfrac{k_p \rho_s}{\rho_f}
 			\end{align} }
 
-			Equation \ref{Model_kinetic_no_sat} represents of the kinetic term according to \citet{Reverchon1996}
+			%Equation \ref{Model_kinetic_no_sat} represents of the kinetic term according to \citet{Reverchon1996}
+			According to \citet{Reverchon1996}, the kinetic term becomes
 
@@
 					\label{Model_kinetic_no_sat}
-					r_e = -\cfrac{{\color{black}D_i}(T(t,z), {\color{black}P}(t), F(t))}{{\color{black} \mu l^2} }\left(c_s - \cfrac{{\color{black}\rho_s}c_f(t,z)}{{\color{black}k_m}(T(t,z))\rho_f}   \right)
+					r_e = -\cfrac{D_i}{ \mu l^2 } \left(c_s - \cfrac{\rho_s c_f}{k_m \rho_f} \right)
 			\end{equation} }
@@
 The pseudo-homogenous phase is assumed to flow only in the axial direction.
-The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid ${\color{black}C_p}(T(t,z),{\color{black}P}(t))$ because the solid phase is stationary.
+The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid $C_p$ because the solid phase is stationary.
 Therefore, this factor can be understood as the fraction of the fluid's total heat through convection.
@@
 						\cfrac{\partial T(t,z)}{\partial t} &= 
-						\underbrace{ -\cfrac{F {\color{black}C_p}(T(t,z),{\color{black}P}(t))}{{\color{black}A} 	[(1-{\color{black}\epsilon})\rho_f {\color{black}C_p} (T(t,z),{\color{black}P}(t)) + {\color{black} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial T(t,z)}{\partial {\color{black}z}}  }_{\text{Convection}} + \\
+						\underbrace{ -\cfrac{F {\color{black}C_p}(T(t,z),{\color{black}P}(t))}{{\color{black}A} 	[(1-{\color{black}\epsilon})\rho_f {\color{black}C_p} (T(t,z),{\color{black}P}(t)) + {\color{black} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial T(t,z)}{\partial z}  }_{\text{Convection}} + \\
 						& + \underbrace{ {\color{black}D^T_e}(T(t,z),{\color{black}P}(t)) \cfrac{\partial^2 T(t,z)}{\partial {\color{black}z^2}} }_{\text{Diffusion}}
@@
 			\begin{align} \label{EQ: Heat_internal}
-				&\cfrac{\partial \left( \rho_f e(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e(t,z) \right)}{\partial {\color{black}z}} \nonumber \\
-				&= -{\color{black}P}(t)\cfrac{\left( A_f v \right)}{\partial {\color{black}z}} + \cfrac{\partial}{\partial {\color{black}z}} \left( \cfrac{\partial T(t,z)}{\partial {\color{black}z}} \right) 
+				&\cfrac{\partial \left( \rho_f e(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e(t,z) \right)}{\partial z} \nonumber \\
+				&= -{\color{black}P}(t)\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T(t,z)}{\partial z} \right) 
 			\end{align}
@@
 A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution (Equation \ref{EQ: Heat_internal}) and the output from Equation \ref{EQ: internal_energy_PR}.
-Such a procedure allows to find a local temperature along spatial direction ${\color{black}z}$ and needs to be repeated every time-step.
+Such a procedure allows to find a local temperature along spatial direction $z$ and needs to be repeated every time-step.
 
@@
 				\begin{align} \label{EQ:Enthalpy_equation}
-					\cfrac{\partial \left(\rho_f {\color{black}h}(t,z) A_f\right)}{\partial t} &= - \cfrac{\partial \left( \rho_f {\color{black}h}(t,z) A_f v \right)}{\partial {\color{black}z}}  \nonumber \\
-					& + \cfrac{\partial \left({\color{black}P}(t) A_f\right)}{\partial t} + \cfrac{\partial}{\partial {\color{black}z}} \left( k \cfrac{\partial T(t,z)}{\partial {\color{black}z}} \right)
+					\cfrac{\partial \left(\rho_f {\color{black}h}(t,z) A_f\right)}{\partial t} &= - \cfrac{\partial \left( \rho_f {\color{black}h}(t,z) A_f v \right)}{\partial z}  \nonumber \\
+					& + \cfrac{\partial \left({\color{black}P}(t) A_f\right)}{\partial t} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T(t,z)}{\partial z} \right)
 				\end{align}
@@
 %				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
-				{\color{black}y}(t) &= \int_{t_0}^{t_f} \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} dt \\
+				y &= \int_{t_0}^{t_f} \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} dt \\
 %				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
-				\cfrac{d{\color{black}y}(t)}{dt} &= \qquad \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} 
+				\cfrac{dy}{dt} &= \qquad \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} 
                 \label{Model_measurment_2}
@@
 		\subsubsection{Initial and boundary conditions} 
-		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{black}c_{s0}}$.
+		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content $c_{s0}$.
 As the residence time is much shorter than the sampling time, the initial state estimate for the concentration of the solute in the fluid phase would be not reliable.
@@
 				\begin{align*}
-					&{\color{black}c_f}(t = 0, z) = 0 && c_s(t = 0, z) = {\color{black}c_{s0}} && {c_f}(t, z=0) = 0 \\
+					&c_f(t = 0, z) = 0 && c_s(t = 0, z) = c_{s0} && {c_f}(t, z=0) = 0 \\
 					&\frac{\partial c_f(t,z=L)}{\partial x} = 0 && c_s(t, z=\{0,L\}) = 0 && y(0) = 0
@@
 
-		The method of lines is used to transform the process model equations into a set of ODEs denoted as ${\color{black}G}({\color{black}x}(t);{\color{black}\Theta})$.
-The partial derivatives in $z$-direction are computed using a first-order and second-order finite difference approximation.
-The backward finite difference is used to approximate the first-order derivative, while the central difference scheme is used to approximate the second-order derivative.
+		The method of lines is used to transform the process model equations into a set of ODEs denoted as $G(x;\Theta)$.
+The backward finite difference is used to approximate the first-order derivative, while the central difference scheme is used to approximate the second-order derivative $z$-direction.
 The length of the fixed bed is divided into $N_z$ equally distributed points in $z$-direction.
-The state-space model after the discretization is represented by $\dot{{\color{black}x}}(t)$.
+The state-space model after the discretization is represented by $x$.
 
@@
 			\begin{align*} \label{discretization}
-				\dot{{\color{black}x}}(t) &= \cfrac{d {\color{black}x}(t)}{d t} = 
+				\dot{{\color{black}x}}(t) &= \cfrac{d x}{d t} = 
 				\begin{bmatrix}
@@
 				\underbrace{\begin{bmatrix}
-						{\color{black}G_1} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right)\\ 
+						{\color{black}G_1} \left( c_f,c_s,{\color{black}h}(t); \Theta \right)\\ 
 						\vdots\\ 
-						{\color{black}G_{N_z}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right)\\ 
+						{\color{black}G_{N_z}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right)\\ 
 						\\ \hline \\ \\
-						{\color{black}G_{N_z+1}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right)\\ 
+						{\color{black}G_{N_z+1}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right)\\ 
 						\vdots\\
-						{\color{black}G_{2N_z}} \left( {\color{black}c}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right)\\ 
+						{\color{black}G_{2N_z}} \left( {\color{black}c}(t),c_s,{\color{black}h}(t); \Theta \right)\\ 
 						\\ \\ \hline \\ 
-						{\color{black}G_{2N_z+1}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right) \\
+						{\color{black}G_{2N_z+1}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) \\
 						\vdots\\
-						{\color{black}G_{3N_z}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right) \\ 
+						{\color{black}G_{3N_z}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) \\ 
 						\\ \\ \hline \\
-						{\color{black}G_{3N_z+1}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right) \\
+						{\color{black}G_{3N_z+1}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) \\
 						\\ \\ \hline \\
-						{\color{black}G_{3N_z+2}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t),{\color{black}h}(t); {\color{black}\Theta} \right) 
-				\end{bmatrix}}_{{\color{black}G} \left( {\color{black}x}(t); {\color{black}\Theta} \right)} 
+						{\color{black}G_{3N_z+2}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) 
+				\end{bmatrix}}_{{\color{black}G} \left( x; \Theta \right)} 
 		\end{align*} }
@@
 			\begin{align*} \label{discretization}
-				\dot{{\color{black}x}}(t) &= \cfrac{d {\color{black}x}(t)}{d t} = 
+				\dot{x} &= \cfrac{d x}{d t} = 
 				\begin{bmatrix}
-					\cfrac{d {\color{black}c_{f,1}}(t)}{d t} 	  \\
+					\cfrac{d c_{f,1}}{d t} 	  \\
 					\vdots		\\	
-					\cfrac{d {\color{black}c_{f,N_z}}(t)}{d t} \\
+					\cfrac{d c_{f,N_z}}{d t} \\
 					\\ \hline  	\\
-					\cfrac{d {\color{black}c_{s,1}}(t)}{d t} 	  \\
+					\cfrac{d c_{s,1}}{d t} 	  \\
 					\vdots		\\
-					\cfrac{d {\color{black}c_{s,N_z}}(t)}{d t} \\
+					\cfrac{d c_{s,N_z}}{d t} \\
 					%\\ \hline \\
@@
 				\underbrace{\begin{bmatrix}
-						{\color{black}G_1} \left( {\color{black}c_f}(t),{\color{black}c_s}(t); {\color{black}\Theta} \right)\\ 
+						G_1 \left( c_f,c_s; \Theta \right)\\ 
 						\vdots\\ 
-						{\color{black}G_{N_z}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t); {\color{black}\Theta} \right)\\ 
+						G_{N_z} \left( c_f,c_s; \Theta \right)\\ 
 						\\ \hline \\ \\
-						{\color{black}G_{N_z+1}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t); {\color{black}\Theta} \right)\\ 
+						G_{N_z+1} \left( c_f,c_s; \Theta \right)\\ 
 						\vdots\\
-						{\color{black}G_{2N_z}} \left( {\color{black}c}(t),{\color{black}c_s}(t); {\color{black}\Theta} \right)\\ 
+						G_{2N_z} \left( c_f,c_s; \Theta \right)\\ 
 						%\\ \\ \hline \\ 
-						%{\color{black}G_{2N_z+1}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t); {\color{black}\Theta} \right) \\
+						%{\color{black}G_{2N_z+1}} \left( c_f,c_s; \Theta \right) \\
 						\\ \\ \hline \\
-						{\color{black}G_{2N_z+2}} \left( {\color{black}c_f}(t),{\color{black}c_s}(t); {\color{black}\Theta} \right) 
-				\end{bmatrix}}_{{\color{black}G} \left( {\color{black}x}(t); {\color{black}\Theta} \right)} 
+						G_{2N_z+2} \left( c_f,c_s; \Theta \right) 
+				\end{bmatrix}}_{G \left( x; \Theta \right)} 
 		\end{align*} }
 
-		where ${\color{black}x} \in \mathbb{R}^{N_x = 2N_z+1} $ and ${\color{black}\Theta} \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters, $N_{u}$ is the number of control variables.
+		where ${\color{black}x} \in \mathbb{R}^{N_x = 2N_z+1} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters, $N_{u}$ is the number of control variables.
 
@@
 				\begin{bmatrix}
-					{\color{black}\bar{\phi_1}} \left( c_f,c_s,{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
-					{\color{black}\bar{\phi_2}} \left( c_f,c_s,{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
-					{\color{black}\bar{\phi_3}} \left( c_f,c_s,{\color{black}h}(t,z); {\color{black}\Theta} \right) \\
-					{\color{black}\bar{\phi_4}} \left( c_f,c_s,{\color{black}h}(t,z); {\color{black}\Theta} \right)\\
-					{\color{black}\bar{\phi_5}} \left( c_f,c_s,{\color{black}h}(t,z); {\color{black}\Theta} \right)
-				\end{bmatrix} = {\color{black}\bar{\phi}} \left( t,z; {\color{black}\Theta} \right) = \cfrac{\partial {\color{black}\chi}(t,z)}{\partial t}
+					{\color{black}\bar{\phi_1}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)\\
+					{\color{black}\bar{\phi_2}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)\\
+					{\color{black}\bar{\phi_3}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right) \\
+					{\color{black}\bar{\phi_4}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)\\
+					{\color{black}\bar{\phi_5}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)
+				\end{bmatrix} = {\color{black}\bar{\phi}} \left( t,z; \Theta \right) = \cfrac{\partial {\color{black}\chi}(t,z)}{\partial t}
 		\end{align} }
 
-		where ${\color{black}\Theta}$ is a paramter space, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.
+		where $\Theta$ is a paramter space, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.
 

### 2024-04-09 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Parameter_estimation.tex
14.03
09.04

--- 2024-02-22 SFE_article_Parameter_Estimation - Chamomile/Sections/Parameter_estimation.tex
@@
 	Only some of the parameters in a process model can be estimated from the theoretical considerations.
-The goal of parameter estimation is to obtain the "best" estimate of unknown parameters ${\color{black} \theta}$ (which is a subset of the parameter space ${\color{black}\Theta}$ containing all parameters of a model) based on the continuous observations ${\color{black}Y}(t)$ or the discrete observations ${\color{black}Y}(t_i)$.
-Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, ${\color{black}y}(t)$ (Equation \ref{Model_measurment_1}), to give the observable dependent variable ${\color{black}Y}(t)$ (for example results of an experiment).
+The goal of parameter estimation is to obtain the "best" estimate of unknown parameters $\theta$ (which is a subset of the parameter space ${\color{black}\Theta}$ containing all parameters of a model) based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$.
+Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, $y(t)$ (Equation \ref{Model_measurment_1}), to give the observable dependent variable $Y(t)$ (for example results of an experiment).
 For discrete observations, this can be expressed as:
@@
 		\begin{equation*}
-			{\color{black}Y}(t_i) = {\color{black}y}({\color{black} \theta}, t_i) + \epsilon(t_i)
+			Y(t_i) = y(\theta, t_i) + \epsilon(t_i)
 	\end{equation*} }
@@
 		\begin{equation*}
-			{\color{black}Y}(t) = {\color{black}y}({\color{black} \theta}, t) + \epsilon(t)
+			Y(t) = y(\theta, t) + \epsilon(t)
 	\end{equation*} }
 
-	However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $d{\color{black}Y}(t_i)/dt$ is measured instead of ${\color{black}Y}(t_i)$ itself.
-In such cases, it is assumed that the unobservable error is added to the deterministic derivative $d{\color{black}y}({\color{black} \theta}, t_i)/dt$ as shown below
+	However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $dY(t_i)/dt$ is measured instead of $Y(t_i)$ itself.
+In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ as shown below
 
@@
 		\begin{equation}  \label{EQ: Measurment_noise}
-			\cfrac{d {\color{black}Y}(t_i)}{dt} = \cfrac{d{\color{black}y}({\color{black} \theta}, t_i)}{dt} + \epsilon(t_i)
+			\cfrac{d Y(t_i)}{dt} = \cfrac{dy(\theta, t_i)}{dt} + \epsilon(t_i)
 	\end{equation} }
@@
 The derivation of the likelihood function under the assumption of the Gaussian distribution is presented in Appendix \ref{CH: ML}.
-The final form of the objective function is presented by Equation \ref{EQ: Objective_function}:
+The objective function is presented by Equation \ref{EQ: Objective_function}:
 
@@
 			\ln L = -\cfrac{n}{2}  \ln \left(2 \pi \sigma^2\right) 
-			- \cfrac{ \sum_{i=1}^{n} \left[  \cfrac{d {Y}(t_i)}{dt} - \cfrac{d{\color{black}y}({\color{black} \theta}, t_i)}{dt} \right]^2 }{2 {\color{black} \sigma}^2}
+			- \cfrac{ \sum_{i=1}^{n} \left[  \cfrac{d {Y}(t_i)}{dt} - \cfrac{dy(\theta, t_i)}{dt} \right]^2 }{2 \sigma^2}
 		\end{equation}
@@
 			\begin{aligned} \label{EQ: Optimization_formulation_MLE}
-				&\hat{{\color{black} \theta}}_{MLE} &= \arg \max_{{\color{black} \sigma}, {\color{black} \theta} \in \Theta} \ln L = \arg \max_{{\color{black} \sigma},{\color{black} \theta} \in \Theta} p({\color{black} \theta}|{\color{black}y}) \\
+				&\hat{\theta}_{MLE} &= \arg \max_{\sigma, \theta \in \Theta} \ln L = \arg \max_{\sigma,\theta \in \Theta} p(\theta|y) \\
 				&\text{subject to}
-				& \dot{ {\color{black}x} } = {\color{black}G}({\color{black} x}(t);{\color{black} \theta}) \\
-				&& {\color{black} \dot{\theta}} = 0 \\
-				&& {\color{black}y} = {\color{black}y}(t) \\
-				&& {\color{black} \theta}^{lb} \leq {\color{black} \theta} \leq {\color{black} \theta}^{ub}
+				& \dot{ x } = G({\color{black} x}(t);\theta) \\
+				&& \dot{\theta} = 0 \\
+				&& y = y(t) \\
+				&& \theta^{lb} \leq \theta \leq \theta^{ub}
 			\end{aligned}
@@
 
-	where $\hat{{\color{black} \theta}}$ is as maximum likelihood estimator, ${\color{black} \theta}^{lb}$ define the minimal value of ${\color{black} \theta}$, ${\color{black} \theta}^{ub}$ is the maximum value of ${\color{black} \theta}$ and $\sigma$ represents the standard deviation of the residuals (errors) between the observed data points and the model outputs.
+	where $\hat{\theta}$ is as maximum likelihood estimator, $\theta^{lb}$ define the minimal value of $\theta$, $\theta^{ub}$ is the maximum value of $\theta$ and $\sigma$ represents the standard deviation of the residuals (errors) between the observed data points and the model outputs.
 
@@
 
-	%Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector ${\color{black} \theta}$ and equating to zero the partial derivatives of $\ln L$:
+	%Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector $\theta$ and equating to zero the partial derivatives of $\ln L$:
 
@@
 	%	\begin{align}\label{EQ: MLE_Basic_Solution}
-	%		\cfrac{\partial \ln L}{\partial {\color{black} \theta}} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( {\color{black}y}(t_i) | {\color{black} \theta} \right) }{\partial {\color{black} \theta}} = 0 
+	%		\cfrac{\partial \ln L}{\partial \theta} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( y(t_i) | \theta \right) }{\partial \theta} = 0 
 	%\end{align} }
 
-	Solution of Equations \ref{EQ: Optimization_formulation_MLE} yield the desired estimates $\hat{{\color{black} \theta}}$.
-For some models, these equations can be explicitly solved for $\hat{{\color{black} \theta}}$ but in general, no closed-form solution to the maximization problem is known or available, and a maximum likelihood estimator can only be found via numerical optimization.
+	Solution of Equations \ref{EQ: Optimization_formulation_MLE} yield the desired estimates $\hat{\theta}$.
+For some models, these equations can be explicitly solved for $\hat{\theta}$ but in general, no closed-form solution to the maximization problem is known or available, and a maximum likelihood estimator can only be found via numerical optimization.
 

### 2024-04-09 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Results_Chamomile.tex
09.04

@@
 			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
-			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s]}% and temperature of 40 $[^\circ C]$}
+			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
 			\label{fig: Fit_1_4_Di_Gamma}
@@
 			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
-			\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s]}% and temperature of 30 $[^\circ C]$}
+			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
 			\label{fig: Fit_5_8_Di_Gamma}

### 2024-04-09 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Saturation.tex
09.04

@@
 
-	Following the idea of the Broken-and-Intact Cell (BIC) model presented by \citet{Sovova2017}, the internal diffusion coefficient ${\color{black}D_i}$ is consider to be a product of the reference value of ${\color{black}D_i^R}$ and the exponential decay function ${\color{black} \gamma}$, as given by Equation \ref{EQ: C_sat_function}.
+	Following the idea of the Broken-and-Intact Cell (BIC) model (\citet{Sovova2017}), the internal diffusion coefficient $D_i$ is consider to be a product of the reference value of $D_i^R$ and the exponential decay function $\gamma$, as given by Equation \ref{EQ: C_sat_function}.
 
@@
 		\begin{equation}
-			{\color{black}D_i} = {\color{black}D_i^R} {\color{black} \gamma}({\color{black} c_s} (t,z)) = {\color{black}D_i^R} \exp\left( {\color{black}\Upsilon} \left( 1-\cfrac{{\color{black} c_s} (t,z) }{{\color{black}c_{s0}}} \right) \right) \label{EQ: C_sat_function}
+			D_i = D_i^R \gamma(c_s) = D_i^R \exp \left( \Upsilon \left( 1-\cfrac{ c_s }{c_{s0}} \right) \right) \label{EQ: C_sat_function}
 		\end{equation} }
 
-	where the ${\color{black}\Upsilon}$ describe the curvature of the decay function. The final form of the extraction kinetic Equation is given by Equation \ref{Model_kinetic}.
+	where the ${\color{black}\Upsilon}$ describe the curvature of the decay function. Equation \ref{Model_kinetic} describes the final form of the kinetic term
 
-	{\scriptsize
+	{\footnotesize
 		\begin{equation}
 			\label{Model_kinetic}
-				r_e = -\cfrac{{\color{black}D_i^R}(T(t,z), {\color{black}P}(t), F(t)) {\color{black} \gamma}({\color{black} c_s} (t,z)) }{{\color{black} \mu l^2} } \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}c_f(t,z)}{{\color{black}k_m}(T(t,z)){\color{black}\rho}(T(t,z),{\color{black}P}(t))}  \right)
+				r_e = -\cfrac{D_i^R \gamma }{ \mu l^2 } \left( c_s  - \cfrac{\rho_s c_f }{ k_m \rho_f }  \right)
 		\end{equation} }
@@
 Considering that the internal diffusion coefficient decay as the concentration of the solute in the solid decrease.
-As the value of the ${\color{black}c_s}$ decrease over time, the exponential term approach unity and $\lim_{ {\color{black}c_s} \rightarrow 0} {\color{black}D_i} =  {\color{black}D_i^R}$.
-${\color{black}D_i^R}$ can be interpreted as the internal diffusion coefficient at vanishing gradient.
+As the value of the $c_s$ decrease over time, the exponential term approach unity and $\lim_{ c_s \rightarrow 0} D_i =  D_i^R$.
+$D_i^R$ can be interpreted as the internal diffusion coefficient at vanishing gradient.
 
-	Alternatively, the decay function ${\color{black}\gamma}$ can be consider with respect to the Shrinking Core model presented by \citet{Goto1996}, where the particle radius change as the amount of solute in the solid phase decrease.
+	Alternatively, the decay function $\gamma$ can be consider with respect to the Shrinking Core model presented by \citet{Goto1996}, where the particle radius change as the amount of solute in the solid phase decrease.
 As the particle size decrease due to dissolution, the diffusion path increase which makes the diffusion slower and reduce the value of a diffusion coefficient.

### 2024-04-09 SFE_article_Parameter_Estimation_short - Chamomile/Short_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
09.04

@@
 		\cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
-		\cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial {\color{black}P}}{\partial z} \label{EQ: CompressibleEuler_2} \\
-		\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -{\color{black}P}\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
+		\cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \label{EQ: CompressibleEuler_2} \\
+		\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
 		\label{EQ: CompressibleEuler_3}
@@
 
-where $\rho_f$ is the density of the fluid, $A_f$ is the function which describe change of the cross-section, $v$ is the velocity, ${\color{black}P}$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
+where $\rho_f$ is the density of the fluid, $A_f$ is the function which describe change of the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
 
@@
 			\node at (5.5,1.5) {$\rho_f+\delta\rho_f$};
-			\node at (4,1.0) {${\color{black}P}$};
-			\node at (5.5,1.0) {${\color{black}P}+\delta {\color{black}P}$};
+			\node at (4,1.0) {$P$};
+			\node at (5.5,1.0) {$P+\delta P$};
 			\node at (4,0.5) {$T$};
@@
 		&\rho_f \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 \\
-		&\delta {\color{black}P} = \delta v \delta \rho_f
+		&\delta P = \delta v \delta \rho_f
 	\end{align*}
@@
 	\begin{equation} \label{EQ: Pressure_Velocity}
-		\cfrac{d v}{d \rho_f} = - \cfrac{d v}{d{\color{black}P}} \cfrac{d {\color{black}P}}{d \rho_f} = -\cfrac{1}{\rho v} \cfrac{d{\color{black}P}}{d\rho_f} = -\cfrac{v}{\rho_f}
+		\cfrac{d v}{d \rho_f} = - \cfrac{d v}{dP} \cfrac{d P}{d \rho_f} = -\cfrac{1}{\rho v} \cfrac{dP}{d\rho_f} = -\cfrac{v}{\rho_f}
 	\end{equation}
@@
 
-Suppose the flow is presumed to be isentropic, $d{\color{black}P}/d\rho_f = c^2$, so $v^2=c^2$, where $c$ is the speed of sound.
+Suppose the flow is presumed to be isentropic, $dP/d\rho_f = c^2$, so $v^2=c^2$, where $c$ is the speed of sound.
 This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow.
-If the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic, which leads to $\partial \rho_f / \partial {\color{black}P} \approx 0$.
+If the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic, which leads to $\partial \rho_f / \partial P \approx 0$.
 The small changes in pressure due to flow velocity changes do not change the density.
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_1_4_correlation.png}
-		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s]}% and temperature of 40 $[^\circ C]$}
+		\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
 		\label{fig: Fit_1_4_Di_Gamma_correlation}
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_5_8_correlation.png}
-		\caption{Results of parameter estimation for experiments at $6.67\times 10^{-5}$ [kg/s]}% and temperature of 30 $[^\circ C]$}
+		\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
 		\label{fig: Fit_5_8_Di_Gamma_correlation}
@@
 
-Laboratory experiments were conducted under various conditions to validate the model.
+Laboratory experiments were conducted by \citet{Povh2001} under various conditions to validate the model.
 The model parameters, such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data.

### 2024-04-11 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Experiments.tex
11.04

@@
 
-	The experiments were conducted using an a semi-batch extractor with diameter of 3.96 [cm] and length of 16.55 [cm].
+	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to calibrate the model based on the experimental the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers.
+The experiments were performed by \citet{Povh2001} and \citet{Rahimi2011}.	The experiments were conducted using an a semi-batch extractor with diameter of 3.96 [cm] and length of 16.55 [cm].
 Twelve experiments were performed under different operating conditions: $30-40^\circ C$, $100 - 200$ [bar], and $0.05 - 0.24$ [kg/h].

### 2024-04-11 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
11.04

@@
 
-	The comprehensive derivation of the mass balance equation for the fluid phase is detailed in Appendix \ref{CH: Gouverning equations}.
+	%The comprehensive derivation of the mass balance equation for the fluid phase is detailed in Appendix \ref{CH: Gouverning equations}. 
 	This equation accounts for the movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}), which is constrained to the axial direction due to the quasi-one-dimensional approach that considers changes in the void fraction.
-It is also assumed that the thermodynamic pressure remains constant throughout the device, as illustrated by Equation \ref{EQ: Pressure_Velocity}.
+It is also assumed that the thermodynamic pressure remains constant throughout the device.
 The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall, leading to a uniform velocity profile across any cross-section perpendicular to the axial direction.
 Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself.
-Thus, the mass balance equation encompasses convection, diffusion, and kinetic terms to represent the fluid phase behaviour accurately.
+Thus, the mass balance equation include convection, diffusion, and kinetic terms to represent the fluid phase behaviour.
 
@@
 
-	The kinetic term in this study is based on the two-film theory proposed by \citet{Reverchon1996}, and the mass transfer kinetic is given by Equation \ref{Model_kinetic_basic}.
+	%In this study, the kinetic term is based on the two-film theory proposed by \citet{Reverchon1996}, and the mass transfer kinetic is given by Equation \ref{Model_kinetic_basic}.
 This equation takes into account the overall diffusion coefficient and the concentration gradient, which acts as the driving force for the process.
@@
 The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
-Figure \ref{fig: SFE_Mechanism} illustrates the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as $c_s$ and the equilibrium concentrations at the solid-fluid interface are denoted as $c_s^*$ and $c_p^*$, respectively, for solid and fluid phases.
+Figure \ref{fig: SFE_Mechanism} shows the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as $c_s$ and the equilibrium concentrations at the solid-fluid interface are denoted as $c_s^*$ and $c_p^*$, respectively, for solid and fluid phases.
 The concentration of the solutes in the fluid phase in the center of the pore is denoted as $c_p$.
 As the solute diffuses through the pore, its concentration changes and reaches $c_{pf}$ at the opening of the pore.
-The solute then diffuses through the film around the particle and reaches bulk concentration $c_f$.
+Then the solute diffuses through the film around the particle and reaches bulk concentration $c_f$.
 The two-film theory describes the solid-fluid interface inside the pore.
-The overall mass transfer coefficient can be determined if the relationship between the solute concentration in one phase and its equilibrium concentration is known.
+The overall mass transfer coefficient can be determined from the relationship between the solute concentration in one phase and its equilibrium concentration.
 
@@
 			\centering
-			\includegraphics[trim = 45cm 0cm 60cm 20cm,clip,width=\columnwidth]{Figures/SFE_PFD.drawio.png}	
-			\caption{The extraction mechanism}
+			\includegraphics[trim = 45cm 0cm 60cm 20cm,clip,width=0.85\columnwidth]{Figures/SFE_PFD.drawio.png}	
+			\caption{The mass transfer mechanism}
 			\label{fig: SFE_Mechanism}
@@
 		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$.
-$c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate is $r_e\left(c_s - c^*_p(c_f)\right)$ or more precisely
+$c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate given by Equation \ref{Model_kinetic_basic}
 
@@
 
-		The efficiency of the process (the yield) is calculated according to Equation \ref{Model_measurment_1} as presented by \citet{Sovova1994a}.
+		The process yield is calculated according to Equation \ref{Model_measurment_1} as presented by \citet{Sovova1994a}.
 The measurement equation evaluates the solute's mass at the extraction unit's outlet and sums it up.
-The integral form of the measurement equation (\ref{Model_measurment_1}) can be transformed into the differential form (\ref{Model_measurment_2}) and augmented with the process model.
+The integral form of the measurement (Equation \ref{Model_measurment_1}) can be transformed into the differential form (Equation \ref{Model_measurment_2}) and augmented with the process model.
 
@@
 As the residence time is much shorter than the sampling time, the initial state estimate for the concentration of the solute in the fluid phase would be not reliable.
-Considering that it is assumed that the $c_{f0}=0$.
-Moreover, it is considered that the extractor is isothermal.
+Considering that it is assumed that the $c_{f0}=0$ and that the system is isothermal.
 %and described by ${\color{black}h_0}$.
-		Therefore, the initial and boundary conditions employed in the simulation are:
+		Therefore, the initial and boundary conditions are define as follow:
 
@@
 
-		As presented in Appendix \ref{CH: Gouverning equations}, all the governing can be written in the integral form using the Divergence Theorem.
+		%As presented in Appendix \ref{CH: Gouverning equations}, all the governing can be written in the integral form using the Divergence Theorem.
 The integral equation states that the change rate of the integral of any quantity over an arbitrary control volume is given by the flux through the boundary of the control volume, with being the outer surface normal through the boundary.
@@
 In other words, after the addition of all terms coming from the discretization over a grid, only the boundary terms should remain, and the artificial interior points should cancel out.
-Discretization is applied to the conservative form of the process model to ensure mass conservation.
+The discretization is applied to the conservative form of the model to ensure mass conservation.
 

### 2024-04-11 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Results_Chamomile.tex
11.04

@@
 	\label{CH: Results}
-
-	\begin{figure*}[!h]
-		\centering
-		\begin{subfigure}{0.3\textwidth}
-			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
-			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
-			\label{fig: Fit_1_4_Di_Gamma}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}{0.3\textwidth}
-			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
-			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
-			\label{fig: Fit_5_8_Di_Gamma}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}{0.3\textwidth}
-			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
-			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
-			\label{fig: Fit_9_12_Di_Gamma}
-		\end{subfigure}
-		\caption{Parameter estimation results}
-		\label{fig: Fit_Di_Gamma}
-	\end{figure*}
 
@@
 
+	\begin{figure}[!h]
+		\centering
+		\begin{subfigure}{0.48\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_Space_Linear_Dataset_1.png}
+			\caption{The linear kinetic model \\ ~}
+			\label{fig: Fit_1_linear}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.48\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_Space_Di_Dx_Dataset_1.png}
+			\caption{The reduced linear kinetic model with axial diffusion}
+			\label{fig: Fit_1_Di_Dx}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.48\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
+			\caption{The modified model}
+			\label{fig: Fit_1_Di_Gamma}
+		\end{subfigure}
+		\caption{Parameter space for experiment 1}
+		%\label{fig: Fit_Di_Gamma}
+	\end{figure}
+
 	Similarly to the previous case, the optimal value of $D_i$ exists, but a unique value for the $D_e^M$ cannot be determined.
@@
 The obtained results show good agreement with experimental data.
+
+	\begin{figure}[!h]
+		\centering
+		\begin{subfigure}{0.66\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
+			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
+			\label{fig: Fit_1_4_Di_Gamma}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.66\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
+			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
+			\label{fig: Fit_5_8_Di_Gamma}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.66\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
+			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
+			\label{fig: Fit_9_12_Di_Gamma}
+		\end{subfigure}
+		\caption{Parameter estimation results}
+		\label{fig: Fit_Di_Gamma}
+	\end{figure}
 
@@
 
+	\begin{figure}[!h]
+		\centering
+		\begin{subfigure}{0.66\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4_correlation.png}
+			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
+			\label{fig: Fit_1_4_Di_Gamma_correlation}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.66\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8_correlation.png}
+			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
+			\label{fig: Fit_5_8_Di_Gamma_correlation}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}{0.66\columnwidth}
+			\centering
+			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12_correlation.png}
+			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
+			\label{fig: Fit_9_12_Di_Gamma_correlation}
+		\end{subfigure}
+		\caption{Parameter estimation results}
+		\label{fig: Fit_Di_Gamma_correlation}
+	\end{figure}
+
 	The correlations are later used against the original dataset to show that the correlations can reproduce the results with satisfactory accuracy.
@@
 
+	%The parameter estimation results are compared to the work of \citet{Povh2001}, who fitted the Sovova model to the same dataset.
+It should be noted that the \citet{Povh2001} use as the initial solute mass ratio a value of 10\% above the total amount of extract for every experimental, while in this work, the initial conditions are the same for all the experiments as explained above.
+Contrary to this work, \citet{Povh2001} has not used any numerical solver in his work but rather a combination of analytical methods and a trial and error procedure.
+\citet{Povh2001} stated that 'the direct fitting of experimental data to the Sovova's model produced parameters that could not be accepted after a careful physical interpretation of the system'.
+The parameters found in this work seem to have a physical interpretation, and their values are in the excerpted range.
+
+	%\citet{Rahimi2011} fitted the same dataset to a model with desorption–dissolution–diffusion mechanism.
+To decrease the number of parameters to be found, \citet{Rahimi2011} applied a set of correlations.
+The remaining parameters were found using a genetic algorithm to solve the parameter estimation problem for each experiment separately.
+The results obtained by \citet{Rahimi2011} show that the desorption–dissolution–diffusion model cannot reproduce the yield data.
+The desorption–dissolution–diffusion model and the model used in this work are structurally similar, with the main difference of $\gamma$ function.
+The $\gamma$ function increases the model's flexibility and allows it to obtain a better fit.
+
+	%For every single experiment, \citet{Povh2001} and \citet{Rahimi2011} delivered a set of independent parameters.
+This work combines the parameters obtained from each experiment to get a single correlation valid for the whole range of investigated operating conditions.
+
+	The parameter estimation results are compared against those presented by \citet{Povh2001}, who applied the Sovova model to the same dataset.
+It is important to note that \citet{Povh2001} use as the initial solute mass ratio a value of 10\% above the total amount of extract for every experimental, while in this work, the initial conditions are the same for all the experiments.
+In contrast to this work, \citet{Povh2001} did not utilize numerical solvers but used a mix of analytical methodologies and trial-and-error procedures.
+\citet{Povh2001} remarked that 'the direct fitting of experimental data to the Sovova's model produced parameters that could not be accepted after a careful physical interpretation of the system'.
+The parameters identified in this study seem to have a physical interpretation and are within the expected range.
+
+	\citet{Rahimi2011} analysed the same dataset using the desorption–dissolution–diffusion model.
+To decrease the number of unknown parameters, \citet{Rahimi2011} applied a set of empirical correlations.
+The remaining parameters were determined through the use of a genetic algorithm to solve the parameter estimation problem for each experiment individually.
+Results obtained by \citet{Rahimi2011} shows that the desorption–dissolution–diffusion model fails to reproduce the yield data.
+The main difference between the model employed by \citet{Rahimi2011} and the one in this study is the $\gamma$ function.
+The $\gamma$ function increases the model's flexibility by adjusting $D_i$ and allows it to obtain a better fit.
+
+	\citet{Povh2001} and \citet{Rahimi2011} delivered a set of independent parameters for every single experiment.
+This work combines the parameters obtained from each experiment to get a single correlation valid for the whole range of investigated operating conditions.
+
 \end{document}

### 2024-04-11 SFE_article_Parameter_Estimation_short - Chamomile/Short_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
11.04

@@
 The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
-The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
-Model parameters, including the partition factor, internal diffusion coefficient, axial diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data, with the assumption of normally distributed errors.
+The physical properties of the solvent are estimated based on the Peng-Robinson equation of state.
+Model parameters, including the partition factor, internal diffusion coefficient, axial diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data assuming normally distributed errors.
 A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s.
@@
 \subsection{Governing equations} \label{CH:Governing_equations_chapter}
-	The governing equations based on the work of \citet{Anderson1995} for quasi-one-dimensional compressible flow in Cartesian coordinates are presented in Appendix \ref{CH: Gouverning equations}.
+	Following the work of \citet{Anderson1995}, the governing equations for quasi-one-dimensional were derived.
 Quasi-one-dimensional flow refers to a fluid flow scenario assuming that flow properties are uniformly distributed across any given cross-section.
@@
 
-	The set of quasi-one-dimensional compressible Navier-Stokes equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}.
-The formulation of these equations is elaborated upon in Appendix \ref{CH: Gouverning equations}, providing a mathematical foundation for analyzing flow dynamics under the assumed conditions.
+	As discussed by \citet{Anderson2023}, all flows are compressible but some of them can be treated as incompressible when the Mach number is smaller than 0.3.
+This assumption leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow.
+The restraint allows for the removal of acoustic waves, and allows for large perturbations in density and/or temperature.
+In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.
+
+	%The governing equations based on the work of \citet{Anderson1995} for quasi-one-dimensional compressible flow in Cartesian coordinates are presented in Appendix \ref{CH: Gouverning equations}.
+
+	The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}.
+%The formulation of these equations is elaborated upon in Appendix \ref{CH: Gouverning equations}, providing a mathematical foundation for analyzing flow dynamics under the assumed conditions.
 
@@
 
+\begin{comment}
 Based on governing equations, the small discontinuity (defined as $\delta$) in flow properties, shown in Figure \ref{fig: Discontinuity_slow_flow}, can be analysed.
@@
 
+\end{comment}
+
 \subsection{Extraction model} \label{CH: Extraction_model}
@@
 \subfile{Sections/Parameter_estimation}
-
-\begin{figure*}[!b]
-	\centering
-	\begin{subfigure}{0.3\textwidth}
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Parameter_Space_Linear_Dataset_1.png}
-		\caption{Parameter space: the linear kinetic model}
-		\label{fig: Fit_1_linear}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}{0.3\textwidth}
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Parameter_Space_Di_Dx_Dataset_1.png}
-		\caption{Parameter space: the reduced linear kinetic model with axial diffusion}
-		\label{fig: Fit_1_Di_Dx}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}{0.3\textwidth}
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
-		\caption{Parameter space: the modified model}
-		\label{fig: Fit_1_Di_Gamma}
-	\end{subfigure}
-	\caption{Parameter estimation results for experiment 1}
-	%\label{fig: Fit_Di_Gamma}
-\end{figure*}
 
@@
 \section{Conclusions} \label{CH: Conclusion}
-
-\begin{figure*}[!h]
-	\centering
-	\begin{subfigure}{0.3\textwidth}
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_1_4_correlation.png}
-		\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
-		\label{fig: Fit_1_4_Di_Gamma_correlation}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}{0.3\textwidth}
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_5_8_correlation.png}
-		\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
-		\label{fig: Fit_5_8_Di_Gamma_correlation}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}{0.3\textwidth}
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\textwidth]{/Results_estimation/Fit_Di_Gamma_9_12_correlation.png}
-		\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
-		\label{fig: Fit_9_12_Di_Gamma_correlation}
-	\end{subfigure}
-	\caption{Parameter estimation results}
-	\label{fig: Fit_Di_Gamma_correlation}
-\end{figure*}
 
@@
 %% Loading bibliography style file
-%\clearpage
+\clearpage
 %\bibliographystyle{model1-num-names}
@@
 
-\subsection{Governing equations}
-\subfile{Sections/Gouverning_equation_derivation}
+%\subsection{Governing equations}
+%\subfile{Sections/Gouverning_equation_derivation}
 
@@
 
-\subsection{Maximum likelihood} \label{CH: ML}
-\subfile{Sections/Likelihood}
+%\subsection{Maximum likelihood} \label{CH: ML}
+%\subfile{Sections/Likelihood}
 

### 2024-04-12 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Results_Chamomile.tex
12.04

@@
 The initial value problem was solved multiple times with varying initial guesses to identify the global minimum.
-Within the model context characterized by linear kinetics, two parameters remain to be determined: the partition coefficient $k_m$ and the internal diffusion coefficient $D_i$.
+In case of the linear, two parameters remain to be determined: the partition coefficient $k_m$ and the internal diffusion coefficient $D_i$.
 
@@
 The model reduction can be introduced by considering the limit of $k_m$ in the extraction kinetic term:
-
-	{\footnotesize
-		\begin{equation*}
-			\begin{split}
-				&\lim_{k_m \rightarrow \infty} \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}(T(t,z)){\color{black}\rho}(T(t,z),{\color{black}P}(t))}  c_f \right)  = \\
-				&= \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{\rho_s}{\infty \cdot \rho(T(t,z),P(t))}  {c_f}(t,z) \right) = \left(c_s(t,z) - 0 \right)
-			\end{split}
-	\end{equation*} }
-
-	The extraction model can be adapted to incorporate adjustments for the reduced kinetic term and axial diffusion.
-In this revised setup, two parameters remain undetermined: the internal diffusion coefficient $D_i$ and the axial diffusion coefficient $D_e^M$.
-Figure \ref{fig: Fit_1_Di_Dx} illustrates the parameter space and associated cost function values.
 
@@
 
+	{\footnotesize
+		\begin{equation*}
+			\begin{split}
+				&\lim_{k_m \rightarrow \infty} \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}(T(t,z)){\color{black}\rho}(T(t,z),{\color{black}P}(t))}  c_f \right)  = \\
+				&= \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{\rho_s}{\infty \cdot \rho(T(t,z),P(t))}  {c_f}(t,z) \right) = \left(c_s(t,z) - 0 \right)
+			\end{split}
+	\end{equation*} }
+
+	The extraction model can be adapted to incorporate adjustments for the reduced kinetic term and axial diffusion.
+In this revised setup, two parameters remain undetermined: the internal diffusion coefficient $D_i$ and the axial diffusion coefficient $D_e^M$.
+Figure \ref{fig: Fit_1_Di_Dx} illustrates the parameter space of the modified model and associated cost function values.
+
 	Similarly to the previous case, the optimal value of $D_i$ exists, but a unique value for the $D_e^M$ cannot be determined.
@@
 Figure \ref{fig: Fit_1_Di_Gamma} shows the parameter space and the corresponding cost function values.
-
-	The parameter space for the revised model exhibits a distinct minimum value corresponding to the solution of the parameter estimation problem for experiment 1.
-The red circle highlights the minimum value of the cost function found by the optimizer.
-The remaining experiments are fitted to the modified extraction model, and results are presented in Figure \ref{fig: Fit_Di_Gamma}.
-The obtained results show good agreement with experimental data.
 
@@
 		\end{subfigure}
-		\caption{Parameter estimation results}
+		\caption{Parameter estimation results obtained from the modified model}
 		\label{fig: Fit_Di_Gamma}
 	\end{figure}
+
+	The parameter space for the modified model exhibits a distinct minimum value corresponding to the solution of the parameter estimation problem for experiment 1.
+The red circle highlights the minimum value of the cost function found by the optimizer.
+The remaining experiments are fitted to the modified extraction model, and results, presented in Figure \ref{fig: Fit_Di_Gamma}, show good agreement with experimental data.
 
@@
 		\end{subfigure}
-		\caption{Parameter estimation results}
+		\caption{Empirical correlations between parameters}
 		%\label{fig: Correlations_surface}
@@
 			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4_correlation.png}
-			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
+			\caption{Simulation results obtained at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
 			\label{fig: Fit_1_4_Di_Gamma_correlation}
@@
 			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8_correlation.png}
-			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
+			\caption{Simulation results obtained at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
 			\label{fig: Fit_5_8_Di_Gamma_correlation}
@@
 			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12_correlation.png}
-			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
+			\caption{Simulation results obtained at $3.33\times 10^{-5}$ [kg/s]}
 			\label{fig: Fit_9_12_Di_Gamma_correlation}
 		\end{subfigure}
-		\caption{Parameter estimation results}
+		\caption{Simulation results from the modified model and correlations}
 		\label{fig: Fit_Di_Gamma_correlation}

### 2024-04-15 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Experiments.tex
12.04
15.04

@@
 	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to calibrate the model based on the experimental the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers.
-The experiments were performed by \citet{Povh2001} and \citet{Rahimi2011}.	The experiments were conducted using an a semi-batch extractor with diameter of 3.96 [cm] and length of 16.55 [cm].
+The experiments were performed by \citet{Povh2001} and \citet{Rahimi2011}.
+The experiments were conducted using a semi-batch extractor with a diameter of 3.96 [cm] and a length of 16.55 [cm].
 Twelve experiments were performed under different operating conditions: $30-40^\circ C$, $100 - 200$ [bar], and $0.05 - 0.24$ [kg/h].
@@
 The total porosity of the bed, including the particles, was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$.
+It is assumed that the total amount of the extract is equal 3 [g], defined as to the biggest obtained yield after rounding up.
 

### 2024-04-15 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
15.04

@@
 
-		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$.
-$c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate given by Equation \ref{Model_kinetic_basic}
+		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$.Concentration $c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate given by Equation \ref{Model_kinetic_basic}
 

### 2024-04-22 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
22.04

@@
 
-	To simplify the system's dynamics, it is assumed that $F$ is a control variable and affects the whole system instantaneously, which allows finding the velocity profile that satisfies mass continuity based on $F$, $\phi$, and $\rho_f$.
+	To simplify the system's dynamics, it is assumed that $F$ is a control variable and affects the whole system instantaneously (due to $\nabla \cdot u = 0$), which allows finding the velocity profile that satisfies mass continuity based on $F$, $\phi$, and $\rho_f$.
 
@@
 
-	$c_f$ represents the concentration of solute in the fluid phase, $r_e$ is a mass transfer kinetic term, and $D^M_e$ is the axial diffusion coefficient.
+	$c_f$ represents the solute's concentration in the fluid phase, $r_e$ is a mass transfer kinetic term, and $D^M_e$ is the axial diffusion coefficient.
 
@@
 The length of the fixed bed is divided into $N_z$ equally distributed points in $z$-direction.
-The state-space model after the discretization is represented by $x$.
+The state-space model after the discretization is denoted as $x$ and defines as follow:
 

### 2024-04-22 SFE_article_Sensitivity_Analysis_short - Chamomile/Article_Sensitivity_Analsysis_short-Chamomile.tex
22.04

--- 2024-03-19 SFE_article_Sensitivity_Analysis - Chamomile/Article_Sensitivity_Analsysis-Chamomile.tex
@@
 
-\subsection{Supercritical fluids} \label{CH: Thermodynamic}
+%\subsection{Supercritical fluids} \label{CH: Thermodynamic}
 %\subfile{Sections/Thermo}
-\subfile{Sections/Thermo_imp}
+%\subfile{Sections/Thermo_imp}
 
@@
 
+%\subsection{Governing equations} \label{CH:Governing_equations_chapter}
+%\subfile{Sections/Gouverning_equation}
+
 \subsection{Governing equations} \label{CH:Governing_equations_chapter}
-\subfile{Sections/Gouverning_equation}
+Following the work of \citet{Anderson1995}, the governing equations for quasi-one-dimensional were derived.
+Quasi-one-dimensional flow refers to a fluid flow scenario assuming that flow properties are uniformly distributed across any given cross-section.
+This simplification is typically applied in situations where the flow channel's cross-sectional area changes, such as through irregular shapes or partial fillings of an extractor.
+According to this assumption, velocity and other flow properties change solely in the flow direction.
+
+As discussed by \citet{Anderson2023}, all flows are compressible but some of them can be treated as incompressible when the Mach number is smaller than 0.3.
+This assumption leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow.
+The restraint allows for the removal of acoustic waves, and allows for large perturbations in density and/or temperature.
+In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.
+
+%The governing equations based on the work of \citet{Anderson1995} for quasi-one-dimensional compressible flow in Cartesian coordinates are presented in Appendix \ref{CH: Gouverning equations}.
+
+The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}.
+%The formulation of these equations is elaborated upon in Appendix \ref{CH: Gouverning equations}, providing a mathematical foundation for analyzing flow dynamics under the assumed conditions.
+
+{\footnotesize
+	\begin{align}
+		\label{EQ: CompressibleEuler_1}
+		\cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
+		\cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \label{EQ: CompressibleEuler_2} \\
+		\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
+		\label{EQ: CompressibleEuler_3}
+	\end{align}  
+}
+
+where $\rho_f$ is the density of the fluid, $A_f$ is the function which describe change of the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
+
+\begin{comment}
+	Based on governing equations, the small discontinuity (defined as $\delta$) in flow properties, shown in Figure \ref{fig: Discontinuity_slow_flow}, can be analysed.
+The analysis follows the work of \citet{Schreier1982}.
+
+	\begin{figure}[!h]
+		\centering
+		\resizebox{0.95\columnwidth}{!}{%
+			\begin{tikzpicture}[]
+				\draw (0,2) -- (9,2);	% Top line
+				\draw (0,0) -- (9,0); 	% Bottom line
+				\draw (4.5,0) -- (4.5,2); 	% Bottom line
+				\node at (4,1.5) {$\rho_f$};
+				\node at (5.5,1.5) {$\rho_f+\delta\rho_f$};
+				\node at (4,1.0) {$P$};
+				\node at (5.5,1.0) {$P+\delta P$};
+				\node at (4,0.5) {$T$};
+				\node at (5.5,0.5) {$T+\delta T$};
+				\node at (1,1.0) {$v \rightarrow$};
+				\node at (8,1.0) {$v + \delta v \rightarrow$};
+		\end{tikzpicture} }
+		\caption{Small discontinuity in one-dimensional flow}
+		\label{fig: Discontinuity_slow_flow}
+	\end{figure}
+
+	The discontinuity is presumed to be at rest relative, and the balance equations become
+
+	{\footnotesize
+		\begin{align*}
+			&\rho_f \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 \\
+			&\delta P = \delta v \delta \rho_f
+		\end{align*}
+	}
+
+	These relations are equally valid if both regions are separated by a region of finite width rather than a discontinuity.
+
+	{\footnotesize
+		\begin{equation*}
+			\lim_{\rho_f v \rightarrow 0} \rho_f \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 / \delta \rho_f \rightarrow \cfrac{d v}{d \rho_f} = - \cfrac{v}{\rho_f}
+		\end{equation*}
+	}
+
+	By combining the momentum equation with the above equation, we get
+
+	{\footnotesize
+		\begin{equation} \label{EQ: Pressure_Velocity}
+			\cfrac{d v}{d \rho_f} = - \cfrac{d v}{dP} \cfrac{d P}{d \rho_f} = -\cfrac{1}{\rho v} \cfrac{dP}{d\rho_f} = -\cfrac{v}{\rho_f}
+		\end{equation}
+	}
+
+	Suppose the flow is presumed to be isentropic, $dP/d\rho_f = c^2$, so $v^2=c^2$, where $c$ is the speed of sound.
+This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow.
+If the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic, which leads to $\partial \rho_f / \partial P \approx 0$.
+The small changes in pressure due to flow velocity changes do not change the density.
+
+	The low Mach number condition leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow.
+The restraint allows for the removal of acoustic waves, but also allows for large perturbations in density and/or temperature.
+The assumption is that the flow remains within a Mach number limit (usually less than 0.3) for any solution using such a constraint to be valid.
+In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.
+
+\end{comment}
 
@@
 
-%\clearpage \appendix \label{appendix}
-%\section{Appendix} 
-%\subsection{Thermodynamic}
-%\subfile{Sections/Qubic_EOS}
+\clearpage \appendix \label{appendix}
+\section{Appendix}
+
+\subsection{Thermodynamic}
+\subfile{Sections/Qubic_EOS} \label{CH: EOS}
 
@@
 
-%\subsection{Cardano's Formula} \label{CH: Cardano}
-%\subfile{Sections/Cardano}
+\subsection{Cardano's Formula} \label{CH: Cardano}
+\subfile{Sections/Cardano}
 

### 2024-04-22 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Model.tex
22.04

--- 2024-04-22 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
@@
 
-		\iffalse	
 		\subsubsection{Heat balance} \label{CH: heat_balance}
+
+		\begin{comment}
 
@@
 We consider no heat loss through the wall, and there is no heat generation in the system.
-Therefore, the temperature of the extractor can be changed only by manipulating the temperature of the inlet stream %$T_{In}(t)$.
+Therefore, the temperature of the extractor can be changed only by manipulating the temperature of the inlet stream %$T_{In}$.
 
@@
 It is considered that there is no heat loss through the walls, and there is no heat generation in the system.
-The temperature of the extractor can be changed only by manipulating the temperature of the inlet stream ${\color{black}T_{Inlet}}(t)$.
+The temperature of the extractor can be changed only by manipulating the temperature of the inlet stream ${\color{black}T_{Inlet}}$.
 			}
@@
 					\begin{split}
-						\cfrac{\partial T(t,z)}{\partial t} &= 
-						\underbrace{ -\cfrac{F {\color{black}C_p}(T(t,z),{\color{black}P}(t))}{{\color{black}A} 	[(1-{\color{black}\epsilon})\rho_f {\color{black}C_p} (T(t,z),{\color{black}P}(t)) + {\color{black} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial T(t,z)}{\partial z}  }_{\text{Convection}} + \\
-						& + \underbrace{ {\color{black}D^T_e}(T(t,z),{\color{black}P}(t)) \cfrac{\partial^2 T(t,z)}{\partial {\color{black}z^2}} }_{\text{Diffusion}}
+						\cfrac{\partial T}{\partial t} &= 
+						\underbrace{ -\cfrac{F {\color{black}C_p}}{{\color{black}A} 	[(1-{\color{black}\epsilon})\rho_f {\color{black}C_p}  + {\color{black} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial T}{\partial z}  }_{\text{Convection}} + \\
+						& + \underbrace{ {\color{black}D^T_e} \cfrac{\partial^2 T}{\partial {\color{black}z^2}} }_{\text{Diffusion}}
 					\end{split}
@@
 
-		where $ {\color{black}D^M_e}(T(t,z),{\color{black}P}(t),F)$ is the axial mass diffusion coefficient, ${\color{black}C_p}(T(t,z),{\color{black}P}(t))$ is the fluid's specific heat, ${\color{black}C_{ps}}$ is the specific heat of the solid phase, ${\color{black}D^T_e}(T(t,z),{\color{black}P}(t),F)$ is the axial heat diffusion coefficient.
+		where $ {\color{black}D^M_e}(T,P,F)$ is the axial mass diffusion coefficient, ${\color{black}C_p}$ is the fluid's specific heat, ${\color{black}C_{ps}}$ is the specific heat of the solid phase, ${\color{black}D^T_e}(T,P,F)$ is the axial heat diffusion coefficient.
 
@@
 
-			The heat governing equation describe the evolution of the energy in the system and it is given by \ref{EQ: Heat_internal}.
-The derivation of the heat equation can be found in Appendix \ref{CH: Gouverning equations}.
+			The heat governing equation describe the evolution of the internal energy in the system and it is given by Equation \ref{EQ: Heat_internal}.
+The derivation of the heat equation can be found in the work of \citet{Anderson1995}.
 
 			{\footnotesize
-			\begin{align} \label{EQ: Heat_internal}
-				&\cfrac{\partial \left( \rho_f e(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e(t,z) \right)}{\partial z} \nonumber \\
-				&= -{\color{black}P}(t)\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T(t,z)}{\partial z} \right) 
-			\end{align}
+			\begin{equation} \label{EQ: Heat_internal}
+				\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e \right)}{\partial z} = -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T}{\partial z} \right)
+			\end{equation}
 			}
 
-			The departure function is a mathematical function that characterizes the deviation of a thermodynamic property (enthalpy, entropy, and internal energy) of a real substance from that of an ideal gas at the same temperature and pressure.
+			Following \citet{Elliott2011} or \citet{Gmehling2019}, a real gas internal energy definition can be obtained from the departure functions, defined through Equation \ref{EQ: internal_energy_def}.	The departure function is a mathematical function that characterizes the deviation of a thermodynamic property (enthalpy, entropy, and internal energy) of a real substance from that of an ideal gas at the same temperature and pressure.
 The departure function is typically defined as the difference between the value of a thermodynamic property for a real fluid and the corresponding value for an ideal gas at the same temperature and pressure.
 They are typically computed by integrating a function that depends on the equation of state and its derivatives.
-Following \citet{Elliott2011} or \citet{Gmehling2019}, a real gas internal energy definition can be obtained from the departure functions, defined through Equation \ref{EQ: internal_energy_def}.
-More information on the departure functions can be found in Appendix \ref{CH:Enthalpy}.
 
@@
 				\begin{equation}
-					de(t,z)=C_vdT-\left[{\color{black}P}(t)-T(t,z)\left(\cfrac{\partial {\color{black}P}(t)}{\partial T(t,z)}\right)_{{\color{black}v_m}\left(T(t,z), {\color{black}P}(t)\right)}\right]d{\color{black}v_m}\left(T(t,z), {\color{black}P}(t)\right)
+					de=C_vdT-\left[P-T\left(\cfrac{\partial P}{\partial T}\right)_{{\color{black}v_m}}\right]d{\color{black}v_m}
 					\label{EQ: internal_energy_def}
@@
 
-			where $e^{id}(t,z)$ is the internal energy of perfect gas.
+			where $e^{id}$ is the internal energy of perfect gas.
 
-			Suppose a gas is considered to be perfectly caloric ($e(t,z)={\color{black}C_v} T(t,z)$), then the energy equation can be written explicitly in the form of temperature.
+			Suppose a gas is considered to be perfectly caloric ($e={\color{black}C_v} T$), then the energy equation can be written explicitly in the form of temperature.
 The perfectly caloric gas can be seen as the special case of a real gas, where the second term of Equation \ref{EQ: internal_energy_def} goes to zero and the heat capacity ${\color{black}C_v}$ is constant.
@@
 				\begin{equation}
-					\begin{aligned}
-					&\cfrac{e(t,z)-e^{id}(t,z)}{RT(t,z)} = \\
-					& - \cfrac{{\color{black}A}\left(T(t,z), {\color{black}P}(t)\right)}{{\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)\sqrt{8}} \cfrac{{\color{black}\kappa} \sqrt{\color{black}T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)} \right]
+					\cfrac{e-e^{id}}{RT} = - \cfrac{{\color{black}A}}{{\color{black}B}\sqrt{8}} \cfrac{{\color{black}\kappa} \sqrt{\color{black}T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{{\color{black}Z}+\left( 1+\sqrt{2} \right){\color{black}B}}{{\color{black}Z}+\left( 1-\sqrt{2} \right){\color{black}B}} \right]
 					\label{EQ: internal_energy_PR}
-				\end{aligned}
 			\end{equation}
@@
 			\begin{equation}
-				e(t,z)=e(T(t,z),{\color{black}P}(t),\rho_f)=e( T(t,z),{\color{black}P}(t), \rho_f ) 
+				e=e(T,P,\rho_f)=e( T,P, \rho_f ) 
 			\end{equation}
@@
 
-			If the value of internal energy $e(t,z)$ is known from the time evolution of the energy Equation \ref{EQ: CompressibleEuler_3}, and pressure is known from measurement, then the temperature can be reconstructed.
+			If the value of internal energy $e$ is known from the time evolution of the energy Equation \ref{EQ: CompressibleEuler_3}, and pressure is known from measurement, then the temperature can be reconstructed.
 A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution (Equation \ref{EQ: Heat_internal}) and the output from Equation \ref{EQ: internal_energy_PR}.
@@
 
-			Another way to express the energy equation is to introduce enthalpy ${\color{black}h}(t,z) = e(t,z) + {\color{black}P}(t) / \rho_f$.
-By introducing the definition of enthalpy, the energy equation becomes
+		\end{comment}
+
+			The heat balance equation describe the evolution of the internal energy in the system and it is given by Equation \ref{EQ:Enthalpy_equation}
 
 			{\footnotesize
-				\begin{align} \label{EQ:Enthalpy_equation}
-					\cfrac{\partial \left(\rho_f {\color{black}h}(t,z) A_f\right)}{\partial t} &= - \cfrac{\partial \left( \rho_f {\color{black}h}(t,z) A_f v \right)}{\partial z}  \nonumber \\
-					& + \cfrac{\partial \left({\color{black}P}(t) A_f\right)}{\partial t} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T(t,z)}{\partial z} \right)
-				\end{align}
+				\begin{equation} \label{EQ:Enthalpy_equation}
+					\cfrac{\partial \left(\rho_f {\color{black}h} A_f\right)}{\partial t} = - \cfrac{\partial \left( \rho_f {\color{black}h} A_f v \right)}{\partial z} + \cfrac{\partial \left(P A_f\right)}{\partial t} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
+				\end{equation}
 			}
 
-			The main advantage of this formulation is the presence of term $\partial {\color{black}P}(t) / \partial t $, which allows it to directly affect the system through the change of thermodynamic pressure (which is a control variable).
-The enthalpy is related to the pressure and temperature through the following equation:
+			The main advantage of this formulation is the presence of term $\partial P / \partial t $, which directly affects the system through the change of thermodynamic pressure (which is a control variable).
+%The enthalpy is related to the pressure and temperature through the following equation:
+
+			If the value of enthalpy $h$ is known from the time evolution of the energy equation, and pressure $P$ is known from measurement, then the temperature $T$ can be reconstructed based on the departure function.
+The departure function is a mathematical function that characterizes the deviation of a thermodynamic property (enthalpy, entropy, and internal energy) of a real substance from that of an ideal gas at the same temperature and pressure.
+The departure function is defined as the difference between the value of a thermodynamic property for a real fluid and the corresponding value for an ideal gas at the same temperature and pressure.
+They are computed by integrating a function that depends on the equation of state and its derivatives.
+As presented by \citet{Gmehling2019}, for the Peng-Robinson equation of state, the enthalpy can be defined by Equation \ref{EQ:Enthalpy_PR}.
 
@@
 				\begin{equation}
-					{\color{black}h}(t,z)={\color{black}h}(T(t,z),{\color{black}P}(t),\rho_f)={\color{black}h}( T(t,z),{\color{black}P}(t), \rho_f ) 
+					{\color{black}h}-{\color{black}h}^{id}={\color{black}R}T \left[{\color{black}T_r}({\color{black}Z}-1) -2.078(1+{\color{black}\kappa} ){\sqrt { {\color{black}\alpha}\left(T\right) } } \ln \left(\cfrac{{\color{black}Z}+\left( 1+\sqrt{2} \right){\color{black}B}}{{\color{black}Z}+\left( 1-\sqrt{2} \right){\color{black}B}}\right)\right]
+					\label{EQ:Enthalpy_PR}
+			\end{equation}				
+			}
+
+			Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which is assumed to be $T_{ref}=298.15$[K] and $P_{ref}=1.01325$[bar].
+
+			A root-finder can be used to find a value of temperature, which minimizes the difference between the value of enthalpy coming from the heat balance and the departure functions.
+The root fining procedure to repeated at every time step to find a local temperature along spatial direction $z$.
+
+			{\footnotesize
+				\begin{equation}
+					\underbrace{h\left(t,x\right)}_{\text{Heat balance}}=\underbrace{h\left(T,P,\rho_f\left(T,P\right)\right)}_{\text{Departure function}}
 					\label{EQ:Enthalpy_root}
@@
 
-			If the value of enthalpy is known from the time evolution and pressure can be measured, then the Equation \ref{EQ:Enthalpy_root} can be solved for the temperature to recover the temperature profile.
-For the Peng-Robinson EoS, the enthalpy can be defined by Equation \ref{EQ:Enthalpy_PR}.
-More details can be found in Appendix \ref{CH:Enthalpy} or given by \citet{Gmehling2019}.
-
-			{\scriptsize
-				\begin{equation}
-					\begin{split}
-					{\color{black}h}(t,z)-{\color{black}h}(t,z)^{id}={\color{black}R}T(t,z) \left[{\color{black}T_r}({\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)-1) \right. \\
-					\left.
--2.078(1+{\color{black}\kappa} ){\sqrt { {\color{black}\alpha}\left(T(t,z)\right) } } \ln \left(\cfrac{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)}\right)\right]
-					\label{EQ:Enthalpy_PR}
-				\end{split}
-			\end{equation}				
-			}
-
-			The Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which in this case is assumed to be ${\color{black}T_{ref}}=298.15~[K]$ and ${\color{black}P_{ref}}=1.01325~[bar]$.
-
-			As discussed by \citet{Gmehling2019}, the influence of the intermolecular forces on the enthalpy is needs to taken into account in high pressures systems.
+			%As discussed by \citet{Gmehling2019}, the influence of the intermolecular forces on the enthalpy is needs to taken into account in high pressures systems.
 In most cases, these forces are attractive, so additional energy is necessary to move the molecules away from each other, that is, to lower the density.
@@
 		The pressure term in the energy equation, given by Equation \ref{EQ:Enthalpy_equation}, describes the change of the thermodynamic pressure with respect to time.
-As explained in Chapters \ref{CH:Governing_equations_chapter}, at Low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound.
-Under such conditions, the term $\partial {\color{black}P}/\partial t$ can be approximated by an ordinary differential equation, which describes the instantaneous change of pressure in the system.
-The pressure (P) in the system is considered a state variable, while the pressure in the new time-step ($P_{in}$) is considered a control variable.
+As discussed above, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound.
+Under such conditions, the term $\partial P/\partial t$ can be approximated by an ordinary differential equation, which describes the instantaneous change of pressure in the system.
+The pressure ($P$) in the system is considered a state variable, while the pressure in the new time-step ($P_{in}$) is considered a control variable.
 
@@
 			\begin{equation}
-				\frac{\partial {\color{black}P}(t)}{\partial t} \approx \frac{{\color{black}P}(t) - {\color{black}P_{in}}(t) }{\Delta t}
+				\frac{\partial P}{\partial t} \approx \frac{P - P_{in} }{\Delta t}
 		\end{equation}}
@@
 In a real system, the dynamics of pressure change would depend on a pump used in an extraction system, as well as a back-pressure regulator used to control an outlet valve.
-
-  		\fi
 
@@
 				\label{Model_measurment_1}
-%				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
+%				y \left[ kg \right] &= \int_{t_0}^{t_f} Q \left[ \cfrac{m^3}{s} \right] c_f \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
 				y &= \int_{t_0}^{t_f} \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} dt \\
-%				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
+%				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q \left[ \cfrac{m^3}{s} \right] c_f \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
 				\cfrac{dy}{dt} &= \qquad \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} 
@@
 As the residence time is much shorter than the sampling time, the initial state estimate for the concentration of the solute in the fluid phase would be not reliable.
-Considering that it is assumed that the $c_{f0}=0$ and that the system is isothermal.
-%and described by ${\color{black}h_0}$.
-		Therefore, the initial and boundary conditions are define as follow:
+Considering that it is assumed that the $c_{f0}=0$ and that the system is isothermal (described by ${\color{black}h_0}$).
+		The initial and boundary conditions are define as follow:
 
@@
 				\begin{align*}
-					&c_f(t = 0, z) = 0 && c_s(t = 0, z) = c_{s0} && {c_f}(t, z=0) = 0 \\
-					&\frac{\partial c_f(t,z=L)}{\partial x} = 0 && c_s(t, z=\{0,L\}) = 0 && y(0) = 0
+					&c_f(t = 0, z) = 0 && c_s(t = 0, z) = c_{s0} && h(t = 0, z) = h_0 \\
+					&\frac{\partial c_f(t,z=L)}{\partial x} = 0 && c_f(t, z=0) = 0 && c_s(t, z=\{0,L\}) = 0 \\
+					&\frac{\partial h(t,z=L)}{\partial x} = 0 && P(t, z=0) = 0  && y(0) = 0
 			\end{align*} }
@@
 
-		\begin{comment}
 		{\footnotesize
 			\begin{align*} \label{discretization}
-				\dot{{\color{black}x}}(t) &= \cfrac{d x}{d t} = 
+				\dot{{\color{black}x}} &= \cfrac{d x}{d t} = 
 				\begin{bmatrix}
-					\cfrac{d {\color{black}c_{f,1}}(t)}{d t} 	  \\
+					\cfrac{d {\color{black}c_{f,1}}}{d t} 	  \\
 					\vdots					  \\
-					\cfrac{d {\color{black}c_{f,N_z}}(t)}{d t} \\
+					\cfrac{d {\color{black}c_{f,N_z}}}{d t} \\
 					\\ \hline \\
-					\cfrac{d {\color{black}c_{s,1}}(t)}{d t} 	  \\
+					\cfrac{d {\color{black}c_{s,1}}}{d t} 	  \\
 					\vdots					  \\
-					\cfrac{d {\color{black}c_{s,N_z}}(t)}{d t} \\
+					\cfrac{d {\color{black}c_{s,N_z}}}{d t} \\
 					\\ \hline \\
-					\cfrac{d {\color{black}h_1}(t)}{d t} 	  \\
+					\cfrac{d {\color{black}h_1}}{d t} 	  \\
 					\vdots 					  \\
-					\cfrac{d {\color{black}h_{N_z}}(t)}{d t} \\
+					\cfrac{d {\color{black}h_{N_z}}}{d t} \\
 					\\ \hline \\
-					\cfrac{d {\color{black}P}(t)}{d t} \\
+					\cfrac{d P}{d t} \\
 					\\ \hline \\
-					\cfrac{d {\color{black}y}(t)}{d t}
+					\cfrac{d {\color{black}y}}{d t}
 				\end{bmatrix}
@@
 				\underbrace{\begin{bmatrix}
-						{\color{black}G_1} \left( c_f,c_s,{\color{black}h}(t); \Theta \right)\\ 
+						{\color{black}G_1} \left( c_f,c_s,{\color{black}h}; \Theta \right)\\ 
 						\vdots\\ 
-						{\color{black}G_{N_z}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right)\\ 
+						{\color{black}G_{N_z}} \left( c_f,c_s,{\color{black}h}; \Theta \right)\\ 
 						\\ \hline \\ \\
-						{\color{black}G_{N_z+1}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right)\\ 
+						{\color{black}G_{N_z+1}} \left( c_f,c_s,{\color{black}h}; \Theta \right)\\ 
 						\vdots\\
-						{\color{black}G_{2N_z}} \left( {\color{black}c}(t),c_s,{\color{black}h}(t); \Theta \right)\\ 
+						{\color{black}G_{2N_z}} \left( {\color{black}c},c_s,{\color{black}h}; \Theta \right)\\ 
 						\\ \\ \hline \\ 
-						{\color{black}G_{2N_z+1}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) \\
+						{\color{black}G_{2N_z+1}} \left( c_f,c_s,{\color{black}h}; \Theta \right) \\
 						\vdots\\
-						{\color{black}G_{3N_z}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) \\ 
+						{\color{black}G_{3N_z}} \left( c_f,c_s,{\color{black}h}; \Theta \right) \\ 
 						\\ \\ \hline \\
-						{\color{black}G_{3N_z+1}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) \\
+						{\color{black}G_{3N_z+1}} \left( c_f,c_s,{\color{black}h}; \Theta \right) \\
 						\\ \\ \hline \\
-						{\color{black}G_{3N_z+2}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) 
+						{\color{black}G_{3N_z+2}} \left( c_f,c_s,{\color{black}h}; \Theta \right) 
 				\end{bmatrix}}_{{\color{black}G} \left( x; \Theta \right)} 
 		\end{align*} }
-	\end{comment}
 
-		{\footnotesize
-			\begin{align*} \label{discretization}
-				\dot{x} &= \cfrac{d x}{d t} = 
-				\begin{bmatrix}
-					\cfrac{d c_{f,1}}{d t} 	  \\
-					\vdots		\\	
-					\cfrac{d c_{f,N_z}}{d t} \\
-					\\ \hline  	\\
-					\cfrac{d c_{s,1}}{d t} 	  \\
-					\vdots		\\
-					\cfrac{d c_{s,N_z}}{d t} \\
-					%\\ \hline \\
-					%\cfrac{d {\color{black}P}(t)}{d t} \\
-					\\ \hline \\
-					\cfrac{d {\color{black}y}(t)}{d t}
-				\end{bmatrix}
-				=
-				\underbrace{\begin{bmatrix}
-						G_1 \left( c_f,c_s; \Theta \right)\\ 
-						\vdots\\ 
-						G_{N_z} \left( c_f,c_s; \Theta \right)\\ 
-						\\ \hline \\ \\
-						G_{N_z+1} \left( c_f,c_s; \Theta \right)\\ 
-						\vdots\\
-						G_{2N_z} \left( c_f,c_s; \Theta \right)\\ 
-						%\\ \\ \hline \\ 
-						%{\color{black}G_{2N_z+1}} \left( c_f,c_s; \Theta \right) \\
-						\\ \\ \hline \\
-						G_{2N_z+2} \left( c_f,c_s; \Theta \right) 
-				\end{bmatrix}}_{G \left( x; \Theta \right)} 
-		\end{align*} }
-
-		where ${\color{black}x} \in \mathbb{R}^{N_x = 2N_z+1} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters, $N_{u}$ is the number of control variables.
+		where ${\color{black}x} \in \mathbb{R}^{N_x = 3N_z+2} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters, $N_{u}$ is the number of control variables.
 
@@
 					\cfrac{\partial c_s}{\partial t}\\
-					\cfrac{\partial {\color{black}h}(t,z)}{\partial t} \\
-					\cfrac{\partial {\color{black}P}(t,z)}{\partial t} \\
-					\cfrac{\partial {\color{black}y}(t)}{\partial t} 
+					\cfrac{\partial {\color{black}h}}{\partial t} \\
+					\cfrac{\partial P}{\partial t} \\
+					\cfrac{\partial {\color{black}y}}{\partial t} 
 				\end{bmatrix}
@@
 				\begin{bmatrix}
-					{\color{black}\bar{\phi_1}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)\\
-					{\color{black}\bar{\phi_2}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)\\
-					{\color{black}\bar{\phi_3}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right) \\
-					{\color{black}\bar{\phi_4}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)\\
-					{\color{black}\bar{\phi_5}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)
-				\end{bmatrix} = {\color{black}\bar{\phi}} \left( t,z; \Theta \right) = \cfrac{\partial {\color{black}\chi}(t,z)}{\partial t}
+					{\color{black}\bar{\phi_1}} \left( c_f,c_s,{\color{black}h}; \Theta \right)\\
+					{\color{black}\bar{\phi_2}} \left( c_f,c_s,{\color{black}h}; \Theta \right)\\
+					{\color{black}\bar{\phi_3}} \left( c_f,c_s,{\color{black}h}; \Theta \right) \\
+					{\color{black}\bar{\phi_4}} \left( c_f,c_s,{\color{black}h}; \Theta \right)\\
+					{\color{black}\bar{\phi_5}} \left( c_f,c_s,{\color{black}h}; \Theta \right)
+				\end{bmatrix} = {\color{black}\bar{\phi}} \left( t,z; \Theta \right) = \cfrac{\partial {\color{black}\chi}}{\partial t}
 		\end{align} }
@@
 		%Function ${\color{black}\bar{\phi}}$ are transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{black}G}$.
-		%The state-space model ${\color{black}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{black}x}}(t)$.
+		%The state-space model ${\color{black}\chi}$ after the discretization is represented by $\dot{{\color{black}x}}$.
 
-		%In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases ($c_f$ and $c_s$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{black}h}(t,z)$).
+		%In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases ($c_f$ and $c_s$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{black}h}$).
 The controllable input variables are the mass flow rate and temperature of the solvent in the feed and the pressure in the extractor.
-Additionally, the pressure change is augmented with the state-space and denoted as ${\color{black}P}(t)$.
-		%The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase, and it can be measured after the separator (${\color{black}Y}(t)$).
+Additionally, the pressure change is augmented with the state-space and denoted as $P$.
+		%The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase, and it can be measured after the separator (${\color{black}Y}$).
 The system is controllable by manipulating the flow rate and temperature (enthalpy) of CO$_2$ in the feed and the pressure in the extractor.

### 2024-04-22 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Parameter_estimation.tex
22.04

--- 2024-04-09 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Parameter_estimation.tex
@@
 	Only some of the parameters in a process model can be estimated from the theoretical considerations.
-The goal of parameter estimation is to obtain the "best" estimate of unknown parameters $\theta$ (which is a subset of the parameter space ${\color{black}\Theta}$ containing all parameters of a model) based on the continuous observations $Y(t)$ or the discrete observations $Y(t_i)$.
-Conceptually, the unobservable error $\epsilon(t)$ is added to the deterministic model output, $y(t)$ (Equation \ref{Model_measurment_1}), to give the observable dependent variable $Y(t)$ (for example results of an experiment).
+The goal of parameter estimation is to obtain the "best" estimate of unknown parameters $\theta$ (which is a subset of the parameter space ${\color{black}\Theta}$ containing all model's parameters) based on the continuous observations or the discrete.
+The unobservable error $\epsilon(t)$ is added to the deterministic model output, $y(t)$, to give the observable dependent variable $Y(t)$.
 For discrete observations, this can be expressed as:
@@
 Although the MLE has often been associated with the normal distribution for mathematical convenience, it can be applied to a wide range of probability distributions.
-The derivation of the likelihood function under the assumption of the Gaussian distribution is presented in Appendix \ref{CH: ML}.
+The derivation of the likelihood function under the assumption of the Gaussian distribution is discussed by \citet{Himmelblau1970}.
 The objective function is presented by Equation \ref{EQ: Objective_function}:

### 2024-04-22 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Results_Chamomile.tex
22.04

--- 2024-04-12 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Results_Chamomile.tex
@@
 	In both scenarios previously discussed, the fitting outcomes were not deemed satisfactory.
-Building upon the concepts underlying the Broken-and-Intact and Shrinking Core models (detailed in Chapter \ref{CH: Gamma_Function}), the gamma function is introduced to capture the decreasing extraction kinetics.
+Building upon the concepts underlying the Broken-and-Intact and Shrinking Core models (detailed in Chapter \ref{CH: Gamma_Function}), the $\gamma$-function is introduced to capture the decreasing extraction kinetics.
 The correction factor is combined with the simplified linear model, resulting in a two-parameter model ($D_i^R$ and $\Upsilon$) as given by Equation \ref{Model_kinetic}.
@@
 Results obtained by \citet{Rahimi2011} shows that the desorption–dissolution–diffusion model fails to reproduce the yield data.
-The main difference between the model employed by \citet{Rahimi2011} and the one in this study is the $\gamma$ function.
-The $\gamma$ function increases the model's flexibility by adjusting $D_i$ and allows it to obtain a better fit.
+The main difference between the model employed by \citet{Rahimi2011} and the one in this study is the $\gamma$-function.
+The $\gamma$-function increases the model's flexibility by adjusting $D_i$ and allows it to obtain a better fit.
 

### 2024-04-22 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Results_Sensitivity.tex
22.04

--- 2024-03-26 SFE_article_Sensitivity_Analysis - Chamomile/Sections/Results_Sensitivity.tex
@@
 
-   Figure \ref{fig:Sensitivty_F_CS} visualizes the local sensitivity of the solute concentration in the solid phase to changes in the mass flow rate during a supercritical fluid extraction process.
-It is postulated that with an increase in the mass flow rate, the driving force for mass transfer—the concentration gradient—becomes more pronounced, leading to an accelerated decrease in solute concentration within the solid matrix.
-This is exhibited by the negative sensitivity values: the solute is depleted more rapidly from the solid phase with higher mass flow rates.
-The most significant sensitivity is seen at the process commencement, particularly at the column inlet (top left corner with bright colours), where the concentration of solute is highest, and the effect of mass flow rate on extraction is most pronounced.
+   Figure \ref{fig:Sensitivty_F_CS} visualizes how the solute concentration in the solid phase is affected by the mass flow change.
+It is postulated that with an increase in the mass flow rate, the concentration gradient becomes larger leading to an accelerated decrease of the solute from solid particles and it is characterized by negative sensitivity values.
+Gradually, the sensitivities decrease until they reach minimum values and the effect of mass flow rate on extraction is most significant.
 
-   As the extraction progresses, the sensitivity values become less negative, moving towards zero, depicted by the gradient transitioning to cooler colors towards the bottom of the figure.
+   \begin{figure}[h!]
+   	\centering
+   	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.png}
+   	\caption{The effect of $F$ change on $C_s$}
+   	\label{fig:Sensitivty_F_CS}
+   \end{figure}
+
+   As the extraction progresses, the sensitivity values become less negative, moving towards zero.
 This gradual change corresponds to the decreasing concentration of the solute in the solid phase, which results in a diminishing concentration gradient and, consequently, a reduction in the rate of extraction.
 The sensitivity approaching zero suggests that the driving force for mass transfer is decreasing as the solute is being depleted.
+The asymptotic behaviour can be interpreted as a point where the remaining solute concentration in the solid phase is minimal and becomes less dependent on the mass flow rate.
+At this stage, other factors, such as internal diffusion within the solid matrix or equilibrium limitations, may limit the extraction rate.
 
-   The asymptotic approach to zero sensitivity indicates a physical plateau in the extraction process, where further increases in mass flow rate no longer enhance the extraction efficiency.
+   %The asymptotic approach to zero sensitivity indicates a physical plateau in the extraction process, where further increases in mass flow rate no longer enhance the extraction efficiency.
 In practical terms, this asymptotic behavior signifies the approach towards an extraction endpoint where the remaining solute concentration in the solid phase is minimal and becomes less dependent on the mass flow rate.
@@
 
-   In the most extreme cases, depicted by the uniform regions in the plot, the solute has been effectively exhausted, and the remaining traces in the solid phase are no longer influenced by changes in the mass flow rate.
+   %In the most extreme cases, depicted by the uniform regions in the plot, the solute has been effectively exhausted, and the remaining traces in the solid phase are no longer influenced by changes in the mass flow rate.
 This stage represents the final equilibrium, where the concentration gradient effectively drops to zero, rendering the mass flow rate inconsequential for the extraction of the remaining solute.
@@
 
+    The Figure \ref{fig:Sensitivty_F_CF} depicts the sensitivity of the solute concentration in the fluid phase to the flow rate within a supercritical fluid extraction system.
+In the initial phase of the extraction, the sensitivities near the inlet are negligible, as characterized by values close to zero.
+This indicates a minimal initial response to changes in the flow rate, which could be due to the presence of an high concentration gradient, allowing the fluid phase to rapidly reach solute regardless of the flow rate.
+
     \begin{figure}[h!]
     	\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.png}
-    	\caption{The effect of $F$ change on $C_s$}
-    	\label{fig:Sensitivty_F_CS}
+    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.png}
+    	\caption{The effect of $F$ change on $C_f$}
+    	\label{fig:Sensitivty_F_CF}
     \end{figure}
 
-    The Figure \ref{fig:Sensitivty_F_CF} depicts the sensitivity of the solute concentration in the fluid phase to the flow rate within a supercritical fluid extraction system.
-This sensitivity analysis reveals how the solute's behavior in the fluid phase is influenced by variations in the flow rate over the course of the extraction process, as depicted by both time and the length of the extraction column.
-
-    In the initial phase of the extraction, the sensitivities near the inlet are negligible, as shown by the colors being close to zero.
-This indicates a minimal initial response to changes in the flow rate, which could be due to the presence of an high concentration gradient, allowing the fluid phase to rapidly reach solute regardless of the flow rate.
-
-    As the extraction progresses, positive sensitivities emerge along the length of the extractor, indicated by the concentration front that develops and moves along the flow direction.
+    As the extraction progresses, positive sensitivities emerge along the length of the extractor and form the concentration front that moves in the flow direction.
 This front represents the increased movement of the solute with the fluid phase as the flow rate increases, suggesting an enhanced mass transfer due to the elevated velocity of the supercritical fluid.
-This velocity increase augments the concentration gradient, thus encouraging a more efficient solute migration from the solid to the fluid phase.
-
 Following the positive front, there is an emergence of a front characterized by negative sensitivities.
 This trend illustrates a diminishing solute concentration in the fluid phase, and it reflects a point in the extraction where the solute availability in the solid phase becomes a limiting factor; the depletion of solute reduces the concentration gradient, thereby decelerating the extraction rate.
+\todo{here}
 
@@
 
+	The Figure \ref{fig:Sensitivty_F_y} depicts the sensitivity of the extraction yield to variations in mass flow rate  as a function of time.
+The curve’s initial rise to a peak followed by a decline conveys the dynamic relationship between the mass flow rate and the extraction yield within the supercritical extraction process.
+
 	\begin{figure}[h!]
 		\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.png}
-    	\caption{The effect of $F$ change on $C_f$}
-    	\label{fig:Sensitivty_F_CF}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_F.png}
+		\caption{The effect of $F$ change on $y(t)$}
+		\label{fig:Sensitivty_F_y}
 	\end{figure}
-
-	The Figure \ref{fig:Sensitivty_F_y} depicts the sensitivity of the extraction yield to variations in mass flow rate  as a function of time.
-The curve’s initial rise to a peak followed by a decline conveys the dynamic relationship between the mass flow rate and the extraction yield within the supercritical extraction process.
 
@@
 This happens because the amount of solute in the fluid phase becomes a limiting factor, and the process is in the diffusion regime.
-
-    \begin{figure}[h!]
-    	\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_F.png}
-    	\caption{The effect of $F$ change on $y(t)$}
-    	\label{fig:Sensitivty_F_y}
-    \end{figure}
 

### 2024-04-22 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/introduction_imp.tex
22.04

--- 2024-04-08 SFE_article_Parameter_Estimation_short - Chamomile/Sections/introduction_imp.tex
@@
 Chamomile has been used for its medicinal benefits, serving as an anti-inflammatory, antioxidant, mild astringent, and healing remedy.
-Chamomile's aqueous extract is widely used as a gentle sedative to calm nerves and mitigate anxiety, hysteria, nightmares, insomnia, and other sleep-related conditions, according to \citet{Srivastava2009}.
+Chamomile's aqueous extract is widely used to calm nerves and mitigate anxiety, hysteria, nightmares, insomnia, and other sleep-related conditions, according to \citet{Srivastava2009}.
 \citet{Orav2010} reported that oil yields from dried chamomile samples ranged from 0.7 to 6.7 mL/kg.
-Notably, the highest yields of essential oil, between 6.1 and 6.7 mL/kg, were derived from chamomile sourced from Latvia and Ukraine, while chamomile from Armenia exhibited a lower oil content of 0.7 mL/kg.
+The highest yields of essential oil, between 6.1 and 6.7 mL/kg, were derived from chamomile sourced from Latvia and Ukraine, while chamomile from Armenia exhibited a lower oil content of 0.7 mL/kg.
 
@@
 This limitation has led to the increased popularity of alternative techniques like supercritical fluid extraction.
-Supercritical carbon dioxide is particularly appealing due to its distinctive properties: it is inflammable, non-toxic, and is non-corrosive.
-Moreover, compared to other fluids, its relatively low critical point positions it as an advantageous alternative to conventional extraction methods.
+Supercritical carbon dioxide is appealing due to its distinctive properties: it is inflammable, non-toxic, and is non-corrosive.
+CO$_2$ is the most used supercritical fluid, sometimes modified by co-solvents such as ethanol.
 Supercritical fluids are capable of exhibiting both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.
 
-	The literature offers various mathematical models to detail the extraction of valuable compounds from a fixed biomass bed.
-Selecting a fitting model necessitates a deep understanding of the physical processes at play within the operational unit, as each model is built on specific assumptions and outlines distinct mass transfer mechanisms and equilibrium dynamics.
+	The literature offers various mathematical models to describe the extraction of valuable compounds from a biomass.
+Selecting a model requires a deep understanding of the physical processes, as each model is built on specific assumptions, mass transfer mechanisms and equilibrium dynamics.
 
-	One model proposed by \citet{Reverchon1993} is the hot ball model, which is based on an analogy to heat transfer and describes an extraction process from solid particles containing small quantities of solute where solubility is not a limiting factor.
+	The model proposed by \citet{Reverchon1993} is the hot ball model, which is based on an analogy to heat transfer and describes an extraction process from solid particles.
+The model is based on assumptions that that particles contains low quantities of solute and solubility is not a limiting factor.
 
@@
 
-	This study focuses on creating a process model for the extraction of natural substances from solid materials using supercritical fluids, with a particular emphasis on supercritical CO$_2$.
+	This study focuses on finding a process model for the extraction of natural substances from solid materials using supercritical fluids, with a particular emphasis on supercritical CO$_2$.
 The approach involves estimating the solvent properties through thermodynamic relationships and determining the extraction kinetic parameters via a series of experiments conducted under a variety of conditions.
-The maximum likelihood estimator method is employed to address the parameter estimation challenge, with the derived parameters subsequently used to establish correlations.
-These correlations are instrumental in extending the applicability of the process model across different temperatures (30 to 40$~^\circ \text{C}$), pressures (100 to 200 bar) and flow rates (3.33 to 6.67 $\times 10^{-5}$ kg/s).
+The maximum likelihood estimation method is employed solve the parameter estimation problem.
+Later, the correlations between parameters and operating conditions are found.
 

### 2024-05-04 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Sections/Experiments.tex
04.05

--- 2024-04-09 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Experiments.tex
@@
 
-	The experiments were conducted using an a semi-batch extractor with diameter of 3.96 [cm] and length of 16.55 [cm].
-Twelve experiments were performed under different operating conditions: $30-40^\circ C$, $100 - 200$ [bar], and $0.05 - 0.24$ [kg/h].
-The amount of solid material used for extraction was $75$ [g], which was sufficient to fill the whole vessel.
+	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to test the process model against the experimental dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers.
+The experiments were performed by \citet{Povh2001} and \citet{Rahimi2011}.
+The experiments were conducted using a semi-batch extractor with a diameter of 3.96 [cm] and a length of 16.55 [cm].
+Twelve experiments were performed under different operating conditions: $30-40^\circ C$, $100 - 200$ [bar], and $0.12 - 0.24$ [kg/h].
+The amount of solid material used for extraction was $75$ [g].
 The bulk density of the bed was computed based on the feed's mass and the extractor's volume.
-The total porosity of the bed, including the particles, was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$.
+The bed porosity was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$.
+It is assumed that the total amount of the solute equals 3 [g], defined as the largest obtained yield after rounding up.
 

### 2024-05-04 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Sections/Model.tex
04.05

--- 2024-04-22 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
@@
 	\subsubsection{Continuity equation} \label{CH: Continuity}
-	 %When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction $\phi$ (where ${\color{black}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}
 
-	%The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function $A_f = A\phi$ to take into account the change of the cross-section available for the fluid.
-The Equation \ref{EQ: Continuity_differential} shows the differential form of the continuity equation:
-
-	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is refined by incorporating a function $A_f = A\phi$.
-This modification accounts for the variability in the cross-sectional area available for fluid flow.
-Equation \ref{EQ: Continuity_differential} presents this adaptation in the differential form of the continuity equation, capturing the dynamics of the flow as it responds to changes in the cross-section.
+	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is redefined by incorporating a function $A_f = A\phi$.
+This modification distinguishing a constant and varying terms, where the varying term accounts for the changes in the cross-sectional area available for the fluid.
+Equation \ref{EQ: Continuity_differential} shows the modified continuity equation:
 
@@
 	where $A$ is the total cross-section of the extractor and $\phi$ describe porosity along the extractor.
-
-	%{\color{black}assign a color of v and u}
 
@@
 	{\footnotesize
-	\begin{equation}
+	\begin{equation} \label{EQ:Velocity_1}
 		v = \cfrac{F}{\rho_f A\phi} 
@@
 	{\footnotesize
-		\begin{equation}
+		\begin{equation} \label{EQ:Velocity_2}
 			u = v \phi = \cfrac{F}{\rho_f A }
@@
 The variation in fluid density may occurs due to pressure or a inlet temperature changes.
+In non-isothermal case, $\rho_f$ in Equations \ref{EQ:Velocity_1} and \ref{EQ:Velocity_2} is consider to be an average fluid density along the extraction column.
 
@@
 
-	%The comprehensive derivation of the mass balance equation for the fluid phase is detailed in Appendix \ref{CH: Gouverning equations}. 
-	This equation accounts for the movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}), which is constrained to the axial direction due to the quasi-one-dimensional approach that considers changes in the void fraction.
+	Equation \ref{Model_fluid}, describes the movement of the solute in the system, which is constrained to the axial direction due to the quasi-one-dimensional assumption.
+Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself.
 It is also assumed that the thermodynamic pressure remains constant throughout the device.
 The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall, leading to a uniform velocity profile across any cross-section perpendicular to the axial direction.
-Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself.
 Thus, the mass balance equation include convection, diffusion, and kinetic terms to represent the fluid phase behaviour.

### 2024-05-04 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Sections/Parameter_estimation.tex
04.05

--- 2024-04-22 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Parameter_estimation.tex
@@
 
-	However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $dY(t_i)/dt$ is measured instead of $Y(t_i)$ itself.
-In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ as shown below
+	However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $\frac{dY(t_i)}{dt}$ is measured instead of $Y(t_i)$ itself.
+In such cases, it is assumed that the unobservable error is added to the deterministic derivative $\frac{dy(\theta, t_i)}{dt}$ as shown below
 
@@
 	\begin{table}[h]
-		\adjustbox{max width=\columnwidth}{%
+		\centering
+		%\adjustbox{max width=\columnwidth}{%
+			\small{
 			\begin{tabular}{ lccccccc }
 				\hline 
-				Parameter		&$k_m$[-] 	& $D_i^R\times10^{-13}$[$m^2/s$] 	& $D_e^M\times10^{-12}$[$m^2/s$]	& $\Upsilon$ [-] \\  \hline
+				Parameter		&$k_m$[-] 	& $D_i^R\times10^{-13}$[$m^2/s$] 	& $\Upsilon$ [-] & $\sigma$		\\  \hline
 				Lower bound		&0	  		& 0 	  							& 0 		  	 & 0			\\ 

### 2024-05-04 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Sections/Results_Chamomile.tex
04.05

--- 2024-04-22 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Results_Chamomile.tex
@@
 	To solve the parameter estimation problem, the single shooting method was used to transform the boundary-value problem into the initial value problem and to formulate the non-linear programming problem.
-This non-linear optimization task was tackled using the CasADi framework (\citet{Andersson2018}).
+This non-linear optimisation task was tackled using the CasADi framework (\citet{Andersson2018}).
 Each time series was fitted separately to the model with the linear extraction kinetics (Equation \ref{Model_kinetic_no_sat}).
-The initial value problem was solved multiple times with varying initial guesses to identify the global minimum.
-In case of the linear, two parameters remain to be determined: the partition coefficient $k_m$ and the internal diffusion coefficient $D_i$.
-
-	Figure \ref{fig: Fit_1_linear} shows the parameter space and corresponding values of the cost function for experiment 1 ($40^\circ C$, 100 bar and 6.67$\times 10^{-5}$ kg/s).
-As the cost function is to be minimized, the lowest value of $-\ln(L)$ indicate the best fit.
-A black vertical stripe at $D_i \approx 0.2$ can be observed.
-That stripe indicates the existence of the optimal value of the $D_i$.
-In the direction of $k_m$, the cost function is almost flat, which suggests that any value of $k_m$ above 0.1 fits the data equally well.
-If $k_m$ can be an arbitrary point, then it can grow to infinity, which suggests that the solvent is far from the saturation, and the model can be simplified.
-The model reduction can be introduced by considering the limit of $k_m$ in the extraction kinetic term:
+The parameter estimation problem was solved multiple times with varying parameter initial values to identify the global minimum.
+In the case of linear, two parameters remain to be determined: the partition coefficient $k_m$ and the internal diffusion coefficient $D_i$.
+\citet{Rahimi2011} analysed the same dataset and reported Peclet numbers between 290 and 400.
+Large Peclet number suggest that the advection term dominates the mass transfer, and the axial diffusion is negligible, which is one of the modelling assumptions.
 
@@
 		\centering
-		\begin{subfigure}{0.48\columnwidth}
+		\begin{subfigure}{0.85\columnwidth}
 			\centering
@@
 		\hfill
-		\begin{subfigure}{0.48\columnwidth}
-			\centering
-			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_Space_Di_Dx_Dataset_1.png}
-			\caption{The reduced linear kinetic model with axial diffusion}
-			\label{fig: Fit_1_Di_Dx}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}{0.48\columnwidth}
+		\begin{subfigure}{0.85\columnwidth}
 			\centering
@@
 
+	Figure \ref{fig: Fit_1_linear} shows the parameter space and corresponding values of the cost function for experiment 1 ($40^\circ C$, 100 bar and 6.67$\times 10^{-5}$ kg/s).
+As the cost function is to be minimized, the lowest value of $-\ln(L)$ indicate the best fit.
+A black vertical stripe at $D_i \approx 0.2$ can be observed.
+That stripe indicates the existence of the optimal value of the $D_i$.
+In the direction of $k_m$, the cost function is almost flat, which suggests that any value of $k_m$ above 0.1 fits the data equally well.
+If $k_m$ can be an arbitrary point, then it can grow to infinity, which suggests that the solvent is far from the saturation, and the model can be simplified.
+The model reduction can be introduced by considering the limit of $k_m$:
+
 	{\footnotesize
@@
 
-	The extraction model can be adapted to incorporate adjustments for the reduced kinetic term and axial diffusion.
-In this revised setup, two parameters remain undetermined: the internal diffusion coefficient $D_i$ and the axial diffusion coefficient $D_e^M$.
-Figure \ref{fig: Fit_1_Di_Dx} illustrates the parameter space of the modified model and associated cost function values.
-
-	Similarly to the previous case, the optimal value of $D_i$ exists, but a unique value for the $D_e^M$ cannot be determined.
-Figure \ref{fig: Fit_1_Di_Dx} illustrates the minimal impact of the axial diffusion coefficient, where a broad range of $D_e^M$ yields identical cost function values.
-By selecting a low value $D_e^M$, the axial diffusion terms can be reduced or eliminated from the model without compromising its generality.
-This observation aligns with the findings of \citet{Rahimi2011}, who analysed the same dataset and reported Peclet numbers ranging between 290 and 400.
-Such high values of the Peclet number suggest that the advection term dominates the mass transfer, and the axial diffusion is negligible.
-
-	In both scenarios previously discussed, the fitting outcomes were not deemed satisfactory.
+	In the scenario previously discussed, the fitting outcomes were not deemed satisfactory.
 Building upon the concepts underlying the Broken-and-Intact and Shrinking Core models (detailed in Chapter \ref{CH: Gamma_Function}), the $\gamma$-function is introduced to capture the decreasing extraction kinetics.
@@
 		\centering
-		\begin{subfigure}{0.66\columnwidth}
+		\begin{subfigure}{0.85\columnwidth}
 			\centering
@@
 		\hfill
-		\begin{subfigure}{0.66\columnwidth}
+		\begin{subfigure}{0.85\columnwidth}
 			\centering
@@
 
-	\iffalse
-	The estimated parameters describe the diminishing trend of the internal diffusion coefficient $D_i$, as delineated by Equation \ref{EQ: C_sat_function}.
-It is hypothesized that the internal diffusion coefficient decreases because solute particles face greater difficulty diffusing from the core of a particle than from positions closer to the surface.
-Decay patterns under various operational conditions, depicted in Figure \ref{fig: Gamma_function}, show that the internal diffusion coefficient is notably higher in fluids under high pressure.
-This observation aligns with the findings of \citet{Giddings1968}, \citet{Gurdial1989}, and \citet{Machida2011}, who explored the solvation capability of solvents and its correlation with the physical properties of CO$_2$ by calculating the Hildebrand solubility parameter $\delta_H$.
-\citet{Giddings1968} introduced a correlation for the solubility parameter $\delta_H[\text{MPa}^{1/2}] = 1.25 P_c^{1/2}\rho_r$, with $P_c$ and $\rho_r$ representing the critical pressure and reduced density, respectively.
-Similarly, \citet{Marcus2006} formulated a correlation based on the Van der Waals equation of state: $\delta_H[\text{MPa}^{1/2}] = 2.79 P_c^{1/4}T_r^{1/4}\rho_r$.
-As Figure \ref{fig: Gamma_function} shows, fluids with higher solubility factors exhibit greater internal diffusion coefficients.
-However, the relationship between $\delta_H$ and $D_i$ should be considered indicative rather than definitive due to the non-ideal nature of the system and the omission of external factors such as fluid velocity.
-
-	\begin{figure}[!h]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Gamma_function.png}
-		\caption{The decaying internal diffusion coefficient}
-		\label{fig: Gamma_function}
-	\end{figure}
-
-	\fi
-
 	The parameter estimation results are combined to analyse the relationship between the obtained parameters and the operating conditions.
@@
 		\hfill
-		\begin{subfigure}{0.48\columnwidth}
+		\begin{subfigure}{0.85\columnwidth}
 			\centering
@@
 		\end{subfigure}
-		\hfill
-		\begin{subfigure}{0.48\columnwidth}
+		\caption{Linear correlations between parameters}
+		%\label{fig: Correlations_surface}
+	\end{figure}
+
+	In Figures \ref{fig: Correlations_Di_Re} and \ref{fig: Correlations_Gamma_Re}, two distinct data clusters emerge, each corresponding to a different mass flow rate.
+Despite the linear trends observed in both sets of correlations, the correlations for $D_i^R$ exhibit a decline with increasing $Re$, whereas those for $\Upsilon$ show an upward trend with $Re$.
+The decrease in $D_i^R$ across each data line can be attributed to higher fluid density and increased mass transfer resistance.
+
+	\begin{figure}[!h]
+		\centering
+		\begin{subfigure}{0.85\columnwidth}
 			\centering
@@
 
-	In Figures \ref{fig: Correlations_Di_Re} and \ref{fig: Correlations_Gamma_Re}, two distinct data clusters emerge, each corresponding to a different mass flow rate.
-Despite the linear trends observed in both sets of correlations, the correlations for $D_i^R$ exhibit a decline with increasing Re, whereas those for $\Upsilon$ show an upward trend with Re.
-The decrease in $D_i^R$ across each data line can be attributed to higher fluid density and increased mass transfer resistance.
-%Conversely, the rise in $\Upsilon$ correlations may be explained by enhanced solubility.
-The Hildebrand solubility factor and the Reynolds number are proportional to the fluid density; hence, $\Upsilon$ can be correlated with Re.
-
 	A more general relationship can be obtained by applying multiple linear regression instead of linear regression.
-The clusters in Figure \ref{fig: Correlations_Di_Re}  and \ref{fig: Correlations_Gamma_Re} are close to parallel, suggesting that a plane would combine all the data points.
-The Reynolds number and flow rate act as independent variables for $D_i^R$ and $\Upsilon$ as presented in Figures \ref{fig: Correlations_Di_Re_F} and \ref{fig: Correlations_Gamma_Re_F}.
+The data clusters in Figure \ref{fig: Correlations_Di_Re} and \ref{fig: Correlations_Gamma_Re} are close to parallel, suggesting that a plane would combine all the data points.
+The Reynolds number and mass flow rate act as independent variables for $D_i^R$ and $\Upsilon$ as presented in Figures \ref{fig: Correlations_Di_Re_F} and \ref{fig: Correlations_Gamma_Re_F}.
 The presented correlations are valid in the whole range of investigated operating conditions.
+The correlations are later tested against the original dataset to show that the correlations can reproduce the results with satisfactory accuracy.
+Figure \ref{fig: Fit_Di_Gamma_correlation} shows the results of the simulations with incorporated correlations.
+A good agreement between simulation results and the dataset can be observed.
+If Figures \ref{fig: Fit_Di_Gamma} and \ref{fig: Fit_Di_Gamma_correlation} are compared, a decrease in the accuracy of simulations can be observed.
+Such a behaviour is expected due to the bias-variance trade-off, which describes the relationship between a model's complexity and the accuracy of its predictions.
 
@@
 
-	The correlations are later used against the original dataset to show that the correlations can reproduce the results with satisfactory accuracy.
-Figure \ref{fig: Fit_Di_Gamma_correlation} shows the results of the simulations with incorporated correlations.
-A good agreement between simulation results and the dataset can be observed.
-If Figures \ref{fig: Fit_Di_Gamma} and \ref{fig: Fit_Di_Gamma_correlation} are compared, a decrease in the accuracy of simulations can be observed.
-Such a behaviour is expected due the bias–variance trade-off, which describes the relationship between a model's complexity and the accuracy of its predictions.
-
-	%The parameter estimation results are compared to the work of \citet{Povh2001}, who fitted the Sovova model to the same dataset.
-It should be noted that the \citet{Povh2001} use as the initial solute mass ratio a value of 10\% above the total amount of extract for every experimental, while in this work, the initial conditions are the same for all the experiments as explained above.
-Contrary to this work, \citet{Povh2001} has not used any numerical solver in his work but rather a combination of analytical methods and a trial and error procedure.
-\citet{Povh2001} stated that 'the direct fitting of experimental data to the Sovova's model produced parameters that could not be accepted after a careful physical interpretation of the system'.
-The parameters found in this work seem to have a physical interpretation, and their values are in the excerpted range.
-
-	%\citet{Rahimi2011} fitted the same dataset to a model with desorption–dissolution–diffusion mechanism.
-To decrease the number of parameters to be found, \citet{Rahimi2011} applied a set of correlations.
-The remaining parameters were found using a genetic algorithm to solve the parameter estimation problem for each experiment separately.
-The results obtained by \citet{Rahimi2011} show that the desorption–dissolution–diffusion model cannot reproduce the yield data.
-The desorption–dissolution–diffusion model and the model used in this work are structurally similar, with the main difference of $\gamma$ function.
-The $\gamma$ function increases the model's flexibility and allows it to obtain a better fit.
-
-	%For every single experiment, \citet{Povh2001} and \citet{Rahimi2011} delivered a set of independent parameters.
-This work combines the parameters obtained from each experiment to get a single correlation valid for the whole range of investigated operating conditions.
-
 	The parameter estimation results are compared against those presented by \citet{Povh2001}, who applied the Sovova model to the same dataset.
-It is important to note that \citet{Povh2001} use as the initial solute mass ratio a value of 10\% above the total amount of extract for every experimental, while in this work, the initial conditions are the same for all the experiments.
-In contrast to this work, \citet{Povh2001} did not utilize numerical solvers but used a mix of analytical methodologies and trial-and-error procedures.
-\citet{Povh2001} remarked that 'the direct fitting of experimental data to the Sovova's model produced parameters that could not be accepted after a careful physical interpretation of the system'.
+It is important to note that \citet{Povh2001} use as the initial solute mass ratio a value of 10\% above the total amount of extract for every experiment, while in this work, the initial conditions are the same for all the experiments.
+In contrast to this work, \citet{Povh2001} did not utilise numerical solvers but used a mix of analytical methodologies and trial-and-error procedures.
+\citet{Povh2001} remarked that 'the direct fitting of experimental data to Sovova's model produced parameters that could not be accepted after a careful physical interpretation of the system'.
 The parameters identified in this study seem to have a physical interpretation and are within the expected range.
@@
 To decrease the number of unknown parameters, \citet{Rahimi2011} applied a set of empirical correlations.
-The remaining parameters were determined through the use of a genetic algorithm to solve the parameter estimation problem for each experiment individually.
-Results obtained by \citet{Rahimi2011} shows that the desorption–dissolution–diffusion model fails to reproduce the yield data.
+The remaining parameters were determined using a genetic algorithm to solve the parameter estimation problem for each experiment individually.
+Results obtained by \citet{Rahimi2011} show that the desorption–dissolution–diffusion model fails to reproduce the yield data.
 The main difference between the model employed by \citet{Rahimi2011} and the one in this study is the $\gamma$-function.
@@
 
-	\citet{Povh2001} and \citet{Rahimi2011} delivered a set of independent parameters for every single experiment.
+	\citet{Povh2001} and \citet{Rahimi2011} delivered a set of independent parameters for every experiment.
 This work combines the parameters obtained from each experiment to get a single correlation valid for the whole range of investigated operating conditions.

### 2024-05-04 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Sections/Saturation.tex
04.05

--- 2024-04-09 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Saturation.tex
@@
 	\subsubsection{Uneven solute's distribution in the solid phase} \label{CH: Gamma_Function}
-
-%	To mimic that not all solute might be obtained at specific operating conditions, the coefficient ${\color{black} \gamma}$ is introduced to limit the available oil.
-The ${\color{black} \gamma}({\color{black} c_s} (t,z))$ describe the reverse logistic function, which is equal to unity above the ${\color{black} c_{lim}}$, the saturation concentration, and equal to zero, below the ${\color{black} c_{lim}}$.
-The ${\color{black} \gamma}$ parameter multiply the solute concentration term in solid phase in the concentration gradient.
-As the concentration of solute decrease, it can reach the limiting value ${\color{black} c_{lim}}$ when the ${\color{black} \gamma}$ goes to zero and stop the extraction from the solid.
-%			
-%	{\footnotesize
-%		\begin{equation}
-%			{\color{black} \gamma}({\color{black} c_s} (t,z)) = \cfrac{1}{1+\exp \left( -{\color{black} k_{lim}} \left( {\color{black} c_s} (t,z) - {\color{black} c_{lim}} \right) \right) }
-%			\label{EQ: C_sat_function}
-%			\end{equation}
-%	}
-%			
-%	where ${\color{black} k_{lim}}$ describe the curvature of the $\gamma$ function, and it is defined as ${\color{black} k_{lim}} = 1$.
-%In the limit when $ {\color{black} k_{lim}}\rightarrow+\infty$ become a step function.
-If the ${\color{black} k_{lim}}$ is to high, the gradient of the ${\color{black} \gamma}$ function become high, or goes to infinity, which might cause difficulties for a gradient-based optimizer.
-%	The ${\color{black} \gamma}({\color{black} c_s} (t,z))$ gamma function is visualised on \ref{fig: Gamma_function}.
-%			
-%	\begin{figure}[h!]
-%		\centering
-%			\begin{tikzpicture}
-%					
-%				\begin{axis}[
-%					legend style={draw=none},
-%					xmin = 0, xmax = 100,
-%					ymin = -0.5, ymax = 1.5,
-%					xlabel = {${\color{black} c_s}(t,z)[kg/m^3]$},
-%					ylabel = {${\color{black} \gamma}({\color{black} c_s}(t,z))[-]$}]
-%					\addplot[
-%					domain = 0:100,
-%					samples = 100,
-%					smooth,
-%					thick,
-%					blue,
-%					] { 1 / (1 + exp( 1 * ( 50 - x ) ) ) };
-%					\addplot[thick, samples=50, dashed, domain=0:1.5, black] coordinates {(50,-0.5)(50,1.5)};
-%					
-%					\addlegendentry{${\color{black} \gamma}({\color{black} c_s} (t,z))$}
-%					\addlegendentry{${\color{black} c_{lim}}$}
-%				\end{axis}
-%					
-%			\end{tikzpicture}
-%			\caption{${\color{black} \gamma}({\color{black} c_s} (t,z))$ function under assumption of ${\color{black} c_{lim}}=50~[kg/m^3]$}
-%			\label{fig: Gamma_function}
-%	\end{figure}
 
@@
 	Such a formulation limits the availability of the solute in the solid phase.
-Similarly to the BIC model, if solute is assumed to be contained in the cells, a part of which is open because the cell walls were broken by grinding, and the rest remains intact.
-The diffusion of the solute from a particle's core takes more time compared to the diffusion of the solute located close to the outer surface.
-Considering that the internal diffusion coefficient decay as the concentration of the solute in the solid decrease.
-As the value of the $c_s$ decrease over time, the exponential term approach unity and $\lim_{ c_s \rightarrow 0} D_i =  D_i^R$.
-$D_i^R$ can be interpreted as the internal diffusion coefficient at vanishing gradient.
+Similarly to the BIC model, the solute is assumed to be contained in the cells, a part of which is open because the cell walls were broken by grinding, and the rest remains intact.
+The diffusion of the solute from a particle's core takes more time than the diffusion of the solute close to the outer surface.
+Following this idea, the mass transfer kinetic in this work assumes one solid phase with a decaying internal diffusion coefficient, where the decreasing term is a function of the solute concentration in the solid.
 

### 2024-05-04 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Sections/introduction_imp.tex
04.05

--- 2024-04-22 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/introduction_imp.tex
@@
 \citet{Orav2010} reported that oil yields from dried chamomile samples ranged from 0.7 to 6.7 mL/kg.
-The highest yields of essential oil, between 6.1 and 6.7 mL/kg, were derived from chamomile sourced from Latvia and Ukraine, while chamomile from Armenia exhibited a lower oil content of 0.7 mL/kg.
-
-	%The present study focuses on extracting essential oil from the chamomile flowers with supercritical fluid extraction and modelling that process.
-Caraway is a biennial plant belonging to the Apiaceae family.
-It is widespread in Asia, Europe, and North Afri``ca.
-The essential oil obtained from caraway finds its potential application as a fragrance ingredient in perfumes, liquors, and toothpaste.
-As presented by \citet{Hromis2015}, the dried caraway contains nearly~2.8–5\% essential oil, from which the main compounds are carvone, pinene, camphene, limonene, and carveol.
-
-	%The economic feasibility of the process is crucial when selecting the appropriate technology.
-Conventional processes, such as distillation and organic solvent extraction, are frequently used for essential oil extraction.
-The distillation process is carried out at a high temperature, which causes thermal degradation of thermolabile compounds—considering that alternative techniques like supercritical fluid extraction gained popularity for extraction.
-Supercritical carbon dioxide, in particular, is attractive due to its unique properties such as being inflammable, non-toxic, low critical temperature, and non-corrosive.
-Furthermore, its critical point is relatively low compared to other fluids, making it a suitable alternative to traditional extraction techniques.
-The supercritical fluids exhibit both gas- and liquid-like properties so that operating conditions can adjust the dissolving power.
-
-	%Various mathematical models have been proposed to describe the extraction of valuable compounds from a fixed biomass bed.
-However, selecting an appropriate extraction model requires understanding the physical phenomena occurring in the operational unit.
-Each model has its own set of assumptions and describes different mass transfer mechanisms and equilibrium relationships.
-
-	%One model proposed by \citet{Reverchon1993} is the hot ball model, which is based on an analogy to heat transfer and describes an extraction process from solid particles containing small quantities of solute where solubility is not a limiting factor.
-
-	%Another model, the Broken-and-Intact Cell model, was presented by \citet{Sovova1994}.
-This model describes a system where the outer surfaces of particles have been mechanically interrupted, allowing easy access of solvent to the solute from the broken cells.
-In contrast, the solute from the intact cells is less accessible due to high mass transfer resistance.
-
-	%\citet{Reverchon1996} developed a model for fluid-solid extraction, where the oil is treated as a single component, and the extraction process is controlled by internal mass transfer resistance, neglecting external mass transfer.
-However, this model does not consider the influence of axial dispersion or changes in fluid density and flow rate along the bed.
-
-	%In this work, the fundamental governing equations are derived and combined with the kinetic model suggested by \citet{Reverchon1996} to obtain a general model for the oil extraction process from the chamomile flower.
-This model simplifies some of the physical behaviour to obtain a control-oriented model.
-It is assumed that the extraction process operates semi-continuously in a cylindrical vessel.
-The solvent is first brought to supercritical conditions, pumped through a fixed bed of finely chopped biomass, and the solute is extracted from the biomass.
-The solvent and solute are then separated in a flush drum, and the extract is collected.
-The feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) of the extractor can be measured and manipulated, while the vessel pressure ($P$) can also be measured and manipulated.
-However, the outlet temperature ($T_{out}$) can only be measured.
-Figure \ref{fig: SFE_drawing} shows a simplified flow diagram.
+The highest yields of essential oil, between 6.1 and 6.7 mL/kg, were derived from chamomile sourced from Latvia and Ukraine.
+In comparison, chamomile from Armenia exhibited a lower oil content of 0.7 mL/kg.
 
@@
 This limitation has led to the increased popularity of alternative techniques like supercritical fluid extraction.
-Supercritical carbon dioxide is appealing due to its distinctive properties: it is inflammable, non-toxic, and is non-corrosive.
-CO$_2$ is the most used supercritical fluid, sometimes modified by co-solvents such as ethanol.
-Supercritical fluids are capable of exhibiting both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.
+Supercritical carbon dioxide is appealing due to its distinctive properties: it is inflammable, non-toxic, and non-corrosive.
+Supercritical fluids can exhibit both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.
 
-	The literature offers various mathematical models to describe the extraction of valuable compounds from a biomass.
-Selecting a model requires a deep understanding of the physical processes, as each model is built on specific assumptions, mass transfer mechanisms and equilibrium dynamics.
+	The literature offers various mathematical models to describe the extraction of valuable compounds from biomass.
+Selecting a process model is case-to-case dependent and requires analysing the specific assumptions of each model about mass transfer and thermodynamic equilibrium.
 
-	The model proposed by \citet{Reverchon1993} is the hot ball model, which is based on an analogy to heat transfer and describes an extraction process from solid particles.
-The model is based on assumptions that that particles contains low quantities of solute and solubility is not a limiting factor.
+	The model proposed by \citet{Reverchon1993} is called the hot ball model, as it is based on an analogy to heat transfer and describes an extraction process from solid particles.
+The model is based on the assumption that particles contain low quantities of solute and solubility is not a limiting factor.
 
-	The Broken-and-Intact Cell model, proposed by \citet{Sovova1994}, assumes that external surfaces of particles are mechanically disrupted, allowing the solvent's access to the solute in broken cells, while the solute in intact cells remains less accessible due to higher mass transfer resistance.
+	The Broken-and-Intact Cell model, proposed by \citet{Sovova1994}, assumes that external surfaces of particles are mechanically disrupted, allowing the solvent's access to the solute in broken cells.
+In contrast, the solute in intact cells remains less accessible due to higher mass transfer resistance.
 
@@
 
-	%This study aims to develop a process model for extracting natural substances from solid materials and liquids using supercritical fluids, specifically supercritical $CO_2$.
-To achieve this, the solvent properties are estimated based on thermodynamic relations, and the extraction kinetic parameters are estimated based on a set of experiments conducted under various conditions.
-The maximum likelihood estimator is used to solve the parameter estimation problem, and the obtained parameters are subjected to regression to derive correlations.
-These correlations enable the process model to be generalized across a range of temperatures (40 to $50~^\circ C$) and pressures (200 to 300 bar).
-
-	%The study is structured as follows: Chapter \ref{CH: Thermodynamic} provides a general discussion on supercritical fluids to familiarize the reader with their properties.
-Chapter \ref{CH:Governing_equations_chapter} introduces the general balance equations.
-The balance equations are combined with the extraction kinetic equation to develop the process model in Chapter \ref{CH: Extraction_model}.
-The maximum likelihood technique is presented in Chapter \ref{CH: Parameter_estimation} and is then combined with the process model.
-Chapter \ref{CH: Experiments} describes the experimental work and the data collected from experiments, which are used to estimate missing parameters related to the extraction kinetics.
-Finally, the parameter estimations and simulation results are discussed in Chapters \ref{CH: Results} and \ref{CH: Conclusion}.
-
 	This study focuses on finding a process model for the extraction of natural substances from solid materials using supercritical fluids, with a particular emphasis on supercritical CO$_2$.
 The approach involves estimating the solvent properties through thermodynamic relationships and determining the extraction kinetic parameters via a series of experiments conducted under a variety of conditions.
-The maximum likelihood estimation method is employed solve the parameter estimation problem.
-Later, the correlations between parameters and operating conditions are found.
-
-	%The organization of the study is as follows: Chapter \ref{CH: Thermodynamic} offers an overview of supercritical fluids, aiming to acquaint the reader with their unique properties. 
-	%Chapter \ref{CH:Governing_equations_chapter} outlines the fundamental balance equations.
-These equations are then integrated with the extraction kinetic equation in Chapter \ref{CH: Extraction_model} to formulate the process model.
-Chapter \ref{CH: Parameter_estimation} introduces the maximum likelihood estimation technique, which is subsequently applied within the context of the process model.
-Chapter \ref{CH: Experiments} details the experimental procedures and the data acquisition necessary for estimating the kinetic parameters related to the extraction process.
-The study culminates in Chapters \ref{CH: Results} and \ref{CH: Conclusion}, where the parameter estimations and simulation outcomes are thoroughly analysed and discussed.
+The maximum likelihood estimation is employed to solve the parameter estimation problem.
+Later, the correlations between parameters and operating conditions are proposed.
 

### 2024-05-04 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Short_no_axDiff_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
04.05

--- 2024-04-11 SFE_article_Parameter_Estimation_short - Chamomile/Short_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
@@
 The physical properties of the solvent are estimated based on the Peng-Robinson equation of state.
-Model parameters, including the partition factor, internal diffusion coefficient, axial diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data assuming normally distributed errors.
+Model parameters, including the partition factor, internal diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data assuming normally distributed errors.
 A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s.
@@
 
-	%The governing equations based on the work of \citet{Anderson1995} for quasi-one-dimensional compressible flow in Cartesian coordinates are presented in Appendix \ref{CH: Gouverning equations}.
-
 	The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}.
-%The formulation of these equations is elaborated upon in Appendix \ref{CH: Gouverning equations}, providing a mathematical foundation for analyzing flow dynamics under the assumed conditions.
 
@@
 By employing the concept of quasi-one-dimensional flow, the study simplifies the spatial dimensions of the extraction process, ensuring uniform flow across any cross-section while allowing for variations in the area available for the fluid phase.
-The physical properties of the solvent are estimated using the Peng-Robinson equation of state, and key model parameters are determined through maximum likelihood estimation based on experimental data, considering normally distributed errors.
+The physical properties of the solvent are estimated using the Peng-Robinson equation of state.
 
 Laboratory experiments were conducted by \citet{Povh2001} under various conditions to validate the model.
-The model parameters, such as partition factor, internal diffusion coefficient, axial diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data.
-The parameter space exploration revealed that while some parameters could be determined with a high degree of confidence, others, like the axial diffusion coefficient, had a low impact on the model's output.
-The identification of the low-impact parameters leads to model reduction
-
+The model parameters, such as partition factor, internal diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data.
+The parameter space exploration revealed that while some parameters could be determined with a high degree of confidence, others, like the partition factor, had a low impact on the model's output.
+The identification of the low-impact parameters leads to model reduction.
 This work introduced a set of correlations to find a general relationship between parameters and the independent variables, which can be determined by operating conditions.
 The obtained correlations were introduced into the model and tested against the dataset.
-The results show good agreement between the simulation results and all the data points.
 
-The presented model can be further used with the presented correlations to introduce an extraction model with dynamically changing operating conditions for multiple purposes, such as yield maximisation, techno-economic analysis, or optimal experiments design.
+The presented model can be further used with the presented correlations to introduce an extraction model with dynamically changing operating conditions for multiple purposes, such as yield maximisation, local sensitivity analysis, techno-economic analysis, or optimal experiments design.
 
@@
 %% Loading bibliography style file
-\clearpage
+%\clearpage
+\newpage
 %\bibliographystyle{model1-num-names}

### 2024-05-06 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Sections/Model.tex
06.05

@@
 The rate of extraction is thus $r_e\left(c_f - c^*_p(c_s)\right)$.
-
-		On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$.Concentration $c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate given by Equation \ref{Model_kinetic_basic}
+On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$.
+Concentration $c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate given by Equation \ref{Model_kinetic_basic}
 
@@
 
-		where $\Theta$ is a paramter space, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.
+		where $\Theta$ is a parameter space, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.
 

### 2024-05-06 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Short_no_axDiff_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
06.05

@@
 Essential oils of chamomile are used extensively for medicinal purposes.
-Many different products of chamomile have been developed, the most popular of which is in the form of herbal tea.
+Many different chamomile products have been developed, the most popular of which is herbal tea.
 A distributed-parameter model describes the fluid-solid extraction process.
@@
 The parameter space exploration revealed that while some parameters could be determined with a high degree of confidence, others, like the partition factor, had a low impact on the model's output.
-The identification of the low-impact parameters leads to model reduction.
+The identification of low-impact parameters leads to model reduction.
 This work introduced a set of correlations to find a general relationship between parameters and the independent variables, which can be determined by operating conditions.

### 2024-05-08 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Sections/Results_Chamomile.tex
08.05

@@
 	Figure \ref{fig: Fit_1_linear} shows the parameter space and corresponding values of the cost function for experiment 1 ($40^\circ C$, 100 bar and 6.67$\times 10^{-5}$ kg/s).
-As the cost function is to be minimized, the lowest value of $-\ln(L)$ indicate the best fit.
-A black vertical stripe at $D_i \approx 0.2$ can be observed.
-That stripe indicates the existence of the optimal value of the $D_i$.
+A black-coloured section, in the shape of a vertical stripe at $D_i \approx 0.2$, indicates the minimum values of the cost function $-\ln(L)$.
 In the direction of $k_m$, the cost function is almost flat, which suggests that any value of $k_m$ above 0.1 fits the data equally well.
@@
 	The parameter estimation results are combined to analyse the relationship between the obtained parameters and the operating conditions.
-Unlike traditional methods that employ a combination of Reynolds, Schmidt, and Sherwood numbers to find correlations—omitted here due to the insignificance of axial diffusion—the approach in this study leverages the Reynolds number $\left(Re = \frac{(2r) \cdot \rho_f \cdot u}{\mu}\right)$ as the sole independent variable.
+Unlike traditional methods that employ a combination of Reynolds, Schmidt, and Sherwood numbers to find correlation, the approach in this study leverages the Reynolds number $\left(Re = \frac{(2r) \cdot \rho_f \cdot u}{\mu}\right)$ as the sole independent variable.
 Using the Reynolds number has the advantage of considering the influence of all the control variables (temperature, pressure and flow rate), which means it can be uniquely defined by selecting operating conditions.
@@
 If Figures \ref{fig: Fit_Di_Gamma} and \ref{fig: Fit_Di_Gamma_correlation} are compared, a decrease in the accuracy of simulations can be observed.
-Such a behaviour is expected due to the bias-variance trade-off, which describes the relationship between a model's complexity and the accuracy of its predictions.
+Such behaviour is expected due to the bias-variance trade-off, which describes the relationship between a model's complexity and the accuracy of its predictions.
 

### 2024-05-08 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Short_no_axDiff_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
08.05

@@
 
-Laboratory experiments were conducted by \citet{Povh2001} under various conditions to validate the model.
+The model calibration is based on the laboratory experiments data conducted by \citet{Povh2001} under various conditions.
 The model parameters, such as partition factor, internal diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data.
@@
 The identification of low-impact parameters leads to model reduction.
-This work introduced a set of correlations to find a general relationship between parameters and the independent variables, which can be determined by operating conditions.
-The obtained correlations were introduced into the model and tested against the dataset.
+This work introduced a set of correlations to find a general relationship between parameters and the operating conditions.
+The obtained correlations were incorporated into the process model and tested against the dataset.
+The process model is capable of reproducing the dataset with satisfactory accuracy.
 

### 2024-05-08 SFE_article_Sensitivity_Analysis_short - Chamomile/Article_Sensitivity_Analsysis_short-Chamomile.tex
08.05

@@
 \subsection{Governing equations} \label{CH:Governing_equations_chapter}
+
 Following the work of \citet{Anderson1995}, the governing equations for quasi-one-dimensional were derived.
@@
 
-%The governing equations based on the work of \citet{Anderson1995} for quasi-one-dimensional compressible flow in Cartesian coordinates are presented in Appendix \ref{CH: Gouverning equations}.
-
 The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}.
-%The formulation of these equations is elaborated upon in Appendix \ref{CH: Gouverning equations}, providing a mathematical foundation for analyzing flow dynamics under the assumed conditions.
 

### 2024-05-08 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Model.tex
08.05

--- 2024-04-22 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
@@
 	{\footnotesize
-	\begin{equation}
+		\begin{equation} \label{EQ:Velocity_1}
 			v = \cfrac{F}{\rho_f A\phi} 
@@
 
-		\iffalse	
+			%\iffalse	
 			\subsubsection{Heat balance} \label{CH: heat_balance}
+
+			\begin{comment}
 
@@
 
-  		\fi
+			\end{comment}
+			The heat balance equation describe the evolution of the internal energy in the system and it is given by Equation \ref{EQ:Enthalpy_equation}
+
+			{\footnotesize
+				\begin{equation} \label{EQ:Enthalpy_equation}
+					\cfrac{\partial \left(\rho_f {\color{black}h} A_f\right)}{\partial t} = - \cfrac{\partial \left( \rho_f {\color{black}h} A_f v \right)}{\partial z} + \cfrac{\partial \left(P A_f\right)}{\partial t} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
+				\end{equation}
+			}
+
+			The main advantage of this formulation is the presence of term $\partial P / \partial t $, which directly affects the system through the change of thermodynamic pressure (which is a control variable).
+%The enthalpy is related to the pressure and temperature through the following equation:
+
+			If the value of enthalpy $h$ is known from the time evolution of the energy equation, and pressure $P$ is known from measurement, then the temperature $T$ can be reconstructed based on the departure function.
+The departure function is a mathematical function that characterizes the deviation of a thermodynamic property (enthalpy, entropy, and internal energy) of a real substance from that of an ideal gas at the same temperature and pressure.
+The departure function is defined as the difference between the value of a thermodynamic property for a real fluid and the corresponding value for an ideal gas at the same temperature and pressure.
+They are computed by integrating a function that depends on the equation of state and its derivatives.
+As presented by \citet{Gmehling2019}, for the Peng-Robinson equation of state, the enthalpy can be defined by Equation \ref{EQ:Enthalpy_PR}.
+
+			{\scriptsize
+				\begin{equation}
+					{\color{black}h}-{\color{black}h}^{id}={\color{black}R}T \left[{\color{black}T_r}({\color{black}Z}-1) -2.078(1+{\color{black}\kappa} ){\sqrt { {\color{black}\alpha}\left(T\right) } } \ln \left(\cfrac{{\color{black}Z}+\left( 1+\sqrt{2} \right){\color{black}B}}{{\color{black}Z}+\left( 1-\sqrt{2} \right){\color{black}B}}\right)\right]
+					\label{EQ:Enthalpy_PR}
+				\end{equation}				
+			}
+
+			Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which is assumed to be $T_{ref}=298.15$[K] and $P_{ref}=1.01325$[bar].
+
+			A root-finder can be used to find a value of temperature, which minimizes the difference between the value of enthalpy coming from the heat balance and the departure functions.
+The root fining procedure to repeated at every time step to find a local temperature along spatial direction $z$.
+
+			{\footnotesize
+				\begin{equation}
+					\underbrace{h\left(t,x\right)}_{\text{Heat balance}}=\underbrace{h\left(T,P,\rho_f\left(T,P\right)\right)}_{\text{Departure function}}
+					\label{EQ:Enthalpy_root}
+				\end{equation}
+			}
 
@@
 				\begin{align*}
-					&c_f(t = 0, z) = 0 && c_s(t = 0, z) = c_{s0} && {c_f}(t, z=0) = 0 \\
-					&\frac{\partial c_f(t,z=L)}{\partial x} = 0 && c_s(t, z=\{0,L\}) = 0 && y(0) = 0
+					&c_f(t = 0, z) = 0  && c_s(t = 0, z) = c_{s0} && h(t = 0, z) = h_0 \\
+					&c_f(t,   z=0) = 0  && h(t, z=0) = h_{in}(t)  && \frac{\partial c_f(t,z=L)}{\partial x} = 0 \\
+					&\frac{\partial h(t,z=L)}{\partial x} = 0   && c_s(t, z=\{0,L\}) = 0 && y(0) = 0
 			\end{align*} }
+
+			\todo{P is missing}
 
@@
 
-		\begin{comment}
 				{\footnotesize
@@
 				\end{align*} }
-	\end{comment}
-
-		{\footnotesize
-			\begin{align*} \label{discretization}
-				\dot{x} &= \cfrac{d x}{d t} = 
-				\begin{bmatrix}
-					\cfrac{d c_{f,1}}{d t} 	  \\
-					\vdots		\\	
-					\cfrac{d c_{f,N_z}}{d t} \\
-					\\ \hline  	\\
-					\cfrac{d c_{s,1}}{d t} 	  \\
-					\vdots		\\
-					\cfrac{d c_{s,N_z}}{d t} \\
-					%\\ \hline \\
-					%\cfrac{d {\color{black}P}(t)}{d t} \\
-					\\ \hline \\
-					\cfrac{d {\color{black}y}(t)}{d t}
-				\end{bmatrix}
-				=
-				\underbrace{\begin{bmatrix}
-						G_1 \left( c_f,c_s; \Theta \right)\\ 
-						\vdots\\ 
-						G_{N_z} \left( c_f,c_s; \Theta \right)\\ 
-						\\ \hline \\ \\
-						G_{N_z+1} \left( c_f,c_s; \Theta \right)\\ 
-						\vdots\\
-						G_{2N_z} \left( c_f,c_s; \Theta \right)\\ 
-						%\\ \\ \hline \\ 
-						%{\color{black}G_{2N_z+1}} \left( c_f,c_s; \Theta \right) \\
-						\\ \\ \hline \\
-						G_{2N_z+2} \left( c_f,c_s; \Theta \right) 
-				\end{bmatrix}}_{G \left( x; \Theta \right)} 
-		\end{align*} }
-
-		where ${\color{black}x} \in \mathbb{R}^{N_x = 2N_z+1} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters, $N_{u}$ is the number of control variables.
+			where ${\color{black}x} \in \mathbb{R}^{N_x = 3N_z+2} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters, $N_{u}$ is the number of control variables.
 
@@
 
-		where $\Theta$ is a paramter space, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.
+			where $\Theta$ is a parameter space, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.
 

### 2024-05-08 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Results_Sensitivity.tex
08.05

--- 2024-03-21 SFE_article_Sensitivity_Analysis - Chamomile/Sections/Results_Sensitivity.tex
@@
 
-	\subsection{Flow rate}
+	%\subfile{Sensitivity_Flow_Rate}
 
-	The increase in the mass-flow rate affects the system simultaneously along the spatial direction by increasing the velocity but without affecting the thermodynamic state of the fluid.
-As a result, Figure \ref{fig:Sensitivty_F_P} indicates that the system's pressure remains unaffected by changes in the flow rate.
+    \subfile{Sensitivity_Pressure}
 
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_F.png}
-		\caption{The effect of $F$ change on $P$}
-		\label{fig:Sensitivty_F_P}
-	\end{figure}
-
-	It is important to note that $h$ represents enthalpy but not total enthalpy, thus excluding kinetic energy.
-As a consequence of the modelling assumptions, changes in $h$ and $\rho$ occur in response to changes in pressure or temperature, which explains no deviation of $h \times \rho$ in Figure \ref{fig:Sensitivty_F_H}.
-
-    %When utilizing Dirichlet boundary conditions, it's crucial to be aware of potential numerical artefacts from the differing methods used to compute them.
-The system's enthalpy is determined through the time evolution of governing equations, while the inlet's enthalpy depends on the inlet temperature and pressure, which are the controls.
-A minor numerical mismatch between these values may manifest as an enthalpy difference propagating along the spatial domain.
-To ensure consistency between the fluid at the inlet and inside the computational domain, this analysis employs Neumann boundary conditions.
-
-    \begin{figure}[h!]
-    	\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.png}
-    	\caption{The effect of $F$ change on $h \times \rho$}
-    	\label{fig:Sensitivty_F_H}
-    \end{figure}
-
-   Figure \ref{fig:Sensitivty_F_CS} visualizes the local sensitivity of the solute concentration in the solid phase to changes in the mass flow rate during a supercritical fluid extraction process.
-It is postulated that with an increase in the mass flow rate, the driving force for mass transfer—the concentration gradient—becomes more pronounced, leading to an accelerated decrease in solute concentration within the solid matrix.
-This is exhibited by the negative sensitivity values: the solute is depleted more rapidly from the solid phase with higher mass flow rates.
-The most significant sensitivity is seen at the process commencement, particularly at the column inlet (top left corner with bright colours), where the concentration of solute is highest, and the effect of mass flow rate on extraction is most pronounced.
-
-   As the extraction progresses, the sensitivity values become less negative, moving towards zero, depicted by the gradient transitioning to cooler colors towards the bottom of the figure.
-This gradual change corresponds to the decreasing concentration of the solute in the solid phase, which results in a diminishing concentration gradient and, consequently, a reduction in the rate of extraction.
-The sensitivity approaching zero suggests that the driving force for mass transfer is decreasing as the solute is being depleted.
-
-   The asymptotic approach to zero sensitivity indicates a physical plateau in the extraction process, where further increases in mass flow rate no longer enhance the extraction efficiency.
-In practical terms, this asymptotic behavior signifies the approach towards an extraction endpoint where the remaining solute concentration in the solid phase is minimal and becomes less dependent on the mass flow rate.
-At this stage, other factors, such as diffusion within the solid matrix or equilibrium limitations, may limit the extraction rate.
-
-   In the most extreme cases, depicted by the uniform regions in the plot, the solute has been effectively exhausted, and the remaining traces in the solid phase are no longer influenced by changes in the mass flow rate.
-This stage represents the final equilibrium, where the concentration gradient effectively drops to zero, rendering the mass flow rate inconsequential for the extraction of the remaining solute.
-At this juncture, the system has reached its thermodynamic limit, and the efficiency of extraction cannot be enhanced by merely increasing the flow rate.
-This underscores the importance of optimizing the mass flow rate at the beginning and throughout the extraction process to ensure efficient solute recovery before reaching this terminal stage.
-
-   %Figure \ref{fig:Sensitivty_F_CS} shows how the flow rate affects the solute concentration in the solid phase.
-At the beginning of the extraction process, the flow rate has a low impact on the extraction process due to the dominance of the concentration gradient in the kinetic regime.
-The corresponding sensitivities are close to zero.
-As time progresses, the increment in the mass flow rate has a greater influence on the extraction kinetics, causing the sensitivities to decrease towards their minimum values.
-Negative sensitivities indicate a faster extraction rate.
-
-    \begin{figure}[h!]
-    	\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.png}
-    	\caption{The effect of $F$ change on $C_s$}
-    	\label{fig:Sensitivty_F_CS}
-    \end{figure}
-
-    The Figure \ref{fig:Sensitivty_F_CF} depicts the sensitivity of the solute concentration in the fluid phase to the flow rate within a supercritical fluid extraction system.
-This sensitivity analysis reveals how the solute's behavior in the fluid phase is influenced by variations in the flow rate over the course of the extraction process, as depicted by both time and the length of the extraction column.
-
-    In the initial phase of the extraction, the sensitivities near the inlet are negligible, as shown by the colors being close to zero.
-This indicates a minimal initial response to changes in the flow rate, which could be due to the presence of an high concentration gradient, allowing the fluid phase to rapidly reach solute regardless of the flow rate.
-
-    As the extraction progresses, positive sensitivities emerge along the length of the extractor, indicated by the concentration front that develops and moves along the flow direction.
-This front represents the increased movement of the solute with the fluid phase as the flow rate increases, suggesting an enhanced mass transfer due to the elevated velocity of the supercritical fluid.
-This velocity increase augments the concentration gradient, thus encouraging a more efficient solute migration from the solid to the fluid phase.
-
-    Following the positive front, there is an emergence of a front characterized by negative sensitivities.
-This trend illustrates a diminishing solute concentration in the fluid phase, and it reflects a point in the extraction where the solute availability in the solid phase becomes a limiting factor; the depletion of solute reduces the concentration gradient, thereby decelerating the extraction rate.
-
-    Toward the end of the extraction process, the sensitivities are shown to increase from their negative values towards zero.
-This asymptotic approach suggests that the system is reaching a kinetic regime where further increases in the flow rate have a low impact on the solute concentration in the fluid phase.
-This behavior reflects a physical limit where the remaining solute in the solid phase is insufficient to sustain a high concentration in the fluid phase, regardless of the flow rate.
-It indicates a terminal phase of the extraction process where the available solute has been largely exhausted, and the system response to changes in flow rate is inherently constrained by the depletion of extractable material.
-
-    %Figure \ref{fig:Sensitivty_F_CF} shows how the concentration of solute in the fluid phase responds to an increase in the flow rate.
-Initially, sensitivities are close to zero, indicating a minimal system response.
-The growth in flow rate affects $C_f(z,t)$ indirectly by increasing the velocity and consequently elevating the concentration gradient.
-As a result, positive sensitivities emerge within the system, forming a front that progresses in the direction of flow.
-The positive front indicates that the larger amount of solute moves faster across the system.
-When the amount of the solute in the solid phase becomes a limiting factor, then the concentration gradient diminishes and slows down the extraction kinetics.
-The corresponding sensitivities form a front composed of negative sensitivities propagating through the extractor.
-The negative front indicates that the solute concentration in the fluid phase becomes lower than before the flow rate increment.
-Eventually, the negative sensitivities start to increase and asymptotically approach zero.
-
-    \begin{figure}[h!]
-    	\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.png}
-    	\caption{The effect of $F$ change on $C_f$}
-    	\label{fig:Sensitivty_F_CF}
-    \end{figure}
-
-	The Figure \ref{fig:Sensitivty_F_y} depicts the sensitivity of the extraction yield to variations in mass flow rate  as a function of time.
-The curve’s initial rise to a peak followed by a decline conveys the dynamic relationship between the mass flow rate and the extraction yield within the supercritical extraction process.
-
-	In the early phase, the sensitivity is minimal, denoting that adjustments to the mass flow rate have a negligible influence on the yield.
-This can be attributed to the initial phase of the extraction, where the mass transport mechanisms are mainly controlled by a high concentration gradient.
-
-	As the process evolves, the curve's ascent to its apex signifies a period during which the extraction yield becomes increasingly sensitive to the mass flow rate.
-This is likely due to the mass flow rate enhancing the convective transport of solute, maximizing the extraction efficiency.
-At this stage, the solute transfer from the solid to the fluid phase is most responsive to changes in flow rate.
-
-	However, the curve’s descent past the peak suggests a diminishing return on sensitivity with further increases in mass flow rate.
-The decrease indicates a transitional phase where the extraction process likely encounters diffusion limitations or a depletion of readily extractable solute.
-The concentration gradient, which drives the mass transfer, may be reduced due to the depletion of solute in the solid phase, or the system may be experiencing diffusive resistances that limit the rate at which solute can be delivered to the fluid phase.
-
-	The asymptotic approach to zero sensitivity towards the end of the curve reflects a regime where the yield is no longer significantly influenced by the mass flow rate.
-At this juncture, the extraction process has likely exhausted the available solute, and any further increase in mass flow rate does not result in a proportional increase in yield.
-The extraction system has reached a point of saturation or equilibrium where the mass transfer is limited by factors other than flow rate, such as the intrinsic properties of the solute or the matrix, indicating that the system has achieved as much extraction as is practically feasible under the given conditions.
-
-	The curve captures the non-linear and transient nature of the extraction yield's response to the mass flow rate, underscoring the importance of optimizing flow rates over the duration of the extraction to maximize yield.
-It also highlights the multifaceted dependencies and constraints inherent in supercritical fluid extraction processes, such as mass transfer rates, solute availability, and diffusion limitations.
-
-    %In Figure \ref{fig:Sensitivty_F_y}, the curve's shape reveals the time-dependent sensitivity of extraction yield to mass flow rate variations.
-The curve peaks and then falls, indicating a transient behavior in extraction efficiency.
-Initially, there's a negligible response, suggesting that changes in mass flow rate have little to no immediate impact on yield.
-As time progresses, however, yield becomes increasingly sensitive to the flow rate, reaching a peak sensitivity.
-Beyond this peak, the sensitivity decreases, which might reflect a saturation point in the extraction process where further increases in mass flow rate do not translate to increased yield, possibly due to limitations in solute diffusion rates from the solid matrix and decreasing concentration gradient.
-Eventually, $dy/dF$ asymptotically approaches zero.
-This happens because the amount of solute in the fluid phase becomes a limiting factor, and the process is in the diffusion regime.
-
-    \begin{figure}[h!]
-    	\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_F.png}
-    	\caption{The effect of $F$ change on $y(t)$}
-    	\label{fig:Sensitivty_F_y}
-    \end{figure}
-
-    \subsection{Pressure}
-
-    As discussed in Chapter \ref{CH:Governing_equations_chapter}, a small pressure wave propagates at the speed of sound relative to the flow.
-If the flow velocity is relatively low, all pressure changes are hydrodynamic (resulting from velocity motion) rather than thermodynamic.
-The Low Mach-number assumption leads to instant propagation of the thermodynamic pressure throughout the system.
-This assumption allows considering a single pressure value for the entire system, as all changes occur simultaneously within the machine.
-Figure \ref{fig:Sensitivty_P_P} illustrates a step function representing the pressure change.
-
-    \begin{figure}[h!]
-    	\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_P.png}
-    	\caption{The effect of $P$ change on $P$ in the system}
-    	\label{fig:Sensitivty_P_P}
-    \end{figure}
-
-    According to Equation \ref{EQ:Enthalpy_equation}, the pressure change directly affects the quantity $h \times \rho$ through $\partial (P(t) A_f) / \partial t$, leading to the step change along the whole system, as presented in Figure \ref{fig:Sensitivty_P_H}.
-The uniform response across the entire extraction column length and time, represented by the homogeneously dark red color, indicates that the entire system experiences an immediate and uniform change in enthalpy density in response to pressure changes.
-This is consistent with the physical expectation that pressure changes should equilibrate rapidly throughout the fluid phase due to the high compressibility of supercritical fluids.
-
-    Regarding the boundary conditions, by applying the Dirichlet boundary conditions( mean setting a fixed temperature at the system boundary) can leads to a possible thermal gradient within the system if the initial temperatures differ.
-In contrast, Neumann boundary conditions would dictate that the heat flux at the boundaries be held constant, ensuring temperature uniformity between the inlet and the rest of the extractor.
-In case of this work, the Neumann boundary conditions have been applied, as indicated by the uniform response in enthalpy density, implying that there is no temperature gradient caused by a heat front propagating through the system.
-Instead, the temperature within the extractor is instantaneously and evenly matched to that at the inlet.
-
-	%According to Equation \ref{EQ:Enthalpy_equation}, the pressure change directly affects the quantity $h \times \rho$ through $\partial (P(t) A_f) / \partial t$, leading to the step change along the whole system, as presented in Figure \ref{fig:Sensitivty_P_H}.
-Depending on the configuration of the system, two cases are possible.
-If Dirichlet boundary conditions are applied, the inlet temperature is maintained at the predefined value and may differ from the temperature in the extractor.
-In such a case, the temperature difference will cause the heat front to propagate through the system.
-Alternatively, Neumann boundary conditions can be applied to ensure that the temperature inside the extractor matches that at its inlet.
-In this work, the second approach was chosen.
-
-    \begin{figure}[h!]
-    	\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P.png}
-    	\caption{The effect of $P$ change on $(h \times \rho)$ in the system}
-    	\label{fig:Sensitivty_P_H}
-    \end{figure}
-
-    The provided figure showcases the sensitivity of the solute concentration in the solid phase with respect to changes in pressure throughout a fixed bed in a supercritical fluid extraction process.
-
-    As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely related to its density, which suggests that with higher fluid density—often associated with increased pressure—the velocity decreases.
-This leads to an extended residence time of the fluid within the system.
-The lower velocity afforded by increased pressure allows for a longer interaction between the solute and the solvent, potentially a higher concentration of solute in the fluid phase.
-
-    Simultaneously, pressure changes alter the fluid's thermodynamic state, affecting the extraction process's kinetics.
-These changes are characterized by correlations ({\color{red}article 1}), such as the increase of the diffusion coefficient $D_i^R$ with fluid density.
-A higher $D_i^R$ indicates enhanced mass transfer capabilities, contributing to an increased rate of extraction.
-
-    Figure \ref{fig:Sensitivty_P_CS} captures these dual effects on the solute concentration within the solid matrix.
-Initially, the system response is low due to a high concentration gradient.
-When the concentration gradient starts to diminish, high sensitivities reveal that changes in pressure have a more pronounced effect.
-This is consistent with the fluid's higher density and lower velocity, resulting in more effective mass transfer from the solid to the fluid phase.
-
-    Over time, the pressure change has a lower effect and the sensitivities decay.
-This trend signifies that the impact of pressure on solute concentration is diminishing, likely due to the depletion of the solute in the solid phase over time.
-The decreasing concentration gradient suggests that the solute availability becomes a limiting factor in the extraction process.
-
-    Eventually, sensitivities asymptotically approach zero.
-The solute concentration in the solid phase has been reduced, and further changes in pressure do not influence the remaining concentration.
-This behaviour reflects that in the later extraction phase, the kinetics of extraction are dominated by the reduced availability of the solute rather than the conditions of the supercritical fluid.
-
-	%The pressure change affects the mass transfer in two ways.
-As discussed in Chapter \ref{CH: Continuity}, the velocity is inversely proportional to the density; hence, the higher density of the fluid leads to a lower velocity and larger residence time.
-The changes in the thermodynamic state of the fluid affect the extraction kinetic parameters, which are defined by correlations presented in {\color{red}article 1}.
-For example, the $D_i^R$ increases with the fluid density, which leads to a higher extraction rate.
-The cumulative effect of the pressure change on the solute concentration in the solid phase can be observed in Figure \ref{fig:Sensitivty_P_CS}.
-The sensitivity plot shows a close-to-uniform decay of sensitivities along the fixed bed.
-After the extremum, the sensitivities asymptotically increase to zero.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.png}
-		\caption{The effect of $P$ change on $C_s$}
-		\label{fig:Sensitivty_P_CS}
-	\end{figure}
-
-	Figure \ref{fig:Sensitivty_P_CF} shows the sensitivity of the solute concentration in the fluid phase as a function of pressure changes throughout the supercritical extraction column's length and over the extraction process's duration.
-An increase in pressure typically enhances the solute's solubility, resulting in its heightened presence in the supercritical fluid, which is seen as a leading front moving through the system.
-Due to the diffusion effect, the gradient becomes more dispersed in regions beyond the fixed bed.
-Following this, the formation of a trailing front characterized by decreasing sensitivities can be observed.
-This trailing front can be explained by the decrease in the concentration gradient as the solute is increasingly extracted and the available concentration within the solid phase diminishes.
-As seen in the figure, sensitivities are declining towards zero.
-This asymptotic trend suggests the driving force for the mass transfer—the concentration gradient—has been minimized, and changes in pressure no longer significantly impact the solute concentration in the fluid phase.
-
-	%The deviation in the solute concentration in the fluid phase caused by the pressure change is presented in Figure \ref{fig:Sensitivty_P_CF}.
-As discussed earlier, the sensitivities related to the solute concentration in the solid phase are characterized by negative sensitivities, suggesting a higher extraction rate due to the pressure change.
-Consequently, an increase in solute concentration in the fluid phase is expected.
-This increase in solute concentration in the fluid phase is visible in Figure \ref{fig:Sensitivty_P_CF} as positive sensitivities, which form a front that moves along the extractor.
-Due to the diffusion effect, the front changes its pattern in the empty section and becomes more spread.
-Accelerating the extraction rate since the beginning of the extraction process leads to a faster decrease in the concentration gradient.
-This effect is reflected in Figure \ref{fig:Sensitivty_P_CF} as the front of the negative sensitivities, which follows the positive front.
-Eventually, the negative sensitivities approach zero when the concentration gradient goes to zero.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.png}
-		\caption{The effect of $P$ change on $C_f$}
-		\label{fig:Sensitivty_P_CF}
-	\end{figure}
-
-	Figure \ref{fig:Sensitivty_P_y} illustrates the temporal evolution of the extraction yield's sensitivity to changes in pressure within a supercritical fluid extraction system.
-
-	Initially, the curve displays an almost flat profile, suggesting a latency in the system's response to pressure changes.
-A minor initial decrease in sensitivity, indicated by a slight dip below zero, may arise due to a decrease in the velocity of the fluid phase.
-For a constant mass flow rate, an increase in fluid density due to heightened pressure results in a lower fluid velocity, potentially leading to this reduced sensitivity.
-
-	As the process continues, the curve ascends sharply, indicating a positive yield response to pressure.
-This increase in sensitivity can be associated with the enhanced solubility and mass transfer capabilities imparted by higher pressures, improving the rate at which solute is extracted into the fluid phase.
-The peak in dy/dP reflects the most responsive period of the system, where pressure changes are highly effective in improving yield.
-
-	Beyond the peak, the sensitivity declines, converging towards zero.
-This descending curve represents a depletion phase: as the available solute in the solid phase diminishes, the potential for further increasing the yield through pressure alone is reduced.
-The remaining solute concentration becomes a limiting factor, and the mass transfer driving force, initially augmented by pressure, no longer plays a dominant role.
-
-	%The impact of pressure increase on extraction yield is depicted in Figure \ref{fig:Sensitivty_P_y}.
-The initial flat curve reflects a system delay caused by the empty space within the extractor that the fluid phase needs to flow through.
-The first observed deviation is a small negative sensitivity, which can be related to a lower fluid phase velocity.
-Keeping the same mass flow rate and increasing the density (by increasing the pressure) decreases the velocity.
-Next, the sensitivity rises, which indicates an increase in yield.
-$dy / dP$ reaches its positive maximum and then declines due to a limited amount of solute remaining in the solid phase.
-The sensitivity curve draws into negative values, reach a minimum point, and converges to zero.
-The simulation duration was extended to demonstrate the convergence of $dy / dP$ towards zero.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_P.png}
-		\caption{The effect of $P$ change on $y(t)$}
-		\label{fig:Sensitivty_P_y}
-	\end{figure}
-
-	\subsection{Inlet temperature}
-
-	The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through it.
-
-	The Figure \ref{fig:Sensitivty_P_T} shows the system pressure response.
-A flat curve indicates an invariant behavior of pressure in response to inlet temperature changes throughout the time.
-The pressure in the modelled system is controlled and maintained independently of the inlet temperature variations as a results of the assumptions as explained in the Chapter X.
-	%The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through the system.
-As the fluid with the modified temperature flows along the system, it gradually modifies the mass transfer parameters.
-One important assumption is that the inlet temperature change does not affect the pressure, which explains a horizontal line in Figure \ref{fig:Sensitivty_P_T}.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_T_{in}.png}
-		\caption{The effect of $T_{in}$ change on $P$ in the system}
-		\label{fig:Sensitivty_P_T}
-	\end{figure}
-
-	The inlet enthalpy is characterized by the Dirichlet boundary condition.
-The boundary value of $(h\times \rho)$ is calculated based on two controls which can be manipulated: inlet temperature and given pressure.
-Any deviation in $T_{in}$ affects $(h\times \rho)$ at the inlet, propagating according to the governing equations.
-	Figure \ref{fig:Sensitivty_T_H} showcases the sensitivity of the fluid enthalpy to the inlet temperature over both time and the length of the extraction bed.
-The fluid entering the extraction bed will have its enthalpy directly influenced by the boundary conditions.
-The heat front propagation from the inlet of the extractor to its outlet.
-As the fluid progresses through the bed, the enthalpy change affects the whole system gradually.
-Over time, the system's approach to a new thermal steady state and the sensitivities becomes zero.
-
-	%The heat front propagation is presented in Figure \ref{fig:Sensitivty_T_H}. The initial system had constant temperature along the whole spatial domain.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_T_{in}.png}
-		\caption{The effect of $T_{in}$ change on $(h \times \rho)$ in the system}
-		\label{fig:Sensitivty_T_H}
-	\end{figure}
-
-	Figure \ref{fig:Sensitivty_T_CS} shows the curve depicts an initial increase (the positive sign of the sensitivities) in the solute concentration in the solid phase as a function of time, which later asymptotically approaches a stable value before decreasing again towards the end of the period.
-Although $D_i^R$ decreases with the fluid's density, the $\Upsilon$ increases, which explains the system responses.
-This suggests that an increase in temperature slows the mass transfer of solutes from the solid phase to the supercritical fluid; hence, the solute concentration in the solid phase increases.
-Over time, this effect stabilizes, which could indicate the exhaustion of easily extractable solutes.
-	%Figure \ref{fig:Sensitivty_T_CS} illustrates how the change in inlet temperature affects the concentration of solute in the solid phase.
-As presented in {\color{red}article 1}, the value of $D_i^R$ decreases as density decreases.
-Therefore, it is expected to observe positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, indicating a slower extraction rate.
-Initially, the sensitivities are zero along the fixed bed because the heat front requires time to reach the fixed bed.
-Since this propagation is not instantaneous, a non-uniform distribution of sensitivities along the fixed bed becomes evident.
-All the sensitivities gradually increase until they reach their maximum.
-When the concentration gradient becomes the limiting factor, the sensitivities decrease.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_T_{in}.png}
-		\caption{The effect of $T_{in}$ change on $C_s$ in the system}
-		\label{fig:Sensitivty_T_CS}
-	\end{figure}
-
-	The Figure \ref{fig:Sensitivty_T_CF} represents the sensitivity of the concentration of solutes in the fluid phase over a period of 600 minutes as a result of changes in the inlet temperature.
-Initially, all the sensitivities remain at zero due to the idle period.
-As the fluid with elevated temperature flows through the fixed bed, the internal mass transfer slows down (the $D_i^R$ is proportional to density as presented in {\color{red}article 1}), resulting in negative sensitivities.
-The negative sensitivities can be explained by considering that the heat front slowed mass transfer, causing more solute to remain in the solid phase.
-After reaching their minima, the sensitivities increase and reach positive values.
-Later the sensitivities starts to increase due higher concentration gradient if compared to before the temperature change.
-Eventually, the system response stabilize around a constant value when the extraction kinetics become a limiting factor.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_T_{in}.png}
-		\caption{The effect of $T_{in}$ change on $C_f$ in the system}
-		\label{fig:Sensitivty_T_CF}
-	\end{figure}
-
-	Figure \ref{fig:Sensitivty_T_y} depicts how an increase in inlet temperature alters the extraction yield.
-Initially, the sensitivity curve remains flat due to the idle time.
-The first observed response of the system is a small increment of the $dy/dT_{in}$ caused by an increment of the velocity( which is inversely proportional to the fluid density).
-After the small positive peak, the sensitivity curve begins to decrease.
-The negative value of the sensitivity indicates a lower process efficiency.
-Over time, the sensitivity reaches its minimum and then increases due to a higher concentration gradient than in the case without the disturbance.
-Eventually, the $dy/dT_{in}$ curve flattens around a negative value.
-The flattening of the yield curve suggests that the mass transfer parameters limit the extraction rate, and the residual solute in the solid phase becomes difficult to obtain.
-The simulation time was extended to show how the sensitivity plot flattened.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_T_{in}.png}
-		\caption{The effect of $T_{in}$ change on $y(t)$ in the system}
-		\label{fig:Sensitivty_T_y}
-	\end{figure}
+    %\texttt{}\subfile{Sensitivity_Inlet_Temperature}
 

### 2024-05-08 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Sensitivity_Pressure.tex
08.05

--- 2024-03-20 SFE_article_Sensitivity_Analysis - Chamomile/Sections/Results_Sensitivity.tex
@@
 \begin{document}
-
-	\label{CH: Results}
-
-	This work investigates the influence of inlet temperature, pressure, and mass flow rate on the state space and the extraction yield.
-The process model and parameters have been discussed in {\color{red}article 1}.
-The process model was calibrated on the set of experiments obtained at different operating conditions, $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s.
-The sensitivity analysis has been performed assuming that the system operates at $35^\circ C$, 150 bar and 5 $\times 10^{-5}$ kg/s.
-
-	\subsection{Flow rate}
-
-	The increase in the mass-flow rate affects the system simultaneously along the spatial direction by increasing the velocity but without affecting the thermodynamic state of the fluid.
-As a result, Figure \ref{fig:Sensitivty_F_P} indicates that the system's pressure remains unaffected by changes in the flow rate.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_F.png}
-		\caption{The effect of $F$ change on $P$}
-		\label{fig:Sensitivty_F_P}
-	\end{figure}
-
-	It is important to note that $h$ represents enthalpy but not total enthalpy, thus excluding kinetic energy.
-As a consequence of the modelling assumptions, changes in $h$ and $\rho$ occur in response to changes in pressure or temperature, which explains no deviation of $h \times \rho$ in Figure \ref{fig:Sensitivty_F_H}.
-
-    %When utilizing Dirichlet boundary conditions, it's crucial to be aware of potential numerical artefacts from the differing methods used to compute them.
-The system's enthalpy is determined through the time evolution of governing equations, while the inlet's enthalpy depends on the inlet temperature and pressure, which are the controls.
-A minor numerical mismatch between these values may manifest as an enthalpy difference propagating along the spatial domain.
-To ensure consistency between the fluid at the inlet and inside the computational domain, this analysis employs Neumann boundary conditions.
-
-    \begin{figure}[h!]
-    	\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.png}
-    	\caption{The effect of $F$ change on $h \times \rho$}
-    	\label{fig:Sensitivty_F_H}
-    \end{figure}
-
-   Figure \ref{fig:Sensitivty_F_CS} represents the sensitivity of solute concentration in the solid phase to changes in the mass flow rate.
-In an extraction process, it is expected that as the mass flow rate increases, the concentration of solute in the solid phase would decrease more quickly due to the increased concentration gradient.
-The improved extraction efficiency is indicated by negative sensitivities, as the loss of the solute from the solid phase is faster.
-Eventually, the amount of solute in the solid phase decreases, and the concentration gradient limits the extraction kinetic.
-This behaviour is represented by sensitivities, which increase from their minimal values and asymptotically approach to zero.
-In extreme cases, when all the solutes have been removed from the solid phase, the concentration gradient is zero, independent of the mass flow rate, which explains the asymptotic behaviour.
-
-   %Figure \ref{fig:Sensitivty_F_CS} shows how the flow rate affects the solute concentration in the solid phase.
-At the beginning of the extraction process, the flow rate has a low impact on the extraction process due to the dominance of the concentration gradient in the kinetic regime.
-The corresponding sensitivities are close to zero.
-As time progresses, the increment in the mass flow rate has a greater influence on the extraction kinetics, causing the sensitivities to decrease towards their minimum values.
-Negative sensitivities indicate a faster extraction rate.
-
-    \begin{figure}[h!]
-    	\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.png}
-    	\caption{The effect of $F$ change on $C_s$}
-    	\label{fig:Sensitivty_F_CS}
-    \end{figure}
-
-    Figure \ref{fig:Sensitivty_F_CF} shows how the concentration of solute in the fluid phase responds to an increase in the flow rate.
-Initially, sensitivities are close to zero, indicating a minimal system response.
-The growth in flow rate affects $C_f(z,t)$ indirectly by increasing the velocity and consequently elevating the concentration gradient.
-As a result, positive sensitivities emerge within the system, forming a front that progresses in the direction of flow.
-The positive front indicates that the larger amount of solute moves faster across the system.
-When the amount of the solute in the solid phase becomes a limiting factor, then the concentration gradient diminishes and slows down the extraction kinetics.
-The corresponding sensitivities form a front composed of negative sensitivities propagating through the extractor.
-The negative front indicates that the solute concentration in the fluid phase becomes lower than before the flow rate increment.
-Eventually, the negative sensitivities start to increase and asymptotically approach zero.
-
-    \begin{figure}[h!]
-    	\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.png}
-    	\caption{The effect of $F$ change on $C_f$}
-    	\label{fig:Sensitivty_F_CF}
-    \end{figure}
-
-    In Figure \ref{fig:Sensitivty_F_y}, the curve's shape reveals the time-dependent sensitivity of extraction yield to mass flow rate variations.
-The curve peaks and then falls, indicating a transient behavior in extraction efficiency.
-Initially, there's a negligible response, suggesting that changes in mass flow rate have little to no immediate impact on yield.
-As time progresses, however, yield becomes increasingly sensitive to the flow rate, reaching a peak sensitivity.
-Beyond this peak, the sensitivity decreases, which might reflect a saturation point in the extraction process where further increases in mass flow rate do not translate to increased yield, possibly due to limitations in solute diffusion rates from the solid matrix and decreasing concentration gradient.
-Eventually, $dy/dF$ asymptotically approaches zero.
-This happens because the amount of solute in the fluid phase becomes a limiting factor, and the process is in the diffusion regime.
-
-    \begin{figure}[h!]
-    	\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_F.png}
-    	\caption{The effect of $F$ change on $y(t)$}
-    	\label{fig:Sensitivty_F_y}
-    \end{figure}
 
@@
 		\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_P.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/P_P.png}
 		\caption{The effect of $P$ change on $P$ in the system}
@@
 
-	According to Equation \ref{EQ:Enthalpy_equation}, the pressure change directly affects the quantity $h \times \rho$ through $\partial (P(t) A_f) / \partial t$, leading to the step change along the whole system, as presented in Figure \ref{fig:Sensitivty_P_H}.
-Depending on the configuration of the system, two cases are possible.
-If Dirichlet boundary conditions are applied, the inlet temperature is maintained at the predefined value and may differ from the temperature in the extractor.
-In such a case, the temperature difference will cause the heat front to propagate through the system.
-Alternatively, Neumann boundary conditions can be applied to ensure that the temperature inside the extractor matches that at its inlet.
-In this work, the second approach was chosen.
+	According to Equation \ref{EQ:Enthalpy_equation}, the pressure change directly affects the quantity $h \times \rho$ through $\frac{\partial (P(t) A_f)}{\partial t}$, leading to the step change along the whole system, as presented in Figure \ref{fig:Sensitivty_P_H}.
+The uniform response across the entire extraction column length and time, represented by the homogeneously dark red colour, indicates that the entire system experiences an immediate and uniform change in enthalpy density in response to pressure changes.
+
+	The pressure change influences the temperature of the fluid in the middle of the computational domain, but the values on boundaries can be defined in multiple ways.
+Applying the Dirichlet boundary conditions assumes a fixed temperature value at the inlet, which leads to a possible thermal gradient propagating along the system.
+In contrast, Neumann boundary conditions would dictate that the heat flux at the boundaries be held constant.
+In this work, the Neumann boundary conditions have been applied, which leads to a uniform response and ensures the temperatures at the inlet and in the middle of the extractor are the same.
 
@@
 		\centering
-    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/H_P.png}
 		\caption{The effect of $P$ change on $(h \times \rho)$ in the system}
@@
 
-	The pressure change affects the mass transfer in two ways.
-As discussed in Chapter \ref{CH: Continuity}, the velocity is inversely proportional to the density; hence, the higher density of the fluid leads to a lower velocity and larger residence time.
-The changes in the thermodynamic state of the fluid affect the extraction kinetic parameters, which are defined by correlations presented in {\color{red}article 1}.
-For example, the $D_i^R$ increases with the fluid density, which leads to a higher extraction rate.
-The cumulative effect of the pressure change on the solute concentration in the solid phase can be observed in Figure \ref{fig:Sensitivty_P_CS}.
-The sensitivity plot shows a close-to-uniform decay of sensitivities along the fixed bed.
-The negative values of sensitivities suggest a faster extraction rate.
-No matter the location of the sensitivity measure in the bed, the general behaviour stays the same.
-Every sensitivity starts with zero and decreases to a minimum value.
-After the extremum, the sensitivities asymptotically increase to zero.
+	Figure \ref{fig:Sensitivty_P_CS} shows the sensitivity of the solute concentration in the solid phase with respect to changes in pressure throughout a fixed bed in a supercritical fluid extraction process.
+As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely related to its density, which suggests that with higher fluid density, the velocity decreases.
+This leads to an extended residence time, ergo, a longer interaction between the solute and the solvent.
+
+	Initially, the extraction process is in the kinetically-controlled regime, where the concentration gradient is high, and the limiting factor is the solute solubility.
+As explained in ({\color{red}article 1}), the system is considered to be far from the saturation, which can explain low system response at the beginning of the process.
+
+	When the concentration gradient diminishes, and the extraction moves from the kinetic-controlled to the diffusion-controlled regime, the system response becomes more profound.
+({\color{red}article 1}) obtained a linear correlation for $D_i^R$, which is incorporated in this model.
+$D_i^R$ increases together with fluid density, which explains negative sensitivities.
+The negative sign can be interpreted as a faster loss of a solute from a solid phase, which corresponds to enhanced mass transfer.
+
+	Over time, the amount of solute becomes a limiting factor and the pressure change has a lower effect on the system and the sensitivities increase.
+Eventually, sensitivities asymptotically approach zero.
+The solute concentration in the solid phase has been reduced, and further changes in pressure do not influence the remaining concentration.
+This behaviour reflects that in the later extraction phase, the kinetics of extraction are controlled by the internal diffusion of the solute from solid particles rather than the conditions of the supercritical fluid.
 
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/CS_P.png}
 		\caption{The effect of $P$ change on $C_s$}
@@
 
-	The deviation in the solute concentration in the fluid phase caused by the pressure change is presented in Figure \ref{fig:Sensitivty_P_CF}.
-As discussed earlier, the sensitivities related to the solute concentration in the solid phase are characterized by negative sensitivities, suggesting a higher extraction rate due to the pressure change.
-Consequently, an increase in solute concentration in the fluid phase is expected.
-This increase in solute concentration in the fluid phase is visible in Figure \ref{fig:Sensitivty_P_CF} as positive sensitivities, which form a front that moves along the extractor.
-Due to the diffusion effect, the front changes its pattern in the empty section and becomes more spread.
-Accelerating the extraction rate since the beginning of the extraction process leads to a faster decrease in the concentration gradient.
-This effect is reflected in Figure \ref{fig:Sensitivty_P_CF} as the front of the negative sensitivities, which follows the positive front.
-Eventually, the negative sensitivities approach zero when the concentration gradient goes to zero.
+	Figure \ref{fig:Sensitivty_P_CF} shows the sensitivity of the solute concentration in the fluid phase as a response to the pressure change.
+As explained above, an increase in pressure enhanced the mass transfer, resulting in concentration front moving through the system.
+Initially, the system response is low due to low response in the solid phase.
+\todo{TODO}
+	Following this, the formation of a trailing front characterized by decreasing sensitivities can be observed.
+This trailing front can be explained by the decrease in the concentration gradient as the solute is increasingly extracted and the available concentration within the solid phase diminishes.
+As seen in the figure, sensitivities are declining towards zero.
+This asymptotic trend suggests the driving force for the mass transfer—the concentration gradient—has been minimized, and changes in pressure no longer significantly impact the solute concentration in the fluid phase.
 
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/CF_P.png}
 		\caption{The effect of $P$ change on $C_f$}
@@
 
-	The impact of pressure increase on extraction yield is depicted in Figure \ref{fig:Sensitivty_P_y}.
-The initial flat curve reflects a system delay caused by the empty space within the extractor that the fluid phase needs to flow through.
-The first observed deviation is a small negative sensitivity, which can be related to a lower fluid phase velocity.
-Keeping the same mass flow rate and increasing the density (by increasing the pressure) decreases the velocity.
-Next, the sensitivity rises, which indicates an increase in yield.
-$dy / dP$ reaches its positive maximum and then declines due to a limited amount of solute remaining in the solid phase.
-The sensitivity curve draws into negative values, reach a minimum point, and converges to zero.
-The simulation duration was extended to demonstrate the convergence of $dy / dP$ towards zero.
+	Figure \ref{fig:Sensitivty_P_y} illustrates the temporal evolution of the extraction yield's sensitivity to changes in pressure within a supercritical fluid extraction system.
+
+	Initially, the curve displays an almost flat profile, suggesting a latency in the system's response to pressure changes.
+A minor initial decrease in sensitivity, indicated by a slight dip below zero, may arise due to a decrease in the velocity of the fluid phase.
+For a constant mass flow rate, an increase in fluid density due to heightened pressure results in a lower fluid velocity, potentially leading to this reduced sensitivity.
+
+	As the process continues, the curve ascends sharply, indicating a positive yield response to pressure.
+This increase in sensitivity can be associated with the enhanced solubility and mass transfer capabilities imparted by higher pressures, improving the rate at which solute is extracted into the fluid phase.
+The peak in dy/dP reflects the most responsive period of the system, where pressure changes are highly effective in improving yield.
+
+	Beyond the peak, the sensitivity declines, converging towards zero.
+This descending curve represents a depletion phase: as the available solute in the solid phase diminishes, the potential for further increasing the yield through pressure alone is reduced.
+The remaining solute concentration becomes a limiting factor, and the mass transfer driving force, initially augmented by pressure, no longer plays a dominant role.
 
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_P.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/Y_P.png}
 		\caption{The effect of $P$ change on $y(t)$}
@@
 
-	\subsection{Inlet temperature}
-
-	The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through it.
-
-	The Figure \ref{fig:Sensitivty_P_T} shows the system pressure response.
-A flat curve indicates an invariant behavior of pressure in response to inlet temperature changes throughout the time.
-The pressure in the modelled system is controlled and maintained independently of the inlet temperature variations as a results of the assumptions as explained in the Chapter X.
-	%The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through the system.
-As the fluid with the modified temperature flows along the system, it gradually modifies the mass transfer parameters.
-One important assumption is that the inlet temperature change does not affect the pressure, which explains a horizontal line in Figure \ref{fig:Sensitivty_P_T}.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_T_{in}.png}
-		\caption{The effect of $T_{in}$ change on $P$ in the system}
-		\label{fig:Sensitivty_P_T}
-	\end{figure}
-
-	The inlet enthalpy is characterized by the Dirichlet boundary condition.
-The boundary value of $(h\times \rho)$ is calculated based on two controls which can be manipulated: inlet temperature and given pressure.
-Any deviation in $T_{in}$ affects $(h\times \rho)$ at the inlet, propagating according to the governing equations.
-	Figure \ref{fig:Sensitivty_T_H} showcases the sensitivity of the fluid enthalpy to the inlet temperature over both time and the length of the extraction bed.
-The fluid entering the extraction bed will have its enthalpy directly influenced by the boundary conditions.
-The heat front propagation from the inlet of the extractor to its outlet.
-As the fluid progresses through the bed, the enthalpy change affects the whole system gradually.
-Over time, the system's approach to a new thermal steady state and the sensitivities becomes zero.
-
-	%The heat front propagation is presented in Figure \ref{fig:Sensitivty_T_H}. The initial system had constant temperature along the whole spatial domain.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_T_{in}.png}
-		\caption{The effect of $T_{in}$ change on $(h \times \rho)$ in the system}
-		\label{fig:Sensitivty_T_H}
-	\end{figure}
-
-	Figure \ref{fig:Sensitivty_T_CS} shows the curve depicts an initial increase (the positive sign of the sensitivities) in the solute concentration in the solid phase as a function of time, which later asymptotically approaches a stable value before decreasing again towards the end of the period.
-Although $D_i^R$ decreases with the fluid's density, the $\Upsilon$ increases, which explains the system responses.
-This suggests that an increase in temperature slows the mass transfer of solutes from the solid phase to the supercritical fluid; hence, the solute concentration in the solid phase increases.
-Over time, this effect stabilizes, which could indicate the exhaustion of easily extractable solutes.
-	%Figure \ref{fig:Sensitivty_T_CS} illustrates how the change in inlet temperature affects the concentration of solute in the solid phase.
-As presented in {\color{red}article 1}, the value of $D_i^R$ decreases as density decreases.
-Therefore, it is expected to observe positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, indicating a slower extraction rate.
-Initially, the sensitivities are zero along the fixed bed because the heat front requires time to reach the fixed bed.
-Since this propagation is not instantaneous, a non-uniform distribution of sensitivities along the fixed bed becomes evident.
-All the sensitivities gradually increase until they reach their maximum.
-When the concentration gradient becomes the limiting factor, the sensitivities decrease.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_T_{in}.png}
-		\caption{The effect of $T_{in}$ change on $C_s$ in the system}
-		\label{fig:Sensitivty_T_CS}
-	\end{figure}
-
-	The Figure \ref{fig:Sensitivty_T_CF} represents the sensitivity of the concentration of solutes in the fluid phase over a period of 600 minutes as a result of changes in the inlet temperature.
-Initially, all the sensitivities remain at zero due to the idle period.
-As the fluid with elevated temperature flows through the fixed bed, the internal mass transfer slows down (the $D_i^R$ is proportional to density as presented in {\color{red}article 1}), resulting in negative sensitivities.
-The negative sensitivities can be explained by considering that the heat front slowed mass transfer, causing more solute to remain in the solid phase.
-After reaching their minima, the sensitivities increase and reach positive values.
-Later the sensitivities starts to increase due higher concentration gradient if compared to before the temperature change.
-Eventually, the system response stabilize around a constant value when the extraction kinetics become a limiting factor.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_T_{in}.png}
-		\caption{The effect of $T_{in}$ change on $C_f$ in the system}
-		\label{fig:Sensitivty_T_CF}
-	\end{figure}
-
-	Figure \ref{fig:Sensitivty_T_y} depicts how an increase in inlet temperature alters the extraction yield.
-Initially, the sensitivity curve remains flat due to the idle time.
-The first observed response of the system is a small increment of the $dy/dT_{in}$ caused by an increment of the velocity( which is inversely proportional to the fluid density).
-After the small positive peak, the sensitivity curve begins to decrease.
-The negative value of the sensitivity indicates a lower process efficiency.
-Over time, the sensitivity reaches its minimum and then increases due to a higher concentration gradient than in the case without the disturbance.
-Eventually, the $dy/dT_{in}$ curve flattens around a negative value.
-The flattening of the yield curve suggests that the mass transfer parameters limit the extraction rate, and the residual solute in the solid phase becomes difficult to obtain.
-The simulation time was extended to show how the sensitivity plot flattened.
-
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_T_{in}.png}
-		\caption{The effect of $T_{in}$ change on $y(t)$ in the system}
-		\label{fig:Sensitivty_T_y}
-	\end{figure}
-
 \end{document}

### 2024-05-08 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/introduction_imp.tex
08.05

@@
 
-	This study focuses on finding a process model for the extraction of natural substances from solid materials using supercritical fluids, with a particular emphasis on supercritical CO$_2$.
+	%This study focuses on finding a process model for the extraction of natural substances from solid materials using supercritical fluids, with a particular emphasis on supercritical CO$_2$.
 The approach involves estimating the solvent properties through thermodynamic relationships and determining the extraction kinetic parameters via a series of experiments conducted under a variety of conditions.

### 2024-05-12 SFE_article_Sensitivity_Analysis_short - Chamomile/Article_Sensitivity_Analsysis_short-Chamomile.tex
12.05

@@
 The sensitivity equations can be obtained in various ways, but the automatic differentiation technique was implemented to obtain the sensitivity equations in this work.
-By identifying which parameters are influential at each period of the simulation, local sensitivity analysis can yield valuable information for guiding the process modelling, the design of experiments or the model reduction.
-The local sensitivity analysis techniques consider the sensitivities at only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions unless the discussed system is a linear model.
+By identifying which parameters are influential at each period of the simulation, local sensitivity analysis can bring valuable information about process modelling, design of experiments or model reduction.
+The local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions unless the discussed system is a linear model.
 
 In this study, the local sensitivity analysis method was introduced to explore the dynamics of the supercritical extraction system, which consists of a set of partial differential equations.
-The sensitivity equations evaluate the influence of control variables such as flow rate, pressure, and inlet temperature on the state-space consisting of the concentration of the solute in solid and liquid phases, the fluid's enthalpy density, system pressure, and extraction yield.
+The sensitivity analysis was used to evaluate the influence of pressure increase on the state-space consisting of the solutes concentration in solid and liquid phases, the fluid's enthalpy density, system pressure, and extraction yield.
 Every change in the control variables leads to a state-space change, eventually affecting the process performance.
 
-Similarities between Figures \ref{fig:Sensitivty_F_y}, \ref{fig:Sensitivty_P_y} and \ref{fig:Sensitivty_T_y} can observed, although the sources of disturbances are different.
+At given operating conditions, the step change of pressure enhance the mass transfer, which leads to observation faster loss of solute by the solid particles and consequently to negative sensitivities.
+Analogous response is visible in the fluid phase, where the concentration of solute increase, which is visible as positive sensitivities.
+As more solute is transported to the fluid phase in shorter time, the extraction yield is also improved.
+
+%Similarities between Figures \ref{fig:Sensitivty_F_y}, \ref{fig:Sensitivty_P_y} and \ref{fig:Sensitivty_T_y} can observed, although the sources of disturbances are different.
 All the plots stay initially plat, and this is because the extraction kinetic is mainly controlled by the concentration gradient.

### 2024-05-12 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Sensitivity_Pressure.tex
12.05

@@
 
-	Figure \ref{fig:Sensitivty_P_CF} shows the sensitivity of the solute concentration in the fluid phase as a response to the pressure change.
-As explained above, an increase in pressure enhanced the mass transfer, resulting in concentration front moving through the system.
-Initially, the system response is low due to low response in the solid phase.
-\todo{TODO}
-	Following this, the formation of a trailing front characterized by decreasing sensitivities can be observed.
-This trailing front can be explained by the decrease in the concentration gradient as the solute is increasingly extracted and the available concentration within the solid phase diminishes.
-As seen in the figure, sensitivities are declining towards zero.
+	Figure \ref{fig:Sensitivty_P_CF} shows the sensitivity of the solute concentration in the fluid phase with respect to the pressure change.
+As explained above, an increase in pressure enhances the mass transfer, resulting in the concentration front moving through the system.
+The system response is initially low, reflecting the idle period discussed above.
+Later, the sensitivities increased due to enhanced mass transfer.
+As the fluid phase is mobile, the advection affects the sensitivities, which causes the sensitivities to move along the system analogously to the solute in the fluid phase.
+
+	After the growth phase, the sensitivities start to decrease, which can be explained by the decrease in the concentration gradient.
+As seen in Figure \ref{fig:Sensitivty_P_CF}, sensitivities decline towards zero.
 This asymptotic trend suggests the driving force for the mass transfer—the concentration gradient—has been minimized, and changes in pressure no longer significantly impact the solute concentration in the fluid phase.
@@
 
-	Figure \ref{fig:Sensitivty_P_y} illustrates the temporal evolution of the extraction yield's sensitivity to changes in pressure within a supercritical fluid extraction system.
+	Figure \ref{fig:Sensitivty_P_y} illustrates how sensitive the extraction yield is to pressure change.
+Initially, the sensitivity curve stays almost flat, suggesting a latency in the system's response to pressure changes.
+A minor decrease in sensitivity arises due to a decrease in the velocity of the fluid phase.
+As the fluid moves slower, it reaches the end of the extractor later, which causes negative sensitivities.
 
-	Initially, the curve displays an almost flat profile, suggesting a latency in the system's response to pressure changes.
-A minor initial decrease in sensitivity, indicated by a slight dip below zero, may arise due to a decrease in the velocity of the fluid phase.
-For a constant mass flow rate, an increase in fluid density due to heightened pressure results in a lower fluid velocity, potentially leading to this reduced sensitivity.
-
-	As the process continues, the curve ascends sharply, indicating a positive yield response to pressure.
-This increase in sensitivity can be associated with the enhanced solubility and mass transfer capabilities imparted by higher pressures, improving the rate at which solute is extracted into the fluid phase.
-The peak in dy/dP reflects the most responsive period of the system, where pressure changes are highly effective in improving yield.
+	As the process continues and the solute reaches the extractor's outlet, the sensitivity curve increases rapidly, indicating an improvement in the process efficiency.
+This increase in sensitivity can be associated with the enhanced solubility and mass transfer imparted by higher pressures.
+The peak in $\frac{dy}{dP}$ reflects when the deviation from the original system is the largest.
 
@@
 This descending curve represents a depletion phase: as the available solute in the solid phase diminishes, the potential for further increasing the yield through pressure alone is reduced.
-The remaining solute concentration becomes a limiting factor, and the mass transfer driving force, initially augmented by pressure, no longer plays a dominant role.
+The remaining concentration gradient becomes a limiting factor, and the enhanced mass transfer no longer plays a dominant role compared to the original system.
 

### 2024-05-14 SFE_article_Sensitivity_Analysis_short - Chamomile/Article_Sensitivity_Analsysis_short-Chamomile.tex
14.05

@@
 The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
-A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s.
+A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
 Sensitivity analyses play a crucial role in assessing the robustness of the findings or conclusions based on mathematical model.

### 2024-05-14 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Sensitivity_Pressure.tex
14.05

@@
 The Low Mach-number assumption leads to instant propagation of the thermodynamic pressure throughout the system.
-This assumption allows considering a single pressure value for the entire system, as all changes occur simultaneously within the machine.
+A single pressure value can be considered for the entire system, as all changes occur simultaneously throughout the machine.
 Figure \ref{fig:Sensitivty_P_P} illustrates a step function representing the pressure change.
@@
 In contrast, Neumann boundary conditions would dictate that the heat flux at the boundaries be held constant.
-In this work, the Neumann boundary conditions have been applied, which leads to a uniform response and ensures the temperatures at the inlet and in the middle of the extractor are the same.
+In this work, the Neumann boundary conditions have been applied, which leads to a uniform response and ensures that the temperatures at the inlet and in the middle of the extractor are the same.
 

### 2024-05-15 SFE_article_Sensitivity_Analysis_short - Chamomile/Article_Sensitivity_Analsysis_short-Chamomile.tex
15.05

@@
 
-The sensitivity analysis is a tool to understand the parametric dependence in the dynamic behaviour of the analysed system.
+Sensitivity analysis is a tool to understand the parametric dependence on the dynamic behaviour of the analysed system.
 The presented formulation involves derivative-based local sensitivity analysis of the model solution with respect to selected parameters and controls.
+The local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions unless the discussed system is a linear model.
 The sensitivity equations can be obtained in various ways, but the automatic differentiation technique was implemented to obtain the sensitivity equations in this work.
-By identifying which parameters are influential at each period of the simulation, local sensitivity analysis can bring valuable information about process modelling, design of experiments or model reduction.
-The local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions unless the discussed system is a linear model.
+Local sensitivity analysis can bring valuable information about process modelling, design of experiments or model reduction by identifying which parameters are influential and how these influence changes in time.
 
-In this study, the local sensitivity analysis method was introduced to explore the dynamics of the supercritical extraction system, which consists of a set of partial differential equations.
-The sensitivity analysis was used to evaluate the influence of pressure increase on the state-space consisting of the solutes concentration in solid and liquid phases, the fluid's enthalpy density, system pressure, and extraction yield.
-Every change in the control variables leads to a state-space change, eventually affecting the process performance.
+This study used sensitivity analysis to evaluate the influence of pressure increase on the state-space, which consisted of the concentration of the solute in solid and liquid phases, the fluid's enthalpy density, system pressure, and extraction yield.
+At given operating conditions ($35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s), the step change of pressure enhance the mass transfer, which leads to faster loss of solute from solid particles and consequently to negative sensitivities.
+An analogous response is visible in the fluid phase, where the concentration of solute increases and is visible as positive sensitivities.
+As more solute is transported to the fluid phase, the extraction yield is improved and characterised by positive sensitivities.
 
-At given operating conditions, the step change of pressure enhance the mass transfer, which leads to observation faster loss of solute by the solid particles and consequently to negative sensitivities.
-Analogous response is visible in the fluid phase, where the concentration of solute increase, which is visible as positive sensitivities.
-As more solute is transported to the fluid phase in shorter time, the extraction yield is also improved.
+This information can be utilised to identify which control variables influence the extraction yield the most.
+The controls with high sensitivities to the extraction can be used to investigate optimal operating conditions from an economic point of view.
 
@@
 It is important to note that the local-sensitivity methods obtain the discussed results, which can be obtained at different operating conditions.
-
-This information can be utilized to identify which control variables influence the extraction yield the most.
-The controls with high sensitivities on the extraction can be used to investigate to find optimal operating conditions from an economic point of view.
 

### 2024-05-15 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Sensitivity_Pressure.tex
14.05
15.05

@@
 The Low Mach-number assumption leads to instant propagation of the thermodynamic pressure throughout the system.
-A single pressure value can be considered for the entire system, as all changes occur simultaneously throughout the machine.
+A single pressure value can be considered for the entire system, as all changes occur simultaneously throughout the device.
 Figure \ref{fig:Sensitivty_P_P} illustrates a step function representing the pressure change.
@@
 
+	\todo{caption and label}
+
 	According to Equation \ref{EQ:Enthalpy_equation}, the pressure change directly affects the quantity $h \times \rho$ through $\frac{\partial (P(t) A_f)}{\partial t}$, leading to the step change along the whole system, as presented in Figure \ref{fig:Sensitivty_P_H}.
@@
 
-	The pressure change influences the temperature of the fluid in the middle of the computational domain, but the values on boundaries can be defined in multiple ways.
-Applying the Dirichlet boundary conditions assumes a fixed temperature value at the inlet, which leads to a possible thermal gradient propagating along the system.
-In contrast, Neumann boundary conditions would dictate that the heat flux at the boundaries be held constant.
-In this work, the Neumann boundary conditions have been applied, which leads to a uniform response and ensures that the temperatures at the inlet and in the middle of the extractor are the same.
+	The pressure change affects the fluid's temperature inside the computational domain, but boundary conditions define the values on boundaries.
+Applying the Dirichlet boundary conditions assumes a fixed temperature value at the inlet, which can lead to a thermal gradient propagating along the system.
+In contrast, Neumann boundary conditions would dictate the heat flux at the boundaries.
+In this work, the Neumann boundary conditions equal to zero have been applied, which leads to a uniform response and ensures that the temperatures at the inlet, the outlet, and the middle of the extractor are the same.
 
@@
 
-	Figure \ref{fig:Sensitivty_P_CS} shows the sensitivity of the solute concentration in the solid phase with respect to changes in pressure throughout a fixed bed in a supercritical fluid extraction process.
-As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely related to its density, which suggests that with higher fluid density, the velocity decreases.
+	Figure \ref{fig:Sensitivty_P_CS} shows the sensitivity of the solute concentration in the solid phase with respect to pressure change along a fixed bed in a supercritical fluid extraction process.
+As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, which suggests that with higher fluid density, the velocity decreases.
 This leads to an extended residence time, ergo, a longer interaction between the solute and the solvent.
-
 Initially, the extraction process is in the kinetically-controlled regime, where the concentration gradient is high, and the limiting factor is the solute solubility.
-As explained in ({\color{red}article 1}), the system is considered to be far from the saturation, which can explain low system response at the beginning of the process.
-
-	When the concentration gradient diminishes, and the extraction moves from the kinetic-controlled to the diffusion-controlled regime, the system response becomes more profound.
-({\color{red}article 1}) obtained a linear correlation for $D_i^R$, which is incorporated in this model.
-$D_i^R$ increases together with fluid density, which explains negative sensitivities.
-The negative sign can be interpreted as a faster loss of a solute from a solid phase, which corresponds to enhanced mass transfer.
-
-	Over time, the amount of solute becomes a limiting factor and the pressure change has a lower effect on the system and the sensitivities increase.
-Eventually, sensitivities asymptotically approach zero.
-The solute concentration in the solid phase has been reduced, and further changes in pressure do not influence the remaining concentration.
-This behaviour reflects that in the later extraction phase, the kinetics of extraction are controlled by the internal diffusion of the solute from solid particles rather than the conditions of the supercritical fluid.
+As discussed in ({\color{red}article 1}), the system is considered to be far from saturation, which can explain the low system response at the beginning of the process.
+The system response becomes more evident when the concentration gradient diminishes, and the extraction moves from the kinetic-controlled to the diffusion-controlled regime.
+The negative sign can be interpreted as a faster loss of a solute from the solid phase, which corresponds to enhanced mass transfer.
+Over time, the amount of solute becomes a limiting factor, and the pressure change has a lower effect on the system, increasing the negative sensitivities.
+Eventually, sensitivities approach zero asymptotically.
+The solute concentration in the solid phase has been reduced, and further changes in pressure have a low influence on the state space.
 
@@
 	Figure \ref{fig:Sensitivty_P_CF} shows the sensitivity of the solute concentration in the fluid phase with respect to the pressure change.
-As explained above, an increase in pressure enhances the mass transfer, resulting in the concentration front moving through the system.
+As analysed above, an increase in pressure enhances the mass transfer, resulting in the concentration front moving through the system.
 The system response is initially low, reflecting the idle period discussed above.
-Later, the sensitivities increased due to enhanced mass transfer.
+Later, the sensitivities start to increase due to faster solute loss from the solid phase, which indicates that more solute is transported to the fluid phase.
+When the amount of solute in the solid phase becomes a limiting factor, the extraction rate slows down, sensitivities decline asymptotic towards zero, and the impact of the pressure change gradually decreases.
 As the fluid phase is mobile, the advection affects the sensitivities, which causes the sensitivities to move along the system analogously to the solute in the fluid phase.
-
-	After the growth phase, the sensitivities start to decrease, which can be explained by the decrease in the concentration gradient.
-As seen in Figure \ref{fig:Sensitivty_P_CF}, sensitivities decline towards zero.
-This asymptotic trend suggests the driving force for the mass transfer—the concentration gradient—has been minimized, and changes in pressure no longer significantly impact the solute concentration in the fluid phase.
 
@@
 
-	Figure \ref{fig:Sensitivty_P_y} illustrates how sensitive the extraction yield is to pressure change.
+	Figure \ref{fig:Sensitivty_P_y} illustrates how sensitive the extraction yield is to the pressure change.
 Initially, the sensitivity curve stays almost flat, suggesting a latency in the system's response to pressure changes.
-A minor decrease in sensitivity arises due to a decrease in the velocity of the fluid phase.
-As the fluid moves slower, it reaches the end of the extractor later, which causes negative sensitivities.
-
-	As the process continues and the solute reaches the extractor's outlet, the sensitivity curve increases rapidly, indicating an improvement in the process efficiency.
-This increase in sensitivity can be associated with the enhanced solubility and mass transfer imparted by higher pressures.
+Due to the decreased velocity of the fluid, the solute reaches the extractor's outlet later, which causes minor negative sensitivities to appear.
+The process continues, and the sensitivity curve increases rapidly when the solute reaches the extractor's outlet.
+The positive yield sensitivity indicates an improvement in the process efficiency, which is directly related to enhanced mass transfer.
 The peak in $\frac{dy}{dP}$ reflects when the deviation from the original system is the largest.
-
-	Beyond the peak, the sensitivity declines, converging towards zero.
-This descending curve represents a depletion phase: as the available solute in the solid phase diminishes, the potential for further increasing the yield through pressure alone is reduced.
-The remaining concentration gradient becomes a limiting factor, and the enhanced mass transfer no longer plays a dominant role compared to the original system.
+Beyond the peak, the sensitivity declines and converges towards zero.
+The concentration gradient becomes a limiting factor, and the enhanced mass transfer no longer plays a dominant role compared to the original system.
 

### 2024-05-19 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Model.tex
14.05
19.05

@@
 			%\iffalse
-			\subsubsection{Heat balance} \label{CH: heat_balance}
 
@@
 If this energy is not added, the substance cools down when it is expanded.
+			\end{comment}
 
@@
 As explained in Chapters \ref{CH:Governing_equations_chapter}, at Low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound.
-Under such conditions, the term $\partial {\color{black}P}/\partial t$ can be approximated by an ordinary differential equation, which describes the instantaneous change of pressure in the system.
-The pressure (P) in the system is considered a state variable, while the pressure in the new time-step ($P_{in}$) is considered a control variable.
+Under such conditions, the term $\partial P/\partial t$ can be approximated by an difference equation, which describes the change of pressure in the whole system.
+The pressure ($P$) in the system is considered a state variable, while the pressure in the new time-step ($P_{in}$) is considered a control variable.
 
@@
 				\begin{equation}
-					\frac{\partial {\color{black}P}(t)}{\partial t} \approx \frac{{\color{black}P}(t) - {\color{black}P_{in}}(t) }{\Delta t}
+					\frac{\partial {\color{black}P}(t)}{\partial t} \approx \frac{{\color{black}P_{in}}(t) - {\color{black}P}(t) }{\Delta t}
 			\end{equation}}
@@
 
-			\end{comment}
+			\subsubsection{Heat balance} \label{CH: heat_balance}
+
 			The heat balance equation describe the evolution of the internal energy in the system and it is given by Equation \ref{EQ:Enthalpy_equation}
@@
 					&c_f(t,   z=0) = 0  && h(t, z=0) = h_{in}(t)  && \frac{\partial c_f(t,z=L)}{\partial x} = 0 \\
-					&\frac{\partial h(t,z=L)}{\partial x} = 0   && c_s(t, z=\{0,L\}) = 0 && y(0) = 0
+					&\frac{\partial h(t,z=L)}{\partial x} = 0   && c_s(t, z=\{0,L\}) = 0 && y(0) = 0 \quad P(0) = P_0 \\
 			\end{align*} }
-
-			\todo{P is missing}
 

### 2024-05-19 SFE_article_Sensitivity_Analysis_short - Chamomile/Sections/Sensitivity_Pressure.tex
19.05

@@
 A single pressure value can be considered for the entire system, as all changes occur simultaneously throughout the device.
-Figure \ref{fig:Sensitivty_P_P} illustrates a step function representing the pressure change.
+A step-function shown on Figure \ref{fig:Sensitivty_P_P} illustrates the pressure change.
 
@@
 
-	The pressure change affects the fluid's temperature inside the computational domain, but boundary conditions define the values on boundaries.
+	The pressure change affects the fluid's temperature inside the computational domain, but boundary values are subject to constraints specified at the extremes of that domain.
 Applying the Dirichlet boundary conditions assumes a fixed temperature value at the inlet, which can lead to a thermal gradient propagating along the system.
